### 2025-01-24 reports/capstone-movielens-report.Rmd
Capstone-MovieLens project added.

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2025-01-27 reports/capstone-movielens-report.Rmd
Report updated!

@@
 output:
-  pdf_document: default
   html_document: 
+    fig_caption: true
+  pdf_document: 
     df_print: paged
+    toc: true
+    fig_caption: true
+    keep_tex: true
 ---
@@
 
-## R Markdown
+## Introduction / Overview / Executive Summary
 
@@
 
-## Including Plots
+## Methods / Analysis
 
@@
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+
+## Conclusion
+
+Hello Conclusion!
+
+This is a great conclusion, isn't is?!!

### 2025-01-29 reports/capstone-movielens-report.Rmd
Rmd Report updated.

@@
 date: "`r Sys.Date()`"
+#bibliography: [references.bib]
+#link-citations: true
 output:
@@
     keep_tex: true
+vignette: >
+  %\VignetteIndexEntry{RMarkdown Citations - Alphabetic Style}
+  %\VignetteEngine{knitr::knitr}
+  %\VignetteEncoding{UTF-8}
 ---
 
-```{r setup, include=FALSE}
+```{r setup, include=TRUE}
+library(RefManageR)
+bib <- ReadBib(system.file("Bib", "references.bib", 
+                           package = "RefManageR"), check = FALSE)
+BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
+Following the^[[Netflix Awards Prize Challenge](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/)] requirements, we will evaluate the RMSE score^[Rafael A.
+Irizarry: Introduction to Data Science, Part II, Section 23.2: Loss function]:
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+Our goal is to achieve a value of less than 0.86490 (vs the Netflix Challenge requirement: of at least 0.8563^[R: A Language and Environment for Statistical Computing, Section 33.6.1 Matrix Factorization, @R-base]).
 
@@
 This is a great conclusion, isn't is?!!
+
+## Refs
+
+[Rafael A. Irizarry. Introduction to Data Science, Part II](https://rafalab.dfci.harvard.edu/dsbook-part-2/)
+
+1.23.2 [Section 23.2: Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function)
+
+[Töscher, A., Jahrer, M., & Bell, R. M. (2009). The BigChaos Solution to the Netflix Grand Prize](https://www.asc.ohio-state.edu/statistics/statgen/joul_aut2009/BigChaos.pdf)

### 2025-01-29 reports/capstone-movielens-report.Rmd
Rmd report updated.

@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the^[[Netflix Awards Prize Challenge](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/)] requirements, we will evaluate the RMSE score^[Rafael A.
-Irizarry: Introduction to Data Science, Part II, Section 23.2: Loss function]:
+Following the `Netflix Grand Prize Challenge` requirements`r AutoCite(bib, "NYT1MNP")`, we will evaluate the RMSE score`r AutoCite(bib, "IDS2_23-2")`:
 
-Our goal is to achieve a value of less than 0.86490 (vs the Netflix Challenge requirement: of at least 0.8563^[R: A Language and Environment for Statistical Computing, Section 33.6.1 Matrix Factorization, @R-base]).
+Our goal is to achieve a value of less than 0.86490 (vs the Netflix Challenge requirement: of at least 0.8563`r AutoCite(bib, "BigChaosSln")`).
 
@@
 [Töscher, A., Jahrer, M., & Bell, R. M. (2009). The BigChaos Solution to the Netflix Grand Prize](https://www.asc.ohio-state.edu/statistics/statgen/joul_aut2009/BigChaos.pdf)
+
+[[Netflix Awards Prize Challenge](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/)]

### 2025-01-29 reports/rmd-report-template.Rmd
Rmd report updated / template added.
Rmd report template fixed.

--- 2025-01-24 reports/capstone-movielens-report.Rmd
@@
 ---
-title: "Capstone Movielens Report"
-author: "Azamat Kurbanaev"
+title: "RMD Report Template"
+author: "John Doe"
 date: "`r Sys.Date()`"
 output:
-  pdf_document: default
   html_document: 
+    fig_caption: true
+  pdf_document: 
     df_print: paged
+    toc: true
+    fig_caption: true
+    keep_tex: true
 ---

### 2025-01-30 reports/capstone-movielens-report.Rmd
Bib-files organized.

@@
 library(RefManageR)
-bib <- ReadBib(system.file("Bib", "references.bib", 
+bib <- ReadBib(system.file("Bib", "biblatexExamples.bib", 
                            package = "RefManageR"), check = FALSE)

### 2025-01-31 reports/capstone-movielens-report.Rmd
First draft version of citing and bibliography implementation.

--- 2025-01-29 reports/capstone-movielens-report.Rmd
@@
 date: "`r Sys.Date()`"
-#bibliography: [references.bib]
-#link-citations: true
+#bibliography: references.bib
+#csl: bit-numerical-mathematics.csl 
 output:
-  html_document: 
-    fig_caption: true
   pdf_document: 
@@
     keep_tex: true
+    citation_package: biblatex
+
+  html_document: 
+    fig_caption: true
+# hyperrefoptions:
+#   - backref
+colorlinks: true
+linkcolor: red
+citecolor: blue
+header-includes:
+    - \usepackage{hyperref}
 vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Alphabetic Style}
+  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
+  %\VignetteEncoding{UTF-8}
   %\VignetteEngine{knitr::knitr}
-  %\VignetteEncoding{UTF-8}
 ---
 
-```{r setup, include=TRUE}
+```{r setup, include=TRUE, echo = FALSE}
 library(RefManageR)
-bib <- ReadBib(system.file("Bib", "references.bib", 
-                           package = "RefManageR"), check = FALSE)
-BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
+bib <- ReadBib("references.bib", check = FALSE)
+BibOptions(check.entries = FALSE,
+           hyperlink = "to.bib",
+           bib.style = "numeric", 
+           style = "markdown", 
+           cite.style = 'numeric')
+
+citeB <- function(citeKey){
+  Cite(bib, citeKey, .opts = list(super = FALSE))
+}
+
 knitr::opts_chunk$set(echo = TRUE)
+
+# \usepackage[utf8]{inputenc}
+# \usepackage[english]{babel}
+# \usepackage{biblatex}
+
 ```
@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the `Netflix Grand Prize Challenge` requirements`r AutoCite(bib, "NYT1MNP")`, we will evaluate the RMSE score`r AutoCite(bib, "IDS2_23-2")`:
+Following the _Netflix Grand Prize Contest_`r # \cite{knuthwebsite}` `r citeB("NYT1MNP")`  requirements, we will evaluate the RMSE score defined as`r citeB("IDS2_23-2")`:
 
-Our goal is to achieve a value of less than 0.86490 (vs the Netflix Challenge requirement: of at least 0.8563`r AutoCite(bib, "BigChaosSln")`).
+$$
+\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
+$$
+
+with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations.
+
+Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563`r citeB("BigChaosSln")`).
+
+### Dataset
 
@@
 
-## Refs
+**References**
 
-[Rafael A. Irizarry. Introduction to Data Science, Part II](https://rafalab.dfci.harvard.edu/dsbook-part-2/)
+```{r results = "asis", echo = FALSE}
+# \addcontentsline{toc}{section}{References} 
+#\printbibliography[title={Whole bibliography}]
+# 
+# \color{black}
+# \bibliography{references}
+# \bibliographystyle{mla-good}
+#\bibliographystyle{mla-good}
+#\bibliographystyle{is-unsrt}
+#\bibliographystyle{is-plain}
+#\bibliographystyle{is-abbrv}
+#\bibliographystyle{apalike}
 
-1.23.2 [Section 23.2: Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function)
+PrintBibliography(bib,
+                  .opts = list(check.entries = FALSE,
+                               hyperlink = "to.bib",
+                               first.inits = FALSE,
+                               bib.style = "numeric",
+                               style = "markdown",
+                               cite.style = 'numeric'))
 
-[Töscher, A., Jahrer, M., & Bell, R. M. (2009). The BigChaos Solution to the Netflix Grand Prize](https://www.asc.ohio-state.edu/statistics/statgen/joul_aut2009/BigChaos.pdf)
-
-[[Netflix Awards Prize Challenge](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/)]
+```

### 2025-02-01 reports/capstone-movielens-report.Rmd
Devepment in progress.

@@
     citation_package: biblatex
-
   html_document: 
@@
     - \usepackage{hyperref}
+    - \hypersetup{backref,
+          pdfpagemode=FullScreen,
+          colorlinks=true,
+          implicit=false}
+    #- \hyper@nopatch@bib = null
 vignette: >
@@
 bib <- ReadBib("references.bib", check = FALSE)
+
 BibOptions(check.entries = FALSE,
@@
 
+bibFound <- SearchBib(bib)
+
 citeB <- function(citeKey){
-  Cite(bib, citeKey, .opts = list(super = FALSE))
+  Cite(bibFound[citeKey], .opts = list(super = FALSE))
 }
@@
 
-PrintBibliography(bib,
+PrintBibliography(bibFound,
                   .opts = list(check.entries = FALSE,

### 2025-02-02 reports/capstone-movielens-report.Rmd
Citing using `citr` add-ins in R Studio.

@@
 date: "`r Sys.Date()`"
-#bibliography: references.bib
+bibliography: references.bib
 #csl: bit-numerical-mathematics.csl 
@@
     - \usepackage{hyperref}
+    - \usepackage[ natbib=true, style=numeric,sorting=none]{biblatex}
     - \hypersetup{backref,
@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the _Netflix Grand Prize Contest_`r # \cite{knuthwebsite}` `r citeB("NYT1MNP")`  requirements, we will evaluate the RMSE score defined as`r citeB("IDS2_23-2")`:
+Following the _Netflix Grand Prize Contest_[@NYT1MNP] requirements, we will evaluate the RMSE score defined as[@IDS2_23-2]:
 
@@
 
-Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563`r citeB("BigChaosSln")`).
+Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).
 
@@
 
-This is a great conclusion, isn't is?!!
-
-**References**
-
-```{r results = "asis", echo = FALSE}
-# \addcontentsline{toc}{section}{References} 
-#\printbibliography[title={Whole bibliography}]
-# 
-# \color{black}
-# \bibliography{references}
-# \bibliographystyle{mla-good}
-#\bibliographystyle{mla-good}
-#\bibliographystyle{is-unsrt}
-#\bibliographystyle{is-plain}
-#\bibliographystyle{is-abbrv}
-#\bibliographystyle{apalike}
-
-PrintBibliography(bibFound,
-                  .opts = list(check.entries = FALSE,
-                               hyperlink = "to.bib",
-                               first.inits = FALSE,
-                               bib.style = "numeric",
-                               style = "markdown",
-                               cite.style = 'numeric'))
-
-```
+This is a great conclusion, isn't it?!!

### 2025-02-02 reports/capstone-movielens-report.Rmd
Alternative citing experiment.

--- 2025-01-31 reports/capstone-movielens-report.Rmd
@@
     keep_tex: true
-    citation_package: biblatex
+    #citation_package: biblatex
 
@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the _Netflix Grand Prize Contest_`r # \cite{knuthwebsite}` `r citeB("NYT1MNP")`  requirements, we will evaluate the RMSE score defined as`r citeB("IDS2_23-2")`:
+Following the _Netflix Grand Prize Contest_ \cite{NYT1MNP} `r #\cite{knuthwebsite}` `r #citeB("NYT1MNP")`  requirements, we will evaluate the RMSE score defined as`r citeB("IDS2_23-2")`:
 
@@
 
+\addcontentsline{toc}{section}{References}
+ \color{black}
+\bibliography{references}
+\bibliographystyle{mla-good}
+
 ```{r results = "asis", echo = FALSE}
 # \addcontentsline{toc}{section}{References}
-#\printbibliography[title={Whole bibliography}]
+# \printbibliography[title={Whole bibliography}]
 # 
@@
 # \bibliography{references}
-# \bibliographystyle{mla-good}
 #\bibliographystyle{mla-good}
@@
 
-PrintBibliography(bib,
-                  .opts = list(check.entries = FALSE,
-                               hyperlink = "to.bib",
-                               first.inits = FALSE,
-                               bib.style = "numeric",
-                               style = "markdown",
-                               cite.style = 'numeric'))
+# PrintBibliography(bib,
+#                   .opts = list(check.entries = FALSE,
+#                                hyperlink = "to.bib",
+#                                first.inits = FALSE,
+#                                bib.style = "numeric",
+#                                style = "markdown",
+#                                cite.style = 'numeric'))
 

### 2025-02-02 reports/capstone-movielens-report.Rmd
Backref citation sample1

@@
     fig_caption: true
-# hyperrefoptions:
-#   - backref
+hyperrefoptions:
+  - backref
 colorlinks: true

### 2025-02-03 reports/capstone-movielens-report.Rmd
Backref citation sample 2

@@
 date: "`r Sys.Date()`"
-#bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
 output:
@@
     keep_tex: true
-    #citation_package: biblatex
 
@@
 
-**References**
-
-\addcontentsline{toc}{section}{References}
- \color{black}
+\addcontentsline{toc}{section}{Whole References}
 \bibliography{references}

### 2025-02-03 reports/capstone-movielens-report.Rmd
Backref support in biblatex

@@
 date: "`r Sys.Date()`"
+bibliography: references.bib
+#csl: bit-numerical-mathematics.csl 
 output:
@@
     keep_tex: true
-
+    citation_package: biblatex
   html_document: 
     fig_caption: true
-hyperrefoptions:
-  - backref
+# hyperrefoptions:
+#   - backref
 colorlinks: true
@@
     - \usepackage{hyperref}
+    - \usepackage[natbib=true, 
+                  style=numeric, 
+                  backref=true, 
+                  sorting=none]{biblatex}
+    - \hypersetup{backref,
+          pdfpagemode=FullScreen,
+          colorlinks=true,
+          implicit=false}
+    #- \hyper@nopatch@bib = null
 vignette: >
@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the _Netflix Grand Prize Contest_ \cite{NYT1MNP} `r #\cite{knuthwebsite}` `r #citeB("NYT1MNP")`  requirements, we will evaluate the RMSE score defined as`r citeB("IDS2_23-2")`:
+Following the _Netflix Grand Prize Contest_[@NYT1MNP] requirements, we will evaluate the RMSE score defined as[@IDS2_23-2]:
 
@@
 
-This is a great conclusion, isn't is?!!
-
-\addcontentsline{toc}{section}{Whole References}
-\bibliography{references}
-\bibliographystyle{mla-good}
-
-```{r results = "asis", echo = FALSE}
-# \addcontentsline{toc}{section}{References}
-# \printbibliography[title={Whole bibliography}]
-# 
-# \color{black}
-# \bibliography{references}
-#\bibliographystyle{mla-good}
-#\bibliographystyle{is-unsrt}
-#\bibliographystyle{is-plain}
-#\bibliographystyle{is-abbrv}
-#\bibliographystyle{apalike}
-
-# PrintBibliography(bib,
-#                   .opts = list(check.entries = FALSE,
-#                                hyperlink = "to.bib",
-#                                first.inits = FALSE,
-#                                bib.style = "numeric",
-#                                style = "markdown",
-#                                cite.style = 'numeric'))
-
-```
+This is a great conclusion, isn't it?!!

### 2025-02-03 reports/capstone-movielens-report.Rmd
Code cleaned up.

@@
     fig_caption: true
-# hyperrefoptions:
-#   - backref
 colorlinks: true
@@
           implicit=false}
-    #- \hyper@nopatch@bib = null
 vignette: >
@@
 ```{r setup, include=TRUE, echo = FALSE}
-library(RefManageR)
-bib <- ReadBib("references.bib", check = FALSE)
-
-BibOptions(check.entries = FALSE,
-           hyperlink = "to.bib",
-           bib.style = "numeric", 
-           style = "markdown", 
-           cite.style = 'numeric')
-
-bibFound <- SearchBib(bib)
-
-citeB <- function(citeKey){
-  Cite(bibFound[citeKey], .opts = list(super = FALSE))
-}
 
 knitr::opts_chunk$set(echo = TRUE)
-
-# \usepackage[utf8]{inputenc}
-# \usepackage[english]{babel}
-# \usepackage{biblatex}
-
 ```

### 2025-02-03 reports/capstone-movielens-report.pdf-template.Rmd
PDF template added for Capstone MovieLens report.

--- 2025-02-03 reports/capstone-movielens-report.Rmd
@@
     citation_package: biblatex
-  html_document: 
-    fig_caption: true
+  # html_document: 
+  #   fig_caption: true
 colorlinks: true
@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the _Netflix Grand Prize Contest_[@NYT1MNP] requirements, we will evaluate the RMSE score defined as[@IDS2_23-2]:
+Following the _Netflix Grand Prize Contest_[@NYT1MNP] requirements, we will evaluate the RMSE score defined as:
 
@@
 
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations.
+with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
 

### 2025-02-03 reports/capstone-movielens-report.html-template.Rmd
HTML template added for Capstone MovieLens report.

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
output:
  html_document: 
    fig_caption: true
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Alphabetic Style}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=TRUE, echo = FALSE}
library(RefManageR)
bib <- ReadBib("references.bib", check = FALSE)
BibOptions(check.entries = FALSE, style = "markdown", bib.style = "numeric", cite.style = 'numeric')

citeB <- function(citeKey){
  AutoCite(bib, citeKey, .opts = list(hyperlink = "to.bib", super = FALSE))
}

knitr::opts_chunk$set(echo = TRUE)
```

## Introduction / Overview / Executive Summary

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the RMSE score defined as:

$$
\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
$$

with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations`r citeB("IDS2_23-2")`.

Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563`r citeB("BigChaosSln")`).

### Dataset

```{r cars}
summary(cars)
```

## Methods / Analysis

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Conclusion

Hello Conclusion!

This is a great conclusion, isn't is?!!

**References**

```{r results = "asis", echo = FALSE}
PrintBibliography(bib, .opts = list(check.entries = FALSE))
```

### 2025-02-03 reports/capstone-movielens-report.Rmd
Fix for Rmd report.

@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the _Netflix Grand Prize Contest_[@NYT1MNP] requirements, we will evaluate the RMSE score defined as[@IDS2_23-2]:
+Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the RMSE score defined as:
 

### 2025-02-03 reports/capstone-movielens-report.pdf-template.Rmd
Fix for Rmd report.

@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the _Netflix Grand Prize Contest_[@NYT1MNP] requirements, we will evaluate the RMSE score defined as:
+Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the RMSE score defined as:
 

### 2025-02-03 reports/capstone-movielens-report.pdf-template.Rmd
Fix for Rmd reports.

@@
     citation_package: biblatex
-  # html_document: 
-  #   fig_caption: true
 colorlinks: true
@@
     - \hypersetup{backref,
-          pdfpagemode=FullScreen,
+          pdfpagemode=Normal,
           colorlinks=true,

### 2025-02-04 reports/capstone-movielens-report.Rmd
`Datasets` section added to the report

@@
     citation_package: biblatex
-  html_document: 
-    fig_caption: true
 colorlinks: true
@@
 
-### Dataset
+### Datasets
+
+To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
+
+* **edx:** we use it to develop and train our algorithms;
+* **final_holdout_test:** According to the course instructions, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
 

### 2025-02-06 reports/capstone-movielens-report.pdf-template.Rmd
Rmd Report: Datasets description started.

@@
 
-### Dataset
+### Datasets
+
+``` {r , echo = FALSE}
+# install.packages("pak")
+pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
+
+```
+
+To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
+
+* **edx:** we use it to develop and train our algorithms;
+* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
 

### 2025-02-06 reports/capstone-movielens-report.Rmd

@@
 ```{r setup, include=TRUE, echo = FALSE}
-
+if(!require(pak)) install.packages("pak")
 knitr::opts_chunk$set(echo = TRUE)
@@
 
+``` {r , echo = FALSE}
+```
+
 To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
@@
 * **edx:** we use it to develop and train our algorithms;
-* **final_holdout_test:** According to the course instructions, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
+* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
 
-```{r cars}
-summary(cars)
+For this purpose the following package has been developed by the author: `edx.capstone.movielens.data`.
+The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
+
+Let us install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
+```{r }
+if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
+
+library(edx.capstone.movielens.data)
+edx <- edx.capstone.movielens.data::edx
+final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
+
+summary(edx)
+summary(final_holdout_test)
 ```
 
+``` {r edx, echo = FALSE}
+```
 ## Methods / Analysis

### 2025-02-07 reports/capstone-movielens-report.Rmd
Report: `edx` dataset analisys updated.

@@
 ```{r setup, include=TRUE, echo = FALSE}
+library(dplyr)
+library(stringr)
+library(caret)
+
 if(!require(pak)) install.packages("pak")
@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the RMSE score defined as:
+Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score defined as:
 
@@
 
-``` {r edx, echo = FALSE}
+Let us look into the details of the `edx` dataset:
+``` {r echo = TRUE}
+str(edx)
 ```
+Note that we have 9000055 rows and six columns in there:  
+```{r }
+dim(edx)
+```
+
+Also, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
+```{r }
+#library(dplyr)
+s <- edx |> group_by(rating) |>
+  summarise(n = n())
+print(s)
+```
+
+Next, we have 10677 different movies 
+```{r}
+n_distinct(edx$movieId)
+```
+and 69878 different users in the dataset:
+```{r}
+n_distinct(edx$userId)
+```
+
+The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
+```{r}
+#library(stringr)
+genres = c("Drama", "Comedy", "Thriller", "Romance")
+sapply(genres, function(g) {
+  sum(str_detect(edx$genres, g))
+})
+```
+
+Further, we can find out the movies that have the greatest number of ratings using the following code:
+```{r}
+ordered_movie_ratings <- edx |> group_by(movieId, title) |>
+  summarize(number_of_ratings = n()) |>
+  arrange(desc(number_of_ratings))
+print(head(ordered_movie_ratings))
+```
+
+and figure out the most given ratings in order from most to least:
+```{r}
+ratings <- edx |>  group_by(rating) |>
+     summarise(count = n()) |>
+     arrange(desc(count))
+print(ratings)
+```
+
+Finally, the following code:
+```{r}
+print(edx |> group_by(rating) |> summarize(count = n()))
+```
+
+allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.)
+
+We can visually see that from the following plot:
+```{r}
+edx |>
+  group_by(rating) |>
+  summarize(count = n()) |>
+  ggplot(aes(x = rating, y = count)) +
+  geom_line()
+
+```
+
+```{r}
+
+```
+
 ## Methods / Analysis

### 2025-02-07 reports/capstone-movielens-report.Rmd
Report: `edx` dataset analisys updated (additional data visualization code added).

@@
 ```{r setup, include=TRUE, echo = FALSE}
+# if(!require(tidyverse)) 
+#   install.packages("tidyverse", repos = "http://cran.us.r-project.org")
+# if(!require(caret)) 
+#   install.packages("caret", repos = "http://cran.us.r-project.org")
+# if(!require(data.table)) 
+#   install.packages("data.table", repos = "http://cran.us.r-project.org")
+if(!require(pak)) 
+  install.packages("pak")
+
+# Loading the required libraries
+library(caret)
+library(cowplot)
+library(data.table)
 library(dplyr)
+library(ggplot2)
+library(ggthemes)
+library(lubridate)
+library(Metrics)
+library(recosystem)
+library(scales)
 library(stringr)
-library(caret)
+library(tibble)
+library(tidyr)
+library(pak)
 
-if(!require(pak)) install.packages("pak")
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-For this purpose the following package has been developed by the author: `edx.capstone.movielens.data`.
+For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
 The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
@@
 
-Finally, the following code:
+The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
 ```{r}
@@
 ```
-
-allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.)
 
@@
 
+Further analysis of the `edx` dataset was inspired by the article: A Movie Recommender System Using R - BEST[@MRS-R-BEST], from which the code and explanatory notes below were cited.
+
+#### Rating distribution plot[@MRS-R-BEST]
+\
+The code below demonstrates another way of visualizing the rating distribution:
+```{r}
+edx |>
+  group_by(rating) |>
+  summarize(count = n()) |>
+  ggplot(aes(x = rating, y = count)) +
+  geom_bar(stat = "identity", fill = "#8888ff") +
+  ggtitle("Rating Distribution") +
+  xlab("Rating") +
+  ylab("Occurrences Count") +
+  scale_y_continuous(labels = comma) +
+  scale_x_continuous(n.breaks = 10) +
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+
+```
+
+This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
+The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
+That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
+
+#### Yearly rating count[@MRS-R-BEST]
+\
+```{r}
+print(edx |> 
+  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
+  group_by(year) |>
+  summarize(count = n())
+)
+```
+
+#### Average rating per year plot[@MRS-R-BEST]
+\
+```{r}
+edx |> 
+  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
+  group_by(year) |>
+  summarize(avg = mean(rating)) |>
+  ggplot(aes(x = year, y = avg)) +
+  geom_bar(stat = "identity", fill = "#8888ff") + 
+  ggtitle("Average rating per year") +
+  xlab("Year") +
+  ylab("Average rating") +
+  scale_y_continuous(labels = comma) + 
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+```
+
+#### Movie popularity count[@MRS-R-BEST]
+\
+```{r}
+print(edx |> 
+  group_by(movieId) |> 
+  summarize(count = n()) |>
+  slice_head(n = 10)
+)
+```
+
+```{r}
+summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
+```
+
+#### Ratings per movie plot[@MRS-R-BEST]
+\
+```{r}
+edx |>
+  group_by(movieId) |>
+  summarize(count = n()) |>
+  ggplot(aes(x = movieId, y = count)) +
+  geom_point(alpha = 0.2, color = "#4020dd") +
+  geom_smooth(color = "red") +
+  ggtitle("Ratings per movie") +
+  xlab("Movies") +
+  ylab("Number of ratings") +
+  scale_y_continuous(labels = comma) +
+  scale_x_continuous(n.breaks = 10) +
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+```
+
+#### Movies' rating histogram[@MRS-R-BEST]
+\
+```{r}
+edx |>
+  group_by(movieId) |>
+  summarize(count = n()) |>
+  ggplot(aes(x = count)) +
+  geom_histogram(fill = "#8888ff", color = "#4020dd") +
+  ggtitle("Movies' rating histogram") +
+  xlab("Rating count") +
+  ylab("Number of movies") +
+  scale_y_continuous(labels = comma) +
+  scale_x_log10(n.breaks = 10) +
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+```
+
+#### Ratings per user[@MRS-R-BEST]
+
+##### User rating count (activity measure)
+\
+```{r}
+print(edx |> 
+  group_by(userId) |> 
+  summarize(count = n()) |>
+  slice_head(n = 10)
+)
+```
+
+##### User rating summary
+\
+```{r}
+summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
+```
+
+##### Ratings per user plot
+\
+```{r}
+edx |>
+  group_by(userId) |>
+  summarize(count = n()) |>
+  ggplot(aes(x = userId, y = count)) +
+  geom_point(alpha = 0.2, color = "#4020dd") +
+  geom_smooth(color = "red") +
+  ggtitle("Ratings per user") +
+  xlab("Users") +
+  ylab("Number of ratings") +
+  scale_y_continuous(labels = comma) +
+  scale_x_continuous(n.breaks = 10) +
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+```
+
+##### Users' rating histogram
+\
+```{r}
+edx |>
+  group_by(userId) |>
+  summarize(count = n()) |>
+  ggplot(aes(x = count)) +
+  geom_histogram(fill = "#8888ff", color = "#4020dd") +
+  ggtitle("Users' rating histogram") +
+  xlab("Rating count") +
+  ylab("Number of users") +
+  scale_y_continuous(labels = comma) +
+  scale_x_log10(n.breaks = 10) +
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+```
+
+##### 
+\
+```{r}
+
+```
+
+##### 
+\
+```{r}
+
+```
+
+##### 
+\
+```{r}
+
+```
+
+##### 
+\
+```{r}
+
+```
+
+```{r}
+
+```
+
+```{r}
+
+```
+
+```{r}
+
+```
+
+```{r}
+
+```
+
+```{r}
+
+```
+
+```{r}
+
+```
+
+#### [@MRS-R-BEST]
+\
 ```{r}
@@
 ```{r pressure, echo=FALSE}
-plot(pressure)
+#plot(pressure)
 ```

### 2025-02-08 reports/capstone-movielens-report.Rmd
`edx` dataset: analysis in progress...

@@
 library(tidyr)
+
+library(rafalib)
 library(pak)
@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score defined as:
-
+Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
 $$
@@
 ```{r }
-dim(edx)
+dim_edx <- dim(edx)
+print(dim_edx)
 ```
@@
 ```{r}
-n_distinct(edx$movieId)
+n_movies <- n_distinct(edx$movieId)
+print(n_movies)
 ```
@@
 ```{r}
-n_distinct(edx$userId)
+n_users <- n_distinct(edx$userId)
+print(n_users)
 ```
 
+Now, note the expressions below which confirm the fact explained in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2]:
+```{r}
+max_possible_ratings <- n_movies*n_users
+sprintf("Maximum possible ratings: %s", max_possible_ratings)
+sprintf("Rows in `edx` dataset: %s", dim_edx[1])
+sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
+
+```
+
+As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
+Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
+A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
+```{r}
+keep <- edx |> 
+  dplyr::count(movieId) |> 
+  top_n(4, n) |> 
+  pull(movieId)
+
+tab <- edx |> 
+  filter(movieId %in% keep) |> 
+  filter(userId %in% c(13:20)) |> 
+  select(userId, title, rating) |> 
+  mutate(title = str_remove(title, ", The"),
+         title = str_remove(title, ":.*")) |>
+  pivot_wider(names_from = "title", values_from = "rating")
+
+print(tab)
+```
+
+The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is[@IDS2_23-1-1]:
+```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
+users <- sample(unique(edx$userId), 100)
+
+rafalib::mypar()
+edx|> 
+  filter(userId %in% users) |> 
+  select(userId, movieId, rating) |>
+  mutate(rating = 1) |>
+  pivot_wider(names_from = movieId, values_from = rating) |> 
+  (\(mat) mat[, sample(ncol(mat), 100)])() |>
+  as.matrix() |> 
+  t() |>
+  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
+```
+
+Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
+```{r movie-id-and-user-hists, echo=FALSE, fig.width=6, fig.height=3}
+p1 <- edx |> 
+  count(movieId) |> 
+  ggplot(aes(n)) + 
+  geom_histogram(bins = 30, color = "black") + 
+  scale_x_log10() + 
+  ggtitle("Movies")
+
+p2 <- edx |> 
+  count(userId) |> 
+  ggplot(aes(n)) + 
+  geom_histogram(bins = 30, color = "black") + 
+  scale_x_log10() + 
+  ggtitle("Users")
+
+gridExtra::grid.arrange(p2, p1, ncol = 2)
+```
+
+Taking into consideration these observations, we came up with a decision to use the data from the dataset only for users who have provided at least 100 ratings[@IDS2_23-1-1].
+
+#### Movie genres
+\
 The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
@@
 
-Further analysis of the `edx` dataset was inspired by the article: A Movie Recommender System Using R - BEST[@MRS-R-BEST], from which the code and explanatory notes below were cited.
+Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
 

### 2025-02-09 reports/capstone-movielens-report.Rmd
Report: Simplest (naive) model described.

@@
 
-Let us install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
+Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
 ```{r }
@@
 ```
-
-Let us look into the details of the `edx` dataset:
+#### `edx` Dataset
+\
+Let's look into the details of the `edx` dataset:
 ``` {r echo = TRUE}
@@
 
-Next, we have 10677 different movies 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
-
-Now, note the expressions below which confirm the fact explained in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2]:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
-
-```
-
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
-
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is[@IDS2_23-1-1]:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=FALSE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Taking into consideration these observations, we came up with a decision to use the data from the dataset only for users who have provided at least 100 ratings[@IDS2_23-1-1].
-
-#### Movie genres
+##### Movie Genres Data 
 \
@@
 
-#### Rating distribution plot[@MRS-R-BEST]
+##### Rating distribution plot[@MRS-R-BEST]
 \
@@
 
-#### Yearly rating count[@MRS-R-BEST]
+##### Yearly rating count[@MRS-R-BEST]
 \
@@
 
-#### Average rating per year plot[@MRS-R-BEST]
+##### Average rating per year plot[@MRS-R-BEST]
 \
@@
 
-#### Movie popularity count[@MRS-R-BEST]
+##### Ratings per movie
+\
+
+###### Movie popularity count[@MRS-R-BEST]
 \
@@
 
-#### Ratings per movie plot[@MRS-R-BEST]
+###### Ratings per movie plot[@MRS-R-BEST]
 \
@@
 
-#### Movies' rating histogram[@MRS-R-BEST]
+###### Movies' rating histogram[@MRS-R-BEST]
 \
@@
 
-#### Ratings per user[@MRS-R-BEST]
+##### Ratings per user[@MRS-R-BEST]
+\
 
-##### User rating count (activity measure)
+###### User rating count (activity measure)
 \
@@
 
-##### User rating summary
+###### User rating summary
 \
@@
 
-##### Ratings per user plot
+###### Ratings per user plot
 \
@@
 
-##### Users' rating histogram
+###### Users' rating histogram
 \
@@
 
-##### 
 \
+```{r echo=FALSE}
+# #### [@MRS-R-BEST]
+```
+
+## Methods / Analysis
+### Defining helper functions
+\
+
+Let's define some helper functions that we will use in our subsequent analysis:
 ```{r}
+start_date <- function(){
+  print(date())
+  Sys.time()
+}
+end_date <- function(start){
+  print(date())
+  Sys.time() - start
+}
+rmse <- function(r) sqrt(mean(r^2))
+RMSE <- function(true_ratings, predicted_ratings){
+  sqrt(mean((true_ratings - predicted_ratings)^2))
+}
+```
+
+### Preparing train and set datasets
+\
+First, let's note that we have 10677 different movies: 
+```{r}
+n_movies <- n_distinct(edx$movieId)
+print(n_movies)
+```
+and 69878 different users in the dataset:
+```{r}
+n_users <- n_distinct(edx$userId)
+print(n_users)
+```
+
+Now, note the expressions below which confirm the fact explained in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
+```{r}
+max_possible_ratings <- n_movies*n_users
+sprintf("Maximum possible ratings: %s", max_possible_ratings)
+sprintf("Rows in `edx` dataset: %s", dim_edx[1])
+sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
 
@@
 
-##### 
+As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
+Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
+A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
+```{r}
+keep <- edx |> 
+  dplyr::count(movieId) |> 
+  top_n(4, n) |> 
+  pull(movieId)
+
+tab <- edx |> 
+  filter(movieId %in% keep) |> 
+  filter(userId %in% c(13:20)) |> 
+  select(userId, title, rating) |> 
+  mutate(title = str_remove(title, ", The"),
+         title = str_remove(title, ":.*")) |>
+  pivot_wider(names_from = "title", values_from = "rating")
+
+print(tab)
+```
+
+The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
+```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
+users <- sample(unique(edx$userId), 100)
+
+rafalib::mypar()
+edx|> 
+  filter(userId %in% users) |> 
+  select(userId, movieId, rating) |>
+  mutate(rating = 1) |>
+  pivot_wider(names_from = movieId, values_from = rating) |> 
+  (\(mat) mat[, sample(ncol(mat), 100)])() |>
+  as.matrix() |> 
+  t() |>
+  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
+```
+
+Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
+```{r movie-id-and-user-hists, echo=FALSE, fig.width=6, fig.height=3}
+p1 <- edx |> 
+  count(movieId) |> 
+  ggplot(aes(n)) + 
+  geom_histogram(bins = 30, color = "black") + 
+  scale_x_log10() + 
+  ggtitle("Movies")
+
+p2 <- edx |> 
+  count(userId) |> 
+  ggplot(aes(n)) + 
+  geom_histogram(bins = 30, color = "black") + 
+  scale_x_log10() + 
+  ggtitle("Users")
+
+gridExtra::grid.arrange(p2, p1, ncol = 2)
+```
+
+Taking into consideration these observations, we came up with a decision to use the data from the dataset only for users who have provided at least 100 ratings.
+
+Now let's split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in the [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1]:
+```{r}
+# Let's ignore the data for users who have not provided at least 100 ratings:
+edx100 <- edx |> 
+  group_by(userId) |>
+  filter(n() >= 100) |>
+  ungroup()
+
+print(edx100 |> summarize(n_distinct(userId), n_distinct(movieId)))
+
+# For each one of these users, we will split their ratings into 80% for training 
+# and 20% for testing:
+
+set.seed(2006)
+indexes <- split(1:nrow(edx100), edx100$userId)
+test_ind <- sapply(indexes, function(i) sample(i, ceiling(length(i)*.2))) |> 
+  unlist() |>
+  sort()
+
+test_set <- edx100[test_ind,] 
+train_set <- edx100[-test_ind,]
+
+# To make sure we don’t include movies in the training set that should not be 
+# there, we remove entries using the semi_join function:
+test_set <- test_set |> semi_join(train_set, by = "movieId") |> as.data.frame()
+summary(test_set)
+
+train_set <- mutate(train_set, userId = factor(userId), movieId = factor(movieId))
+summary(train_set)
+```
+
+We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
+To create this matrix, we use `tidyr::pivot_wider` function:
+
+```{r}
+y <- dplyr::select(train_set, movieId, userId, rating) |>
+pivot_wider(names_from = movieId, values_from = rating) |>
+column_to_rownames("userId") |>
+as.matrix()
+
+dim(y)
+```
+
+To be able to map movie IDs to titles we create the following lookup table:
+```{r}
+movie_map <- train_set |> dplyr::select(movieId, title, genres) |> 
+  distinct(movieId, .keep_all = TRUE)
+
+summary(movie_map)
+```
+
+Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
+
+### Naive Model
 \
+Let's begin our analysis by evaluating the simplest model described in [Section 23.3 The First Model of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
+It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
+
+$$
+Y_{i,j} = \mu + \varepsilon_{i,j}
+$$
+
+with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
+
+We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
+
+```{r pressure, echo=TRUE}
+mu <- mean(y, na.rm = TRUE)
+print(mu)
+```
+
+If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE:
+
 ```{r}
+rmse(test_set$rating - mu)
+```
+
+If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
+```{r}
+plugged_numbers <- seq(0, 6, 0.1) - 3
+print(plugged_numbers)
+
+rmses <- sapply(plugged_numbers, function(x){
+  rmse(test_set$rating - mu + x)
+})
+
+plot(plugged_numbers, rmses, type = "l")
+
+sprintf("Minimum RMSE is achieved when `plugged number is`: %s", plugged_numbers[which.min(rmses)])
 
 ```
+
+To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
+
+### Taking into account User effects
+\
 
@@
 
-```{r}
-
-```
-
-```{r}
-
-```
-
-#### [@MRS-R-BEST]
-\
-```{r}
-
-```
-
-## Methods / Analysis
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-#plot(pressure)
-```
-
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2025-02-09 reports/capstone-movielens-report.Rmd
Report: acounted for user effects.

@@
 }
+
+# Because we know ratings can’t be below 0.5 or above 5, 
+# we define the function clamp:
+clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
+
 ```
@@
 ```{r}
-plugged_numbers <- seq(0, 6, 0.1) - 3
-print(plugged_numbers)
+deviation <- seq(0, 6, 0.1) - 3
+print(deviation)
 
-rmses <- sapply(plugged_numbers, function(x){
-  rmse(test_set$rating - mu + x)
+rmse_value <- sapply(deviation, function(diff){
+  rmse(test_set$rating - mu + diff)
 })
 
-plot(plugged_numbers, rmses, type = "l")
+plot(deviation, rmse_value, type = "l")
 
-sprintf("Minimum RMSE is achieved when `plugged number is`: %s", plugged_numbers[which.min(rmses)])
+sprintf("Minimum RMSE is achieved when the deviation from the mean is: %s", 
+        deviation[which.min(rmse_value)])
 
@@
 \
+To improve our model let's now take into consideration user effects as explained in [Section 23.4 User effects of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects).
+If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
+```{r}
+hist(rowMeans(y, na.rm = TRUE), nclass = 30)
+```
 
+Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
+The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
+So we write the model as:
+
+$$
+Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
+$$
+
+Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
+
+As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we compute them this way:
 ```{r}
+a <- rowMeans(y - mu, na.rm = TRUE)
+```
 
+Finally, we are ready to compute the `RMSE` (additionally using the helper function `clamp` we defined above to keep predictions in the proper range):
+```{r}
+# Compute the RMSE taking into account user effects:
+user_effects_rmse <- test_set |> 
+    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
+    mutate(resid = rating - clamp(mu + a)) |> 
+    filter(!is.na(resid)) |>
+    pull(resid) |> rmse()
+
+print(user_effects_rmse)
 ```
@@
 
-```{r}
-
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
-
 ## Conclusion

### 2025-02-13 reports/capstone-movielens-report.Rmd
Report: Movie effects & Penalized least squares described.

@@
 
-Now, note the expressions below which confirm the fact explained in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
+Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
 ```{r}
@@
 \
-Let's begin our analysis by evaluating the simplest model described in [Section 23.3 The First Model of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
+Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
 It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
@@
 \
-To improve our model let's now take into consideration user effects as explained in [Section 23.4 User effects of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects).
+To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects).
 If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
@@
 The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
-So we write the model as:
+So we write the model as follows:
 
@@
 ```
+### Taking into account Movie effects
+\
+In [Section _23.5 Movie effects_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) the author draws our attention to the fact that some movies are generally rated higher than others.
+He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
+
+$$
+Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
+$$
+The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:
 
 ```{r}
+b <- colMeans(y - mu - a, na.rm = TRUE)
+```
 
+We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
+```{r}
+user_and_movie_effects_rmse <- test_set |> 
+    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
+    left_join(data.frame(movieId = as.integer(names(b)), b = b), by = "movieId") |>
+    mutate(resid = rating - clamp(mu + a + b)) |>  
+    filter(!is.na(resid)) |>
+    pull(resid) |> rmse()
+
+print(user_and_movie_effects_rmse)
 ```
+### Utilizing Penalized least squares
+\
+[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
+The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
+Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
+
+$$ 
+\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
+$$
+The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
+Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
+
+$$
+\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
+$$
+
+where $n_j$ is the number of ratings made for movie $j$.
+
+This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
+Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
+The larger the $\lambda$, the more we shrink[@IDS2_23-6].
 

### 2025-02-15 reports/capstone-movielens-report.Rmd
Penalized estimates computed.

@@
 
+#### Support function
+\
+We will use the following function to calculate _RMSE_ in this section:
 ```{r}
+reg_rmse <- function(b){
+  test_set |> 
+    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
+    left_join(data.frame(movieId = as.integer(names(b)), b = b), by = "movieId") |>
+    mutate(resid = rating - clamp(mu + a + b)) |> 
+    filter(!is.na(resid)) |>
+    pull(resid) |> rmse()
+}
 
+```
+
+Let's now figure out the $\lambda$ that minimizes the _RMSE_:
+```{r}
+# Here we will simply compute the RMSE for different values of `lambda` 
+n <- colSums(!is.na(y))
+
+sums <- colSums(y - mu - a, na.rm = TRUE)
+lambdas <- seq(0, 10, 0.1)
+
+rmses <- sapply(lambdas, function(lambda){
+  b <-  sums / (n + lambda)
+  reg_rmse(b)
+})
+
+# Here is a plot of the RMSE versus `lambda`:
+plot(lambdas, rmses, type = "l")
+```
+Now we can determine the minimal _RMSE_:
+```{r}
+print(min(rmses))
+```
+
+which is achieved for the following $\lambda$:
+```{r}
+lambda <- lambdas[which.min(rmses)] 
+print(lambda)
+```
+
+Using this $\lambda$ we can compute the regularized estimates:
+```{r}
+b_reg <- sums / (n + lambda)
+
+str(b_reg)
+```
+Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
+```{r}
+reg_rmse(b_reg)
 ```

### 2025-02-15 r/work/3.movielens.draft3.R
Code amended.

@@ -346,7 +346,7 @@ b_reg <- sums / (n + lambda)
 ### Model testing ----------------------------------------------------------------
 reg_rmse(test_set, b_reg)
 #> [1] 0.8659219
-reg_rmse(final_holdout_test, b_reg)
+# reg_rmse(final_holdout_test, b_reg)
 #> [1] 0.8663589
 
 ## Matrix factorization --------------------------------------------------------

### 2025-02-17 reports/capstone-movielens-report.Rmd
R - script added; Date Smoothed effect implemented.

@@
 That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-
-##### Yearly rating count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(count = n())
-)
-```
-
-##### Average rating per year plot[@MRS-R-BEST]
-\
-```{r}
-edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(avg = mean(rating)) |>
-  ggplot(aes(x = year, y = avg)) +
-  geom_bar(stat = "identity", fill = "#8888ff") + 
-  ggtitle("Average rating per year") +
-  xlab("Year") +
-  ylab("Average rating") +
-  scale_y_continuous(labels = comma) + 
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
 
@@
 Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=FALSE, fig.width=6, fig.height=3}
+```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
 p1 <- edx |> 
@@
 ```
+### Accounting for Date effects
+
+##### Yearly rating count[@MRS-R-BEST]
+\
+```{r}
+print(edx |> 
+  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
+  group_by(year) |>
+  summarize(count = n())
+)
+```
+
+##### Average rating per year plot[@MRS-R-BEST]
+\
+```{r}
+edx |> 
+  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
+  group_by(year) |>
+  summarize(avg = mean(rating)) |>
+  ggplot(aes(x = year, y = avg)) +
+  geom_bar(stat = "identity", fill = "#8888ff") + 
+  ggtitle("Average rating per year") +
+  xlab("Year") +
+  ylab("Average rating") +
+  scale_y_continuous(labels = comma) + 
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+```
 

### 2025-02-17 r/capstone-movielens.R

@@ -1,0 +1,588 @@
+# Setup datasets
+
+# if(!require(tidyverse)) 
+#   install.packages("tidyverse", repos = "http://cran.us.r-project.org")
+# if(!require(caret)) 
+#   install.packages("caret", repos = "http://cran.us.r-project.org")
+# if(!require(data.table)) 
+#   install.packages("data.table", repos = "http://cran.us.r-project.org")
+if(!require(pak)) 
+  install.packages("pak")
+
+# Loading the required libraries
+library(caret)
+library(cowplot)
+library(data.table)
+library(dplyr)
+library(ggplot2)
+library(ggthemes)
+library(lubridate)
+library(Metrics)
+library(recosystem)
+library(scales)
+library(stringr)
+library(tibble)
+library(tidyr)
+
+library(rafalib)
+library(pak)
+
+## Introduction / Overview / Executive Summar
+
+### Datasets
+
+# To start with we have to generate two datasets derived from the MovieLens one:
+#   
+# *`edx`: we use it to develop and train our algorithms;
+# * `final_holdout_test`:  according to the course requirements, 
+#    we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
+# 
+# For this purpose the following package has been developed by the author of this 
+# script: `edx.capstone.movielens.data`. The source code of the package is available 
+# on `GitHub`(https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data).
+# 
+# Let's install the development version of this package from the `GitHub` repository 
+# and attach the correspondent library to the global environment:
+
+if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
+
+library(edx.capstone.movielens.data)
+edx <- edx.capstone.movielens.data::edx
+final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
+
+summary(edx)
+summary(final_holdout_test)
+
+#### `edx` Dataset
+
+# Let's look into the details of the `edx` dataset:
+str(edx)
+
+#> Also, we can see that no movies have a rating of 0. 
+#> Movies are rated from 0.5 to 5.0 in 0.5 increments:
+
+#library(dplyr)
+s <- edx |> group_by(rating) |>
+  summarise(n = n())
+print(s)
+
+##### Movie Genres Data 
+
+#>The following code computes movie rating summaries by popular genres 
+#>like Drama, Comedy, Thriller, and Romance:
+
[…]

### 2025-02-18 reports/capstone-movielens-report.Rmd
Accounting for Date & Genre effects (in progress).

@@
 library(tidyr)
+
+library(dslabs)
+library(tidyverse)
 
@@
 
+We use the following models to account for the `date` effect:
+
+$$
+Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
+$$
+
+### Accounting for Genre effect
+\
+As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
+This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
+
+The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
+
+```{r}
+# Preparing data for plotting:
+train_set_grp <- train_set |> 
+  mutate(genre_categories = as.factor(genres)) |>
+  group_by(genre_categories) |>
+  summarize(n = n(), avg = mean(rating), se = sd(rating)/sqrt(n())) |>
+  filter(n > 20000) |> 
+  mutate(genres = reorder(genre_categories, avg)) |>
+  select(genres, avg, se, n)
+
+dim(train_set_grp)
+print(train_set_grp |> sort_by.data.frame(~ avg))
+
+# Creating plot:
+train_set_grp |> 
+  ggplot(aes(x = genres, y = avg, ymin = avg - 2*se, ymax = avg + 2*se)) + 
+  geom_point() +
+  geom_errorbar() + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+```
+Below are worst and best ratings categories:
+```{r}
+sprintf("The worst ratings are for the genre category: %s",
+        train_set_grp$genres[which.min(train_set_grp$genres)])
+
+sprintf("The best ratings are for the genre category: %s",
+        train_set_grp$genres[which.max(train_set_grp$genres)])
+```
+
+If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
+
+$$
+Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \sum_{k=1}^K x_{i,j} \beta_k + \varepsilon_{i,j}
+$$
+
+with $x^k_{i,j} = 1$ if $g_{i,j}$ is genre $k$.
+
 ## Conclusion

### 2025-02-18 r/capstone-movielens.R

@@ -24,8 +24,13 @@ library(stringr)
 library(tibble)
 library(tidyr)
 
+library(dslabs)
+library(tidyverse)
+
 library(rafalib)
 library(pak)
+
+
 
 ## Introduction / Overview / Executive Summar
 
@@ -389,7 +394,8 @@ reg_rmse(b_reg)
 #> [1] 0.8659219
 
 # Calculate Date Smoothed Effect -------------------------------------------------------
-# Y(i,u) = μ + b(i) + b(u) + f(d(u,i)) + ε(i,u)
+# Y[i,j] = μ + α[i] + β[j] + f(d(i,j)) + ε[i,j]
+
 # with `j` a smooth function of `d(u,i)`
 
 # library(lubridate)
@@ -584,5 +590,43 @@ print(date_smoothed_rmse)
 # 
 # RMSE(final_preds, final_test_set$rating)
 #> [1] 0.8641795
+
+### Accounting for Genre effect ------------------------------------------------
+
+# Reference: the Textbook Section "23.7 Exercises" of the Chapter "23 Regularization"
+# https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises
+
+#> The `edx` dataset also has a genres column. This column includes 
+#> every genre that applies to the movie 
+#> (some movies fall under several genres)[@IDS2_23-7].
+
+train_set_grp <- train_set |> 
+  mutate(genre_categories = as.factor(genres)) |>
+  group_by(genre_categories) |>
+  summarize(n = n(), avg = mean(rating), se = sd(rating)/sqrt(n())) |>
+  filter(n > 20000) |> 
+  mutate(genres = reorder(genre_categories, avg)) |>
+  select(genres, avg, se, n)
+
+dim(train_set_grp)
+print(train_set_grp |> sort_by.data.frame(~ avg))
+
+train_set_grp |> 
+  ggplot(aes(x = genres, y = avg, ymin = avg - 2*se, ymax = avg + 2*se)) + 
+  geom_point() +
+  geom_errorbar() + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
+sprintf("The worst ratings were for the genre category: %s",
+        train_set_grp$genres[which.min(train_set_grp$genres)])
+
+sprintf("The best ratings were for the genre category: %s",
[…]

### 2025-02-19 reports/capstone-movielens-report.draft1.tex
Version 1 of draft report files added.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{hyperref}
\usepackage[natbib=true, style=numeric, backref=true, sorting=none]{biblatex}
\hypersetup{backref, pdfpagemode=Normal, colorlinks=true, implicit=false}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{biblatex}
\addbibresource{references.bib}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Capstone Movielens Report},
  pdfauthor={Azamat Kurbanaev},
  colorlinks=true,
  linkcolor={red},
  filecolor={Maroon},
  citecolor={blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Capstone Movielens Report}
\author{Azamat Kurbanaev}
\date{2025-02-19}

\begin{document}
\maketitle

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{2}
\tableofcontents
}
\begin{verbatim}
## Loading required package: tidyverse
\end{verbatim}

\begin{verbatim}
## Warning: package 'lubridate' was built under R version 4.4.2
\end{verbatim}

\begin{verbatim}
## -- Attaching core tidyverse packages ------------------------ tidyverse 2.0.0 --
## v dplyr     1.1.4     v readr     2.1.5
## v forcats   1.0.0     v stringr   1.5.1
## v ggplot2   3.5.1     v tibble    3.2.1
## v lubridate 1.9.4     v tidyr     1.3.1
## v purrr     1.0.2
\end{verbatim}

\begin{verbatim}
## -- Conflicts ------------------------------------------ tidyverse_conflicts() --
## x dplyr::filter() masks stats::filter()
## x dplyr::lag()    masks stats::lag()
## i Use the conflicted package (<http://conflicted.r-lib.org/>) to force all conflicts to become errors
## Loading required package: caret
\end{verbatim}

\begin{verbatim}
## Warning: package 'caret' was built under R version 4.4.2
\end{verbatim}

\begin{verbatim}
## Loading required package: lattice
## 
## Attaching package: 'caret'
## 
## The following object is masked from 'package:purrr':
## 
##     lift
## 
## Loading required package: data.table
\end{verbatim}

\begin{verbatim}
## Warning: package 'data.table' was built under R version 4.4.2
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'data.table'
## 
## The following objects are masked from 'package:lubridate':
## 
##     hour, isoweek, mday, minute, month, quarter, second, wday, week,
##     yday, year
## 
## The following objects are masked from 'package:dplyr':
## 
##     between, first, last
## 
## The following object is masked from 'package:purrr':
## 
##     transpose
## 
## Loading required package: gtools
\end{verbatim}

\begin{verbatim}
## Warning: package 'gtools' was built under R version 4.4.2
\end{verbatim}

\begin{verbatim}
## Loading required package: pak
\end{verbatim}

\begin{verbatim}
## Warning: package 'pak' was built under R version 4.4.2
\end{verbatim}

\begin{verbatim}
## Warning: package 'dslabs' was built under R version 4.4.2
\end{verbatim}

\begin{verbatim}
## Warning: package 'cowplot' was built under R version 4.4.2
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'cowplot'
## 
## The following object is masked from 'package:lubridate':
## 
##     stamp
\end{verbatim}

\begin{verbatim}
## Warning: package 'ggthemes' was built under R version 4.4.2
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'ggthemes'
## 
## The following object is masked from 'package:cowplot':
## 
##     theme_map
\end{verbatim}

\begin{verbatim}
## Warning: package 'Metrics' was built under R version 4.4.2
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'Metrics'
## 
## The following objects are masked from 'package:caret':
## 
##     precision, recall
\end{verbatim}

\begin{verbatim}
## Warning: package 'recosystem' was built under R version 4.4.2
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'scales'
## 
## The following object is masked from 'package:purrr':
## 
##     discard
## 
## The following object is masked from 'package:readr':
## 
##     col_factor
\end{verbatim}

\subsection{Introduction / Overview / Executive
Summary}\label{introduction-overview-executive-summary}

The goal of the project is to build a Recommendation System using a
\href{http://grouplens.org/datasets/movielens/10m/}{10M version of the
MovieLens dataset}. Following the
\href{https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html}{Netflix
Grand Prize Contest} requirements, we will evaluate the \emph{Root Mean
Square Error} (\emph{RMSE}) score, which, as shown in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#sec-netflix-loss-function}{Section
23.2 Loss function} of the \emph{Course Textbook}, is defined as: \[
\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
\]

with \(N\) being the number of user/movie combinations for which we make
predictions and the sum occurring over all these
combinations\autocite{IDS2_23-2}.

Our goal is to achieve a value of less than 0.86490 (compare with the
\emph{Netflix Grand Prize} requirement: of at least
0.8563\autocite{BigChaosSln}).

\subsubsection{Datasets}\label{datasets}

To start with we have to generate two datasets derived from the
\emph{MovieLens} one mentioned above:

\begin{itemize}
\tightlist
\item
  \textbf{edx:} we use it to develop and train our algorithms;
\item
  \textbf{final\_holdout\_test:} according to the course requirements,
  we use it exclusively to evaluate the \emph{\textbf{RMSE}} of our
  final algorithm.
\end{itemize}

For this purpose the following package has been developed by the author
of this report: \texttt{edx.capstone.movielens.data}. The source code of
the package is available
\href{https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data}{on
GitHub}\autocite{edx_capstone_movielens_data}.

Let's install the development version of this package from the GitHub
repository and attach the correspondent library to the global
environment:

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{if}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{require}\NormalTok{(edx.capstone.movielens.data)) pak}\SpecialCharTok{::}\FunctionTok{pak}\NormalTok{(}\StringTok{"AzKurban{-}edX{-}DS/edx.capstone.movielens.data"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Loading required package: edx.capstone.movielens.data
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(edx.capstone.movielens.data)}
\NormalTok{edx }\OtherTok{\textless{}{-}}\NormalTok{ edx.capstone.movielens.data}\SpecialCharTok{::}\NormalTok{edx}
\NormalTok{final\_holdout\_test }\OtherTok{\textless{}{-}}\NormalTok{ edx.capstone.movielens.data}\SpecialCharTok{::}\NormalTok{final\_holdout\_test}

\FunctionTok{summary}\NormalTok{(edx)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      userId         movieId          rating        timestamp        
##  Min.   :    1   Min.   :    1   Min.   :0.500   Min.   :7.897e+08  
##  1st Qu.:18124   1st Qu.:  648   1st Qu.:3.000   1st Qu.:9.468e+08  
##  Median :35738   Median : 1834   Median :4.000   Median :1.035e+09  
##  Mean   :35870   Mean   : 4122   Mean   :3.512   Mean   :1.033e+09  
##  3rd Qu.:53607   3rd Qu.: 3626   3rd Qu.:4.000   3rd Qu.:1.127e+09  
##  Max.   :71567   Max.   :65133   Max.   :5.000   Max.   :1.231e+09  
##     title              genres         
##  Length:9000055     Length:9000055    
##  Class :character   Class :character  
##  Mode  :character   Mode  :character  
##                                       
##                                       
## 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{summary}\NormalTok{(final\_holdout\_test)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      userId         movieId          rating        timestamp        
##  Min.   :    1   Min.   :    1   Min.   :0.500   Min.   :7.897e+08  
##  1st Qu.:18096   1st Qu.:  648   1st Qu.:3.000   1st Qu.:9.467e+08  
##  Median :35768   Median : 1827   Median :4.000   Median :1.035e+09  
##  Mean   :35870   Mean   : 4108   Mean   :3.512   Mean   :1.033e+09  
##  3rd Qu.:53621   3rd Qu.: 3624   3rd Qu.:4.000   3rd Qu.:1.127e+09  
##  Max.   :71567   Max.   :65133   Max.   :5.000   Max.   :1.231e+09  
##     title              genres         
##  Length:999999      Length:999999     
##  Class :character   Class :character  
##  Mode  :character   Mode  :character  
##                                       
##                                       
## 
\end{verbatim}

\paragraph{\texorpdfstring{\texttt{edx}
Dataset}{edx Dataset}}\label{edx-dataset}

\hfill\break
Let's look into the details of the \texttt{edx} dataset:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{str}\NormalTok{(edx)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 'data.frame':    9000055 obs. of  6 variables:
##  $ userId   : int  1 1 1 1 1 1 1 1 1 1 ...
##  $ movieId  : int  122 185 292 316 329 355 356 362 364 370 ...
##  $ rating   : num  5 5 5 5 5 5 5 5 5 5 ...
##  $ timestamp: int  838985046 838983525 838983421 838983392 838983392 838984474 838983653 838984885 838983707 838984596 ...
##  $ title    : chr  "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Stargate (1994)" ...
##  $ genres   : chr  "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Sci-Fi" ...
\end{verbatim}

Note that we have 9000055 rows and six columns in there:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dim\_edx }\OtherTok{\textless{}{-}} \FunctionTok{dim}\NormalTok{(edx)}
\FunctionTok{print}\NormalTok{(dim\_edx)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 9000055       6
\end{verbatim}

Also, we can see that no movies have a rating of 0. Movies are rated
from 0.5 to 5.0 in 0.5 increments:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#library(dplyr)}
\NormalTok{s }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(rating) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{n =} \FunctionTok{n}\NormalTok{())}
\FunctionTok{print}\NormalTok{(s)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 10 x 2
##    rating       n
##     <dbl>   <int>
##  1    0.5   85374
##  2    1    345679
##  3    1.5  106426
##  4    2    711422
##  5    2.5  333010
##  6    3   2121240
##  7    3.5  791624
##  8    4   2588430
##  9    4.5  526736
## 10    5   1390114
\end{verbatim}

\subparagraph{Movie Genres Data}\label{movie-genres-data}

\hfill\break
The following code computes movie rating summaries by popular genres
like Drama, Comedy, Thriller, and Romance:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#library(stringr)}
\NormalTok{genres }\OtherTok{=} \FunctionTok{c}\NormalTok{(}\StringTok{"Drama"}\NormalTok{, }\StringTok{"Comedy"}\NormalTok{, }\StringTok{"Thriller"}\NormalTok{, }\StringTok{"Romance"}\NormalTok{)}
\FunctionTok{sapply}\NormalTok{(genres, }\ControlFlowTok{function}\NormalTok{(g) \{}
  \FunctionTok{sum}\NormalTok{(}\FunctionTok{str\_detect}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{genres, g))}
\NormalTok{\})}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##    Drama   Comedy Thriller  Romance 
##  3910127  3540930  2325899  1712100
\end{verbatim}

Further, we can find out the movies that have the greatest number of
ratings using the following code:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ordered\_movie\_ratings }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(movieId, title) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{number\_of\_ratings =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(number\_of\_ratings))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## `summarise()` has grouped output by 'movieId'. You can override using the
## `.groups` argument.
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{print}\NormalTok{(}\FunctionTok{head}\NormalTok{(ordered\_movie\_ratings))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 6 x 3
## # Groups:   movieId [6]
##   movieId title                            number_of_ratings
##     <int> <chr>                                        <int>
## 1     296 Pulp Fiction (1994)                          31362
## 2     356 Forrest Gump (1994)                          31079
## 3     593 Silence of the Lambs, The (1991)             30382
## 4     480 Jurassic Park (1993)                         29360
## 5     318 Shawshank Redemption, The (1994)             28015
## 6     110 Braveheart (1995)                            26212
\end{verbatim}

and figure out the most given ratings in order from most to least:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ratings }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}}  \FunctionTok{group\_by}\NormalTok{(rating) }\SpecialCharTok{|\textgreater{}}
     \FunctionTok{summarise}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
     \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(count))}
\FunctionTok{print}\NormalTok{(ratings)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 10 x 2
##    rating   count
##     <dbl>   <int>
##  1    4   2588430
##  2    3   2121240
##  3    5   1390114
##  4    3.5  791624
##  5    2    711422
##  6    4.5  526736
##  7    1    345679
##  8    2.5  333010
##  9    1.5  106426
## 10    0.5   85374
\end{verbatim}

The following code allows us to summarize that in general, half-star
ratings are less common than whole-star ratings (e.g., there are fewer
ratings of 3.5 than there are ratings of 3 or 4, etc.):

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{print}\NormalTok{(edx }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(rating) }\SpecialCharTok{|\textgreater{}} \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 10 x 2
##    rating   count
##     <dbl>   <int>
##  1    0.5   85374
##  2    1    345679
##  3    1.5  106426
##  4    2    711422
##  5    2.5  333010
##  6    3   2121240
##  7    3.5  791624
##  8    4   2588430
##  9    4.5  526736
## 10    5   1390114
\end{verbatim}

We can visually see that from the following plot:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{edx }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{group\_by}\NormalTok{(rating) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ rating, }\AttributeTok{y =}\NormalTok{ count)) }\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{() }
\end{Highlighting}
\end{Shaded}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-10-1.pdf}

Further analysis of the \texttt{edx} dataset have been also inspired by
the article mentioned above\autocite{MRS-R-BEST}, from which the code
and explanatory notes below were cited.

\subparagraph{\texorpdfstring{Rating distribution
plot\autocite{MRS-R-BEST}}{Rating distribution plot{[}@MRS-R-BEST{]}}}\label{rating-distribution-plotmrs-r-best}

\hfill\break
The code below demonstrates another way of visualizing the rating
distribution:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{edx }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{group\_by}\NormalTok{(rating) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ rating, }\AttributeTok{y =}\NormalTok{ count)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{stat =} \StringTok{"identity"}\NormalTok{, }\AttributeTok{fill =} \StringTok{"\#8888ff"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Rating Distribution"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{xlab}\NormalTok{(}\StringTok{"Rating"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Occurrences Count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ comma) }\SpecialCharTok{+}
  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{n.breaks =} \DecValTok{10}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_economist}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \SpecialCharTok{{-}}\DecValTok{5}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{axis.title.y =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \DecValTok{10}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\FloatTok{0.5}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FloatTok{1.2}\NormalTok{, }\StringTok{"cm"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-11-1.pdf}

This graph is another confirmation of what we found out above: rounded
ratings occur more often than half-stared ones. The upward trend
previously discussed is now perfectly clear, although it seems to top
right between the 3 and 4-star ratings lowering the occurrences count
afterward. That might be due to users being more hesitant to rate with
the highest mark for whichever reasons they might
hold\autocite{MRS-R-BEST}.

\subparagraph{Ratings per movie}\label{ratings-per-movie}

\hfill\break

Movie popularity count\autocite{MRS-R-BEST}

\hfill\break

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{print}\NormalTok{(edx }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{group\_by}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{slice\_head}\NormalTok{(}\AttributeTok{n =} \DecValTok{10}\NormalTok{)}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 10 x 2
##    movieId count
##      <int> <int>
##  1       1 23790
##  2       2 10779
##  3       3  7028
##  4       4  1577
##  5       5  6400
##  6       6 12346
##  7       7  7259
##  8       8   821
##  9       9  2278
## 10      10 15187
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{summary}\NormalTok{(edx }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}} \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}} \FunctionTok{select}\NormalTok{(count))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      count        
##  Min.   :    1.0  
##  1st Qu.:   30.0  
##  Median :  122.0  
##  Mean   :  842.9  
##  3rd Qu.:  565.0  
##  Max.   :31362.0
\end{verbatim}

Ratings per movie plot\autocite{MRS-R-BEST}

\hfill\break

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{edx }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{group\_by}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ movieId, }\AttributeTok{y =}\NormalTok{ count)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#4020dd"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{color =} \StringTok{"red"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Ratings per movie"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{xlab}\NormalTok{(}\StringTok{"Movies"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Number of ratings"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ comma) }\SpecialCharTok{+}
  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{n.breaks =} \DecValTok{10}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_economist}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \SpecialCharTok{{-}}\DecValTok{5}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{axis.title.y =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \DecValTok{10}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\FloatTok{0.5}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FloatTok{1.2}\NormalTok{, }\StringTok{"cm"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## `geom_smooth()` using method = 'gam' and formula = 'y ~ s(x, bs = "cs")'
\end{verbatim}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-14-1.pdf}

Movies' rating histogram\autocite{MRS-R-BEST}

\hfill\break

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{edx }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{group\_by}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ count)) }\SpecialCharTok{+}
  \FunctionTok{geom\_histogram}\NormalTok{(}\AttributeTok{fill =} \StringTok{"\#8888ff"}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#4020dd"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Movies\textquotesingle{} rating histogram"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{xlab}\NormalTok{(}\StringTok{"Rating count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Number of movies"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ comma) }\SpecialCharTok{+}
  \FunctionTok{scale\_x\_log10}\NormalTok{(}\AttributeTok{n.breaks =} \DecValTok{10}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_economist}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \SpecialCharTok{{-}}\DecValTok{5}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{axis.title.y =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \DecValTok{10}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\FloatTok{0.5}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FloatTok{1.2}\NormalTok{, }\StringTok{"cm"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## `stat_bin()` using `bins = 30`. Pick better value with `binwidth`.
\end{verbatim}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-15-1.pdf}

\subparagraph{\texorpdfstring{Ratings per
user\autocite{MRS-R-BEST}}{Ratings per user{[}@MRS-R-BEST{]}}}\label{ratings-per-usermrs-r-best}

\hfill\break

User rating count (activity measure)

\hfill\break

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{print}\NormalTok{(edx }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{group\_by}\NormalTok{(userId) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{slice\_head}\NormalTok{(}\AttributeTok{n =} \DecValTok{10}\NormalTok{)}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 10 x 2
##    userId count
##     <int> <int>
##  1      1    19
##  2      2    17
##  3      3    31
##  4      4    35
##  5      5    74
##  6      6    39
##  7      7    96
##  8      8   727
##  9      9    21
## 10     10   112
\end{verbatim}

User rating summary

\hfill\break

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{summary}\NormalTok{(edx }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(userId) }\SpecialCharTok{|\textgreater{}} \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}} \FunctionTok{select}\NormalTok{(count))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      count       
##  Min.   :  10.0  
##  1st Qu.:  32.0  
##  Median :  62.0  
##  Mean   : 128.8  
##  3rd Qu.: 141.0  
##  Max.   :6616.0
\end{verbatim}

Ratings per user plot

\hfill\break

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{edx }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{group\_by}\NormalTok{(userId) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ userId, }\AttributeTok{y =}\NormalTok{ count)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.2}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#4020dd"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{color =} \StringTok{"red"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Ratings per user"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{xlab}\NormalTok{(}\StringTok{"Users"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Number of ratings"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ comma) }\SpecialCharTok{+}
  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{n.breaks =} \DecValTok{10}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_economist}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \SpecialCharTok{{-}}\DecValTok{5}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{axis.title.y =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \DecValTok{10}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\FloatTok{0.5}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FloatTok{1.2}\NormalTok{, }\StringTok{"cm"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## `geom_smooth()` using method = 'gam' and formula = 'y ~ s(x, bs = "cs")'
\end{verbatim}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-18-1.pdf}

Users' rating histogram

\hfill\break

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{edx }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{group\_by}\NormalTok{(userId) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ count)) }\SpecialCharTok{+}
  \FunctionTok{geom\_histogram}\NormalTok{(}\AttributeTok{fill =} \StringTok{"\#8888ff"}\NormalTok{, }\AttributeTok{color =} \StringTok{"\#4020dd"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Users\textquotesingle{} rating histogram"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{xlab}\NormalTok{(}\StringTok{"Rating count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Number of users"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ comma) }\SpecialCharTok{+}
  \FunctionTok{scale\_x\_log10}\NormalTok{(}\AttributeTok{n.breaks =} \DecValTok{10}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_economist}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \SpecialCharTok{{-}}\DecValTok{5}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{axis.title.y =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \DecValTok{10}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\FloatTok{0.5}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FloatTok{1.2}\NormalTok{, }\StringTok{"cm"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## `stat_bin()` using `bins = 30`. Pick better value with `binwidth`.
\end{verbatim}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-19-1.pdf}

\subparagraph{}\label{section}

\hfill\break

\subparagraph{}\label{section-1}

\hfill\break

\hfill\break

\subsection{Methods / Analysis}\label{methods-analysis}

\subsubsection{Defining helper
functions}\label{defining-helper-functions}

\hfill\break

Let's define some helper functions that we will use in our subsequent
analysis:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{start\_date }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{()\{}
  \FunctionTok{print}\NormalTok{(}\FunctionTok{date}\NormalTok{())}
  \FunctionTok{Sys.time}\NormalTok{()}
\NormalTok{\}}
\NormalTok{end\_date }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(start)\{}
  \FunctionTok{print}\NormalTok{(}\FunctionTok{date}\NormalTok{())}
  \FunctionTok{Sys.time}\NormalTok{() }\SpecialCharTok{{-}}\NormalTok{ start}
\NormalTok{\}}
\NormalTok{rmse }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(r) }\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mean}\NormalTok{(r}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}
\NormalTok{RMSE }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(true\_ratings, predicted\_ratings)\{}
  \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mean}\NormalTok{((true\_ratings }\SpecialCharTok{{-}}\NormalTok{ predicted\_ratings)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}
\NormalTok{\}}

\CommentTok{\# Because we know ratings can’t be below 0.5 or above 5, }
\CommentTok{\# we define the function clamp:}
\NormalTok{clamp }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x, }\AttributeTok{min =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{max =} \DecValTok{5}\NormalTok{) }\FunctionTok{pmax}\NormalTok{(}\FunctionTok{pmin}\NormalTok{(x, max), min)}
\end{Highlighting}
\end{Shaded}

\subsubsection{Preparing train and set
datasets}\label{preparing-train-and-set-datasets}

\hfill\break
First, let's note that we have 10677 different movies:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{n\_movies }\OtherTok{\textless{}{-}} \FunctionTok{n\_distinct}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{movieId)}
\FunctionTok{print}\NormalTok{(n\_movies)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 10677
\end{verbatim}

and 69878 different users in the dataset:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{n\_users }\OtherTok{\textless{}{-}} \FunctionTok{n\_distinct}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{userId)}
\FunctionTok{print}\NormalTok{(n\_users)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 69878
\end{verbatim}

Now, note the expressions below which confirm the fact explained in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movielens-data}{Section
\emph{23.1.1 Movielens data}} of the \emph{Course
Textbook}\autocite{IDS2} that not every user rated every movie:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{max\_possible\_ratings }\OtherTok{\textless{}{-}}\NormalTok{ n\_movies}\SpecialCharTok{*}\NormalTok{n\_users}
\FunctionTok{sprintf}\NormalTok{(}\StringTok{"Maximum possible ratings: \%s"}\NormalTok{, max\_possible\_ratings)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "Maximum possible ratings: 746087406"
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{sprintf}\NormalTok{(}\StringTok{"Rows in \textasciigrave{}edx\textasciigrave{} dataset: \%s"}\NormalTok{, dim\_edx[}\DecValTok{1}\NormalTok{])}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "Rows in `edx` dataset: 9000055"
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{sprintf}\NormalTok{(}\StringTok{"Not every movie was rated: \%s"}\NormalTok{, max\_possible\_ratings }\SpecialCharTok{\textgreater{}}\NormalTok{ dim\_edx[}\DecValTok{1}\NormalTok{])}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "Not every movie was rated: TRUE"
\end{verbatim}

As also explained in that section, we can think of these data as a very
large matrix, with users on the rows and movies on the columns, with
many empty cells. Therefore, we can think of a recommendation system as
filling in the \texttt{NA}s in the dataset for the movies that some or
all the users do not rate. A sample from the \texttt{edx} data below
illustrates this idea\autocite{IDS2_23-1-1}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{keep }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{count}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{top\_n}\NormalTok{(}\DecValTok{4}\NormalTok{, n) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{pull}\NormalTok{(movieId)}

\NormalTok{tab }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{filter}\NormalTok{(movieId }\SpecialCharTok{\%in\%}\NormalTok{ keep) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{filter}\NormalTok{(userId }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\DecValTok{13}\SpecialCharTok{:}\DecValTok{20}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{select}\NormalTok{(userId, title, rating) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{title =} \FunctionTok{str\_remove}\NormalTok{(title, }\StringTok{", The"}\NormalTok{),}
         \AttributeTok{title =} \FunctionTok{str\_remove}\NormalTok{(title, }\StringTok{":.*"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =} \StringTok{"title"}\NormalTok{, }\AttributeTok{values\_from =} \StringTok{"rating"}\NormalTok{)}

\FunctionTok{print}\NormalTok{(tab)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 5 x 5
##   userId `Pulp Fiction (1994)` `Jurassic Park (1993)` Silence of the Lambs (19~1
##    <int>                 <dbl>                  <dbl>                      <dbl>
## 1     13                     4                     NA                         NA
## 2     16                    NA                      3                         NA
## 3     17                    NA                     NA                          5
## 4     18                     5                      3                          5
## 5     19                    NA                      1                         NA
## # i abbreviated name: 1: `Silence of the Lambs (1991)`
## # i 1 more variable: `Forrest Gump (1994)` <dbl>
\end{verbatim}

The following plot of the matrix for a random sample of 100 movies and
100 users with yellow indicating a user/movie combination for which we
have a rating shows how \emph{sparse} the matrix is:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{users }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(}\FunctionTok{unique}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{userId), }\DecValTok{100}\NormalTok{)}

\NormalTok{rafalib}\SpecialCharTok{::}\FunctionTok{mypar}\NormalTok{()}
\NormalTok{edx}\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{filter}\NormalTok{(userId }\SpecialCharTok{\%in\%}\NormalTok{ users) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{select}\NormalTok{(userId, movieId, rating) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{rating =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ movieId, }\AttributeTok{values\_from =}\NormalTok{ rating) }\SpecialCharTok{|\textgreater{}} 
\NormalTok{  (\textbackslash{}(mat) mat[, }\FunctionTok{sample}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(mat), }\DecValTok{100}\NormalTok{)])() }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{as.matrix}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{t}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{image}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\DecValTok{100}\NormalTok{, }\DecValTok{1}\SpecialCharTok{:}\DecValTok{100}\NormalTok{, }\AttributeTok{z =}\NormalTok{ \_ , }\AttributeTok{xlab =} \StringTok{"Movies"}\NormalTok{, }\AttributeTok{ylab =} \StringTok{"Users"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics[width=0.4\linewidth]{capstone-movielens-report.draft1_files/figure-latex/sparsity-of-movie-recs-1}

Further observations highlighted there that, as we can see from the
distributions the author presented, some movies get rated more than
others, and some users are more active than others in rating movies:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{p1 }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{count}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(n)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_histogram}\NormalTok{(}\AttributeTok{bins =} \DecValTok{30}\NormalTok{, }\AttributeTok{color =} \StringTok{"black"}\NormalTok{) }\SpecialCharTok{+} 
  \FunctionTok{scale\_x\_log10}\NormalTok{() }\SpecialCharTok{+} 
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Movies"}\NormalTok{)}

\NormalTok{p2 }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{count}\NormalTok{(userId) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(n)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_histogram}\NormalTok{(}\AttributeTok{bins =} \DecValTok{30}\NormalTok{, }\AttributeTok{color =} \StringTok{"black"}\NormalTok{) }\SpecialCharTok{+} 
  \FunctionTok{scale\_x\_log10}\NormalTok{() }\SpecialCharTok{+} 
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Users"}\NormalTok{)}

\NormalTok{gridExtra}\SpecialCharTok{::}\FunctionTok{grid.arrange}\NormalTok{(p2, p1, }\AttributeTok{ncol =} \DecValTok{2}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/movie-id-and-user-hists-1.pdf}

Taking into consideration these observations, we came up with a decision
to use the data from the dataset only for users who have provided at
least 100 ratings.

Now let's split the \texttt{edx} dataset into a training set, which we
will use to build and train our models, and a test set in which we will
compute the accuracy of our predictions, the way described in the
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movielens-data}{Section
23.1.1 Movielens data} of the \emph{Course Textbook} mentioned
above\autocite{IDS2_23-1-1}:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Let\textquotesingle{}s ignore the data for users who have not provided at least 100 ratings:}
\NormalTok{edx100 }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{group\_by}\NormalTok{(userId) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{filter}\NormalTok{(}\FunctionTok{n}\NormalTok{() }\SpecialCharTok{\textgreater{}=} \DecValTok{100}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{ungroup}\NormalTok{()}

\FunctionTok{print}\NormalTok{(edx100 }\SpecialCharTok{|\textgreater{}} \FunctionTok{summarize}\NormalTok{(}\FunctionTok{n\_distinct}\NormalTok{(userId), }\FunctionTok{n\_distinct}\NormalTok{(movieId)))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 1 x 2
##   `n_distinct(userId)` `n_distinct(movieId)`
##                  <int>                 <int>
## 1                24115                 10665
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# For each one of these users, we will split their ratings into 80\% for training }
\CommentTok{\# and 20\% for testing:}

\FunctionTok{set.seed}\NormalTok{(}\DecValTok{2006}\NormalTok{)}
\NormalTok{indexes }\OtherTok{\textless{}{-}} \FunctionTok{split}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(edx100), edx100}\SpecialCharTok{$}\NormalTok{userId)}
\NormalTok{test\_ind }\OtherTok{\textless{}{-}} \FunctionTok{sapply}\NormalTok{(indexes, }\ControlFlowTok{function}\NormalTok{(i) }\FunctionTok{sample}\NormalTok{(i, }\FunctionTok{ceiling}\NormalTok{(}\FunctionTok{length}\NormalTok{(i)}\SpecialCharTok{*}\NormalTok{.}\DecValTok{2}\NormalTok{))) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{unlist}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{sort}\NormalTok{()}

\NormalTok{test\_set }\OtherTok{\textless{}{-}}\NormalTok{ edx100[test\_ind,] }
\NormalTok{train\_set }\OtherTok{\textless{}{-}}\NormalTok{ edx100[}\SpecialCharTok{{-}}\NormalTok{test\_ind,]}

\CommentTok{\# To make sure we don’t include movies in the training set that should not be }
\CommentTok{\# there, we remove entries using the semi\_join function:}
\NormalTok{test\_set }\OtherTok{\textless{}{-}}\NormalTok{ test\_set }\SpecialCharTok{|\textgreater{}} \FunctionTok{semi\_join}\NormalTok{(train\_set, }\AttributeTok{by =} \StringTok{"movieId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \FunctionTok{as.data.frame}\NormalTok{()}
\FunctionTok{summary}\NormalTok{(test\_set)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      userId         movieId          rating        timestamp        
##  Min.   :    8   Min.   :    1   Min.   :0.500   Min.   :8.248e+08  
##  1st Qu.:18161   1st Qu.: 1022   1st Qu.:3.000   1st Qu.:9.655e+08  
##  Median :35666   Median : 2109   Median :3.500   Median :1.058e+09  
##  Mean   :35902   Mean   : 4616   Mean   :3.473   Mean   :1.051e+09  
##  3rd Qu.:53645   3rd Qu.: 3993   3rd Qu.:4.000   3rd Qu.:1.135e+09  
##  Max.   :71565   Max.   :65133   Max.   :5.000   Max.   :1.231e+09  
##     title              genres         
##  Length:1397040     Length:1397040    
##  Class :character   Class :character  
##  Mode  :character   Mode  :character  
##                                       
##                                       
## 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{train\_set }\OtherTok{\textless{}{-}} \FunctionTok{mutate}\NormalTok{(train\_set, }\AttributeTok{userId =} \FunctionTok{factor}\NormalTok{(userId), }\AttributeTok{movieId =} \FunctionTok{factor}\NormalTok{(movieId))}
\FunctionTok{summary}\NormalTok{(train\_set)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      userId           movieId            rating        timestamp        
##  59269  :   5292   356    :  12769   Min.   :0.500   Min.   :8.248e+08  
##  67385  :   5088   296    :  12439   1st Qu.:3.000   1st Qu.:9.657e+08  
##  14463  :   3718   480    :  12390   Median :3.500   Median :1.059e+09  
##  68259  :   3228   593    :  12333   Mean   :3.472   Mean   :1.051e+09  
##  27468  :   3218   260    :  12142   3rd Qu.:4.000   3rd Qu.:1.135e+09  
##  19635  :   3016   1196   :  11586   Max.   :5.000   Max.   :1.231e+09  
##  (Other):5516391   (Other):5466292                                      
##     title              genres         
##  Length:5539951     Length:5539951    
##  Class :character   Class :character  
##  Mode  :character   Mode  :character  
##                                       
##                                       
##                                       
## 
\end{verbatim}

We will use the array representation described in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html\#sec-anova}{Section
17.5 of the Textbook}, for the training data: we denote ranking for
movie \(j\) by user \(i\) as \(y_{i,j}\). To create this matrix, we use
\texttt{tidyr::pivot\_wider} function:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{y }\OtherTok{\textless{}{-}}\NormalTok{ dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(train\_set, movieId, userId, rating) }\SpecialCharTok{|\textgreater{}}
\FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ movieId, }\AttributeTok{values\_from =}\NormalTok{ rating) }\SpecialCharTok{|\textgreater{}}
\FunctionTok{column\_to\_rownames}\NormalTok{(}\StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
\FunctionTok{as.matrix}\NormalTok{()}

\FunctionTok{dim}\NormalTok{(y)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 24115 10630
\end{verbatim}

To be able to map movie IDs to titles we create the following lookup
table:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{movie\_map }\OtherTok{\textless{}{-}}\NormalTok{ train\_set }\SpecialCharTok{|\textgreater{}}\NormalTok{ dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(movieId, title, genres) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{distinct}\NormalTok{(movieId, }\AttributeTok{.keep\_all =} \ConstantTok{TRUE}\NormalTok{)}

\FunctionTok{summary}\NormalTok{(movie\_map)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##     movieId         title              genres         
##  1      :    1   Length:10630       Length:10630      
##  2      :    1   Class :character   Class :character  
##  3      :    1   Mode  :character   Mode  :character  
##  4      :    1                                        
##  5      :    1                                        
##  6      :    1                                        
##  (Other):10624
\end{verbatim}

Note that titles cannot be considered unique, so we can't use them as
IDs\autocite{IDS2_23-1-1}.

\subsubsection{Naive Model}\label{naive-model}

\hfill\break
Let's begin our analysis by evaluating the simplest model described in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#a-first-model}{Section
\emph{23.3 The First Model} of the \emph{Course Textbook}}, and then
gradually refine it through further research. It is about a model that
assumes the same rating for all movies and users with all the
differences explained by random variation would look as follows:

\[
Y_{i,j} = \mu + \varepsilon_{i,j}
\]

with \(\varepsilon_{i,j}\) independent errors sampled from the same
distribution centered at 0 and \(\mu\) the \emph{true} rating for all
movies.

We know that the estimate that minimizes the RMSE is the least squares
estimate of \(\mu\) and, in this case, is the average of all ratings:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(y, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{print}\NormalTok{(mu)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 3.47184
\end{verbatim}

If we predict all unknown ratings with \(\hat{\mu}\), we obtain the
following RMSE:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{rmse}\NormalTok{(test\_set}\SpecialCharTok{$}\NormalTok{rating }\SpecialCharTok{{-}}\NormalTok{ mu)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 1.054739
\end{verbatim}

If we plug in any other number, we will get a higher RMSE. Let's prove
that by the following small investigation:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{deviation }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{6}\NormalTok{, }\FloatTok{0.1}\NormalTok{) }\SpecialCharTok{{-}} \DecValTok{3}
\FunctionTok{print}\NormalTok{(deviation)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##  [1] -3.0 -2.9 -2.8 -2.7 -2.6 -2.5 -2.4 -2.3 -2.2 -2.1 -2.0 -1.9 -1.8 -1.7 -1.6
## [16] -1.5 -1.4 -1.3 -1.2 -1.1 -1.0 -0.9 -0.8 -0.7 -0.6 -0.5 -0.4 -0.3 -0.2 -0.1
## [31]  0.0  0.1  0.2  0.3  0.4  0.5  0.6  0.7  0.8  0.9  1.0  1.1  1.2  1.3  1.4
## [46]  1.5  1.6  1.7  1.8  1.9  2.0  2.1  2.2  2.3  2.4  2.5  2.6  2.7  2.8  2.9
## [61]  3.0
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{rmse\_value }\OtherTok{\textless{}{-}} \FunctionTok{sapply}\NormalTok{(deviation, }\ControlFlowTok{function}\NormalTok{(diff)\{}
  \FunctionTok{rmse}\NormalTok{(test\_set}\SpecialCharTok{$}\NormalTok{rating }\SpecialCharTok{{-}}\NormalTok{ mu }\SpecialCharTok{+}\NormalTok{ diff)}
\NormalTok{\})}

\FunctionTok{plot}\NormalTok{(deviation, rmse\_value, }\AttributeTok{type =} \StringTok{"l"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-32-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{sprintf}\NormalTok{(}\StringTok{"Minimum RMSE is achieved when the deviation from the mean is: \%s"}\NormalTok{, }
\NormalTok{        deviation[}\FunctionTok{which.min}\NormalTok{(rmse\_value)])}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "Minimum RMSE is achieved when the deviation from the mean is: 0"
\end{verbatim}

To win the grand prize of \$1,000,000, a participating team had to get
an RMSE of at least 0.8563\autocite{BigChaosSln}. So we can definitely
do better!\autocite{IDS2_23-3}

\subsubsection{Taking into account User
effects}\label{taking-into-account-user-effects}

\hfill\break
To improve our model let's now take into consideration user effects as
explained in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#user-effects}{Section
\emph{23.4 User effects} of the \emph{Course Textbook}}. If we visualize
the average rating for each user the way the
\href{https://x.com/rafalab}{the author} shows, we can see that there is
substantial variability in the average ratings across users:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{hist}\NormalTok{(}\FunctionTok{rowMeans}\NormalTok{(y, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{), }\AttributeTok{nclass =} \DecValTok{30}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-33-1.pdf}

Following the author's further explanation, to account for this
variability, we will use a linear model with a \emph{treatment effect}
\(\alpha_i\) for each user. The sum \(\mu+\alpha_i\) can be interpreted
as the typical rating user \(i\) gives to movies. So we write the model
as follows:

\[
Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
\]

Statistics textbooks refer to the \(\alpha\)s as treatment effects. In
the Netflix challenge papers, they refer to them as
\emph{bias}\autocite{IDS2_23-4,MFT_RS}.

As it is stated here\autocite{IDS2_23-4}, it can be shown that the least
squares estimate \(\hat{\alpha}_i\) is just the average of
\(y_{i,j} - \hat{\mu}\) for each user \(i\). So we compute them this
way:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{a }\OtherTok{\textless{}{-}} \FunctionTok{rowMeans}\NormalTok{(y }\SpecialCharTok{{-}}\NormalTok{ mu, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

Finally, we are ready to compute the \texttt{RMSE} (additionally using
the helper function \texttt{clamp} we defined above to keep predictions
in the proper range):

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Compute the RMSE taking into account user effects:}
\NormalTok{user\_effects\_rmse }\OtherTok{\textless{}{-}}\NormalTok{ test\_set }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(a)), }\AttributeTok{a =}\NormalTok{ a), }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{resid =}\NormalTok{ rating }\SpecialCharTok{{-}} \FunctionTok{clamp}\NormalTok{(mu }\SpecialCharTok{+}\NormalTok{ a)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{filter}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(resid)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{pull}\NormalTok{(resid) }\SpecialCharTok{|\textgreater{}} \FunctionTok{rmse}\NormalTok{()}

\FunctionTok{print}\NormalTok{(user\_effects\_rmse)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 0.9707208
\end{verbatim}

\subsubsection{Taking into account Movie
effects}\label{taking-into-account-movie-effects}

\hfill\break
In
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movie-effects}{Section
\emph{23.5 Movie effects} of the \emph{Course Textbook}} the author
draws our attention to the fact that some movies are generally rated
higher than others. He also explains that~a linear model with a
\emph{treatment effect} \(\beta_j\) for each movie can be used in this
case, which can be interpreted as movie effect or the difference between
the average ranking for movie \(j\) and the overall average \(\mu\):

\[
Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
\] The author then shows how to use an approximation by first computing
the least square estimate \(\hat{\mu}\) and \(\hat{\alpha}_i\), and then
estimating \(\hat{\beta}_j\) as the average of the residuals
\(y_{i,j} - \hat{\mu} - \hat{\alpha}_i\):

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{b }\OtherTok{\textless{}{-}} \FunctionTok{colMeans}\NormalTok{(y }\SpecialCharTok{{-}}\NormalTok{ mu }\SpecialCharTok{{-}}\NormalTok{ a, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

We can now construct predictors and see how much the \texttt{RMSE}
improves\autocite{IDS2_23-5}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{user\_and\_movie\_effects\_rmse }\OtherTok{\textless{}{-}}\NormalTok{ test\_set }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(a)), }\AttributeTok{a =}\NormalTok{ a), }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{movieId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(b)), }\AttributeTok{b =}\NormalTok{ b), }\AttributeTok{by =} \StringTok{"movieId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{resid =}\NormalTok{ rating }\SpecialCharTok{{-}} \FunctionTok{clamp}\NormalTok{(mu }\SpecialCharTok{+}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ b)) }\SpecialCharTok{|\textgreater{}}  
    \FunctionTok{filter}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(resid)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{pull}\NormalTok{(resid) }\SpecialCharTok{|\textgreater{}} \FunctionTok{rmse}\NormalTok{()}

\FunctionTok{print}\NormalTok{(user\_and\_movie\_effects\_rmse)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 0.8662207
\end{verbatim}

\subsubsection{Utilizing Penalized least
squares}\label{utilizing-penalized-least-squares}

\hfill\break
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#penalized-least-squares}{Section
\emph{23.6 Penalized least squares} of the \emph{Course Textbook}}
explains why and how we should use \emph{Penalized least squares} to
improve our predictions. The author also explains that the general idea
of penalized regression is to control the total variability of the movie
effects: \(\sum_{j=1}^n \beta_j^2\). Specifically, instead of minimizing
the least squares equation, we minimize an equation that adds a penalty:

\[ 
\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
\] The first term is just the sum of squares and the second is a penalty
that gets larger when many \(\beta_i\)s are large. Using calculus, we
can actually show that the values of \(\beta_i\) that minimize this
equation are:

\[
\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
\]

where \(n_j\) is the number of ratings made for movie \(j\).

This approach will have our desired effect: when our sample size \(n_j\)
is very large, we obtain a stable estimate and the penalty \(\lambda\)
is effectively ignored since \(n_j+\lambda \approx n_j\). Yet when the
\(n_j\) is small, then the estimate \(\hat{\beta}_i(\lambda)\) is
shrunken towards 0. The larger the \(\lambda\), the more we
shrink\autocite{IDS2_23-6}.

\paragraph{Support function}\label{support-function}

\hfill\break
We will use the following function to calculate \emph{RMSE} in this
section:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{reg\_rmse }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(b)\{}
\NormalTok{  test\_set }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(a)), }\AttributeTok{a =}\NormalTok{ a), }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{movieId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(b)), }\AttributeTok{b =}\NormalTok{ b), }\AttributeTok{by =} \StringTok{"movieId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{resid =}\NormalTok{ rating }\SpecialCharTok{{-}} \FunctionTok{clamp}\NormalTok{(mu }\SpecialCharTok{+}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ b)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{filter}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(resid)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{pull}\NormalTok{(resid) }\SpecialCharTok{|\textgreater{}} \FunctionTok{rmse}\NormalTok{()}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

Let's now figure out the \(\lambda\) that minimizes the \emph{RMSE}:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Here we will simply compute the RMSE for different values of \textasciigrave{}lambda\textasciigrave{} }
\NormalTok{n }\OtherTok{\textless{}{-}} \FunctionTok{colSums}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(y))}

\NormalTok{sums }\OtherTok{\textless{}{-}} \FunctionTok{colSums}\NormalTok{(y }\SpecialCharTok{{-}}\NormalTok{ mu }\SpecialCharTok{{-}}\NormalTok{ a, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)}
\NormalTok{lambdas }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{10}\NormalTok{, }\FloatTok{0.1}\NormalTok{)}

\NormalTok{rmses }\OtherTok{\textless{}{-}} \FunctionTok{sapply}\NormalTok{(lambdas, }\ControlFlowTok{function}\NormalTok{(lambda)\{}
\NormalTok{  b }\OtherTok{\textless{}{-}}\NormalTok{  sums }\SpecialCharTok{/}\NormalTok{ (n }\SpecialCharTok{+}\NormalTok{ lambda)}
  \FunctionTok{reg\_rmse}\NormalTok{(b)}
\NormalTok{\})}

\CommentTok{\# Here is a plot of the RMSE versus \textasciigrave{}lambda\textasciigrave{}:}
\FunctionTok{plot}\NormalTok{(lambdas, rmses, }\AttributeTok{type =} \StringTok{"l"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-39-1.pdf}
Now we can determine the minimal \emph{RMSE}:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{print}\NormalTok{(}\FunctionTok{min}\NormalTok{(rmses))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 0.8661143
\end{verbatim}

which is achieved for the following \(\lambda\):

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{lambda }\OtherTok{\textless{}{-}}\NormalTok{ lambdas[}\FunctionTok{which.min}\NormalTok{(rmses)] }
\FunctionTok{print}\NormalTok{(lambda)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 3.2
\end{verbatim}

Using this \(\lambda\) we can compute the regularized estimates:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{b\_reg }\OtherTok{\textless{}{-}}\NormalTok{ sums }\SpecialCharTok{/}\NormalTok{ (n }\SpecialCharTok{+}\NormalTok{ lambda)}

\FunctionTok{str}\NormalTok{(b\_reg)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##  Named num [1:10630] -0.516 0.327 -0.903 -0.154 -0.29 ...
##  - attr(*, "names")= chr [1:10630] "5" "6" "19" "22" ...
\end{verbatim}

Finally, let's verify that the penalized estimates
\(\hat{b}_i(\lambda)\) we have just computed actually result in the
minimal \emph{RMSE} figured out above:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{reg\_rmse}\NormalTok{(b\_reg)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 0.8661143
\end{verbatim}

\subsubsection{Accounting for Date
effects}\label{accounting-for-date-effects}

\subparagraph{\texorpdfstring{Yearly rating
count\autocite{MRS-R-BEST}}{Yearly rating count{[}@MRS-R-BEST{]}}}\label{yearly-rating-countmrs-r-best}

\hfill\break

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{print}\NormalTok{(edx }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{year =} \FunctionTok{year}\NormalTok{(}\FunctionTok{as\_datetime}\NormalTok{(timestamp, }\AttributeTok{origin =} \StringTok{"1970{-}01{-}01"}\NormalTok{))) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{group\_by}\NormalTok{(year) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{())}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 15 x 2
##     year   count
##    <int>   <int>
##  1  1995       2
##  2  1996  942772
##  3  1997  414101
##  4  1998  181634
##  5  1999  709893
##  6  2000 1144349
##  7  2001  683355
##  8  2002  524959
##  9  2003  619938
## 10  2004  691429
## 11  2005 1059277
## 12  2006  689315
## 13  2007  629168
## 14  2008  696740
## 15  2009   13123
\end{verbatim}

\subparagraph{\texorpdfstring{Average rating per year
plot\autocite{MRS-R-BEST}}{Average rating per year plot{[}@MRS-R-BEST{]}}}\label{average-rating-per-year-plotmrs-r-best}

\hfill\break

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{edx }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{year =} \FunctionTok{year}\NormalTok{(}\FunctionTok{as\_datetime}\NormalTok{(timestamp, }\AttributeTok{origin =} \StringTok{"1970{-}01{-}01"}\NormalTok{))) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{group\_by}\NormalTok{(year) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{rating\_avg =} \FunctionTok{mean}\NormalTok{(rating)) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ year, }\AttributeTok{y =}\NormalTok{ rating\_avg)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{stat =} \StringTok{"identity"}\NormalTok{, }\AttributeTok{fill =} \StringTok{"\#8888ff"}\NormalTok{) }\SpecialCharTok{+} 
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Average rating per year"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{xlab}\NormalTok{(}\StringTok{"Year"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Average rating"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ comma) }\SpecialCharTok{+} 
  \FunctionTok{theme\_economist}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \SpecialCharTok{{-}}\DecValTok{5}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{axis.title.y =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \DecValTok{10}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{), }
        \AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\FloatTok{0.5}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FloatTok{1.2}\NormalTok{, }\StringTok{"cm"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-45-1.pdf}

We use the following models to account for the \texttt{date} effect:

\[
Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
\]

\subsubsection{Accounting for Genre
effect}\label{accounting-for-genre-effect}

\hfill\break
As mentioned in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#exercises}{Section
23.7: Exercises} of the \emph{Chapter ``23 Regularization'' of the
Course Textbook} the \texttt{Movielens} dataset also has a genres
column. This column includes every genre that applies to the movie (some
movies fall under several genres)\autocite{IDS2_23-7}.

The plot below shows strong evidence of a genre effect (for illustrative
purposes, the plot shows only categories with more than 20, 000
ratings).

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Preparing data for plotting:}
\NormalTok{genre\_ratins\_grp }\OtherTok{\textless{}{-}}\NormalTok{ train\_set }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{genre\_categories =} \FunctionTok{as.factor}\NormalTok{(genres)) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{group\_by}\NormalTok{(genre\_categories) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{n =} \FunctionTok{n}\NormalTok{(), }\AttributeTok{rating\_avg =} \FunctionTok{mean}\NormalTok{(rating), }\AttributeTok{se =} \FunctionTok{sd}\NormalTok{(rating)}\SpecialCharTok{/}\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{n}\NormalTok{())) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{filter}\NormalTok{(n }\SpecialCharTok{\textgreater{}} \DecValTok{20000}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{genres =} \FunctionTok{reorder}\NormalTok{(genre\_categories, rating\_avg)) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{select}\NormalTok{(genres, rating\_avg, se, n)}

\FunctionTok{dim}\NormalTok{(genre\_ratins\_grp)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 53  4
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{genre\_ratins\_grp\_sorted }\OtherTok{\textless{}{-}}\NormalTok{ genre\_ratins\_grp }\SpecialCharTok{|\textgreater{}} \FunctionTok{sort\_by.data.frame}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ rating\_avg)}
\FunctionTok{print}\NormalTok{(genre\_ratins\_grp\_sorted)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 53 x 4
##    genres                  rating_avg      se      n
##    <fct>                        <dbl>   <dbl>  <int>
##  1 Comedy|Horror                 2.83 0.00701  24892
##  2 Horror                        2.85 0.00556  48671
##  3 Children|Comedy               2.86 0.00575  40435
##  4 Horror|Sci-Fi                 2.88 0.00787  20524
##  5 Action|Comedy                 2.96 0.00581  34118
##  6 Comedy|Sci-Fi                 3.06 0.00668  27888
##  7 Action|Sci-Fi                 3.08 0.00749  27971
##  8 Horror|Thriller               3.09 0.00543  49751
##  9 Action|Adventure|Comedy       3.17 0.00616  28256
## 10 Comedy                        3.21 0.00167 439352
## # i 43 more rows
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Creating plot:}
\NormalTok{genre\_ratins\_grp }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ genres, }\AttributeTok{y =}\NormalTok{ rating\_avg, }\AttributeTok{ymin =}\NormalTok{ rating\_avg }\SpecialCharTok{{-}} \DecValTok{2}\SpecialCharTok{*}\NormalTok{se, }\AttributeTok{ymax =}\NormalTok{ rating\_avg }\SpecialCharTok{+} \DecValTok{2}\SpecialCharTok{*}\NormalTok{se)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{geom\_errorbar}\NormalTok{() }\SpecialCharTok{+} 
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Average rating per Genre"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Average rating"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.text.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{angle =} \DecValTok{90}\NormalTok{, }\AttributeTok{hjust =} \DecValTok{1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-46-1.pdf}
Below are worst and best ratings categories:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{sprintf}\NormalTok{(}\StringTok{"The worst ratings are for the genre category: \%s"}\NormalTok{,}
\NormalTok{        genre\_ratins\_grp}\SpecialCharTok{$}\NormalTok{genres[}\FunctionTok{which.min}\NormalTok{(genre\_ratins\_grp}\SpecialCharTok{$}\NormalTok{genres)])}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "The worst ratings are for the genre category: Comedy|Horror"
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{sprintf}\NormalTok{(}\StringTok{"The best ratings are for the genre category: \%s"}\NormalTok{,}
\NormalTok{        genre\_ratins\_grp}\SpecialCharTok{$}\NormalTok{genres[}\FunctionTok{which.max}\NormalTok{(genre\_ratins\_grp}\SpecialCharTok{$}\NormalTok{genres)])}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "The best ratings are for the genre category: Comedy|Crime|Drama"
\end{verbatim}

Another way of visualizing a genre effect is shown in the section
\href{https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook\#Average-rating-for-each-genre}{Average
rating for each genre} of the article ``Movie Recommendation System
using R - BEST'' written by
\href{https://www.kaggle.com/amirmotefaker}{Amir
Moterfaker}\autocite{MRS-R-BEST}:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# For better visibility, we reduce the data for plotting }
\CommentTok{\# while keeping the worst and best rating rows:}
\NormalTok{plot\_ind }\OtherTok{\textless{}{-}} \FunctionTok{odd}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(genre\_ratins\_grp))}
\NormalTok{plot\_dat }\OtherTok{\textless{}{-}}\NormalTok{ genre\_ratins\_grp\_sorted[plot\_ind,] }

\NormalTok{plot\_dat }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ rating\_avg, }\AttributeTok{y =}\NormalTok{ genres)) }\SpecialCharTok{+}
  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Genre Average Rating"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{stat =} \StringTok{"identity"}\NormalTok{, }\AttributeTok{width =} \FloatTok{0.6}\NormalTok{, }\AttributeTok{fill =} \StringTok{"\#8888ff"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{xlab}\NormalTok{(}\StringTok{"Average ratings"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{ylab}\NormalTok{(}\StringTok{"Genres"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{labels =}\NormalTok{ comma, }\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.0}\NormalTok{, }\FloatTok{5.0}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{theme\_economist}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{plot.title =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \FloatTok{3.5}\NormalTok{),}
        \AttributeTok{axis.title.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \SpecialCharTok{{-}}\DecValTok{5}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{),}
        \AttributeTok{axis.title.y =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \DecValTok{10}\NormalTok{, }\AttributeTok{face =} \StringTok{"bold"}\NormalTok{),}
        \AttributeTok{axis.text.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \DecValTok{1}\NormalTok{, }\AttributeTok{hjust =} \DecValTok{1}\NormalTok{, }\AttributeTok{angle =} \DecValTok{0}\NormalTok{),}
        \AttributeTok{axis.text.y =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{vjust =} \FloatTok{0.25}\NormalTok{, }\AttributeTok{hjust =} \DecValTok{1}\NormalTok{, }\AttributeTok{size =} \DecValTok{8}\NormalTok{),}
        \AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\FloatTok{0.5}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FloatTok{1.2}\NormalTok{, }\StringTok{"cm"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-48-1.pdf}

If we define \(g_{i,j}\) as the genre for user's \(i\) rating of movie
\(j\), we can use the following models to account for the \texttt{genre}
effect:

\[
Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \sum_{k=1}^K x_{i,j}^k \gamma_k + \varepsilon_{i,j}
\]

with \(x^k_{i,j} = 1\) if \(g_{i,j}\) is genre \(k\).

\subsection{Conclusion}\label{conclusion}

Hello Conclusion!

This is a great conclusion, isn't it?!!

\printbibliography

\end{document}

### 2025-02-19 r/capstone-movielens.draft1.R

@@ -34,7 +34,7 @@ library(pak)
 
 ## Introduction / Overview / Executive Summar
 
-### Datasets
+### Datasets ===================================================================
 
 # To start with we have to generate two datasets derived from the MovieLens one:
 #   
@@ -124,7 +124,7 @@ edx |>
         axis.title.y = element_text(vjust = 10, face = "bold"), 
         plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
 
-## Methods / Analysis ----------------------------------------------------------
+## Methods / Analysis ==========================================================
 ### Defining helper functions --------------------------------------------------
 
 #> Let's define some helper functions that we will use in our subsequent analysis:
@@ -600,33 +600,60 @@ print(date_smoothed_rmse)
 #> every genre that applies to the movie 
 #> (some movies fall under several genres)[@IDS2_23-7].
 
-train_set_grp <- train_set |> 
+# Preparing data for plotting:
+genre_ratins_grp <- train_set |> 
   mutate(genre_categories = as.factor(genres)) |>
   group_by(genre_categories) |>
-  summarize(n = n(), avg = mean(rating), se = sd(rating)/sqrt(n())) |>
+  summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
   filter(n > 20000) |> 
-  mutate(genres = reorder(genre_categories, avg)) |>
-  select(genres, avg, se, n)
+  mutate(genres = reorder(genre_categories, rating_avg)) |>
+  select(genres, rating_avg, se, n)
 
-dim(train_set_grp)
-print(train_set_grp |> sort_by.data.frame(~ avg))
+dim(genre_ratins_grp)
+genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
+print(genre_ratins_grp_sorted)
 
-train_set_grp |> 
-  ggplot(aes(x = genres, y = avg, ymin = avg - 2*se, ymax = avg + 2*se)) + 
+# Creating plot:
+genre_ratins_grp |> 
+  ggplot(aes(x = genres, y = rating_avg, ymin = rating_avg - 2*se, ymax = rating_avg + 2*se)) + 
   geom_point() +
   geom_errorbar() + 
+  ggtitle("Average rating per Genre") +
[…]

### 2025-02-20 reports/capstone-movielens-report.Rmd

--- 2025-02-15 reports/capstone-movielens-report.Rmd
@@
 date: "`r Sys.Date()`"
-bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
 output:
+  html_document: 
+    fig_caption: true
   pdf_document: 
@@
     keep_tex: true
-    citation_package: biblatex
-colorlinks: true
-linkcolor: red
-citecolor: blue
-header-includes:
-    - \usepackage{hyperref}
-    - \usepackage[natbib=true, 
-                  style=numeric, 
-                  backref=true, 
-                  sorting=none]{biblatex}
-    - \hypersetup{backref,
-          pdfpagemode=Normal,
-          colorlinks=true,
-          implicit=false}
 vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
+  %\VignetteIndexEntry{RMarkdown Citations - Alphabetic Style}
+  %\VignetteEngine{knitr::knitr}
   %\VignetteEncoding{UTF-8}
-  %\VignetteEngine{knitr::knitr}
 ---
@@
 ```{r setup, include=TRUE, echo = FALSE}
-# if(!require(tidyverse)) 
-#   install.packages("tidyverse", repos = "http://cran.us.r-project.org")
-# if(!require(caret)) 
-#   install.packages("caret", repos = "http://cran.us.r-project.org")
-# if(!require(data.table)) 
-#   install.packages("data.table", repos = "http://cran.us.r-project.org")
-if(!require(pak)) 
-  install.packages("pak")
+library(RefManageR)
+bib <- ReadBib("references.bib", check = FALSE)
+BibOptions(check.entries = FALSE, style = "markdown", bib.style = "numeric", cite.style = 'numeric')
 
-# Loading the required libraries
-library(caret)
-library(cowplot)
-library(data.table)
-library(dplyr)
-library(ggplot2)
-library(ggthemes)
-library(lubridate)
-library(Metrics)
-library(recosystem)
-library(scales)
-library(stringr)
-library(tibble)
-library(tidyr)
-
-library(rafalib)
-library(pak)
+citeB <- function(citeKey){
+  AutoCite(bib, citeKey, .opts = list(hyperlink = "to.bib", super = FALSE))
+}
 
@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
+Following the _Netflix Grand Prize Contest_`r citeB("NYT1MNP")` requirements, we will evaluate the RMSE score defined as`r citeB("IDS2_23-2")`:
+
 $$
@@
 
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
+with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations.
 
-Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).
+Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563`r citeB("BigChaosSln")`).
 
-### Datasets
+### Dataset
 
-``` {r , echo = FALSE}
-```
-
-To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
-
-* **edx:** we use it to develop and train our algorithms;
-* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
-
-For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
-The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
-
-Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r }
-if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
-
-library(edx.capstone.movielens.data)
-edx <- edx.capstone.movielens.data::edx
-final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
-
-summary(edx)
-summary(final_holdout_test)
-```
-#### `edx` Dataset
-\
-Let's look into the details of the `edx` dataset:
-``` {r echo = TRUE}
-str(edx)
-```
-Note that we have 9000055 rows and six columns in there:  
-```{r }
-dim_edx <- dim(edx)
-print(dim_edx)
-```
-
-Also, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
-```{r }
-#library(dplyr)
-s <- edx |> group_by(rating) |>
-  summarise(n = n())
-print(s)
-```
-
-##### Movie Genres Data 
-\
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r}
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r}
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r}
-print(edx |> group_by(rating) |> summarize(count = n()))
-```
-
-We can visually see that from the following plot:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
-
-##### Rating distribution plot[@MRS-R-BEST]
-\
-The code below demonstrates another way of visualizing the rating distribution:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-
-```
-
-This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-
-##### Yearly rating count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(count = n())
-)
-```
-
-##### Average rating per year plot[@MRS-R-BEST]
-\
-```{r}
-edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(avg = mean(rating)) |>
-  ggplot(aes(x = year, y = avg)) +
-  geom_bar(stat = "identity", fill = "#8888ff") + 
-  ggtitle("Average rating per year") +
-  xlab("Year") +
-  ylab("Average rating") +
-  scale_y_continuous(labels = comma) + 
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Ratings per movie
-\
-
-###### Movie popularity count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  group_by(movieId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-```{r}
-summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
-```
-
-###### Ratings per movie plot[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-###### Movies' rating histogram[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Ratings per user[@MRS-R-BEST]
-\
-
-###### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-###### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-
-###### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-###### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### 
-\
-```{r}
-
-```
-
-##### 
-\
-```{r}
-
-```
-
-\
-```{r echo=FALSE}
-# #### [@MRS-R-BEST]
+```{r cars}
+summary(cars)
 ```
@@
 ## Methods / Analysis
-### Defining helper functions
-\
 
-Let's define some helper functions that we will use in our subsequent analysis:
-```{r}
-start_date <- function(){
-  print(date())
-  Sys.time()
-}
-end_date <- function(start){
-  print(date())
-  Sys.time() - start
-}
-rmse <- function(r) sqrt(mean(r^2))
-RMSE <- function(true_ratings, predicted_ratings){
-  sqrt(mean((true_ratings - predicted_ratings)^2))
-}
+You can also embed plots, for example:
 
-# Because we know ratings can’t be below 0.5 or above 5, 
-# we define the function clamp:
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-
+```{r pressure, echo=FALSE}
+plot(pressure)
 ```
 
-### Preparing train and set datasets
-\
-First, let's note that we have 10677 different movies: 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
-
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
-
-```
-
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
-
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=FALSE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Taking into consideration these observations, we came up with a decision to use the data from the dataset only for users who have provided at least 100 ratings.
-
-Now let's split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in the [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1]:
-```{r}
-# Let's ignore the data for users who have not provided at least 100 ratings:
-edx100 <- edx |> 
-  group_by(userId) |>
-  filter(n() >= 100) |>
-  ungroup()
-
-print(edx100 |> summarize(n_distinct(userId), n_distinct(movieId)))
-
-# For each one of these users, we will split their ratings into 80% for training 
-# and 20% for testing:
-
-set.seed(2006)
-indexes <- split(1:nrow(edx100), edx100$userId)
-test_ind <- sapply(indexes, function(i) sample(i, ceiling(length(i)*.2))) |> 
-  unlist() |>
-  sort()
-
-test_set <- edx100[test_ind,] 
-train_set <- edx100[-test_ind,]
-
-# To make sure we don’t include movies in the training set that should not be 
-# there, we remove entries using the semi_join function:
-test_set <- test_set |> semi_join(train_set, by = "movieId") |> as.data.frame()
-summary(test_set)
-
-train_set <- mutate(train_set, userId = factor(userId), movieId = factor(movieId))
-summary(train_set)
-```
-
-We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
-To create this matrix, we use `tidyr::pivot_wider` function:
-
-```{r}
-y <- dplyr::select(train_set, movieId, userId, rating) |>
-pivot_wider(names_from = movieId, values_from = rating) |>
-column_to_rownames("userId") |>
-as.matrix()
-
-dim(y)
-```
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r}
-movie_map <- train_set |> dplyr::select(movieId, title, genres) |> 
-  distinct(movieId, .keep_all = TRUE)
-
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
-
-### Naive Model
-\
-Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
-It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
-
-$$
-Y_{i,j} = \mu + \varepsilon_{i,j}
-$$
-
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
-
-We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
-
-```{r pressure, echo=TRUE}
-mu <- mean(y, na.rm = TRUE)
-print(mu)
-```
-
-If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE:
-
-```{r}
-rmse(test_set$rating - mu)
-```
-
-If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r}
-deviation <- seq(0, 6, 0.1) - 3
-print(deviation)
-
-rmse_value <- sapply(deviation, function(diff){
-  rmse(test_set$rating - mu + diff)
-})
-
-plot(deviation, rmse_value, type = "l")
-
-sprintf("Minimum RMSE is achieved when the deviation from the mean is: %s", 
-        deviation[which.min(rmse_value)])
-
-```
-
-To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
-
-### Taking into account User effects
-\
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects).
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
-```{r}
-hist(rowMeans(y, na.rm = TRUE), nclass = 30)
-```
-
-Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
-The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
-So we write the model as follows:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
-$$
-
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
-
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we compute them this way:
-```{r}
-a <- rowMeans(y - mu, na.rm = TRUE)
-```
-
-Finally, we are ready to compute the `RMSE` (additionally using the helper function `clamp` we defined above to keep predictions in the proper range):
-```{r}
-# Compute the RMSE taking into account user effects:
-user_effects_rmse <- test_set |> 
-    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
-    mutate(resid = rating - clamp(mu + a)) |> 
-    filter(!is.na(resid)) |>
-    pull(resid) |> rmse()
-
-print(user_effects_rmse)
-```
-### Taking into account Movie effects
-\
-In [Section _23.5 Movie effects_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) the author draws our attention to the fact that some movies are generally rated higher than others.
-He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
-$$
-The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:
-
-```{r}
-b <- colMeans(y - mu - a, na.rm = TRUE)
-```
-
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
-```{r}
-user_and_movie_effects_rmse <- test_set |> 
-    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
-    left_join(data.frame(movieId = as.integer(names(b)), b = b), by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |>  
-    filter(!is.na(resid)) |>
-    pull(resid) |> rmse()
-
-print(user_and_movie_effects_rmse)
-```
-### Utilizing Penalized least squares
-\
-[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-
-$$ 
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
-$$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-
-$$
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-where $n_j$ is the number of ratings made for movie $j$.
-
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-#### Support function
-\
-We will use the following function to calculate _RMSE_ in this section:
-```{r}
-reg_rmse <- function(b){
-  test_set |> 
-    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
-    left_join(data.frame(movieId = as.integer(names(b)), b = b), by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    filter(!is.na(resid)) |>
-    pull(resid) |> rmse()
-}
-
-```
-
-Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r}
-# Here we will simply compute the RMSE for different values of `lambda` 
-n <- colSums(!is.na(y))
-
-sums <- colSums(y - mu - a, na.rm = TRUE)
-lambdas <- seq(0, 10, 0.1)
-
-rmses <- sapply(lambdas, function(lambda){
-  b <-  sums / (n + lambda)
-  reg_rmse(b)
-})
-
-# Here is a plot of the RMSE versus `lambda`:
-plot(lambdas, rmses, type = "l")
-```
-Now we can determine the minimal _RMSE_:
-```{r}
-print(min(rmses))
-```
-
-which is achieved for the following $\lambda$:
-```{r}
-lambda <- lambdas[which.min(rmses)] 
-print(lambda)
-```
-
-Using this $\lambda$ we can compute the regularized estimates:
-```{r}
-b_reg <- sums / (n + lambda)
-
-str(b_reg)
-```
-Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r}
-reg_rmse(b_reg)
-```
+Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
 
@@
 
-This is a great conclusion, isn't it?!!
+This is a great conclusion, isn't is?!!
+
+**References**
+
+```{r results = "asis", echo = FALSE}
+PrintBibliography(bib, .opts = list(check.entries = FALSE))
+```

### 2025-02-21 reports/capstone-movielens-report.draft1.Rmd

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
bibliography: references.bib
#csl: bit-numerical-mathematics.csl 
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
    citation_package: biblatex
colorlinks: true
linkcolor: red
citecolor: blue
header-includes:
    - \usepackage{hyperref}
    - \usepackage[natbib=true, 
                  style=numeric, 
                  backref=true, 
                  sorting=none]{biblatex}
    - \hypersetup{backref,
          pdfpagemode=Normal,
          colorlinks=true,
          implicit=false}
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
---

```{r setup, include=TRUE, echo = FALSE}
if(!require(tidyverse))
  install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(caret))
  install.packages("caret", repos = "http://cran.us.r-project.org")
if(!require(data.table))
  install.packages("data.table", repos = "http://cran.us.r-project.org")

if(!require(gtools)) 
  install.packages("gtools")
if(!require(pak)) 
  install.packages("pak")

# Loading the required libraries
library(dslabs)
library(tidyverse)

library(caret)
library(cowplot)
library(data.table)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(lubridate)
library(Metrics)
library(recosystem)
library(scales)
library(stringr)
library(tibble)
library(tidyr)

library(rafalib)
library(gtools)
library(pak)

knitr::opts_chunk$set(echo = TRUE)
```

## Introduction / Overview / Executive Summary

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
$$
\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
$$

with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].

Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).

### Datasets

``` {r , echo = FALSE}
```

To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:

* **edx:** we use it to develop and train our algorithms;
* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.

For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`. The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].

Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
```{r }
if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")

library(edx.capstone.movielens.data)
edx <- edx.capstone.movielens.data::edx
final_holdout_test <- edx.capstone.movielens.data::final_holdout_test

summary(edx)
summary(final_holdout_test)
```
#### `edx` Dataset
\
Let's look into the details of the `edx` dataset:
``` {r echo = TRUE}
str(edx)
```
Note that we have 9000055 rows and six columns in there:  
```{r }
dim_edx <- dim(edx)
print(dim_edx)
```

Also, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
```{r }
#library(dplyr)
s <- edx |> group_by(rating) |>
  summarise(n = n())
print(s)
```

##### Movie Genres Data 
\
The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
```{r}
#library(stringr)
genres = c("Drama", "Comedy", "Thriller", "Romance")
sapply(genres, function(g) {
  sum(str_detect(edx$genres, g))
})
```

Further, we can find out the movies that have the greatest number of ratings using the following code:
```{r}
ordered_movie_ratings <- edx |> group_by(movieId, title) |>
  summarize(number_of_ratings = n()) |>
  arrange(desc(number_of_ratings))
print(head(ordered_movie_ratings))
```

and figure out the most given ratings in order from most to least:
```{r}
ratings <- edx |>  group_by(rating) |>
     summarise(count = n()) |>
     arrange(desc(count))
print(ratings)
```

The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
```{r}
print(edx |> group_by(rating) |> summarize(count = n()))
```

We can visually see that from the following plot:
```{r}
edx |>
  group_by(rating) |>
  summarize(count = n()) |>
  ggplot(aes(x = rating, y = count)) +
  geom_line()

```

Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.

##### Rating distribution plot[@MRS-R-BEST]
\
The code below demonstrates another way of visualizing the rating distribution:
```{r}
edx |>
  group_by(rating) |>
  summarize(count = n()) |>
  ggplot(aes(x = rating, y = count)) +
  geom_bar(stat = "identity", fill = "#8888ff") +
  ggtitle("Rating Distribution") +
  xlab("Rating") +
  ylab("Occurrences Count") +
  scale_y_continuous(labels = comma) +
  scale_x_continuous(n.breaks = 10) +
  theme_economist() +
  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
        axis.title.y = element_text(vjust = 10, face = "bold"), 
        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))

```

This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones. The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward. That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].

##### Ratings per movie
\

###### Movie popularity count[@MRS-R-BEST]
\
```{r}
print(edx |> 
  group_by(movieId) |> 
  summarize(count = n()) |>
  slice_head(n = 10)
)
```

```{r}
summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
```

###### Ratings per movie plot[@MRS-R-BEST]
\
```{r}
edx |>
  group_by(movieId) |>
  summarize(count = n()) |>
  ggplot(aes(x = movieId, y = count)) +
  geom_point(alpha = 0.2, color = "#4020dd") +
  geom_smooth(color = "red") +
  ggtitle("Ratings per movie") +
  xlab("Movies") +
  ylab("Number of ratings") +
  scale_y_continuous(labels = comma) +
  scale_x_continuous(n.breaks = 10) +
  theme_economist() +
  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
        axis.title.y = element_text(vjust = 10, face = "bold"), 
        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
```

###### Movies' rating histogram[@MRS-R-BEST]
\
```{r}
edx |>
  group_by(movieId) |>
  summarize(count = n()) |>
  ggplot(aes(x = count)) +
  geom_histogram(fill = "#8888ff", color = "#4020dd") +
  ggtitle("Movies' rating histogram") +
  xlab("Rating count") +
  ylab("Number of movies") +
  scale_y_continuous(labels = comma) +
  scale_x_log10(n.breaks = 10) +
  theme_economist() +
  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
        axis.title.y = element_text(vjust = 10, face = "bold"), 
        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
```

##### Ratings per user[@MRS-R-BEST]
\

###### User rating count (activity measure)
\
```{r}
print(edx |> 
  group_by(userId) |> 
  summarize(count = n()) |>
  slice_head(n = 10)
)
```

###### User rating summary
\
```{r}
summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
```

###### Ratings per user plot
\
```{r}
edx |>
  group_by(userId) |>
  summarize(count = n()) |>
  ggplot(aes(x = userId, y = count)) +
  geom_point(alpha = 0.2, color = "#4020dd") +
  geom_smooth(color = "red") +
  ggtitle("Ratings per user") +
  xlab("Users") +
  ylab("Number of ratings") +
  scale_y_continuous(labels = comma) +
  scale_x_continuous(n.breaks = 10) +
  theme_economist() +
  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
        axis.title.y = element_text(vjust = 10, face = "bold"), 
        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
```

###### Users' rating histogram
\
```{r}
edx |>
  group_by(userId) |>
  summarize(count = n()) |>
  ggplot(aes(x = count)) +
  geom_histogram(fill = "#8888ff", color = "#4020dd") +
  ggtitle("Users' rating histogram") +
  xlab("Rating count") +
  ylab("Number of users") +
  scale_y_continuous(labels = comma) +
  scale_x_log10(n.breaks = 10) +
  theme_economist() +
  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
        axis.title.y = element_text(vjust = 10, face = "bold"), 
        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
```

##### 
\
```{r}

```

##### 
\
```{r}

```

\
```{r echo=FALSE}
# #### [@MRS-R-BEST]
```

## Methods / Analysis
### Defining helper functions
\

Let's define some helper functions that we will use in our subsequent analysis:
```{r}
start_date <- function(){
  print(date())
  Sys.time()
}
end_date <- function(start){
  print(date())
  Sys.time() - start
}
rmse <- function(r) sqrt(mean(r^2))
RMSE <- function(true_ratings, predicted_ratings){
  sqrt(mean((true_ratings - predicted_ratings)^2))
}

# Because we know ratings can’t be below 0.5 or above 5, 
# we define the function clamp:
clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)

```

### Preparing train and set datasets
\
First, let's note that we have 10677 different movies: 
```{r}
n_movies <- n_distinct(edx$movieId)
print(n_movies)
```
and 69878 different users in the dataset:
```{r}
n_users <- n_distinct(edx$userId)
print(n_users)
```

Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
```{r}
max_possible_ratings <- n_movies*n_users
sprintf("Maximum possible ratings: %s", max_possible_ratings)
sprintf("Rows in `edx` dataset: %s", dim_edx[1])
sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])

```

As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells. Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate. A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]: 
```{r}
keep <- edx |> 
  dplyr::count(movieId) |> 
  top_n(4, n) |> 
  pull(movieId)

tab <- edx |> 
  filter(movieId %in% keep) |> 
  filter(userId %in% c(13:20)) |> 
  select(userId, title, rating) |> 
  mutate(title = str_remove(title, ", The"),
         title = str_remove(title, ":.*")) |>
  pivot_wider(names_from = "title", values_from = "rating")

print(tab)
```

The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
users <- sample(unique(edx$userId), 100)

rafalib::mypar()
edx|> 
  filter(userId %in% users) |> 
  select(userId, movieId, rating) |>
  mutate(rating = 1) |>
  pivot_wider(names_from = movieId, values_from = rating) |> 
  (\(mat) mat[, sample(ncol(mat), 100)])() |>
  as.matrix() |> 
  t() |>
  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
```

Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
p1 <- edx |> 
  count(movieId) |> 
  ggplot(aes(n)) + 
  geom_histogram(bins = 30, color = "black") + 
  scale_x_log10() + 
  ggtitle("Movies")

p2 <- edx |> 
  count(userId) |> 
  ggplot(aes(n)) + 
  geom_histogram(bins = 30, color = "black") + 
  scale_x_log10() + 
  ggtitle("Users")

gridExtra::grid.arrange(p2, p1, ncol = 2)
```

Taking into consideration these observations, we came up with a decision to use the data from the dataset only for users who have provided at least 100 ratings.

Now let's split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in the [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1]:
```{r}
# Let's ignore the data for users who have not provided at least 100 ratings:
edx100 <- edx |> 
  group_by(userId) |>
  filter(n() >= 100) |>
  ungroup()

print(edx100 |> summarize(n_distinct(userId), n_distinct(movieId)))

# For each one of these users, we will split their ratings into 80% for training 
# and 20% for testing:

set.seed(2006)
indexes <- split(1:nrow(edx100), edx100$userId)
test_ind <- sapply(indexes, function(i) sample(i, ceiling(length(i)*.2))) |> 
  unlist() |>
  sort()

test_set <- edx100[test_ind,] 
train_set <- edx100[-test_ind,]

# To make sure we don’t include movies in the training set that should not be 
# there, we remove entries using the semi_join function:
test_set <- test_set |> semi_join(train_set, by = "movieId") |> as.data.frame()
summary(test_set)

train_set <- mutate(train_set, userId = factor(userId), movieId = factor(movieId))
summary(train_set)
```

We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$. To create this matrix, we use `tidyr::pivot_wider` function:

```{r}
y <- dplyr::select(train_set, movieId, userId, rating) |>
pivot_wider(names_from = movieId, values_from = rating) |>
column_to_rownames("userId") |>
as.matrix()

dim(y)
```

To be able to map movie IDs to titles we create the following lookup table:
```{r}
movie_map <- train_set |> dplyr::select(movieId, title, genres) |> 
  distinct(movieId, .keep_all = TRUE)

summary(movie_map)
```

Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].

### Naive Model
\
Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:

$$
Y_{i,j} = \mu + \varepsilon_{i,j}
$$

with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.

We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:

```{r pressure, echo=TRUE}
mu <- mean(y, na.rm = TRUE)
print(mu)
```

If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE:

```{r}
rmse(test_set$rating - mu)
```

If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
```{r}
deviation <- seq(0, 6, 0.1) - 3
print(deviation)

rmse_value <- sapply(deviation, function(diff){
  rmse(test_set$rating - mu + diff)
})

plot(deviation, rmse_value, type = "l")

sprintf("Minimum RMSE is achieved when the deviation from the mean is: %s", 
        deviation[which.min(rmse_value)])

```

To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]

### Taking into account User effects
\
To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects). 
If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
```{r}
hist(rowMeans(y, na.rm = TRUE), nclass = 30)
```

Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user. The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies. So we write the model as follows:

$$
Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
$$

Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].

As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we compute them this way:
```{r}
a <- rowMeans(y - mu, na.rm = TRUE)
```

Finally, we are ready to compute the `RMSE` (additionally using the helper function `clamp` we defined above to keep predictions in the proper range):
```{r}
# Compute the RMSE taking into account user effects:
user_effects_rmse <- test_set |> 
    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
    mutate(resid = rating - clamp(mu + a)) |> 
    filter(!is.na(resid)) |>
    pull(resid) |> rmse()

print(user_effects_rmse)
```
### Taking into account Movie effects
\
In [Section _23.5 Movie effects_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) the author draws our attention to the fact that some movies are generally rated higher than others. He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:

$$
Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
$$
The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:

```{r}
b <- colMeans(y - mu - a, na.rm = TRUE)
```

We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
```{r}
user_and_movie_effects_rmse <- test_set |> 
    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
    left_join(data.frame(movieId = as.integer(names(b)), b = b), by = "movieId") |>
    mutate(resid = rating - clamp(mu + a + b)) |>  
    filter(!is.na(resid)) |>
    pull(resid) |> rmse()

print(user_and_movie_effects_rmse)
```
### Utilizing Penalized least squares
\
[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions. The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$. Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:

$$ 
\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
$$
The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large. Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:

$$
\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
$$

where $n_j$ is the number of ratings made for movie $j$.

This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$. Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0. The larger the $\lambda$, the more we shrink[@IDS2_23-6].

#### Support function
\
We will use the following function to calculate _RMSE_ in this section:
```{r}
reg_rmse <- function(b){
  test_set |> 
    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
    left_join(data.frame(movieId = as.integer(names(b)), b = b), by = "movieId") |>
    mutate(resid = rating - clamp(mu + a + b)) |> 
    filter(!is.na(resid)) |>
    pull(resid) |> rmse()
}

```

Let's now figure out the $\lambda$ that minimizes the _RMSE_:
```{r}
# Here we will simply compute the RMSE for different values of `lambda` 
n <- colSums(!is.na(y))

sums <- colSums(y - mu - a, na.rm = TRUE)
lambdas <- seq(0, 10, 0.1)

rmses <- sapply(lambdas, function(lambda){
  b <-  sums / (n + lambda)
  reg_rmse(b)
})

# Here is a plot of the RMSE versus `lambda`:
plot(lambdas, rmses, type = "l")
```
Now we can determine the minimal _RMSE_:
```{r}
print(min(rmses))
```

which is achieved for the following $\lambda$:
```{r}
lambda <- lambdas[which.min(rmses)] 
print(lambda)
```

Using this $\lambda$ we can compute the regularized estimates:
```{r}
b_reg <- sums / (n + lambda)

str(b_reg)
```
Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
```{r}
reg_rmse(b_reg)
```
### Accounting for Date effects

##### Yearly rating count[@MRS-R-BEST]
\
```{r}
print(edx |> 
  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
  group_by(year) |>
  summarize(count = n())
)
```

##### Average rating per year plot[@MRS-R-BEST]
\
```{r}
edx |> 
  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
  group_by(year) |>
  summarize(rating_avg = mean(rating)) |>
  ggplot(aes(x = year, y = rating_avg)) +
  geom_bar(stat = "identity", fill = "#8888ff") + 
  ggtitle("Average rating per year") +
  xlab("Year") +
  ylab("Average rating") +
  scale_y_continuous(labels = comma) + 
  theme_economist() +
  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
        axis.title.y = element_text(vjust = 10, face = "bold"), 
        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
```

We use the following models to account for the `date` effect:

$$
Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
$$

### Accounting for Genre effect
\
As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column. This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].

The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).

```{r}
# Preparing data for plotting:
genre_ratins_grp <- train_set |> 
  mutate(genre_categories = as.factor(genres)) |>
  group_by(genre_categories) |>
  summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
  filter(n > 20000) |> 
  mutate(genres = reorder(genre_categories, rating_avg)) |>
  select(genres, rating_avg, se, n)

dim(genre_ratins_grp)
genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
print(genre_ratins_grp_sorted)

# Creating plot:
genre_ratins_grp |> 
  ggplot(aes(x = genres, y = rating_avg, ymin = rating_avg - 2*se, ymax = rating_avg + 2*se)) + 
  geom_point() +
  geom_errorbar() + 
  ggtitle("Average rating per Genre") +
  ylab("Average rating") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
Below are worst and best ratings categories:
```{r}
sprintf("The worst ratings are for the genre category: %s",
        genre_ratins_grp$genres[which.min(genre_ratins_grp$genres)])

sprintf("The best ratings are for the genre category: %s",
        genre_ratins_grp$genres[which.max(genre_ratins_grp$genres)])
```

Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
```{r}
# For better visibility, we reduce the data for plotting 
# while keeping the worst and best rating rows:
plot_ind <- odd(1:nrow(genre_ratins_grp))
plot_dat <- genre_ratins_grp_sorted[plot_ind,]

plot_dat |>
  ggplot(aes(x = rating_avg, y = genres)) +
  ggtitle("Genre Average Rating") +
  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
  xlab("Average ratings") +
  ylab("Genres") +
  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
  theme_economist() +
  theme(plot.title = element_text(vjust = 3.5),
        axis.title.x = element_text(vjust = -5, face = "bold"),
        axis.title.y = element_text(vjust = 10, face = "bold"),
        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
```

If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:

$$
Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \sum_{k=1}^K x_{i,j}^k \gamma_k + \varepsilon_{i,j}
$$

with $x^k_{i,j} = 1$ if $g_{i,j}$ is genre $k$.

## Conclusion

Hello Conclusion!

This is a great conclusion, isn't it?!!

### 2025-02-23 reports/capstone-movielens-report.draft2.Rmd
Genre effect accounting (in progress)

--- 2025-02-21 reports/capstone-movielens-report.draft1.Rmd
@@
   install.packages("pak")
+if(!require("pacman")) 
+  install.packages("pacman")
 
@@
 library(pak)
+library(pacman)
+
+p_load(latex2exp)
 

### 2025-02-23 r/capstone-movielens.draft2.R

@@ -11,6 +11,9 @@ if(!require(gtools))
   install.packages("gtools")
 if(!require(pak)) 
   install.packages("pak")
+if(!require("pacman")) 
+  install.packages("pacman")
+
 
 # Loading the required libraries
 library(dslabs)
@@ -34,6 +37,9 @@ library(tidyr)
 library(rafalib)
 library(gtools)
 library(pak)
+library(pacman)
+
+p_load(latex2exp)
 
 ## Datasets ===================================================================
 
@@ -282,6 +288,8 @@ sprintf("Minimum RMSE is achieved when the deviation from the mean is: %s",
 # If we visualize the average rating for each user:
 hist(rowMeans(y, na.rm = TRUE), nclass = 30)
 
+#### Model building: user effect ----------------------------------------------
+
 # we notice that there is substantial variability across users.
 #>  To account for this, we can use a linear model with a treatment effect `α[i]` 
 #>  for each user. The sum `μ + α[i]` can be interpreted as the typical 
@@ -296,9 +304,16 @@ a <- rowMeans(y - mu, na.rm = TRUE)
 #> Finally, we are ready to compute the `RMSE` (additionally using the helper 
 #> function `clamp` we defined above to keep predictions in the proper range):
 
+user_effects <- data.frame(userId = as.integer(names(a)), a = a)
+
+# Plot a histogram of the user effects
+par(cex = 0.7)
+hist(user_effects$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
+     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
+
 # Compute the RMSE taking into account user effects:
 user_effects_rmse <- test_set |> 
-  left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
+  left_join(user_effects, by = "userId") |>
   mutate(resid = rating - clamp(mu + a)) |> 
   filter(!is.na(resid)) |>
   pull(resid) |> rmse()
@@ -306,7 +321,7 @@ user_effects_rmse <- test_set |>
 print(user_effects_rmse)
 #> [1] 0.9711968
 
-### Taking into account Movie effects ------------------------------------------
+### Taking into account Movie effect ------------------------------------------
 
[…]

### 2025-03-01 reports/capstone-movielens-report.draft3.Rmd
Accounting for Genre Effect: draft version.

--- 2025-02-23 reports/capstone-movielens-report.draft2.Rmd
@@
 
+To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
+
 $$
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \sum_{k=1}^K x_{i,j}^k \gamma_k + \varepsilon_{i,j}
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
 $$
 
-with $x^k_{i,j} = 1$ if $g_{i,j}$ is genre $k$.
+where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p.
+712) book[@RRSK_RS_HB].
+
+In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:
+
+$$
+g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
+$$
+
+with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.
+
+$$
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
+$$
+
+$$
+ \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
+$$
 

### 2025-03-01 r/capstone-movielens.draft3.R

@@ -774,125 +774,91 @@ rmse_kable()
 #   pull(resid) |> final_rmse()
 #> [1] 0.8660814
 
-###### Enhanced By-Genre model: user+movie effects RMSE ------------------------
-
-# Y[i,j] = μ(g) + α[i] + β[j] + ε[i,j]
-# which μ(g) is average rating for the combination of genres for movie `i`
-
-
-# user_and_movie_effects_by_genre_rmse <- test_set |> 
-#   left_join(user_effects, by = "userId") |>
-#   left_join(movie_effects, by = "movieId") |>
-#   left_join(movie_effects_by_genre, by = "movieId") |>
-#   #left_join(genre_ratings_avg, by = "genres" ) |>
-#   mutate(resid = rating - clamp(mu_g + a + b)) |>  
-#   filter(!is.na(resid)) |>
-#   pull(resid) |> rmse()
-
-movie_effects_by_genre_rmse <- train_set |>
-  mutate(userId = as.integer(userId),
-         movieId = as.integer(movieId)) |>
-  left_join(user_effects, by = "userId") |>
-  left_join(genre_ratings_avg, by = "genres" ) |>
-  mutate(resid = rating - (mu + a)) |>  
-  filter(!is.na(resid)) |>
-  pull(resid) |> rmse()
-
-print(movie_effects_by_genre_rmse)
-
-#nseq <- seq(10000, 140000, 1000)
-nseq <- seq(58000, 60000, 100)
-nseq
-
-calc__genre_effect <- function(ng){
-  genre_effects <- train_set |>
-    mutate(userId = as.integer(userId),
-           movieId = as.integer(movieId)) |>
-    left_join(user_effects, by = "userId") |>
-    left_join(movie_effects, by = "movieId") |>
-    filter(!is.na(rating)) |>
-    mutate(a = ifelse(is.na(a), 0, a),
-           b = ifelse(is.na(b), 0, b)) |>
-    mutate(rsd = rating - (mu + a + b)) |>
-    # filter(!is.na(a)) |>
-    # filter(!is.na(b)) |>
-    select(genres, rating, a, b, rsd) |>
-    group_by(genres) |>
-    summarise(g = mean(rsd, rm.na = TRUE), n = n()) |>
-    #sort_by.data.frame(~ n) |>
-    filter(n >= ng)
-
-  # Plot a histogram of the genre effects
-  par(cex = 0.7)
-  hist(genre_effects$g, 30, xlab = TeX(r'[$\hat{g}$]'),
[…]

### 2025-05-02 reports/capstone-movielens-report.draft4.Rmd
Version 4 of the RMD report added.

--- 2025-03-01 reports/capstone-movielens-report.draft3.Rmd
@@
 ```{r setup, include=TRUE, echo = FALSE}
+## Setup -----------------------------------------------------------------------
+#> Reference: Some ideas and code snippers were used from the following GitHub repository:
+#> https://github.com/AzKurban-edX-DS/harvardx-movielens
+
 if(!require(tidyverse))
   install.packages("tidyverse", repos = "http://cran.us.r-project.org")
+
+#> `stringr` library is already included to the `tidyverse` package,
+#> there's no need to install `stringr`
+# if(!require(stringr))
+#   install.packages("stringr")
+
 if(!require(caret))
@@
   install.packages("data.table", repos = "http://cran.us.r-project.org")
+if(!require(gridExtra))
+  install.packages("gridExtra")
+if(!require("logr")) 
+  install.packages("logr")
 
@@
   install.packages("pacman")
+
+if(!require("recommenderlab")) 
+  install.packages("recommenderlab")
 
@@
 library(recosystem)
+library(recommenderlab)
+
 library(scales)
@@
 library(tidyr)
+library(gridExtra)
+library(logr)
 
@@
 
-p_load(latex2exp)
+p_load(conflicted, latex2exp, kableExtra)
+
+#p_load(latex2exp)
+
+### Resolve conflicts ----------------------------------------------------------
+
+# For functions with identical names in different packages, ensure the
+# right one is chosen:
+conflict_prefer("first", "dplyr", quiet = TRUE)
+conflict_prefer("count", "dplyr", quiet = TRUE)
+conflict_prefer("select", "dplyr", quiet = TRUE)
+conflict_prefer("group_by", "dplyr", quiet = TRUE)
+conflict_prefer("ungroup", "dplyr", quiet = TRUE)
+conflict_prefer("summarise", "dplyr", quiet = TRUE)
+conflict_prefer("summarize", "dplyr", quiet = TRUE)
+conflict_prefer("distinct", "dplyr", quiet = TRUE)
+conflict_prefer("top_n", "dplyr", quiet = TRUE)
+conflict_prefer("arrange", "dplyr", quiet = TRUE)
+conflict_prefer("mutate", "dplyr", quiet = TRUE)
+conflict_prefer("semi_join", "dplyr", quiet = TRUE)
+conflict_prefer("left_join", "dplyr", quiet = TRUE)
+conflict_prefer("filter", "dplyr", quiet = TRUE)
+conflict_prefer("slice", "dplyr", quiet = TRUE)
+conflict_prefer("glimpse", "dplyr", quiet = TRUE)
+conflict_prefer("union", "dplyr", quiet = TRUE)
+
+conflict_prefer("pivot_wider", "tidyr", quiet = TRUE)
+conflict_prefer("kable", "kableExtra", quiet = TRUE)
+conflict_prefer("year", "lubridate", quiet = TRUE)
+conflicts_prefer(base::as.matrix)
 

### 2025-05-02 r/src/capstone-movielens.main.R
Code cleaned-up.

@@ -2,7 +2,6 @@
 #> Reference: Some ideas and code snippers were used from the following GitHub repository:
 #> https://github.com/AzKurban-edX-DS/harvardx-movielens
 
-
 if(!require(tidyverse))
   install.packages("tidyverse", repos = "http://cran.us.r-project.org")
 

### 2025-05-02 reports/0ld/capstone-movielens-report.draft3.tex
Draft version 4 of the RMD report compiled.

--- 2025-02-19 reports/capstone-movielens-report.draft1.tex
@@
 \author{Azamat Kurbanaev}
-\date{2025-02-19}
+\date{2025-03-01}
 
@@
 ## Warning: package 'pak' was built under R version 4.4.2
+\end{verbatim}
+
+\begin{verbatim}
+## Loading required package: pacman
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'pacman' was built under R version 4.4.2
 \end{verbatim}
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-10-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-10-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-11-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-11-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-14-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-14-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-15-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-15-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-18-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-18-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-19-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-19-1.pdf}
 
@@
 
-\includegraphics[width=0.4\linewidth]{capstone-movielens-report.draft1_files/figure-latex/sparsity-of-movie-recs-1}
+\includegraphics[width=0.4\linewidth]{capstone-movielens-report.draft3_files/figure-latex/sparsity-of-movie-recs-1}
 
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/movie-id-and-user-hists-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/movie-id-and-user-hists-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-32-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-32-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-33-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-33-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-39-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-39-1.pdf}
 Now we can determine the minimal \emph{RMSE}:
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-45-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-45-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-46-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-46-1.pdf}
 Below are worst and best ratings categories:
@@
 
-\includegraphics{capstone-movielens-report.draft1_files/figure-latex/unnamed-chunk-48-1.pdf}
+\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-48-1.pdf}
 
@@
 
+To account for \emph{genre effects} we will use the model suggested in
+the
+\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#exercises}{Section
+23.7: Exercises} of the \emph{Chapter ``23 Regularization'' of the
+Course Textbook}\autocite{IDS2_23-7}:
+
 \[
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \sum_{k=1}^K x_{i,j}^k \gamma_k + \varepsilon_{i,j}
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
 \]
 
-with \(x^k_{i,j} = 1\) if \(g_{i,j}\) is genre \(k\).
+where \(g_{i,j}\) is an \emph{aggregation function} which is explained
+in detail in \emph{Section 22.3: ``Review of Aggregation Functions'' of
+``Recommender Systems Handbook''} (\emph{Chapter 22: ``Aggregation of
+Preferences in Recommender Systems''}, p.~712)
+book\autocite{RRSK_RS_HB}.
+
+In the formula above \(g_{i,j}\) denotes a \emph{genre effect} for
+user's \(i\) rating of movie \(j\), so that:
+
+\[
+g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
+\]
+
+with \(x^k_{i,j} = 1\) if \(g_{i,j}\) includes genre \(k\), and
+\(x^k_{i,j} = 0\) otherwise.
+
+\[
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
+\]
+
+\[
+ \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
+\]
 

### 2025-05-02 reports/capstone-movielens-report.draft4.tex
Draft version 4 of the RMD report compiled.

--- 2025-05-02 reports/0ld/capstone-movielens-report.draft3.tex
@@
 \hypersetup{backref, pdfpagemode=Normal, colorlinks=true, implicit=false}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \ifLuaTeX
@@
 \author{Azamat Kurbanaev}
-\date{2025-03-01}
+\date{2025-05-03}
 
@@
 ## 
+## Loading required package: gridExtra
+## 
+## Attaching package: 'gridExtra'
+## 
+## The following object is masked from 'package:dplyr':
+## 
+##     combine
+## 
+## Loading required package: logr
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'logr' was built under R version 4.4.3
+\end{verbatim}
+
+\begin{verbatim}
+## Loading required package: common
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'common' was built under R version 4.4.3
+\end{verbatim}
+
+\begin{verbatim}
 ## Loading required package: gtools
@@
 \begin{verbatim}
+## Loading required package: recommenderlab
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'recommenderlab' was built under R version 4.4.3
+\end{verbatim}
+
+\begin{verbatim}
+## Loading required package: Matrix
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'Matrix' was built under R version 4.4.2
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Attaching package: 'Matrix'
+## 
+## The following objects are masked from 'package:tidyr':
+## 
+##     expand, pack, unpack
+## 
+## Loading required package: arules
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: package 'arules' was built under R version 4.4.3
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Attaching package: 'arules'
+## 
+## The following object is masked from 'package:dplyr':
+## 
+##     recode
+## 
+## The following objects are masked from 'package:base':
+## 
+##     abbreviate, write
+## 
+## Loading required package: proxy
+## 
+## Attaching package: 'proxy'
+## 
+## The following object is masked from 'package:Matrix':
+## 
+##     as.matrix
+## 
+## The following objects are masked from 'package:stats':
+## 
+##     as.dist, dist
+## 
+## The following object is masked from 'package:base':
+## 
+##     as.matrix
+## 
+## Registered S3 methods overwritten by 'registry':
+##   method               from 
+##   print.registry_field proxy
+##   print.registry_entry proxy
+## 
+## Attaching package: 'recommenderlab'
+## 
+## The following objects are masked from 'package:caret':
+## 
+##     MAE, RMSE
+\end{verbatim}
+
+\begin{verbatim}
 ## Warning: package 'dslabs' was built under R version 4.4.2
@@
 ##     col_factor
+## 
+## [conflicted] Will prefer base::as.matrix over any other package.
 \end{verbatim}
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-10-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-10-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-11-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-14-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-14-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-15-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-18-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-18-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-19-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
 
@@
 
-\includegraphics[width=0.4\linewidth]{capstone-movielens-report.draft3_files/figure-latex/sparsity-of-movie-recs-1}
+\includegraphics[width=0.4\linewidth]{capstone-movielens-report.draft4_files/figure-latex/sparsity-of-movie-recs-1}
 
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/movie-id-and-user-hists-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/movie-id-and-user-hists-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-32-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-32-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-33-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-33-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-39-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-39-1.pdf}
 Now we can determine the minimal \emph{RMSE}:
@@
 ##     year   count
-##    <int>   <int>
+##    <dbl>   <int>
 ##  1  1995       2
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-45-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-45-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-46-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-46-1.pdf}
 Below are worst and best ratings categories:
@@
 
-\includegraphics{capstone-movielens-report.draft3_files/figure-latex/unnamed-chunk-48-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-48-1.pdf}
 

### 2025-05-03 reports/capstone-movielens-report.draft4.Rmd
Resumed development of the RMD report.

--- 2025-03-01 reports/capstone-movielens-report.draft3.Rmd
@@
 #csl: bit-numerical-mathematics.csl 
+envir:
+  parent.frame()
 output:
@@
 
-```{r setup, include=TRUE, echo = FALSE}
-if(!require(tidyverse))
-  install.packages("tidyverse", repos = "http://cran.us.r-project.org")
-if(!require(caret))
-  install.packages("caret", repos = "http://cran.us.r-project.org")
-if(!require(data.table))
-  install.packages("data.table", repos = "http://cran.us.r-project.org")
+```{r setup, include=FALSE, echo = FALSE}
+r.path <- "../r"
+src.folder <- "src"
+support_scripts.folder <- "support-scripts"
+support_functions.folder <- "support-functions"
 
-if(!require(gtools)) 
-  install.packages("gtools")
-if(!require(pak)) 
-  install.packages("pak")
-if(!require("pacman")) 
-  install.packages("pacman")
+r.src.path <- file.path(r.path, src.folder)
+support_scripts.path <- file.path(r.src.path, support_scripts.folder)
+support_functions.path <- file.path(r.src.path, support_functions.folder)
+## Setup -----------------------------------------------------------------------
+setup_script.file_path <- file.path(support_scripts.path,
+                                               "setup.R")
 
-# Loading the required libraries
-library(dslabs)
-library(tidyverse)
+# main_script.file_path <- file.path(r.src.path,
+#                                    "capstone-movielens.main.R")
+# stop(main_script.file_path)
+stopifnot(file.exists(setup_script.file_path))
 
-library(caret)
-library(cowplot)
-library(data.table)
-library(dplyr)
-library(ggplot2)
-library(ggthemes)
-library(lubridate)
-library(Metrics)
-library(recosystem)
-library(scales)
-library(stringr)
-library(tibble)
-library(tidyr)
+source(setup_script.file_path, 
+       local = knitr::knit_global())
+# or sys.source("your-script.R", envir = knitr::knit_global())
 
-library(rafalib)
-library(gtools)
-library(pak)
-library(pacman)
+## External Common Helper functions -------------------------------------
+# common_helper_functions.file_path <- file.path(support_functions.path,
+#                                             "common-helper.functions.R")
+# source(common_helper_functions.file_path, 
+#        local = knitr::knit_global())
 
-p_load(latex2exp)
+# knitr::knit_global()
+#knitr::opts_chunk$set(echo = FALSE)
+```
 
-knitr::opts_chunk$set(echo = TRUE)
+## Plot dependency of RMSEs vs Overal Mean Rating Deviation
+\
+```{r}
+
+data.frame(delta = deviation, 
+           delta.RMSE = deviation.RMSE) |> 
+tuning.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
+              xname = "delta", 
+              yname = "delta.RMSE", 
+              xlabel = TeX(r'[$\delta$]'), 
+              ylabel = "RMSE")
+
 ```
@@
         plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### 
-\
-```{r}
-
 ```

### 2025-05-03 reports/capstone-movielens-report.draft4.tex
Resumed development of the RMD report.

@@
 \hypersetup{backref, pdfpagemode=Normal, colorlinks=true, implicit=false}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
 \ifLuaTeX
@@
 }
-\begin{verbatim}
-## Loading required package: tidyverse
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'lubridate' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## -- Attaching core tidyverse packages ------------------------ tidyverse 2.0.0 --
-## v dplyr     1.1.4     v readr     2.1.5
-## v forcats   1.0.0     v stringr   1.5.1
-## v ggplot2   3.5.1     v tibble    3.2.1
-## v lubridate 1.9.4     v tidyr     1.3.1
-## v purrr     1.0.2
-\end{verbatim}
-
-\begin{verbatim}
-## -- Conflicts ------------------------------------------ tidyverse_conflicts() --
-## x dplyr::filter() masks stats::filter()
-## x dplyr::lag()    masks stats::lag()
-## i Use the conflicted package (<http://conflicted.r-lib.org/>) to force all conflicts to become errors
-## Loading required package: caret
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'caret' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## Loading required package: lattice
-## 
-## Attaching package: 'caret'
-## 
-## The following object is masked from 'package:purrr':
-## 
-##     lift
-## 
-## Loading required package: data.table
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'data.table' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## Attaching package: 'data.table'
-## 
-## The following objects are masked from 'package:lubridate':
-## 
-##     hour, isoweek, mday, minute, month, quarter, second, wday, week,
-##     yday, year
-## 
-## The following objects are masked from 'package:dplyr':
-## 
-##     between, first, last
-## 
-## The following object is masked from 'package:purrr':
-## 
-##     transpose
-## 
-## Loading required package: gridExtra
-## 
-## Attaching package: 'gridExtra'
-## 
-## The following object is masked from 'package:dplyr':
-## 
-##     combine
-## 
-## Loading required package: logr
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'logr' was built under R version 4.4.3
-\end{verbatim}
-
-\begin{verbatim}
-## Loading required package: common
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'common' was built under R version 4.4.3
-\end{verbatim}
-
-\begin{verbatim}
-## Loading required package: gtools
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'gtools' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## Loading required package: pak
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'pak' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## Loading required package: pacman
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'pacman' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## Loading required package: recommenderlab
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'recommenderlab' was built under R version 4.4.3
-\end{verbatim}
-
-\begin{verbatim}
-## Loading required package: Matrix
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'Matrix' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## Attaching package: 'Matrix'
-## 
-## The following objects are masked from 'package:tidyr':
-## 
-##     expand, pack, unpack
-## 
-## Loading required package: arules
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'arules' was built under R version 4.4.3
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## Attaching package: 'arules'
-## 
-## The following object is masked from 'package:dplyr':
-## 
-##     recode
-## 
-## The following objects are masked from 'package:base':
-## 
-##     abbreviate, write
-## 
-## Loading required package: proxy
-## 
-## Attaching package: 'proxy'
-## 
-## The following object is masked from 'package:Matrix':
-## 
-##     as.matrix
-## 
-## The following objects are masked from 'package:stats':
-## 
-##     as.dist, dist
-## 
-## The following object is masked from 'package:base':
-## 
-##     as.matrix
-## 
-## Registered S3 methods overwritten by 'registry':
-##   method               from 
-##   print.registry_field proxy
-##   print.registry_entry proxy
-## 
-## Attaching package: 'recommenderlab'
-## 
-## The following objects are masked from 'package:caret':
-## 
-##     MAE, RMSE
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'dslabs' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'cowplot' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## Attaching package: 'cowplot'
-## 
-## The following object is masked from 'package:lubridate':
-## 
-##     stamp
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'ggthemes' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## Attaching package: 'ggthemes'
-## 
-## The following object is masked from 'package:cowplot':
-## 
-##     theme_map
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'Metrics' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## Attaching package: 'Metrics'
-## 
-## The following objects are masked from 'package:caret':
-## 
-##     precision, recall
-\end{verbatim}
-
-\begin{verbatim}
-## Warning: package 'recosystem' was built under R version 4.4.2
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## Attaching package: 'scales'
-## 
-## The following object is masked from 'package:purrr':
-## 
-##     discard
-## 
-## The following object is masked from 'package:readr':
-## 
-##     col_factor
-## 
-## [conflicted] Will prefer base::as.matrix over any other package.
-\end{verbatim}
+\subsection{Plot dependency of RMSEs vs Overal Mean Rating
+Deviation}\label{plot-dependency-of-rmses-vs-overal-mean-rating-deviation}
+
+\hfill\break
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{delta =}\NormalTok{ deviation, }
+           \AttributeTok{delta.RMSE =}\NormalTok{ deviation.RMSE) }\SpecialCharTok{|\textgreater{}} 
+\FunctionTok{tuning.plot}\NormalTok{(}\AttributeTok{title =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[RMSE as a function of deviation ($\textbackslash{}delta$) from the Overall Mean Rating ($\textbackslash{}hat\{mu\}$)]\textquotesingle{}}\NormalTok{),}
+              \AttributeTok{xname =} \StringTok{"delta"}\NormalTok{, }
+              \AttributeTok{yname =} \StringTok{"delta.RMSE"}\NormalTok{, }
+              \AttributeTok{xlabel =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[$\textbackslash{}delta$]\textquotesingle{}}\NormalTok{), }
+              \AttributeTok{ylabel =} \StringTok{"RMSE"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-1-1.pdf}
 
@@
 \ControlFlowTok{if}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{require}\NormalTok{(edx.capstone.movielens.data)) pak}\SpecialCharTok{::}\FunctionTok{pak}\NormalTok{(}\StringTok{"AzKurban{-}edX{-}DS/edx.capstone.movielens.data"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Loading required package: edx.capstone.movielens.data
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
+
 \FunctionTok{library}\NormalTok{(edx.capstone.movielens.data)}
@@
 \begin{verbatim}
-##      userId         movieId          rating        timestamp        
-##  Min.   :    1   Min.   :    1   Min.   :0.500   Min.   :7.897e+08  
-##  1st Qu.:18124   1st Qu.:  648   1st Qu.:3.000   1st Qu.:9.468e+08  
-##  Median :35738   Median : 1834   Median :4.000   Median :1.035e+09  
+##      userId         movieId          rating        timestamp            title              genres         
+##  Min.   :    1   Min.   :    1   Min.   :0.500   Min.   :7.897e+08   Length:9000055     Length:9000055    
+##  1st Qu.:18124   1st Qu.:  648   1st Qu.:3.000   1st Qu.:9.468e+08   Class :character   Class :character  
+##  Median :35738   Median : 1834   Median :4.000   Median :1.035e+09   Mode  :character   Mode  :character  
 ##  Mean   :35870   Mean   : 4122   Mean   :3.512   Mean   :1.033e+09                                        
@@
 ##  Max.   :71567   Max.   :65133   Max.   :5.000   Max.   :1.231e+09
-##     title              genres         
-##  Length:9000055     Length:9000055    
-##  Class :character   Class :character  
-##  Mode  :character   Mode  :character  
-##                                       
-##                                       
-## 
 \end{verbatim}
@@
 \begin{verbatim}
-##      userId         movieId          rating        timestamp        
-##  Min.   :    1   Min.   :    1   Min.   :0.500   Min.   :7.897e+08  
-##  1st Qu.:18096   1st Qu.:  648   1st Qu.:3.000   1st Qu.:9.467e+08  
-##  Median :35768   Median : 1827   Median :4.000   Median :1.035e+09  
+##      userId         movieId          rating        timestamp            title              genres         
+##  Min.   :    1   Min.   :    1   Min.   :0.500   Min.   :7.897e+08   Length:999999      Length:999999     
+##  1st Qu.:18096   1st Qu.:  648   1st Qu.:3.000   1st Qu.:9.467e+08   Class :character   Class :character  
+##  Median :35768   Median : 1827   Median :4.000   Median :1.035e+09   Mode  :character   Mode  :character  
 ##  Mean   :35870   Mean   : 4108   Mean   :3.512   Mean   :1.033e+09                                        
@@
 ##  Max.   :71567   Max.   :65133   Max.   :5.000   Max.   :1.231e+09
-##     title              genres         
-##  Length:999999      Length:999999     
-##  Class :character   Class :character  
-##  Mode  :character   Mode  :character  
-##                                       
-##                                       
-## 
 \end{verbatim}
@@
 \begin{verbatim}
-## `summarise()` has grouped output by 'movieId'. You can override using the
-## `.groups` argument.
+## `summarise()` has grouped output by 'movieId'. You can override using the `.groups` argument.
 \end{verbatim}
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-10-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-12-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-14-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-16-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-18-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-20-1.pdf}
 
 \subparagraph{}\label{section}
-
-\hfill\break
-
-\subparagraph{}\label{section-1}
 
@@
 ## # A tibble: 5 x 5
-##   userId `Pulp Fiction (1994)` `Jurassic Park (1993)` Silence of the Lambs (19~1
-##    <int>                 <dbl>                  <dbl>                      <dbl>
-## 1     13                     4                     NA                         NA
-## 2     16                    NA                      3                         NA
-## 3     17                    NA                     NA                          5
-## 4     18                     5                      3                          5
-## 5     19                    NA                      1                         NA
-## # i abbreviated name: 1: `Silence of the Lambs (1991)`
-## # i 1 more variable: `Forrest Gump (1994)` <dbl>
+##   userId `Pulp Fiction (1994)` `Jurassic Park (1993)` `Silence of the Lambs (1991)` `Forrest Gump (1994)`
+##    <int>                 <dbl>                  <dbl>                         <dbl>                 <dbl>
+## 1     13                     4                     NA                            NA                    NA
+## 2     16                    NA                      3                            NA                    NA
+## 3     17                    NA                     NA                             5                    NA
+## 4     18                     5                      3                             5                    NA
+## 5     19                    NA                      1                            NA                     4
 \end{verbatim}
@@
 \begin{verbatim}
-##      userId         movieId          rating        timestamp        
-##  Min.   :    8   Min.   :    1   Min.   :0.500   Min.   :8.248e+08  
-##  1st Qu.:18161   1st Qu.: 1022   1st Qu.:3.000   1st Qu.:9.655e+08  
-##  Median :35666   Median : 2109   Median :3.500   Median :1.058e+09  
+##      userId         movieId          rating        timestamp            title              genres         
+##  Min.   :    8   Min.   :    1   Min.   :0.500   Min.   :8.248e+08   Length:1397040     Length:1397040    
+##  1st Qu.:18161   1st Qu.: 1022   1st Qu.:3.000   1st Qu.:9.655e+08   Class :character   Class :character  
+##  Median :35666   Median : 2109   Median :3.500   Median :1.058e+09   Mode  :character   Mode  :character  
 ##  Mean   :35902   Mean   : 4616   Mean   :3.473   Mean   :1.051e+09                                        
@@
 ##  Max.   :71565   Max.   :65133   Max.   :5.000   Max.   :1.231e+09
-##     title              genres         
-##  Length:1397040     Length:1397040    
-##  Class :character   Class :character  
-##  Mode  :character   Mode  :character  
-##                                       
-##                                       
-## 
 \end{verbatim}
@@
 \begin{verbatim}
-##      userId           movieId            rating        timestamp        
-##  59269  :   5292   356    :  12769   Min.   :0.500   Min.   :8.248e+08  
-##  67385  :   5088   296    :  12439   1st Qu.:3.000   1st Qu.:9.657e+08  
-##  14463  :   3718   480    :  12390   Median :3.500   Median :1.059e+09  
+##      userId           movieId            rating        timestamp            title              genres         
+##  59269  :   5292   356    :  12769   Min.   :0.500   Min.   :8.248e+08   Length:5539951     Length:5539951    
+##  67385  :   5088   296    :  12439   1st Qu.:3.000   1st Qu.:9.657e+08   Class :character   Class :character  
+##  14463  :   3718   480    :  12390   Median :3.500   Median :1.059e+09   Mode  :character   Mode  :character  
 ##  68259  :   3228   593    :  12333   Mean   :3.472   Mean   :1.051e+09                                        
@@
 ##  (Other):5516391   (Other):5466292
-##     title              genres         
-##  Length:5539951     Length:5539951    
-##  Class :character   Class :character  
-##  Mode  :character   Mode  :character  
-##                                       
-##                                       
-##                                       
-## 
 \end{verbatim}
@@
 \begin{verbatim}
-##  [1] -3.0 -2.9 -2.8 -2.7 -2.6 -2.5 -2.4 -2.3 -2.2 -2.1 -2.0 -1.9 -1.8 -1.7 -1.6
-## [16] -1.5 -1.4 -1.3 -1.2 -1.1 -1.0 -0.9 -0.8 -0.7 -0.6 -0.5 -0.4 -0.3 -0.2 -0.1
-## [31]  0.0  0.1  0.2  0.3  0.4  0.5  0.6  0.7  0.8  0.9  1.0  1.1  1.2  1.3  1.4
-## [46]  1.5  1.6  1.7  1.8  1.9  2.0  2.1  2.2  2.3  2.4  2.5  2.6  2.7  2.8  2.9
-## [61]  3.0
+##  [1] -3.0 -2.9 -2.8 -2.7 -2.6 -2.5 -2.4 -2.3 -2.2 -2.1 -2.0 -1.9 -1.8 -1.7 -1.6 -1.5 -1.4 -1.3 -1.2 -1.1 -1.0 -0.9 -0.8 -0.7 -0.6 -0.5 -0.4 -0.3 -0.2 -0.1  0.0  0.1  0.2  0.3  0.4  0.5
+## [37]  0.6  0.7  0.8  0.9  1.0  1.1  1.2  1.3  1.4  1.5  1.6  1.7  1.8  1.9  2.0  2.1  2.2  2.3  2.4  2.5  2.6  2.7  2.8  2.9  3.0
 \end{verbatim}

### 2025-05-03 r/src/capstone-movielens.main.R

@@ -1,90 +1,3 @@
-## Setup -----------------------------------------------------------------------
-#> Reference: Some ideas and code snippers were used from the following GitHub repository:
-#> https://github.com/AzKurban-edX-DS/harvardx-movielens
-
-if(!require(tidyverse))
-  install.packages("tidyverse", repos = "http://cran.us.r-project.org")
-
-#> `stringr` library is already included to the `tidyverse` package,
-#> there's no need to install `stringr`
-# if(!require(stringr))
-#   install.packages("stringr")
-
-if(!require(caret))
-  install.packages("caret", repos = "http://cran.us.r-project.org")
-if(!require(data.table))
-  install.packages("data.table", repos = "http://cran.us.r-project.org")
-if(!require(gridExtra))
-  install.packages("gridExtra")
-if(!require("logr")) 
-  install.packages("logr")
-
-if(!require(gtools)) 
-  install.packages("gtools")
-if(!require(pak)) 
-  install.packages("pak")
-if(!require("pacman")) 
-  install.packages("pacman")
-
-if(!require("recommenderlab")) 
-  install.packages("recommenderlab")
-
-# Loading the required libraries
-library(dslabs)
-library(tidyverse)
-
-library(caret)
-library(cowplot)
-library(data.table)
-library(dplyr)
-library(ggplot2)
-library(ggthemes)
-library(lubridate)
-library(Metrics)
-library(recosystem)
-library(recommenderlab)
-
-library(scales)
-library(stringr)
-library(tibble)
-library(tidyr)
-library(gridExtra)
-library(logr)
-
-library(rafalib)
-library(gtools)
-library(pak)
-library(pacman)
-
-p_load(conflicted, latex2exp, kableExtra)
-
-### Resolve conflicts ----------------------------------------------------------
-
-# For functions with identical names in different packages, ensure the
-# right one is chosen:
-conflict_prefer("first", "dplyr", quiet = TRUE)
-conflict_prefer("count", "dplyr", quiet = TRUE)
-conflict_prefer("select", "dplyr", quiet = TRUE)
-conflict_prefer("group_by", "dplyr", quiet = TRUE)
-conflict_prefer("ungroup", "dplyr", quiet = TRUE)
-conflict_prefer("summarise", "dplyr", quiet = TRUE)
-conflict_prefer("summarize", "dplyr", quiet = TRUE)
-conflict_prefer("distinct", "dplyr", quiet = TRUE)
-conflict_prefer("top_n", "dplyr", quiet = TRUE)
[…]

### 2025-05-04 reports/capstone-movielens-report.draft4.Rmd
pdf-report updated.

@@
 ## Methods / Analysis
-### Defining helper functions
+:::{.callout-note}
+All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src). 
+:::
+
+### Defining Logging and Mesuring helper functions
 \
 
-Let's define some helper functions that we will use in our subsequent analysis:
+Let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
+
 ```{r}
-start_date <- function(){
+open_logfile <- function(file_name){
+  log_file_name <- as.character(Sys.time()) |> 
+    str_replace_all(':', '_') |> 
+    str_replace(' ', 'T') |>
+    str_c(file_name)
+
+  log_open(file_name = log_file_name)
+}
+print_start_date <- function(){
   print(date())
@@
 }
-end_date <- function(start){
+put_start_date <- function(){
+  put(date())
+  Sys.time()
+}
+print_end_date <- function(start){
   print(date())
-  Sys.time() - start
+  print(Sys.time() - start)
 }
-rmse <- function(r) sqrt(mean(r^2))
-RMSE <- function(true_ratings, predicted_ratings){
-  sqrt(mean((true_ratings - predicted_ratings)^2))
+put_end_date <- function(start){
+  put(date())
+  put(Sys.time() - start)
 }
 
-# Because we know ratings can’t be below 0.5 or above 5, 
-# we define the function clamp:
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
+print_log <- function(msg){
+  print(str_glue(msg))
+}
+put_log <- function(msg){
+  put(str_glue(msg))
+}
+put_log1 <- function(msg_template, arg1){
+  msg <- str_replace_all(msg_template, "%1", as.character(arg1))
+  put(str_glue(msg))
+}
+put_log2 <- function(msg_template, arg1, arg2){
+  msg <- msg_template |> 
+    str_replace_all("%1", as.character(arg1)) |>
+    str_replace_all("%2", as.character(arg2)) |>
+    str_glue()
+
+  put(msg)
+}
 
 ```
+
+:::{.callout-note}
+The full source code of these functions is available in the [Logging Helper function section of the Capstone MovieLens Main R Script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/capstone-movielens.main.R#L1).
+:::
 

### 2025-05-04 reports/capstone-movielens-report.draft4.tex
pdf-report updated.

@@
 \author{Azamat Kurbanaev}
-\date{2025-05-03}
+\date{2025-05-04}
 
@@
 
-\subsubsection{Defining helper
-functions}\label{defining-helper-functions}
-
-\hfill\break
-
-Let's define some helper functions that we will use in our subsequent
-analysis:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{start\_date }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{()\{}
+All the source code of the R-scripts is available on the project's
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src}{GitHub
+repository}.
+
+\subsubsection{Defining Logging and Mesuring helper
+functions}\label{defining-logging-and-mesuring-helper-functions}
+
+\hfill\break
+
+Let's define some helper functions for logging and time-measuring
+features that we will use in our R scripts. Some of them are listed
+below:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{open\_logfile }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(file\_name)\{}
+\NormalTok{  log\_file\_name }\OtherTok{\textless{}{-}} \FunctionTok{as.character}\NormalTok{(}\FunctionTok{Sys.time}\NormalTok{()) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{str\_replace\_all}\NormalTok{(}\StringTok{\textquotesingle{}:\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}\_\textquotesingle{}}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{str\_replace}\NormalTok{(}\StringTok{\textquotesingle{} \textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}T\textquotesingle{}}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{str\_c}\NormalTok{(file\_name)}
+
+  \FunctionTok{log\_open}\NormalTok{(}\AttributeTok{file\_name =}\NormalTok{ log\_file\_name)}
+\NormalTok{\}}
+\NormalTok{print\_start\_date }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{()\{}
   \FunctionTok{print}\NormalTok{(}\FunctionTok{date}\NormalTok{())}
@@
 \NormalTok{\}}
-\NormalTok{end\_date }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(start)\{}
+\NormalTok{put\_start\_date }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{()\{}
+  \FunctionTok{put}\NormalTok{(}\FunctionTok{date}\NormalTok{())}
+  \FunctionTok{Sys.time}\NormalTok{()}
+\NormalTok{\}}
+\NormalTok{print\_end\_date }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(start)\{}
   \FunctionTok{print}\NormalTok{(}\FunctionTok{date}\NormalTok{())}
-  \FunctionTok{Sys.time}\NormalTok{() }\SpecialCharTok{{-}}\NormalTok{ start}
+  \FunctionTok{print}\NormalTok{(}\FunctionTok{Sys.time}\NormalTok{() }\SpecialCharTok{{-}}\NormalTok{ start)}
 \NormalTok{\}}
-\NormalTok{rmse }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(r) }\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mean}\NormalTok{(r}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}
-\NormalTok{RMSE }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(true\_ratings, predicted\_ratings)\{}
-  \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mean}\NormalTok{((true\_ratings }\SpecialCharTok{{-}}\NormalTok{ predicted\_ratings)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{))}
+\NormalTok{put\_end\_date }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(start)\{}
+  \FunctionTok{put}\NormalTok{(}\FunctionTok{date}\NormalTok{())}
+  \FunctionTok{put}\NormalTok{(}\FunctionTok{Sys.time}\NormalTok{() }\SpecialCharTok{{-}}\NormalTok{ start)}
 \NormalTok{\}}
 
-\CommentTok{\# Because we know ratings can’t be below 0.5 or above 5, }
-\CommentTok{\# we define the function clamp:}
-\NormalTok{clamp }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x, }\AttributeTok{min =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{max =} \DecValTok{5}\NormalTok{) }\FunctionTok{pmax}\NormalTok{(}\FunctionTok{pmin}\NormalTok{(x, max), min)}
-\end{Highlighting}
-\end{Shaded}
+\NormalTok{print\_log }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg)\{}
+  \FunctionTok{print}\NormalTok{(}\FunctionTok{str\_glue}\NormalTok{(msg))}
+\NormalTok{\}}
+\NormalTok{put\_log }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg)\{}
+  \FunctionTok{put}\NormalTok{(}\FunctionTok{str\_glue}\NormalTok{(msg))}
+\NormalTok{\}}
+\NormalTok{put\_log1 }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg\_template, arg1)\{}
+\NormalTok{  msg }\OtherTok{\textless{}{-}} \FunctionTok{str\_replace\_all}\NormalTok{(msg\_template, }\StringTok{"\%1"}\NormalTok{, }\FunctionTok{as.character}\NormalTok{(arg1))}
+  \FunctionTok{put}\NormalTok{(}\FunctionTok{str\_glue}\NormalTok{(msg))}
+\NormalTok{\}}
+\NormalTok{put\_log2 }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg\_template, arg1, arg2)\{}
+\NormalTok{  msg }\OtherTok{\textless{}{-}}\NormalTok{ msg\_template }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{str\_replace\_all}\NormalTok{(}\StringTok{"\%1"}\NormalTok{, }\FunctionTok{as.character}\NormalTok{(arg1)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{str\_replace\_all}\NormalTok{(}\StringTok{"\%2"}\NormalTok{, }\FunctionTok{as.character}\NormalTok{(arg2)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{str\_glue}\NormalTok{()}
+
+  \FunctionTok{put}\NormalTok{(msg)}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+The full source code of these functions is available in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/capstone-movielens.main.R\#L1}{Logging
+Helper function section of the Capstone MovieLens Main R Script}.
 

### 2025-05-04 reports/capstone-movielens-report.draft4.Rmd
Draft report updated.

@@
 header-includes:
+    - \usepackage{awesomebox}
     - \usepackage{hyperref}
@@
 ---
+
+\newenvironment{infobox}[1]
+  {
+  \begin{itemize}
+  \renewcommand{\labelitemi}{
+    \raisebox{-.7\height}[0pt][0pt]{
+      {\setkeys{Gin}{width=3em,keepaspectratio}
+        \includegraphics{images/#1}}
+    }
+  }
+  \setlength{\fboxsep}{1em}
+  \begin{blackbox}
+  \item
+  }
+  {
+  \end{blackbox}
+  \end{itemize}
+  }
 
@@
 
-## Plot dependency of RMSEs vs Overal Mean Rating Deviation
-\
-```{r}
-
-data.frame(delta = deviation, 
-           delta.RMSE = deviation.RMSE) |> 
-tuning.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
-              xname = "delta", 
-              yname = "delta.RMSE", 
-              xlabel = TeX(r'[$\delta$]'), 
-              ylabel = "RMSE")
-
-```
-
 ## Introduction / Overview / Executive Summary
@@
 
-### Datasets
-
-``` {r , echo = FALSE}
-```
+### Datasets Overview
 
@@
 Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r }
+```{r eval=FALSE }
 if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
@@
 final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
+```
 
+Now, we have the datasets listed above:
+```{r }
 summary(edx)
+```
+
+```{r }
 summary(final_holdout_test)
 ```
+
 #### `edx` Dataset
@@
 
-Also, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
+First, let's note that we have 10677 different movies: 
+```{r}
+n_movies <- n_distinct(edx$movieId)
+print(n_movies)
+```
+and 69878 different users in the dataset:
+```{r}
+n_users <- n_distinct(edx$userId)
+print(n_users)
+```
+
+Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
+```{r}
+max_possible_ratings <- n_movies*n_users
+sprintf("Maximum possible ratings: %s", max_possible_ratings)
+sprintf("Rows in `edx` dataset: %s", dim_edx[1])
+sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
+
+```
+
+As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
+Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
+A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
+```{r}
+keep <- edx |> 
+  dplyr::count(movieId) |> 
+  top_n(4, n) |> 
+  pull(movieId)
+
+tab <- edx |> 
+  filter(movieId %in% keep) |> 
+  filter(userId %in% c(13:20)) |> 
+  select(userId, title, rating) |> 
+  mutate(title = str_remove(title, ", The"),
+         title = str_remove(title, ":.*")) |>
+  pivot_wider(names_from = "title", values_from = "rating")
+
+print(tab)
+```
+
+The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
+```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
+users <- sample(unique(edx$userId), 100)
+
+rafalib::mypar()
+edx|> 
+  filter(userId %in% users) |> 
+  select(userId, movieId, rating) |>
+  mutate(rating = 1) |>
+  pivot_wider(names_from = movieId, values_from = rating) |> 
+  (\(mat) mat[, sample(ncol(mat), 100)])() |>
+  as.matrix() |> 
+  t() |>
+  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
+```
+
+Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
+```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
+p1 <- edx |> 
+  count(movieId) |> 
+  ggplot(aes(n)) + 
+  geom_histogram(bins = 30, color = "black") + 
+  scale_x_log10() + 
+  ggtitle("Movies")
+
+p2 <- edx |> 
+  count(userId) |> 
+  ggplot(aes(n)) + 
+  geom_histogram(bins = 30, color = "black") + 
+  scale_x_log10() + 
+  ggtitle("Users")
+
+gridExtra::grid.arrange(p2, p1, ncol = 2)
+```
+
+Finally, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
 ```{r }
@@
 ## Methods / Analysis
-:::{.callout-note}
+::: {.noteblock data-latex=""}
 All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src). 
@@
 
-Let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
+First, let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
 
-```{r}
+```{r eval=FALSE }
 open_logfile <- function(file_name){
@@
 
-:::{.callout-note}
+::: {.noteblock data-latex=""}
 The full source code of these functions is available in the [Logging Helper function section of the Capstone MovieLens Main R Script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/capstone-movielens.main.R#L1).
@@
 \
-First, let's note that we have 10677 different movies: 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
 
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
+We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method the way described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
+To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
 
-```
+- `make_source_datasets`;
+- `init_source_datasets`.
 
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
+::: {.noteblock data-latex=""}
+The full source code of the function listed above is available in the [`Initialize input datasets` section of the `data.helper.functions.R` script on _GitHub_](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R#L86)
+:::
 
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Taking into consideration these observations, we came up with a decision to use the data from the dataset only for users who have provided at least 100 ratings.
-
-Now let's split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in the [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1]:
-```{r}
+```{r eval=FALSE, echo=TRUE, include=TRUE}
 # Let's ignore the data for users who have not provided at least 100 ratings:

### 2025-05-04 reports/capstone-movielens-report.draft4.tex
Draft report updated.

@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\usepackage{awesomebox}
 \usepackage{hyperref}
@@
 \author{Azamat Kurbanaev}
-\date{2025-05-04}
+\date{2025-05-05}
 
@@
 }
-\subsection{Plot dependency of RMSEs vs Overal Mean Rating
-Deviation}\label{plot-dependency-of-rmses-vs-overal-mean-rating-deviation}
-
-\hfill\break
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{delta =}\NormalTok{ deviation, }
-           \AttributeTok{delta.RMSE =}\NormalTok{ deviation.RMSE) }\SpecialCharTok{|\textgreater{}} 
-\FunctionTok{tuning.plot}\NormalTok{(}\AttributeTok{title =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[RMSE as a function of deviation ($\textbackslash{}delta$) from the Overall Mean Rating ($\textbackslash{}hat\{mu\}$)]\textquotesingle{}}\NormalTok{),}
-              \AttributeTok{xname =} \StringTok{"delta"}\NormalTok{, }
-              \AttributeTok{yname =} \StringTok{"delta.RMSE"}\NormalTok{, }
-              \AttributeTok{xlabel =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[$\textbackslash{}delta$]\textquotesingle{}}\NormalTok{), }
-              \AttributeTok{ylabel =} \StringTok{"RMSE"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-1-1.pdf}
+\newenvironment{infobox}[1]
+  {
+  \begin{itemize}
+  \renewcommand{\labelitemi}{
+    \raisebox{-.7\height}[0pt][0pt]{
+      {\setkeys{Gin}{width=3em,keepaspectratio}
+        \includegraphics{images/#1}}
+    }
+  }
+  \setlength{\fboxsep}{1em}
+  \begin{blackbox}
+  \item
+  }
+  {
+  \end{blackbox}
+  \end{itemize}
+  }
 
@@
 
-\subsubsection{Datasets}\label{datasets}
+\subsubsection{Datasets Overview}\label{datasets-overview}
 
@@
 \NormalTok{final\_holdout\_test }\OtherTok{\textless{}{-}}\NormalTok{ edx.capstone.movielens.data}\SpecialCharTok{::}\NormalTok{final\_holdout\_test}
-
+\end{Highlighting}
+\end{Shaded}
+
+Now, we have the datasets listed above:
+
+\begin{Shaded}
+\begin{Highlighting}[]
 \FunctionTok{summary}\NormalTok{(edx)}
@@
 
-Also, we can see that no movies have a rating of 0. Movies are rated
+First, let's note that we have 10677 different movies:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{n\_movies }\OtherTok{\textless{}{-}} \FunctionTok{n\_distinct}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{movieId)}
+\FunctionTok{print}\NormalTok{(n\_movies)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 10677
+\end{verbatim}
+
+and 69878 different users in the dataset:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{n\_users }\OtherTok{\textless{}{-}} \FunctionTok{n\_distinct}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{userId)}
+\FunctionTok{print}\NormalTok{(n\_users)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 69878
+\end{verbatim}
+
+Now, note the expressions below which confirm the fact explained in
+\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movielens-data}{Section
+\emph{23.1.1 Movielens data}} of the \emph{Course
+Textbook}\autocite{IDS2} that not every user rated every movie:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{max\_possible\_ratings }\OtherTok{\textless{}{-}}\NormalTok{ n\_movies}\SpecialCharTok{*}\NormalTok{n\_users}
+\FunctionTok{sprintf}\NormalTok{(}\StringTok{"Maximum possible ratings: \%s"}\NormalTok{, max\_possible\_ratings)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] "Maximum possible ratings: 746087406"
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{sprintf}\NormalTok{(}\StringTok{"Rows in \textasciigrave{}edx\textasciigrave{} dataset: \%s"}\NormalTok{, dim\_edx[}\DecValTok{1}\NormalTok{])}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] "Rows in `edx` dataset: 9000055"
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{sprintf}\NormalTok{(}\StringTok{"Not every movie was rated: \%s"}\NormalTok{, max\_possible\_ratings }\SpecialCharTok{\textgreater{}}\NormalTok{ dim\_edx[}\DecValTok{1}\NormalTok{])}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] "Not every movie was rated: TRUE"
+\end{verbatim}
+
+As also explained in that section, we can think of these data as a very
+large matrix, with users on the rows and movies on the columns, with
+many empty cells. Therefore, we can think of a recommendation system as
+filling in the \texttt{NA}s in the dataset for the movies that some or
+all the users do not rate. A sample from the \texttt{edx} data below
+illustrates this idea\autocite{IDS2_23-1-1}:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{keep }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
+\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{count}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{top\_n}\NormalTok{(}\DecValTok{4}\NormalTok{, n) }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{pull}\NormalTok{(movieId)}
+
+\NormalTok{tab }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{filter}\NormalTok{(movieId }\SpecialCharTok{\%in\%}\NormalTok{ keep) }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{filter}\NormalTok{(userId }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\DecValTok{13}\SpecialCharTok{:}\DecValTok{20}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{select}\NormalTok{(userId, title, rating) }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{title =} \FunctionTok{str\_remove}\NormalTok{(title, }\StringTok{", The"}\NormalTok{),}
+         \AttributeTok{title =} \FunctionTok{str\_remove}\NormalTok{(title, }\StringTok{":.*"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =} \StringTok{"title"}\NormalTok{, }\AttributeTok{values\_from =} \StringTok{"rating"}\NormalTok{)}
+
+\FunctionTok{print}\NormalTok{(tab)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## # A tibble: 5 x 5
+##   userId `Pulp Fiction (1994)` `Jurassic Park (1993)` `Silence of the Lambs (1991)` `Forrest Gump (1994)`
+##    <int>                 <dbl>                  <dbl>                         <dbl>                 <dbl>
+## 1     13                     4                     NA                            NA                    NA
+## 2     16                    NA                      3                            NA                    NA
+## 3     17                    NA                     NA                             5                    NA
+## 4     18                     5                      3                             5                    NA
+## 5     19                    NA                      1                            NA                     4
+\end{verbatim}
+
+The following plot of the matrix for a random sample of 100 movies and
+100 users with yellow indicating a user/movie combination for which we
+have a rating shows how \emph{sparse} the matrix is:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{users }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(}\FunctionTok{unique}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{userId), }\DecValTok{100}\NormalTok{)}
+
+\NormalTok{rafalib}\SpecialCharTok{::}\FunctionTok{mypar}\NormalTok{()}
+\NormalTok{edx}\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{filter}\NormalTok{(userId }\SpecialCharTok{\%in\%}\NormalTok{ users) }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{select}\NormalTok{(userId, movieId, rating) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{rating =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ movieId, }\AttributeTok{values\_from =}\NormalTok{ rating) }\SpecialCharTok{|\textgreater{}} 
+\NormalTok{  (\textbackslash{}(mat) mat[, }\FunctionTok{sample}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(mat), }\DecValTok{100}\NormalTok{)])() }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{as.matrix}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{t}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{image}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\DecValTok{100}\NormalTok{, }\DecValTok{1}\SpecialCharTok{:}\DecValTok{100}\NormalTok{, }\AttributeTok{z =}\NormalTok{ \_ , }\AttributeTok{xlab =} \StringTok{"Movies"}\NormalTok{, }\AttributeTok{ylab =} \StringTok{"Users"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics[width=0.4\linewidth]{capstone-movielens-report.draft4_files/figure-latex/sparsity-of-movie-recs-1}
+
+Further observations highlighted there that, as we can see from the
+distributions the author presented, some movies get rated more than
+others, and some users are more active than others in rating movies:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{p1 }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{count}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(n)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_histogram}\NormalTok{(}\AttributeTok{bins =} \DecValTok{30}\NormalTok{, }\AttributeTok{color =} \StringTok{"black"}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{scale\_x\_log10}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Movies"}\NormalTok{)}
+
+\NormalTok{p2 }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{count}\NormalTok{(userId) }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(n)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_histogram}\NormalTok{(}\AttributeTok{bins =} \DecValTok{30}\NormalTok{, }\AttributeTok{color =} \StringTok{"black"}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{scale\_x\_log10}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Users"}\NormalTok{)}
+
+\NormalTok{gridExtra}\SpecialCharTok{::}\FunctionTok{grid.arrange}\NormalTok{(p2, p1, }\AttributeTok{ncol =} \DecValTok{2}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/movie-id-and-user-hists-1.pdf}
+
+Finally, we can see that no movies have a rating of 0. Movies are rated
 from 0.5 to 5.0 in 0.5 increments:
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-12-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-16-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-16-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-20-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-23-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-20-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-24-1.pdf}
 
@@
 
+\begin{noteblock}
 All the source code of the R-scripts is available on the project's
@@
 
+\end{noteblock}
+
 \subsubsection{Defining Logging and Mesuring helper
@@
 
-Let's define some helper functions for logging and time-measuring
+First, let's define some helper functions for logging and time-measuring
 features that we will use in our R scripts. Some of them are listed
@@
 
+\begin{noteblock}
 The full source code of these functions is available in the
@@
 
+\end{noteblock}
+
 \subsubsection{Preparing train and set
@@
 \hfill\break
-First, let's note that we have 10677 different movies:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{n\_movies }\OtherTok{\textless{}{-}} \FunctionTok{n\_distinct}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{movieId)}
-\FunctionTok{print}\NormalTok{(n\_movies)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 10677
-\end{verbatim}
-
-and 69878 different users in the dataset:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{n\_users }\OtherTok{\textless{}{-}} \FunctionTok{n\_distinct}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{userId)}
-\FunctionTok{print}\NormalTok{(n\_users)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 69878
-\end{verbatim}
-
-Now, note the expressions below which confirm the fact explained in
-\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movielens-data}{Section
-\emph{23.1.1 Movielens data}} of the \emph{Course
-Textbook}\autocite{IDS2} that not every user rated every movie:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{max\_possible\_ratings }\OtherTok{\textless{}{-}}\NormalTok{ n\_movies}\SpecialCharTok{*}\NormalTok{n\_users}
-\FunctionTok{sprintf}\NormalTok{(}\StringTok{"Maximum possible ratings: \%s"}\NormalTok{, max\_possible\_ratings)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] "Maximum possible ratings: 746087406"
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{sprintf}\NormalTok{(}\StringTok{"Rows in \textasciigrave{}edx\textasciigrave{} dataset: \%s"}\NormalTok{, dim\_edx[}\DecValTok{1}\NormalTok{])}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] "Rows in `edx` dataset: 9000055"
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{sprintf}\NormalTok{(}\StringTok{"Not every movie was rated: \%s"}\NormalTok{, max\_possible\_ratings }\SpecialCharTok{\textgreater{}}\NormalTok{ dim\_edx[}\DecValTok{1}\NormalTok{])}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] "Not every movie was rated: TRUE"
-\end{verbatim}
-
-As also explained in that section, we can think of these data as a very
-large matrix, with users on the rows and movies on the columns, with
-many empty cells. Therefore, we can think of a recommendation system as
-filling in the \texttt{NA}s in the dataset for the movies that some or
-all the users do not rate. A sample from the \texttt{edx} data below
-illustrates this idea\autocite{IDS2_23-1-1}:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{keep }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
-\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{count}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{top\_n}\NormalTok{(}\DecValTok{4}\NormalTok{, n) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{pull}\NormalTok{(movieId)}
-
-\NormalTok{tab }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{filter}\NormalTok{(movieId }\SpecialCharTok{\%in\%}\NormalTok{ keep) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{filter}\NormalTok{(userId }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\DecValTok{13}\SpecialCharTok{:}\DecValTok{20}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{select}\NormalTok{(userId, title, rating) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{title =} \FunctionTok{str\_remove}\NormalTok{(title, }\StringTok{", The"}\NormalTok{),}
-         \AttributeTok{title =} \FunctionTok{str\_remove}\NormalTok{(title, }\StringTok{":.*"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =} \StringTok{"title"}\NormalTok{, }\AttributeTok{values\_from =} \StringTok{"rating"}\NormalTok{)}
-
-\FunctionTok{print}\NormalTok{(tab)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## # A tibble: 5 x 5
-##   userId `Pulp Fiction (1994)` `Jurassic Park (1993)` `Silence of the Lambs (1991)` `Forrest Gump (1994)`
-##    <int>                 <dbl>                  <dbl>                         <dbl>                 <dbl>
-## 1     13                     4                     NA                            NA                    NA
-## 2     16                    NA                      3                            NA                    NA
-## 3     17                    NA                     NA                             5                    NA
-## 4     18                     5                      3                             5                    NA
-## 5     19                    NA                      1                            NA                     4
-\end{verbatim}
-
-The following plot of the matrix for a random sample of 100 movies and
-100 users with yellow indicating a user/movie combination for which we
-have a rating shows how \emph{sparse} the matrix is:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{users }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(}\FunctionTok{unique}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{userId), }\DecValTok{100}\NormalTok{)}
-
-\NormalTok{rafalib}\SpecialCharTok{::}\FunctionTok{mypar}\NormalTok{()}
-\NormalTok{edx}\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{filter}\NormalTok{(userId }\SpecialCharTok{\%in\%}\NormalTok{ users) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{select}\NormalTok{(userId, movieId, rating) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{rating =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ movieId, }\AttributeTok{values\_from =}\NormalTok{ rating) }\SpecialCharTok{|\textgreater{}} 
-\NormalTok{  (\textbackslash{}(mat) mat[, }\FunctionTok{sample}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(mat), }\DecValTok{100}\NormalTok{)])() }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{as.matrix}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{t}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{image}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\DecValTok{100}\NormalTok{, }\DecValTok{1}\SpecialCharTok{:}\DecValTok{100}\NormalTok{, }\AttributeTok{z =}\NormalTok{ \_ , }\AttributeTok{xlab =} \StringTok{"Movies"}\NormalTok{, }\AttributeTok{ylab =} \StringTok{"Users"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics[width=0.4\linewidth]{capstone-movielens-report.draft4_files/figure-latex/sparsity-of-movie-recs-1}
-
-Further observations highlighted there that, as we can see from the
-distributions the author presented, some movies get rated more than
-others, and some users are more active than others in rating movies:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{p1 }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{count}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(n)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_histogram}\NormalTok{(}\AttributeTok{bins =} \DecValTok{30}\NormalTok{, }\AttributeTok{color =} \StringTok{"black"}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{scale\_x\_log10}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Movies"}\NormalTok{)}
-
-\NormalTok{p2 }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{count}\NormalTok{(userId) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(n)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_histogram}\NormalTok{(}\AttributeTok{bins =} \DecValTok{30}\NormalTok{, }\AttributeTok{color =} \StringTok{"black"}\NormalTok{) }\SpecialCharTok{+} 
-  \FunctionTok{scale\_x\_log10}\NormalTok{() }\SpecialCharTok{+} 
-  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Users"}\NormalTok{)}
-
-\NormalTok{gridExtra}\SpecialCharTok{::}\FunctionTok{grid.arrange}\NormalTok{(p2, p1, }\AttributeTok{ncol =} \DecValTok{2}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/movie-id-and-user-hists-1.pdf}
-
-Taking into consideration these observations, we came up with a decision
-to use the data from the dataset only for users who have provided at
-least 100 ratings.
-
-Now let's split the \texttt{edx} dataset into a training set, which we
+
+We will split the \texttt{edx} dataset into a training set, which we
 will use to build and train our models, and a test set in which we will
-compute the accuracy of our predictions, the way described in the
+compute the accuracy of our predictions, the way described in
 \href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movielens-data}{Section
 23.1.1 Movielens data} of the \emph{Course Textbook} mentioned
-above\autocite{IDS2_23-1-1}:
+above\autocite{IDS2_23-1-1}.We will also use the \emph{5-Fold Cross
+Validation} method the way described in
+\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html\#cross-validation}{Section
+29.6 Cross validation} of the \emph{Course Textbook}. To prepare
+datasets for processing, we will use the following functions,
+specifically designed for these operations:
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{make\_source\_datasets};
+\item
+  \texttt{init\_source\_datasets}.
+\end{itemize}
+
+\begin{noteblock}
+The full source code of the function listed above is available in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R\#L86}{\texttt{Initialize\ input\ datasets}
+section of the \texttt{data.helper.functions.R} script on \emph{GitHub}}
+
+\end{noteblock}
 
@@
 \FunctionTok{print}\NormalTok{(edx100 }\SpecialCharTok{|\textgreater{}} \FunctionTok{summarize}\NormalTok{(}\FunctionTok{n\_distinct}\NormalTok{(userId), }\FunctionTok{n\_distinct}\NormalTok{(movieId)))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## # A tibble: 1 x 2
-##   `n_distinct(userId)` `n_distinct(movieId)`
-##                  <int>                 <int>
-## 1                24115                 10665
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
+
 \CommentTok{\# For each one of these users, we will split their ratings into 80\% for training }
@@
 \FunctionTok{summary}\NormalTok{(test\_set)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##      userId         movieId          rating        timestamp            title              genres         
-##  Min.   :    8   Min.   :    1   Min.   :0.500   Min.   :8.248e+08   Length:1397040     Length:1397040    
-##  1st Qu.:18161   1st Qu.: 1022   1st Qu.:3.000   1st Qu.:9.655e+08   Class :character   Class :character  
-##  Median :35666   Median : 2109   Median :3.500   Median :1.058e+09   Mode  :character   Mode  :character  
-##  Mean   :35902   Mean   : 4616   Mean   :3.473   Mean   :1.051e+09                                        
-##  3rd Qu.:53645   3rd Qu.: 3993   3rd Qu.:4.000   3rd Qu.:1.135e+09                                        
-##  Max.   :71565   Max.   :65133   Max.   :5.000   Max.   :1.231e+09
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
+
 \NormalTok{train\_set }\OtherTok{\textless{}{-}} \FunctionTok{mutate}\NormalTok{(train\_set, }\AttributeTok{userId =} \FunctionTok{factor}\NormalTok{(userId), }\AttributeTok{movieId =} \FunctionTok{factor}\NormalTok{(movieId))}
@@
 \end{Shaded}
-
-\begin{verbatim}
-##      userId           movieId            rating        timestamp            title              genres         
-##  59269  :   5292   356    :  12769   Min.   :0.500   Min.   :8.248e+08   Length:5539951     Length:5539951    
-##  67385  :   5088   296    :  12439   1st Qu.:3.000   1st Qu.:9.657e+08   Class :character   Class :character  
-##  14463  :   3718   480    :  12390   Median :3.500   Median :1.059e+09   Mode  :character   Mode  :character  
-##  68259  :   3228   593    :  12333   Mean   :3.472   Mean   :1.051e+09                                        
-##  27468  :   3218   260    :  12142   3rd Qu.:4.000   3rd Qu.:1.135e+09                                        
-##  19635  :   3016   1196   :  11586   Max.   :5.000   Max.   :1.231e+09                                        
-##  (Other):5516391   (Other):5466292
-\end{verbatim}
 

### 2025-05-05 reports/capstone-movielens-report.draft4.Rmd
Draft report updated.

@@
 
-##### 
-\
-```{r}
-
-```
-
-\
-```{r echo=FALSE}
-# #### [@MRS-R-BEST]
-```
-
 ## Methods / Analysis
 ::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src). 
+All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
 :::
@@
 To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
-
+```{r eval=FALSE }
+make_source_datasets()
+init_source_datasets()
+```
 - `make_source_datasets`;
@@
 :::
-
-```{r eval=FALSE, echo=TRUE, include=TRUE}
-# Let's ignore the data for users who have not provided at least 100 ratings:
-edx100 <- edx |> 
-  group_by(userId) |>
-  filter(n() >= 100) |>
-  ungroup()
-
-print(edx100 |> summarize(n_distinct(userId), n_distinct(movieId)))
-
-# For each one of these users, we will split their ratings into 80% for training 
-# and 20% for testing:
-
-set.seed(2006)
-indexes <- split(1:nrow(edx100), edx100$userId)
-test_ind <- sapply(indexes, function(i) sample(i, ceiling(length(i)*.2))) |> 
-  unlist() |>
-  sort()
-
-test_set <- edx100[test_ind,] 
-train_set <- edx100[-test_ind,]
-
-# To make sure we don’t include movies in the training set that should not be 
-# there, we remove entries using the semi_join function:
-test_set <- test_set |> semi_join(train_set, by = "movieId") |> as.data.frame()
-summary(test_set)
-
-train_set <- mutate(train_set, userId = factor(userId), movieId = factor(movieId))
-summary(train_set)
-```
 

### 2025-05-05 reports/capstone-movielens-report.draft4.tex
Draft report updated.

@@
 
-\subparagraph{}\label{section}
-
-\hfill\break
-
-\hfill\break
-
 \subsection{Methods / Analysis}\label{methods-analysis}
@@
 \href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src}{GitHub
-repository}.
+repository}\autocite{edx_capstone_movielens}.
 
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{make\_source\_datasets}\NormalTok{()}
+\FunctionTok{init\_source\_datasets}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
+
 \begin{itemize}
@@
 \end{noteblock}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Let\textquotesingle{}s ignore the data for users who have not provided at least 100 ratings:}
-\NormalTok{edx100 }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{group\_by}\NormalTok{(userId) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{filter}\NormalTok{(}\FunctionTok{n}\NormalTok{() }\SpecialCharTok{\textgreater{}=} \DecValTok{100}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{ungroup}\NormalTok{()}
-
-\FunctionTok{print}\NormalTok{(edx100 }\SpecialCharTok{|\textgreater{}} \FunctionTok{summarize}\NormalTok{(}\FunctionTok{n\_distinct}\NormalTok{(userId), }\FunctionTok{n\_distinct}\NormalTok{(movieId)))}
-
-\CommentTok{\# For each one of these users, we will split their ratings into 80\% for training }
-\CommentTok{\# and 20\% for testing:}
-
-\FunctionTok{set.seed}\NormalTok{(}\DecValTok{2006}\NormalTok{)}
-\NormalTok{indexes }\OtherTok{\textless{}{-}} \FunctionTok{split}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(edx100), edx100}\SpecialCharTok{$}\NormalTok{userId)}
-\NormalTok{test\_ind }\OtherTok{\textless{}{-}} \FunctionTok{sapply}\NormalTok{(indexes, }\ControlFlowTok{function}\NormalTok{(i) }\FunctionTok{sample}\NormalTok{(i, }\FunctionTok{ceiling}\NormalTok{(}\FunctionTok{length}\NormalTok{(i)}\SpecialCharTok{*}\NormalTok{.}\DecValTok{2}\NormalTok{))) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{unlist}\NormalTok{() }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{sort}\NormalTok{()}
-
-\NormalTok{test\_set }\OtherTok{\textless{}{-}}\NormalTok{ edx100[test\_ind,] }
-\NormalTok{train\_set }\OtherTok{\textless{}{-}}\NormalTok{ edx100[}\SpecialCharTok{{-}}\NormalTok{test\_ind,]}
-
-\CommentTok{\# To make sure we don’t include movies in the training set that should not be }
-\CommentTok{\# there, we remove entries using the semi\_join function:}
-\NormalTok{test\_set }\OtherTok{\textless{}{-}}\NormalTok{ test\_set }\SpecialCharTok{|\textgreater{}} \FunctionTok{semi\_join}\NormalTok{(train\_set, }\AttributeTok{by =} \StringTok{"movieId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \FunctionTok{as.data.frame}\NormalTok{()}
-\FunctionTok{summary}\NormalTok{(test\_set)}
-
-\NormalTok{train\_set }\OtherTok{\textless{}{-}} \FunctionTok{mutate}\NormalTok{(train\_set, }\AttributeTok{userId =} \FunctionTok{factor}\NormalTok{(userId), }\AttributeTok{movieId =} \FunctionTok{factor}\NormalTok{(movieId))}
-\FunctionTok{summary}\NormalTok{(train\_set)}
-\end{Highlighting}
-\end{Shaded}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-32-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-30-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-33-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-31-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-39-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-37-1.pdf}
 Now we can determine the minimal \emph{RMSE}:
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-45-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-43-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-46-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-44-1.pdf}
 Below are worst and best ratings categories:
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-48-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-46-1.pdf}
 

### 2025-05-05 reports/capstone-movielens-report.draft4.tex
Draft RMD report updated.

@@
 
-\subparagraph{Movie Genres Data}\label{movie-genres-data}
-
-\hfill\break
-The following code computes movie rating summaries by popular genres
-like Drama, Comedy, Thriller, and Romance:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\#library(stringr)}
-\NormalTok{genres }\OtherTok{=} \FunctionTok{c}\NormalTok{(}\StringTok{"Drama"}\NormalTok{, }\StringTok{"Comedy"}\NormalTok{, }\StringTok{"Thriller"}\NormalTok{, }\StringTok{"Romance"}\NormalTok{)}
-\FunctionTok{sapply}\NormalTok{(genres, }\ControlFlowTok{function}\NormalTok{(g) \{}
-  \FunctionTok{sum}\NormalTok{(}\FunctionTok{str\_detect}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{genres, g))}
-\NormalTok{\})}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##    Drama   Comedy Thriller  Romance 
-##  3910127  3540930  2325899  1712100
-\end{verbatim}
-
-Further, we can find out the movies that have the greatest number of
-ratings using the following code:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{ordered\_movie\_ratings }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(movieId, title) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{number\_of\_ratings =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(number\_of\_ratings))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## `summarise()` has grouped output by 'movieId'. You can override using the `.groups` argument.
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{print}\NormalTok{(}\FunctionTok{head}\NormalTok{(ordered\_movie\_ratings))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## # A tibble: 6 x 3
-## # Groups:   movieId [6]
-##   movieId title                            number_of_ratings
-##     <int> <chr>                                        <int>
-## 1     296 Pulp Fiction (1994)                          31362
-## 2     356 Forrest Gump (1994)                          31079
-## 3     593 Silence of the Lambs, The (1991)             30382
-## 4     480 Jurassic Park (1993)                         29360
-## 5     318 Shawshank Redemption, The (1994)             28015
-## 6     110 Braveheart (1995)                            26212
-\end{verbatim}
-
-and figure out the most given ratings in order from most to least:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{ratings }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}}  \FunctionTok{group\_by}\NormalTok{(rating) }\SpecialCharTok{|\textgreater{}}
-     \FunctionTok{summarise}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
-     \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(count))}
-\FunctionTok{print}\NormalTok{(ratings)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## # A tibble: 10 x 2
-##    rating   count
-##     <dbl>   <int>
-##  1    4   2588430
-##  2    3   2121240
-##  3    5   1390114
-##  4    3.5  791624
-##  5    2    711422
-##  6    4.5  526736
-##  7    1    345679
-##  8    2.5  333010
-##  9    1.5  106426
-## 10    0.5   85374
-\end{verbatim}
-
-The following code allows us to summarize that in general, half-star
-ratings are less common than whole-star ratings (e.g., there are fewer
-ratings of 3.5 than there are ratings of 3 or 4, etc.):
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{print}\NormalTok{(edx }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(rating) }\SpecialCharTok{|\textgreater{}} \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## # A tibble: 10 x 2
-##    rating   count
-##     <dbl>   <int>
-##  1    0.5   85374
-##  2    1    345679
-##  3    1.5  106426
-##  4    2    711422
-##  5    2.5  333010
-##  6    3   2121240
-##  7    3.5  791624
-##  8    4   2588430
-##  9    4.5  526736
-## 10    5   1390114
-\end{verbatim}
-
-We can visually see that from the following plot:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{edx }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{group\_by}\NormalTok{(rating) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ rating, }\AttributeTok{y =}\NormalTok{ count)) }\SpecialCharTok{+}
-  \FunctionTok{geom\_line}\NormalTok{() }
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
-
 Further analysis of the \texttt{edx} dataset have been also inspired by
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-16-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-18-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-20-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-23-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-22-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-24-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-23-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-30-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-29-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-31-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-30-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-37-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-36-1.pdf}
 Now we can determine the minimal \emph{RMSE}:
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-43-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-42-1.pdf}
 
@@
 movies fall under several genres)\autocite{IDS2_23-7}.
+
+\paragraph{Genre Data Analysis}\label{genre-data-analysis}
+
+\hfill\break
+\#\#\#\#\# Movie Genres Data\\
+The following code computes movie rating summaries by popular genres
+like Drama, Comedy, Thriller, and Romance:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\#library(stringr)}
+\NormalTok{genres }\OtherTok{=} \FunctionTok{c}\NormalTok{(}\StringTok{"Drama"}\NormalTok{, }\StringTok{"Comedy"}\NormalTok{, }\StringTok{"Thriller"}\NormalTok{, }\StringTok{"Romance"}\NormalTok{)}
+\FunctionTok{sapply}\NormalTok{(genres, }\ControlFlowTok{function}\NormalTok{(g) \{}
+  \FunctionTok{sum}\NormalTok{(}\FunctionTok{str\_detect}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{genres, g))}
+\NormalTok{\})}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+##    Drama   Comedy Thriller  Romance 
+##  3910127  3540930  2325899  1712100
+\end{verbatim}
+
+Further, we can find out the movies that have the greatest number of
+ratings using the following code:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{ordered\_movie\_ratings }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(movieId, title) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{number\_of\_ratings =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(number\_of\_ratings))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## `summarise()` has grouped output by 'movieId'. You can override using the `.groups` argument.
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{print}\NormalTok{(}\FunctionTok{head}\NormalTok{(ordered\_movie\_ratings))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## # A tibble: 6 x 3
+## # Groups:   movieId [6]
+##   movieId title                            number_of_ratings
+##     <int> <chr>                                        <int>
+## 1     296 Pulp Fiction (1994)                          31362
+## 2     356 Forrest Gump (1994)                          31079
+## 3     593 Silence of the Lambs, The (1991)             30382
+## 4     480 Jurassic Park (1993)                         29360
+## 5     318 Shawshank Redemption, The (1994)             28015
+## 6     110 Braveheart (1995)                            26212
+\end{verbatim}
+
+and figure out the most given ratings in order from most to least:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{ratings }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}}  \FunctionTok{group\_by}\NormalTok{(rating) }\SpecialCharTok{|\textgreater{}}
+     \FunctionTok{summarise}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
+     \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(count))}
+\FunctionTok{print}\NormalTok{(ratings)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## # A tibble: 10 x 2
+##    rating   count
+##     <dbl>   <int>
+##  1    4   2588430
+##  2    3   2121240
+##  3    5   1390114
+##  4    3.5  791624
+##  5    2    711422
+##  6    4.5  526736
+##  7    1    345679
+##  8    2.5  333010
+##  9    1.5  106426
+## 10    0.5   85374
+\end{verbatim}
+
+The following code allows us to summarize that in general, half-star
+ratings are less common than whole-star ratings (e.g., there are fewer
+ratings of 3.5 than there are ratings of 3 or 4, etc.):
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{print}\NormalTok{(edx }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(rating) }\SpecialCharTok{|\textgreater{}} \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## # A tibble: 10 x 2
+##    rating   count
+##     <dbl>   <int>
+##  1    0.5   85374
+##  2    1    345679
+##  3    1.5  106426
+##  4    2    711422
+##  5    2.5  333010
+##  6    3   2121240
+##  7    3.5  791624
+##  8    4   2588430
+##  9    4.5  526736
+## 10    5   1390114
+\end{verbatim}
+
+We can visually see that from the following plot:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{edx }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{group\_by}\NormalTok{(rating) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{count =} \FunctionTok{n}\NormalTok{()) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ rating, }\AttributeTok{y =}\NormalTok{ count)) }\SpecialCharTok{+}
+  \FunctionTok{geom\_line}\NormalTok{() }
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-47-1.pdf}
+
+\subparagraph{Movie Genres Effect}\label{movie-genres-effect}
+
+\hfill\break
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-44-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-48-1.pdf}
 Below are worst and best ratings categories:
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-46-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-50-1.pdf}
 

### 2025-05-05 r/src/support-functions/data.helper.functions.R
Minor fix for function: `make_source_datasets`.

@@ -201,7 +201,6 @@ Set of K-Fold Cross Validation datasets created: edx_CV")
   
   list(edx_CV = edx_CV,
        edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
        tuning_sets = tuning_sets,
        movie_map = movie_map,
        date_days_map = date_days_map)

### 2025-05-05 r/src/capstone-movielens.main.R
Fix for Main R Script.

@@ -1,3 +1,22 @@
+## Source File Paths -----------------------------------------------------------
+r.path <- "r"
+src.folder <- "src"
+support_scripts.folder <- "support-scripts"
+support_functions.folder <- "support-functions"
+
+r.src.path <- file.path(r.path, src.folder)
+support_scripts.path <- file.path(r.src.path, support_scripts.folder)
+support_functions.path <- file.path(r.src.path, support_functions.folder)
+## Setup -----------------------------------------------------------------------
+setup_script.file_path <- file.path(support_scripts.path,
+                                               "setup.R")
+source(setup_script.file_path, 
+       catch.aborts = TRUE,
+       echo = TRUE,
+       spaced = TRUE,
+       verbose = TRUE,
+       keep.source = TRUE)
+
 ## Logging Helper functions -----------------------------------------------------
 open_logfile <- function(file_name){
   log_file_name <- as.character(Sys.time()) |> 
@@ -69,25 +88,6 @@ put_log3 <- function(msg_template, arg1, arg2, arg3, arg4){
 }
 ### Open log file for `Initialize Source File Paths` Feature -------------------
 open_logfile(".src.file-paths")
-## Source File Paths -----------------------------------------------------------
-r.path <- "r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-## Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-source(setup_script.file_path, 
-       catch.aborts = TRUE,
-       echo = TRUE,
-       spaced = TRUE,
-       verbose = TRUE,
-       keep.source = TRUE)
-
 ## External Common Helper functions -------------------------------------
 common_helper_functions.file_path <- file.path(support_functions.path,
                                             "common-helper.functions.R")

### 2025-05-06 reports/capstone-movielens-report.draft4.Rmd
Draft RMD report updated.

@@
 
-##### Movie Genres Data 
-\
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r}
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r}
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r}
-print(edx |> group_by(rating) |> summarize(count = n()))
-```
-
-We can visually see that from the following plot:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
 Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
@@
 
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method the way described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
+We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
 To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
@@
 ```
-- `make_source_datasets`;
-- `init_source_datasets`.
 
@@
 
+#### The `make_source_datasets` function
+\
+
+Let's take a closer look at the objects we will receive as a result of executing this function.
+
+```{r eval=FALSE}
+
+make_source_datasets <- function(){
+  # ...
+  list(edx_CV = edx_CV,
+       edx.mx = edx.mx,
+       edx.sgr = edx.sgr,
+       tuning_sets = tuning_sets,
+       movie_map = movie_map,
+       date_days_map = date_days_map)
+}
+```
+
+##### `edx.mx` Matrix Object
+\
+
 We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
@@
 
-```{r}
-y <- dplyr::select(train_set, movieId, userId, rating) |>
+```{r eval=FALSE}
+
+  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
+  edx.mx <- edx |> 
+    mutate(userId = factor(userId),
+           movieId = factor(movieId)) |>
+    select(movieId, userId, rating) |>
     pivot_wider(names_from = movieId, values_from = rating) |>
@@
 
-dim(y)
+  put_log("Function: `make_source_datasets`:
+Matrix created: `edx.mx` of the following dimentions:")
+
 ```
 
+```{r}
+  str(edx.mx)
+```
+
+##### `edx.sgr` Object
+\
+
+To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
+```{r eval=FALSE}
+  put_log("Function: `make_source_datasets`: 
+To account for the Movie Genre Effect, we need a dataset with split rows 
+for movies belonging to multiple genres.")
+  edx.sgr <- splitGenreRows(edx)
+```
+```{r}
+str(edx.sgr)
+summary(edx.sgr)
+```
+
+Note that we use the `splitGenreRows` function to split rows of the original dataset:
+```{r eval=FALSE}
+splitGenreRows <- function(data){
+  put("Splitting dataset rows related to multiple genres...")
+  start <- put_start_date()
+  gs_splitted <- data |>
+    separate_rows(genres, sep = "\\|")
+  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
+  put_end_date(start)
+  gs_splitted
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the function mentioned above is also available in the [`Initialize input datasets` section of the `data.helper.functions.R` script on _GitHub_](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R#L86)
+:::
+
+##### `movie_map` Object
+\
+
 To be able to map movie IDs to titles we create the following lookup table:
-```{r}
-movie_map <- train_set |> dplyr::select(movieId, title, genres) |> 
+```{r eval=FALSE}
+movie_map <- edx |> select(movieId, title, genres) |> 
     distinct(movieId, .keep_all = TRUE)
 
+  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
+```
+
+```{r}
+str(movie_map)
 summary(movie_map)
@@
 
-### Naive Model
+##### `date_days_map` Object
 \
+
+We have a `timestamp` field in the `edx` dataset.
+To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
+```{r eval=FALSE}
+  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
+  date_days_map <- edx |>
+    mutate(date_time = as_datetime(timestamp)) |>
+    mutate(date = as_date(date_time)) |>
+    mutate(year = year(date_time)) |>
+    mutate(days = as.integer(date - min(date))) |>
+    select(timestamp, date_time, date, year, days) |>
+    distinct(timestamp, .keep_all = TRUE)
+
+  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
+```
+``` {r}
+  str(date_days_map)
+  summary(date_days_map)
+```
+
+##### `edx_CV` Object
+\
+
+Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
+as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_:
+```{r eval=FALSE}
+  start <- put_start_date()
+  edx_CV <- lapply(kfold_index,  function(fold_i){
+
+    put_log1("Method `make_source_datasets`: 
+Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
+
+    #> We split the initial datasets into training sets, which we will use to build 
+    #> and train our models, and validation sets in which we will compute the accuracy 
+    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
+    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
+    #> of the Course Textbook.
+
+    split_sets <- edx |>
+      sample_train_validation_sets(fold_i*1000)
+
+    train_set <- split_sets$train_set
+    validation_set <- split_sets$validation_set
+
+    put_log("Function: `make_source_datasets`: 
+Sampling 20% from the split-row version of the `edx` dataset...")
+    split_sets.gs <- edx.sgr |>
+      sample_train_validation_sets(fold_i*2000)
+
+    train.sgr <- split_sets.gs$train_set
+    validation.sgr <- split_sets.gs$validation_set
+
+    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
+    # put(summary(validation.sgr))
+
+    #> We will use the array representation described in `Section 17.5 of the Textbook`
+    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
+    #> for the training data. 
+    #> To create this matrix, we use `tidyr::pivot_wider` function:
+
+    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
+    train_mx <- train_set |> 
+      mutate(userId = factor(userId),
+             movieId = factor(movieId)) |>
+      select(movieId, userId, rating) |>
+      pivot_wider(names_from = movieId, values_from = rating) |>
+      column_to_rownames("userId") |>
+      as.matrix()
+
+    put_log("Function: `make_source_datasets`:
+Matrix created: `train_mx` of the following dimentions:")
+    put(dim(train_mx))
+
+    list(train_set = train_set,
+         train_mx = train_mx,
+         train.sgr = train.sgr,
+         validation_set = validation_set)
+  })
+  put_end_date(start)
+  put_log("Function: `make_source_datasets`: 
+Set of K-Fold Cross Validation datasets created: edx_CV")
+```
+```{r}
+str(edx_CV)
+```
+
+::: {.noteblock data-latex=""}
+This code snippet is a part of the `make_source_datasets` _function_ code described above.
+:::
+
+Note that we used the `sample_train_validation_sets` function call to split the original dataset (`edx` in this case): 
+```{r eval=FALSE}
+    split_sets <- edx |>
+      sample_train_validation_sets(fold_i*1000)
+```
+
+::: {.noteblock data-latex=""}
+The `sample_train_validation_sets` function is defined in the same script as the `make_source_datasets` one, from where it is called.  
+:::
+```{r eval=FALSE}
+sample_train_validation_sets <- function(data, seed){
+  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
+  set.seed(seed)
+  validation_ind <- 
+    sapply(splitByUser(data),
+           function(i) sample(i, ceiling(length(i)*.2))) |> 
+    unlist() |> 
+    sort()
+
+  put_log("Function: `sample_train_validation_sets`: 
+Extracting 80% of the original `data` not used for the Validation Set, 
+excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
+
+  train_set <- data[-validation_ind,]
+
+  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
+  put(summary(train_set))
+
+  put_log("Function: `sample_train_validation_sets`: 
+To make sure we don’t include movies in the Training Set that should not be there, 
+we exclude entries using the semi_join function from the Validation Set.")
+  tmp.data <- data[validation_ind,]
+
+  validation_set <- tmp.data |> 
+    semi_join(train_set, by = "movieId") |> 
+    semi_join(train_set, by = "userId") |>
+    as.data.frame()
+
+  # Add rows excluded from `validation_set` into `train_set`
+  tmp.excluded <- anti_join(tmp.data, validation_set)
+  train_set <- rbind(train_set, tmp.excluded)
+
+  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
+  put(summary(validation_set))
+
+  # CV train & test sets Consistency Test
+  validation.left_join.Nas <- train_set |>
+    mutate(tst.col = rating) |>
+    select(userId, movieId, tst.col) |>
+    data.consistency.test(validation_set)
+
+  put_log("Function: `sample_train_validation_sets`:
+Below are the data consistency verification results")
+  put(validation.left_join.Nas)
+
+  # Return result datassets ----------------------------------------------------    
+  list(train_set = train_set, 
+       validation_set = validation_set)
+}
+
+```
+
+#### Common Helper Functions
+\
+
+For our further analysis, we are going to use the following _common helper functions:
+
+##### `clamp` function
+\
+
+As explained in [Section  24.4 User effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings can’t be below 0.5 or above 5.
+For this reason, we will use the `clamp` function described in that section:
+```{r eval=FALSE}
+clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
+```
+
+##### Functions to calculate _(Root) Mean Squared Error
+
+We will need the following functions to calculate _(R)MSEs:
+```{r eval=FALSE}
+mse <- function(r) mean(r^2)
+
+mse_cv <- function(r_list) {
+  mses <- sapply(r_list, mse(r))
+  mean(mses)
+}
+
+rmse <- function(r) sqrt(mse(r))
+# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
+
+rmse2 <- function(true_ratings, predicted_ratings) {
+  rmse(true_ratings - predicted_ratings)
+}
+
+```
+
+### Overall Mean Rating (Naive) Model
+\
+
 Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
@@
 
-```{r pressure, echo=TRUE}
-mu <- mean(y, na.rm = TRUE)
+```{r pressure, echo=TRUE, eval=FALSE}
+  mu <- mean(edx$rating)
+```
+```{r}
 print(mu)
@@
 
+```{r eval=FALSE}
+  mu.RMSE <- sqrt(mean(MSEs))
+```
 ```{r}
-rmse(test_set$rating - mu)
+mu.RMSE
 ```
@@
 If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r}
+```{r eval=FALSE}
 deviation <- seq(0, 6, 0.1) - 3
@@
 ```{r}
-hist(rowMeans(y, na.rm = TRUE), nclass = 30)
+hist(edx.user_mean_ratings$mean_rating, nclass = 30)
+print("A histogram of the User Mean Rating distribution has been plotted.")
 ```
@@
 As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we compute them this way:
-```{r}
+```{r eval=FALSE}
 a <- rowMeans(y - mu, na.rm = TRUE)
@@
 Finally, we are ready to compute the `RMSE` (additionally using the helper function `clamp` we defined above to keep predictions in the proper range):
-```{r}
+```{r eval=FALSE}
 # Compute the RMSE taking into account user effects:
@@
 
-```{r}
+```{r eval=FALSE}
 b <- colMeans(y - mu - a, na.rm = TRUE)
@@
 We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
-```{r}
+```{r eval=FALSE}
 user_and_movie_effects_rmse <- test_set |> 
@@
 We will use the following function to calculate _RMSE_ in this section:
-```{r}
+```{r eval=FALSE}
 reg_rmse <- function(b){
@@
 Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r}
+```{r eval=FALSE}
 # Here we will simply compute the RMSE for different values of `lambda` 
@@
 ```{r}
-print(min(rmses))
+# print(min(rmses))
 ```
@@
 which is achieved for the following $\lambda$:
-```{r}
+```{r eval=FALSE}
 lambda <- lambdas[which.min(rmses)] 
@@
 Using this $\lambda$ we can compute the regularized estimates:
-```{r}
+```{r eval=FALSE}
 b_reg <- sums / (n + lambda)
@@
 Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r}
+```{r eval=FALSE}
 reg_rmse(b_reg)
@@
 
+#### Genre Data Analysis
+\
+##### Movie Genres Data 
+\
+The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
+```{r eval=FALSE}
+#library(stringr)
+genres = c("Drama", "Comedy", "Thriller", "Romance")
+sapply(genres, function(g) {
+  sum(str_detect(edx$genres, g))
+})
+```
+
+Further, we can find out the movies that have the greatest number of ratings using the following code:
+```{r eval=FALSE}
+ordered_movie_ratings <- edx |> group_by(movieId, title) |>
+  summarize(number_of_ratings = n()) |>
+  arrange(desc(number_of_ratings))
+print(head(ordered_movie_ratings))
+```
+
+and figure out the most given ratings in order from most to least:
+```{r eval=FALSE}
+ratings <- edx |>  group_by(rating) |>
+     summarise(count = n()) |>
+     arrange(desc(count))
+print(ratings)
+```
+
+The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
+```{r eval=FALSE}
+print(edx |> group_by(rating) |> summarize(count = n()))
+```
+
+We can visually see that from the following plot:
+```{r eval=FALSE}
+edx |>
+  group_by(rating) |>
+  summarize(count = n()) |>
+  ggplot(aes(x = rating, y = count)) +
+  geom_line()
+
+```
+
+##### Movie Genres Effect 
+\
+
 The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
 
-```{r}
+```{r eval=FALSE}
 # Preparing data for plotting:
@@
 Below are worst and best ratings categories:
-```{r}
+```{r eval=FALSE}
 sprintf("The worst ratings are for the genre category: %s",
@@
 Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
-```{r}
+```{r eval=FALSE}
 # For better visibility, we reduce the data for plotting 

### 2025-05-06 reports/capstone-movielens-report.draft4.tex
Draft RMD report updated.

@@
 \author{Azamat Kurbanaev}
-\date{2025-05-05}
+\date{2025-05-06}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-18-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-14-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-22-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-18-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-23-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
 
@@
 above\autocite{IDS2_23-1-1}.We will also use the \emph{5-Fold Cross
-Validation} method the way described in
+Validation} method as described in
 \href{https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html\#cross-validation}{Section
@@
 
-\begin{itemize}
-\tightlist
-\item
-  \texttt{make\_source\_datasets};
-\item
-  \texttt{init\_source\_datasets}.
-\end{itemize}
-
 \begin{noteblock}
@@
 \end{noteblock}
+
+\paragraph{\texorpdfstring{The \texttt{make\_source\_datasets}
+function}{The make\_source\_datasets function}}\label{the-make_source_datasets-function}
+
+\hfill\break
+
+Let's take a closer look at the objects we will receive as a result of
+executing this function.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{make\_source\_datasets }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{()\{}
+  \CommentTok{\# ...}
+  \FunctionTok{list}\NormalTok{(}\AttributeTok{edx\_CV =}\NormalTok{ edx\_CV,}
+       \AttributeTok{edx.mx =}\NormalTok{ edx.mx,}
+       \AttributeTok{edx.sgr =}\NormalTok{ edx.sgr,}
+       \AttributeTok{tuning\_sets =}\NormalTok{ tuning\_sets,}
+       \AttributeTok{movie\_map =}\NormalTok{ movie\_map,}
+       \AttributeTok{date\_days\_map =}\NormalTok{ date\_days\_map)}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\subparagraph{\texorpdfstring{\texttt{edx.mx} Matrix
+Object}{edx.mx Matrix Object}}\label{edx.mx-matrix-object}
+
+\hfill\break
 
@@
 \begin{Highlighting}[]
-\NormalTok{y }\OtherTok{\textless{}{-}}\NormalTok{ dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(train\_set, movieId, userId, rating) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Creating Rating Matrix from \textasciigrave{}edx\textasciigrave{} dataset..."}\NormalTok{)}
+\NormalTok{  edx.mx }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{factor}\NormalTok{(userId),}
+           \AttributeTok{movieId =} \FunctionTok{factor}\NormalTok{(movieId)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{select}\NormalTok{(movieId, userId, rating) }\SpecialCharTok{|\textgreater{}}
     \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ movieId, }\AttributeTok{values\_from =}\NormalTok{ rating) }\SpecialCharTok{|\textgreater{}}
@@
 
-\FunctionTok{dim}\NormalTok{(y)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 24115 10630
-\end{verbatim}
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}:}
+\StringTok{Matrix created: \textasciigrave{}edx.mx\textasciigrave{} of the following dimentions:"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+  \FunctionTok{str}\NormalTok{(edx.mx)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+##  num [1:69878, 1:10677] 5 NA NA NA NA NA NA NA NA NA ...
+##  - attr(*, "dimnames")=List of 2
+##   ..$ : chr [1:69878] "1" "2" "3" "4" ...
+##   ..$ : chr [1:10677] "122" "185" "292" "316" ...
+\end{verbatim}
+
+\subparagraph{\texorpdfstring{\texttt{edx.sgr}
+Object}{edx.sgr Object}}\label{edx.sgr-object}
+
+\hfill\break
+
+To account for the Movie Genre Effect more accurately, we need a dataset
+with split rows for movies belonging to multiple genres:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: }
+\StringTok{To account for the Movie Genre Effect, we need a dataset with split rows }
+\StringTok{for movies belonging to multiple genres."}\NormalTok{)}
+\NormalTok{  edx.sgr }\OtherTok{\textless{}{-}} \FunctionTok{splitGenreRows}\NormalTok{(edx)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{str}\NormalTok{(edx.sgr)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## tibble [23,371,423 x 6] (S3: tbl_df/tbl/data.frame)
+##  $ userId   : int [1:23371423] 1 1 1 1 1 1 1 1 1 1 ...
+##  $ movieId  : int [1:23371423] 122 122 185 185 185 292 292 292 292 316 ...
+##  $ rating   : num [1:23371423] 5 5 5 5 5 5 5 5 5 5 ...
+##  $ timestamp: int [1:23371423] 838985046 838985046 838983525 838983525 838983525 838983421 838983421 838983421 838983421 838983392 ...
+##  $ title    : chr [1:23371423] "Boomerang (1992)" "Boomerang (1992)" "Net, The (1995)" "Net, The (1995)" ...
+##  $ genres   : chr [1:23371423] "Comedy" "Romance" "Action" "Crime" ...
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{summary}\NormalTok{(edx.sgr)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+##      userId         movieId          rating        timestamp            title              genres         
+##  Min.   :    1   Min.   :    1   Min.   :0.500   Min.   :7.897e+08   Length:23371423    Length:23371423   
+##  1st Qu.:18140   1st Qu.:  616   1st Qu.:3.000   1st Qu.:9.472e+08   Class :character   Class :character  
+##  Median :35784   Median : 1748   Median :4.000   Median :1.042e+09   Mode  :character   Mode  :character  
+##  Mean   :35886   Mean   : 4277   Mean   :3.527   Mean   :1.035e+09                                        
+##  3rd Qu.:53638   3rd Qu.: 3635   3rd Qu.:4.000   3rd Qu.:1.131e+09                                        
+##  Max.   :71567   Max.   :65133   Max.   :5.000   Max.   :1.231e+09
+\end{verbatim}
+
+Note that we use the \texttt{splitGenreRows} function to split rows of
+the original dataset:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{splitGenreRows }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data)\{}
+  \FunctionTok{put}\NormalTok{(}\StringTok{"Splitting dataset rows related to multiple genres..."}\NormalTok{)}
+\NormalTok{  start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
+\NormalTok{  gs\_splitted }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{separate\_rows}\NormalTok{(genres, }\AttributeTok{sep =} \StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{|"}\NormalTok{)}
+  \FunctionTok{put}\NormalTok{(}\StringTok{"Dataset rows related to multiple genres have been splitted to have single genre per row."}\NormalTok{)}
+  \FunctionTok{put\_end\_date}\NormalTok{(start)}
+\NormalTok{  gs\_splitted}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{noteblock}
+The source code of the function mentioned above is also available in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R\#L86}{\texttt{Initialize\ input\ datasets}
+section of the \texttt{data.helper.functions.R} script on \emph{GitHub}}
+
+\end{noteblock}
+
+\subparagraph{\texorpdfstring{\texttt{movie\_map}
+Object}{movie\_map Object}}\label{movie_map-object}
+
+\hfill\break
 
@@
 \begin{Highlighting}[]
-\NormalTok{movie\_map }\OtherTok{\textless{}{-}}\NormalTok{ train\_set }\SpecialCharTok{|\textgreater{}}\NormalTok{ dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(movieId, title, genres) }\SpecialCharTok{|\textgreater{}}
+\NormalTok{movie\_map }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} \FunctionTok{select}\NormalTok{(movieId, title, genres) }\SpecialCharTok{|\textgreater{}} 
     \FunctionTok{distinct}\NormalTok{(movieId, }\AttributeTok{.keep\_all =} \ConstantTok{TRUE}\NormalTok{)}
 
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Dataset created: movie\_map"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{str}\NormalTok{(movie\_map)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 'data.frame':    10677 obs. of  3 variables:
+##  $ movieId: int  122 185 292 316 329 355 356 362 364 370 ...
+##  $ title  : chr  "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Stargate (1994)" ...
+##  $ genres : chr  "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Sci-Fi" ...
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
 \FunctionTok{summary}\NormalTok{(movie\_map)}
@@
 ##     movieId         title              genres         
-##  1      :    1   Length:10630       Length:10630      
-##  2      :    1   Class :character   Class :character  
-##  3      :    1   Mode  :character   Mode  :character  
-##  4      :    1                                        
-##  5      :    1                                        
-##  6      :    1                                        
-##  (Other):10624
+##  Min.   :    1   Length:10677       Length:10677      
+##  1st Qu.: 2754   Class :character   Class :character  
+##  Median : 5434   Mode  :character   Mode  :character  
+##  Mean   :13105                                        
+##  3rd Qu.: 8710                                        
+##  Max.   :65133
 \end{verbatim}
@@
 
-\subsubsection{Naive Model}\label{naive-model}
-
-\hfill\break
+\subparagraph{\texorpdfstring{\texttt{date\_days\_map}
+Object}{date\_days\_map Object}}\label{date_days_map-object}
+
+\hfill\break
+
+We have a \texttt{timestamp} field in the \texttt{edx} dataset. To be
+able to map the date, year, and number of days since the earliest record
+in the \texttt{edx} dataset with the corresponding value in this field,
+we create the following lookup table:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Creating Date{-}Days Map dataset..."}\NormalTok{)}
+\NormalTok{  date\_days\_map }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date\_time =} \FunctionTok{as\_datetime}\NormalTok{(timestamp)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date =} \FunctionTok{as\_date}\NormalTok{(date\_time)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{year =} \FunctionTok{year}\NormalTok{(date\_time)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{days =} \FunctionTok{as.integer}\NormalTok{(date }\SpecialCharTok{{-}} \FunctionTok{min}\NormalTok{(date))) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{select}\NormalTok{(timestamp, date\_time, date, year, days) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{distinct}\NormalTok{(timestamp, }\AttributeTok{.keep\_all =} \ConstantTok{TRUE}\NormalTok{)}
+
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Dataset created: date\_days\_map"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+  \FunctionTok{str}\NormalTok{(date\_days\_map)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 'data.frame':    6519590 obs. of  5 variables:
+##  $ timestamp: int  838985046 838983525 838983421 838983392 838984474 838983653 838984885 838983707 838984596 838983834 ...
+##  $ date_time: POSIXct, format: "1996-08-02 11:24:06" "1996-08-02 10:58:45" "1996-08-02 10:57:01" "1996-08-02 10:56:32" ...
+##  $ date     : Date, format: "1996-08-02" "1996-08-02" "1996-08-02" "1996-08-02" ...
+##  $ year     : num  1996 1996 1996 1996 1996 ...
+##  $ days     : int  571 571 571 571 571 571 571 571 571 571 ...
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+  \FunctionTok{summary}\NormalTok{(date\_days\_map)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+##    timestamp           date_time                           date                 year           days     
+##  Min.   :7.897e+08   Min.   :1995-01-09 11:46:49.00   Min.   :1995-01-09   Min.   :1995   Min.   :   0  
+##  1st Qu.:9.783e+08   1st Qu.:2001-01-01 05:05:01.75   1st Qu.:2001-01-01   1st Qu.:2001   1st Qu.:2184  
+##  Median :1.091e+09   Median :2004-08-03 01:08:18.50   Median :2004-08-03   Median :2004   Median :3494  
+##  Mean   :1.066e+09   Mean   :2003-10-10 23:15:02.07   Mean   :2003-10-10   Mean   :2003   Mean   :3196  
+##  3rd Qu.:1.152e+09   3rd Qu.:2006-07-04 20:41:57.50   3rd Qu.:2006-07-04   3rd Qu.:2006   3rd Qu.:4194  
+##  Max.   :1.231e+09   Max.   :2009-01-05 05:02:16.00   Max.   :2009-01-05   Max.   :2009   Max.   :5110
+\end{verbatim}
+
+\subparagraph{\texorpdfstring{\texttt{edx\_CV}
+Object}{edx\_CV Object}}\label{edx_cv-object}
+
+\hfill\break
+
+Here we have a list of sample objects we need to perform the
+\emph{5-Fold Cross Validation} as explained in
+\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html\#k-fold-cross-validation}{Section
+29.6.1 K-fold cross validation} of the \emph{Course Textbook}:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{  start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
+\NormalTok{  edx\_CV }\OtherTok{\textless{}{-}} \FunctionTok{lapply}\NormalTok{(kfold\_index,  }\ControlFlowTok{function}\NormalTok{(fold\_i)\{}
+
+    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Method \textasciigrave{}make\_source\_datasets\textasciigrave{}: }
+\StringTok{Creating K{-}Fold Cross Validation Datasets, Fold \%1"}\NormalTok{, fold\_i)}
+
+    \CommentTok{\#\textgreater{} We split the initial datasets into training sets, which we will use to build }
+    \CommentTok{\#\textgreater{} and train our models, and validation sets in which we will compute the accuracy }
+    \CommentTok{\#\textgreater{} of our predictions, the way described in the \textasciigrave{}Section 23.1.1 Movielens data\textasciigrave{}}
+    \CommentTok{\#\textgreater{} (https://rafalab.dfci.harvard.edu/dsbook{-}part{-}2/highdim/regularization.html\#movielens{-}data) }
+    \CommentTok{\#\textgreater{} of the Course Textbook.}
+
+\NormalTok{    split\_sets }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{sample\_train\_validation\_sets}\NormalTok{(fold\_i}\SpecialCharTok{*}\DecValTok{1000}\NormalTok{)}
+
+\NormalTok{    train\_set }\OtherTok{\textless{}{-}}\NormalTok{ split\_sets}\SpecialCharTok{$}\NormalTok{train\_set}
+\NormalTok{    validation\_set }\OtherTok{\textless{}{-}}\NormalTok{ split\_sets}\SpecialCharTok{$}\NormalTok{validation\_set}
+
+    \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: }
+\StringTok{Sampling 20\% from the split{-}row version of the \textasciigrave{}edx\textasciigrave{} dataset..."}\NormalTok{)}
+\NormalTok{    split\_sets.gs }\OtherTok{\textless{}{-}}\NormalTok{ edx.sgr }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{sample\_train\_validation\_sets}\NormalTok{(fold\_i}\SpecialCharTok{*}\DecValTok{2000}\NormalTok{)}
+
+\NormalTok{    train.sgr }\OtherTok{\textless{}{-}}\NormalTok{ split\_sets.gs}\SpecialCharTok{$}\NormalTok{train\_set}
+\NormalTok{    validation.sgr }\OtherTok{\textless{}{-}}\NormalTok{ split\_sets.gs}\SpecialCharTok{$}\NormalTok{validation\_set}
+
+    \CommentTok{\# put\_log("Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Dataset created: validation.sgr")}
+    \CommentTok{\# put(summary(validation.sgr))}
+
+    \CommentTok{\#\textgreater{} We will use the array representation described in \textasciigrave{}Section 17.5 of the Textbook\textasciigrave{}}
+    \CommentTok{\#\textgreater{} (https://rafalab.dfci.harvard.edu/dsbook{-}part{-}2/linear{-}models/treatment{-}effect{-}models.html\#sec{-}anova), }
+    \CommentTok{\#\textgreater{} for the training data. }
+    \CommentTok{\#\textgreater{} To create this matrix, we use \textasciigrave{}tidyr::pivot\_wider\textasciigrave{} function:}
+
+    \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Creating Rating Matrix from Train Set..."}\NormalTok{)}
+\NormalTok{    train\_mx }\OtherTok{\textless{}{-}}\NormalTok{ train\_set }\SpecialCharTok{|\textgreater{}} 
+      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{factor}\NormalTok{(userId),}
+             \AttributeTok{movieId =} \FunctionTok{factor}\NormalTok{(movieId)) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{select}\NormalTok{(movieId, userId, rating) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ movieId, }\AttributeTok{values\_from =}\NormalTok{ rating) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{column\_to\_rownames}\NormalTok{(}\StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{as.matrix}\NormalTok{()}
+
+    \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}:}
+\StringTok{Matrix created: \textasciigrave{}train\_mx\textasciigrave{} of the following dimentions:"}\NormalTok{)}
+    \FunctionTok{put}\NormalTok{(}\FunctionTok{dim}\NormalTok{(train\_mx))}
+
+    \FunctionTok{list}\NormalTok{(}\AttributeTok{train\_set =}\NormalTok{ train\_set,}
+         \AttributeTok{train\_mx =}\NormalTok{ train\_mx,}
+         \AttributeTok{train.sgr =}\NormalTok{ train.sgr,}
+         \AttributeTok{validation\_set =}\NormalTok{ validation\_set)}
+\NormalTok{  \})}
+  \FunctionTok{put\_end\_date}\NormalTok{(start)}
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: }
+\StringTok{Set of K{-}Fold Cross Validation datasets created: edx\_CV"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{str}\NormalTok{(edx\_CV)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## List of 5
+##  $ :List of 4
+##   ..$ train_set     :'data.frame':   7172311 obs. of  6 variables:
+##   .. ..$ userId   : int [1:7172311] 1 1 1 1 1 1 1 1 1 1 ...
+##   .. ..$ movieId  : int [1:7172311] 122 185 292 329 356 362 364 370 420 466 ...
+##   .. ..$ rating   : num [1:7172311] 5 5 5 5 5 5 5 5 5 5 ...
+##   .. ..$ timestamp: int [1:7172311] 838985046 838983525 838983421 838983392 838983653 838984885 838983707 838984596 838983834 838984679 ...
+##   .. ..$ title    : chr [1:7172311] "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Star Trek: Generations (1994)" ...
+##   .. ..$ genres   : chr [1:7172311] "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Drama|Sci-Fi" ...
+##   ..$ train_mx      : num [1:69878, 1:10677] 5 NA NA NA NA NA NA NA NA NA ...
+##   .. ..- attr(*, "dimnames")=List of 2
+##   .. .. ..$ : chr [1:69878] "1" "2" "3" "4" ...
+##   .. .. ..$ : chr [1:10677] "122" "185" "292" "329" ...
+##   ..$ train.sgr     : tibble [18,669,190 x 6] (S3: tbl_df/tbl/data.frame)
+##   .. ..$ userId   : int [1:18669190] 1 1 1 1 1 1 1 1 1 1 ...
+##   .. ..$ movieId  : int [1:18669190] 122 122 185 185 292 292 292 292 316 316 ...
+##   .. ..$ rating   : num [1:18669190] 5 5 5 5 5 5 5 5 5 5 ...
+##   .. ..$ timestamp: int [1:18669190] 838985046 838985046 838983525 838983525 838983421 838983421 838983421 838983421 838983392 838983392 ...
+##   .. ..$ title    : chr [1:18669190] "Boomerang (1992)" "Boomerang (1992)" "Net, The (1995)" "Net, The (1995)" ...
+##   .. ..$ genres   : chr [1:18669190] "Comedy" "Romance" "Action" "Crime" ...
+##   ..$ validation_set:'data.frame':   1827744 obs. of  6 variables:
+##   .. ..$ userId   : int [1:1827744] 1 1 1 1 2 2 2 2 3 3 ...
+##   .. ..$ movieId  : int [1:1827744] 316 355 377 588 260 376 648 1049 110 1252 ...
+##   .. ..$ rating   : num [1:1827744] 5 5 5 5 5 3 2 3 4.5 4 ...
+##   .. ..$ timestamp: int [1:1827744] 838983392 838984474 838983834 838983339 868244562 868245920 868244699 868245920 1136075500 1133571071 ...
+##   .. ..$ title    : chr [1:1827744] "Stargate (1994)" "Flintstones, The (1994)" "Speed (1994)" "Aladdin (1992)" ...
+##   .. ..$ genres   : chr [1:1827744] "Action|Adventure|Sci-Fi" "Children|Comedy|Fantasy" "Action|Romance|Thriller" "Adventure|Animation|Children|Comedy|Musical" ...
+##  $ :List of 4
+##   ..$ train_set     :'data.frame':   7172306 obs. of  6 variables:
+##   .. ..$ userId   : int [1:7172306] 1 1 1 1 1 1 1 1 1 1 ...
+##   .. ..$ movieId  : int [1:7172306] 122 185 292 316 329 355 356 364 370 377 ...
+##   .. ..$ rating   : num [1:7172306] 5 5 5 5 5 5 5 5 5 5 ...
+##   .. ..$ timestamp: int [1:7172306] 838985046 838983525 838983421 838983392 838983392 838984474 838983653 838983707 838984596 838983834 ...
+##   .. ..$ title    : chr [1:7172306] "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Stargate (1994)" ...
+##   .. ..$ genres   : chr [1:7172306] "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Sci-Fi" ...
+##   ..$ train_mx      : num [1:69878, 1:10677] 5 NA NA NA NA NA NA NA NA NA ...
+##   .. ..- attr(*, "dimnames")=List of 2
+##   .. .. ..$ : chr [1:69878] "1" "2" "3" "4" ...
+##   .. .. ..$ : chr [1:10677] "122" "185" "292" "316" ...
+##   ..$ train.sgr     : tibble [18,669,201 x 6] (S3: tbl_df/tbl/data.frame)
+##   .. ..$ userId   : int [1:18669201] 1 1 1 1 1 1 1 1 1 1 ...
+##   .. ..$ movieId  : int [1:18669201] 122 122 185 185 185 292 292 316 316 329 ...
+##   .. ..$ rating   : num [1:18669201] 5 5 5 5 5 5 5 5 5 5 ...
+##   .. ..$ timestamp: int [1:18669201] 838985046 838985046 838983525 838983525 838983525 838983421 838983421 838983392 838983392 838983392 ...
+##   .. ..$ title    : chr [1:18669201] "Boomerang (1992)" "Boomerang (1992)" "Net, The (1995)" "Net, The (1995)" ...
+##   .. ..$ genres   : chr [1:18669201] "Comedy" "Romance" "Action" "Crime" ...
+##   ..$ validation_set:'data.frame':   1827749 obs. of  6 variables:
+##   .. ..$ userId   : int [1:1827749] 1 1 1 1 2 2 2 2 3 3 ...
+##   .. ..$ movieId  : int [1:1827749] 362 520 539 594 539 590 733 1210 1252 1408 ...
+##   .. ..$ rating   : num [1:1827749] 5 5 5 5 3 5 3 4 4 3.5 ...
+##   .. ..$ timestamp: int [1:1827749] 838984885 838984679 838984068 838984679 868246262 868245608 868244562 868245644 1133571071 1133571145 ...
+##   .. ..$ title    : chr [1:1827749] "Jungle Book, The (1994)" "Robin Hood: Men in Tights (1993)" "Sleepless in Seattle (1993)" "Snow White and the Seven Dwarfs (1937)" ...
+##   .. ..$ genres   : chr [1:1827749] "Adventure|Children|Romance" "Comedy" "Comedy|Drama|Romance" "Animation|Children|Drama|Fantasy|Musical" ...
+##  $ :List of 4
+##   ..$ train_set     :'data.frame':   7172307 obs. of  6 variables:
+##   .. ..$ userId   : int [1:7172307] 1 1 1 1 1 1 1 1 1 1 ...
+##   .. ..$ movieId  : int [1:7172307] 122 185 292 316 329 355 362 370 377 420 ...
+##   .. ..$ rating   : num [1:7172307] 5 5 5 5 5 5 5 5 5 5 ...
+##   .. ..$ timestamp: int [1:7172307] 838985046 838983525 838983421 838983392 838983392 838984474 838984885 838984596 838983834 838983834 ...
+##   .. ..$ title    : chr [1:7172307] "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Stargate (1994)" ...
+##   .. ..$ genres   : chr [1:7172307] "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Sci-Fi" ...
+##   ..$ train_mx      : num [1:69878, 1:10677] 5 NA NA NA NA NA NA NA NA NA ...
+##   .. ..- attr(*, "dimnames")=List of 2
+##   .. .. ..$ : chr [1:69878] "1" "2" "3" "4" ...
+##   .. .. ..$ : chr [1:10677] "122" "185" "292" "316" ...
+##   ..$ train.sgr     : tibble [18,669,195 x 6] (S3: tbl_df/tbl/data.frame)
+##   .. ..$ userId   : int [1:18669195] 1 1 1 1 1 1 1 1 1 1 ...
+##   .. ..$ movieId  : int [1:18669195] 122 122 185 185 185 292 292 292 316 329 ...
+##   .. ..$ rating   : num [1:18669195] 5 5 5 5 5 5 5 5 5 5 ...
+##   .. ..$ timestamp: int [1:18669195] 838985046 838985046 838983525 838983525 838983525 838983421 838983421 838983421 838983392 838983392 ...
+##   .. ..$ title    : chr [1:18669195] "Boomerang (1992)" "Boomerang (1992)" "Net, The (1995)" "Net, The (1995)" ...
+##   .. ..$ genres   : chr [1:18669195] "Comedy" "Romance" "Action" "Crime" ...
+##   ..$ validation_set:'data.frame':   1827748 obs. of  6 variables:
+##   .. ..$ userId   : int [1:1827748] 1 1 1 1 2 2 2 2 3 3 ...
+##   .. ..$ movieId  : int [1:1827748] 356 364 539 616 590 719 780 786 151 213 ...
+##   .. ..$ rating   : num [1:1827748] 5 5 5 5 5 3 3 3 4.5 5 ...
+##   .. ..$ timestamp: int [1:1827748] 838983653 838983707 838984068 838984941 868245608 868246191 868244698 868244562 1133571026 1136075789 ...
+##   .. ..$ title    : chr [1:1827748] "Forrest Gump (1994)" "Lion King, The (1994)" "Sleepless in Seattle (1993)" "Aristocats, The (1970)" ...
+##   .. ..$ genres   : chr [1:1827748] "Comedy|Drama|Romance|War" "Adventure|Animation|Children|Drama|Musical" "Comedy|Drama|Romance" "Animation|Children" ...
+##  $ :List of 4
+##   ..$ train_set     :'data.frame':   7172311 obs. of  6 variables:
+##   .. ..$ userId   : int [1:7172311] 1 1 1 1 1 1 1 1 1 1 ...
+##   .. ..$ movieId  : int [1:7172311] 122 185 292 316 329 355 356 362 364 370 ...
+##   .. ..$ rating   : num [1:7172311] 5 5 5 5 5 5 5 5 5 5 ...
+##   .. ..$ timestamp: int [1:7172311] 838985046 838983525 838983421 838983392 838983392 838984474 838983653 838984885 838983707 838984596 ...
+##   .. ..$ title    : chr [1:7172311] "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Stargate (1994)" ...
+##   .. ..$ genres   : chr [1:7172311] "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Sci-Fi" ...
+##   ..$ train_mx      : num [1:69878, 1:10677] 5 NA NA NA NA NA NA NA NA NA ...
+##   .. ..- attr(*, "dimnames")=List of 2
+##   .. .. ..$ : chr [1:69878] "1" "2" "3" "4" ...
+##   .. .. ..$ : chr [1:10677] "122" "185" "292" "316" ...
+##   ..$ train.sgr     : tibble [18,669,192 x 6] (S3: tbl_df/tbl/data.frame)
+##   .. ..$ userId   : int [1:18669192] 1 1 1 1 1 1 1 1 1 1 ...
+##   .. ..$ movieId  : int [1:18669192] 122 122 185 185 292 292 316 316 329 329 ...
+##   .. ..$ rating   : num [1:18669192] 5 5 5 5 5 5 5 5 5 5 ...
+##   .. ..$ timestamp: int [1:18669192] 838985046 838985046 838983525 838983525 838983421 838983421 838983392 838983392 838983392 838983392 ...
+##   .. ..$ title    : chr [1:18669192] "Boomerang (1992)" "Boomerang (1992)" "Net, The (1995)" "Net, The (1995)" ...
+##   .. ..$ genres   : chr [1:18669192] "Comedy" "Romance" "Action" "Thriller" ...
+##   ..$ validation_set:'data.frame':   1827744 obs. of  6 variables:
+##   .. ..$ userId   : int [1:1827744] 1 1 1 1 2 2 2 2 3 3 ...
+##   .. ..$ movieId  : int [1:1827744] 377 520 588 616 110 648 1049 1356 1148 1276 ...
+##   .. ..$ rating   : num [1:1827744] 5 5 5 5 5 2 3 3 4 3.5 ...
+##   .. ..$ timestamp: int [1:1827744] 838983834 838984679 838983339 838984941 868245777 868244699 868245920 868244603 1133571121 1133571205 ...
+##   .. ..$ title    : chr [1:1827744] "Speed (1994)" "Robin Hood: Men in Tights (1993)" "Aladdin (1992)" "Aristocats, The (1970)" ...
+##   .. ..$ genres   : chr [1:1827744] "Action|Romance|Thriller" "Comedy" "Adventure|Animation|Children|Comedy|Musical" "Animation|Children" ...
+##  $ :List of 4
+##   ..$ train_set     :'data.frame':   7172301 obs. of  6 variables:
+##   .. ..$ userId   : int [1:7172301] 1 1 1 1 1 1 1 1 1 1 ...
+##   .. ..$ movieId  : int [1:7172301] 122 185 292 316 355 356 364 370 420 466 ...
+##   .. ..$ rating   : num [1:7172301] 5 5 5 5 5 5 5 5 5 5 ...
+##   .. ..$ timestamp: int [1:7172301] 838985046 838983525 838983421 838983392 838984474 838983653 838983707 838984596 838983834 838984679 ...
+##   .. ..$ title    : chr [1:7172301] "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Stargate (1994)" ...
+##   .. ..$ genres   : chr [1:7172301] "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Sci-Fi" ...
+##   ..$ train_mx      : num [1:69878, 1:10677] 5 NA NA NA NA NA NA NA NA NA ...
+##   .. ..- attr(*, "dimnames")=List of 2
+##   .. .. ..$ : chr [1:69878] "1" "2" "3" "4" ...
+##   .. .. ..$ : chr [1:10677] "122" "185" "292" "316" ...
+##   ..$ train.sgr     : tibble [18,669,194 x 6] (S3: tbl_df/tbl/data.frame)
+##   .. ..$ userId   : int [1:18669194] 1 1 1 1 1 1 1 1 1 1 ...
+##   .. ..$ movieId  : int [1:18669194] 122 122 185 185 292 292 316 329 329 355 ...
+##   .. ..$ rating   : num [1:18669194] 5 5 5 5 5 5 5 5 5 5 ...
+##   .. ..$ timestamp: int [1:18669194] 838985046 838985046 838983525 838983525 838983421 838983421 838983392 838983392 838983392 838984474 ...
+##   .. ..$ title    : chr [1:18669194] "Boomerang (1992)" "Boomerang (1992)" "Net, The (1995)" "Net, The (1995)" ...
+##   .. ..$ genres   : chr [1:18669194] "Comedy" "Romance" "Crime" "Thriller" ...
+##   ..$ validation_set:'data.frame':   1827754 obs. of  6 variables:
+##   .. ..$ userId   : int [1:1827754] 1 1 1 1 2 2 2 2 3 3 ...
+##   .. ..$ movieId  : int [1:1827754] 329 362 377 594 110 376 539 736 1252 1408 ...
+##   .. ..$ rating   : num [1:1827754] 5 5 5 5 5 3 3 3 4 3.5 ...
+##   .. ..$ timestamp: int [1:1827754] 838983392 838984885 838983834 838984679 868245777 868245920 868246262 868244698 1133571071 1133571145 ...
+##   .. ..$ title    : chr [1:1827754] "Star Trek: Generations (1994)" "Jungle Book, The (1994)" "Speed (1994)" "Snow White and the Seven Dwarfs (1937)" ...
+##   .. ..$ genres   : chr [1:1827754] "Action|Adventure|Drama|Sci-Fi" "Adventure|Children|Romance" "Action|Romance|Thriller" "Animation|Children|Drama|Fantasy|Musical" ...
+\end{verbatim}
+
+\begin{noteblock}
+This code snippet is a part of the \texttt{make\_source\_datasets}
+\emph{function} code described above.
+
+\end{noteblock}
+
+Note that we used the \texttt{sample\_train\_validation\_sets} function
+call to split the original dataset (\texttt{edx} in this case):
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{    split\_sets }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{sample\_train\_validation\_sets}\NormalTok{(fold\_i}\SpecialCharTok{*}\DecValTok{1000}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{noteblock}
+The \texttt{sample\_train\_validation\_sets} function is defined in the
+same script as the \texttt{make\_source\_datasets} one, from where it is
+called.
+
+\end{noteblock}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{sample\_train\_validation\_sets }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data, seed)\{}
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}sample\_train\_validation\_sets\textasciigrave{}: Sampling 20\% of the \textasciigrave{}data\textasciigrave{} data..."}\NormalTok{)}
+  \FunctionTok{set.seed}\NormalTok{(seed)}
+\NormalTok{  validation\_ind }\OtherTok{\textless{}{-}} 
+    \FunctionTok{sapply}\NormalTok{(}\FunctionTok{splitByUser}\NormalTok{(data),}
+           \ControlFlowTok{function}\NormalTok{(i) }\FunctionTok{sample}\NormalTok{(i, }\FunctionTok{ceiling}\NormalTok{(}\FunctionTok{length}\NormalTok{(i)}\SpecialCharTok{*}\NormalTok{.}\DecValTok{2}\NormalTok{))) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{unlist}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{sort}\NormalTok{()}
+
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}sample\_train\_validation\_sets\textasciigrave{}: }
+\StringTok{Extracting 80\% of the original \textasciigrave{}data\textasciigrave{} not used for the Validation Set, }
+\StringTok{excluding data for users who provided no more than a specified number of ratings: \{min\_nratings\}."}\NormalTok{)}
+
+\NormalTok{  train\_set }\OtherTok{\textless{}{-}}\NormalTok{ data[}\SpecialCharTok{{-}}\NormalTok{validation\_ind,]}
+
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}sample\_train\_validation\_sets\textasciigrave{}: Dataset created: train\_set"}\NormalTok{)}
+  \FunctionTok{put}\NormalTok{(}\FunctionTok{summary}\NormalTok{(train\_set))}
+
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}sample\_train\_validation\_sets\textasciigrave{}: }
+\StringTok{To make sure we don’t include movies in the Training Set that should not be there, }
+\StringTok{we exclude entries using the semi\_join function from the Validation Set."}\NormalTok{)}
+\NormalTok{  tmp.data }\OtherTok{\textless{}{-}}\NormalTok{ data[validation\_ind,]}
+
+\NormalTok{  validation\_set }\OtherTok{\textless{}{-}}\NormalTok{ tmp.data }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{semi\_join}\NormalTok{(train\_set, }\AttributeTok{by =} \StringTok{"movieId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{semi\_join}\NormalTok{(train\_set, }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{as.data.frame}\NormalTok{()}
+
+  \CommentTok{\# Add rows excluded from \textasciigrave{}validation\_set\textasciigrave{} into \textasciigrave{}train\_set\textasciigrave{}}
+\NormalTok{  tmp.excluded }\OtherTok{\textless{}{-}} \FunctionTok{anti\_join}\NormalTok{(tmp.data, validation\_set)}
+\NormalTok{  train\_set }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(train\_set, tmp.excluded)}
+
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}sample\_train\_validation\_sets\textasciigrave{}: Dataset created: validation\_set"}\NormalTok{)}
+  \FunctionTok{put}\NormalTok{(}\FunctionTok{summary}\NormalTok{(validation\_set))}
+
+  \CommentTok{\# CV train \& test sets Consistency Test}
+\NormalTok{  validation.left\_join.Nas }\OtherTok{\textless{}{-}}\NormalTok{ train\_set }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{tst.col =}\NormalTok{ rating) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{select}\NormalTok{(userId, movieId, tst.col) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{data.consistency.test}\NormalTok{(validation\_set)}
+
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}sample\_train\_validation\_sets\textasciigrave{}:}
+\StringTok{Below are the data consistency verification results"}\NormalTok{)}
+  \FunctionTok{put}\NormalTok{(validation.left\_join.Nas)}
+
+  \CommentTok{\# Return result datassets {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}    }
+  \FunctionTok{list}\NormalTok{(}\AttributeTok{train\_set =}\NormalTok{ train\_set, }
+       \AttributeTok{validation\_set =}\NormalTok{ validation\_set)}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\paragraph{Common Helper Functions}\label{common-helper-functions}
+
+\hfill\break
+
+For our further analysis, we are going to use the following \_common
+helper functions:
+
+\subparagraph{\texorpdfstring{\texttt{clamp}
+function}{clamp function}}\label{clamp-function}
+
+\hfill\break
+
+As explained in
+\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#user-effects}{Section
+24.4 User effects} of the \emph{Course Textbook} we know ratings can't
+be below 0.5 or above 5. For this reason, we will use the \texttt{clamp}
+function described in that section:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{clamp }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x, }\AttributeTok{min =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{max =} \DecValTok{5}\NormalTok{) }\FunctionTok{pmax}\NormalTok{(}\FunctionTok{pmin}\NormalTok{(x, max), min)}
+\end{Highlighting}
+\end{Shaded}
+
+\subparagraph{Functions to calculate \_(Root) Mean Squared
+Error}\label{functions-to-calculate-_root-mean-squared-error}
+
+We will need the following functions to calculate \_(R)MSEs:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{mse }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(r) }\FunctionTok{mean}\NormalTok{(r}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{)}
+
+\NormalTok{mse\_cv }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(r\_list) \{}
+\NormalTok{  mses }\OtherTok{\textless{}{-}} \FunctionTok{sapply}\NormalTok{(r\_list, }\FunctionTok{mse}\NormalTok{(r))}
+  \FunctionTok{mean}\NormalTok{(mses)}
+\NormalTok{\}}
+
+\NormalTok{rmse }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(r) }\FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mse}\NormalTok{(r))}
+\CommentTok{\# rmse\_cv \textless{}{-} function(r\_list) sqrt(mse\_cv(r\_list))}
+
+\NormalTok{rmse2 }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(true\_ratings, predicted\_ratings) \{}
+  \FunctionTok{rmse}\NormalTok{(true\_ratings }\SpecialCharTok{{-}}\NormalTok{ predicted\_ratings)}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\subsubsection{Overall Mean Rating (Naive)
+Model}\label{overall-mean-rating-naive-model}
+
+\hfill\break
+
 Let's begin our analysis by evaluating the simplest model described in
@@
 \begin{Highlighting}[]
-\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(y, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)}
+\NormalTok{  mu }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{rating)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
 \FunctionTok{print}\NormalTok{(mu)}
@@
 \begin{Highlighting}[]
-\FunctionTok{rmse}\NormalTok{(test\_set}\SpecialCharTok{$}\NormalTok{rating }\SpecialCharTok{{-}}\NormalTok{ mu)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 1.054739
+\NormalTok{  mu.RMSE }\OtherTok{\textless{}{-}} \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mean}\NormalTok{(MSEs))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{mu.RMSE}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] 1.060346
 \end{verbatim}
@@
 \FunctionTok{print}\NormalTok{(deviation)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##  [1] -3.0 -2.9 -2.8 -2.7 -2.6 -2.5 -2.4 -2.3 -2.2 -2.1 -2.0 -1.9 -1.8 -1.7 -1.6 -1.5 -1.4 -1.3 -1.2 -1.1 -1.0 -0.9 -0.8 -0.7 -0.6 -0.5 -0.4 -0.3 -0.2 -0.1  0.0  0.1  0.2  0.3  0.4  0.5
-## [37]  0.6  0.7  0.8  0.9  1.0  1.1  1.2  1.3  1.4  1.5  1.6  1.7  1.8  1.9  2.0  2.1  2.2  2.3  2.4  2.5  2.6  2.7  2.8  2.9  3.0
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
+
 \NormalTok{rmse\_value }\OtherTok{\textless{}{-}} \FunctionTok{sapply}\NormalTok{(deviation, }\ControlFlowTok{function}\NormalTok{(diff)\{}
@@
 \FunctionTok{plot}\NormalTok{(deviation, rmse\_value, }\AttributeTok{type =} \StringTok{"l"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-29-1.pdf}
-
-\begin{Shaded}
-\begin{Highlighting}[]
+
 \FunctionTok{sprintf}\NormalTok{(}\StringTok{"Minimum RMSE is achieved when the deviation from the mean is: \%s"}\NormalTok{, }
@@
 \end{Shaded}
-
-\begin{verbatim}
-## [1] "Minimum RMSE is achieved when the deviation from the mean is: 0"
-\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{hist}\NormalTok{(}\FunctionTok{rowMeans}\NormalTok{(y, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{), }\AttributeTok{nclass =} \DecValTok{30}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-30-1.pdf}
+\FunctionTok{hist}\NormalTok{(edx.user\_mean\_ratings}\SpecialCharTok{$}\NormalTok{mean\_rating, }\AttributeTok{nclass =} \DecValTok{30}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-42-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{print}\NormalTok{(}\StringTok{"A histogram of the User Mean Rating distribution has been plotted."}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## [1] "A histogram of the User Mean Rating distribution has been plotted."
+\end{verbatim}
 
@@
 \end{Shaded}
-
-\begin{verbatim}
-## [1] 0.9707208
-\end{verbatim}
 
@@
 
-\begin{verbatim}
-## [1] 0.8662207
-\end{verbatim}
-
 \subsubsection{Utilizing Penalized least
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-36-1.pdf}
 Now we can determine the minimal \emph{RMSE}:
@@
 \begin{Highlighting}[]
-\FunctionTok{print}\NormalTok{(}\FunctionTok{min}\NormalTok{(rmses))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 0.8661143
-\end{verbatim}
+\CommentTok{\# print(min(rmses))}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
-\begin{verbatim}
-## [1] 3.2
-\end{verbatim}
-
 Using this \(\lambda\) we can compute the regularized estimates:
@@
 \end{Shaded}
-
-\begin{verbatim}
-##  Named num [1:10630] -0.516 0.327 -0.903 -0.154 -0.29 ...
-##  - attr(*, "names")= chr [1:10630] "5" "6" "19" "22" ...
-\end{verbatim}
 
@@
 \end{Shaded}
-
-\begin{verbatim}
-## [1] 0.8661143
-\end{verbatim}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-42-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-54-1.pdf}
 
@@
 
-\begin{verbatim}
-##    Drama   Comedy Thriller  Romance 
-##  3910127  3540930  2325899  1712100
-\end{verbatim}
-
 Further, we can find out the movies that have the greatest number of
@@
   \FunctionTok{arrange}\NormalTok{(}\FunctionTok{desc}\NormalTok{(number\_of\_ratings))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## `summarise()` has grouped output by 'movieId'. You can override using the `.groups` argument.
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
 \FunctionTok{print}\NormalTok{(}\FunctionTok{head}\NormalTok{(ordered\_movie\_ratings))}
@@
 \end{Shaded}
-
-\begin{verbatim}
-## # A tibble: 6 x 3
-## # Groups:   movieId [6]
-##   movieId title                            number_of_ratings
-##     <int> <chr>                                        <int>
-## 1     296 Pulp Fiction (1994)                          31362
-## 2     356 Forrest Gump (1994)                          31079
-## 3     593 Silence of the Lambs, The (1991)             30382
-## 4     480 Jurassic Park (1993)                         29360
-## 5     318 Shawshank Redemption, The (1994)             28015
-## 6     110 Braveheart (1995)                            26212
-\end{verbatim}
 
@@
 
-\begin{verbatim}
-## # A tibble: 10 x 2
-##    rating   count
-##     <dbl>   <int>
-##  1    4   2588430
-##  2    3   2121240
-##  3    5   1390114
-##  4    3.5  791624
-##  5    2    711422
-##  6    4.5  526736
-##  7    1    345679
-##  8    2.5  333010
-##  9    1.5  106426
-## 10    0.5   85374
-\end{verbatim}
-
 The following code allows us to summarize that in general, half-star
@@
 \end{Shaded}
-
-\begin{verbatim}
-## # A tibble: 10 x 2
-##    rating   count
-##     <dbl>   <int>
-##  1    0.5   85374
-##  2    1    345679
-##  3    1.5  106426
-##  4    2    711422
-##  5    2.5  333010
-##  6    3   2121240
-##  7    3.5  791624
-##  8    4   2588430
-##  9    4.5  526736
-## 10    5   1390114
-\end{verbatim}
 
@@
 \end{Shaded}
-
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-47-1.pdf}
 
@@
 \FunctionTok{dim}\NormalTok{(genre\_ratins\_grp)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 53  4
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
 \NormalTok{genre\_ratins\_grp\_sorted }\OtherTok{\textless{}{-}}\NormalTok{ genre\_ratins\_grp }\SpecialCharTok{|\textgreater{}} \FunctionTok{sort\_by.data.frame}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ rating\_avg)}
 \FunctionTok{print}\NormalTok{(genre\_ratins\_grp\_sorted)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## # A tibble: 53 x 4
-##    genres                  rating_avg      se      n
-##    <fct>                        <dbl>   <dbl>  <int>
-##  1 Comedy|Horror                 2.83 0.00701  24892
-##  2 Horror                        2.85 0.00556  48671
-##  3 Children|Comedy               2.86 0.00575  40435
-##  4 Horror|Sci-Fi                 2.88 0.00787  20524
-##  5 Action|Comedy                 2.96 0.00581  34118
-##  6 Comedy|Sci-Fi                 3.06 0.00668  27888
-##  7 Action|Sci-Fi                 3.08 0.00749  27971
-##  8 Horror|Thriller               3.09 0.00543  49751
-##  9 Action|Adventure|Comedy       3.17 0.00616  28256
-## 10 Comedy                        3.21 0.00167 439352
-## # i 43 more rows
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
+
 \CommentTok{\# Creating plot:}
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-48-1.pdf}
 Below are worst and best ratings categories:
@@
 \NormalTok{        genre\_ratins\_grp}\SpecialCharTok{$}\NormalTok{genres[}\FunctionTok{which.min}\NormalTok{(genre\_ratins\_grp}\SpecialCharTok{$}\NormalTok{genres)])}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] "The worst ratings are for the genre category: Comedy|Horror"
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
+
 \FunctionTok{sprintf}\NormalTok{(}\StringTok{"The best ratings are for the genre category: \%s"}\NormalTok{,}
@@
 \end{Shaded}
-
-\begin{verbatim}
-## [1] "The best ratings are for the genre category: Comedy|Crime|Drama"
-\end{verbatim}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-50-1.pdf}
-
 If we define \(g_{i,j}\) as the genre for user's \(i\) rating of movie

### 2025-05-06 reports/capstone-movielens-report.draft4.Rmd
Fix for Draft RMD report.

@@
 ::: {.noteblock data-latex=""}
-This code snippet is a part of the `make_source_datasets` _function_ code described above.
+This code snippet is a part of the [`make_source_datasets` _function_ code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R#L87) described above.
 :::
@@
 
-::: {.noteblock data-latex=""}
-The `sample_train_validation_sets` function is defined in the same script as the `make_source_datasets` one, from where it is called.  
-:::
+which returns a pair of train/validation sets:
 ```{r eval=FALSE}
@@
 
+::: {.noteblock data-latex=""}
+The [`sample_train_validation_sets` function](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R#L15) is defined in the same script as the `make_source_datasets` one, from where it is called.
+:::
+
 #### Common Helper Functions
@@
 
-##### Functions to calculate _(Root) Mean Squared Error
-
-We will need the following functions to calculate _(R)MSEs:
+##### Functions to calculate _(Root) Mean Squared Error_
+\
+
+We will need the following functions to calculate _(R)MSEs_:
 ```{r eval=FALSE}

### 2025-05-06 reports/capstone-movielens-report.draft4.tex
Fix for Draft RMD report.

@@
 \begin{noteblock}
-This code snippet is a part of the \texttt{make\_source\_datasets}
-\emph{function} code described above.
+This code snippet is a part of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R\#L87}{\texttt{make\_source\_datasets}
+\emph{function} code} described above.
 
@@
 
-\begin{noteblock}
-The \texttt{sample\_train\_validation\_sets} function is defined in the
-same script as the \texttt{make\_source\_datasets} one, from where it is
-called.
-
-\end{noteblock}
+which returns a pair of train/validation sets:
 
@@
 
+\begin{noteblock}
+The
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R\#L15}{\texttt{sample\_train\_validation\_sets}
+function} is defined in the same script as the
+\texttt{make\_source\_datasets} one, from where it is called.
+
+\end{noteblock}
+
 \paragraph{Common Helper Functions}\label{common-helper-functions}
@@
 
-\subparagraph{Functions to calculate \_(Root) Mean Squared
-Error}\label{functions-to-calculate-_root-mean-squared-error}
-
-We will need the following functions to calculate \_(R)MSEs:
+\subparagraph{\texorpdfstring{Functions to calculate \emph{(Root) Mean
+Squared
+Error}}{Functions to calculate (Root) Mean Squared Error}}\label{functions-to-calculate-root-mean-squared-error}
+
+\hfill\break
+
+We will need the following functions to calculate \emph{(R)MSEs}:
 

### 2025-05-06 r/src/capstone-movielens.main.R
Refactoring: Data Visualization feature.

@@ -395,8 +395,15 @@ if (file.exists(file_path_tmp)) {
 } else {
   mu <- mean(edx$rating)
 
-  MSEs <- naive_model_MSEs(mu)
-  plot(MSEs)
+  mu.MSEs <- naive_model_MSEs(mu)
+  # plot(MSEs)
+
+  data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
+    data.plot(title = "MSE resuls of the 5-fold Cross Validation performed for the Overall Mean Rating Model",
+                xname = "fold_No", 
+                yname = "MSE")
+  
+  
   put_log1("MSE values plotted for %1-Fold Cross Validation samples.", CVFolds_N)
   mu.RMSE <- sqrt(mean(MSEs))
   # mu.RMSE <- naive_model_RMSE(mu)
@@ -473,7 +480,7 @@ writeLines("")
 ##### Plot dependency of RMSEs vs Overal Mean Rating Deviation -----------------  
 data.frame(delta = deviation, 
            delta.RMSE = deviation.RMSE) |> 
-tuning.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
+data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
               xname = "delta", 
               yname = "delta.RMSE", 
               xlabel = TeX(r'[$\delta$]'), 
@@ -818,7 +825,7 @@ put(cv.UME.preset.result$best_result)
 
 ##### Plot (rough) dependency of RMSEs vs lambdas ------------------------------  
 cv.UME.preset.result$tuned.result |>
-  tuning.plot(title = TeX(r'[Preliminary set-up of $\lambda$ for Regularazation of the User+Movie Effect Model.]'),
+  data.plot(title = TeX(r'[Preliminary set-up of $\lambda$ for Regularazation of the User+Movie Effect Model.]'),
               xname = "parameter.value", 
               yname = "RMSE", 
               xlabel = TeX(r'[$\lambda$]'), 
@@ -858,7 +865,7 @@ put(UME.rglr.fine_tune.results$best_result)
 ###### Plot (fine-tuned) dependency of RMSEs vs lambdas -------------------------  
 
 UME.rglr.fine_tune.results$tuned.result |>
-  tuning.plot(title = "Fine-tune Stage results of the Regularization Process for the User+Movie Model",
[…]

### 2025-05-06 r/src/support-functions/common-helper.functions.R

@@ -481,9 +481,9 @@ Currently reached best RMSE for `parameter value = %1`: %2",
                                  RMSE = result.RMSE))
 }
 
-### Model Tuning Results Visualization -----------------------------------------
+### Model Data Visualization -----------------------------------------
 
-tuning.plot.left_detailed <- function(data, 
+data.plot.left_detailed <- function(data, 
                                       left.n = 0,
                                       title = NULL,
                                       title.left = NULL,
@@ -510,7 +510,7 @@ tuning.plot.left_detailed <- function(data,
   }
 
   p1 <- data |>
-    tuning.plot(title = title,
+    data.plot(title = title,
                 xname = xname, 
                 yname = yname, 
                 xlabel = xlabel1, 
@@ -518,7 +518,7 @@ tuning.plot.left_detailed <- function(data,
                 line_col = line_col1)
 
   p2 <- data |>
-    tuning.plot.left.n(left.n = left.n,
+    data.plot.left.n(left.n = left.n,
                        title = title.left,
                        xname = xname, 
                        yname = yname, 
@@ -528,7 +528,7 @@ tuning.plot.left_detailed <- function(data,
                        normalize = normalize)
   grid.arrange(p1, p2)
 }
-tuning.plot.left.n <- function(data, 
+data.plot.left.n <- function(data, 
                                left.n = 0,
                                title, 
                                xname, 
@@ -549,7 +549,7 @@ tuning.plot.left.n <- function(data,
   }
 
   data.left |>
-    tuning.plot(title = title,
+    data.plot(title = title,
                 xname = xname,
                 yname = yname,
                 xlabel = xlabel,
@@ -558,7 +558,7 @@ tuning.plot.left.n <- function(data,
                 normalize = normalize)
 }
 
-tuning.plot.right_detailed <- function(data, 
+data.plot.right_detailed <- function(data, 
                                       shift = 1,
                                       title = NULL,
                                       title.right = NULL,
@@ -585,7 +585,7 @@ tuning.plot.right_detailed <- function(data,
   }
 
   p1 <- data |>
-    tuning.plot(title = title,
+    data.plot(title = title,
                 xname = xname, 
                 yname = yname, 
                 xlabel = xlabel1, 
@@ -593,7 +593,7 @@ tuning.plot.right_detailed <- function(data,
                 line_col = line_col1)
 
   p2 <- data |>
-    tuning.plot.shifted.right(shift = shift,
+    data.plot.shifted.right(shift = shift,
[…]

### 2025-05-07 r/src/capstone-movielens.main.R
Minor fix.

@@ -445,7 +445,6 @@ if (file.exists(file_path_tmp)) {
 } else {
   deviation <- seq(0, 6, 0.1) - 3
 
-  start = put_start_date()
   deviation.RMSE <- sapply(deviation, function(delta){
     naive_model_RMSE(mu + delta)
   })

### 2025-05-07 r/src/support-functions/common-helper.functions.R

@@ -631,8 +631,8 @@ data.plot <- function(data,
                         title, 
                         xname, 
                         yname, 
-                        xlabel = NA, 
-                        ylabel = NA,
+                        xlabel = NULL, 
+                        ylabel = NULL,
                         line_col = "blue",
                         # scale = 1,
                         normalize = FALSE) {
@@ -642,10 +642,10 @@ data.plot <- function(data,
     y <- y - min(y)
   }
   
-  if (is.na(xlabel)) {
+  if (is.null(xlabel)) {
     xlabel = xname
   }
-  if (is.na(ylabel)) {
+  if (is.null(ylabel)) {
     ylabel = yname
   }
   

### 2025-05-07 r/src/support-functions/common-helper.functions.R
Minor fix.

@@ -481,7 +481,7 @@ Currently reached best RMSE for `parameter value = %1`: %2",
                                  RMSE = result.RMSE))
 }
 
-### Model Data Visualization -----------------------------------------
+## Model Data Visualization -----------------------------------------
 
 data.plot.left_detailed <- function(data, 
                                       left.n = 0,

### 2025-05-07 reports/capstone-movielens-report.draft4.Rmd
RMD report updated.

@@
 }
-
 ```
@@
 If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
-
-```{r eval=FALSE}
-  mu.RMSE <- sqrt(mean(MSEs))
-```
-```{r}
+```{r eval=FALSE}
+mu.MSEs <- naive_model_MSEs(mu)
+```
+```{r}
+  data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
+    data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
+                xname = "fold_No", 
+                yname = "MSE")
+
+mu.RMSE <- sqrt(mean(mu.MSEs))
 mu.RMSE
 ```
+::: {.noteblock data-latex=""}
+For the _Mean Squared Error_ data visualization we used [`data.plot` function](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R#L630) defined in [_Model Data Visualization_ section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R#L484) of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script.
+:::
+
+Here we also used [`naive_model_MSEs` function](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R#L54) defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
+
+```{r eval=FALSE}
+naive_model_MSEs <- function(val) {
+  sapply(edx_CV, function(cv_item){
+    mse(cv_item$validation_set$rating - val)
+  })
+}
+```
+
+One more function we will need for further analysis of the current model is the [`naive_model_RMSE` one](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R#L59) defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script already mentioned above:
+```{r}
+naive_model_RMSE <- function(val){
+  sqrt(mean(naive_model_MSEs(val)))
+}
+```
+
+#### Ensure that `mu.RMSE` value is the best for the current model
+\
 
@@
   deviation <- seq(0, 6, 0.1) - 3
-print(deviation)
-
-rmse_value <- sapply(deviation, function(diff){
-  rmse(test_set$rating - mu + diff)
+
+  deviation.RMSE <- sapply(deviation, function(delta){
+    naive_model_RMSE(mu + delta)
   })
-
-plot(deviation, rmse_value, type = "l")
-
-sprintf("Minimum RMSE is achieved when the deviation from the mean is: %s", 
-        deviation[which.min(rmse_value)])
+  put_log1("RMSE values have been computed for %1 deviations from the Overall Mean Rating.",
+           length(deviation))
+```
+
+Let's make a quick investigation of the `deviation.RMSE` result we have just got: 
+```{r}
+data.frame(delta = deviation, 
+           delta.RMSE = deviation.RMSE) |> 
+data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
+              xname = "delta", 
+              yname = "delta.RMSE", 
+              xlabel = TeX(r'[$\delta$]'), 
+              ylabel = "RMSE")
+
+which_min_deviation <- deviation[which.min(deviation.RMSE)]
+min_rmse = min(deviation.RMSE)
+
+put_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
+         which_min_deviation)
+
+put_log1("Is the previously computed RMSE the best for the current model: %1",
+         mu.RMSE == min_rmse)
 

### 2025-05-07 reports/capstone-movielens-report.draft4.Rmd
Draft report, section fixed: Overall Mean Rating (Naive) Model.

@@
 ```{r eval=FALSE }
+## Logging Helper functions -----------------------------------------------------
 open_logfile <- function(file_name){
@@
 
+msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
+  msg_template |> 
+    str_replace_all(arg.name, as.character(arg))
+}
+msg.glue <- function(msg_template, arg, arg.name = "%1"){
+  msg_template |>
+    msg.set_arg(arg, arg.name) |>
+    str_glue()
+}
+
 print_log <- function(msg){
@@
 }
+
+get_log1 <- function(msg_template, arg1) {
+  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
+}
+print_log1 <- function(msg_template, arg1){
+  print(get_log1(msg_template, arg1))
+}
 put_log1 <- function(msg_template, arg1){
-  msg <- str_replace_all(msg_template, "%1", as.character(arg1))
-  put(str_glue(msg))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  msg <- msg_template |> 
+  put(get_log1(msg_template, arg1))
+}
+
+get_log2 <- function(msg_template, arg1, arg2) {
+  msg_template |> 
     str_replace_all("%1", as.character(arg1)) |>
@@
     str_glue()
-
-  put(msg)
-}
-
+}
+print_log2 <- function(msg_template, arg1, arg2){
+  print(get_log1(msg_template, arg1, arg2))
+}
+put_log2 <- function(msg_template, arg1, arg2){
+  put(get_log1(msg_template, arg1, arg2))
+}
+
+# ...
 ```
@@
 
-```{r pressure, echo=TRUE, eval=FALSE}
+```{r pressure, echo=TRUE}
 mu <- mean(edx$rating)
-```
-```{r}
 print(mu)
@@
 If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
-```{r eval=FALSE}
+```{r}
 mu.MSEs <- naive_model_MSEs(mu)
-```
-```{r}
 data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
@@
 
-```{r eval=FALSE}
+```{r eval=FALSE }
 naive_model_MSEs <- function(val) {
@@
 One more function we will need for further analysis of the current model is the [`naive_model_RMSE` one](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R#L59) defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script already mentioned above:
-```{r}
+```{r eval=FALSE }
 naive_model_RMSE <- function(val){
@@
 If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r eval=FALSE}
+```{r }
   deviation <- seq(0, 6, 0.1) - 3
@@
   })
-  put_log1("RMSE values have been computed for %1 deviations from the Overall Mean Rating.",
-           length(deviation))
 ```
@@
 
-put_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
+print_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
          which_min_deviation)
 
-put_log1("Is the previously computed RMSE the best for the current model: %1",
+print_log1("Is the previously computed RMSE the best for the current model: %1",
          mu.RMSE == min_rmse)

### 2025-05-07 r/src/capstone-movielens.main.R

@@ -59,32 +59,57 @@ print_log <- function(msg){
 put_log <- function(msg){
   put(str_glue(msg))
 }
-put_log1 <- function(msg_template, arg1){
-  msg <- str_replace_all(msg_template, "%1", as.character(arg1))
-  put(str_glue(msg))
+
+get_log1 <- function(msg_template, arg1) {
+  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
 }
-put_log2 <- function(msg_template, arg1, arg2){
-  msg <- msg_template |> 
+print_log1 <- function(msg_template, arg1){
+  print(get_log1(msg_template, arg1))
+}
+put_log1 <- function(msg_template, arg1){
+  put(get_log1(msg_template, arg1))
+}
+
+get_log2 <- function(msg_template, arg1, arg2) {
+  msg_template |> 
     str_replace_all("%1", as.character(arg1)) |>
     str_replace_all("%2", as.character(arg2)) |>
     str_glue()
-  
-  put(msg)
 }
-put_log3 <- function(msg_template, arg1, arg2, arg3){
-  msg <- msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_replace_all("%3", as.character(arg2))
-  put(str_glue(msg))
+print_log2 <- function(msg_template, arg1, arg2){
+  print(get_log1(msg_template, arg1, arg2))
 }
-put_log3 <- function(msg_template, arg1, arg2, arg3, arg4){
-  msg <- msg_template |> 
+put_log2 <- function(msg_template, arg1, arg2){
+  put(get_log1(msg_template, arg1, arg2))
+}
+
+get_log3 <- function(msg_template, arg1, arg2, arg3) {
+  msg_template |> 
     str_replace_all("%1", as.character(arg1)) |>
     str_replace_all("%2", as.character(arg2)) |>
     str_replace_all("%3", as.character(arg2)) |>
-    str_replace_all("%4", as.character(arg2))
-  put(str_glue(msg))
+    str_glue()
+}
+print_log3 <- function(msg_template, arg1, arg2, arg3){
+  print(get_log1(msg_template, arg1, arg2, arg3))
+}
+put_log3 <- function(msg_template, arg1, arg2, arg3){
+  put(get_log1(msg_template, arg1, arg2, arg3))
+}
+
+get_log4 <- function() {
+  msg_template |> 
[…]

### 2025-05-07 r/src/support-functions/common-helper.functions.R

@@ -481,184 +481,3 @@ Currently reached best RMSE for `parameter value = %1`: %2",
                                  RMSE = result.RMSE))
 }
 
-## Model Data Visualization -----------------------------------------
-
-data.plot.left_detailed <- function(data, 
-                                      left.n = 0,
-                                      title = NULL,
-                                      title.left = NULL,
-                                      xname, 
-                                      yname, 
-                                      xlabel1 = NULL, 
-                                      xlabel2 = NULL, 
-                                      ylabel1 = NULL,
-                                      ylabel2 = NULL,
-                                      line_col1 = "blue",
-                                      line_col2 = "red",
-                                      normalize = FALSE) {
-  if(is.null(xlabel1)) {
-    xlabel1 <- xname
-  }
-  if(is.null(xlabel2)) {
-    xlabel2 <- str_glue(xlabel1, " (left part)")
-  }
-  if(is.null(ylabel1)) {
-    ylabel1 <- yname
-  }
-  if(is.null(ylabel2)) {
-    ylabel2 <- ylabel1
-  }
-
-  p1 <- data |>
-    data.plot(title = title,
-                xname = xname, 
-                yname = yname, 
-                xlabel = xlabel1, 
-                ylabel = ylabel1,
-                line_col = line_col1)
-
-  p2 <- data |>
-    data.plot.left.n(left.n = left.n,
-                       title = title.left,
-                       xname = xname, 
-                       yname = yname, 
-                       xlabel = xlabel2, 
-                       ylabel = ylabel2,
-                       line_col = line_col2,
-                       normalize = normalize)
-  grid.arrange(p1, p2)
-}
-data.plot.left.n <- function(data, 
-                               left.n = 0,
-                               title, 
-                               xname, 
-                               yname, 
-                               xlabel, 
-                               ylabel,
-                               line_col = "red",
-                               normalize = FALSE) {
-  x_col <- data[, xname] 
-  y_col <- data[, yname]
-  
-  
-  data.left <- data
-  
-  if (left.n > 0) {
-    data.left <- data |> 
-      head(left.n)
-  }
-
-  data.left |>
-    data.plot(title = title,
-                xname = xname,
-                yname = yname,
-                xlabel = xlabel,
-                ylabel = ylabel,
-                line_col = line_col,
-                normalize = normalize)
-}
-
-data.plot.right_detailed <- function(data, 
-                                      shift = 1,
[…]

### 2025-05-07 r/src/support-functions/data.helper.functions.R

@@ -428,7 +428,7 @@ datasets.left_join.NAs <- function(test_set,
     movie.NAs = m.NAs, 
     days.NAs = d.NAs)
 }
-## Model training ---------------------------------------------------
+## Model training --------------------------------------------------------------
 union_cv_results <- function(data_list) {
   out_dat <- data_list[[1]]
   
@@ -443,4 +443,181 @@ get_best_param.result <- function(param_values, rmses){
   best_pvalue_idx <- which.min(rmses)
   c(param.best_value = param_values[best_pvalue_idx], 
     best_RMSE = rmses[best_pvalue_idx])
+}
+## Data Visualization ----------------------------------------------------------
+data.plot.left_detailed <- function(data, 
+                                    left.n = 0,
+                                    title = NULL,
+                                    title.left = NULL,
+                                    xname, 
+                                    yname, 
+                                    xlabel1 = NULL, 
+                                    xlabel2 = NULL, 
+                                    ylabel1 = NULL,
+                                    ylabel2 = NULL,
+                                    line_col1 = "blue",
+                                    line_col2 = "red",
+                                    normalize = FALSE) {
+  if(is.null(xlabel1)) {
+    xlabel1 <- xname
+  }
+  if(is.null(xlabel2)) {
+    xlabel2 <- str_glue(xlabel1, " (left part)")
+  }
+  if(is.null(ylabel1)) {
+    ylabel1 <- yname
+  }
+  if(is.null(ylabel2)) {
+    ylabel2 <- ylabel1
+  }
+  
+  p1 <- data |>
+    data.plot(title = title,
+              xname = xname, 
+              yname = yname, 
+              xlabel = xlabel1, 
+              ylabel = ylabel1,
+              line_col = line_col1)
+  
+  p2 <- data |>
+    data.plot.left.n(left.n = left.n,
+                     title = title.left,
+                     xname = xname, 
+                     yname = yname, 
+                     xlabel = xlabel2, 
+                     ylabel = ylabel2,
+                     line_col = line_col2,
+                     normalize = normalize)
+  grid.arrange(p1, p2)
+}
+data.plot.left.n <- function(data, 
+                             left.n = 0,
+                             title, 
+                             xname, 
+                             yname, 
+                             xlabel, 
+                             ylabel,
+                             line_col = "red",
+                             normalize = FALSE) {
+  x_col <- data[, xname] 
+  y_col <- data[, yname]
+  
+  
[…]

### 2025-05-07 reports/capstone-movielens-report.draft4.tex

@@
 \author{Azamat Kurbanaev}
-\date{2025-05-06}
+\date{2025-05-07}
 
@@
 \begin{Highlighting}[]
-\NormalTok{  mu.RMSE }\OtherTok{\textless{}{-}} \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mean}\NormalTok{(MSEs))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
+\NormalTok{mu.MSEs }\OtherTok{\textless{}{-}} \FunctionTok{naive\_model\_MSEs}\NormalTok{(mu)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+  \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{fold\_No =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{, }\AttributeTok{MSE =}\NormalTok{ mu.MSEs) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{data.plot}\NormalTok{(}\AttributeTok{title =} \StringTok{"MSE resuls of the 5{-}fold CV method applied to the Overall Mean Rating Model"}\NormalTok{,}
+                \AttributeTok{xname =} \StringTok{"fold\_No"}\NormalTok{, }
+                \AttributeTok{yname =} \StringTok{"MSE"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-40-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{mu.RMSE }\OtherTok{\textless{}{-}} \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mean}\NormalTok{(mu.MSEs))}
 \NormalTok{mu.RMSE}
@@
 \begin{verbatim}
-## [1] 1.060346
-\end{verbatim}
+## [1] 1.061191
+\end{verbatim}
+
+\begin{noteblock}
+For the \emph{Mean Squared Error} data visualization we used
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R\#L630}{\texttt{data.plot}
+function} defined in
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R\#L484}{\emph{Model
+Data Visualization} section} of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R}{common-helper.functions.R}
+script.
+
+\end{noteblock}
+
+Here we also used
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R\#L54}{\texttt{naive\_model\_MSEs}
+function} defined in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R}{same
+script} to compute \emph{Mean Squared Errors} using \emph{5-Fold Cross
+Validation} method:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{naive\_model\_MSEs }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(val) \{}
+  \FunctionTok{sapply}\NormalTok{(edx\_CV, }\ControlFlowTok{function}\NormalTok{(cv\_item)\{}
+    \FunctionTok{mse}\NormalTok{(cv\_item}\SpecialCharTok{$}\NormalTok{validation\_set}\SpecialCharTok{$}\NormalTok{rating }\SpecialCharTok{{-}}\NormalTok{ val)}
+\NormalTok{  \})}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+One more function we will need for further analysis of the current model
+is the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R\#L59}{\texttt{naive\_model\_RMSE}
+one} defined in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R}{common-helper.functions.R}
+script already mentioned above:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{naive\_model\_RMSE }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(val)\{}
+  \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mean}\NormalTok{(}\FunctionTok{naive\_model\_MSEs}\NormalTok{(val)))}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\paragraph{\texorpdfstring{Ensure that \texttt{mu.RMSE} value is the
+best for the current
+model}{Ensure that mu.RMSE value is the best for the current model}}\label{ensure-that-mu.rmse-value-is-the-best-for-the-current-model}
+
+\hfill\break
 
@@
 \begin{Highlighting}[]
-\NormalTok{deviation }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{6}\NormalTok{, }\FloatTok{0.1}\NormalTok{) }\SpecialCharTok{{-}} \DecValTok{3}
-\FunctionTok{print}\NormalTok{(deviation)}
-
-\NormalTok{rmse\_value }\OtherTok{\textless{}{-}} \FunctionTok{sapply}\NormalTok{(deviation, }\ControlFlowTok{function}\NormalTok{(diff)\{}
-  \FunctionTok{rmse}\NormalTok{(test\_set}\SpecialCharTok{$}\NormalTok{rating }\SpecialCharTok{{-}}\NormalTok{ mu }\SpecialCharTok{+}\NormalTok{ diff)}
-\NormalTok{\})}
-
-\FunctionTok{plot}\NormalTok{(deviation, rmse\_value, }\AttributeTok{type =} \StringTok{"l"}\NormalTok{)}
-
-\FunctionTok{sprintf}\NormalTok{(}\StringTok{"Minimum RMSE is achieved when the deviation from the mean is: \%s"}\NormalTok{, }
-\NormalTok{        deviation[}\FunctionTok{which.min}\NormalTok{(rmse\_value)])}
-\end{Highlighting}
-\end{Shaded}
+\NormalTok{  deviation }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{6}\NormalTok{, }\FloatTok{0.1}\NormalTok{) }\SpecialCharTok{{-}} \DecValTok{3}
+
+\NormalTok{  deviation.RMSE }\OtherTok{\textless{}{-}} \FunctionTok{sapply}\NormalTok{(deviation, }\ControlFlowTok{function}\NormalTok{(delta)\{}
+    \FunctionTok{naive\_model\_RMSE}\NormalTok{(mu }\SpecialCharTok{+}\NormalTok{ delta)}
+\NormalTok{  \})}
+  \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"RMSE values have been computed for \%1 deviations from the Overall Mean Rating."}\NormalTok{,}
+           \FunctionTok{length}\NormalTok{(deviation))}
+\end{Highlighting}
+\end{Shaded}
+
+Let's make a quick investigation of the \texttt{deviation.RMSE} result
+we have just got:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{delta =}\NormalTok{ deviation, }
+           \AttributeTok{delta.RMSE =}\NormalTok{ deviation.RMSE) }\SpecialCharTok{|\textgreater{}} 
+\FunctionTok{data.plot}\NormalTok{(}\AttributeTok{title =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[RMSE as a function of deviation ($\textbackslash{}delta$) from the Overall Mean Rating ($\textbackslash{}hat\{mu\}$)]\textquotesingle{}}\NormalTok{),}
+              \AttributeTok{xname =} \StringTok{"delta"}\NormalTok{, }
+              \AttributeTok{yname =} \StringTok{"delta.RMSE"}\NormalTok{, }
+              \AttributeTok{xlabel =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[$\textbackslash{}delta$]\textquotesingle{}}\NormalTok{), }
+              \AttributeTok{ylabel =} \StringTok{"RMSE"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Warning in is.na(xlabel): is.na() applied to non-(list or vector) of type 'expression'
+\end{verbatim}
+
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-44-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{which\_min\_deviation }\OtherTok{\textless{}{-}}\NormalTok{ deviation[}\FunctionTok{which.min}\NormalTok{(deviation.RMSE)]}
+\NormalTok{min\_rmse }\OtherTok{=} \FunctionTok{min}\NormalTok{(deviation.RMSE)}
+
+\FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Minimum RMSE is achieved when the deviation from the mean is: \%1"}\NormalTok{,}
+\NormalTok{         which\_min\_deviation)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Minimum RMSE is achieved when the deviation from the mean is: 0
+\end{verbatim}
+
+\begin{verbatim}
+## Log is not open.
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Is the previously computed RMSE the best for the current model: \%1"}\NormalTok{,}
+\NormalTok{         mu.RMSE }\SpecialCharTok{==}\NormalTok{ min\_rmse)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Is the previously computed RMSE the best for the current model: FALSE
+\end{verbatim}
+
+\begin{verbatim}
+## Log is not open.
+\end{verbatim}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-42-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-45-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-54-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-57-1.pdf}
 

### 2025-05-07 reports/capstone-movielens-report.draft4.tex
Draft report updated.

@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-22-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-14-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-25-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-26-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-18-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-29-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-30-1.pdf}
 
@@
 
-\subsubsection{Defining Logging and Mesuring helper
-functions}\label{defining-logging-and-mesuring-helper-functions}
+\subsubsection{Defining Logging and Time Measuring Helper
+Functions}\label{defining-logging-and-time-measuring-helper-functions}
 
@@
 \begin{Highlighting}[]
+\DocumentationTok{\#\# Logging Helper functions {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
 \NormalTok{open\_logfile }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(file\_name)\{}
@@
 
+\NormalTok{msg.set\_arg }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg\_template, arg, }\AttributeTok{arg.name =} \StringTok{"\%1"}\NormalTok{) \{}
+\NormalTok{  msg\_template }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{str\_replace\_all}\NormalTok{(arg.name, }\FunctionTok{as.character}\NormalTok{(arg))}
+\NormalTok{\}}
+\NormalTok{msg.glue }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg\_template, arg, }\AttributeTok{arg.name =} \StringTok{"\%1"}\NormalTok{)\{}
+\NormalTok{  msg\_template }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{msg.set\_arg}\NormalTok{(arg, arg.name) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{str\_glue}\NormalTok{()}
+\NormalTok{\}}
+
 \NormalTok{print\_log }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg)\{}
@@
 \NormalTok{\}}
+
+\NormalTok{get\_log1 }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg\_template, arg1) \{}
+  \FunctionTok{str\_glue}\NormalTok{(}\FunctionTok{str\_replace\_all}\NormalTok{(msg\_template, }\StringTok{"\%1"}\NormalTok{, }\FunctionTok{as.character}\NormalTok{(arg1)))}
+\NormalTok{\}}
+\NormalTok{print\_log1 }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg\_template, arg1)\{}
+  \FunctionTok{print}\NormalTok{(}\FunctionTok{get\_log1}\NormalTok{(msg\_template, arg1))}
+\NormalTok{\}}
 \NormalTok{put\_log1 }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg\_template, arg1)\{}
-\NormalTok{  msg }\OtherTok{\textless{}{-}} \FunctionTok{str\_replace\_all}\NormalTok{(msg\_template, }\StringTok{"\%1"}\NormalTok{, }\FunctionTok{as.character}\NormalTok{(arg1))}
-  \FunctionTok{put}\NormalTok{(}\FunctionTok{str\_glue}\NormalTok{(msg))}
-\NormalTok{\}}
-\NormalTok{put\_log2 }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg\_template, arg1, arg2)\{}
-\NormalTok{  msg }\OtherTok{\textless{}{-}}\NormalTok{ msg\_template }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{put}\NormalTok{(}\FunctionTok{get\_log1}\NormalTok{(msg\_template, arg1))}
+\NormalTok{\}}
+
+\NormalTok{get\_log2 }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg\_template, arg1, arg2) \{}
+\NormalTok{  msg\_template }\SpecialCharTok{|\textgreater{}} 
     \FunctionTok{str\_replace\_all}\NormalTok{(}\StringTok{"\%1"}\NormalTok{, }\FunctionTok{as.character}\NormalTok{(arg1)) }\SpecialCharTok{|\textgreater{}}
@@
     \FunctionTok{str\_glue}\NormalTok{()}
-
-  \FunctionTok{put}\NormalTok{(msg)}
-\NormalTok{\}}
+\NormalTok{\}}
+\NormalTok{print\_log2 }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg\_template, arg1, arg2)\{}
+  \FunctionTok{print}\NormalTok{(}\FunctionTok{get\_log1}\NormalTok{(msg\_template, arg1, arg2))}
+\NormalTok{\}}
+\NormalTok{put\_log2 }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(msg\_template, arg1, arg2)\{}
+  \FunctionTok{put}\NormalTok{(}\FunctionTok{get\_log1}\NormalTok{(msg\_template, arg1, arg2))}
+\NormalTok{\}}
+
+\CommentTok{\# ...}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{  mu }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{rating)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
+\NormalTok{mu }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(edx}\SpecialCharTok{$}\NormalTok{rating)}
 \FunctionTok{print}\NormalTok{(mu)}
@@
 \begin{verbatim}
-## [1] 3.47184
+## [1] 3.512465
 \end{verbatim}
@@
 \NormalTok{mu.MSEs }\OtherTok{\textless{}{-}} \FunctionTok{naive\_model\_MSEs}\NormalTok{(mu)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
 \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{fold\_No =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{, }\AttributeTok{MSE =}\NormalTok{ mu.MSEs) }\SpecialCharTok{|\textgreater{}}
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-40-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-49-1.pdf}
 
@@
 \begin{verbatim}
-## [1] 1.061191
+## [1] 1.060346
 \end{verbatim}
@@
 \NormalTok{  \})}
-  \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"RMSE values have been computed for \%1 deviations from the Overall Mean Rating."}\NormalTok{,}
-           \FunctionTok{length}\NormalTok{(deviation))}
 \end{Highlighting}
@@
 
-\begin{verbatim}
-## Warning in is.na(xlabel): is.na() applied to non-(list or vector) of type 'expression'
-\end{verbatim}
-
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-44-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-53-1.pdf}
 
@@
 
-\FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Minimum RMSE is achieved when the deviation from the mean is: \%1"}\NormalTok{,}
+\FunctionTok{print\_log1}\NormalTok{(}\StringTok{"Minimum RMSE is achieved when the deviation from the mean is: \%1"}\NormalTok{,}
 \NormalTok{         which\_min\_deviation)}
@@
 
-\begin{verbatim}
-## Log is not open.
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Is the previously computed RMSE the best for the current model: \%1"}\NormalTok{,}
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{print\_log1}\NormalTok{(}\StringTok{"Is the previously computed RMSE the best for the current model: \%1"}\NormalTok{,}
 \NormalTok{         mu.RMSE }\SpecialCharTok{==}\NormalTok{ min\_rmse)}
@@
 \begin{verbatim}
-## Is the previously computed RMSE the best for the current model: FALSE
-\end{verbatim}
-
-\begin{verbatim}
-## Log is not open.
+## Is the previously computed RMSE the best for the current model: TRUE
 \end{verbatim}
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-45-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-54-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-57-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-66-1.pdf}
 

### 2025-05-07 reports/capstone-movielens-report.draft4.Rmd
Draft report updated.

@@
 
-### Defining Logging and Mesuring helper functions
+### Defining Logging and Time Measuring Helper Functions
 \
@@
 ::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper function section of the Capstone MovieLens Main R Script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/capstone-movielens.main.R#L1).
+The full source code of these functions is available in the [Logging Helper function section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) of the [Capstone MovieLens Main R Script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R).
 :::
@@
 ::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [`Initialize input datasets` section of the `data.helper.functions.R` script on _GitHub_](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R#L86)
+The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the function mentioned above is also available in the [`Initialize input datasets` section of the `data.helper.functions.R` script on _GitHub_](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R#L86)
+The source code of the function mentioned above is also available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-This code snippet is a part of the [`make_source_datasets` _function_ code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R#L87) described above.
+This code snippet is a part of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
 :::
@@
 ::: {.noteblock data-latex=""}
-The [`sample_train_validation_sets` function](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R#L15) is defined in the same script as the `make_source_datasets` one, from where it is called.
+The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)` one, from where it is called.
 :::
@@
 
-For our further analysis, we are going to use the following _common helper functions:
+For our further analysis, we are going to use the following _common helper functions_:
 
@@
 ```
+
+::: {.noteblock data-latex=""}
+All the _common helper functions_, including those described above, are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+:::
 
@@
 ::: {.noteblock data-latex=""}
-For the _Mean Squared Error_ data visualization we used [`data.plot` function](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R#L630) defined in [_Model Data Visualization_ section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R#L484) of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script.
+For the _Mean Squared Error_ data visualization we used [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function] defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.function.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script.
 :::
 
-Here we also used [`naive_model_MSEs` function](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R#L54) defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
+```{r eval=FALSE}
+data.plot <- function(data, 
+                      title, 
+                      xname, 
+                      yname, 
+                      xlabel = NULL, 
+                      ylabel = NULL,
+                      line_col = "blue",
+                      # scale = 1,
+                      normalize = FALSE) {
+  y <- data[, yname]
+
+  if (normalize) {
+    y <- y - min(y)
+  }
+
+  if (is.null(xlabel)) {
+    xlabel = xname
+  }
+  if (is.null(ylabel)) {
+    ylabel = yname
+  }
+
+  aes_mapping <- aes(x = data[, xname], y = y)
+
+  data |> 
+    ggplot(mapping = aes_mapping) +
+    ggtitle(title) +
+    xlab(xlabel) +
+    ylab(ylabel) +
+    geom_point() + 
+    geom_line(color=line_col)
+}
+```
+
+Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
 
@@
 
-One more function we will need for further analysis of the current model is the [`naive_model_RMSE` one](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R#L59) defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script already mentioned above:
+One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L59) one:
 ```{r eval=FALSE }
@@
 
-### Taking into account User effects
+### Taking into account User Effect
 \

### 2025-05-07 reports/capstone-movielens-report.draft4.tex
Draft report updated.

@@
 \author{Azamat Kurbanaev}
-\date{2025-05-07}
+\date{2025-05-08}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-22-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-25-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-14-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-26-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-29-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-18-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-30-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
 
@@
 The full source code of these functions is available in the
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/capstone-movielens.main.R\#L1}{Logging
-Helper function section of the Capstone MovieLens Main R Script}.
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R\#L20}{Logging
+Helper function section} of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R}{Capstone
+MovieLens Main R Script}.
 
@@
 The full source code of the function listed above is available in the
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R\#L86}{\texttt{Initialize\ input\ datasets}
-section of the \texttt{data.helper.functions.R} script on \emph{GitHub}}
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R\#L86}{Initialize
+input datasets} section of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R}{data.helper.functions.R}
+script on \emph{GitHub}.
 
@@
 The source code of the function mentioned above is also available in the
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R\#L86}{\texttt{Initialize\ input\ datasets}
-section of the \texttt{data.helper.functions.R} script on \emph{GitHub}}
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R\#L86}{Initialize
+input datasets} section of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R}{data.helper.functions.R}
+script on \emph{GitHub}.
 
@@
 This code snippet is a part of the
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R\#L87}{\texttt{make\_source\_datasets}
-\emph{function} code} described above.
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R\#L87}{make\_source\_datasets}
+\emph{function} code described above.
 
@@
 The
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R\#L15}{\texttt{sample\_train\_validation\_sets}
-function} is defined in the same script as the
-\texttt{make\_source\_datasets} one, from where it is called.
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R\#L15}{sample\_train\_validation\_sets}
+function is defined in the same script as the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R\#L87}{make\_source\_datasets}`
+one, from where it is called.
 
@@
 
-For our further analysis, we are going to use the following \_common
-helper functions:
+For our further analysis, we are going to use the following \emph{common
+helper functions}:
 
@@
 \end{Shaded}
+
+\begin{noteblock}
+All the \emph{common helper functions}, including those described above,
+are defined in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R}{common-helper.functions.R}
+script on \emph{GitHub}.
+
+\end{noteblock}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-49-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-38-1.pdf}
 
@@
 For the \emph{Mean Squared Error} data visualization we used
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R\#L630}{\texttt{data.plot}
-function} defined in
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R\#L484}{\emph{Model
-Data Visualization} section} of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R\#L592}{data.plot}
+function{]} defined in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R\#L447}{Data
+Visualization} section of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R}{data.helper.function.R}
+script.
+
+\end{noteblock}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{data.plot }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data, }
+\NormalTok{                      title, }
+\NormalTok{                      xname, }
+\NormalTok{                      yname, }
+                      \AttributeTok{xlabel =} \ConstantTok{NULL}\NormalTok{, }
+                      \AttributeTok{ylabel =} \ConstantTok{NULL}\NormalTok{,}
+                      \AttributeTok{line\_col =} \StringTok{"blue"}\NormalTok{,}
+                      \CommentTok{\# scale = 1,}
+                      \AttributeTok{normalize =} \ConstantTok{FALSE}\NormalTok{) \{}
+\NormalTok{  y }\OtherTok{\textless{}{-}}\NormalTok{ data[, yname]}
+
+  \ControlFlowTok{if}\NormalTok{ (normalize) \{}
+\NormalTok{    y }\OtherTok{\textless{}{-}}\NormalTok{ y }\SpecialCharTok{{-}} \FunctionTok{min}\NormalTok{(y)}
+\NormalTok{  \}}
+
+  \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{is.null}\NormalTok{(xlabel)) \{}
+\NormalTok{    xlabel }\OtherTok{=}\NormalTok{ xname}
+\NormalTok{  \}}
+  \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{is.null}\NormalTok{(ylabel)) \{}
+\NormalTok{    ylabel }\OtherTok{=}\NormalTok{ yname}
+\NormalTok{  \}}
+
+\NormalTok{  aes\_mapping }\OtherTok{\textless{}{-}} \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ data[, xname], }\AttributeTok{y =}\NormalTok{ y)}
+
+\NormalTok{  data }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{mapping =}\NormalTok{ aes\_mapping) }\SpecialCharTok{+}
+    \FunctionTok{ggtitle}\NormalTok{(title) }\SpecialCharTok{+}
+    \FunctionTok{xlab}\NormalTok{(xlabel) }\SpecialCharTok{+}
+    \FunctionTok{ylab}\NormalTok{(ylabel) }\SpecialCharTok{+}
+    \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} 
+    \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color=}\NormalTok{line\_col)}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+Here we also used
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L54}{naive\_model\_MSEs}
+function defined in the
 \href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R}{common-helper.functions.R}
-script.
-
-\end{noteblock}
-
-Here we also used
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R\#L54}{\texttt{naive\_model\_MSEs}
-function} defined in the
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R}{same
-script} to compute \emph{Mean Squared Errors} using \emph{5-Fold Cross
-Validation} method:
+script (already mentioned above) to compute \emph{Mean Squared Errors}
+using \emph{5-Fold Cross Validation} method:
 
@@
 
-One more function we will need for further analysis of the current model
-is the
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/914dd47023dc21b6b06a0ca412b7f7281602275a/r/src/support-functions/common-helper.functions.R\#L59}{\texttt{naive\_model\_RMSE}
-one} defined in the
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R}{common-helper.functions.R}
-script already mentioned above:
+One more function, defined in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R}{same
+script}, that we will need for further analysis of the current model, is
+the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L59}{naive\_model\_RMSE}
+one:
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-53-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-43-1.pdf}
 
@@
 \subsubsection{Taking into account User
-effects}\label{taking-into-account-user-effects}
+Effect}\label{taking-into-account-user-effect}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-54-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-44-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-66-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-56-1.pdf}
 

### 2025-05-08 r/src/capstone-movielens.main.R
Draft report: User Effect Model described.

@@ -513,10 +513,10 @@ data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Ove
 put_log("A plot was constructed for the deviations from the Overall Mean Rating.")
 
 #### Add a row to the RMSE Result Tibble for the Overall Mean Rating Model ------ 
-RMSEs.ResultTibble <- RMSEs.ResultTibble |> 
+RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
   RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
 
-RMSE_kable(RMSEs.ResultTibble)
+RMSE_kable(RMSEs.ResultTibble.OMR)
 put_log("A row has been added to the RMSE Result Tibble for the `Overall Mean Rating Model`.")
 #### Close Log ---------------------------------------------------------------
 log_close()
@@ -652,7 +652,7 @@ hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
      main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
 put_log("A histogram of the User Effect distribution has been plotted.")
 
-###### Computing the RMSE taking into account user effects ---------------------
+###### Computing the RMSE taking into account User Effect ---------------------
 #> Finally, we are ready to compute the `RMSE` (additionally using the helper 
 #> function `clamp` we defined above to keep predictions in the proper range):
 
@@ -666,7 +666,12 @@ edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
 })
 put_end_date(start)
 
-plot(edx.user_effect.MSEs)
+data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
+  data.plot(title = "MSE resuls of the 5-fold CV method applied to the User Effect Model",
+            xname = "fold_No", 
+            yname = "MSE")
+
+
 put_log1("RMSE values have been plotted for the %1-Fold Cross Validation samples.", 
          CVFolds_N)
 
@@ -678,10 +683,10 @@ edx.user_effect.RMSE
 #> [1] 0.9716054
 
 ###### Add a row to the RMSE Result Tibble for the User Effect Model -----------
-RMSEs.ResultTibble <- RMSEs.ResultTibble |> 
+RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
[…]

### 2025-05-08 r/src/support-functions/user-effect.functions.R

@@ -1,102 +1,0 @@
-# User+Movie Effect Model Functions --------------------------------------------
-train_user_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_effect
-`lambda` is `NA`")
-  }
-
-  train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    # filter(!is.na(resid)) |>
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-}
-train_user_effect.cv <- function(lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_effect.cv
-`lambda` is `NA`")
-  }
-  
-  if(lambda == 0) put_log("Function: train_user_effect.cv:
-Computing User+Movie Effect...")
-  else put_log1("Function: train_user_effect.cv:
-Computing User+Movie Effect for lambda: %1...",
-                lambda)
-  
-  start <- put_start_date()
-  user_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_effect(lambda)
-  })
-  put_end_date(start)
-  str(user_effects_ls)
-  put_log("Function: train_user_effect.cv:
-User+Movie Effect list have been computed")
-  
-  user_effects_united <- union_cv_results(user_effects_ls)
-  str(user_effects_united)
-  # sum(is.na(user_effects_united$cv_dat)) # 0 (there are no NAs in there)
-  
-  user_effect <- user_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  
-  # sum(is.na(user_effect$b)) # 0 (there are no NAs in there)
-  
-  #user_effect <- data.frame(movieId = as.integer(names(b)), b = b)
-  if(lambda == 0) put_log("Function: train_user_effect.cv:
-Training completed: User+Movie Effects model.")
-  else put_log1("Function: train_user_effect.cv:
-Training completed: User+Movie Effects model for lambda: %1...",
-                lambda)
-  
-  user_effect
-}
-calc_user_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_effect_MSE(um_effect)
-  sqrt(mse)
-}
[…]

### 2025-05-08 r/src/capstone-movielens.main.R
R-script code fixed & cleaned up.

@@ -652,7 +652,7 @@ hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
      main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
 put_log("A histogram of the User Effect distribution has been plotted.")
 
-###### Computing the RMSE taking into account User Effect ---------------------
+###### Compute RMSE for User Effect Model ------------------------------------
 #> Finally, we are ready to compute the `RMSE` (additionally using the helper 
 #> function `clamp` we defined above to keep predictions in the proper range):
 
@@ -775,10 +775,10 @@ put_log("A histogram of the Mean User+Movie Effects distribution has been plotte
 cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
 #> [1] 0.8732081
 ##### Add a row to the RMSE Result Tibble for the User+Movie Effect Model --------
-RMSEs.ResultTibble <- RMSEs.ResultTibble |> 
+RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
   RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
 
-RMSE_kable(RMSEs.ResultTibble)
+RMSE_kable(RMSEs.ResultTibble.UME)
 put_log("A row has been added to the RMSE Result Tibble for the `User+Movie Effect Model`.")
 
 #### Close Log -----------------------------------------------------------------

### 2025-05-08 r/src/support-functions/UM-effect.functions.R

@@ -31,21 +31,15 @@ Computing User+Movie Effect for lambda: %1...",
     cv_fold_dat$train_set |> train_user_movie_effect(lambda)
   })
   put_end_date(start)
-  str(user_movie_effects_ls)
   put_log("Function: train_user_movie_effect.cv:
 User+Movie Effect list have been computed")
   
   user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-  str(user_movie_effects_united)
-  # sum(is.na(user_movie_effects_united$cv_dat)) # 0 (there are no NAs in there)
-  
+
   user_movie_effect <- user_movie_effects_united |>
     group_by(movieId) |>
     summarise(b = mean(b), n = mean(n))
-  
-  # sum(is.na(user_movie_effect$b)) # 0 (there are no NAs in there)
-  
-  #user_movie_effect <- data.frame(movieId = as.integer(names(b)), b = b)
+
   if(lambda == 0) put_log("Function: train_user_movie_effect.cv:
 Training completed: User+Movie Effects model.")
   else put_log1("Function: train_user_movie_effect.cv:
@@ -63,7 +57,6 @@ calc_user_movie_effect_MSE <- function(test_set, um_effect){
     left_join(edx.user_effect, by = "userId") |>
     left_join(um_effect, by = "movieId") |>
     mutate(resid = rating - clamp(mu + a + b)) |> 
-    # filter(!is.na(resid)) |>
     pull(resid) |> mse()
   
   stopifnot(!is.na(mse.result))

### 2025-05-08 reports/capstone-movielens-report.draft4.Rmd

@@
 ::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper function section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) of the [Capstone MovieLens Main R Script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R).
+The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-This code snippet is a part of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
+This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
 :::
@@
          mu.RMSE == min_rmse)
-
+```
+```{r eval=FALSE}
+RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
+  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.OMR)
 ```
@@
 \
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects).
+To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
 If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
@@
 hist(edx.user_mean_ratings$mean_rating, nclass = 30)
-print("A histogram of the User Mean Rating distribution has been plotted.")
 ```
@@
 
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we compute them this way:
+As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we can compute them this way:
 ```{r eval=FALSE}
@@
 
-Finally, we are ready to compute the `RMSE` (additionally using the helper function `clamp` we defined above to keep predictions in the proper range):
-```{r eval=FALSE}
-# Compute the RMSE taking into account user effects:
-user_effects_rmse <- test_set |> 
-    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
+These considerations alows us to compute a _User Mean Ratings_ the following way:
+```{r eval=FALSE}
+put_log("Computing Average Ratings per User (User Mean Ratings)...")
+user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
+user_ratings.n <- rowSums(!is.na(edx.mx))
+
+edx.user_mean_ratings <- 
+  data.frame(userId = names(user.mean_ratings), 
+             mean_rating = user.mean_ratings,
+             n = user_ratings.n)
+
+put_log("User Mean Ratings have been computed.")
+```
+```{r}
+str(edx.user_mean_ratings)
+```
+
+And then we compute a _User Effect_ this way:
+```{r eval=FALSE}
+put_log("Computing User Effect per users ...")
+edx.user_effect <- edx.user_mean_ratings |>
+  mutate(userId = as.integer(userId),
+         a = mean_rating - mu)
+
+put_log("A User Effect Model has been builded")
+```
+```{r}
+par(cex = 0.7)
+hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
+     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
+
+str(edx.user_effect)
+```
+
+::: {.noteblock data-latex=""}
+The full source code of the _User Effect_ computation is available in the [Model building: User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L531) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+:::
+
+Finally, we are ready to compute the `RMSE` (additionally using the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) helper function we defined above to keep predictions in the proper range):
+```{r eval=FALSE}
+put_log("Computing the RMSE taking into account user effects...")
+start <- put_start_date()
+edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
+  cv_fold_dat$validation_set |>
+    left_join(edx.user_effect, by = "userId") |>
     mutate(resid = rating - clamp(mu + a)) |> 
-    filter(!is.na(resid)) |>
-    pull(resid) |> rmse()
-
-print(user_effects_rmse)
-```
+    pull(resid) |> mse()
+})
+put_end_date(start)
+
+edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
+
+RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
+  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
+```
+```{r}
+data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
+  data.plot(title = "MSE resuls of the 5-fold CV method applied to the User Effect Model",
+            xname = "fold_No", 
+            yname = "MSE")
+
+RMSE_kable(RMSEs.ResultTibble.UE)
+```
+
+::: {.noteblock data-latex=""}
+The full source code of the _User Effect Model RMSE_ computation is available in the [Computing the RMSE taking into account User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+:::
+
 ### Taking into account Movie effects
 \
+
 In [Section _23.5 Movie effects_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) the author draws our attention to the fact that some movies are generally rated higher than others.

### 2025-05-08 reports/capstone-movielens-report.draft4.tex

@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-20-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-14-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-23-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-24-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-18-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-27-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-28-1.pdf}
 
@@
 \href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R\#L20}{Logging
-Helper function section} of the
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R}{Capstone
-MovieLens Main R Script}.
+Helper functions} section of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R}{capstone-movielens.main.R}
+script on \emph{GitHub}.
 
@@
 \begin{noteblock}
-This code snippet is a part of the
+This code snippet is a
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R\#L140}{part}
+of the
 \href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R\#L87}{make\_source\_datasets}
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-38-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-47-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-43-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-52-1.pdf}
 
@@
 \end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{RMSEs.ResultTibble.OMR }\OtherTok{\textless{}{-}}\NormalTok{ RMSEs.ResultTibble }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{RMSEs.AddRow}\NormalTok{(}\StringTok{"Overall Mean Rating Model"}\NormalTok{, mu.RMSE)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{RMSE\_kable}\NormalTok{(RMSEs.ResultTibble.OMR)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{35em}>{\centering\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{50em}}
+\toprule
+\textbf{Method} & \textbf{RMSE} & \textbf{Comment}\\
+\midrule
+Project Objective & 0.864900 & \\
+Overall Mean Rating Model & 1.060346 & \\
+\bottomrule
+\end{longtable}
 
@@
 \href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#user-effects}{Section
-\emph{23.4 User effects} of the \emph{Course Textbook}}. If we visualize
+\emph{23.4 User effects}} of the \emph{Course Textbook}. If we visualize
 the average rating for each user the way the
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-44-1.pdf}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{print}\NormalTok{(}\StringTok{"A histogram of the User Mean Rating distribution has been plotted."}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] "A histogram of the User Mean Rating distribution has been plotted."
-\end{verbatim}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-55-1.pdf}
 
@@
 squares estimate \(\hat{\alpha}_i\) is just the average of
-\(y_{i,j} - \hat{\mu}\) for each user \(i\). So we compute them this
+\(y_{i,j} - \hat{\mu}\) for each user \(i\). So we can compute them this
 way:
@@
 
+These considerations alows us to compute a \emph{User Mean Ratings} the
+following way:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{put\_log}\NormalTok{(}\StringTok{"Computing Average Ratings per User (User Mean Ratings)..."}\NormalTok{)}
+\NormalTok{user.mean\_ratings }\OtherTok{\textless{}{-}} \FunctionTok{rowMeans}\NormalTok{(edx.mx, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)}
+\NormalTok{user\_ratings.n }\OtherTok{\textless{}{-}} \FunctionTok{rowSums}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(edx.mx))}
+
+\NormalTok{edx.user\_mean\_ratings }\OtherTok{\textless{}{-}} 
+  \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{names}\NormalTok{(user.mean\_ratings), }
+             \AttributeTok{mean\_rating =}\NormalTok{ user.mean\_ratings,}
+             \AttributeTok{n =}\NormalTok{ user\_ratings.n)}
+
+\FunctionTok{put\_log}\NormalTok{(}\StringTok{"User Mean Ratings have been computed."}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{str}\NormalTok{(edx.user\_mean\_ratings)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 'data.frame':    69878 obs. of  3 variables:
+##  $ userId     : chr  "1" "2" "3" "4" ...
+##  $ mean_rating: num  5 3.29 3.94 4.06 3.92 ...
+##  $ n          : num  19 17 31 35 74 39 96 727 21 112 ...
+\end{verbatim}
+
+And then we compute a \emph{User Effect} this way:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{put\_log}\NormalTok{(}\StringTok{"Computing User Effect per users ..."}\NormalTok{)}
+\NormalTok{edx.user\_effect }\OtherTok{\textless{}{-}}\NormalTok{ edx.user\_mean\_ratings }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{as.integer}\NormalTok{(userId),}
+         \AttributeTok{a =}\NormalTok{ mean\_rating }\SpecialCharTok{{-}}\NormalTok{ mu)}
+
+\FunctionTok{put\_log}\NormalTok{(}\StringTok{"A User Effect Model has been builded"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{par}\NormalTok{(}\AttributeTok{cex =} \FloatTok{0.7}\NormalTok{)}
+\FunctionTok{hist}\NormalTok{(edx.user\_effect}\SpecialCharTok{$}\NormalTok{a, }\DecValTok{30}\NormalTok{, }\AttributeTok{xlab =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[$\textbackslash{}hat\{alpha\}\_\{i\}$]\textquotesingle{}}\NormalTok{),}
+     \AttributeTok{main =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[Histogram of $\textbackslash{}hat\{alpha\}\_\{i\}$]\textquotesingle{}}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-60-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{str}\NormalTok{(edx.user\_effect)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 'data.frame':    69878 obs. of  4 variables:
+##  $ userId     : int  1 2 3 4 5 6 7 8 9 10 ...
+##  $ mean_rating: num  5 3.29 3.94 4.06 3.92 ...
+##  $ n          : num  19 17 31 35 74 39 96 727 21 112 ...
+##  $ a          : num  1.488 -0.218 0.423 0.545 0.406 ...
+\end{verbatim}
+
+\begin{noteblock}
+The full source code of the \emph{User Effect} computation is available
+in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R\#L531}{Model
+building: User Effect} section of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R}{capstone-movielens.main.R}
+script on \emph{GitHub}.
+
+\end{noteblock}
+
 Finally, we are ready to compute the \texttt{RMSE} (additionally using
-the helper function \texttt{clamp} we defined above to keep predictions
-in the proper range):
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Compute the RMSE taking into account user effects:}
-\NormalTok{user\_effects\_rmse }\OtherTok{\textless{}{-}}\NormalTok{ test\_set }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(a)), }\AttributeTok{a =}\NormalTok{ a), }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L4}{clamp}
+helper function we defined above to keep predictions in the proper
+range):
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{put\_log}\NormalTok{(}\StringTok{"Computing the RMSE taking into account user effects..."}\NormalTok{)}
+\NormalTok{start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
+\NormalTok{edx.user\_effect.MSEs }\OtherTok{\textless{}{-}} \FunctionTok{sapply}\NormalTok{(edx\_CV, }\ControlFlowTok{function}\NormalTok{(cv\_fold\_dat)\{}
+\NormalTok{  cv\_fold\_dat}\SpecialCharTok{$}\NormalTok{validation\_set }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{left\_join}\NormalTok{(edx.user\_effect, }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
     \FunctionTok{mutate}\NormalTok{(}\AttributeTok{resid =}\NormalTok{ rating }\SpecialCharTok{{-}} \FunctionTok{clamp}\NormalTok{(mu }\SpecialCharTok{+}\NormalTok{ a)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{filter}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(resid)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{pull}\NormalTok{(resid) }\SpecialCharTok{|\textgreater{}} \FunctionTok{rmse}\NormalTok{()}
-
-\FunctionTok{print}\NormalTok{(user\_effects\_rmse)}
-\end{Highlighting}
-\end{Shaded}
+    \FunctionTok{pull}\NormalTok{(resid) }\SpecialCharTok{|\textgreater{}} \FunctionTok{mse}\NormalTok{()}
+\NormalTok{\})}
+\FunctionTok{put\_end\_date}\NormalTok{(start)}
+
+\NormalTok{edx.user\_effect.RMSE }\OtherTok{\textless{}{-}} \FunctionTok{sqrt}\NormalTok{(}\FunctionTok{mean}\NormalTok{(edx.user\_effect.MSEs))}
+
+\NormalTok{RMSEs.ResultTibble.UE }\OtherTok{\textless{}{-}}\NormalTok{ RMSEs.ResultTibble.OMR }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{RMSEs.AddRow}\NormalTok{(}\StringTok{"User Effect Model"}\NormalTok{, edx.user\_effect.RMSE)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{fold\_No =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{, }\AttributeTok{MSE =}\NormalTok{ edx.user\_effect.MSEs) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{data.plot}\NormalTok{(}\AttributeTok{title =} \StringTok{"MSE resuls of the 5{-}fold CV method applied to the User Effect Model"}\NormalTok{,}
+            \AttributeTok{xname =} \StringTok{"fold\_No"}\NormalTok{, }
+            \AttributeTok{yname =} \StringTok{"MSE"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-62-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{RMSE\_kable}\NormalTok{(RMSEs.ResultTibble.UE)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{35em}>{\centering\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{50em}}
+\toprule
+\textbf{Method} & \textbf{RMSE} & \textbf{Comment}\\
+\midrule
+Project Objective & 0.8649000 & \\
+Overall Mean Rating Model & 1.0603462 & \\
+User Effect Model & 0.9697962 & \\
+\bottomrule
+\end{longtable}
+
+\begin{noteblock}
+The full source code of the \emph{User Effect Model RMSE} computation is
+available in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R\#L655}{Computing
+the RMSE taking into account User Effect} section of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R}{capstone-movielens.main.R}
+script on \emph{GitHub}.
+
+\end{noteblock}
 
@@
 \hfill\break
+
 In
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-56-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-72-1.pdf}
 

### 2025-05-08 reports/capstone-movielens-report.draft4.Rmd
Draft report updated.

@@
 
-### Taking into account User Effect
+### User Effect Model
 \
@@
 ::: {.noteblock data-latex=""}
-The full source code of the _User Effect Model RMSE_ computation is available in the [Computing the RMSE taking into account User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
 :::
 
-### Taking into account Movie effects
-\
-
-In [Section _23.5 Movie effects_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) the author draws our attention to the fact that some movies are generally rated higher than others.
+### User+Movie Effect (UME) Model
+\
+
+In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
 He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
@@
 
+Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
+
+#### UME Model: Support Functions
+\
+
+::: {.noteblock data-latex=""}
+The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
+:::
+
+##### `train_user_movie_effect` Function
+\
+
+We use this function to build and train our model using the `train_set` dataset:
+```{r eval=FALSE}
+train_user_movie_effect <- function(train_set, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_user_movie_effect
+`lambda` is `NA`")
+  }
+
+  UM.effect <- train_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    mutate(resid = rating - (mu + a)) |> 
+    group_by(movieId) |>
+    summarise(b = mean_reg(resid, lambda), n = n())
+
+  stopifnot(!is.na(mean(UM.effect$b)))
+  UM.effect
+}
+```
+
+::: {.noteblock data-latex=""}
+The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need for the *Regularization*.
+We will explain that later in the [Regularization Method] section. 
+For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the `mean_reg` function is equivalent to the simple `mean` one.
+:::
+
+```{r eval=FALSE}
+## Regularization --------------------------------------------------------------
+mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
+  if (is.na(lambda)) {
+    stop("Function: mean_reg
+`lambda` is `NA`")
+  }
+
+  names(lambda) <- NULL
+  sums <- sum(vals, na.rm = na.rm)
+  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
+  sums/(N + lambda)
+}
+```
+
+##### `train_user_movie_effect.cv` Function
+\
+
+We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method.
+Below, we provide the most important part of the code of that function:
+```{r eval=FALSE}
+train_user_movie_effect.cv <- function(lambda = 0){
+# ...
+  start <- put_start_date()
+  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
+    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
+  })
+  put_end_date(start)
+  put_log("Function: train_user_movie_effect.cv:
+User+Movie Effect list have been computed")
+
+  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
+
+  user_movie_effect <- user_movie_effects_united |>
+    group_by(movieId) |>
+    summarise(b = mean(b), n = mean(n))
+  # ...
+  user_movie_effect
+}
+
+```
+
+::: {.noteblock data-latex=""}
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the "cross-validation" results.
+:::
+```{r eval=FALSE}
+union_cv_results <- function(data_list) {
+  out_dat <- data_list[[1]]
+
+  for (i in 2:CVFolds_N){
+    out_dat <- union(out_dat, 
+                     data_list[[i]])
+  }
+
+  out_dat
+}
+```
+
+##### `calc_user_movie_effect_MSE` Function
+\
+
+The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `MSE` of the `UME Model` for the given `Test Set` is provided below:
+```{r eval=FALSE}
+calc_user_movie_effect_MSE <- function(test_set, um_effect){
+  mse.result <- test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(um_effect, by = "movieId") |>
+    mutate(resid = rating - clamp(mu + a + b)) |> 
+    pull(resid) |> mse()
+
+  stopifnot(!is.na(mse.result))
+  mse.result
+}
+```
+
+##### `calc_user_movie_effect_MSE.cv` Function
+\
+
+The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
+```{r eval=FALSE}
+calc_user_movie_effect_MSE.cv <- function(um_effect){
+  put_log("Function: user_movie_effects_MSE.cv:
+Computing the RMSE taking into account User+Movie Effects...")
+  start <- put_start_date()
+  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
+    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
+  })
+  put_end_date(start)
+
+  put_log1("Function: user_movie_effects_MSE.cv:
+MSE values have been plotted for the %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  mean(user_movie_effects_MSEs)
+}
+
+```
+
+##### `calc_user_movie_effect_RMSE` Function
+\
+
+The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `RMSE` of the `UME Model` for the given `Test Set` is provided below:
+
+```{r eval=FALSE}
+calc_user_movie_effect_RMSE <- function(test_set, um_effect){
+  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
+  sqrt(mse)
+}
+```
+
+##### `calc_user_movie_effect_RMSE.cv` Function
+\
+
+The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
+
+```{r eval=FALSE}
+calc_user_movie_effect_RMSE.cv <- function(um_effect){
+  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
+  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
+  put_log2("Function: user_movie_effects_RMSE.cv:
+%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
+  um_effect_RMSE
+}
+
+```
+
+#### Model Building
+\
+
+::: {.noteblock data-latex=""}
+The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+:::
+
+Below, we provide the most important code of the training our model using the `5-Fold Cross Validation` method:
+```{r eval=FALSE}
+  cv.UM_effect <- train_user_movie_effect.cv()
+```
+```{r}
+par(cex = 0.7)
+hist(cv.UM_effect$b, 30, xlab = TeX(r'[$\hat{beta}_{j}$)]'),
+     main = TeX(r'[Histogram of $\hat{beta}_{j}$]'))
+```
+
 We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
 ```{r eval=FALSE}
-user_and_movie_effects_rmse <- test_set |> 
-    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
-    left_join(data.frame(movieId = as.integer(names(b)), b = b), by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |>  
-    filter(!is.na(resid)) |>
-    pull(resid) |> rmse()
-
-print(user_and_movie_effects_rmse)
-```
+cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
+
+RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
+  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
+
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.UME)
+```
+
 ### Utilizing Penalized least squares
@@
 ```
+
+##### `` Function
+\
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+##### `` Function
+\
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+##### `` Function
+\
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
 ### Accounting for Date effects

### 2025-05-08 reports/capstone-movielens-report.draft4.tex
Draft report updated.

@@
 \author{Azamat Kurbanaev}
-\date{2025-05-08}
+\date{2025-05-09}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-20-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-23-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-14-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-24-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-27-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-18-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-28-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-47-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-38-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-52-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-43-1.pdf}
 
@@
 
-\subsubsection{Taking into account User
-Effect}\label{taking-into-account-user-effect}
+\subsubsection{User Effect Model}\label{user-effect-model}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-55-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-46-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-60-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-51-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-62-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-53-1.pdf}
 
@@
 available in the
-\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R\#L655}{Computing
-the RMSE taking into account User Effect} section of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R\#L655}{Compute
+RMSE for User Effect Model} section of the
 \href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R}{capstone-movielens.main.R}
@@
 
-\subsubsection{Taking into account Movie
-effects}\label{taking-into-account-movie-effects}
+\subsubsection{User+Movie Effect (UME)
+Model}\label{usermovie-effect-ume-model}
 
@@
 In
-\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movie-effects}{Section
-\emph{23.5 Movie effects} of the \emph{Course Textbook}} the author
-draws our attention to the fact that some movies are generally rated
-higher than others. He also explains that~a linear model with a
-\emph{treatment effect} \(\beta_j\) for each movie can be used in this
-case, which can be interpreted as movie effect or the difference between
-the average ranking for movie \(j\) and the overall average \(\mu\):
+\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movie-effects}{23.5
+Movie effects} section of the \emph{Course Textbook} the author draws
+our attention to the fact that some movies are generally rated higher
+than others. He also explains that a linear model with a \emph{treatment
+effect} \(\beta_j\) for each movie can be used in this case, which can
+be interpreted as movie effect or the difference between the average
+ranking for movie \(j\) and the overall average \(\mu\):
 
@@
 
+Inspired by this idea, a few support functions were developed by the
+author of this report, which we will use for our further analysis.
+
+\paragraph{UME Model: Support
+Functions}\label{ume-model-support-functions}
+
+\hfill\break
+
+\begin{noteblock}
+The full source code of the functions described in this section is
+available in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L1}{User+Movie
+Effect Model Functions} section of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
+script on \emph{GitHub}.
+
+\end{noteblock}
+
+\subparagraph{\texorpdfstring{\texttt{train\_user\_movie\_effect}
+Function}{train\_user\_movie\_effect Function}}\label{train_user_movie_effect-function}
+
+\hfill\break
+
+We use this function to build and train our model using the
+\texttt{train\_set} dataset:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{train\_user\_movie\_effect }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(train\_set, }\AttributeTok{lambda =} \DecValTok{0}\NormalTok{)\{}
+  \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{is.na}\NormalTok{(lambda)) \{}
+    \FunctionTok{stop}\NormalTok{(}\StringTok{"Function: train\_user\_movie\_effect}
+\StringTok{\textasciigrave{}lambda\textasciigrave{} is \textasciigrave{}NA\textasciigrave{}"}\NormalTok{)}
+\NormalTok{  \}}
+
+\NormalTok{  UM.effect }\OtherTok{\textless{}{-}}\NormalTok{ train\_set }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{left\_join}\NormalTok{(edx.user\_effect, }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{resid =}\NormalTok{ rating }\SpecialCharTok{{-}}\NormalTok{ (mu }\SpecialCharTok{+}\NormalTok{ a)) }\SpecialCharTok{|\textgreater{}} 
+    \FunctionTok{group\_by}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{b =} \FunctionTok{mean\_reg}\NormalTok{(resid, lambda), }\AttributeTok{n =} \FunctionTok{n}\NormalTok{())}
+
+  \FunctionTok{stopifnot}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(}\FunctionTok{mean}\NormalTok{(UM.effect}\SpecialCharTok{$}\NormalTok{b)))}
+\NormalTok{  UM.effect}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{noteblock}
+The function described above accepts the \texttt{lambda} parameter,
+which we will need later for the \emph{Regularization} method. We also
+use the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L63}{mean\_reg}
+function call, which we will also need for the \emph{Regularization}. We
+will explain that later in the {[}Regularization Method{]} section. For
+now, we omit the \texttt{lambda} parameter, accepting its default value
+\texttt{lambda\ =\ 0}. In this case, the \texttt{mean\_reg} function is
+equivalent to the simple \texttt{mean} one.
+
+\end{noteblock}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\DocumentationTok{\#\# Regularization {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
+\NormalTok{mean\_reg }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(vals, }\AttributeTok{lambda =} \DecValTok{0}\NormalTok{, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)\{}
+  \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{is.na}\NormalTok{(lambda)) \{}
+    \FunctionTok{stop}\NormalTok{(}\StringTok{"Function: mean\_reg}
+\StringTok{\textasciigrave{}lambda\textasciigrave{} is \textasciigrave{}NA\textasciigrave{}"}\NormalTok{)}
+\NormalTok{  \}}
+
+  \FunctionTok{names}\NormalTok{(lambda) }\OtherTok{\textless{}{-}} \ConstantTok{NULL}
+\NormalTok{  sums }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(vals, }\AttributeTok{na.rm =}\NormalTok{ na.rm)}
+\NormalTok{  N }\OtherTok{\textless{}{-}} \FunctionTok{ifelse}\NormalTok{(na.rm, }\FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(vals)), }\FunctionTok{length}\NormalTok{(vals))}
+\NormalTok{  sums}\SpecialCharTok{/}\NormalTok{(N }\SpecialCharTok{+}\NormalTok{ lambda)}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\subparagraph{\texorpdfstring{\texttt{train\_user\_movie\_effect.cv}
+Function}{train\_user\_movie\_effect.cv Function}}\label{train_user_movie_effect.cv-function}
+
+\hfill\break
+
+We use the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L17}{train\_user\_movie\_effect.cv}
+function to build and train our model using the
+\texttt{5-Fold\ Cross\ Validation} method. Below, we provide the most
+important part of the code of that function:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{train\_user\_movie\_effect.cv }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{lambda =} \DecValTok{0}\NormalTok{)\{}
+\CommentTok{\# ...}
+\NormalTok{  start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
+\NormalTok{  user\_movie\_effects\_ls }\OtherTok{\textless{}{-}} \FunctionTok{lapply}\NormalTok{(edx\_CV, }\ControlFlowTok{function}\NormalTok{(cv\_fold\_dat)\{}
+\NormalTok{    cv\_fold\_dat}\SpecialCharTok{$}\NormalTok{train\_set }\SpecialCharTok{|\textgreater{}} \FunctionTok{train\_user\_movie\_effect}\NormalTok{(lambda)}
+\NormalTok{  \})}
+  \FunctionTok{put\_end\_date}\NormalTok{(start)}
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: train\_user\_movie\_effect.cv:}
+\StringTok{User+Movie Effect list have been computed"}\NormalTok{)}
+
+\NormalTok{  user\_movie\_effects\_united }\OtherTok{\textless{}{-}} \FunctionTok{union\_cv\_results}\NormalTok{(user\_movie\_effects\_ls)}
+
+\NormalTok{  user\_movie\_effect }\OtherTok{\textless{}{-}}\NormalTok{ user\_movie\_effects\_united }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{group\_by}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{b =} \FunctionTok{mean}\NormalTok{(b), }\AttributeTok{n =} \FunctionTok{mean}\NormalTok{(n))}
+  \CommentTok{\# ...}
+\NormalTok{  user\_movie\_effect}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{noteblock}
+Here we use the function call
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R\#L432}{union\_cv\_results},
+which is defined in the script
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R}{common-helper.functions.R},
+to aggregate the ``cross-validation'' results.
+
+\end{noteblock}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{union\_cv\_results }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data\_list) \{}
+\NormalTok{  out\_dat }\OtherTok{\textless{}{-}}\NormalTok{ data\_list[[}\DecValTok{1}\NormalTok{]]}
+
+  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{2}\SpecialCharTok{:}\NormalTok{CVFolds\_N)\{}
+\NormalTok{    out\_dat }\OtherTok{\textless{}{-}} \FunctionTok{union}\NormalTok{(out\_dat, }
+\NormalTok{                     data\_list[[i]])}
+\NormalTok{  \}}
+
+\NormalTok{  out\_dat}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\subparagraph{\texorpdfstring{\texttt{calc\_user\_movie\_effect\_MSE}
+Function}{calc\_user\_movie\_effect\_MSE Function}}\label{calc_user_movie_effect_mse-function}
+
+\hfill\break
+
+The code of the function
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L55}{calc\_user\_movie\_effect\_MSE}
+defined in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
+script to calculate the \texttt{MSE} of the \texttt{UME\ Model} for the
+given \texttt{Test\ Set} is provided below:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{calc\_user\_movie\_effect\_MSE }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(test\_set, um\_effect)\{}
+\NormalTok{  mse.result }\OtherTok{\textless{}{-}}\NormalTok{ test\_set }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{left\_join}\NormalTok{(edx.user\_effect, }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{left\_join}\NormalTok{(um\_effect, }\AttributeTok{by =} \StringTok{"movieId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{resid =}\NormalTok{ rating }\SpecialCharTok{{-}} \FunctionTok{clamp}\NormalTok{(mu }\SpecialCharTok{+}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ b)) }\SpecialCharTok{|\textgreater{}}
+    \FunctionTok{pull}\NormalTok{(resid) }\SpecialCharTok{|\textgreater{}} \FunctionTok{mse}\NormalTok{()}
+
+  \FunctionTok{stopifnot}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(mse.result))}
+\NormalTok{  mse.result}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\subparagraph{\texorpdfstring{\texttt{calc\_user\_movie\_effect\_MSE.cv}
+Function}{calc\_user\_movie\_effect\_MSE.cv Function}}\label{calc_user_movie_effect_mse.cv-function}
+
+\hfill\break
+
+The code of the function
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L72}{calc\_user\_movie\_effect\_MSE.cv}
+defined in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
+script to calculate the \texttt{5-Fold\ Cross\ Validation} MSE result of
+the \texttt{UME\ Model} is provided below:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{calc\_user\_movie\_effect\_MSE.cv }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(um\_effect)\{}
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: user\_movie\_effects\_MSE.cv:}
+\StringTok{Computing the RMSE taking into account User+Movie Effects..."}\NormalTok{)}
+\NormalTok{  start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
+\NormalTok{  user\_movie\_effects\_MSEs }\OtherTok{\textless{}{-}} \FunctionTok{sapply}\NormalTok{(edx\_CV, }\ControlFlowTok{function}\NormalTok{(cv\_fold\_dat)\{}
+\NormalTok{    cv\_fold\_dat}\SpecialCharTok{$}\NormalTok{validation\_set }\SpecialCharTok{|\textgreater{}} \FunctionTok{calc\_user\_movie\_effect\_MSE}\NormalTok{(um\_effect)}
+\NormalTok{  \})}
+  \FunctionTok{put\_end\_date}\NormalTok{(start)}
+
+  \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: user\_movie\_effects\_MSE.cv:}
+\StringTok{MSE values have been plotted for the \%1{-}Fold Cross Validation samples."}\NormalTok{, }
+\NormalTok{           CVFolds\_N)}
+
+  \FunctionTok{mean}\NormalTok{(user\_movie\_effects\_MSEs)}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\subparagraph{\texorpdfstring{\texttt{calc\_user\_movie\_effect\_RMSE}
+Function}{calc\_user\_movie\_effect\_RMSE Function}}\label{calc_user_movie_effect_rmse-function}
+
+\hfill\break
+
+The code of the function
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L51}{calc\_user\_movie\_effect\_RMSE}
+defined in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
+script to calculate the \texttt{RMSE} of the \texttt{UME\ Model} for the
+given \texttt{Test\ Set} is provided below:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{calc\_user\_movie\_effect\_RMSE }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(test\_set, um\_effect)\{}
+\NormalTok{  mse }\OtherTok{\textless{}{-}}\NormalTok{ test\_set }\SpecialCharTok{|\textgreater{}} \FunctionTok{calc\_user\_movie\_effect\_MSE}\NormalTok{(um\_effect)}
+  \FunctionTok{sqrt}\NormalTok{(mse)}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\subparagraph{\texorpdfstring{\texttt{calc\_user\_movie\_effect\_RMSE.cv}
+Function}{calc\_user\_movie\_effect\_RMSE.cv Function}}\label{calc_user_movie_effect_rmse.cv-function}
+
+\hfill\break
+
+The code of the function
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L65}{calc\_user\_movie\_effect\_RMSE.cv}
+defined in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
+script to calculate the \texttt{5-Fold\ Cross\ Validation} RMSE result
+of the \texttt{UME\ Model} is provided below:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{calc\_user\_movie\_effect\_RMSE.cv }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(um\_effect)\{}
+\NormalTok{  user\_movie\_effects\_MSE }\OtherTok{\textless{}{-}} \FunctionTok{calc\_user\_movie\_effect\_MSE.cv}\NormalTok{(um\_effect)}
+\NormalTok{  um\_effect\_RMSE }\OtherTok{\textless{}{-}} \FunctionTok{sqrt}\NormalTok{(user\_movie\_effects\_MSE)}
+  \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function: user\_movie\_effects\_RMSE.cv:}
+\StringTok{\%1{-}Fold Cross Validation ultimate RMSE: \%2"}\NormalTok{, CVFolds\_N, um\_effect\_RMSE)}
+\NormalTok{  um\_effect\_RMSE}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\paragraph{Model Building}\label{model-building}
+
+\hfill\break
+
+\begin{noteblock}
+The full source code of builing and training the current model is
+available in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R\#L721}{Model
+building: User+Movie Effect} section of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R}{capstone-movielens.main.R}
+script on \emph{GitHub}.
+
+\end{noteblock}
+
+Below, we provide the most important code of the training our model
+using the \texttt{5-Fold\ Cross\ Validation} method:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{  cv.UM\_effect }\OtherTok{\textless{}{-}} \FunctionTok{train\_user\_movie\_effect.cv}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{par}\NormalTok{(}\AttributeTok{cex =} \FloatTok{0.7}\NormalTok{)}
+\FunctionTok{hist}\NormalTok{(cv.UM\_effect}\SpecialCharTok{$}\NormalTok{b, }\DecValTok{30}\NormalTok{, }\AttributeTok{xlab =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[$\textbackslash{}hat\{beta\}\_\{j\}$)]\textquotesingle{}}\NormalTok{),}
+     \AttributeTok{main =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[Histogram of $\textbackslash{}hat\{beta\}\_\{j\}$]\textquotesingle{}}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-64-1.pdf}
+
 We can now construct predictors and see how much the \texttt{RMSE}
@@
 \begin{Highlighting}[]
-\NormalTok{user\_and\_movie\_effects\_rmse }\OtherTok{\textless{}{-}}\NormalTok{ test\_set }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(a)), }\AttributeTok{a =}\NormalTok{ a), }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{movieId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(b)), }\AttributeTok{b =}\NormalTok{ b), }\AttributeTok{by =} \StringTok{"movieId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{resid =}\NormalTok{ rating }\SpecialCharTok{{-}} \FunctionTok{clamp}\NormalTok{(mu }\SpecialCharTok{+}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ b)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{filter}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(resid)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{pull}\NormalTok{(resid) }\SpecialCharTok{|\textgreater{}} \FunctionTok{rmse}\NormalTok{()}
-
-\FunctionTok{print}\NormalTok{(user\_and\_movie\_effects\_rmse)}
-\end{Highlighting}
-\end{Shaded}
+\NormalTok{cv.UM\_effect.RMSE }\OtherTok{\textless{}{-}} \FunctionTok{calc\_user\_movie\_effect\_RMSE.cv}\NormalTok{(cv.UM\_effect)}
+
+\NormalTok{RMSEs.ResultTibble.UME }\OtherTok{\textless{}{-}}\NormalTok{ RMSEs.ResultTibble.UE }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{RMSEs.AddRow}\NormalTok{(}\StringTok{"User+Movie Effect Model"}\NormalTok{, cv.UM\_effect.RMSE)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{RMSE\_kable}\NormalTok{(RMSEs.ResultTibble.UME)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{35em}>{\centering\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{50em}}
+\toprule
+\textbf{Method} & \textbf{RMSE} & \textbf{Comment}\\
+\midrule
+Project Objective & 0.8649000 & \\
+Overall Mean Rating Model & 1.0603462 & \\
+User Effect Model & 0.9697962 & \\
+User+Movie Effect Model & 0.8732081 & \\
+\bottomrule
+\end{longtable}
 
@@
 \end{Shaded}
+
+\subparagraph{`` Function}\label{function}
+
+\hfill\break
+
+\subparagraph{`` Function}\label{function-1}
+
+\hfill\break
+
+\subparagraph{`` Function}\label{function-2}
+
+\hfill\break
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-72-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-83-1.pdf}
 

### 2025-05-09 reports/capstone-movielens-report.draft4.Rmd
Draft report: documenting User+Movie Effect Model Regularization feature (in progress)

@@
 ::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the "cross-validation" results.
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the `Cross Validation` results.
 :::
@@
 
-The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `MSE` of the `UME Model` for the given `Test Set` is provided below:
+The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
 ```{r eval=FALSE}
@@
 
-The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `RMSE` of the `UME Model` for the given `Test Set` is provided below:
+The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
 
@@
 ```{r}
+str(cv.UM_effect)
+
 par(cex = 0.7)
@@
 
-### Utilizing Penalized least squares
+### Regularizing User+Movie Effect Model
+
+#### Utilizing Penalized least squares
 \
@@
 
-#### Support function
-\
-We will use the following function to calculate _RMSE_ in this section:
-```{r eval=FALSE}
-reg_rmse <- function(b){
-  test_set |> 
-    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
-    left_join(data.frame(movieId = as.integer(names(b)), b = b), by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    filter(!is.na(resid)) |>
-    pull(resid) |> rmse()
-}
-
-```
+We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
+
+  1. **Preconfiguration:** Preliminary determination of the optimal range of `lambda` values for the `5-Fold Cross Validation` samples;
+  2. **Fine-tuning:** figuring out the value of `lambda` that minimizes the model's RMSE.
+
+#### Regularization: Common Helper Functions
+\
+
+::: {.noteblock data-latex=""}
+The functions described below are defined in the [Model Tuning]() section of the [common-helper.functions.R]() script.
+:::
+
+##### `tune.model_param` Function
+\
+
+```{r eval=FALSE}
+}
+
+```
+
+##### `` Function
+\
+
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+##### `` Function
+\
+
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+##### `` Function
+\
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+#### UME Model Regularization: Support Function
+\
+
+::: {.noteblock data-latex=""}
+The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+
+##### `regularize.test_lambda.UM_effect.cv` Function
+\
+
+This function calculates the _RMSE_ for the given $\lambda$ parameter value:
+```{r eval=FALSE}
+regularize.test_lambda.UM_effect.cv <- function(lambda){
+  if (is.na(lambda)) {
+    stop("Function: regularize.test_lambda.UM_effect.cv
+`lambda` is `NA`")
+  }
+  um_effect <- train_user_movie_effect.cv(lambda)
+  calc_user_movie_effect_RMSE.cv(um_effect)
+}
+```
+
+::: {.noteblock data-latex=""}
+Note that we reuse the function [train_user_movie_effect.cv]() calling it from the [regularize.test_lambda.UM_effect.cv](), but now with the $\lambda$ parameter different from the default (zero) value.
+:::
 
@@
 reg_rmse(b_reg)
-```
-
-##### `` Function
-\
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-##### `` Function
-\
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-##### `` Function
-\
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
 ```

### 2025-05-09 reports/capstone-movielens-report.draft4.tex
Draft report: documenting User+Movie Effect Model Regularization feature (in progress)

@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-20-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-38-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-39-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-43-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-44-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-46-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-47-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-51-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-52-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-53-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-54-1.pdf}
 
@@
 \href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R}{common-helper.functions.R},
-to aggregate the ``cross-validation'' results.
+to aggregate the \texttt{Cross\ Validation} results.
 
@@
 \href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
-script to calculate the \texttt{MSE} of the \texttt{UME\ Model} for the
-given \texttt{Test\ Set} is provided below:
+script to calculate the \texttt{Mean\ Squared\ Error\ (MSE)} of the
+\texttt{UME\ Model} for the given \texttt{Test\ Set} is provided below:
 
@@
 \href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
-script to calculate the \texttt{RMSE} of the \texttt{UME\ Model} for the
-given \texttt{Test\ Set} is provided below:
+script to calculate the \texttt{Root\ Mean\ Squared\ Error\ (RMSE)} of
+the \texttt{UME\ Model} for the given \texttt{Test\ Set} is provided
+below:
 
@@
 \begin{Highlighting}[]
+\FunctionTok{str}\NormalTok{(cv.UM\_effect)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## tibble [10,677 x 3] (S3: tbl_df/tbl/data.frame)
+##  $ movieId: int [1:10677] 1 2 3 4 5 6 7 8 9 10 ...
+##  $ b      : num [1:10677] 0.335 -0.306 -0.365 -0.598 -0.444 ...
+##  $ n      : num [1:10677] 18907 8593 5574 1253 5065 ...
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
 \FunctionTok{par}\NormalTok{(}\AttributeTok{cex =} \FloatTok{0.7}\NormalTok{)}
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-64-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-65-1.pdf}
 
@@
 
-\subsubsection{Utilizing Penalized least
+\subsubsection{Regularizing User+Movie Effect
+Model}\label{regularizing-usermovie-effect-model}
+
+\paragraph{Utilizing Penalized least
 squares}\label{utilizing-penalized-least-squares}
@@
 
-\paragraph{Support function}\label{support-function}
-
-\hfill\break
-We will use the following function to calculate \emph{RMSE} in this
-section:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{reg\_rmse }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(b)\{}
-\NormalTok{  test\_set }\SpecialCharTok{|\textgreater{}} 
-    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(a)), }\AttributeTok{a =}\NormalTok{ a), }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{movieId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(b)), }\AttributeTok{b =}\NormalTok{ b), }\AttributeTok{by =} \StringTok{"movieId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{resid =}\NormalTok{ rating }\SpecialCharTok{{-}} \FunctionTok{clamp}\NormalTok{(mu }\SpecialCharTok{+}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ b)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{filter}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(resid)) }\SpecialCharTok{|\textgreater{}}
-    \FunctionTok{pull}\NormalTok{(resid) }\SpecialCharTok{|\textgreater{}} \FunctionTok{rmse}\NormalTok{()}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
+We will implement the \emph{Regularization} method on our models
+(starting from the current model) in two steps:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  \textbf{Preconfiguration:} Preliminary determination of the optimal
+  range of \texttt{lambda} values for the
+  \texttt{5-Fold\ Cross\ Validation} samples;
+\item
+  \textbf{Fine-tuning:} figuring out the value of \texttt{lambda} that
+  minimizes the model's RMSE.
+\end{enumerate}
+
+\paragraph{Regularization: Common Helper
+Functions}\label{regularization-common-helper-functions}
+
+\hfill\break
+
+\begin{noteblock}
+The functions described below are defined in the \href{}{Model Tuning}
+section of the \href{}{common-helper.functions.R} script.
+
+\end{noteblock}
+
+\subparagraph{\texorpdfstring{\texttt{tune.model\_param}
+Function}{tune.model\_param Function}}\label{tune.model_param-function}
+
+\hfill\break
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\ErrorTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\subparagraph{`` Function}\label{function}
+
+\hfill\break
+
+\begin{noteblock}
+!!! Note!
+
+\end{noteblock}
+
+\subparagraph{`` Function}\label{function-1}
+
+\hfill\break
+
+\begin{noteblock}
+!!! Note!
+
+\end{noteblock}
+
+\begin{noteblock}
+!!! Note!
+
+\end{noteblock}
+
+\begin{noteblock}
+!!! Note!
+
+\end{noteblock}
+
+\subparagraph{`` Function}\label{function-2}
+
+\hfill\break
+
+\paragraph{UME Model Regularization: Support
+Function}\label{ume-model-regularization-support-function}
+
+\hfill\break
+
+\begin{noteblock}
+The \href{}{regularize.test\_lambda.UM\_effect.cv} function described
+below are defined in the \href{}{Regularization} section of the
+\href{}{UM-effect.functions.R} script.
+
+\end{noteblock}
+
+\subparagraph{\texorpdfstring{\texttt{regularize.test\_lambda.UM\_effect.cv}
+Function}{regularize.test\_lambda.UM\_effect.cv Function}}\label{regularize.test_lambda.um_effect.cv-function}
+
+\hfill\break
+
+This function calculates the \emph{RMSE} for the given \(\lambda\)
+parameter value:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{regularize.test\_lambda.UM\_effect.cv }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(lambda)\{}
+  \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{is.na}\NormalTok{(lambda)) \{}
+    \FunctionTok{stop}\NormalTok{(}\StringTok{"Function: regularize.test\_lambda.UM\_effect.cv}
+\StringTok{\textasciigrave{}lambda\textasciigrave{} is \textasciigrave{}NA\textasciigrave{}"}\NormalTok{)}
+\NormalTok{  \}}
+\NormalTok{  um\_effect }\OtherTok{\textless{}{-}} \FunctionTok{train\_user\_movie\_effect.cv}\NormalTok{(lambda)}
+  \FunctionTok{calc\_user\_movie\_effect\_RMSE.cv}\NormalTok{(um\_effect)}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{noteblock}
+Note that we reuse the function \href{}{train\_user\_movie\_effect.cv}
+calling it from the \href{}{regularize.test\_lambda.UM\_effect.cv}, but
+now with the \(\lambda\) parameter different from the default (zero)
+value.
+
+\end{noteblock}
 
@@
 \end{Shaded}
-
-\subparagraph{`` Function}\label{function}
-
-\hfill\break
-
-\subparagraph{`` Function}\label{function-1}
-
-\hfill\break
-
-\subparagraph{`` Function}\label{function-2}
-
-\hfill\break
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-83-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-85-1.pdf}
 

### 2025-05-09 reports/capstone-movielens-report.draft4.Rmd
Report updated: UME Model Regularization feature.

@@
 
-  1. **Preconfiguration:** Preliminary determination of the optimal range of `lambda` values for the `5-Fold Cross Validation` samples;
-  2. **Fine-tuning:** figuring out the value of `lambda` that minimizes the model's RMSE.
+  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
+  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
 
@@
 ```{r eval=FALSE}
+tune.model_param <- function(param_values, 
+                             fn_tune.test.param_value, 
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+  n <- length(param_values)
+  param_vals_tmp <- numeric()
+  RMSEs_tmp <- numeric()
+  RMSE_min <- Inf
+  i_max.beyond_RMSE_min <- Inf
+  prm_val.best <- NA
+
+  put_log("Function: `tune.model_param`:
+param_values:")
+  put(param_values)
+
+  for (i in 1:n) {
+    put_log1("Function: `tune.model_param`:
+Iteration %1", i)
+    prm_val <- param_values[i]
+    put_log1("Function: `tune.model_param`:
+prm_val: %1", prm_val)
+    param_vals_tmp[i] <- prm_val
+
+    put_log2("Function: `tune.model_param`:
+param_vals_tmp[%1]: %2", i, param_vals_tmp[i])
+    put_log1("Function: `tune.model_param`:
+param_vals_tmp length: %1", length(param_vals_tmp))
+    put(param_vals_tmp)
+
+    RMSE_tmp <- fn_tune.test.param_value(prm_val)
+
+    put_log1("Function: `tune.model_param`:
+RMSE_tmp: %1", RMSE_tmp)
+    RMSEs_tmp[i] <- RMSE_tmp
+
+    put_log2("Function: `tune.model_param`:
+RMSEs_tmp[%1]: %2", i, RMSEs_tmp[i])
+    put_log1("Function: `tune.model_param`:
+RMSEs_tmp length: %1", length(RMSEs_tmp))
+    put(RMSEs_tmp)
+
+    plot(param_vals_tmp[RMSEs_tmp > 0], RMSEs_tmp[RMSEs_tmp > 0])
+    # browser()
+
+    if(RMSE_tmp > RMSE_min){
+      warning("Function: `tune.model_param`:
+`RSME` reached its minimum: ", RMSE_min, "
+for parameter value: ", prm_val)
+      put_log2("Function: `tune.model_param`:
+Current `RMSE` value is %1 related to parameter value: %2",
+               RMSE_tmp,
+               prm_val)
+
+      if (i > i_max.beyond_RMSE_min) {
+        warning("Function: `tune.model_param`:
+Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
+        # browser()
+        break
+      }
+      # browser()
+      next
+    }
+
+    RMSE_min <- RMSE_tmp
+    prm_val.best <- prm_val
+
+    if (break.if_min) {
+      i_max.beyond_RMSE_min <- i + steps.beyond_min
+    }
+    # browser()
+  }
+
+  param_values.best_result <- c(param.best_value = prm_val.best, 
+                                best_RMSE = RMSE_min)
+
+  put_log1("Function: `tune.model_param`:
+Completed with RMSEs_tmp length: %1", length(RMSEs_tmp))
+  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
+                                parameter.value = param_vals_tmp),
+       best_result = param_values.best_result)
 }
@@
 
-This function calculates the _RMSE_ for the given $\lambda$ parameter value:
+This function calculates _RMSE_ of the _UME Model_ using _5-Fold CV_ method for the given $\lambda$ parameter value:
 ```{r eval=FALSE}

### 2025-05-09 reports/capstone-movielens-report.draft4.tex
Report updated: UME Model Regularization feature.

@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-12-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-14-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-39-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-38-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-44-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-43-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-47-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-46-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-52-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-51-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-54-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-53-1.pdf}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-65-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-64-1.pdf}
 
@@
   \textbf{Preconfiguration:} Preliminary determination of the optimal
-  range of \texttt{lambda} values for the
-  \texttt{5-Fold\ Cross\ Validation} samples;
+  range of \(\lambda\) values for the \texttt{5-Fold\ Cross\ Validation}
+  samples;
 \item
-  \textbf{Fine-tuning:} figuring out the value of \texttt{lambda} that
+  \textbf{Fine-tuning:} figuring out the value of \(\lambda\) that
   minimizes the model's RMSE.
@@
 \begin{Highlighting}[]
-\ErrorTok{\}}
+\NormalTok{tune.model\_param }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(param\_values, }
+\NormalTok{                             fn\_tune.test.param\_value, }
+                             \AttributeTok{break.if\_min =} \ConstantTok{TRUE}\NormalTok{,}
+                             \AttributeTok{steps.beyond\_min =} \DecValTok{2}\NormalTok{)\{}
+\NormalTok{  n }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(param\_values)}
+\NormalTok{  param\_vals\_tmp }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{()}
+\NormalTok{  RMSEs\_tmp }\OtherTok{\textless{}{-}} \FunctionTok{numeric}\NormalTok{()}
+\NormalTok{  RMSE\_min }\OtherTok{\textless{}{-}} \ConstantTok{Inf}
+\NormalTok{  i\_max.beyond\_RMSE\_min }\OtherTok{\textless{}{-}} \ConstantTok{Inf}
+\NormalTok{  prm\_val.best }\OtherTok{\textless{}{-}} \ConstantTok{NA}
+
+  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{param\_values:"}\NormalTok{)}
+  \FunctionTok{put}\NormalTok{(param\_values)}
+
+  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{n) \{}
+    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{Iteration \%1"}\NormalTok{, i)}
+\NormalTok{    prm\_val }\OtherTok{\textless{}{-}}\NormalTok{ param\_values[i]}
+    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{prm\_val: \%1"}\NormalTok{, prm\_val)}
+\NormalTok{    param\_vals\_tmp[i] }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val}
+
+    \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{param\_vals\_tmp[\%1]: \%2"}\NormalTok{, i, param\_vals\_tmp[i])}
+    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{param\_vals\_tmp length: \%1"}\NormalTok{, }\FunctionTok{length}\NormalTok{(param\_vals\_tmp))}
+    \FunctionTok{put}\NormalTok{(param\_vals\_tmp)}
+
+\NormalTok{    RMSE\_tmp }\OtherTok{\textless{}{-}} \FunctionTok{fn\_tune.test.param\_value}\NormalTok{(prm\_val)}
+
+    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{RMSE\_tmp: \%1"}\NormalTok{, RMSE\_tmp)}
+\NormalTok{    RMSEs\_tmp[i] }\OtherTok{\textless{}{-}}\NormalTok{ RMSE\_tmp}
+
+    \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{RMSEs\_tmp[\%1]: \%2"}\NormalTok{, i, RMSEs\_tmp[i])}
+    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{RMSEs\_tmp length: \%1"}\NormalTok{, }\FunctionTok{length}\NormalTok{(RMSEs\_tmp))}
+    \FunctionTok{put}\NormalTok{(RMSEs\_tmp)}
+
+    \FunctionTok{plot}\NormalTok{(param\_vals\_tmp[RMSEs\_tmp }\SpecialCharTok{\textgreater{}} \DecValTok{0}\NormalTok{], RMSEs\_tmp[RMSEs\_tmp }\SpecialCharTok{\textgreater{}} \DecValTok{0}\NormalTok{])}
+    \CommentTok{\# browser()}
+
+    \ControlFlowTok{if}\NormalTok{(RMSE\_tmp }\SpecialCharTok{\textgreater{}}\NormalTok{ RMSE\_min)\{}
+      \FunctionTok{warning}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{\textasciigrave{}RSME\textasciigrave{} reached its minimum: "}\NormalTok{, RMSE\_min, }\StringTok{"}
+\StringTok{for parameter value: "}\NormalTok{, prm\_val)}
+      \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{Current \textasciigrave{}RMSE\textasciigrave{} value is \%1 related to parameter value: \%2"}\NormalTok{,}
+\NormalTok{               RMSE\_tmp,}
+\NormalTok{               prm\_val)}
+
+      \ControlFlowTok{if}\NormalTok{ (i }\SpecialCharTok{\textgreater{}}\NormalTok{ i\_max.beyond\_RMSE\_min) \{}
+        \FunctionTok{warning}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{Operation is breaked (after \textasciigrave{}RSME\textasciigrave{} reached its minimum) on the following step: "}\NormalTok{, i)}
+        \CommentTok{\# browser()}
+        \ControlFlowTok{break}
+\NormalTok{      \}}
+      \CommentTok{\# browser()}
+      \ControlFlowTok{next}
+\NormalTok{    \}}
+
+\NormalTok{    RMSE\_min }\OtherTok{\textless{}{-}}\NormalTok{ RMSE\_tmp}
+\NormalTok{    prm\_val.best }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val}
+
+    \ControlFlowTok{if}\NormalTok{ (break.if\_min) \{}
+\NormalTok{      i\_max.beyond\_RMSE\_min }\OtherTok{\textless{}{-}}\NormalTok{ i }\SpecialCharTok{+}\NormalTok{ steps.beyond\_min}
+\NormalTok{    \}}
+    \CommentTok{\# browser()}
+\NormalTok{  \}}
+
+\NormalTok{  param\_values.best\_result }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\AttributeTok{param.best\_value =}\NormalTok{ prm\_val.best, }
+                                \AttributeTok{best\_RMSE =}\NormalTok{ RMSE\_min)}
+
+  \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
+\StringTok{Completed with RMSEs\_tmp length: \%1"}\NormalTok{, }\FunctionTok{length}\NormalTok{(RMSEs\_tmp))}
+  \FunctionTok{list}\NormalTok{(}\AttributeTok{tuned.result =} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{RMSE =}\NormalTok{ RMSEs\_tmp,}
+                                \AttributeTok{parameter.value =}\NormalTok{ param\_vals\_tmp),}
+       \AttributeTok{best\_result =}\NormalTok{ param\_values.best\_result)}
+\NormalTok{\}}
 \end{Highlighting}
@@
 
-This function calculates the \emph{RMSE} for the given \(\lambda\)
-parameter value:
+This function calculates \emph{RMSE} of the \emph{UME Model} using
+\emph{5-Fold CV} method for the given \(\lambda\) parameter value:
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-85-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-84-1.pdf}
 

### 2025-05-10 reports/capstone-movielens-report.draft4.Rmd
Reportupdate: `tune.model_param` function described.

--- 2025-05-09 reports/capstone-movielens-report.draft4.Rmd
@@
 
-Below, we provide the most important code of the training our model using the `5-Fold Cross Validation` method:
+Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
 ```{r eval=FALSE}
@@
 
-  1. **Preconfiguration:** Preliminary determination of the optimal range of `lambda` values for the `5-Fold Cross Validation` samples;
-  2. **Fine-tuning:** figuring out the value of `lambda` that minimizes the model's RMSE.
+  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
+
+  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
 
@@
 ::: {.noteblock data-latex=""}
-The functions described below are defined in the [Model Tuning]() section of the [common-helper.functions.R]() script.
-:::
-
-##### `tune.model_param` Function
-\
-
-```{r eval=FALSE}
-}
-
-```
+The full source code of the functions described below are are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+:::
+
+##### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function
+\
+
+Below is the most significant part of the code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
+```{r eval=FALSE}
+tune.model_param <- function(param_values, 
+                             fn_tune.test.param_value, 
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+  n <- length(param_values)
+  param_vals_tmp <- numeric()
+  RMSEs_tmp <- numeric()
+  RMSE_min <- Inf
+  i_max.beyond_RMSE_min <- Inf
+  prm_val.best <- NA
+
+  # ...
+
+  for (i in 1:n) {
+    put_log1("Function: `tune.model_param`:
+Iteration %1", i)
+    prm_val <- param_values[i]
+    param_vals_tmp[i] <- prm_val
+
+    RMSE_tmp <- fn_tune.test.param_value(prm_val)
+    RMSEs_tmp[i] <- RMSE_tmp
+
+    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
+
+    if(RMSE_tmp > RMSE_min){
+      warning("Function: `tune.model_param`:
+`RSME` reached its minimum: ", RMSE_min, "
+for parameter value: ", prm_val)
+      put_log2("Function: `tune.model_param`:
+Current `RMSE` value is %1 related to parameter value: %2",
+               RMSE_tmp,
+               prm_val)
+
+      if (i > i_max.beyond_RMSE_min) {
+        warning("Function: `tune.model_param`:
+Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
+        break
+      }
+      next
+    }
+
+    RMSE_min <- RMSE_tmp
+    prm_val.best <- prm_val
+
+    if (break.if_min) {
+      i_max.beyond_RMSE_min <- i + steps.beyond_min
+    }
+  }
+
+  param_values.best_result <- c(param.best_value = prm_val.best, 
+                                best_RMSE = RMSE_min)
+
+  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
+                                parameter.value = param_vals_tmp),
+       best_result = param_values.best_result)
+}
+
+```
+
+###### Parameters
+\
+
+**param_values:**; 
+**fn_tune.test.param_value:**; 
+**break.if_min = TRUE:**;
+**steps.beyond_min = 2:**:.
+
+  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
+  - **fn_tune.test.param_value:** A function that calculates the value of the `RMSE` for a given parameter value.; 
+  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
+
+###### Details
+\
+
+The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
+During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
+
+::: {.noteblock data-latex=""}
+Note that the function assumes that the dependence of the mean square error on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
+That is, it is assumed to have a unique minimum in the domain of definition.
+:::
+
+###### Value
+\
+
+The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values.
 
@@
 
-```{r eval=FALSE}
-
-```
-
+##### `` Function
+\
+
+##### `` Function
+\
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
 ::: {.noteblock data-latex=""}

### 2025-05-10 reports/capstone-movielens-report.draft4.tex
PDF doc updated.

@@
 \author{Azamat Kurbanaev}
-\date{2025-05-09}
+\date{2025-05-10}
 
@@
 
-Below, we provide the most important code of the training our model
-using the \texttt{5-Fold\ Cross\ Validation} method:
+Below, we provide the most significant part of the code for training our
+model using the \texttt{5-Fold\ Cross\ Validation} method:
 
@@
 \def\labelenumi{\arabic{enumi}.}
-\tightlist
 \item
@@
 \begin{noteblock}
-The functions described below are defined in the \href{}{Model Tuning}
-section of the \href{}{common-helper.functions.R} script.
+The full source code of the functions described below are are available
+in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L74}{Model
+Tuning} section of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R}{common-helper.functions.R}
+script on \emph{GitHub}.
 
@@
 
-\subparagraph{\texorpdfstring{\texttt{tune.model\_param}
+\subparagraph{\texorpdfstring{\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
 Function}{tune.model\_param Function}}\label{tune.model_param-function}
@@
 \hfill\break
+
+Below is the most significant part of the code of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
+function:
 
@@
 
-  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
-\StringTok{param\_values:"}\NormalTok{)}
-  \FunctionTok{put}\NormalTok{(param\_values)}
+  \CommentTok{\# ...}
 
@@
 \NormalTok{    prm\_val }\OtherTok{\textless{}{-}}\NormalTok{ param\_values[i]}
-    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
-\StringTok{prm\_val: \%1"}\NormalTok{, prm\_val)}
 \NormalTok{    param\_vals\_tmp[i] }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val}
 
-    \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
-\StringTok{param\_vals\_tmp[\%1]: \%2"}\NormalTok{, i, param\_vals\_tmp[i])}
-    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
-\StringTok{param\_vals\_tmp length: \%1"}\NormalTok{, }\FunctionTok{length}\NormalTok{(param\_vals\_tmp))}
-    \FunctionTok{put}\NormalTok{(param\_vals\_tmp)}
-
 \NormalTok{    RMSE\_tmp }\OtherTok{\textless{}{-}} \FunctionTok{fn\_tune.test.param\_value}\NormalTok{(prm\_val)}
-
-    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
-\StringTok{RMSE\_tmp: \%1"}\NormalTok{, RMSE\_tmp)}
 \NormalTok{    RMSEs\_tmp[i] }\OtherTok{\textless{}{-}}\NormalTok{ RMSE\_tmp}
 
-    \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
-\StringTok{RMSEs\_tmp[\%1]: \%2"}\NormalTok{, i, RMSEs\_tmp[i])}
-    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
-\StringTok{RMSEs\_tmp length: \%1"}\NormalTok{, }\FunctionTok{length}\NormalTok{(RMSEs\_tmp))}
-    \FunctionTok{put}\NormalTok{(RMSEs\_tmp)}
-
-    \FunctionTok{plot}\NormalTok{(param\_vals\_tmp[RMSEs\_tmp }\SpecialCharTok{\textgreater{}} \DecValTok{0}\NormalTok{], RMSEs\_tmp[RMSEs\_tmp }\SpecialCharTok{\textgreater{}} \DecValTok{0}\NormalTok{])}
-    \CommentTok{\# browser()}
+    \FunctionTok{plot}\NormalTok{(param\_vals\_tmp[RMSEs\_tmp], RMSEs\_tmp[RMSEs\_tmp])}
 
@@
 \StringTok{Operation is breaked (after \textasciigrave{}RSME\textasciigrave{} reached its minimum) on the following step: "}\NormalTok{, i)}
-        \CommentTok{\# browser()}
         \ControlFlowTok{break}
 \NormalTok{      \}}
-      \CommentTok{\# browser()}
       \ControlFlowTok{next}
@@
 \NormalTok{    \}}
-    \CommentTok{\# browser()}
 \NormalTok{  \}}
@@
 
-  \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: \textasciigrave{}tune.model\_param\textasciigrave{}:}
-\StringTok{Completed with RMSEs\_tmp length: \%1"}\NormalTok{, }\FunctionTok{length}\NormalTok{(RMSEs\_tmp))}
   \FunctionTok{list}\NormalTok{(}\AttributeTok{tuned.result =} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{RMSE =}\NormalTok{ RMSEs\_tmp,}
@@
 
+Parameters
+
+\hfill\break
+
+\textbf{param\_values:}; \textbf{fn\_tune.test.param\_value:};
+\textbf{break.if\_min = TRUE:}; \textbf{steps.beyond\_min = 2:}:.
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{param\_values:} A list of values to search for the value
+  corresponding to the minimum value of the \texttt{RMSE} ;
+\item
+  \textbf{fn\_tune.test.param\_value:} A function that calculates the
+  value of the \texttt{RMSE} for a given parameter value.;
+\item
+  \textbf{break.if\_min = TRUE:} A Boolean parameter that determines
+  whether the function should terminate after completing the number of
+  steps specified by the parameter \texttt{steps.beyond\_min}, after the
+  minimum value of the \texttt{RMSE} has been found;
+\item
+  \textbf{steps.beyond\_min = 2:} (takes effect only if
+  \texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the
+  number of steps after finding the minimum value of the \texttt{RMSE},
+  upon completion of which the function should terminate.
+\end{itemize}
+
+Details
+
+\hfill\break
+
+The function searches for the parameter value corresponding to the
+minimum value of the \texttt{RMSE} from the list of values specified by
+the \texttt{param\_values} parameter. During execution, the function
+uses a helper function specified by the
+\texttt{fn\_tune.test.param\_value} parameter, which calculates the
+\texttt{RMSE} value for the given parameter from the list determined by
+the \texttt{param\_values} parameter.
+
+\begin{noteblock}
+Note that the function assumes that the dependence of the mean square
+error on the input parameter is a monotonically decreasing function
+until a minimum is reached and monotonically increasing thereafter. That
+is, it is assumed to have a unique minimum in the domain of definition.
+
+\end{noteblock}
+
+Value
+
+\hfill\break
+
+The function returns a data structure containing the found value of the
+input parameter \texttt{param\_values} for which the \texttt{RMSE} value
+is minimal, as well as the minimum \texttt{RMSE} value itself, along
+with a sequence of all calculated \texttt{RMSE} values.
+
 \subparagraph{`` Function}\label{function}
+
+\hfill\break
+
+\subparagraph{`` Function}\label{function-1}
+
+\hfill\break
+
+\subparagraph{`` Function}\label{function-2}
 
@@
 
-\subparagraph{`` Function}\label{function-1}
+\subparagraph{`` Function}\label{function-3}
 
@@
 
-\subparagraph{`` Function}\label{function-2}
+\subparagraph{`` Function}\label{function-4}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-84-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-86-1.pdf}
 

### 2025-05-10 reports/capstone-movielens-report.draft4.Rmd
Draft report updated: describing a function `model.tune.param_range` (in progress)

@@
 ::: {.noteblock data-latex=""}
-The full source code of the functions described below are are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
 :::
@@
 
+The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
+
+###### Sugnature
+\
+```{r eval=FALSE}
+tune.model_param <- function(param_values, 
+                             fn_tune.test.param_value, 
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+
+# ...
+  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
+                                parameter.value = param_vals_tmp),
+       best_result = param_values.best_result)
+}  
+```
+
+###### Parameters
+\
+  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
+  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
+  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
+
+###### Details
+\
+During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
+
+::: {.noteblock data-latex=""}
+Note that the function assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
+That is, it is assumed to have a single minimum in the domain of definition.
+:::
+
+###### Value
+\
+The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values.
+
+###### Source Code
+\
 Below is the most significant part of the code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
@@
 
+##### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function
+\
+
+The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
+
+###### Sugnature
+\
+```{r eval=FALSE}
+model.tune.param_range <- function(loop_starter,
+                             tune_dir_path,
+                             cache_file_base_name,
+                             fn_tune.test.param_value,
+                             max.identical.min_RMSE.count = 4,
+                             is.cv = TRUE,
+                             endpoint.min_diff = 0, #1e-07,
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+  # ...
+  list(best_result = param_values.best_result,
+       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
+       tuned.result = data.frame(parameter.value = parameter.value,
+                                 RMSE = result.RMSE))
+}
+```
+
 ###### Parameters
 \
-
-**param_values:**; 
-**fn_tune.test.param_value:**; 
-**break.if_min = TRUE:**;
-**steps.beyond_min = 2:**:.
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
-  - **fn_tune.test.param_value:** A function that calculates the value of the `RMSE` for a given parameter value.; 
+  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
   - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
@@
 \
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
+During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+
+###### Value
+\
+
+###### Source Code
+\
+Below is the most significant part of the code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
+```{r eval=FALSE}
+model.tune.param_range <- function(loop_starter,
+                             tune_dir_path,
+                             cache_file_base_name,
+                             fn_tune.test.param_value,
+                             max.identical.min_RMSE.count = 4,
+                             is.cv = TRUE,
+                             endpoint.min_diff = 0, #1e-07,
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+
+  seq_start <- loop_starter[1]
+  seq_end <- loop_starter[2]
+  range_divider <- loop_starter[3]
+
+  if (range_divider < 4) {
+    range_divider <- 4
+  }
+
+  prm_val.leftmost <- seq_start
+  prm_val.rightmost <- seq_end
+
+  RMSE.leftmost <- NA
+  RMSE.rightmost <- NA
+
+  best_RMSE <- NA
+  param.best_value <- 0
+
+  param_values.best_result <- c(param.best_value = param.best_value, 
+                                best_RMSE = best_RMSE)
+
+  repeat{
+    seq_increment <- (seq_end - seq_start)/range_divider
+
+    if (seq_increment < 0.0000000000001) {
+      warning("Function `model.tune.param_range`:
+parameter value increment is too small.")
+
+      put_log2("Function `model.tune.param_range`:
+Final best RMSE for `parameter value = %1`: %2",
+               param_values.best_result["param.best_value"],
+               param_values.best_result["best_RMSE"])
+      break
+    }
+
+    test_param_vals <- seq(seq_start, seq_end, seq_increment)
+
+    file_name_tmp <- cache_file_base_name |>
+      str_c("_") |>
+      str_c(as.character(loop_starter[1])) |>
+      str_c("_") |>
+      str_c(as.character(loop_starter[3])) |>
+      str_c("_") |>
+      str_c(as.character(range_divider)) |>
+      str_c(".") |>
+      str_c(as.character(seq_start)) |>
+      str_c("-") |>
+      str_c(as.character(seq_end)) |>
+      str_c(".RData")
+
+    file_path_tmp <- file.path(tune_dir_path, file_name_tmp)
+
+    put_log1("Function `model.tune.param_range`:
+File path generated: %1", file_path_tmp)
+
+    if (file.exists(file_path_tmp)) {
+      put_log1("Function `model.tune.param_range`:
+Loading tuning data from file: %1...", file_path_tmp)
+
+      start <- put_start_date()
+      load(file_path_tmp)
+      put_end_date(start)
+      put_log1("Function `model.tune.param_range`:
+Tuning data has been loaded from file: %1", file_path_tmp)
+
+      tuned.result <- tuned_result$tuned.result
+
+      if(length(file_path_tmp) > 0) {
+      }
+    } else {
+      tuned_result <- tune.model_param(test_param_vals, 
+                                        fn_tune.test.param_value,
+                                        break.if_min,
+                                        steps.beyond_min)
+
+      tuned.result <- tuned_result$tuned.result
+
+      save(tuned_result,
+           param.best_value,
+           seq_increment,
+           range_divider,
+           file = file_path_tmp)
+
+      put_log1("Function `model.tune.param_range`:
+File saved: %1", file_path_tmp)
+    }
+
+    plot(tuned.result$parameter.value, tuned.result$RMSE)
+
+    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
+    start.idx <- bound.idx["start"]
+    end.idx <- bound.idx["end"]
+    best_RMSE.idx <- bound.idx["best"]
+
+    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
+    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
+
+    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
+    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
+
+    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
+    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
+
+    seq_start <- prm_val.leftmost.tmp
+    seq_end <- prm_val.rightmost.tmp
+
+    if (is.na(best_RMSE)) {
+      prm_val.leftmost <- prm_val.leftmost.tmp
+      RMSE.leftmost <- RMSE.leftmost.tmp
+
+      prm_val.rightmost <- prm_val.rightmost.tmp
+      RMSE.rightmost <- RMSE.rightmost.tmp
+
+      param.best_value <- min_RMSE.prm_val
+      best_RMSE <- min_RMSE
+    }
+
+    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
+      prm_val.leftmost <- prm_val.leftmost.tmp
+      RMSE.leftmost <- RMSE.leftmost.tmp
+    }
+
+    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
+      prm_val.rightmost <- prm_val.rightmost.tmp
+      RMSE.rightmost <- RMSE.rightmost.tmp
+    }
+
+    if (end.idx - start.idx <= 0) {
+      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
+      break
+    }
+
+    if (best_RMSE == min_RMSE) {
+      warning("Currently computed minimal RMSE equals the previously reached best one: ",
+              best_RMSE, "
+Currently computed minial value is: ", min_RMSE)
+
+      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
+        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
+                max.identical.min_RMSE.count)
+
+        param_values.best_result <-
+          get_best_param.result(tuned.result$parameter.value,
+                                tuned.result$RMSE)
+
+        put_log2("Function `model.tune.param_range`:
+      Reached the best RMSE for `parameter value = %1`: %2",
+                 param_values.best_result["param.best_value"],
+                 param_values.best_result["best_RMSE"])
+        break
+      }
+
+    } else if (best_RMSE < min_RMSE) {
+      stop("Current minimal RMSE is greater than previously computed best value: ",
+           best_RMSE, "
+Currently computed minial value is: ", min_RMSE)
+    }
+
+    best_RMSE <- min_RMSE
+    param.best_value <- min_RMSE.prm_val
+
+    param_values.best_result <- 
+      get_best_param.result(tuned.result$parameter.value, 
+                          tuned.result$RMSE)
+
+    put_log2("Function `model.tune.param_range`:
+Currently reached best RMSE for `parameter value = %1`: %2",
+             param_values.best_result["param.best_value"],
+             param_values.best_result["best_RMSE"])
+  }
+
+  n <- length(tuned.result$parameter.value)
+  parameter.value <- tuned.result$parameter.value
+  result.RMSE <- tuned.result$RMSE
+
+  if (result.RMSE[1] == best_RMSE) {
+    parameter.value[1] <- prm_val.leftmost
+    result.RMSE[1] <- RMSE.leftmost
+  }
+  if (result.RMSE[n] == best_RMSE) {
+    parameter.value[n+1] <- prm_val.rightmost
+    result.RMSE[n+1] <- RMSE.rightmost
+    # browser()
+  }
+
+  list(best_result = param_values.best_result,
+       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
+       tuned.result = data.frame(parameter.value = parameter.value,
+                                 RMSE = result.RMSE))
+}
+```
+
+##### `` Function
+\
+
+###### Sugnature
+\
+```{r eval=FALSE}
+
+```
+
+###### Parameters
+\
+  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
+  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
+
+###### Details
+\
 During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
@@
 ::: {.noteblock data-latex=""}
-Note that the function assumes that the dependence of the mean square error on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed to have a unique minimum in the domain of definition.
+Note 
 :::
@@
 
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values.
+###### Source Code
+\
+Below is the most significant part of the code of the [function]() function:
+```{r eval=FALSE}
+
+```
 
@@
 
+###### Sugnature
+\
+```{r eval=FALSE}
+
+```
+
+###### Parameters
+\
+  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
+  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
+
+###### Details
+\
+During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+
+###### Value
+\
+
+###### Source Code
+\
+Below is the most significant part of the code of the [function]() function:
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
 ##### `` Function
@@
 
+###### Sugnature
+\
+```{r eval=FALSE}
+
+```
+
+###### Parameters
+\
+  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
+  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
+
+###### Details
+\
+During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+
+###### Value
+\
+
+###### Source Code
+\
+Below is the most significant part of the code of the [function]() function:
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
 ##### `` Function
@@
 
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-##### `` Function
-\
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-##### `` Function
-\
+###### Sugnature
+\
+```{r eval=FALSE}
+
+```
+
+###### Parameters
+\
+  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
+  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
+
+###### Details
+\
+During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+
+###### Value
+\
+
+###### Source Code
+\
+Below is the most significant part of the code of the [function]() function:
+```{r eval=FALSE}
+
+```
 

### 2025-05-10 reports/capstone-movielens-report.draft4.tex
Draft report updated: describing a function `model.tune.param_range` (in progress)

@@
 \begin{noteblock}
-The full source code of the functions described below are are available
-in the
+The full source code of the functions described below are available in
+the
 \href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L74}{Model
@@
 
+The function searches for the parameter value corresponding to the
+minimum value of the \texttt{RMSE} from the list of values specified by
+the \texttt{param\_values} parameter.
+
+Sugnature
+
+\hfill\break
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{tune.model\_param }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(param\_values, }
+\NormalTok{                             fn\_tune.test.param\_value, }
+                             \AttributeTok{break.if\_min =} \ConstantTok{TRUE}\NormalTok{,}
+                             \AttributeTok{steps.beyond\_min =} \DecValTok{2}\NormalTok{)\{}
+
+\CommentTok{\# ...}
+  \FunctionTok{list}\NormalTok{(}\AttributeTok{tuned.result =} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{RMSE =}\NormalTok{ RMSEs\_tmp,}
+                                \AttributeTok{parameter.value =}\NormalTok{ param\_vals\_tmp),}
+       \AttributeTok{best\_result =}\NormalTok{ param\_values.best\_result)}
+\NormalTok{\}  }
+\end{Highlighting}
+\end{Shaded}
+
+Parameters
+
+\hfill\break
+- \textbf{param\_values:} A list of values to search for the value
+corresponding to the minimum value of the \texttt{RMSE} ; -
+\textbf{fn\_tune.test.param\_value:} A helper function that calculates
+the value of the \texttt{RMSE} for a given parameter value.; -
+\textbf{break.if\_min = TRUE:} A Boolean parameter that determines
+whether the function should terminate after completing the number of
+steps specified by the parameter \texttt{steps.beyond\_min}, after the
+minimum value of the \texttt{RMSE} has been found; -
+\textbf{steps.beyond\_min = 2:} (takes effect only if
+\texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the number
+of steps after finding the minimum value of the \texttt{RMSE}, upon
+completion of which the function should terminate.
+
+Details
+
+\hfill\break
+During execution, the function uses a helper function specified by the
+\texttt{fn\_tune.test.param\_value} parameter, which calculates the
+\texttt{RMSE} value for the given parameter from the list determined by
+the \texttt{param\_values} parameter.
+
+\begin{noteblock}
+Note that the function assumes that the dependence of the \texttt{RMSE}
+on the input parameter is a monotonically decreasing function until a
+minimum is reached and monotonically increasing thereafter. That is, it
+is assumed to have a single minimum in the domain of definition.
+
+\end{noteblock}
+
+Value
+
+\hfill\break
+The function returns a data structure containing the found value of the
+input parameter \texttt{param\_values} for which the \texttt{RMSE} value
+is minimal, as well as the minimum \texttt{RMSE} value itself, along
+with a sequence of all calculated \texttt{RMSE} values.
+
+Source Code
+
+\hfill\break
 Below is the most significant part of the code of the
@@
 
+\subparagraph{\texorpdfstring{\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L198}{model.tune.param\_range}
+Function}{model.tune.param\_range Function}}\label{model.tune.param_range-function}
+
+\hfill\break
+
+The function fine-tunes the model by searching for the best possible
+value of the input parameter over a given interval for which the
+corresponding \texttt{RMSE} value is minimal.
+
+Sugnature
+
+\hfill\break
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{model.tune.param\_range }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(loop\_starter,}
+\NormalTok{                             tune\_dir\_path,}
+\NormalTok{                             cache\_file\_base\_name,}
+\NormalTok{                             fn\_tune.test.param\_value,}
+                             \AttributeTok{max.identical.min\_RMSE.count =} \DecValTok{4}\NormalTok{,}
+                             \AttributeTok{is.cv =} \ConstantTok{TRUE}\NormalTok{,}
+                             \AttributeTok{endpoint.min\_diff =} \DecValTok{0}\NormalTok{, }\CommentTok{\#1e{-}07,}
+                             \AttributeTok{break.if\_min =} \ConstantTok{TRUE}\NormalTok{,}
+                             \AttributeTok{steps.beyond\_min =} \DecValTok{2}\NormalTok{)\{}
+  \CommentTok{\# ...}
+  \FunctionTok{list}\NormalTok{(}\AttributeTok{best\_result =}\NormalTok{ param\_values.best\_result,}
+       \AttributeTok{param\_values.endpoints =} \FunctionTok{c}\NormalTok{(prm\_val.leftmost, prm\_val.rightmost, seq\_increment),}
+       \AttributeTok{tuned.result =} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{parameter.value =}\NormalTok{ parameter.value,}
+                                 \AttributeTok{RMSE =}\NormalTok{ result.RMSE))}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
 Parameters
@@
 \hfill\break
-
-\textbf{param\_values:}; \textbf{fn\_tune.test.param\_value:};
-\textbf{break.if\_min = TRUE:}; \textbf{steps.beyond\_min = 2:}:.
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{param\_values:} A list of values to search for the value
-  corresponding to the minimum value of the \texttt{RMSE} ;
-\item
-  \textbf{fn\_tune.test.param\_value:} A function that calculates the
-  value of the \texttt{RMSE} for a given parameter value.;
-\item
+- \textbf{fn\_tune.test.param\_value:} A helper function that calculates
+the value of the \texttt{RMSE} for a given parameter value.; -
 \textbf{break.if\_min = TRUE:} A Boolean parameter that determines
@@
 steps specified by the parameter \texttt{steps.beyond\_min}, after the
-  minimum value of the \texttt{RMSE} has been found;
-\item
+minimum value of the \texttt{RMSE} has been found; -
 \textbf{steps.beyond\_min = 2:} (takes effect only if
-  \texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the
-  number of steps after finding the minimum value of the \texttt{RMSE},
-  upon completion of which the function should terminate.
-\end{itemize}
+\texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the number
+of steps after finding the minimum value of the \texttt{RMSE}, upon
+completion of which the function should terminate.
 
@@
 \hfill\break
-
-The function searches for the parameter value corresponding to the
-minimum value of the \texttt{RMSE} from the list of values specified by
-the \texttt{param\_values} parameter. During execution, the function
-uses a helper function specified by the
+During execution, the function uses a helper function specified by the
+\texttt{fn\_tune.test.param\_value} parameter, which calculates the
+\texttt{RMSE} value for the given parameter from the list determined by
+the inner \texttt{param\_values} sequence.
+
+\begin{noteblock}
+Note
+
+\end{noteblock}
+
+Value
+
+\hfill\break
+
+Source Code
+
+\hfill\break
+Below is the most significant part of the code of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L198}{model.tune.param\_range}
+function:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{model.tune.param\_range }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(loop\_starter,}
+\NormalTok{                             tune\_dir\_path,}
+\NormalTok{                             cache\_file\_base\_name,}
+\NormalTok{                             fn\_tune.test.param\_value,}
+                             \AttributeTok{max.identical.min\_RMSE.count =} \DecValTok{4}\NormalTok{,}
+                             \AttributeTok{is.cv =} \ConstantTok{TRUE}\NormalTok{,}
+                             \AttributeTok{endpoint.min\_diff =} \DecValTok{0}\NormalTok{, }\CommentTok{\#1e{-}07,}
+                             \AttributeTok{break.if\_min =} \ConstantTok{TRUE}\NormalTok{,}
+                             \AttributeTok{steps.beyond\_min =} \DecValTok{2}\NormalTok{)\{}
+
+\NormalTok{  seq\_start }\OtherTok{\textless{}{-}}\NormalTok{ loop\_starter[}\DecValTok{1}\NormalTok{]}
+\NormalTok{  seq\_end }\OtherTok{\textless{}{-}}\NormalTok{ loop\_starter[}\DecValTok{2}\NormalTok{]}
+\NormalTok{  range\_divider }\OtherTok{\textless{}{-}}\NormalTok{ loop\_starter[}\DecValTok{3}\NormalTok{]}
+
+  \ControlFlowTok{if}\NormalTok{ (range\_divider }\SpecialCharTok{\textless{}} \DecValTok{4}\NormalTok{) \{}
+\NormalTok{    range\_divider }\OtherTok{\textless{}{-}} \DecValTok{4}
+\NormalTok{  \}}
+
+\NormalTok{  prm\_val.leftmost }\OtherTok{\textless{}{-}}\NormalTok{ seq\_start}
+\NormalTok{  prm\_val.rightmost }\OtherTok{\textless{}{-}}\NormalTok{ seq\_end}
+
+\NormalTok{  RMSE.leftmost }\OtherTok{\textless{}{-}} \ConstantTok{NA}
+\NormalTok{  RMSE.rightmost }\OtherTok{\textless{}{-}} \ConstantTok{NA}
+
+\NormalTok{  best\_RMSE }\OtherTok{\textless{}{-}} \ConstantTok{NA}
+\NormalTok{  param.best\_value }\OtherTok{\textless{}{-}} \DecValTok{0}
+
+\NormalTok{  param\_values.best\_result }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\AttributeTok{param.best\_value =}\NormalTok{ param.best\_value, }
+                                \AttributeTok{best\_RMSE =}\NormalTok{ best\_RMSE)}
+
+  \ControlFlowTok{repeat}\NormalTok{\{}
+\NormalTok{    seq\_increment }\OtherTok{\textless{}{-}}\NormalTok{ (seq\_end }\SpecialCharTok{{-}}\NormalTok{ seq\_start)}\SpecialCharTok{/}\NormalTok{range\_divider }
+
+    \ControlFlowTok{if}\NormalTok{ (seq\_increment }\SpecialCharTok{\textless{}} \FloatTok{0.0000000000001}\NormalTok{) \{}
+      \FunctionTok{warning}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
+\StringTok{parameter value increment is too small."}\NormalTok{)}
+
+      \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
+\StringTok{Final best RMSE for \textasciigrave{}parameter value = \%1\textasciigrave{}: \%2"}\NormalTok{,}
+\NormalTok{               param\_values.best\_result[}\StringTok{"param.best\_value"}\NormalTok{],}
+\NormalTok{               param\_values.best\_result[}\StringTok{"best\_RMSE"}\NormalTok{])}
+      \ControlFlowTok{break}
+\NormalTok{    \}}
+
+\NormalTok{    test\_param\_vals }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(seq\_start, seq\_end, seq\_increment)}
+
+\NormalTok{    file\_name\_tmp }\OtherTok{\textless{}{-}}\NormalTok{ cache\_file\_base\_name }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"\_"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(loop\_starter[}\DecValTok{1}\NormalTok{])) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"\_"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(loop\_starter[}\DecValTok{3}\NormalTok{])) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"\_"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(range\_divider)) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"."}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(seq\_start)) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"{-}"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(seq\_end)) }\SpecialCharTok{|\textgreater{}}
+      \FunctionTok{str\_c}\NormalTok{(}\StringTok{".RData"}\NormalTok{)}
+
+\NormalTok{    file\_path\_tmp }\OtherTok{\textless{}{-}} \FunctionTok{file.path}\NormalTok{(tune\_dir\_path, file\_name\_tmp)}
+
+    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
+\StringTok{File path generated: \%1"}\NormalTok{, file\_path\_tmp)}
+
+    \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{file.exists}\NormalTok{(file\_path\_tmp)) \{}
+      \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
+\StringTok{Loading tuning data from file: \%1..."}\NormalTok{, file\_path\_tmp)}
+
+\NormalTok{      start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
+      \FunctionTok{load}\NormalTok{(file\_path\_tmp)}
+      \FunctionTok{put\_end\_date}\NormalTok{(start)}
+      \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
+\StringTok{Tuning data has been loaded from file: \%1"}\NormalTok{, file\_path\_tmp)}
+
+\NormalTok{      tuned.result }\OtherTok{\textless{}{-}}\NormalTok{ tuned\_result}\SpecialCharTok{$}\NormalTok{tuned.result}
+
+      \ControlFlowTok{if}\NormalTok{(}\FunctionTok{length}\NormalTok{(file\_path\_tmp) }\SpecialCharTok{\textgreater{}} \DecValTok{0}\NormalTok{) \{}
+\NormalTok{      \}}
+\NormalTok{    \} }\ControlFlowTok{else}\NormalTok{ \{}
+\NormalTok{      tuned\_result }\OtherTok{\textless{}{-}} \FunctionTok{tune.model\_param}\NormalTok{(test\_param\_vals, }
+\NormalTok{                                        fn\_tune.test.param\_value,}
+\NormalTok{                                        break.if\_min,}
+\NormalTok{                                        steps.beyond\_min)}
+
+\NormalTok{      tuned.result }\OtherTok{\textless{}{-}}\NormalTok{ tuned\_result}\SpecialCharTok{$}\NormalTok{tuned.result}
+
+      \FunctionTok{save}\NormalTok{(tuned\_result,}
+\NormalTok{           param.best\_value,}
+\NormalTok{           seq\_increment,}
+\NormalTok{           range\_divider,}
+           \AttributeTok{file =}\NormalTok{ file\_path\_tmp)}
+
+      \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
+\StringTok{File saved: \%1"}\NormalTok{, file\_path\_tmp)}
+\NormalTok{    \}}
+
+    \FunctionTok{plot}\NormalTok{(tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value, tuned.result}\SpecialCharTok{$}\NormalTok{RMSE)}
+
+\NormalTok{    bound.idx }\OtherTok{\textless{}{-}} \FunctionTok{get\_fine\_tune.param.endpoints.idx}\NormalTok{(tuned.result)}
+\NormalTok{    start.idx }\OtherTok{\textless{}{-}}\NormalTok{ bound.idx[}\StringTok{"start"}\NormalTok{]}
+\NormalTok{    end.idx }\OtherTok{\textless{}{-}}\NormalTok{ bound.idx[}\StringTok{"end"}\NormalTok{]}
+\NormalTok{    best\_RMSE.idx }\OtherTok{\textless{}{-}}\NormalTok{ bound.idx[}\StringTok{"best"}\NormalTok{]}
+
+\NormalTok{    prm\_val.leftmost.tmp }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value[start.idx]}
+\NormalTok{    RMSE.leftmost.tmp }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{RMSE[start.idx]}
+
+\NormalTok{    prm\_val.rightmost.tmp }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value[end.idx]}
+\NormalTok{    RMSE.rightmost.tmp }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{RMSE[end.idx]}
+
+\NormalTok{    min\_RMSE }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{RMSE[best\_RMSE.idx]}
+\NormalTok{    min\_RMSE.prm\_val }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value[best\_RMSE.idx]}
+
+\NormalTok{    seq\_start }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.leftmost.tmp}
+\NormalTok{    seq\_end }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.rightmost.tmp}
+
+    \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{is.na}\NormalTok{(best\_RMSE)) \{}
+\NormalTok{      prm\_val.leftmost }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.leftmost.tmp}
+\NormalTok{      RMSE.leftmost }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.leftmost.tmp}
+
+\NormalTok{      prm\_val.rightmost }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.rightmost.tmp}
+\NormalTok{      RMSE.rightmost }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.rightmost.tmp}
+
+\NormalTok{      param.best\_value }\OtherTok{\textless{}{-}}\NormalTok{ min\_RMSE.prm\_val}
+\NormalTok{      best\_RMSE }\OtherTok{\textless{}{-}}\NormalTok{ min\_RMSE}
+\NormalTok{    \}}
+
+    \ControlFlowTok{if}\NormalTok{ (RMSE.leftmost.tmp }\SpecialCharTok{{-}}\NormalTok{ min\_RMSE }\SpecialCharTok{\textgreater{}=}\NormalTok{ endpoint.min\_diff) \{}
+\NormalTok{      prm\_val.leftmost }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.leftmost.tmp}
+\NormalTok{      RMSE.leftmost }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.leftmost.tmp}
+\NormalTok{    \} }
+
+    \ControlFlowTok{if}\NormalTok{ (RMSE.rightmost.tmp }\SpecialCharTok{{-}}\NormalTok{ min\_RMSE }\SpecialCharTok{\textgreater{}=}\NormalTok{ endpoint.min\_diff) \{}
+\NormalTok{      prm\_val.rightmost }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.rightmost.tmp}
+\NormalTok{      RMSE.rightmost }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.rightmost.tmp}
+\NormalTok{    \} }
+
+    \ControlFlowTok{if}\NormalTok{ (end.idx }\SpecialCharTok{{-}}\NormalTok{ start.idx }\SpecialCharTok{\textless{}=} \DecValTok{0}\NormalTok{) \{}
+      \FunctionTok{warning}\NormalTok{(}\StringTok{"\textasciigrave{}tuned.result$parameter.value\textasciigrave{} sequential start index are the same or greater than end one."}\NormalTok{)}
+      \ControlFlowTok{break}
+\NormalTok{    \}}
+
+    \ControlFlowTok{if}\NormalTok{ (best\_RMSE }\SpecialCharTok{==}\NormalTok{ min\_RMSE) \{}
+      \FunctionTok{warning}\NormalTok{(}\StringTok{"Currently computed minimal RMSE equals the previously reached best one: "}\NormalTok{,}
+\NormalTok{              best\_RMSE, }\StringTok{"}
+\StringTok{Currently computed minial value is: "}\NormalTok{, min\_RMSE)}
+
+      \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{sum}\NormalTok{(tuned.result}\SpecialCharTok{$}\NormalTok{RMSE[tuned.result}\SpecialCharTok{$}\NormalTok{RMSE }\SpecialCharTok{==}\NormalTok{ min\_RMSE]) }\SpecialCharTok{\textgreater{}=}\NormalTok{ max.identical.min\_RMSE.count) \{}
+        \FunctionTok{warning}\NormalTok{(}\StringTok{"Minimal \textasciigrave{}RMSE\textasciigrave{}identical values count reached it maximum allowed value: "}\NormalTok{,}
+\NormalTok{                max.identical.min\_RMSE.count)}
+
+\NormalTok{        param\_values.best\_result }\OtherTok{\textless{}{-}}
+          \FunctionTok{get\_best\_param.result}\NormalTok{(tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value,}
+\NormalTok{                                tuned.result}\SpecialCharTok{$}\NormalTok{RMSE)}
+
+        \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
+\StringTok{      Reached the best RMSE for \textasciigrave{}parameter value = \%1\textasciigrave{}: \%2"}\NormalTok{,}
+\NormalTok{                 param\_values.best\_result[}\StringTok{"param.best\_value"}\NormalTok{],}
+\NormalTok{                 param\_values.best\_result[}\StringTok{"best\_RMSE"}\NormalTok{])}
+        \ControlFlowTok{break}
+\NormalTok{      \}}
+
+\NormalTok{    \} }\ControlFlowTok{else} \ControlFlowTok{if}\NormalTok{ (best\_RMSE }\SpecialCharTok{\textless{}}\NormalTok{ min\_RMSE) \{}
+      \FunctionTok{stop}\NormalTok{(}\StringTok{"Current minimal RMSE is greater than previously computed best value: "}\NormalTok{,}
+\NormalTok{           best\_RMSE, }\StringTok{"}
+\StringTok{Currently computed minial value is: "}\NormalTok{, min\_RMSE)}
+\NormalTok{    \}}
+
+\NormalTok{    best\_RMSE }\OtherTok{\textless{}{-}}\NormalTok{ min\_RMSE}
+\NormalTok{    param.best\_value }\OtherTok{\textless{}{-}}\NormalTok{ min\_RMSE.prm\_val}
+
+\NormalTok{    param\_values.best\_result }\OtherTok{\textless{}{-}} 
+      \FunctionTok{get\_best\_param.result}\NormalTok{(tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value, }
+\NormalTok{                          tuned.result}\SpecialCharTok{$}\NormalTok{RMSE)}
+
+    \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
+\StringTok{Currently reached best RMSE for \textasciigrave{}parameter value = \%1\textasciigrave{}: \%2"}\NormalTok{,}
+\NormalTok{             param\_values.best\_result[}\StringTok{"param.best\_value"}\NormalTok{],}
+\NormalTok{             param\_values.best\_result[}\StringTok{"best\_RMSE"}\NormalTok{])}
+\NormalTok{  \}}
+
+\NormalTok{  n }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value)}
+\NormalTok{  parameter.value }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value}
+\NormalTok{  result.RMSE }\OtherTok{\textless{}{-}}\NormalTok{ tuned.result}\SpecialCharTok{$}\NormalTok{RMSE}
+
+  \ControlFlowTok{if}\NormalTok{ (result.RMSE[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{==}\NormalTok{ best\_RMSE) \{}
+\NormalTok{    parameter.value[}\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.leftmost}
+\NormalTok{    result.RMSE[}\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.leftmost}
+\NormalTok{  \}}
+  \ControlFlowTok{if}\NormalTok{ (result.RMSE[n] }\SpecialCharTok{==}\NormalTok{ best\_RMSE) \{}
+\NormalTok{    parameter.value[n}\SpecialCharTok{+}\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ prm\_val.rightmost}
+\NormalTok{    result.RMSE[n}\SpecialCharTok{+}\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ RMSE.rightmost}
+    \CommentTok{\# browser()}
+\NormalTok{  \}}
+
+  \FunctionTok{list}\NormalTok{(}\AttributeTok{best\_result =}\NormalTok{ param\_values.best\_result,}
+       \AttributeTok{param\_values.endpoints =} \FunctionTok{c}\NormalTok{(prm\_val.leftmost, prm\_val.rightmost, seq\_increment),}
+       \AttributeTok{tuned.result =} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{parameter.value =}\NormalTok{ parameter.value,}
+                                 \AttributeTok{RMSE =}\NormalTok{ result.RMSE))}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\subparagraph{`` Function}\label{function}
+
+\hfill\break
+
+Sugnature
+
+\hfill\break
+
+Parameters
+
+\hfill\break
+- \textbf{fn\_tune.test.param\_value:} A helper function that calculates
+the value of the \texttt{RMSE} for a given parameter value.; -
+\textbf{break.if\_min = TRUE:} A Boolean parameter that determines
+whether the function should terminate after completing the number of
+steps specified by the parameter \texttt{steps.beyond\_min}, after the
+minimum value of the \texttt{RMSE} has been found; -
+\textbf{steps.beyond\_min = 2:} (takes effect only if
+\texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the number
+of steps after finding the minimum value of the \texttt{RMSE}, upon
+completion of which the function should terminate.
+
+Details
+
+\hfill\break
+During execution, the function uses a helper function specified by the
 \texttt{fn\_tune.test.param\_value} parameter, which calculates the
@@
 \begin{noteblock}
-Note that the function assumes that the dependence of the mean square
-error on the input parameter is a monotonically decreasing function
-until a minimum is reached and monotonically increasing thereafter. That
-is, it is assumed to have a unique minimum in the domain of definition.
+Note
 
@@
 
-The function returns a data structure containing the found value of the
-input parameter \texttt{param\_values} for which the \texttt{RMSE} value
-is minimal, as well as the minimum \texttt{RMSE} value itself, along
-with a sequence of all calculated \texttt{RMSE} values.
-
-\subparagraph{`` Function}\label{function}
-
-\hfill\break
+Source Code
+
+\hfill\break
+Below is the most significant part of the code of the \href{}{function}
+function:
 
@@
 
-\subparagraph{`` Function}\label{function-2}
-
-\hfill\break
+Sugnature
+
+\hfill\break
+
+Parameters
+
+\hfill\break
+- \textbf{fn\_tune.test.param\_value:} A helper function that calculates
+the value of the \texttt{RMSE} for a given parameter value.; -
+\textbf{break.if\_min = TRUE:} A Boolean parameter that determines
+whether the function should terminate after completing the number of
+steps specified by the parameter \texttt{steps.beyond\_min}, after the
+minimum value of the \texttt{RMSE} has been found; -
+\textbf{steps.beyond\_min = 2:} (takes effect only if
+\texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the number
+of steps after finding the minimum value of the \texttt{RMSE}, upon
+completion of which the function should terminate.
+
+Details
+
+\hfill\break
+During execution, the function uses a helper function specified by the
+\texttt{fn\_tune.test.param\_value} parameter, which calculates the
+\texttt{RMSE} value for the given parameter from the list determined by
+the \texttt{param\_values} parameter.
+
+\begin{noteblock}
+Note
+
+\end{noteblock}
+
+Value
+
+\hfill\break
+
+Source Code
+
+\hfill\break
+Below is the most significant part of the code of the \href{}{function}
+function:
 
@@
 
-\subparagraph{`` Function}\label{function-3}
-
-\hfill\break
+\subparagraph{`` Function}\label{function-2}
+
+\hfill\break
+
+Sugnature
+
+\hfill\break
+
+Parameters
+
+\hfill\break
+- \textbf{fn\_tune.test.param\_value:} A helper function that calculates
+the value of the \texttt{RMSE} for a given parameter value.; -
+\textbf{break.if\_min = TRUE:} A Boolean parameter that determines
+whether the function should terminate after completing the number of
+steps specified by the parameter \texttt{steps.beyond\_min}, after the
+minimum value of the \texttt{RMSE} has been found; -
+\textbf{steps.beyond\_min = 2:} (takes effect only if
+\texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the number
+of steps after finding the minimum value of the \texttt{RMSE}, upon
+completion of which the function should terminate.
+
+Details
+
+\hfill\break
+During execution, the function uses a helper function specified by the
+\texttt{fn\_tune.test.param\_value} parameter, which calculates the
+\texttt{RMSE} value for the given parameter from the list determined by
+the \texttt{param\_values} parameter.
+
+\begin{noteblock}
+Note
+
+\end{noteblock}
+
+Value
+
+\hfill\break
+
+Source Code
+
+\hfill\break
+Below is the most significant part of the code of the \href{}{function}
+function:
 
@@
 
-\subparagraph{`` Function}\label{function-4}
-
-\hfill\break
+\subparagraph{`` Function}\label{function-3}
+
+\hfill\break
+
+Sugnature
+
+\hfill\break
+
+Parameters
+
+\hfill\break
+- \textbf{fn\_tune.test.param\_value:} A helper function that calculates
+the value of the \texttt{RMSE} for a given parameter value.; -
+\textbf{break.if\_min = TRUE:} A Boolean parameter that determines
+whether the function should terminate after completing the number of
+steps specified by the parameter \texttt{steps.beyond\_min}, after the
+minimum value of the \texttt{RMSE} has been found; -
+\textbf{steps.beyond\_min = 2:} (takes effect only if
+\texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the number
+of steps after finding the minimum value of the \texttt{RMSE}, upon
+completion of which the function should terminate.
+
+Details
+
+\hfill\break
+During execution, the function uses a helper function specified by the
+\texttt{fn\_tune.test.param\_value} parameter, which calculates the
+\texttt{RMSE} value for the given parameter from the list determined by
+the \texttt{param\_values} parameter.
+
+\begin{noteblock}
+Note
+
+\end{noteblock}
+
+Value
+
+\hfill\break
+
+Source Code
+
+\hfill\break
+Below is the most significant part of the code of the \href{}{function}
+function:
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-86-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-95-1.pdf}
 

### 2025-05-10 reports/capstone-movielens-report.draft4.Rmd
Draft report development:  function `model.tune.param_range` (in progress)

@@
 \
+
   - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
@@
 \
+
   - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
@@
                                 best_RMSE = best_RMSE)
-
+  # Start repeat loop
   repeat{
@@
 parameter value increment is too small.")
-
-      put_log2("Function `model.tune.param_range`:
-Final best RMSE for `parameter value = %1`: %2",
-               param_values.best_result["param.best_value"],
-               param_values.best_result["best_RMSE"])
       break
@@
 
-    file_name_tmp <- cache_file_base_name |>
-      str_c("_") |>
-      str_c(as.character(loop_starter[1])) |>
-      str_c("_") |>
-      str_c(as.character(loop_starter[3])) |>
-      str_c("_") |>
-      str_c(as.character(range_divider)) |>
-      str_c(".") |>
-      str_c(as.character(seq_start)) |>
-      str_c("-") |>
-      str_c(as.character(seq_end)) |>
-      str_c(".RData")
-
-    file_path_tmp <- file.path(tune_dir_path, file_name_tmp)
-
-    put_log1("Function `model.tune.param_range`:
-File path generated: %1", file_path_tmp)
-
-    if (file.exists(file_path_tmp)) {
-      put_log1("Function `model.tune.param_range`:
-Loading tuning data from file: %1...", file_path_tmp)
-
-      start <- put_start_date()
-      load(file_path_tmp)
-      put_end_date(start)
-      put_log1("Function `model.tune.param_range`:
-Tuning data has been loaded from file: %1", file_path_tmp)
-
-      tuned.result <- tuned_result$tuned.result
-
-      if(length(file_path_tmp) > 0) {
-      }
-    } else {
     tuned_result <- tune.model_param(test_param_vals, 
@@
     tuned.result <- tuned_result$tuned.result
-
-      save(tuned_result,
-           param.best_value,
-           seq_increment,
-           range_divider,
-           file = file_path_tmp)
-
-      put_log1("Function `model.tune.param_range`:
-File saved: %1", file_path_tmp)
-    }
-
     plot(tuned.result$parameter.value, tuned.result$RMSE)
@@
                                 tuned.result$RMSE)
-
-        put_log2("Function `model.tune.param_range`:
-      Reached the best RMSE for `parameter value = %1`: %2",
-                 param_values.best_result["param.best_value"],
-                 param_values.best_result["best_RMSE"])
         break
@@
                           tuned.result$RMSE)
-
-    put_log2("Function `model.tune.param_range`:
-Currently reached best RMSE for `parameter value = %1`: %2",
-             param_values.best_result["param.best_value"],
-             param_values.best_result["best_RMSE"])
-  }
+  }
+  # End repeat loop
 

### 2025-05-10 reports/capstone-movielens-report.draft4.tex
Draft report development:  function `model.tune.param_range` (in progress)

@@
 \hfill\break
-- \textbf{param\_values:} A list of values to search for the value
-corresponding to the minimum value of the \texttt{RMSE} ; -
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{param\_values:} A list of values to search for the value
+  corresponding to the minimum value of the \texttt{RMSE} ;
+\item
   \textbf{fn\_tune.test.param\_value:} A helper function that calculates
-the value of the \texttt{RMSE} for a given parameter value.; -
+  the value of the \texttt{RMSE} for a given parameter value.;
+\item
   \textbf{break.if\_min = TRUE:} A Boolean parameter that determines
@@
   steps specified by the parameter \texttt{steps.beyond\_min}, after the
-minimum value of the \texttt{RMSE} has been found; -
+  minimum value of the \texttt{RMSE} has been found;
+\item
   \textbf{steps.beyond\_min = 2:} (takes effect only if
-\texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the number
-of steps after finding the minimum value of the \texttt{RMSE}, upon
-completion of which the function should terminate.
+  \texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the
+  number of steps after finding the minimum value of the \texttt{RMSE},
+  upon completion of which the function should terminate.
+\end{itemize}
 
@@
 \hfill\break
-- \textbf{fn\_tune.test.param\_value:} A helper function that calculates
-the value of the \texttt{RMSE} for a given parameter value.; -
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{fn\_tune.test.param\_value:} A helper function that calculates
+  the value of the \texttt{RMSE} for a given parameter value.;
+\item
   \textbf{break.if\_min = TRUE:} A Boolean parameter that determines
@@
                                 \AttributeTok{best\_RMSE =}\NormalTok{ best\_RMSE)}
-
+  \CommentTok{\# Start repeat loop}
   \ControlFlowTok{repeat}\NormalTok{\{}
@@
 \StringTok{parameter value increment is too small."}\NormalTok{)}
-
-      \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
-\StringTok{Final best RMSE for \textasciigrave{}parameter value = \%1\textasciigrave{}: \%2"}\NormalTok{,}
-\NormalTok{               param\_values.best\_result[}\StringTok{"param.best\_value"}\NormalTok{],}
-\NormalTok{               param\_values.best\_result[}\StringTok{"best\_RMSE"}\NormalTok{])}
       \ControlFlowTok{break}
@@
 
-\NormalTok{    file\_name\_tmp }\OtherTok{\textless{}{-}}\NormalTok{ cache\_file\_base\_name }\SpecialCharTok{|\textgreater{}}
-      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"\_"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(loop\_starter[}\DecValTok{1}\NormalTok{])) }\SpecialCharTok{|\textgreater{}}
-      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"\_"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(loop\_starter[}\DecValTok{3}\NormalTok{])) }\SpecialCharTok{|\textgreater{}}
-      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"\_"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(range\_divider)) }\SpecialCharTok{|\textgreater{}}
-      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"."}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(seq\_start)) }\SpecialCharTok{|\textgreater{}}
-      \FunctionTok{str\_c}\NormalTok{(}\StringTok{"{-}"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-      \FunctionTok{str\_c}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(seq\_end)) }\SpecialCharTok{|\textgreater{}}
-      \FunctionTok{str\_c}\NormalTok{(}\StringTok{".RData"}\NormalTok{)}
-
-\NormalTok{    file\_path\_tmp }\OtherTok{\textless{}{-}} \FunctionTok{file.path}\NormalTok{(tune\_dir\_path, file\_name\_tmp)}
-
-    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
-\StringTok{File path generated: \%1"}\NormalTok{, file\_path\_tmp)}
-
-    \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{file.exists}\NormalTok{(file\_path\_tmp)) \{}
-      \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
-\StringTok{Loading tuning data from file: \%1..."}\NormalTok{, file\_path\_tmp)}
-
-\NormalTok{      start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
-      \FunctionTok{load}\NormalTok{(file\_path\_tmp)}
-      \FunctionTok{put\_end\_date}\NormalTok{(start)}
-      \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
-\StringTok{Tuning data has been loaded from file: \%1"}\NormalTok{, file\_path\_tmp)}
-
-\NormalTok{      tuned.result }\OtherTok{\textless{}{-}}\NormalTok{ tuned\_result}\SpecialCharTok{$}\NormalTok{tuned.result}
-
-      \ControlFlowTok{if}\NormalTok{(}\FunctionTok{length}\NormalTok{(file\_path\_tmp) }\SpecialCharTok{\textgreater{}} \DecValTok{0}\NormalTok{) \{}
-\NormalTok{      \}}
-\NormalTok{    \} }\ControlFlowTok{else}\NormalTok{ \{}
 \NormalTok{    tuned\_result }\OtherTok{\textless{}{-}} \FunctionTok{tune.model\_param}\NormalTok{(test\_param\_vals, }
@@
 \NormalTok{    tuned.result }\OtherTok{\textless{}{-}}\NormalTok{ tuned\_result}\SpecialCharTok{$}\NormalTok{tuned.result}
-
-      \FunctionTok{save}\NormalTok{(tuned\_result,}
-\NormalTok{           param.best\_value,}
-\NormalTok{           seq\_increment,}
-\NormalTok{           range\_divider,}
-           \AttributeTok{file =}\NormalTok{ file\_path\_tmp)}
-
-      \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
-\StringTok{File saved: \%1"}\NormalTok{, file\_path\_tmp)}
-\NormalTok{    \}}
-
     \FunctionTok{plot}\NormalTok{(tuned.result}\SpecialCharTok{$}\NormalTok{parameter.value, tuned.result}\SpecialCharTok{$}\NormalTok{RMSE)}
@@
 \NormalTok{                                tuned.result}\SpecialCharTok{$}\NormalTok{RMSE)}
-
-        \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
-\StringTok{      Reached the best RMSE for \textasciigrave{}parameter value = \%1\textasciigrave{}: \%2"}\NormalTok{,}
-\NormalTok{                 param\_values.best\_result[}\StringTok{"param.best\_value"}\NormalTok{],}
-\NormalTok{                 param\_values.best\_result[}\StringTok{"best\_RMSE"}\NormalTok{])}
         \ControlFlowTok{break}
@@
 \NormalTok{                          tuned.result}\SpecialCharTok{$}\NormalTok{RMSE)}
-
-    \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function \textasciigrave{}model.tune.param\_range\textasciigrave{}:}
-\StringTok{Currently reached best RMSE for \textasciigrave{}parameter value = \%1\textasciigrave{}: \%2"}\NormalTok{,}
-\NormalTok{             param\_values.best\_result[}\StringTok{"param.best\_value"}\NormalTok{],}
-\NormalTok{             param\_values.best\_result[}\StringTok{"best\_RMSE"}\NormalTok{])}
 \NormalTok{  \}}
+  \CommentTok{\# End repeat loop}
 

### 2025-05-10 r/src/support-functions/common-helper.functions.R

@@ -228,7 +228,7 @@ model.tune.param_range <- function(loop_starter,
   
   param_values.best_result <- c(param.best_value = param.best_value, 
                                 best_RMSE = best_RMSE)
-  
+  # Start repeat loop
   repeat{
     seq_increment <- (seq_end - seq_start)/range_divider 
     
@@ -457,6 +457,8 @@ Currently reached best RMSE for `parameter value = %1`: %2",
 #     }
     
   }
+  # End repeat loop
+  
   n <- length(tuned.result$parameter.value)
   
   # browser()

### 2025-05-10 reports/capstone-movielens-report.draft4.Rmd
Draft report development:  function `model.tune.param_range` (in progress).

@@
 ::: {.noteblock data-latex=""}
-Note that the function assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed to have a single minimum in the domain of definition.
+Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
+That is, it is assumed that the function has a single minimum on the given interval.
 :::

### 2025-05-10 reports/capstone-movielens-report.draft4.tex
Draft report development:  function `model.tune.param_range` (in progress).

@@
 \begin{noteblock}
-Note that the function assumes that the dependence of the \texttt{RMSE}
+Note that the algorithm assumes that the dependence of the \texttt{RMSE}
 on the input parameter is a monotonically decreasing function until a
 minimum is reached and monotonically increasing thereafter. That is, it
-is assumed to have a single minimum in the domain of definition.
+is assumed that the function has a single minimum on the given interval.
 

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Draft report development: function `model.tune.param_range`, `loop_starter` parameter described.

@@
                              is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
+                             endpoint.min_diff = 0,
                              break.if_min = TRUE,
@@
 
+  - **loop_starter:** A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
+`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
+For this purpose, the sequence step is calculated as follows:
+$$
+seq_step = \frac{end - start}{dvs}
+$$
+
+The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
+```{r eval=FALSE}
+seq(start, end, step)
+```
+
+  - **tune_dir_path:** ;
+  - **cache_file_base_name:** ;
   - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.;
+  - **max.identical.min_RMSE.count:** ;
+  - **is.cv:** ;
+  - **endpoint.min_diff:** ;
   - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
@@
 \
-Below is the most significant part of the code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
+Below is the simplified version of the code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
 ```{r eval=FALSE}
@@
 ```
+
+::: {.noteblock data-latex=""}
+The full version of the code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
+:::
 

### 2025-05-11 reports/capstone-movielens-report.draft4.tex
Draft report development: function `model.tune.param_range`, `loop_starter` parameter described.

@@
 \author{Azamat Kurbanaev}
-\date{2025-05-10}
+\date{2025-05-11}
 
@@
                              \AttributeTok{is.cv =} \ConstantTok{TRUE}\NormalTok{,}
-                             \AttributeTok{endpoint.min\_diff =} \DecValTok{0}\NormalTok{, }\CommentTok{\#1e{-}07,}
+                             \AttributeTok{endpoint.min\_diff =} \DecValTok{0}\NormalTok{,}
                              \AttributeTok{break.if\_min =} \ConstantTok{TRUE}\NormalTok{,}
@@
 \item
+  \textbf{loop\_starter:} A numeric vector of the form
+  \texttt{c(start,\ end,\ dvs)}, where \texttt{start} and \texttt{end}
+  are the endpoints of the interval on which the parameter value that
+  minimizes \texttt{RMSE} is sought. \texttt{dvs} is a divisor for
+  splitting the interval to transform it into a sequence of values among
+  which the value that minimizes \texttt{RMSE} is sought. For this
+  purpose, the sequence step is calculated as follows: \[
+  seq_step = \frac{end - start}{dvs}
+  \]
+\end{itemize}
+
+The sequence obtained as a result of the transformation is equivalent to
+the one generated by the function \texttt{seq} as follows:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{seq}\NormalTok{(start, end, step)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{tune\_dir\_path:} ;
+\item
+  \textbf{cache\_file\_base\_name:} ;
+\item
   \textbf{fn\_tune.test.param\_value:} A helper function that calculates
   the value of the \texttt{RMSE} for a given parameter value.;
+\item
+  \textbf{max.identical.min\_RMSE.count:} ;
+\item
+  \textbf{is.cv:} ;
+\item
+  \textbf{endpoint.min\_diff:} ;
 \item
@@
 \hfill\break
-Below is the most significant part of the code of the
+Below is the simplified version of the code of the
 \href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L198}{model.tune.param\_range}
@@
 \end{Shaded}
+
+\begin{noteblock}
+The full version of the code of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L198}{model.tune.param\_range}
+is available in the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L74}{Model
+Tuning} section of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L198}{common-helper.functions.R}
+script.
+
+\end{noteblock}
 
@@
 
-\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-95-1.pdf}
+\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-96-1.pdf}
 

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Draft report development: function `model.tune.param_range`, `tune_dir_path`, `cach_file_base_name`, `fn_tune.test.param_value` parameters described.

@@
 
-##### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function
+##### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
 \
@@
 \
-
-  - **loop_starter:** A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
+####### loop_starter 
+\
+A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
 `dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
@@
 $$
-seq_step = \frac{end - start}{dvs}
+step = \frac{end - start}{dvs}
 $$
@@
 ```  
-
-  - **tune_dir_path:** ;
-  - **cache_file_base_name:** ;
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.;
+In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
+
+####### tune_dir_path 
+\
+
+To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the cache files are saved.
+
+####### cache_file_base_name 
+\
+
+The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
+
+#######  fn_tune.test.param_value
+\
+
+This is a helper function name that is passed to the same-named parameter of the [tune.model_param] function that is called internally during the execution (see the [description of the `tune.model_param` function](#func.tune.model_param) above).
+
+#######  
+\
+
   - **max.identical.min_RMSE.count:** ;
+
+#######  
+\
+
   - **is.cv:** ;
+
+#######  
+\
+
   - **endpoint.min_diff:** ;
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+
+#######  
+\
+
+  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps
+
+#######  
+\
+
+specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+
   - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
+
+#######  
+\
 

### 2025-05-11 reports/capstone-movielens-report.draft4.tex
Draft report development: function `model.tune.param_range`, `tune_dir_path`, `cach_file_base_name`, `fn_tune.test.param_value` parameters described.

@@
 \subparagraph{\texorpdfstring{\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
-Function}{tune.model\_param Function}}\label{tune.model_param-function}
+Function}{tune.model\_param Function}}\label{func.tune.model_param}
 
@@
 \hfill\break
+\#\#\#\#\#\#\# loop\_starter\\
+A numeric vector of the form \texttt{c(start,\ end,\ dvs)}, where
+\texttt{start} and \texttt{end} are the endpoints of the interval on
+which the parameter value that minimizes \texttt{RMSE} is sought.
+\texttt{dvs} is a divisor for splitting the interval to transform it
+into a sequence of values among which the value that minimizes
+\texttt{RMSE} is sought. For this purpose, the sequence step is
+calculated as follows: \[
+step = \frac{end - start}{dvs}
+\]
+
+The sequence obtained as a result of the transformation is equivalent to
+the one generated by the function \texttt{seq} as follows:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{seq}\NormalTok{(start, end, step)}
+\end{Highlighting}
+\end{Shaded}
+
+In fact, the \texttt{seq} function is called internally to generate the
+sequence during the execution of the \texttt{model.tune.param\_range}
+function.
+
+tune\_dir\_path
+
+\hfill\break
+
+To improve performance, the algorithm caches intermediate results in the
+file system. This parameter specifies the path to the directory where
+the cache files are saved.
+
+cache\_file\_base\_name
+
+\hfill\break
+
+The algorithm generates unique names for cache files based on this and
+the \texttt{loop\_starter} parameter, as well as some other intermediate
+values calculated during the execution.
+
+fn\_tune.test.param\_value
+
+\hfill\break
+
+This is a helper function name that is passed to the same-named
+parameter of the {[}tune.model\_param{]} function that is called
+internally during the execution (see the
+\hyperref[func.tune.model_param]{description of the
+\texttt{tune.model\_param} function} above).
+
+\hfill\break
 
@@
 \item
-  \textbf{loop\_starter:} A numeric vector of the form
-  \texttt{c(start,\ end,\ dvs)}, where \texttt{start} and \texttt{end}
-  are the endpoints of the interval on which the parameter value that
-  minimizes \texttt{RMSE} is sought. \texttt{dvs} is a divisor for
-  splitting the interval to transform it into a sequence of values among
-  which the value that minimizes \texttt{RMSE} is sought. For this
-  purpose, the sequence step is calculated as follows: \[
-  seq_step = \frac{end - start}{dvs}
-  \]
+  \textbf{max.identical.min\_RMSE.count:} ;
 \end{itemize}
 
-The sequence obtained as a result of the transformation is equivalent to
-the one generated by the function \texttt{seq} as follows:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{seq}\NormalTok{(start, end, step)}
-\end{Highlighting}
-\end{Shaded}
+\hfill\break
 
@@
 \item
-  \textbf{tune\_dir\_path:} ;
-\item
-  \textbf{cache\_file\_base\_name:} ;
-\item
-  \textbf{fn\_tune.test.param\_value:} A helper function that calculates
-  the value of the \texttt{RMSE} for a given parameter value.;
-\item
-  \textbf{max.identical.min\_RMSE.count:} ;
-\item
   \textbf{is.cv:} ;
+\end{itemize}
+
+\hfill\break
+
+\begin{itemize}
+\tightlist
 \item
   \textbf{endpoint.min\_diff:} ;
+\end{itemize}
+
+\hfill\break
+
+\begin{itemize}
+\tightlist
 \item
@@
   whether the function should terminate after completing the number of
-  steps specified by the parameter \texttt{steps.beyond\_min}, after the
-  minimum value of the \texttt{RMSE} has been found;
+  steps
+\end{itemize}
+
+\hfill\break
+
+specified by the parameter \texttt{steps.beyond\_min}, after the minimum
+value of the \texttt{RMSE} has been found;
+
+\begin{itemize}
+\tightlist
 \item
@@
 \end{itemize}
+
+\hfill\break
 

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Draft report development: function `model.tune.param_range`, cross reference to the `tune.model_param` fuction description in `fn_tune.test.param_value` parameter description fixed.

@@
 \
+
 A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
@@
 
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the cache files are saved.
+To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
 
@@
 
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param] function that is called internally during the execution (see the [description of the `tune.model_param` function](#func.tune.model_param) above).
+This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
 

### 2025-05-11 reports/capstone-movielens-report.draft4.tex
Draft report development: function `model.tune.param_range`, cross reference to the `tune.model_param` fuction description in `fn_tune.test.param_value` parameter description fixed.

@@
 \#\#\#\#\#\#\# loop\_starter\\
+
 A numeric vector of the form \texttt{c(start,\ end,\ dvs)}, where
@@
 file system. This parameter specifies the path to the directory where
-the cache files are saved.
+the files are cached.
 
@@
 This is a helper function name that is passed to the same-named
-parameter of the {[}tune.model\_param{]} function that is called
-internally during the execution (see the
-\hyperref[func.tune.model_param]{description of the
-\texttt{tune.model\_param} function} above).
+parameter of the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
+function that is called internally during the execution (see the
+description of the \texttt{tune.model\_param} function
+\hyperref[func.tune.model_param]{above}).
 

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Draft report development: `` parameter of the `model.tune.param_range` function described.

--- 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
@@
 \
+
 ####### loop_starter 
@@
 \
-
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the cache files are saved.
+To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
 
@@
 \
-
 The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
@@
 \
-
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param] function that is called internally during the execution (see the [description of the `tune.model_param` function](#func.tune.model_param) above).
-
-#######  
-\
-
-  - **max.identical.min_RMSE.count:** ;
+This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+
+####### max.identical.min_RMSE.count
+\
+If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
+When it is reached, the algorithm considers the task execution to be complete.
 

### 2025-05-11 reports/capstone-movielens-report.draft4.tex
Draft report development: `` parameter of the `model.tune.param_range` function described.

@@
 \hfill\break
-\#\#\#\#\#\#\# loop\_starter\\
-
+
+loop\_starter
+
+\hfill\break
 A numeric vector of the form \texttt{c(start,\ end,\ dvs)}, where
@@
 \hfill\break
-
 To improve performance, the algorithm caches intermediate results in the
@@
 \hfill\break
-
 The algorithm generates unique names for cache files based on this and
@@
 \hfill\break
-
 This is a helper function name that is passed to the same-named
@@
 
-\hfill\break
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{max.identical.min\_RMSE.count:} ;
-\end{itemize}
+max.identical.min\_RMSE.count
+
+\hfill\break
+If more than one identical minimum \texttt{RMSE} value is calculated
+during execution, the number of identical minimums is limited by the
+value of this parameter. When it is reached, the algorithm considers the
+task execution to be complete.
 

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Draft report development:  the `model.tune.param_range` function input parameters described.

@@
 
-##### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function
+##### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
 \
@@
                              max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
                              endpoint.min_diff = 0,
@@
 
-####### max.identical.min_RMSE.count
+####### max.identical.min_RMSE.count = 4
 \
@@
 
-#######  
-\
-
-  - **is.cv:** ;
-
-#######  
-\
-
-  - **endpoint.min_diff:** ;
-
-#######  
-\
-
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps
-
-#######  
-\
-
-specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#######  
-\
-
-###### Details
+####### endpoint.min_diff = 0
+\
+Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the [Details](#func.model.tune.param_range.details) section below).
+
+####### break.if_min = TRUE 
+\
+This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+
+####### steps.beyond_min = 2 
+\
+This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+
+###### Details {#func.model.tune.param_range.details}
 \

### 2025-05-11 reports/capstone-movielens-report.draft4.tex
Draft report development:  the `model.tune.param_range` function input parameters described.

@@
 \subparagraph{\texorpdfstring{\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L198}{model.tune.param\_range}
-Function}{model.tune.param\_range Function}}\label{model.tune.param_range-function}
+Function}{model.tune.param\_range Function}}\label{func.model.tune.param_range}
 
@@
                              \AttributeTok{max.identical.min\_RMSE.count =} \DecValTok{4}\NormalTok{,}
-                             \AttributeTok{is.cv =} \ConstantTok{TRUE}\NormalTok{,}
                              \AttributeTok{endpoint.min\_diff =} \DecValTok{0}\NormalTok{,}
@@
 
-max.identical.min\_RMSE.count
+max.identical.min\_RMSE.count = 4
 
@@
 
-\hfill\break
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{is.cv:} ;
-\end{itemize}
-
-\hfill\break
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{endpoint.min\_diff:} ;
-\end{itemize}
-
-\hfill\break
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{break.if\_min = TRUE:} A Boolean parameter that determines
-  whether the function should terminate after completing the number of
-  steps
-\end{itemize}
-
-\hfill\break
-
-specified by the parameter \texttt{steps.beyond\_min}, after the minimum
-value of the \texttt{RMSE} has been found;
-
-\begin{itemize}
-\tightlist
-\item
-  \textbf{steps.beyond\_min = 2:} (takes effect only if
-  \texttt{break.if\_min} parameter is \texttt{TRUE}) Specifies the
-  number of steps after finding the minimum value of the \texttt{RMSE},
-  upon completion of which the function should terminate.
-\end{itemize}
-
-\hfill\break
+endpoint.min\_diff = 0
+
+\hfill\break
+Defines the sensitivity threshold for determining the neighborhood
+boundaries of the minimum \texttt{RMSE} value (for details, see the
+\hyperref[func.model.tune.param_range.details]{Details} section below).
+
+break.if\_min = TRUE
+
+\hfill\break
+This is a parameter that is required for the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
+function that is called internally during execution (see the description
+of the \texttt{tune.model\_param} function
+\hyperref[func.tune.model_param]{above}).
+
+steps.beyond\_min = 2
+
+\hfill\break
+This is a parameter that is required for the
+\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
+function that is called internally during execution (see the description
+of the \texttt{tune.model\_param} function
+\hyperref[func.tune.model_param]{above}).
 

### 2025-05-11 r/src/support-functions/common-helper.functions.R

@@ -201,7 +201,6 @@ model.tune.param_range <- function(loop_starter,
                              fn_tune.test.param_value,
                              # range_divider.multiplier = 4,
                              max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
                              endpoint.min_diff = 0, #1e-07,
                              break.if_min = TRUE,
                              steps.beyond_min = 2){

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Temp commit.

@@
 \
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the [Details](#func.model.tune.param_range.details) section below).
+Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section below).
 
@@
 
-###### Details {#func.model.tune.param_range.details}
-\
+::: Details {#func.model.tune.param_range.details }
+
 During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.
+:::
+
+###### Details
+\
+
+(ref:foo) During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.
+
+###### Value
+\
+See the `Details`section [above](#func.model.tune.param_range.details). 
+See the `Details`section [above](ref:foo). 
+See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range). 
+pdf_document2
 
@@
 :::
-
-###### Value
-\
 

### 2025-05-11 reports/capstone-movielens-report.draft4.tex
Temp commit.

@@
 boundaries of the minimum \texttt{RMSE} value (for details, see the
-\hyperref[func.model.tune.param_range.details]{Details} section below).
+\texttt{Details} section below).
 
@@
 
-Details
-
-\hfill\break
+::: Details \{\#func.model.tune.param\_range.details \}
+
 During execution, the function uses a helper function specified by the
@@
 \texttt{RMSE} value for the given parameter from the list determined by
-the inner \texttt{param\_values} sequence.
+the inner \texttt{param\_values} sequence. :::
+
+Details
+
+\hfill\break
+
+(ref:foo) During execution, the function uses a helper function
+specified by the \texttt{fn\_tune.test.param\_value} parameter, which
+calculates the \texttt{RMSE} value for the given parameter from the list
+determined by the inner \texttt{param\_values} sequence.
+
+Value
+
+\hfill\break
+See the \texttt{Details}section
+\hyperref[func.model.tune.param_range.details]{above}. See the
+\texttt{Details}section \href{ref:foo}{above}. See the
+\texttt{func.model.tune.param\_range} Function description
+\hyperref[func.model.tune.param_range]{above}. pdf\_document2
 
@@
 \end{noteblock}
-
-Value
-
-\hfill\break
 

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Draft report development:  the `model.tune.param_range` function input parameters description: troubleshooting.

@@
+```{r setup, include=FALSE, echo = FALSE}
+r.path <- "../r"
+src.folder <- "src"
+support_scripts.folder <- "support-scripts"
+support_functions.folder <- "support-functions"
+
+r.src.path <- file.path(r.path, src.folder)
+support_scripts.path <- file.path(r.src.path, support_scripts.folder)
+support_functions.path <- file.path(r.src.path, support_functions.folder)
+## Setup -----------------------------------------------------------------------
+setup_script.file_path <- file.path(support_scripts.path,
+                                               "setup.R")
+
+# main_script.file_path <- file.path(r.src.path,
+#                                    "capstone-movielens.main.R")
+# stop(main_script.file_path)
+stopifnot(file.exists(setup_script.file_path))
+
+source(setup_script.file_path, 
+       local = knitr::knit_global())
+# or sys.source("your-script.R", envir = knitr::knit_global())
+
+## External Common Helper functions -------------------------------------
+# common_helper_functions.file_path <- file.path(support_functions.path,
+#                                             "common-helper.functions.R")
+# source(common_helper_functions.file_path, 
+#        local = knitr::knit_global())
+
+# knitr::knit_global()
+#knitr::opts_chunk$set(echo = FALSE)
+```
+
 ---
@@
 output: 
-  pdf_document: 
+  bookdown::pdf_document2: 
     df_print: paged
@@
 
-```{r setup, include=FALSE, echo = FALSE}
-r.path <- "../r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-## Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-# stop(main_script.file_path)
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
-## External Common Helper functions -------------------------------------
-# common_helper_functions.file_path <- file.path(support_functions.path,
-#                                             "common-helper.functions.R")
-# source(common_helper_functions.file_path, 
-#        local = knitr::knit_global())
-
-# knitr::knit_global()
-#knitr::opts_chunk$set(echo = FALSE)
-```
-
 ## Introduction / Overview / Executive Summary
@@
 \
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section below).
+Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
 
@@
 
-::: Details {#func.model.tune.param_range.details }
+::: { #func.model.tune.param_range.details .sidebar }
+***Details***
 
@@
 
-###### Details
-\
-
-(ref:foo) During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.
-
-###### Value
-\
-See the `Details`section [above](#func.model.tune.param_range.details). 
-See the `Details`section [above](ref:foo). 
+::: { #func.model.tune.param_range.details2 .sidebar }
+**DETAILS**
+
+During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.
+:::
+
+###### **Details3**
+\
+
+During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.
+
+###### **Value**
+\
+
 See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-pdf_document2
 
@@
 \
+
+See the `Details`section [above](#func.model.tune.param_range.details).
+
+See the `Details`section above \@ref(sec:func.model.tune.param_range.details)
 

### 2025-05-11 r/src/support-scripts/setup.R

@@ -29,6 +29,9 @@ if(!require("pacman"))
 if(!require("recommenderlab")) 
   install.packages("recommenderlab")
 
+if(!require("bookdown")) 
+  install.packages("bookdown")
+
 # Loading the required libraries
 library(dslabs)
 library(tidyverse)
@@ -55,6 +58,7 @@ library(rafalib)
 library(gtools)
 library(pak)
 library(pacman)
+library(bookdown)
 
 p_load(conflicted, latex2exp, kableExtra)
 

### 2025-05-12 reports/capstone-movielens-report.draft4.Rmd
Draft report development:  the `model.tune.param_range` function input parameters description: fixed.
Draft report development:  the `model.tune.param_range` function description completed.

@@
 
-###### Value
+###### Value  {#func.tune.model_param.value}
 \
@@
 \
-Below is the most significant part of the code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
+Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
 ```{r eval=FALSE}
@@
 
-###### Parameters
-\
-
-####### loop_starter 
-\
+###### **Parameters**
+\
+
+::: { #func.model.tune.param_range.params.loop_starter .sidebar }
+***loop_starter***
+
 A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
@@
 In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-
-####### tune_dir_path 
-\
+:::
+
+::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
+***tune_dir_path***
+
 To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-
-####### cache_file_base_name 
-\
+:::
+
+::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
+***cache_file_base_name***
+
 The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-
-#######  fn_tune.test.param_value
-\
+:::
+
+::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
+***fn_tune.test.param_value***
+
 This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-####### max.identical.min_RMSE.count = 4
-\
+:::
+
+::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
+***max.identical.min_RMSE.count = 4***
+
 If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
 When it is reached, the algorithm considers the task execution to be complete.
-
-####### endpoint.min_diff = 0
-\
+:::
+
+::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
+***endpoint.min_diff = 0***
+
 Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-
-####### break.if_min = TRUE 
-\
+:::
+
+::: { #func.model.tune.param_range.params.break.if_min .sidebar }
+***break.if_min = TRUE***
+
 This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-####### steps.beyond_min = 2 
-\
+:::
+
+::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
+***steps.beyond_min = 2***
+
 This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
 
-::: { #func.model.tune.param_range.details .sidebar }
-***Details***
-
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.
-:::
-
-::: { #func.model.tune.param_range.details2 .sidebar }
-**DETAILS**
-
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.
-:::
-
-###### **Details3**
-\
-
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the inner `param_values` sequence.
+###### **Details** { #func.model.tune.param_range.details } 
+\
+
+First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
+
+The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
+
+Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
+
+The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
+The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
+
+Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
+
+The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
 
@@
 
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
+A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found.
 
@@
 \
-Below is the simplified version of the code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
+Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
 ```{r eval=FALSE}
@@
   seq_end <- loop_starter[2]
-  range_divider <- loop_starter[3]
-
-  if (range_divider < 4) {
-    range_divider <- 4
+  interval_divisor <- loop_starter[3]
+
+  if (interval_divisor < 4) {
+    interval_divisor <- 4
   }
@@
   repeat{
-    seq_increment <- (seq_end - seq_start)/range_divider
+    seq_increment <- (seq_end - seq_start)/interval_divisor
 
@@
     result.RMSE[n+1] <- RMSE.rightmost
-    # browser()
   }
@@
 
-##### `` Function
-\
-
-See the `Details`section [above](#func.model.tune.param_range.details).
-
-See the `Details`section above \@ref(sec:func.model.tune.param_range.details)
+##### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
+\
 
@@
 ```{r eval=FALSE}
-
+get_fine_tune.param.endpoints.idx <- function(preset.result) {
+  # ...
+
+  c(start = i, 
+    end = j,
+    best = best_RMSE.idx)
+}
 ```
@@
 \
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-##### `` Function
+The source code of the [get_fine_tune.param.endpoints.idx] (https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints.idx <- function(preset.result) {
+  best_RMSE <- min(preset.result$RMSE)
+  best_RMSE.idx <- which.min(preset.result$RMSE)
+  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
+
+  preset.result.N <- length(preset.result$RMSE)
+  i <- best_RMSE.idx
+  j <- i
+
+  while (i > 1) {
+    i <- i - 1
+
+    if (preset.result$RMSE[i] > best_RMSE) {
+      break
+    }
+  }
+
+  while (j < preset.result.N) {
+    j <- j + 1
+
+    if (preset.result$RMSE[j] > best_RMSE) {
+      break
+    }
+  }
+
+  c(start = i, 
+    end = j,
+    best = best_RMSE.idx)
+}
+
+```
+
+##### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
 \
@@
 ```{r eval=FALSE}
+get_best_param.result <- function(param_values, rmses){
+  # ...
+
+  c(param.best_value = param_values[best_pvalue_idx], 
+    best_RMSE = rmses[best_pvalue_idx])
 
@@
 ```{r eval=FALSE}
-
+get_best_param.result <- function(param_values, rmses){
+  best_pvalue_idx <- which.min(rmses)
+  c(param.best_value = param_values[best_pvalue_idx], 
+    best_RMSE = rmses[best_pvalue_idx])
 ```
@@
 
-##### `` Function
-\
+##### []() Function {#func.}
+\
+
+See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
+
+::: {.noteblock data-latex=""}
+Note 
+:::
 
@@
 
-##### `` Function
+##### []() Function {#func.}
 \

### 2025-05-12 r/src/support-functions/common-helper.functions.R

@@ -199,7 +199,7 @@ model.tune.param_range <- function(loop_starter,
                              tune_dir_path,
                              cache_file_base_name,
                              fn_tune.test.param_value,
-                             # range_divider.multiplier = 4,
+                             # interval_divisor.multiplier = 4,
                              max.identical.min_RMSE.count = 4,
                              endpoint.min_diff = 0, #1e-07,
                              break.if_min = TRUE,
@@ -214,11 +214,11 @@ model.tune.param_range <- function(loop_starter,
   RMSE.leftmost <- NA
   RMSE.rightmost <- NA
   
-  range_divider <- loop_starter[3]
-  if (range_divider < 4) {
-    range_divider <- 4
+  interval_divisor <- loop_starter[3]
+  if (interval_divisor < 4) {
+    interval_divisor <- 4
   }
-  # max_range_divider <- loop_starter[4]
+  # max_interval_divisor <- loop_starter[4]
   
   
   best_RMSE <- NA
@@ -229,7 +229,7 @@ model.tune.param_range <- function(loop_starter,
                                 best_RMSE = best_RMSE)
   # Start repeat loop
   repeat{
-    seq_increment <- (seq_end - seq_start)/range_divider 
+    seq_increment <- (seq_end - seq_start)/interval_divisor 
     
     if (seq_increment < 0.0000000000001) {
       warning("Function `model.tune.param_range`:
@@ -255,7 +255,7 @@ Final best RMSE for `parameter value = %1`: %2",
       str_c("_") |>
       str_c(as.character(loop_starter[3])) |>
       str_c("_") |>
-      str_c(as.character(range_divider)) |>
+      str_c(as.character(interval_divisor)) |>
       str_c(".") |>
       str_c(as.character(seq_start)) |>
       str_c("-") |>
@@ -297,7 +297,7 @@ Tuning data has been loaded from file: %1", file_path_tmp)
            param.best_value,
            # best_RMSE,
            seq_increment,
-           range_divider,
+           interval_divisor,
            file = file_path_tmp)
 
       put_log1("Function `model.tune.param_range`:
@@ -401,14 +401,14 @@ So far reached best RMSE for `parameter value = %1`: %2",
         break
       }
 
-      # if (range_divider < max_range_divider) {
-      #   range_divider <- range_divider*range_divider.multiplier
+      # if (interval_divisor < max_interval_divisor) {
+      #   interval_divisor <- interval_divisor*interval_divisor.multiplier
       #   # browser()
       # } else {
[…]

### 2025-05-12 reports/capstone-movielens-report.draft4.Rmd
Fix for report.

@@
 \
-The source code of the [get_fine_tune.param.endpoints.idx] (https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
 ```{r eval=FALSE}
@@
 \
-Below is the most significant part of the code of the [function]() function:
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
 ```{r eval=FALSE}

### 2025-05-12 reports/capstone-movielens-report.draft4.Rmd
Fix for report.

@@
 
-###### Value  {#func.tune.model_param.value}
+::: { #func.tune.model_param.value  .sidebar }
+###### Value
 \
 The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values.
+:::
 
@@
 
-###### **Details** { #func.model.tune.param_range.details } 
-\
-
+::: { #func.model.tune.param_range.details .sidebar }
+###### **Details** 
+\
 First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
@@
 The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
+:::
 
@@
 
-##### []() Function {#func.}
+##### []() Function {#func.1}
 \
@@
 
-##### []() Function {#func.}
+##### []() Function {#func.2}
 \

### 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
Report: `get_fine_tune.param.endpoints.idx` function described.

@@
 \
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values.
+The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
+```{r eval=FALSE}
+  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
+                                parameter.value = param_vals_tmp),
+       best_result = param_values.best_result)
+```
 :::
@@
 
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found.
-
+A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
+```{r eval=FALSE}
+  list(best_result = param_values.best_result,
+       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
+       tuned.result = data.frame(parameter.value = parameter.value,
+                                 RMSE = result.RMSE))
+```
+
+::: {#func.model.tune.param_range.code .sidebar }
 ###### Source Code
@@
 :::
+:::
 
@@
 
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
+::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
+***preset.result***
+
+A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
+Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
+```{r eval=FALSE}
+    tuned_result <- tune.model_param(test_param_vals, 
+                                  fn_tune.test.param_value,
+                                  break.if_min,
+                                  steps.beyond_min)
+
+    tuned.result <- tuned_result$tuned.result
+    # tuned.result = data.frame(RMSE, parameter.value)
+    # ...
+    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
+```
+:::
 
@@
 \
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
+The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
 
@@
 \
+
+A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start = i, 
+    end = j,
+    best = best_RMSE.idx)
+```
 
@@
 See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
+
+::: {.noteblock data-latex=""}
+Note 
+:::
 

### 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
Report structure fixed.

@@
 support_functions.path <- file.path(r.src.path, support_functions.folder)
-## Setup -----------------------------------------------------------------------
+# Setup -----------------------------------------------------------------------
 setup_script.file_path <- file.path(support_scripts.path,
@@
 
-## External Common Helper functions -------------------------------------
+# External Common Helper functions -------------------------------------
 # common_helper_functions.file_path <- file.path(support_functions.path,
@@
 
-## Introduction / Overview / Executive Summary
+# Introduction / Overview / Executive Summary
 
@@
 
-### Datasets Overview
+## Datasets Overview
 
@@
 
-#### `edx` Dataset
+### `edx` Dataset
 \
@@
 
-##### Rating distribution plot[@MRS-R-BEST]
+#### Rating distribution plot[@MRS-R-BEST]
 \
@@
 
-##### Ratings per movie
-\
-
-###### Movie popularity count[@MRS-R-BEST]
+#### Ratings per movie
+\
+
+##### Movie popularity count[@MRS-R-BEST]
 \
@@
 
-###### Ratings per movie plot[@MRS-R-BEST]
+##### Ratings per movie plot[@MRS-R-BEST]
 \
@@
 
-###### Movies' rating histogram[@MRS-R-BEST]
+##### Movies' rating histogram[@MRS-R-BEST]
 \
@@
 
-##### Ratings per user[@MRS-R-BEST]
-\
-
-###### User rating count (activity measure)
+#### Ratings per user[@MRS-R-BEST]
+\
+
+##### User rating count (activity measure)
 \
@@
 
-###### User rating summary
+##### User rating summary
 \
@@
 
-###### Ratings per user plot
+##### Ratings per user plot
 \
@@
 
-###### Users' rating histogram
+##### Users' rating histogram
 \
@@
 
-## Methods / Analysis
+# Methods / Analysis
 ::: {.noteblock data-latex=""}
@@
 
-### Defining Logging and Time Measuring Helper Functions
+## Defining Logging and Time Measuring Helper Functions
 \
@@
 ```{r eval=FALSE }
-## Logging Helper functions -----------------------------------------------------
+# Logging Helper functions -----------------------------------------------------
 open_logfile <- function(file_name){
@@
 
-### Preparing train and set datasets
+## Preparing train and set datasets
 \
@@
 
-#### The `make_source_datasets` function
+### The `make_source_datasets` function
 \
@@
 
-##### `edx.mx` Matrix Object
+#### `edx.mx` Matrix Object
 \
@@
 
-##### `edx.sgr` Object
+#### `edx.sgr` Object
 \
@@
 
-##### `movie_map` Object
+#### `movie_map` Object
 \
@@
 
-##### `date_days_map` Object
+#### `date_days_map` Object
 \
@@
 
-##### `edx_CV` Object
+#### `edx_CV` Object
 \
@@
 
-#### Common Helper Functions
+### Common Helper Functions
 \
@@
 
-##### `clamp` function
+#### `clamp` function
 \
@@
 
-##### Functions to calculate _(Root) Mean Squared Error_
+#### Functions to calculate _(Root) Mean Squared Error_
 \
@@
 
-### Overall Mean Rating (Naive) Model
+## Overall Mean Rating (Naive) Model
 \
@@
 
-#### Ensure that `mu.RMSE` value is the best for the current model
+### Ensure that `mu.RMSE` value is the best for the current model
 \
@@
 
-### User Effect Model
+## User Effect Model
 \
@@
 
-### User+Movie Effect (UME) Model
+## User+Movie Effect (UME) Model
 \
@@
 
-#### UME Model: Support Functions
+### UME Model: Support Functions
 \
@@
 
-##### `train_user_movie_effect` Function
+#### `train_user_movie_effect` Function
 \
@@
 ```{r eval=FALSE}
-## Regularization --------------------------------------------------------------
+# Regularization --------------------------------------------------------------
 mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
@@
 
-##### `train_user_movie_effect.cv` Function
+#### `train_user_movie_effect.cv` Function
 \
@@
 
-##### `calc_user_movie_effect_MSE` Function
+#### `calc_user_movie_effect_MSE` Function
 \
@@
 
-##### `calc_user_movie_effect_MSE.cv` Function
+#### `calc_user_movie_effect_MSE.cv` Function
 \
@@
 
-##### `calc_user_movie_effect_RMSE` Function
+#### `calc_user_movie_effect_RMSE` Function
 \
@@
 
-##### `calc_user_movie_effect_RMSE.cv` Function
+#### `calc_user_movie_effect_RMSE.cv` Function
 \
@@
 
-#### Model Building
+### Model Building
 \
@@
 
-### Regularizing User+Movie Effect Model
-
-#### Utilizing Penalized least squares
+## Regularizing User+Movie Effect Model
+
+### Utilizing Penalized least squares
 \
@@
 
-#### Regularization: Common Helper Functions
+### Regularization: Common Helper Functions
 \
@@
 
-##### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
+#### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
 \
@@
 
-###### Sugnature
+##### Sugnature
 \
@@
 
-###### Parameters
+##### Parameters
 \
@@
 
-###### Details
+##### Details
 \
@@
 ::: { #func.tune.model_param.value .sidebar }
-###### Value
+##### Value
 \
@@
 
-###### Source Code
+##### Source Code
 \
@@
 
-##### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
+#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
 \
@@
 
-###### **Parameters**
+##### **Parameters**
 \
@@
 ::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-***loop_starter***
-
+###### ***loop_starter***
+\
 A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
@@
 ::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-***tune_dir_path***
-
+###### ***tune_dir_path***
+\
 To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
@@
 ::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-***cache_file_base_name***
-
+###### ***cache_file_base_name***
+\
 The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
@@
 ::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-***fn_tune.test.param_value***
-
+###### ***fn_tune.test.param_value***
+\
 This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
@@
 ::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-***max.identical.min_RMSE.count = 4***
-
+###### ***max.identical.min_RMSE.count = 4***
+\
 If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
@@
 ::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-***endpoint.min_diff = 0***
-
+###### ***endpoint.min_diff = 0***
+\
 Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
@@
 ::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-***break.if_min = TRUE***
-
+###### ***break.if_min = TRUE***
+\
 This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
@@
 ::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-***steps.beyond_min = 2***
-
+###### ***steps.beyond_min = 2***
+\
 This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
@@
 ::: { #func.model.tune.param_range.details .sidebar }
-###### **Details** 
+##### **Details** 
 \
@@
 
-###### **Value**
+##### **Value**
 \
@@
 ::: {#func.model.tune.param_range.code .sidebar }
-###### Source Code
+##### Source Code
 \
@@
 
-##### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-###### Sugnature
+#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
+\
+
+##### Sugnature
 \
@@
 ::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-***preset.result***
-
+###### ***preset.result***
+\
 A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
@@
 
-###### Value
-\
-
+##### Value
+\
 A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
@@
 
-##### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-###### Sugnature
+#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
+\
+
+##### Sugnature
 \
@@
 
-###### Parameters
-\
-
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-###### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-###### Value
-\
-
-###### Source Code
+##### Parameters
+\
+
+  - **:** ; 
+  - **:** .
+
+##### Details
+\
+
+##### Value
+\
+
+##### Source Code
 \
@@
 
+::: {.noteblock data-latex=""}
+Note 
+:::
+
 ```{r eval=FALSE}
@@
 
-##### []() Function {#func.1}
+#### []() Function {#func.1}
 \
@@
 
-###### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-###### Parameters
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+
+##### Parameters
 \
@@
 
-###### Value
-\
-
-###### Source Code
+##### Value
+\
+
+##### Source Code
 \
@@
 
-##### []() Function {#func.2}
-\
-
-###### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-###### Parameters
+#### []() Function {#func.2}
+\
+
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+
+##### Parameters
 \
@@
 
-#### UME Model Regularization: Support Function
+### UME Model Regularization: Support Function
 \
@@
 
-##### `regularize.test_lambda.UM_effect.cv` Function
+#### `regularize.test_lambda.UM_effect.cv` Function
 \
@@
 
-### Accounting for Date effects
-
-##### Yearly rating count[@MRS-R-BEST]
+## Accounting for Date effects
+
+#### Yearly rating count[@MRS-R-BEST]
 \
@@
 
-##### Average rating per year plot[@MRS-R-BEST]
+#### Average rating per year plot[@MRS-R-BEST]
 \
@@
 
-### Accounting for Genre effect
+## Accounting for Genre effect
 \
@@
 
-#### Genre Data Analysis
-\
-##### Movie Genres Data 
+### Genre Data Analysis
+\
+#### Movie Genres Data 
 \
@@
 
-##### Movie Genres Effect 
+#### Movie Genres Effect 
 \
@@
 
-## Conclusion
+# Conclusion
 

### 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
Report: teamplate applied for description of user functions.

@@
 
-### Regularization: Common Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-#### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-##### Sugnature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-##### Parameters
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-##### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-##### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-##### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-##### Sugnature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-##### **Parameters**
-\
-
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-###### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-###### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-###### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-###### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-###### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-###### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-###### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-###### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-##### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-##### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-##### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The full version of the code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
-:::
-:::
-
-#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-##### Sugnature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-##### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-###### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-```
-:::
-
-##### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-##### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-```
-
-##### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-##### Sugnature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-##### Parameters
-\
-
-  - **:** ; 
-  - **:** .
-
-##### Details
-\
-
-##### Value
-\
-
-##### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-#### []() Function {#func.1}
-\
-
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-##### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-##### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-##### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-##### Value
-\
-
-##### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-#### []() Function {#func.2}
-\
-
-##### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-##### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-##### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-##### Value
-\
-
-##### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-### UME Model Regularization: Support Function
+### UME Model Regularization: Support Functions
 \
@@
 
-#### `regularize.test_lambda.UM_effect.cv` Function
-\
-
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold CV_ method for the given $\lambda$ parameter value:
+#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
+\
+
+This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
 ```{r eval=FALSE}
@@
 This is a great conclusion, isn't it?!!
+
+# Appendix
+
+### Regularization: Common Helper Functions
+\
+::: {.noteblock data-latex=""}
+The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+:::
+
+#### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
+\
+
+The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
+
+##### Sugnature
+\
+```{r eval=FALSE}
+tune.model_param <- function(param_values, 
+                             fn_tune.test.param_value, 
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+
+# ...
+  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
+                                parameter.value = param_vals_tmp),
+       best_result = param_values.best_result)
+}  
+```
+
+##### Parameters
+\
+
+  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
+  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
+  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
+
+##### Details
+\
+During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
+
+::: {.noteblock data-latex=""}
+Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
+That is, it is assumed that the function has a single minimum on the given interval.
+:::
+
+::: { #func.tune.model_param.value .sidebar }
+##### Value
+\
+The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
+```{r eval=FALSE}
+  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
+                                parameter.value = param_vals_tmp),
+       best_result = param_values.best_result)
+```
+:::
+
+##### Source Code
+\
+Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
+```{r eval=FALSE}
+tune.model_param <- function(param_values, 
+                             fn_tune.test.param_value, 
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+  n <- length(param_values)
+  param_vals_tmp <- numeric()
+  RMSEs_tmp <- numeric()
+  RMSE_min <- Inf
+  i_max.beyond_RMSE_min <- Inf
+  prm_val.best <- NA
+
+  # ...
+
+  for (i in 1:n) {
+    put_log1("Function: `tune.model_param`:
+Iteration %1", i)
+    prm_val <- param_values[i]
+    param_vals_tmp[i] <- prm_val
+
+    RMSE_tmp <- fn_tune.test.param_value(prm_val)
+    RMSEs_tmp[i] <- RMSE_tmp
+
+    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
+
+    if(RMSE_tmp > RMSE_min){
+      warning("Function: `tune.model_param`:
+`RSME` reached its minimum: ", RMSE_min, "
+for parameter value: ", prm_val)
+      put_log2("Function: `tune.model_param`:
+Current `RMSE` value is %1 related to parameter value: %2",
+               RMSE_tmp,
+               prm_val)
+
+      if (i > i_max.beyond_RMSE_min) {
+        warning("Function: `tune.model_param`:
+Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
+        break
+      }
+      next
+    }
+
+    RMSE_min <- RMSE_tmp
+    prm_val.best <- prm_val
+
+    if (break.if_min) {
+      i_max.beyond_RMSE_min <- i + steps.beyond_min
+    }
+  }
+
+  param_values.best_result <- c(param.best_value = prm_val.best, 
+                                best_RMSE = RMSE_min)
+
+  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
+                                parameter.value = param_vals_tmp),
+       best_result = param_values.best_result)
+}
+```
+
+#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
+\
+
+The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
+
+##### Sugnature
+\
+```{r eval=FALSE}
+model.tune.param_range <- function(loop_starter,
+                             tune_dir_path,
+                             cache_file_base_name,
+                             fn_tune.test.param_value,
+                             max.identical.min_RMSE.count = 4,
+                             endpoint.min_diff = 0,
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+  # ...
+  list(best_result = param_values.best_result,
+       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
+       tuned.result = data.frame(parameter.value = parameter.value,
+                                 RMSE = result.RMSE))
+}
+```
+
+##### **Parameters**
+\
+
+::: { #func.model.tune.param_range.params.loop_starter .sidebar }
+###### ***loop_starter***
+\
+A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
+`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
+For this purpose, the sequence step is calculated as follows:
+$$
+step = \frac{end - start}{dvs}
+$$
+
+The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
+```{r eval=FALSE}
+seq(start, end, step)
+```  
+In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
+:::
+
+::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
+###### ***tune_dir_path***
+\
+To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
+:::
+
+::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
+###### ***cache_file_base_name***
+\
+The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
+:::
+
+::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
+###### ***fn_tune.test.param_value***
+\
+This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+:::
+
+::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
+###### ***max.identical.min_RMSE.count = 4***
+\
+If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
+When it is reached, the algorithm considers the task execution to be complete.
+:::
+
+::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
+###### ***endpoint.min_diff = 0***
+\
+Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
+:::
+
+::: { #func.model.tune.param_range.params.break.if_min .sidebar }
+###### ***break.if_min = TRUE***
+\
+This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+:::
+
+::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
+###### ***steps.beyond_min = 2***
+\
+This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+
+::: { #func.model.tune.param_range.details .sidebar }
+##### **Details** 
+\
+First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
+
+The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
+
+Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
+
+The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
+The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
+
+Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
+
+The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
+:::
+
+##### **Value**
+\
+
+A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
+```{r eval=FALSE}
+  list(best_result = param_values.best_result,
+       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
+       tuned.result = data.frame(parameter.value = parameter.value,
+                                 RMSE = result.RMSE))
+```
+
+::: {#func.model.tune.param_range.code .sidebar }
+##### Source Code
+\
+Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
+```{r eval=FALSE}
+model.tune.param_range <- function(loop_starter,
+                             tune_dir_path,
+                             cache_file_base_name,
+                             fn_tune.test.param_value,
+                             max.identical.min_RMSE.count = 4,
+                             is.cv = TRUE,
+                             endpoint.min_diff = 0, #1e-07,
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+
+  seq_start <- loop_starter[1]
+  seq_end <- loop_starter[2]
+  interval_divisor <- loop_starter[3]
+
+  if (interval_divisor < 4) {
+    interval_divisor <- 4
+  }
+
+  prm_val.leftmost <- seq_start
+  prm_val.rightmost <- seq_end
+
+  RMSE.leftmost <- NA
+  RMSE.rightmost <- NA
+
+  best_RMSE <- NA
+  param.best_value <- 0
+
+  param_values.best_result <- c(param.best_value = param.best_value, 
+                                best_RMSE = best_RMSE)
+  # Start repeat loop
+  repeat{
+    seq_increment <- (seq_end - seq_start)/interval_divisor
+
+    if (seq_increment < 0.0000000000001) {
+      warning("Function `model.tune.param_range`:
+parameter value increment is too small.")
+      break
+    }
+
+    test_param_vals <- seq(seq_start, seq_end, seq_increment)
+
+    tuned_result <- tune.model_param(test_param_vals, 
+                                  fn_tune.test.param_value,
+                                  break.if_min,
+                                  steps.beyond_min)
+
+    tuned.result <- tuned_result$tuned.result
+    plot(tuned.result$parameter.value, tuned.result$RMSE)
+
+    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
+    start.idx <- bound.idx["start"]
+    end.idx <- bound.idx["end"]
+    best_RMSE.idx <- bound.idx["best"]
+
+    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
+    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
+
+    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
+    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
+
+    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
+    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
+
+    seq_start <- prm_val.leftmost.tmp
+    seq_end <- prm_val.rightmost.tmp
+
+    if (is.na(best_RMSE)) {
+      prm_val.leftmost <- prm_val.leftmost.tmp
+      RMSE.leftmost <- RMSE.leftmost.tmp
+
+      prm_val.rightmost <- prm_val.rightmost.tmp
+      RMSE.rightmost <- RMSE.rightmost.tmp
+
+      param.best_value <- min_RMSE.prm_val
+      best_RMSE <- min_RMSE
+    }
+
+    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
+      prm_val.leftmost <- prm_val.leftmost.tmp
+      RMSE.leftmost <- RMSE.leftmost.tmp
+    }
+
+    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
+      prm_val.rightmost <- prm_val.rightmost.tmp
+      RMSE.rightmost <- RMSE.rightmost.tmp
+    }
+
+    if (end.idx - start.idx <= 0) {
+      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
+      break
+    }
+
+    if (best_RMSE == min_RMSE) {
+      warning("Currently computed minimal RMSE equals the previously reached best one: ",
+              best_RMSE, "
+Currently computed minial value is: ", min_RMSE)
+
+      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
+        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
+                max.identical.min_RMSE.count)
+
+        param_values.best_result <-
+          get_best_param.result(tuned.result$parameter.value,
+                                tuned.result$RMSE)
+        break
+      }
+
+    } else if (best_RMSE < min_RMSE) {
+      stop("Current minimal RMSE is greater than previously computed best value: ",
+           best_RMSE, "
+Currently computed minial value is: ", min_RMSE)
+    }
+
+    best_RMSE <- min_RMSE
+    param.best_value <- min_RMSE.prm_val
+
+    param_values.best_result <- 
+      get_best_param.result(tuned.result$parameter.value, 
+                          tuned.result$RMSE)
+  }
+  # End repeat loop
+
+  n <- length(tuned.result$parameter.value)
+  parameter.value <- tuned.result$parameter.value
+  result.RMSE <- tuned.result$RMSE
+
+  if (result.RMSE[1] == best_RMSE) {
+    parameter.value[1] <- prm_val.leftmost
+    result.RMSE[1] <- RMSE.leftmost
+  }
+  if (result.RMSE[n] == best_RMSE) {
+    parameter.value[n+1] <- prm_val.rightmost
+    result.RMSE[n+1] <- RMSE.rightmost
+  }
+
+  list(best_result = param_values.best_result,
+       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
+       tuned.result = data.frame(parameter.value = parameter.value,
+                                 RMSE = result.RMSE))
+}
+```
+
+::: {.noteblock data-latex=""}
+The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
+:::
+:::
+
+#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
+\
+
+##### Sugnature
+\
+```{r eval=FALSE}
+get_fine_tune.param.endpoints.idx <- function(preset.result) {
+  # ...
+
+  c(start = i, 
+    end = j,
+    best = best_RMSE.idx)
+}
+```
+
+##### Parameters
+\
+
+::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
+###### ***preset.result***
+\
+A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
+Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
+```{r eval=FALSE}
+    tuned_result <- tune.model_param(test_param_vals, 
+                                  fn_tune.test.param_value,
+                                  break.if_min,
+                                  steps.beyond_min)
+
+    tuned.result <- tuned_result$tuned.result
+    # tuned.result = data.frame(RMSE, parameter.value)
+    # ...
+    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
+    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
+```
+:::
+
+##### Details
+\
+The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
+
+##### Value
+\
+A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start, # interval start index
+    end,   # interval end index
+    best)  # index of the best `RMSE`
+```
+
+##### Source Code
+\
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints.idx <- function(preset.result) {
+  best_RMSE <- min(preset.result$RMSE)
+  best_RMSE.idx <- which.min(preset.result$RMSE)
+  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
+
+  preset.result.N <- length(preset.result$RMSE)
+  i <- best_RMSE.idx
+  j <- i
+
+  while (i > 1) {
+    i <- i - 1
+
+    if (preset.result$RMSE[i] > best_RMSE) {
+      break
+    }
+  }
+
+  while (j < preset.result.N) {
+    j <- j + 1
+
+    if (preset.result$RMSE[j] > best_RMSE) {
+      break
+    }
+  }
+
+  c(start = i, 
+    end = j,
+    best = best_RMSE.idx)
+}
+
+```
+
+#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
+\
+
+##### Sugnature
+\
+```{r eval=FALSE}
+get_best_param.result <- function(param_values, rmses){
+  # ...
+
+  c(param.best_value = param_values[best_pvalue_idx], 
+    best_RMSE = rmses[best_pvalue_idx])
+
+```
+
+##### Parameters
+\
+A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
+
+  - **param_values:** A vector containing the values of the input parameters for tuning;; 
+  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
+
+##### Details
+\
+Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
+
+##### Value
+\
+A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
+```{r eval=FALSE}
+c(param.best_value, best_RMSE)
+```
+
+##### Source Code
+\
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
+```{r eval=FALSE}
+get_best_param.result <- function(param_values, rmses){
+  best_pvalue_idx <- which.min(rmses)
+  c(param.best_value = param_values[best_pvalue_idx], 
+    best_RMSE = rmses[best_pvalue_idx])
+```
+
+### Support Functions
+
+#### [func.00]() Function {#func.00}
+\
+
+::: { #func.00.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.00.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.00.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.00.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.00.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+#### [func]() Function {#func.01}
+\
+
+::: { #func.01.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.01.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.01.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.01.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.01.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+#### [func]() Function {#func.02}
+\
+
+::: { #func.02.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.02.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.02.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.02.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.02.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+#### [func.0]() Function {#func.0}
+\
+
+::: { #func.0.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.0.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.0.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.0.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.0.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+#### [func1]() Function {#func.03}
+\
+
+::: { #func.03.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.03.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.03.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.03.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.03.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+:::
+
+#### [func1]() Function {#func.1}
+\
+
+::: { #func.1.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.1.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.1.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.1.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.1.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+#### [func.2]() Function {#func.2}
+\
+
+::: { #func.2.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.2.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.2.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.2.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.2.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+--------------------------------------------------------------------------------
+
+#### [func.3]() Function {#func.3}
+\
+
+::: { #func.3.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.3.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.3.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.3.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.3.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+#### [func.4]() Function {#func.4}
+\
+
+::: { #func.4.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.4.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.4.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.4.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.4.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+#### [func.5]() Function {#func.5}
+\
+
+::: { #func.5.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.5.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.5.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.5.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.5.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+#### [func.6]() Function {#func.6}
+\
+
+::: { #func.6.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.6.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.6.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.6.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.6.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+#### [func.7]() Function {#func.7}
+\
+
+::: { #func.7.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.7.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.7.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.7.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.7.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+#### [func.8]() Function {#func.8}
+\
+
+::: { #func.8.signature .sidebar }
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.8.params .sidebar }
+##### Parameters
+\
+  - **param1:** description; 
+  - **param2:** description.
+
+:::
+
+::: { #func.8.details .sidebar }
+##### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.8.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.8.code .sidebar }
+##### Source Code
+\
+The soure code of the [function]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+:::
+
+--------------------------------------------------------------------------------
+
+#### []() Function {#func.3-1}
+\
+
+##### Sugnature
+\
+```{r eval=FALSE}
+
+```
+
+##### Parameters
+\
+  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
+  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
+
+##### Details
+\
+During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+
+##### Value
+\
+
+##### Source Code
+\
+Below is the most significant part of the code of the [function]() function:
+```{r eval=FALSE}
+
+```
+
+================================================================================
+
+```{r eval=FALSE}
+
+```
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+::: {.noteblock data-latex=""}
+!!! Note!
+:::
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```
+
+```{r eval=FALSE}
+
+```

### 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
Report Appendix: minor fix.

@@
 \
+
 ::: {.noteblock data-latex=""}

### 2025-05-13 reports/capstone-movielens-report.draft4.Rmd

@@
 
-### Regularization: Common Helper Functions
+## Regularization: Common Helper Functions
 \
@@
 
-#### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
+### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
 \
@@
 
-##### Sugnature
+#### Sugnature
 \
@@
 
-##### Parameters
+#### Parameters
 \
@@
 
-##### Details
+#### Details
 \
@@
 ::: { #func.tune.model_param.value .sidebar }
-##### Value
+#### Value
 \
@@
 
-##### Source Code
+#### Source Code
 \
@@
 
-#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
+### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
 \
@@
 
-##### **Parameters**
+#### **Parameters**
 \
@@
 ::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-###### ***loop_starter***
+##### ***loop_starter***
 \
@@
 ::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-###### ***tune_dir_path***
+##### ***tune_dir_path***
 \
@@
 ::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-###### ***cache_file_base_name***
+##### ***cache_file_base_name***
 \
@@
 ::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-###### ***fn_tune.test.param_value***
+##### ***fn_tune.test.param_value***
 \
@@
 ::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-###### ***max.identical.min_RMSE.count = 4***
+##### ***max.identical.min_RMSE.count = 4***
 \
@@
 ::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-###### ***endpoint.min_diff = 0***
+##### ***endpoint.min_diff = 0***
 \
@@
 ::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-###### ***break.if_min = TRUE***
+##### ***break.if_min = TRUE***
 \
@@
 ::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-###### ***steps.beyond_min = 2***
+##### ***steps.beyond_min = 2***
 \
@@
 ::: { #func.model.tune.param_range.details .sidebar }
-##### **Details** 
+#### **Details** 
 \
@@
 
-##### **Value**
+#### **Value**
 \
@@
 ::: {#func.model.tune.param_range.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-##### Sugnature
+### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
+\
+
+#### Sugnature
 \
@@
 ::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-###### ***preset.result***
+##### ***preset.result***
 \
@@
 
-##### Value
+#### Value
 \
@@
 
-#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-##### Sugnature
+### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
+\
+
+#### Sugnature
 \
@@
 
-### Support Functions
-
-#### [func.00]() Function {#func.00}
+## Support Functions
+
+### [func.00]() Function {#func.00}
 \
@@
 ::: { #func.00.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.00.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.00.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.00.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.00.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func]() Function {#func.01}
+### [func]() Function {#func.01}
 \
@@
 ::: { #func.01.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.01.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.01.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.01.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.01.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func]() Function {#func.02}
+### [func]() Function {#func.02}
 \
@@
 ::: { #func.02.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.02.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.02.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.02.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.02.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func.0]() Function {#func.0}
+### [func.0]() Function {#func.0}
 \
@@
 ::: { #func.0.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.0.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.0.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.0.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.0.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func1]() Function {#func.03}
+### [func1]() Function {#func.03}
 \
@@
 ::: { #func.03.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.03.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.03.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.03.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.03.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func1]() Function {#func.1}
+### [func1]() Function {#func.1}
 \
@@
 ::: { #func.1.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.1.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.1.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.1.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.1.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func.2]() Function {#func.2}
+### [func.2]() Function {#func.2}
 \
@@
 ::: { #func.2.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.2.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.2.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.2.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.2.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func.3]() Function {#func.3}
+### [func.3]() Function {#func.3}
 \
@@
 ::: { #func.3.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.3.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.3.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.3.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.3.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func.4]() Function {#func.4}
+### [func.4]() Function {#func.4}
 \
@@
 ::: { #func.4.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.4.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.4.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.4.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.4.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func.5]() Function {#func.5}
+### [func.5]() Function {#func.5}
 \
@@
 ::: { #func.5.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.5.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.5.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.5.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.5.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func.6]() Function {#func.6}
+### [func.6]() Function {#func.6}
 \
@@
 ::: { #func.6.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.6.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.6.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.6.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.6.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func.7]() Function {#func.7}
+### [func.7]() Function {#func.7}
 \
@@
 ::: { #func.7.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.7.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.7.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.7.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.7.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### [func.8]() Function {#func.8}
+### [func.8]() Function {#func.8}
 \
@@
 ::: { #func.8.signature .sidebar }
-##### Sugnature
+#### Sugnature
 \
@@
 ::: { #func.8.params .sidebar }
-##### Parameters
+#### Parameters
 \
@@
 ::: { #func.8.details .sidebar }
-##### Details
+#### Details
 \
@@
 ::: { #func.8.value .sidebar }
-##### Value
+#### Value
 \
@@
 ::: { #func.8.code .sidebar }
-##### Source Code
+#### Source Code
 \
@@
 
-#### []() Function {#func.3-1}
-\
-
-##### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-##### Parameters
+### []() Function {#func.3-1}
+\
+
+#### Sugnature
+\
+```{r eval=FALSE}
+
+```
+
+#### Parameters
 \
@@
 
-##### Value
-\
-
-##### Source Code
+#### Value
+\
+
+#### Source Code
 \

### 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
draft 4 RMD report: /newpage mark added.

@@
 Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]). 
+\newpage
 
@@
 ```
+\newpage
 
@@
 Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
+\newpage
 
@@
 That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
+\newpage
 
@@
 \
-
 ##### Movie popularity count[@MRS-R-BEST]
@@
 \
-
 ##### User rating count (activity measure)
@@
 :::
+\newpage
 
@@
 
+\newpage
+
 ### Common Helper Functions
@@
 :::
+
+\newpage
 
@@
 To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
+\newpage
 
@@
 \
+
 To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
@@
 This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
-```{r eval=FALSE}
+```{r, eval=FALSE}
 regularize.test_lambda.UM_effect.cv <- function(lambda){
@@
 ```
+
+### User+Movie Effect Model Tuning: Preconfiguratioin
+
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Appendix](#appendix.a) of this report.
+
+Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
+
+::: {.noteblock data-latex=""}
+The complete version of the code provided in this section can be found in the [Process Preliminary setting-up of lambda range for UM Effect regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
+:::
 
@@
 
-# Appendix
+# Appendix {#appendix.a}
 

### 2025-05-14 reports/capstone-movielens.site/01.intro.Rmd
Report update: splitted to multifile report.

--- 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
@@
-```{r setup, include=FALSE, echo = FALSE}
-r.path <- "../r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-# Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-# stop(main_script.file_path)
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
-# External Common Helper functions -------------------------------------
-# common_helper_functions.file_path <- file.path(support_functions.path,
-#                                             "common-helper.functions.R")
-# source(common_helper_functions.file_path, 
-#        local = knitr::knit_global())
-
-# knitr::knit_global()
-#knitr::opts_chunk$set(echo = FALSE)
-```
-
----
-title: "Capstone Movielens Report"
-author: "Azamat Kurbanaev"
-date: "`r Sys.Date()`"
-bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
-envir:
-  parent.frame()
-output: 
-  bookdown::pdf_document2: 
-    df_print: paged
-    toc: true
-    fig_caption: true
-    keep_tex: true
-    citation_package: biblatex
-colorlinks: true
-linkcolor: red
-citecolor: blue
-header-includes:
-    - \usepackage{awesomebox}
-    - \usepackage{hyperref}
-    - \usepackage[natbib=true, 
-                  style=numeric, 
-                  backref=true, 
-                  sorting=none]{biblatex}
-    - \hypersetup{backref,
-          pdfpagemode=Normal,
-          colorlinks=true,
-          implicit=false}
-vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
-  %\VignetteEncoding{UTF-8}
-  %\VignetteEngine{knitr::knitr}
----
-
-\newenvironment{infobox}[1]
-  {
-  \begin{itemize}
-  \renewcommand{\labelitemi}{
-    \raisebox{-.7\height}[0pt][0pt]{
-      {\setkeys{Gin}{width=3em,keepaspectratio}
-        \includegraphics{images/#1}}
-    }
-  }
-  \setlength{\fboxsep}{1em}
-  \begin{blackbox}
-  \item
-  }
-  {
-  \end{blackbox}
-  \end{itemize}
-  }
-
 # Introduction / Overview / Executive Summary
@@
 ```
-
-# Methods / Analysis
-::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
-:::
-
-## Defining Logging and Time Measuring Helper Functions
-\
-
-First, let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
-
-```{r eval=FALSE }
-# Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log1(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log1(msg_template, arg1, arg2))
-}
-
-# ...
-```
-
-::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## Preparing train and set datasets
-\
-
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
-To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
-```{r eval=FALSE }
-make_source_datasets()
-init_source_datasets()
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-### The `make_source_datasets` function
-\
-
-Let's take a closer look at the objects we will receive as a result of executing this function.
-
-```{r eval=FALSE}
-
-make_source_datasets <- function(){
-  # ...
-  list(edx_CV = edx_CV,
-       edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
-       tuning_sets = tuning_sets,
-       movie_map = movie_map,
-       date_days_map = date_days_map)
-}
-```
-
-#### `edx.mx` Matrix Object
-\
-
-We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
-To create this matrix, we use `tidyr::pivot_wider` function:
-
-```{r eval=FALSE}
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-
-```
-
-```{r}
-  str(edx.mx)
-```
-
-#### `edx.sgr` Object
-\
-
-To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-```
-```{r}
-str(edx.sgr)
-summary(edx.sgr)
-```
-
-Note that we use the `splitGenreRows` function to split rows of the original dataset:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function mentioned above is also available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-#### `movie_map` Object
-\
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r eval=FALSE}
-movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-```
-
-```{r}
-str(movie_map)
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
-
-#### `date_days_map` Object
-\
-
-We have a `timestamp` field in the `edx` dataset.
-To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-```
-``` {r}
-  str(date_days_map)
-  summary(date_days_map)
-```
-
-#### `edx_CV` Object
-\
-
-Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_:
-```{r eval=FALSE}
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
-```
-```{r}
-str(edx_CV)
-```
-
-::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
-:::
-
-Note that we used the `sample_train_validation_sets` function call to split the original dataset (`edx` in this case): 
-```{r eval=FALSE}
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-```
-
-which returns a pair of train/validation sets:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets ----------------------------------------------------    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)` one, from where it is called.
-:::
-
-### Common Helper Functions
-\
-
-For our further analysis, we are going to use the following _common helper functions_:
-
-#### `clamp` function
-\
-
-As explained in [Section  24.4 User effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings can’t be below 0.5 or above 5.
-For this reason, we will use the `clamp` function described in that section:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
-#### Functions to calculate _(Root) Mean Squared Error_
-\
-
-We will need the following functions to calculate _(R)MSEs_:
-```{r eval=FALSE}
-mse <- function(r) mean(r^2)
-
-mse_cv <- function(r_list) {
-  mses <- sapply(r_list, mse(r))
-  mean(mses)
-}
-
-rmse <- function(r) sqrt(mse(r))
-# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
-
-rmse2 <- function(true_ratings, predicted_ratings) {
-  rmse(true_ratings - predicted_ratings)
-}
-```
-
-::: {.noteblock data-latex=""}
-All the _common helper functions_, including those described above, are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-## Overall Mean Rating (Naive) Model
-\
-
-Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
-It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
-
-$$
-Y_{i,j} = \mu + \varepsilon_{i,j}
-$$
-
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
-
-We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
-
-```{r pressure, echo=TRUE}
-mu <- mean(edx$rating)
-print(mu)
-```
-
-If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
-```{r}
-mu.MSEs <- naive_model_MSEs(mu)
-data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
-              xname = "fold_No", 
-              yname = "MSE")
-
-mu.RMSE <- sqrt(mean(mu.MSEs))
-mu.RMSE
-```
-::: {.noteblock data-latex=""}
-For the _Mean Squared Error_ data visualization we used [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function] defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.function.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script.
-:::
-
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      # scale = 1,
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
-
-Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
-
-```{r eval=FALSE }
-naive_model_MSEs <- function(val) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - val)
-  })
-}
-```
-
-One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L59) one:
-```{r eval=FALSE }
-naive_model_RMSE <- function(val){
-  sqrt(mean(naive_model_MSEs(val)))
-}
-```
-
-### Ensure that `mu.RMSE` value is the best for the current model
-\
-
-If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r }
-  deviation <- seq(0, 6, 0.1) - 3
-
-  deviation.RMSE <- sapply(deviation, function(delta){
-    naive_model_RMSE(mu + delta)
-  })
-```
-
-Let's make a quick investigation of the `deviation.RMSE` result we have just got: 
-```{r}
-data.frame(delta = deviation, 
-           delta.RMSE = deviation.RMSE) |> 
-data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
-              xname = "delta", 
-              yname = "delta.RMSE", 
-              xlabel = TeX(r'[$\delta$]'), 
-              ylabel = "RMSE")
-
-which_min_deviation <- deviation[which.min(deviation.RMSE)]
-min_rmse = min(deviation.RMSE)
-
-print_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
-         which_min_deviation)
-
-print_log1("Is the previously computed RMSE the best for the current model: %1",
-         mu.RMSE == min_rmse)
-```
-```{r eval=FALSE}
-RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
-  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.OMR)
-```
-
-To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
-
-## User Effect Model
-\
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
-```{r}
-hist(edx.user_mean_ratings$mean_rating, nclass = 30)
-```
-
-Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
-The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
-So we write the model as follows:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
-$$
-
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
-
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we can compute them this way:
-```{r eval=FALSE}
-a <- rowMeans(y - mu, na.rm = TRUE)
-```
-
-These considerations alows us to compute a _User Mean Ratings_ the following way:
-```{r eval=FALSE}
-put_log("Computing Average Ratings per User (User Mean Ratings)...")
-user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
-user_ratings.n <- rowSums(!is.na(edx.mx))
-
-edx.user_mean_ratings <- 
-  data.frame(userId = names(user.mean_ratings), 
-             mean_rating = user.mean_ratings,
-             n = user_ratings.n)
-
-put_log("User Mean Ratings have been computed.")
-```
-```{r}
-str(edx.user_mean_ratings)
-```
-
-And then we compute a _User Effect_ this way:
-```{r eval=FALSE}
-put_log("Computing User Effect per users ...")
-edx.user_effect <- edx.user_mean_ratings |>
-  mutate(userId = as.integer(userId),
-         a = mean_rating - mu)
-
-put_log("A User Effect Model has been builded")
-```
-```{r}
-par(cex = 0.7)
-hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
-     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
-
-str(edx.user_effect)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect_ computation is available in the [Model building: User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L531) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Finally, we are ready to compute the `RMSE` (additionally using the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) helper function we defined above to keep predictions in the proper range):
-```{r eval=FALSE}
-put_log("Computing the RMSE taking into account user effects...")
-start <- put_start_date()
-edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
-  cv_fold_dat$validation_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - clamp(mu + a)) |> 
-    pull(resid) |> mse()
-})
-put_end_date(start)
-
-edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
-
-RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
-  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
-```
-```{r}
-data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the User Effect Model",
-            xname = "fold_No", 
-            yname = "MSE")
-
-RMSE_kable(RMSEs.ResultTibble.UE)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## User+Movie Effect (UME) Model
-\
-
-In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
-He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
-$$
-The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:
-
-```{r eval=FALSE}
-b <- colMeans(y - mu - a, na.rm = TRUE)
-```
-
-Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
-
-### UME Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
-:::
-
-#### `train_user_movie_effect` Function
-\
-
-We use this function to build and train our model using the `train_set` dataset:
-```{r eval=FALSE}
-train_user_movie_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_effect
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need for the *Regularization*.
-We will explain that later in the [Regularization Method] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the `mean_reg` function is equivalent to the simple `mean` one.
-:::
-
-```{r eval=FALSE}
-# Regularization --------------------------------------------------------------
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-#### `train_user_movie_effect.cv` Function
-\
-
-We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method.
-Below, we provide the most important part of the code of that function:
-```{r eval=FALSE}
-train_user_movie_effect.cv <- function(lambda = 0){
-# ...
-  start <- put_start_date()
-  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
-  })
-  put_end_date(start)
-  put_log("Function: train_user_movie_effect.cv:
-User+Movie Effect list have been computed")
-
-  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-
-  user_movie_effect <- user_movie_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  # ...
-  user_movie_effect
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the `Cross Validation` results.
-:::
-```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
-```
-
-#### `calc_user_movie_effect_MSE` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE <- function(test_set, um_effect){
-  mse.result <- test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(um_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    pull(resid) |> mse()
-
-  stopifnot(!is.na(mse.result))
-  mse.result
-}
-```
-
-#### `calc_user_movie_effect_MSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv <- function(um_effect){
-  put_log("Function: user_movie_effects_MSE.cv:
-Computing the RMSE taking into account User+Movie Effects...")
-  start <- put_start_date()
-  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
-  })
-  put_end_date(start)
-
-  put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_effects_MSEs)
-}
-
-```
-
-#### `calc_user_movie_effect_RMSE` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-  sqrt(mse)
-}
-```
-
-#### `calc_user_movie_effect_RMSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
-  um_effect_RMSE
-}
-
-```
-
-### Model Building
-\
-
-::: {.noteblock data-latex=""}
-The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
-```{r eval=FALSE}
-  cv.UM_effect <- train_user_movie_effect.cv()
-```
-```{r}
-str(cv.UM_effect)
-
-par(cex = 0.7)
-hist(cv.UM_effect$b, 30, xlab = TeX(r'[$\hat{beta}_{j}$)]'),
-     main = TeX(r'[Histogram of $\hat{beta}_{j}$]'))
-```
-
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
-```{r eval=FALSE}
-cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
-
-RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
-  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
-
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.UME)
-```
-
-## Regularizing User+Movie Effect Model
-
-### Utilizing Penalized least squares
-\
-[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-
-$$ 
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
-$$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-
-$$
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-where $n_j$ is the number of ratings made for movie $j$.
-
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
-
-  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
-
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
-
-### UME Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-
-#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
-\
-
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
-```{r eval=FALSE}
-regularize.test_lambda.UM_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UM_effect.cv
-`lambda` is `NA`")
-  }
-  um_effect <- train_user_movie_effect.cv(lambda)
-  calc_user_movie_effect_RMSE.cv(um_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_effect.cv]() calling it from the [regularize.test_lambda.UM_effect.cv](), but now with the $\lambda$ parameter different from the default (zero) value.
-:::
-
-Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r eval=FALSE}
-# Here we will simply compute the RMSE for different values of `lambda` 
-n <- colSums(!is.na(y))
-
-sums <- colSums(y - mu - a, na.rm = TRUE)
-lambdas <- seq(0, 10, 0.1)
-
-rmses <- sapply(lambdas, function(lambda){
-  b <-  sums / (n + lambda)
-  reg_rmse(b)
-})
-
-# Here is a plot of the RMSE versus `lambda`:
-plot(lambdas, rmses, type = "l")
-```
-Now we can determine the minimal _RMSE_:
-```{r}
-# print(min(rmses))
-```
-
-which is achieved for the following $\lambda$:
-```{r eval=FALSE}
-lambda <- lambdas[which.min(rmses)] 
-print(lambda)
-```
-
-Using this $\lambda$ we can compute the regularized estimates:
-```{r eval=FALSE}
-b_reg <- sums / (n + lambda)
-
-str(b_reg)
-```
-Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r eval=FALSE}
-reg_rmse(b_reg)
-```
-
-## Accounting for Date effects
-
-#### Yearly rating count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(count = n())
-)
-```
-
-#### Average rating per year plot[@MRS-R-BEST]
-\
-```{r}
-edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(rating_avg = mean(rating)) |>
-  ggplot(aes(x = year, y = rating_avg)) +
-  geom_bar(stat = "identity", fill = "#8888ff") + 
-  ggtitle("Average rating per year") +
-  xlab("Year") +
-  ylab("Average rating") +
-  scale_y_continuous(labels = comma) + 
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-We use the following models to account for the `date` effect:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
-$$
-
-## Accounting for Genre effect
-\
-As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
-This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
-
-### Genre Data Analysis
-\
-#### Movie Genres Data 
-\
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r eval=FALSE}
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r eval=FALSE}
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r eval=FALSE}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r eval=FALSE}
-print(edx |> group_by(rating) |> summarize(count = n()))
-```
-
-We can visually see that from the following plot:
-```{r eval=FALSE}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
-#### Movie Genres Effect 
-\
-
-The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
-
-```{r eval=FALSE}
-# Preparing data for plotting:
-genre_ratins_grp <- train_set |> 
-  mutate(genre_categories = as.factor(genres)) |>
-  group_by(genre_categories) |>
-  summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
-  filter(n > 20000) |> 
-  mutate(genres = reorder(genre_categories, rating_avg)) |>
-  select(genres, rating_avg, se, n)
-
-dim(genre_ratins_grp)
-genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
-print(genre_ratins_grp_sorted)
-
-# Creating plot:
-genre_ratins_grp |> 
-  ggplot(aes(x = genres, y = rating_avg, ymin = rating_avg - 2*se, ymax = rating_avg + 2*se)) + 
-  geom_point() +
-  geom_errorbar() + 
-  ggtitle("Average rating per Genre") +
-  ylab("Average rating") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-```
-Below are worst and best ratings categories:
-```{r eval=FALSE}
-sprintf("The worst ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.min(genre_ratins_grp$genres)])
-
-sprintf("The best ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.max(genre_ratins_grp$genres)])
-```
-
-Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
-```{r eval=FALSE}
-# For better visibility, we reduce the data for plotting 
-# while keeping the worst and best rating rows:
-plot_ind <- odd(1:nrow(genre_ratins_grp))
-plot_dat <- genre_ratins_grp_sorted[plot_ind,]
-
-plot_dat |>
-  ggplot(aes(x = rating_avg, y = genres)) +
-  ggtitle("Genre Average Rating") +
-  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
-  xlab("Average ratings") +
-  ylab("Genres") +
-  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
-  theme_economist() +
-  theme(plot.title = element_text(vjust = 3.5),
-        axis.title.x = element_text(vjust = -5, face = "bold"),
-        axis.title.y = element_text(vjust = 10, face = "bold"),
-        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
-        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-
-To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
-$$
-
-where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p.
-712) book[@RRSK_RS_HB].
-
-In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:
-
-$$
-g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
-$$
-
-with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
-$$
-
-$$
- \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-# Conclusion
-
-Hello Conclusion!
-
-This is a great conclusion, isn't it?!!
-
-# Appendix
-
-## Regularization: Common Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-#### Parameters
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-#### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-#### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-#### **Parameters**
-\
-
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-##### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-##### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-##### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-##### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-##### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-##### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-##### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-##### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-#### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-#### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-#### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
-:::
-:::
-
-### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-#### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-##### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-#### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-#### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-#### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-#### Parameters
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-#### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-#### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-#### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-## Support Functions
-
-### [func.00]() Function {#func.00}
-\
-
-::: { #func.00.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.00.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.00.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.00.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.00.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.01}
-\
-
-::: { #func.01.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.01.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.01.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.01.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.01.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.02}
-\
-
-::: { #func.02.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.02.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.02.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.02.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.02.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.0]() Function {#func.0}
-\
-
-::: { #func.0.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.0.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.0.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.0.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func1]() Function {#func.03}
-\
-
-::: { #func.03.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.03.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.03.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.03.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.03.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [func1]() Function {#func.1}
-\
-
-::: { #func.1.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.1.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.1.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.1.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.1.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.2]() Function {#func.2}
-\
-
-::: { #func.2.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.2.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.2.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.2.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.2.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
---------------------------------------------------------------------------------
-
-### [func.3]() Function {#func.3}
-\
-
-::: { #func.3.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.3.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.3.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.3.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.3.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.4]() Function {#func.4}
-\
-
-::: { #func.4.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.4.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.4.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.4.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.4.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.5]() Function {#func.5}
-\
-
-::: { #func.5.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.5.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.5.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.5.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.5.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.6]() Function {#func.6}
-\
-
-::: { #func.6.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.6.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.6.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.6.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.6.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.7]() Function {#func.7}
-\
-
-::: { #func.7.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.7.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.7.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.7.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.7.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.8]() Function {#func.8}
-\
-
-::: { #func.8.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.8.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.8.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.8.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.8.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### []() Function {#func.3-1}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-#### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-#### Value
-\
-
-#### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-================================================================================
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
+\newpage

### 2025-05-14 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Report update: splitted to multifile report.

--- 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
@@
-```{r setup, include=FALSE, echo = FALSE}
-r.path <- "../r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-# Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-# stop(main_script.file_path)
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
-# External Common Helper functions -------------------------------------
-# common_helper_functions.file_path <- file.path(support_functions.path,
-#                                             "common-helper.functions.R")
-# source(common_helper_functions.file_path, 
-#        local = knitr::knit_global())
-
-# knitr::knit_global()
-#knitr::opts_chunk$set(echo = FALSE)
-```
-
----
-title: "Capstone Movielens Report"
-author: "Azamat Kurbanaev"
-date: "`r Sys.Date()`"
-bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
-envir:
-  parent.frame()
-output: 
-  bookdown::pdf_document2: 
-    df_print: paged
-    toc: true
-    fig_caption: true
-    keep_tex: true
-    citation_package: biblatex
-colorlinks: true
-linkcolor: red
-citecolor: blue
-header-includes:
-    - \usepackage{awesomebox}
-    - \usepackage{hyperref}
-    - \usepackage[natbib=true, 
-                  style=numeric, 
-                  backref=true, 
-                  sorting=none]{biblatex}
-    - \hypersetup{backref,
-          pdfpagemode=Normal,
-          colorlinks=true,
-          implicit=false}
-vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
-  %\VignetteEncoding{UTF-8}
-  %\VignetteEngine{knitr::knitr}
----
-
-\newenvironment{infobox}[1]
-  {
-  \begin{itemize}
-  \renewcommand{\labelitemi}{
-    \raisebox{-.7\height}[0pt][0pt]{
-      {\setkeys{Gin}{width=3em,keepaspectratio}
-        \includegraphics{images/#1}}
-    }
-  }
-  \setlength{\fboxsep}{1em}
-  \begin{blackbox}
-  \item
-  }
-  {
-  \end{blackbox}
-  \end{itemize}
-  }
-
-# Introduction / Overview / Executive Summary
-
-The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
-$$
-\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
-$$
-
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
-
-Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).
-
-## Datasets Overview
-
-To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
-
-* **edx:** we use it to develop and train our algorithms;
-* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
-
-For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
-The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
-
-Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r eval=FALSE }
-if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
-
-library(edx.capstone.movielens.data)
-edx <- edx.capstone.movielens.data::edx
-final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
-```
-
-Now, we have the datasets listed above:
-```{r }
-summary(edx)
-```
-
-```{r }
-summary(final_holdout_test)
-```
-
-### `edx` Dataset
-\
-Let's look into the details of the `edx` dataset:
-``` {r echo = TRUE}
-str(edx)
-```
-Note that we have 9000055 rows and six columns in there:  
-```{r }
-dim_edx <- dim(edx)
-print(dim_edx)
-```
-
-First, let's note that we have 10677 different movies: 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
-
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
-
-```
-
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
-
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Finally, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
-```{r }
-#library(dplyr)
-s <- edx |> group_by(rating) |>
-  summarise(n = n())
-print(s)
-```
-
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
-
-#### Rating distribution plot[@MRS-R-BEST]
-\
-The code below demonstrates another way of visualizing the rating distribution:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-
-```
-
-This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-
-#### Ratings per movie
-\
-
-##### Movie popularity count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  group_by(movieId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-```{r}
-summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per movie plot[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Movies' rating histogram[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-#### Ratings per user[@MRS-R-BEST]
-\
-
-##### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-##### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-# Methods / Analysis
-::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
-:::
-
-## Defining Logging and Time Measuring Helper Functions
-\
-
-First, let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
-
-```{r eval=FALSE }
-# Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log1(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log1(msg_template, arg1, arg2))
-}
-
-# ...
-```
-
-::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## Preparing train and set datasets
-\
-
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
-To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
-```{r eval=FALSE }
-make_source_datasets()
-init_source_datasets()
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-### The `make_source_datasets` function
-\
-
-Let's take a closer look at the objects we will receive as a result of executing this function.
-
-```{r eval=FALSE}
-
-make_source_datasets <- function(){
-  # ...
-  list(edx_CV = edx_CV,
-       edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
-       tuning_sets = tuning_sets,
-       movie_map = movie_map,
-       date_days_map = date_days_map)
-}
-```
-
-#### `edx.mx` Matrix Object
-\
-
-We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
-To create this matrix, we use `tidyr::pivot_wider` function:
-
-```{r eval=FALSE}
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-
-```
-
-```{r}
-  str(edx.mx)
-```
-
-#### `edx.sgr` Object
-\
-
-To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-```
-```{r}
-str(edx.sgr)
-summary(edx.sgr)
-```
-
-Note that we use the `splitGenreRows` function to split rows of the original dataset:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function mentioned above is also available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-#### `movie_map` Object
-\
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r eval=FALSE}
-movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-```
-
-```{r}
-str(movie_map)
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
-
-#### `date_days_map` Object
-\
-
-We have a `timestamp` field in the `edx` dataset.
-To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-```
-``` {r}
-  str(date_days_map)
-  summary(date_days_map)
-```
-
-#### `edx_CV` Object
-\
-
-Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_:
-```{r eval=FALSE}
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
-```
-```{r}
-str(edx_CV)
-```
-
-::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
-:::
-
-Note that we used the `sample_train_validation_sets` function call to split the original dataset (`edx` in this case): 
-```{r eval=FALSE}
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-```
-
-which returns a pair of train/validation sets:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets ----------------------------------------------------    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)` one, from where it is called.
-:::
-
-### Common Helper Functions
-\
-
-For our further analysis, we are going to use the following _common helper functions_:
-
-#### `clamp` function
-\
-
-As explained in [Section  24.4 User effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings can’t be below 0.5 or above 5.
-For this reason, we will use the `clamp` function described in that section:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
-#### Functions to calculate _(Root) Mean Squared Error_
-\
-
-We will need the following functions to calculate _(R)MSEs_:
-```{r eval=FALSE}
-mse <- function(r) mean(r^2)
-
-mse_cv <- function(r_list) {
-  mses <- sapply(r_list, mse(r))
-  mean(mses)
-}
-
-rmse <- function(r) sqrt(mse(r))
-# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
-
-rmse2 <- function(true_ratings, predicted_ratings) {
-  rmse(true_ratings - predicted_ratings)
-}
-```
-
-::: {.noteblock data-latex=""}
-All the _common helper functions_, including those described above, are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
 ## Overall Mean Rating (Naive) Model
@@
 
-## User Effect Model
-\
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
-```{r}
-hist(edx.user_mean_ratings$mean_rating, nclass = 30)
-```
-
-Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
-The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
-So we write the model as follows:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
-$$
-
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
-
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we can compute them this way:
-```{r eval=FALSE}
-a <- rowMeans(y - mu, na.rm = TRUE)
-```
-
-These considerations alows us to compute a _User Mean Ratings_ the following way:
-```{r eval=FALSE}
-put_log("Computing Average Ratings per User (User Mean Ratings)...")
-user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
-user_ratings.n <- rowSums(!is.na(edx.mx))
-
-edx.user_mean_ratings <- 
-  data.frame(userId = names(user.mean_ratings), 
-             mean_rating = user.mean_ratings,
-             n = user_ratings.n)
-
-put_log("User Mean Ratings have been computed.")
-```
-```{r}
-str(edx.user_mean_ratings)
-```
-
-And then we compute a _User Effect_ this way:
-```{r eval=FALSE}
-put_log("Computing User Effect per users ...")
-edx.user_effect <- edx.user_mean_ratings |>
-  mutate(userId = as.integer(userId),
-         a = mean_rating - mu)
-
-put_log("A User Effect Model has been builded")
-```
-```{r}
-par(cex = 0.7)
-hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
-     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
-
-str(edx.user_effect)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect_ computation is available in the [Model building: User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L531) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Finally, we are ready to compute the `RMSE` (additionally using the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) helper function we defined above to keep predictions in the proper range):
-```{r eval=FALSE}
-put_log("Computing the RMSE taking into account user effects...")
-start <- put_start_date()
-edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
-  cv_fold_dat$validation_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - clamp(mu + a)) |> 
-    pull(resid) |> mse()
-})
-put_end_date(start)
-
-edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
-
-RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
-  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
-```
-```{r}
-data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the User Effect Model",
-            xname = "fold_No", 
-            yname = "MSE")
-
-RMSE_kable(RMSEs.ResultTibble.UE)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## User+Movie Effect (UME) Model
-\
-
-In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
-He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
-$$
-The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:
-
-```{r eval=FALSE}
-b <- colMeans(y - mu - a, na.rm = TRUE)
-```
-
-Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
-
-### UME Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
-:::
-
-#### `train_user_movie_effect` Function
-\
-
-We use this function to build and train our model using the `train_set` dataset:
-```{r eval=FALSE}
-train_user_movie_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_effect
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need for the *Regularization*.
-We will explain that later in the [Regularization Method] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the `mean_reg` function is equivalent to the simple `mean` one.
-:::
-
-```{r eval=FALSE}
-# Regularization --------------------------------------------------------------
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-#### `train_user_movie_effect.cv` Function
-\
-
-We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method.
-Below, we provide the most important part of the code of that function:
-```{r eval=FALSE}
-train_user_movie_effect.cv <- function(lambda = 0){
-# ...
-  start <- put_start_date()
-  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
-  })
-  put_end_date(start)
-  put_log("Function: train_user_movie_effect.cv:
-User+Movie Effect list have been computed")
-
-  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-
-  user_movie_effect <- user_movie_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  # ...
-  user_movie_effect
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the `Cross Validation` results.
-:::
-```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
-```
-
-#### `calc_user_movie_effect_MSE` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE <- function(test_set, um_effect){
-  mse.result <- test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(um_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    pull(resid) |> mse()
-
-  stopifnot(!is.na(mse.result))
-  mse.result
-}
-```
-
-#### `calc_user_movie_effect_MSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv <- function(um_effect){
-  put_log("Function: user_movie_effects_MSE.cv:
-Computing the RMSE taking into account User+Movie Effects...")
-  start <- put_start_date()
-  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
-  })
-  put_end_date(start)
-
-  put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_effects_MSEs)
-}
-
-```
-
-#### `calc_user_movie_effect_RMSE` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-  sqrt(mse)
-}
-```
-
-#### `calc_user_movie_effect_RMSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
-  um_effect_RMSE
-}
-
-```
-
-### Model Building
-\
-
-::: {.noteblock data-latex=""}
-The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
-```{r eval=FALSE}
-  cv.UM_effect <- train_user_movie_effect.cv()
-```
-```{r}
-str(cv.UM_effect)
-
-par(cex = 0.7)
-hist(cv.UM_effect$b, 30, xlab = TeX(r'[$\hat{beta}_{j}$)]'),
-     main = TeX(r'[Histogram of $\hat{beta}_{j}$]'))
-```
-
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
-```{r eval=FALSE}
-cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
-
-RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
-  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
-
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.UME)
-```
-
-## Regularizing User+Movie Effect Model
-
-### Utilizing Penalized least squares
-\
-[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-
-$$ 
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
-$$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-
-$$
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-where $n_j$ is the number of ratings made for movie $j$.
-
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
-
-  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
-
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
-
-### UME Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-
-#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
-\
-
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
-```{r eval=FALSE}
-regularize.test_lambda.UM_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UM_effect.cv
-`lambda` is `NA`")
-  }
-  um_effect <- train_user_movie_effect.cv(lambda)
-  calc_user_movie_effect_RMSE.cv(um_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_effect.cv]() calling it from the [regularize.test_lambda.UM_effect.cv](), but now with the $\lambda$ parameter different from the default (zero) value.
-:::
-
-Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r eval=FALSE}
-# Here we will simply compute the RMSE for different values of `lambda` 
-n <- colSums(!is.na(y))
-
-sums <- colSums(y - mu - a, na.rm = TRUE)
-lambdas <- seq(0, 10, 0.1)
-
-rmses <- sapply(lambdas, function(lambda){
-  b <-  sums / (n + lambda)
-  reg_rmse(b)
-})
-
-# Here is a plot of the RMSE versus `lambda`:
-plot(lambdas, rmses, type = "l")
-```
-Now we can determine the minimal _RMSE_:
-```{r}
-# print(min(rmses))
-```
-
-which is achieved for the following $\lambda$:
-```{r eval=FALSE}
-lambda <- lambdas[which.min(rmses)] 
-print(lambda)
-```
-
-Using this $\lambda$ we can compute the regularized estimates:
-```{r eval=FALSE}
-b_reg <- sums / (n + lambda)
-
-str(b_reg)
-```
-Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r eval=FALSE}
-reg_rmse(b_reg)
-```
-
-## Accounting for Date effects
-
-#### Yearly rating count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(count = n())
-)
-```
-
-#### Average rating per year plot[@MRS-R-BEST]
-\
-```{r}
-edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(rating_avg = mean(rating)) |>
-  ggplot(aes(x = year, y = rating_avg)) +
-  geom_bar(stat = "identity", fill = "#8888ff") + 
-  ggtitle("Average rating per year") +
-  xlab("Year") +
-  ylab("Average rating") +
-  scale_y_continuous(labels = comma) + 
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-We use the following models to account for the `date` effect:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
-$$
-
-## Accounting for Genre effect
-\
-As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
-This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
-
-### Genre Data Analysis
-\
-#### Movie Genres Data 
-\
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r eval=FALSE}
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r eval=FALSE}
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r eval=FALSE}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r eval=FALSE}
-print(edx |> group_by(rating) |> summarize(count = n()))
-```
-
-We can visually see that from the following plot:
-```{r eval=FALSE}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
-#### Movie Genres Effect 
-\
-
-The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
-
-```{r eval=FALSE}
-# Preparing data for plotting:
-genre_ratins_grp <- train_set |> 
-  mutate(genre_categories = as.factor(genres)) |>
-  group_by(genre_categories) |>
-  summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
-  filter(n > 20000) |> 
-  mutate(genres = reorder(genre_categories, rating_avg)) |>
-  select(genres, rating_avg, se, n)
-
-dim(genre_ratins_grp)
-genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
-print(genre_ratins_grp_sorted)
-
-# Creating plot:
-genre_ratins_grp |> 
-  ggplot(aes(x = genres, y = rating_avg, ymin = rating_avg - 2*se, ymax = rating_avg + 2*se)) + 
-  geom_point() +
-  geom_errorbar() + 
-  ggtitle("Average rating per Genre") +
-  ylab("Average rating") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-```
-Below are worst and best ratings categories:
-```{r eval=FALSE}
-sprintf("The worst ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.min(genre_ratins_grp$genres)])
-
-sprintf("The best ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.max(genre_ratins_grp$genres)])
-```
-
-Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
-```{r eval=FALSE}
-# For better visibility, we reduce the data for plotting 
-# while keeping the worst and best rating rows:
-plot_ind <- odd(1:nrow(genre_ratins_grp))
-plot_dat <- genre_ratins_grp_sorted[plot_ind,]
-
-plot_dat |>
-  ggplot(aes(x = rating_avg, y = genres)) +
-  ggtitle("Genre Average Rating") +
-  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
-  xlab("Average ratings") +
-  ylab("Genres") +
-  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
-  theme_economist() +
-  theme(plot.title = element_text(vjust = 3.5),
-        axis.title.x = element_text(vjust = -5, face = "bold"),
-        axis.title.y = element_text(vjust = 10, face = "bold"),
-        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
-        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-
-To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
-$$
-
-where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p.
-712) book[@RRSK_RS_HB].
-
-In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:
-
-$$
-g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
-$$
-
-with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
-$$
-
-$$
- \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-# Conclusion
-
-Hello Conclusion!
-
-This is a great conclusion, isn't it?!!
-
-# Appendix
-
-## Regularization: Common Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-#### Parameters
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-#### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-#### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-#### **Parameters**
-\
-
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-##### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-##### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-##### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-##### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-##### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-##### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-##### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-##### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-#### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-#### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-#### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
-:::
-:::
-
-### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-#### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-##### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-#### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-#### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-#### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-#### Parameters
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-#### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-#### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-#### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-## Support Functions
-
-### [func.00]() Function {#func.00}
-\
-
-::: { #func.00.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.00.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.00.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.00.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.00.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.01}
-\
-
-::: { #func.01.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.01.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.01.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.01.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.01.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.02}
-\
-
-::: { #func.02.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.02.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.02.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.02.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.02.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.0]() Function {#func.0}
-\
-
-::: { #func.0.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.0.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.0.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.0.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func1]() Function {#func.03}
-\
-
-::: { #func.03.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.03.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.03.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.03.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.03.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [func1]() Function {#func.1}
-\
-
-::: { #func.1.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.1.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.1.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.1.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.1.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.2]() Function {#func.2}
-\
-
-::: { #func.2.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.2.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.2.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.2.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.2.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
---------------------------------------------------------------------------------
-
-### [func.3]() Function {#func.3}
-\
-
-::: { #func.3.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.3.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.3.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.3.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.3.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.4]() Function {#func.4}
-\
-
-::: { #func.4.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.4.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.4.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.4.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.4.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.5]() Function {#func.5}
-\
-
-::: { #func.5.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.5.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.5.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.5.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.5.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.6]() Function {#func.6}
-\
-
-::: { #func.6.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.6.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.6.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.6.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.6.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.7]() Function {#func.7}
-\
-
-::: { #func.7.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.7.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.7.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.7.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.7.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.8]() Function {#func.8}
-\
-
-::: { #func.8.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.8.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.8.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.8.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.8.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### []() Function {#func.3-1}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-#### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-#### Value
-\
-
-#### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-================================================================================
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
+\newpage

### 2025-05-14 reports/capstone-movielens.site/02.4.UE-model.Rmd
Report update: splitted to multifile report.

--- 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
@@
-```{r setup, include=FALSE, echo = FALSE}
-r.path <- "../r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-# Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-# stop(main_script.file_path)
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
-# External Common Helper functions -------------------------------------
-# common_helper_functions.file_path <- file.path(support_functions.path,
-#                                             "common-helper.functions.R")
-# source(common_helper_functions.file_path, 
-#        local = knitr::knit_global())
-
-# knitr::knit_global()
-#knitr::opts_chunk$set(echo = FALSE)
-```
-
----
-title: "Capstone Movielens Report"
-author: "Azamat Kurbanaev"
-date: "`r Sys.Date()`"
-bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
-envir:
-  parent.frame()
-output: 
-  bookdown::pdf_document2: 
-    df_print: paged
-    toc: true
-    fig_caption: true
-    keep_tex: true
-    citation_package: biblatex
-colorlinks: true
-linkcolor: red
-citecolor: blue
-header-includes:
-    - \usepackage{awesomebox}
-    - \usepackage{hyperref}
-    - \usepackage[natbib=true, 
-                  style=numeric, 
-                  backref=true, 
-                  sorting=none]{biblatex}
-    - \hypersetup{backref,
-          pdfpagemode=Normal,
-          colorlinks=true,
-          implicit=false}
-vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
-  %\VignetteEncoding{UTF-8}
-  %\VignetteEngine{knitr::knitr}
----
-
-\newenvironment{infobox}[1]
-  {
-  \begin{itemize}
-  \renewcommand{\labelitemi}{
-    \raisebox{-.7\height}[0pt][0pt]{
-      {\setkeys{Gin}{width=3em,keepaspectratio}
-        \includegraphics{images/#1}}
-    }
-  }
-  \setlength{\fboxsep}{1em}
-  \begin{blackbox}
-  \item
-  }
-  {
-  \end{blackbox}
-  \end{itemize}
-  }
-
-# Introduction / Overview / Executive Summary
-
-The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
-$$
-\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
-$$
-
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
-
-Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).
-
-## Datasets Overview
-
-To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
-
-* **edx:** we use it to develop and train our algorithms;
-* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
-
-For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
-The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
-
-Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r eval=FALSE }
-if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
-
-library(edx.capstone.movielens.data)
-edx <- edx.capstone.movielens.data::edx
-final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
-```
-
-Now, we have the datasets listed above:
-```{r }
-summary(edx)
-```
-
-```{r }
-summary(final_holdout_test)
-```
-
-### `edx` Dataset
-\
-Let's look into the details of the `edx` dataset:
-``` {r echo = TRUE}
-str(edx)
-```
-Note that we have 9000055 rows and six columns in there:  
-```{r }
-dim_edx <- dim(edx)
-print(dim_edx)
-```
-
-First, let's note that we have 10677 different movies: 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
-
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
-
-```
-
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
-
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Finally, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
-```{r }
-#library(dplyr)
-s <- edx |> group_by(rating) |>
-  summarise(n = n())
-print(s)
-```
-
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
-
-#### Rating distribution plot[@MRS-R-BEST]
-\
-The code below demonstrates another way of visualizing the rating distribution:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-
-```
-
-This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-
-#### Ratings per movie
+## User Effect Model
 \
 
-##### Movie popularity count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  group_by(movieId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-```{r}
-summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per movie plot[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Movies' rating histogram[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-#### Ratings per user[@MRS-R-BEST]
-\
-
-##### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-##### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-# Methods / Analysis
-::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
-:::
-
-## Defining Logging and Time Measuring Helper Functions
-\
-
-First, let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
-
-```{r eval=FALSE }
-# Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log1(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log1(msg_template, arg1, arg2))
-}
-
-# ...
-```
-
-::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## Preparing train and set datasets
-\
-
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
-To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
-```{r eval=FALSE }
-make_source_datasets()
-init_source_datasets()
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-### The `make_source_datasets` function
-\
-
-Let's take a closer look at the objects we will receive as a result of executing this function.
-
-```{r eval=FALSE}
-
-make_source_datasets <- function(){
-  # ...
-  list(edx_CV = edx_CV,
-       edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
-       tuning_sets = tuning_sets,
-       movie_map = movie_map,
-       date_days_map = date_days_map)
-}
-```
-
-#### `edx.mx` Matrix Object
-\
-
-We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
-To create this matrix, we use `tidyr::pivot_wider` function:
-
-```{r eval=FALSE}
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-
-```
-
-```{r}
-  str(edx.mx)
-```
-
-#### `edx.sgr` Object
-\
-
-To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-```
-```{r}
-str(edx.sgr)
-summary(edx.sgr)
-```
-
-Note that we use the `splitGenreRows` function to split rows of the original dataset:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function mentioned above is also available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-#### `movie_map` Object
-\
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r eval=FALSE}
-movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-```
-
-```{r}
-str(movie_map)
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
-
-#### `date_days_map` Object
-\
-
-We have a `timestamp` field in the `edx` dataset.
-To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-```
-``` {r}
-  str(date_days_map)
-  summary(date_days_map)
-```
-
-#### `edx_CV` Object
-\
-
-Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_:
-```{r eval=FALSE}
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
-```
-```{r}
-str(edx_CV)
-```
-
-::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
-:::
-
-Note that we used the `sample_train_validation_sets` function call to split the original dataset (`edx` in this case): 
-```{r eval=FALSE}
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-```
-
-which returns a pair of train/validation sets:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets ----------------------------------------------------    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)` one, from where it is called.
-:::
-
-### Common Helper Functions
-\
-
-For our further analysis, we are going to use the following _common helper functions_:
-
-#### `clamp` function
-\
-
-As explained in [Section  24.4 User effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings can’t be below 0.5 or above 5.
-For this reason, we will use the `clamp` function described in that section:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
-#### Functions to calculate _(Root) Mean Squared Error_
-\
-
-We will need the following functions to calculate _(R)MSEs_:
-```{r eval=FALSE}
-mse <- function(r) mean(r^2)
-
-mse_cv <- function(r_list) {
-  mses <- sapply(r_list, mse(r))
-  mean(mses)
-}
-
-rmse <- function(r) sqrt(mse(r))
-# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
-
-rmse2 <- function(true_ratings, predicted_ratings) {
-  rmse(true_ratings - predicted_ratings)
-}
-```
-
-::: {.noteblock data-latex=""}
-All the _common helper functions_, including those described above, are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-## Overall Mean Rating (Naive) Model
-\
-
-Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
-It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
-
-$$
-Y_{i,j} = \mu + \varepsilon_{i,j}
-$$
-
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
-
-We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
-
-```{r pressure, echo=TRUE}
-mu <- mean(edx$rating)
-print(mu)
-```
-
-If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
-```{r}
-mu.MSEs <- naive_model_MSEs(mu)
-data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
-              xname = "fold_No", 
-              yname = "MSE")
-
-mu.RMSE <- sqrt(mean(mu.MSEs))
-mu.RMSE
-```
-::: {.noteblock data-latex=""}
-For the _Mean Squared Error_ data visualization we used [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function] defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.function.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script.
-:::
-
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      # scale = 1,
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
-
-Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
-
-```{r eval=FALSE }
-naive_model_MSEs <- function(val) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - val)
-  })
-}
-```
-
-One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L59) one:
-```{r eval=FALSE }
-naive_model_RMSE <- function(val){
-  sqrt(mean(naive_model_MSEs(val)))
-}
-```
-
-### Ensure that `mu.RMSE` value is the best for the current model
-\
-
-If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r }
-  deviation <- seq(0, 6, 0.1) - 3
-
-  deviation.RMSE <- sapply(deviation, function(delta){
-    naive_model_RMSE(mu + delta)
-  })
-```
-
-Let's make a quick investigation of the `deviation.RMSE` result we have just got: 
-```{r}
-data.frame(delta = deviation, 
-           delta.RMSE = deviation.RMSE) |> 
-data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
-              xname = "delta", 
-              yname = "delta.RMSE", 
-              xlabel = TeX(r'[$\delta$]'), 
-              ylabel = "RMSE")
-
-which_min_deviation <- deviation[which.min(deviation.RMSE)]
-min_rmse = min(deviation.RMSE)
-
-print_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
-         which_min_deviation)
-
-print_log1("Is the previously computed RMSE the best for the current model: %1",
-         mu.RMSE == min_rmse)
-```
-```{r eval=FALSE}
-RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
-  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.OMR)
-```
-
-To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
-
-## User Effect Model
-\
 To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
@@
 
-## User+Movie Effect (UME) Model
-\
-
-In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
-He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
-$$
-The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:
-
-```{r eval=FALSE}
-b <- colMeans(y - mu - a, na.rm = TRUE)
-```
-
-Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
-
-### UME Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
-:::
-
-#### `train_user_movie_effect` Function
-\
-
-We use this function to build and train our model using the `train_set` dataset:
-```{r eval=FALSE}
-train_user_movie_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_effect
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need for the *Regularization*.
-We will explain that later in the [Regularization Method] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the `mean_reg` function is equivalent to the simple `mean` one.
-:::
-
-```{r eval=FALSE}
-# Regularization --------------------------------------------------------------
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-#### `train_user_movie_effect.cv` Function
-\
-
-We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method.
-Below, we provide the most important part of the code of that function:
-```{r eval=FALSE}
-train_user_movie_effect.cv <- function(lambda = 0){
-# ...
-  start <- put_start_date()
-  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
-  })
-  put_end_date(start)
-  put_log("Function: train_user_movie_effect.cv:
-User+Movie Effect list have been computed")
-
-  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-
-  user_movie_effect <- user_movie_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  # ...
-  user_movie_effect
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the `Cross Validation` results.
-:::
-```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
-```
-
-#### `calc_user_movie_effect_MSE` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE <- function(test_set, um_effect){
-  mse.result <- test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(um_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    pull(resid) |> mse()
-
-  stopifnot(!is.na(mse.result))
-  mse.result
-}
-```
-
-#### `calc_user_movie_effect_MSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv <- function(um_effect){
-  put_log("Function: user_movie_effects_MSE.cv:
-Computing the RMSE taking into account User+Movie Effects...")
-  start <- put_start_date()
-  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
-  })
-  put_end_date(start)
-
-  put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_effects_MSEs)
-}
-
-```
-
-#### `calc_user_movie_effect_RMSE` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-  sqrt(mse)
-}
-```
-
-#### `calc_user_movie_effect_RMSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
-  um_effect_RMSE
-}
-
-```
-
-### Model Building
-\
-
-::: {.noteblock data-latex=""}
-The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
-```{r eval=FALSE}
-  cv.UM_effect <- train_user_movie_effect.cv()
-```
-```{r}
-str(cv.UM_effect)
-
-par(cex = 0.7)
-hist(cv.UM_effect$b, 30, xlab = TeX(r'[$\hat{beta}_{j}$)]'),
-     main = TeX(r'[Histogram of $\hat{beta}_{j}$]'))
-```
-
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
-```{r eval=FALSE}
-cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
-
-RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
-  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
-
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.UME)
-```
-
-## Regularizing User+Movie Effect Model
-
-### Utilizing Penalized least squares
-\
-[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-
-$$ 
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
-$$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-
-$$
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-where $n_j$ is the number of ratings made for movie $j$.
-
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
-
-  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
-
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
-
-### UME Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-
-#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
-\
-
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
-```{r eval=FALSE}
-regularize.test_lambda.UM_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UM_effect.cv
-`lambda` is `NA`")
-  }
-  um_effect <- train_user_movie_effect.cv(lambda)
-  calc_user_movie_effect_RMSE.cv(um_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_effect.cv]() calling it from the [regularize.test_lambda.UM_effect.cv](), but now with the $\lambda$ parameter different from the default (zero) value.
-:::
-
-Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r eval=FALSE}
-# Here we will simply compute the RMSE for different values of `lambda` 
-n <- colSums(!is.na(y))
-
-sums <- colSums(y - mu - a, na.rm = TRUE)
-lambdas <- seq(0, 10, 0.1)
-
-rmses <- sapply(lambdas, function(lambda){
-  b <-  sums / (n + lambda)
-  reg_rmse(b)
-})
-
-# Here is a plot of the RMSE versus `lambda`:
-plot(lambdas, rmses, type = "l")
-```
-Now we can determine the minimal _RMSE_:
-```{r}
-# print(min(rmses))
-```
-
-which is achieved for the following $\lambda$:
-```{r eval=FALSE}
-lambda <- lambdas[which.min(rmses)] 
-print(lambda)
-```
-
-Using this $\lambda$ we can compute the regularized estimates:
-```{r eval=FALSE}
-b_reg <- sums / (n + lambda)
-
-str(b_reg)
-```
-Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r eval=FALSE}
-reg_rmse(b_reg)
-```
-
-## Accounting for Date effects
-
-#### Yearly rating count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(count = n())
-)
-```
-
-#### Average rating per year plot[@MRS-R-BEST]
-\
-```{r}
-edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(rating_avg = mean(rating)) |>
-  ggplot(aes(x = year, y = rating_avg)) +
-  geom_bar(stat = "identity", fill = "#8888ff") + 
-  ggtitle("Average rating per year") +
-  xlab("Year") +
-  ylab("Average rating") +
-  scale_y_continuous(labels = comma) + 
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-We use the following models to account for the `date` effect:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
-$$
-
-## Accounting for Genre effect
-\
-As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
-This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
-
-### Genre Data Analysis
-\
-#### Movie Genres Data 
-\
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r eval=FALSE}
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r eval=FALSE}
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r eval=FALSE}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r eval=FALSE}
-print(edx |> group_by(rating) |> summarize(count = n()))
-```
-
-We can visually see that from the following plot:
-```{r eval=FALSE}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
-#### Movie Genres Effect 
-\
-
-The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
-
-```{r eval=FALSE}
-# Preparing data for plotting:
-genre_ratins_grp <- train_set |> 
-  mutate(genre_categories = as.factor(genres)) |>
-  group_by(genre_categories) |>
-  summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
-  filter(n > 20000) |> 
-  mutate(genres = reorder(genre_categories, rating_avg)) |>
-  select(genres, rating_avg, se, n)
-
-dim(genre_ratins_grp)
-genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
-print(genre_ratins_grp_sorted)
-
-# Creating plot:
-genre_ratins_grp |> 
-  ggplot(aes(x = genres, y = rating_avg, ymin = rating_avg - 2*se, ymax = rating_avg + 2*se)) + 
-  geom_point() +
-  geom_errorbar() + 
-  ggtitle("Average rating per Genre") +
-  ylab("Average rating") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-```
-Below are worst and best ratings categories:
-```{r eval=FALSE}
-sprintf("The worst ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.min(genre_ratins_grp$genres)])
-
-sprintf("The best ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.max(genre_ratins_grp$genres)])
-```
-
-Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
-```{r eval=FALSE}
-# For better visibility, we reduce the data for plotting 
-# while keeping the worst and best rating rows:
-plot_ind <- odd(1:nrow(genre_ratins_grp))
-plot_dat <- genre_ratins_grp_sorted[plot_ind,]
-
-plot_dat |>
-  ggplot(aes(x = rating_avg, y = genres)) +
-  ggtitle("Genre Average Rating") +
-  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
-  xlab("Average ratings") +
-  ylab("Genres") +
-  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
-  theme_economist() +
-  theme(plot.title = element_text(vjust = 3.5),
-        axis.title.x = element_text(vjust = -5, face = "bold"),
-        axis.title.y = element_text(vjust = 10, face = "bold"),
-        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
-        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-
-To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
-$$
-
-where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p.
-712) book[@RRSK_RS_HB].
-
-In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:
-
-$$
-g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
-$$
-
-with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
-$$
-
-$$
- \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-# Conclusion
-
-Hello Conclusion!
-
-This is a great conclusion, isn't it?!!
-
-# Appendix
-
-## Regularization: Common Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-#### Parameters
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-#### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-#### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-#### **Parameters**
-\
-
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-##### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-##### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-##### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-##### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-##### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-##### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-##### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-##### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-#### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-#### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-#### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
-:::
-:::
-
-### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-#### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-##### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-#### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-#### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-#### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-#### Parameters
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-#### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-#### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-#### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-## Support Functions
-
-### [func.00]() Function {#func.00}
-\
-
-::: { #func.00.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.00.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.00.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.00.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.00.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.01}
-\
-
-::: { #func.01.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.01.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.01.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.01.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.01.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.02}
-\
-
-::: { #func.02.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.02.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.02.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.02.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.02.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.0]() Function {#func.0}
-\
-
-::: { #func.0.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.0.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.0.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.0.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func1]() Function {#func.03}
-\
-
-::: { #func.03.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.03.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.03.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.03.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.03.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [func1]() Function {#func.1}
-\
-
-::: { #func.1.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.1.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.1.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.1.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.1.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.2]() Function {#func.2}
-\
-
-::: { #func.2.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.2.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.2.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.2.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.2.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
---------------------------------------------------------------------------------
-
-### [func.3]() Function {#func.3}
-\
-
-::: { #func.3.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.3.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.3.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.3.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.3.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.4]() Function {#func.4}
-\
-
-::: { #func.4.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.4.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.4.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.4.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.4.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.5]() Function {#func.5}
-\
-
-::: { #func.5.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.5.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.5.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.5.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.5.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.6]() Function {#func.6}
-\
-
-::: { #func.6.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.6.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.6.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.6.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.6.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.7]() Function {#func.7}
-\
-
-::: { #func.7.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.7.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.7.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.7.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.7.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.8]() Function {#func.8}
-\
-
-::: { #func.8.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.8.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.8.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.8.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.8.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### []() Function {#func.3-1}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-#### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-#### Value
-\
-
-#### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-================================================================================
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
+\newpage

### 2025-05-14 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report update: splitted to multifile report.

--- 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
@@
-```{r setup, include=FALSE, echo = FALSE}
-r.path <- "../r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-# Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-# stop(main_script.file_path)
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
-# External Common Helper functions -------------------------------------
-# common_helper_functions.file_path <- file.path(support_functions.path,
-#                                             "common-helper.functions.R")
-# source(common_helper_functions.file_path, 
-#        local = knitr::knit_global())
-
-# knitr::knit_global()
-#knitr::opts_chunk$set(echo = FALSE)
-```
-
----
-title: "Capstone Movielens Report"
-author: "Azamat Kurbanaev"
-date: "`r Sys.Date()`"
-bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
-envir:
-  parent.frame()
-output: 
-  bookdown::pdf_document2: 
-    df_print: paged
-    toc: true
-    fig_caption: true
-    keep_tex: true
-    citation_package: biblatex
-colorlinks: true
-linkcolor: red
-citecolor: blue
-header-includes:
-    - \usepackage{awesomebox}
-    - \usepackage{hyperref}
-    - \usepackage[natbib=true, 
-                  style=numeric, 
-                  backref=true, 
-                  sorting=none]{biblatex}
-    - \hypersetup{backref,
-          pdfpagemode=Normal,
-          colorlinks=true,
-          implicit=false}
-vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
-  %\VignetteEncoding{UTF-8}
-  %\VignetteEngine{knitr::knitr}
----
-
-\newenvironment{infobox}[1]
-  {
-  \begin{itemize}
-  \renewcommand{\labelitemi}{
-    \raisebox{-.7\height}[0pt][0pt]{
-      {\setkeys{Gin}{width=3em,keepaspectratio}
-        \includegraphics{images/#1}}
-    }
-  }
-  \setlength{\fboxsep}{1em}
-  \begin{blackbox}
-  \item
-  }
-  {
-  \end{blackbox}
-  \end{itemize}
-  }
-
-# Introduction / Overview / Executive Summary
-
-The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
-$$
-\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
-$$
-
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
-
-Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]). 
-\newpage
-
-## Datasets Overview
-
-To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
-
-* **edx:** we use it to develop and train our algorithms;
-* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
-
-For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
-The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
-
-Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r eval=FALSE }
-if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
-
-library(edx.capstone.movielens.data)
-edx <- edx.capstone.movielens.data::edx
-final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
-```
-
-Now, we have the datasets listed above:
-```{r }
-summary(edx)
-```
-
-```{r }
-summary(final_holdout_test)
-```
-\newpage
-
-### `edx` Dataset
-\
-Let's look into the details of the `edx` dataset:
-``` {r echo = TRUE}
-str(edx)
-```
-Note that we have 9000055 rows and six columns in there:  
-```{r }
-dim_edx <- dim(edx)
-print(dim_edx)
-```
-
-First, let's note that we have 10677 different movies: 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
-
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
-
-```
-
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
-
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Finally, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
-```{r }
-#library(dplyr)
-s <- edx |> group_by(rating) |>
-  summarise(n = n())
-print(s)
-```
-
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
-\newpage
-
-#### Rating distribution plot[@MRS-R-BEST]
-\
-The code below demonstrates another way of visualizing the rating distribution:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-
-```
-
-This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-\newpage
-
-#### Ratings per movie
-\
-##### Movie popularity count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  group_by(movieId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-```{r}
-summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
-```
-\newpage
-
-##### Ratings per movie plot[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Movies' rating histogram[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-\newpage
-
-#### Ratings per user[@MRS-R-BEST]
-\
-##### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-##### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-\newpage
-
-##### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-\newpage
-
-# Methods / Analysis
-::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
-:::
-
-## Defining Logging and Time Measuring Helper Functions
-\
-
-First, let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
-
-```{r eval=FALSE }
-# Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log1(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log1(msg_template, arg1, arg2))
-}
-
-# ...
-```
-
-::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-\newpage
-
-## Preparing train and set datasets
-\
-
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
-To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
-```{r eval=FALSE }
-make_source_datasets()
-init_source_datasets()
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-### The `make_source_datasets` function
-\
-
-Let's take a closer look at the objects we will receive as a result of executing this function.
-
-```{r eval=FALSE}
-
-make_source_datasets <- function(){
-  # ...
-  list(edx_CV = edx_CV,
-       edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
-       tuning_sets = tuning_sets,
-       movie_map = movie_map,
-       date_days_map = date_days_map)
-}
-```
-
-#### `edx.mx` Matrix Object
-\
-
-We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
-To create this matrix, we use `tidyr::pivot_wider` function:
-
-```{r eval=FALSE}
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-
-```
-
-```{r}
-  str(edx.mx)
-```
-
-#### `edx.sgr` Object
-\
-
-To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-```
-```{r}
-str(edx.sgr)
-summary(edx.sgr)
-```
-
-Note that we use the `splitGenreRows` function to split rows of the original dataset:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function mentioned above is also available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-#### `movie_map` Object
-\
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r eval=FALSE}
-movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-```
-
-```{r}
-str(movie_map)
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
-
-#### `date_days_map` Object
-\
-
-We have a `timestamp` field in the `edx` dataset.
-To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-```
-``` {r}
-  str(date_days_map)
-  summary(date_days_map)
-```
-
-#### `edx_CV` Object
-\
-
-Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_:
-```{r eval=FALSE}
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
-```
-```{r}
-str(edx_CV)
-```
-
-::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
-:::
-
-Note that we used the `sample_train_validation_sets` function call to split the original dataset (`edx` in this case): 
-```{r eval=FALSE}
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-```
-
-which returns a pair of train/validation sets:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets ----------------------------------------------------    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)` one, from where it is called.
-:::
-
-\newpage
-
-### Common Helper Functions
-\
-
-For our further analysis, we are going to use the following _common helper functions_:
-
-#### `clamp` function
-\
-
-As explained in [Section  24.4 User effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings can’t be below 0.5 or above 5.
-For this reason, we will use the `clamp` function described in that section:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
-#### Functions to calculate _(Root) Mean Squared Error_
-\
-
-We will need the following functions to calculate _(R)MSEs_:
-```{r eval=FALSE}
-mse <- function(r) mean(r^2)
-
-mse_cv <- function(r_list) {
-  mses <- sapply(r_list, mse(r))
-  mean(mses)
-}
-
-rmse <- function(r) sqrt(mse(r))
-# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
-
-rmse2 <- function(true_ratings, predicted_ratings) {
-  rmse(true_ratings - predicted_ratings)
-}
-```
-
-::: {.noteblock data-latex=""}
-All the _common helper functions_, including those described above, are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-\newpage
-
-## Overall Mean Rating (Naive) Model
-\
-
-Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
-It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
-
-$$
-Y_{i,j} = \mu + \varepsilon_{i,j}
-$$
-
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
-
-We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
-
-```{r pressure, echo=TRUE}
-mu <- mean(edx$rating)
-print(mu)
-```
-
-If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
-```{r}
-mu.MSEs <- naive_model_MSEs(mu)
-data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
-              xname = "fold_No", 
-              yname = "MSE")
-
-mu.RMSE <- sqrt(mean(mu.MSEs))
-mu.RMSE
-```
-::: {.noteblock data-latex=""}
-For the _Mean Squared Error_ data visualization we used [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function] defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.function.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script.
-:::
-
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      # scale = 1,
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
-
-Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
-
-```{r eval=FALSE }
-naive_model_MSEs <- function(val) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - val)
-  })
-}
-```
-
-One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L59) one:
-```{r eval=FALSE }
-naive_model_RMSE <- function(val){
-  sqrt(mean(naive_model_MSEs(val)))
-}
-```
-\newpage
-
-### Ensure that `mu.RMSE` value is the best for the current model
-\
-
-If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r }
-  deviation <- seq(0, 6, 0.1) - 3
-
-  deviation.RMSE <- sapply(deviation, function(delta){
-    naive_model_RMSE(mu + delta)
-  })
-```
-
-Let's make a quick investigation of the `deviation.RMSE` result we have just got: 
-```{r}
-data.frame(delta = deviation, 
-           delta.RMSE = deviation.RMSE) |> 
-data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
-              xname = "delta", 
-              yname = "delta.RMSE", 
-              xlabel = TeX(r'[$\delta$]'), 
-              ylabel = "RMSE")
-
-which_min_deviation <- deviation[which.min(deviation.RMSE)]
-min_rmse = min(deviation.RMSE)
-
-print_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
-         which_min_deviation)
-
-print_log1("Is the previously computed RMSE the best for the current model: %1",
-         mu.RMSE == min_rmse)
-```
-```{r eval=FALSE}
-RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
-  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.OMR)
-```
-
-To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
-\newpage
-
-## User Effect Model
-\
-
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
-```{r}
-hist(edx.user_mean_ratings$mean_rating, nclass = 30)
-```
-
-Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
-The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
-So we write the model as follows:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
-$$
-
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
-
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we can compute them this way:
-```{r eval=FALSE}
-a <- rowMeans(y - mu, na.rm = TRUE)
-```
-
-These considerations alows us to compute a _User Mean Ratings_ the following way:
-```{r eval=FALSE}
-put_log("Computing Average Ratings per User (User Mean Ratings)...")
-user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
-user_ratings.n <- rowSums(!is.na(edx.mx))
-
-edx.user_mean_ratings <- 
-  data.frame(userId = names(user.mean_ratings), 
-             mean_rating = user.mean_ratings,
-             n = user_ratings.n)
-
-put_log("User Mean Ratings have been computed.")
-```
-```{r}
-str(edx.user_mean_ratings)
-```
-
-And then we compute a _User Effect_ this way:
-```{r eval=FALSE}
-put_log("Computing User Effect per users ...")
-edx.user_effect <- edx.user_mean_ratings |>
-  mutate(userId = as.integer(userId),
-         a = mean_rating - mu)
-
-put_log("A User Effect Model has been builded")
-```
-```{r}
-par(cex = 0.7)
-hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
-     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
-
-str(edx.user_effect)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect_ computation is available in the [Model building: User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L531) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Finally, we are ready to compute the `RMSE` (additionally using the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) helper function we defined above to keep predictions in the proper range):
-```{r eval=FALSE}
-put_log("Computing the RMSE taking into account user effects...")
-start <- put_start_date()
-edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
-  cv_fold_dat$validation_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - clamp(mu + a)) |> 
-    pull(resid) |> mse()
-})
-put_end_date(start)
-
-edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
-
-RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
-  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
-```
-```{r}
-data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the User Effect Model",
-            xname = "fold_No", 
-            yname = "MSE")
-
-RMSE_kable(RMSEs.ResultTibble.UE)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
 ## User+Movie Effect (UME) Model
@@
 Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
+
+\newpage
 
@@
 
+\newpage
+
 ### Model Building
@@
 
-## Regularizing User+Movie Effect Model
+### Regularizing User+Movie Effect Model
+\
 
-### Utilizing Penalized least squares
+#### Utilizing Penalized least squares
 \
+
 [Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
@@
 
-### UME Model Regularization: Support Functions
+\newpage
+
+#### UME Model Regularization: Support Functions
 \
@@
 
-#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
+##### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
 \
@@
 
-### User+Movie Effect Model Tuning: Preconfiguratioin
+\newpage
+
+#### User+Movie Effect Model Tuning: Preconfiguratioin
 
@@
 
-## Accounting for Date effects
+\newpage
 
-#### Yearly rating count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(count = n())
-)
-```
+#### User+Movie Effect Model: Fine-Tuning
 
-#### Average rating per year plot[@MRS-R-BEST]
-\
-```{r}
-edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(rating_avg = mean(rating)) |>
-  ggplot(aes(x = year, y = rating_avg)) +
-  geom_bar(stat = "identity", fill = "#8888ff") + 
-  ggtitle("Average rating per year") +
-  xlab("Year") +
-  ylab("Average rating") +
-  scale_y_continuous(labels = comma) + 
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-We use the following models to account for the `date` effect:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
-$$
-
-## Accounting for Genre effect
-\
-As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
-This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
-
-### Genre Data Analysis
-\
-#### Movie Genres Data 
-\
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r eval=FALSE}
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r eval=FALSE}
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r eval=FALSE}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r eval=FALSE}
-print(edx |> group_by(rating) |> summarize(count = n()))
-```
-
-We can visually see that from the following plot:
-```{r eval=FALSE}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
-#### Movie Genres Effect 
-\
-
-The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
-
-```{r eval=FALSE}
-# Preparing data for plotting:
-genre_ratins_grp <- train_set |> 
-  mutate(genre_categories = as.factor(genres)) |>
-  group_by(genre_categories) |>
-  summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
-  filter(n > 20000) |> 
-  mutate(genres = reorder(genre_categories, rating_avg)) |>
-  select(genres, rating_avg, se, n)
-
-dim(genre_ratins_grp)
-genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
-print(genre_ratins_grp_sorted)
-
-# Creating plot:
-genre_ratins_grp |> 
-  ggplot(aes(x = genres, y = rating_avg, ymin = rating_avg - 2*se, ymax = rating_avg + 2*se)) + 
-  geom_point() +
-  geom_errorbar() + 
-  ggtitle("Average rating per Genre") +
-  ylab("Average rating") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-```
-Below are worst and best ratings categories:
-```{r eval=FALSE}
-sprintf("The worst ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.min(genre_ratins_grp$genres)])
-
-sprintf("The best ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.max(genre_ratins_grp$genres)])
-```
-
-Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
-```{r eval=FALSE}
-# For better visibility, we reduce the data for plotting 
-# while keeping the worst and best rating rows:
-plot_ind <- odd(1:nrow(genre_ratins_grp))
-plot_dat <- genre_ratins_grp_sorted[plot_ind,]
-
-plot_dat |>
-  ggplot(aes(x = rating_avg, y = genres)) +
-  ggtitle("Genre Average Rating") +
-  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
-  xlab("Average ratings") +
-  ylab("Genres") +
-  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
-  theme_economist() +
-  theme(plot.title = element_text(vjust = 3.5),
-        axis.title.x = element_text(vjust = -5, face = "bold"),
-        axis.title.y = element_text(vjust = 10, face = "bold"),
-        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
-        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-
-To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
-$$
-
-where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p.
-712) book[@RRSK_RS_HB].
-
-In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:
-
-$$
-g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
-$$
-
-with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
-$$
-
-$$
- \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-# Conclusion
-
-Hello Conclusion!
-
-This is a great conclusion, isn't it?!!
-
-# Appendix {#appendix.a}
-
-## Regularization: Common Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-#### Parameters
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-#### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-#### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-#### **Parameters**
-\
-
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-##### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-##### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-##### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-##### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-##### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-##### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-##### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-##### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-#### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-#### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-#### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
-:::
-:::
-
-### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-#### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-##### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-#### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-#### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-#### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-#### Parameters
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-#### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-#### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-#### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-## Support Functions
-
-### [func.00]() Function {#func.00}
-\
-
-::: { #func.00.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.00.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.00.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.00.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.00.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.01}
-\
-
-::: { #func.01.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.01.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.01.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.01.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.01.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.02}
-\
-
-::: { #func.02.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.02.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.02.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.02.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.02.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.0]() Function {#func.0}
-\
-
-::: { #func.0.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.0.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.0.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.0.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func1]() Function {#func.03}
-\
-
-::: { #func.03.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.03.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.03.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.03.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.03.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [func1]() Function {#func.1}
-\
-
-::: { #func.1.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.1.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.1.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.1.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.1.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.2]() Function {#func.2}
-\
-
-::: { #func.2.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.2.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.2.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.2.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.2.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
---------------------------------------------------------------------------------
-
-### [func.3]() Function {#func.3}
-\
-
-::: { #func.3.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.3.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.3.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.3.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.3.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.4]() Function {#func.4}
-\
-
-::: { #func.4.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.4.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.4.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.4.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.4.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.5]() Function {#func.5}
-\
-
-::: { #func.5.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.5.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.5.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.5.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.5.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.6]() Function {#func.6}
-\
-
-::: { #func.6.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.6.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.6.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.6.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.6.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.7]() Function {#func.7}
-\
-
-::: { #func.7.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.7.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.7.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.7.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.7.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.8]() Function {#func.8}
-\
-
-::: { #func.8.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.8.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.8.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.8.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.8.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### []() Function {#func.3-1}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-#### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-#### Value
-\
-
-#### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-================================================================================
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
+\newpage

### 2025-05-14 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report update: splitted to multifile report.

--- 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
@@
-```{r setup, include=FALSE, echo = FALSE}
-r.path <- "../r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-# Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-# stop(main_script.file_path)
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
-# External Common Helper functions -------------------------------------
-# common_helper_functions.file_path <- file.path(support_functions.path,
-#                                             "common-helper.functions.R")
-# source(common_helper_functions.file_path, 
-#        local = knitr::knit_global())
-
-# knitr::knit_global()
-#knitr::opts_chunk$set(echo = FALSE)
-```
-
----
-title: "Capstone Movielens Report"
-author: "Azamat Kurbanaev"
-date: "`r Sys.Date()`"
-bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
-envir:
-  parent.frame()
-output: 
-  bookdown::pdf_document2: 
-    df_print: paged
-    toc: true
-    fig_caption: true
-    keep_tex: true
-    citation_package: biblatex
-colorlinks: true
-linkcolor: red
-citecolor: blue
-header-includes:
-    - \usepackage{awesomebox}
-    - \usepackage{hyperref}
-    - \usepackage[natbib=true, 
-                  style=numeric, 
-                  backref=true, 
-                  sorting=none]{biblatex}
-    - \hypersetup{backref,
-          pdfpagemode=Normal,
-          colorlinks=true,
-          implicit=false}
-vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
-  %\VignetteEncoding{UTF-8}
-  %\VignetteEngine{knitr::knitr}
----
-
-\newenvironment{infobox}[1]
-  {
-  \begin{itemize}
-  \renewcommand{\labelitemi}{
-    \raisebox{-.7\height}[0pt][0pt]{
-      {\setkeys{Gin}{width=3em,keepaspectratio}
-        \includegraphics{images/#1}}
-    }
-  }
-  \setlength{\fboxsep}{1em}
-  \begin{blackbox}
-  \item
-  }
-  {
-  \end{blackbox}
-  \end{itemize}
-  }
-
-# Introduction / Overview / Executive Summary
-
-The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
-$$
-\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
-$$
-
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
-
-Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).
-
-## Datasets Overview
-
-To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
-
-* **edx:** we use it to develop and train our algorithms;
-* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
-
-For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
-The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
-
-Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r eval=FALSE }
-if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
-
-library(edx.capstone.movielens.data)
-edx <- edx.capstone.movielens.data::edx
-final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
-```
-
-Now, we have the datasets listed above:
-```{r }
-summary(edx)
-```
-
-```{r }
-summary(final_holdout_test)
-```
-
-### `edx` Dataset
+## User+Movie+Genre+Year Effect (UMGYE) Model
 \
-Let's look into the details of the `edx` dataset:
-``` {r echo = TRUE}
-str(edx)
-```
-Note that we have 9000055 rows and six columns in there:  
-```{r }
-dim_edx <- dim(edx)
-print(dim_edx)
-```
-
-First, let's note that we have 10677 different movies: 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
-
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
-
-```
-
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
-
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Finally, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
-```{r }
-#library(dplyr)
-s <- edx |> group_by(rating) |>
-  summarise(n = n())
-print(s)
-```
-
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
-
-#### Rating distribution plot[@MRS-R-BEST]
-\
-The code below demonstrates another way of visualizing the rating distribution:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-
-```
-
-This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-
-#### Ratings per movie
-\
-
-##### Movie popularity count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  group_by(movieId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-```{r}
-summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per movie plot[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Movies' rating histogram[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-#### Ratings per user[@MRS-R-BEST]
-\
-
-##### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-##### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-# Methods / Analysis
-::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
-:::
-
-## Defining Logging and Time Measuring Helper Functions
-\
-
-First, let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
-
-```{r eval=FALSE }
-# Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log1(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log1(msg_template, arg1, arg2))
-}
-
-# ...
-```
-
-::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## Preparing train and set datasets
-\
-
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
-To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
-```{r eval=FALSE }
-make_source_datasets()
-init_source_datasets()
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-### The `make_source_datasets` function
-\
-
-Let's take a closer look at the objects we will receive as a result of executing this function.
-
-```{r eval=FALSE}
-
-make_source_datasets <- function(){
-  # ...
-  list(edx_CV = edx_CV,
-       edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
-       tuning_sets = tuning_sets,
-       movie_map = movie_map,
-       date_days_map = date_days_map)
-}
-```
-
-#### `edx.mx` Matrix Object
-\
-
-We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
-To create this matrix, we use `tidyr::pivot_wider` function:
-
-```{r eval=FALSE}
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-
-```
-
-```{r}
-  str(edx.mx)
-```
-
-#### `edx.sgr` Object
-\
-
-To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-```
-```{r}
-str(edx.sgr)
-summary(edx.sgr)
-```
-
-Note that we use the `splitGenreRows` function to split rows of the original dataset:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function mentioned above is also available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-#### `movie_map` Object
-\
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r eval=FALSE}
-movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-```
-
-```{r}
-str(movie_map)
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
-
-#### `date_days_map` Object
-\
-
-We have a `timestamp` field in the `edx` dataset.
-To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-```
-``` {r}
-  str(date_days_map)
-  summary(date_days_map)
-```
-
-#### `edx_CV` Object
-\
-
-Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_:
-```{r eval=FALSE}
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
-```
-```{r}
-str(edx_CV)
-```
-
-::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
-:::
-
-Note that we used the `sample_train_validation_sets` function call to split the original dataset (`edx` in this case): 
-```{r eval=FALSE}
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-```
-
-which returns a pair of train/validation sets:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets ----------------------------------------------------    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)` one, from where it is called.
-:::
-
-### Common Helper Functions
-\
-
-For our further analysis, we are going to use the following _common helper functions_:
-
-#### `clamp` function
-\
-
-As explained in [Section  24.4 User effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings can’t be below 0.5 or above 5.
-For this reason, we will use the `clamp` function described in that section:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
-#### Functions to calculate _(Root) Mean Squared Error_
-\
-
-We will need the following functions to calculate _(R)MSEs_:
-```{r eval=FALSE}
-mse <- function(r) mean(r^2)
-
-mse_cv <- function(r_list) {
-  mses <- sapply(r_list, mse(r))
-  mean(mses)
-}
-
-rmse <- function(r) sqrt(mse(r))
-# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
-
-rmse2 <- function(true_ratings, predicted_ratings) {
-  rmse(true_ratings - predicted_ratings)
-}
-```
-
-::: {.noteblock data-latex=""}
-All the _common helper functions_, including those described above, are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-## Overall Mean Rating (Naive) Model
-\
-
-Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
-It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
-
-$$
-Y_{i,j} = \mu + \varepsilon_{i,j}
-$$
-
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
-
-We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
-
-```{r pressure, echo=TRUE}
-mu <- mean(edx$rating)
-print(mu)
-```
-
-If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
-```{r}
-mu.MSEs <- naive_model_MSEs(mu)
-data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
-              xname = "fold_No", 
-              yname = "MSE")
-
-mu.RMSE <- sqrt(mean(mu.MSEs))
-mu.RMSE
-```
-::: {.noteblock data-latex=""}
-For the _Mean Squared Error_ data visualization we used [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function] defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.function.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script.
-:::
-
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      # scale = 1,
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
-
-Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
-
-```{r eval=FALSE }
-naive_model_MSEs <- function(val) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - val)
-  })
-}
-```
-
-One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L59) one:
-```{r eval=FALSE }
-naive_model_RMSE <- function(val){
-  sqrt(mean(naive_model_MSEs(val)))
-}
-```
-
-### Ensure that `mu.RMSE` value is the best for the current model
-\
-
-If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r }
-  deviation <- seq(0, 6, 0.1) - 3
-
-  deviation.RMSE <- sapply(deviation, function(delta){
-    naive_model_RMSE(mu + delta)
-  })
-```
-
-Let's make a quick investigation of the `deviation.RMSE` result we have just got: 
-```{r}
-data.frame(delta = deviation, 
-           delta.RMSE = deviation.RMSE) |> 
-data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
-              xname = "delta", 
-              yname = "delta.RMSE", 
-              xlabel = TeX(r'[$\delta$]'), 
-              ylabel = "RMSE")
-
-which_min_deviation <- deviation[which.min(deviation.RMSE)]
-min_rmse = min(deviation.RMSE)
-
-print_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
-         which_min_deviation)
-
-print_log1("Is the previously computed RMSE the best for the current model: %1",
-         mu.RMSE == min_rmse)
-```
-```{r eval=FALSE}
-RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
-  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.OMR)
-```
-
-To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
-
-## User Effect Model
-\
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
-```{r}
-hist(edx.user_mean_ratings$mean_rating, nclass = 30)
-```
-
-Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
-The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
-So we write the model as follows:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
-$$
-
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
-
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we can compute them this way:
-```{r eval=FALSE}
-a <- rowMeans(y - mu, na.rm = TRUE)
-```
-
-These considerations alows us to compute a _User Mean Ratings_ the following way:
-```{r eval=FALSE}
-put_log("Computing Average Ratings per User (User Mean Ratings)...")
-user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
-user_ratings.n <- rowSums(!is.na(edx.mx))
-
-edx.user_mean_ratings <- 
-  data.frame(userId = names(user.mean_ratings), 
-             mean_rating = user.mean_ratings,
-             n = user_ratings.n)
-
-put_log("User Mean Ratings have been computed.")
-```
-```{r}
-str(edx.user_mean_ratings)
-```
-
-And then we compute a _User Effect_ this way:
-```{r eval=FALSE}
-put_log("Computing User Effect per users ...")
-edx.user_effect <- edx.user_mean_ratings |>
-  mutate(userId = as.integer(userId),
-         a = mean_rating - mu)
-
-put_log("A User Effect Model has been builded")
-```
-```{r}
-par(cex = 0.7)
-hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
-     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
-
-str(edx.user_effect)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect_ computation is available in the [Model building: User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L531) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Finally, we are ready to compute the `RMSE` (additionally using the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) helper function we defined above to keep predictions in the proper range):
-```{r eval=FALSE}
-put_log("Computing the RMSE taking into account user effects...")
-start <- put_start_date()
-edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
-  cv_fold_dat$validation_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - clamp(mu + a)) |> 
-    pull(resid) |> mse()
-})
-put_end_date(start)
-
-edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
-
-RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
-  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
-```
-```{r}
-data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the User Effect Model",
-            xname = "fold_No", 
-            yname = "MSE")
-
-RMSE_kable(RMSEs.ResultTibble.UE)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## User+Movie Effect (UME) Model
-\
-
-In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
-He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
-$$
-The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:
-
-```{r eval=FALSE}
-b <- colMeans(y - mu - a, na.rm = TRUE)
-```
-
-Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
-
-### UME Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
-:::
-
-#### `train_user_movie_effect` Function
-\
-
-We use this function to build and train our model using the `train_set` dataset:
-```{r eval=FALSE}
-train_user_movie_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_effect
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need for the *Regularization*.
-We will explain that later in the [Regularization Method] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the `mean_reg` function is equivalent to the simple `mean` one.
-:::
-
-```{r eval=FALSE}
-# Regularization --------------------------------------------------------------
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-#### `train_user_movie_effect.cv` Function
-\
-
-We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method.
-Below, we provide the most important part of the code of that function:
-```{r eval=FALSE}
-train_user_movie_effect.cv <- function(lambda = 0){
-# ...
-  start <- put_start_date()
-  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
-  })
-  put_end_date(start)
-  put_log("Function: train_user_movie_effect.cv:
-User+Movie Effect list have been computed")
-
-  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-
-  user_movie_effect <- user_movie_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  # ...
-  user_movie_effect
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the `Cross Validation` results.
-:::
-```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
-```
-
-#### `calc_user_movie_effect_MSE` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE <- function(test_set, um_effect){
-  mse.result <- test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(um_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    pull(resid) |> mse()
-
-  stopifnot(!is.na(mse.result))
-  mse.result
-}
-```
-
-#### `calc_user_movie_effect_MSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv <- function(um_effect){
-  put_log("Function: user_movie_effects_MSE.cv:
-Computing the RMSE taking into account User+Movie Effects...")
-  start <- put_start_date()
-  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
-  })
-  put_end_date(start)
-
-  put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_effects_MSEs)
-}
-
-```
-
-#### `calc_user_movie_effect_RMSE` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-  sqrt(mse)
-}
-```
-
-#### `calc_user_movie_effect_RMSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
-  um_effect_RMSE
-}
-
-```
-
-### Model Building
-\
-
-::: {.noteblock data-latex=""}
-The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
-```{r eval=FALSE}
-  cv.UM_effect <- train_user_movie_effect.cv()
-```
-```{r}
-str(cv.UM_effect)
-
-par(cex = 0.7)
-hist(cv.UM_effect$b, 30, xlab = TeX(r'[$\hat{beta}_{j}$)]'),
-     main = TeX(r'[Histogram of $\hat{beta}_{j}$]'))
-```
-
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
-```{r eval=FALSE}
-cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
-
-RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
-  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
-
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.UME)
-```
-
-## Regularizing User+Movie Effect Model
-
-### Utilizing Penalized least squares
-\
-[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-
-$$ 
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
-$$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-
-$$
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-where $n_j$ is the number of ratings made for movie $j$.
-
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
-
-  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
-
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
-
-### UME Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-
-#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
-\
-
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
-```{r eval=FALSE}
-regularize.test_lambda.UM_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UM_effect.cv
-`lambda` is `NA`")
-  }
-  um_effect <- train_user_movie_effect.cv(lambda)
-  calc_user_movie_effect_RMSE.cv(um_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_effect.cv]() calling it from the [regularize.test_lambda.UM_effect.cv](), but now with the $\lambda$ parameter different from the default (zero) value.
-:::
-
-Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r eval=FALSE}
-# Here we will simply compute the RMSE for different values of `lambda` 
-n <- colSums(!is.na(y))
-
-sums <- colSums(y - mu - a, na.rm = TRUE)
-lambdas <- seq(0, 10, 0.1)
-
-rmses <- sapply(lambdas, function(lambda){
-  b <-  sums / (n + lambda)
-  reg_rmse(b)
-})
-
-# Here is a plot of the RMSE versus `lambda`:
-plot(lambdas, rmses, type = "l")
-```
-Now we can determine the minimal _RMSE_:
-```{r}
-# print(min(rmses))
-```
-
-which is achieved for the following $\lambda$:
-```{r eval=FALSE}
-lambda <- lambdas[which.min(rmses)] 
-print(lambda)
-```
-
-Using this $\lambda$ we can compute the regularized estimates:
-```{r eval=FALSE}
-b_reg <- sums / (n + lambda)
-
-str(b_reg)
-```
-Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r eval=FALSE}
-reg_rmse(b_reg)
-```
-
-## Accounting for Date effects
 
@@
 
-## Accounting for Genre effect
-\
-As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
-This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
-
-### Genre Data Analysis
-\
-#### Movie Genres Data 
-\
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r eval=FALSE}
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r eval=FALSE}
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r eval=FALSE}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r eval=FALSE}
-print(edx |> group_by(rating) |> summarize(count = n()))
-```
-
-We can visually see that from the following plot:
-```{r eval=FALSE}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
-#### Movie Genres Effect 
-\
-
-The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
-
-```{r eval=FALSE}
-# Preparing data for plotting:
-genre_ratins_grp <- train_set |> 
-  mutate(genre_categories = as.factor(genres)) |>
-  group_by(genre_categories) |>
-  summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
-  filter(n > 20000) |> 
-  mutate(genres = reorder(genre_categories, rating_avg)) |>
-  select(genres, rating_avg, se, n)
-
-dim(genre_ratins_grp)
-genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
-print(genre_ratins_grp_sorted)
-
-# Creating plot:
-genre_ratins_grp |> 
-  ggplot(aes(x = genres, y = rating_avg, ymin = rating_avg - 2*se, ymax = rating_avg + 2*se)) + 
-  geom_point() +
-  geom_errorbar() + 
-  ggtitle("Average rating per Genre") +
-  ylab("Average rating") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-```
-Below are worst and best ratings categories:
-```{r eval=FALSE}
-sprintf("The worst ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.min(genre_ratins_grp$genres)])
-
-sprintf("The best ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.max(genre_ratins_grp$genres)])
-```
-
-Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
-```{r eval=FALSE}
-# For better visibility, we reduce the data for plotting 
-# while keeping the worst and best rating rows:
-plot_ind <- odd(1:nrow(genre_ratins_grp))
-plot_dat <- genre_ratins_grp_sorted[plot_ind,]
-
-plot_dat |>
-  ggplot(aes(x = rating_avg, y = genres)) +
-  ggtitle("Genre Average Rating") +
-  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
-  xlab("Average ratings") +
-  ylab("Genres") +
-  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
-  theme_economist() +
-  theme(plot.title = element_text(vjust = 3.5),
-        axis.title.x = element_text(vjust = -5, face = "bold"),
-        axis.title.y = element_text(vjust = 10, face = "bold"),
-        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
-        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-
-To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
-$$
-
-where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p.
-712) book[@RRSK_RS_HB].
-
-In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:
-
-$$
-g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
-$$
-
-with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
-$$
-
-$$
- \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-# Conclusion
-
-Hello Conclusion!
-
-This is a great conclusion, isn't it?!!
-
-# Appendix
-
-## Regularization: Common Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-#### Parameters
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-#### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-#### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-#### **Parameters**
-\
-
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-##### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-##### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-##### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-##### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-##### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-##### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-##### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-##### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-#### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-#### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-#### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
-:::
-:::
-
-### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-#### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-##### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-#### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-#### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-#### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-#### Parameters
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-#### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-#### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-#### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-## Support Functions
-
-### [func.00]() Function {#func.00}
-\
-
-::: { #func.00.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.00.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.00.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.00.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.00.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.01}
-\
-
-::: { #func.01.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.01.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.01.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.01.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.01.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.02}
-\
-
-::: { #func.02.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.02.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.02.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.02.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.02.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.0]() Function {#func.0}
-\
-
-::: { #func.0.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.0.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.0.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.0.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func1]() Function {#func.03}
-\
-
-::: { #func.03.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.03.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.03.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.03.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.03.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [func1]() Function {#func.1}
-\
-
-::: { #func.1.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.1.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.1.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.1.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.1.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.2]() Function {#func.2}
-\
-
-::: { #func.2.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.2.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.2.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.2.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.2.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
---------------------------------------------------------------------------------
-
-### [func.3]() Function {#func.3}
-\
-
-::: { #func.3.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.3.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.3.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.3.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.3.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.4]() Function {#func.4}
-\
-
-::: { #func.4.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.4.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.4.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.4.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.4.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.5]() Function {#func.5}
-\
-
-::: { #func.5.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.5.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.5.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.5.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.5.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.6]() Function {#func.6}
-\
-
-::: { #func.6.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.6.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.6.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.6.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.6.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.7]() Function {#func.7}
-\
-
-::: { #func.7.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.7.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.7.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.7.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.7.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.8]() Function {#func.8}
-\
-
-::: { #func.8.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.8.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.8.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.8.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.8.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### []() Function {#func.3-1}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-#### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-#### Value
-\
-
-#### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-================================================================================
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
+\newpage

### 2025-05-14 reports/capstone-movielens.site/02-0.methods.Rmd

--- 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
@@
-```{r setup, include=FALSE, echo = FALSE}
-r.path <- "../r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-# Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-# stop(main_script.file_path)
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
-# External Common Helper functions -------------------------------------
-# common_helper_functions.file_path <- file.path(support_functions.path,
-#                                             "common-helper.functions.R")
-# source(common_helper_functions.file_path, 
-#        local = knitr::knit_global())
-
-# knitr::knit_global()
-#knitr::opts_chunk$set(echo = FALSE)
-```
-
----
-title: "Capstone Movielens Report"
-author: "Azamat Kurbanaev"
-date: "`r Sys.Date()`"
-bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
-envir:
-  parent.frame()
-output: 
-  bookdown::pdf_document2: 
-    df_print: paged
-    toc: true
-    fig_caption: true
-    keep_tex: true
-    citation_package: biblatex
-colorlinks: true
-linkcolor: red
-citecolor: blue
-header-includes:
-    - \usepackage{awesomebox}
-    - \usepackage{hyperref}
-    - \usepackage[natbib=true, 
-                  style=numeric, 
-                  backref=true, 
-                  sorting=none]{biblatex}
-    - \hypersetup{backref,
-          pdfpagemode=Normal,
-          colorlinks=true,
-          implicit=false}
-vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
-  %\VignetteEncoding{UTF-8}
-  %\VignetteEngine{knitr::knitr}
----
-
-\newenvironment{infobox}[1]
-  {
-  \begin{itemize}
-  \renewcommand{\labelitemi}{
-    \raisebox{-.7\height}[0pt][0pt]{
-      {\setkeys{Gin}{width=3em,keepaspectratio}
-        \includegraphics{images/#1}}
-    }
-  }
-  \setlength{\fboxsep}{1em}
-  \begin{blackbox}
-  \item
-  }
-  {
-  \end{blackbox}
-  \end{itemize}
-  }
-
-# Introduction / Overview / Executive Summary
-
-The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
-$$
-\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
-$$
-
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
-
-Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).
-
-## Datasets Overview
-
-To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
-
-* **edx:** we use it to develop and train our algorithms;
-* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
-
-For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
-The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
-
-Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r eval=FALSE }
-if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
-
-library(edx.capstone.movielens.data)
-edx <- edx.capstone.movielens.data::edx
-final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
-```
-
-Now, we have the datasets listed above:
-```{r }
-summary(edx)
-```
-
-```{r }
-summary(final_holdout_test)
-```
-
-### `edx` Dataset
-\
-Let's look into the details of the `edx` dataset:
-``` {r echo = TRUE}
-str(edx)
-```
-Note that we have 9000055 rows and six columns in there:  
-```{r }
-dim_edx <- dim(edx)
-print(dim_edx)
-```
-
-First, let's note that we have 10677 different movies: 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
-
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
-
-```
-
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
-
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Finally, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
-```{r }
-#library(dplyr)
-s <- edx |> group_by(rating) |>
-  summarise(n = n())
-print(s)
-```
-
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
-
-#### Rating distribution plot[@MRS-R-BEST]
-\
-The code below demonstrates another way of visualizing the rating distribution:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-
-```
-
-This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-
-#### Ratings per movie
-\
-
-##### Movie popularity count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  group_by(movieId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-```{r}
-summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per movie plot[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Movies' rating histogram[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-#### Ratings per user[@MRS-R-BEST]
-\
-
-##### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-##### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
 # Methods / Analysis
@@
 ::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
+The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) script on _GitHub_.
+:::
+
+\newpage
 
@@
 To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
-```{r eval=FALSE }
-make_source_datasets()
-init_source_datasets()
-```
+
+::: { #func.make_source_datasets .sidebar }
+  - [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)
+:::
+
+::: { #func.init_source_datasets .sidebar }
+  - [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L209)
+:::
 
@@
 
-### The `make_source_datasets` function
+### The [make_source_datasets](#func.make_source_datasets) function
 \
@@
 ::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
-:::
-
-Note that we used the `sample_train_validation_sets` function call to split the original dataset (`edx` in this case): 
+This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](#func.make_source_datasets) _function_ code described above.
+:::
+
+Note that we used the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function call to split the original dataset (`edx` in this case):
 ```{r eval=FALSE}
@@
 
-## Overall Mean Rating (Naive) Model
-\
-
-Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
-It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
-
-$$
-Y_{i,j} = \mu + \varepsilon_{i,j}
-$$
-
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
-
-We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
-
-```{r pressure, echo=TRUE}
-mu <- mean(edx$rating)
-print(mu)
-```
-
-If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
-```{r}
-mu.MSEs <- naive_model_MSEs(mu)
-data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
-              xname = "fold_No", 
-              yname = "MSE")
-
-mu.RMSE <- sqrt(mean(mu.MSEs))
-mu.RMSE
-```
-::: {.noteblock data-latex=""}
-For the _Mean Squared Error_ data visualization we used [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function] defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.function.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script.
-:::
-
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      # scale = 1,
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
-
-Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
-
-```{r eval=FALSE }
-naive_model_MSEs <- function(val) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - val)
-  })
-}
-```
-
-One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L59) one:
-```{r eval=FALSE }
-naive_model_RMSE <- function(val){
-  sqrt(mean(naive_model_MSEs(val)))
-}
-```
-
-### Ensure that `mu.RMSE` value is the best for the current model
-\
-
-If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r }
-  deviation <- seq(0, 6, 0.1) - 3
-
-  deviation.RMSE <- sapply(deviation, function(delta){
-    naive_model_RMSE(mu + delta)
-  })
-```
-
-Let's make a quick investigation of the `deviation.RMSE` result we have just got: 
-```{r}
-data.frame(delta = deviation, 
-           delta.RMSE = deviation.RMSE) |> 
-data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
-              xname = "delta", 
-              yname = "delta.RMSE", 
-              xlabel = TeX(r'[$\delta$]'), 
-              ylabel = "RMSE")
-
-which_min_deviation <- deviation[which.min(deviation.RMSE)]
-min_rmse = min(deviation.RMSE)
-
-print_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
-         which_min_deviation)
-
-print_log1("Is the previously computed RMSE the best for the current model: %1",
-         mu.RMSE == min_rmse)
-```
-```{r eval=FALSE}
-RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
-  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.OMR)
-```
-
-To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
-
-## User Effect Model
-\
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
-```{r}
-hist(edx.user_mean_ratings$mean_rating, nclass = 30)
-```
-
-Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
-The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
-So we write the model as follows:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
-$$
-
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
-
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we can compute them this way:
-```{r eval=FALSE}
-a <- rowMeans(y - mu, na.rm = TRUE)
-```
-
-These considerations alows us to compute a _User Mean Ratings_ the following way:
-```{r eval=FALSE}
-put_log("Computing Average Ratings per User (User Mean Ratings)...")
-user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
-user_ratings.n <- rowSums(!is.na(edx.mx))
-
-edx.user_mean_ratings <- 
-  data.frame(userId = names(user.mean_ratings), 
-             mean_rating = user.mean_ratings,
-             n = user_ratings.n)
-
-put_log("User Mean Ratings have been computed.")
-```
-```{r}
-str(edx.user_mean_ratings)
-```
-
-And then we compute a _User Effect_ this way:
-```{r eval=FALSE}
-put_log("Computing User Effect per users ...")
-edx.user_effect <- edx.user_mean_ratings |>
-  mutate(userId = as.integer(userId),
-         a = mean_rating - mu)
-
-put_log("A User Effect Model has been builded")
-```
-```{r}
-par(cex = 0.7)
-hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
-     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
-
-str(edx.user_effect)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect_ computation is available in the [Model building: User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L531) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Finally, we are ready to compute the `RMSE` (additionally using the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) helper function we defined above to keep predictions in the proper range):
-```{r eval=FALSE}
-put_log("Computing the RMSE taking into account user effects...")
-start <- put_start_date()
-edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
-  cv_fold_dat$validation_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - clamp(mu + a)) |> 
-    pull(resid) |> mse()
-})
-put_end_date(start)
-
-edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
-
-RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
-  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
-```
-```{r}
-data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the User Effect Model",
-            xname = "fold_No", 
-            yname = "MSE")
-
-RMSE_kable(RMSEs.ResultTibble.UE)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## User+Movie Effect (UME) Model
-\
-
-In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
-He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
-$$
-The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:
-
-```{r eval=FALSE}
-b <- colMeans(y - mu - a, na.rm = TRUE)
-```
-
-Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
-
-### UME Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
-:::
-
-#### `train_user_movie_effect` Function
-\
-
-We use this function to build and train our model using the `train_set` dataset:
-```{r eval=FALSE}
-train_user_movie_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_effect
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need for the *Regularization*.
-We will explain that later in the [Regularization Method] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the `mean_reg` function is equivalent to the simple `mean` one.
-:::
-
-```{r eval=FALSE}
-# Regularization --------------------------------------------------------------
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-#### `train_user_movie_effect.cv` Function
-\
-
-We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method.
-Below, we provide the most important part of the code of that function:
-```{r eval=FALSE}
-train_user_movie_effect.cv <- function(lambda = 0){
-# ...
-  start <- put_start_date()
-  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
-  })
-  put_end_date(start)
-  put_log("Function: train_user_movie_effect.cv:
-User+Movie Effect list have been computed")
-
-  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-
-  user_movie_effect <- user_movie_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  # ...
-  user_movie_effect
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the `Cross Validation` results.
-:::
-```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
-```
-
-#### `calc_user_movie_effect_MSE` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE <- function(test_set, um_effect){
-  mse.result <- test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(um_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    pull(resid) |> mse()
-
-  stopifnot(!is.na(mse.result))
-  mse.result
-}
-```
-
-#### `calc_user_movie_effect_MSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv <- function(um_effect){
-  put_log("Function: user_movie_effects_MSE.cv:
-Computing the RMSE taking into account User+Movie Effects...")
-  start <- put_start_date()
-  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
-  })
-  put_end_date(start)
-
-  put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_effects_MSEs)
-}
-
-```
-
-#### `calc_user_movie_effect_RMSE` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-  sqrt(mse)
-}
-```
-
-#### `calc_user_movie_effect_RMSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
-  um_effect_RMSE
-}
-
-```
-
-### Model Building
-\
-
-::: {.noteblock data-latex=""}
-The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
-```{r eval=FALSE}
-  cv.UM_effect <- train_user_movie_effect.cv()
-```
-```{r}
-str(cv.UM_effect)
-
-par(cex = 0.7)
-hist(cv.UM_effect$b, 30, xlab = TeX(r'[$\hat{beta}_{j}$)]'),
-     main = TeX(r'[Histogram of $\hat{beta}_{j}$]'))
-```
-
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
-```{r eval=FALSE}
-cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
-
-RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
-  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
-
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.UME)
-```
-
-## Regularizing User+Movie Effect Model
-
-### Utilizing Penalized least squares
-\
-[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-
-$$ 
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
-$$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-
-$$
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-where $n_j$ is the number of ratings made for movie $j$.
-
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
-
-  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
-
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
-
-### UME Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-
-#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
-\
-
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
-```{r eval=FALSE}
-regularize.test_lambda.UM_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UM_effect.cv
-`lambda` is `NA`")
-  }
-  um_effect <- train_user_movie_effect.cv(lambda)
-  calc_user_movie_effect_RMSE.cv(um_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_effect.cv]() calling it from the [regularize.test_lambda.UM_effect.cv](), but now with the $\lambda$ parameter different from the default (zero) value.
-:::
-
-Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r eval=FALSE}
-# Here we will simply compute the RMSE for different values of `lambda` 
-n <- colSums(!is.na(y))
-
-sums <- colSums(y - mu - a, na.rm = TRUE)
-lambdas <- seq(0, 10, 0.1)
-
-rmses <- sapply(lambdas, function(lambda){
-  b <-  sums / (n + lambda)
-  reg_rmse(b)
-})
-
-# Here is a plot of the RMSE versus `lambda`:
-plot(lambdas, rmses, type = "l")
-```
-Now we can determine the minimal _RMSE_:
-```{r}
-# print(min(rmses))
-```
-
-which is achieved for the following $\lambda$:
-```{r eval=FALSE}
-lambda <- lambdas[which.min(rmses)] 
-print(lambda)
-```
-
-Using this $\lambda$ we can compute the regularized estimates:
-```{r eval=FALSE}
-b_reg <- sums / (n + lambda)
-
-str(b_reg)
-```
-Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r eval=FALSE}
-reg_rmse(b_reg)
-```
-
-## Accounting for Date effects
-
-#### Yearly rating count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(count = n())
-)
-```
-
-#### Average rating per year plot[@MRS-R-BEST]
-\
-```{r}
-edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(rating_avg = mean(rating)) |>
-  ggplot(aes(x = year, y = rating_avg)) +
-  geom_bar(stat = "identity", fill = "#8888ff") + 
-  ggtitle("Average rating per year") +
-  xlab("Year") +
-  ylab("Average rating") +
-  scale_y_continuous(labels = comma) + 
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-We use the following models to account for the `date` effect:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
-$$
-
-## Accounting for Genre effect
-\
-As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
-This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
-
-### Genre Data Analysis
-\
-#### Movie Genres Data 
-\
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r eval=FALSE}
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r eval=FALSE}
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r eval=FALSE}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r eval=FALSE}
-print(edx |> group_by(rating) |> summarize(count = n()))
-```
-
-We can visually see that from the following plot:
-```{r eval=FALSE}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
-#### Movie Genres Effect 
-\
-
-The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
-
-```{r eval=FALSE}
-# Preparing data for plotting:
-genre_ratins_grp <- train_set |> 
-  mutate(genre_categories = as.factor(genres)) |>
-  group_by(genre_categories) |>
-  summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
-  filter(n > 20000) |> 
-  mutate(genres = reorder(genre_categories, rating_avg)) |>
-  select(genres, rating_avg, se, n)
-
-dim(genre_ratins_grp)
-genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
-print(genre_ratins_grp_sorted)
-
-# Creating plot:
-genre_ratins_grp |> 
-  ggplot(aes(x = genres, y = rating_avg, ymin = rating_avg - 2*se, ymax = rating_avg + 2*se)) + 
-  geom_point() +
-  geom_errorbar() + 
-  ggtitle("Average rating per Genre") +
-  ylab("Average rating") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-```
-Below are worst and best ratings categories:
-```{r eval=FALSE}
-sprintf("The worst ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.min(genre_ratins_grp$genres)])
-
-sprintf("The best ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.max(genre_ratins_grp$genres)])
-```
-
-Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
-```{r eval=FALSE}
-# For better visibility, we reduce the data for plotting 
-# while keeping the worst and best rating rows:
-plot_ind <- odd(1:nrow(genre_ratins_grp))
-plot_dat <- genre_ratins_grp_sorted[plot_ind,]
-
-plot_dat |>
-  ggplot(aes(x = rating_avg, y = genres)) +
-  ggtitle("Genre Average Rating") +
-  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
-  xlab("Average ratings") +
-  ylab("Genres") +
-  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
-  theme_economist() +
-  theme(plot.title = element_text(vjust = 3.5),
-        axis.title.x = element_text(vjust = -5, face = "bold"),
-        axis.title.y = element_text(vjust = 10, face = "bold"),
-        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
-        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-
-To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
-$$
-
-where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p.
-712) book[@RRSK_RS_HB].
-
-In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:
-
-$$
-g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
-$$
-
-with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
-$$
-
-$$
- \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-# Conclusion
-
-Hello Conclusion!
-
-This is a great conclusion, isn't it?!!
-
-# Appendix
-
-## Regularization: Common Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-#### Parameters
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-#### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-#### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-#### **Parameters**
-\
-
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-##### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-##### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-##### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-##### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-##### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-##### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-##### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-##### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-#### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-#### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-#### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
-:::
-:::
-
-### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-#### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-##### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-#### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-#### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-#### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-#### Parameters
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-#### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-#### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-#### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-## Support Functions
-
-### [func.00]() Function {#func.00}
-\
-
-::: { #func.00.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.00.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.00.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.00.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.00.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.01}
-\
-
-::: { #func.01.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.01.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.01.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.01.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.01.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.02}
-\
-
-::: { #func.02.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.02.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.02.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.02.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.02.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.0]() Function {#func.0}
-\
-
-::: { #func.0.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.0.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.0.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.0.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func1]() Function {#func.03}
-\
-
-::: { #func.03.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.03.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.03.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.03.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.03.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [func1]() Function {#func.1}
-\
-
-::: { #func.1.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.1.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.1.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.1.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.1.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.2]() Function {#func.2}
-\
-
-::: { #func.2.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.2.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.2.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.2.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.2.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
---------------------------------------------------------------------------------
-
-### [func.3]() Function {#func.3}
-\
-
-::: { #func.3.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.3.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.3.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.3.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.3.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.4]() Function {#func.4}
-\
-
-::: { #func.4.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.4.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.4.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.4.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.4.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.5]() Function {#func.5}
-\
-
-::: { #func.5.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.5.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.5.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.5.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.5.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.6]() Function {#func.6}
-\
-
-::: { #func.6.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.6.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.6.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.6.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.6.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.7]() Function {#func.7}
-\
-
-::: { #func.7.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.7.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.7.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.7.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.7.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.8]() Function {#func.8}
-\
-
-::: { #func.8.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.8.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.8.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.8.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.8.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### []() Function {#func.3-1}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-#### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-#### Value
-\
-
-#### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-================================================================================
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
+\newpage

### 2025-05-14 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

--- 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
@@
-```{r setup, include=FALSE, echo = FALSE}
-r.path <- "../r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-# Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-# stop(main_script.file_path)
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
-# External Common Helper functions -------------------------------------
-# common_helper_functions.file_path <- file.path(support_functions.path,
-#                                             "common-helper.functions.R")
-# source(common_helper_functions.file_path, 
-#        local = knitr::knit_global())
-
-# knitr::knit_global()
-#knitr::opts_chunk$set(echo = FALSE)
-```
-
----
-title: "Capstone Movielens Report"
-author: "Azamat Kurbanaev"
-date: "`r Sys.Date()`"
-bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
-envir:
-  parent.frame()
-output: 
-  bookdown::pdf_document2: 
-    df_print: paged
-    toc: true
-    fig_caption: true
-    keep_tex: true
-    citation_package: biblatex
-colorlinks: true
-linkcolor: red
-citecolor: blue
-header-includes:
-    - \usepackage{awesomebox}
-    - \usepackage{hyperref}
-    - \usepackage[natbib=true, 
-                  style=numeric, 
-                  backref=true, 
-                  sorting=none]{biblatex}
-    - \hypersetup{backref,
-          pdfpagemode=Normal,
-          colorlinks=true,
-          implicit=false}
-vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
-  %\VignetteEncoding{UTF-8}
-  %\VignetteEngine{knitr::knitr}
----
-
-\newenvironment{infobox}[1]
-  {
-  \begin{itemize}
-  \renewcommand{\labelitemi}{
-    \raisebox{-.7\height}[0pt][0pt]{
-      {\setkeys{Gin}{width=3em,keepaspectratio}
-        \includegraphics{images/#1}}
-    }
-  }
-  \setlength{\fboxsep}{1em}
-  \begin{blackbox}
-  \item
-  }
-  {
-  \end{blackbox}
-  \end{itemize}
-  }
-
-# Introduction / Overview / Executive Summary
-
-The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
-$$
-\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
-$$
-
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
-
-Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).
-
-## Datasets Overview
-
-To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
-
-* **edx:** we use it to develop and train our algorithms;
-* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
-
-For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
-The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
-
-Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r eval=FALSE }
-if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
-
-library(edx.capstone.movielens.data)
-edx <- edx.capstone.movielens.data::edx
-final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
-```
-
-Now, we have the datasets listed above:
-```{r }
-summary(edx)
-```
-
-```{r }
-summary(final_holdout_test)
-```
-
-### `edx` Dataset
-\
-Let's look into the details of the `edx` dataset:
-``` {r echo = TRUE}
-str(edx)
-```
-Note that we have 9000055 rows and six columns in there:  
-```{r }
-dim_edx <- dim(edx)
-print(dim_edx)
-```
-
-First, let's note that we have 10677 different movies: 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
-
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
-
-```
-
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
-
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Finally, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
-```{r }
-#library(dplyr)
-s <- edx |> group_by(rating) |>
-  summarise(n = n())
-print(s)
-```
-
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
-
-#### Rating distribution plot[@MRS-R-BEST]
-\
-The code below demonstrates another way of visualizing the rating distribution:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-
-```
-
-This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-
-#### Ratings per movie
+## User+Movie+Genre Effect (UMGE) Model
 \
 
-##### Movie popularity count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  group_by(movieId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-```{r}
-summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per movie plot[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Movies' rating histogram[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-#### Ratings per user[@MRS-R-BEST]
-\
-
-##### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-##### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-# Methods / Analysis
-::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
-:::
-
-## Defining Logging and Time Measuring Helper Functions
-\
-
-First, let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
-
-```{r eval=FALSE }
-# Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log1(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log1(msg_template, arg1, arg2))
-}
-
-# ...
-```
-
-::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## Preparing train and set datasets
-\
-
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
-To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
-```{r eval=FALSE }
-make_source_datasets()
-init_source_datasets()
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-### The `make_source_datasets` function
-\
-
-Let's take a closer look at the objects we will receive as a result of executing this function.
-
-```{r eval=FALSE}
-
-make_source_datasets <- function(){
-  # ...
-  list(edx_CV = edx_CV,
-       edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
-       tuning_sets = tuning_sets,
-       movie_map = movie_map,
-       date_days_map = date_days_map)
-}
-```
-
-#### `edx.mx` Matrix Object
-\
-
-We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
-To create this matrix, we use `tidyr::pivot_wider` function:
-
-```{r eval=FALSE}
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-
-```
-
-```{r}
-  str(edx.mx)
-```
-
-#### `edx.sgr` Object
-\
-
-To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-```
-```{r}
-str(edx.sgr)
-summary(edx.sgr)
-```
-
-Note that we use the `splitGenreRows` function to split rows of the original dataset:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function mentioned above is also available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-#### `movie_map` Object
-\
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r eval=FALSE}
-movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-```
-
-```{r}
-str(movie_map)
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
-
-#### `date_days_map` Object
-\
-
-We have a `timestamp` field in the `edx` dataset.
-To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-```
-``` {r}
-  str(date_days_map)
-  summary(date_days_map)
-```
-
-#### `edx_CV` Object
-\
-
-Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_:
-```{r eval=FALSE}
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
-```
-```{r}
-str(edx_CV)
-```
-
-::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
-:::
-
-Note that we used the `sample_train_validation_sets` function call to split the original dataset (`edx` in this case): 
-```{r eval=FALSE}
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-```
-
-which returns a pair of train/validation sets:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets ----------------------------------------------------    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)` one, from where it is called.
-:::
-
-### Common Helper Functions
-\
-
-For our further analysis, we are going to use the following _common helper functions_:
-
-#### `clamp` function
-\
-
-As explained in [Section  24.4 User effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings can’t be below 0.5 or above 5.
-For this reason, we will use the `clamp` function described in that section:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
-#### Functions to calculate _(Root) Mean Squared Error_
-\
-
-We will need the following functions to calculate _(R)MSEs_:
-```{r eval=FALSE}
-mse <- function(r) mean(r^2)
-
-mse_cv <- function(r_list) {
-  mses <- sapply(r_list, mse(r))
-  mean(mses)
-}
-
-rmse <- function(r) sqrt(mse(r))
-# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
-
-rmse2 <- function(true_ratings, predicted_ratings) {
-  rmse(true_ratings - predicted_ratings)
-}
-```
-
-::: {.noteblock data-latex=""}
-All the _common helper functions_, including those described above, are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-## Overall Mean Rating (Naive) Model
-\
-
-Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
-It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
-
-$$
-Y_{i,j} = \mu + \varepsilon_{i,j}
-$$
-
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
-
-We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
-
-```{r pressure, echo=TRUE}
-mu <- mean(edx$rating)
-print(mu)
-```
-
-If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
-```{r}
-mu.MSEs <- naive_model_MSEs(mu)
-data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
-              xname = "fold_No", 
-              yname = "MSE")
-
-mu.RMSE <- sqrt(mean(mu.MSEs))
-mu.RMSE
-```
-::: {.noteblock data-latex=""}
-For the _Mean Squared Error_ data visualization we used [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function] defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.function.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script.
-:::
-
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      # scale = 1,
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
-
-Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
-
-```{r eval=FALSE }
-naive_model_MSEs <- function(val) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - val)
-  })
-}
-```
-
-One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L59) one:
-```{r eval=FALSE }
-naive_model_RMSE <- function(val){
-  sqrt(mean(naive_model_MSEs(val)))
-}
-```
-
-### Ensure that `mu.RMSE` value is the best for the current model
-\
-
-If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r }
-  deviation <- seq(0, 6, 0.1) - 3
-
-  deviation.RMSE <- sapply(deviation, function(delta){
-    naive_model_RMSE(mu + delta)
-  })
-```
-
-Let's make a quick investigation of the `deviation.RMSE` result we have just got: 
-```{r}
-data.frame(delta = deviation, 
-           delta.RMSE = deviation.RMSE) |> 
-data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
-              xname = "delta", 
-              yname = "delta.RMSE", 
-              xlabel = TeX(r'[$\delta$]'), 
-              ylabel = "RMSE")
-
-which_min_deviation <- deviation[which.min(deviation.RMSE)]
-min_rmse = min(deviation.RMSE)
-
-print_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
-         which_min_deviation)
-
-print_log1("Is the previously computed RMSE the best for the current model: %1",
-         mu.RMSE == min_rmse)
-```
-```{r eval=FALSE}
-RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
-  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.OMR)
-```
-
-To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
-
-## User Effect Model
-\
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
-```{r}
-hist(edx.user_mean_ratings$mean_rating, nclass = 30)
-```
-
-Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
-The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
-So we write the model as follows:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
-$$
-
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
-
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we can compute them this way:
-```{r eval=FALSE}
-a <- rowMeans(y - mu, na.rm = TRUE)
-```
-
-These considerations alows us to compute a _User Mean Ratings_ the following way:
-```{r eval=FALSE}
-put_log("Computing Average Ratings per User (User Mean Ratings)...")
-user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
-user_ratings.n <- rowSums(!is.na(edx.mx))
-
-edx.user_mean_ratings <- 
-  data.frame(userId = names(user.mean_ratings), 
-             mean_rating = user.mean_ratings,
-             n = user_ratings.n)
-
-put_log("User Mean Ratings have been computed.")
-```
-```{r}
-str(edx.user_mean_ratings)
-```
-
-And then we compute a _User Effect_ this way:
-```{r eval=FALSE}
-put_log("Computing User Effect per users ...")
-edx.user_effect <- edx.user_mean_ratings |>
-  mutate(userId = as.integer(userId),
-         a = mean_rating - mu)
-
-put_log("A User Effect Model has been builded")
-```
-```{r}
-par(cex = 0.7)
-hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
-     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
-
-str(edx.user_effect)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect_ computation is available in the [Model building: User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L531) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Finally, we are ready to compute the `RMSE` (additionally using the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) helper function we defined above to keep predictions in the proper range):
-```{r eval=FALSE}
-put_log("Computing the RMSE taking into account user effects...")
-start <- put_start_date()
-edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
-  cv_fold_dat$validation_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - clamp(mu + a)) |> 
-    pull(resid) |> mse()
-})
-put_end_date(start)
-
-edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
-
-RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
-  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
-```
-```{r}
-data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the User Effect Model",
-            xname = "fold_No", 
-            yname = "MSE")
-
-RMSE_kable(RMSEs.ResultTibble.UE)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## User+Movie Effect (UME) Model
-\
-
-In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
-He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
-$$
-The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:
-
-```{r eval=FALSE}
-b <- colMeans(y - mu - a, na.rm = TRUE)
-```
-
-Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
-
-### UME Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
-:::
-
-#### `train_user_movie_effect` Function
-\
-
-We use this function to build and train our model using the `train_set` dataset:
-```{r eval=FALSE}
-train_user_movie_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_effect
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need for the *Regularization*.
-We will explain that later in the [Regularization Method] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the `mean_reg` function is equivalent to the simple `mean` one.
-:::
-
-```{r eval=FALSE}
-# Regularization --------------------------------------------------------------
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-#### `train_user_movie_effect.cv` Function
-\
-
-We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method.
-Below, we provide the most important part of the code of that function:
-```{r eval=FALSE}
-train_user_movie_effect.cv <- function(lambda = 0){
-# ...
-  start <- put_start_date()
-  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
-  })
-  put_end_date(start)
-  put_log("Function: train_user_movie_effect.cv:
-User+Movie Effect list have been computed")
-
-  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-
-  user_movie_effect <- user_movie_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  # ...
-  user_movie_effect
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the `Cross Validation` results.
-:::
-```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
-```
-
-#### `calc_user_movie_effect_MSE` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE <- function(test_set, um_effect){
-  mse.result <- test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(um_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    pull(resid) |> mse()
-
-  stopifnot(!is.na(mse.result))
-  mse.result
-}
-```
-
-#### `calc_user_movie_effect_MSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv <- function(um_effect){
-  put_log("Function: user_movie_effects_MSE.cv:
-Computing the RMSE taking into account User+Movie Effects...")
-  start <- put_start_date()
-  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
-  })
-  put_end_date(start)
-
-  put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_effects_MSEs)
-}
-
-```
-
-#### `calc_user_movie_effect_RMSE` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-  sqrt(mse)
-}
-```
-
-#### `calc_user_movie_effect_RMSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
-  um_effect_RMSE
-}
-
-```
-
-### Model Building
-\
-
-::: {.noteblock data-latex=""}
-The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
-```{r eval=FALSE}
-  cv.UM_effect <- train_user_movie_effect.cv()
-```
-```{r}
-str(cv.UM_effect)
-
-par(cex = 0.7)
-hist(cv.UM_effect$b, 30, xlab = TeX(r'[$\hat{beta}_{j}$)]'),
-     main = TeX(r'[Histogram of $\hat{beta}_{j}$]'))
-```
-
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
-```{r eval=FALSE}
-cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
-
-RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
-  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
-
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.UME)
-```
-
-## Regularizing User+Movie Effect Model
-
-### Utilizing Penalized least squares
-\
-[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-
-$$ 
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
-$$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-
-$$
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-where $n_j$ is the number of ratings made for movie $j$.
-
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
-
-  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
-
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
-
-### UME Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-
-#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
-\
-
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
-```{r eval=FALSE}
-regularize.test_lambda.UM_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UM_effect.cv
-`lambda` is `NA`")
-  }
-  um_effect <- train_user_movie_effect.cv(lambda)
-  calc_user_movie_effect_RMSE.cv(um_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_effect.cv]() calling it from the [regularize.test_lambda.UM_effect.cv](), but now with the $\lambda$ parameter different from the default (zero) value.
-:::
-
-Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r eval=FALSE}
-# Here we will simply compute the RMSE for different values of `lambda` 
-n <- colSums(!is.na(y))
-
-sums <- colSums(y - mu - a, na.rm = TRUE)
-lambdas <- seq(0, 10, 0.1)
-
-rmses <- sapply(lambdas, function(lambda){
-  b <-  sums / (n + lambda)
-  reg_rmse(b)
-})
-
-# Here is a plot of the RMSE versus `lambda`:
-plot(lambdas, rmses, type = "l")
-```
-Now we can determine the minimal _RMSE_:
-```{r}
-# print(min(rmses))
-```
-
-which is achieved for the following $\lambda$:
-```{r eval=FALSE}
-lambda <- lambdas[which.min(rmses)] 
-print(lambda)
-```
-
-Using this $\lambda$ we can compute the regularized estimates:
-```{r eval=FALSE}
-b_reg <- sums / (n + lambda)
-
-str(b_reg)
-```
-Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r eval=FALSE}
-reg_rmse(b_reg)
-```
-
-## Accounting for Date effects
-
-#### Yearly rating count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(count = n())
-)
-```
-
-#### Average rating per year plot[@MRS-R-BEST]
-\
-```{r}
-edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(rating_avg = mean(rating)) |>
-  ggplot(aes(x = year, y = rating_avg)) +
-  geom_bar(stat = "identity", fill = "#8888ff") + 
-  ggtitle("Average rating per year") +
-  xlab("Year") +
-  ylab("Average rating") +
-  scale_y_continuous(labels = comma) + 
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-We use the following models to account for the `date` effect:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
-$$
-
-## Accounting for Genre effect
-\
 As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
@@
 
-# Conclusion
-
-Hello Conclusion!
-
-This is a great conclusion, isn't it?!!
-
-# Appendix
-
-## Regularization: Common Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-#### Parameters
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-#### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-#### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-#### **Parameters**
-\
-
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-##### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-##### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-##### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-##### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-##### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-##### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-##### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-##### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-#### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-#### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-#### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
-:::
-:::
-
-### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-#### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-##### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-#### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-#### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-#### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-#### Parameters
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-#### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-#### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-#### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-## Support Functions
-
-### [func.00]() Function {#func.00}
-\
-
-::: { #func.00.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.00.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.00.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.00.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.00.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.01}
-\
-
-::: { #func.01.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.01.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.01.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.01.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.01.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.02}
-\
-
-::: { #func.02.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.02.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.02.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.02.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.02.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.0]() Function {#func.0}
-\
-
-::: { #func.0.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.0.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.0.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.0.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func1]() Function {#func.03}
-\
-
-::: { #func.03.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.03.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.03.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.03.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.03.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [func1]() Function {#func.1}
-\
-
-::: { #func.1.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.1.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.1.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.1.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.1.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.2]() Function {#func.2}
-\
-
-::: { #func.2.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.2.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.2.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.2.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.2.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
---------------------------------------------------------------------------------
-
-### [func.3]() Function {#func.3}
-\
-
-::: { #func.3.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.3.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.3.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.3.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.3.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.4]() Function {#func.4}
-\
-
-::: { #func.4.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.4.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.4.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.4.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.4.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.5]() Function {#func.5}
-\
-
-::: { #func.5.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.5.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.5.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.5.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.5.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.6]() Function {#func.6}
-\
-
-::: { #func.6.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.6.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.6.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.6.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.6.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.7]() Function {#func.7}
-\
-
-::: { #func.7.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.7.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.7.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.7.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.7.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.8]() Function {#func.8}
-\
-
-::: { #func.8.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.8.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.8.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.8.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.8.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### []() Function {#func.3-1}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-#### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-#### Value
-\
-
-#### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-================================================================================
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
+\newpage

### 2025-05-14 reports/capstone-movielens.site/03.conclusion.Rmd

--- 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
@@
-```{r setup, include=FALSE, echo = FALSE}
-r.path <- "../r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-# Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-# stop(main_script.file_path)
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
-# External Common Helper functions -------------------------------------
-# common_helper_functions.file_path <- file.path(support_functions.path,
-#                                             "common-helper.functions.R")
-# source(common_helper_functions.file_path, 
-#        local = knitr::knit_global())
-
-# knitr::knit_global()
-#knitr::opts_chunk$set(echo = FALSE)
-```
-
----
-title: "Capstone Movielens Report"
-author: "Azamat Kurbanaev"
-date: "`r Sys.Date()`"
-bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
-envir:
-  parent.frame()
-output: 
-  bookdown::pdf_document2: 
-    df_print: paged
-    toc: true
-    fig_caption: true
-    keep_tex: true
-    citation_package: biblatex
-colorlinks: true
-linkcolor: red
-citecolor: blue
-header-includes:
-    - \usepackage{awesomebox}
-    - \usepackage{hyperref}
-    - \usepackage[natbib=true, 
-                  style=numeric, 
-                  backref=true, 
-                  sorting=none]{biblatex}
-    - \hypersetup{backref,
-          pdfpagemode=Normal,
-          colorlinks=true,
-          implicit=false}
-vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
-  %\VignetteEncoding{UTF-8}
-  %\VignetteEngine{knitr::knitr}
----
-
-\newenvironment{infobox}[1]
-  {
-  \begin{itemize}
-  \renewcommand{\labelitemi}{
-    \raisebox{-.7\height}[0pt][0pt]{
-      {\setkeys{Gin}{width=3em,keepaspectratio}
-        \includegraphics{images/#1}}
-    }
-  }
-  \setlength{\fboxsep}{1em}
-  \begin{blackbox}
-  \item
-  }
-  {
-  \end{blackbox}
-  \end{itemize}
-  }
-
-# Introduction / Overview / Executive Summary
-
-The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
-$$
-\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
-$$
-
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
-
-Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).
-
-## Datasets Overview
-
-To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
-
-* **edx:** we use it to develop and train our algorithms;
-* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
-
-For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
-The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
-
-Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r eval=FALSE }
-if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
-
-library(edx.capstone.movielens.data)
-edx <- edx.capstone.movielens.data::edx
-final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
-```
-
-Now, we have the datasets listed above:
-```{r }
-summary(edx)
-```
-
-```{r }
-summary(final_holdout_test)
-```
-
-### `edx` Dataset
+# Conclusion
 \
-Let's look into the details of the `edx` dataset:
-``` {r echo = TRUE}
-str(edx)
-```
-Note that we have 9000055 rows and six columns in there:  
-```{r }
-dim_edx <- dim(edx)
-print(dim_edx)
-```
-
-First, let's note that we have 10677 different movies: 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
-
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
-
-```
-
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
-
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Finally, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
-```{r }
-#library(dplyr)
-s <- edx |> group_by(rating) |>
-  summarise(n = n())
-print(s)
-```
-
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
-
-#### Rating distribution plot[@MRS-R-BEST]
-\
-The code below demonstrates another way of visualizing the rating distribution:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-
-```
-
-This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-
-#### Ratings per movie
-\
-
-##### Movie popularity count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  group_by(movieId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-```{r}
-summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per movie plot[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Movies' rating histogram[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-#### Ratings per user[@MRS-R-BEST]
-\
-
-##### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-##### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-# Methods / Analysis
-::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
-:::
-
-## Defining Logging and Time Measuring Helper Functions
-\
-
-First, let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
-
-```{r eval=FALSE }
-# Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log1(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log1(msg_template, arg1, arg2))
-}
-
-# ...
-```
-
-::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## Preparing train and set datasets
-\
-
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
-To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
-```{r eval=FALSE }
-make_source_datasets()
-init_source_datasets()
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-### The `make_source_datasets` function
-\
-
-Let's take a closer look at the objects we will receive as a result of executing this function.
-
-```{r eval=FALSE}
-
-make_source_datasets <- function(){
-  # ...
-  list(edx_CV = edx_CV,
-       edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
-       tuning_sets = tuning_sets,
-       movie_map = movie_map,
-       date_days_map = date_days_map)
-}
-```
-
-#### `edx.mx` Matrix Object
-\
-
-We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
-To create this matrix, we use `tidyr::pivot_wider` function:
-
-```{r eval=FALSE}
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-
-```
-
-```{r}
-  str(edx.mx)
-```
-
-#### `edx.sgr` Object
-\
-
-To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-```
-```{r}
-str(edx.sgr)
-summary(edx.sgr)
-```
-
-Note that we use the `splitGenreRows` function to split rows of the original dataset:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function mentioned above is also available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-#### `movie_map` Object
-\
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r eval=FALSE}
-movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-```
-
-```{r}
-str(movie_map)
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
-
-#### `date_days_map` Object
-\
-
-We have a `timestamp` field in the `edx` dataset.
-To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-```
-``` {r}
-  str(date_days_map)
-  summary(date_days_map)
-```
-
-#### `edx_CV` Object
-\
-
-Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_:
-```{r eval=FALSE}
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
-```
-```{r}
-str(edx_CV)
-```
-
-::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
-:::
-
-Note that we used the `sample_train_validation_sets` function call to split the original dataset (`edx` in this case): 
-```{r eval=FALSE}
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-```
-
-which returns a pair of train/validation sets:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets ----------------------------------------------------    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)` one, from where it is called.
-:::
-
-### Common Helper Functions
-\
-
-For our further analysis, we are going to use the following _common helper functions_:
-
-#### `clamp` function
-\
-
-As explained in [Section  24.4 User effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings can’t be below 0.5 or above 5.
-For this reason, we will use the `clamp` function described in that section:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
-#### Functions to calculate _(Root) Mean Squared Error_
-\
-
-We will need the following functions to calculate _(R)MSEs_:
-```{r eval=FALSE}
-mse <- function(r) mean(r^2)
-
-mse_cv <- function(r_list) {
-  mses <- sapply(r_list, mse(r))
-  mean(mses)
-}
-
-rmse <- function(r) sqrt(mse(r))
-# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
-
-rmse2 <- function(true_ratings, predicted_ratings) {
-  rmse(true_ratings - predicted_ratings)
-}
-```
-
-::: {.noteblock data-latex=""}
-All the _common helper functions_, including those described above, are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-## Overall Mean Rating (Naive) Model
-\
-
-Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
-It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
-
-$$
-Y_{i,j} = \mu + \varepsilon_{i,j}
-$$
-
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
-
-We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
-
-```{r pressure, echo=TRUE}
-mu <- mean(edx$rating)
-print(mu)
-```
-
-If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
-```{r}
-mu.MSEs <- naive_model_MSEs(mu)
-data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
-              xname = "fold_No", 
-              yname = "MSE")
-
-mu.RMSE <- sqrt(mean(mu.MSEs))
-mu.RMSE
-```
-::: {.noteblock data-latex=""}
-For the _Mean Squared Error_ data visualization we used [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function] defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.function.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script.
-:::
-
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      # scale = 1,
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
-
-Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
-
-```{r eval=FALSE }
-naive_model_MSEs <- function(val) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - val)
-  })
-}
-```
-
-One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L59) one:
-```{r eval=FALSE }
-naive_model_RMSE <- function(val){
-  sqrt(mean(naive_model_MSEs(val)))
-}
-```
-
-### Ensure that `mu.RMSE` value is the best for the current model
-\
-
-If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r }
-  deviation <- seq(0, 6, 0.1) - 3
-
-  deviation.RMSE <- sapply(deviation, function(delta){
-    naive_model_RMSE(mu + delta)
-  })
-```
-
-Let's make a quick investigation of the `deviation.RMSE` result we have just got: 
-```{r}
-data.frame(delta = deviation, 
-           delta.RMSE = deviation.RMSE) |> 
-data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
-              xname = "delta", 
-              yname = "delta.RMSE", 
-              xlabel = TeX(r'[$\delta$]'), 
-              ylabel = "RMSE")
-
-which_min_deviation <- deviation[which.min(deviation.RMSE)]
-min_rmse = min(deviation.RMSE)
-
-print_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
-         which_min_deviation)
-
-print_log1("Is the previously computed RMSE the best for the current model: %1",
-         mu.RMSE == min_rmse)
-```
-```{r eval=FALSE}
-RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
-  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.OMR)
-```
-
-To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
-
-## User Effect Model
-\
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
-```{r}
-hist(edx.user_mean_ratings$mean_rating, nclass = 30)
-```
-
-Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
-The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
-So we write the model as follows:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
-$$
-
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
-
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we can compute them this way:
-```{r eval=FALSE}
-a <- rowMeans(y - mu, na.rm = TRUE)
-```
-
-These considerations alows us to compute a _User Mean Ratings_ the following way:
-```{r eval=FALSE}
-put_log("Computing Average Ratings per User (User Mean Ratings)...")
-user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
-user_ratings.n <- rowSums(!is.na(edx.mx))
-
-edx.user_mean_ratings <- 
-  data.frame(userId = names(user.mean_ratings), 
-             mean_rating = user.mean_ratings,
-             n = user_ratings.n)
-
-put_log("User Mean Ratings have been computed.")
-```
-```{r}
-str(edx.user_mean_ratings)
-```
-
-And then we compute a _User Effect_ this way:
-```{r eval=FALSE}
-put_log("Computing User Effect per users ...")
-edx.user_effect <- edx.user_mean_ratings |>
-  mutate(userId = as.integer(userId),
-         a = mean_rating - mu)
-
-put_log("A User Effect Model has been builded")
-```
-```{r}
-par(cex = 0.7)
-hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
-     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
-
-str(edx.user_effect)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect_ computation is available in the [Model building: User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L531) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Finally, we are ready to compute the `RMSE` (additionally using the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) helper function we defined above to keep predictions in the proper range):
-```{r eval=FALSE}
-put_log("Computing the RMSE taking into account user effects...")
-start <- put_start_date()
-edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
-  cv_fold_dat$validation_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - clamp(mu + a)) |> 
-    pull(resid) |> mse()
-})
-put_end_date(start)
-
-edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
-
-RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
-  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
-```
-```{r}
-data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the User Effect Model",
-            xname = "fold_No", 
-            yname = "MSE")
-
-RMSE_kable(RMSEs.ResultTibble.UE)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## User+Movie Effect (UME) Model
-\
-
-In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
-He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
-$$
-The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:
-
-```{r eval=FALSE}
-b <- colMeans(y - mu - a, na.rm = TRUE)
-```
-
-Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
-
-### UME Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
-:::
-
-#### `train_user_movie_effect` Function
-\
-
-We use this function to build and train our model using the `train_set` dataset:
-```{r eval=FALSE}
-train_user_movie_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_effect
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need for the *Regularization*.
-We will explain that later in the [Regularization Method] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the `mean_reg` function is equivalent to the simple `mean` one.
-:::
-
-```{r eval=FALSE}
-# Regularization --------------------------------------------------------------
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-#### `train_user_movie_effect.cv` Function
-\
-
-We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method.
-Below, we provide the most important part of the code of that function:
-```{r eval=FALSE}
-train_user_movie_effect.cv <- function(lambda = 0){
-# ...
-  start <- put_start_date()
-  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
-  })
-  put_end_date(start)
-  put_log("Function: train_user_movie_effect.cv:
-User+Movie Effect list have been computed")
-
-  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-
-  user_movie_effect <- user_movie_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  # ...
-  user_movie_effect
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the `Cross Validation` results.
-:::
-```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
-```
-
-#### `calc_user_movie_effect_MSE` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE <- function(test_set, um_effect){
-  mse.result <- test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(um_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    pull(resid) |> mse()
-
-  stopifnot(!is.na(mse.result))
-  mse.result
-}
-```
-
-#### `calc_user_movie_effect_MSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv <- function(um_effect){
-  put_log("Function: user_movie_effects_MSE.cv:
-Computing the RMSE taking into account User+Movie Effects...")
-  start <- put_start_date()
-  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
-  })
-  put_end_date(start)
-
-  put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_effects_MSEs)
-}
-
-```
-
-#### `calc_user_movie_effect_RMSE` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-  sqrt(mse)
-}
-```
-
-#### `calc_user_movie_effect_RMSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
-  um_effect_RMSE
-}
-
-```
-
-### Model Building
-\
-
-::: {.noteblock data-latex=""}
-The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
-```{r eval=FALSE}
-  cv.UM_effect <- train_user_movie_effect.cv()
-```
-```{r}
-str(cv.UM_effect)
-
-par(cex = 0.7)
-hist(cv.UM_effect$b, 30, xlab = TeX(r'[$\hat{beta}_{j}$)]'),
-     main = TeX(r'[Histogram of $\hat{beta}_{j}$]'))
-```
-
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
-```{r eval=FALSE}
-cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
-
-RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
-  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
-
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.UME)
-```
-
-## Regularizing User+Movie Effect Model
-
-### Utilizing Penalized least squares
-\
-[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-
-$$ 
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
-$$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-
-$$
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-where $n_j$ is the number of ratings made for movie $j$.
-
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
-
-  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
-
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
-
-### UME Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-
-#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
-\
-
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
-```{r eval=FALSE}
-regularize.test_lambda.UM_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UM_effect.cv
-`lambda` is `NA`")
-  }
-  um_effect <- train_user_movie_effect.cv(lambda)
-  calc_user_movie_effect_RMSE.cv(um_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_effect.cv]() calling it from the [regularize.test_lambda.UM_effect.cv](), but now with the $\lambda$ parameter different from the default (zero) value.
-:::
-
-Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r eval=FALSE}
-# Here we will simply compute the RMSE for different values of `lambda` 
-n <- colSums(!is.na(y))
-
-sums <- colSums(y - mu - a, na.rm = TRUE)
-lambdas <- seq(0, 10, 0.1)
-
-rmses <- sapply(lambdas, function(lambda){
-  b <-  sums / (n + lambda)
-  reg_rmse(b)
-})
-
-# Here is a plot of the RMSE versus `lambda`:
-plot(lambdas, rmses, type = "l")
-```
-Now we can determine the minimal _RMSE_:
-```{r}
-# print(min(rmses))
-```
-
-which is achieved for the following $\lambda$:
-```{r eval=FALSE}
-lambda <- lambdas[which.min(rmses)] 
-print(lambda)
-```
-
-Using this $\lambda$ we can compute the regularized estimates:
-```{r eval=FALSE}
-b_reg <- sums / (n + lambda)
-
-str(b_reg)
-```
-Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r eval=FALSE}
-reg_rmse(b_reg)
-```
-
-## Accounting for Date effects
-
-#### Yearly rating count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(count = n())
-)
-```
-
-#### Average rating per year plot[@MRS-R-BEST]
-\
-```{r}
-edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(rating_avg = mean(rating)) |>
-  ggplot(aes(x = year, y = rating_avg)) +
-  geom_bar(stat = "identity", fill = "#8888ff") + 
-  ggtitle("Average rating per year") +
-  xlab("Year") +
-  ylab("Average rating") +
-  scale_y_continuous(labels = comma) + 
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-We use the following models to account for the `date` effect:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
-$$
-
-## Accounting for Genre effect
-\
-As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
-This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
-
-### Genre Data Analysis
-\
-#### Movie Genres Data 
-\
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r eval=FALSE}
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r eval=FALSE}
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r eval=FALSE}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r eval=FALSE}
-print(edx |> group_by(rating) |> summarize(count = n()))
-```
-
-We can visually see that from the following plot:
-```{r eval=FALSE}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
-#### Movie Genres Effect 
-\
-
-The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
-
-```{r eval=FALSE}
-# Preparing data for plotting:
-genre_ratins_grp <- train_set |> 
-  mutate(genre_categories = as.factor(genres)) |>
-  group_by(genre_categories) |>
-  summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
-  filter(n > 20000) |> 
-  mutate(genres = reorder(genre_categories, rating_avg)) |>
-  select(genres, rating_avg, se, n)
-
-dim(genre_ratins_grp)
-genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
-print(genre_ratins_grp_sorted)
-
-# Creating plot:
-genre_ratins_grp |> 
-  ggplot(aes(x = genres, y = rating_avg, ymin = rating_avg - 2*se, ymax = rating_avg + 2*se)) + 
-  geom_point() +
-  geom_errorbar() + 
-  ggtitle("Average rating per Genre") +
-  ylab("Average rating") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-```
-Below are worst and best ratings categories:
-```{r eval=FALSE}
-sprintf("The worst ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.min(genre_ratins_grp$genres)])
-
-sprintf("The best ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.max(genre_ratins_grp$genres)])
-```
-
-Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
-```{r eval=FALSE}
-# For better visibility, we reduce the data for plotting 
-# while keeping the worst and best rating rows:
-plot_ind <- odd(1:nrow(genre_ratins_grp))
-plot_dat <- genre_ratins_grp_sorted[plot_ind,]
-
-plot_dat |>
-  ggplot(aes(x = rating_avg, y = genres)) +
-  ggtitle("Genre Average Rating") +
-  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
-  xlab("Average ratings") +
-  ylab("Genres") +
-  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
-  theme_economist() +
-  theme(plot.title = element_text(vjust = 3.5),
-        axis.title.x = element_text(vjust = -5, face = "bold"),
-        axis.title.y = element_text(vjust = 10, face = "bold"),
-        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
-        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-
-To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
-$$
-
-where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p.
-712) book[@RRSK_RS_HB].
-
-In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:
-
-$$
-g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
-$$
-
-with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
-$$
-
-$$
- \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-# Conclusion
 
@@
 
-# Appendix
-
-## Regularization: Common Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-#### Parameters
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-#### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-#### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-#### **Parameters**
-\
-
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-##### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-##### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-##### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-##### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-##### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-##### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-##### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-##### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-#### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-#### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-#### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
-:::
-:::
-
-### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-#### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-##### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-#### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-#### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-#### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-#### Parameters
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-#### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-#### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-#### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-## Support Functions
-
-### [func.00]() Function {#func.00}
-\
-
-::: { #func.00.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.00.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.00.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.00.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.00.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.01}
-\
-
-::: { #func.01.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.01.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.01.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.01.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.01.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.02}
-\
-
-::: { #func.02.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.02.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.02.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.02.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.02.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.0]() Function {#func.0}
-\
-
-::: { #func.0.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.0.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.0.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.0.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func1]() Function {#func.03}
-\
-
-::: { #func.03.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.03.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.03.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.03.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.03.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [func1]() Function {#func.1}
-\
-
-::: { #func.1.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.1.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.1.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.1.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.1.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.2]() Function {#func.2}
-\
-
-::: { #func.2.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.2.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.2.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.2.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.2.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
---------------------------------------------------------------------------------
-
-### [func.3]() Function {#func.3}
-\
-
-::: { #func.3.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.3.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.3.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.3.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.3.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.4]() Function {#func.4}
-\
-
-::: { #func.4.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.4.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.4.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.4.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.4.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.5]() Function {#func.5}
-\
-
-::: { #func.5.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.5.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.5.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.5.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.5.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.6]() Function {#func.6}
-\
-
-::: { #func.6.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.6.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.6.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.6.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.6.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.7]() Function {#func.7}
-\
-
-::: { #func.7.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.7.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.7.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.7.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.7.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.8]() Function {#func.8}
-\
-
-::: { #func.8.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.8.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.8.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.8.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.8.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### []() Function {#func.3-1}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-#### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-#### Value
-\
-
-#### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-================================================================================
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
+\newpage

### 2025-05-14 reports/capstone-movielens.site/04.appendix.Rmd

--- 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
@@
-```{r setup, include=FALSE, echo = FALSE}
-r.path <- "../r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-# Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-# stop(main_script.file_path)
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
-# External Common Helper functions -------------------------------------
-# common_helper_functions.file_path <- file.path(support_functions.path,
-#                                             "common-helper.functions.R")
-# source(common_helper_functions.file_path, 
-#        local = knitr::knit_global())
-
-# knitr::knit_global()
-#knitr::opts_chunk$set(echo = FALSE)
-```
-
----
-title: "Capstone Movielens Report"
-author: "Azamat Kurbanaev"
-date: "`r Sys.Date()`"
-bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
-envir:
-  parent.frame()
-output: 
-  bookdown::pdf_document2: 
-    df_print: paged
-    toc: true
-    fig_caption: true
-    keep_tex: true
-    citation_package: biblatex
-colorlinks: true
-linkcolor: red
-citecolor: blue
-header-includes:
-    - \usepackage{awesomebox}
-    - \usepackage{hyperref}
-    - \usepackage[natbib=true, 
-                  style=numeric, 
-                  backref=true, 
-                  sorting=none]{biblatex}
-    - \hypersetup{backref,
-          pdfpagemode=Normal,
-          colorlinks=true,
-          implicit=false}
-vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
-  %\VignetteEncoding{UTF-8}
-  %\VignetteEngine{knitr::knitr}
----
-
-\newenvironment{infobox}[1]
-  {
-  \begin{itemize}
-  \renewcommand{\labelitemi}{
-    \raisebox{-.7\height}[0pt][0pt]{
-      {\setkeys{Gin}{width=3em,keepaspectratio}
-        \includegraphics{images/#1}}
-    }
-  }
-  \setlength{\fboxsep}{1em}
-  \begin{blackbox}
-  \item
-  }
-  {
-  \end{blackbox}
-  \end{itemize}
-  }
-
-# Introduction / Overview / Executive Summary
-
-The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
-$$
-\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
-$$
-
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
-
-Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).
-
-## Datasets Overview
-
-To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
-
-* **edx:** we use it to develop and train our algorithms;
-* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
-
-For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
-The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
-
-Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r eval=FALSE }
-if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
-
-library(edx.capstone.movielens.data)
-edx <- edx.capstone.movielens.data::edx
-final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
-```
-
-Now, we have the datasets listed above:
-```{r }
-summary(edx)
-```
-
-```{r }
-summary(final_holdout_test)
-```
-
-### `edx` Dataset
-\
-Let's look into the details of the `edx` dataset:
-``` {r echo = TRUE}
-str(edx)
-```
-Note that we have 9000055 rows and six columns in there:  
-```{r }
-dim_edx <- dim(edx)
-print(dim_edx)
-```
-
-First, let's note that we have 10677 different movies: 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
-
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
-
-```
-
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
-
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Finally, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
-```{r }
-#library(dplyr)
-s <- edx |> group_by(rating) |>
-  summarise(n = n())
-print(s)
-```
-
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
-
-#### Rating distribution plot[@MRS-R-BEST]
-\
-The code below demonstrates another way of visualizing the rating distribution:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-
-```
-
-This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-
-#### Ratings per movie
-\
-
-##### Movie popularity count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  group_by(movieId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-```{r}
-summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per movie plot[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Movies' rating histogram[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-#### Ratings per user[@MRS-R-BEST]
-\
-
-##### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-##### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-# Methods / Analysis
-::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
-:::
-
-## Defining Logging and Time Measuring Helper Functions
-\
-
-First, let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
-
-```{r eval=FALSE }
-# Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log1(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log1(msg_template, arg1, arg2))
-}
-
-# ...
-```
-
-::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## Preparing train and set datasets
-\
-
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
-To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
-```{r eval=FALSE }
-make_source_datasets()
-init_source_datasets()
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-### The `make_source_datasets` function
-\
-
-Let's take a closer look at the objects we will receive as a result of executing this function.
-
-```{r eval=FALSE}
-
-make_source_datasets <- function(){
-  # ...
-  list(edx_CV = edx_CV,
-       edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
-       tuning_sets = tuning_sets,
-       movie_map = movie_map,
-       date_days_map = date_days_map)
-}
-```
-
-#### `edx.mx` Matrix Object
-\
-
-We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
-To create this matrix, we use `tidyr::pivot_wider` function:
-
-```{r eval=FALSE}
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-
-```
-
-```{r}
-  str(edx.mx)
-```
-
-#### `edx.sgr` Object
-\
-
-To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-```
-```{r}
-str(edx.sgr)
-summary(edx.sgr)
-```
-
-Note that we use the `splitGenreRows` function to split rows of the original dataset:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function mentioned above is also available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-#### `movie_map` Object
-\
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r eval=FALSE}
-movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-```
-
-```{r}
-str(movie_map)
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
-
-#### `date_days_map` Object
-\
-
-We have a `timestamp` field in the `edx` dataset.
-To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-```
-``` {r}
-  str(date_days_map)
-  summary(date_days_map)
-```
-
-#### `edx_CV` Object
-\
-
-Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_:
-```{r eval=FALSE}
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
-```
-```{r}
-str(edx_CV)
-```
-
-::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
-:::
-
-Note that we used the `sample_train_validation_sets` function call to split the original dataset (`edx` in this case): 
-```{r eval=FALSE}
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-```
-
-which returns a pair of train/validation sets:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets ----------------------------------------------------    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)` one, from where it is called.
-:::
-
-### Common Helper Functions
-\
-
-For our further analysis, we are going to use the following _common helper functions_:
-
-#### `clamp` function
-\
-
-As explained in [Section  24.4 User effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings can’t be below 0.5 or above 5.
-For this reason, we will use the `clamp` function described in that section:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
-#### Functions to calculate _(Root) Mean Squared Error_
-\
-
-We will need the following functions to calculate _(R)MSEs_:
-```{r eval=FALSE}
-mse <- function(r) mean(r^2)
-
-mse_cv <- function(r_list) {
-  mses <- sapply(r_list, mse(r))
-  mean(mses)
-}
-
-rmse <- function(r) sqrt(mse(r))
-# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
-
-rmse2 <- function(true_ratings, predicted_ratings) {
-  rmse(true_ratings - predicted_ratings)
-}
-```
-
-::: {.noteblock data-latex=""}
-All the _common helper functions_, including those described above, are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-## Overall Mean Rating (Naive) Model
-\
-
-Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
-It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
-
-$$
-Y_{i,j} = \mu + \varepsilon_{i,j}
-$$
-
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
-
-We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
-
-```{r pressure, echo=TRUE}
-mu <- mean(edx$rating)
-print(mu)
-```
-
-If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
-```{r}
-mu.MSEs <- naive_model_MSEs(mu)
-data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
-              xname = "fold_No", 
-              yname = "MSE")
-
-mu.RMSE <- sqrt(mean(mu.MSEs))
-mu.RMSE
-```
-::: {.noteblock data-latex=""}
-For the _Mean Squared Error_ data visualization we used [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function] defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.function.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script.
-:::
-
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      # scale = 1,
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
-
-Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
-
-```{r eval=FALSE }
-naive_model_MSEs <- function(val) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - val)
-  })
-}
-```
-
-One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L59) one:
-```{r eval=FALSE }
-naive_model_RMSE <- function(val){
-  sqrt(mean(naive_model_MSEs(val)))
-}
-```
-
-### Ensure that `mu.RMSE` value is the best for the current model
-\
-
-If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r }
-  deviation <- seq(0, 6, 0.1) - 3
-
-  deviation.RMSE <- sapply(deviation, function(delta){
-    naive_model_RMSE(mu + delta)
-  })
-```
-
-Let's make a quick investigation of the `deviation.RMSE` result we have just got: 
-```{r}
-data.frame(delta = deviation, 
-           delta.RMSE = deviation.RMSE) |> 
-data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
-              xname = "delta", 
-              yname = "delta.RMSE", 
-              xlabel = TeX(r'[$\delta$]'), 
-              ylabel = "RMSE")
-
-which_min_deviation <- deviation[which.min(deviation.RMSE)]
-min_rmse = min(deviation.RMSE)
-
-print_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
-         which_min_deviation)
-
-print_log1("Is the previously computed RMSE the best for the current model: %1",
-         mu.RMSE == min_rmse)
-```
-```{r eval=FALSE}
-RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
-  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.OMR)
-```
-
-To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
-
-## User Effect Model
-\
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
-```{r}
-hist(edx.user_mean_ratings$mean_rating, nclass = 30)
-```
-
-Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
-The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
-So we write the model as follows:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
-$$
-
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
-
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we can compute them this way:
-```{r eval=FALSE}
-a <- rowMeans(y - mu, na.rm = TRUE)
-```
-
-These considerations alows us to compute a _User Mean Ratings_ the following way:
-```{r eval=FALSE}
-put_log("Computing Average Ratings per User (User Mean Ratings)...")
-user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
-user_ratings.n <- rowSums(!is.na(edx.mx))
-
-edx.user_mean_ratings <- 
-  data.frame(userId = names(user.mean_ratings), 
-             mean_rating = user.mean_ratings,
-             n = user_ratings.n)
-
-put_log("User Mean Ratings have been computed.")
-```
-```{r}
-str(edx.user_mean_ratings)
-```
-
-And then we compute a _User Effect_ this way:
-```{r eval=FALSE}
-put_log("Computing User Effect per users ...")
-edx.user_effect <- edx.user_mean_ratings |>
-  mutate(userId = as.integer(userId),
-         a = mean_rating - mu)
-
-put_log("A User Effect Model has been builded")
-```
-```{r}
-par(cex = 0.7)
-hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
-     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
-
-str(edx.user_effect)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect_ computation is available in the [Model building: User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L531) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Finally, we are ready to compute the `RMSE` (additionally using the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) helper function we defined above to keep predictions in the proper range):
-```{r eval=FALSE}
-put_log("Computing the RMSE taking into account user effects...")
-start <- put_start_date()
-edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
-  cv_fold_dat$validation_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - clamp(mu + a)) |> 
-    pull(resid) |> mse()
-})
-put_end_date(start)
-
-edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
-
-RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
-  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
-```
-```{r}
-data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the User Effect Model",
-            xname = "fold_No", 
-            yname = "MSE")
-
-RMSE_kable(RMSEs.ResultTibble.UE)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## User+Movie Effect (UME) Model
-\
-
-In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
-He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
-$$
-The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:
-
-```{r eval=FALSE}
-b <- colMeans(y - mu - a, na.rm = TRUE)
-```
-
-Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
-
-### UME Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
-:::
-
-#### `train_user_movie_effect` Function
-\
-
-We use this function to build and train our model using the `train_set` dataset:
-```{r eval=FALSE}
-train_user_movie_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_effect
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need for the *Regularization*.
-We will explain that later in the [Regularization Method] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the `mean_reg` function is equivalent to the simple `mean` one.
-:::
-
-```{r eval=FALSE}
-# Regularization --------------------------------------------------------------
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-#### `train_user_movie_effect.cv` Function
-\
-
-We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method.
-Below, we provide the most important part of the code of that function:
-```{r eval=FALSE}
-train_user_movie_effect.cv <- function(lambda = 0){
-# ...
-  start <- put_start_date()
-  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
-  })
-  put_end_date(start)
-  put_log("Function: train_user_movie_effect.cv:
-User+Movie Effect list have been computed")
-
-  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-
-  user_movie_effect <- user_movie_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  # ...
-  user_movie_effect
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the `Cross Validation` results.
-:::
-```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
-```
-
-#### `calc_user_movie_effect_MSE` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE <- function(test_set, um_effect){
-  mse.result <- test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(um_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    pull(resid) |> mse()
-
-  stopifnot(!is.na(mse.result))
-  mse.result
-}
-```
-
-#### `calc_user_movie_effect_MSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv <- function(um_effect){
-  put_log("Function: user_movie_effects_MSE.cv:
-Computing the RMSE taking into account User+Movie Effects...")
-  start <- put_start_date()
-  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
-  })
-  put_end_date(start)
-
-  put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_effects_MSEs)
-}
-
-```
-
-#### `calc_user_movie_effect_RMSE` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-  sqrt(mse)
-}
-```
-
-#### `calc_user_movie_effect_RMSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
-  um_effect_RMSE
-}
-
-```
-
-### Model Building
-\
-
-::: {.noteblock data-latex=""}
-The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
-```{r eval=FALSE}
-  cv.UM_effect <- train_user_movie_effect.cv()
-```
-```{r}
-str(cv.UM_effect)
-
-par(cex = 0.7)
-hist(cv.UM_effect$b, 30, xlab = TeX(r'[$\hat{beta}_{j}$)]'),
-     main = TeX(r'[Histogram of $\hat{beta}_{j}$]'))
-```
-
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
-```{r eval=FALSE}
-cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
-
-RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
-  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
-
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.UME)
-```
-
-## Regularizing User+Movie Effect Model
-
-### Utilizing Penalized least squares
-\
-[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-
-$$ 
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
-$$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-
-$$
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-where $n_j$ is the number of ratings made for movie $j$.
-
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
-
-  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
-
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
-
-### UME Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-
-#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
-\
-
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
-```{r eval=FALSE}
-regularize.test_lambda.UM_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UM_effect.cv
-`lambda` is `NA`")
-  }
-  um_effect <- train_user_movie_effect.cv(lambda)
-  calc_user_movie_effect_RMSE.cv(um_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_effect.cv]() calling it from the [regularize.test_lambda.UM_effect.cv](), but now with the $\lambda$ parameter different from the default (zero) value.
-:::
-
-Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r eval=FALSE}
-# Here we will simply compute the RMSE for different values of `lambda` 
-n <- colSums(!is.na(y))
-
-sums <- colSums(y - mu - a, na.rm = TRUE)
-lambdas <- seq(0, 10, 0.1)
-
-rmses <- sapply(lambdas, function(lambda){
-  b <-  sums / (n + lambda)
-  reg_rmse(b)
-})
-
-# Here is a plot of the RMSE versus `lambda`:
-plot(lambdas, rmses, type = "l")
-```
-Now we can determine the minimal _RMSE_:
-```{r}
-# print(min(rmses))
-```
-
-which is achieved for the following $\lambda$:
-```{r eval=FALSE}
-lambda <- lambdas[which.min(rmses)] 
-print(lambda)
-```
-
-Using this $\lambda$ we can compute the regularized estimates:
-```{r eval=FALSE}
-b_reg <- sums / (n + lambda)
-
-str(b_reg)
-```
-Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r eval=FALSE}
-reg_rmse(b_reg)
-```
-
-## Accounting for Date effects
-
-#### Yearly rating count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(count = n())
-)
-```
-
-#### Average rating per year plot[@MRS-R-BEST]
-\
-```{r}
-edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(rating_avg = mean(rating)) |>
-  ggplot(aes(x = year, y = rating_avg)) +
-  geom_bar(stat = "identity", fill = "#8888ff") + 
-  ggtitle("Average rating per year") +
-  xlab("Year") +
-  ylab("Average rating") +
-  scale_y_continuous(labels = comma) + 
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-We use the following models to account for the `date` effect:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
-$$
-
-## Accounting for Genre effect
-\
-As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
-This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
-
-### Genre Data Analysis
-\
-#### Movie Genres Data 
-\
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r eval=FALSE}
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r eval=FALSE}
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r eval=FALSE}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r eval=FALSE}
-print(edx |> group_by(rating) |> summarize(count = n()))
-```
-
-We can visually see that from the following plot:
-```{r eval=FALSE}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
-#### Movie Genres Effect 
-\
-
-The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
-
-```{r eval=FALSE}
-# Preparing data for plotting:
-genre_ratins_grp <- train_set |> 
-  mutate(genre_categories = as.factor(genres)) |>
-  group_by(genre_categories) |>
-  summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
-  filter(n > 20000) |> 
-  mutate(genres = reorder(genre_categories, rating_avg)) |>
-  select(genres, rating_avg, se, n)
-
-dim(genre_ratins_grp)
-genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
-print(genre_ratins_grp_sorted)
-
-# Creating plot:
-genre_ratins_grp |> 
-  ggplot(aes(x = genres, y = rating_avg, ymin = rating_avg - 2*se, ymax = rating_avg + 2*se)) + 
-  geom_point() +
-  geom_errorbar() + 
-  ggtitle("Average rating per Genre") +
-  ylab("Average rating") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-```
-Below are worst and best ratings categories:
-```{r eval=FALSE}
-sprintf("The worst ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.min(genre_ratins_grp$genres)])
-
-sprintf("The best ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.max(genre_ratins_grp$genres)])
-```
-
-Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
-```{r eval=FALSE}
-# For better visibility, we reduce the data for plotting 
-# while keeping the worst and best rating rows:
-plot_ind <- odd(1:nrow(genre_ratins_grp))
-plot_dat <- genre_ratins_grp_sorted[plot_ind,]
-
-plot_dat |>
-  ggplot(aes(x = rating_avg, y = genres)) +
-  ggtitle("Genre Average Rating") +
-  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
-  xlab("Average ratings") +
-  ylab("Genres") +
-  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
-  theme_economist() +
-  theme(plot.title = element_text(vjust = 3.5),
-        axis.title.x = element_text(vjust = -5, face = "bold"),
-        axis.title.y = element_text(vjust = 10, face = "bold"),
-        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
-        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-
-To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
-$$
-
-where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p.
-712) book[@RRSK_RS_HB].
-
-In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:
-
-$$
-g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
-$$
-
-with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
-$$
-
-$$
- \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-# Conclusion
-
-Hello Conclusion!
-
-This is a great conclusion, isn't it?!!
-
-# Appendix
+# Appendix {#appendix.a}
 
@@
 ```
+
+\newpage
 
@@
 
+\newpage
+
 ### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
@@
 
+\newpage
+
 ### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
@@
 
+\newpage
+
 ## Support Functions
+\
 
@@
 \
+
 ```{r eval=FALSE}
@@
 \
+
 The soure code of the [function]() function is shown below:
@@
 :::
-
---------------------------------------------------------------------------------
 
@@
 ```
+
+s

### 2025-05-15 reports/capstone-movielens.site/02.8-1.MF.UMGYDE-model.Rmd
RMD report: `mean_reg` function described.

### UMGYDE Model: Matrix Factorization
\

\newpage

### 2025-05-15 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 
-#### `train_user_movie_effect` Function
+#### [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) Function {#func.train_user_movie_effect}
 \
@@
 The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need for the *Regularization*.
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (For details, see the [mean_reg](#func.mean_reg) function description in the [Appendix](#appendix.a) of this report).
 We will explain that later in the [Regularization Method] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the `mean_reg` function is equivalent to the simple `mean` one.
+For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
+In this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
 :::
 
-```{r eval=FALSE}
-# Regularization --------------------------------------------------------------
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
+\newpage
 
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-#### `train_user_movie_effect.cv` Function
+#### `train_user_movie_effect.cv` Function {#func.train_user_movie_effect.cv}
 \

### 2025-05-15 reports/capstone-movielens.site/04.appendix.Rmd

@@
 The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+:::
+
+### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) Function {#func.mean_reg}
+\
+
+A general function for computing the arithmetic mean given a _regularization parameter_ $\lambda$. We will call it the _penaized mean_.
+
+::: { #func.mean_reg.usage .sidebar }
+#### Usage
+\
+
+```{r eval=FALSE}
+mean_reg(vals, lambda = 0, na.rm = TRUE)
+
+```
+:::
+
+::: { #func.mean_reg.params .sidebar }
+#### Parameters
+\
+
+::: { #func.mean_reg.params.vals .sidebar }
+  - **vals:** values (usually a numeric vector) to calculate the _penalized mean_;
+
+:::
+::: { #func.mean_reg.params.lambda .sidebar }
+  - **lambda:** a _regularization parameter_ $\lambda$ used in the _Regularization techniques_.
+
+:::
+  - **na.rm:** a logical evaluating to TRUE or FALSE indicating whether NA values should be stripped before the computation proceeds.
+
+:::
+
+::: { #func.mean_reg.details .sidebar }
+#### Details
+\
+We call this function internally from the functions that compute the _penalized estimates_  as described in section [23.6 Penalized Least Squares](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook_[@IDS2_23-6].
+
+::: {.noteblock data-latex=""}
+If the [lambda](#func.mean_reg.params.lambda) parameter is `0` (the default), the function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean), calling with the parameter `trim = 0` (the default for the `base::mean` function).
+:::
+:::
+
+::: { #func.mean_reg.value .sidebar }
+#### Value
+\
+
+The function calculates the _penalized mean_ of the [vals](#func.mean_reg.params.vals) parameter as follows:
+$$
+\mu(\lambda) = \frac{1}{\lambda + N} \sum_{i=1}^{N} x_i
+$$
+
+When the [lambda](#func.mean_reg.params.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean as follows:
+$$
+\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
+$$
+
+:::
+
+::: { #func.mean_reg.code .sidebar }
+#### Source Code
+\
+
+The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function is shown below:
+```{r eval=FALSE}
+mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
+  if (is.na(lambda)) {
+    stop("Function: mean_reg
+`lambda` is `NA`")
+  }
+
+  names(lambda) <- NULL
+  sums <- sum(vals, na.rm = na.rm)
+  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
+  sums/(N + lambda)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L62) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) script.
+:::
 :::

### 2025-05-15 r/src/support-scripts/rmd.render.R
RMD report; Citation issue fixed.

@@ -1,24 +1,4 @@
 # Setup & Render ---------------------------------------------------------------
-## Setup
-r.path <- "r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-setup_script.file_path <- file.path(support_scripts.path,
-                                    "setup.R")
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
 
 # rmarkdown::render("reports/capstone-movielens-report.draft4.Rmd",
 #                   output_format = "pdf_document2")
@@ -44,5 +24,16 @@ put(summary(final_holdout_test))
 
 # Render RMD Report
 rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
-                  output_format = "pdf_document2",
-                  output_file = "capstone-movielens.report.pdf")
+                  #output_format = "pdf_document2",
+                  output_file = "capstone-movielens.report.pdf",
+                  run_pandoc = TRUE)
+
+# rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
+#                   output_file = "capstone-movielens.report.pdf",
+#                   # output_format = "pdf_document2",
+#                   output_format = rmarkdown::pdf_document(
+#                     pandoc_args = c("--metadata-file", "main.yaml")
+#                   ),
+#                   envir = .GlobalEnv)
+
+

### 2025-05-15 reports/capstone-movielens.site/04.appendix.Rmd
Report, Appendix updated: function `union_cv_results` described.

@@
 # Appendix {#appendix.a}
+## Data Helper Functions
+\
+
+### [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) Function {#func.union_cv_results}
+\
+
+Aggregates the input data frames into a single data frame.
+
+::: { #func.union_cv_results.Usage .sidebar }
+#### Usage
+\
+
+```{r eval=FALSE}
+union_cv_results(data_list = data)
+
+```
+:::
+
+::: { #func.union_cv_results.params .sidebar }
+#### Parameters
+\
+::: { #func.mean_reg.params.data_list .sidebar }
+  - **data_list:** List of data frames representing the results of the _N-Fold Cross Validation_ method execution.;
+
+:::
+:::
+
+::: { #func.union_cv_results.details .sidebar }
+#### Details
+\
+
+The function is used to aggregate the _N-Fold Cross Validation_ method result data into a single data frame for further processing.
+
+:::
+
+::: { #func.union_cv_results.value .sidebar }
+#### Value
+\
+
+A data frame that is a union of the input data frames.
+:::
+
+::: { #func.union_cv_results.code .sidebar }
+#### Source Code
+\
+
+The soure code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) function is shown below:
+```{r eval=FALSE}
+union_cv_results <- function(data_list) {
+  out_dat <- data_list[[1]]
+
+  for (i in 2:CVFolds_N){
+    out_dat <- union(out_dat, 
+                     data_list[[i]])
+  }
+
+  out_dat
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) is also available in the [Model training](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L431) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) script.
+:::
+:::
 
@@
 
-#### Sugnature
+#### Signature
 \
@@
 
-### [func.00]() Function {#func.00}
-\
-
-::: { #func.00.signature .sidebar }
-#### Sugnature
-\
-
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.00.params .sidebar }
+### [fname00]() Function {#func.fname00}
+\
+
+::: { #func.fname00.Usage .sidebar }
+#### Usage
+\
+
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname00.params .sidebar }
+#### Parameters
+\
+::: { #func.mean_reg.params.param1s .sidebar }
+  - **param1:** description;
+
+:::
+::: { #func.mean_reg.params.param2 .sidebar }
+  - **param2:** description.
+
+:::
+:::
+
+::: { #func.fname00.details .sidebar }
+#### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.fname00.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname00.code .sidebar }
+#### Source Code
+\
+
+The soure code of the [fname00]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [fname00]() is also available in the [Some.Section]() section of the [Somefunctions.R]() script.
+:::
+:::
+
+### [fname01]() Function {#func.fname01}
+\
+
+::: { #func.fname01.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname01.params .sidebar }
 #### Parameters
@@
 
-::: { #func.00.details .sidebar }
+::: { #func.fname01.details .sidebar }
 #### Details
@@
 
-::: { #func.00.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.00.code .sidebar }
-#### Source Code
-\
-
+::: { #func.fname01.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname01.code .sidebar }
+#### Source Code
+\
 The soure code of the [function]() function is shown below:
@@
 
-### [func]() Function {#func.01}
-\
-
-::: { #func.01.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.01.params .sidebar }
+### [fname02]() Function {#func.fname02}
+\
+
+::: { #func.fname02.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname02.params .sidebar }
 #### Parameters
@@
 
-::: { #func.01.details .sidebar }
+::: { #func.fname02.details .sidebar }
 #### Details
@@
 
-::: { #func.01.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.01.code .sidebar }
+::: { #func.fname02.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname02.code .sidebar }
 #### Source Code
@@
 
-### [func]() Function {#func.02}
-\
-
-::: { #func.02.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.02.params .sidebar }
+### [fname0]() Function {#func.fname0}
+\
+
+::: { #func.fname0.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname0.params .sidebar }
 #### Parameters
@@
 
-::: { #func.02.details .sidebar }
+::: { #func.fname0.details .sidebar }
 #### Details
@@
 
-::: { #func.02.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.02.code .sidebar }
+::: { #func.fname0.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname0.code .sidebar }
 #### Source Code
@@
 
---------------------------------------------------------------------------------
-
-### [func.0]() Function {#func.0}
-\
-
-::: { #func.0.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.0.params .sidebar }
+### [fname03]() Function {#func.fname03}
+\
+
+::: { #func.fname03.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname03.params .sidebar }
 #### Parameters
@@
 
-::: { #func.0.details .sidebar }
+::: { #func.fname03.details .sidebar }
 #### Details
@@
 
-::: { #func.0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.0.code .sidebar }
+::: { #func.fname03.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname03.code .sidebar }
 #### Source Code
@@
 ::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func1]() Function {#func.03}
-\
-
-::: { #func.03.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.03.params .sidebar }
+The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+:::
+
+### [fname1]() Function {#func.fname1}
+\
+
+::: { #func.fname1.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname1.params .sidebar }
 #### Parameters
@@
 
-::: { #func.03.details .sidebar }
+::: { #func.fname1.details .sidebar }
 #### Details
@@
 
-::: { #func.03.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.03.code .sidebar }
+::: { #func.fname1.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname1.code .sidebar }
 #### Source Code
@@
 
-### [func1]() Function {#func.1}
-\
-
-::: { #func.1.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.1.params .sidebar }
+--------------------------------------------------------------------------------
+
+### [fname2]() Function {#func.fname2}
+\
+
+::: { #func.fname2.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname2.params .sidebar }
 #### Parameters
@@
 
-::: { #func.1.details .sidebar }
+::: { #func.fname2.details .sidebar }
 #### Details
@@
 
-::: { #func.1.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.1.code .sidebar }
+::: { #func.fname2.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname2.code .sidebar }
 #### Source Code
@@
 
-### [func.2]() Function {#func.2}
-\
-
-::: { #func.2.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.2.params .sidebar }
+--------------------------------------------------------------------------------
+
+### [fname3]() Function {#func.fname3}
+\
+
+::: { #func.fname3.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname3.params .sidebar }
 #### Parameters
@@
 
-::: { #func.2.details .sidebar }
+::: { #func.fname3.details .sidebar }
 #### Details
@@
 
-::: { #func.2.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.2.code .sidebar }
+::: { #func.fname3.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname3.code .sidebar }
 #### Source Code
@@
 
---------------------------------------------------------------------------------
-
-### [func.3]() Function {#func.3}
-\
-
-::: { #func.3.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.3.params .sidebar }
+### [fname4]() Function {#func.fname4}
+\
+
+::: { #func.fname4.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname4.params .sidebar }
 #### Parameters
@@
 
-::: { #func.3.details .sidebar }
+::: { #func.fname4.details .sidebar }
 #### Details
@@
 
-::: { #func.3.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.3.code .sidebar }
+::: { #func.fname4.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname4.code .sidebar }
 #### Source Code
@@
 
-### [func.4]() Function {#func.4}
-\
-
-::: { #func.4.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.4.params .sidebar }
+### [fname5]() Function {#func.fname5}
+\
+
+::: { #func.fname5.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname5.params .sidebar }
 #### Parameters
@@
 
-::: { #func.4.details .sidebar }
+::: { #func.fname5.details .sidebar }
 #### Details
@@
 
-::: { #func.4.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.4.code .sidebar }
+::: { #func.fname5.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname5.code .sidebar }
 #### Source Code
@@
 
-### [func.5]() Function {#func.5}
-\
-
-::: { #func.5.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.5.params .sidebar }
+### [fname6]() Function {#func.fname6}
+\
+
+::: { #func.fname6.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname6.params .sidebar }
 #### Parameters
@@
 
-::: { #func.5.details .sidebar }
+::: { #func.fname6.details .sidebar }
 #### Details
@@
 
-::: { #func.5.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.5.code .sidebar }
+::: { #func.fname6.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname6.code .sidebar }
 #### Source Code
@@
 
-### [func.6]() Function {#func.6}
-\
-
-::: { #func.6.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.6.params .sidebar }
+### [fname7]() Function {#func.fname7}
+\
+
+::: { #func.fname7.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname7.params .sidebar }
 #### Parameters
@@
 
-::: { #func.6.details .sidebar }
+::: { #func.fname7.details .sidebar }
 #### Details
@@
 
-::: { #func.6.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.6.code .sidebar }
+::: { #func.fname7.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname7.code .sidebar }
 #### Source Code
@@
 
-### [func.7]() Function {#func.7}
-\
-
-::: { #func.7.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.7.params .sidebar }
+### [fname8]() Function {#func.fname8}
+\
+
+::: { #func.fname8.signature .sidebar }
+#### Signature
+\
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.fname8.params .sidebar }
 #### Parameters
@@
 
-::: { #func.7.details .sidebar }
+::: { #func.fname8.details .sidebar }
 #### Details
@@
 
-::: { #func.7.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.7.code .sidebar }
+::: { #func.fname8.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.fname8.code .sidebar }
 #### Source Code
@@
 --------------------------------------------------------------------------------
-
-### [func.8]() Function {#func.8}
-\
-
-::: { #func.8.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.8.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.8.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.8.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.8.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### []() Function {#func.3-1}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-#### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-#### Value
-\
-
-#### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-================================================================================
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-s

### 2025-05-15 r/src/support-scripts/rmd.render.R

@@ -23,11 +23,6 @@ sum(is.na(final_holdout_test$rating))
 put(summary(final_holdout_test))
 
 # Render RMD Report
-rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
-                  #output_format = "pdf_document2",
-                  output_file = "capstone-movielens.report.pdf",
-                  run_pandoc = TRUE)
-
 # rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
 #                   output_file = "capstone-movielens.report.pdf",
 #                   # output_format = "pdf_document2",
@@ -35,5 +30,14 @@ rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
 #                     pandoc_args = c("--metadata-file", "main.yaml")
 #                   ),
 #                   envir = .GlobalEnv)
+
+# rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
+#                   #output_format = "pdf_document2",
+#                   output_file = "capstone-movielens.report.pdf",
+#                   run_pandoc = TRUE)
+
+rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
+                  output_file = "capstone-movielens.report.pdf",
+                  run_pandoc = TRUE)
 
 

### 2025-05-16 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report: UME Model Regularization: Preconfiguratin step described.

@@
 The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (For details, see the [mean_reg](#func.mean_reg) function description in the [Appendix](#appendix.a) of this report).
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the [mean_reg](#func.mean_reg) function description in the [Appendix](#appendix.a) of this report).
 We will explain that later in the [Regularization Method] section. 
@@
 ::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the `Cross Validation` results.
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the
+[Appendix](#appendix.a) of this report).
 :::
-```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
-```
 
@@
 
-##### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
+##### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function {#func.regularize.test_lambda.UM_effect.cv}
 \
@@
 ::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_effect.cv]() calling it from the [regularize.test_lambda.UM_effect.cv](), but now with the $\lambda$ parameter different from the default (zero) value.
+Note that we reuse the function [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) calling it from the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
 :::
-
-Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r eval=FALSE}
-# Here we will simply compute the RMSE for different values of `lambda` 
-n <- colSums(!is.na(y))
-
-sums <- colSums(y - mu - a, na.rm = TRUE)
-lambdas <- seq(0, 10, 0.1)
-
-rmses <- sapply(lambdas, function(lambda){
-  b <-  sums / (n + lambda)
-  reg_rmse(b)
-})
-
-# Here is a plot of the RMSE versus `lambda`:
-plot(lambdas, rmses, type = "l")
-```
-Now we can determine the minimal _RMSE_:
-```{r}
-# print(min(rmses))
-```
-
-which is achieved for the following $\lambda$:
-```{r eval=FALSE}
-lambda <- lambdas[which.min(rmses)] 
-print(lambda)
-```
-
-Using this $\lambda$ we can compute the regularized estimates:
-```{r eval=FALSE}
-b_reg <- sums / (n + lambda)
-
-str(b_reg)
-```
-Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r eval=FALSE}
-reg_rmse(b_reg)
-```
 
@@
 #### User+Movie Effect Model Tuning: Preconfiguratioin
-
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Appendix](#appendix.a) of this report.
+\
 
@@
 
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Appendix](#appendix.a) of this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
+
+```{r, eval=FALSE}
+lambdas <- seq(0, 1, 0.1)
+
+cv.UME.preset.result <- 
+  tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)
+
+put_log1("Preliminary regularization set-up of `lambda`s range for the UME Model has been completed
+for the %1-Fold Cross Validation samples.",
+CVFolds_N)
+
+```
+```{r}
+str(cv.UME.preset.result)
+```
+
 ::: {.noteblock data-latex=""}
-The complete version of the code provided in this section can be found in the [Process Preliminary setting-up of lambda range for UM Effect regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
+The complete version of the source code provided in this section can be found in the [Process Preliminary setting-up of lambda range for UM Effect regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
+:::
+
+Now, let's visualize the results of the $\lambda$ range preconfiguration:
+``` {r}
+cv.UME.preset.result$tuned.result |>
+  data.plot(title = TeX(r'[Preliminary set-up of $\lambda$ for Regularazation of the User+Movie Effect Model.]'),
+              xname = "parameter.value", 
+              yname = "RMSE", 
+              xlabel = TeX(r'[$\lambda$]'), 
+              ylabel = "RMSE")
+```
+
+::: {.noteblock data-latex=""}
+We use the custom data visualization function [data.plot](#func.data.plot) described in the [Appendix](#appendix.a.data_helper.functions) of this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
 :::

### 2025-05-16 reports/capstone-movielens.site/04.appendix.Rmd
Report: UME Model Regularization: Preconfiguratin step described.

@@
 # Appendix {#appendix.a}
-## Data Helper Functions
+## Data Helper Functions {#appendix.a.data_helper.functions}
 \
@@
 :::
+
+### [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) Function {#func.data.plot}
+\
+
+::: { #func.data.plot.Usage .sidebar }
+#### Usage
+\
+
+```{r eval=FALSE}
+data.plot(data, 
+          title, 
+          xname, 
+          yname, 
+          xlabel = NULL, 
+          ylabel = NULL,
+          line_col = "blue",
+          # scale = 1,
+          normalize = FALSE)
+```
+:::
+
+::: { #func.data.plot.params .sidebar }
+#### Parameters
+\
+::: { #func.mean_reg.params.param1s .sidebar }
+  - **param1:** description;
+
+:::
+::: { #func.mean_reg.params.param2 .sidebar }
+  - **param2:** description.
+
+:::
+:::
+
+::: { #func.data.plot.details .sidebar }
+#### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.data.plot.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.data.plot.code .sidebar }
+#### Source Code
+\
+
+The soure code of the [data.plot]() function is shown below:
+```{r eval=FALSE}
+data.plot <- function(data, 
+                      title, 
+                      xname, 
+                      yname, 
+                      xlabel = NULL, 
+                      ylabel = NULL,
+                      line_col = "blue",
+                      # scale = 1,
+                      normalize = FALSE) {
+  y <- data[, yname]
+
+  if (normalize) {
+    y <- y - min(y)
+  }
+
+  if (is.null(xlabel)) {
+    xlabel = xname
+  }
+  if (is.null(ylabel)) {
+    ylabel = yname
+  }
+
+  aes_mapping <- aes(x = data[, xname], y = y)
+
+  data |> 
+    ggplot(mapping = aes_mapping) +
+    ggtitle(title) +
+    xlab(xlabel) +
+    ylab(ylabel) +
+    geom_point() + 
+    geom_line(color=line_col)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
+:::
+:::
+
+---------------------------------------------------------
 
@@
   - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ;
+
+::: { #func.tune.model_param.params.fn_tune.test.param_value .sidebar }
   - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.;
+
+:::  
   - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+
   - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.

### 2025-05-16 reports/capstone-movielens.site/02.5.UME-model.Rmd
RMD report: minor refactoring (troubleshooting cross-references)

@@
 The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the [mean_reg](#func.mean_reg) function description in the [Appendix](#appendix.a) of this report).
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] section).
 We will explain that later in the [Regularization Method] section. 
@@
 Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the
-[Appendix](#appendix.a) of this report).
+[Appendix](#appndx_a) of this report).
 :::
@@
 
-### Regularizing User+Movie Effect Model
+### User+Movie Effect Model Regularization
 \
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Appendix](#appendix.a) of this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Appendix](#appndx_a) of this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
 
@@
 ::: {.noteblock data-latex=""}
-We use the custom data visualization function [data.plot](#func.data.plot) described in the [Appendix](#appendix.a.data_helper.functions) of this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
+We use the custom data visualization function [data.plot](#func.data.plot) described in the [Appendix](#appndx_a.data_helper.functions) of this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
 :::

### 2025-05-16 reports/capstone-movielens.site/04.appendix.Rmd
RMD report: minor refactoring (troubleshooting cross-references)

@@
-# Appendix {#appendix.a}
-## Data Helper Functions {#appendix.a.data_helper.functions}
+# Appendix {#appndx_a}
+## Data Helper Functions {#appndx_a.data_helper.functions}
 \
@@
 \
-::: { #func.mean_reg.params.param1s .sidebar }
+::: { #func.mean_reg.params.param1 .sidebar }
   - **param1:** description;
@@
 
-## Regularization: Common Helper Functions
+## Regularization: Common Helper Functions {#appndx_a.rglr.common_helper.functions}
 \
@@
 \
-::: { #func.mean_reg.params.param1s .sidebar }
+::: { #func.fname00.params.param1 .sidebar }
   - **param1:** description;
@@
 :::
-::: { #func.mean_reg.params.param2 .sidebar }
+::: { #func.fname00.params.param2 .sidebar }
   - **param2:** description.

### 2025-05-16 reports/capstone-movielens.site/02.5.UME-model.Rmd
Monor fix for report.

@@
 The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] section).
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
 We will explain that later in the [Regularization Method] section. 

### 2025-05-16 reports/capstone-movielens.site/02.5.UME-model.Rmd
RMD report: cross-references fixed.

@@
 ::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the
-[Appendix](#appndx_a) of this report).
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
 :::
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Appendix](#appndx_a) of this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
+We are going to use the [tune.model_param](#func.tune.model_param) function described in [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) the section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
 
@@
 ::: {.noteblock data-latex=""}
-We use the custom data visualization function [data.plot](#func.data.plot) described in the [Appendix](#appndx_a.data_helper.functions) of this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
+We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
 :::

### 2025-05-16 reports/capstone-movielens.site/02.5.UME-model.Rmd
Couple of minor fixes for report.

@@
 ::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
+The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
 We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
-We will explain that later in the [Regularization Method] section. 
+We will explain that later in the [User+Movie Effect Model Regularization] section. 
 For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.

### 2025-05-16 reports/capstone-movielens.site/04.appendix.Rmd
Couple of minor fixes for report.

@@
 \
+
 ::: { #func.mean_reg.params.data_list .sidebar }

### 2025-05-16 reports/capstone-movielens.site/02.5.UME-model.Rmd
RMD report: fix for the formula.

@@
 [Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
+The author also explains that the general idea of penalized regression is to control the total variability of the movie effects:
+$$
+\sum_{j=1}^{n} \beta_j^2
+$$ 
 Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-
 $$ 
@@
 Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-
 $$
@@
 $$
-
 where $n_j$ is the number of ratings made for movie $j$.
@@
 
-  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
+  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
 
@@
 
-#### User+Movie Effect Model Tuning: Preconfiguratioin
+#### User+Movie Effect Model Tuning: Pre-configuratioin
 \

### 2025-05-16 reports/capstone-movielens.site/02.5.UME-model.Rmd
Minor fix for report.

@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) the section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
 

### 2025-05-16 reports/capstone-movielens.site/04.appendix.Rmd
Minor fix.

@@
           line_col = "blue",
-          # scale = 1,
           normalize = FALSE)
@@
 \
+
 ::: { #func.mean_reg.params.param1 .sidebar }
@@
                       line_col = "blue",
-                      # scale = 1,
                       normalize = FALSE) {
@@
 \
+
 ::: { #func.fname00.params.param1 .sidebar }

### 2025-05-17 reports/capstone-movielens.site/04.appendix.Rmd
RMD report updated: `data.plot` function description completed.

@@
 \
+
+Plots a graph based on the dataset passed in the [data](#func.mean_reg.params.data) parameter, using both points and a line.
 
@@
 
-::: { #func.mean_reg.params.param1 .sidebar }
-  - **param1:** description;
-
-:::
-::: { #func.mean_reg.params.param2 .sidebar }
-  - **param2:** description.
+::: { #func.mean_reg.params.data .sidebar }
+  - **data:** Dataset to use for the plot;
+
+:::
+::: { #func.mean_reg.params.title .sidebar }
+  - **title:** Title of the plot;
+
+:::
+::: { #func.mean_reg.params.xname .sidebar }
+  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;
+
+:::
+::: { #func.mean_reg.params.yname .sidebar }
+  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;
+
+:::
+::: { #func.mean_reg.params.xlabel .sidebar }
+  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
+
+:::
+::: { #func.mean_reg.params.ylabel .sidebar }
+  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;
+
+:::
+::: { #func.mean_reg.params. .sidebar }
+  - **line_col = blue:** The line color;
+
+:::
+::: { #func.mean_reg.params. .sidebar }
+  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
 
@@
 
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.data.plot.value .sidebar }
-#### Value
-\
+The function is a wrapper for the [ggplot2::ggplot](https://ggplot2.tidyverse.org/reference/ggplot.html) function and is a simple and convenient tool for visualizing the data of this project.
 
@@
 
----------------------------------------------------------
+### [data.helper.func0]() Function {#func.data.helper.func0}
+\
+
+::: { #func.data.helper.func0.Usage .sidebar }
+#### Usage
+\
+
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.data.helper.func0.params .sidebar }
+#### Parameters
+\
+
+::: { #func.data.helper.func0.params.p1 .sidebar }
+  - **p1:** description;
+
+:::
+::: { #func.data.helper.func0.params.2 .sidebar }
+  - **p2:** description.
+
+:::
+:::
+
+::: { #func.data.helper.func0.details .sidebar }
+#### Details
+\
+
+::: {.noteblock data-latex=""}
+Note 
+:::
+:::
+
+::: { #func.data.helper.func0.value .sidebar }
+#### Value
+\
+
+:::
+
+::: { #func.data.helper.func0.code .sidebar }
+#### Source Code
+\
+
+The soure code of the [data.helper.func0]() function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [data.helper.func0]() is also available in the [Some.Section]() section of the [Somefunctions.R]() script.
+:::
+:::
 
@@
 
-::: { #func.fname00.params.param1 .sidebar }
-  - **param1:** description;
-
-:::
-::: { #func.fname00.params.param2 .sidebar }
-  - **param2:** description.
+::: { #func.fname00.params.p1 .sidebar }
+  - **p1:** description;
+
+:::
+::: { #func.fname00.params.2 .sidebar }
+  - **p2:** description.
 
@@
 
---------------------------------------------------------------------------------
+## Other Function Templates
+\
 
@@
 
---------------------------------------------------------------------------------
-
---------------------------------------------------------------------------------
-
 ### [fname3]() Function {#func.fname3}
@@
 
---------------------------------------------------------------------------------
-
 ### [fname4]() Function {#func.fname4}
@@
 
---------------------------------------------------------------------------------
-
 ### [fname5]() Function {#func.fname5}
@@
 
---------------------------------------------------------------------------------
-
 ### [fname6]() Function {#func.fname6}
@@
 
---------------------------------------------------------------------------------
-
 ### [fname7]() Function {#func.fname7}
@@
 
---------------------------------------------------------------------------------
-
 ### [fname8]() Function {#func.fname8}
@@
 :::
-
---------------------------------------------------------------------------------

### 2025-05-17 reports/capstone-movielens.site/02.5.UME-model.Rmd
RMD report updated: `data.plot` function description completed.
RMD Report update: UME Model Regularization Metod described.

@@
 Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
-
-\newpage
 
@@
 :::
-
-\newpage
 
@@
 
+  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.
+
 \newpage
@@
 ::: {.noteblock data-latex=""}
-We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
+We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
 :::
@@
 #### User+Movie Effect Model: Fine-Tuning
+\
+
+We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
+
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter:
+```{r, eval=FALSE}
+endpoints <- 
+  get_fine_tune.param.endpoints(cv.UME.preset.result$tuned.result)
+
+UM_effect.loop_starter <- c(endpoints["start"], 
+                            endpoints["end"], 
+                            8)
+UM_effect.loop_starter
+#> [1] 0.3 0.5 8.0
+
+UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"
+
+UME.rglr.fine_tune.results <- 
+  model.tune.param_range(UM_effect.loop_starter,
+                         UME.rglr.fine_tune.cache.path,
+                         UME.rglr.fine_tune.cache.base_name,
+                         regularize.test_lambda.UM_effect.cv)
+                         #endpoint.min_diff = 1e-07/4)
+
+UME.rglr.fine_tune.RMSE.best <- UME.rglr.fine_tune.results$best_result["best_RMSE"]
+```
+```{r}
+writeLines("*** Fine-tuning results object data structure ***")
+str(UME.rglr.fine_tune.results)
+writeLines("--------")
+writeLines('')
+
+writeLines("*** Fine-tuning: best results ***")
+UME.rglr.fine_tune.results$best_result
+writeLines("------")
+writeLines('')
+
+writeLines("*** Fine-tuning: best parameter value ***")
+UME.rglr.fine_tune.RMSE.best
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be also found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+:::
+
+Let's visualize the fine-tuning results:
+```{r}
+UME.rglr.fine_tune.results$tuned.result |>
+  data.plot(title = "Fine-tune Stage results of the Regularization Process for the User+Movie Model",
+              xname = "parameter.value",
+              yname = "RMSE",
+              xlabel = TeX(r'[$\lambda$]'),
+              ylabel = str_glue("Deviation from the best RMSE value (",
+                                as.character(round(UME.rglr.fine_tune.RMSE.best, digits = 7)), 
+                                ")"),
+              normalize = TRUE)
+```
+\newpage
+
+#### Retraining User+Movie Effect Model with the best $\lambda$
+\
+
+Finally, we retrain our model with the best $\lambda$ parameter value we have just figured out:
+```{r, eval=FALSE}
+  UME.rglr.best_lambda <- best_result["param.best_value"]
+  UME.rglr.best_lambda
+
+  rglr.UM_effect <- train_user_movie_effect(edx, UME.rglr.best_lambda)
+
+```
+```{r}
+writeLines("*** The Best Fine-tuning Results ***")
+UME.rglr.fine_tune.results$best_result
+writeLines("------")
+writeLines('')
+
+  print_log1("Re-training Regularized User+Movie Effect Model for the best `lambda`: %1...",
+           UME.rglr.best_lambda)
+writeLines("------")
+writeLines('')
+
+writeLines("*** Regularized User+Movie Effect Structure ***")
+str(rglr.UM_effect)
+writeLines("------")
+writeLines('')
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section are available in the [Re-training Regularized User+Movie Effect Model for the best $\lambda$](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) script on _GitHub_.
+:::
+
+Finally, after _Regularization_, we obtained the following result:
+```{r, eval=FALSE}
+UME.rglr.retrain.RMSE <- calc_user_movie_effect_RMSE.cv(rglr.UM_effect)
+
+RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
+  RMSEs.AddRow("Regularized User+Movie Effect Model", 
+               UME.rglr.retrain.RMSE,
+               comment = "Computed for `lambda` = %1" |>
+                 msg.glue(UME.rglr.best_lambda))
+```
+```{r}
+print_log1("Regularized User+Movie Effect Model has been re-trained for the best `lambda`: %1.",
+         UME.rglr.best_lambda)
+print_log1("The best RMSE after being regularized: %1",
+         UME.rglr.retrain.RMSE)
+
+RMSE_kable(RMSEs.ResultTibble.rglr.UME)
+```
 

### 2025-05-17 r/src/capstone-movielens.main.R

@@ -864,7 +864,7 @@ cv.UME.preset.result$tuned.result |>
 log_close()
 ##### Open log file for Fine-tune Stage of the User+Movie Effect regularization ----
 open_logfile(".UME.rg.fine-tuning")
-##### Fine-tune Stage of the Regularization Process for the User+Movie Model ---- 
+##### Fine-tuning Step of the Regularization Method for the User+Movie Model ---- 
 endpoints <- 
   get_fine_tune.param.endpoints(cv.UME.preset.result$tuned.result)
 
@@ -907,7 +907,7 @@ UME.rglr.fine_tune.results$tuned.result |>
 log_close()
 ##### Open log file for re-train Regularized User+Movie Effect Model -----------
 open_logfile(".UME.rg.re-train.best-lambda")
-##### Re-train Regularized User+Movie Effect Model for the best `lambda` -------
+##### Re-training Regularized User+Movie Effect Model for the best `lambda` -------
 file_name_tmp <- "2.UME.rglr.re-train.best-lambda.RData"
 file_path_tmp <- file.path(UME.regularization.path, file_name_tmp)
 
@@ -977,10 +977,12 @@ put_log1("Regularized User+Movie Effect Model has been re-trained for the best `
 put_log1("The best RMSE after being regularized: %1",
          UME.rglr.retrain.RMSE)
 ##### Add a row to the RMSE Result Table for the Regularized User+Movie Effect Model --------
-RMSEs.ResultTibble <- RMSEs.ResultTibble |> 
+RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
   RMSEs.AddRow("Regularized User+Movie Effect Model", 
-               UME.rglr.retrain.RMSE)
-RMSE_kable(RMSEs.ResultTibble)
+               UME.rglr.retrain.RMSE,
+               comment = "Computed for `lambda` = %1" |>
+                 msg.glue(UME.rglr.best_lambda))
+RMSE_kable(RMSEs.ResultTibble.rglr.UME)
 put_log("A row has been added to the RMSE Result Tibble 
 for the `Regularized User+Movie Effect Model`.")
 ##### Close Log -----------------------------------------------------------------

### 2025-05-18 reports/capstone-movielens.site/02.5.UME-model.Rmd
RMD report: `User+Movie Effect Model` section completed.

@@
 ```
-```{r}
+```{r, echo=FALSE}
 writeLines("*** The Best Fine-tuning Results ***")
 UME.rglr.fine_tune.results$best_result
-writeLines("------")
-writeLines('')
-
-  print_log1("Re-training Regularized User+Movie Effect Model for the best `lambda`: %1...",
-           UME.rglr.best_lambda)
-writeLines("------")
-writeLines('')
 
@@
 str(rglr.UM_effect)
-writeLines("------")
-writeLines('')
 ```
@@
 ```
-```{r}
+```{r, echo=FALSE}
 print_log1("Regularized User+Movie Effect Model has been re-trained for the best `lambda`: %1.",
@@
          UME.rglr.retrain.RMSE)
-
+```
+```{r}
 RMSE_kable(RMSEs.ResultTibble.rglr.UME)

### 2025-05-18 r/src/capstone-movielens.main.R

@@ -1194,9 +1194,9 @@ cv.UMG_effect.RMSE
 #> [1] 0.859473
 
 #### Add a row to the RMSE Result Tibble for the User+Movie+Genre Effect Model ---- 
-RMSEs.ResultTibble <- RMSEs.ResultTibble |> 
+RMSEs.ResultTibble.UMGE <- RMSEs.ResultTibble.rglr.UME |> 
   RMSEs.AddRow("User+Movie+Genre Effect Model", cv.UMG_effect.RMSE)
-RMSE_kable(RMSEs.ResultTibble)
+RMSE_kable(RMSEs.ResultTibble.UMGE)
 put_log("A row has been added to the RMSE Result Tibble for the `User+Movie+Genre Effect Model`.")
 
 #### Close Log -----------------------------------------------------------------

### 2025-05-18 r/src/support-functions/common-helper.functions.R

@@ -41,15 +41,20 @@ RMSEs.AddRow <- function(RMSEs, method, value, comment = ""){
             RMSE = value,
             Comment = comment)
 }
-RMSE_kable <- function(RMSEs){
+RMSE_kable <- function(RMSEs,
+                       col1width = 20,
+                       col2width = 5,
+                       col3width = 20){
   RMSEs |>
     kable(align='lcl', booktabs = T, padding = 5) |> 
     row_spec(0, bold = T) |>
-    column_spec(column = 1, width = "35em") |>
-    column_spec(column = 2, width = "10em") |>
-    column_spec(column = 3, width = "50em") 
+    column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
+    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
+    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
 }
-
+RSME.tibble.col_width <- function(x){
+  "%1em" |> msg.glue(x)
+}
 ## Overall Mean Rating Model ---------------------------------------------------
 naive_model_MSEs <- function(val) {
   sapply(edx_CV, function(cv_item){

### 2025-05-18 reports/capstone-movielens.site/01.intro.Rmd

@@
 Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r eval=FALSE }
+```{r}
 if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")

### 2025-05-18 reports/capstone-movielens.site/04.appendix.Rmd

@@
 
-::: { #func.mean_reg.params.data_list .sidebar }
+::: { #func.union_cv_results.params.data_list .sidebar }
   - **data_list:** List of data frames representing the results of the _N-Fold Cross Validation_ method execution.;
@@
 
-Plots a graph based on the dataset passed in the [data](#func.mean_reg.params.data) parameter, using both points and a line.
+Plots a graph based on the dataset passed in the [data](#func.data.plot.params.data) parameter, using both points and a line.
 
@@
 
-::: { #func.mean_reg.params.data .sidebar }
+::: { #func.data.plot.params.data .sidebar }
   - **data:** Dataset to use for the plot;
@@
 :::
-::: { #func.mean_reg.params.title .sidebar }
+::: { #func.data.plot.params.title .sidebar }
   - **title:** Title of the plot;
@@
 :::
-::: { #func.mean_reg.params.xname .sidebar }
+::: { #func.data.plot.params.xname .sidebar }
   - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;
@@
 :::
-::: { #func.mean_reg.params.yname .sidebar }
+::: { #func.data.plot.params.yname .sidebar }
   - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;
@@
 :::
-::: { #func.mean_reg.params.xlabel .sidebar }
+::: { #func.data.plot.params.xlabel .sidebar }
   - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
@@
 :::
-::: { #func.mean_reg.params.ylabel .sidebar }
+::: { #func.data.plot.params.ylabel .sidebar }
   - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;
@@
 :::
-::: { #func.mean_reg.params. .sidebar }
+::: { #func.data.plot.params.line_col .sidebar }
   - **line_col = blue:** The line color;
@@
 :::
-::: { #func.mean_reg.params. .sidebar }
+::: { #func.data.plot.params.normalize .sidebar }
   - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.

### 2025-05-18 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 
-#### `calc_user_movie_effect_RMSE.cv` Function
+#### `calc_user_movie_effect_RMSE.cv` Function { #func.calc_user_movie_effect_RMSE.cv }
 \
@@
 ```
-```{r}
+```{r, echo=FALSE}
 writeLines("*** Fine-tuning results object data structure ***")
 str(UME.rglr.fine_tune.results)
-writeLines("--------")
-writeLines('')
 
@@
 UME.rglr.fine_tune.results$best_result
-writeLines("------")
-writeLines('')
-
-writeLines("*** Fine-tuning: best parameter value ***")
-UME.rglr.fine_tune.RMSE.best
 ```
@@
 
-Finally, we retrain our model with the best $\lambda$ parameter value we have just figured out:
+Now, we can calculate the _Regularized User+Movie Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
 ```{r, eval=FALSE}
@@
   rglr.UM_effect <- train_user_movie_effect(edx, UME.rglr.best_lambda)
-
 ```
@@
 str(rglr.UM_effect)
+
+print_log1("Regularized User+Movie Effect Model has been re-trained for the best `lambda`: %1.",
+         UME.rglr.best_lambda)
 ```
@@
 
-Finally, after _Regularization_, we obtained the following result:
+We calculate the _Root Mean Squared Error_ for the ultimately computed _User+Movie Effect_ using [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function described above as follows:
 ```{r, eval=FALSE}
 UME.rglr.retrain.RMSE <- calc_user_movie_effect_RMSE.cv(rglr.UM_effect)
+```
+```{r}
+print_log1("The best RMSE after being regularized: %1",
+         UME.rglr.retrain.RMSE)
+```
 
+Finally, we add the definitive result for the current model to our _Result Table_:
+```{r, eval=FALSE}
 RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
@@
 ```
-```{r, echo=FALSE}
-print_log1("Regularized User+Movie Effect Model has been re-trained for the best `lambda`: %1.",
-         UME.rglr.best_lambda)
-print_log1("The best RMSE after being regularized: %1",
-         UME.rglr.retrain.RMSE)
-```
 ```{r}

### 2025-05-18 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Started working on the current model (in progress).

@@
 \
+
 #### Movie Genres Data 
 \
+
 The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r eval=FALSE}
+```{r }
 #library(stringr)
@@
 Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r eval=FALSE}
+```{r }
 ordered_movie_ratings <- edx |> group_by(movieId, title) |>
@@
 and figure out the most given ratings in order from most to least:
-```{r eval=FALSE}
+```{r}
 ratings <- edx |>  group_by(rating) |>
@@
 The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r eval=FALSE}
-print(edx |> group_by(rating) |> summarize(count = n()))
+```{r}
+edx |> group_by(rating) |> summarize(count = n())
 ```
@@
 We can visually see that from the following plot:
-```{r eval=FALSE}
+```{r}
 edx |>
@@
 
-```{r eval=FALSE}
+```{r }
 # Preparing data for plotting:
-genre_ratins_grp <- train_set |> 
+genre_ratins_grp <- edx |> 
   mutate(genre_categories = as.factor(genres)) |>
@@
   summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
-  filter(n > 20000) |> 
+  filter(n > 40000) |> 
   mutate(genres = reorder(genre_categories, rating_avg)) |>
@@
 Below are worst and best ratings categories:
-```{r eval=FALSE}
+```{r, echo=FALSE}
 sprintf("The worst ratings are for the genre category: %s",
@@
 Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
-```{r eval=FALSE}
+```{r }
 # For better visibility, we reduce the data for plotting 

### 2025-05-19 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
`UMGE Model: Support Funcions` section added.

@@
 
+### UMGE Model: Support Functions
+\
+
+::: {.noteblock data-latex=""}
+The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L1) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script on _GitHub_.
+:::
+
+#### [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L40) Function {#func.train_user_movie_genre_effect}
+\
+
+We use this function to build and train our model using a _Train Set_ (passing it to the `train.sgr` parameter), which can be any sample of the `edx.sgr` dataset (or the entire dataset itself) described above in the [`edx.sgr` Object] section.
+Here I only remind that it is the dataset created from the `edx` one by splitting its rows to ensure that each one belongs to a single _genre_.
+Here is the source code of the function:
+```{r eval=FALSE}
+train_user_movie_genre_effect <- function(train.sgr, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_user_movie_genre_effect
+`lambda` is `NA`")
+  }
+
+  genre_bias <- train.sgr |>
+      left_join(edx.user_effect, by = "userId") |>
+      left_join(rglr.UM_effect, by = "movieId") |>
+      mutate(resid = rating - (mu + a + b)) |>
+      group_by(genres) |>
+      summarise(g = mean_reg(resid, lambda), n = n())
+
+    train.sgr |>
+      left_join(genre_bias, by = "genres") |>
+      left_join(rglr.UM_effect, by = "movieId") |>
+      group_by(movieId) |>
+      summarise(g = mean(g))
+}
+```
+
+::: {.noteblock data-latex=""}
+The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We have already explained that in the [User+Movie Effect Model Regularization] section. 
+For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
+Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
+:::
+
+#### `train_user_movie_genre_effect.cv` Function {#func.train_user_movie_genre_effect.cv}
+\
+
+We use the [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) function to build and train our model using the `5-Fold Cross Validation` method.
+Below, we provide a slightly simplified version of the source code of that function:
+```{r eval=FALSE}
+train_user_movie_genre_effect.cv <- function(lambda = 0){
+  # ...
+
+put_log1("Function `train_user_movie_genre_effect.cv`:
+Computing User+Movie+Genre Effects list for %1-Fold Cross Validation samples...", 
+           CVFolds_N)
+
+  start <- put_start_date()
+  user_movie_genre_effects_ls <- lapply(kfold_index, function(fold_i){
+    cv_fold_dat <- edx_CV[[fold_i]]
+
+    put_log2("Processing User+Movie+Genre Effects for %1-Fold Cross Validation samples (Fold %2)...",
+             CVFolds_N,
+             fold_i)
+    umg_effect <- cv_fold_dat$train.sgr |> train_user_movie_genre_effect(lambda)
+
+    put_log2("User+Movie+Genre Effects have been computed for the Fold %1 
+of the %2-Fold Cross Validation samples.",
+             fold_i,
+             CVFolds_N)
+    umg_effect
+  })
+  put_end_date(start)
+  put_log1("Function `train_user_movie_genre_effect.cv`:
+User+Movie+Genre Effects list has been computed for %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  user_movie_genre_effects_united <- union_cv_results(user_movie_genre_effects_ls)
+
+  user_movie_genre_effect <- user_movie_genre_effects_united |>
+    group_by(movieId) |>
+    summarise(g = mean(g))
+
+  if(lambda == 0) put_log("Function `train_user_movie_genre_effect.cv`:
+Training completed: User+Movie+Genre Effects model.")
+  else put_log1("Function `train_user_movie_genre_effect.cv`:
+Training completed: User+Movie+Genre Effects model for lambda: %1...",
+                lambda)
+
+  user_movie_genre_effect
+}
+```
+
+::: {.noteblock data-latex=""}
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
+:::
+
+#### `calc_user_movie_genre_effect_MSE` Function
+\
+
+The code of the function [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L110) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
+```{r eval=FALSE}
+calc_user_movie_genre_effect_MSE <- function(test_set, umg_effect){
+  test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(umg_effect, by = "movieId") |>
+    mutate(resid = rating - clamp(mu + a + b + g)) |> 
+    pull(resid) |> mse()
+}
+```
+
 \newpage
+
+#### `calc_user_movie_genre_effect_MSE.cv` Function
+\
+
+The code of the function [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L72) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
+```{r eval=FALSE}
+```
+
+#### `calc_user_movie_genre_effect_RMSE` Function
+\
+
+The code of the function [calc_user_movie_genre_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L51) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
+
+```{r eval=FALSE}
+
+```
+
+#### `calc_user_movie_genre_effect_RMSE.cv` Function { #func.calc_user_movie_genre_effect_RMSE.cv }
+\
+
+The code of the function [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L65) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
+
+```{r eval=FALSE}
+
+```
+
+\newpage
+
+### UMGE Model: Genre Mean Rating
+\
+
+We start with computing _Genre Mean Rating_ to build our next model based on the _UM Effect_ one described in the previous section.
+We will call the new model the _User+Movie+Genre Effect (UMGE)_  Model or _UMG Effect_ Model.
+
+\newpage

### 2025-05-19 r/src/support-functions/UMG-effect.functions.R

@@ -47,17 +47,12 @@ train_user_movie_genre_effect <- function(train.sgr, lambda = 0){
       left_join(edx.user_effect, by = "userId") |>
       left_join(rglr.UM_effect, by = "movieId") |>
       mutate(resid = rating - (mu + a + b)) |>
-      # filter(!is.na(resid)) |>
       group_by(genres) |>
-      summarise(g = mean_reg(resid, lambda), n = n()) #|>
-    #filter(n > min_nratings)
-    
-    # print(c(g_NAs = sum(is.na(genre_bias$g))))
-    
+      summarise(g = mean_reg(resid, lambda), n = n())
+
     train.sgr |>
       left_join(genre_bias, by = "genres") |>
       left_join(rglr.UM_effect, by = "movieId") |>
-      # filter(!is.na(g)) |>
       group_by(movieId) |>
       summarise(g = mean(g))
 }
@@ -91,22 +86,15 @@ Computing User+Movie+Genre Effects list for %1-Fold Cross Validation samples..."
 of the %2-Fold Cross Validation samples.",
              fold_i,
              CVFolds_N)
-    # print(movie_genre_effects)
     umg_effect
   })
-  print(str(user_movie_genre_effects_ls))
   put_end_date(start)
-  #> Time difference of 34.83447 secs
   put_log1("Function `train_user_movie_genre_effect.cv`:
 User+Movie+Genre Effects list has been computed for %1-Fold Cross Validation samples.", 
            CVFolds_N)
 
   user_movie_genre_effects_united <- union_cv_results(user_movie_genre_effects_ls)
-  print(str(user_movie_genre_effects_united))
-  # sum(user_movie_genre_effects_united$g != 0)
-  # sum(is.na(user_movie_genre_effects_united$b))
-  # sum(is.na(user_movie_genre_effects_united$g))
-  
+
   user_movie_genre_effect <- user_movie_genre_effects_united |>
     group_by(movieId) |>
     summarise(g = mean(g))
@@ -117,7 +105,6 @@ Training completed: User+Movie+Genre Effects model.")
 Training completed: User+Movie+Genre Effects model for lambda: %1...",
                 lambda)
   
-  # print(str(user_movie_genre_effect))
   user_movie_genre_effect
 }
 calc_user_movie_genre_effect_MSE <- function(test_set, umg_effect){
[…]

### 2025-05-19 reports/capstone-movielens.site/02.5.UME-model.Rmd
Basic model documented.

@@
 ::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
+The complete source code of the functions described in this section is available in the [UME Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
 :::
@@
 
-The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
+The source code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the _Mean Squared Error (MSE)_ of the _UME Model_ for the given `Test Set` is provided below:
 ```{r eval=FALSE}
@@
 
-\newpage
-
 #### `calc_user_movie_effect_MSE.cv` Function
@@
 
-The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
+The source code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the _5-Fold Cross Validation_ **MSE**_ result of the _UME Model_ is provided below:
 ```{r eval=FALSE}
@@
 
-The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
+The source code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
 
@@
 
-The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
+The source code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
 
@@
 
-### Model Building
+### UME Model Building
 \
@@
 ::: {.noteblock data-latex=""}
-The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+The complete source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
 :::
@@
 
-#### User+Movie Effect Model Tuning: Pre-configuratioin
+#### UME Model Regularization: Pre-configuratioin
 \
@@
 
-#### User+Movie Effect Model: Fine-Tuning
+#### UME Model Regularization: Fine-tuning
 \
@@
 
-#### Retraining User+Movie Effect Model with the best $\lambda$
+#### UME Model Regularization: Retraining Model with the best $\lambda$
 \

### 2025-05-19 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Basic model documented.

@@
 This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
+
+To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
 
@@
 
+### Mathematical Description of the UMGE Model
+\
+
 If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-
-To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
-
 $$
@@
 
+Therefore, for our current model, we can compute the expected value 
 $$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
+\hat{g}_{i,j} = g_{i,j} + \varepsilon_{i,j}
 $$
-
+as a residual: 
 $$
- \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
+\hat{g}_{i,j} = Y_{i,j} - (\mu + \alpha_i + \beta_j)
 $$
@@
 ::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L1) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script on _GitHub_.
+The complete source code of the functions described in this section is available in the [UMGE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L1) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script on _GitHub_.
 :::
@@
 
-The code of the function [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L110) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
+The source code of the function [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L110) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _Mean Squared Error (MSE)_ of the _UMGE Model_ for the given _Test Set_ is provided below:
 ```{r eval=FALSE}
@@
 
-The code of the function [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L72) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
+The source code of the function [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L122) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _5-Fold Cross Validation MSE_ result of the _UMGE Model_ is provided below:
 ```{r eval=FALSE}
+calc_user_movie_genre_effect_MSE.cv <- function(umg_effect){
+  put_log("Computing RMSEs.ResultTibble on Validation Sets...")
+  start <- put_start_date()
+  user_movie_genre_effects_MSEs <- sapply(edx_CV, function(cv_dat){
+    cv_dat$validation_set |> calc_user_movie_genre_effect_MSE(umg_effect)
+  })
+  put_end_date(start)
+
+  plot(user_movie_genre_effects_MSEs)
+  put_log1("MSE values have been plotted for the %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  mean(user_movie_genre_effects_MSEs)
+}
 ```
@@
 
-The code of the function [calc_user_movie_genre_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L51) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
+The source code of the function [calc_user_movie_genre_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L118) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _Root Mean Squared Error (RMSE)_ of the _UMGE Model_ for the given _Test Set_ is provided below:
 
 ```{r eval=FALSE}
-
+calc_user_movie_genre_effect_RMSE <- function(test_set, umg_effect){
+  umg_mse <- test_set |> calc_user_movie_genre_effect_MSE(umg_effect)
+  sqrt(umg_mse)
+}
 ```
@@
 
-The code of the function [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L65) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
+The source code of the function [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L136) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _5-Fold Cross Validation **RMSE**_ result of the _UMGE Model_ is provided below:
 
 ```{r eval=FALSE}
+calc_user_movie_genre_effect_RMSE.cv <- function(umg_effect){
+  umg_effect_RMSE <- sqrt(calc_user_movie_genre_effect_MSE.cv(umg_effect))
+  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
+           CVFolds_N, 
+           umg_effect_RMSE)
 
+  umg_effect_RMSE
+}
 ```
@@
 
-### UMGE Model: Genre Mean Rating
+### UMGE Model Building
 \
 
-We start with computing _Genre Mean Rating_ to build our next model based on the _UM Effect_ one described in the previous section.
-We will call the new model the _User+Movie+Genre Effect (UMGE)_  Model or _UMG Effect_ Model.
+::: {.noteblock data-latex=""}
+The complete source code of builing and training the current model is available in the [Model building: User+Movie+Genre Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1149) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+:::
+
+Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
+```{r, eval=FALSE}
+  cv.UMG_effect <- train_user_movie_genre_effect.cv()
+```
+```{r}
+str(cv.UMG_effect)
+
+par(cex = 0.7)
+hist(cv.UMG_effect$g, 30, xlab = TeX(r'[$\hat{g}_{i,j}$]'),
+     main = TeX(r'[Histogram of $\hat{g}_{i,j}$]'))
+```
+
+We can now construct predictors and calculate the _RMSE_ of the current model using the [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) function described above:
+
+```{r, eval=FALSE}
+cv.UMG_effect.RMSE <- calc_user_movie_genre_effect_RMSE.cv(cv.UMG_effect)
+
+RMSEs.ResultTibble.UMGE <- RMSEs.ResultTibble.rglr.UME |> 
+  RMSEs.AddRow("User+Movie+Genre Effect Model", cv.UMG_effect.RMSE)
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.UMGE)
+```
+
+::: {.noteblock data-latex=""}
+Unfortunately, we do not see any improvement here yet.
+:::
 
 \newpage
+
+$$
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
+$$
+
+$$
+ \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
+$$

### 2025-05-19 r/src/support-functions/UM-effect.functions.R

@@ -1,4 +1,4 @@
-# User+Movie Effect Model Functions --------------------------------------------
+# UME Model Support Functions --------------------------------------------------
 train_user_movie_effect <- function(train_set, lambda = 0){
   if (is.na(lambda)) {
     stop("Function: train_user_movie_effect

### 2025-05-19 r/src/support-functions/UMG-effect.functions.R

@@ -1,4 +1,4 @@
-# User+Movie+Genre Effect Support Functions ------------------------------------
+# UMGE Model Support Functions -------------------------------------------------
 calc_genre_mean_ratings <- function(train_set, min_nratings = 0) {
   genre.min_ratings <- train_set |> 
     mutate(genre_categories = as.factor(genres)) |>
@@ -127,7 +127,6 @@ calc_user_movie_genre_effect_MSE.cv <- function(umg_effect){
   })
   put_end_date(start)
   
-  # browser()
   plot(user_movie_genre_effects_MSEs)
   put_log1("MSE values have been plotted for the %1-Fold Cross Validation samples.", 
            CVFolds_N)

### 2025-05-19 reports/capstone-movielens.site/02.5.UME-model.Rmd
Bunch of minor fixes.

@@
 The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
 We will explain that later in the [User+Movie Effect Model Regularization] section. 

### 2025-05-19 r/src/capstone-movielens.main.R
Minor fix.

@@ -1195,7 +1195,7 @@ cv.UMG_effect.RMSE
 
 #### Add a row to the RMSE Result Tibble for the User+Movie+Genre Effect Model ---- 
 RMSEs.ResultTibble.UMGE <- RMSEs.ResultTibble.rglr.UME |> 
-  RMSEs.AddRow("User+Movie+Genre Effect Model", cv.UMG_effect.RMSE)
+  RMSEs.AddRow("User+Movie+Genre Effect (UMGE) Model", cv.UMG_effect.RMSE)
 RMSE_kable(RMSEs.ResultTibble.UMGE)
 put_log("A row has been added to the RMSE Result Tibble for the `User+Movie+Genre Effect Model`.")
 

### 2025-05-19 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Minor fix.

@@
 
-Therefore, for our current model, we can compute the expected value 
+Therefore, for our current model, we can compute a predicted value 
 $$
@@
 We use this function to build and train our model using a _Train Set_ (passing it to the `train.sgr` parameter), which can be any sample of the `edx.sgr` dataset (or the entire dataset itself) described above in the [`edx.sgr` Object] section.
-Here I only remind that it is the dataset created from the `edx` one by splitting its rows to ensure that each one belongs to a single _genre_.
+Here, I only remind that it is the dataset created from the `edx` one by splitting its rows to ensure each belongs to a single _genre_.
 Here is the source code of the function:
@@
 The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
 We have already explained that in the [User+Movie Effect Model Regularization] section. 
@@
 
+\newpage
+
 We can now construct predictors and calculate the _RMSE_ of the current model using the [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) function described above:
@@
 RMSEs.ResultTibble.UMGE <- RMSEs.ResultTibble.rglr.UME |> 
-  RMSEs.AddRow("User+Movie+Genre Effect Model", cv.UMG_effect.RMSE)
+  RMSEs.AddRow("User+Movie+Genre Effect (UMGE) Model", cv.UMG_effect.RMSE)
 ```
@@
 ::: {.noteblock data-latex=""}
-Unfortunately, we do not see any improvement here yet.
+Unfortunately, for some reason, we do not see any improvement here yet.
 :::
@@
 $$
+
+\newpage

### 2025-05-20 reports/templates/02.X.UM+model.template.Rmd
Model RMD Template added.

## UM? Effect (UM?E) Model
\

### Mathematical Description of the UM?E Model
\

$$
Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
$$

If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
$$
Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
$$

where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p. 712) book[@RRSK_RS_HB].

In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:

$$
g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
$$

with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.

Therefore, for our current model, we can compute a predicted value 
$$
\hat{g}_{i,j} = g_{i,j} + \varepsilon_{i,j}
$$
as a residual: 
$$
\hat{g}_{i,j} = Y_{i,j} - (\mu + \alpha_i + \beta_j)
$$

### UM?E Model: Support Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the [UM?E Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) section of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script on _GitHub_.
:::

#### [train_UM?_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) Function {#func.train_UM?_effect}
\

We use this function to build and train our model using the `train_set` dataset:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method. We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
We have already explained that in the [UM? Effect Model Regularization] section. 
For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
:::

#### `train_UM?E_effect.cv` Function {#func.train_UM?E_effect.cv}
\

We use the [train_UM?E_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/#L59) function to build and train our model using the `5-Fold Cross Validation` method. Below, we provide a slightly simplified version of the source code of that function:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
:::

#### `calc_UM?E_effect_MSE` Function
\

The source code of the function [calc_UM?E_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _Mean Squared Error (MSE)_ of the _UM?E Model_ for the given _Test Set_ is provided below:
```{r eval=FALSE}
```

\newpage

#### `calc_UM?E_effect_MSE.cv` Function
\

The source code of the function [calc_UM?E_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _5-Fold Cross Validation MSE_ result of the _UM?E Model_ is provided below:
```{r eval=FALSE}
```

#### `calc_UM?E_effect_RMSE` Function
\

The source code of the function [calc_UM?E_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/#L118) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _Root Mean Squared Error (RMSE)_ of the _UM?E Model_ for the given _Test Set_ is provided below:

```{r eval=FALSE}
```

#### `calc_UM?E_effect_RMSE.cv` Function { #func.calc_UM?E_effect_RMSE.cv }
\

The source code of the function [calc_UM?E_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _5-Fold Cross Validation **RMSE**_ result of the _UM?E Model_ is provided below:

```{r eval=FALSE}
```

\newpage

### UM?E Model Building
\

::: {.noteblock data-latex=""}
The complete source code of builing and training the current model is available in the [Model building: UM? Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
:::

Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
```{r, eval=FALSE}
```

\newpage

We can now construct predictors and calculate the _RMSE_ of the current model using the [calc_UM?E_effect_RMSE.cv](#func.calc_UM?E_effect_RMSE.cv) function described above:

```{r, eval=FALSE}
cv.UMG_effect.RMSE <- calc_UM?E_effect_RMSE.cv(cv.UMG_effect)

RMSEs.ResultTibble.UM?E <- RMSEs.ResultTibble.rglr.UM?E |> 
  RMSEs.AddRow("UM? Effect (UM?E) Model", cv.UMG_effect.RMSE,
               comment = "Comment")
```
```{r}
RMSE_kable(RMSEs.ResultTibble.UM?E)
```

::: {.noteblock data-latex=""}
Hello Note!!!
:::

\newpage

### UM? Effect Model Regularization
\

We have already explained the idea of the _Linear Model Regularization_ in the [Regularizing the User+Movie Effect Model] section above. Let's extend the concept outlined there to our current model.

$$
\sum_{j=1}^{n} \beta_j^2
$$ 
Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
$$ 
\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
$$
The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large. Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
$$
\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
$$
where $n_j$ is the number of ratings made for movie $j$.

This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$. Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0. The larger the $\lambda$, the more we shrink[@IDS2_23-6].

We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:

  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;

  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.

  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.

\newpage

#### UM?E Model Regularization: Support Functions
\

::: {.noteblock data-latex=""}
The [regularize.test_lambda.UM?_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::

##### [regularize.test_lambda.UM?_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function {#func.regularize.test_lambda.UM?_effect.cv}
\

This function calculates _RMSE_ of the _UM?E Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
```{r, eval=FALSE}
```

::: {.noteblock data-latex=""}
Note that we reuse the function [train_UM?_effect.cv](#func.train_UM?_effect.cv) calling it from the [regularize.test_lambda.UM?_effect.cv](#func.regularize.test_lambda.UM?_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
:::

\newpage

#### UM?E Model Regularization: Pre-configuratioin
\

Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:

We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM?_effect.cv](#func.regularize.test_lambda.UM?_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:

```{r, eval=FALSE}
```

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be found in the [Preliminary setting-up of lambda range for UM? Effect regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
:::

Now, let's visualize the results of the $\lambda$ range preconfiguration:
``` {r}
```

::: {.noteblock data-latex=""}
We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
:::

\newpage

#### UM?E Model Regularization: Fine-tuning
\

We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.

Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM?_effect.cv](#func.regularize.test_lambda.UM?_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter:
```{r, eval=FALSE}
```

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be also found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
:::

Let's visualize the fine-tuning results:
```{r}
```
\newpage

#### UM?E Model Regularization: Retraining Model with the best $\lambda$
\

Now, we can calculate the _Regularized UM? Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
```{r, eval=FALSE}
```

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section are available in the [Re-training Regularized UM? Effect Model for the best $\lambda$](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) script on _GitHub_.
:::

We calculate the _Root Mean Squared Error_ for the ultimately computed _UM? Effect_ using [calc_UM?_effect_RMSE.cv](#func.calc_UM?_effect_RMSE.cv) function described above as follows:
```{r, eval=FALSE}
```

Finally, we add the definitive result for the current model to our _Result Table_:
```{r, eval=FALSE}
RMSEs.ResultTibble.rglr.UM?E <- RMSEs.ResultTibble.UM?E |> 
  RMSEs.AddRow("Regularized UM? Effect Model", 
               UM?E.rglr.retrain.RMSE,
               comment = "Computed for `lambda` = %1" |>
                 msg.glue(UM?E.rglr.best_lambda))
```
```{r}
RMSE_kable(RMSEs.ResultTibble.rglr.UM?E)
```

\newpage

### 2025-05-20 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Model Regularization template added  to the UMGE Model.

@@
 
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
-$$
+### UMG Effect Model Regularization
+\
+
+We have already explained the idea of the _Linear Model Regularization_ in the [Regularizing the User+Movie Effect Model] section above. Let's extend the concept outlined there to our current model.
 
 $$
- \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
+\sum_{j=1}^{n} \beta_j^2
 $$ 
+Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
+$$ 
+\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
+$$
+The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
+Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
+$$
+\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
+$$
+where $n_j$ is the number of ratings made for movie $j$.
+
+This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
+Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
+The larger the $\lambda$, the more we shrink[@IDS2_23-6].
+
+We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
+
+  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
+
+  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
+
+  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.
 
 \newpage
+
+#### UMGE Model Regularization: Support Functions
+\
+
+::: {.noteblock data-latex=""}
+The [regularize.test_lambda.UMG_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+
+##### [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function {#func.regularize.test_lambda.UMG_effect.cv}
+\
+
+This function calculates _RMSE_ of the _UMGE Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
+```{r, eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note that we reuse the function [train_UMG_effect.cv](#func.train_UMG_effect.cv) calling it from the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
+:::
+
+\newpage
+
+#### UMGE Model Regularization: Pre-configuratioin
+\
+
+Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
+
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
+
+```{r, eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [Preliminary setting-up of lambda range for UMG Effect regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
+:::
+
+Now, let's visualize the results of the $\lambda$ range preconfiguration:
+``` {r}
+```
+
+::: {.noteblock data-latex=""}
+We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+:::
+
+\newpage
+
+#### UMGE Model Regularization: Fine-tuning
+\
+
+We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
+
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter:
+```{r, eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be also found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+:::
+
+Let's visualize the fine-tuning results:
+```{r}
+```
+\newpage
+
+#### UMGE Model Regularization: Retraining Model with the best $\lambda$
+\
+
+Now, we can calculate the _Regularized UMG Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
+```{r, eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section are available in the [Re-training Regularized UMG Effect Model for the best $\lambda$](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) script on _GitHub_.
+:::
+
+We calculate the _Root Mean Squared Error_ for the ultimately computed _UMG Effect_ using [calc_UMG_effect_RMSE.cv](#func.calc_UMG_effect_RMSE.cv) function described above as follows:
+```{r, eval=FALSE}
+```
+
+Finally, we add the definitive result for the current model to our _Result Table_:
+```{r, eval=FALSE}
+RMSEs.ResultTibble.rglr.UMGE <- RMSEs.ResultTibble.UMGE |> 
+  RMSEs.AddRow("Regularized UMG Effect Model", 
+               UMGE.rglr.retrain.RMSE,
+               comment = "Computed for `lambda` = %1" |>
+                 msg.glue(UMGE.rglr.best_lambda))
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.rglr.UMGE)
+```
+
+\newpage

### 2025-05-20 reports/capstone-movielens.site/02.5.UME-model.Rmd
Fix for section names & content: <Model Name> Model Regularization: Pre-configurations

@@
 
-### User+Movie Effect Model Regularization
-\
-
-#### Utilizing Penalized least squares
+### UME Model Regularization
 \
@@
 
-#### UME Model Regularization: Pre-configuratioin
+#### UME Model Regularization: Pre-configuration
 \
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [Process Preliminary setting-up of lambda range for UM Effect regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
+The complete version of the source code provided in this section can be found in the [UME Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
 :::

### 2025-05-20 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Fix for section names & content: <Model Name> Model Regularization: Pre-configurations

@@
 This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
-
-To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
 
@@
 \
+
+To account for a _genre effect_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
 
@@
 
-### UMG Effect Model Regularization
+### UMGE Model Regularization
 \
 
-We have already explained the idea of the _Linear Model Regularization_ in the [Regularizing the User+Movie Effect Model] section above. Let's extend the concept outlined there to our current model.
+We have already explained the idea of the _Linear Model Regularization_ in the [UME Model Regularization] section above. Let's extend the concept outlined there to our current model.
 
+For the current model we add the penalty to our equation as follows:
 $$ 
-\sum_{j=1}^{n} \beta_j^2
+\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - g_{i,j}\right)^2 + \lambda \sum_{i,j} g_{i,j}^2
 $$
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
+
+Therefore, the values of $g_{i,j}$ that minimize this equation are:
 $$
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
+\hat{g}_{i,j}(\lambda) = \frac{1}{\lambda + n_g} \sum_{i=1}^{n_{g}} \left(Y_{i,j} - \mu - \alpha_i - \beta_j\right)
 $$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-$$
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-where $n_j$ is the number of ratings made for movie $j$.
+where $n_{g}$ is the number of ratings made per each genre.
 
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
+As stated in the [UME Model Regularization] section, we will implement the _Regularization_ method on our  current model in three steps:
 
@@
 ::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UMG_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
+The [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L146) function described below are defined in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L145) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L146) script.
 :::
 
-##### [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function {#func.regularize.test_lambda.UMG_effect.cv}
+##### [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L146) Function {#func.regularize.test_lambda.UMG_effect.cv}
 \
@@
 ```{r, eval=FALSE}
+regularize.test_lambda.UMG_effect.cv <- function(lambda){
+  if (is.na(lambda)) {
+    stop("Function: regularize.test_lambda.user_movie_genre_effect.cv
+`lambda` is `NA`")
+  }
+
+  umg_effect <- train_user_movie_genre_effect.cv(lambda)
+  calc_user_movie_genre_effect_RMSE.cv(umg_effect)
+}
 ```
@@
 ::: {.noteblock data-latex=""}
-Note that we reuse the function [train_UMG_effect.cv](#func.train_UMG_effect.cv) calling it from the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
+Note that we reuse the function [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) calling it from the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
 :::
@@
 
-#### UMGE Model Regularization: Pre-configuratioin
+#### UMGE Model Regularization: Pre-configuration
 \
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [Preliminary setting-up of lambda range for UMG Effect regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
+The complete version of the source code provided in this section can be found in the [UMGE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
 :::
@@
 RMSEs.ResultTibble.rglr.UMGE <- RMSEs.ResultTibble.UMGE |> 
-  RMSEs.AddRow("Regularized UMG Effect Model", 
-               UMGE.rglr.retrain.RMSE,
+  RMSEs.AddRow("Regularized User+Movie+Genre Effect Model", 
+               rglr.UMG_effect.RMSE,
                comment = "Computed for `lambda` = %1" |>
@@
 
+::: {.noteblock data-latex=""}
+As we can see, the current model still does not show much improvement after _regularization_, even though the data analysis we made in the [Movie Genres Effect] section showed strong evidence of a genre effect.
+It looks like we need a better model to account for a genre effect more efficiently.
+
+Or, maybe, we have implemented the current model not quite correctly (?)
+:::
+
 \newpage

### 2025-05-20 reports/templates/02.X.UM+model.template.Rmd
Model Regularization template added  to the UMGE Model.
Fix for section names & content: <Model Name> Model Regularization: Pre-configurations

@@
 
-We have already explained the idea of the _Linear Model Regularization_ in the [Regularizing the User+Movie Effect Model] section above. Let's extend the concept outlined there to our current model.
+We have already explained the idea of the _Linear Model Regularization_ in the [UME Model Regularization] section above. Let's extend the concept outlined there to our current model.
 
-$$
-\sum_{j=1}^{n} \beta_j^2
-$$ 
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
+For the current model we add the penalty to our equation as follows:
 $$ 
@@
 $$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
+
+Therefore, the values of $\beta_i$ that minimize this equation are:
 $$
@@
 
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
+As stated in the [UME Model Regularization] section, we will implement the _Regularization_ method on our  current model in three steps:
 
@@
 
-#### UM?E Model Regularization: Pre-configuratioin
+#### UM?E Model Regularization: Pre-configuration
 \
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [Preliminary setting-up of lambda range for UM?
-Effect regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
+The complete version of the source code provided in this section can be found in the [UM?E Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
 :::

### 2025-05-20 r/src/capstone-movielens.main.R

@@ -811,7 +811,7 @@ UME.rglr.fine_tune.cache.path <- file.path(UME.regularization.path,
 dir.create(UME.rglr.fine_tune.cache.path)
 put_log1("Directory path has been created: %1", UME.rglr.fine_tune.cache.path)
 
-##### Process Preliminary setting-up of lambda range for UM Effect regularization ----
+##### UME Model Regularization: Pre-configuration ------------------------------
 file_name_tmp <- "1.UME.rglr.pre-set.RData" # UME stands for `User+Movie Effect`
 file_path_tmp <- file.path(UME.regularization.path, file_name_tmp)
 
@@ -1215,7 +1215,7 @@ UMGE.rglr.fine_tune.cache.path <- file.path(UMGE.regularization.path,
                                            fine_tune.cache.folder)
 dir.create(UMGE.rglr.fine_tune.cache.path)
 put_log1("Directory path has been created: %1", UMGE.rglr.fine_tune.cache.path)
-##### Process Preliminary setting-up of lambda range ---------------------------
+##### UMGE Model Regularization: Pre-configuration ----------------------------
 file_name_tmp <- "1.UMGE.rglr.pre-set.RData" # UMGE stands for `User+Movie+Genre Effect`
 file_path_tmp <- file.path(UMGE.regularization.path, file_name_tmp)
 
@@ -1357,6 +1357,7 @@ if (file.exists(file_path_tmp)) {
        edx.user_effect,
        rglr.UM_effect,
        rglr.UMG_effect,
+       UMGE.rglr.best_lambda,
        rglr.UMG_effect.RMSE,
        file = file_path_tmp)
   put_end_date(start)
@@ -1367,11 +1368,13 @@ if (file.exists(file_path_tmp)) {
 } 
 
 ##### Add a row to the RMSE Result Tibble for the Regularized User+Movie+Genre Effect Model ----
-RMSEs.ResultTibble <- RMSEs.ResultTibble |> 
+RMSEs.ResultTibble.rglr.UMGE <- RMSEs.ResultTibble.UMGE |> 
   RMSEs.AddRow("Regularized User+Movie+Genre Effect Model", 
-               rglr.UMG_effect.RMSE)
+               rglr.UMG_effect.RMSE,
+               comment = "Computed for `lambda` = %1" |>
+                 msg.glue(UMGE.rglr.best_lambda))
 
-RMSE_kable(RMSEs.ResultTibble)
+RMSE_kable(RMSEs.ResultTibble.rglr.UMGE)
[…]

### 2025-05-22 reports/capstone-movielens.site/02.5.UME-model.Rmd
RMD Report Update: Working on `UMGYE Model: Support Functions` Section (in progress)

@@
 
+\newpage
+
 ### UME Model Regularization
@@
 Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-$$ 
+
+\begin{equation}
 \sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2 
-$$
+(\#eq:ME-penalty)
+\end{equation}
+
 The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
 Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-$$
+
+\begin{equation}
 \hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
+(\#eq:ME-regularized)
+\end{equation}
+
 where $n_j$ is the number of ratings made for movie $j$.
@@
 cv.UME.preset.result$tuned.result |>
-  data.plot(title = TeX(r'[Preliminary set-up of $\lambda$ for Regularazation of the User+Movie Effect Model.]'),
+  data.plot(title = TeX(r'[UME Model Regularization: $\lambda$ Range Pre-configuration]'),
               xname = "parameter.value", 
@@
 UME.rglr.fine_tune.results$tuned.result |>
-  data.plot(title = "Fine-tune Stage results of the Regularization Process for the User+Movie Model",
+  data.plot(title = "UME Model Regularization: Fine-tuned result",
               xname = "parameter.value",

### 2025-05-22 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
RMD Report Update: Working on `UMGYE Model: Support Functions` Section (in progress)

@@
 
-Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
+Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article [Movie Recommendation System using R - BEST](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook) mentioned above[@MRS-R-BEST]:
 ```{r }
@@
 
-If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-$$
+If we define a _genre treatment effect_ $g_{i,j}$ for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
+
+\begin{equation}
 Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
-$$
+(\#eq:UMGE-model)
+\end{equation}
 
@@
 as a residual:
-$$
+
+\begin{equation}
 \hat{g}_{i,j} = Y_{i,j} - (\mu + \alpha_i + \beta_j)
-$$
+(\#eq:genre-effect)
+\end{equation}
 
@@
 
-We can now construct predictors and calculate the _RMSE_ of the current model using the [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) function described above:
+We can now construct predictors and calculate the _RMSE_ of the current model using the
+[calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) function described above:
 
@@
 
-For the current model we add the penalty to our equation as follows:
-$$ 
+In this case, the formula \@ref(eq:ME-penalty) for adding a penalty takes the following form:
+
+\begin{equation}
 \sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - g_{i,j}\right)^2 + \lambda \sum_{i,j} g_{i,j}^2
-$$
+(\#eq:GE-penalty)
+\end{equation}
 
-Therefore, the values of $g_{i,j}$ that minimize this equation are:
-$$
+And the formula \@ref(eq:ME-regularized) for calculating the values of the _genre effect_ that minimize the equation takes the following form:
+
+\begin{equation}
 \hat{g}_{i,j}(\lambda) = \frac{1}{\lambda + n_g} \sum_{i=1}^{n_{g}} \left(Y_{i,j} - \mu - \alpha_i - \beta_j\right)
-$$
-where $n_{g}$ is the number of ratings made per each genre.
+(\#eq:GE-regularized)
+\end{equation}
+
+where $n_{g}$ is the number of ratings made for genre $g$.
 
@@
 ```{r, eval=FALSE}
+  put_log1("Preliminary setting-up of `lambda`s range for %1-Fold Cross Validation samples...",
+           CVFolds_N)
+
+  start <- put_start_date()
+  lambdas <- seq(0, 0.2, 0.01)
+  cv.UMGE.preset.result <- 
+    tune.model_param(lambdas, regularize.test_lambda.UMG_effect.cv)
+  put_end_date(start)
+  put_log1("Preliminary regularization set-up of `lambda`s range for the UMGE Model has been completed
+for the %1-Fold Cross Validation samples.",
+CVFolds_N)
+```
+```{r}
+str(cv.UMGE.preset.result)
+cv.UMGE.preset.result$best_result
 ```
@@
 ``` {r}
+cv.UMGE.preset.result$tuned.result |>
+  data.plot(title = TeX(r'[UMGE Model Regularization: $\lambda$ Range Pre-configuration]'),
+              xname = "parameter.value", 
+              yname = "RMSE", 
+              xlabel = TeX(r'[$\lambda$]'), 
+              ylabel = str_glue("Deviation from the best RMSE value (",
+                                as.character(round(cv.UMGE.preset.result$best_result["best_RMSE"], 
+                                                   digits = 7)),
+                                ")"),
+              normalize = TRUE)
 ```
@@
 ```{r, eval=FALSE}
+endpoints <- 
+  get_fine_tune.param.endpoints(cv.UMGE.preset.result$tuned.result)
+
+UMG_effect.loop_starter <- c(endpoints["start"], 
+                            endpoints["end"], 
+                            8)
+UMG_effect.loop_starter
+#> [1] 0.0   0.1   8.0
+
+UMGE.rglr.fine_tune.cache.base_name <- "UMGE.rglr.fine-tuning"
+
+UMGE.rglr.fine_tune.results <- 
+  model.tune.param_range(UMG_effect.loop_starter,
+                         UMGE.rglr.fine_tune.cache.path,
+                         UMGE.rglr.fine_tune.cache.base_name,
+                         regularize.test_lambda.UMG_effect.cv)
+
+UMGE.rglr.fine_tune.RMSE.best <- UMGE.rglr.fine_tune.results$best_result["best_RMSE"]
+# best_RMSE 
+#  0.872973
+
+```
+```{r}
+str(UMGE.rglr.fine_tune.results)
+UMGE.rglr.fine_tune.results$best_result
 ```
@@
 ```{r}
+UMGE.rglr.fine_tune.results$tuned.result |>
+  data.plot(title = "UMGE Model Regularization: Fine-tuned result",
+              xname = "parameter.value",
+              yname = "RMSE",
+              xlabel = TeX(r'[$\lambda$]'),
+              ylabel = str_glue("Deviation from the best RMSE value (",
+                                as.character(round(UMGE.rglr.fine_tune.RMSE.best, digits = 7)),
+                                ")"),
+              normalize = TRUE)
 ```
@@
 ```{r, eval=FALSE}
+  best_result <- UMGE.rglr.fine_tune.results$best_result
+  # param.best_value        best_RMSE 
+  #     0.03554688       0.87297303
+
+  UMGE.rglr.best_lambda <- best_result["param.best_value"]
+  UMGE.rglr.best_RMSE <- best_result["best_RMSE"]
+
+  put_log1("Re-training Regularized User+Movie+Genre Effect Model for the best `lambda`: %1...",
+           UMGE.rglr.best_lambda)
+
+  rglr.UMG_effect <- edx.sgr |> train_user_movie_genre_effect(UMGE.rglr.best_lambda)
+```
+```{r}
+str(rglr.UMG_effect)
 ```
@@
 ```{r, eval=FALSE}
+  rglr.UMG_effect.RMSE <- calc_user_movie_genre_effect_RMSE.cv(rglr.UMG_effect)
+```
+```{r, echo=FALSE}
+  print_log2("Regularized User+Movie+Genre Effect RMSE has been computed for the best `lambda = %1`: %2.",
+           UMGE.rglr.best_lambda,
+           rglr.UMG_effect.RMSE)
 ```

### 2025-05-22 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
RMD Report Update: Working on `UMGYE Model: Support Functions` Section (in progress)

@@
 \
+
+### Year Effect Analysis
+
+::: {.noteblock data-latex=""}
+The _Year Effect_ visualization and analysis code in this section are cited from the article [Movie Recommendation System using R - BEST](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook) mentioned earlier in this report[@MRS-R-BEST].
+:::
 
@@
 
-We use the following models to account for the `date` effect:
+\newpage
 
+### Mathematical Description of the UMGYE Model
+\
+
+If we define $\gamma(q)$ as the _year effect_ for the year (which is denotes by $q$ here) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the following form:
+
+\begin{equation}
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(q) + \varepsilon_{i,j}
+(\#eq:UMGYE-model)
+\end{equation}
+
+Therefore, the formula \@ref(eq:genre-effect) for calculation the prediction of a _genre effect_ as a residual, for a _year effect_ 
 $$
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
+\hat{\gamma}(q) = \gamma(q) + \varepsilon_{i,j}
 $$
 
+takes the following form:
+
+\begin{equation}
+\hat{\gamma}(q) = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j})
+(\#eq:year-effect)
+\end{equation}
+
+### UMGYE Model: Support Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R) script on _GitHub_.
+:::
+
+#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+#### [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) Function {#func.calc_date_general_effect}
+\
+
+Below is slightly simplified version of the source code:
+```{r eval=FALSE}
+calc_date_general_effect <- function(train_set, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: calc_date_general_effect
+`lambda` is `NA`")
+  }
+
+  if(lambda == 0) put_log("Function `calc_date_general_effect`:
+Computing Date Global Effect for given Train Set data...")
+  else put_log1("Function `calc_date_general_effect`:
+Computing Date Global Effect for lambda: %1...",
+                lambda)
+  dg_effect <- train_set |> 
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    mutate(resid = rating - (mu + a + b + g)) |>
+    # filter(!is.na(resid)) |>
+  group_by(days) |>
+    summarise(de = mean_reg(resid, lambda), 
+              year = mean(year))
+  dg_effect
+}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+#### [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L73) Function {#func.calc_UMGY_effect}
+\
+
+```{r eval=FALSE}
+calc_UMGY_effect <- function(date_general_effect){
+  date_general_effect |>
+    group_by(year) |>
+    summarise(ye = mean(de, na.rm = TRUE))
+}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L78) Function {#func.train_UMGY_effect}
+\
+
+We use this function to build and train our model using the `train_set` dataset:
+```{r eval=FALSE}
+train_UMGY_effect <- function(train_set, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_UMGY_effect
+`lambda` is `NA`")
+  }
+
+  train_set |>
+    calc_date_general_effect(lambda) |>
+    calc_UMGY_effect()
+}
+
+```
+
+::: {.noteblock data-latex=""}
+This function accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We have already explained that in the [UMGYE Effect Model Regularization] section. 
+For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
+Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
+:::
+
+#### `train_UMGY_effect.cv` Function {#func.train_UMGY_effect.cv}
+\
+
+We use the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L59) function to build and train our model using the `5-Fold Cross Validation` method.
+Below, we provide a slightly simplified version of the source code of that function:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
+:::
+
+#### `calc_UMGY_effect_MSE` Function
+\
+
+The source code of the function [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _Mean Squared Error (MSE)_ of the _UMGYE Model_ for the given _Test Set_ is provided below:
+```{r eval=FALSE}
+```
+
 \newpage
+
+#### `calc_UMGY_effect_MSE.cv` Function
+\
+
+The source code of the function [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _5-Fold Cross Validation MSE_ result of the _UMGYE Model_ is provided below:
+```{r eval=FALSE}
+```
+
+#### `calc_UMGY_effect_RMSE` Function
+\
+
+The source code of the function [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _Root Mean Squared Error (RMSE)_ of the _UMGYE Model_ for the given _Test Set_ is provided below:
+
+```{r eval=FALSE}
+```
+
+#### `calc_UMGY_effect_RMSE.cv` Function { #func.calc_UMGY_effect_RMSE.cv }
+\
+
+The source code of the function [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _5-Fold Cross Validation **RMSE**_ result of the _UMGYE Model_ is provided below:
+
+```{r eval=FALSE}
+```
+
+\newpage
+
+### UMGYE Model Building
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of builing and training the current model is available in the [Model building: UMGYE Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+:::
+
+Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
+```{r, eval=FALSE}
+```
+
+\newpage
+
+We can now construct predictors and calculate the _RMSE_ of the current model using the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described above:
+
+```{r, eval=FALSE}
+cv.UMG_effect.RMSE <- calc_UMGY_effect_RMSE.cv(cv.UMG_effect)
+
+RMSEs.ResultTibble.UMGYE <- RMSEs.ResultTibble.rglr.UMGYE |> 
+  RMSEs.AddRow("UMGYE Effect (UMGYE) Model", cv.UMG_effect.RMSE,
+               comment = "Comment")
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.UMGYE)
+```
+
+::: {.noteblock data-latex=""}
+Hello Note!!!
+:::
+
+\newpage
+
+### UMGYE Effect Model Regularization
+\
+
+We have already explained the idea of the _Linear Model Regularization_ in the [UME Model Regularization] section above. Let's extend the concept outlined there to our current model.
+
+In this case, the formula \@ref(eq:ME-penalty) for adding a penalty takes the following form:
+
+\begin{equation}
+\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - ...\right)^2 + \lambda \sum_{j} \beta_j^2 
+(\#eq:YE-penalty)
+\end{equation}
+
+And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimize the equation takes the following form:
+
+\begin{equation}
+\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
+(\#eq:YE-regularized)
+\end{equation}
+
+where $n_y$ is the number of ratings made in year $y$.
+
+As stated in the [UME Model Regularization] section, we will implement the _Regularization_ method on our  current model in three steps:
+
+  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
+
+  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
+
+  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.
+
+\newpage
+
+#### UMGYE Model Regularization: Support Functions
+\
+
+::: {.noteblock data-latex=""}
+The [regularize.test_lambda.UMGY_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
+:::
+
+##### [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L96) Function {#func.regularize.test_lambda.UMGY_effect.cv}
+\
+
+This function calculates _RMSE_ of the _UMGYE Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
+```{r, eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note that we reuse the function [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) calling it from the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
+:::
+
+\newpage
+
+#### UMGYE Model Regularization: Pre-configuration
+\
+
+Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
+
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
+
+```{r, eval=FALSE}
+```
+```{r}
+str(cv.UMGYE.preset.result)
+cv.UMGYE.preset.result$best_result
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
+:::
+
+Now, let's visualize the results of the $\lambda$ range preconfiguration:
+``` {r}
+# title = TeX(r'[UMGE Model Regularization: $\lambda$ Range Pre-configuration]')
+```
+
+::: {.noteblock data-latex=""}
+We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+:::
+
+\newpage
+
+#### UMGYE Model Regularization: Fine-tuning
+\
+
+We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
+
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter:
+```{r, eval=FALSE}
+```
+```{r}
+str(UMGYE.rglr.fine_tune.results)
+UMGYE.rglr.fine_tune.results$best_result
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be also found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+:::
+
+Let's visualize the fine-tuning results:
+```{r}
+```
+\newpage
+
+#### UMGYE Model Regularization: Retraining Model with the best $\lambda$
+\
+
+Now, we can calculate the _Regularized UMGYE Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
+```{r, eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section are available in the [Re-training Regularized UMGYE Effect Model for the best $\lambda$](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) script on _GitHub_.
+:::
+
+We calculate the _Root Mean Squared Error_ for the ultimately computed _UMGYE Effect_ using [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described above as follows:
+```{r, eval=FALSE}
+```
+
+Finally, we add the definitive result for the current model to our _Result Table_:
+```{r, eval=FALSE}
+RMSEs.ResultTibble.rglr.UMGYE <- RMSEs.ResultTibble.UMGYE |> 
+  RMSEs.AddRow("Regularized UMGYE Effect Model", 
+               UMGYE.rglr.retrain.RMSE,
+               comment = "Computed for `lambda` = %1" |>
+                 msg.glue(UMGYE.rglr.best_lambda))
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.rglr.UMGYE)
+```
+
+\newpage

### 2025-05-22 reports/templates/02.X.UM+model.template.Rmd
RMD Report Update: Working on `UMGYE Model: Support Functions` Section (in progress)

@@
 
+If we define $\gamma(q)$ as the _year effect_ for the year (which is denotes by $q$ here) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the following form:
+
+\begin{equation}
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(q) + \varepsilon_{i,j}
+(\#eq:UMGYE-model)
+\end{equation}
+
+Therefore, the formula \@ref(eq:genre-effect) for prediction a _genre effect_ as a residual, for a _year effect_ 
 $$
-Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
+\hat{\gamma}(q) = \gamma(q) + \varepsilon_{i,j}
 $$
 
-If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
-$$
+takes the following form:
 
-where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p.
-712) book[@RRSK_RS_HB].
-
-In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:
-
-$$
-g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
-$$
-
-with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.
-
-Therefore, for our current model, we can compute a predicted value 
-$$
-\hat{g}_{i,j} = g_{i,j} + \varepsilon_{i,j}
-$$
-as a residual: 
-$$
-\hat{g}_{i,j} = Y_{i,j} - (\mu + \alpha_i + \beta_j)
-$$
+\begin{equation}
+\hat{\gamma}(q) = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j})
+(\#eq:year-effect)
+\end{equation}
 
@@
 
-For the current model we add the penalty to our equation as follows:
-$$ 
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
-$$
+In this case, the formula \@ref(eq:ME-penalty) for adding a penalty takes the following form:
 
-Therefore, the values of $\beta_i$ that minimize this equation are:
-$$
+\begin{equation}
+\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - ...\right)^2 + \lambda \sum_{j} \beta_j^2 
+(\#eq:?E-penalty)
+\end{equation}
+
+And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimize the equation takes the following form:
+
+\begin{equation}
 \hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-where $n_j$ is the number of ratings made for movie $j$.
+(\#eq:?E-regularized)
+\end{equation}
+
+where $n_$ is the number of ratings made for movie $j$.
 
@@
 ```
+```{r}
+str(cv.UM?E.preset.result)
+cv.UM?E.preset.result$best_result
+```
 
@@
 ``` {r}
+# title = TeX(r'[UMGE Model Regularization: $\lambda$ Range Pre-configuration]')
 ```
@@
 ```{r, eval=FALSE}
+```
+```{r}
+str(UM?E.rglr.fine_tune.results)
+UM?E.rglr.fine_tune.results$best_result
 ```

### 2025-05-22 r/src/capstone-movielens.main.R

@@ -854,7 +854,7 @@ put(cv.UME.preset.result$best_result)
 
 ##### Plot (rough) dependency of RMSEs vs lambdas ------------------------------  
 cv.UME.preset.result$tuned.result |>
-  data.plot(title = TeX(r'[Preliminary set-up of $\lambda$ for Regularazation of the User+Movie Effect Model.]'),
+  data.plot(title = TeX(r'[UME Model Regularization: $\lambda$ Range Pre-configuration]'),
               xname = "parameter.value", 
               yname = "RMSE", 
               xlabel = TeX(r'[$\lambda$]'), 
@@ -894,7 +894,7 @@ put(UME.rglr.fine_tune.results$best_result)
 ###### Plot (fine-tuned) dependency of RMSEs vs lambdas -------------------------  
 
 UME.rglr.fine_tune.results$tuned.result |>
-  data.plot(title = "Fine-tune Stage results of the Regularization Process for the User+Movie Model",
+  data.plot(title = "UME Model Regularization: Fine-tuned result",
               xname = "parameter.value",
               yname = "RMSE",
               xlabel = TeX(r'[$\lambda$]'),
@@ -1259,7 +1259,7 @@ put(cv.UMGE.preset.result$best_result)
 
 ###### Plot (rough) dependency of RMSEs vs lambdas -----------------------------  
 cv.UMGE.preset.result$tuned.result |>
-  data.plot(title = TeX(r'[Preliminary set-up of $\lambda$ for Regularazation of the User+Movie+Genre Effect Model.]'),
+  data.plot(title = TeX(r'[UMGE Model Regularization: $\lambda$ Range Pre-configuration]'),
               xname = "parameter.value", 
               yname = "RMSE", 
               xlabel = TeX(r'[$\lambda$]'), 
@@ -1273,7 +1273,7 @@ cv.UMGE.preset.result$tuned.result |>
 log_close()
 ##### Open log file for UMG Effect Regularization (Fine-Tuning)` feature -------
 open_logfile(".UMGE.rglr.fine-tuning")
-##### Fine-tuning UMGE Model for `lambda` parameter values --------------------- 
+##### UMGE Model Regularization: Fine-tuning ----------------------------------- 
 endpoints <- 
[…]

### 2025-05-22 r/src/support-functions/UMGY-effect.functions.R

@@ -1,4 +1,4 @@
-# User+Movie+Genre+Year Effect functions ---------------------------------------
+# UMGYE Model Support Functions ------------------------------------------------
 calc_date_general_effect <- function(train_set, lambda = 0){
   if (is.na(lambda)) {
     stop("Function: calc_date_general_effect

### 2025-05-22 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Intermediate commit: report updating in progress: UMGYE Model. Helper function `calc_date_general_effect.cv` updated: code cleaned up.

@@
 
-We use the [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) function to build and train our model using the `5-Fold Cross Validation` method.
+We use the [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) function to train the current model using the _5-Fold Cross Validation_ method.
 Below, we provide a slightly simplified version of the source code of that function:

### 2025-05-22 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Intermediate commit: report updating in progress: UMGYE Model. Helper function `calc_date_general_effect.cv` updated: code cleaned up.

@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R) script on _GitHub_.
+Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We have already explained that in the [UMGYE Effect Model Regularization] section. 
+For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
+Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
 :::
@@
 
-Below is slightly simplified version of the source code:
+This is a helper function that calculates the _date general effect_ of the user ratings and is intended to be used in other functions and scripts (for instance in [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+
+The following is a slightly simplified version of the function's source code:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-Note
+The complete version of the source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) function is available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) script on _GitHub.
 :::
@@
 
+This is a helper function that calculates the _UMGY effect_ of the user ratings and is intended to be used in other functions and scripts (for instance in [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+
+##### Parameters
+\
+
+The function accepts the only parameter `date_general_effect`, which is a data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) function described above.
+
+##### Source Code
+\
+
+The following is the source code of the function:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-Note
+The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L73) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L73) script on _GitHub.
 :::
@@
 
-We use this function to build and train our model using the `train_set` dataset:
+This function is used to train the current model using the _Train Set_ dataset passed in the `train_set` parameter.
+The following is the source code of the function:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-This function accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
-We have already explained that in the [UMGYE Effect Model Regularization] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
-Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
+The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L78) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L78) script on _GitHub.
 :::
 
-#### `train_UMGY_effect.cv` Function {#func.train_UMGY_effect.cv}
+#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L88) Function {#func.train_UMGY_effect.cv}
 \
 
-We use the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L59) function to build and train our model using the `5-Fold Cross Validation` method.
-Below, we provide a slightly simplified version of the source code of that function:
+This function is used to train the current model using the _5-Fold Cross Validation_ method.
+The following is the source code of the function:
 ```{r eval=FALSE}
+train_UMGY_effect.cv <- function(lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_UMGY_effect.cv
+`lambda` is `NA`")
+  }
+
+  calc_date_general_effect.cv(lambda) |> calc_UMGY_effect()  
+}
 ```

### 2025-05-22 reports/capstone-movielens.site/04.appendix.Rmd
Intermediate commit: report updating in progress: UMGYE Model. Helper function `calc_date_general_effect.cv` updated: code cleaned up.

@@
 ::: {.noteblock data-latex=""}
-The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
+The complete version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
 :::

### 2025-05-22 r/src/support-functions/UMGY-effect.functions.R

@@ -45,7 +45,6 @@ Computing Date Global Effect list for %1-Fold Cross Validation samples...",
            CVFolds_N)
   start <- put_start_date()
   date_general_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
-    # start <- put_start_date()
     cv_fold_dat$train_set |> calc_date_general_effect(lambda)
   })
   str(date_general_effect_ls)
@@ -58,7 +57,6 @@ Date Global Effect list has been computed for %1-Fold Cross Validation samples."
   str(date_general_effect_united)
   
   date_general_effect <- date_general_effect_united |>
-    #filter(!is.na(de)) |>
     group_by(days) |>
     summarise(de = mean(de, na.rm = TRUE), year = mean(year, na.rm = TRUE))
   

### 2025-05-23 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
UMGYE Model, Support functions described.

@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the [UMGE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L1) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script on _GitHub_.
+Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We have already explained that in the [UME Model Regularization] section. 
+For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
+Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
 :::
@@
 
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
-We have already explained that in the [User+Movie Effect Model Regularization] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
-Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
-:::
-
-#### `train_user_movie_genre_effect.cv` Function {#func.train_user_movie_genre_effect.cv}
+#### [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) Function {#func.train_user_movie_genre_effect.cv}
 \
 
-We use the [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) function to train the current model using the _5-Fold Cross Validation_ method.
+We use this function, defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) script, to train the current model using the _5-Fold Cross Validation_ method.
 Below, we provide a slightly simplified version of the source code of that function:
@@
 Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
-```{r, eval=FALSE}
+```{r, fn.train_user_movie_genre_effect.cv,   eval=FALSE}
 cv.UMG_effect <- train_user_movie_genre_effect.cv()
 ```
-```{r}
+```{r, hist.cv.UMG_effect }
 str(cv.UMG_effect)

### 2025-05-23 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
UMGYE Model, Support functions described.

@@
 
-If we define $\gamma(q)$ as the _year effect_ for the year (which is denotes by $q$ here) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the following form:
+If we define $\gamma(r)$ as the _year effect_ for the year (here denotes by $r$) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the following form:
 
 \begin{equation}
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(q) + \varepsilon_{i,j}
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(r) + \varepsilon_{i,j}
 (\#eq:UMGYE-model)
@@
 $$
-\hat{\gamma}(q) = \gamma(q) + \varepsilon_{i,j}
+\hat{\gamma}(r) = \gamma(r) + \varepsilon_{i,j}
 $$
@@
 \begin{equation}
-\hat{\gamma}(q) = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j})
+\hat{\gamma}(r) = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j})
 (\#eq:year-effect)
 \end{equation}
+
+\newpage
 
@@
 Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
-We have already explained that in the [UMGYE Effect Model Regularization] section. 
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We have already explained that in the [UME Model Regularization] section. 
 For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
 Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
-:::
-
-#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
-\
-
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-Note
-:::
-
-#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
-\
-
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-Note
-:::
-
-#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
-\
-
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-Note
-:::
-
-#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
-\
-
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-Note
-:::
-
-#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
-\
-
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-Note
 :::
@@
     mutate(resid = rating - (mu + a + b + g)) |>
-    # filter(!is.na(resid)) |>
   group_by(days) |>
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) function is available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) script on _GitHub.
+The complete version of the source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) function is available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) script on _GitHub_.
 :::
 
-#### [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L73) Function {#func.calc_UMGY_effect}
+##### Return
+
+A data structure containg information about _Date General Effect_.
+
+#### [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) Function {#func.calc_date_general_effect.cv}
+\
+
+This is a helper function that calculates the _date general effect_ of the user ratings using the _5-Fold Cross Validation_ method and is intended to be used in other functions and scripts (for instance in [train_UMGY_effect.cv](#func.train_UMGY_effect.cv)) described below.
+The following is a simplified version of the function's source code:
+```{r eval=FALSE}
+calc_date_general_effect.cv <- function(lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: calc_date_general_effect.cv
+`lambda` is `NA`")
+  }
+
+  date_general_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
+    cv_fold_dat$train_set |> calc_date_general_effect(lambda)
+  })
+  str(date_general_effect_ls)
+
+  date_general_effect_united <- union_cv_results(date_general_effect_ls)
+
+  date_general_effect_united |>
+    group_by(days) |>
+    summarise(de = mean(de, na.rm = TRUE), year = mean(year, na.rm = TRUE))
+}
+```
+
+::: {.noteblock data-latex=""}
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
+:::
+
+::: {.noteblock data-latex=""}
+The complete version of the source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) function is available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) script on _GitHub_.
+:::
+
+##### Return
+
+A data structure containg information about _Date General Effect_ as result of _5-Fold Cross Validation_.
+
+#### [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L69) Function {#func.calc_UMGY_effect}
 \
@@
 
-The function accepts the only parameter `date_general_effect`, which is a data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) function described above.
+The function accepts the only parameter `date_general_effect`, which is a data structure returned by any of the following functions described above:
+
+  - [calc_date_general_effect](#func.calc_date_general_effect);
+  - [calc_date_general_effect.cv](#func.calc_date_general_effect.cv).
 
@@
 ::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L73) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L73) script on _GitHub.
+The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L69) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L69) script on _GitHub_.
 :::
 
-#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L78) Function {#func.train_UMGY_effect}
+##### Return
+
+A data structure containg information about _User+Movie+Genre+Year (UMGY) Effect_.
+
+#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) Function {#func.train_UMGY_effect}
 \
@@
 ::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L78) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L78) script on _GitHub.
+The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) script on _GitHub_.
 :::
 
-#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L88) Function {#func.train_UMGY_effect.cv}
+##### Return
+
+A data structure containg information about _User+Movie+Genre+Year (UMGY) Effect_.
+
+#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) Function {#func.train_UMGY_effect.cv}
 \
@@
 ::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
+The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) function is also available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) script on _GitHub_.
 :::
 
-#### `calc_UMGY_effect_MSE` Function
+##### Return
+
+A data structure containg information about _User+Movie+Genre+Year (UMGY) Effect_.
+
+#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) Function
 \
 
-The source code of the function [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _Mean Squared Error (MSE)_ of the _UMGYE Model_ for the given _Test Set_ is provided below:
+The function calculates the _Mean Squared Error (MSE)_ of the _UMGYE Model_ for the given _Test Set_ passed in the `test_set` parameter.
+
+##### Parameters
+\
+
+  - **test_set:** A _Test Set_ dataset used for _UMGYE Model_ validation;
+  - **UMGY_effect:** A data structure returned by any of the following functions described above:
+    - [calc_UMGY_effect](#func.train_UMGY_effect);
+    - [train_UMGY_effect](#func.train_UMGY_effect);
+    - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
+
+##### Source Code
+\
+
+The source code of the function is provided below:
 ```{r eval=FALSE}
+calc_UMGY_effect_MSE <- function(test_set, UMGY_effect){
+  test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(UMGY_effect, by='year') |>
+    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
+    pull(resid) |> mse()
+}
 ```
+
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) script.
+:::
 
@@
 
-#### `calc_UMGY_effect_MSE.cv` Function
+#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) Function
 \
 
-The source code of the function [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _5-Fold Cross Validation MSE_ result of the _UMGYE Model_ is provided below:
+The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGY Effect_ data passed in the `UMGY_effect` parameter.
+
+##### Parameters
+\
+
+The function accepts the only parameter: `UMGY_effect`, which is a data structure returned by the one of the following functions described above:
+
+  - [calc_UMGY_effect](#func.train_UMGY_effect);
+  - [train_UMGY_effect](#func.train_UMGY_effect);
+  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
+
+##### Source Code
+\
+
+The source code of the function is provided below:
 ```{r eval=FALSE}
+calc_UMGY_effect_MSE.cv <- function(UMGY_effect){
+  start <- put_start_date()
+  UMGY_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
+    cv_fold_dat$validation_set |> calc_UMGY_effect_MSE(UMGY_effect)
+  })
+  put_end_date(start)
+  put_log1("Function: calc_UMGY_effect_MSE.cv
+Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  mean(UMGY_effect_MSEs)
+}
+
 ```
 
-#### `calc_UMGY_effect_RMSE` Function
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) script.
+:::
+
+#### [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) Function
 \
 
-The source code of the function [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _Root Mean Squared Error (RMSE)_ of the _UMGYE Model_ for the given _Test Set_ is provided below:
+The function calculates the _Mean Squared Error (MSE)_ of the _UMGYE Model_ for the given _Test Set_ passed in the `test_set` parameter.
 
+##### Parameters
+\
+
+  - **test_set:** A _Test Set_ dataset used for _UMGYE Model_ validation;
+  - **UMGY_effect:** A data structure returned by any of the following functions described above:
+    - [calc_UMGY_effect](#func.train_UMGY_effect);
+    - [train_UMGY_effect](#func.train_UMGY_effect);
+    - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
+
+##### Source Code
+\
+
+The source code of the function is provided below:
 ```{r eval=FALSE}
+calc_UMGY_effect_RMSE <- function(test_set, UMGY_effect){
+  mse <- test_set |> calc_UMGY_effect_MSE(UMGY_effect)
+  sqrt(mse)
+}
 ```
 
-#### `calc_UMGY_effect_RMSE.cv` Function { #func.calc_UMGY_effect_RMSE.cv }
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) script.
+:::
+
+\newpage
+
+#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) Function
 \
 
-The source code of the function [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _5-Fold Cross Validation **RMSE**_ result of the _UMGYE Model_ is provided below:
+The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGY Effect_ data passed in the `UMGY_effect` parameter.
 
+##### Parameters
+\
+
+The function accepts the only parameter: `UMGY_effect`, which is a data structure returned by the one of the following functions described above:
+
+  - [calc_UMGY_effect](#func.train_UMGY_effect);
+  - [train_UMGY_effect](#func.train_UMGY_effect);
+  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
+
+##### Source Code
+\
+
+The source code of the function is provided below:
 ```{r eval=FALSE}
+calc_UMGY_effect_RMSE.cv <- function(UMGY_effect){
+  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGY_effect))
+  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
+           CVFolds_N, 
+           UMGY_effect_RMSE)
+
+  UMGY_effect_RMSE
+}
 ```
 
-\newpage
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) script.
+:::
 

### 2025-05-23 reports/templates/02.X.UM+model.template.Rmd
UMGYE Model, Support functions described.

@@
 Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(q) + \varepsilon_{i,j}
-(\#eq:UMGYE-model)
+(\#eq:UM?E-model)
 \end{equation}
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the [UM?E Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) section of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script on _GitHub_.
-:::
-
-#### [train_UM?_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) Function {#func.train_UM?_effect}
-\
-
-We use this function to build and train our model using the `train_set` dataset:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
-We have already explained that in the [UM? Effect Model Regularization] section. 
+Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We have already explained that in the [UME Model Regularization] section. 
 For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
@@
 
-#### `train_UM?E_effect.cv` Function {#func.train_UM?E_effect.cv}
+#### [calc_UM?_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L70) Function {#func.calc_UM?_effect}
 \
 
-We use the [train_UM?E_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/#L59) function to build and train our model using the `5-Fold Cross Validation` method.
-Below, we provide a slightly simplified version of the source code of that function:
+This is a helper function that calculates the _UM?
+effect_ of the user ratings and is intended to be used in other functions and scripts (for instance in [train_UM?_effect](#func.train_UM?_effect)) described below.
+
+##### Parameters
+\
+
+The function accepts the only parameter `date_general_effect`, which is a data structure returned by any of the following functions described above:
+
+  - [calc_date_general_effect](#func.calc_date_general_effect);
+  - [calc_date_general_effect.cv](#func.calc_date_general_effect.cv).
+
+##### Source Code
+\
+
+The following is the source code of the function:
 ```{r eval=FALSE}
+
 ```
@@
 ::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
+The source code of the [calc_UM?_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L70) function is also available in the [UM?E Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L1) section of the [UM?-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L70) script on _GitHub_.
 :::
 
-#### `calc_UM?E_effect_MSE` Function
+##### Return
+
+A data structure containg information about _User+Movie+Genre+Year (UM?) Effect_.
+
+#### [train_UM?_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L75) Function {#func.train_UM?_effect}
 \
 
-The source code of the function [calc_UM?E_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _Mean Squared Error (MSE)_ of the _UM?E Model_ for the given _Test Set_ is provided below:
+This function is used to train the current model using the _Train Set_ dataset passed in the `train_set` parameter.
+The following is the source code of the function:
 ```{r eval=FALSE}
+
 ```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UM?_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L75) function is also available in the [UM?E Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L1) section of the [UM?-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L75) script on _GitHub_.
+:::
+
+##### Return
+
+A data structure containg information about _User+Movie+Genre+Year (UM?) Effect_.
+
+#### [train_UM?_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L85) Function {#func.train_UM?_effect.cv}
+\
+
+This function is used to train the current model using the _5-Fold Cross Validation_ method.
+The following is the source code of the function:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UM?_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L85) function is also available in the [UM?E Model Support Functions](#L1) section of the [UM?-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L85) script on _GitHub_.
+:::
+
+##### Return
+
+A data structure containg information about _User+Movie+Genre+Year (UM?) Effect_.
+
+#### [calc_UM?_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L93) Function
+\
+
+The function calculates the _Mean Squared Error (MSE)_ of the _UM?E Model_ for the given _Test Set_ passed in the `test_set` parameter.
+
+##### Parameters
+\
+
+  - **test_set:** A _Test Set_ dataset used for _UM?E Model_ validation;
+  - **UM?_effect:** A data structure returned by any of the following functions described above:
+    - [calc_UM?_effect](#func.train_UM?_effect);
+    - [train_UM?_effect](#train_UM?_effect) functions.
+    - [train_UM?_effect.cv](#train_UM?_effect.cv).
+
+##### Source Code
+\
+
+The source code of the function is provided below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UM?_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L93) is also available in the [UM?E Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L93) script.
+:::
 
@@
 
-#### `calc_UM?E_effect_MSE.cv` Function
+#### [calc_UM?_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) Function
 \
 
-The source code of the function [calc_UM?E_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _5-Fold Cross Validation MSE_ result of the _UM?E Model_ is provided below:
+The function calculates the _5-Fold Cross Validation MSE_ result for the _UM? Effect_ data passed in the `UM?_effect` parameter.
+
+##### Parameters
+\
+
+The function accepts the only parameter: `UM?_effect`, which is a data structure returned by the one of the following functions described above:
+
+  - [calc_UM?_effect](#func.train_UM?_effect);
+  - [train_UM?_effect](#train_UM?_effect) functions.
+  - [train_UM?_effect.cv](#train_UM?_effect.cv).
+
+##### Source Code
+\
+
+The source code of the function is provided below:
 ```{r eval=FALSE}
+calc_UM?_effect_MSE.cv <- function(UM?_effect){
+  start <- put_start_date()
+  UM?_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
+    cv_fold_dat$validation_set |> calc_UM?_effect_MSE(UM?_effect)
+  })
+  put_end_date(start)
+  put_log1("Function: calc_UM?_effect_MSE.cv
+Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  mean(UM?_effect_MSEs)
+}
+
 ```
 
-#### `calc_UM?E_effect_RMSE` Function
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UM?_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) is also available in the [UM?E Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) script.
+:::
+
+#### [calc_UM?_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L115) Function
 \
 
-The source code of the function [calc_UM?E_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/#L118) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _Root Mean Squared Error (RMSE)_ of the _UM?E Model_ for the given _Test Set_ is provided below:
+The function calculates the _Mean Squared Error (MSE)_ of the _UM?E Model_ for the given _Test Set_ passed in the `test_set` parameter.
 
+##### Parameters
+\
+
+  - **test_set:** A _Test Set_ dataset used for _UM?E Model_ validation;
+  - **UM?_effect:** A data structure returned by any of the following functions described above:
+    - [calc_UM?_effect](#func.train_UM?_effect);
+    - [train_UM?_effect](#train_UM?_effect) functions.
+    - [train_UM?_effect.cv](#train_UM?_effect.cv).
+
+##### Source Code
+\
+
+The source code of the function is provided below:
 ```{r eval=FALSE}
+
 ```
 
-#### `calc_UM?E_effect_RMSE.cv` Function { #func.calc_UM?E_effect_RMSE.cv }
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UM?_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L115) is also available in the [UM?E Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L115) script.
+:::
+
+\newpage
+
+#### [calc_UM?_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) Function
 \
 
-The source code of the function [calc_UM?E_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/#L) defined in the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/) script to calculate the _5-Fold Cross Validation **RMSE**_ result of the _UM?E Model_ is provided below:
+The function calculates the _5-Fold Cross Validation MSE_ result for the _UM? Effect_ data passed in the `UM?_effect` parameter.
 
+##### Parameters
+\
+
+The function accepts the only parameter: `UM?_effect`, which is a data structure returned by the one of the following functions described above:
+
+  - [calc_UM?_effect](#func.train_UM?_effect);
+  - [train_UM?_effect](#train_UM?_effect) functions.
+  - [train_UM?_effect.cv](#train_UM?_effect.cv).
+
+##### Source Code
+\
+
+The source code of the function is provided below:
 ```{r eval=FALSE}
+
 ```
+
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UM?_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) is also available in the [UM?E Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) script.
+:::
 
@@
 \newpage
+
+## Additional Function Templates
+\
+
+#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+#### [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L) Function {#func.}
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note
+:::
+
+\newpage

### 2025-05-23 r/src/support-functions/UMGY-effect.functions.R

@@ -16,7 +16,6 @@ Computing Date Global Effect for lambda: %1...",
     left_join(rglr.UMG_effect, by = "movieId") |>
     left_join(date_days_map, by = "timestamp") |>
     mutate(resid = rating - (mu + a + b + g)) |>
-    # filter(!is.na(resid)) |>
   group_by(days) |>
     summarise(de = mean_reg(resid, lambda), 
               year = mean(year))
@@ -54,8 +53,7 @@ Date Global Effect list has been computed for %1-Fold Cross Validation samples."
            CVFolds_N)
   
   date_general_effect_united <- union_cv_results(date_general_effect_ls)
-  str(date_general_effect_united)
-  
+
   date_general_effect <- date_general_effect_united |>
     group_by(days) |>
     summarise(de = mean(de, na.rm = TRUE), year = mean(year, na.rm = TRUE))
@@ -99,7 +97,6 @@ calc_UMGY_effect_MSE <- function(test_set, UMGY_effect){
     left_join(date_days_map, by = "timestamp") |>
     left_join(UMGY_effect, by='year') |>
     mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
-    # filter(!is.na(resid)) |>
     pull(resid) |> mse()
 }
 calc_UMGY_effect_MSE.cv <- function(UMGY_effect){

### 2025-05-23 reports/capstone-movielens.site/01.intro.Rmd
`UMGE Model: Support Funcions` section added.

@@
 
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
+::: {.noteblock data-latex=""}
+Further analysis of the `edx` dataset was also inspired by the article [Movie Recommendation System using R - BEST](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook) written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST], from which the code and explanatory notes below were cited.
+:::
+
 \newpage
@@
 \
+
 ##### Movie popularity count[@MRS-R-BEST]

### 2025-05-23 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd

--- 2025-05-13 reports/capstone-movielens-report.draft4.Rmd
@@
-```{r setup, include=FALSE, echo = FALSE}
-r.path <- "../r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-# Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
-
-# main_script.file_path <- file.path(r.src.path,
-#                                    "capstone-movielens.main.R")
-# stop(main_script.file_path)
-stopifnot(file.exists(setup_script.file_path))
-
-source(setup_script.file_path, 
-       local = knitr::knit_global())
-# or sys.source("your-script.R", envir = knitr::knit_global())
-
-# External Common Helper functions -------------------------------------
-# common_helper_functions.file_path <- file.path(support_functions.path,
-#                                             "common-helper.functions.R")
-# source(common_helper_functions.file_path, 
-#        local = knitr::knit_global())
-
-# knitr::knit_global()
-#knitr::opts_chunk$set(echo = FALSE)
-```
-
----
-title: "Capstone Movielens Report"
-author: "Azamat Kurbanaev"
-date: "`r Sys.Date()`"
-bibliography: references.bib
-#csl: bit-numerical-mathematics.csl 
-envir:
-  parent.frame()
-output: 
-  bookdown::pdf_document2: 
-    df_print: paged
-    toc: true
-    fig_caption: true
-    keep_tex: true
-    citation_package: biblatex
-colorlinks: true
-linkcolor: red
-citecolor: blue
-header-includes:
-    - \usepackage{awesomebox}
-    - \usepackage{hyperref}
-    - \usepackage[natbib=true, 
-                  style=numeric, 
-                  backref=true, 
-                  sorting=none]{biblatex}
-    - \hypersetup{backref,
-          pdfpagemode=Normal,
-          colorlinks=true,
-          implicit=false}
-vignette: >
-  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
-  %\VignetteEncoding{UTF-8}
-  %\VignetteEngine{knitr::knitr}
----
-
-\newenvironment{infobox}[1]
-  {
-  \begin{itemize}
-  \renewcommand{\labelitemi}{
-    \raisebox{-.7\height}[0pt][0pt]{
-      {\setkeys{Gin}{width=3em,keepaspectratio}
-        \includegraphics{images/#1}}
-    }
-  }
-  \setlength{\fboxsep}{1em}
-  \begin{blackbox}
-  \item
-  }
-  {
-  \end{blackbox}
-  \end{itemize}
-  }
-
-# Introduction / Overview / Executive Summary
-
-The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
-$$
-\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
-$$
-
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
-
-Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).
-
-## Datasets Overview
-
-To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
-
-* **edx:** we use it to develop and train our algorithms;
-* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
-
-For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
-The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
-
-Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
-```{r eval=FALSE }
-if(!require(edx.capstone.movielens.data)) pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
-
-library(edx.capstone.movielens.data)
-edx <- edx.capstone.movielens.data::edx
-final_holdout_test <- edx.capstone.movielens.data::final_holdout_test
-```
-
-Now, we have the datasets listed above:
-```{r }
-summary(edx)
-```
-
-```{r }
-summary(final_holdout_test)
-```
-
-### `edx` Dataset
+## User+Movie+Genre+Year+Day Effect (UMGYDE) Model
 \
-Let's look into the details of the `edx` dataset:
-``` {r echo = TRUE}
-str(edx)
-```
-Note that we have 9000055 rows and six columns in there:  
-```{r }
-dim_edx <- dim(edx)
-print(dim_edx)
-```
-
-First, let's note that we have 10677 different movies: 
-```{r}
-n_movies <- n_distinct(edx$movieId)
-print(n_movies)
-```
-and 69878 different users in the dataset:
-```{r}
-n_users <- n_distinct(edx$userId)
-print(n_users)
-```
-
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
-```{r}
-max_possible_ratings <- n_movies*n_users
-sprintf("Maximum possible ratings: %s", max_possible_ratings)
-sprintf("Rows in `edx` dataset: %s", dim_edx[1])
-sprintf("Not every movie was rated: %s", max_possible_ratings > dim_edx[1])
-
-```
-
-As also explained in that section, we can think of these data as a very large matrix, with users on the rows and movies on the columns, with many empty cells.
-Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
-```{r}
-keep <- edx |> 
-  dplyr::count(movieId) |> 
-  top_n(4, n) |> 
-  pull(movieId)
-
-tab <- edx |> 
-  filter(movieId %in% keep) |> 
-  filter(userId %in% c(13:20)) |> 
-  select(userId, title, rating) |> 
-  mutate(title = str_remove(title, ", The"),
-         title = str_remove(title, ":.*")) |>
-  pivot_wider(names_from = "title", values_from = "rating")
-
-print(tab)
-```
-
-The following plot of the matrix for a random sample of 100 movies and 100 users with yellow indicating a user/movie combination for which we have a rating shows how _sparse_ the matrix is:
-```{r sparsity-of-movie-recs, echo=TRUE, fig.width=3, fig.height=3, out.width="40%"}
-users <- sample(unique(edx$userId), 100)
-
-rafalib::mypar()
-edx|> 
-  filter(userId %in% users) |> 
-  select(userId, movieId, rating) |>
-  mutate(rating = 1) |>
-  pivot_wider(names_from = movieId, values_from = rating) |> 
-  (\(mat) mat[, sample(ncol(mat), 100)])() |>
-  as.matrix() |> 
-  t() |>
-  image(1:100, 1:100, z = _ , xlab = "Movies", ylab = "Users")
-```
-
-Further observations highlighted there that, as we can see from the distributions the author presented, some movies get rated more than others, and some users are more active than others in rating movies:
-```{r movie-id-and-user-hists, echo=TRUE, fig.width=6, fig.height=3}
-p1 <- edx |> 
-  count(movieId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Movies")
-
-p2 <- edx |> 
-  count(userId) |> 
-  ggplot(aes(n)) + 
-  geom_histogram(bins = 30, color = "black") + 
-  scale_x_log10() + 
-  ggtitle("Users")
-
-gridExtra::grid.arrange(p2, p1, ncol = 2)
-```
-
-Finally, we can see that no movies have a rating of 0. Movies are rated from 0.5 to 5.0 in 0.5 increments:
-```{r }
-#library(dplyr)
-s <- edx |> group_by(rating) |>
-  summarise(n = n())
-print(s)
-```
-
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
-
-#### Rating distribution plot[@MRS-R-BEST]
-\
-The code below demonstrates another way of visualizing the rating distribution:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-
-```
-
-This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-
-#### Ratings per movie
-\
-
-##### Movie popularity count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  group_by(movieId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-```{r}
-summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per movie plot[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Movies' rating histogram[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-#### Ratings per user[@MRS-R-BEST]
-\
-
-##### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-##### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-
-##### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-##### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-# Methods / Analysis
-::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
-:::
-
-## Defining Logging and Time Measuring Helper Functions
-\
-
-First, let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
-
-```{r eval=FALSE }
-# Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log1(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log1(msg_template, arg1, arg2))
-}
-
-# ...
-```
-
-::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## Preparing train and set datasets
-\
-
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
-To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
-```{r eval=FALSE }
-make_source_datasets()
-init_source_datasets()
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-### The `make_source_datasets` function
-\
-
-Let's take a closer look at the objects we will receive as a result of executing this function.
-
-```{r eval=FALSE}
-
-make_source_datasets <- function(){
-  # ...
-  list(edx_CV = edx_CV,
-       edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
-       tuning_sets = tuning_sets,
-       movie_map = movie_map,
-       date_days_map = date_days_map)
-}
-```
-
-#### `edx.mx` Matrix Object
-\
-
-We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
-To create this matrix, we use `tidyr::pivot_wider` function:
-
-```{r eval=FALSE}
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-
-```
-
-```{r}
-  str(edx.mx)
-```
-
-#### `edx.sgr` Object
-\
-
-To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-```
-```{r}
-str(edx.sgr)
-summary(edx.sgr)
-```
-
-Note that we use the `splitGenreRows` function to split rows of the original dataset:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function mentioned above is also available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-#### `movie_map` Object
-\
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r eval=FALSE}
-movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-```
-
-```{r}
-str(movie_map)
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
-
-#### `date_days_map` Object
-\
-
-We have a `timestamp` field in the `edx` dataset.
-To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-```
-``` {r}
-  str(date_days_map)
-  summary(date_days_map)
-```
-
-#### `edx_CV` Object
-\
-
-Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_:
-```{r eval=FALSE}
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
-```
-```{r}
-str(edx_CV)
-```
-
-::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) _function_ code described above.
-:::
-
-Note that we used the `sample_train_validation_sets` function call to split the original dataset (`edx` in this case): 
-```{r eval=FALSE}
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-```
-
-which returns a pair of train/validation sets:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets ----------------------------------------------------    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)` one, from where it is called.
-:::
-
-### Common Helper Functions
-\
-
-For our further analysis, we are going to use the following _common helper functions_:
-
-#### `clamp` function
-\
-
-As explained in [Section  24.4 User effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings can’t be below 0.5 or above 5.
-For this reason, we will use the `clamp` function described in that section:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
-#### Functions to calculate _(Root) Mean Squared Error_
-\
-
-We will need the following functions to calculate _(R)MSEs_:
-```{r eval=FALSE}
-mse <- function(r) mean(r^2)
-
-mse_cv <- function(r_list) {
-  mses <- sapply(r_list, mse(r))
-  mean(mses)
-}
-
-rmse <- function(r) sqrt(mse(r))
-# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
-
-rmse2 <- function(true_ratings, predicted_ratings) {
-  rmse(true_ratings - predicted_ratings)
-}
-```
-
-::: {.noteblock data-latex=""}
-All the _common helper functions_, including those described above, are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-## Overall Mean Rating (Naive) Model
-\
-
-Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
-It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
-
-$$
-Y_{i,j} = \mu + \varepsilon_{i,j}
-$$
-
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
-
-We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
-
-```{r pressure, echo=TRUE}
-mu <- mean(edx$rating)
-print(mu)
-```
-
-If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
-```{r}
-mu.MSEs <- naive_model_MSEs(mu)
-data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the Overall Mean Rating Model",
-              xname = "fold_No", 
-              yname = "MSE")
-
-mu.RMSE <- sqrt(mean(mu.MSEs))
-mu.RMSE
-```
-::: {.noteblock data-latex=""}
-For the _Mean Squared Error_ data visualization we used [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function] defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.function.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script.
-:::
-
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      # scale = 1,
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
-
-Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
-
-```{r eval=FALSE }
-naive_model_MSEs <- function(val) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - val)
-  })
-}
-```
-
-One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L59) one:
-```{r eval=FALSE }
-naive_model_RMSE <- function(val){
-  sqrt(mean(naive_model_MSEs(val)))
-}
-```
-
-### Ensure that `mu.RMSE` value is the best for the current model
-\
-
-If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
-```{r }
-  deviation <- seq(0, 6, 0.1) - 3
-
-  deviation.RMSE <- sapply(deviation, function(delta){
-    naive_model_RMSE(mu + delta)
-  })
-```
-
-Let's make a quick investigation of the `deviation.RMSE` result we have just got: 
-```{r}
-data.frame(delta = deviation, 
-           delta.RMSE = deviation.RMSE) |> 
-data.plot(title = TeX(r'[RMSE as a function of deviation ($\delta$) from the Overall Mean Rating ($\hat{mu}$)]'),
-              xname = "delta", 
-              yname = "delta.RMSE", 
-              xlabel = TeX(r'[$\delta$]'), 
-              ylabel = "RMSE")
-
-which_min_deviation <- deviation[which.min(deviation.RMSE)]
-min_rmse = min(deviation.RMSE)
-
-print_log1("Minimum RMSE is achieved when the deviation from the mean is: %1",
-         which_min_deviation)
-
-print_log1("Is the previously computed RMSE the best for the current model: %1",
-         mu.RMSE == min_rmse)
-```
-```{r eval=FALSE}
-RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
-  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.OMR)
-```
-
-To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]
-
-## User Effect Model
-\
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
-```{r}
-hist(edx.user_mean_ratings$mean_rating, nclass = 30)
-```
-
-Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
-The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
-So we write the model as follows:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \varepsilon_{i,j}
-$$
-
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
-
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we can compute them this way:
-```{r eval=FALSE}
-a <- rowMeans(y - mu, na.rm = TRUE)
-```
-
-These considerations alows us to compute a _User Mean Ratings_ the following way:
-```{r eval=FALSE}
-put_log("Computing Average Ratings per User (User Mean Ratings)...")
-user.mean_ratings <- rowMeans(edx.mx, na.rm = TRUE)
-user_ratings.n <- rowSums(!is.na(edx.mx))
-
-edx.user_mean_ratings <- 
-  data.frame(userId = names(user.mean_ratings), 
-             mean_rating = user.mean_ratings,
-             n = user_ratings.n)
-
-put_log("User Mean Ratings have been computed.")
-```
-```{r}
-str(edx.user_mean_ratings)
-```
-
-And then we compute a _User Effect_ this way:
-```{r eval=FALSE}
-put_log("Computing User Effect per users ...")
-edx.user_effect <- edx.user_mean_ratings |>
-  mutate(userId = as.integer(userId),
-         a = mean_rating - mu)
-
-put_log("A User Effect Model has been builded")
-```
-```{r}
-par(cex = 0.7)
-hist(edx.user_effect$a, 30, xlab = TeX(r'[$\hat{alpha}_{i}$]'),
-     main = TeX(r'[Histogram of $\hat{alpha}_{i}$]'))
-
-str(edx.user_effect)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect_ computation is available in the [Model building: User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L531) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Finally, we are ready to compute the `RMSE` (additionally using the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) helper function we defined above to keep predictions in the proper range):
-```{r eval=FALSE}
-put_log("Computing the RMSE taking into account user effects...")
-start <- put_start_date()
-edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
-  cv_fold_dat$validation_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - clamp(mu + a)) |> 
-    pull(resid) |> mse()
-})
-put_end_date(start)
-
-edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
-
-RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
-  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
-```
-```{r}
-data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
-  data.plot(title = "MSE resuls of the 5-fold CV method applied to the User Effect Model",
-            xname = "fold_No", 
-            yname = "MSE")
-
-RMSE_kable(RMSEs.ResultTibble.UE)
-```
-
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-## User+Movie Effect (UME) Model
-\
-
-In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
-He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
-$$
-The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:
-
-```{r eval=FALSE}
-b <- colMeans(y - mu - a, na.rm = TRUE)
-```
-
-Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
-
-### UME Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
-:::
-
-#### `train_user_movie_effect` Function
-\
-
-We use this function to build and train our model using the `train_set` dataset:
-```{r eval=FALSE}
-train_user_movie_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_effect
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need for the *Regularization*.
-We will explain that later in the [Regularization Method] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the `mean_reg` function is equivalent to the simple `mean` one.
-:::
-
-```{r eval=FALSE}
-# Regularization --------------------------------------------------------------
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-#### `train_user_movie_effect.cv` Function
-\
-
-We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method.
-Below, we provide the most important part of the code of that function:
-```{r eval=FALSE}
-train_user_movie_effect.cv <- function(lambda = 0){
-# ...
-  start <- put_start_date()
-  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
-  })
-  put_end_date(start)
-  put_log("Function: train_user_movie_effect.cv:
-User+Movie Effect list have been computed")
-
-  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-
-  user_movie_effect <- user_movie_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  # ...
-  user_movie_effect
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the `Cross Validation` results.
-:::
-```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
-```
-
-#### `calc_user_movie_effect_MSE` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE <- function(test_set, um_effect){
-  mse.result <- test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(um_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    pull(resid) |> mse()
-
-  stopifnot(!is.na(mse.result))
-  mse.result
-}
-```
-
-#### `calc_user_movie_effect_MSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv <- function(um_effect){
-  put_log("Function: user_movie_effects_MSE.cv:
-Computing the RMSE taking into account User+Movie Effects...")
-  start <- put_start_date()
-  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
-  })
-  put_end_date(start)
-
-  put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_effects_MSEs)
-}
-
-```
-
-#### `calc_user_movie_effect_RMSE` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-  sqrt(mse)
-}
-```
-
-#### `calc_user_movie_effect_RMSE.cv` Function
-\
-
-The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
-  um_effect_RMSE
-}
-
-```
-
-### Model Building
-\
-
-::: {.noteblock data-latex=""}
-The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
-```{r eval=FALSE}
-  cv.UM_effect <- train_user_movie_effect.cv()
-```
-```{r}
-str(cv.UM_effect)
-
-par(cex = 0.7)
-hist(cv.UM_effect$b, 30, xlab = TeX(r'[$\hat{beta}_{j}$)]'),
-     main = TeX(r'[Histogram of $\hat{beta}_{j}$]'))
-```
-
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
-```{r eval=FALSE}
-cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
-
-RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
-  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
-
-```
-```{r}
-RMSE_kable(RMSEs.ResultTibble.UME)
-```
-
-## Regularizing User+Movie Effect Model
-
-### Utilizing Penalized least squares
-\
-[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$.
-Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:
-
-$$ 
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
-$$
-The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large.
-Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:
-
-$$
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
-
-where $n_j$ is the number of ratings made for movie $j$.
-
-This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$.
-Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
-
-  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
-
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
-
-### UME Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-
-#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function
-\
-
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
-```{r eval=FALSE}
-regularize.test_lambda.UM_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UM_effect.cv
-`lambda` is `NA`")
-  }
-  um_effect <- train_user_movie_effect.cv(lambda)
-  calc_user_movie_effect_RMSE.cv(um_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_effect.cv]() calling it from the [regularize.test_lambda.UM_effect.cv](), but now with the $\lambda$ parameter different from the default (zero) value.
-:::
-
-Let's now figure out the $\lambda$ that minimizes the _RMSE_:
-```{r eval=FALSE}
-# Here we will simply compute the RMSE for different values of `lambda` 
-n <- colSums(!is.na(y))
-
-sums <- colSums(y - mu - a, na.rm = TRUE)
-lambdas <- seq(0, 10, 0.1)
-
-rmses <- sapply(lambdas, function(lambda){
-  b <-  sums / (n + lambda)
-  reg_rmse(b)
-})
-
-# Here is a plot of the RMSE versus `lambda`:
-plot(lambdas, rmses, type = "l")
-```
-Now we can determine the minimal _RMSE_:
-```{r}
-# print(min(rmses))
-```
-
-which is achieved for the following $\lambda$:
-```{r eval=FALSE}
-lambda <- lambdas[which.min(rmses)] 
-print(lambda)
-```
-
-Using this $\lambda$ we can compute the regularized estimates:
-```{r eval=FALSE}
-b_reg <- sums / (n + lambda)
-
-str(b_reg)
-```
-Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
-```{r eval=FALSE}
-reg_rmse(b_reg)
-```
-
-## Accounting for Date effects
-
-#### Yearly rating count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(count = n())
-)
-```
-
-#### Average rating per year plot[@MRS-R-BEST]
-\
-```{r}
-edx |> 
-  mutate(year = year(as_datetime(timestamp, origin = "1970-01-01"))) |>
-  group_by(year) |>
-  summarize(rating_avg = mean(rating)) |>
-  ggplot(aes(x = year, y = rating_avg)) +
-  geom_bar(stat = "identity", fill = "#8888ff") + 
-  ggtitle("Average rating per year") +
-  xlab("Year") +
-  ylab("Average rating") +
-  scale_y_continuous(labels = comma) + 
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-We use the following models to account for the `date` effect:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + f(d_{i,j}) + \varepsilon_{i,j}
-$$
-
-## Accounting for Genre effect
-\
-As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
-This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
-
-### Genre Data Analysis
-\
-#### Movie Genres Data 
-\
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r eval=FALSE}
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r eval=FALSE}
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r eval=FALSE}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r eval=FALSE}
-print(edx |> group_by(rating) |> summarize(count = n()))
-```
-
-We can visually see that from the following plot:
-```{r eval=FALSE}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
-#### Movie Genres Effect 
-\
-
-The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
-
-```{r eval=FALSE}
-# Preparing data for plotting:
-genre_ratins_grp <- train_set |> 
-  mutate(genre_categories = as.factor(genres)) |>
-  group_by(genre_categories) |>
-  summarize(n = n(), rating_avg = mean(rating), se = sd(rating)/sqrt(n())) |>
-  filter(n > 20000) |> 
-  mutate(genres = reorder(genre_categories, rating_avg)) |>
-  select(genres, rating_avg, se, n)
-
-dim(genre_ratins_grp)
-genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
-print(genre_ratins_grp_sorted)
-
-# Creating plot:
-genre_ratins_grp |> 
-  ggplot(aes(x = genres, y = rating_avg, ymin = rating_avg - 2*se, ymax = rating_avg + 2*se)) + 
-  geom_point() +
-  geom_errorbar() + 
-  ggtitle("Average rating per Genre") +
-  ylab("Average rating") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-```
-Below are worst and best ratings categories:
-```{r eval=FALSE}
-sprintf("The worst ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.min(genre_ratins_grp$genres)])
-
-sprintf("The best ratings are for the genre category: %s",
-        genre_ratins_grp$genres[which.max(genre_ratins_grp$genres)])
-```
-
-Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article "Movie Recommendation System using R - BEST" written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST]:
-```{r eval=FALSE}
-# For better visibility, we reduce the data for plotting 
-# while keeping the worst and best rating rows:
-plot_ind <- odd(1:nrow(genre_ratins_grp))
-plot_dat <- genre_ratins_grp_sorted[plot_ind,]
-
-plot_dat |>
-  ggplot(aes(x = rating_avg, y = genres)) +
-  ggtitle("Genre Average Rating") +
-  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
-  xlab("Average ratings") +
-  ylab("Genres") +
-  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
-  theme_economist() +
-  theme(plot.title = element_text(vjust = 3.5),
-        axis.title.x = element_text(vjust = -5, face = "bold"),
-        axis.title.y = element_text(vjust = 10, face = "bold"),
-        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
-        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-If we define $g_{i,j}$ as the genre for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
-
-To account for _genre effects_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
-
-$$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \varepsilon_{i,j}
-$$
-
-where $g_{i,j}$ is an _aggregation function_ which is explained in detail in _Section 22.3: "Review of Aggregation Functions" of "Recommender Systems Handbook"_ (_Chapter 22: "Aggregation of Preferences in Recommender Systems"_, p.
-712) book[@RRSK_RS_HB].
-
-In the formula above $g_{i,j}$ denotes a _genre effect_ for user's $i$ rating of movie $j$, so that:
-
-$$
-g_{i,j} = \sum_{k=1}^K x_{i,j}^k \gamma_k
-$$
-
-with $x^k_{i,j} = 1$ if $g_{i,j}$ includes genre $k$, and $x^k_{i,j} = 0$ otherwise.
 
@@
 
-# Conclusion
+\newpage
 
-Hello Conclusion!
-
-This is a great conclusion, isn't it?!!
-
-# Appendix
-
-## Regularization: Common Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-#### Parameters
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ; 
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-#### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-#### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-#### Sugnature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-#### **Parameters**
-\
-
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-##### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-##### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-##### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-##### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-##### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-##### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-##### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-##### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-#### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-#### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-#### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The full version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
-:::
-:::
-
-### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-#### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-##### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-#### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-#### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-#### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-#### Parameters
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-#### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-#### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-#### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-## Support Functions
-
-### [func.00]() Function {#func.00}
-\
-
-::: { #func.00.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.00.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.00.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.00.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.00.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.01}
-\
-
-::: { #func.01.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.01.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.01.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.01.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.01.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func]() Function {#func.02}
-\
-
-::: { #func.02.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.02.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.02.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.02.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.02.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.0]() Function {#func.0}
-\
-
-::: { #func.0.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.0.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.0.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.0.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func1]() Function {#func.03}
-\
-
-::: { #func.03.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.03.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.03.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.03.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.03.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [func1]() Function {#func.1}
-\
-
-::: { #func.1.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.1.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.1.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.1.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.1.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.2]() Function {#func.2}
-\
-
-::: { #func.2.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.2.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.2.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.2.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.2.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
---------------------------------------------------------------------------------
-
-### [func.3]() Function {#func.3}
-\
-
-::: { #func.3.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.3.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.3.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.3.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.3.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.4]() Function {#func.4}
-\
-
-::: { #func.4.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.4.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.4.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.4.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.4.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.5]() Function {#func.5}
-\
-
-::: { #func.5.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.5.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.5.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.5.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.5.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.6]() Function {#func.6}
-\
-
-::: { #func.6.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.6.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.6.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.6.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.6.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.7]() Function {#func.7}
-\
-
-::: { #func.7.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.7.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.7.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.7.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.7.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### [func.8]() Function {#func.8}
-\
-
-::: { #func.8.signature .sidebar }
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.8.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.8.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.8.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.8.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
---------------------------------------------------------------------------------
-
-### []() Function {#func.3-1}
-\
-
-#### Sugnature
-\
-```{r eval=FALSE}
-
-```
-
-#### Parameters
-\
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-#### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-#### Value
-\
-
-#### Source Code
-\
-Below is the most significant part of the code of the [function]() function:
-```{r eval=FALSE}
-
-```
-
-================================================================================
-
-```{r eval=FALSE}
-
-```
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-::: {.noteblock data-latex=""}
-!!! Note!
-:::
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
-
-```{r eval=FALSE}
-
-```
+\newpage

### 2025-05-24 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Report review; working on UMGYE Model Building (in progress)

@@
-## Overall Mean Rating (Naive) Model
+## Overall Mean Rating (OMR) Model
 \
@@
 Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
+
+### Mathematical Description of the OMR Model
+\
+
 It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
@@
 with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
+
+### OMR Model Building
+\
 
@@
 ```
+
 ::: {.noteblock data-latex=""}
-For the _Mean Squared Error_ data visualization we used [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function] defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.function.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script.
+For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
 :::
-
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      # scale = 1,
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
 
@@
 
-### Ensure that `mu.RMSE` value is the best for the current model
+### OMR Value Is the Best for the Current Model
 \

### 2025-05-24 r/src/capstone-movielens.main.R

@@ -1,3 +1,4 @@
+# Init Project Environment -----------------------------------------------------
 ## Source File Paths -----------------------------------------------------------
 r.path <- "r"
 src.folder <- "src"
@@ -8,16 +9,15 @@ r.src.path <- file.path(r.path, src.folder)
 support_scripts.path <- file.path(r.src.path, support_scripts.folder)
 support_functions.path <- file.path(r.src.path, support_functions.folder)
 ## Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path,
-                                               "setup.R")
+setup_script.file_path <- file.path(support_scripts.path, "setup.R")
+
 source(setup_script.file_path, 
        catch.aborts = TRUE,
        echo = TRUE,
        spaced = TRUE,
        verbose = TRUE,
        keep.source = TRUE)
-
-## Logging Helper functions -----------------------------------------------------
+### Logging Helper functions -----------------------------------------------------
 open_logfile <- function(file_name){
   log_file_name <- as.character(Sys.time()) |> 
     str_replace_all(':', '_') |> 
@@ -113,7 +113,7 @@ put_log4 <- function(msg_template, arg1, arg2, arg3, arg4){
 }
 ### Open log file for `Initialize Source File Paths` Feature -------------------
 open_logfile(".src.file-paths")
-## External Common Helper functions -------------------------------------
+### External Common Helper functions -------------------------------------
 common_helper_functions.file_path <- file.path(support_functions.path,
                                             "common-helper.functions.R")
 source(common_helper_functions.file_path, 
@@ -122,7 +122,7 @@ source(common_helper_functions.file_path,
        spaced = TRUE,
        verbose = TRUE,
        keep.source = TRUE)
-## Init Project Global Variables ----------------------------------------------
+### Init Project Global Variables ----------------------------------------------
 put("Set Project Objective according to Capstone course requirements")
 project_objective <- 0.86490
 put(project_objective)
@@ -136,7 +136,7 @@ kfold_index <- seq(from = 1:CVFolds_N)
 
 #RMSEs.ResultTibble <- NULL
 
-### Data File Paths ------------------------------------------------------------
+#### Data File Paths ------------------------------------------------------------
 data.path <- "data"
 dir.create(data.path)
 put_log1("Directory path has been created: %1", data.path)
[…]

### 2025-05-24 reports/capstone-movielens.site/01.intro.Rmd

--- 2025-05-18 reports/capstone-movielens.site/01.intro.Rmd
@@
 
-Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
 \newpage
-
-#### Rating distribution plot[@MRS-R-BEST]
-\
-The code below demonstrates another way of visualizing the rating distribution:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-
-```
-
-This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-\newpage
-
-#### Ratings per movie
-\
-##### Movie popularity count[@MRS-R-BEST]
-\
-```{r}
-print(edx |> 
-  group_by(movieId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-```{r}
-summary(edx |> group_by(movieId) |> summarize(count = n()) |> select(count))
-```
-\newpage
-
-##### Ratings per movie plot[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-\newpage
-
-##### Movies' rating histogram[@MRS-R-BEST]
-\
-```{r}
-edx |>
-  group_by(movieId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-\newpage
-
-#### Ratings per user[@MRS-R-BEST]
-\
-
-##### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-##### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-\newpage
-
-##### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-\newpage
-
-##### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-\newpage

### 2025-05-24 reports/capstone-movielens.site/02.4.UE-model.Rmd

@@
-## User Effect Model
+## User Effect (UE) Model
 \
 
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
+### User Effect Anasysis
+\
+
+To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*[@IDS2_23-4].
+
 If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
@@
 ```
+
+\newpage
+
+#### Ratings per user
+\
+eponymous
+homonymous
+
+::: {.noteblock data-latex=""}
+The code in this section is cited from [the eponymous section](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Ratings-per-user) of the article _Movie Recommendation System using R - BEST_[@MRS-R-BEST].
+:::
+##### User rating count (activity measure)
+\
+```{r}
+print(edx |> 
+  group_by(userId) |> 
+  summarize(count = n()) |>
+  slice_head(n = 10)
+)
+```
+
+##### User rating summary
+\
+```{r}
+summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
+```
+\newpage
+
+##### Ratings per user plot
+\
+```{r}
+edx |>
+  group_by(userId) |>
+  summarize(count = n()) |>
+  ggplot(aes(x = userId, y = count)) +
+  geom_point(alpha = 0.2, color = "#4020dd") +
+  geom_smooth(color = "red") +
+  ggtitle("Ratings per user") +
+  xlab("Users") +
+  ylab("Number of ratings") +
+  scale_y_continuous(labels = comma) +
+  scale_x_continuous(n.breaks = 10) +
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+```
+\newpage
+
+##### Users' rating histogram
+\
+```{r}
+edx |>
+  group_by(userId) |>
+  summarize(count = n()) |>
+  ggplot(aes(x = count)) +
+  geom_histogram(fill = "#8888ff", color = "#4020dd") +
+  ggtitle("Users' rating histogram") +
+  xlab("Rating count") +
+  ylab("Number of users") +
+  scale_y_continuous(labels = comma) +
+  scale_x_log10(n.breaks = 10) +
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+```
+
+\newpage
+
+### Mathematical Description of the UE Model
+\
 
@@
 Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
+
+### UE Model Building
+\
 
@@
 
-Finally, we are ready to compute the `RMSE` (additionally using the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) helper function we defined above to keep predictions in the proper range):
+Finally, we are ready to compute the `RMSE` (additionally using the [clamp](#func.clamp) helper function we described above to keep predictions in the proper range):
+
+Now, we are ready to compute the _Mean Squared Errors_ from the _5-Fold Cross Validation_ (additionally using the [clamp](#func.clamp) helper function we described above):
 ```{r eval=FALSE}
@@
 put_end_date(start)
-
-edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
-
-RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
-  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
 ```
@@
 
+```
+
+::: {.noteblock data-latex=""}
+For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+:::
+
+Finally, we calculate the `RMSE` as the _square root_ of the average of the _Mean Squared Errors_ we obtained through the _5-Fold Cross Validation_ above:   
+```{r, eval=FALSE}
+edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
+
+RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
+  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
+```
+```{r}
 RMSE_kable(RMSEs.ResultTibble.UE)

### 2025-05-24 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 
+### Movie Effect Analysis
+\
+
+#### Movies' Popularity
+\
+
+::: {#textbook.23.5.movie_effects .sidebar }
 In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
-He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$:
+:::
+
+To prove this fact, we can find out the movies with the highest number of ratings using the following code:
+```{r, eval=FALSE}
+edx.ordered_movie_ratings <- edx |> group_by(movieId, title) |>
+  summarize(number_of_ratings = n()) |>
+  arrange(desc(number_of_ratings))
+```
+```{r }
+print(head(edx.ordered_movie_ratings))
+```
+
+\newpage
+
+Now, we can figure out the most given ratings in order from most to least:
+```{r, eval=FALSE}
+edx.rating_groups <- edx |>  group_by(rating) |>
+     summarise(count = n()) |>
+     arrange(desc(count))
+```
+```{r, include=TRUE}
+print(edx.rating_groups)
+```
+
+\newpage
+
+#### Rating Distribution
+\
+
+The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
+```{r, include=TRUE}
+print(edx.rating_groups |> arrange(rating))
+```
+
+We can visually see that from the following plot:
+```{r}
+edx.rating_groups |>
+  ggplot(aes(x = rating, y = count)) +
+  geom_line()
+
+```
+
+\newpage
+
+The more sophisticated way of visualizing the rating distribution shown below is cited from the [Rating distribution plot](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Rating-distribution-plot) section of the article _Movie Recommendation System using R - BEST_[@MRS-R-BEST] already referenced above in the [Ratings per user] section of this report.
+
+```{r}
+edx.rating_groups |>
+  ggplot(aes(x = rating, y = count)) +
+  geom_bar(stat = "identity", fill = "#8888ff") +
+  ggtitle("Rating Distribution") +
+  xlab("Rating") +
+  ylab("Occurrences Count") +
+  scale_y_continuous(labels = comma) +
+  scale_x_continuous(n.breaks = 10) +
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+```
+
+> This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
+The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
+That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
+
+The two more plots below, from the same article, give us an additional visual representation of the movies' popularity.
+
+\newpage
+
+##### [Ratings per movie plot](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Ratings-per-movie-plot)
+\
+
+```{r}
+edx.movie_groups <- edx |>
+  group_by(movieId) |>
+  summarize(count = n())
+
+edx.movie_groups |>
+  ggplot(aes(x = movieId, y = count)) +
+  geom_point(alpha = 0.2, color = "#4020dd") +
+  geom_smooth(color = "red") +
+  ggtitle("Ratings per movie") +
+  xlab("Movies") +
+  ylab("Number of ratings") +
+  scale_y_continuous(labels = comma) +
+  scale_x_continuous(n.breaks = 10) +
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+```
+\newpage
+
+##### [Movies' rating histogram](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Movies'-rating-histogram)
+\
+
+```{r}
+edx.movie_groups |>
+  ggplot(aes(x = count)) +
+  geom_histogram(fill = "#8888ff", color = "#4020dd") +
+  ggtitle("Movies' rating histogram") +
+  xlab("Rating count") +
+  ylab("Number of movies") +
+  scale_y_continuous(labels = comma) +
+  scale_x_log10(n.breaks = 10) +
+  theme_economist() +
+  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
+        axis.title.y = element_text(vjust = 10, face = "bold"), 
+        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+```
+
+> This histogram better conveys the information provided by the summary() function, where the quantiles’ values state that half the movies are rated between 30 and 565 times[@MRS-R-BEST].
+
+\newpage
+
+### Mathematical Description of the UME Model
+\
+
+The author of the *Course Textbook* mentioned [above](#textbook.23.5.movie_effects) also explains that in this case one can use a linear model with a _treatment effect_ $\beta_j$ for each movie, which can be interpreted as the movie effect, or the difference between the average rating for movie $j$ and the overall average $\mu$:
 

### 2025-05-24 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

@@
 
-### Genre Data Analysis
-\
-
-#### Movie Genres Data 
-\
-
-The following code computes movie rating summaries by popular genres like Drama, Comedy, Thriller, and Romance:
-```{r }
-#library(stringr)
-genres = c("Drama", "Comedy", "Thriller", "Romance")
-sapply(genres, function(g) {
-  sum(str_detect(edx$genres, g))
-})
-```
-
-Further, we can find out the movies that have the greatest number of ratings using the following code:
-```{r }
-ordered_movie_ratings <- edx |> group_by(movieId, title) |>
-  summarize(number_of_ratings = n()) |>
-  arrange(desc(number_of_ratings))
-print(head(ordered_movie_ratings))
-```
-
-and figure out the most given ratings in order from most to least:
-```{r}
-ratings <- edx |>  group_by(rating) |>
-     summarise(count = n()) |>
-     arrange(desc(count))
-print(ratings)
-```
-
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r}
-edx |> group_by(rating) |> summarize(count = n())
-```
-
-We can visually see that from the following plot:
-```{r}
-edx |>
-  group_by(rating) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_line()
-
-```
-
-#### Movie Genres Effect 
+### Movie Genres Effect Anasysis
 \

### 2025-05-25 reports/templates/02.X.UM+model.template.Rmd
Section `UMGYE Model Building` completed.

@@
 
-#### [calc_UM?_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L93) Function
+#### [calc_UM?_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L93) Function {#func.calc_UM?_effect_MSE}
 \
@@
 
-#### [calc_UM?_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) Function
+#### [calc_UM?_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) Function {#func.calc_UM?_effect_MSE.cv}
 \
@@
 
-#### [calc_UM?_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L115) Function
+#### [calc_UM?_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L115) Function {#func.calc_UM?_effect_RMSE}
 \
@@
 
-#### [calc_UM?_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) Function
+#### [calc_UM?_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) Function {#func.calc_UM?_effect_RMSE.cv}
 \

### 2025-05-25 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd

@@
 This is a helper function that calculates the _date general effect_ of the user ratings using the _5-Fold Cross Validation_ method and is intended to be used in other functions and scripts (for instance in [train_UMGY_effect.cv](#func.train_UMGY_effect.cv)) described below.
+
+##### Souurce Code
+\
+
+::: {.noteblock data-latex=""}
+The complete version of the source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) function is available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) script on _GitHub_.
+:::
+
 The following is a simplified version of the function's source code:
@@
 
-::: {.noteblock data-latex=""}
-The complete version of the source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) function is available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) script on _GitHub_.
-:::
-
 ##### Return
@@
 A data structure containg information about _Date General Effect_ as result of _5-Fold Cross Validation_.
+
+\newpage
 
@@
 
-This function is used to train the current model using the _5-Fold Cross Validation_ method.
+This function is used to train the current model using the _5-Fold Cross Validation_.
 The following is the source code of the function:
@@
 ::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) function is also available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) script on _GitHub_.
+The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) script on _GitHub_.
 :::
@@
 
-#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) Function
+#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) Function {#func.calc_UMGY_effect_MSE}
 \
@@
     - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
+
+\newpage
 
@@
 
-\newpage
-
-#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) Function
+#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) Function {#func.calc_UMGY_effect_MSE.cv}
 \
@@
 
-#### [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) Function
+#### [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) Function {#func.calc_UMGY_effect_RMSE}
 \
@@
 
-\newpage
-
-#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) Function
+#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) Function {#func.calc_UMGY_effect_RMSE.cv}
 \
@@
 
+\newpage
+
 ### UMGYE Model Building
@@
 ::: {.noteblock data-latex=""}
-The complete source code of builing and training the current model is available in the [Model building: UMGYE Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+The complete source code of building and training the current model is available in the [UMGYE Model Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1432) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1432) script on _GitHub_.
 :::
 
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
+Below, we provide the most significant line of the code for training our model using the `5-Fold Cross Validation` method:
 ```{r, eval=FALSE}
+  cv.UMGY_effect <- train_UMGY_effect.cv()
+```
+```{r}
+str(cv.UMGY_effect)
+summary(cv.UMGY_effect)
 ```
 
-\newpage
+::: {.noteblock data-latex=""}
+We use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function described above to compute the _UMGY Effect_.
+:::
 
@@
 ```{r, eval=FALSE}
-cv.UMG_effect.RMSE <- calc_UMGY_effect_RMSE.cv(cv.UMG_effect)
+cv.UMGY_effect.RMSE <- calc_UMGY_effect_RMSE.cv(cv.UMGY_effect)
 
-RMSEs.ResultTibble.UMGYE <- RMSEs.ResultTibble.rglr.UMGYE |> 
-  RMSEs.AddRow("UMGYE Effect (UMGYE) Model", cv.UMG_effect.RMSE,
-               comment = "Comment")
+RMSEs.ResultTibble.UMGYE <- RMSEs.ResultTibble.rglr.UMGE |> 
+  RMSEs.AddRow("UMGYE Model", 
+               cv.UMGY_effect.RMSE,
+               comment = "User+Movie+Genre+Year Effect (UMGYE) Model")
 ```
@@
 
+\newpage
+
 ::: {.noteblock data-latex=""}
-Hello Note!!!
+Now, we have a bit better result than one for the previous model.
 :::
 
-\newpage
-
-### UMGYE Effect Model Regularization
+### UMGYE Model Regularization
 \

### 2025-05-26 reports/capstone-movielens.site/02.5.UME-model.Rmd
RMD report:  UMGYE Model completed.

@@
 
-We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:
+We will implement the _Regularization_ method on our  models (starting from the current model) in following three steps:
 
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
 
+Below we provide the most significant part of the code that performs this operation:
 ```{r, eval=FALSE}
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter:
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+
+Below we provide the most significant part of the code that performs this operation:
 ```{r, eval=FALSE}

### 2025-05-26 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Minor fix for the UMGYE Model Building section.
RMD report:  UMGYE Model completed.

@@
 
-If we define $\gamma(r)$ as the _year effect_ for the year (here denotes by $r$) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the following form:
+If we define $\gamma(r)$ as the _year effect_ for the year (here denotes by $r$) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the form:
 
@@
 Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
 We have already explained that in the [UME Model Regularization] section. 
@@
 
-\newpage
-
 ::: {.noteblock data-latex=""}
@@
 
+\newpage
+
 ### UMGYE Model Regularization
@@
 
-We have already explained the idea of the _Linear Model Regularization_ in the [UME Model Regularization] section above. Let's extend the concept outlined there to our current model.
-
-In this case, the formula \@ref(eq:ME-penalty) for adding a penalty takes the following form:
+We have already explained the idea of _Linear Model Regularization_ in the [UME Model Regularization] section above.
+We have also seen how the formula \@ref(eq:ME-penalty) for adding a penalty to the _UME Model_ is transformed into the formula \@ref(eq:GE-penalty) for the _UMGE Model_.
+For the current model, this formula takes the form:
 
 \begin{equation}
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - ...\right)^2 + \lambda \sum_{j} \beta_j^2 
+\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - g_{i,j} - \gamma(r)\right)^2 + \lambda \sum_{r} \gamma(r)^2
 (\#eq:YE-penalty)
@@
 
-And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimize the equation takes the following form:
+And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
 
 \begin{equation}
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
+\hat{\gamma}(r, \lambda) = \frac{1}{\lambda + n_r} \sum_{i=1}^{n_{r}} \left(Y_{i,j} - \mu - \alpha_i - \beta_j - g_{i,j}\right)
 (\#eq:YE-regularized)
@@
 
-where $n_y$ is the number of ratings made in year $y$.
+where $n_r$ is the number of ratings made in year $r$.
 
-As stated in the [UME Model Regularization] section, we will implement the _Regularization_ method on our  current model in three steps:
+As with the previous models, we implement the _Regularization_ method for the current model in the following three steps:
 
@@
 ::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UMGY_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
+The [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L128) function described below are defined in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L127) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L128) script.
 :::
 
-##### [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L96) Function {#func.regularize.test_lambda.UMGY_effect.cv}
+##### [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#128) Function {#func.regularize.test_lambda.UMGY_effect.cv}
 \
 
-This function calculates _RMSE_ of the _UMGYE Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
+This function calculates _RMSE_ of the _UMGYE Model_ using _5-Fold Cross Validation_ for the given $\lambda$ parameter value:
 ```{r, eval=FALSE}
+regularize.test_lambda.UMGY_effect.cv <- function(lambda){
+  if (is.na(lambda)) {
+    stop("Function: regularize.test_lambda.UMGY_effect.cv
+`lambda` is `NA`")
+  }
+
+  train_UMGY_effect.cv(lambda) |>
+    calc_UMGY_effect_RMSE.cv()
+}
 ```
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
 
+Below we provide the most significant part of the code that performs this operation:
 ```{r, eval=FALSE}
+  lambdas <- seq(0, 512, 32)
+  cv.UMGYE.preset.result <- 
+    tune.model_param(lambdas, 
+                     regularize.test_lambda.UMGY_effect.cv,
+                     steps.beyond_min = 16)
 ```
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
+The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) script.
 :::
@@
 ``` {r}
-# title = TeX(r'[UMGE Model Regularization: $\lambda$ Range Pre-configuration]')
+cv.UMGYE.preset.result$tuned.result |>
+  data.plot(title = TeX(r'[UMGYE Model Regularization: $\lambda$ Range Pre-configuration]'),
+              xname = "parameter.value", 
+              yname = "RMSE", 
+              xlabel = TeX(r'[$\lambda$]'), 
+              ylabel = "RMSE")
 ```
@@
 
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+:::
+
 We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter:
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+
+Below we provide the most significant part of the code that performs this operation:
 ```{r, eval=FALSE}
+endpoints <- 
+  get_fine_tune.param.endpoints(cv.UMGYE.preset.result$tuned.result)
+
+UMGYE.loop_starter <- c(endpoints["start"], 
+                        endpoints["end"], 
+                        8)
+UMGYE.loop_starter
+#> [1]
+
+cache.base_name <- "UMGYE.rglr.fine-tuning"
+
+UMGYE.rglr.fine_tune.results <- 
+  model.tune.param_range(UMGYE.loop_starter,
+                         UMGYE.rglr.fine_tune.cache.path,
+                         cache.base_name,
+                         regularize.test_lambda.UMGY_effect.cv)
 ```
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be also found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
 :::
+
+\newpage
 
@@
 ```{r}
+UMGYE.rglr.fine_tune.results$tuned.result |>
+  data.plot(title = "UMGYE Model Regularization: Fine-tuned result",
+              xname = "parameter.value",
+              yname = "RMSE",
+              xlabel = TeX(r'[$\lambda$]'),
+              ylabel = str_glue("Deviation from the best RMSE value (",
+                                as.character(round(UMGYE.rglr.fine_tune.RMSE.best, digits = 7)),
+                                ")"),
+              normalize = TRUE)
 ```
+
+::: {.noteblock data-latex=""}
+We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+:::
+
 \newpage
@@
 
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section are available in the [Re-train Regularized UMGYE Model for the best `lambda`](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1589) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1589) script on _GitHub_.
+:::
+
 Now, we can calculate the _Regularized UMGYE Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
+
 ```{r, eval=FALSE}
+  rglr.UMGY_effect <- edx |> train_UMGY_effect(UMGYE.rglr.best_lambda)
+
 ```
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section are available in the [Re-training Regularized UMGYE Effect Model for the best $\lambda$](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) script on _GitHub_.
+Here we use the helper function [train_UMGY_effect](#func.train_UMGY_effect) described above in the [UMGYE Model Regularization: Support Functions] section.
 :::
 
-We calculate the _Root Mean Squared Error_ for the ultimately computed _UMGYE Effect_ using [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described above as follows:
+We calculate the _Root Mean Squared Error_ for the ultimately computed _UMGYE Effect_ using the helper function [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) described above in the [UMGYE Model Regularization: Support Functions] section as follows:
 ```{r, eval=FALSE}
+  rglr.UMGY_effect.RMSE <- calc_UMGY_effect_RMSE.cv(rglr.UMGY_effect)
 ```
@@
 RMSEs.ResultTibble.rglr.UMGYE <- RMSEs.ResultTibble.UMGYE |> 
-  RMSEs.AddRow("Regularized UMGYE Effect Model", 
-               UMGYE.rglr.retrain.RMSE,
+  RMSEs.AddRow("Regularized UMGYE Model", 
+               rglr.UMGY_effect.RMSE,
                comment = "Computed for `lambda` = %1" |>
                  msg.glue(UMGYE.rglr.best_lambda))
+
 ```

### 2025-05-26 reports/capstone-movielens.site/04.appendix.Rmd
RMD report:  UMGYE Model completed.

@@
 
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function `get_fine_tune.param.endpoints.idx` (see the description of the function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) below) and, using one more helper function `get_best_param.result`  (see the description of the function [get_best_param.result](#func.get_best_param.result) below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
+Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) (see the description below) and, using one more helper function [get_best_param.result](#func.get_best_param.result)  (see the description below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
 
@@
 
+### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) Function {#func.get_fine_tune.param.endpoints}
+\
+
+The algorithm finds the values of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
+
+#### Signature
+\
+```{r eval=FALSE}
+get_fine_tune.param.endpoints <- function(preset.result) {
+  # ...
+
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+}
+```
+
+#### Parameters
+\
+
+::: {#func.get_fine_tune.param.endpoints.params.preset.result .sidebar }
+##### ***preset.result***
+\
+A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
+Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
+```{r eval=FALSE}
+    tuned_result <- tune.model_param(test_param_vals, 
+                                  fn_tune.test.param_value,
+                                  break.if_min,
+                                  steps.beyond_min)
+
+    tuned.result <- tuned_result$tuned.result
+    # tuned.result = data.frame(RMSE, parameter.value)
+    # ...
+    bound.idx <- get_fine_tune.param.endpoints(tuned.result)
+    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
+```
+:::
+
+#### Details
+\
+
+Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.params.preset.result) parameter.
+
+#### Value
+\
+A vector containing the element value corresponding to the minimum `RMSE` in a given sequence, along with the values of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+```
+
+#### Source Code
+\
+The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) function is provided below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints <- function(preset.result) {
+
+  preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
+
+  i <- preset.result.idx["start"]
+  j <- preset.result.idx["end"]
+  best.idx <- preset.result.idx["best"]
+
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+}
+```
+
+\newpage
+
 ### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}

### 2025-05-26 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
RMD report:  UMGYE Model completed (minor fix).

@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) script.
+The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) script on _GitHub_.
 :::

### 2025-05-26 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

@@
 
-In this case, the formula \@ref(eq:ME-penalty) for adding a penalty takes the following form:
+In this case, the formula \@ref(eq:ME-penalty) for adding a penalty takes the form:
 
@@
 
-And the formula \@ref(eq:ME-regularized) for calculating the values of the _genre effect_ that minimize the equation takes the following form:
+And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
 
@@
 
-As stated in the [UME Model Regularization] section, we will implement the _Regularization_ method on our  current model in three steps:
+As stated in the [UME Model Regularization] section, we implement the _Regularization_ method for our models in the following three steps:
 
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
 
+Below we provide the most significant part of the code that performs this operation:
 ```{r, eval=FALSE}
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter:
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+
+Below we provide the most significant part of the code that performs this operation:
 ```{r, eval=FALSE}

### 2025-05-26 reports/templates/02.X.UM+model.template.Rmd

@@
 
-If we define $\gamma(q)$ as the _year effect_ for the year (which is denotes by $q$ here) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the following form:
+If we define $\gamma(r)$ as the _year effect_ for the year (here denotes by $r$) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the form:
 
 \begin{equation}
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(q) + \varepsilon_{i,j}
-(\#eq:UM?E-model)
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(r) + \varepsilon_{i,j}
+(\#eq:UMGYE-model)
 \end{equation}
 
-Therefore, the formula \@ref(eq:genre-effect) for prediction a _genre effect_ as a residual, for a _year effect_ 
+Therefore, the formula \@ref(eq:genre-effect) for calculation the prediction of a _genre effect_ as a residual, for a _year effect_ 
 $$
-\hat{\gamma}(q) = \gamma(q) + \varepsilon_{i,j}
+\hat{\gamma}(r) = \gamma(r) + \varepsilon_{i,j}
 $$
@@
 
-We have already explained the idea of the _Linear Model Regularization_ in the [UME Model Regularization] section above. Let's extend the concept outlined there to our current model.
-
 In this case, the formula \@ref(eq:ME-penalty) for adding a penalty takes the following form:
 
+We have already explained the idea of _Linear Model Regularization_ in the [UME Model Regularization] section above.
+We have also seen how the formula \@ref(eq:ME-penalty) for adding a penalty to the _UME Model_ is transformed into the formula \@ref(eq:GE-penalty) for the _UMGE Model_.
+For the current model, this formula takes the form:
+
 \begin{equation}
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - ...\right)^2 + \lambda \sum_{j} \beta_j^2 
+\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - g_{i,j}\right)^2 + \lambda \sum_{i,j} g_{i,j}^2
 (\#eq:?E-penalty)
@@
 
-And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimize the equation takes the following form:
+And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
 
 \begin{equation}
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
+\hat{g}_{i,j}(\lambda) = \frac{1}{\lambda + n_g} \sum_{i=1}^{n_{g}} \left(Y_{i,j} - \mu - \alpha_i - \beta_j\right)
 (\#eq:?E-regularized)
@@
 
-As stated in the [UME Model Regularization] section, we will implement the _Regularization_ method on our  current model in three steps:
+As with the previous models, we implement the _Regularization_ method for the current model in the following three steps:
 
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM?_effect.cv](#func.regularize.test_lambda.UM?_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM?_effect.cv](#func.regularize.test_lambda.UM?_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
 
+Below we provide the most significant part of the code that performs this operation:
 ```{r, eval=FALSE}
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM?_effect.cv](#func.regularize.test_lambda.UM?_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter:
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM?_effect.cv](#func.regularize.test_lambda.UM?_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+
+Below we provide the most significant part of the code that performs this operation:
 ```{r, eval=FALSE}

### 2025-05-27 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Started working on new model: model template added.

@@
 
-If we define $\gamma(r)$ as the _year effect_ for the year (here denotes by $r$) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the form:
+If we define $\gamma(v_{i,j})$ as the _year effect_ for the year (here denotes by $v_{i,j}$) of rating a movie $j$ by a user $i$, the formula \@ref(eq:UMGE-model) describing the _UMGE Model_, for the current model, takes the form:
 
 \begin{equation}
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(r) + \varepsilon_{i,j}
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(v_{i,j}) + \varepsilon_{i,j}
 (\#eq:UMGYE-model)
@@
 $$
-\hat{\gamma}(r) = \gamma(r) + \varepsilon_{i,j}
+\hat{\gamma}(v_{i,j}) = \gamma(v_{i,j}) + \varepsilon_{i,j}
 $$
@@
 \begin{equation}
-\hat{\gamma}(r) = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j})
+\hat{\gamma}(v_{i,j}) = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j})
 (\#eq:year-effect)
@@
 \begin{equation}
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - g_{i,j} - \gamma(r)\right)^2 + \lambda \sum_{r} \gamma(r)^2
+\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - g_{i,j} - \gamma(v_{i,j})\right)^2 + \lambda \sum_{i,j} \gamma(v_{i,j})^2
 (\#eq:YE-penalty)
@@
 \begin{equation}
-\hat{\gamma}(r, \lambda) = \frac{1}{\lambda + n_r} \sum_{i=1}^{n_{r}} \left(Y_{i,j} - \mu - \alpha_i - \beta_j - g_{i,j}\right)
+\hat{\gamma}(v_{i,j}, \lambda) = \frac{1}{\lambda + n_v} \sum_{r=1}^{n_v} \left(Y_{i,j} - \mu - \alpha_i - \beta_j - g_{i,j}\right)
 (\#eq:YE-regularized)

### 2025-05-27 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Started working on new model: model template added.

@@
 
+### Day Effect Analysis
+
+::: {.noteblock data-latex=""}
+The _Year Effect_ visualization and analysis code in this section are cited from the article [Movie Recommendation System using R - BEST](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook) mentioned earlier in this report[@MRS-R-BEST].
+:::
+
+### Mathematical Description of the UMGYDE Model
+\
+
+If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@res(eq:UMGYE-model) describing the _UMGYE Model_, for the current model, takes the form:
+
+\begin{equation}
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(v_{i,j}) + s(d_{i,j}) \varepsilon_{i,j}
+(\#eq:UMGYDE-model)
+\end{equation}
+
+with $s$ a smooth function of $d_{i,j}$
+
+Therefore, the formula \@res(eq:year-effect) for calculation the prediction of a _year effect_ as a residual, for a _smoothed day effect_ 
 $$
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + f(d_{i,j})
+\hat{f} = s(d_{i,j}) + \varepsilon_{i,j}
 $$
 
-$$
- \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
-$$
+takes the following form:
+
+\begin{equation}
+\hat{s(d_{i,j})} = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j} + \gamma(v_{i,j}))
+(\#eq:smoothed-day-effect)
+\end{equation}
 
@@
 
+### UMGYDE Model: Support Functions
+\
+
+::: {.noteblock data-latex=""}
+Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We have already explained that in the [UME Model Regularization] section. 
+For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
+Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
+:::
+
+#### [calc_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) Function {#func.calc_UMGYD_effect}
+\
+
+This is a helper function that calculates the _UMGYD effect_ of the user ratings and is intended to be used in other functions and scripts (for instance in [train_UMGYD_effect](#func.train_UMGYD_effect)) described below.
+
+##### Parameters
+\
+
+The function accepts the only parameter `date_general_effect`, which is a data structure returned by any of the following functions described above:
+
+  - [calc_date_general_effect](#func.calc_date_general_effect);
+  - [calc_date_general_effect.cv](#func.calc_date_general_effect.cv).
+
+##### Source Code
+\
+
+The following is the source code of the function:
+```{r eval=FALSE}
+calc_UMGYD_effect <- function(date_general_effect){
+  date_general_effect |>
+    group_by(year) |>
+    summarise(ye = mean(de, na.rm = TRUE))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) script on _GitHub_.
+:::
+
+##### Return
+
+A data structure containg information about _User+Movie+Genre+Year (UMGYD) Effect_.
+
+#### [train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) Function {#func.train_UMGYD_effect}
+\
+
+This function is used to train the current model using the _Train Set_ dataset passed in the `train_set` parameter.
+The following is the source code of the function:
+```{r eval=FALSE}
+train_UMGYD_effect <- function(train_set, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_UMGYD_effect
+`lambda` is `NA`")
+  }
+
+  train_set |>
+    calc_date_general_effect(lambda) |>
+    calc_UMGYD_effect()
+}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) script on _GitHub_.
+:::
+
+##### Return
+
+A data structure containg information about _User+Movie+Genre+Year (UMGYD) Effect_.
+
+#### [train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L84) Function {#func.train_UMGYD_effect.cv}
+\
+
+This function is used to train the current model using the _5-Fold Cross Validation_.
+The following is the source code of the function:
+```{r eval=FALSE}
+train_UMGYD_effect.cv <- function(lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_UMGYD_effect.cv
+`lambda` is `NA`")
+  }
+
+  calc_date_general_effect.cv(lambda) |> calc_UMGYD_effect()  
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L84) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L84) script on _GitHub_.
+:::
+
+##### Return
+
+A data structure containg information about _User+Movie+Genre+Year (UMGYD) Effect_.
+
+#### [calc_UMGYD_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L92) Function {#func.calc_UMGYD_effect_MSE}
+\
+
+The function calculates the _Mean Squared Error (MSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed in the `test_set` parameter.
+
+##### Parameters
+\
+
+  - **test_set:** A _Test Set_ dataset used for _UMGYDE Model_ validation;
+  - **UMGYD_effect:** A data structure returned by any of the following functions described above:
+    - [calc_UMGYD_effect](#func.train_UMGYD_effect);
+    - [train_UMGYD_effect](#func.train_UMGYD_effect);
+    - [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv).
+
 \newpage
+
+##### Source Code
+\
+
+The source code of the function is provided below:
+```{r eval=FALSE}
+calc_UMGYD_effect_MSE <- function(test_set, UMGYD_effect){
+  test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(UMGYD_effect, by='year') |>
+    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
+    pull(resid) |> mse()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UMGYD_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L92) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L92) script.
+:::
+
+#### [calc_UMGYD_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L102) Function {#func.calc_UMGYD_effect_MSE.cv}
+\
+
+The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGYD Effect_ data passed in the `UMGYD_effect` parameter.
+
+##### Parameters
+\
+
+The function accepts the only parameter: `UMGYD_effect`, which is a data structure returned by the one of the following functions described above:
+
+  - [calc_UMGYD_effect](#func.train_UMGYD_effect);
+  - [train_UMGYD_effect](#func.train_UMGYD_effect);
+  - [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv).
+
+##### Source Code
+\
+
+The source code of the function is provided below:
+```{r eval=FALSE}
+calc_UMGYD_effect_MSE.cv <- function(UMGYD_effect){
+  start <- put_start_date()
+  UMGYD_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
+    cv_fold_dat$validation_set |> calc_UMGYD_effect_MSE(UMGYD_effect)
+  })
+  put_end_date(start)
+  put_log1("Function: calc_UMGYD_effect_MSE.cv
+Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  mean(UMGYD_effect_MSEs)
+}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UMGYD_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L102) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L102) script.
+:::
+
+#### [calc_UMGYD_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L114) Function {#func.calc_UMGYD_effect_RMSE}
+\
+
+The function calculates the _Mean Squared Error (MSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed in the `test_set` parameter.
+
+##### Parameters
+\
+
+  - **test_set:** A _Test Set_ dataset used for _UMGYDE Model_ validation;
+  - **UMGYD_effect:** A data structure returned by any of the following functions described above:
+    - [calc_UMGYD_effect](#func.train_UMGYD_effect);
+    - [train_UMGYD_effect](#func.train_UMGYD_effect);
+    - [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv).
+
+##### Source Code
+\
+
+The source code of the function is provided below:
+```{r eval=FALSE}
+calc_UMGYD_effect_RMSE <- function(test_set, UMGYD_effect){
+  mse <- test_set |> calc_UMGYD_effect_MSE(UMGYD_effect)
+  sqrt(mse)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UMGYD_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L114) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L114) script.
+:::
+
+#### [calc_UMGYD_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L118) Function {#func.calc_UMGYD_effect_RMSE.cv}
+\
+
+The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGYD Effect_ data passed in the `UMGYD_effect` parameter.
+
+##### Parameters
+\
+
+The function accepts the only parameter: `UMGYD_effect`, which is a data structure returned by the one of the following functions described above:
+
+  - [calc_UMGYD_effect](#func.train_UMGYD_effect);
+  - [train_UMGYD_effect](#func.train_UMGYD_effect);
+  - [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv).
+
+##### Source Code
+\
+
+The source code of the function is provided below:
+```{r eval=FALSE}
+calc_UMGYD_effect_RMSE.cv <- function(UMGYD_effect){
+  UMGYD_effect_RMSE <- sqrt(calc_UMGYD_effect_MSE.cv(UMGYD_effect))
+  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
+           CVFolds_N, 
+           UMGYD_effect_RMSE)
+
+  UMGYD_effect_RMSE
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the function [calc_UMGYD_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L118) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L118) script.
+:::
+
+\newpage
+
+### UMGYDE Model Building
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of building and training the current model is available in the [UMGYDE Model Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1432) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1432) script on _GitHub_.
+:::
+
+Below, we provide the most significant line of the code for training our model using the `5-Fold Cross Validation` method:
+```{r, eval=FALSE}
+```
+```{r}
+```
+
+::: {.noteblock data-latex=""}
+We use the [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv) function described above to compute the _UMGYD Effect_.
+:::
+
+We can now construct predictors and calculate the _RMSE_ of the current model using the [calc_UMGYD_effect_RMSE.cv](#func.calc_UMGYD_effect_RMSE.cv) function described above:
+
+```{r, eval=FALSE}
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.UMGYDE)
+```
+
+::: {.noteblock data-latex=""}
+Now, we have a bit better result than one for the previous model.
+:::
+
+\newpage
+
+### UMGYDE Model Regularization
+\
+
+We have already explained the idea of _Linear Model Regularization_ in the [UME Model Regularization] section above.
+We have also seen how the formula \@res(eq:ME-penalty) for adding a penalty to the _UME Model_ is transformed into the formula \@res(eq:GE-penalty) for the _UMGE Model_ and then into the formula \@res(eq:GYE-penalty) for the _UMGYE Model_.
+For the current model, this formula takes the form:
+
+\begin{equation}
+\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - g_{i,j} - \gamma(v_{i,j}) - s(d_{i,j})\right)^2 + \lambda \sum_{i,j} s(d_{i,j})^2
+(\#eq:DE-penalty)
+\end{equation}
+
+And the formula \@res(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
+
+\begin{equation}
+\hat{s}(d_{i,j}, \lambda) = \frac{1}{\lambda + n_d} \sum_{r=1}^{n_{d}} \left(Y_{i,j} - \mu - \alpha_i - \beta_j - g_{i,j} - \gamma(v_{i,j})\right)
+(\#eq:DE-regularized)
+\end{equation}
+
+where $n_d$ is the number of ratings made on the day $d$.
+
+As with the previous models, we implement the _Regularization_ method for the current model in the following three steps:
+
+  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
+
+  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
+
+  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.
+
+\newpage
+
+#### UMGYDE Model Regularization: Support Functions
+\
+
+::: {.noteblock data-latex=""}
+The [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L128) function described below are defined in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L127) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L128) script.
+:::
+
+##### [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#128) Function {#func.regularize.test_lambda.UMGYD_effect.cv}
+\
+
+This function calculates _RMSE_ of the _UMGYDE Model_ using _5-Fold Cross Validation_ for the given $\lambda$ parameter value:
+```{r, eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+Note that we reuse the function [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv) calling it from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
+:::
+
+\newpage
+
+#### UMGYDE Model Regularization: Pre-configuration
+\
+
+Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
+
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
+
+Below we provide the most significant part of the code that performs this operation:
+```{r, eval=FALSE}
+```
+```{r}
+str(cv.UMGYDE.preset.result)
+cv.UMGYDE.preset.result$best_result
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [UMGYDE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) script on _GitHub_.
+:::
+
+Now, let's visualize the results of the $\lambda$ range preconfiguration:
+``` {r}
+cv.UMGYDE.preset.result$tuned.result |>
+  data.plot(title = TeX(r'[UMGYDE Model Regularization: $\lambda$ Range Pre-configuration]'),
+              xname = "parameter.value", 
+              yname = "RMSE", 
+              xlabel = TeX(r'[$\lambda$]'), 
+              ylabel = "RMSE")
+```
+
+::: {.noteblock data-latex=""}
+We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+:::
+
+\newpage
+
+#### UMGYDE Model Regularization: Fine-tuning
+\
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+:::
+
+We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
+
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+
+Below we provide the most significant part of the code that performs this operation:
+```{r, eval=FALSE}
+```
+```{r}
+str(UMGYDE.rglr.fine_tune.results)
+UMGYDE.rglr.fine_tune.results$best_result
+```
+
+::: {.noteblock data-latex=""}
+Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
+:::
+
+\newpage
+
+Let's visualize the fine-tuning results:
+```{r}
+UMGYDE.rglr.fine_tune.results$tuned.result |>
+  data.plot(title = "UMGYDE Model Regularization: Fine-tuned result",
+              xname = "parameter.value",
+              yname = "RMSE",
+              xlabel = TeX(r'[$\lambda$]'),
+              ylabel = str_glue("Deviation from the best RMSE value (",
+                                as.character(round(UMGYDE.rglr.fine_tune.RMSE.best, digits = 7)),
+                                ")"),
+              normalize = TRUE)
+```
+
+::: {.noteblock data-latex=""}
+We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+:::
+
+\newpage
+
+#### UMGYDE Model Regularization: Retraining Model with the best $\lambda$
+\
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section are available in the [Re-train Regularized UMGYDE Model for the best `lambda`](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1589) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1589) script on _GitHub_.
+:::
+
+Now, we can calculate the _Regularized UMGYDE Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
+
+```{r, eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+Here we use the helper function [train_UMGYD_effect](#func.train_UMGYD_effect) described above in the [UMGYDE Model Regularization: Support Functions] section.
+:::
+
+We calculate the _Root Mean Squared Error_ for the ultimately computed _UMGYDE Effect_ using the helper function [calc_UMGYD_effect_RMSE.cv](#func.calc_UMGYD_effect_RMSE.cv) described above in the [UMGYDE Model Regularization: Support Functions] section as follows:
+```{r, eval=FALSE}
+```
+
+Finally, we add the definitive result for the current model to our _Result Table_:
+```{r, eval=FALSE}
+```
+```{r}
+```
+
+\newpage

### 2025-05-27 reports/templates/02.8.UMGYDE-model-template.Rmd
Started working on new model: model template added.

--- 2025-05-27 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
@@
 
-If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@res(eq:UMGYE-model) describing the _UMGYE Model_, for the current model, takes the form:
+If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@ref(eq:UMGYE-model) describing the _UMGYE Model_, for the current model, takes the form:
 
 \begin{equation}
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(v_{i,j}) + s(d_{i,j}) \varepsilon_{i,j}
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(r_{i,j}) + f(d_{i,j}) \varepsilon_{i,j}
 (\#eq:UMGYDE-model)
@@
 
-with $s$ a smooth function of $d_{i,j}$
+with $f$ a smooth function of $d_{i,j}$
 
-Therefore, the formula \@res(eq:year-effect) for calculation the prediction of a _year effect_ as a residual, for a _smoothed day effect_ 
+Therefore, the formula \@ref(eq:year-effect) for calculation the prediction of a _year effect_ as a residual, for a _smoothed day effect_ 
 $$
-\hat{f} = s(d_{i,j}) + \varepsilon_{i,j}
+\hat{f} = f(d_{i,j}) + \varepsilon_{i,j}
 $$
@@
 \begin{equation}
-\hat{s(d_{i,j})} = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j} + \gamma(v_{i,j}))
+\hat{f(d_{i,j})} = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j} + \gamma(r_{i,j}))
 (\#eq:smoothed-day-effect)
@@
 :::
+
+#### [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) Function {#func.calc_date_general_effect}
+\
+
+This is a helper function that calculates the _date general effect_ of the user ratings and is intended to be used in other functions and scripts (for instance in [train_UMGYD_effect](#func.train_UMGYD_effect)) described below.
+
+The following is a slightly simplified version of the function's source code:
+```{r eval=FALSE}
+calc_date_general_effect <- function(train_set, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: calc_date_general_effect
+`lambda` is `NA`")
+  }
+
+  if(lambda == 0) put_log("Function `calc_date_general_effect`:
+Computing Date Global Effect for given Train Set data...")
+  else put_log1("Function `calc_date_general_effect`:
+Computing Date Global Effect for lambda: %1...",
+                lambda)
+  dg_effect <- train_set |> 
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    mutate(resid = rating - (mu + a + b + g)) |>
+  group_by(days) |>
+    summarise(de = mean_reg(resid, lambda), 
+              year = mean(year))
+  dg_effect
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) function is available in the [UMGYDE Model Support Functions](#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) script on _GitHub_.
+:::
+
+##### Return
+
+A data structure containg information about _Date General Effect_.
+
+#### [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L30) Function {#func.calc_date_general_effect.cv}
+\
+
+This is a helper function that calculates the _date general effect_ of the user ratings using the _5-Fold Cross Validation_ method and is intended to be used in other functions and scripts (for instance in [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv)) described below.
+
+##### Souurce Code
+\
+
+::: {.noteblock data-latex=""}
+The complete version of the source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L30) function is available in the [UMGYDE Model Support Functions](#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L30) script on _GitHub_.
+:::
+
+The following is a simplified version of the function's source code:
+```{r eval=FALSE}
+calc_date_general_effect.cv <- function(lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: calc_date_general_effect.cv
+`lambda` is `NA`")
+  }
+
+  date_general_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
+    cv_fold_dat$train_set |> calc_date_general_effect(lambda)
+  })
+  str(date_general_effect_ls)
+
+  date_general_effect_united <- union_cv_results(date_general_effect_ls)
+
+  date_general_effect_united |>
+    group_by(days) |>
+    summarise(de = mean(de, na.rm = TRUE), year = mean(year, na.rm = TRUE))
+}
+```
+
+::: {.noteblock data-latex=""}
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
+:::
+
+##### Return
+
+A data structure containg information about _Date General Effect_ as result of _5-Fold Cross Validation_.
+
+\newpage
 
@@
 ```{r, eval=FALSE}
+  cv.UMGYD_effect <- train_UMGYD_effect.cv()
 ```
 ```{r}
+str(cv.UMGYD_effect)
+summary(cv.UMGYD_effect)
 ```
@@
 ```{r, eval=FALSE}
+cv.UMGYD_effect.RMSE <- calc_UMGYD_effect_RMSE.cv(cv.UMGYD_effect)
+
+RMSEs.ResultTibble.UMGYDE <- RMSEs.ResultTibble.rglr.UMGYE |> 
+  RMSEs.AddRow("UMGYDE Model", 
+               cv.UMGYD_effect.RMSE,
+               comment = "User+Movie+Genre+Year+Day Effect (UMGYDE) Model")
 ```
@@
 We have already explained the idea of _Linear Model Regularization_ in the [UME Model Regularization] section above.
-We have also seen how the formula \@res(eq:ME-penalty) for adding a penalty to the _UME Model_ is transformed into the formula \@res(eq:GE-penalty) for the _UMGE Model_ and then into the formula \@res(eq:GYE-penalty) for the _UMGYE Model_.
+We have also seen how the formula \@ref(eq:ME-penalty) for adding a penalty to the _UME Model_ is transformed into the formula \@ref(eq:GE-penalty) for the _UMGE Model_ and then into the formula \@ref(eq:GYE-penalty) for the _UMGYE Model_.
 For the current model, this formula takes the form:
@@
 \begin{equation}
-\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - g_{i,j} - \gamma(v_{i,j}) - s(d_{i,j})\right)^2 + \lambda \sum_{i,j} s(d_{i,j})^2
+\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - g_{i,j} - \gamma(r_{i,j}) - f(d_{i,j})\right)^2 + \lambda \sum_{i,j} f(d_{i,j})^2
 (\#eq:DE-penalty)
@@
 
-And the formula \@res(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
+And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
 
 \begin{equation}
-\hat{s}(d_{i,j}, \lambda) = \frac{1}{\lambda + n_d} \sum_{r=1}^{n_{d}} \left(Y_{i,j} - \mu - \alpha_i - \beta_j - g_{i,j} - \gamma(v_{i,j})\right)
+\hat{\gamma}(r, \lambda) = \frac{1}{\lambda + n_d} \sum_{i=1}^{n_{d}} \left(Y_{i,j} - \mu - \alpha_i - \beta_j - g_{i,j} - \gamma(r)\right)
 (\#eq:DE-regularized)
@@
 ```{r, eval=FALSE}
+regularize.test_lambda.UMGYD_effect.cv <- function(lambda){
+  if (is.na(lambda)) {
+    stop("Function: regularize.test_lambda.UMGYD_effect.cv
+`lambda` is `NA`")
+  }
+
+  train_UMGYD_effect.cv(lambda) |>
+    calc_UMGYD_effect_RMSE.cv()
+}
 ```
@@
 ```{r, eval=FALSE}
+  lambdas <- seq(0, 512, 32)
+  cv.UMGYDE.preset.result <- 
+    tune.model_param(lambdas, 
+                     regularize.test_lambda.UMGYD_effect.cv,
+                     steps.beyond_min = 16)
 ```
@@
 ```{r, eval=FALSE}
+endpoints <- 
+  get_fine_tune.param.endpoints(cv.UMGYDE.preset.result$tuned.result)
+
+UMGYDE.loop_starter <- c(endpoints["start"], 
+                        endpoints["end"], 
+                        8)
+UMGYDE.loop_starter
+#> [1]
+
+cache.base_name <- "UMGYDE.rglr.fine-tuning"
+
+UMGYDE.rglr.fine_tune.results <- 
+  model.tune.param_range(UMGYDE.loop_starter,
+                         UMGYDE.rglr.fine_tune.cache.path,
+                         cache.base_name,
+                         regularize.test_lambda.UMGYD_effect.cv)
 ```
@@
 ```{r, eval=FALSE}
+  rglr.UMGYD_effect <- edx |> train_UMGYD_effect(UMGYDE.rglr.best_lambda)
 
@@
 ```{r, eval=FALSE}
+  rglr.UMGYD_effect.RMSE <- calc_UMGYD_effect_RMSE.cv(rglr.UMGYD_effect)
 ```
@@
 ```{r, eval=FALSE}
+RMSEs.ResultTibble.rglr.UMGYDE <- RMSEs.ResultTibble.UMGYDE |> 
+  RMSEs.AddRow("Regularized UMGYDE Model", 
+               rglr.UMGYD_effect.RMSE,
+               comment = "Computed for `lambda` = %1" |>
+                 msg.glue(UMGYDE.rglr.best_lambda))
+
 ```
 ```{r}
+RMSE_kable(RMSEs.ResultTibble.rglr.UMGYDE)
 ```

### 2025-05-27 r/src/capstone-movielens.main.R

@@ -1648,7 +1648,7 @@ log_close()
 ### Accounting for User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect (UMGYDE) ----
 # Y[i,j] = μ + α[i] + β[j] + g[i,j] yr[i,j]  + f(d[i,j]) + ε[i,j]
 
-# with `f` a smooth function of `d[(i,j]`
+# with `f` a smooth function of `d[i,j]`
 ### Support Functions --------------------------------------------------------
 cv.UMGYDE.default_params.functions_file <- "UMGYD-effect.functions.R"
 cv.UMGYDE.default_params.functions.file_path <- file.path(support_functions.path, 

### 2025-05-27 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
The model mathematical description completed.

@@
 
-If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@res(eq:UMGYE-model) describing the _UMGYE Model_, for the current model, takes the form:
+If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@ref(eq:UMGYE-model) describing the _UMGYE Model_, for the current model, takes the form:
 
 \begin{equation}
-Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(v_{i,j}) + s(d_{i,j}) \varepsilon_{i,j}
+Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(v_{i,j}) + s(d_{i,j}) + \varepsilon_{i,j}
 (\#eq:UMGYDE-model)
@@
 
-with $s$ a smooth function of $d_{i,j}$
+with $s$ a _smoothed day_ function of $d_{i,j}$
 
-Therefore, the formula \@res(eq:year-effect) for calculation the prediction of a _year effect_ as a residual, for a _smoothed day effect_ 
+Therefore, the formula \@ref(eq:year-effect) for calculation the prediction of a _year effect_ as a residual, for a _smoothed day effect_ 
 $$
-\hat{f} = s(d_{i,j}) + \varepsilon_{i,j}
+\hat{s}(d_{i,j}) = s(d_{i,j}) + \varepsilon_{i,j}
 $$
@@
 \begin{equation}
-\hat{s(d_{i,j})} = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j} + \gamma(v_{i,j}))
+\hat{s}(d_{i,j}) = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j} + \gamma(v_{i,j}))
 (\#eq:smoothed-day-effect)
@@
 
-And the formula \@res(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
+And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
 

### 2025-05-27 r/src/capstone-movielens.main.R
Main R script: code restructured.

@@ -1645,7 +1645,7 @@ for the `Regularized User+Movie+Genre+Year Effect Model`.")
 ### Close Log -----------------------------------------------------------------
 log_close()
 
-### Accounting for User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect (UMGYDE) ----
+## User+Movie+Genre+Year+Day Effect (UMGYDE) Model -----------------------------
 # Y[i,j] = μ + α[i] + β[j] + g[i,j] yr[i,j]  + f(d[i,j]) + ε[i,j]
 
 # with `f` a smooth function of `d[i,j]`
@@ -1661,9 +1661,9 @@ source(cv.UMGYDE.default_params.functions.file_path,
        verbose = TRUE,
        keep.source = TRUE)
 
-### Open log file for training the UMGYDE model using `loess` function with default parameters ----
+### Open log for training with default parameters ------------------------------
 open_logfile(".UMGYDE.loess.default-params")
-##### Model Tuning Data File Paths --------------------------------------------
+### Model Tuning Data File Paths -----------------------------------------------
 UMGYDE.tuning_folder <- "UMGYD-effect"
 
 UMGYDE.tuning.data.path <- 
@@ -1742,7 +1742,7 @@ the `User+Movie+Genre+Year+(Smoothed)Day Effect Model` data
 using `loess` function with parameter `degree = 2`: %1", 
 UMGYDE.fine_tune.degree2.data.path)
 
-### Train model using `loess` function with default `span` & `degree` params----
+### Training with default parameters -------------------------------------------
 file_name_tmp <- "9.cv.UMGYDE.loess.default-params.RData"
 file_path_tmp <- file.path(data.models.path, file_name_tmp)
 
@@ -1785,10 +1785,7 @@ CVFolds_N)
 
 put(str(cv.UMGYDE.default_params))
 
-### User+Movie+Genre+Year+Day-Smoothed Effect Model Visualization -------------
-# mean_day_smoothed_effect <- compute_mean_dse(day_smoothed_effect_ls)
-# str(mean_day_smoothed_effect)
-
+#### UMGYD Effect Visualization ------------------------------------------------
 cv.UMGYDE.default_params |>
   ggplot(aes(x = days)) +
   geom_point(aes(y = de), size = 3, alpha = .5, color = "grey") + 
[…]

### 2025-05-28 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
The model mathematical description completed.
fix for UMGYE Model; dev: function described: calc_day_general_effect, calc_day_general_effect described.

@@
 
-This is a helper function that calculates the _date general effect_ of the user ratings and is intended to be used in other functions and scripts (for instance in [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+This is a helper function that calculates the _date general effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
 
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) function is available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) script on _GitHub_.
+The complete version of the source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) function is available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) script on _GitHub_.
 :::
@@
 
-A data structure containg information about _Date General Effect_.
+A data structure containing information about _Date General Effect_.
 
@@
 
-This is a helper function that calculates the _date general effect_ of the user ratings using the _5-Fold Cross Validation_ method and is intended to be used in other functions and scripts (for instance in [train_UMGY_effect.cv](#func.train_UMGY_effect.cv)) described below.
+This is a helper function that calculates the _date general effect_ of the user ratings using the _5-Fold Cross Validation_ method and is intended to be used in other functions and scripts (such as [train_UMGY_effect.cv](#func.train_UMGY_effect.cv)) described below.
 
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) function is available in the [UMGYE Model Support Functions](#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) script on _GitHub_.
+The complete version of the source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) function is available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
 :::
@@
 
-A data structure containg information about _Date General Effect_ as result of _5-Fold Cross Validation_.
+A data structure containing information about _Date General Effect_ as result of _5-Fold Cross Validation_.
 
@@
 
-This is a helper function that calculates the _UMGY effect_ of the user ratings and is intended to be used in other functions and scripts (for instance in [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+This is a helper function that calculates the _UMGY effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
 
@@
 
-A data structure containg information about _User+Movie+Genre+Year (UMGY) Effect_.
+A data structure containing information about _User+Movie+Genre+Year (UMGY) Effect_.
 
@@
 
-where $n_r$ is the number of ratings made in year $r$.
+where $n_v$ is the number of ratings made in year $v$.
 

### 2025-05-28 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
fix for UMGYE Model; dev: function described: calc_day_general_effect, calc_day_general_effect described.

@@
 \
-
-### Day Effect Analysis
-
-::: {.noteblock data-latex=""}
-The _Year Effect_ visualization and analysis code in this section are cited from the article [Movie Recommendation System using R - BEST](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook) mentioned earlier in this report[@MRS-R-BEST].
-:::
 
@@
 
-If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@ref(eq:UMGYE-model) describing the _UMGYE Model_, for the current model, takes the form:
+If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@ref(eq:UMGYDE-model) describing the _UMGYDE Model_, for the current model, takes the form:
 
@@
 
+#### [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) Function {#func.calc_day_general_effect}
+\
+
+This is a helper function that calculates the _day general effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
+
+The following is a simplified version of the function's source code:
+```{r eval=FALSE}
+calc_day_general_effect <- function(train_set, lambda = 0){
+  train_set |> 
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(rglr.UMGY_effect, by='year') |>
+    mutate(resid = rating - (mu + a + b + g + ye)) |>
+    group_by(days) |>
+    summarise(de = mean_reg(resid, lambda), 
+              year = mean(year))
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code of the [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) function is available in the [UMGYDE Model Support Functions]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) script on _GitHub_.
+:::
+
+##### Return
+
+A data structure containing information about _Day General Effect_.
+
+#### [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L31) Function {#func.calc_day_general_effect.cv}
+\
+
+This is a helper function that calculates the _day general effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset using the _5-Fold Cross Validation_ and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.
+
+##### Souurce Code
+\
+
+::: {.noteblock data-latex=""}
+The complete version of the source code of the [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L31) function is available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L30) script on _GitHub_.
+:::
+
+The following is a simplified version of the function's source code:
+```{r eval=FALSE}
+calc_day_general_effect.cv <- function(lambda = 0){
+  gday_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
+    cv_fold_dat$train_set |> calc_day_general_effect(lambda)
+  })
+
+  gday_effect_united <- union_cv_results(gday_effect_ls)
+
+  gday_effect_united |>
+    group_by(days) |>
+    summarise(de = mean(de), year = mean(year))
+}
+```
+
+::: {.noteblock data-latex=""}
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
+:::
+
+##### Return
+
+A data structure containing information about _Date General Effect_ as result of _5-Fold Cross Validation_.
+
+\newpage
+
 #### [calc_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) Function {#func.calc_UMGYD_effect}
@@
 
-This is a helper function that calculates the _UMGYD effect_ of the user ratings and is intended to be used in other functions and scripts (for instance in [train_UMGYD_effect](#func.train_UMGYD_effect)) described below.
+This is a helper function that calculates the _UMGYD effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGYD_effect](#func.train_UMGYD_effect)) described below.
 
@@
 
-  - [calc_date_general_effect](#func.calc_date_general_effect);
-  - [calc_date_general_effect.cv](#func.calc_date_general_effect.cv).
+  - [calc_day_general_effect](#func.calc_day_general_effect);
+  - [calc_day_general_effect.cv](#func.calc_day_general_effect.cv).
 
@@
 
-A data structure containg information about _User+Movie+Genre+Year (UMGYD) Effect_.
+A data structure containing information about _User+Movie+Genre+Year (UMGYD) Effect_.
 
@@
   train_set |>
-    calc_date_general_effect(lambda) |>
+    calc_day_general_effect(lambda) |>
     calc_UMGYD_effect()
@@
 
-  calc_date_general_effect.cv(lambda) |> calc_UMGYD_effect()  
+  calc_day_general_effect.cv(lambda) |> calc_UMGYD_effect()  
 }
@@
 We have already explained the idea of _Linear Model Regularization_ in the [UME Model Regularization] section above.
-We have also seen how the formula \@ref(eq:ME-penalty) for adding a penalty to the _UME Model_ is transformed into the formula \@ref(eq:GE-penalty) for the _UMGE Model_ and then into the formula \@ref(eq:GYE-penalty) for the _UMGYE Model_.
+We have also seen how the formula \@ref(eq:ME-penalty) for adding a penalty to the _UME Model_ is transformed into the formula \@ref(eq:GE-penalty) for the _UMGE Model_ and then into the formula \@ref(eq:GYE-penalty) for the _UMGYDE Model_.
 For the current model, this formula takes the form:

### 2025-05-28 r/src/support-functions/UMGYD-effect.functions.R

@@ -1,4 +1,4 @@
-# Support Functions --------------------------------------------------------
+# UMGYDE Model Support Functions -----------------------------------------------
 calc_day_general_effect <- function(train_set, lambda = 0){
   if (is.na(lambda)) {
     stop("Function:calc_day_general_effect 
@@ -17,7 +17,6 @@ Computing Day General Effect for lambda: %1...",
     left_join(date_days_map, by = "timestamp") |>
     left_join(rglr.UMGY_effect, by='year') |>
     mutate(resid = rating - (mu + a + b + g + ye)) |>
-    # filter(!is.na(resid)) |>
     group_by(days) |>
     summarise(de = mean_reg(resid, lambda), 
               year = mean(year))
@@ -46,20 +45,16 @@ Computing Day General Effect list for %1-Fold Cross Validation samples...",
            CVFolds_N)
   start <- put_start_date()
   gday_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
-    # start <- put_start_date()
     cv_fold_dat$train_set |> calc_day_general_effect(lambda)
   })
-  str(gday_effect_ls)
   put_end_date(start)
   put_log1("Function `calc_day_general_effect.cv`:
 Day General Effect list has been computed for %1-Fold Cross Validation samples.", 
            CVFolds_N)
   
   gday_effect_united <- union_cv_results(gday_effect_ls)
-  str(gday_effect_united)
-  
+
   gday_effect <- gday_effect_united |>
-    #filter(!is.na(de)) |>
     group_by(days) |>
     summarise(de = mean(de), year = mean(year))
   
@@ -141,7 +136,6 @@ UMGY_SmoothedDay_effect.predict <- function(test_set, day_smoothed_effect) {
                                ifelse(is.na(de_smoothed), 
                                       0, 
                                       de_smoothed))) |> 
-    # filter(!is.na(predicted)) |>
     select(userId, movieId, timestamp, rating, predicted)
 }
 
@@ -156,7 +150,6 @@ calc_UMGY_SmoothedDay_effect.MSE <- function(test_set, day_smoothed_effect) {
     # left_join(rglr.UMGY_effect, by='year') |>
     # left_join(day_smoothed_effect, by='days') |>
     mutate(resid = rating - predicted) |> 
-    # filter(!is.na(resid)) |>
     pull(resid) |> mse()
 }
 calc_UMGY_SmoothedDay_effect.MSE.cv <- function(day_smoothed_effect){

### 2025-05-28 r/src/capstone-movielens.main.R
.pdf report updated; fix for global environment.

@@ -2302,18 +2302,6 @@ put_log("A row has been added to the RMSE Result Tibble
 for the tuned `User+Movie+Genre+Year+(Smoothed)Day Effect Model`
 using `loess` function call with the best degree & span values.")
 
-# start <- put_start_date()
-# final_holdout_test |>
-#   left_join(date_days_map, by = "timestamp") |>
-#   left_join(edx.user_effect, by = "userId") |>
-#   left_join(mean_user_movie_genre_bias, by = "movieId") |>
-#   left_join(# cv.UMGYDE.default_params, by='days') |>
-#   mutate(resid = rating - clamp(mu + a + b + g + de_smoothed)) |>
-#   filter(!is.na(resid)) |>
-#   pull(resid) |> final_rmse()
-# put_end_date(start)
-#> [1] 0.8724055
-
 #### Close Log -----------------------------------------------------------------
 log_close()
 ### UMGDYE Model Regularization ------------------------------------------------

### 2025-05-28 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
loess function draft description.

@@
 
+#### [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) Function {#func.loess_de}
+\
+
+This is a helper function that calculates the _Smoothed Day Effect_ of user ratings and is intended to be used in other functions and scripts (such as [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)) described below.
+
+##### Parameters
+\
+
+###### ***de_bias.dat***
+\
+The _day general effect_ data, which is a data structure returned by any of the following functions described above:
+
+  - [calc_day_general_effect](#func.calc_day_general_effect);
+  - [calc_day_general_effect.cv](#func.calc_day_general_effect.cv).
+
+###### ***degree***
+\
+
+###### ***span***
+\
+
+##### Details
+\
+
+The function is a wrapper to the [stats::loess] and calls it under the hood.
+
+##### Source Code
+\
+
+The following is the source code of the function:
+```{r eval=FALSE}
+loess_de <- function(de_bias.dat, degree = NA, span = NA){
+  if(is.na(degree)) degree = 2
+  if(is.na(span)) span = 0.75
+  loess(de ~ days, span = span, degree = degree, data = de_bias.dat)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) script on _GitHub_.
+:::
+
+##### Return
+
+A data structure containing information about _User+Movie+Genre+Year (UMGYD) Effect_.
+
 #### [calc_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) Function {#func.calc_UMGYD_effect}
@@
 
-This is a helper function that calculates the _UMGYD effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGYD_effect](#func.train_UMGYD_effect)) described below.
+This is a helper function that calculates the _UMGYD Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGYD_effect](#func.train_UMGYD_effect)) described below.
 
@@
 ```{r eval=FALSE}
-calc_UMGYD_effect <- function(date_general_effect){
-  date_general_effect |>
-    group_by(year) |>
-    summarise(ye = mean(de, na.rm = TRUE))
-}
+
 ```
@@
 ```{r eval=FALSE}
-train_UMGYD_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_UMGYD_effect
-`lambda` is `NA`")
-  }
-
-  train_set |>
-    calc_day_general_effect(lambda) |>
-    calc_UMGYD_effect()
-}
 

### 2025-05-28 r/src/support-functions/UMGYD-effect.functions.R

@@ -67,7 +67,7 @@ Training completed: Day General Effects model for lambda: %1...",
   gday_effect
 }
 loess_de <- function(de_bias.dat, degree = NA, span = NA){
-  if(is.na(degree)) degree = 2
+  if(is.na(degree)) degree = 1
   if(is.na(span)) span = 0.75
   loess(de ~ days, span = span, degree = degree, data = de_bias.dat)
 }

### 2025-05-29 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
The helper functions described in the `UMGYDE Model Support Functions` section of the `UMGYD-effect.functions.R` script.

@@
 \
-
 ### Mathematical Description of the UMGYDE Model
@@
 
-::: {.noteblock data-latex=""}
+::: {#sec.umgydem.support_functions.note.lambda .noteblock data-latex=""}
 Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
@@
 We have already explained that in the [UME Model Regularization] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
+For now, we omit the `lambda` parameter, implicitly using its default value `lambda = 0`.
 Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
@@
 
-This is a helper function that calculates the _day general effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
+This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
+
+##### Parameters
+\
+
+###### ***train_set***
+\
+The _Train Set_ dataset.
+
+###### ***lambda***
+\
+As explained [above](#sec.umgydem.support_functions.note.lambda) in this section, this parameter is used for the _Regularization_ techniques.
+Otherwise, it is omitted, meaning its default (zero) value is used.
+
+##### Source Code
+\
 
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code of the [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) function is available in the [UMGYDE Model Support Functions]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) script on _GitHub_.
+The complete version of the source code of the [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) function is available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) script on _GitHub_.
 :::
@@
 ##### Return
+\
+A data frame object representing the _Day General Effect_.
 
-A data structure containing information about _Day General Effect_.
+\newpage
 
@@
 
-This is a helper function that calculates the _day general effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset using the _5-Fold Cross Validation_ and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.
+This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset using the _5-Fold Cross Validation_ and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.
+
+##### Parameters
+\
+
+###### ***lambda***
+\
+As explained [above](#sec.umgydem.support_functions.note.lambda) in this section, this parameter is used for the _Regularization_ techniques.
+Otherwise, it is omitted, meaning its default (zero) value is used.
 
@@
 ##### Return
-
-A data structure containing information about _Date General Effect_ as result of _5-Fold Cross Validation_.
+\
+A data frame object representing the _Day General Effect_.
 
@@
 \
-The _day general effect_ data, which is a data structure returned by any of the following functions described above:
+A data frame object representing the _Day General Effect_. It can be returned by the following functions described above:
 
@@
 \
+A parameter to pass to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function (see the [Details](#func.loess_de.details) section below), meaning the degree of the polynomials to be used.
 
@@
 \
+A parameter to pass to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function (see the [Details](#func.loess_de.details) section below) to control the degree of smoothing.
 
+::: { #func.loess_de.details .sidebar }
 ##### Details
 \
-
-The function is a wrapper to the [stats::loess] and calls it under the hood.
+The function is a wrapper for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) and calls it under the hood.
+:::
 
@@
 ##### Return
+\
+An object of class `loess` returned by the internally called function [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) (see the [Details](#func.loess_de.details) section above).
 
-A data structure containing information about _User+Movie+Genre+Year (UMGYD) Effect_.
+\newpage
 
-#### [calc_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) Function {#func.calc_UMGYD_effect}
+#### [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) Function {#func.calc_UMGY_SmoothedDay_effect}
 \
 
-This is a helper function that calculates the _UMGYD Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGYD_effect](#func.train_UMGYD_effect)) described below.
+This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
 
@@
 
-The function accepts the only parameter `date_general_effect`, which is a data structure returned by any of the following functions described above:
+::: { #func.calc_UMGY_SmoothedDay_effect.params.day_gen_effect .sidebar }
+###### ***day_gen_effect***
+\
+A data frame object representing the _Day General Effect_. It can be returned by the following functions described above:
 
@@
   - [calc_day_general_effect.cv](#func.calc_day_general_effect.cv).
+:::
+
+###### ***degree***
+\
+A parameter to pass to the internally called [loess_de](#func.loess_de) function (see the [Details](#func.calc_UMGY_SmoothedDay_effect.details) section below), meaning the degree of the polynomials to be used.
+
+###### ***span***
+\
+A parameter to pass to the internally called [loess_de](#func.loess_de) function (see the [Details](#func.calc_UMGY_SmoothedDay_effect.details) section below) to control the degree of smoothing.
+
+::: { #func.calc_UMGY_SmoothedDay_effect.details .sidebar }
+##### Details
+\
+Under the hood, the function internally calls the [loess_de](#func.loess_de) described above and constructs the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ data object based on the object of class `loess` it returns along with the data passed by the [day_gen_effect](#func.calc_UMGY_SmoothedDay_effect.params.day_gen_effect) parameter.
+:::
 
@@
 ```{r eval=FALSE}
+calc_UMGY_SmoothedDay_effect <- function(day_gen_effect, 
+                                         degree = NA, 
+                                         span = NA){
+  put_log2("Function `calc_UMGY_SmoothedDay_effect`: 
+Training model using `loess` function with the following parameters:
+degree: %1;
+span: %2
+...",
+           degree,
+           span)
+  # browser()
+  fit <- day_gen_effect |> loess_de(degree, span)
+  smth_day_effect <- day_gen_effect |> mutate(de_smoothed = fit$fitted)
+
+  put_log2("Function `calc_UMGY_SmoothedDay_effect`: 
+Model has been trained using `loess` function with the following parameters:
+degree: %1;
+span: %2.",
+           degree,
+           span)
+
+  smth_day_effect
+}
 
@@
 ::: {.noteblock data-latex=""}
-The source code of the [calc_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) script on _GitHub_.
+The source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) script on _GitHub_.
 :::
@@
 ##### Return
+\
+A data frame object representing the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_.
 
-A data structure containing information about _User+Movie+Genre+Year (UMGYD) Effect_.
+\newpage
 
-#### [train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) Function {#func.train_UMGYD_effect}
+#### [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) Function {#func.train_UMGY_SmoothedDay_effect}
 \
 
-This function is used to train the current model using the _Train Set_ dataset passed in the `train_set` parameter.
+This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
+
+##### Parameters
+\
+
+###### ***train_set***
+\
+The _Train Set_ dataset.
+
+###### ***degree***
+\
+A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.details) section below), meaning the degree of the polynomials to be used.
+
+###### ***span***
+\
+A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.details) section below) to control the degree of smoothing.
+
+###### ***lambda***
+\
+As explained [above](#sec.umgydem.support_functions.note.lambda) in this section, this parameter is used for the _Regularization_ techniques.
+Otherwise, it is omitted, meaning its default (zero) value is used.
+
+::: { #func.train_UMGY_SmoothedDay_effect.details .sidebar }
+##### Details
+\
+Under the hood, the function internally calls the [calc_day_general_effect](#func.calc_day_general_effect) and then [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above, and returns the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ data object that the latter inner function returns.
+:::
+
+##### Source Code
+\
+
 The following is the source code of the function:
 ```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect <- function(train_set, 
+                                          degree = NA, 
+                                          span = NA,
+                                          lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_UMGY_SmoothedDay_effect
+`lambda` is `NA`")
+  }
+
+  train_set |> 
+    calc_day_general_effect(lambda) |>
+    train_UMGY_SmoothedDay_effect(degree, span)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) script on _GitHub_.
+:::
+
+##### Return
+\
+A data frame object representing the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_.
+
+\newpage
+
+#### [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L111) Function {#func.train_UMGY_SmoothedDay_effect.cv}
+\
+
+This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.
+
+##### Parameters
+\
+
+###### ***degree***
+\
+A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.cv.details) section below), meaning the degree of the polynomials to be used.
+
+###### ***span***
+\
+A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.cv.details) section below) to control the degree of smoothing.
+
+###### ***lambda***
+\
+As explained [above](#sec.umgydem.support_functions.note.lambda) in this section, this parameter is used for the _Regularization_ techniques.
+Otherwise, it is omitted, meaning its default (zero) value is used.
+
+::: { #func.train_UMGY_SmoothedDay_effect.cv.details .sidebar }
+##### Details
+\
+Under the hood, the function internally calls the [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and then [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above, and returns the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ data object that the latter inner function returns.
+:::
+
+##### Source Code
+\
+
+The following is the source code of the function:
+```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect.cv <- function(degree = NA, 
+                                             span = NA,
+                                             lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_UMGY_SmoothedDay_effect.cv
+`lambda` is `NA`")
+  }
+
+  calc_day_general_effect.cv.cv(lambda) |>
+    calc_UMGY_SmoothedDay_effect(degree, span)
+}
 
@@
 ::: {.noteblock data-latex=""}
-The source code of the [train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) script on _GitHub_.
+The source code of the [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L111) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L111) script on _GitHub_.
 :::
@@
 ##### Return
+\
+A data frame object representing the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_.
 
-A data structure containing information about _User+Movie+Genre+Year (UMGYD) Effect_.
-
-#### [train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L84) Function {#func.train_UMGYD_effect.cv}
+#### [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L123) Function {#func.UMGY_SmoothedDay_effect.predict}
 \
 
-This function is used to train the current model using the _5-Fold Cross Validation_.
-The following is the source code of the function:
+This is a helper function that predicts user rating values on the _Test Set_ passed by the [test_set](#func.UMGY_SmoothedDay_effect.predict.params.test_set) parameter, taking into account the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ passed by the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect) parameter.
+
+##### Parameters
+\
+
+::: { #func.UMGY_SmoothedDay_effect.predict.params.test_set .sidebar }
+###### ***test_set***
+\
+A _Test Set_ dataset for the _UMGYDE Model_ validation.
+:::
+
+::: { #func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect .sidebar }
+
+###### ***day_smoothed_effect***
+\
+A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:
+
+  - [calc_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
+  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
+  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
+
+:::
+
+##### Source Code
+\
+
+Below is the source code of the function:
 ```{r eval=FALSE}
-train_UMGYD_effect.cv <- function(lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_UMGYD_effect.cv
-`lambda` is `NA`")
-  }
-
-  calc_day_general_effect.cv(lambda) |> calc_UMGYD_effect()  
+UMGY_SmoothedDay_effect.predict <- function(test_set, day_smoothed_effect) {
+  test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(rglr.UMGY_effect, by='year') |>
+    left_join(day_smoothed_effect, by='days') |>
+    mutate(predicted = clamp(mu + a + b + g + 
+                               ifelse(is.na(ye), 0, ye) +
+                               ifelse(is.na(de_smoothed), 
+                                      0, 
+                                      de_smoothed))) |> 
+    select(userId, movieId, timestamp, rating, predicted)
 }
@@
 ::: {.noteblock data-latex=""}
-The source code of the [train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L84) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L84) script on _GitHub_.
+The source code of the [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L123) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L123) script on _GitHub_.
 :::
@@
 ##### Return
-
-A data structure containing information about _User+Movie+Genre+Year (UMGYD) Effect_.
-
-#### [calc_UMGYD_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L92) Function {#func.calc_UMGYD_effect_MSE}
 \
 
-The function calculates the _Mean Squared Error (MSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed in the `test_set` parameter.
+A data frame object containing predicted values.
+
+\newpage
+
+#### [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L139) Function {#func.calc_UMGY_SmoothedDay_effect.MSE}
+\
+
+The function calculates the _Mean Squared Error (MSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.params.test_set) parameter.
 
@@
 
-  - **test_set:** A _Test Set_ dataset used for _UMGYDE Model_ validation;
-  - **UMGYD_effect:** A data structure returned by any of the following functions described above:
-    - [calc_UMGYD_effect](#func.train_UMGYD_effect);
-    - [train_UMGYD_effect](#func.train_UMGYD_effect);
-    - [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv).
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.params.test_set .sidebar }
+###### ***test_set***
+\
+A _Test Set_ dataset for the _UMGYDE Model_ validation.
+:::
 
-\newpage
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.params.day_smoothed_effect .sidebar }
+
+###### ***day_smoothed_effect***
+\
+A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:
+
+  - [calc_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
+  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
+  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
+
+:::
 
@@
 ```{r eval=FALSE}
-calc_UMGYD_effect_MSE <- function(test_set, UMGYD_effect){
+calc_UMGY_SmoothedDay_effect.MSE <- function(test_set, day_smoothed_effect) {
   test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    left_join(UMGYD_effect, by='year') |>
-    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
+    UMGY_SmoothedDay_effect.predict(day_smoothed_effect) |>
+    mutate(resid = rating - predicted) |> 
     pull(resid) |> mse()
@@
 ::: {.noteblock data-latex=""}
-The source code of the function [calc_UMGYD_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L92) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L92) script.
+The source code of the function [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L139) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L139) script on _GitHub_.
 :::
 
-#### [calc_UMGYD_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L102) Function {#func.calc_UMGYD_effect_MSE.cv}
+##### Return
+\
+The _Mean Squared Error (MSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.params.test_set) parameter.
+
+#### [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L145) Function {#func.calc_UMGY_SmoothedDay_effect.MSE.cv}
 \
 
-The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGYD Effect_ data passed in the `UMGYD_effect` parameter.
+The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.params.day_smoothed_effect) parameter.
 
@@
 
-The function accepts the only parameter: `UMGYD_effect`, which is a data structure returned by the one of the following functions described above:
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.params.day_smoothed_effect .sidebar }
 
-  - [calc_UMGYD_effect](#func.train_UMGYD_effect);
-  - [train_UMGYD_effect](#func.train_UMGYD_effect);
-  - [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv).
+###### ***day_smoothed_effect***
+\
+A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:
+
+  - [calc_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
+  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
+  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
+
+:::
+
+##### Source Code
+\
+
+Below is a simplified version of the function's source code:
+```{r eval=FALSE}
+calc_UMGY_SmoothedDay_effect.MSE.cv <- function(day_smoothed_effect){
+  smth_day_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
+    cv_fold_dat$validation_set |> 
+      calc_UMGY_SmoothedDay_effect.MSE(day_smoothed_effect)
+  })
+
+  mean(smth_day_effect_MSEs)
+}
+
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code of the [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L145) function is available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L145) script on _GitHub_.
+:::
+
+##### Return
+\
+The _Mean Squared Error (MSE)_ value of the _UMGYDE Model_ computed as the mean of the _5-Fold Cross Validation_ results.
+
+#### [calc_UMGY_SmoothedDay_effect.RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L161) Function {#func.calc_UMGY_SmoothedDay_effect.RMSE}
+\
+
+The function calculates the _Root Mean Squared Error (RMSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.params.test_set) parameter.
+
+##### Parameters
+\
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.params.test_set .sidebar }
+###### ***test_set***
+\
+A _Test Set_ dataset for the _UMGYDE Model_ validation.
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.params.day_smoothed_effect .sidebar }
+###### ***day_smoothed_effect***
+\
+A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:
+
+  - [calc_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
+  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
+  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
+
+:::
 
@@
 ```{r eval=FALSE}
-calc_UMGYD_effect_MSE.cv <- function(UMGYD_effect){
-  start <- put_start_date()
-  UMGYD_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_UMGYD_effect_MSE(UMGYD_effect)
-  })
-  put_end_date(start)
-  put_log1("Function: calc_UMGYD_effect_MSE.cv
-Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
+calc_UMGY_SmoothedDay_effect.RMSE <- function(test_set, day_smoothed_effect){
+  day_smth_effect_MSe <- test_set |> 
+    calc_UMGY_SmoothedDay_effect.MSE(day_smoothed_effect)
 
-  mean(UMGYD_effect_MSEs)
+  sqrt(day_smth_effect_MSe)
 }
-
 ```
@@
 ::: {.noteblock data-latex=""}
-The source code of the function [calc_UMGYD_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L102) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L102) script.
+The source code of the function [calc_UMGY_SmoothedDay_effect.RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L161) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L161) script.
 :::
 
-#### [calc_UMGYD_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L114) Function {#func.calc_UMGYD_effect_RMSE}
+##### Return
+\
+The _Root Mean Squared Error (RMSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.params.test_set) parameter.
+
+#### [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L167) Function {#func.calc_UMGY_SmoothedDay_effect.RMSE.cv}
 \
 
-The function calculates the _Mean Squared Error (MSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed in the `test_set` parameter.
+The function calculates the _5-Fold Cross Validation RMSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.params.day_smoothed_effect) parameter.
 
@@
 
-  - **test_set:** A _Test Set_ dataset used for _UMGYDE Model_ validation;
-  - **UMGYD_effect:** A data structure returned by any of the following functions described above:
-    - [calc_UMGYD_effect](#func.train_UMGYD_effect);
-    - [train_UMGYD_effect](#func.train_UMGYD_effect);
-    - [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv).
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.params.day_smoothed_effect .sidebar }
+###### ***day_smoothed_effect***
+\
+A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:
+
+  - [calc_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
+  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
+  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
+
+:::
 
@@
 ```{r eval=FALSE}
-calc_UMGYD_effect_RMSE <- function(test_set, UMGYD_effect){
-  mse <- test_set |> calc_UMGYD_effect_MSE(UMGYD_effect)
-  sqrt(mse)
+calc_UMGY_SmoothedDay_effect.RMSE.cv <- function(day_smoothed_effect){
+  sqrt(calc_UMGY_SmoothedDay_effect.MSE.cv(day_smoothed_effect))
 }
@@
 ::: {.noteblock data-latex=""}
-The source code of the function [calc_UMGYD_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L114) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L114) script.
+The source code of the function [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L167) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L167)  script.
 :::
 
-#### [calc_UMGYD_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L118) Function {#func.calc_UMGYD_effect_RMSE.cv}
+##### Return
 \
+The _Root Mean Squared Error (RMSE)_ value of the _UMGYDE Model_ computed as the square root of the _5-Fold Cross Validation MSE_ result.
 
-The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGYD Effect_ data passed in the `UMGYD_effect` parameter.
-
-##### Parameters
-\
-
-The function accepts the only parameter: `UMGYD_effect`, which is a data structure returned by the one of the following functions described above:
-
-  - [calc_UMGYD_effect](#func.train_UMGYD_effect);
-  - [train_UMGYD_effect](#func.train_UMGYD_effect);
-  - [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv).
-
-##### Source Code
-\
-
-The source code of the function is provided below:
-```{r eval=FALSE}
-calc_UMGYD_effect_RMSE.cv <- function(UMGYD_effect){
-  UMGYD_effect_RMSE <- sqrt(calc_UMGYD_effect_MSE.cv(UMGYD_effect))
-  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
-           CVFolds_N, 
-           UMGYD_effect_RMSE)
-
-  UMGYD_effect_RMSE
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function [calc_UMGYD_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L118) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L118) script.
-:::
+----------------------------------------------------
 

### 2025-05-29 r/src/support-functions/UMGYD-effect.functions.R

@@ -121,9 +121,6 @@ train_UMGY_SmoothedDay_effect.cv <- function(degree = NA,
 }
 
 UMGY_SmoothedDay_effect.predict <- function(test_set, day_smoothed_effect) {
-  # mean.ye <- mean(rglr.UMGY_effect$ye)
-  # mean.de_smoothed <- mean(rglr.UMGYD_effect$de_smoothed)
-  
   test_set |>
     left_join(edx.user_effect, by = "userId") |>
     left_join(rglr.UM_effect, by = "movieId") |>
@@ -140,15 +137,8 @@ UMGY_SmoothedDay_effect.predict <- function(test_set, day_smoothed_effect) {
 }
 
 calc_UMGY_SmoothedDay_effect.MSE <- function(test_set, day_smoothed_effect) {
-  # browser()
   test_set |>
     UMGY_SmoothedDay_effect.predict(day_smoothed_effect) |>
-    # left_join(edx.user_effect, by = "userId") |>
-    # left_join(rglr.UM_effect, by = "movieId") |>
-    # left_join(rglr.UMG_effect, by = "movieId") |>
-    # left_join(date_days_map, by = "timestamp") |>
-    # left_join(rglr.UMGY_effect, by='year') |>
-    # left_join(day_smoothed_effect, by='days') |>
     mutate(resid = rating - predicted) |> 
     pull(resid) |> mse()
 }

### 2025-05-30 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd

@@
   - [calc_day_general_effect.cv](#func.calc_day_general_effect.cv).
+
 :::
@@
 ::: { #func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect .sidebar }
-
 ###### ***day_smoothed_effect***
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.MSE.params.day_smoothed_effect .sidebar }
-
 ###### ***day_smoothed_effect***
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.params.day_smoothed_effect .sidebar }
-
 ###### ***day_smoothed_effect***
@@
 \
-The _Root Mean Squared Error (RMSE)_ value of the _UMGYDE Model_ computed as the square root of the _5-Fold Cross Validation MSE_ result.
-
-----------------------------------------------------
+The _Root Mean Squared Error (RMSE)_ of the _UMGYD Model_ computed as the square root of the _5-Fold Cross Validation MSE_ result.
 
@@
 :::
+
+\newpage
+
+### UMGYDE Model Tuning
+\
+
+#### UMGYDE Model Tuning: Support Functions
+\
+
+##### [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L171) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv}
+\
+The function is designed to tune the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function's parameters ([degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span)), which is ultimately called internally under the hood.
+
+###### Parameters
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree .sidebar }
+  - ***degree:***
+A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to specify the degree of the polynomials to be used.
+
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span .sidebar }
+  - ***span:***
+A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.
+
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.details .sidebar }
+###### Details
+\
+Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) and then [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above to compute the `RMSE` of the model to be tuned.
+:::
+
+###### Source Code
+\
+Below is a simplified version of the function's source code:
+```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect.RMSE.cv <- function(degree = NA, span = NA) {
+  train_UMGY_SmoothedDay_effect.cv(degree, span) |>
+    calc_UMGY_SmoothedDay_effect.RMSE.cv()
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L171) function is available in the [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L170) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L171) script on _GitHub_.
+:::
+
+###### Return
+\
+The _Root Mean Squared Error (RMSE)_ of the _UMGYD Model_.
+
+##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0}
+\
+The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 0.
+
+###### Parameters
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.params.span .sidebar }
+  - ***span:***
+A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.
+
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.details .sidebar }
+###### Details
+\
+Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 0 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.params.span) of this function to compute the `RMSE` of the model to be tuned.
+:::
+
+###### Source Code
+\
+Below is the function's source code:
+```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect.RMSE.cv.degree0 <- function(span) {
+  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 0, span)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) function is also available in the [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L170) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) script on _GitHub_.
+:::
+
+###### Return
+\
+_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.params.span) parameter and the `degree` parameter value equal to 0.
+
+\newpage
+
+##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L193) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1}
+\
+The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 1.
+
+###### Parameters
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.params.span .sidebar }
+  - ***span:***
+A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.
+
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.details .sidebar }
+###### Details
+\
+Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 1 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.params.span) of this function to compute the `RMSE` of the model to be tuned.
+:::
+
+###### Source Code
+\
+Below is the function's source code:
+```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect.RMSE.cv.degree1 <- function(span) {
+  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 1, span)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L193) function is also available in the [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L170) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L193) script on _GitHub_.
+:::
+
+###### Return
+\
+_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.params.span) parameter and the `degree` parameter value equal to 1.
+
+##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L196) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2}
+\
+The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 2.
+
+###### Parameters
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.params.span .sidebar }
+  - ***span:***
+A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.
+
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.details .sidebar }
+###### Details
+\
+Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 2 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.params.span) of this function to compute the `RMSE` of the model to be tuned.
+:::
+
+###### Source Code
+\
+Below is the function's source code:
+```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect.RMSE.cv.degree2 <- function(span) {
+  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 2, span)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L196) function is also available in the [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L170) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L196) script on _GitHub_.
+:::
+
+###### Return
+\
+_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.params.span) parameter and the `degree` parameter value of 2.
 
@@
 
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L128) function described below are defined in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L127) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L128) script.
+##### [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) Function {#func.regularize.train_UMGYD_effect}
+\
+
+This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [regularize.train_UMGYD_effect](#func.regularize.train_UMGYD_effect)) described below.
+
+###### Parameters
+\
+
+::: { #func..params. .sidebar }
+  - ***train_set:***
+The _Train Set_ dataset.
+
 :::
 
-##### [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#128) Function {#func.regularize.test_lambda.UMGYD_effect.cv}
+::: { #func..params. .sidebar }
+  - ***lambda:***
+As explained [above](#sec.umgydem.support_functions.note.lambda) in the [] section, this is the $\lambda$ coefficient of the penalty of the _Regularization_ method.
+
+:::
+
+::: { #func.regularize.train_UMGYD_effect.details .sidebar }
+###### Details
+\
+Under the hood, the function internally calls the 
+:::
+
+###### Source Code
 \
 
+The following is the source code of the function:
+```{r eval=FALSE}
+regularize.train_UMGYD_effect <- function(train_set, lambda) {
+  best_degree <- lss.UMGYDE.best_params["degree"]
+  best_span <- lss.UMGYDE.best_params["span"]
+
+  train_set |>
+    train_UMGY_SmoothedDay_effect(best_degree, 
+                                  best_span, 
+                                  lambda)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) script on _GitHub_.
+:::
+
+###### Return
+\
+A data frame object representing the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_.
+
+\newpage
+
+##### [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) Function {#func.regularize.train_UMGYD_effect.cv}
+\
+The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 0.
+
+###### Parameters
+\
+
+::: { #func.regularize.train_UMGYD_effect.cv.params.lambda .sidebar }
+  - ***lambda:***
+As explained [above](#sec.umgydem.support_functions.note.lambda) in the [] section, this is the $\lambda$ coefficient of the penalty of the _Regularization_ method.
+
+:::
+
+::: { #func.regularize.train_UMGYD_effect.cv.details .sidebar }
+###### Details
+\
+Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 0 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span) parameter value taken from the [parameter of the same name](#func.regularize.train_UMGYD_effect.cv.params.span) of this function to compute the `RMSE` of the model to be tuned.
+:::
+
+###### Source Code
+\
+Below is the function's source code:
+```{r eval=FALSE}
+regularize.train_UMGYD_effect.cv <- function(lambda) {
+  best_degree <- lss.UMGYDE.best_params["degree"]
+  best_span <- lss.UMGYDE.best_params["span"]
+
+  train_UMGY_SmoothedDay_effect.cv(best_degree, 
+                                   best_span, 
+                                   lambda)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) function is also available in the [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L170) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) script on _GitHub_.
+:::
+
+###### Return
+\
+_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.regularize.train_UMGYD_effect.cv.params.span) parameter and the `degree` parameter value equal to 0.
+
+\newpage
+
+##### [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L240) Function {#func.regularize.test_lambda.UMGYD_effect.cv}
+\
+
+::: {.noteblock data-latex=""}
+The [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L240) function are defined in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L222) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L240) script on _GitHub.
+:::
+
 This function calculates _RMSE_ of the _UMGYDE Model_ using _5-Fold Cross Validation_ for the given $\lambda$ parameter value:
+
 ```{r, eval=FALSE}
+regularize.test_lambda.UMGYD_effect.cv <- function(lambda){
+  if (is.na(lambda)) {
+    stop("Function: regularize.test_lambda.UMGY_effect.cv
+`lambda` is `NA`")
+  }
+
+  regularize.train_UMGYD_effect.cv(lambda) |>
+    calc_UMGY_SmoothedDay_effect.RMSE.cv()
+}
 ```

### 2025-05-31 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Model regularization: support functions described.

@@
 
+::: { #func.train_UMGY_SmoothedDay_effect.params.degree .sidebar }
 ###### ***degree***
@@
 A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.details) section below), meaning the degree of the polynomials to be used.
-
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.params.span .sidebar }
 ###### ***span***
@@
 A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.details) section below) to control the degree of smoothing.
+:::
 
@@
 ::: {.noteblock data-latex=""}
-The complete source code of building and training the current model is available in the [UMGYDE Model Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1432) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1432) script on _GitHub_.
+The complete source code of building and training the current model is available in the [UMGYDE Model (UMGYDEM) Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1745) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1745) script on _GitHub_.
 :::
@@
 ### UMGYDE Model Regularization
+\
+
+#### UMGYDE Model Regularization: Mathematical Description
 \
@@
 
-##### [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) Function {#func.regularize.train_UMGYD_effect}
-\
-
-This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [regularize.train_UMGYD_effect](#func.regularize.train_UMGYD_effect)) described below.
+##### [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L223) Function {#func.regularize.train_UMGYD_effect}
+\
+
+The function is an overloaded version of the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.params.degree) and [span](#func.train_UMGY_SmoothedDay_effect.params.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.
 
@@
 
-::: { #func..params. .sidebar }
+::: { #func.regularize.train_UMGYD_effect.params.train_set .sidebar }
   - ***train_set:***
-The _Train Set_ dataset.
-
-:::
-
-::: { #func..params. .sidebar }
+The _Train Set_ dataset .
+
+:::
+
+::: { #func.regularize.train_UMGYD_effect.params.lambda .sidebar }
   - ***lambda:***
-As explained [above](#sec.umgydem.support_functions.note.lambda) in the [] section, this is the $\lambda$ coefficient of the penalty of the _Regularization_ method.
-
-:::
-
-::: { #func.regularize.train_UMGYD_effect.details .sidebar }
-###### Details
-\
-Under the hood, the function internally calls the 
+  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.
+
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) script on _GitHub_.
+The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L223) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L222) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L223) script on _GitHub_.
 :::
@@
 \
-A data frame object representing the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_.
-
-\newpage
-
-##### [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) Function {#func.regularize.train_UMGYD_effect.cv}
-\
-The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 0.
+A data frame object representing the _UMGYD Effect_.
+
+\newpage
+
+##### [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L232) Function {#func.regularize.train_UMGYD_effect.cv}
+\
+
+::: {.noteblock data-latex=""}
+The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L232) function is defined in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L222) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L232) script on _GitHub_.
+:::
+
+The function is an overloaded version of the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.cv.params.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.params.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.
 
@@
   - ***lambda:***
-As explained [above](#sec.umgydem.support_functions.note.lambda) in the [] section, this is the $\lambda$ coefficient of the penalty of the _Regularization_ method.
-
-:::
-
-::: { #func.regularize.train_UMGYD_effect.cv.details .sidebar }
-###### Details
-\
-Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 0 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span) parameter value taken from the [parameter of the same name](#func.regularize.train_UMGYD_effect.cv.params.span) of this function to compute the `RMSE` of the model to be tuned.
+  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.
+
 :::
@@
 \
-Below is the function's source code:
+The source code of the function is provided below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) function is also available in the [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L170) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) script on _GitHub_.
+Note that we reuse the function [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) calling it internally from the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
 :::
@@
 \
-_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.regularize.train_UMGYD_effect.cv.params.span) parameter and the `degree` parameter value equal to 0.
+A data frame object representing the _UMGYD Effect_.
 
@@
 
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L240) function are defined in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L222) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L240) script on _GitHub.
-:::
-
-This function calculates _RMSE_ of the _UMGYDE Model_ using _5-Fold Cross Validation_ for the given $\lambda$ parameter value:
-
+The function calculates _RMSE_ of the _UMGYDE Model_ using _5-Fold Cross Validation_ for the given $\lambda$ parameter value.
+
+::: { #func.regularize.test_lambda.UMGYD_effect.cv.params.lambda .sidebar }
+  - ***lambda:***
+  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.
+
+:::
+
+::: { #func.regularize.test_lambda.UMGYD_effect.cv.details .sidebar }
+##### Details
+\
+Under the hood, the function internally calls the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) and then [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above, and returns the _RMSE_ value that the latter inner function calculates for the given [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.params.lambda) parameter value passed to the former one.
+:::
+
+###### Source Code
+\
+The source code of the function is provided below:
 ```{r, eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-Note that we reuse the function [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv) calling it from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
-:::
+The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L240) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L222) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L240) script on _GitHub_.
+:::
+
+###### Return
+\
+_Root Mean Squared Error (RMSE)_ of the _UMGYD Model_ trained for the given [lambda](#func.regularize.train_UMGYD_effect.cv.params.span) parameter value.
 

### 2025-05-31 r/src/capstone-movielens.main.R

@@ -1742,7 +1742,8 @@ the `User+Movie+Genre+Year+(Smoothed)Day Effect Model` data
 using `loess` function with parameter `degree = 2`: %1", 
 UMGYDE.fine_tune.degree2.data.path)
 
-### Training with default parameters -------------------------------------------
+### UMGYDE Model (UMGYDEM) Building --------------------------------------------
+#### UMGYDEM Training with default parameters -------------------------------------------
 file_name_tmp <- "9.cv.UMGYDE.loess.default-params.RData"
 file_path_tmp <- file.path(data.models.path, file_name_tmp)
 

### 2025-05-31 r/src/capstone-movielens.main.R
Fix for scripts.

@@ -1743,7 +1743,7 @@ using `loess` function with parameter `degree = 2`: %1",
 UMGYDE.fine_tune.degree2.data.path)
 
 ### UMGYDE Model (UMGYDEM) Building --------------------------------------------
-#### UMGYDEM Training with default parameters -------------------------------------------
+#### UMGYDEM Training with default parameters ----------------------------------
 file_name_tmp <- "9.cv.UMGYDE.loess.default-params.RData"
 file_path_tmp <- file.path(data.models.path, file_name_tmp)
 
@@ -1812,7 +1812,7 @@ RMSEs.ResultTibble.UMGYDE <- RMSEs.ResultTibble.rglr.UMGYE |>
   RMSEs.AddRow("UMGYDE (Default) Model", 
                cv.UMGYDE.default_params.RMSE,
                comment = "User+Movie+Genre+Year+Day Effect (UMGYDE) Model 
-computed using `loess` function with default `degree` & `span` parameters.")
+computed using `stats::loess` function with `degree=1` & `span=0.75` parameter values.")
 
 RMSE_kable(RMSEs.ResultTibble.UMGYDE)
 put_log("A row has been added to the RMSE Result Tibble 

### 2025-05-31 r/src/support-functions/common-helper.functions.R

@@ -42,15 +42,15 @@ RMSEs.AddRow <- function(RMSEs, method, value, comment = ""){
             Comment = comment)
 }
 RMSE_kable <- function(RMSEs,
-                       col1width = 20,
+                       col1width = 10,
                        col2width = 5,
                        col3width = 20){
   RMSEs |>
     kable(align='lcl', booktabs = T, padding = 5) |> 
     row_spec(0, bold = T) |>
     column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
-    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
-    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
+    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) #|>
+    # column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
 }
 RSME.tibble.col_width <- function(x){
   "%1em" |> msg.glue(x)

### 2025-06-01 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Model training with default parameters described.

@@
 
-### UMGYDE Model: Support Functions
+### UMGYDE Model: Helper Functions
 \
@@
 
-### UMGYDE Model Building
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of building and training the current model is available in the [UMGYDE Model (UMGYDEM) Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1745) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1745) script on _GitHub_.
-:::
+### UMGYDE Model Building With Default Parameters
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of building and training the current model is available in the [UMGYDEM Training with default parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1745) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1745) script on _GitHub_.
+:::
+
+We are going to use our helper function [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described in the [UMGYDE Model: Helper Functions] section, which, as we explained, internally calls the R function [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess).
+
+We will start by calling the `train_UMGY_SmoothedDay_effect.cv` with default parameters, which means that the `loess` function will be implicitly called with `degree = 1` and `span = 0.75` parameters (the default values for our custom [loess_de](#func.loess_de) function, which, in turn, calls the `loess` under the hood).
 
@@
 ```{r, eval=FALSE}
+  cv.UMGYDE.default_params <- train_UMGY_SmoothedDay_effect.cv()
 ```
 ```{r}
-```
-
-::: {.noteblock data-latex=""}
-We use the [train_UMGYD_effect.cv](#func.train_UMGYD_effect.cv) function described above to compute the _UMGYD Effect_.
-:::
-
-We can now construct predictors and calculate the _RMSE_ of the current model using the [calc_UMGYD_effect_RMSE.cv](#func.calc_UMGYD_effect_RMSE.cv) function described above:
+str(cv.UMGYDE.default_params)
+```
+
+Below is the visual representation of the UMGYD Effect data we have just computed:
+
+```{r}
+cv.UMGYDE.default_params |>
+  ggplot(aes(x = days)) +
+  geom_point(aes(y = de), size = 3, alpha = .5, color = "grey") + 
+  geom_line(aes(y = de_smoothed), color = "red")
+```
+
+Let's calculate the _RMSE_ of the current model using the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function described above:
 
 ```{r, eval=FALSE}
+cv.UMGYDE.default_params.RMSE <- cv.UMGYDE.default_params |>
+  calc_UMGY_SmoothedDay_effect.RMSE.cv()
+
+RMSEs.ResultTibble.UMGYDE <- RMSEs.ResultTibble.rglr.UMGYE |> 
+  RMSEs.AddRow("UMGYDE (Default) Model", 
+               cv.UMGYDE.default_params.RMSE,
+               comment = "User+Movie+Genre+Year+Day Effect (UMGYDE) Model 
+computed using `stats::loess` function with `degree=1` & `span=0.75` parameter values.")
 ```
@@
 
-::: {.noteblock data-latex=""}
-Now, we have a bit better result than one for the previous model.
-:::
-
-\newpage
-
-### UMGYDE Model Tuning
+Unfortunately, with the default parameters, we obtained an even worse result than before.
+Let's tune the current model by adjusting the `degree` and `span` parameters and see what we get.
+
+::: {.noteblock data-latex=""}
+Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three steps - one per each possible value of the `degree` parameter.
+:::
+
+\newpage
+
+### UMGYDE Model Tuning by `degree` and `span` Parameters
 \
@@
 _Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.params.span) parameter and the `degree` parameter value of 2.
+
+\newpage
+
+#### UMGYDE Model Tuning: Step 1 (`degree = 0`)
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the ***Step 1*** of the current model tuning is available in the [UMGYDE Model Tuning: Step 1 (`degree = `)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1823) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1823) script on _GitHub_.
+:::
+
+#### UMGYDE Model Tuning: Step 2 (`degree = 1`)
+\
+
+::: {.noteblock data-latex=""}
+The complete source code the ***Step 2*** of the current model tuning is available in the [UMGYDE Model Tuning: Step  (`degree = `)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1) script on _GitHub_.
+:::
+
+#### UMGYDE Model Tuning: Step 3 (`degree = 2`)
+\
+
+::: {.noteblock data-latex=""}
+The complete source code the ***Step 3*** of the current model tuning is available in the [UMGYDE Model Tuning: Step  (`degree = `)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1) script on _GitHub_.
+:::
+
+::: {.noteblock data-latex=""}
+Now, we have a bit better result than one for the previous model.
+:::
 

### 2025-06-01 r/src/capstone-movielens.main.R

@@ -1820,7 +1820,7 @@ for the tuned `User+Movie+Genre+Year+(Smoothed)Day Effect Model`.")
 ### Close Log -----------------------------------------------------------------
 log_close()
 ### UMGYDE Model Tuning by `span` & `degree` parameters ------------------------
-#### 1. `degree = 0` -----------------------------------------------------------
+#### UMGYDE Model Tuning: Step 1 (`degree = 0`) --------------------------------
 ##### Open log for UMGYDE Model Tuning: Pre-configuration (`degree = 0`) -------
 open_logfile(".UMGYDE.loess.degree0.pre-tuning")
 put("Case 1. `degree = 0`")
@@ -1937,7 +1937,7 @@ RMSEs.ResultTibble.UMGYDE0 <- RMSEs.ResultTibble.UMGYDE |>
 RMSE_kable(RMSEs.ResultTibble.UMGYDE0)
 ##### Close Log ---------------------------------------------------------------
 log_close()
-#### 2. `degree = 1` -----------------------------------------------------------
+#### UMGYDE Model Tuning: Step 2 (`degree = 1`) --------------------------------
 ##### Open log for UMGYDE Model Tuning: Pre-configuration (`degree = 1`) -------
 open_logfile(".UMGYDE.loess.degree1.pre-tuning")
 put("Case 2. `degree = 1`")
@@ -2049,7 +2049,7 @@ RMSE_kable(RMSEs.ResultTibble.UMGYDE1)
 
 ##### Close Log ---------------------------------------------------------------
 log_close()
-#### 3. `degree = 2` -----------------------------------------------------------
+#### UMGYDE Model Tuning: Step 3 (`degree = 2`) --------------------------------
 ##### Open log for UMGYDE Model Tuning: Pre-configuration (`degree = 2`) -------
 open_logfile(".UMGYDE.loess.degree2.pre-tuning")
 put("Case 3. `degree = 2`")

### 2025-06-01 r/src/support-functions/common-helper.functions.R

@@ -42,15 +42,15 @@ RMSEs.AddRow <- function(RMSEs, method, value, comment = ""){
             Comment = comment)
 }
 RMSE_kable <- function(RMSEs,
-                       col1width = 10,
+                       col1width = 15,
                        col2width = 5,
-                       col3width = 20){
+                       col3width = 32){
   RMSEs |>
     kable(align='lcl', booktabs = T, padding = 5) |> 
     row_spec(0, bold = T) |>
     column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
-    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) #|>
-    # column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
+    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
+    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
 }
 RSME.tibble.col_width <- function(x){
   "%1em" |> msg.glue(x)

### 2025-06-01 reports/capstone-movielens.site/04.appendix.Rmd
UMGYDE Model Tuning by `degree` & `span` parameters of the stats::loess function (completed).

@@
 
-The soure code of the [data.plot]() function is shown below:
+The soure code of the [data.plot]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function is shown below:
 ```{r eval=FALSE}
@@
 The source code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
+:::
+:::
+
+### [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) Function {#func.data.plot.left.n}
+\
+
+Plots a graph based on the dataset passed in the [data](#func.data.plot.left.n.params.data) parameter, using both points and a line.
+
+::: { #func.data.plot.left.n.Usage .sidebar }
+#### Usage
+\
+
+```{r eval=FALSE}
+data.plot.left.n <- function(data, 
+                             left.n = 0,
+                             title, 
+                             xname, 
+                             yname, 
+                             xlabel, 
+                             ylabel,
+                             line_col = "red",
+                             normalize = FALSE)
+```
+:::
+
+::: { #func.data.plot.left.n.params .sidebar }
+#### Parameters
+\
+
+::: { #func.data.plot.left.n.params.data .sidebar }
+  - **data:** Dataset to use for the plot;
+
+:::
+::: { #func.data.plot.left.n.params.title .sidebar }
+  - **title:** Title of the plot;
+
+:::
+::: { #func.data.plot.left.n.params.xname .sidebar }
+  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;
+
+:::
+::: { #func.data.plot.left.n.params.yname .sidebar }
+  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;
+
+:::
+::: { #func.data.plot.left.n.params.xlabel .sidebar }
+  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
+
+:::
+::: { #func.data.plot.left.n.params.ylabel .sidebar }
+  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;
+
+:::
+::: { #func.data.plot.left.n.params.line_col .sidebar }
+  - **line_col = blue:** The line color;
+
+:::
+::: { #func.data.plot.left.n.params.normalize .sidebar }
+  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
+
+:::
+:::
+
+::: { #func.data.plot.left.n.details .sidebar }
+#### Details
+\
+
+The function is a wrapper for the [data.plot](#func.data.plot) function described above and is a simple and convenient tool for more detailed visualizing the left part of the graph.
+
+:::
+
+::: { #func.data.plot.left.n.code .sidebar }
+#### Source Code
+\
+
+The soure code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) function is shown below:
+```{r eval=FALSE}
+data.plot.left.n <- function(data, 
+                             left.n = 0,
+                             title, 
+                             xname, 
+                             yname, 
+                             xlabel, 
+                             ylabel,
+                             line_col = "red",
+                             normalize = FALSE) {
+  x_col <- data[, xname] 
+  y_col <- data[, yname]
+
+  data.left <- data
+
+  if (left.n > 0) {
+    data.left <- data |> 
+      head(left.n)
+  }
+
+  data.left |>
+    data.plot(title = title,
+              xname = xname,
+              yname = yname,
+              xlabel = xlabel,
+              ylabel = ylabel,
+              line_col = line_col,
+              normalize = normalize)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) script.
+:::
+:::
+
+### [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) Function {#func.data.plot.left_detailed}
+\
+
+Plots a graph based on the dataset passed in the [data](#func.data.plot.left_detailed.params.data) parameter, using both points and a line.
+
+::: { #func.data.plot.left_detailed.Usage .sidebar }
+#### Usage
+\
+
+```{r eval=FALSE}
+data.plot.left_detailed <- function(data, 
+                                    left.n = 0,
+                                    title = NULL,
+                                    title.left = NULL,
+                                    xname, 
+                                    yname, 
+                                    xlabel1 = NULL, 
+                                    xlabel2 = NULL, 
+                                    ylabel1 = NULL,
+                                    ylabel2 = NULL,
+                                    line_col1 = "blue",
+                                    line_col2 = "red",
+                                    normalize = FALSE)
+```
+:::
+
+::: { #func.data.plot.left_detailed.params .sidebar }
+#### Parameters
+\
+
+::: { #func.data.plot.left_detailed.params.data .sidebar }
+  - **data:** Dataset to use for the plot;
+
+:::
+::: { #func.data.plot.left_detailed.params.title .sidebar }
+  - **title:** Title of the plot;
+
+:::
+::: { #func.data.plot.left_detailed.params.xname .sidebar }
+  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;
+
+:::
+::: { #func.data.plot.left_detailed.params.yname .sidebar }
+  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;
+
+:::
+::: { #func.data.plot.left_detailed.params.xlabel .sidebar }
+  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
+
+:::
+::: { #func.data.plot.left_detailed.params.ylabel .sidebar }
+  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;
+
+:::
+::: { #func.data.plot.left_detailed.params.line_col .sidebar }
+  - **line_col = blue:** The line color;
+
+:::
+::: { #func.data.plot.left_detailed.params.normalize .sidebar }
+  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
+
+:::
+:::
+
+::: { #func.data.plot.left_detailed.details .sidebar }
+#### Details
+\
+
+The function is a wrapper for the [data.plot.left.n](#func.data.plot.left.n) function described above and is a simple and convenient tool for more detailed visualizing the left part of the graph.
+
+:::
+
+::: { #func.data.plot.left_detailed.code .sidebar }
+#### Source Code
+\
+
+The soure code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) function is shown below:
+```{r eval=FALSE}
+data.plot.left_detailed <- function(data, 
+                                    left.n = 0,
+                                    title = NULL,
+                                    title.left = NULL,
+                                    xname, 
+                                    yname, 
+                                    xlabel1 = NULL, 
+                                    xlabel2 = NULL, 
+                                    ylabel1 = NULL,
+                                    ylabel2 = NULL,
+                                    line_col1 = "blue",
+                                    line_col2 = "red",
+                                    normalize = FALSE) {
+  if(is.null(xlabel1)) {
+    xlabel1 <- xname
+  }
+  if(is.null(xlabel2)) {
+    xlabel2 <- str_glue(xlabel1, " (left part)")
+  }
+  if(is.null(ylabel1)) {
+    ylabel1 <- yname
+  }
+  if(is.null(ylabel2)) {
+    ylabel2 <- ylabel1
+  }
+
+  p1 <- data |>
+    data.plot(title = title,
+              xname = xname, 
+              yname = yname, 
+              xlabel = xlabel1, 
+              ylabel = ylabel1,
+              line_col = line_col1)
+
+  p2 <- data |>
+    data.plot.left.n(left.n = left.n,
+                     title = title.left,
+                     xname = xname, 
+                     yname = yname, 
+                     xlabel = xlabel2, 
+                     ylabel = ylabel2,
+                     line_col = line_col2,
+                     normalize = normalize)
+  grid.arrange(p1, p2)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) script.
 :::

### 2025-06-01 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd

@@
 
-::: {.noteblock data-latex=""}
-The complete source code of the ***Step 1*** of the current model tuning is available in the [UMGYDE Model Tuning: Step 1 (`degree = `)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1823) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1823) script on _GitHub_.
-:::
+##### Pre-configuration: `span` Range Determination
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration (`degree = 0`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1827) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1827) script on _GitHub_.
+:::
+
+Below the most significant part of the code performing the current model tuning, the _Pre-configuration Step_ is provided:
+```{r, eval=FALSE}
+  spans <- seq(0.0005, 1, 0.001)
+  lss.UMGYDE.preset.degree0.result <- 
+    tune.model_param(spans, train_UMGY_SmoothedDay_effect.RMSE.cv.degree0)
+```
+```{r}
+str(lss.UMGYDE.preset.degree0.result)
+```
+
+Below is the visual representation of the `span` parameter values range we have figured out in this step of tuning:
+```{r}
+plt.title = "UMGYDE Model, `loess` function args: range of `span` values for `degree = 0`"
+lss.UMGYDE.preset.degree0.result$tuned.result |>
+  data.plot(plt.title,
+              xname = "parameter.value", 
+              yname = "RMSE", 
+              xlabel = "spans", 
+              ylabel = "RMSE")
+rm(plt.title)
+```
+
+##### UMGYDE Model Fine-tuning (`degree = 0`)
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 0`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1893) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1893) script on _GitHub_.
+:::
+
+Below the most significant part of the code performing the current model _Fine-tuning_ is provided:
+```{r, eval=FALSE}
+lss.fine_tune.loop_starter <- 
+  c(lss.UMGYDE.preset.degree0.result$tuned.result$parameter.value[1], 
+    lss.UMGYDE.preset.degree0.result$tuned.result$parameter.value[3], 
+    8)
+
+cache_file.base_name <- "UMGYDE.degree0.tuning-span"
+
+lss.UMGYDE.fine_tune.degree0.result <- 
+  model.tune.param_range(lss.fine_tune.loop_starter,
+                         UMGYDE.fine_tune.degree0.data.path,
+                         cache_file.base_name,
+                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree0)
+```
+```{r}
+lss.fine_tune.loop_starter
+str(lss.UMGYDE.fine_tune.degree0.result)
+```
+
+Below is the visual representation of the current model _Fine-tuning_ results for the parameter value: `degree = 0`:
+```{r}
+plt.title = "Fine-tuned UMGYDE Model with `loess` parameter: `degree` = 0"
+
+lss.UMGYDE.fine_tune.degree0.result$tuned.result |>
+  data.plot(plt.title, 
+              xname = "parameter.value", 
+              yname = "RMSE", 
+              xlabel = "spans", 
+              ylabel = "RMSE")
+rm(plt.title)
+```
+Now, we can add the _UMGYDE Model Tuning_ result for `degree = 0` to our _Result Table_:
+```{r, eval=FALSE}
+RMSEs.ResultTibble.UMGYDE0 <- RMSEs.ResultTibble.UMGYDE |> 
+  RMSEs.AddRow("Tuned UMGYDE.d0 Model", 
+               lss.UMGYDE.fine_tune.degree0.result.best_RMSE,
+               comment = "UMGYDE Model computed using function call: `loess(degree = 0, span = %1)`" |>
+                 msg.glue(lss.UMGYDE.fine_tune.degree0.result.best_span))
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.UMGYDE0)
+```
 
@@
 
-::: {.noteblock data-latex=""}
-The complete source code the ***Step 2*** of the current model tuning is available in the [UMGYDE Model Tuning: Step  (`degree = `)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1) script on _GitHub_.
-:::
+##### Pre-configuration: `span` Range Determination
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration  (`degree = 1`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1944) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1944) script on _GitHub_.
+:::
+
+Below the most significant part of the code performing the current model tuning, the _Pre-configuration Step_ is provided:
+```{r, eval=FALSE}
+  lss.UMGYDE.preset.degree1.result <- 
+    tune.model_param(spans, train_UMGY_SmoothedDay_effect.RMSE.cv.degree1)
+```
+```{r}
+str(lss.UMGYDE.preset.degree1.result)
+```
+
+Below is the visual representation of the `span` parameter values range we have figured out in this step of tuning:
+```{r}
+lss.UMGYDE.preset.degree1.result$tuned.result |>
+  data.plot(title = "UMGYDE Model, `loess` function args: range of `span` values for `degree = 1`",
+              xname = "parameter.value", 
+              yname = "RMSE", 
+              xlabel = "spans", 
+              ylabel = "RMSE")
+```
+
+##### UMGYDE Model Fine-tuning (`degree = 1`)
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 1`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2007) script on _GitHub_.
+:::
+
+Below the most significant part of the code performing the current model _Fine-tuning_ is provided:
+```{r, eval=FALSE}
+lss.fine_tune.loop_starter <- 
+  c(lss.UMGYDE.preset.degree1.result$tuned.result$parameter.value[1], 
+    lss.UMGYDE.preset.degree1.result$tuned.result$parameter.value[3], 
+    8)
+
+cache_file.base_name <- "UMGYDE.degree1.tuning-span"
+
+lss.UMGYDE.fine_tune.degree1.result <- 
+  model.tune.param_range(lss.fine_tune.loop_starter,
+                         UMGYDE.fine_tune.degree1.data.path,
+                         cache_file.base_name,
+                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree1)
+```
+```{r}
+lss.fine_tune.loop_starter
+str(lss.UMGYDE.fine_tune.degree1.result)
+```
+
+Below is the visual representation of the current model _Fine-tuning_ results for the parameter value: `degree = 1`:
+```{r}
+lss.UMGYDE.fine_tune.degree1.result$tuned.result |>
+  data.plot(title = "Fine-tuned UMGYDE Model with `loess` parameter: `degree = 1`", 
+                             xname = "parameter.value", 
+                             yname = "RMSE", 
+                             xlabel = "spans", 
+                             ylabel = "RMSE")
+```
+
+Now, we can add the _UMGYDE Model Tuning_ result for `degree = 1` to our _Result Table_:
+```{r, eval=FALSE}
+RMSEs.ResultTibble.UMGYDE1 <- RMSEs.ResultTibble.UMGYDE0 |> 
+  RMSEs.AddRow("Tuned UMGYDE.d1 Model", 
+               lss.UMGYDE.fine_tune.degree1.result.best_RMSE,
+               comment = "UMGYDE Model computed using function call: `loess(degree = 1, span = %1)`" |>
+                 msg.glue(lss.UMGYDE.fine_tune.degree1.result.best_span))
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.UMGYDE1)
+```
 
@@
 
-::: {.noteblock data-latex=""}
-The complete source code the ***Step 3*** of the current model tuning is available in the [UMGYDE Model Tuning: Step  (`degree = `)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1) script on _GitHub_.
-:::
-
-::: {.noteblock data-latex=""}
-Now, we have a bit better result than one for the previous model.
-:::
+##### Pre-configuration: `span` Range Determination
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration (`degree = 2`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2056) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2057) script on _GitHub_.
+:::
+
+Below the most significant part of the code performing the current model tuning, the _Pre-configuration Step_ is provided:
+```{r, eval=FALSE}
+  spans <- seq(0.0005, 1, 0.001)
+  lss.UMGYDE.preset.degree2.result <- 
+    tune.model_param(spans, train_UMGY_SmoothedDay_effect.RMSE.cv.degree2)
+```
+```{r}
+str(lss.UMGYDE.preset.degree2.result)
+```
+
+Below is the visual representation of the `span` parameter values range we have figured out in this step of tuning:
+```{r}
+lss.UMGYDE.preset.degree2.result$tuned.result |>
+  data.plot(title = "UMGYDE Model, `loess` function args: range of `span` values for `degree = 2`",
+              xname = "parameter.value", 
+              yname = "RMSE", 
+              xlabel = "spans", 
+              ylabel = "RMSE")
+```
+
+##### UMGYDE Model Fine-tuning (`degree = 2`)
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 2`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2119) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2119) script on _GitHub_.
+:::
+
+Below the most significant part of the code performing the current model _Fine-tuning_ is provided:
+```{r, eval=FALSE}
+lss.fine_tune.loop_starter <- 
+  c(lss.UMGYDE.preset.degree2.result$tuned.result$parameter.value[1], 
+    lss.UMGYDE.preset.degree2.result$tuned.result$parameter.value[3], 
+    8)
+
+cache_file.base_name <- "UMGYDE.degree2.tuning-span"
+
+lss.UMGYDE.fine_tune.degree2.result <- 
+  model.tune.param_range(lss.fine_tune.loop_starter,
+                         UMGYDE.fine_tune.degree2.data.path,
+                         cache_file.base_name,
+                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree2)
+```
+```{r}
+lss.fine_tune.loop_starter
+str(lss.UMGYDE.fine_tune.degree2.result)
+```
+
+Below is the visual representation of the current model _Fine-tuning_ results for the parameter value: `degree = 2`:
+```{r}
+lss.UMGYDE.fine_tune.degree2.result$tuned.result |>
+  data.plot.left_detailed(title = "Fine-tuned UMGYDE Model with `loess` parameter: `degree = 2`", 
+                             title.left = "Left Part of the Chart Above (Zoomed in)",
+                             left.n = 8,
+                             xname = "parameter.value", 
+                             yname = "RMSE", 
+                             xlabel1 = "spans", 
+                             ylabel1 = "RMSE")
+```
+
+::: {.noteblock data-latex=""}
+The custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) we used above is described in the [Data Helper Functions] section of the [Appendix] to this report.
+:::
+
+Now, we can add the _UMGYDE Model Tuning_ result for `degree = 2` to our _Result Table_:
+```{r, eval=FALSE}
+RMSEs.ResultTibble.UMGYDE2 <- RMSEs.ResultTibble.UMGYDE1 |> 
+  RMSEs.AddRow("Tuned UMGYDE.d2 Model", 
+               lss.UMGYDE.fine_tune.degree2.result.best_RMSE,
+               comment = "UMGYDE Model computed using function call: `loess(degree = 2, span = %1)`" |>
+                 msg.glue(lss.UMGYDE.fine_tune.degree2.result.best_span))
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.UMGYDE2)
+```
+
+\newpage
+
+#### UMGYDE Model Tuning: Re-training with the Best `degree` & `span` Parameters
+\
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section are available in the [UMGYDE Tuned Model: Retraining with the best params](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#2169) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2169) script on _GitHub_.
+:::
+
+Now, we can calculate the _Regularized UMGYDE Effect_ by retraining our model on the entire `edx` dataset with the best values of the `degree` and `span` parameters we figured out above, for the definitive _Root Mean Squared Error_ calculation and use in subsequent processing.
+
+The most significant part of the code that performs this operation is shown below:
+```{r, eval=FALSE}
+lss.best_results <- data.frame(degree = degree, 
+                         span = c(lss.UMGYDE.fine_tune.degree0.result.best_span,
+                                  lss.UMGYDE.fine_tune.degree1.result.best_span,
+                                  lss.UMGYDE.fine_tune.degree2.result.best_span),
+
+                         RMSE = c(lss.UMGYDE.fine_tune.degree0.result.best_RMSE, 
+                                  lss.UMGYDE.fine_tune.degree1.result.best_RMSE,
+                                  lss.UMGYDE.fine_tune.degree2.result.best_RMSE))
+
+lss.best_RMSE.idx <- which.min(lss.best_results$RMSE)
+
+lss.UMGYDE.best_params <- 
+  c(degree =  lss.best_results[lss.best_RMSE.idx, "degree"],  # 1
+    span = lss.best_results[lss.best_RMSE.idx, "span"], # 0.00087,
+    RMSE = lss.best_results[lss.best_RMSE.idx, "RMSE"]) # 0.8568619
+
+lss.best_degree <- lss.UMGYDE.best_params["degree"]
+lss.best_span <- lss.UMGYDE.best_params["span"]
+lss.best_RMSE <- lss.UMGYDE.best_params["RMSE"]
+
+put_log2("Re-training model using `loess` function with the best parameters: 
+span = %1, degree = %2", lss.best_span, lss.best_degree)
+
+lss.UMGYD_effect <- edx |> 
+  train_UMGY_SmoothedDay_effect(lss.best_degree, lss.best_span)
+```
+```{r}
+lss.UMGYDE.best_params
+str(lss.UMGYD_effect)
+```
+
+::: {.noteblock data-latex=""}
+Here we use the helper function [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) described above in the [UMGYDE Model: Helper Functions] section.
+:::
+
+Let's now visualize final Smoothed Day effect we have obtained:
+```{r}
+lss.UMGYD_effect |>
+  ggplot(aes(x = days)) +
+  geom_point(aes(y = de), size = 3, alpha = .5, color = "grey") + 
+  geom_line(aes(y = de_smoothed), color = "red")
+```
+
+::: {.noteblock data-latex=""}
+It should be noted, however, that the graph above is not as smooth as before, although the data now provides better results.
+:::
+
+We calculate the _Root Mean Squared Error_ for the ultimately computed _UMGYDE Effect_ using the helper function [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above in the [UMGYDE Model: Helper Functions] section above as follows:
+```{r, eval=FALSE}
+lss.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(lss.UMGYD_effect)
+```
+
+Finally, we add the definitive result for the current model to our _Result Table_:
+```{r, eval=FALSE}
+RMSEs.ResultTibble.UMGYDE.tuned <- RMSEs.ResultTibble.UMGYDE2 |> 
+  RMSEs.AddRow("Tuned UMGYDE Best Model", 
+               lss.UMGYD_effect.RMSE,
+               comment = "UMGYDE Model computed using `loess` function call with the best degree & span values.")
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.UMGYDE.tuned)
+```
+
+Finally, let's regularize our tuned model as we did with the previous ones.
 
@@
 
-\newpage
+::: {.noteblock data-latex=""}
+Now, we have a better result than one for the previous model, but still insufficient to meet the Project Objective.
+:::
+
+\newpage

### 2025-06-02 r/src/capstone-movielens.main.R
The code cleaned up.

@@ -2394,14 +2394,6 @@ UMGYDE.rglr.fine_tune.results <-
                          cache.base_name,
                          regularize.test_lambda.UMGYD_effect.cv)
 
-# UMGYDE.rglr.fine_tune.results$tuned.result |>
-#   data.plot(title = TeX(r'[Fine-tune Stage results of the Regularization Process for the UMGYD Model.]'),
-#               xname = "parameter.value", 
-#               yname = "RMSE", 
-#               xlabel = TeX(r'[$\lambda$]'), 
-#               ylabel = "RMSE")
-# 
-
 put_log("Fine-tuning stage of the User+Movie+Genre+Year+(Smoothed)Day Effect Model Regularization 
 has ended up with with the following results:")
 put(UMGYDE.rglr.fine_tune.results$best_result)

### 2025-06-02 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
UMGYDE Model Analysis: complted.

@@
 
-#### UMGYDE Model Regularization: Support Functions
+#### UMGYDE Model Regularization: Helper Functions
 \
@@
 ::: { #func.regularize.test_lambda.UMGYD_effect.cv.details .sidebar }
-##### Details
+###### Details
 \
@@
 
+::: {.noteblock data-latex=""}
+The complete version of the source code shown in this section is available in the [UMGYDE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2322) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2322) script on _GitHub_.
+:::
+
 Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
@@
 ```{r, eval=FALSE}
+  lambdas <- seq(0, 256, 16)
+  cv.UMGYDE.preset.result <- 
+    tune.model_param(lambdas, regularize.test_lambda.UMGYD_effect.cv)
 ```
@@
 ```
-
-::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [UMGYDE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) script on _GitHub_.
-:::
 
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+The complete version of the source code shown in this section can be found in the [UMGYDE Model Regularization: Fine-tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2378) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2378) script on _GitHub_.
 :::
@@
 ```{r, eval=FALSE}
+endpoints <- 
+  get_fine_tune.param.endpoints(cv.UMGYDE.preset.result$tuned.result)
+
+UMGYDE.loop_starter <- c(endpoints["start"], 
+                        endpoints["end"], 
+                        8)
+
+cache.base_name <- "UMGYDE.rglr.fine-tuning"
+
+UMGYDE.rglr.fine_tune.results <- 
+  model.tune.param_range(UMGYDE.loop_starter,
+                         UMGYDE.rglr.fine_tune.cache.path,
+                         cache.base_name,
+                         regularize.test_lambda.UMGYD_effect.cv)
 ```
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section are available in the [Re-train Regularized UMGYDE Model for the best `lambda`](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1589) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1589) script on _GitHub_.
-:::
-
-Now, we can calculate the _Regularized UMGYDE Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
-
-```{r, eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-Here we use the helper function [train_UMGYD_effect](#func.train_UMGYD_effect) described above in the [UMGYDE Model Regularization: Support Functions] section.
-:::
-
-We calculate the _Root Mean Squared Error_ for the ultimately computed _UMGYDE Effect_ using the helper function [calc_UMGYD_effect_RMSE.cv](#func.calc_UMGYD_effect_RMSE.cv) described above in the [UMGYDE Model Regularization: Support Functions] section as follows:
-```{r, eval=FALSE}
-```
-
-Finally, we add the definitive result for the current model to our _Result Table_:
-```{r, eval=FALSE}
-```
-```{r}
-```
-
-::: {.noteblock data-latex=""}
-Now, we have a better result than one for the previous model, but still insufficient to meet the Project Objective.
-:::
-
-\newpage
+The complete version of the source code shown in this section is available in the [UMGYDE Regularized Model: Retraining with the best params](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2417) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2417) script on _GitHub_.
+:::
+
+Now, we can compute the _Regularized UMGYDE Effect_ by re-training our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we have just figured out and use it in subsequent analysis.
+
+The most significant part of the code for this operation is shown below: 
+```{r, eval=FALSE}
+  best_result <- UMGYDE.rglr.fine_tune.results$best_result
+  UMGYDE.rglr.best_lambda <- best_result["param.best_value"]
+  UMGYDE.rglr.best_RMSE <- best_result["best_RMSE"]
+
+  put_log1("Re-training Regularized User+Movie+Genre+Year+(Smoothed)Day Effect Model for the best `lambda`: %1...",
+           UMGYDE.rglr.best_lambda)
+
+  rglr.UMGYD_effect <- edx |> 
+    regularize.train_UMGYD_effect(UMGYDE.rglr.best_lambda)
+```
+```{r}
+  str(rglr.UMGYD_effect)
+```
+
+::: {.noteblock data-latex=""}
+Here we use the helper function [regularize.train_UMGYD_effect](#func.regularize.train_UMGYD_effect) described above in the [UMGYDE Model: Helper Functions] section.
+:::
+
+We calculate the _Root Mean Squared Error_ for the ultimately computed _Regularized UMGYDE Effect_ using the helper function [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above in the [UMGYDE Model: Helper Functions] section as follows:
+```{r, eval=FALSE}
+  rglr.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(rglr.UMGYD_effect)
+```
+
+As always, we add the definitive result for the current model to our _Result Table_:
+```{r, eval=FALSE}
+RMSEs.ResultTibble.UMGYDE.rglr.tuned <- RMSEs.ResultTibble.UMGYDE.tuned |> 
+  RMSEs.AddRow("Regularized UMGYDE Model", 
+               rglr.UMGYD_effect.RMSE,
+               comment = "The best tuned and regularized UMGYDE Model.")
+```
+```{r}
+RMSE_kable(RMSEs.ResultTibble.UMGYDE.rglr.tuned)
+```
+
+::: {.noteblock data-latex=""}
+Now, we have a better result than the ones for the previous models, but still insufficient to meet the Project Objective. Let's see what else we can do to achieve our ultimate goal. 
+:::
+
+\newpage
+
+#### UMGYDE Model: Final Holdout Test (Preliminary Assesment)
+
+::: {.noteblock data-latex=""}
+The complete version of the source code shown in this section is available in the [UMGYDE Model: Final Holdout Test](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2498) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2498) script on _GitHub_.
+:::
+
+Let's see what we have achieved so far, using the `final_holdout_test` dataset for the first time.
+Firstly, we compute predictions for our current model:
+```{r, eval=FALSE}
+final.UMGYDE.predicted <- final_holdout_test |>
+  UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
+```
+```{r}
+str(final.UMGYDE.predicted)
+```
+::: {.noteblock data-latex=""}
+Here we use the helper function [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) described above in the [UMGYDE Model: Helper Functions] section.
+:::
+
+Then we compute the _RMSE_ and add the result to our _Result Table_:
+```{r, eval=FALSE}
+final.UMGYDE.predicted.RMSE <- rmse2(final_holdout_test$rating,
+                                     final.UMGYDE.predicted$predicted)
+
+final.RMSEs.ResultTibble.UMGYDE.rglr.tuned <- RMSEs.ResultTibble.UMGYDE.rglr.tuned |> 
+  RMSEs.AddRow("Best UMGYDE Model (Final Test)", 
+               final.UMGYDE.predicted.RMSE,
+               comment = "Final Holdout Test of the best tuned and regularized UMGYDE Model.")
+```
+```{r}
+RMSE_kable(final.RMSEs.ResultTibble.UMGYDE.rglr.tuned)
+```
+
+::: {.noteblock data-latex=""}
+Here we use the helper function [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) to calculate the _RMSE_ that is defined in the  [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L18) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) script on _GitHub_.
+:::
+
+::: {.noteblock data-latex=""}
+As expected, we have not achieved a result that is good enough to meet our _Project Objective_.
+:::
+
+\newpage

### 2025-06-02 reports/capstone-movielens.site/04.appendix.Rmd
UMGYDE Model Analysis: complted.

@@
 
-Plots a graph based on the dataset passed in the [data](#func.data.plot.left.n.params.data) parameter, using both points and a line.
+Plots a graph based on the first $n$ rows (the $n$ is specified by the [left.n](#func.data.plot.left.n.params.left.n) parameter) of the dataset passed in the [data](#func.data.plot.left.n.params.data) parameter, using both points and a line.
+
+::: {.noteblock data-latex=""}
+The dataset passed in the [data](#func.data.plot.left.n.params.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.params.xname) parameter).
+:::
 
@@
 ::: { #func.data.plot.left.n.params.data .sidebar }
-  - **data:** Dataset to use for the plot;
+  - **data:** Dataset to use for the plot.
+
+:::
+::: { #func.data.plot.left.n.params.left.n .sidebar }
+  - **left.n:** If a positive numeric value, specifies the number of the first rows of the dataset to plot. Otherwise, the entire dataset data is set to plot.
 
@@
 ::: { #func.data.plot.left.n.params.title .sidebar }
-  - **title:** Title of the plot;
+  - **title:** Title of the plot.
 
@@
 ::: { #func.data.plot.left.n.params.xname .sidebar }
-  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;
+  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot.
 
@@
 ::: { #func.data.plot.left.n.params.yname .sidebar }
-  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;
+  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot.
 
@@
 ::: { #func.data.plot.left.n.params.xlabel .sidebar }
-  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
+  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label.
 
@@
 ::: { #func.data.plot.left.n.params.ylabel .sidebar }
-  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;
+  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.
 
@@
 ::: { #func.data.plot.left.n.params.line_col .sidebar }
-  - **line_col = blue:** The line color;
+  - **line_col = blue:** The line color.
 
@@
 
-The function is a wrapper for the [data.plot](#func.data.plot) function described above and is a simple and convenient tool for more detailed visualizing the left part of the graph.
-
+The function is a wrapper for the [data.plot](#func.data.plot) function described above and is a simple and convenient tool for more detailed visualization of the left part of the graph, initially built based on the entire data set passed in the [data](#func.data.plot.left.n.params.data) parameter.
 :::
@@
 
-The soure code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) function is shown below:
+The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) function is shown below:
 ```{r eval=FALSE}
@@
 
-Plots a graph based on the dataset passed in the [data](#func.data.plot.left_detailed.params.data) parameter, using both points and a line.
+Combines two graphs plotted by the internally called helper functions in a grid: the first is a standard graph plotted by the [data.plot](#func.data.plot) function described above, the second is a graph based on the first $n$ rows (the $n$ is specified by the [left.n](#func.data.plot.left.n.params.left.n) parameter) of the dataset plotted by the [data.plot.left.n](#func.data.plot.left.n) function also described above (The data for both graphs is passed in the [data]).(#func.data.plot.left.n.params.data) parameter).
+
+::: {.noteblock data-latex=""}
+The dataset passed in the [data](#func.data.plot.left.n.params.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.params.xname) parameter).
+:::
 
@@
 ::: { #func.data.plot.left_detailed.params.data .sidebar }
-  - **data:** Dataset to use for the plot;
+  - **data:** Dataset to use for the plot.
+
+:::
+::: { #func.data.plot.left.n.params.left.n .sidebar }
+  - **left.n:** If a positive numeric value, specifies the number of the first rows of the dataset to plot. Otherwise, the entire dataset data is set to plot.
 
@@
 ::: { #func.data.plot.left_detailed.params.title .sidebar }
-  - **title:** Title of the plot;
+  - **title:** Title of the plot.
 
@@
 ::: { #func.data.plot.left_detailed.params.xname .sidebar }
-  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;
+  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot.
 
@@
 ::: { #func.data.plot.left_detailed.params.yname .sidebar }
-  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;
-
-:::
-::: { #func.data.plot.left_detailed.params.xlabel .sidebar }
-  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
-
-:::
-::: { #func.data.plot.left_detailed.params.ylabel .sidebar }
-  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;
+  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot.
+
+:::
+::: { #func.data.plot.left_detailed.params.xlabel1 .sidebar }
+  - *xlabel1 = NULL*:** The $x$ axis label for the first plot. If `NULL`, the value of the `xname` parameter is used for the label.
+
+:::
+::: { #func.data.plot.left_detailed.params.xlabel2 .sidebar }
+  - *xlabel2 = NULL*:** The $x$ axis label for the second plot. If `NULL`, the value of the `xname` parameter is used for the label.
+
+:::
+::: { #func.data.plot.left_detailed.params.ylabel1 .sidebar }
+  - **ylabel1 = NULL:** The $y$ axis label for the first plot. If `NULL`, the value of the `yname` parameter is used for the label.
+
+:::
+::: { #func.data.plot.left_detailed.params.ylabel2 .sidebar }
+  - **ylabel2 = NULL:** The $y$ axis label for the second plot. If `NULL`, the value of the `yname` parameter is used for the label.
 
@@
 ::: { #func.data.plot.left_detailed.params.line_col .sidebar }
-  - **line_col = blue:** The line color;
+  - **line_col = blue:** The line color.
 
@@
 
-The function is a wrapper for the [data.plot.left.n](#func.data.plot.left.n) function described above and is a simple and convenient tool for more detailed visualizing the left part of the graph.
-
+Under the hood, the function calls internally the [data.plot](#func.data.plot) and [data.plot.left.n](#func.data.plot.left.n) functions (described above) to build two graphs and combines them into a grid.
 :::

### 2025-06-03 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Started working on new model: model template added.
MF: Mathematical Description section completed.

@@
 
-To account for a _genre effect_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_[@IDS2_23-7]:
+To account for a _genre effect_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter 23 "Regularization" of the Course Textbook_[@IDS2_23-7]:
 
@@
 \begin{equation}
-\hat{g}_{i,j}(\lambda) = \frac{1}{\lambda + n_g} \sum_{i=1}^{n_{g}} \left(Y_{i,j} - \mu - \alpha_i - \beta_j\right)
+\hat{g}_{i,j}(\lambda) = \frac{1}{\lambda + n_g} \sum_{r=1}^{n_{g}} \left(Y_{i,j} - \mu - \alpha_i - \beta_j\right)
 (\#eq:GE-regularized)

### 2025-06-03 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
MF: Mathematical Description section completed.

@@
 #### UMGYDE Model: Final Holdout Test (Preliminary Assesment)
+\
 
@@
 ```
+
+::: {.noteblock data-latex=""}
+Here we use the helper function [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) to calculate the _RMSE_ that is defined in the  [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L18) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) script on _GitHub_.
+:::
+
+And finally, we print out the results:
 ```{r}
@@
 ::: {.noteblock data-latex=""}
-Here we use the helper function [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) to calculate the _RMSE_ that is defined in the  [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L18) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) script on _GitHub_.
-:::
-
-::: {.noteblock data-latex=""}
 As expected, we have not achieved a result that is good enough to meet our _Project Objective_.
@@
 
-\newpage
+As explained in the [Chapter 24 `Matrix Factorization`](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/matrix-factorization.html) of the _Course Textbook_, so far our models _"ignore an important source of information related to the fact that groups of movies have similar rating patterns and groups of users have similar rating patterns as well..."_ [@IDS2_24]
+
+Then the author shows that in this case, the _Matrix Factorization_ method can considerably improve our results.
+In the next section, we will apply this method to our current model and see what we get.
+
+\newpage

### 2025-06-03 reports/capstone-movielens.site/02.8-1.MF.UMGYDE-model.Rmd
MF: Mathematical Description section completed.

@@
-### UMGYDE Model: Matrix Factorization
+## UMGYDE Model: Matrix Factorization (MF)
 \
 
+For our next solution, we will use the [`recosystem` package](https://cran.r-project.org/web/packages/recosystem/index.html) to perform the _Parallel Matrix Factorization_.
+
+### MF: Matematical Description
+\
+
+As outlined in [this article](https://cran.r-project.org/web/packages/recosystem/vignettes/introduction.html)[@yqiu_recosystem230505], the idea of the _Matrix Factorization_ method is to approximate the whole rating matrix $R_{m \times n}$ by the product of two matrices of lower dimensions, $P_{n \times k}$ and $Q_{n\times k}$, such that
+
+\begin{equation}
+\mathbb{R} \approx \mathbb{PQ^T}
+(\#eq:R-PQ-MF)
+\end{equation}
+
+In relation to our model, the expression \@ref(eq:R-PQ-MF) will take the form:
+
+\begin{equation}
+\mathbf{R} \thicksim \mathbf{\hat{R}} + \mathbf{PQ^T} +  \varepsilon
+(\#eq:UMGYDE-MF)
+\end{equation}
+
+where:
+
+  - $\mathbf{R}$ is the $U_\mathrm{m} \times M_n$ rating matrix with $U_m$ users and $M_n$ movies;
+  - $\mathbf{\hat{R}}$ represents the predictions from our best model: _Regularized UMGYDE Model_;
+  - $\mathbf{P}$ and $\mathbf{Q}$ are $P_{m \times k}$ and $Q_{n \times k}$ matrices, respectively, where $k$ is the number of _latent features_ to be found.
+
+If we denote the $u$-th row of $\mathbf{P}$ as $\mathbf{p}_u$ and the $v$-th row of $\mathbf{Q}$ as $\mathbf{q}_v$, then the unknown rating $\mathbf{r}_{u,v}$ given by user $u$ on movie item $v$ for our model can be estimated as $\hat{\mathbf{r}}_{u,v} + \mathbf{p}_{u}\mathbf{q}^T_{v}$, where the $\hat{\mathbf{r}}_{u,v}$ is the prediction given by our last _Regularized UMGYDE Model_.
+
+A typical solution for $\mathbf{P}$ and $\mathbf{Q}$ is given by the following optimization problem [@chin_FPSGM_MF_SMS2015a; @chin_LRS_SGM_MF2015b]:
+
+$$
+\begin{array}{cc} min \\
+\tiny{P,Q} \end{array} \sum_{(u,v)\in R}[f(\mathbf{p}_u, \mathbf{q}_v; \mathbf{r}_{u,v}) + \mu_P\parallel\mathbf{p}_u\parallel_1 + \mu_Q\parallel\mathbf{q}_v\parallel_1 + \frac{\lambda_P}2\parallel\mathbf{p}_u\parallel^2_2 + \frac{\lambda_Q}2\parallel\mathbf{q}_v\parallel^2_2]
+$$
+
+where $(u, v)$ are locations of observed entries in $\mathbf{R}, \mathbf{r}_{u,v}$ is the observed ratings, $f$ is the loss function, and $\mu_P$, $\mu_Q$, $\lambda_P$, $\lambda_Q$ are penalty parameters to avoid overfitting.[@yqiu_recosystem230505]
+
+::: { custom-style="blockquote" } 
+> _The process of solving the matrices $P$ and $Q$ is referred to as model training, and the selection of penalty parameters is called parameter tuning.
+In `recosystem`, we provide convenient functions for these two tasks, and additionally have functions for model exporting (outputting $P$ and $Q$ matrices) and prediction._[@yqiu_recosystem230505]
+
+:::
+
 \newpage
+
+### MF: Helper Funtions
+
+\newpage

### 2025-06-03 r/src/capstone-movielens.main.R

@@ -2553,7 +2553,7 @@ log_close()
 
 ### Open log for MF ------------------------------------------------------------
 open_logfile(".matrix-factorization")
-### MF: Support Functions ------------------------------------------------------
+### MF: Helper Functions ------------------------------------------------------
 MF.functions.file <- "MF.functions.R"
 MF.functions.file_path <- file.path(support_functions.path, 
                                     MF.functions.file)

### 2025-06-03 r/src/support-functions/common-helper.functions.R

@@ -44,7 +44,7 @@ RMSEs.AddRow <- function(RMSEs, method, value, comment = ""){
 RMSE_kable <- function(RMSEs,
                        col1width = 15,
                        col2width = 5,
-                       col3width = 32){
+                       col3width = 30){
   RMSEs |>
     kable(align='lcl', booktabs = T, padding = 5) |> 
     row_spec(0, bold = T) |>

### 2025-06-04 reports/capstone-movielens.site/02.8-1.MF.UMGYDE-model.Rmd
Matrix Factorization: Helper functions described.

@@
 
-### MF: Helper Funtions
+### MF: Helper Functions
+
+#### [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) Function {#func.mf.residual.dataframe}
+\
+
+::: { #func.mf.residual.dataframe.params.description .sidebar }
+##### Description
+\
+
+Computes residuals, defined as the difference between the observed and predicted values of the fully trained _UMGYDE Model_ as described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section.
+
+##### Parameters
+\
+
+###### ***train_set***
+\
+
+::: { #func.mf.residual.dataframe.params.train_set .sidebar }
+The dataset to be trained.
+:::
+
+##### Source Code
+\
+
+The folowing is the source code of the function:
+```{r eval=FALSE}
+mf.residual.dataframe <- function(train_set){
+  train_set |> 
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(rglr.UMGY_effect, by='year') |>
+    left_join(rglr.UMGYD_effect, by='days') |>
+    mutate(rsdl = rating - (mu + a + b + g + ye + de_smoothed)) |>
+    select(userId, movieId, rsdl)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) script on _GitHub_.
+:::
+
+##### Return
+\
+
+A data frame object containing the residuals (see the [Description](#func.mf.residual.dataframe.params.description) above for the details).
+
+#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) Function {#func.UMGYDE_model.predict}
+\
+
+This is a wrapper for the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [UMGYDE Model: Helper Functions] section above with the fixed [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect) parameter value obtained after the _UMGYDE Model_ (described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section)  has been fully trained.
+
+##### Parameters
+\
+
+::: { #func.UMGYDE_model.predict.params.test_set .sidebar }
+###### ***test_set***
+\
+
+The dataset for testing the _UMGYDE Model_ after it has been fully trained.
+:::
+
+##### Source Code
+\
+
+The following is the source code of the function:
+```{r eval=FALSE}
+UMGYDE_model.predict <- function(test_set) {
+  test_set |>
+    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) script on _GitHub_.
+:::
+
+##### Return
+\
+
+A data frame object containing predicted values.
 

### 2025-06-04 r/src/capstone-movielens.main.R

@@ -2579,9 +2579,7 @@ if (file.exists(file_path_tmp)) {
   put_log1("Overall mean rating data has been loaded from file: %1",
            file_path_tmp)
 } else {
-  mf.edx.residual <- mf.residual.dataframe(edx) #|>
-    #pull(rsdl)
-  
+  mf.edx.residual <- mf.residual.dataframe(edx)
   str(mf.edx.residual)
   sum(is.na(mf.edx.residual))
   #> [1] 0

### 2025-06-04 r/src/support-functions/MF.functions.R

@@ -1,5 +1,5 @@
-mf.residual.dataframe <- function(data){
-  data |> 
+mf.residual.dataframe <- function(train_set){
+  train_set |> 
     left_join(edx.user_effect, by = "userId") |>
     left_join(rglr.UM_effect, by = "movieId") |>
     left_join(rglr.UMG_effect, by = "movieId") |>
@@ -8,7 +8,6 @@ mf.residual.dataframe <- function(data){
     left_join(rglr.UMGYD_effect, by='days') |>
     mutate(rsdl = rating - (mu + a + b + g + ye + de_smoothed)) |>
     select(userId, movieId, rsdl)
-    #filter(!is.na(rsdl)) 
 }
 UMGYDE_model.predict <- function(test_set) {
   test_set |>

### 2025-06-04 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Methods section completed.

@@
 
-#### UMGYDE Model: Final Holdout Test (Preliminary Assesment)
+#### UMGYDE Model: Final Holdout Test (Preliminary Assessment)
 \
@@
 ::: {.noteblock data-latex=""}
-As expected, we have not achieved a result that is good enough to meet our _Project Objective_.
+As expected, we have not yet achieved a result that meets our Project Objective.
 :::

### 2025-06-04 reports/capstone-movielens.site/04.appendix.Rmd
Methods section completed.

@@
 ```
-
-\newpage
-
-## Support Functions
-\
-
-### [fname00]() Function {#func.fname00}
-\
-
-::: { #func.fname00.Usage .sidebar }
-#### Usage
-\
-
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname00.params .sidebar }
-#### Parameters
-\
-
-::: { #func.fname00.params.p1 .sidebar }
-  - **p1:** description;
-
-:::
-::: { #func.fname00.params.2 .sidebar }
-  - **p2:** description.
-
-:::
-:::
-
-::: { #func.fname00.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname00.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname00.code .sidebar }
-#### Source Code
-\
-
-The soure code of the [fname00]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [fname00]() is also available in the [Some.Section]() section of the [Somefunctions.R]() script.
-:::
-:::
-
-### [fname01]() Function {#func.fname01}
-\
-
-::: { #func.fname01.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname01.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname01.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname01.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname01.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
-### [fname02]() Function {#func.fname02}
-\
-
-::: { #func.fname02.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname02.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname02.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname02.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname02.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
-### [fname0]() Function {#func.fname0}
-\
-
-::: { #func.fname0.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname0.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname0.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname0.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L95) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) script.
-:::
-:::
-
-### [fname03]() Function {#func.fname03}
-\
-
-::: { #func.fname03.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname03.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname03.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname03.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname03.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [fname1]() Function {#func.fname1}
-\
-
-::: { #func.fname1.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname1.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname1.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname1.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname1.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-## Other Function Templates
-\
-
-### [fname2]() Function {#func.fname2}
-\
-
-::: { #func.fname2.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname2.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname2.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname2.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname2.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [fname3]() Function {#func.fname3}
-\
-
-::: { #func.fname3.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname3.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname3.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname3.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname3.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [fname4]() Function {#func.fname4}
-\
-
-::: { #func.fname4.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname4.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname4.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname4.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname4.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [fname5]() Function {#func.fname5}
-\
-
-::: { #func.fname5.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname5.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname5.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname5.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname5.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [fname6]() Function {#func.fname6}
-\
-
-::: { #func.fname6.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname6.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname6.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname6.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname6.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [fname7]() Function {#func.fname7}
-\
-
-::: { #func.fname7.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname7.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname7.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname7.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname7.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::
-
-### [fname8]() Function {#func.fname8}
-\
-
-::: { #func.fname8.signature .sidebar }
-#### Signature
-\
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.fname8.params .sidebar }
-#### Parameters
-\
-  - **param1:** description; 
-  - **param2:** description.
-
-:::
-
-::: { #func.fname8.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.fname8.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.fname8.code .sidebar }
-#### Source Code
-\
-The soure code of the [function]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the []() is also available in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-:::

### 2025-06-04 reports/capstone-movielens.site/bak/02.8-1.MF.UMGYDE-model.bak.Rmd
Methods section completed.

--- 2025-06-04 reports/capstone-movielens.site/02.8-1.MF.UMGYDE-model.Rmd
@@
 $$
-\begin{array}{cc} min \\
-\tiny{P,Q} \end{array} \sum_{(u,v)\in R}[f(\mathbf{p}_u, \mathbf{q}_v; \mathbf{r}_{u,v}) + \mu_P\parallel\mathbf{p}_u\parallel_1 + \mu_Q\parallel\mathbf{q}_v\parallel_1 + \frac{\lambda_P}2\parallel\mathbf{p}_u\parallel^2_2 + \frac{\lambda_Q}2\parallel\mathbf{q}_v\parallel^2_2]
+\begin{array}{c} {\scriptscriptstyle min} \\
+{\scriptscriptstyle P,Q} \end{array} \sum_{(u,v)\in R}[f(\mathbf{p}_u, \mathbf{q}_v; \mathbf{r}_{u,v}) + \mu_P\parallel\mathbf{p}_u\parallel_1 + \mu_Q\parallel\mathbf{q}_v\parallel_1 + \frac{\lambda_P}2\parallel\mathbf{p}_u\parallel^2_2 + \frac{\lambda_Q}2\parallel\mathbf{q}_v\parallel^2_2]
 $$
@@
 
+\newpage
+
 #### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) Function {#func.UMGYDE_model.predict}
@@
 \newpage
+
+### MF: Performing Operation
+
+::: {.noteblock data-latex=""}
+The complete source code shown in this section is available in the [Perform the Matrix Factorization & Final Test](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2567) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2567) script on _GitHub_.
+:::
+
+We assume that the _Matrix Factorization_ method is going to be the last one to provide sufficient results, so we will use the entire `edx` dataset as a _Training Set_ and `final_holdout_test` as a _Test Set_ for our final model, skipping the intermediate _train/test_ operations on the split _train/validation_ datasets.
+
+#### MF: Getting Residuals From the UMGYDE Model Prediction Values
+\
+
+First, we get residuals from the _UMGYDE Model_ prediction values using the [mf.residual.dataframe](#func.mf.residual.dataframe) function described above:
+```{r, eval=FALSE}
+  mf.edx.residual <- mf.residual.dataframe(edx)
+```
+```{r}
+  str(mf.edx.residual)
+```
+#### MF: Transforming Input Data to Be Compatible With the `recosystem` Package
+\
+
+Now, let's convert the residuals data and `final_holdout_test` dataset to the input data compatible with the [recosystem](https://cran.r-project.org/web/packages/recosystem/index.html) package to process:
+```{r, eval=FALSE}
+  set.seed(5430)
+  mf.edx.residual.reco <- with(mf.edx.residual, 
+                               data_memory(user_index = userId, 
+                                           item_index = movieId,
+                                           rating = rsdl))
+
+  final_holdout_test.reco <- with(final_holdout_test, 
+                          data_memory(user_index = userId, 
+                                      item_index = movieId, 
+                                      rating = rating))
+```
+```{r}
+str(mf.edx.residual.reco)
+str(final_holdout_test.reco)
+```
+
+#### MF: Creating and Tuning the `Reco` Object
+\
+
+We then create a `reco` object of the `Reco` class and tune it using the `reco$tune` method, passing to it as a `train_data` parameter residual data prepared in the previous step:
+```{r, eval=FALSE}
+  reco <- Reco()
+
+  reco.tuned <- reco$tune(mf.edx.residual.reco, opts = list(dim = c(10, 20, 30),
+                                                lrate    = c(0.1, 0.2),
+                                                nthread  = 4,
+                                                niter    = 10,
+                                                verbose  = TRUE))
+```
+```{r}
+str(reco)
+str(reco.tuned)
+```
+
+#### MF: Final Training
+\
+
+Finally, we train the model for the last time using the `reco$train` method, passing to it as a `train_data` parameter the same residual data we used for the tuning:
+```{r, eval=FALSE}
+  reco$train(mf.edx.residual.reco, opts = c(reco.tuned$min,
+                                       niter = 20, 
+                                       nthread = 4)) 
+```
+
+#### MF: Final Holdout Test
+\
+
+From now on, we will work with the `final_holdout_test` dataset for the final testing of our model, obtaining final predictions, and computing the _Root Mean Squared Error_.
+
+First, we get the final predictions combining the predicted residuals from the `reco` objects and predicted values we lastly get from the _UMGYDE Model_ as described in the [UMGYDE Model: Final Holdout Test (Preliminary Assessment)] section:
+```{r, eval=FALSE}
+  mf.reco.residual <- reco$predict(final_holdout_test.reco, out_memory())
+
+  mf.predicted_ratings <- 
+    clamp(final.UMGYDE.predicted$predicted + mf.reco.residual)
+```
+```{r}
+str(mf.reco.residual)
+str(mf.predicted_ratings)
+```
+Next, we compute the _RMSE_ using the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) custom helper function, already mentioned above in the [UMGYDE Model: Final Holdout Test (Preliminary Assessment)] section, and add the result to our _Result Table_:
+```{r, eval=FALSE}
+final_holdout_test.RMSE <- rmse2(final_holdout_test$rating,
+                                     mf.predicted_ratings)
+```
+
+::: {.noteblock data-latex=""}
+The function [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) is defined in the  [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L18) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) script on _GitHub_.
+:::
+
+And add the result to our _Result Table_:
+```{r, eval=FALSE}
+final.MF.RMSEs.ResultTibble <- final.RMSEs.ResultTibble.UMGYDE.rglr.tuned |> 
+  RMSEs.AddRow("MF (Final Test)", 
+               final_holdout_test.RMSE,
+               comment = "Matrix Factorization of the Best Model Residuals, Final Holdout Test")
+```
+```{r}
+RMSE_kable(final.MF.RMSEs.ResultTibble)
+```
+
+::: {.noteblock data-latex=""}
+Finally, we have reached our ultimate goal, since the _Root Mean Squared Error_ we obtained has achieved the required _Project Objective_.
+:::
+
+\newpage

### 2025-06-04 r/src/capstone-movielens.main.R

@@ -2589,14 +2589,12 @@ if (file.exists(file_path_tmp)) {
                                data_memory(user_index = userId, 
                                            item_index = movieId,
                                            rating = rsdl))
-                                           # index1 = TRUE))
-  
+
   final_holdout_test.reco <- with(final_holdout_test, 
                           data_memory(user_index = userId, 
                                       item_index = movieId, 
                                       rating = rating))
-  ## index1 = TRUE))
-  
+
   reco <- Reco()
   
   reco.tuned <- reco$tune(mf.edx.residual.reco, opts = list(dim = c(10, 20, 30),
@@ -2626,7 +2624,11 @@ if (file.exists(file_path_tmp)) {
   put_log1("Saving User+Movie+Genre+Year+(Smoothed)Day Effect Model data to file: %1...", 
            file_path_tmp)
   start <- put_start_date()
-  save(mf.reco.residual,
+  save(mf.edx.residual,
+       mf.edx.residual.reco,
+       final_holdout_test.reco,
+       reco.tuned,
+       mf.reco.residual,
        final.UMGYDE.predicted,
        mf.predicted_ratings,
        file = file_path_tmp)

### 2025-06-04 reports/capstone-movielens.site/04.appendix.Rmd
Methods section completed and .pdf report rendered.

@@
 
-### [data.helper.func0]() Function {#func.data.helper.func0}
-\
-
-::: { #func.data.helper.func0.Usage .sidebar }
-#### Usage
-\
-
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.data.helper.func0.params .sidebar }
-#### Parameters
-\
-
-::: { #func.data.helper.func0.params.p1 .sidebar }
-  - **p1:** description;
-
-:::
-::: { #func.data.helper.func0.params.2 .sidebar }
-  - **p2:** description.
-
-:::
-:::
-
-::: { #func.data.helper.func0.details .sidebar }
-#### Details
-\
-
-::: {.noteblock data-latex=""}
-Note 
-:::
-:::
-
-::: { #func.data.helper.func0.value .sidebar }
-#### Value
-\
-
-:::
-
-::: { #func.data.helper.func0.code .sidebar }
-#### Source Code
-\
-
-The soure code of the [data.helper.func0]() function is shown below:
-```{r eval=FALSE}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [data.helper.func0]() is also available in the [Some.Section]() section of the [Somefunctions.R]() script.
-:::
-:::
+\newpage
 

### 2025-06-04 reports/capstone-movielens.site/02.8-1.MF.UMGYDE-model.Rmd

@@
 $$
-\begin{array}{cc} min \\
-\tiny{P,Q} \end{array} \sum_{(u,v)\in R}[f(\mathbf{p}_u, \mathbf{q}_v; \mathbf{r}_{u,v}) + \mu_P\parallel\mathbf{p}_u\parallel_1 + \mu_Q\parallel\mathbf{q}_v\parallel_1 + \frac{\lambda_P}2\parallel\mathbf{p}_u\parallel^2_2 + \frac{\lambda_Q}2\parallel\mathbf{q}_v\parallel^2_2]
+\begin{array}{c} { min} \\
+{\scriptstyle P,Q} \end{array} \sum_{(u,v)\in R}[f(\mathbf{p}_u, \mathbf{q}_v; \mathbf{r}_{u,v}) + \mu_P\parallel\mathbf{p}_u\parallel_1 + \mu_Q\parallel\mathbf{q}_v\parallel_1 + \frac{\lambda_P}2\parallel\mathbf{p}_u\parallel^2_2 + \frac{\lambda_Q}2\parallel\mathbf{q}_v\parallel^2_2]
 $$
@@
 \newpage
+
+### MF: Performing Operation
+
+::: {.noteblock data-latex=""}
+The complete source code shown in this section is available in the [Perform the Matrix Factorization & Final Test](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2567) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2567) script on _GitHub_.
+:::
+
+We assume that the _Matrix Factorization_ method is going to be the last one to provide sufficient results, so we will use the entire `edx` dataset as a _Training Set_ and `final_holdout_test` as a _Test Set_ for our final model, skipping the intermediate _train/test_ operations on the split _train/validation_ datasets.
+
+#### MF: Getting Residuals From the UMGYDE Model Prediction Values
+\
+
+First, we get residuals from the _UMGYDE Model_ prediction values using the [mf.residual.dataframe](#func.mf.residual.dataframe) function described above:
+```{r, eval=FALSE}
+  mf.edx.residual <- mf.residual.dataframe(edx)
+```
+```{r}
+  str(mf.edx.residual)
+```
+#### MF: Transforming Input Data to Be Compatible With the `recosystem` Package
+\
+
+Now, let's convert the residuals data and `final_holdout_test` dataset to the input data compatible with the [recosystem](https://cran.r-project.org/web/packages/recosystem/index.html) package to process:
+```{r, eval=FALSE}
+  set.seed(5430)
+  mf.edx.residual.reco <- with(mf.edx.residual, 
+                               data_memory(user_index = userId, 
+                                           item_index = movieId,
+                                           rating = rsdl))
+
+  final_holdout_test.reco <- with(final_holdout_test, 
+                          data_memory(user_index = userId, 
+                                      item_index = movieId, 
+                                      rating = rating))
+```
+```{r}
+str(mf.edx.residual.reco)
+str(final_holdout_test.reco)
+```
+
+#### MF: Creating and Tuning the `Reco` Object
+\
+
+We then create a `reco` object of the `Reco` class and tune it using the `reco$tune` method, passing to it as a `train_data` parameter residual data prepared in the previous step:
+```{r, eval=FALSE}
+  reco <- Reco()
+
+  reco.tuned <- reco$tune(mf.edx.residual.reco, opts = list(dim = c(10, 20, 30),
+                                                lrate    = c(0.1, 0.2),
+                                                nthread  = 4,
+                                                niter    = 10,
+                                                verbose  = TRUE))
+```
+```{r}
+str(reco)
+str(reco.tuned)
+```
+
+#### MF: Final Training
+\
+
+Finally, we train the model for the last time using the `reco$train` method, passing to it as a `train_data` parameter the same residual data we used for the tuning:
+```{r, eval=FALSE}
+  reco$train(mf.edx.residual.reco, opts = c(reco.tuned$min,
+                                       niter = 20, 
+                                       nthread = 4)) 
+```
+
+#### MF: Final Holdout Test
+\
+
+From now on, we will work with the `final_holdout_test` dataset for the final testing of our model, obtaining final predictions, and computing the _Root Mean Squared Error_.
+
+First, we get the final predictions combining the predicted residuals from the `reco` objects and predicted values we lastly get from the _UMGYDE Model_ as described in the [UMGYDE Model: Final Holdout Test (Preliminary Assessment)] section:
+```{r, eval=FALSE}
+  mf.reco.residual <- reco$predict(final_holdout_test.reco, out_memory())
+
+  mf.predicted_ratings <- 
+    clamp(final.UMGYDE.predicted$predicted + mf.reco.residual)
+```
+```{r}
+str(mf.reco.residual)
+str(mf.predicted_ratings)
+```
+Next, we compute the _RMSE_ using the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) custom helper function, already mentioned above in the [UMGYDE Model: Final Holdout Test (Preliminary Assessment)] section:
+```{r, eval=FALSE}
+final_holdout_test.RMSE <- rmse2(final_holdout_test$rating,
+                                     mf.predicted_ratings)
+```
+
+::: {.noteblock data-latex=""}
+The function [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) is defined in the  [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L18) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) script on _GitHub_.
+:::
+
+And add the result to our _Result Table_:
+```{r, eval=FALSE}
+final.MF.RMSEs.ResultTibble <- final.RMSEs.ResultTibble.UMGYDE.rglr.tuned |> 
+  RMSEs.AddRow("MF (Final Test)", 
+               final_holdout_test.RMSE,
+               comment = "Matrix Factorization of the Best Model Residuals, Final Holdout Test")
+```
+```{r}
+RMSE_kable(final.MF.RMSEs.ResultTibble)
+```
+
+::: {.noteblock data-latex=""}
+Finally, we have reached our ultimate goal, since the _Root Mean Squared Error_ we obtained has achieved the required _Project Objective_.
+:::
+
+\newpage

### 2025-06-06 reports/capstone-movielens.site/03.conclusion.Rmd
Working on Conclution section (in progress)

@@
 
-Hello Conclusion!
+In this project, a _Machine Learning Algorithm_ was successfully developed for a _Recommender System_ (hereinafter referred to as _RS MLA_) to predict movie ratings using the [10M version of the MovieLens](http://grouplens.org/datasets/movielens/10m/) dataset.
 
-This is a great conclusion, isn't it?!!
+Since it was needed to convert the original dataset into a _Data Source_, suitable for processing by the _RS MLA_, a package [edx.capstone.movielens.data], specifically designed for this purpose, was developed and used, providing the _RS MLA_ with the necessary datasets.
+
+Following the Netflix Grand Prize Contest requirements, the _Root Mean Squared Error (RMSE)_ metric was used to evaluate the accuracy of our models.
+
+By incorporating essential factors such as overall average rating, movie, user, and some other observable effects, as well as efficient techniques such as _Regularization_ and _Matrix Factorization_ methods, the accuracy was significantly improved compared to the baseline model.
+
+The baseline model was the _Overall Mean Rating_ model described in the [Overall Mean Rating (OMR) Model] section.
+
+The following effects were taken into account:
+
+  - ***User:*** based on which the _User Effect (UE) Model_ described in the [User Effect (UE) Model] section was built;
+  - ***Movie:*** ;
+  - ***Genre:*** ;
+  - ***Year:*** ;
+  - ***Day*** ;.
 

### 2025-06-06 r/src/capstone-movielens.main.R

@@ -2652,6 +2652,8 @@ final.MF.RMSEs.ResultTibble <- final.RMSEs.ResultTibble.UMGYDE.rglr.tuned |>
 RMSE_kable(final.MF.RMSEs.ResultTibble)
 put_log("A row has been added to the RMSE Result Tibble 
 for the `Final Holdout Test of the User+Movie+Genre+Year+(Smoothed)Day Effect Model`.")
-### Close Log -----------------------------------------------------------------
+### Total Results Tibbe --------------------------------------------------------
+total.RMSEs.ResultTibble <- RMSEs.AddDiffColumn(final.MF.RMSEs.ResultTibble)
+s### Close Log -----------------------------------------------------------------
 log_close()
 

### 2025-06-06 r/src/support-functions/common-helper.functions.R

@@ -35,12 +35,43 @@ CreateRMSEs_ResultTibble <- function(){
          RMSE = project_objective,
          Comment = " ")
 }
-RMSEs.AddRow <- function(RMSEs, method, value, comment = ""){
+RMSEs.AddRow <- function(RMSEs, method, 
+                         value, 
+                         comment = "", 
+                         before = NULL){
   RMSEs |>
     add_row(Method = method,
             RMSE = value,
-            Comment = comment)
+            Comment = comment,
+            .before = before)
 }
+RMSEs.AddDiffColumn <- function(RMSEs){
+  RMSEs.Diff <- RMSEs |>
+    RMSEs.AddRow(NULL, project_objective, before = 1) #|>
+    #RMSEs.AddRow(NULL, 0, before = 1)
+    
+  
+  RMSEs.Diff <- RMSEs.Diff[-nrow(RMSEs.Diff),]
+    
+  RMSEs |>
+  add_column(Diff = RMSEs.Diff$RMSE - RMSEs$RMSE, 
+             .before = "Comment")
+  
+}
+RMSE.Total_kable <- function(RMSEs,
+                       col1width = 15,
+                       col2width = 7,
+                       col3width = 5, 
+                       col4width = 25){
+  RMSEs |> 
+    RMSE_kable(col1width,
+               col2width,
+               col3width) |>
+    column_spec(column = 4, 
+                width = RSME.tibble.col_width(col4width)) 
+}
+  
+
 RMSE_kable <- function(RMSEs,
                        col1width = 15,
                        col2width = 5,

### 2025-06-06 reports/capstone-movielens.site/02.5.UME-model.Rmd
Started working on new model: model template added.
Appendix: `Regularization: Common Helper Functions` section renamed to `Common Helper Functions: Regularization`.

@@
 The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report).
 We will explain that later in the [User+Movie Effect Model Regularization] section. 
@@
 \begin{equation}
-\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
+\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_j} \left(Y_{i,j} - \mu - \alpha_i\right)
 (\#eq:ME-regularized)
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
 
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
 

### 2025-06-06 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Appendix: `Regularization: Common Helper Functions` section renamed to `Common Helper Functions: Regularization`.

@@
 Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report).
 We have already explained that in the [UME Model Regularization] section. 
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
 
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
 

### 2025-06-06 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Appendix: `Regularization: Common Helper Functions` section renamed to `Common Helper Functions: Regularization`.

@@
 Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report).
 We have already explained that in the [UME Model Regularization] section. 
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
 
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
 
@@
 ::: {.noteblock data-latex=""}
-Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
+Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
 :::

### 2025-06-06 reports/capstone-movielens.site/04.appendix.Rmd
Appendix: `Regularization: Common Helper Functions` section renamed to `Common Helper Functions: Regularization`.
Appendix: function `RMSEs.AddDiffColumn` described.

@@
 \
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+:::
 
@@
 ::: {.noteblock data-latex=""}
-The source code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) is also available in the [Model training](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L431) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) script.
+The source code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) is also available in the [Model training](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L431) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
+The source code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) script.
+The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) script.
+The source code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) script on _GitHub_.
 :::
@@
 
-## Regularization: Common Helper Functions {#appndx_a.rglr.common_helper.functions}
-\
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described below are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+## Common Helper Functions
+
+### Common Helper Functions: Result RMSEs Table
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+:::
+### [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) Function {#func.RMSEs.}
+\
+
+::: { #func.RMSEs..usage .sidebar }
+#### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.RMSEs..params .sidebar }
+#### Parameters
+\
+
+::: { #func.RMSEs..params.vals .sidebar }
+  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
+
+:::
+
+::: { #func.RMSEs..details .sidebar }
+#### Details
+\
+
+::: { #func.RMSEs..code .sidebar }
+#### Source Code
+\
+
+The soure code of the [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) script on _GitHub_.
+:::
+:::
+
+#### Return
+
+The modified _Resut (RMSEs) Table_.
+
+### [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) Function {#func.RMSEs.AddDiffColumn}
+\
+
+Adds a calculated column named _Diff_ to the _Result(RMSEs)_ table (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.params.RMSEs) parameter) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row.
+This is true for each row except the first, for which the value is always zero.
+
+::: { #func.RMSEs.AddDiffColumn.usage .sidebar }
+#### Usage
+\
+
+```{r eval=FALSE}
+RMSEs.ModifiedTable <- RMSEs.AddDiffColumn(RMSEs)
+```
+:::
+
+::: { #func.RMSEs.AddDiffColumn.params .sidebar }
+#### Parameters
+\
+
+::: { #func.RMSEs.AddDiffColumn.params.RMSEs .sidebar }
+  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
+
+:::
+
+::: { #func.RMSEs.AddDiffColumn.details .sidebar }
+#### Details
+\
+
+::: { #func.RMSEs.AddDiffColumn.code .sidebar }
+#### Source Code
+\
+
+The soure code of the [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) function is shown below:
+```{r eval=FALSE}
+RMSEs.AddDiffColumn <- function(RMSEs){
+  RMSEs.Diff <- RMSEs |>
+    RMSEs.AddRow(NULL, project_objective, before = 1) #|>
+    #RMSEs.AddRow(NULL, 0, before = 1)
+
+  RMSEs.Diff <- RMSEs.Diff[-nrow(RMSEs.Diff),]
+
+  RMSEs |>
+  add_column(Diff = RMSEs.Diff$RMSE - RMSEs$RMSE, 
+             .before = "Comment")
+
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) script on _GitHub_.
+:::
+:::
+
+#### Return
+
+The modified _Resut (RMSEs) Table_.
+
+### Common Helper Functions: Regularization {#appndx_a.CHF.regularization}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
 :::
@@
 If the [lambda](#func.mean_reg.params.lambda) parameter is `0` (the default), the function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean), calling with the parameter `trim = 0` (the default for the `base::mean` function).
+:::
+:::
+
+::: { #func.mean_reg.code .sidebar }
+#### Source Code
+\
+
+The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function is shown below:
+```{r eval=FALSE}
+mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
+  if (is.na(lambda)) {
+    stop("Function: mean_reg
+`lambda` is `NA`")
+  }
+
+  names(lambda) <- NULL
+  sums <- sum(vals, na.rm = na.rm)
+  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
+  sums/(N + lambda)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L62) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) script on _GitHub_.
 :::
@@
 
-:::
-
-::: { #func.mean_reg.code .sidebar }
-#### Source Code
-\
-
-The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function is shown below:
-```{r eval=FALSE}
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L62) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) script.
-:::
 :::
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script.
+The complete version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
 :::

### 2025-06-06 reports/capstone-movielens.site/04.appendix.Rmd
Appendix: RMSEs.AddRow function described; `RMSEs.AddDiffColumn` function fixed.

@@
 ### Common Helper Functions: Result RMSEs Table
+\
 
@@
 :::
-### [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) Function {#func.RMSEs.}
-\
-
-::: { #func.RMSEs..usage .sidebar }
-#### Usage
-\
-
-```{r eval=FALSE}
-```
-:::
-
-::: { #func.RMSEs..params .sidebar }
-#### Parameters
-\
-
-::: { #func.RMSEs..params.vals .sidebar }
+
+#### [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) Function {#func.RMSEs.}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) script on _GitHub_.
+:::
+
+::: { #func.RMSEs.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.RMSEs.params .sidebar }
+##### Parameters
+\
+
+::: { #func.RMSEs.params.RMSEs .sidebar }
   - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
@@
 
-::: { #func.RMSEs..details .sidebar }
-#### Details
-\
-
-::: { #func.RMSEs..code .sidebar }
-#### Source Code
-\
-
-The soure code of the [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) script on _GitHub_.
-:::
-:::
-
-#### Return
+::: { #func.RMSEs.params. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.params. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.params. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.params. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.params. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.params. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.params. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.params. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.details .sidebar }
+##### Details
+\
+
+::: { #func.RMSEs.code .sidebar }
+##### Source Code
+\
+
+The soure code of the function is provided below:
+```{r eval=FALSE}
+```
+:::
+
+##### Return
 
@@
 
-### [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) Function {#func.RMSEs.AddDiffColumn}
-\
+#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) Function {#func.RMSEs.AddRow}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) script on _GitHub_.
+:::
+
+::: { #func.RMSEs.AddRow.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+RMSEs.AddRow(RMSEs, 
+             method, 
+             value, 
+             comment = "", 
+             before = NULL)
+```
+:::
+
+::: { #func.RMSEs.AddRow.params .sidebar }
+##### Parameters
+\
+
+::: { #func.RMSEs.AddRow.params.RMSEs .sidebar }
+  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
+
+:::
+
+::: { #func.RMSEs.params. .sidebar }
+  - ***method:*** The _Method or Model_ being evaluated;
+
+:::
+
+::: { #func.RMSEs.params. .sidebar }
+  - ***value:*** The _Root Mean Squared Error (RMSE)_ value;
+
+:::
+
+::: { #func.RMSEs.params. .sidebar }
+  - ***comment:*** Detailed information about the record or any other comment (if needed);
+
+:::
+
+::: { #func.RMSEs.params. .sidebar }
+  - ***before:*** One-based row index where to add the new rows, if NULL (default): after last row;
+
+:::
+
+::: { #func.RMSEs.AddRow.code .sidebar }
+##### Source Code
+\
+
+The soure code of the function is provided below:
+```{r eval=FALSE}
+RMSEs.AddRow <- function(RMSEs, 
+                         method, 
+                         value, 
+                         comment = "", 
+                         before = NULL){
+  RMSEs |>
+    add_row(Method = method,
+            RMSE = value,
+            Comment = comment,
+            .before = before)
+}
+```
+:::
+
+##### Return
+
+The modified _Resut (RMSEs) Table_.
+
+#### [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L49) Function {#func.RMSEs.AddDiffColumn}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L49) script on _GitHub_.
+:::
 
@@
 ::: { #func.RMSEs.AddDiffColumn.usage .sidebar }
-#### Usage
+##### Usage
 \
@@
 ::: { #func.RMSEs.AddDiffColumn.params .sidebar }
-#### Parameters
+##### Parameters
 \
@@
 
-::: { #func.RMSEs.AddDiffColumn.details .sidebar }
-#### Details
-\
-
 ::: { #func.RMSEs.AddDiffColumn.code .sidebar }
-#### Source Code
-\
-
-The soure code of the [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) function is shown below:
+##### Source Code
+\
+
+The soure code of the function is provided below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L48) script on _GitHub_.
-:::
-:::
-
-#### Return
+Under the hood, the function calls internally the [RMSEs.AddRow](#func.RMSEs.AddRow) function described above.
+:::
+:::
+
+##### Return
 
@@
 
-### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) Function {#func.mean_reg}
+#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) Function {#func.mean_reg}
 \
@@
 ::: { #func.mean_reg.usage .sidebar }
-#### Usage
+##### Usage
 \
@@
 ::: { #func.mean_reg.params .sidebar }
-#### Parameters
+##### Parameters
 \
@@
 ::: { #func.mean_reg.details .sidebar }
-#### Details
+##### Details
 \
@@
 ::: { #func.mean_reg.code .sidebar }
-#### Source Code
+##### Source Code
 \
@@
 ::: { #func.mean_reg.value .sidebar }
-#### Value
+##### Value
 \
@@
 
-### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
+#### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
 \
@@
 
-#### Signature
+##### Signature
 \
@@
 
-#### Parameters
+##### Parameters
 \
@@
 
-#### Details
+##### Details
 \
@@
 ::: { #func.tune.model_param.value .sidebar }
-#### Value
+##### Value
 \
@@
 
-#### Source Code
+##### Source Code
 \
@@
 
-### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
+#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
 \
@@
 
-#### **Parameters**
+##### **Parameters**
 \
@@
 ::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-##### ***loop_starter***
+###### ***loop_starter***
 \
@@
 ::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-##### ***tune_dir_path***
+###### ***tune_dir_path***
 \
@@
 ::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-##### ***cache_file_base_name***
+###### ***cache_file_base_name***
 \
@@
 ::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-##### ***fn_tune.test.param_value***
+###### ***fn_tune.test.param_value***
 \
@@
 ::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-##### ***max.identical.min_RMSE.count = 4***
+###### ***max.identical.min_RMSE.count = 4***
 \
@@
 ::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-##### ***endpoint.min_diff = 0***
+###### ***endpoint.min_diff = 0***
 \
@@
 ::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-##### ***break.if_min = TRUE***
+###### ***break.if_min = TRUE***
 \
@@
 ::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-##### ***steps.beyond_min = 2***
+###### ***steps.beyond_min = 2***
 \
@@
 ::: { #func.model.tune.param_range.details .sidebar }
-#### **Details** 
+##### **Details** 
 \
@@
 
-#### **Value**
+##### **Value**
 \
@@
 ::: {#func.model.tune.param_range.code .sidebar }
-#### Source Code
+##### Source Code
 \
@@
 
-### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) Function {#func.get_fine_tune.param.endpoints}
+#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) Function {#func.get_fine_tune.param.endpoints}
 \
@@
 ::: {#func.get_fine_tune.param.endpoints.params.preset.result .sidebar }
-##### ***preset.result***
+###### ***preset.result***
 \
@@
 
-#### Value
+##### Value
 \
@@
 
-### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-#### Signature
+#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
+\
+
+##### Signature
 \
@@
 ::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-##### ***preset.result***
+###### ***preset.result***
 \
@@
 
-### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-#### Signature
+#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
+\
+
+##### Signature
 \

### 2025-06-06 r/src/support-functions/common-helper.functions.R

@@ -35,7 +35,8 @@ CreateRMSEs_ResultTibble <- function(){
          RMSE = project_objective,
          Comment = " ")
 }
-RMSEs.AddRow <- function(RMSEs, method, 
+RMSEs.AddRow <- function(RMSEs, 
+                         method, 
                          value, 
                          comment = "", 
                          before = NULL){

### 2025-06-07 r/src/support-functions/common-helper.functions.R
Code cleaned up.

@@ -71,8 +71,6 @@ RMSE.Total_kable <- function(RMSEs,
     column_spec(column = 4, 
                 width = RSME.tibble.col_width(col4width)) 
 }
-  
-
 RMSE_kable <- function(RMSEs,
                        col1width = 15,
                        col2width = 5,

### 2025-06-07 r/src/capstone-movielens.main.R
Report: Summary Result Table added.

@@ -2654,6 +2654,7 @@ put_log("A row has been added to the RMSE Result Tibble
 for the `Final Holdout Test of the User+Movie+Genre+Year+(Smoothed)Day Effect Model`.")
 ### Total Results Tibbe --------------------------------------------------------
 total.RMSEs.ResultTibble <- RMSEs.AddDiffColumn(final.MF.RMSEs.ResultTibble)
-s### Close Log -----------------------------------------------------------------
+RMSE.Total_kable(total.RMSEs.ResultTibble)
+### Close Log -----------------------------------------------------------------
 log_close()
 

### 2025-09-18 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Last update made on June 2025.

@@
 ::: {.noteblock data-latex=""}
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+:::
+
 Unfortunately, for some reason, we do not see any improvement here yet.
-:::
 
@@
 ::: {.noteblock data-latex=""}
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+:::
+
 As we can see, the current model still does not show much improvement after _regularization_, even though the data analysis we made in the [Movie Genres Effect] section showed strong evidence of a genre effect.
@@
 Or, maybe, we have implemented the current model not quite correctly (?)
-:::
 

### 2025-09-18 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Last update made on June 2025.

@@
 ::: {.noteblock data-latex=""}
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+:::
+
 Now, we have a bit better result than one for the previous model.
-:::
 
@@
 
+::: {.noteblock data-latex=""}
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+:::
+
 \newpage

### 2025-09-18 reports/capstone-movielens.site/03.results.Rmd
Last update made on June 2025.

# Results
\

The *Result Summary Table* constructed below shows in detail the progress of our *Recommender System* improvement:

```{r, eval=FALSE}
total.RMSEs.ResultTibble <- RMSEs.AddDiffColumn(final.MF.RMSEs.ResultTibble)
```
```{r}
RMSE.Total_kable(total.RMSEs.ResultTibble)
```

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddDiffColumn](#func.RMSEs.AddDiffColumn) and [RMSE.Total_kable](#func.RMSE.Total_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
:::

\newpage

### 2025-09-18 reports/capstone-movielens.site/05.appendix.Rmd
Last update made on June 2025.

--- 2025-06-06 reports/capstone-movielens.site/04.appendix.Rmd
@@
 
-::: { #func.RMSEs.params .sidebar }
+::: { #func.RMSEs..params .sidebar }
 ##### Parameters
@@
 
-::: { #func.RMSEs.params.RMSEs .sidebar }
+::: { #func.RMSEs..params.RMSEs .sidebar }
   - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
@@
 
-::: { #func.RMSEs.params. .sidebar }
+::: { #func.RMSEs..params. .sidebar }
   - ***:*** ;
@@
 
-#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) Function {#func.RMSEs.AddRow}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) script on _GitHub_.
+#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) Function {#func.RMSEs.AddRow}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) script on _GitHub_.
 :::
@@
 
-::: { #func.RMSEs.params. .sidebar }
+::: { #func.RMSEs.AddRow.params.method .sidebar }
   - ***method:*** The _Method or Model_ being evaluated;
@@
 
-::: { #func.RMSEs.params. .sidebar }
+::: { #func.RMSEs.AddRow.params.value .sidebar }
   - ***value:*** The _Root Mean Squared Error (RMSE)_ value;
@@
 
-::: { #func.RMSEs.params. .sidebar }
+::: { #func.RMSEs.AddRow.params.comment .sidebar }
   - ***comment:*** Detailed information about the record or any other comment (if needed);
@@
 
-::: { #func.RMSEs.params. .sidebar }
+::: { #func.RMSEs.AddRow.params.before .sidebar }
   - ***before:*** One-based row index where to add the new rows, if NULL (default): after last row;
@@
 The modified _Resut (RMSEs) Table_.
+
+#### [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) Function {#func.RMSE_kable}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) script on _GitHub_.
+:::
+
+Prints the _Resut (RMSEs) Table_.
+
+::: {.noteblock data-latex=""}
+It is assumed that the table has the following three columns:
+
+  1. *Method*;
+  2. *RMSE*;
+  3. *Comment*;
+
+:::
+
+::: { #func.RMSE_kableusage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+RMSE_kable <- function(RMSEs,
+                       col1width = 15,
+                       col2width = 5,
+                       col3width = 30)
+```
+:::
+
+::: { #func.RMSE_kable.params .sidebar }
+##### Parameters
+\
+
+::: { #func.RMSE_kable.params.RMSEs .sidebar }
+  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
+
+:::
+
+::: { #func.RMSE_kable.params.col1width .sidebar }
+  - ***col1width:*** Width of the first column;
+
+:::
+
+::: { #func.RMSE_kable.params.col2width .sidebar }
+  - ***col2width:*** Width of the second column;
+
+:::
+
+::: { #func.RMSE_kable.params.col3width .sidebar }
+  - ***col3width:*** Width of the third column;
+
+:::
+
+::: { #func.RMSE_kablecode .sidebar }
+##### Source Code
+\
+
+The soure code of the function is provided below:
+```{r eval=FALSE}
+RMSE_kable <- function(RMSEs,
+                       col1width = 15,
+                       col2width = 5,
+                       col3width = 30){
+  RMSEs |>
+    kable(align='lcl', booktabs = T, padding = 5) |> 
+    row_spec(0, bold = T) |>
+    column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
+    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
+    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
+}
+```
+:::
+
+#### [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) Function {#func.RMSE.Total_kable}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) script on _GitHub_.
+:::
+
+Prints the _Resut (RMSEs) Table_.
+
+::: {.noteblock data-latex=""}
+It is assumed that the table has the following four columns:
+
+  1. *Method*;
+  2. *RMSE*;
+  3. *Diff*;
+  4. *Comment*;
+
+:::
+
+::: { #func.RMSE.Total_kableusage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+RMSE.Total_kable <- function(RMSEs,
+                       col1width = 15,
+                       col2width = 7,
+                       col3width = 5,
+                       col4width = 25)
+```
+:::
+
+::: { #func.RMSE.Total_kable.params .sidebar }
+##### Parameters
+\
+
+::: { #func.RMSE.Total_kable.params.RMSEs .sidebar }
+  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
+
+:::
+
+::: { #func.RMSE.Total_kable.params. .sidebar }
+  - ***col1width:*** Width of the first column;
+
+:::
+
+::: { #func.RMSE.Total_kable.params. .sidebar }
+  - ***col2width:*** Width of the second column;
+
+:::
+
+::: { #func.RMSE.Total_kable.params. .sidebar }
+  - ***col3width:*** Width of the third column;
+
+:::
+
+::: { #func.RMSE.Total_kable.params. .sidebar }
+  - ***col4width:*** Width of the fourth column;
+
+:::
+
+::: { #func.RMSE.Total_kablecode .sidebar }
+##### Source Code
+\
+
+The soure code of the function is provided below:
+```{r eval=FALSE}
+RMSE.Total_kable <- function(RMSEs,
+                       col1width = 15,
+                       col2width = 7,
+                       col3width = 5, 
+                       col4width = 25){
+  RMSEs |> 
+    RMSE_kable(col1width,
+               col2width,
+               col3width) |>
+    column_spec(column = 4, 
+                width = RSME.tibble.col_width(col4width)) 
+}
+
+```
+
+::: {.noteblock data-latex=""}
+Under the hood, the function calls internally the [RMSE_kable](#func.RMSE_kable) function described above.
+:::
+:::
 

### 2025-09-18 r/src/capstone-movielens.main.R
Refactoring: in progress...

@@ -17,267 +17,6 @@ source(setup_script.file_path,
        spaced = TRUE,
        verbose = TRUE,
        keep.source = TRUE)
-### Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-  
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log2(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log2(msg_template, arg1, arg2))
-}
-
-get_log3 <- function(msg_template, arg1, arg2, arg3) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
[…]

### 2025-09-18 r/src/support-scripts/rmd.render.R

@@ -1,4 +1,26 @@
-# Setup & Render ---------------------------------------------------------------
+# Setup & Render
+
+## Source File Paths -----------------------------------------------------------
+r.path <- "r"
+src.folder <- "src"
+support_scripts.folder <- "support-scripts"
+support_functions.folder <- "support-functions"
+
+r.src.path <- file.path(r.path, src.folder)
+support_scripts.path <- file.path(r.src.path, support_scripts.folder)
+support_functions.path <- file.path(r.src.path, support_functions.folder)
+
+## Setup -----------------------------------------------------------------------
+setup_script.file_path <- file.path(support_scripts.path, "setup.R")
+
+source(setup_script.file_path, 
+       catch.aborts = TRUE,
+       echo = TRUE,
+       spaced = TRUE,
+       verbose = TRUE,
+       keep.source = TRUE)
+
+## Render -----------------------------------------------------------------------
 
 # rmarkdown::render("reports/capstone-movielens-report.draft4.Rmd",
 #                   output_format = "pdf_document2")

### 2025-09-18 r/src/support-scripts/setup.R

@@ -89,3 +89,266 @@ conflict_prefer("kable", "kableExtra", quiet = TRUE)
 conflict_prefer("year", "lubridate", quiet = TRUE)
 conflicts_prefer(base::as.matrix)
 
+### Logging Helper functions -----------------------------------------------------
+open_logfile <- function(file_name){
+  log_file_name <- as.character(Sys.time()) |> 
+    str_replace_all(':', '_') |> 
+    str_replace(' ', 'T') |>
+    str_c(file_name)
+  
+  log_open(file_name = log_file_name)
+}
+print_start_date <- function(){
+  print(date())
+  Sys.time()
+}
+put_start_date <- function(){
+  put(date())
+  Sys.time()
+}
+print_end_date <- function(start){
+  print(date())
+  print(Sys.time() - start)
+}
+put_end_date <- function(start){
+  put(date())
+  put(Sys.time() - start)
+}
+
+msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
+  msg_template |> 
+    str_replace_all(arg.name, as.character(arg))
+}
+msg.glue <- function(msg_template, arg, arg.name = "%1"){
+  msg_template |>
+    msg.set_arg(arg, arg.name) |>
+    str_glue()
+}
+
+print_log <- function(msg){
+  print(str_glue(msg))
+}
+put_log <- function(msg){
+  put(str_glue(msg))
+}
+
+get_log1 <- function(msg_template, arg1) {
+  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
+}
+print_log1 <- function(msg_template, arg1){
+  print(get_log1(msg_template, arg1))
+}
+put_log1 <- function(msg_template, arg1){
+  put(get_log1(msg_template, arg1))
+}
+
+get_log2 <- function(msg_template, arg1, arg2) {
+  msg_template |> 
+    str_replace_all("%1", as.character(arg1)) |>
+    str_replace_all("%2", as.character(arg2)) |>
+    str_glue()
+}
+print_log2 <- function(msg_template, arg1, arg2){
+  print(get_log2(msg_template, arg1, arg2))
+}
+put_log2 <- function(msg_template, arg1, arg2){
+  put(get_log2(msg_template, arg1, arg2))
+}
+
+get_log3 <- function(msg_template, arg1, arg2, arg3) {
+  msg_template |> 
+    str_replace_all("%1", as.character(arg1)) |>
[…]

### 2025-09-18 r/_startup/1.init.R
Refactoring (continue): in progress...

@@ -1,0 +1,219 @@
+# Setup & Init
+
+## Source File Paths -----------------------------------------------------------
+r.path <- "r"
+src.folder <- "src"
+support_scripts.folder <- "support-scripts"
+support_functions.folder <- "support-functions"
+
+r.src.path <- file.path(r.path, src.folder)
+support_scripts.path <- file.path(r.src.path, support_scripts.folder)
+support_functions.path <- file.path(r.src.path, support_functions.folder)
+
+## Setup -----------------------------------------------------------------------
+setup_script.file_path <- file.path(support_scripts.path, "setup.R")
+
+source(setup_script.file_path, 
+       catch.aborts = TRUE,
+       echo = TRUE,
+       spaced = TRUE,
+       verbose = TRUE,
+       keep.source = TRUE)
+
+## Define Logging Functions ----------------------------------------------------
+log-func_script.file_path <- file.path(support_functions.path, "logging-functions.R")
+
+source(log-func_script.file_path, 
+       catch.aborts = TRUE,
+       echo = TRUE,
+       spaced = TRUE,
+       verbose = TRUE,
+       keep.source = TRUE)
+
+## Load Source Datasets from Specially Designed Package ------------------------
+if(!require(edx.capstone.movielens.data)) {
+  start <- put_start_date()
+  pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
+  put_end_date(start)
+}
+
+put_log("Dataset loaded from `edx.capstone.movielens.data` package: edx")
+put(str(edx))
+sum(is.na(edx$rating))
+#> [1] 0
+put(summary(edx))
+
+put_log1("Dataset loaded from `edx.capstone.movielens.data` package: final_holdout_test:
+%1", str(final_holdout_test))
+sum(is.na(final_holdout_test$rating))
+#> [1] 0
+put(summary(final_holdout_test))
+
+### Open log file for `Initialize Source File Paths` Feature -------------------
+open_logfile(".src.file-paths")
+### External Common Helper functions -------------------------------------
+common_helper_functions.file_path <- file.path(support_functions.path,
+                                               "common-helper.functions.R")
+source(common_helper_functions.file_path, 
+       catch.aborts = TRUE,
+       echo = TRUE,
+       spaced = TRUE,
+       verbose = TRUE,
+       keep.source = TRUE)
+### Init Project Global Variables ----------------------------------------------
[…]

### 2025-09-18 r/_startup/3.rmd.render.R

@@ -1,0 +1,24 @@
+# RMD Render
+
+# rmarkdown::render("reports/capstone-movielens-report.draft4.Rmd",
+#                   output_format = "pdf_document2")
+
+# Render RMD Report
+# rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
+#                   output_file = "capstone-movielens.report.pdf",
+#                   # output_format = "pdf_document2",
+#                   output_format = rmarkdown::pdf_document(
+#                     pandoc_args = c("--metadata-file", "main.yaml")
+#                   ),
+#                   envir = .GlobalEnv)
+
+# rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
+#                   #output_format = "pdf_document2",
+#                   output_file = "capstone-movielens.report.pdf",
+#                   run_pandoc = TRUE)
+
+rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
+                  output_file = "capstone-movielens.report.pdf",
+                  run_pandoc = TRUE)
+
+

### 2025-09-18 r/src/capstone-movielens.main.R

@@ -1,22 +1,5 @@
-# Init Project Environment -----------------------------------------------------
-## Source File Paths -----------------------------------------------------------
-r.path <- "r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
+# Capstone MovieLens Main Script
 
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-## Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path, "setup.R")
-
-source(setup_script.file_path, 
-       catch.aborts = TRUE,
-       echo = TRUE,
-       spaced = TRUE,
-       verbose = TRUE,
-       keep.source = TRUE)
 ## Data Analysis ===============================================================
 ### Open log -------------------------------------------------------------------
 open_logfile(".data-analysis")

### 2025-09-18 r/src/support-scripts/rmd.render.R

@@ -1,65 +1,0 @@
-# Setup & Render
-
-## Source File Paths -----------------------------------------------------------
-r.path <- "r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-
-## Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path, "setup.R")
-
-source(setup_script.file_path, 
-       catch.aborts = TRUE,
-       echo = TRUE,
-       spaced = TRUE,
-       verbose = TRUE,
-       keep.source = TRUE)
-
-## Render -----------------------------------------------------------------------
-
-# rmarkdown::render("reports/capstone-movielens-report.draft4.Rmd",
-#                   output_format = "pdf_document2")
-
-## Load Source Datasets from Specially Designed Package
-if(!require(edx.capstone.movielens.data)) {
-  start <- put_start_date()
-  pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
-  put_end_date(start)
-}
-
-put_log("Dataset loaded from `edx.capstone.movielens.data` package: edx")
-put(str(edx))
-sum(is.na(edx$rating))
-#> [1] 0
-put(summary(edx))
-
-put_log1("Dataset loaded from `edx.capstone.movielens.data` package: final_holdout_test:
-%1", str(final_holdout_test))
-sum(is.na(final_holdout_test$rating))
-#> [1] 0
-put(summary(final_holdout_test))
-
-# Render RMD Report
-# rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
-#                   output_file = "capstone-movielens.report.pdf",
-#                   # output_format = "pdf_document2",
-#                   output_format = rmarkdown::pdf_document(
-#                     pandoc_args = c("--metadata-file", "main.yaml")
-#                   ),
-#                   envir = .GlobalEnv)
-
-# rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
-#                   #output_format = "pdf_document2",
-#                   output_file = "capstone-movielens.report.pdf",
-#                   run_pandoc = TRUE)
-
-rmarkdown::render("reports/capstone-movielens.site/index.Rmd",
-                  output_file = "capstone-movielens.report.pdf",
-                  run_pandoc = TRUE)
-
-

### 2025-09-18 r/src/support-scripts/setup.R

@@ -88,267 +88,3 @@ conflict_prefer("pivot_wider", "tidyr", quiet = TRUE)
 conflict_prefer("kable", "kableExtra", quiet = TRUE)
 conflict_prefer("year", "lubridate", quiet = TRUE)
 conflicts_prefer(base::as.matrix)
-
-### Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-  
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log2(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log2(msg_template, arg1, arg2))
-}
-
-get_log3 <- function(msg_template, arg1, arg2, arg3) {
-  msg_template |> 
[…]

### 2025-09-18 r/_startup/_run-all.R
Refactoring (continue): in progress...

@@ -1,0 +1,31 @@
+# Run All Scripts
+## Source File Paths -----------------------------------------------------------
+startup.path <- "r/_startup"
+init.script_path = file.path(startup.path, "1.init.R")
+main.script_path = file.path(startup.path, "2.run-main-script.R")
+rmd_render.script_path = file.path(startup.path, "3.rmd.render.R")
+
+## Run Scripts -----------------------------------------------------------------
+
+source(init.script_path, 
+       catch.aborts = TRUE,
+       echo = TRUE,
+       spaced = TRUE,
+       verbose = TRUE,
+       keep.source = TRUE)
+
+# source(path, 
+#        catch.aborts = TRUE,
+#        echo = TRUE,
+#        spaced = TRUE,
+#        verbose = TRUE,
+#        keep.source = TRUE)
+# 
+# source(path, 
+#        catch.aborts = TRUE,
+#        echo = TRUE,
+#        spaced = TRUE,
+#        verbose = TRUE,
+#        keep.source = TRUE)
+# 
+

### 2025-09-18 r/_startup/1.init.R
Fix for initialize script.

@@ -21,9 +21,9 @@ source(setup_script.file_path,
        keep.source = TRUE)
 
 ## Define Logging Functions ----------------------------------------------------
-log-func_script.file_path <- file.path(support_functions.path, "logging-functions.R")
+log_func_script.file_path <- file.path(support_functions.path, "logging-functions.R")
 
-source(log-func_script.file_path, 
+source(log_func_script.file_path, 
        catch.aborts = TRUE,
        echo = TRUE,
        spaced = TRUE,

### 2025-09-19 r/_startup/_run-all.R
Fix for main script.

@@ -1,9 +1,9 @@
 # Run All Scripts
 ## Source File Paths -----------------------------------------------------------
 startup.path <- "r/_startup"
-init.script_path = file.path(startup.path, "1.init.R")
-main.script_path = file.path(startup.path, "2.run-main-script.R")
-rmd_render.script_path = file.path(startup.path, "3.rmd.render.R")
+init.script_path <- file.path(startup.path, "1.init.R")
+run_main.script_path <- file.path(startup.path, "2.run-main-script.R")
+rmd_render.script_path < file.path(startup.path, "3.rmd.render.R")
 
 ## Run Scripts -----------------------------------------------------------------
 
@@ -14,13 +14,13 @@ source(init.script_path,
        verbose = TRUE,
        keep.source = TRUE)
 
-# source(path, 
-#        catch.aborts = TRUE,
-#        echo = TRUE,
-#        spaced = TRUE,
-#        verbose = TRUE,
-#        keep.source = TRUE)
-# 
+source(run_main.script_path,
+       catch.aborts = TRUE,
+       echo = TRUE,
+       spaced = TRUE,
+       verbose = TRUE,
+       keep.source = TRUE)
+
 # source(path, 
 #        catch.aborts = TRUE,
 #        echo = TRUE,

### 2025-09-19 r/_startup/_run-all.R
Minor fix.

@@ -3,7 +3,7 @@
 startup.path <- "r/_startup"
 init.script_path <- file.path(startup.path, "1.init.R")
 run_main.script_path <- file.path(startup.path, "2.run-main-script.R")
-rmd_render.script_path < file.path(startup.path, "3.rmd.render.R")
+rmd_render.script_path <- file.path(startup.path, "3.rmd.render.R")
 
 ## Run Scripts -----------------------------------------------------------------
 

### 2025-09-19 r/_startup/1.init.R
Fix for biblatex options.

@@ -1,24 +1,4 @@
-# Setup & Init
-
-## Source File Paths -----------------------------------------------------------
-r.path <- "r"
-src.folder <- "src"
-support_scripts.folder <- "support-scripts"
-support_functions.folder <- "support-functions"
-
-r.src.path <- file.path(r.path, src.folder)
-support_scripts.path <- file.path(r.src.path, support_scripts.folder)
-support_functions.path <- file.path(r.src.path, support_functions.folder)
-
-## Setup -----------------------------------------------------------------------
-setup_script.file_path <- file.path(support_scripts.path, "setup.R")
-
-source(setup_script.file_path, 
-       catch.aborts = TRUE,
-       echo = TRUE,
-       spaced = TRUE,
-       verbose = TRUE,
-       keep.source = TRUE)
+# Init
 
 ## Define Logging Functions ----------------------------------------------------
 log_func_script.file_path <- file.path(support_functions.path, "logging-functions.R")

### 2025-09-19 r/_startup/_run-all.R

@@ -1,11 +1,19 @@
 # Run All Scripts
 ## Source File Paths -----------------------------------------------------------
 startup.path <- "r/_startup"
+setup.script_path <- file.path(startup.path, "0.setup.R")
 init.script_path <- file.path(startup.path, "1.init.R")
 run_main.script_path <- file.path(startup.path, "2.run-main-script.R")
 rmd_render.script_path <- file.path(startup.path, "3.rmd.render.R")
 
 ## Run Scripts -----------------------------------------------------------------
+
+source(setup.script_path, 
+       catch.aborts = TRUE,
+       echo = TRUE,
+       spaced = TRUE,
+       verbose = TRUE,
+       keep.source = TRUE)
 
 source(init.script_path, 
        catch.aborts = TRUE,

### 2025-09-21 reports/capstone-movielens.site/01.intro.Rmd
Working on Conclution section (in progress)
Refactoring: in progress...
Fix for Intro section.

@@
-# Introduction / Overview / Executive Summary
+# Overview and Executive Summary {#intro}
 
@@
 Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563[@BigChaosSln]).
-\newpage
 
@@
 
-To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:
+To start with we have to generate two datasets derived from the _MovieLens_ dataset mentioned [above](#intro):
 
@@
 
-For this purpose the following package has been developed by the author of this report: `edx.capstone.movielens.data`.
-The source code of the package is available [on GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
+For this purpose, a dedicated package, [edx.capstone.movielens.data](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data), has been developed by the author of this report.
+The source code of the package is available on [GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
 

### 2025-09-21 reports/capstone-movielens.site/01.intro.Rmd
Fix for 1.1 Datasets Overview section.

@@
 
-For this purpose, a dedicated package, [edx.capstone.movielens.data](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data), has been developed by the author of this report.
-The source code of the package is available on [GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data)[@edx_capstone_movielens_data].
+For this purpose, a dedicated package, [edx.capstone.movielens.data](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data/blob/main/README.md), has been developed by the author of this report.
+The source code of the package is available on [GitHub](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data) (the main `R` script that prepares the necessary datasets is located in the file [init-movielens-data.R](https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data/blob/main/data-raw/init-movielens-data.R))[@edx_capstone_movielens_data].
 
-Let's install the development version of this package from the GitHub repository and attach the correspondent library to the global environment:
+Let's install the development version of this package from the _GitHub repository_ and attach the correspondent library to the global environment:
 ```{r}

### 2025-09-22 reports/capstone-movielens.site/01.intro.Rmd

@@
 
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
+Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2_23-1-1] that not every user rated every movie:
 ```{r}

### 2025-09-22 reports/capstone-movielens.site/02-0.methods.Rmd
Report review; working on UMGYE Model Building (in progress)

@@
-# Methods / Analysis
+# Methods and Analysis
 ::: {.noteblock data-latex=""}
@@
 
-#### `clamp` function
+#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) function {#func.clamp}
 \

### 2025-09-22 reports/capstone-movielens.site/02.4.UE-model.Rmd
Section `UMGYE Model Building` completed.

@@
 
-Finally, we are ready to compute the `RMSE` (additionally using the [clamp](#func.clamp) helper function we described above to keep predictions in the proper range):
-
 Now, we are ready to compute the _Mean Squared Errors_ from the _5-Fold Cross Validation_ (additionally using the [clamp](#func.clamp) helper function we described above):
@@
 ::: {.noteblock data-latex=""}
-For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report.
+
+The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
 :::

### 2025-09-22 reports/capstone-movielens.site/04.conclusion.Rmd

# Conclusion
\

In this project, a _Machine Learning Algorithm_ was successfully developed for a _Recommender System_ (hereinafter referred to as _RS MLA_) to predict movie ratings using the [10M version of the MovieLens](http://grouplens.org/datasets/movielens/10m/) dataset.

Since it was needed to convert the original dataset into a _Data Source_, suitable for processing by the _RS MLA_, a package [edx.capstone.movielens.data], specifically designed for this purpose, was developed and used, providing the _RS MLA_ with the necessary datasets.

Following the Netflix Grand Prize Contest requirements, the _Root Mean Squared Error (RMSE)_ metric was used to evaluate the accuracy of our models.

By incorporating essential factors such as overall average rating, movie, user, and some other observable effects, as well as efficient techniques such as _Regularization_ and _Matrix Factorization_ methods, the accuracy was significantly improved compared to the baseline model.

The baseline model was the _Overall Mean Rating_ model described in the [Overall Mean Rating (OMR) Model] section.

The following effects were taken into account:

  - ***User:*** based on which the _User Effect (UE) Model_ described in the [User Effect (UE) Model] section was built (significantly improved the _RMSE_ compared to the baseline model);
  - ***Movie:*** based on which (and the _User Effect_) the _Regularized User+Movie Effect (UME) Model_ described in the [User+Movie Effect (UME) Model] section was eventually built (even better improved the _RMSE_ compared to the previous (*UE*) model);
  - ***Genre:*** based on which (and the previous effects) the _Regularized User+Movie+Genre Effect (UMGE) Model_ described in the [User+Movie+Genre Effect (UMGE) Model] section was built (even after _regularization_ it showed very little improvement in _RMSE_ compared to the previous (*UME*) model; before regularization, for some reason, there was no improvement at all);
  - ***Year:*** based on which (and the previous effects) the _Regularized User+Movie+Genre+Year Effect (UMGYE) Model_ described in the [User+Movie+Genre+Year Effect (UMGYE) Model] section was built (provided a much better improvement in _RMSE_ compared to the previous (*UMGE*) model but still two orders of magnitude less than the *UE* and *UME* models showed);
  - ***Day*** based on which (and the previous effects) the _Regularized (and Tuned) User+Movie+Genre+Year+Day Effect (UMGYDE) Model_ described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section was built (showed almost twice better improvement than the previous (*UMGYE*) model but still not good enough to meet the *Project Objective*);.
  - ***Day (Matrix Factorization):*** (described in the [UMGYDE Model: Matrix Factorization (MF)] section) *Matrix Factorization* method performed on the _Regularized UMGYDE Model_ provided substantial improvement comparable to that shown by the *UE* and *UME* models, and finally permitted to reach the *Project Objective*.

The *Result Summary Table* constructed below shows in detail the progress of our *Recommender System* improvement:

```{r, eval=FALSE}
total.RMSEs.ResultTibble <- RMSEs.AddDiffColumn(final.MF.RMSEs.ResultTibble)
```
```{r}
RMSE.Total_kable(total.RMSEs.ResultTibble)
```

\newpage

### 2025-09-22 reports/capstone-movielens.site/02-0.methods.Rmd
Fix for report, Section 2.1 Defining Logging and Time Measuring Helper Functions.

@@
 ::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r/src)[@edx_capstone_movielens]. 
+All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r)[@edx_capstone_movielens]. 
 :::
@@
 ::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L20) script on _GitHub_.
+The full source code of these functions is available in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R) script on _GitHub_.
 :::

### 2025-09-23 reports/capstone-movielens.site/02-0.methods.Rmd
Fix for Section 2.2 Preparing train and set datasets.

@@
 
-::: { #func.make_source_datasets .sidebar }
-  - [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)
-:::
+  - [init_source_datasets](#func.init_source_datasets)
 
-::: { #func.init_source_datasets .sidebar }
-  - [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L209)
-:::
+  - [make_source_datasets](#func.make_source_datasets)
 
@@
 
-### The [make_source_datasets](#func.make_source_datasets) function
-\
+### [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L209) Function {#func.init_source_datasets}
+
+The _init_source_datasets_ function checks whether the required source datasets are cached on the hard disk, and, if so, loads the datasets from the cache file.
+
+Otherwise, it calls the [make_source_datasets](#func.make_source_datasets) function, which creates all the necessary datasets.
+
+Finally, it stores the data into a cache file on the disk.
+
+The simplified version of the function's source code is shown below:
+
+```{r eval=FALSE}
+init_source_datasets <- function(){
+  put_log("Method `init_source_datasets`: 
+Initializing sourse datasets...")
+
+  if(file.exists(movielens_datasets_file_path)){
+    movielens_datasets <- load_movielens_data_from_file(movielens_datasets_file_path)
+  } else if(file.exists(movielens_datasets_zip)) {
+    put_log("Method `init_source_datasets`: 
+Unzipping MovieLens data file from zip-archive: {movielens_datasets_zip}...")
+
+    unzip(movielens_datasets_zip, movielens_datasets_file_path)
+
+    if(!file.exists(movielens_datasets_file_path)) {
+      put_log("Method `init_source_datasets`: 
+File does not exists: {movielens_datasets_file}.")
+      stop("Failed to unzip MovieLens data zip-archive.")
+    }
+
+    movielens_datasets <- load_movielens_data_from_file(movielens_datasets_file_path)
+  } else {
+    put_log("Method `init_source_datasets`: 
+Creating datasets...")
+    library(edx.capstone.movielens.data)
+    put_log("Method `init_source_datasets`: 
+Library attached: 'edx.capstone.movielens.data'")
+
+    movielens_datasets <- make_source_datasets()
+    put("Method `init_source_datasets`: 
+All required datasets have been created.")
+
+    put_log("Method `init_source_datasets`: 
+Saving newly created input datasets to file...")
+    save(movielens_datasets, file =  movielens_datasets_file_path)
+
+    if(!file.exists(movielens_datasets_file_path)) {
+      put_log("Method `init_source_datasets`: 
+File was not created: {movielens_datasets_file}.")
+      warning("MovieLens data was not saved to file.")
+    } else {
+      put_log("Method `init_source_datasets`: 
+Datasets have been saved to file: {movielens_datasets_file_path}.")
+
+      put_log("Method `init_source_datasets`: 
+Creating zip-archive: {movielens_datasets_zip}...") 
+      zip(movielens_datasets_zip, movielens_datasets_file_path)
+    # ...
+    }
+  }
+  movielens_datasets
+}
+```
+
+### [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) Function {#func.make_source_datasets}
 
@@
 ```{r eval=FALSE}
-
 make_source_datasets <- function(){

### 2025-09-24 reports/capstone-movielens.site/02-0.methods.Rmd
Fix fro Section 2.2 Preparing train and set datasets.

@@
 
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_.
+We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_[@IDS2_29-6].
 To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
@@
 
-We will use the array representation described in [Section 17.5 of the Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
+We will use the array representation described in [Section 17.5 Analysis of variance (ANOVA)](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook_[@IDS2_17-5], for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
 To create this matrix, we use `tidyr::pivot_wider` function:

### 2025-09-25 reports/capstone-movielens.site/02-0.methods.Rmd
Fixes for sections 1-2.3.

@@
 
-We will use the array representation described in [Section 17.5 Analysis of variance (ANOVA)](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook_[@IDS2_17-5], for the training data: we denote ranking for movie $j$ by user $i$ as $y_{i,j}$.
-To create this matrix, we use `tidyr::pivot_wider` function:
+We will use the array representation described in [Section 17.5 Analysis of variance (ANOVA)](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook_[@IDS2_17-5], for the training data.
+For this purpose, we will convert the `edx` dataset into a matrix using the `tidyr::pivot_wider` function:
 
@@
 ::: {.noteblock data-latex=""}
-The source code of the function mentioned above is also available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
+The [source code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L71) of the function mentioned above is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L1) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
 :::
@@
 
-Note that titles cannot be considered unique, so we can't use them as IDs[@IDS2_23-1-1].
+Note that titles cannot be considered unique, so we cannot use them as IDs[@IDS2_23-1-1].
 
@@
 Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_:
+as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_[@IDS2_29-6-1]:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87)` one, from where it is called.
+The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](#func.make_source_datasets), from which it is called.
 :::
@@
 
+::: {.noteblock data-latex=""}
+All the _Common Helper functions_ described below in this section are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+:::
+
 For our further analysis, we are going to use the following _common helper functions_:
@@
 
-As explained in [Section  24.4 User effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings can’t be below 0.5 or above 5.
+As explained in [Section  23.4 _User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_[@IDS2_23-4] we know ratings can’t be below 0.5 or above 5.
 For this reason, we will use the `clamp` function described in that section:
@@
 
-::: {.noteblock data-latex=""}
-All the _common helper functions_, including those described above, are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
 \newpage

### 2025-09-25 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Last update made on June 2025.
Fixes for sections 1-2.3.

@@
 
-Let's begin our analysis by evaluating the simplest model described in [Section _23.3 The First Model_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model), and then gradually refine it through further research.
+Let's begin our analysis by evaluating the simplest model described in [Section 23.3 _A first model_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook*[@IDS2_23-3], and then gradually refine it through further research.
 
@@
 
-It is about a model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
+The _Overal Mean Rating_ model that assumes the same rating for all movies and users with all the differences explained by random variation would look as follows:
 
@@
 
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ the _true_ rating for all movies.
+with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ is the rating for all movies.
 
@@
 
+::: {.noteblock data-latex=""}
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+:::
+
 To win the grand prize of $1,000,000, a participating team had to get an RMSE of at least 0.8563[@BigChaosSln]. So we can definitely do better![@IDS2_23-3]

### 2025-09-25 reports/capstone-movielens.site/02-0.methods.Rmd
Minor fix for sections  1-2.3.

@@
 Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_[@IDS2_29-6-1]:
+as explained in [Section 29.6.1 _K-fold cross validation_](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_[@IDS2_29-6-1]:
 ```{r eval=FALSE}
@@
 
-As explained in [Section  23.4 _User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_[@IDS2_23-4] we know ratings can’t be below 0.5 or above 5.
+As explained in [Section  23.4 _User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_[@IDS2_23-4] we know ratings cannot be below 0.5 or above 5.
 For this reason, we will use the `clamp` function described in that section:

### 2025-09-25 reports/capstone-movielens.site/01.intro.Rmd
Fixes for citations.

--- 2025-09-21 reports/capstone-movielens.site/01.intro.Rmd
@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
+Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 *Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
 $$
@@
 
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
+Now, note the expressions below which confirm the fact explained in [Section 23.1.1 *Movielens data*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ that not every user rated every movie[@IDS2_23-1-1]:
 ```{r}

### 2025-09-25 reports/capstone-movielens.site/02-0.methods.Rmd
Fixes for citations.

--- 2025-09-25 reports/capstone-movielens.site/02-0.methods.Rmd
@@
 
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 Movielens data](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 Cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_[@IDS2_29-6].
+We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 *Movielens data*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_[@IDS2_29-6].
 To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
@@
 
-We will use the array representation described in [Section 17.5 Analysis of variance (ANOVA)](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook_[@IDS2_17-5], for the training data.
+We will use the array representation described in [Section 17.5 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook_, for the training data[@IDS2_17-5].
 For this purpose, we will convert the `edx` dataset into a matrix using the `tidyr::pivot_wider` function:
@@
 Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 K-fold cross validation](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_[@IDS2_29-6-1]:
+as explained in [Section 29.6.1 *K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_[@IDS2_29-6-1]:
 ```{r eval=FALSE}
@@
 
-As explained in [Section  23.4 _User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_[@IDS2_23-4] we know ratings can’t be below 0.5 or above 5.
-For this reason, we will use the `clamp` function described in that section:
+As explained in [Section  23.4 *User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
+For this reason, we will use the `clamp` function described in that section[@IDS2_23-4]:
 ```{r eval=FALSE}

### 2025-09-25 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Minor fix for sections  1-2.3.
Fixes for citations.

@@
 
-Let's begin our analysis by evaluating the simplest model described in [Section 23.3 _A first model_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook*[@IDS2_23-3], and then gradually refine it through further research.
+Let's begin our analysis by evaluating the simplest model described in [Section 23.3 *A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook*[@IDS2_23-3], and then gradually refine it through further research.
 
@@
 
-with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ is the rating for all movies.
+with $\varepsilon_{i,j}$ independent errors sampled from the same distribution centered at 0 and $\mu$ is the average rating for all movies.
 

### 2025-09-25 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Fixes for citations.

@@
 
-As mentioned in [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter "23 Regularization" of the Course Textbook_ the `Movielens` dataset also has a genres column.
+As mentioned in [Chapter 23: *Regularization*, Section 23.7: *Exercises*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the *Course Textbook* the `Movielens` dataset also has a genres column.
 This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
@@
 
-To account for a _genre effect_ we will use the model suggested in the [Section 23.7: Exercises](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the _Chapter 23 "Regularization" of the Course Textbook_[@IDS2_23-7]:
+To account for a _genre effect_ we will use the model suggested in the [Chapter 23: *Regularization*, Section 23.7: *Exercises*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the *Course Textbook*:
 
-If we define a _genre treatment effect_ $g_{i,j}$ for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
+If we define a _genre treatment effect_ $g_{i,j}$ for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect[@IDS2_23-7]:
 

### 2025-09-26 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Fixes for OMR model.

@@
 
-Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
+Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L89) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L89) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
 
@@
 
-One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L59) one:
+One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L94), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L94) one:
 ```{r eval=FALSE }

### 2025-09-26 reports/capstone-movielens.site/02.4.UE-model.Rmd

@@
 
-To improve our model let's now take into consideration user effects as explained in [Section _23.4 User effects_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*[@IDS2_23-4].
+To improve our model let's now take into consideration user effects as explained in [Section 23.4 *User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
 
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users: 
+If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users[@IDS2_23-4]:
 ```{r}

### 2025-09-26 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 
-[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects:
+[Section 23.6 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook* explains why and how we should use _Penalized least squares_ to improve our predictions.
+The author also explains that the general idea of penalized regression is to control the total variability of the movie effects[@IDS2_23-6]:
 $$

### 2025-09-26 reports/capstone-movielens.site/05.appendix.Rmd

@@
 ::: { #func.data.plot.params.xlabel .sidebar }
-  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
+  - **xlabel = NULL:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
 
@@
 
-The soure code of the [data.plot]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function is shown below:
+The soure code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function is shown below:
 ```{r eval=FALSE}

### 2025-09-26 reports/capstone-movielens.site/02.5.UME-model.Rmd
Refactoring: functions' descriptions.

@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
 
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
 

### 2025-09-26 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Refactoring: functions' descriptions.

@@
 
-##### Parameters
+##### Arguments
 \
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
 
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
 

### 2025-09-26 reports/capstone-movielens.site/05.appendix.Rmd
Refactoring: functions' descriptions.

@@
 
-### [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) Function {#func.union_cv_results}
+### Model Training Functions
+
+#### [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) Function {#func.union_cv_results}
 \
@@
 ::: { #func.union_cv_results.Usage .sidebar }
-#### Usage
+##### Usage
 \
@@
 
-::: { #func.union_cv_results.params .sidebar }
-#### Parameters
-\
-
-::: { #func.union_cv_results.params.data_list .sidebar }
+::: { #func.union_cv_results.args .sidebar }
+##### Arguments
+\
+
+::: { #func.union_cv_results.args.data_list .sidebar }
   - **data_list:** List of data frames representing the results of the _N-Fold Cross Validation_ method execution.;
@@
 ::: { #func.union_cv_results.details .sidebar }
-#### Details
+##### Details
 \
@@
 ::: { #func.union_cv_results.value .sidebar }
-#### Value
+##### Value
 \
@@
 ::: { #func.union_cv_results.code .sidebar }
-#### Source Code
+##### Source Code
 \
@@
 
-### [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) Function {#func.data.plot}
-\
-
-Plots a graph based on the dataset passed in the [data](#func.data.plot.params.data) parameter, using both points and a line.
+#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
+\
+
+Selects the best parameter value and the corresponding minimum Root Mean Squared Error value from the function's input arguments.
+
+::: { #func.get_best_param.result.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+get_best_param.result(param_values, rmses)
+
+```
+:::
+
+::: { #func.get_best_param.result.args .sidebar }
+##### Arguments
+\
+
+::: { #func.get_best_param.result.args.param_values .sidebar }
+  - **param_values:** List of parameters to choose the best value.;
+
+:::
+::: { #func.get_best_param.result.args.rmses .sidebar }
+  - **rmses:** A list of Root Mean Squared Errors corresponding to the parameter values specified in the list passed by the argument [param_values](#func.get_best_param.result.args.param_values).
+
+:::
+:::
+
+::: { #func.get_best_param.result.details .sidebar }
+##### Details
+\
+
+A parameter value that corresponds to the minimum RMSE is considered the best.
+
+:::
+
+::: { #func.get_best_param.result.value .sidebar }
+##### Value
+\
+
+A data frame that is a union of the input data frames.
+:::
+
+::: { #func.get_best_param.result.code .sidebar }
+##### Source Code
+\
+
+The soure code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
+```{r eval=FALSE}
+get_best_param.result <- function(param_values, rmses){
+  best_pvalue_idx <- which.min(rmses)
+  c(param.best_value = param_values[best_pvalue_idx], 
+    best_RMSE = rmses[best_pvalue_idx])
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) is also available in the [Model training](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L431) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) script on _GitHub_.
+:::
+:::
+
+### Data Visualization Functions
+
+#### [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) Function {#func.data.plot}
+\
+
+Plots a graph based on the dataset passed in the [data](#func.data.plot.args.data) parameter, using both points and a line.
 
 ::: { #func.data.plot.Usage .sidebar }
-#### Usage
+##### Usage
 \
@@
 
-::: { #func.data.plot.params .sidebar }
-#### Parameters
-\
-
-::: { #func.data.plot.params.data .sidebar }
+::: { #func.data.plot.args .sidebar }
+##### Arguments
+\
+
+::: { #func.data.plot.args.data .sidebar }
   - **data:** Dataset to use for the plot;
@@
 :::
-::: { #func.data.plot.params.title .sidebar }
+::: { #func.data.plot.args.title .sidebar }
   - **title:** Title of the plot;
@@
 :::
-::: { #func.data.plot.params.xname .sidebar }
+::: { #func.data.plot.args.xname .sidebar }
   - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;
@@
 :::
-::: { #func.data.plot.params.yname .sidebar }
+::: { #func.data.plot.args.yname .sidebar }
   - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;
@@
 :::
-::: { #func.data.plot.params.xlabel .sidebar }
+::: { #func.data.plot.args.xlabel .sidebar }
   - **xlabel = NULL:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
@@
 :::
-::: { #func.data.plot.params.ylabel .sidebar }
+::: { #func.data.plot.args.ylabel .sidebar }
   - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;
@@
 :::
-::: { #func.data.plot.params.line_col .sidebar }
+::: { #func.data.plot.args.line_col .sidebar }
   - **line_col = blue:** The line color;
@@
 :::
-::: { #func.data.plot.params.normalize .sidebar }
+::: { #func.data.plot.args.normalize .sidebar }
   - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
@@
 ::: { #func.data.plot.details .sidebar }
-#### Details
+##### Details
 \
@@
 ::: { #func.data.plot.code .sidebar }
-#### Source Code
+##### Source Code
 \
@@
 
-### [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) Function {#func.data.plot.left.n}
-\
-
-Plots a graph based on the first $n$ rows (the $n$ is specified by the [left.n](#func.data.plot.left.n.params.left.n) parameter) of the dataset passed in the [data](#func.data.plot.left.n.params.data) parameter, using both points and a line.
-
-::: {.noteblock data-latex=""}
-The dataset passed in the [data](#func.data.plot.left.n.params.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.params.xname) parameter).
+#### [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) Function {#func.data.plot.left.n}
+\
+
+Plots a graph based on the first $n$ rows (the $n$ is specified by the [left.n](#func.data.plot.left.n.args.left.n) parameter) of the dataset passed in the [data](#func.data.plot.left.n.args.data) parameter, using both points and a line.
+
+::: {.noteblock data-latex=""}
+The dataset passed in the [data](#func.data.plot.left.n.args.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.args.xname) parameter).
 :::
@@
 ::: { #func.data.plot.left.n.Usage .sidebar }
-#### Usage
+##### Usage
 \
@@
 
-::: { #func.data.plot.left.n.params .sidebar }
-#### Parameters
-\
-
-::: { #func.data.plot.left.n.params.data .sidebar }
+::: { #func.data.plot.left.n.args .sidebar }
+##### Arguments
+\
+
+::: { #func.data.plot.left.n.args.data .sidebar }
   - **data:** Dataset to use for the plot.
@@
 :::
-::: { #func.data.plot.left.n.params.left.n .sidebar }
+::: { #func.data.plot.left.n.args.left.n .sidebar }
   - **left.n:** If a positive numeric value, specifies the number of the first rows of the dataset to plot. Otherwise, the entire dataset data is set to plot.
@@
 :::
-::: { #func.data.plot.left.n.params.title .sidebar }
+::: { #func.data.plot.left.n.args.title .sidebar }
   - **title:** Title of the plot.
@@
 :::
-::: { #func.data.plot.left.n.params.xname .sidebar }
+::: { #func.data.plot.left.n.args.xname .sidebar }
   - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot.
@@
 :::
-::: { #func.data.plot.left.n.params.yname .sidebar }
+::: { #func.data.plot.left.n.args.yname .sidebar }
   - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot.
@@
 :::
-::: { #func.data.plot.left.n.params.xlabel .sidebar }
+::: { #func.data.plot.left.n.args.xlabel .sidebar }
   - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label.
@@
 :::
-::: { #func.data.plot.left.n.params.ylabel .sidebar }
+::: { #func.data.plot.left.n.args.ylabel .sidebar }
   - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.
@@
 :::
-::: { #func.data.plot.left.n.params.line_col .sidebar }
+::: { #func.data.plot.left.n.args.line_col .sidebar }
   - **line_col = blue:** The line color.
@@
 :::
-::: { #func.data.plot.left.n.params.normalize .sidebar }
+::: { #func.data.plot.left.n.args.normalize .sidebar }
   - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
@@
 ::: { #func.data.plot.left.n.details .sidebar }
-#### Details
-\
-
-The function is a wrapper for the [data.plot](#func.data.plot) function described above and is a simple and convenient tool for more detailed visualization of the left part of the graph, initially built based on the entire data set passed in the [data](#func.data.plot.left.n.params.data) parameter.
+##### Details
+\
+
+The function is a wrapper for the [data.plot](#func.data.plot) function described above and is a simple and convenient tool for more detailed visualization of the left part of the graph, initially built based on the entire data set passed in the [data](#func.data.plot.left.n.args.data) parameter.
 :::
@@
 ::: { #func.data.plot.left.n.code .sidebar }
-#### Source Code
+##### Source Code
 \
@@
 
-### [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) Function {#func.data.plot.left_detailed}
-\
-
-Combines two graphs plotted by the internally called helper functions in a grid: the first is a standard graph plotted by the [data.plot](#func.data.plot) function described above, the second is a graph based on the first $n$ rows (the $n$ is specified by the [left.n](#func.data.plot.left.n.params.left.n) parameter) of the dataset plotted by the [data.plot.left.n](#func.data.plot.left.n) function also described above (The data for both graphs is passed in the [data]).(#func.data.plot.left.n.params.data) parameter).
-
-::: {.noteblock data-latex=""}
-The dataset passed in the [data](#func.data.plot.left.n.params.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.params.xname) parameter).
+#### [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) Function {#func.data.plot.left_detailed}
+\
+
+Combines two graphs plotted by the internally called helper functions in a grid: the first is a standard graph plotted by the [data.plot](#func.data.plot) function described above, the second is a graph based on the first $n$ rows (the $n$ is specified by the [left.n](#func.data.plot.left.n.args.left.n) parameter) of the dataset plotted by the [data.plot.left.n](#func.data.plot.left.n) function also described above (The data for both graphs is passed in the [data]).(#func.data.plot.left.n.args.data) parameter).
+
+::: {.noteblock data-latex=""}
+The dataset passed in the [data](#func.data.plot.left.n.args.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.args.xname) parameter).
 :::
@@
 ::: { #func.data.plot.left_detailed.Usage .sidebar }
-#### Usage
+##### Usage
 \
@@
 
-::: { #func.data.plot.left_detailed.params .sidebar }
-#### Parameters
-\
-
-::: { #func.data.plot.left_detailed.params.data .sidebar }
+::: { #func.data.plot.left_detailed.args .sidebar }
+##### Arguments
+\
+
+::: { #func.data.plot.left_detailed.args.data .sidebar }
   - **data:** Dataset to use for the plot.
@@
 :::
-::: { #func.data.plot.left_detailed.params.title .sidebar }
+::: { #func.data.plot.left_detailed.args.title .sidebar }
   - **title:** Title of the plot.
@@
 :::
-::: { #func.data.plot.left_detailed.params.xname .sidebar }
+::: { #func.data.plot.left_detailed.args.xname .sidebar }
   - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot.
@@
 :::
-::: { #func.data.plot.left_detailed.params.yname .sidebar }
+::: { #func.data.plot.left_detailed.args.yname .sidebar }
   - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot.
@@
 :::
-::: { #func.data.plot.left_detailed.params.xlabel1 .sidebar }
+::: { #func.data.plot.left_detailed.args.xlabel1 .sidebar }
   - *xlabel1 = NULL*:** The $x$ axis label for the first plot. If `NULL`, the value of the `xname` parameter is used for the label.
@@
 :::
-::: { #func.data.plot.left_detailed.params.xlabel2 .sidebar }
+::: { #func.data.plot.left_detailed.args.xlabel2 .sidebar }
   - *xlabel2 = NULL*:** The $x$ axis label for the second plot. If `NULL`, the value of the `xname` parameter is used for the label.
@@
 :::
-::: { #func.data.plot.left_detailed.params.ylabel1 .sidebar }
+::: { #func.data.plot.left_detailed.args.ylabel1 .sidebar }
   - **ylabel1 = NULL:** The $y$ axis label for the first plot. If `NULL`, the value of the `yname` parameter is used for the label.
@@
 :::
-::: { #func.data.plot.left_detailed.params.ylabel2 .sidebar }
+::: { #func.data.plot.left_detailed.args.ylabel2 .sidebar }
   - **ylabel2 = NULL:** The $y$ axis label for the second plot. If `NULL`, the value of the `yname` parameter is used for the label.
@@
 :::
-::: { #func.data.plot.left_detailed.params.line_col .sidebar }
+::: { #func.data.plot.left_detailed.args.line_col .sidebar }
   - **line_col = blue:** The line color.
@@
 :::
-::: { #func.data.plot.left_detailed.params.normalize .sidebar }
+::: { #func.data.plot.left_detailed.args.normalize .sidebar }
   - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
@@
 ::: { #func.data.plot.left_detailed.details .sidebar }
-#### Details
+##### Details
 \
@@
 ::: { #func.data.plot.left_detailed.code .sidebar }
-#### Source Code
+##### Source Code
 \
@@
 
-### Common Helper Functions: Result RMSEs Table
+### Result RMSEs Table Functions
 \
@@
 
-::: { #func.RMSEs..params .sidebar }
-##### Parameters
-\
-
-::: { #func.RMSEs..params.RMSEs .sidebar }
+::: { #func.RMSEs..args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSEs..args.RMSEs .sidebar }
   - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
@@
 
-::: { #func.RMSEs..params. .sidebar }
+::: { #func.RMSEs..args. .sidebar }
   - ***:*** ;
@@
 
-::: { #func.RMSEs.AddRow.params .sidebar }
-##### Parameters
-\
-
-::: { #func.RMSEs.AddRow.params.RMSEs .sidebar }
+::: { #func.RMSEs.AddRow.args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSEs.AddRow.args.RMSEs .sidebar }
   - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
@@
 
-::: { #func.RMSEs.AddRow.params.method .sidebar }
+::: { #func.RMSEs.AddRow.args.method .sidebar }
   - ***method:*** The _Method or Model_ being evaluated;
@@
 
-::: { #func.RMSEs.AddRow.params.value .sidebar }
+::: { #func.RMSEs.AddRow.args.value .sidebar }
   - ***value:*** The _Root Mean Squared Error (RMSE)_ value;
@@
 
-::: { #func.RMSEs.AddRow.params.comment .sidebar }
+::: { #func.RMSEs.AddRow.args.comment .sidebar }
   - ***comment:*** Detailed information about the record or any other comment (if needed);
@@
 
-::: { #func.RMSEs.AddRow.params.before .sidebar }
+::: { #func.RMSEs.AddRow.args.before .sidebar }
   - ***before:*** One-based row index where to add the new rows, if NULL (default): after last row;
@@
 
-Adds a calculated column named _Diff_ to the _Result(RMSEs)_ table (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.params.RMSEs) parameter) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row.
+Adds a calculated column named _Diff_ to the _Result(RMSEs)_ table (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.args.RMSEs) parameter) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row.
 This is true for each row except the first, for which the value is always zero.
@@
 
-::: { #func.RMSEs.AddDiffColumn.params .sidebar }
-##### Parameters
-\
-
-::: { #func.RMSEs.AddDiffColumn.params.RMSEs .sidebar }
+::: { #func.RMSEs.AddDiffColumn.args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSEs.AddDiffColumn.args.RMSEs .sidebar }
   - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
@@
 
-::: { #func.RMSE_kable.params .sidebar }
-##### Parameters
-\
-
-::: { #func.RMSE_kable.params.RMSEs .sidebar }
+::: { #func.RMSE_kable.args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSE_kable.args.RMSEs .sidebar }
   - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
@@
 
-::: { #func.RMSE_kable.params.col1width .sidebar }
+::: { #func.RMSE_kable.args.col1width .sidebar }
   - ***col1width:*** Width of the first column;
@@
 
-::: { #func.RMSE_kable.params.col2width .sidebar }
+::: { #func.RMSE_kable.args.col2width .sidebar }
   - ***col2width:*** Width of the second column;
@@
 
-::: { #func.RMSE_kable.params.col3width .sidebar }
+::: { #func.RMSE_kable.args.col3width .sidebar }
   - ***col3width:*** Width of the third column;
@@
 
-::: { #func.RMSE.Total_kable.params .sidebar }
-##### Parameters
-\
-
-::: { #func.RMSE.Total_kable.params.RMSEs .sidebar }
+::: { #func.RMSE.Total_kable.args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
   - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
@@
 
-::: { #func.RMSE.Total_kable.params. .sidebar }
+::: { #func.RMSE.Total_kable.args. .sidebar }
   - ***col1width:*** Width of the first column;
@@
 
-::: { #func.RMSE.Total_kable.params. .sidebar }
+::: { #func.RMSE.Total_kable.args. .sidebar }
   - ***col2width:*** Width of the second column;
@@
 
-::: { #func.RMSE.Total_kable.params. .sidebar }
+::: { #func.RMSE.Total_kable.args. .sidebar }
   - ***col3width:*** Width of the third column;
@@
 
-::: { #func.RMSE.Total_kable.params. .sidebar }
+::: { #func.RMSE.Total_kable.args. .sidebar }
   - ***col4width:*** Width of the fourth column;
@@
 
-::: { #func.mean_reg.params .sidebar }
-##### Parameters
-\
-
-::: { #func.mean_reg.params.vals .sidebar }
+::: { #func.mean_reg.args .sidebar }
+##### Arguments
+\
+
+::: { #func.mean_reg.args.vals .sidebar }
   - **vals:** values (usually a numeric vector) to calculate the _penalized mean_;
@@
 :::
-::: { #func.mean_reg.params.lambda .sidebar }
+::: { #func.mean_reg.args.lambda .sidebar }
   - **lambda:** a _regularization parameter_ $\lambda$ used in the _Regularization techniques_.
@@
 ::: {.noteblock data-latex=""}
-If the [lambda](#func.mean_reg.params.lambda) parameter is `0` (the default), the function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean), calling with the parameter `trim = 0` (the default for the `base::mean` function).
+If the [lambda](#func.mean_reg.args.lambda) parameter is `0` (the default), the function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean), calling with the parameter `trim = 0` (the default for the `base::mean` function).
 :::
@@
 
-The function calculates the _penalized mean_ of the [vals](#func.mean_reg.params.vals) parameter as follows:
+The function calculates the _penalized mean_ of the [vals](#func.mean_reg.args.vals) parameter as follows:
 $$
@@
 
-When the [lambda](#func.mean_reg.params.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean as follows:
+When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean as follows:
 $$
@@
 
-::: { #func.tune.model_param.params.fn_tune.test.param_value .sidebar }
+::: { #func.tune.model_param.args.fn_tune.test.param_value .sidebar }
   - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.;
@@
 
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
+::: { #func.model.tune.param_range.args.loop_starter .sidebar }
 ###### ***loop_starter***
@@
 
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
+::: { #func.model.tune.param_range.args.tune_dir_path .sidebar }
 ###### ***tune_dir_path***
@@
 
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
+::: { #func.model.tune.param_range.args.cache_file_base_name .sidebar }
 ###### ***cache_file_base_name***
@@
 
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
+::: { #func.model.tune.param_range.args.fn_tune.test.param_value .sidebar }
 ###### ***fn_tune.test.param_value***
@@
 
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
+::: { #func.model.tune.param_range.args.max.identical.min_RMSE.count .sidebar }
 ###### ***max.identical.min_RMSE.count = 4***
@@
 
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
+::: { #func.model.tune.param_range.args.endpoint.min_diff .sidebar }
 ###### ***endpoint.min_diff = 0***
@@
 
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
+::: { #func.model.tune.param_range.args.break.if_min .sidebar }
 ###### ***break.if_min = TRUE***
@@
 
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
+::: { #func.model.tune.param_range.args.steps.beyond_min .sidebar }
 ###### ***steps.beyond_min = 2***
@@
 \
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
+First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.args.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
 
@@
 The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
+The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.args.loop_starter) parameter above for details).
 
@@
 
-##### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.params.preset.result .sidebar }
+##### Arguments
+\
+
+::: {#func.get_fine_tune.param.endpoints.args.preset.result .sidebar }
 ###### ***preset.result***
@@
 
-Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.params.preset.result) parameter.
+Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) parameter.
 
@@
 
-##### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
+##### Arguments
+\
+
+::: {#func.get_fine_tune.param.endpoints.idx.args.preset.result .sidebar }
 ###### ***preset.result***

### 2025-09-28 r/src/support-functions/UMG-effect.functions.R
Support Functions: Refactoring.

@@ -1,4 +1,6 @@
-# UMGE Model Support Functions -------------------------------------------------
+# User+Movie+Genre Effect (UMGE) Model Support Functions 
+
+## UMGE Model Utility Functions ------------------------------------------------
 calc_genre_mean_ratings <- function(train_set, min_nratings = 0) {
   genre.min_ratings <- train_set |> 
     mutate(genre_categories = as.factor(genres)) |>
@@ -142,7 +144,7 @@ calc_user_movie_genre_effect_RMSE.cv <- function(umg_effect){
   umg_effect_RMSE
 }
 
-## Regularization --------------------------------------------------------------
+## UMGE Model Regularization ---------------------------------------------------
 regularize.test_lambda.UMG_effect.cv <- function(lambda){
   if (is.na(lambda)) {
     stop("Function: regularize.test_lambda.user_movie_genre_effect.cv

### 2025-09-28 r/src/support-functions/common-helper.functions.R

@@ -1,4 +1,5 @@
-## Common Helper Functions -----------------------------------------------------
+# Common Helper Functions
+Utility Functions --------------------------------------------------------------
 # Because we know ratings can’t be below 0.5 or above 5, 
 # we define the function clamp:
 clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)

### 2025-09-28 r/src/support-functions/logging-functions.R

@@ -1,4 +1,5 @@
-### Logging Helper functions
+# Logging Helper functions
+
 open_logfile <- function(file_name){
   log_file_name <- as.character(Sys.time()) |> 
     str_replace_all(':', '_') |> 

### 2025-09-28 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
 
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
 

### 2025-09-28 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd

@@
 
-##### Parameters
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.params.day_gen_effect .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_SmoothedDay_effect.args.day_gen_effect .sidebar }
 ###### ***day_gen_effect***
@@
 \
-Under the hood, the function internally calls the [loess_de](#func.loess_de) described above and constructs the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ data object based on the object of class `loess` it returns along with the data passed by the [day_gen_effect](#func.calc_UMGY_SmoothedDay_effect.params.day_gen_effect) parameter.
+Under the hood, the function internally calls the [loess_de](#func.loess_de) described above and constructs the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ data object based on the object of class `loess` it returns along with the data passed by the [day_gen_effect](#func.calc_UMGY_SmoothedDay_effect.args.day_gen_effect) parameter.
 :::
@@
 
-::: { #func.train_UMGY_SmoothedDay_effect.params.degree .sidebar }
+::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
 ###### ***degree***
@@
 
-::: { #func.train_UMGY_SmoothedDay_effect.params.span .sidebar }
+::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
 ###### ***span***
@@
 
-This is a helper function that predicts user rating values on the _Test Set_ passed by the [test_set](#func.UMGY_SmoothedDay_effect.predict.params.test_set) parameter, taking into account the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ passed by the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect) parameter.
-
-##### Parameters
-\
-
-::: { #func.UMGY_SmoothedDay_effect.predict.params.test_set .sidebar }
+This is a helper function that predicts user rating values on the _Test Set_ passed by the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) parameter, taking into account the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ passed by the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) parameter.
+
+##### Arguments
+\
+
+::: { #func.UMGY_SmoothedDay_effect.predict.args.test_set .sidebar }
 ###### ***test_set***
@@
 
-::: { #func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect .sidebar }
+::: { #func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect .sidebar }
 ###### ***day_smoothed_effect***
@@
 
-The function calculates the _Mean Squared Error (MSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.params.test_set) parameter.
-
-##### Parameters
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.params.test_set .sidebar }
+The function calculates the _Mean Squared Error (MSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) parameter.
+
+##### Arguments
+\
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set .sidebar }
 ###### ***test_set***
@@
 
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.params.day_smoothed_effect .sidebar }
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect .sidebar }
 ###### ***day_smoothed_effect***
@@
 \
-The _Mean Squared Error (MSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.params.test_set) parameter.
+The _Mean Squared Error (MSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) parameter.
 
@@
 
-The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.params.day_smoothed_effect) parameter.
-
-##### Parameters
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.params.day_smoothed_effect .sidebar }
+The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) parameter.
+
+##### Arguments
+\
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect .sidebar }
 ###### ***day_smoothed_effect***
@@
 
-The function calculates the _Root Mean Squared Error (RMSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.params.test_set) parameter.
-
-##### Parameters
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.params.test_set .sidebar }
+The function calculates the _Root Mean Squared Error (RMSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.args.test_set) parameter.
+
+##### Arguments
+\
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.args.test_set .sidebar }
 ###### ***test_set***
@@
 
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.params.day_smoothed_effect .sidebar }
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.args.day_smoothed_effect .sidebar }
 ###### ***day_smoothed_effect***
@@
 \
-The _Root Mean Squared Error (RMSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.params.test_set) parameter.
+The _Root Mean Squared Error (RMSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.args.test_set) parameter.
 
@@
 
-The function calculates the _5-Fold Cross Validation RMSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.params.day_smoothed_effect) parameter.
-
-##### Parameters
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.params.day_smoothed_effect .sidebar }
+The function calculates the _5-Fold Cross Validation RMSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) parameter.
+
+##### Arguments
+\
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect .sidebar }
 ###### ***day_smoothed_effect***
@@
 
+::: {.noteblock data-latex=""}
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+:::
+
 Unfortunately, with the default parameters, we obtained an even worse result than before.
@@
 \
-The function is designed to tune the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function's parameters ([degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span)), which is ultimately called internally under the hood.
-
-###### Parameters
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree .sidebar }
+The function is designed to tune the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function's parameters ([degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span)), which is ultimately called internally under the hood.
+
+###### Arguments
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree .sidebar }
   - ***degree:***
@@
 
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span .sidebar }
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span .sidebar }
   - ***span:***
@@
 \
-The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 0.
-
-###### Parameters
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.params.span .sidebar }
+The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 0.
+
+###### Arguments
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span .sidebar }
   - ***span:***
@@
 \
-Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 0 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.params.span) of this function to compute the `RMSE` of the model to be tuned.
+Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 0 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) of this function to compute the `RMSE` of the model to be tuned.
 :::
@@
 \
-_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.params.span) parameter and the `degree` parameter value equal to 0.
+_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) parameter and the `degree` parameter value equal to 0.
 
@@
 \
-The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 1.
-
-###### Parameters
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.params.span .sidebar }
+The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 1.
+
+###### Arguments
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span .sidebar }
   - ***span:***
@@
 \
-Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 1 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.params.span) of this function to compute the `RMSE` of the model to be tuned.
+Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 1 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) of this function to compute the `RMSE` of the model to be tuned.
 :::
@@
 \
-_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.params.span) parameter and the `degree` parameter value equal to 1.
+_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) parameter and the `degree` parameter value equal to 1.
 
@@
 \
-The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 2.
-
-###### Parameters
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.params.span .sidebar }
+The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 2.
+
+###### Arguments
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span .sidebar }
   - ***span:***
@@
 \
-Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 2 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.params.span) of this function to compute the `RMSE` of the model to be tuned.
+Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 2 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) of this function to compute the `RMSE` of the model to be tuned.
 :::
@@
 \
-_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.params.span) parameter and the `degree` parameter value of 2.
+_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) parameter and the `degree` parameter value of 2.
 
@@
 
+::: {.noteblock data-latex=""}
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+:::
+
 #### UMGYDE Model Tuning: Step 2 (`degree = 1`)
@@
 ```
+
+::: {.noteblock data-latex=""}
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+:::
 
@@
 
+::: {.noteblock data-latex=""}
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+:::
+
 Finally, let's regularize our tuned model as we did with the previous ones.
@@
 
-The function is an overloaded version of the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.params.degree) and [span](#func.train_UMGY_SmoothedDay_effect.params.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.
-
-###### Parameters
-\
-
-::: { #func.regularize.train_UMGYD_effect.params.train_set .sidebar }
+The function is an overloaded version of the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.args.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.
+
+###### Arguments
+\
+
+::: { #func.regularize.train_UMGYD_effect.args.train_set .sidebar }
   - ***train_set:***
@@
 
-::: { #func.regularize.train_UMGYD_effect.params.lambda .sidebar }
+::: { #func.regularize.train_UMGYD_effect.args.lambda .sidebar }
   - ***lambda:***
@@
 
-The function is an overloaded version of the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.cv.params.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.params.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.
-
-###### Parameters
-\
-
-::: { #func.regularize.train_UMGYD_effect.cv.params.lambda .sidebar }
+The function is an overloaded version of the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.
+
+###### Arguments
+\
+
+::: { #func.regularize.train_UMGYD_effect.cv.args.lambda .sidebar }
   - ***lambda:***
@@
 
-::: { #func.regularize.test_lambda.UMGYD_effect.cv.params.lambda .sidebar }
+::: { #func.regularize.test_lambda.UMGYD_effect.cv.args.lambda .sidebar }
   - ***lambda:***
@@
 \
-Under the hood, the function internally calls the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) and then [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above, and returns the _RMSE_ value that the latter inner function calculates for the given [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.params.lambda) parameter value passed to the former one.
+Under the hood, the function internally calls the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) and then [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above, and returns the _RMSE_ value that the latter inner function calculates for the given [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.args.lambda) parameter value passed to the former one.
 :::
@@
 \
-_Root Mean Squared Error (RMSE)_ of the _UMGYD Model_ trained for the given [lambda](#func.regularize.train_UMGYD_effect.cv.params.span) parameter value.
+_Root Mean Squared Error (RMSE)_ of the _UMGYD Model_ trained for the given [lambda](#func.regularize.train_UMGYD_effect.cv.args.span) parameter value.
 
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
 
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
 

### 2025-09-28 reports/capstone-movielens.site/02.8-1.MF.UMGYDE-model.Rmd

@@
 
-::: { #func.mf.residual.dataframe.params.description .sidebar }
+::: { #func.mf.residual.dataframe.args.description .sidebar }
 ##### Description
@@
 
-::: { #func.mf.residual.dataframe.params.train_set .sidebar }
+::: { #func.mf.residual.dataframe.args.train_set .sidebar }
 The dataset to be trained.
@@
 
-A data frame object containing the residuals (see the [Description](#func.mf.residual.dataframe.params.description) above for the details).
+A data frame object containing the residuals (see the [Description](#func.mf.residual.dataframe.args.description) above for the details).
 
@@
 
-This is a wrapper for the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [UMGYDE Model: Helper Functions] section above with the fixed [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect) parameter value obtained after the _UMGYDE Model_ (described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section)  has been fully trained.
+This is a wrapper for the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [UMGYDE Model: Helper Functions] section above with the fixed [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) parameter value obtained after the _UMGYDE Model_ (described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section)  has been fully trained.
 
-##### Parameters
+##### Arguments
 \
 
-::: { #func.UMGYDE_model.predict.params.test_set .sidebar }
+::: { #func.UMGYDE_model.predict.args.test_set .sidebar }
 ###### ***test_set***

### 2025-09-29 reports/capstone-movielens.site/05.appendix.Rmd
Support Functions: Refactoring.
Refactoing, `clamp` function description added.

@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
-:::
+The complete source code of the functions described in this section is available in the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
+:::
+
+### Data Processing Functions
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) script on _GitHub_.
+:::
+
+#### [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) Function {#func.sample_train_validation_sets}
+\
+
+##### Usage
 
@@
 
-The soure code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) function is shown below:
+The source code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) function is shown below:
 ```{r eval=FALSE}
@@
 ## Common Helper Functions
+### Utility Functions {#appndx_a.CHF.utility_funcs}
+
+#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/common-helper.functions.R#L6) Function {#func.clamp}
+\
+
+Clamps the input value passed in [r](#func.clamp.args.r) argument between the values passed in [min](#func.clamp.args.min) and [max](#func.clamp.args.max) arguments.
+
+::: { #func.clamp.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+r_clamped <- clamp(r, min = 0.5, max = 5)
+```
+:::
+
+::: { #func.clamp.args .sidebar }
+##### Arguments
+\
+
+::: { #func.clamp.args.r .sidebar }
+  - **r:** Value to clamp;
+
+:::
+::: { #func.clamp.args.min .sidebar }
+  - **min:** Minimum allowed value;
+
+:::
+:::
+::: { #func.clamp.args.max .sidebar }
+  - **max:** Maximum allowed value;
+
+:::
+:::
+
+::: { #func.clamp.details .sidebar }
+##### Details
+\
+
+As explained in [Section  23.4 *User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
+For this reason, we need a function described in that section[@IDS2_23-4]:
+
+Therefore, in our project this function is used to clamp the computed movie rating values between 0.5 and 5.
+
+:::
+
+::: { #func.clamp.value .sidebar }
+##### Value
+\
+
+The value clamped between [min](#func.clamp.args.min) and [max](#func.clamp.args.max) argument values.
+
+:::
+
+::: { #func.clamp.code .sidebar }
+##### Source Code
+\
+
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/common-helper.functions.R#L6) function is shown below:
+```{r eval=FALSE}
+clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L6) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) script on _GitHub_.
+:::
+:::
 
@@
 
-### Common Helper Functions: Regularization {#appndx_a.CHF.regularization}
+### Regularization {#appndx_a.CHF.regularization}
 \

### 2025-09-29 reports/capstone-movielens.site/work/func-descr.template.Rmd
Refactoing, `clamp` function description added.

---
title: "func-descr.template"
output: html_document
---

#### [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/.R#LX) Function {#func.@@func}
\

::: { #func.@@func.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
@@func()

```
:::

::: { #func.@@func.args .sidebar }
##### Arguments
\

::: { #func.@@func.args. .sidebar }
  - **:** ;

:::
::: { #func.@@func.args. .sidebar }
  - **:** ;

:::
:::

::: { #func.@@func.details .sidebar }
##### Details
\

:::

::: { #func.@@func.value .sidebar }
##### Value
\

:::

::: { #func.@@func.code .sidebar }
##### Source Code
\

The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#L432) script on _GitHub_.
:::
:::

### 2025-09-29 r/src/support-functions/common-helper.functions.R

@@ -1,5 +1,6 @@
 # Common Helper Functions
-Utility Functions --------------------------------------------------------------
+
+##Utility Functions --------------------------------------------------------------
 # Because we know ratings can’t be below 0.5 or above 5, 
 # we define the function clamp:
 clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
@@ -17,7 +18,6 @@ make_ordinal_no <- function(n){
 }
 
 ## (R)MSE-related functions ---------------------------------------------------- 
-
 #> Let's define some helper functions that we will use in our subsequent analysis:
 mse <- function(r) mean(r^2)
 mse_cv <- function(r_list) {

### 2025-09-29 reports/capstone-movielens.site/02-0.methods.Rmd

@@
 
-#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L4) function {#func.clamp}
-\
-
-As explained in [Section  23.4 *User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
-For this reason, we will use the `clamp` function described in that section[@IDS2_23-4]:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
 #### Functions to calculate _(Root) Mean Squared Error_

### 2025-09-29 reports/capstone-movielens.site/work/draft-snippert.Rmd

--- 2025-09-26 reports/capstone-movielens.site/05.appendix.Rmd
@@
-# Appendix {#appndx_a}
-## Data Helper Functions {#appndx_a.data_helper.functions}
+---
+title: "func-descr.template"
+output: html_document
+---
+
+#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/common-helper.functions.R#L6) Function {#func.clamp}
 \
 
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
-:::
+Clamps the input value passed in [r](#func.clamp.args.r) argument between the values passed in [min](#func.clamp.args.min) and [max](#func.clamp.args.max) arguments.
 
-### [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) Function {#func.union_cv_results}
-\
-
-Aggregates the input data frames into a single data frame.
-
-::: { #func.union_cv_results.Usage .sidebar }
-#### Usage
+::: { #func.clamp.Usage .sidebar }
+##### Usage
 \
@@
 ```{r eval=FALSE}
-union_cv_results(data_list = data)
-
+r_clamped <- clamp(r, min = 0.5, max = 5)
 ```
@@
 
-::: { #func.union_cv_results.params .sidebar }
-#### Parameters
+::: { #func.clamp.args .sidebar }
+##### Arguments
 \
 
-::: { #func.union_cv_results.params.data_list .sidebar }
-  - **data_list:** List of data frames representing the results of the _N-Fold Cross Validation_ method execution.;
+::: { #func.clamp.args.r .sidebar }
+  - **r:** Value to clamp;
+
+:::
+::: { #func.clamp.args.min .sidebar }
+  - **min:** Minimum allowed value;
+
+:::
+:::
+::: { #func.clamp.args.max .sidebar }
+  - **max:** Maximum allowed value;
 
@@
 
-::: { #func.union_cv_results.details .sidebar }
-#### Details
+::: { #func.clamp.details .sidebar }
+##### Details
 \
 
-The function is used to aggregate the _N-Fold Cross Validation_ method result data into a single data frame for further processing.
+As explained in [Section  23.4 *User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
+For this reason, we need a function described in that section[@IDS2_23-4]:
+
+Therefore, in our project this function is used to clamp the computed movie rating values between 0.5 and 5.
 
@@
 
-::: { #func.union_cv_results.value .sidebar }
-#### Value
+::: { #func.clamp.value .sidebar }
+##### Value
 \
 
-A data frame that is a union of the input data frames.
+The value clamped between [min](#func.clamp.args.min) and [max](#func.clamp.args.max) argument values.
+
 :::
 
-::: { #func.union_cv_results.code .sidebar }
-#### Source Code
+::: { #func.clamp.code .sidebar }
+##### Source Code
 \
 
-The soure code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) function is shown below:
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/common-helper.functions.R#L6) function is shown below:
 ```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
+clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
 ```
@@
 ::: {.noteblock data-latex=""}
-The source code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) is also available in the [Model training](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L431) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) script on _GitHub_.
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L6) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) script on _GitHub_.
 :::
 :::
-
-### [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) Function {#func.data.plot}
-\
-
-Plots a graph based on the dataset passed in the [data](#func.data.plot.params.data) parameter, using both points and a line.
-
-::: { #func.data.plot.Usage .sidebar }
-#### Usage
-\
-
-```{r eval=FALSE}
-data.plot(data, 
-          title, 
-          xname, 
-          yname, 
-          xlabel = NULL, 
-          ylabel = NULL,
-          line_col = "blue",
-          normalize = FALSE)
-```
-:::
-
-::: { #func.data.plot.params .sidebar }
-#### Parameters
-\
-
-::: { #func.data.plot.params.data .sidebar }
-  - **data:** Dataset to use for the plot;
-
-:::
-::: { #func.data.plot.params.title .sidebar }
-  - **title:** Title of the plot;
-
-:::
-::: { #func.data.plot.params.xname .sidebar }
-  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;
-
-:::
-::: { #func.data.plot.params.yname .sidebar }
-  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;
-
-:::
-::: { #func.data.plot.params.xlabel .sidebar }
-  - **xlabel = NULL:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
-
-:::
-::: { #func.data.plot.params.ylabel .sidebar }
-  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;
-
-:::
-::: { #func.data.plot.params.line_col .sidebar }
-  - **line_col = blue:** The line color;
-
-:::
-::: { #func.data.plot.params.normalize .sidebar }
-  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
-
-:::
-:::
-
-::: { #func.data.plot.details .sidebar }
-#### Details
-\
-
-The function is a wrapper for the [ggplot2::ggplot](https://ggplot2.tidyverse.org/reference/ggplot.html) function and is a simple and convenient tool for visualizing the data of this project.
-
-:::
-
-::: { #func.data.plot.code .sidebar }
-#### Source Code
-\
-
-The soure code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function is shown below:
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
-:::
-:::
-
-### [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) Function {#func.data.plot.left.n}
-\
-
-Plots a graph based on the first $n$ rows (the $n$ is specified by the [left.n](#func.data.plot.left.n.params.left.n) parameter) of the dataset passed in the [data](#func.data.plot.left.n.params.data) parameter, using both points and a line.
-
-::: {.noteblock data-latex=""}
-The dataset passed in the [data](#func.data.plot.left.n.params.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.params.xname) parameter).
-:::
-
-::: { #func.data.plot.left.n.Usage .sidebar }
-#### Usage
-\
-
-```{r eval=FALSE}
-data.plot.left.n <- function(data, 
-                             left.n = 0,
-                             title, 
-                             xname, 
-                             yname, 
-                             xlabel, 
-                             ylabel,
-                             line_col = "red",
-                             normalize = FALSE)
-```
-:::
-
-::: { #func.data.plot.left.n.params .sidebar }
-#### Parameters
-\
-
-::: { #func.data.plot.left.n.params.data .sidebar }
-  - **data:** Dataset to use for the plot.
-
-:::
-::: { #func.data.plot.left.n.params.left.n .sidebar }
-  - **left.n:** If a positive numeric value, specifies the number of the first rows of the dataset to plot. Otherwise, the entire dataset data is set to plot.
-
-:::
-::: { #func.data.plot.left.n.params.title .sidebar }
-  - **title:** Title of the plot.
-
-:::
-::: { #func.data.plot.left.n.params.xname .sidebar }
-  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot.
-
-:::
-::: { #func.data.plot.left.n.params.yname .sidebar }
-  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot.
-
-:::
-::: { #func.data.plot.left.n.params.xlabel .sidebar }
-  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left.n.params.ylabel .sidebar }
-  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left.n.params.line_col .sidebar }
-  - **line_col = blue:** The line color.
-
-:::
-::: { #func.data.plot.left.n.params.normalize .sidebar }
-  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
-
-:::
-:::
-
-::: { #func.data.plot.left.n.details .sidebar }
-#### Details
-\
-
-The function is a wrapper for the [data.plot](#func.data.plot) function described above and is a simple and convenient tool for more detailed visualization of the left part of the graph, initially built based on the entire data set passed in the [data](#func.data.plot.left.n.params.data) parameter.
-:::
-
-::: { #func.data.plot.left.n.code .sidebar }
-#### Source Code
-\
-
-The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) function is shown below:
-```{r eval=FALSE}
-data.plot.left.n <- function(data, 
-                             left.n = 0,
-                             title, 
-                             xname, 
-                             yname, 
-                             xlabel, 
-                             ylabel,
-                             line_col = "red",
-                             normalize = FALSE) {
-  x_col <- data[, xname] 
-  y_col <- data[, yname]
-
-  data.left <- data
-
-  if (left.n > 0) {
-    data.left <- data |> 
-      head(left.n)
-  }
-
-  data.left |>
-    data.plot(title = title,
-              xname = xname,
-              yname = yname,
-              xlabel = xlabel,
-              ylabel = ylabel,
-              line_col = line_col,
-              normalize = normalize)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) script on _GitHub_.
-:::
-:::
-
-### [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) Function {#func.data.plot.left_detailed}
-\
-
-Combines two graphs plotted by the internally called helper functions in a grid: the first is a standard graph plotted by the [data.plot](#func.data.plot) function described above, the second is a graph based on the first $n$ rows (the $n$ is specified by the [left.n](#func.data.plot.left.n.params.left.n) parameter) of the dataset plotted by the [data.plot.left.n](#func.data.plot.left.n) function also described above (The data for both graphs is passed in the [data]).(#func.data.plot.left.n.params.data) parameter).
-
-::: {.noteblock data-latex=""}
-The dataset passed in the [data](#func.data.plot.left.n.params.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.params.xname) parameter).
-:::
-
-::: { #func.data.plot.left_detailed.Usage .sidebar }
-#### Usage
-\
-
-```{r eval=FALSE}
-data.plot.left_detailed <- function(data, 
-                                    left.n = 0,
-                                    title = NULL,
-                                    title.left = NULL,
-                                    xname, 
-                                    yname, 
-                                    xlabel1 = NULL, 
-                                    xlabel2 = NULL, 
-                                    ylabel1 = NULL,
-                                    ylabel2 = NULL,
-                                    line_col1 = "blue",
-                                    line_col2 = "red",
-                                    normalize = FALSE)
-```
-:::
-
-::: { #func.data.plot.left_detailed.params .sidebar }
-#### Parameters
-\
-
-::: { #func.data.plot.left_detailed.params.data .sidebar }
-  - **data:** Dataset to use for the plot.
-
-:::
-::: { #func.data.plot.left.n.params.left.n .sidebar }
-  - **left.n:** If a positive numeric value, specifies the number of the first rows of the dataset to plot. Otherwise, the entire dataset data is set to plot.
-
-:::
-::: { #func.data.plot.left_detailed.params.title .sidebar }
-  - **title:** Title of the plot.
-
-:::
-::: { #func.data.plot.left_detailed.params.xname .sidebar }
-  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot.
-
-:::
-::: { #func.data.plot.left_detailed.params.yname .sidebar }
-  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot.
-
-:::
-::: { #func.data.plot.left_detailed.params.xlabel1 .sidebar }
-  - *xlabel1 = NULL*:** The $x$ axis label for the first plot. If `NULL`, the value of the `xname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left_detailed.params.xlabel2 .sidebar }
-  - *xlabel2 = NULL*:** The $x$ axis label for the second plot. If `NULL`, the value of the `xname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left_detailed.params.ylabel1 .sidebar }
-  - **ylabel1 = NULL:** The $y$ axis label for the first plot. If `NULL`, the value of the `yname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left_detailed.params.ylabel2 .sidebar }
-  - **ylabel2 = NULL:** The $y$ axis label for the second plot. If `NULL`, the value of the `yname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left_detailed.params.line_col .sidebar }
-  - **line_col = blue:** The line color.
-
-:::
-::: { #func.data.plot.left_detailed.params.normalize .sidebar }
-  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
-
-:::
-:::
-
-::: { #func.data.plot.left_detailed.details .sidebar }
-#### Details
-\
-
-Under the hood, the function calls internally the [data.plot](#func.data.plot) and [data.plot.left.n](#func.data.plot.left.n) functions (described above) to build two graphs and combines them into a grid.
-:::
-
-::: { #func.data.plot.left_detailed.code .sidebar }
-#### Source Code
-\
-
-The soure code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) function is shown below:
-```{r eval=FALSE}
-data.plot.left_detailed <- function(data, 
-                                    left.n = 0,
-                                    title = NULL,
-                                    title.left = NULL,
-                                    xname, 
-                                    yname, 
-                                    xlabel1 = NULL, 
-                                    xlabel2 = NULL, 
-                                    ylabel1 = NULL,
-                                    ylabel2 = NULL,
-                                    line_col1 = "blue",
-                                    line_col2 = "red",
-                                    normalize = FALSE) {
-  if(is.null(xlabel1)) {
-    xlabel1 <- xname
-  }
-  if(is.null(xlabel2)) {
-    xlabel2 <- str_glue(xlabel1, " (left part)")
-  }
-  if(is.null(ylabel1)) {
-    ylabel1 <- yname
-  }
-  if(is.null(ylabel2)) {
-    ylabel2 <- ylabel1
-  }
-
-  p1 <- data |>
-    data.plot(title = title,
-              xname = xname, 
-              yname = yname, 
-              xlabel = xlabel1, 
-              ylabel = ylabel1,
-              line_col = line_col1)
-
-  p2 <- data |>
-    data.plot.left.n(left.n = left.n,
-                     title = title.left,
-                     xname = xname, 
-                     yname = yname, 
-                     xlabel = xlabel2, 
-                     ylabel = ylabel2,
-                     line_col = line_col2,
-                     normalize = normalize)
-  grid.arrange(p1, p2)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-## Common Helper Functions
-
-### Common Helper Functions: Result RMSEs Table
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-#### [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) Function {#func.RMSEs.}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) script on _GitHub_.
-:::
-
-::: { #func.RMSEs.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-```
-:::
-
-::: { #func.RMSEs..params .sidebar }
-##### Parameters
-\
-
-::: { #func.RMSEs..params.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
-
-:::
-
-::: { #func.RMSEs..params. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..params. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..params. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..params. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..params. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..params. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..params. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..params. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs.details .sidebar }
-##### Details
-\
-
-::: { #func.RMSEs.code .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
-```{r eval=FALSE}
-```
-:::
-
-##### Return
-
-The modified _Resut (RMSEs) Table_.
-
-#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) Function {#func.RMSEs.AddRow}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) script on _GitHub_.
-:::
-
-::: { #func.RMSEs.AddRow.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSEs.AddRow(RMSEs, 
-             method, 
-             value, 
-             comment = "", 
-             before = NULL)
-```
-:::
-
-::: { #func.RMSEs.AddRow.params .sidebar }
-##### Parameters
-\
-
-::: { #func.RMSEs.AddRow.params.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
-
-:::
-
-::: { #func.RMSEs.AddRow.params.method .sidebar }
-  - ***method:*** The _Method or Model_ being evaluated;
-
-:::
-
-::: { #func.RMSEs.AddRow.params.value .sidebar }
-  - ***value:*** The _Root Mean Squared Error (RMSE)_ value;
-
-:::
-
-::: { #func.RMSEs.AddRow.params.comment .sidebar }
-  - ***comment:*** Detailed information about the record or any other comment (if needed);
-
-:::
-
-::: { #func.RMSEs.AddRow.params.before .sidebar }
-  - ***before:*** One-based row index where to add the new rows, if NULL (default): after last row;
-
-:::
-
-::: { #func.RMSEs.AddRow.code .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
-```{r eval=FALSE}
-RMSEs.AddRow <- function(RMSEs, 
-                         method, 
-                         value, 
-                         comment = "", 
-                         before = NULL){
-  RMSEs |>
-    add_row(Method = method,
-            RMSE = value,
-            Comment = comment,
-            .before = before)
-}
-```
-:::
-
-##### Return
-
-The modified _Resut (RMSEs) Table_.
-
-#### [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L49) Function {#func.RMSEs.AddDiffColumn}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L49) script on _GitHub_.
-:::
-
-Adds a calculated column named _Diff_ to the _Result(RMSEs)_ table (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.params.RMSEs) parameter) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row.
-This is true for each row except the first, for which the value is always zero.
-
-::: { #func.RMSEs.AddDiffColumn.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSEs.ModifiedTable <- RMSEs.AddDiffColumn(RMSEs)
-```
-:::
-
-::: { #func.RMSEs.AddDiffColumn.params .sidebar }
-##### Parameters
-\
-
-::: { #func.RMSEs.AddDiffColumn.params.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
-
-:::
-
-::: { #func.RMSEs.AddDiffColumn.code .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
-```{r eval=FALSE}
-RMSEs.AddDiffColumn <- function(RMSEs){
-  RMSEs.Diff <- RMSEs |>
-    RMSEs.AddRow(NULL, project_objective, before = 1) #|>
-    #RMSEs.AddRow(NULL, 0, before = 1)
-
-  RMSEs.Diff <- RMSEs.Diff[-nrow(RMSEs.Diff),]
-
-  RMSEs |>
-  add_column(Diff = RMSEs.Diff$RMSE - RMSEs$RMSE, 
-             .before = "Comment")
-
-}
-```
-
-::: {.noteblock data-latex=""}
-Under the hood, the function calls internally the [RMSEs.AddRow](#func.RMSEs.AddRow) function described above.
-:::
-:::
-
-##### Return
-
-The modified _Resut (RMSEs) Table_.
-
-#### [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) Function {#func.RMSE_kable}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) script on _GitHub_.
-:::
-
-Prints the _Resut (RMSEs) Table_.
-
-::: {.noteblock data-latex=""}
-It is assumed that the table has the following three columns:
-
-  1. *Method*;
-  2. *RMSE*;
-  3. *Comment*;
-
-:::
-
-::: { #func.RMSE_kableusage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSE_kable <- function(RMSEs,
-                       col1width = 15,
-                       col2width = 5,
-                       col3width = 30)
-```
-:::
-
-::: { #func.RMSE_kable.params .sidebar }
-##### Parameters
-\
-
-::: { #func.RMSE_kable.params.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
-
-:::
-
-::: { #func.RMSE_kable.params.col1width .sidebar }
-  - ***col1width:*** Width of the first column;
-
-:::
-
-::: { #func.RMSE_kable.params.col2width .sidebar }
-  - ***col2width:*** Width of the second column;
-
-:::
-
-::: { #func.RMSE_kable.params.col3width .sidebar }
-  - ***col3width:*** Width of the third column;
-
-:::
-
-::: { #func.RMSE_kablecode .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
-```{r eval=FALSE}
-RMSE_kable <- function(RMSEs,
-                       col1width = 15,
-                       col2width = 5,
-                       col3width = 30){
-  RMSEs |>
-    kable(align='lcl', booktabs = T, padding = 5) |> 
-    row_spec(0, bold = T) |>
-    column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
-    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
-    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
-}
-```
-:::
-
-#### [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) Function {#func.RMSE.Total_kable}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) script on _GitHub_.
-:::
-
-Prints the _Resut (RMSEs) Table_.
-
-::: {.noteblock data-latex=""}
-It is assumed that the table has the following four columns:
-
-  1. *Method*;
-  2. *RMSE*;
-  3. *Diff*;
-  4. *Comment*;
-
-:::
-
-::: { #func.RMSE.Total_kableusage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSE.Total_kable <- function(RMSEs,
-                       col1width = 15,
-                       col2width = 7,
-                       col3width = 5,
-                       col4width = 25)
-```
-:::
-
-::: { #func.RMSE.Total_kable.params .sidebar }
-##### Parameters
-\
-
-::: { #func.RMSE.Total_kable.params.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
-
-:::
-
-::: { #func.RMSE.Total_kable.params. .sidebar }
-  - ***col1width:*** Width of the first column;
-
-:::
-
-::: { #func.RMSE.Total_kable.params. .sidebar }
-  - ***col2width:*** Width of the second column;
-
-:::
-
-::: { #func.RMSE.Total_kable.params. .sidebar }
-  - ***col3width:*** Width of the third column;
-
-:::
-
-::: { #func.RMSE.Total_kable.params. .sidebar }
-  - ***col4width:*** Width of the fourth column;
-
-:::
-
-::: { #func.RMSE.Total_kablecode .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
-```{r eval=FALSE}
-RMSE.Total_kable <- function(RMSEs,
-                       col1width = 15,
-                       col2width = 7,
-                       col3width = 5, 
-                       col4width = 25){
-  RMSEs |> 
-    RMSE_kable(col1width,
-               col2width,
-               col3width) |>
-    column_spec(column = 4, 
-                width = RSME.tibble.col_width(col4width)) 
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Under the hood, the function calls internally the [RMSE_kable](#func.RMSE_kable) function described above.
-:::
-:::
-
-### Common Helper Functions: Regularization {#appndx_a.CHF.regularization}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) Function {#func.mean_reg}
-\
-
-A general function for computing the arithmetic mean given a _regularization parameter_ $\lambda$. We will call it the _penaized mean_.
-
-::: { #func.mean_reg.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-mean_reg(vals, lambda = 0, na.rm = TRUE)
-
-```
-:::
-
-::: { #func.mean_reg.params .sidebar }
-##### Parameters
-\
-
-::: { #func.mean_reg.params.vals .sidebar }
-  - **vals:** values (usually a numeric vector) to calculate the _penalized mean_;
-
-:::
-::: { #func.mean_reg.params.lambda .sidebar }
-  - **lambda:** a _regularization parameter_ $\lambda$ used in the _Regularization techniques_.
-
-:::
-  - **na.rm:** a logical evaluating to TRUE or FALSE indicating whether NA values should be stripped before the computation proceeds.
-
-:::
-
-::: { #func.mean_reg.details .sidebar }
-##### Details
-\
-We call this function internally from the functions that compute the _penalized estimates_  as described in section [23.6 Penalized Least Squares](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook_[@IDS2_23-6].
-
-::: {.noteblock data-latex=""}
-If the [lambda](#func.mean_reg.params.lambda) parameter is `0` (the default), the function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean), calling with the parameter `trim = 0` (the default for the `base::mean` function).
-:::
-:::
-
-::: { #func.mean_reg.code .sidebar }
-##### Source Code
-\
-
-The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function is shown below:
-```{r eval=FALSE}
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L62) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) script on _GitHub_.
-:::
-:::
-
-::: { #func.mean_reg.value .sidebar }
-##### Value
-\
-
-The function calculates the _penalized mean_ of the [vals](#func.mean_reg.params.vals) parameter as follows:
-$$
-\mu(\lambda) = \frac{1}{\lambda + N} \sum_{i=1}^{N} x_i
-$$
-
-When the [lambda](#func.mean_reg.params.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean as follows:
-$$
-\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
-$$
-
-:::
-
-#### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-##### Signature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-##### Parameters
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ;
-
-::: { #func.tune.model_param.params.fn_tune.test.param_value .sidebar }
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.;
-
-:::  
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-##### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-##### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-##### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-\newpage
-
-#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-##### Signature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-##### **Parameters**
-\
-
-::: { #func.model.tune.param_range.params.loop_starter .sidebar }
-###### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.params.tune_dir_path .sidebar }
-###### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.params.cache_file_base_name .sidebar }
-###### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.params.fn_tune.test.param_value .sidebar }
-###### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.max.identical.min_RMSE.count .sidebar }
-###### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.params.endpoint.min_diff .sidebar }
-###### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.params.break.if_min .sidebar }
-###### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.params.steps.beyond_min .sidebar }
-###### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-##### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) (see the description below) and, using one more helper function [get_best_param.result](#func.get_best_param.result)  (see the description below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.params.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-##### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-##### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) Function {#func.get_fine_tune.param.endpoints}
-\
-
-The algorithm finds the values of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-##### Signature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints <- function(preset.result) {
-  # ...
-
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-}
-```
-
-##### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.params.preset.result .sidebar }
-###### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-##### Details
-\
-
-Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.params.preset.result) parameter.
-
-##### Value
-\
-A vector containing the element value corresponding to the minimum `RMSE` in a given sequence, along with the values of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-```
-
-##### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) function is provided below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints <- function(preset.result) {
-
-  preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
-
-  i <- preset.result.idx["start"]
-  j <- preset.result.idx["end"]
-  best.idx <- preset.result.idx["best"]
-
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-}
-```
-
-\newpage
-
-#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-##### Signature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-##### Parameters
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.params.preset.result .sidebar }
-###### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-##### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-##### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-##### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-\newpage
-
-#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-##### Signature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-##### Parameters
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-##### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-##### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-##### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```

### 2025-09-29 reports/capstone-movielens.site/05.appendix.Rmd
Report: Fix for `clamp` function description.

@@
 ::: {.noteblock data-latex=""}
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L6) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) script on _GitHub_.
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) script on _GitHub_.
 :::
@@
 
-### Regularization {#appndx_a.CHF.regularization}
+### Regularization Functions {#appndx_a.CHF.regularization}
 \

### 2025-09-29 reports/capstone-movielens.site/work/draft-snippert.Rmd
Report: Fix for `clamp` function description.

@@
 
-#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/common-helper.functions.R#L6) Function {#func.clamp}
+#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) Function {#func.clamp}
 \
@@
 
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/common-helper.functions.R#L6) function is shown below:
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is shown below:
 ```{r eval=FALSE}

### 2025-09-29 reports/capstone-movielens.site/work/func-descr.template.Rmd
Report: Fix for `clamp` function description.

@@
 
-#### [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/.R#LX) Function {#func.@@func}
+#### [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) Function {#func.@@func}
 \
@@
 
-The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/.R#LX) function is shown below:
+The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#L432) script on _GitHub_.
+The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) script on _GitHub_.
 :::

### 2025-09-29 reports/capstone-movielens.site/05.appendix.Rmd
Capstone Report: `open_logfile` function description added.

@@
 # Appendix {#appndx_a}
+## Common Helper Functions
+### Logging Functions {#appndx_a.CHF.logging-funcs}
+
+::: {.noteblock data-latex=""}
+The full source code of the functions described in this section is available in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R) script on _GitHub_.
+:::
+
+#### [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) Function {#func.open_logfile}
+\
+
+A function to initialize the log file.
+
+::: { #func.open_logfile.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+open_logfile(file_name)
+```
+:::
+
+::: { #func.open_logfile.args .sidebar }
+##### Arguments
+\
+
+::: { #func.open_logfile.args.r .sidebar }
+  - **file_name:** A name used as a base to generate a unique log file name;
+
+:::
+:::
+
+::: { #func.open_logfile.details .sidebar }
+##### Details
+\
+
+This function is a wrapper to [logr::log_open](https://www.rdocumentation.org/packages/logr/versions/1.3.9/topics/log_open) function.
+It also calls internally the following functions to generate a unique file name based on the [file_name] argument and _system time_:
+  - [Sys.time]();
+  - [stringr::str_replace](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace);
+  - [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace)
+
+For more information on the _inner functions_ listed above, see the [R Documentation](https://www.rdocumentation.org/).
+
+:::
+
+::: { #func.open_logfile.value .sidebar }
+##### Value
+\
+
+The path of the log.
+
+:::
+
+::: { #func.open_logfile.code .sidebar }
+##### Source Code
+\
+
+The source code of the [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) function is shown below:
+```{r eval=FALSE}
+library(logr)
+library(stringr)
+
+open_logfile <- function(file_name){
+  log_file_name <- as.character(Sys.time()) |> 
+    str_replace_all(':', '_') |> 
+    str_replace(' ', 'T') |>
+    str_c(file_name)
+
+  log_open(file_name = log_file_name)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) function is also available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L1) section of the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) script on _GitHub_.
+:::
+:::
+
+### Utility Functions {#appndx_a.CHF.utility_funcs}
+
+#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) Function {#func.clamp}
+\
+
+Clamps the input value passed in [r](#func.clamp.args.r) argument between the values passed in [min](#func.clamp.args.min) and [max](#func.clamp.args.max) arguments.
+
+::: { #func.clamp.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+r_clamped <- clamp(r, min = 0.5, max = 5)
+```
+:::
+
+::: { #func.clamp.args .sidebar }
+##### Arguments
+\
+
+::: { #func.clamp.args.r .sidebar }
+  - **r:** Value to clamp;
+
+:::
+::: { #func.clamp.args.min .sidebar }
+  - **min:** Minimum allowed value;
+
+:::
+:::
+::: { #func.clamp.args.max .sidebar }
+  - **max:** Maximum allowed value;
+
+:::
+:::
+
+::: { #func.clamp.details .sidebar }
+##### Details
+\
+
+As explained in [Section  23.4 *User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
+For this reason, we need a function described in that section[@IDS2_23-4]:
+
+Therefore, in our project this function is used to clamp the computed movie rating values between 0.5 and 5.
+
+:::
+
+::: { #func.clamp.value .sidebar }
+##### Value
+\
+
+The value clamped between [min](#func.clamp.args.min) and [max](#func.clamp.args.max) argument values.
+
+:::
+
+::: { #func.clamp.code .sidebar }
+##### Source Code
+\
+
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is shown below:
+```{r eval=FALSE}
+clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) script on _GitHub_.
+:::
+:::
+
+### Result RMSEs Table Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+:::
+
+#### [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) Function {#func.RMSEs.}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) script on _GitHub_.
+:::
+
+::: { #func.RMSEs.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.RMSEs..args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSEs..args.RMSEs .sidebar }
+  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.details .sidebar }
+##### Details
+\
+
+::: { #func.RMSEs.code .sidebar }
+##### Source Code
+\
+
+The soure code of the function is provided below:
+```{r eval=FALSE}
+```
+:::
+
+##### Return
+
+The modified _Resut (RMSEs) Table_.
+
+#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) Function {#func.RMSEs.AddRow}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) script on _GitHub_.
+:::
+
+::: { #func.RMSEs.AddRow.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+RMSEs.AddRow(RMSEs, 
+             method, 
+             value, 
+             comment = "", 
+             before = NULL)
+```
+:::
+
+::: { #func.RMSEs.AddRow.args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSEs.AddRow.args.RMSEs .sidebar }
+  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
+
+:::
+
+::: { #func.RMSEs.AddRow.args.method .sidebar }
+  - ***method:*** The _Method or Model_ being evaluated;
+
+:::
+
+::: { #func.RMSEs.AddRow.args.value .sidebar }
+  - ***value:*** The _Root Mean Squared Error (RMSE)_ value;
+
+:::
+
+::: { #func.RMSEs.AddRow.args.comment .sidebar }
+  - ***comment:*** Detailed information about the record or any other comment (if needed);
+
+:::
+
+::: { #func.RMSEs.AddRow.args.before .sidebar }
+  - ***before:*** One-based row index where to add the new rows, if NULL (default): after last row;
+
+:::
+
+::: { #func.RMSEs.AddRow.code .sidebar }
+##### Source Code
+\
+
+The soure code of the function is provided below:
+```{r eval=FALSE}
+RMSEs.AddRow <- function(RMSEs, 
+                         method, 
+                         value, 
+                         comment = "", 
+                         before = NULL){
+  RMSEs |>
+    add_row(Method = method,
+            RMSE = value,
+            Comment = comment,
+            .before = before)
+}
+```
+:::
+
+##### Return
+
+The modified _Resut (RMSEs) Table_.
+
+#### [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L49) Function {#func.RMSEs.AddDiffColumn}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L49) script on _GitHub_.
+:::
+
+Adds a calculated column named _Diff_ to the _Result(RMSEs)_ table (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.args.RMSEs) parameter) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row.
+This is true for each row except the first, for which the value is always zero.
+
+::: { #func.RMSEs.AddDiffColumn.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+RMSEs.ModifiedTable <- RMSEs.AddDiffColumn(RMSEs)
+```
+:::
+
+::: { #func.RMSEs.AddDiffColumn.args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSEs.AddDiffColumn.args.RMSEs .sidebar }
+  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
+
+:::
+
+::: { #func.RMSEs.AddDiffColumn.code .sidebar }
+##### Source Code
+\
+
+The soure code of the function is provided below:
+```{r eval=FALSE}
+RMSEs.AddDiffColumn <- function(RMSEs){
+  RMSEs.Diff <- RMSEs |>
+    RMSEs.AddRow(NULL, project_objective, before = 1) #|>
+    #RMSEs.AddRow(NULL, 0, before = 1)
+
+  RMSEs.Diff <- RMSEs.Diff[-nrow(RMSEs.Diff),]
+
+  RMSEs |>
+  add_column(Diff = RMSEs.Diff$RMSE - RMSEs$RMSE, 
+             .before = "Comment")
+
+}
+```
+
+::: {.noteblock data-latex=""}
+Under the hood, the function calls internally the [RMSEs.AddRow](#func.RMSEs.AddRow) function described above.
+:::
+:::
+
+##### Return
+
+The modified _Resut (RMSEs) Table_.
+
+#### [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) Function {#func.RMSE_kable}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) script on _GitHub_.
+:::
+
+Prints the _Resut (RMSEs) Table_.
+
+::: {.noteblock data-latex=""}
+It is assumed that the table has the following three columns:
+
+  1. *Method*;
+  2. *RMSE*;
+  3. *Comment*;
+
+:::
+
+::: { #func.RMSE_kableusage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+RMSE_kable <- function(RMSEs,
+                       col1width = 15,
+                       col2width = 5,
+                       col3width = 30)
+```
+:::
+
+::: { #func.RMSE_kable.args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSE_kable.args.RMSEs .sidebar }
+  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
+
+:::
+
+::: { #func.RMSE_kable.args.col1width .sidebar }
+  - ***col1width:*** Width of the first column;
+
+:::
+
+::: { #func.RMSE_kable.args.col2width .sidebar }
+  - ***col2width:*** Width of the second column;
+
+:::
+
+::: { #func.RMSE_kable.args.col3width .sidebar }
+  - ***col3width:*** Width of the third column;
+
+:::
+
+::: { #func.RMSE_kablecode .sidebar }
+##### Source Code
+\
+
+The soure code of the function is provided below:
+```{r eval=FALSE}
+RMSE_kable <- function(RMSEs,
+                       col1width = 15,
+                       col2width = 5,
+                       col3width = 30){
+  RMSEs |>
+    kable(align='lcl', booktabs = T, padding = 5) |> 
+    row_spec(0, bold = T) |>
+    column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
+    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
+    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
+}
+```
+:::
+
+#### [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) Function {#func.RMSE.Total_kable}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) script on _GitHub_.
+:::
+
+Prints the _Resut (RMSEs) Table_.
+
+::: {.noteblock data-latex=""}
+It is assumed that the table has the following four columns:
+
+  1. *Method*;
+  2. *RMSE*;
+  3. *Diff*;
+  4. *Comment*;
+
+:::
+
+::: { #func.RMSE.Total_kableusage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+RMSE.Total_kable <- function(RMSEs,
+                       col1width = 15,
+                       col2width = 7,
+                       col3width = 5,
+                       col4width = 25)
+```
+:::
+
+::: { #func.RMSE.Total_kable.args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
+  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
+
+:::
+
+::: { #func.RMSE.Total_kable.args. .sidebar }
+  - ***col1width:*** Width of the first column;
+
+:::
+
+::: { #func.RMSE.Total_kable.args. .sidebar }
+  - ***col2width:*** Width of the second column;
+
+:::
+
+::: { #func.RMSE.Total_kable.args. .sidebar }
+  - ***col3width:*** Width of the third column;
+
+:::
+
+::: { #func.RMSE.Total_kable.args. .sidebar }
+  - ***col4width:*** Width of the fourth column;
+
+:::
+
+::: { #func.RMSE.Total_kablecode .sidebar }
+##### Source Code
+\
+
+The soure code of the function is provided below:
+```{r eval=FALSE}
+RMSE.Total_kable <- function(RMSEs,
+                       col1width = 15,
+                       col2width = 7,
+                       col3width = 5, 
+                       col4width = 25){
+  RMSEs |> 
+    RMSE_kable(col1width,
+               col2width,
+               col3width) |>
+    column_spec(column = 4, 
+                width = RSME.tibble.col_width(col4width)) 
+}
+
+```
+
+::: {.noteblock data-latex=""}
+Under the hood, the function calls internally the [RMSE_kable](#func.RMSE_kable) function described above.
+:::
+:::
+
+### Regularization Functions {#appndx_a.CHF.regularization}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+:::
+
+#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) Function {#func.mean_reg}
+\
+
+A general function for computing the arithmetic mean given a _regularization parameter_ $\lambda$. We will call it the _penaized mean_.
+
+::: { #func.mean_reg.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+mean_reg(vals, lambda = 0, na.rm = TRUE)
+
+```
+:::
+
+::: { #func.mean_reg.args .sidebar }
+##### Arguments
+\
+
+::: { #func.mean_reg.args.vals .sidebar }
+  - **vals:** values (usually a numeric vector) to calculate the _penalized mean_;
+
+:::
+::: { #func.mean_reg.args.lambda .sidebar }
+  - **lambda:** a _regularization parameter_ $\lambda$ used in the _Regularization techniques_.
+
+:::
+  - **na.rm:** a logical evaluating to TRUE or FALSE indicating whether NA values should be stripped before the computation proceeds.
+
+:::
+
+::: { #func.mean_reg.details .sidebar }
+##### Details
+\
+We call this function internally from the functions that compute the _penalized estimates_  as described in section [23.6 Penalized Least Squares](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook_[@IDS2_23-6].
+
+::: {.noteblock data-latex=""}
+If the [lambda](#func.mean_reg.args.lambda) parameter is `0` (the default), the function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean), calling with the parameter `trim = 0` (the default for the `base::mean` function).
+:::
+:::
+
+::: { #func.mean_reg.code .sidebar }
+##### Source Code
+\
+
+The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function is shown below:
+```{r eval=FALSE}
+mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
+  if (is.na(lambda)) {
+    stop("Function: mean_reg
+`lambda` is `NA`")
+  }
+
+  names(lambda) <- NULL
+  sums <- sum(vals, na.rm = na.rm)
+  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
+  sums/(N + lambda)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L62) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) script on _GitHub_.
+:::
+:::
+
+::: { #func.mean_reg.value .sidebar }
+##### Value
+\
+
+The function calculates the _penalized mean_ of the [vals](#func.mean_reg.args.vals) parameter as follows:
+$$
+\mu(\lambda) = \frac{1}{\lambda + N} \sum_{i=1}^{N} x_i
+$$
+
+When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean as follows:
+$$
+\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
+$$
+
+:::
+
+#### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
+\
+
+The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
+
+##### Signature
+\
+```{r eval=FALSE}
+tune.model_param <- function(param_values, 
+                             fn_tune.test.param_value, 
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+
+# ...
+  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
+                                parameter.value = param_vals_tmp),
+       best_result = param_values.best_result)
+}  
+```
+
+##### Arguments
+\
+
+  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ;
+
+::: { #func.tune.model_param.args.fn_tune.test.param_value .sidebar }
+  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.;
+
+:::  
+  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
+
+  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
+
+##### Details
+\
+During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
+
+::: {.noteblock data-latex=""}
+Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
+That is, it is assumed that the function has a single minimum on the given interval.
+:::
+
+::: { #func.tune.model_param.value .sidebar }
+##### Value
+\
+The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
+```{r eval=FALSE}
+  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
+                                parameter.value = param_vals_tmp),
+       best_result = param_values.best_result)
+```
+:::
+
+##### Source Code
+\
+Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
+```{r eval=FALSE}
+tune.model_param <- function(param_values, 
+                             fn_tune.test.param_value, 
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+  n <- length(param_values)
+  param_vals_tmp <- numeric()
+  RMSEs_tmp <- numeric()
+  RMSE_min <- Inf
+  i_max.beyond_RMSE_min <- Inf
+  prm_val.best <- NA
+
+  # ...
+
+  for (i in 1:n) {
+    put_log1("Function: `tune.model_param`:
+Iteration %1", i)
+    prm_val <- param_values[i]
+    param_vals_tmp[i] <- prm_val
+
+    RMSE_tmp <- fn_tune.test.param_value(prm_val)
+    RMSEs_tmp[i] <- RMSE_tmp
+
+    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
+
+    if(RMSE_tmp > RMSE_min){
+      warning("Function: `tune.model_param`:
+`RSME` reached its minimum: ", RMSE_min, "
+for parameter value: ", prm_val)
+      put_log2("Function: `tune.model_param`:
+Current `RMSE` value is %1 related to parameter value: %2",
+               RMSE_tmp,
+               prm_val)
+
+      if (i > i_max.beyond_RMSE_min) {
+        warning("Function: `tune.model_param`:
+Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
+        break
+      }
+      next
+    }
+
+    RMSE_min <- RMSE_tmp
+    prm_val.best <- prm_val
+
+    if (break.if_min) {
+      i_max.beyond_RMSE_min <- i + steps.beyond_min
+    }
+  }
+
+  param_values.best_result <- c(param.best_value = prm_val.best, 
+                                best_RMSE = RMSE_min)
+
+  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
+                                parameter.value = param_vals_tmp),
+       best_result = param_values.best_result)
+}
+```
+
+\newpage
+
+#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
+\
+
+The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
+
+##### Signature
+\
+```{r eval=FALSE}
+model.tune.param_range <- function(loop_starter,
+                             tune_dir_path,
+                             cache_file_base_name,
+                             fn_tune.test.param_value,
+                             max.identical.min_RMSE.count = 4,
+                             endpoint.min_diff = 0,
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+  # ...
+  list(best_result = param_values.best_result,
+       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
+       tuned.result = data.frame(parameter.value = parameter.value,
+                                 RMSE = result.RMSE))
+}
+```
+
+##### **Parameters**
+\
+
+::: { #func.model.tune.param_range.args.loop_starter .sidebar }
+###### ***loop_starter***
+\
+A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
+`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
+For this purpose, the sequence step is calculated as follows:
+$$
+step = \frac{end - start}{dvs}
+$$
+
+The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
+```{r eval=FALSE}
+seq(start, end, step)
+```  
+In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
+:::
+
+::: { #func.model.tune.param_range.args.tune_dir_path .sidebar }
+###### ***tune_dir_path***
+\
+To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
+:::
+
+::: { #func.model.tune.param_range.args.cache_file_base_name .sidebar }
+###### ***cache_file_base_name***
+\
+The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
+:::
+
+::: { #func.model.tune.param_range.args.fn_tune.test.param_value .sidebar }
+###### ***fn_tune.test.param_value***
+\
+This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+:::
+
+::: { #func.model.tune.param_range.args.max.identical.min_RMSE.count .sidebar }
+###### ***max.identical.min_RMSE.count = 4***
+\
+If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
+When it is reached, the algorithm considers the task execution to be complete.
+:::
+
+::: { #func.model.tune.param_range.args.endpoint.min_diff .sidebar }
+###### ***endpoint.min_diff = 0***
+\
+Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
+:::
+
+::: { #func.model.tune.param_range.args.break.if_min .sidebar }
+###### ***break.if_min = TRUE***
+\
+This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+:::
+
+::: { #func.model.tune.param_range.args.steps.beyond_min .sidebar }
+###### ***steps.beyond_min = 2***
+\
+This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+
+::: { #func.model.tune.param_range.details .sidebar }
+##### **Details** 
+\
+First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.args.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
+
+The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
+
+Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) (see the description below) and, using one more helper function [get_best_param.result](#func.get_best_param.result)  (see the description below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
+
+The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
+The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.args.loop_starter) parameter above for details).
+
+Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
+
+The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
+:::
+
+##### **Value**
+\
+
+A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
+```{r eval=FALSE}
+  list(best_result = param_values.best_result,
+       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
+       tuned.result = data.frame(parameter.value = parameter.value,
+                                 RMSE = result.RMSE))
+```
+
+::: {#func.model.tune.param_range.code .sidebar }
+##### Source Code
+\
+Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
+```{r eval=FALSE}
+model.tune.param_range <- function(loop_starter,
+                             tune_dir_path,
+                             cache_file_base_name,
+                             fn_tune.test.param_value,
+                             max.identical.min_RMSE.count = 4,
+                             is.cv = TRUE,
+                             endpoint.min_diff = 0, #1e-07,
+                             break.if_min = TRUE,
+                             steps.beyond_min = 2){
+
+  seq_start <- loop_starter[1]
+  seq_end <- loop_starter[2]
+  interval_divisor <- loop_starter[3]
+
+  if (interval_divisor < 4) {
+    interval_divisor <- 4
+  }
+
+  prm_val.leftmost <- seq_start
+  prm_val.rightmost <- seq_end
+
+  RMSE.leftmost <- NA
+  RMSE.rightmost <- NA
+
+  best_RMSE <- NA
+  param.best_value <- 0
+
+  param_values.best_result <- c(param.best_value = param.best_value, 
+                                best_RMSE = best_RMSE)
+  # Start repeat loop
+  repeat{
+    seq_increment <- (seq_end - seq_start)/interval_divisor
+
+    if (seq_increment < 0.0000000000001) {
+      warning("Function `model.tune.param_range`:
+parameter value increment is too small.")
+      break
+    }
+
+    test_param_vals <- seq(seq_start, seq_end, seq_increment)
+
+    tuned_result <- tune.model_param(test_param_vals, 
+                                  fn_tune.test.param_value,
+                                  break.if_min,
+                                  steps.beyond_min)
+
+    tuned.result <- tuned_result$tuned.result
+    plot(tuned.result$parameter.value, tuned.result$RMSE)
+
+    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
+    start.idx <- bound.idx["start"]
+    end.idx <- bound.idx["end"]
+    best_RMSE.idx <- bound.idx["best"]
+
+    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
+    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
+
+    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
+    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
+
+    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
+    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
+
+    seq_start <- prm_val.leftmost.tmp
+    seq_end <- prm_val.rightmost.tmp
+
+    if (is.na(best_RMSE)) {
+      prm_val.leftmost <- prm_val.leftmost.tmp
+      RMSE.leftmost <- RMSE.leftmost.tmp
+
+      prm_val.rightmost <- prm_val.rightmost.tmp
+      RMSE.rightmost <- RMSE.rightmost.tmp
+
+      param.best_value <- min_RMSE.prm_val
+      best_RMSE <- min_RMSE
+    }
+
+    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
+      prm_val.leftmost <- prm_val.leftmost.tmp
+      RMSE.leftmost <- RMSE.leftmost.tmp
+    }
+
+    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
+      prm_val.rightmost <- prm_val.rightmost.tmp
+      RMSE.rightmost <- RMSE.rightmost.tmp
+    }
+
+    if (end.idx - start.idx <= 0) {
+      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
+      break
+    }
+
+    if (best_RMSE == min_RMSE) {
+      warning("Currently computed minimal RMSE equals the previously reached best one: ",
+              best_RMSE, "
+Currently computed minial value is: ", min_RMSE)
+
+      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
+        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
+                max.identical.min_RMSE.count)
+
+        param_values.best_result <-
+          get_best_param.result(tuned.result$parameter.value,
+                                tuned.result$RMSE)
+        break
+      }
+
+    } else if (best_RMSE < min_RMSE) {
+      stop("Current minimal RMSE is greater than previously computed best value: ",
+           best_RMSE, "
+Currently computed minial value is: ", min_RMSE)
+    }
+
+    best_RMSE <- min_RMSE
+    param.best_value <- min_RMSE.prm_val
+
+    param_values.best_result <- 
+      get_best_param.result(tuned.result$parameter.value, 
+                          tuned.result$RMSE)
+  }
+  # End repeat loop
+
+  n <- length(tuned.result$parameter.value)
+  parameter.value <- tuned.result$parameter.value
+  result.RMSE <- tuned.result$RMSE
+
+  if (result.RMSE[1] == best_RMSE) {
+    parameter.value[1] <- prm_val.leftmost
+    result.RMSE[1] <- RMSE.leftmost
+  }
+  if (result.RMSE[n] == best_RMSE) {
+    parameter.value[n+1] <- prm_val.rightmost
+    result.RMSE[n+1] <- RMSE.rightmost
+  }
+
+  list(best_result = param_values.best_result,
+       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
+       tuned.result = data.frame(parameter.value = parameter.value,
+                                 RMSE = result.RMSE))
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) Function {#func.get_fine_tune.param.endpoints}
+\
+
+The algorithm finds the values of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
+
+##### Signature
+\
+```{r eval=FALSE}
+get_fine_tune.param.endpoints <- function(preset.result) {
+  # ...
+
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+}
+```
+
+##### Arguments
+\
+
+::: {#func.get_fine_tune.param.endpoints.args.preset.result .sidebar }
+###### ***preset.result***
+\
+A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
+Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
+```{r eval=FALSE}
+    tuned_result <- tune.model_param(test_param_vals, 
+                                  fn_tune.test.param_value,
+                                  break.if_min,
+                                  steps.beyond_min)
+
+    tuned.result <- tuned_result$tuned.result
+    # tuned.result = data.frame(RMSE, parameter.value)
+    # ...
+    bound.idx <- get_fine_tune.param.endpoints(tuned.result)
+    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
+```
+:::
+
+##### Details
+\
+
+Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) parameter.
+
+##### Value
+\
+A vector containing the element value corresponding to the minimum `RMSE` in a given sequence, along with the values of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+```
+
+##### Source Code
+\
+The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) function is provided below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints <- function(preset.result) {
+
+  preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
+
+  i <- preset.result.idx["start"]
+  j <- preset.result.idx["end"]
+  best.idx <- preset.result.idx["best"]
+
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+}
+```
+
+\newpage
+
+#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
+\
+
+##### Signature
+\
+```{r eval=FALSE}
+get_fine_tune.param.endpoints.idx <- function(preset.result) {
+  # ...
+
+  c(start = i, 
+    end = j,
+    best = best_RMSE.idx)
+}
+```
+
+##### Arguments
+\
+
+::: {#func.get_fine_tune.param.endpoints.idx.args.preset.result .sidebar }
+###### ***preset.result***
+\
+A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
+Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
+```{r eval=FALSE}
+    tuned_result <- tune.model_param(test_param_vals, 
+                                  fn_tune.test.param_value,
+                                  break.if_min,
+                                  steps.beyond_min)
+
+    tuned.result <- tuned_result$tuned.result
+    # tuned.result = data.frame(RMSE, parameter.value)
+    # ...
+    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
+    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
+```
+:::
+
+##### Details
+\
+The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
+
+##### Value
+\
+A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start, # interval start index
+    end,   # interval end index
+    best)  # index of the best `RMSE`
+```
+
+##### Source Code
+\
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints.idx <- function(preset.result) {
+  best_RMSE <- min(preset.result$RMSE)
+  best_RMSE.idx <- which.min(preset.result$RMSE)
+  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
+
+  preset.result.N <- length(preset.result$RMSE)
+  i <- best_RMSE.idx
+  j <- i
+
+  while (i > 1) {
+    i <- i - 1
+
+    if (preset.result$RMSE[i] > best_RMSE) {
+      break
+    }
+  }
+
+  while (j < preset.result.N) {
+    j <- j + 1
+
+    if (preset.result$RMSE[j] > best_RMSE) {
+      break
+    }
+  }
+
+  c(start = i, 
+    end = j,
+    best = best_RMSE.idx)
+}
+
+```
+
+\newpage
+
+#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
+\
+
+##### Signature
+\
+```{r eval=FALSE}
+get_best_param.result <- function(param_values, rmses){
+  # ...
+
+  c(param.best_value = param_values[best_pvalue_idx], 
+    best_RMSE = rmses[best_pvalue_idx])
+
+```
+
+##### Arguments
+\
+A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
+
+  - **param_values:** A vector containing the values of the input parameters for tuning;; 
+  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
+
+##### Details
+\
+Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
+
+##### Value
+\
+A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
+```{r eval=FALSE}
+c(param.best_value, best_RMSE)
+```
+
+##### Source Code
+\
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
+```{r eval=FALSE}
+get_best_param.result <- function(param_values, rmses){
+  best_pvalue_idx <- which.min(rmses)
+  c(param.best_value = param_values[best_pvalue_idx], 
+    best_RMSE = rmses[best_pvalue_idx])
+```
+
 ## Data Helper Functions {#appndx_a.data_helper.functions}
@@
 \newpage
-
-## Common Helper Functions
-### Utility Functions {#appndx_a.CHF.utility_funcs}
-
-#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) Function {#func.clamp}
-\
-
-Clamps the input value passed in [r](#func.clamp.args.r) argument between the values passed in [min](#func.clamp.args.min) and [max](#func.clamp.args.max) arguments.
-
-::: { #func.clamp.Usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-r_clamped <- clamp(r, min = 0.5, max = 5)
-```
-:::
-
-::: { #func.clamp.args .sidebar }
-##### Arguments
-\
-
-::: { #func.clamp.args.r .sidebar }
-  - **r:** Value to clamp;
-
-:::
-::: { #func.clamp.args.min .sidebar }
-  - **min:** Minimum allowed value;
-
-:::
-:::
-::: { #func.clamp.args.max .sidebar }
-  - **max:** Maximum allowed value;
-
-:::
-:::
-
-::: { #func.clamp.details .sidebar }
-##### Details
-\
-
-As explained in [Section  23.4 *User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
-For this reason, we need a function described in that section[@IDS2_23-4]:
-
-Therefore, in our project this function is used to clamp the computed movie rating values between 0.5 and 5.
-
-:::
-
-::: { #func.clamp.value .sidebar }
-##### Value
-\
-
-The value clamped between [min](#func.clamp.args.min) and [max](#func.clamp.args.max) argument values.
-
-:::
-
-::: { #func.clamp.code .sidebar }
-##### Source Code
-\
-
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is shown below:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) script on _GitHub_.
-:::
-:::
-
-### Result RMSEs Table Functions
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-#### [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) Function {#func.RMSEs.}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) script on _GitHub_.
-:::
-
-::: { #func.RMSEs.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-```
-:::
-
-::: { #func.RMSEs..args .sidebar }
-##### Arguments
-\
-
-::: { #func.RMSEs..args.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs.details .sidebar }
-##### Details
-\
-
-::: { #func.RMSEs.code .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
-```{r eval=FALSE}
-```
-:::
-
-##### Return
-
-The modified _Resut (RMSEs) Table_.
-
-#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) Function {#func.RMSEs.AddRow}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) script on _GitHub_.
-:::
-
-::: { #func.RMSEs.AddRow.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSEs.AddRow(RMSEs, 
-             method, 
-             value, 
-             comment = "", 
-             before = NULL)
-```
-:::
-
-::: { #func.RMSEs.AddRow.args .sidebar }
-##### Arguments
-\
-
-::: { #func.RMSEs.AddRow.args.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
-
-:::
-
-::: { #func.RMSEs.AddRow.args.method .sidebar }
-  - ***method:*** The _Method or Model_ being evaluated;
-
-:::
-
-::: { #func.RMSEs.AddRow.args.value .sidebar }
-  - ***value:*** The _Root Mean Squared Error (RMSE)_ value;
-
-:::
-
-::: { #func.RMSEs.AddRow.args.comment .sidebar }
-  - ***comment:*** Detailed information about the record or any other comment (if needed);
-
-:::
-
-::: { #func.RMSEs.AddRow.args.before .sidebar }
-  - ***before:*** One-based row index where to add the new rows, if NULL (default): after last row;
-
-:::
-
-::: { #func.RMSEs.AddRow.code .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
-```{r eval=FALSE}
-RMSEs.AddRow <- function(RMSEs, 
-                         method, 
-                         value, 
-                         comment = "", 
-                         before = NULL){
-  RMSEs |>
-    add_row(Method = method,
-            RMSE = value,
-            Comment = comment,
-            .before = before)
-}
-```
-:::
-
-##### Return
-
-The modified _Resut (RMSEs) Table_.
-
-#### [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L49) Function {#func.RMSEs.AddDiffColumn}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L49) script on _GitHub_.
-:::
-
-Adds a calculated column named _Diff_ to the _Result(RMSEs)_ table (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.args.RMSEs) parameter) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row.
-This is true for each row except the first, for which the value is always zero.
-
-::: { #func.RMSEs.AddDiffColumn.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSEs.ModifiedTable <- RMSEs.AddDiffColumn(RMSEs)
-```
-:::
-
-::: { #func.RMSEs.AddDiffColumn.args .sidebar }
-##### Arguments
-\
-
-::: { #func.RMSEs.AddDiffColumn.args.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
-
-:::
-
-::: { #func.RMSEs.AddDiffColumn.code .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
-```{r eval=FALSE}
-RMSEs.AddDiffColumn <- function(RMSEs){
-  RMSEs.Diff <- RMSEs |>
-    RMSEs.AddRow(NULL, project_objective, before = 1) #|>
-    #RMSEs.AddRow(NULL, 0, before = 1)
-
-  RMSEs.Diff <- RMSEs.Diff[-nrow(RMSEs.Diff),]
-
-  RMSEs |>
-  add_column(Diff = RMSEs.Diff$RMSE - RMSEs$RMSE, 
-             .before = "Comment")
-
-}
-```
-
-::: {.noteblock data-latex=""}
-Under the hood, the function calls internally the [RMSEs.AddRow](#func.RMSEs.AddRow) function described above.
-:::
-:::
-
-##### Return
-
-The modified _Resut (RMSEs) Table_.
-
-#### [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) Function {#func.RMSE_kable}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) script on _GitHub_.
-:::
-
-Prints the _Resut (RMSEs) Table_.
-
-::: {.noteblock data-latex=""}
-It is assumed that the table has the following three columns:
-
-  1. *Method*;
-  2. *RMSE*;
-  3. *Comment*;
-
-:::
-
-::: { #func.RMSE_kableusage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSE_kable <- function(RMSEs,
-                       col1width = 15,
-                       col2width = 5,
-                       col3width = 30)
-```
-:::
-
-::: { #func.RMSE_kable.args .sidebar }
-##### Arguments
-\
-
-::: { #func.RMSE_kable.args.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
-
-:::
-
-::: { #func.RMSE_kable.args.col1width .sidebar }
-  - ***col1width:*** Width of the first column;
-
-:::
-
-::: { #func.RMSE_kable.args.col2width .sidebar }
-  - ***col2width:*** Width of the second column;
-
-:::
-
-::: { #func.RMSE_kable.args.col3width .sidebar }
-  - ***col3width:*** Width of the third column;
-
-:::
-
-::: { #func.RMSE_kablecode .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
-```{r eval=FALSE}
-RMSE_kable <- function(RMSEs,
-                       col1width = 15,
-                       col2width = 5,
-                       col3width = 30){
-  RMSEs |>
-    kable(align='lcl', booktabs = T, padding = 5) |> 
-    row_spec(0, bold = T) |>
-    column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
-    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
-    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
-}
-```
-:::
-
-#### [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) Function {#func.RMSE.Total_kable}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) script on _GitHub_.
-:::
-
-Prints the _Resut (RMSEs) Table_.
-
-::: {.noteblock data-latex=""}
-It is assumed that the table has the following four columns:
-
-  1. *Method*;
-  2. *RMSE*;
-  3. *Diff*;
-  4. *Comment*;
-
-:::
-
-::: { #func.RMSE.Total_kableusage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSE.Total_kable <- function(RMSEs,
-                       col1width = 15,
-                       col2width = 7,
-                       col3width = 5,
-                       col4width = 25)
-```
-:::
-
-::: { #func.RMSE.Total_kable.args .sidebar }
-##### Arguments
-\
-
-::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
-
-:::
-
-::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col1width:*** Width of the first column;
-
-:::
-
-::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col2width:*** Width of the second column;
-
-:::
-
-::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col3width:*** Width of the third column;
-
-:::
-
-::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col4width:*** Width of the fourth column;
-
-:::
-
-::: { #func.RMSE.Total_kablecode .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
-```{r eval=FALSE}
-RMSE.Total_kable <- function(RMSEs,
-                       col1width = 15,
-                       col2width = 7,
-                       col3width = 5, 
-                       col4width = 25){
-  RMSEs |> 
-    RMSE_kable(col1width,
-               col2width,
-               col3width) |>
-    column_spec(column = 4, 
-                width = RSME.tibble.col_width(col4width)) 
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Under the hood, the function calls internally the [RMSE_kable](#func.RMSE_kable) function described above.
-:::
-:::
-
-### Regularization Functions {#appndx_a.CHF.regularization}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) Function {#func.mean_reg}
-\
-
-A general function for computing the arithmetic mean given a _regularization parameter_ $\lambda$. We will call it the _penaized mean_.
-
-::: { #func.mean_reg.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-mean_reg(vals, lambda = 0, na.rm = TRUE)
-
-```
-:::
-
-::: { #func.mean_reg.args .sidebar }
-##### Arguments
-\
-
-::: { #func.mean_reg.args.vals .sidebar }
-  - **vals:** values (usually a numeric vector) to calculate the _penalized mean_;
-
-:::
-::: { #func.mean_reg.args.lambda .sidebar }
-  - **lambda:** a _regularization parameter_ $\lambda$ used in the _Regularization techniques_.
-
-:::
-  - **na.rm:** a logical evaluating to TRUE or FALSE indicating whether NA values should be stripped before the computation proceeds.
-
-:::
-
-::: { #func.mean_reg.details .sidebar }
-##### Details
-\
-We call this function internally from the functions that compute the _penalized estimates_  as described in section [23.6 Penalized Least Squares](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook_[@IDS2_23-6].
-
-::: {.noteblock data-latex=""}
-If the [lambda](#func.mean_reg.args.lambda) parameter is `0` (the default), the function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean), calling with the parameter `trim = 0` (the default for the `base::mean` function).
-:::
-:::
-
-::: { #func.mean_reg.code .sidebar }
-##### Source Code
-\
-
-The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function is shown below:
-```{r eval=FALSE}
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L62) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) script on _GitHub_.
-:::
-:::
-
-::: { #func.mean_reg.value .sidebar }
-##### Value
-\
-
-The function calculates the _penalized mean_ of the [vals](#func.mean_reg.args.vals) parameter as follows:
-$$
-\mu(\lambda) = \frac{1}{\lambda + N} \sum_{i=1}^{N} x_i
-$$
-
-When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean as follows:
-$$
-\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
-$$
-
-:::
-
-#### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
-
-##### Signature
-\
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-##### Arguments
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ;
-
-::: { #func.tune.model_param.args.fn_tune.test.param_value .sidebar }
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.;
-
-:::  
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-##### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-##### Value
-\
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-##### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-\newpage
-
-#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
-\
-
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
-
-##### Signature
-\
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  # ...
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-##### **Parameters**
-\
-
-::: { #func.model.tune.param_range.args.loop_starter .sidebar }
-###### ***loop_starter***
-\
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
-$$
-step = \frac{end - start}{dvs}
-$$
-
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
-```{r eval=FALSE}
-seq(start, end, step)
-```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
-:::
-
-::: { #func.model.tune.param_range.args.tune_dir_path .sidebar }
-###### ***tune_dir_path***
-\
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
-:::
-
-::: { #func.model.tune.param_range.args.cache_file_base_name .sidebar }
-###### ***cache_file_base_name***
-\
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
-:::
-
-::: { #func.model.tune.param_range.args.fn_tune.test.param_value .sidebar }
-###### ***fn_tune.test.param_value***
-\
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.args.max.identical.min_RMSE.count .sidebar }
-###### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
-When it is reached, the algorithm considers the task execution to be complete.
-:::
-
-::: { #func.model.tune.param_range.args.endpoint.min_diff .sidebar }
-###### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
-:::
-
-::: { #func.model.tune.param_range.args.break.if_min .sidebar }
-###### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-:::
-
-::: { #func.model.tune.param_range.args.steps.beyond_min .sidebar }
-###### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
-
-::: { #func.model.tune.param_range.details .sidebar }
-##### **Details** 
-\
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.args.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) (see the description below) and, using one more helper function [get_best_param.result](#func.get_best_param.result)  (see the description below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.args.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-##### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-##### Source Code
-\
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-  interval_divisor <- loop_starter[3]
-
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
-    if (end.idx - start.idx <= 0) {
-      warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
-      break
-    }
-
-    if (best_RMSE == min_RMSE) {
-      warning("Currently computed minimal RMSE equals the previously reached best one: ",
-              best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        break
-      }
-
-    } else if (best_RMSE < min_RMSE) {
-      stop("Current minimal RMSE is greater than previously computed best value: ",
-           best_RMSE, "
-Currently computed minial value is: ", min_RMSE)
-    }
-
-    best_RMSE <- min_RMSE
-    param.best_value <- min_RMSE.prm_val
-
-    param_values.best_result <- 
-      get_best_param.result(tuned.result$parameter.value, 
-                          tuned.result$RMSE)
-  }
-  # End repeat loop
-
-  n <- length(tuned.result$parameter.value)
-  parameter.value <- tuned.result$parameter.value
-  result.RMSE <- tuned.result$RMSE
-
-  if (result.RMSE[1] == best_RMSE) {
-    parameter.value[1] <- prm_val.leftmost
-    result.RMSE[1] <- RMSE.leftmost
-  }
-  if (result.RMSE[n] == best_RMSE) {
-    parameter.value[n+1] <- prm_val.rightmost
-    result.RMSE[n+1] <- RMSE.rightmost
-  }
-
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) Function {#func.get_fine_tune.param.endpoints}
-\
-
-The algorithm finds the values of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-##### Signature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints <- function(preset.result) {
-  # ...
-
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-}
-```
-
-##### Arguments
-\
-
-::: {#func.get_fine_tune.param.endpoints.args.preset.result .sidebar }
-###### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-##### Details
-\
-
-Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) parameter.
-
-##### Value
-\
-A vector containing the element value corresponding to the minimum `RMSE` in a given sequence, along with the values of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-```
-
-##### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) function is provided below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints <- function(preset.result) {
-
-  preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
-
-  i <- preset.result.idx["start"]
-  j <- preset.result.idx["end"]
-  best.idx <- preset.result.idx["best"]
-
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-}
-```
-
-\newpage
-
-#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-##### Signature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-##### Arguments
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.args.preset.result .sidebar }
-###### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-##### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-##### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-##### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-\newpage
-
-#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-##### Signature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-##### Arguments
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-##### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-##### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-##### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```

### 2025-09-29 reports/capstone-movielens.site/work/draft-snippert.Rmd
Capstone Report: `open_logfile` function description added.

--- 2025-09-29 reports/capstone-movielens.site/work/draft-snippert.Rmd
@@
 
-#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/common-helper.functions.R#L6) Function {#func.clamp}
+#### [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) Function {#func.open_logfile}
 \
 
-Clamps the input value passed in [r](#func.clamp.args.r) argument between the values passed in [min](#func.clamp.args.min) and [max](#func.clamp.args.max) arguments.
+A function to initialize the log file.
 
-::: { #func.clamp.Usage .sidebar }
+::: { #func.open_logfile.Usage .sidebar }
 ##### Usage
@@
 ```{r eval=FALSE}
-r_clamped <- clamp(r, min = 0.5, max = 5)
+open_logfile(file_name)
 ```
@@
 
-::: { #func.clamp.args .sidebar }
+::: { #func.open_logfile.args .sidebar }
 ##### Arguments
@@
 
-::: { #func.clamp.args.r .sidebar }
-  - **r:** Value to clamp;
-
-:::
-::: { #func.clamp.args.min .sidebar }
-  - **min:** Minimum allowed value;
-
-:::
-:::
-::: { #func.clamp.args.max .sidebar }
-  - **max:** Maximum allowed value;
+::: { #func.open_logfile.args.r .sidebar }
+  - **file_name:** A name used as a base to generate a unique log file name;
 
@@
 
-::: { #func.clamp.details .sidebar }
+::: { #func.open_logfile.details .sidebar }
 ##### Details
@@
 
-As explained in [Section  23.4 *User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
-For this reason, we need a function described in that section[@IDS2_23-4]:
+This function is a wrapper to [logr::log_open](https://www.rdocumentation.org/packages/logr/versions/1.3.9/topics/log_open) function.
+It also calls internally the following functions to generate a unique file name based on the [file_name] argument and _system time_:
+  - [Sys.time]();
+  - [stringr::str_replace](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace);
+  - [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace)
 
-Therefore, in our project this function is used to clamp the computed movie rating values between 0.5 and 5.
+For more information on the _inner functions_ listed above, see the [R Documentation](https://www.rdocumentation.org/).
 
@@
 
-::: { #func.clamp.value .sidebar }
+::: { #func.open_logfile.value .sidebar }
 ##### Value
@@
 
-The value clamped between [min](#func.clamp.args.min) and [max](#func.clamp.args.max) argument values.
+The path of the log.
 
@@
 
-::: { #func.clamp.code .sidebar }
+::: { #func.open_logfile.code .sidebar }
 ##### Source Code
@@
 
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/common-helper.functions.R#L6) function is shown below:
+The source code of the [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) function is shown below:
 ```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
+library(logr)
+library(stringr)
+
+open_logfile <- function(file_name){
+  log_file_name <- as.character(Sys.time()) |> 
+    str_replace_all(':', '_') |> 
+    str_replace(' ', 'T') |>
+    str_c(file_name)
+
+  log_open(file_name = log_file_name)
+}
 ```
@@
 ::: {.noteblock data-latex=""}
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L6) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) script on _GitHub_.
+The source code of the [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) function is also available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L1) section of the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) script on _GitHub_.
 :::

### 2025-09-29 reports/capstone-movielens.site/05.appendix.Rmd
Capstone Report: fix for `open_logfile` function description added.

@@
 
-::: { #func.open_logfile.args.r .sidebar }
+::: { #func.open_logfile.args.file_name .sidebar }
   - **file_name:** A name used as a base to generate a unique log file name;
@@
 This function is a wrapper to [logr::log_open](https://www.rdocumentation.org/packages/logr/versions/1.3.9/topics/log_open) function.
-It also calls internally the following functions to generate a unique file name based on the [file_name] argument and _system time_:
-  - [Sys.time]();
+It also calls internally the following functions to generate a unique file name based on the [file_name](#func.open_logfile.args.file_name) argument and _system time_:
+
+  - [Sys.time](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/Sys.time);
+
   - [stringr::str_replace](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace);
+
   - [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace)
@@
 ::: {.noteblock data-latex=""}
-The source code of the [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) function is also available in the [Logging Helper functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L1) section of the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) script on _GitHub_.
+The source code of the [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) script on _GitHub_.
 :::

### 2025-10-16 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: print_start_date, put_start_date, print_end_date.

@@
 :::
+
+#### [print_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) Function {#func.print_start_date}
+\
+
+Prints the system date and time at the time the function is called and returns the system's idea of the current date and time.
+
+::: { #func.print_start_date.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+print_start_date()
+```
+:::
+
+::: { #func.print_start_date.details .sidebar }
+##### Details
+\
+
+This function internally calls [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print), [base::date](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/date), and [base::Sys.time](https://www.rdocumentation.org/link/Sys.time?package=base&version=3.6.2) `R` functions.
+
+It first prints the value returned by the `date` function, then returns the object returned by the `Sys.time` function.
+:::
+
+::: { #func.print_start_date.value .sidebar }
+##### Value
+\
+
+Returns an object of class `POSIXct` (see {DateTimeClasses}(https://www.rdocumentation.org/link/DateTimeClasses?package=base&version=3.6.2)).
+
+:::
+
+::: { #func.print_start_date.code .sidebar }
+##### Source Code
+\
+
+The source code of the [print_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) function is shown below:
+```{r eval=FALSE}
+print_start_date <- function(){
+  print(date())
+  Sys.time()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [print_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) script on _GitHub_.
+:::
+:::
+
+#### [put_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) Function {#func.put_start_date}
+\
+
+Prints the system date and time to the currently opened log (using the [open_logfile](#func.open_logfile) function described above) at the time the function is called and returns the system's idea of the current date and time.
+
+::: { #func.put_start_date.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+put_start_date()
+```
+:::
+
+::: { #func.put_start_date.details .sidebar }
+##### Details
+\
+
+This function internally calls [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print), [base::date](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/date), and [base::Sys.time](https://www.rdocumentation.org/link/Sys.time?package=base&version=3.6.2) `R` functions.
+
+It first prints the value returned by the `date` function to the currently opened log, then returns the object returned by the `Sys.time` function.
+:::
+
+::: { #func.put_start_date.value .sidebar }
+##### Value
+\
+
+Returns an object of class `POSIXct` (see {DateTimeClasses}(https://www.rdocumentation.org/link/DateTimeClasses?package=base&version=3.6.2)).
+
+:::
+
+::: { #func.put_start_date.code .sidebar }
+##### Source Code
+\
+
+The source code of the [put_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) function is shown below:
+```{r eval=FALSE}
+put_start_date <- function(){
+  print(date())
+  Sys.time()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [put_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) script on _GitHub_.
+:::
+:::
+
+#### [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) Function {#func.print_end_date}
+\
+
+Prints the system date and time at the time the function is called, and then the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
+
+::: { #func.print_end_date.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+print_end_date(start)
+```
+:::
+
+::: { #func.print_end_date.args .sidebar }
+##### Arguments
+\
+
+::: { #func.print_end_date.args.start .sidebar }
+  - **start:** An object of class `POSIXct` representing the value of the moment from which time is measured.
+
+:::
+:::
+
+::: { #func.print_end_date.details .sidebar }
+##### Details
+\
+
+This function internally calls [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print), [base::date](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/date), and [base::Sys.time](https://www.rdocumentation.org/link/Sys.time?package=base&version=3.6.2) `R` functions.
+
+It first prints the value returned by the `date` function, then returns an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
+:::
+
+::: { #func.print_end_date.value .sidebar }
+##### Value
+\
+
+Returns an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
+
+:::
+
+::: { #func.print_end_date.code .sidebar }
+##### Source Code
+\
+
+The source code of the [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is shown below:
+```{r eval=FALSE}
+print_end_date <- function(start){
+  print(date())
+  print(Sys.time() - start)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) script on _GitHub_.
+:::
+:::
+
+# ------------------------------------------------------------------------------
 

### 2025-10-16 reports/capstone-movielens.site/work/func-descr.template.Rmd
Functions described: print_start_date, put_start_date, print_end_date.

@@
 ---
+
+#### [log_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) Function {#func.log_func_tmpl}
+\
+
+::: { #func.log_func_tmpl.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.log_func_tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.log_func_tmpl.args.file_name .sidebar }
+  - **file_name:** A name used as a base to generate a unique log file name;
+
+:::
+:::
+
+::: { #func.log_func_tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.log_func_tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.log_func_tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [log_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [log_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) script on _GitHub_.
+:::
+:::
 

### 2025-10-17 reports/capstone-movielens.site/05.appendix.Rmd
`put_end_date` function described. `print_end_date` function fixed.

@@
 The source code of the [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) script on _GitHub_.
+:::
+:::
+
+#### [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) Function {#func.print_end_date}
+\
+
+Prints the system date and time at the time the function is called, and then the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
+
+::: { #func.print_end_date.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+print_end_date(start)
+```
+:::
+
+::: { #func.print_end_date.args .sidebar }
+##### Arguments
+\
+
+::: { #func.print_end_date.args.start .sidebar }
+  - **start:** An object of class `POSIXct` representing the value of the moment from which time is measured.
+
+:::
+:::
+
+::: { #func.print_end_date.details .sidebar }
+##### Details
+\
+
+This function internally calls [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print), [base::date](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/date), and [base::Sys.time](https://www.rdocumentation.org/link/Sys.time?package=base&version=3.6.2) `R` functions.
+
+It first prints the value returned by the `date` function, then builds an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument, prints the object, and, finally, returns the object to the client code.
+
+:::
+
+::: { #func.print_end_date.value .sidebar }
+##### Value
+\
+
+Returns an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
+
+:::
+
+::: { #func.print_end_date.code .sidebar }
+##### Source Code
+\
+
+The source code of the [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is shown below:
+```{r eval=FALSE}
+print_end_date <- function(start){
+  print(date())
+  print(Sys.time() - start)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) script on _GitHub_.
+:::
+:::
+
+#### [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) Function {#func.put_end_date}
+\
+
+Outputs the system date and time to the currently open log (using the [open_logfile](#func.open_logfile) function described above).
+
+The first value in the output is the system date and time at the time the function is called, and the second value is the time elapsed since the date and time specified by the [start](#func.put_end_date.args.start) argument.
+
+::: { #func.put_end_date.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+put_end_date(start)
+```
+:::
+
+::: { #func.put_end_date.args .sidebar }
+##### Arguments
+\
+
+::: { #func.put_end_date.args.start .sidebar }
+  - **start:** An object of class `POSIXct` representing the value of the moment from which time is measured.
+
+:::
+:::
+
+::: { #func.put_end_date.details .sidebar }
+##### Details
+\
+
+This function works similarly to the [print_end_date](#func.print_end_date) function described above, but unlike the latter, it outputs the information to the currently open log file.
+
+:::
+
+::: { #func.put_end_date.value .sidebar }
+##### Value
+\
+
+Returns an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.put_end_date.args.start) argument.
+
+:::
+
+::: { #func.put_end_date.code .sidebar }
+##### Source Code
+\
+
+The source code of the [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is shown below:
+```{r eval=FALSE}
+put_end_date <- function(start){
+  put(date())
+  put(Sys.time() - start)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) script on _GitHub_.
 :::

### 2025-10-19 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: `print_log`, `put_log`.

@@
 
-Returns an object of class `POSIXct` (see {DateTimeClasses}(https://www.rdocumentation.org/link/DateTimeClasses?package=base&version=3.6.2)).
+An object of class `POSIXct` (see [DateTimeClasses](https://www.rdocumentation.org/link/DateTimeClasses?package=base&version=3.6.2)).
 
@@
 
-Prints the system date and time to the currently opened log (using the [open_logfile](#func.open_logfile) function described above) at the time the function is called and returns the system's idea of the current date and time.
+Outputs the system date and time to the currently opened log (using the [open_logfile](#func.open_logfile) function described above) at the time the function is called and returns the system's idea of the current date and time.
 
@@
 
-It first prints the value returned by the `date` function to the currently opened log, then returns the object returned by the `Sys.time` function.
+It first outputs the value returned by the `date` function to the currently opened log, then returns the object returned by the `Sys.time` function.
 :::
@@
 put_start_date <- function(){
-  print(date())
+  put(date())
   Sys.time()
@@
 
-It first prints the value returned by the `date` function, then returns an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
+It first prints the value returned by the `date` function, then builds an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument, prints the object, and, finally, returns the object to the client code.
+
 :::
@@
 
-Returns an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
+An object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
 
@@
 
-#### [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) Function {#func.print_end_date}
-\
-
-Prints the system date and time at the time the function is called, and then the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
-
-::: { #func.print_end_date.Usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-print_end_date(start)
-```
-:::
-
-::: { #func.print_end_date.args .sidebar }
-##### Arguments
-\
-
-::: { #func.print_end_date.args.start .sidebar }
-  - **start:** An object of class `POSIXct` representing the value of the moment from which time is measured.
-
-:::
-:::
-
-::: { #func.print_end_date.details .sidebar }
-##### Details
-\
-
-This function internally calls [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print), [base::date](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/date), and [base::Sys.time](https://www.rdocumentation.org/link/Sys.time?package=base&version=3.6.2) `R` functions.
-
-It first prints the value returned by the `date` function, then builds an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument, prints the object, and, finally, returns the object to the client code.
-
-:::
-
-::: { #func.print_end_date.value .sidebar }
-##### Value
-\
-
-Returns an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
-
-:::
-
-::: { #func.print_end_date.code .sidebar }
-##### Source Code
-\
-
-The source code of the [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is shown below:
-```{r eval=FALSE}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) script on _GitHub_.
-:::
-:::
-
 #### [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) Function {#func.put_end_date}
@@
 
-Returns an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.put_end_date.args.start) argument.
+An object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.put_end_date.args.start) argument.
 
@@
 
+#### [print_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L28) Function {#func.print_log}
+\
+
+Prints a multiline string specified by the [msg](#func.print_log.args.msg) argument.
+
+::: { #func.print_log.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+print_log(msg)
+```
+:::
+
+::: { #func.print_log.args .sidebar }
+##### Arguments
+\
+
+::: { #func.print_log.args.msg .sidebar }
+  - **msg:** A string to print (can be multiline).
+
+:::
+:::
+
+::: { #func.print_log.details .sidebar }
+##### Details
+\
+
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` functions to print the (possibly multiline) string specified by the [msg](#func.print_log.args.msg) argument.
+
+:::
+
+::: { #func.print_log.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html)
+
+:::
+
+::: { #func.print_log.code .sidebar }
+##### Source Code
+\
+
+The source code of the [print_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L28) function is shown below:
+```{r eval=FALSE}
+print_log <- function(msg){
+  print(str_glue(msg))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [print_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L28) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L28) script on _GitHub_.
+:::
+:::
+
+#### [put_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L31) Function {#func.put_log}
+\
+
+Outputs a multiline string specified by the [msg](#func.put_log.args.msg) argument to the currently opened log (using the [open_logfile](#func.open_logfile) function described above).
+
+::: { #func.put_log.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+put_log(msg)
+```
+:::
+
+::: { #func.put_log.args .sidebar }
+##### Arguments
+\
+
+::: { #func.put_log.args.msg .sidebar }
+  - **msg:** A string to print (can be multiline).
+
+:::
+:::
+
+::: { #func.put_log.details .sidebar }
+##### Details
+\
+
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` functions to output the (possibly multiline) string specified by the [msg](#func.put_log.args.msg) argument.
+
+The function works similarly to the [print_log](#func.print_log) function described above, but unlike the latter, it outputs the information to the currently open log file.
+
+:::
+
+::: { #func.put_log.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html)
+
+:::
+
+::: { #func.put_log.code .sidebar }
+##### Source Code
+\
+
+The source code of the [put_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L31) function is shown below:
+```{r eval=FALSE}
+put_log <- function(msg){
+  put(str_glue(msg))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [put_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L31) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L31) script on _GitHub_.
+:::
+:::
+
 # ------------------------------------------------------------------------------
@@
 
-#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) Function {#func.clamp}
+#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) Function {#func.clamp}
 \
@@
 
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is shown below:
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) script on _GitHub_.
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L504) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) script on _GitHub_.
 :::

### 2025-10-19 r/src/0ld/capstone-movielens.draft2.R

@@ -1,1009 +1,0 @@
-## Setup -----------------------------------------------------------------------
-#> Reference: Some ideas and code snippers were used from the following GitHub repository:
-#> https://github.com/AzKurban-edX-DS/harvardx-movielens
-
-
-if(!require(tidyverse))
-  install.packages("tidyverse", repos = "http://cran.us.r-project.org")
-if(!require(caret))
-  install.packages("caret", repos = "http://cran.us.r-project.org")
-if(!require(data.table))
-  install.packages("data.table", repos = "http://cran.us.r-project.org")
-
-if(!require(gtools)) 
-  install.packages("gtools")
-if(!require(pak)) 
-  install.packages("pak")
-if(!require("pacman")) 
-  install.packages("pacman")
-
-
-# Loading the required libraries
-library(dslabs)
-library(tidyverse)
-
-library(caret)
-library(cowplot)
-library(data.table)
-library(dplyr)
-library(ggplot2)
-library(ggthemes)
-library(lubridate)
-library(Metrics)
-library(recosystem)
-library(scales)
-library(stringr)
-library(tibble)
-library(tidyr)
-
-
-library(rafalib)
-library(gtools)
-library(pak)
-library(pacman)
-
-p_load(conflicted, latex2exp, kableExtra)
-
-# For functions with identical names in different packages, ensure the
-# right one is chosen:
-conflict_prefer("first", "dplyr")
-conflict_prefer("count", "dplyr")
-conflict_prefer("select", "dplyr")
-conflict_prefer("filter", "dplyr")
-conflict_prefer("kable", "kableExtra")
-
-## Datasets ===================================================================
-
-# To start with we have to generate two datasets derived from the MovieLens one:
-#   
-# *`edx`: we use it to develop and train our algorithms;
-# * `final_holdout_test`:  according to the course requirements, 
-#    we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
-# 
-# For this purpose the following package has been developed by the author of this 
-# script: `edx.capstone.movielens.data`. The source code of the package is available 
-# on `GitHub`(https://github.com/AzKurban-edX-DS/edx.capstone.movielens.data).
-# 
-# Let's install the development version of this package from the `GitHub` repository 
-# and attach the correspondent library to the global environment:
-
[…]

### 2025-10-19 r/src/0ld/capstone-movielens.draft3.R

@@ -1,3701 +1,0 @@
-## Setup -----------------------------------------------------------------------
-#> Reference: Some ideas and code snippers were used from the following GitHub repository:
-#> https://github.com/AzKurban-edX-DS/harvardx-movielens
-
-
-if(!require(tidyverse))
-  install.packages("tidyverse", repos = "http://cran.us.r-project.org")
-
-#> `stringr` library is already included to the `tidyverse` package,
-#> there's no need to install `stringr`
-# if(!require(stringr))
-#   install.packages("stringr")
-
-if(!require(caret))
-  install.packages("caret", repos = "http://cran.us.r-project.org")
-if(!require(data.table))
-  install.packages("data.table", repos = "http://cran.us.r-project.org")
-if(!require(gridExtra))
-  install.packages("gridExtra")
-if(!require("logr")) 
-  install.packages("logr")
-
-if(!require(gtools)) 
-  install.packages("gtools")
-if(!require(pak)) 
-  install.packages("pak")
-if(!require("pacman")) 
-  install.packages("pacman")
-
-# Loading the required libraries
-library(dslabs)
-library(tidyverse)
-
-library(caret)
-library(cowplot)
-library(data.table)
-library(dplyr)
-library(ggplot2)
-library(ggthemes)
-library(lubridate)
-library(Metrics)
-library(recosystem)
-library(scales)
-library(stringr)
-library(tibble)
-library(tidyr)
-library(gridExtra)
-library(logr)
-
-library(rafalib)
-library(gtools)
-library(pak)
-library(pacman)
-
-p_load(conflicted, latex2exp, kableExtra)
-
-### Resolve conflicts ----------------------------------------------------------
-
-# For functions with identical names in different packages, ensure the
-# right one is chosen:
-conflict_prefer("first", "dplyr", quiet = TRUE)
-conflict_prefer("count", "dplyr", quiet = TRUE)
-conflict_prefer("select", "dplyr", quiet = TRUE)
-conflict_prefer("group_by", "dplyr", quiet = TRUE)
-conflict_prefer("ungroup", "dplyr", quiet = TRUE)
-conflict_prefer("summarise", "dplyr", quiet = TRUE)
-conflict_prefer("summarize", "dplyr", quiet = TRUE)
-conflict_prefer("distinct", "dplyr", quiet = TRUE)
-conflict_prefer("top_n", "dplyr", quiet = TRUE)
-conflict_prefer("arrange", "dplyr", quiet = TRUE)
[…]

### 2025-10-19 r/src/0ld/capstone-movielens.draft6.R

@@ -1,2556 +1,0 @@
-## Setup -----------------------------------------------------------------------
-#> Reference: Some ideas and code snippers were used from the following GitHub repository:
-#> https://github.com/AzKurban-edX-DS/harvardx-movielens
-
-
-if(!require(tidyverse))
-  install.packages("tidyverse", repos = "http://cran.us.r-project.org")
-
-#> `stringr` library is already included to the `tidyverse` package,
-#> there's no need to install `stringr`
-# if(!require(stringr))
-#   install.packages("stringr")
-
-if(!require(caret))
-  install.packages("caret", repos = "http://cran.us.r-project.org")
-if(!require(data.table))
-  install.packages("data.table", repos = "http://cran.us.r-project.org")
-if(!require(gridExtra))
-  install.packages("gridExtra")
-if(!require("logr")) 
-  install.packages("logr")
-
-if(!require(gtools)) 
-  install.packages("gtools")
-if(!require(pak)) 
-  install.packages("pak")
-if(!require("pacman")) 
-  install.packages("pacman")
-
-# Loading the required libraries
-library(dslabs)
-library(tidyverse)
-
-library(caret)
-library(cowplot)
-library(data.table)
-library(dplyr)
-library(ggplot2)
-library(ggthemes)
-library(lubridate)
-library(Metrics)
-library(recosystem)
-library(scales)
-library(stringr)
-library(tibble)
-library(tidyr)
-library(gridExtra)
-library(logr)
-
-library(rafalib)
-library(gtools)
-library(pak)
-library(pacman)
-
-p_load(conflicted, latex2exp, kableExtra)
-
-### Resolve conflicts ----------------------------------------------------------
-
-# For functions with identical names in different packages, ensure the
-# right one is chosen:
-conflict_prefer("first", "dplyr", quiet = TRUE)
-conflict_prefer("count", "dplyr", quiet = TRUE)
-conflict_prefer("select", "dplyr", quiet = TRUE)
-conflict_prefer("group_by", "dplyr", quiet = TRUE)
-conflict_prefer("ungroup", "dplyr", quiet = TRUE)
-conflict_prefer("summarise", "dplyr", quiet = TRUE)
-conflict_prefer("summarize", "dplyr", quiet = TRUE)
-conflict_prefer("distinct", "dplyr", quiet = TRUE)
-conflict_prefer("top_n", "dplyr", quiet = TRUE)
[…]

### 2025-10-19 r/src/0ld/user-movie-effect-regularization.R

@@ -1,217 +1,0 @@
-# User+Movie Effect Regularization
-## Global Variables -------------------------------------------------------------
-ume_regularization_path <- file.path(regularization_data_path, 
-                                      "user-movie-effect")
-
-## Open log -------------------------------------------------------------------
-open_logfile(".reg-um-effect.loop_0_10_d10")
-
-## Process lamdas in loop starting from `ume_reg_lambdas = seq(0, 10, 10/10` -------
-loop_starter <- c(0, 4, 2)
-ume_seq_start <- loop_starter[1]
-ume_seq_end <- loop_starter[2]
-ume_range_divider <- loop_starter[3] 
-ume_max_range_divider <- 128
-
-ume_best_RMSE <- Inf
-ume_best_lambda <- 0
-
-ume_reg_lambdas_best_results <- c(best_lambda = ume_best_lambda, 
-                                 best_RMSE = ume_best_RMSE)
-
-repeat{
-  ume_seq_increment <- (ume_seq_end - ume_seq_start)/ume_range_divider 
-  
-  if (ume_seq_increment < 0.0000000000001) {
-    warning("Main loop:
-lambda increment is too small.")
-    
-    put_log2("Main loop:
-Final best RMSE for `lambda = %1`: %2",
-             ume_reg_lambdas_best_results["best_lambda"],
-             ume_reg_lambdas_best_results["best_RMSE"])
-    
-    put(ume_reg_lambdas_best_results)
-    # best_lambda   best_RMSE 
-    # -75.0000000   0.8578522  
-    # browser()
-    break
-  }
-  
-  test_lambdas <- seq(ume_seq_start, ume_seq_end, ume_seq_increment)
-
-  file_name_tmp <- "umgy_reg-loop_" |>
-    str_c(as.character(loop_starter[1])) |>
-    str_c("_") |>
-    str_c(as.character(loop_starter[3])) |>
-    str_c("_") |>
-    str_c(as.character(ume_range_divider)) |>
-    str_c(".") |>
-    str_c(as.character(ume_seq_start)) |>
-    str_c("-") |>
-    str_c(as.character(ume_seq_end)) |>
-    str_c(".RData")
-  
-  file_path_tmp <- file.path(ume_regularization_path, file_name_tmp)
-  
-  put_log1("Main loop:
-File path generated: %1", file_path_tmp)
-  
-  if (file.exists(file_path_tmp)) {
-    put_log1("Main loop:
[…]

### 2025-10-19 reports/capstone-movielens.site/02-0.methods.Rmd
Capstone Report: `open_logfile` function description added.

@@
 # Logging Helper functions -----------------------------------------------------
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-
 msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
@@
 ```
-
-::: {.noteblock data-latex=""}
-The full source code of these functions is available in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R) script on _GitHub_.
-:::
 

### 2025-10-19 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: get_log1, print_log1, put_log1.

@@
 The source code of the [put_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L31) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L31) script on _GitHub_.
+:::
+:::
+
+#### [get_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L35) Function {#func.get_log1}
+\
+
+Builds a string from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1).
+
+::: { #func.get_log1.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+get_log1(msg_template, arg1)
+```
+:::
+
+::: { #func.get_log1.args .sidebar }
+##### Arguments
+\
+
+::: { #func.get_log1.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.get_log1.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log1.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.get_log1.details .sidebar }
+##### Details
+\
+
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log1.args.msg_template) and [arg1](#func.get_log1.args.arg1)  arguments, respectively.
+
+:::
+
+::: { #func.get_log1.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
+
+:::
+
+::: { #func.get_log1.code .sidebar }
+##### Source Code
+\
+
+The source code of the [get_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L35) function is shown below:
+```{r eval=FALSE}
+get_log1 <- function(msg_template, arg1) {
+  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L35) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L35) script on _GitHub_.
+:::
+:::
+
+#### [print_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L38) Function {#func.print_log1}
+\
+
+Prints a string formed from the template passed in the [msg_template](#func.print_log1.args.msg_template) argument using the format value specified by the [arg1](#func.print_log1.args.arg1).
+
+::: { #func.print_log1.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+print_log1(msg_template, arg1)
+```
+:::
+
+::: { #func.print_log1.args .sidebar }
+##### Arguments
+\
+
+::: { #func.print_log1.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.print_log1.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log1.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.print_log1.details .sidebar }
+##### Details
+\
+
+This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log1](#func.get_log1) function described above.
+
+:::
+
+::: { #func.print_log1.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log1](#func.get_log1) function described above.
+
+:::
+
+::: { #func.print_log1.code .sidebar }
+##### Source Code
+\
+
+The source code of the [print_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L38) function is shown below:
+```{r eval=FALSE}
+print_log1 <- function(msg_template, arg1){
+  print(get_log1(msg_template, arg1))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [print_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L38) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L38) script on _GitHub_.
+:::
+:::
+
+#### [put_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) Function {#func.put_log1}
+\
+
+Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1).
+
+::: { #func.put_log1.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+put_log1(msg_template, arg1)
+```
+:::
+
+::: { #func.put_log1.args .sidebar }
+##### Arguments
+\
+
+::: { #func.put_log1.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.put_log1.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log1.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.put_log1.details .sidebar }
+##### Details
+\
+
+This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log1](#func.get_log1) function described above.
+
+The function works similarly to the [print_log1](#func.print_log1) function described above, but unlike the latter, it outputs the information to the currently open log file.
+
+:::
+
+::: { #func.put_log1.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log1](#func.get_log1) function described above.
+:::
+
+::: { #func.put_log1.code .sidebar }
+##### Source Code
+\
+
+The source code of the [put_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) function is shown below:
+```{r eval=FALSE}
+put_log1 <- function(msg_template, arg1){
+  put(get_log1(msg_template, arg1))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [put_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) script on _GitHub_.
 :::

### 2025-10-20 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the following functions: get_log1, print_log1, put_log1.

@@
 
-This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log1](#func.get_log1) function described above.
+This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [print_log1](#func.print_log1) function described above.
 
@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log1](#func.get_log1) function described above.
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [print_log1](#func.print_log1) function described above.
 
@@
 print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
+  print(print_log1(msg_template, arg1))
 }
@@
 
-Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1).
+Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log1.args.msg_template) argument using the format value specified by the [arg1](#func.put_log1.args.arg1).
 
@@
 ::: { #func.put_log1.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log1.args.msg_template) argument.
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log1.args.msg_template) argument.
 
@@
 
-This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log1](#func.get_log1) function described above.
+This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [put_log1](#func.put_log1) function described above.
 
@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log1](#func.get_log1) function described above.
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [put_log1](#func.put_log1) function described above.
 :::
@@
 put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
+  put(put_log1(msg_template, arg1))
 }

### 2025-10-20 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the following functions: print_log1, put_log1

--- 2025-10-19 reports/capstone-movielens.site/05.appendix.Rmd
@@
 
+\newpage
+
 #### [print_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L38) Function {#func.print_log1}
@@
 
+\newpage
+
 #### [put_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) Function {#func.put_log1}

### 2025-10-21 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: get_log2, print_log2, put_log2, get_log3, print_log3, put_log3.

@@
 The source code of the [put_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [get_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) Function {#func.get_log2}
+\
+
+Builds a string from the template passed in the [msg_template](#func.get_log2.args.msg_template) argument using the format values specified by the [arg1](#func.get_log2.args.arg1) and [arg2](#func.get_log2.args.arg2) arguments.
+
+::: { #func.get_log2.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+get_log2(msg_template, arg1, arg2)
+```
+:::
+
+::: { #func.get_log2.args .sidebar }
+##### Arguments
+\
+
+::: { #func.get_log2.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.get_log2.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log2.args.msg_template) argument.
+
+:::
+
+::: { #func.get_log2.args.arg2 .sidebar }
+  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.get_log2.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.get_log2.details .sidebar }
+##### Details
+\
+
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log2.args.msg_template), [arg1](#func.get_log2.args.arg1), and [arg2](#func.get_log2.args.arg2)  arguments, respectively.
+
+:::
+
+::: { #func.get_log2.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
+
+:::
+
+::: { #func.get_log2.code .sidebar }
+##### Source Code
+\
+
+The source code of the [get_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) function is shown below:
+```{r eval=FALSE}
+get_log2 <- function(msg_template, arg1, arg2) {
+  msg_template |> 
+    str_replace_all("%1", as.character(arg1)) |>
+    str_replace_all("%2", as.character(arg2)) |>
+    str_glue()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [print_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) Function {#func.print_log2}
+\
+
+Prints a string formed from the template passed in the [msg_template](#func.print_log2.args.msg_template) argument using the format values specified by the [arg1](#func.print_log2.args.arg1) and [arg2](#func.print_log2.args.arg2) arguments.
+
+::: { #func.print_log2.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+print_log2(msg_template, arg1, arg2)
+```
+:::
+
+::: { #func.print_log2.args .sidebar }
+##### Arguments
+\
+
+::: { #func.print_log2.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.print_log2.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log2.args.msg_template) argument.
+
+:::
+
+::: { #func.print_log2.args.arg2 .sidebar }
+  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.print_log2.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.print_log2.details .sidebar }
+##### Details
+\
+
+This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log2](#func.get_log2) function described above.
+
+:::
+
+::: { #func.print_log2.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log2](#func.get_log2) function described above.
+
+:::
+
+::: { #func.print_log2.code .sidebar }
+##### Source Code
+\
+
+The source code of the [print_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) function is shown below:
+```{r eval=FALSE}
+print_log2 <- function(msg_template, arg1, arg2){
+  print(get_log2(msg_template, arg1, arg2))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [print_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [put_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) Function {#func.put_log2}
+\
+
+Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log2.args.msg_template) argument using the format values specified by the [arg1](#func.put_log2.args.arg1) and [arg2](#func.put_log2.args.arg2) arguments.
+
+::: { #func.put_log2.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+put_log2(msg_template, arg1, arg2)
+```
+:::
+
+::: { #func.put_log2.args .sidebar }
+##### Arguments
+\
+
+::: { #func.put_log2.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.put_log2.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log2.args.msg_template) argument.
+
+:::
+
+::: { #func.put_log2.args.arg2 .sidebar }
+  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.put_log2.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.put_log2.details .sidebar }
+##### Details
+\
+
+This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log2](#func.get_log2) function described above.
+
+The function works similarly to the [print_log2](#func.print_log2) function described above, but unlike the latter, it outputs the information to the currently open log file.
+
+:::
+
+::: { #func.put_log2.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log2](#func.get_log2) function described above.
+:::
+
+::: { #func.put_log2.code .sidebar }
+##### Source Code
+\
+
+The source code of the [put_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) function is shown below:
+```{r eval=FALSE}
+put_log2 <- function(msg_template, arg1, arg2){
+  put(get_log2(msg_template, arg1, arg2))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [put_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#--------------------------------------
+
+#### [get_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) Function {#func.get_log3}
+\
+
+Builds a string from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument using the format values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3) arguments.
+
+::: { #func.get_log3.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+get_log3(msg_template, arg1, arg2, arg3)
+```
+:::
+
+::: { #func.get_log3.args .sidebar }
+##### Arguments
+\
+
+::: { #func.get_log3.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.get_log3.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.
+
+:::
+
+::: { #func.get_log3.args.arg2 .sidebar }
+  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.
+
+:::
+
+::: { #func.get_log3.args.arg3 .sidebar }
+  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.get_log3.details .sidebar }
+##### Details
+\
+
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log3.args.msg_template), [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3)  arguments, respectively.
+
+:::
+
+::: { #func.get_log3.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
+
+:::
+
+::: { #func.get_log3.code .sidebar }
+##### Source Code
+\
+
+The source code of the [get_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) function is shown below:
+```{r eval=FALSE}
+get_log3 <- function(msg_template, arg1, arg2, arg3) {
+  msg_template |> 
+    str_replace_all("%1", as.character(arg1)) |>
+    str_replace_all("%2", as.character(arg2)) |>
+    str_glue()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [print_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) Function {#func.print_log3}
+\
+
+Prints a string formed from the template passed in the [msg_template](#func.print_log3.args.msg_template) argument using the format values specified by the [arg1](#func.print_log3.args.arg1), [arg2](#func.print_log3.args.arg2), and [arg3](#func.print_log3.args.arg3) arguments.
+
+::: { #func.print_log3.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+print_log3(msg_template, arg1, arg2, arg3)
+```
+:::
+
+::: { #func.print_log3.args .sidebar }
+##### Arguments
+\
+
+::: { #func.print_log3.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.print_log3.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.
+
+:::
+
+::: { #func.print_log3.args.arg2 .sidebar }
+  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.
+
+:::
+
+::: { #func.print_log3.args.arg3 .sidebar }
+  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.print_log3.details .sidebar }
+##### Details
+\
+
+This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log3](#func.get_log3) function described above.
+
+:::
+
+::: { #func.print_log3.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log3](#func.get_log3) function described above.
+
+:::
+
+::: { #func.print_log3.code .sidebar }
+##### Source Code
+\
+
+The source code of the [print_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) function is shown below:
+```{r eval=FALSE}
+print_log3 <- function(msg_template, arg1, arg2, arg3){
+  print(get_log3(msg_template, arg1, arg2, arg3))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [print_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [put_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) Function {#func.put_log3}
+\
+
+Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log3.args.msg_template) argument using the format values specified by the [arg1](#func.put_log3.args.arg1), [arg2](#func.put_log3.args.arg2), and [arg3](#func.put_log3.args.arg3) arguments.
+
+::: { #func.put_log3.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+put_log3(msg_template, arg1, arg2, arg3)
+```
+:::
+
+::: { #func.put_log3.args .sidebar }
+##### Arguments
+\
+
+::: { #func.put_log3.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.put_log3.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.
+
+:::
+
+::: { #func.put_log3.args.arg2 .sidebar }
+  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.
+
+:::
+
+::: { #func.get_log3.args.arg3 .sidebar }
+  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.put_log3.details .sidebar }
+##### Details
+\
+
+This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log3](#func.get_log3) function described above.
+
+The function works similarly to the [print_log3](#func.print_log3) function described above, but unlike the latter, it outputs the information to the currently open log file.
+
+:::
+
+::: { #func.put_log3.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log3](#func.get_log3) function described above.
+:::
+
+::: { #func.put_log3.code .sidebar }
+##### Source Code
+\
+
+The source code of the [put_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) function is shown below:
+```{r eval=FALSE}
+put_log3 <- function(msg_template, arg1, arg2, arg3){
+  put(get_log3(msg_template, arg1, arg2, arg3))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [put_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) script on _GitHub_.
 :::

### 2025-10-22 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: get_log4, print_log4, put_log4.

@@
 
-#--------------------------------------
-
 #### [get_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) Function {#func.get_log3}
@@
 The source code of the [put_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#--------------------------------------
+
+#### [get_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L72) Function {#func.get_log4}
+\
+
+Builds a string from the template passed in the [msg_template](#func.get_log4.args.msg_template) argument using the format values specified by the [arg1](#func.get_log4.args.arg1), [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3) arguments, and [arg4](#func.get_log4.args.arg4) arguments.
+
+::: { #func.get_log4.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+get_log4(msg_template, arg1, arg2, arg3, arg4)
+```
+:::
+
+::: { #func.get_log4.args .sidebar }
+##### Arguments
+\
+
+::: { #func.get_log4.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.get_log4.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log4.args.msg_template) argument.
+
+:::
+
+::: { #func.get_log4.args.arg2 .sidebar }
+  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.get_log4.args.msg_template) argument.
+
+:::
+
+::: { #func.get_log4.args.arg3 .sidebar }
+  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.get_log4.args.msg_template) argument.
+
+:::
+
+::: { #func.get_log4.args.arg4 .sidebar }
+  - **arg4:** The value to replace the format elements represented by the substring `%4` in the message template specified by the [msg_template](#func.get_log4.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.get_log4.details .sidebar }
+##### Details
+\
+
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log4.args.msg_template), [arg1](#func.get_log4.args.arg1), [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3), and [arg4](#func.get_log4.args.arg4) arguments, respectively.
+
+:::
+
+::: { #func.get_log4.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
+
+:::
+
+::: { #func.get_log4.code .sidebar }
+##### Source Code
+\
+
+The source code of the [get_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L72) function is shown below:
+```{r eval=FALSE}
+get_log4 <- function(msg_template, arg1, arg2, arg3, arg4) {
+  msg_template |> 
+    str_replace_all("%1", as.character(arg1)) |>
+    str_replace_all("%2", as.character(arg2)) |>
+    str_replace_all("%3", as.character(arg2)) |>
+    str_replace_all("%4", as.character(arg2)) |>
+    str_glue()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L72) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L72) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [print_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L80) Function {#func.print_log4}
+\
+
+Prints a string formed from the template passed in the [msg_template](#func.print_log4.args.msg_template) argument using the format values specified by the [arg1](#func.print_log4.args.arg1), [arg2](#func.print_log4.args.arg2), [arg3](#func.print_log4.args.arg3), and [arg4](#func.print_log4.args.arg4) arguments.
+
+::: { #func.print_log4.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+print_log4(msg_template, arg1, arg2, arg3, arg4)
+```
+:::
+
+::: { #func.print_log4.args .sidebar }
+##### Arguments
+\
+
+::: { #func.print_log4.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.print_log4.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log4.args.msg_template) argument.
+
+:::
+
+::: { #func.print_log4.args.arg2 .sidebar }
+  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.print_log4.args.msg_template) argument.
+
+:::
+
+::: { #func.print_log4.args.arg3 .sidebar }
+  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.print_log4.args.msg_template) argument.
+
+:::
+
+::: { #func.print_log4.args.arg4 .sidebar }
+  - **arg4:** The value to replace the format elements represented by the substring `%4` in the message template specified by the [msg_template](#func.print_log4.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.print_log4.details .sidebar }
+##### Details
+\
+
+This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log4](#func.get_log4) function described above.
+
+:::
+
+::: { #func.print_log4.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log4](#func.get_log4) function described above.
+
+:::
+
+::: { #func.print_log4.code .sidebar }
+##### Source Code
+\
+
+The source code of the [print_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L80) function is shown below:
+```{r eval=FALSE}
+print_log4 <- function(msg_template, arg1, arg2, arg3, arg4){
+  print(get_log4(msg_template, arg1, arg2, arg3, arg4))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [print_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L80) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L80) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [put_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L83) Function {#func.put_log4}
+\
+
+Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log4.args.msg_template) argument using the format values specified by the [arg1](#func.put_log4.args.arg1), [arg2](#func.put_log4.args.arg2), [arg3](#func.put_log4.args.arg3), and [arg4](#func.put_log4.args.arg4) arguments.
+
+::: { #func.put_log4.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+put_log4(msg_template, arg1, arg2, arg3, arg4)
+```
+:::
+
+::: { #func.put_log4.args .sidebar }
+##### Arguments
+\
+
+::: { #func.put_log4.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+
+:::
+
+::: { #func.put_log4.args.arg1 .sidebar }
+  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log4.args.msg_template) argument.
+
+:::
+
+::: { #func.put_log4.args.arg2 .sidebar }
+  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.put_log4.args.msg_template) argument.
+
+:::
+
+::: { #func.get_log4.args.arg3 .sidebar }
+  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.put_log4.args.msg_template) argument.
+
+:::
+
+::: { #func.get_log4.args.arg4 .sidebar }
+  - **arg4:** The value to replace the format elements represented by the substring `%4` in the message template specified by the [msg_template](#func.put_log4.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.put_log4.details .sidebar }
+##### Details
+\
+
+This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log4](#func.get_log4) function described above.
+
+The function works similarly to the [print_log4](#func.print_log4) function described above, but unlike the latter, it outputs the information to the currently open log file.
+
+:::
+
+::: { #func.put_log4.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log4](#func.get_log4) function described above.
+:::
+
+::: { #func.put_log4.code .sidebar }
+##### Source Code
+\
+
+The source code of the [put_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L83) function is shown below:
+```{r eval=FALSE}
+put_log4 <- function(msg_template, arg1, arg2, arg3, arg4){
+  put(get_log4(msg_template, arg1, arg2, arg3, arg4))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [put_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L83) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L83) script on _GitHub_.
 :::

### 2025-10-22 reports/capstone-movielens.site/05.appendix.Rmd
Logging Functions documented.
Fix for the Logging functions.

@@
 ::: { #func.get_log1.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.
 
@@
 ::: { #func.print_log1.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:**Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.
 
@@
 ::: { #func.put_log1.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.
 
@@
 ::: { #func.get_log2.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one combination of the following substrings: `%1`, `%2`.
 
@@
 ::: { #func.print_log2.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one combination of the following substrings: `%1`, `%2`.
 
@@
 ::: { #func.put_log2.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one combination of the following substrings: `%1`, `%2`.
 
@@
 ::: { #func.get_log3.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.
 
@@
 ::: { #func.print_log3.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.
 
@@
 ::: { #func.put_log3.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.
 
@@
 
-#--------------------------------------
-
 #### [get_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L72) Function {#func.get_log4}
@@
 ::: { #func.get_log4.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`, `%4`.
 
@@
 ::: { #func.print_log4.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`, `%4`.
 
@@
 ::: { #func.put_log4.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`, `%4`.
 
@@
 \newpage
-
-# ------------------------------------------------------------------------------
 

### 2025-10-22 reports/capstone-movielens.site/02-0.methods.Rmd
Functions describing: msg.set_arg, msg.glue (in progress)

@@
     str_glue()
-}
-
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log1(msg_template, arg1, arg2))
-}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log1(msg_template, arg1, arg2))
 }

### 2025-10-22 reports/capstone-movielens.site/05.appendix.Rmd
Functions describing: msg.set_arg, msg.glue (in progress)

@@
 :::
+
+#### [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) Function {#func.msg.set_arg}
+\
+
+Builds a message string from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format element specified by the following arguments:
+  - [arg.name](#func.msg.set_arg.args.arg.name): name of the element; 
+  - [arg](#func.msg.set_arg.args.arg): the element value.
+
+::: { #func.msg.set_arg.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+msg.set_arg(msg_template, arg, arg, arg.name = "%1")
+```
+:::
+
+::: { #func.msg.set_arg.args .sidebar }
+##### Arguments
+\
+
+::: { #func.msg.set_arg.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.
+
+:::
+
+::: { #func.msg.set_arg.args.arg.name .sidebar }
+  - **arg.name:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument.
+:::
+
+::: { #func.msg.set_arg.args.arg .sidebar }
+  - **arg:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.msg.set_arg.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.msg.set_arg.details .sidebar }
+##### Details
+\
+
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.msg.set_arg.args.msg_template) and [arg](#func.msg.set_arg.args.arg)  arguments, respectively.
+
+:::
+
+::: { #func.msg.set_arg.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
+
+:::
+
+::: { #func.msg.set_arg.code .sidebar }
+##### Source Code
+\
+
+The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) function is shown below:
+```{r eval=FALSE}
+msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
+  msg_template |> 
+    str_replace_all(arg.name, as.character(arg))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) function is defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) Function {#func.msg.glue}
+\
+
+Builds a message string from the template passed in the [msg_template](#func.msg.glue.args.msg_template) argument using the format element specified by the following arguments:
+  - [arg.name](#func.msg.glue.args.arg.name): name of the element; 
+  - [arg](#func.msg.glue.args.arg): the element value.
+
+::: { #func.msg.glue.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+msg.glue(msg_template, arg, arg, arg.name = "%1")
+```
+:::
+
+::: { #func.msg.glue.args .sidebar }
+##### Arguments
+\
+
+::: { #func.msg.glue.args.msg_template .sidebar }
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.
+
+:::
+
+::: { #func.msg.glue.args.arg.name .sidebar }
+  - **arg.name:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.glue.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument.
+:::
+
+::: { #func.msg.glue.args.arg .sidebar }
+  - **arg:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.msg.glue.args.msg_template) argument.
+
+:::
+:::
+
+::: { #func.msg.glue.details .sidebar }
+##### Details
+\
+
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.msg.glue.args.msg_template) and [arg](#func.msg.glue.args.arg)  arguments, respectively.
+
+:::
+
+::: { #func.msg.glue.value .sidebar }
+##### Value
+\
+
+A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
+
+:::
+
+::: { #func.msg.glue.code .sidebar }
+##### Source Code
+\
+
+The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) function is shown below:
+```{r eval=FALSE}
+msg.glue <- function(msg_template, arg, arg.name = "%1"){
+  msg_template |>
+    msg.set_arg(arg, arg.name) |>
+    str_glue()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) function is defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) script on _GitHub_.
+:::
+:::
+
+\newpage
 

### 2025-10-23 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the functions' descriptions.

@@
 
-Builds a string from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1).
+Builds a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1) argument.
 
@@
 ::: { #func.get_log1.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of the pattern `%1` to be replaced by the value specified by the [arg1](#func.get_log1.args.arg1) argument.
 
@@
 ::: { #func.get_log1.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log1.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the pattern `%1` in the message template passed in the [msg_template](#func.get_log1.args.msg_template) argument.
 
@@
 
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log1.args.msg_template) and [arg1](#func.get_log1.args.arg1)  arguments, respectively.
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1)  argument.
 
@@
 Builds a message string from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format element specified by the following arguments:
-  - [arg.name](#func.msg.set_arg.args.arg.name): name of the element; 
-  - [arg](#func.msg.set_arg.args.arg): the element value.
+
+  - [arg.name](#func.msg.set_arg.args.arg.name): the pattern to be replaced by the value passed in the [arg] argument;
+
+  - [arg](#func.msg.set_arg.args.arg): the value to replace all occurrences of the pattern passed in the [arg.name](#func.msg.set_arg.args.arg.name) argument.
 
@@
 ::: { #func.msg.set_arg.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of a pattern specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument.
 
@@
 ::: { #func.msg.set_arg.args.arg.name .sidebar }
-  - **arg.name:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument.
+  - **arg.name:** Substring to replace in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.
+
 :::
@@
 ::: { #func.msg.set_arg.args.arg .sidebar }
-  - **arg:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.msg.set_arg.args.msg_template) argument.
-
+  - **arg:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument.
 :::
@@
 
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.msg.set_arg.args.msg_template) and [arg](#func.msg.set_arg.args.arg)  arguments, respectively.
+This function internally calls [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format value specified by the [arg](#func.msg.set_arg.args.arg)  argument to replace all occurances of the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument (`%1` by default).
 
@@
 Builds a message string from the template passed in the [msg_template](#func.msg.glue.args.msg_template) argument using the format element specified by the following arguments:
+
   - [arg.name](#func.msg.glue.args.arg.name): name of the element;
+
   - [arg](#func.msg.glue.args.arg): the element value.
@@
 ::: { #func.msg.glue.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.
+  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring specified by the [arg.name](#func.msg.msg.glue.args.arg.name) argument.
 
@@
 ::: { #func.msg.glue.args.arg.name .sidebar }
-  - **arg.name:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.glue.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument.
+  - **arg.name:** Substring to replace in the message template passed in the [msg_template](#func.msg.msg.glue.args.msg_template) argument with the value specified in the [arg](#func.msg.msg.glue.args.arg) argument.
 :::
@@
 ::: { #func.msg.glue.args.arg .sidebar }
-  - **arg:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.msg.glue.args.msg_template) argument.
+  - **arg:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.glue.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix ;for the functions: get_log1, print_log1.

@@
 
-Builds a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1) argument.
+Creates a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument, using the value specified by the [arg1](#func.get_log1.args.arg1) argument to replace all the occurrences of the pattern `%1` found in the template.
 
@@
 
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1)  argument.
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument, using the value specified by the [arg1](#func.get_log1.args.arg1)  argument to replace all the occurrences of the pattern `%1` found in the template.
 
@@
 
-Prints a string formed from the template passed in the [msg_template](#func.print_log1.args.msg_template) argument using the format value specified by the [arg1](#func.print_log1.args.arg1).
+Prints a log created from the template passed in the [msg_template](#func.print_log1.args.msg_template) argument, using the value specified by the [arg1](#func.print_log1.args.arg1) argument to replace all the occurrences of the pattern `%1` found in the template.
 
@@
 ::: { #func.print_log1.args.msg_template .sidebar }
-  - **msg_template:**Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of the pattern `%1` to be replaced by the value specified by the [arg1](#func.print_log1.args.arg1) argument.
 
@@
 ::: { #func.print_log1.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log1.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the pattern `%1` in the message template passed in the [msg_template](#func.print_log1.args.msg_template) argument.
 
@@
 
-This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log1](#func.get_log1) function described above.
+This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the object returned by the [get_log1](#func.get_log1) function (also called internally) described above.
 
@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log1](#func.get_log1) function described above.
-
+A glue object, returned by the internally called function [get_log1](#func.get_log1) described above.
 :::
@@
 
-Builds a message string from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format element specified by the following arguments:
-
-  - [arg.name](#func.msg.set_arg.args.arg.name): the pattern to be replaced by the value passed in the [arg] argument;
+Builds a character vector from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format element specified by the following arguments:
+
+  - [arg.name](#func.msg.set_arg.args.arg.name): the pattern to be replaced by the value passed in the [arg](#func.msg.set_arg.args.arg) argument;
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function: put_log1.

@@
 
-Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log1.args.msg_template) argument using the format value specified by the [arg1](#func.put_log1.args.arg1).
+Outputs a log to the currently open log file (using the [open_logfile](#func.open_logfile) function described above), created from the template passed in the [msg_template](#func.put_log1.args.msg_template) argument, using the value specified by the [arg1](#func.put_log1.args.arg1) argument to replace all the occurrences of the pattern `%1` found in the template.
 
@@
 ::: { #func.put_log1.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of the pattern `%1` to be replaced by the value specified by the [arg1](#func.put_log1.args.arg1) argument.
 
@@
 ::: { #func.put_log1.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log1.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the pattern `%1` in the message template passed in the [msg_template](#func.put_log1.args.msg_template) argument.
 
@@
 
-This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log1](#func.get_log1) function described above.
+This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log1](#func.get_log1) function described above.
 
@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log1](#func.get_log1) function described above.
+A glue object, returned by the internally called function [get_log1](#func.get_log1) described above.
+
 :::

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the function: get_log2.

@@
 
-Builds a string from the template passed in the [msg_template](#func.get_log2.args.msg_template) argument using the format values specified by the [arg1](#func.get_log2.args.arg1) and [arg2](#func.get_log2.args.arg2) arguments.
+Creates a character vector from the template passed in the [msg_template](#func.get_log2.args.msg_template) argument, using the values specified by the [arg1](#func.get_log2.args.arg1) and [arg2](#func.get_log2.args.arg2) arguments to replace all the occurrences of the placeholders `%1` and `%2`, respectively, found in the template.
 
@@
 ::: { #func.get_log2.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one combination of the following substrings: `%1`, `%2`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.get_log2.args.arg1) and  [arg2](#func.get_log2.args.arg2) arguments, respectively.
 
@@
 ::: { #func.get_log2.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log2.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.get_log2.args.msg_template) argument.
 
@@
 ::: { #func.get_log2.args.arg2 .sidebar }
-  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.get_log2.args.msg_template) argument.
+  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.get_log2.args.msg_template) argument.
 
@@
 
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log2.args.msg_template), [arg1](#func.get_log2.args.arg1), and [arg2](#func.get_log2.args.arg2)  arguments, respectively.
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log2.args.msg_template) argument, using the values specified by the [arg1](#func.get_log2.args.arg1) and [arg2](#func.get_log2.args.arg2)  arguments to replace all the occurrences of the placeholders `%1` and `%2`, respectively, found in the template.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the functions: get_log1, get_log2, get_log3, get_log4.

@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
+A glue object, returned by the internally called [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) function, created from the character vector returned by the (also internally called) function [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Arguments section): print_log2, put_log2.

@@
 ::: { #func.print_log2.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one combination of the following substrings: `%1`, `%2`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.print_log2.args.arg1) and  [arg2](#func.print_log2.args.arg2) arguments, respectively.
 
@@
 ::: { #func.print_log2.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log2.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.print_log2.args.msg_template) argument.
 
@@
 ::: { #func.print_log2.args.arg2 .sidebar }
-  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.print_log2.args.msg_template) argument.
+  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.print_log2.args.msg_template) argument.
 
@@
 ::: { #func.put_log2.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one combination of the following substrings: `%1`, `%2`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.put_log2.args.arg1) and  [arg2](#func.put_log2.args.arg2) arguments, respectively.
 
@@
 ::: { #func.put_log2.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log2.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.put_log2.args.msg_template) argument.
 
@@
 ::: { #func.put_log2.args.arg2 .sidebar }
-  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.put_log2.args.msg_template) argument.
+  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.put_log2.args.msg_template) argument.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Summary): get_log3, get_log4.

@@
 
-Builds a string from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument using the format values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3) arguments.
+Creates a character vector from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument, using the values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3) arguments to replace all the occurrences of the placeholders `%1`, `%2`, and `%3`, respectively, found in the template.
 
@@
 
-Builds a string from the template passed in the [msg_template](#func.get_log4.args.msg_template) argument using the format values specified by the [arg1](#func.get_log4.args.arg1), [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3) arguments, and [arg4](#func.get_log4.args.arg4) arguments.
+Creates a character vector from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument, using the values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), [arg3](#func.get_log3.args.arg3), and [arg4](#func.get_log3.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Arguments section): get_log3, print_log3, put_log3.

@@
 ::: { #func.get_log3.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.get_log3.args.arg1) and  [arg2](#func.get_log3.args.arg2) arguments, respectively.
 
@@
 ::: { #func.get_log3.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.get_log3.args.msg_template) argument.
 
@@
 ::: { #func.get_log3.args.arg2 .sidebar }
-  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.
+  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.get_log3.args.msg_template) argument.
 
@@
 ::: { #func.get_log3.args.arg3 .sidebar }
-  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.get_log3.args.msg_template) argument.
+  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.get_log3.args.msg_template) argument.
 
@@
 ::: { #func.print_log3.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.print_log3.args.arg1) and  [arg2](#func.print_log3.args.arg2) arguments, respectively.
 
@@
 ::: { #func.print_log3.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.print_log3.args.msg_template) argument.
 
@@
 ::: { #func.print_log3.args.arg2 .sidebar }
-  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.
+  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.print_log3.args.msg_template) argument.
 
@@
 ::: { #func.print_log3.args.arg3 .sidebar }
-  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.print_log3.args.msg_template) argument.
+  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.print_log3.args.msg_template) argument.
 
@@
 ::: { #func.put_log3.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.put_log3.args.arg1) and  [arg2](#func.put_log3.args.arg2) arguments, respectively.
 
@@
 ::: { #func.put_log3.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.put_log3.args.msg_template) argument.
 
@@
 ::: { #func.put_log3.args.arg2 .sidebar }
-  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.
-
-:::
-
-::: { #func.get_log3.args.arg3 .sidebar }
-  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.put_log3.args.msg_template) argument.
+  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.put_log3.args.msg_template) argument.
+
+:::
+
+::: { #func.put_log3.args.arg3 .sidebar }
+  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.put_log3.args.msg_template) argument.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Arguments section): get_log4, print_log4, put_log4.

@@
 ::: { #func.get_log4.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`, `%4`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.get_log4.args.arg1) and  [arg2](#func.get_log4.args.arg2) arguments, respectively.
 
@@
 ::: { #func.get_log4.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log4.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.get_log4.args.msg_template) argument.
 
@@
 ::: { #func.get_log4.args.arg2 .sidebar }
-  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.get_log4.args.msg_template) argument.
+  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.get_log4.args.msg_template) argument.
 
@@
 ::: { #func.get_log4.args.arg3 .sidebar }
-  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.get_log4.args.msg_template) argument.
+  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.get_log4.args.msg_template) argument.
 
@@
 ::: { #func.get_log4.args.arg4 .sidebar }
-  - **arg4:** The value to replace the format elements represented by the substring `%4` in the message template specified by the [msg_template](#func.get_log4.args.msg_template) argument.
+  - **arg4:** Value to replace all occurrences of the placeholder `%4` in the message template passed in the [msg_template](#func.get_log4.args.msg_template) argument.
 
@@
 ::: { #func.print_log4.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`, `%4`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.print_log4.args.arg1) and  [arg2](#func.print_log4.args.arg2) arguments, respectively.
 
@@
 ::: { #func.print_log4.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.print_log4.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.print_log4.args.msg_template) argument.
 
@@
 ::: { #func.print_log4.args.arg2 .sidebar }
-  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.print_log4.args.msg_template) argument.
+  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.print_log4.args.msg_template) argument.
 
@@
 ::: { #func.print_log4.args.arg3 .sidebar }
-  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.print_log4.args.msg_template) argument.
+  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.print_log4.args.msg_template) argument.
 
@@
 ::: { #func.print_log4.args.arg4 .sidebar }
-  - **arg4:** The value to replace the format elements represented by the substring `%4` in the message template specified by the [msg_template](#func.print_log4.args.msg_template) argument.
+  - **arg4:** Value to replace all occurrences of the placeholder `%4` in the message template passed in the [msg_template](#func.print_log4.args.msg_template) argument.
 
@@
 ::: { #func.put_log4.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`, `%4`.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.put_log4.args.arg1) and  [arg2](#func.put_log4.args.arg2) arguments, respectively.
 
@@
 ::: { #func.put_log4.args.arg1 .sidebar }
-  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.put_log4.args.msg_template) argument.
+  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.put_log4.args.msg_template) argument.
 
@@
 ::: { #func.put_log4.args.arg2 .sidebar }
-  - **arg2:** The value to replace the format elements represented by the substring `%2` in the message template specified by the [msg_template](#func.put_log4.args.msg_template) argument.
-
-:::
-
-::: { #func.get_log4.args.arg3 .sidebar }
-  - **arg3:** The value to replace the format elements represented by the substring `%3` in the message template specified by the [msg_template](#func.put_log4.args.msg_template) argument.
-
-:::
-
-::: { #func.get_log4.args.arg4 .sidebar }
-  - **arg4:** The value to replace the format elements represented by the substring `%4` in the message template specified by the [msg_template](#func.put_log4.args.msg_template) argument.
+  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.put_log4.args.msg_template) argument.
+
+:::
+
+::: { #func.put_log4.args.arg3 .sidebar }
+  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.put_log4.args.msg_template) argument.
+
+:::
+
+::: { #func.put_log4.args.arg4 .sidebar }
+  - **arg4:** Value to replace all occurrences of the placeholder `%4` in the message template passed in the [msg_template](#func.put_log4.args.msg_template) argument.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Summary): print_log2, print_log3, print_log4.

@@
 
-Prints a string formed from the template passed in the [msg_template](#func.print_log2.args.msg_template) argument using the format values specified by the [arg1](#func.print_log2.args.arg1) and [arg2](#func.print_log2.args.arg2) arguments.
+Prints a log created from the template passed in the [msg_template](#func.print_log2.args.msg_template) argument, using the values specified by the [arg1](#func.print_log2.args.arg1) and [arg2](#func.print_log2.args.arg2) arguments to replace all the occurrences of the placeholders `%1` and `%2`, respectively, found in the template.
 
@@
 
-Prints a string formed from the template passed in the [msg_template](#func.print_log3.args.msg_template) argument using the format values specified by the [arg1](#func.print_log3.args.arg1), [arg2](#func.print_log3.args.arg2), and [arg3](#func.print_log3.args.arg3) arguments.
+Prints a log created from the template passed in the [msg_template](#func.print_log3.args.msg_template) argument, using the values specified by the [arg1](#func.print_log3.args.arg1), [arg2](#func.print_log3.args.arg2), and [arg3](#func.print_log3.args.arg3) arguments to replace all the occurrences of the placeholders `%1`, `%2`, and `%3`, respectively, found in the template.
 
@@
 
-Prints a string formed from the template passed in the [msg_template](#func.print_log4.args.msg_template) argument using the format values specified by the [arg1](#func.print_log4.args.arg1), [arg2](#func.print_log4.args.arg2), [arg3](#func.print_log4.args.arg3), and [arg4](#func.print_log4.args.arg4) arguments.
+Prints a log created from the template passed in the [msg_template](#func.print_log4.args.msg_template) argument, using the values specified by the [arg1](#func.print_log4.args.arg1), [arg2](#func.print_log4.args.arg2), [arg3](#func.print_log4.args.arg3), and [arg4](#func.print_log4.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Summary): put_log2, put_log3, put_log4.

@@
 
-Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log2.args.msg_template) argument using the format values specified by the [arg1](#func.put_log2.args.arg1) and [arg2](#func.put_log2.args.arg2) arguments.
+Outputs a log to the currently open log file (using the [open_logfile](#func.open_logfile) function described above), created from the template passed in the [msg_template](#func.put_log2.args.msg_template) argument, using the values specified by the [arg1](#func.put_log2.args.arg1) and [arg2](#func.put_log2.args.arg2) arguments to replace all the occurrences of the placeholders `%1` and `%2`, respectively, found in the template.
 
@@
 
-Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log3.args.msg_template) argument using the format values specified by the [arg1](#func.put_log3.args.arg1), [arg2](#func.put_log3.args.arg2), and [arg3](#func.put_log3.args.arg3) arguments.
+Outputs a log to the currently open log file (using the [open_logfile](#func.open_logfile) function described above), created from the template passed in the [msg_template](#func.put_log3.args.msg_template) argument, using the values specified by the [arg1](#func.put_log3.args.arg1), [arg2](#func.put_log3.args.arg2), and [arg3](#func.put_log3.args.arg3) arguments to replace all the occurrences of the placeholders `%1`, `%2`, and `%3`, respectively, found in the template.
 
@@
 
-Outputs a string to the currently open log (using the [open_logfile](#func.open_logfile) function described above) formed from the template passed in the [msg_template](#func.put_log4.args.msg_template) argument using the format values specified by the [arg1](#func.put_log4.args.arg1), [arg2](#func.put_log4.args.arg2), [arg3](#func.put_log4.args.arg3), and [arg4](#func.put_log4.args.arg4) arguments.
+Outputs a log to the currently open log file (using the [open_logfile](#func.open_logfile) function described above), created from the template passed in the [msg_template](#func.put_log4.args.msg_template) argument, using the values specified by the [arg1](#func.put_log4.args.arg1), [arg2](#func.put_log4.args.arg2), [arg3](#func.put_log4.args.arg3), and [arg4](#func.put_log4.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Details section): get_log3, get_log4.

@@
 
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log3.args.msg_template), [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3)  arguments, respectively.
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument, using the values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3)  arguments to replace all the occurrences of the placeholders `%1`, `%2`, and `%3`, respectively, found in the template.
 
@@
 
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log4.args.msg_template), [arg1](#func.get_log4.args.arg1), [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3), and [arg4](#func.get_log4.args.arg4) arguments, respectively.
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument, using the values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), [arg3](#func.get_log3.args.arg3), and [arg4](#func.get_log3.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Details section): print_log2, print_log3, print_log4.

@@
 
-This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log2](#func.get_log2) function described above.
+This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the object returned by the [get_log2](#func.get_log2) function (also called internally) described above.
 
@@
 
-This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log3](#func.get_log3) function described above.
+This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the object returned by the [get_log3](#func.get_log3) function (also called internally) described above.
 
@@
 
-This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the string (possibly multiline) produced by the (also called internally) [get_log4](#func.get_log4) function described above.
+This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the object returned by the [get_log4](#func.get_log4) function (also called internally) described above.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Details section): put_log2, put_log3, put_log4.

@@
 
-This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log2](#func.get_log2) function described above.
+This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log2](#func.get_log2) function described above.
 
@@
 
-This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log3](#func.get_log3) function described above.
+This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log3](#func.get_log3) function described above.
 
@@
 
-This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the string (possibly multiline) produced by the (also called internally) [get_log4](#func.get_log4) function described above.
+This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log4](#func.get_log4) function described above.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Value section): print_log2, put_log2, print_log3, put_log3, print_log4, put_log4.

@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log2](#func.get_log2) function described above.
+A glue object, returned by the internally called function [get_log2](#func.get_log2) described above.
 
@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log2](#func.get_log2) function described above.
+A glue object, returned by the internally called function [get_log2](#func.get_log2) described above.
 :::
@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log3](#func.get_log3) function described above.
+A glue object, returned by the internally called function [get_log3](#func.get_log3) described above.
 
@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log3](#func.get_log3) function described above.
+A glue object, returned by the internally called function [get_log3](#func.get_log3) described above.
+
 :::
@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log4](#func.get_log4) function described above.
+A glue object, returned by the internally called function [get_log4](#func.get_log4) described above.
 
@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the internally called [get_log4](#func.get_log4) function described above.
+A glue object, returned by the internally called function [get_log4](#func.get_log4) described above.
 :::

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function: put_end_date.

@@
 
-#### [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) Function {#func.put_end_date}
+#### [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L23) Function {#func.put_end_date}
 \
@@
 
-The source code of the [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is shown below:
+The source code of the [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L23) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) script on _GitHub_.
+The source code of the [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L23) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L23) script on _GitHub_.
 :::

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Argument section): get_log3, print_log3, put_log3, get_log4, print_log4, put_log4.

@@
 ::: { #func.get_log3.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.get_log3.args.arg1) and  [arg2](#func.get_log3.args.arg2) arguments, respectively.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.get_log3.args.arg1),  [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3) arguments, respectively.
 
@@
 ::: { #func.print_log3.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.print_log3.args.arg1) and  [arg2](#func.print_log3.args.arg2) arguments, respectively.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.print_log3.args.arg1),  [arg2](#func.print_log3.args.arg2), and [arg3](#func.print_log3.args.arg3) arguments, respectively.
 
@@
 ::: { #func.put_log3.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.put_log3.args.arg1) and  [arg2](#func.put_log3.args.arg2) arguments, respectively.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.put_log3.args.arg1),  [arg2](#func.put_log3.args.arg2), and [arg3](#func.put_log3.args.arg3) arguments, respectively.
 
@@
 ::: { #func.get_log4.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.get_log4.args.arg1) and  [arg2](#func.get_log4.args.arg2) arguments, respectively.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.get_log4.args.arg1),  [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3), and [arg4](#func.get_log4.args.arg4) arguments, respectively.
 
@@
 ::: { #func.print_log4.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.print_log4.args.arg1) and  [arg2](#func.print_log4.args.arg2) arguments, respectively.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.print_log4.args.arg1),  [arg2](#func.print_log4.args.arg2), [arg3](#func.print_log4.args.arg3), and [arg4](#func.print_log4.args.arg4) arguments, respectively.
 
@@
 ::: { #func.put_log4.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.put_log4.args.arg1) and  [arg2](#func.put_log4.args.arg2) arguments, respectively.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.put_log4.args.arg1),  [arg2](#func.put_log4.args.arg2), [arg3](#func.put_log4.args.arg3), and [arg4](#func.put_log4.args.arg4) arguments, respectively.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (source code): get_log3, get_log4.

@@
     str_replace_all("%2", as.character(arg2)) |>
+    str_replace_all("%3", as.character(arg3)) |>
     str_glue()
@@
     str_replace_all("%2", as.character(arg2)) |>
-    str_replace_all("%3", as.character(arg2)) |>
-    str_replace_all("%4", as.character(arg2)) |>
+    str_replace_all("%3", as.character(arg3)) |>
+    str_replace_all("%4", as.character(arg4)) |>
     str_glue()

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function: get_log4.

@@
 
-Creates a character vector from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument, using the values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), [arg3](#func.get_log3.args.arg3), and [arg4](#func.get_log3.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
+Creates a character vector from the template passed in the [msg_template](#func.get_log4.args.msg_template) argument, using the values specified by the [arg1](#func.get_log4.args.arg1), [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3), and [arg4](#func.get_log4.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
 

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Argument section): get_log4, print_log4, put_log4.

@@
 ::: { #func.get_log4.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.get_log4.args.arg1),  [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3), and [arg4](#func.get_log4.args.arg4) arguments, respectively.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, `%3`, and `%4` to be replaced by the values specified by the [arg1](#func.get_log4.args.arg1),  [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3), and [arg4](#func.get_log4.args.arg4) arguments, respectively.
 
@@
 ::: { #func.print_log4.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.print_log4.args.arg1),  [arg2](#func.print_log4.args.arg2), [arg3](#func.print_log4.args.arg3), and [arg4](#func.print_log4.args.arg4) arguments, respectively.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, `%3`, and `%4` to be replaced by the values specified by the [arg1](#func.print_log4.args.arg1),  [arg2](#func.print_log4.args.arg2), [arg3](#func.print_log4.args.arg3), and [arg4](#func.print_log4.args.arg4) arguments, respectively.
 
@@
 ::: { #func.put_log4.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.put_log4.args.arg1),  [arg2](#func.put_log4.args.arg2), [arg3](#func.put_log4.args.arg3), and [arg4](#func.put_log4.args.arg4) arguments, respectively.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, `%3`, and `%4` to be replaced by the values specified by the [arg1](#func.put_log4.args.arg1),  [arg2](#func.put_log4.args.arg2), [arg3](#func.put_log4.args.arg3), and [arg4](#func.put_log4.args.arg4) arguments, respectively.
 

### 2025-10-25 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function: get_log4.

@@
 
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument, using the values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), [arg3](#func.get_log3.args.arg3), and [arg4](#func.get_log3.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
+This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log4.args.msg_template) argument, using the values specified by the [arg1](#func.get_log4.args.arg1), [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3), and [arg4](#func.get_log4.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
 

### 2025-10-26 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function: msg.set_arg.

@@
 
-Builds a character vector from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format element specified by the following arguments:
-
-  - [arg.name](#func.msg.set_arg.args.arg.name): the pattern to be replaced by the value passed in the [arg](#func.msg.set_arg.args.arg) argument;
-
-  - [arg](#func.msg.set_arg.args.arg): the value to replace all occurrences of the pattern passed in the [arg.name](#func.msg.set_arg.args.arg.name) argument.
+Creates a character vector from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument, using the value specified by the [arg](#func.msg.set_arg.args.arg) argument to replace all the occurrences of the placeholder passed in the [arg.name](#func.msg.set_arg.args.arg.name) argument found in the template.
 
@@
 ```{r eval=FALSE}
-msg.set_arg(msg_template, arg, arg, arg.name = "%1")
+msg.set_arg(msg_template, arg, arg.name = "%1")
 ```
@@
 ::: { #func.msg.set_arg.args.arg.name .sidebar }
-  - **arg.name:** Substring to replace in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.
+  - **arg.name:** Substring (pattern) to replace all occurrences found in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.
 
@@
 ::: { #func.msg.set_arg.args.arg .sidebar }
-  - **arg:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument.
+  - **arg:** Value to replace all occurrences of the pattern specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument.
+
 :::

### 2025-10-26 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function: msg.set_arg.

@@
 
-This function is a wrapper to [logr::log_open](https://www.rdocumentation.org/packages/logr/versions/1.3.9/topics/log_open) function.
+This function is a wrapper for the [logr::log_open](https://www.rdocumentation.org/packages/logr/versions/1.3.9/topics/log_open) function.
 It also calls internally the following functions to generate a unique file name based on the [file_name](#func.open_logfile.args.file_name) argument and _system time_:
@@
 
-This function internally calls [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format value specified by the [arg](#func.msg.set_arg.args.arg)  argument to replace all occurances of the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument (`%1` by default).
+This function is a wrapper for the [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` function, which is called internally to replace all occurrences of the substring specified by the [arg_name](#func.msg.set_arg.args.arg.name) argument, in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument (`%1` by default).
 
@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
+The character vector returned by the internally called [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
 

### 2025-10-26 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function: msg.glue.

@@
 
-Builds a message string from the template passed in the [msg_template](#func.msg.glue.args.msg_template) argument using the format element specified by the following arguments:
-
-  - [arg.name](#func.msg.glue.args.arg.name): name of the element;
-
-  - [arg](#func.msg.glue.args.arg): the element value.
+Creates a [glue::glue](https://glue.tidyverse.org/reference/glue.html) object from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument, using the value specified by the [arg](#func.msg.set_arg.args.arg) argument to replace all the occurrences of the placeholder passed in the [arg.name](#func.msg.set_arg.args.arg.name) argument found in the template.
 
@@
 ::: { #func.msg.glue.args.msg_template .sidebar }
-  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring specified by the [arg.name](#func.msg.msg.glue.args.arg.name) argument.
+  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of a pattern specified by the [arg.name](#func.msg.glue.args.arg.name) argument.
 
@@
 ::: { #func.msg.glue.args.arg.name .sidebar }
-  - **arg.name:** Substring to replace in the message template passed in the [msg_template](#func.msg.msg.glue.args.msg_template) argument with the value specified in the [arg](#func.msg.msg.glue.args.arg) argument.
+  - **arg.name:** Substring (pattern) to replace all occurrences found in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument with the value specified in the [arg](#func.msg.glue.args.arg) argument.
+
 :::
@@
 ::: { #func.msg.glue.args.arg .sidebar }
-  - **arg:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.glue.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument.
+  - **arg:** Value to replace all occurrences of the pattern specified by the [arg.name](#func.msg.glue.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument.
 
@@
 
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.msg.glue.args.msg_template) and [arg](#func.msg.glue.args.arg)  arguments, respectively.
+This function internally calls the [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) `R` function to format the character vector returned by the (also called internally) [msg.set_arg](#func.msg.set_arg) function described above.
 
@@
 
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
+A [glue::glue](https://glue.tidyverse.org/reference/glue.html) object created from the character vector returned by the internally called [msg.set_arg](#func.msg.set_arg) function.
 

### 2025-10-26 reports/capstone-movielens.site/02-0.methods.Rmd
Fix for Methods section.

@@
 :::
-
-## Defining Logging and Time Measuring Helper Functions
-\
-
-First, let's define some helper functions for logging and time-measuring features that we will use in our R scripts. Some of them are listed below:
-
-```{r eval=FALSE }
-# Logging Helper functions -----------------------------------------------------
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-
-# ...
-```
-
-\newpage
 

### 2025-10-26 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions: msg.set_arg, msg.glue.

@@
 ::: { #func.msg.set_arg.args.arg.name .sidebar }
-  - **arg.name:** Substring (pattern) to replace all occurrences found in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.
+  - **arg.name:** (*Optional: `%1` by default*) Substring (pattern or *placeholder*) to replace all occurrences found in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.
 
@@
 
-This function is a wrapper for the [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` function, which is called internally to replace all occurrences of the substring specified by the [arg_name](#func.msg.set_arg.args.arg.name) argument, in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument (`%1` by default).
+This function is a wrapper for the [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` function, which is called internally to replace all occurrences of the pattern (placeholder) specified by the [arg_name](#func.msg.set_arg.args.arg.name) argument (`%1` by default), in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.
 
@@
 
-Creates a [glue::glue](https://glue.tidyverse.org/reference/glue.html) object from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument, using the value specified by the [arg](#func.msg.set_arg.args.arg) argument to replace all the occurrences of the placeholder passed in the [arg.name](#func.msg.set_arg.args.arg.name) argument found in the template.
+Creates a [glue::glue](https://glue.tidyverse.org/reference/glue.html) object from the template passed in the [msg_template](#func.msg.glue.args.msg_template) argument, using the value specified by the [arg](#func.msg.glue.args.arg) argument to replace all the occurrences of the placeholder passed in the [arg.name](#func.msg.glue.args.arg.name) argument found in the template.
 
@@
 ::: { #func.msg.glue.args.arg.name .sidebar }
-  - **arg.name:** Substring (pattern) to replace all occurrences found in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument with the value specified in the [arg](#func.msg.glue.args.arg) argument.
+  - **arg.name:** (*Optional: `%1` by default*) Substring (pattern or *placeholder*) to replace all occurrences found in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument with the value specified in the [arg](#func.msg.glue.args.arg) argument.
 
@@
 
-A [glue::glue](https://glue.tidyverse.org/reference/glue.html) object created from the character vector returned by the internally called [msg.set_arg](#func.msg.set_arg) function.
+A [glue::glue](https://glue.tidyverse.org/reference/glue.html) object created from the character vector returned by the internally called [msg.set_arg()](#func.msg.set_arg).
 

### 2025-10-26 reports/capstone-movielens.site/02-0.methods.Rmd
Minor fix for the Methods section.

@@
 ::: {.noteblock data-latex=""}
-All the source code of the R-scripts is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r)[@edx_capstone_movielens]. 
+All the source code of the `R` scripts utilized in this project is available on the project's [GitHub repository](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/tree/main/r)[@edx_capstone_movielens].
 :::

### 2025-10-27 reports/capstone-movielens.site/01.intro.Rmd
Fix for bibliography / citations.

--- 2025-09-21 reports/capstone-movielens.site/01.intro.Rmd
@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 23.2 Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook_, is defined as:
+Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_, is defined as:
 $$
@@
 
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_23-2].
+with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_25-1].
 
@@
 
-Now, note the expressions below which confirm the fact explained in [Section _23.1.1 Movielens data_](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_[@IDS2] that not every user rated every movie:
+Now, note the expressions below which confirm the fact explained in [Section 33.7.1 *Movielens data*](https://rafalab.dfci.harvard.edu/dsbook/large-datasets.html#movielens-data) of the _Course Textbook (First Edition)_ that not every user rated every movie[@IDS_E1_33-7-1]:
 ```{r}
@@
 Therefore, we can think of a recommendation system as filling in the `NA`s in the dataset for the movies that some or all the users do not rate.
-A sample from the `edx` data below illustrates this idea[@IDS2_23-1-1]:
+A sample from the `edx` data below illustrates this idea[@IDS_E1_33-7-1]:
 ```{r}

### 2025-10-27 reports/capstone-movielens.site/02-0.methods.Rmd
Fix for bibliography / citations.

@@
 
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 23.1.1 *Movielens data*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) of the _Course Textbook_ mentioned above[@IDS2_23-1-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook_[@IDS2_29-6].
+We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 25.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_25-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 31.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
 To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
@@
 ::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L86) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
+The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
 :::
 
-### [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L209) Function {#func.init_source_datasets}
+### [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L211) Function {#func.init_source_datasets}
 
@@
 
-### [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L87) Function {#func.make_source_datasets}
+### [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) Function {#func.make_source_datasets}
 
@@
 
-We will use the array representation described in [Section 17.5 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook_, for the training data[@IDS2_17-5].
+We will use the array representation described in [Section 18.5 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook (New Edition)_, for the training data[@IDS2_18-5].
 For this purpose, we will convert the `edx` dataset into a matrix using the `tidyr::pivot_wider` function:
@@
 ::: {.noteblock data-latex=""}
-The [source code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L71) of the function mentioned above is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L1) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
+The [source code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) of the function mentioned above is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
 :::
@@
 
-Note that titles cannot be considered unique, so we cannot use them as IDs[@IDS2_23-1-1].
+Note that titles cannot be considered unique, so we cannot use them as IDs[@IDS2_25-1].
 
@@
 Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 29.6.1 *K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook_[@IDS2_29-6-1]:
+as explained in [Section 31.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6]:
 ```{r eval=FALSE}
@@
 
-Note that we used the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function call to split the original dataset (`edx` in this case):
+Note that we used the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function call to split the original dataset (`edx` in this case):
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L15) function is defined in the same script as the [make_source_datasets](#func.make_source_datasets), from which it is called.
+The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function is defined in the same script as the [make_source_datasets](#func.make_source_datasets), from which it is called.
 :::

### 2025-10-27 reports/capstone-movielens.site/work/func-descr.template.Rmd
Fix for bibliography / citations.

@@
 The source code of the [log_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) script on _GitHub_.
+:::
+:::
+
+#### [helper-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.helper-func.tmpl}
+\
+
+::: { #func.helper-func.tmpl.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+helper-func.tmpl()
+
+```
+:::
+
+::: { #func.helper-func.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.helper-func.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.helper-func.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.helper-func.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.helper-func.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.helper-func.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [helper-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [helper-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+:::
+:::
+
+#### [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.dat-func.tmpl}
+\
+
+::: { #func.dat-func.tmpl.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+dat-func.tmpl()
+
+```
+:::
+
+::: { #func.dat-func.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.dat-func.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.dat-func.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.dat-func.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.dat-func.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.dat-func.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) script on _GitHub_.
 :::

### 2025-10-30 reports/capstone-movielens.site/05.appendix.Rmd
Fix for bibliography / citations.
Common Helper Functions script: `(R)MSE-related functions` section functions described.

@@
 
+### (Root) Mean Squared Error Calculation
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section are available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+:::
+
+#### [mse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) Function {#func.mse}
+\
+
+Calculates *Mean Squared Error* as described in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_25-1].
+
+::: { #func.mse.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+mse(r)
+
+```
+:::
+
+::: { #func.mse.args .sidebar }
+##### Arguments
+\
+
+::: { #func.mse.args.r .sidebar }
+  - **r:** Numeric vector representing a set of residuals as described in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_25-1].
+
+:::
+:::
+
+::: { #func.mse.code .sidebar }
+##### Source Code
+\
+
+The source code of the [mse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) function is shown below:
+```{r eval=FALSE}
+mse <- function(r) mean(r^2)
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L5) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) script on _GitHub_.
+:::
+:::
+
+#### [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) Function {#func.mse_cv}
+\
+
+Calculates the average value of the *Mean Squared Errors* calculated using the _K-Fold Cross Validation_ method as described in [Section 31.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
+
+::: { #func.mse_cv.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+mse_cv(r_list)
+
+```
+:::
+
+::: { #func.mse_cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.mse_cv.args.r_list .sidebar }
+  - **r_list:** List of numeric vectors, each representing a set of residuals as described in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_25-1], calculated in `K`th iteration using the _K-Fold Cross Validation_ method.
+
+:::
+:::
+
+::: { #funcc.mse_cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) function is shown below:
+```{r eval=FALSE}
+mse_cv <- function(r_list) {
+  mses <- sapply(r_list, mse(r))
+  mean(mses)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L5) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) script on _GitHub_.
+:::
+:::
+
+#### [rmse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) Function {#func.rmse}
+\
+
+Calculates *Root Mean Squared Error* as described in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_25-1].
+
+::: { #func.rmse.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+rmse(r)
+
+```
+:::
+
+::: { #func.rmse.args .sidebar }
+##### Arguments
+\
+
+::: { #func.rmse.args.r .sidebar }
+  - **r:** Numeric vector representing a set of residuals as described in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_25-1].
+
+:::
+:::
+
+::: { #func.rmse.code .sidebar }
+##### Source Code
+\
+
+The source code of the [rmse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) function is shown below:
+```{r eval=FALSE}
+rmse <- function(r) sqrt(mse(r))
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [rmse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L10) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) script on _GitHub_.
+:::
+:::
+
+#### [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) Function {#func.rmse2}
+\
+
+Calculates *Root Mean Squared Error* as described in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_25-1].
+
+::: { #func.rmse2.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+rmse2(true_ratings, predicted_ratings)
+
+```
+:::
+
+::: { #func.rmse2.args .sidebar }
+##### Arguments
+\
+
+::: { #func.rmse2.args.true_ratings .sidebar }
+  - **true_ratings:** Numeric vector representing a set of *actual rating* values stored in the validation dataset.
+
+:::
+
+::: { #func.rmse2.args.predicted_ratings .sidebar }
+  - **predicted_ratings:** A numeric vector representing a set of *predicted rating values* computed from the data stored in the test dataset.
+
+:::
+:::
+
+::: { #func.rmse2.code .sidebar }
+##### Source Code
+\
+
+The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) function is shown below:
+```{r eval=FALSE}
+rmse2 <- function(true_ratings, predicted_ratings) {
+  rmse(true_ratings - predicted_ratings)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L12) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) script on _GitHub_.
+:::
+:::
+
 ### Result RMSEs Table Functions
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+The complete source code of the functions described in this section are available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
 :::

### 2025-10-30 reports/capstone-movielens.site/work/func-descr.template.Rmd
Common Helper Functions script: `(R)MSE-related functions` section functions described.

@@
 ::: {.noteblock data-latex=""}
-The source code of the [helper-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+The source code of the [helper-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L0) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
 :::

### 2025-10-31 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Functions described: CreateRMSEs_ResultTibble, RMSEs.AddRow.

@@
 
-Let's begin our analysis by evaluating the simplest model described in [Section 23.3 *A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook*[@IDS2_23-3], and then gradually refine it through further research.
+Let's begin our analysis by evaluating the simplest model described in [Section 25.1 *Case study: recommendation systems / A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook*[@IDS2_25-1], and then gradually refine it through further research.
 

### 2025-10-31 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: CreateRMSEs_ResultTibble, RMSEs.AddRow.

@@
 ::: {.noteblock data-latex=""}
-The source code of the [mse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L5) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) script on _GitHub_.
-:::
-:::
-
-#### [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) Function {#func.mse_cv}
+The source code of the [mse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) Function {#func.mse_cv}
 \
@@
 
-The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) function is shown below:
+The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L5) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) script on _GitHub_.
-:::
-:::
+The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) script on _GitHub_.
+:::
+:::
+
+\newpage
 
@@
 ::: {.noteblock data-latex=""}
-The source code of the [rmse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L10) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) script on _GitHub_.
-:::
-:::
+The source code of the [rmse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) script on _GitHub_.
+:::
+:::
+
+\newpage
 
@@
 ::: { #func.rmse2.args.predicted_ratings .sidebar }
-  - **predicted_ratings:** A numeric vector representing a set of *predicted rating values* computed from the data stored in the test dataset.
+  - **predicted_ratings:** A numeric vector representing a set of *predicted rating* values computed from the data stored in the test dataset.
 
@@
 ::: {.noteblock data-latex=""}
-The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L12) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) script on _GitHub_.
-:::
-:::
+The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) script on _GitHub_.
+:::
+:::
+
+\newpage
 
@@
 
-#### [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) Function {#func.RMSEs.}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) script on _GitHub_.
-:::
-
-::: { #func.RMSEs.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-```
-:::
-
-::: { #func.RMSEs..args .sidebar }
-##### Arguments
-\
-
-::: { #func.RMSEs..args.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs..args. .sidebar }
-  - ***:*** ;
-
-:::
-
-::: { #func.RMSEs.details .sidebar }
-##### Details
-\
-
-::: { #func.RMSEs.code .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
-```{r eval=FALSE}
-```
-:::
-
-##### Return
-
-The modified _Resut (RMSEs) Table_.
-
-#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) Function {#func.RMSEs.AddRow}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) script on _GitHub_.
-:::
+#### [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) Function {#func.CreateRMSEs_ResultTibble}
+\
+
+Creates a _Result (RMSEs) Table_ of type *data frame*.
+::: { #func.CreateRMSEs_ResultTibble.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+RMSEs.ResultTibble <- CreateRMSEs_ResultTibble()
+```
+:::
+
+::: { #func.CreateRMSEs_ResultTibble.args .sidebar }
+##### Details
+\
+
+This function is a wrapper for the [tibble::tibble](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble) function, which is called internally to construct a data frame representing the _Result (RMSEs) Table_ to store the _RMSE_ values for every model used in the project to predict movie ratings.
+
+The result data frame, which is returned to the client code, has the following columns:
+
+  - *Method* (chr);
+  - *RMSE* (num);
+  - *Comment* (chr)
+
+::: { #func.CreateRMSEs_ResultTibble.value .sidebar }
+##### Value
+\
+
+A tibble returned by the internally called [tibble::tibble()](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble)
+
+:::
+
+::: { #func.CreateRMSEs_ResultTibble.code .sidebar }
+##### Source Code
+\
+
+The source code of the [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) function is shown below:
+```{r eval=FALSE}
+CreateRMSEs_ResultTibble <- function(){
+  tibble(Method = c("Project Objective"),
+         RMSE = project_objective,
+         Comment = " ")
+}
+```
+:::
+
+::: {.noteblock data-latex=""}
+The source code of the [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) script on _GitHub_.
+:::
+
+#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) Function {#func.RMSEs.AddRow}
+\
+
+Adds a row to the original _Result (RMSEs) Table_ passed in the [RMSEs](#func.RMSEs.AddRow.args.RMSEs) argument.
 
@@
 ::: { #func.RMSEs.AddRow.args.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
+  - ***RMSEs:*** Original _Resut (RMSEs) Table_ (of type *data frame*) to modify;
 
@@
 :::
+:::
 
 ::: { #func.RMSEs.AddRow.code .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
+##### Details
+\
+
+This function is a wrapper for the [tibble::add_row](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row) function, which is called internally to modify a data frame representing the original _Result (RMSEs) Table_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
+
+:::
+
+::: { #func.RMSEs.AddRow.value .sidebar }
+##### Value
+\
+
+The modified tibble returned by the internally called [tibble::add_row()](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row).
+
+:::
+
+::: { #func.RMSEs.AddRow.code .sidebar }
+##### Source Code
+\
+
+The source code of the [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) function is shown below:
 ```{r eval=FALSE}
@@
 
-##### Return
-
-The modified _Resut (RMSEs) Table_.
+::: {.noteblock data-latex=""}
+The source code of the [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) script on _GitHub_.
+:::
 
@@
 ::: { #func.RMSEs.AddDiffColumn.args.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;
+  - ***RMSEs:*** _Result (RMSEs) Table_ to modify;
 
@@
 
-The modified _Resut (RMSEs) Table_.
+The modified _Result (RMSEs) Table_.
 
@@
 
-Prints the _Resut (RMSEs) Table_.
+Prints the _Result (RMSEs) Table_.
 
@@
 ::: { #func.RMSE_kable.args.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
+  - ***RMSEs:*** _Result (RMSEs) Table_ to print;
 
@@
 ::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
-  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;
+  - ***RMSEs:*** _Result (RMSEs) Table_ to print;
 

### 2025-10-31 reports/capstone-movielens.site/work/func-descr.template.Rmd
Functions described: CreateRMSEs_ResultTibble, RMSEs.AddRow.

@@
 
+#### [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.RMSEs.}
+\
+
+Modifies the original _Result (RMSEs) Table_ passed in the [RMSEs](#func.RMSEs..args.RMSEs) argument.
+
+::: { #func.RMSEs..usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.RMSEs..args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSEs..args.RMSEs .sidebar }
+  - ***RMSEs:*** Original _Resut (RMSEs) Table_ (of type *data frame*) to modify;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs..args. .sidebar }
+  - ***:*** ;
+
+:::
+:::
+
+::: { #func.RMSEs.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the [tibble::]() function, which is called internally to modify a data frame representing the original _Result (RMSEs) Table_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
+:::
+::: { #func.RMSEs..value .sidebar }
+##### Value
+\
+
+The modified tibble returned by the internally called [tibble::()]().
+
+:::
+
+::: { #func.RMSEs..code .sidebar }
+##### Source Code
+\
+
+The source code of the [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+:::
+
+::: {.noteblock data-latex=""}
+The source code of the [RMSEs.](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+:::
+
 #### [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.dat-func.tmpl}

### 2025-11-01 reports/capstone-movielens.site/05.appendix.Rmd
Function described: RMSEs.AddDiffColumn

@@
 
-#### [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) Function {#func.rmse2}
+#### [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L11) Function {#func.rmse2}
 \
@@
 
-The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) function is shown below:
+The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L11) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L12) script on _GitHub_.
+The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L11) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L11) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-#### [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) Function {#func.CreateRMSEs_ResultTibble}
-\
-
-Creates a _Result (RMSEs) Table_ of type *data frame*.
+The complete source code of the functions described in this section are available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+:::
+
+#### [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) Function {#func.CreateRMSEs_ResultTibble}
+\
+
+Creates a _RMSEs Result Tibble_ of type *data frame*.
+
 ::: { #func.CreateRMSEs_ResultTibble.usage .sidebar }
@@
 
-::: { #func.CreateRMSEs_ResultTibble.args .sidebar }
-##### Details
-\
-
-This function is a wrapper for the [tibble::tibble](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble) function, which is called internally to construct a data frame representing the _Result (RMSEs) Table_ to store the _RMSE_ values for every model used in the project to predict movie ratings.
+::: { #func.CreateRMSEs_ResultTibble.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the [tibble::tibble](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble) function, which is called internally to construct a data frame representing the _RMSEs Result Tibble_ to store the _RMSE_ values for every model used in the project to predict movie ratings.
 
@@
 
-The source code of the [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) function is shown below:
+The source code of the [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L17) script on _GitHub_.
-:::
-
-#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) Function {#func.RMSEs.AddRow}
-\
-
-Adds a row to the original _Result (RMSEs) Table_ passed in the [RMSEs](#func.RMSEs.AddRow.args.RMSEs) argument.
+The source code of the [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) script on _GitHub_.
+:::
+
+#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L21) Function {#func.RMSEs.AddRow}
+\
+
+Adds a row to the original _RMSEs Result Tibble_ passed in the [RMSEs](#func.RMSEs.AddRow.args.RMSEs) argument.
 
@@
 ::: { #func.RMSEs.AddRow.args.RMSEs .sidebar }
-  - ***RMSEs:*** Original _Resut (RMSEs) Table_ (of type *data frame*) to modify;
+  - ***RMSEs:*** Original _RMSEs Result Tibble_ (of type *data frame*) to modify;
 
@@
 
-::: { #func.RMSEs.AddRow.code .sidebar }
-##### Details
-\
-
-This function is a wrapper for the [tibble::add_row](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row) function, which is called internally to modify a data frame representing the original _Result (RMSEs) Table_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
+::: { #func.RMSEs.AddRow.code.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the [tibble::add_row](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row) function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
+
+For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
 
@@
 
-The source code of the [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) function is shown below:
+The source code of the [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L21) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L22) script on _GitHub_.
-:::
-
-#### [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L49) Function {#func.RMSEs.AddDiffColumn}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L49) script on _GitHub_.
-:::
-
-Adds a calculated column named _Diff_ to the _Result(RMSEs)_ table (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.args.RMSEs) parameter) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row.
+The source code of the [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L21) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L21) script on _GitHub_.
+:::
+
+#### [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) Function {#func.RMSEs.AddDiffColumn}
+\
+
+Adds a calculated column named _Diff_ to the _RMSEs Result Tibble_ (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.args.RMSEs) parameter) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row.
 This is true for each row except the first, for which the value is always zero.
@@
 ::: { #func.RMSEs.AddDiffColumn.args.RMSEs .sidebar }
-  - ***RMSEs:*** _Result (RMSEs) Table_ to modify;
-
+  - ***RMSEs:*** _RMSEs Result Tibble_ to modify;
+
+:::
+:::
+
+::: { #func.RMSEs.AddDiffColumn.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the [tibble::add_column](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_column) function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_.
+It also internally uses the [RMSEs.AddRow](#func.RMSEs.AddRow) function described above to perform the necessary intermediate calculations.
+
+For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
+
+:::
+
+::: { #func.RMSEs.AddRow.value .sidebar }
+##### Value
+\
+
+The modified tibble returned by the internally called [tibble::add_column()](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_column).
 :::
@@
 
-The soure code of the function is provided below:
+The source code of the [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) function is shown below:
 ```{r eval=FALSE}
@@
     RMSEs.AddRow(NULL, project_objective, before = 1) #|>
-    #RMSEs.AddRow(NULL, 0, before = 1)
 
@@
 ```
-
-::: {.noteblock data-latex=""}
-Under the hood, the function calls internally the [RMSEs.AddRow](#func.RMSEs.AddRow) function described above.
-:::
-:::
-
-##### Return
-
-The modified _Result (RMSEs) Table_.
+:::
+
+::: {.noteblock data-latex=""}
+The source code of the [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) script on _GitHub_.
+:::
 
@@
 
-Prints the _Result (RMSEs) Table_.
+Prints the _RMSEs Result Tibble_.
 
@@
 ::: { #func.RMSE_kable.args.RMSEs .sidebar }
-  - ***RMSEs:*** _Result (RMSEs) Table_ to print;
+  - ***RMSEs:*** _RMSEs Result Tibble_ to print;
 
@@
 ::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
-  - ***RMSEs:*** _Result (RMSEs) Table_ to print;
+  - ***RMSEs:*** _RMSEs Result Tibble_ to print;
 

### 2025-11-01 reports/capstone-movielens.site/work/func-descr.template.Rmd
Function described: RMSEs.AddDiffColumn

--- 2025-10-30 reports/capstone-movielens.site/work/func-descr.template.Rmd
@@
 
+#### [RMSEs.tibble-tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.RMSEs.tibble-tmpl}
+\
+
+Modifies the original _RMSEs Result Tibble_ passed in the [RMSEs](#func.RMSEs.tibble-tmpl.args.RMSEs) argument.
+
+::: { #func.RMSEs.tibble-tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.RMSEs.tibble-tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSEs.tibble-tmpl.args.RMSEs .sidebar }
+  - ***RMSEs:*** Original _RMSEs Result Tibble_ (of type *data frame*) to modify;
+
+:::
+
+::: { #func.RMSEs.tibble-tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble-tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble-tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble-tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble-tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble-tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble-tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble-tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+:::
+
+::: { #func.RMSEs.tibble-tmpl.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the [tibble::]() function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
+:::
+
+::: { #func.RMSEs.tibble-tmpl.value .sidebar }
+##### Value
+\
+
+The modified tibble returned by the internally called [tibble::()]().
+
+:::
+
+::: { #func.RMSEs.tibble-tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [RMSEs.tibble-tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+:::
+
+::: {.noteblock data-latex=""}
+The source code of the [RMSEs.tibble-tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+:::
+
 #### [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.dat-func.tmpl}

### 2025-11-01 r/src/support-functions/common-helper.functions.R

@@ -8,7 +8,6 @@ mse_cv <- function(r_list) {
   mean(mses)
 }
 rmse <- function(r) sqrt(mse(r))
-# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
 rmse2 <- function(true_ratings, predicted_ratings) {
   rmse(true_ratings - predicted_ratings)
 }
@@ -33,15 +32,24 @@ RMSEs.AddRow <- function(RMSEs,
 RMSEs.AddDiffColumn <- function(RMSEs){
   RMSEs.Diff <- RMSEs |>
     RMSEs.AddRow(NULL, project_objective, before = 1) #|>
-    #RMSEs.AddRow(NULL, 0, before = 1)
-    
-  
+
   RMSEs.Diff <- RMSEs.Diff[-nrow(RMSEs.Diff),]
     
   RMSEs |>
   add_column(Diff = RMSEs.Diff$RMSE - RMSEs$RMSE, 
              .before = "Comment")
   
+}
+RMSE_kable <- function(RMSEs,
+                       col1width = 15,
+                       col2width = 5,
+                       col3width = 30){
+  RMSEs |>
+    kable(align='lcl', booktabs = T, padding = 5) |> 
+    row_spec(0, bold = T) |>
+    column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
+    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
+    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
 }
 RMSE.Total_kable <- function(RMSEs,
                        col1width = 15,
@@ -54,17 +62,6 @@ RMSE.Total_kable <- function(RMSEs,
                col3width) |>
     column_spec(column = 4, 
                 width = RSME.tibble.col_width(col4width)) 
-}
-RMSE_kable <- function(RMSEs,
-                       col1width = 15,
-                       col2width = 5,
-                       col3width = 30){
-  RMSEs |>
-    kable(align='lcl', booktabs = T, padding = 5) |> 
-    row_spec(0, bold = T) |>
-    column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
-    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
-    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
 }
 RSME.tibble.col_width <- function(x){
   "%1em" |> msg.glue(x)

### 2025-11-01 reports/capstone-movielens.site/02-0.methods.Rmd

@@
 \newpage
-
-### Common Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-All the _Common Helper functions_ described below in this section are defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
-:::
-
-For our further analysis, we are going to use the following _common helper functions_:
-
-#### Functions to calculate _(Root) Mean Squared Error_
-\
-
-We will need the following functions to calculate _(R)MSEs_:
-```{r eval=FALSE}
-mse <- function(r) mean(r^2)
-
-mse_cv <- function(r_list) {
-  mses <- sapply(r_list, mse(r))
-  mean(mses)
-}
-
-rmse <- function(r) sqrt(mse(r))
-# rmse_cv <- function(r_list) sqrt(mse_cv(r_list))
-
-rmse2 <- function(true_ratings, predicted_ratings) {
-  rmse(true_ratings - predicted_ratings)
-}
-```
-
-\newpage

### 2025-11-02 reports/capstone-movielens.site/05.appendix.Rmd

@@
 
+\newpage
+
 #### [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) Function {#func.RMSEs.AddDiffColumn}
@@
 
-Adds a calculated column named _Diff_ to the _RMSEs Result Tibble_ (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.args.RMSEs) parameter) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row.
+Adds a calculated column named _Diff_ to the _RMSEs Result Tibble_ (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.args.RMSEs) argument) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row.
 This is true for each row except the first, for which the value is always zero.
@@
 For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
-
 :::
@@
 
-#### [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) Function {#func.RMSE_kable}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) script on _GitHub_.
-:::
+\newpage
+
+#### [RSME.tibble.col_width](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) Function {#func.RSME.tibble.col_width}
+\
+
+Converts the _RMSEs Result Tibble_ column width value passed in argument [x](#func.RSME.tibble.col_width.args.x) to a character string compatible for use as the `width` argument value to pass to the [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) function.
+
+::: { #func.RSME.tibble.col_width.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+width_em <- RSME.tibble.col_width(x)
+```
+:::
+
+::: { #func.RSME.tibble.col_width.args .sidebar }
+##### Arguments
+\
+
+::: { #func.RSME.tibble.col_width.args.x .sidebar }
+  - ***x:*** (Numeric) Column width value to be formatted;
+
+:::
+:::
+
+::: { #func.RSME.tibble.col_width.details .sidebar }
+##### Details
+\
+
+This is a utility function, a wrapper for the [msg.glue](#func.msg.glue) function described above, which is called internally to format the value passed in argument [x](#func.RSME.tibble.col_width.args.x) for subsequent passing to the function [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) as a value of the `width` argument.
+:::
+
+::: { #func.RSME.tibble.col_width.value .sidebar }
+##### Value
+\
+
+A character string representing the formatted column width value.
+:::
+
+::: { #func.RSME.tibble.col_width.code .sidebar }
+##### Source Code
+\
+
+The source code of the [RSME.tibble.col_width](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) function is shown below:
+```{r eval=FALSE}
+RSME.tibble.col_width <- function(x){
+  "%1em" |> msg.glue(x)
+}
+```
+:::
+
+::: {.noteblock data-latex=""}
+The source code of the [RSME.tibble.col_width](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) script on _GitHub_.
+:::
+
+\newpage
+
+#### [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) Function {#func.RMSE_kable}
+\
 
@@
 ::: {.noteblock data-latex=""}
-It is assumed that the table has the following three columns:
+It is assumed that the tibble has the following three columns:
 
@@
 
-::: { #func.RMSE_kableusage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSE_kable <- function(RMSEs,
+::: { #func.RMSE_kable.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+RMSE_kable(RMSEs,
            col1width = 15,
@@
 ::: { #func.RMSE_kable.args.col1width .sidebar }
-  - ***col1width:*** Width of the first column;
+  - ***col1width:*** Width of the first column (15 by default);
 
@@
 ::: { #func.RMSE_kable.args.col2width .sidebar }
-  - ***col2width:*** Width of the second column;
+  - ***col2width:*** Width of the second column (5 by default);
 
@@
 ::: { #func.RMSE_kable.args.col3width .sidebar }
-  - ***col3width:*** Width of the third column;
-
-:::
-
-::: { #func.RMSE_kablecode .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
+  - ***col3width:*** Width of the third column (30 by default).
+
+:::
+:::
+
+::: { #func.RMSE_kable.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the [knitr::kable](https://www.rdocumentation.org/packages/knitr/versions/1.43/topics/kable) function, which is called internally to create a table (based on the _RMSEs Result Tibble_ data), formatted for output in the project report.
+
+The [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) function, along with the [RSME.tibble.col_width](#func.RSME.tibble.col_width) function described above, are also used internally to specify the width of the table columns.
+
+For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
+:::
+
+::: { #func.RMSE_kable.value .sidebar }
+##### Value
+\
+
+The table created by the internally called [knitr::kable()]().
+
+:::
+
+::: { #func.RMSE_kable.code .sidebar }
+##### Source Code
+\
+
+The source code of the [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) function is shown below:
 ```{r eval=FALSE}
@@
 
-#### [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) Function {#func.RMSE.Total_kable}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) script on _GitHub_.
-:::
-
-Prints the _RMSEs Result Tibble_.
-
-::: {.noteblock data-latex=""}
-It is assumed that the table has the following four columns:
+::: {.noteblock data-latex=""}
+The source code of the [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) script on _GitHub_.
+:::
+
+\newpage
+
+#### [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) Function {#func.RMSE.Total_kable}
+\
+
+Prints the final _RMSEs Result Tibble_.
+
+::: {.noteblock data-latex=""}
+It is assumed that the tibble has the following four columns:
 
@@
 ```{r eval=FALSE}
-RMSE.Total_kable <- function(RMSEs,
+RMSE.Total_kable(RMSEs,
                  col1width = 15,
@@
 ::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
-  - ***RMSEs:*** _RMSEs Result Tibble_ to print;
+  - ***RMSEs:*** The final _RMSEs Result Tibble_ to print;
 
@@
 ::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col1width:*** Width of the first column;
+  - ***col1width:*** Width of the first column (15 by default);
 
@@
 ::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col2width:*** Width of the second column;
+  - ***col2width:*** Width of the second column (7 by default);
 
@@
 ::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col3width:*** Width of the third column;
+  - ***col3width:*** Width of the third column(5 by default);
 
@@
 ::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col4width:*** Width of the fourth column;
-
-:::
-
-::: { #func.RMSE.Total_kablecode .sidebar }
-##### Source Code
-\
-
-The soure code of the function is provided below:
+  - ***col4width:*** Width of the fourth column (25 by default);
+
+:::
+:::
+
+::: { #func.RMSE.Total_kable.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the [RMSE_kable](#func.RMSE_kable) function described above, which is called internally to print the table, created from the final _RMSEs Result Tibble_ data.
+
+The [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) function, along with the [RSME.tibble.col_width](#func.RSME.tibble.col_width) function described above, are also used internally to set the width of the last column of the table.
+
+For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
+:::
+
+::: { #func.RMSE.Total_kable.value .sidebar }
+##### Value
+\
+
+The table returned by the internally called [RMSE_kable()](#func.RMSE_kable).
+:::
+
+::: { #func.RMSE.Total_kable.code .sidebar }
+##### Source Code
+\
+
+The source code of the [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function is shown below:
 ```{r eval=FALSE}
@@
   RMSEs |> 
-    RMSE_kable(col1width,
+    RMSE.Total_kable(col1width,
                col2width,
@@
 }
-
-```
-
-::: {.noteblock data-latex=""}
-Under the hood, the function calls internally the [RMSE_kable](#func.RMSE_kable) function described above.
-:::
-:::
+```
+:::
+
+::: {.noteblock data-latex=""}
+The source code of the [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) script on _GitHub_.
+:::
+
+\newpage
 

### 2025-11-02 reports/capstone-movielens.site/work/func-descr.template.Rmd

--- 2025-10-30 reports/capstone-movielens.site/work/func-descr.template.Rmd
@@
 
+#### [RMSEs.tibble_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.RMSEs.tibble_tmpl}
+\
+
+Modifies the original _RMSEs Result Tibble_ passed in the [RMSEs](#func.RMSEs.tibble_tmpl.args.RMSEs) argument.
+
+::: { #func.RMSEs.tibble_tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.RMSEs.tibble_tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.RMSEs.tibble_tmpl.args.RMSEs .sidebar }
+  - ***RMSEs:*** Original _RMSEs Result Tibble_ (of type *data frame*) to modify;
+
+:::
+
+::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+
+::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
+  - ***:*** ;
+
+:::
+:::
+
+::: { #func.RMSEs.tibble_tmpl.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the [tibble::]() function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
+
+For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
+:::
+
+::: { #func.RMSEs.tibble_tmpl.value .sidebar }
+##### Value
+\
+
+The modified tibble returned by the internally called [tibble::()]().
+
+:::
+
+::: { #func.RMSEs.tibble_tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [RMSEs.tibble_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+:::
+
+::: {.noteblock data-latex=""}
+The source code of the [RMSEs.tibble_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+:::
+
+\newpage
+
 #### [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.dat-func.tmpl}

### 2025-11-02 reports/capstone-movielens.site/05.appendix.Rmd
Report layout: minor fix.
RMSE.Total_kable function: hotfix.

@@
 
-\newpage
-
 #### [RSME.tibble.col_width](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) Function {#func.RSME.tibble.col_width}
@@
 
-The table created by the internally called [knitr::kable()]().
+The table created by the internally called [knitr::kable()](https://www.rdocumentation.org/packages/knitr/versions/1.43/topics/kable).
 
@@
 
-Prints the final _RMSEs Result Tibble_.
+Prints the _Final RMSEs Result Tibble_.
 
@@
 This function is a wrapper for the [RMSE_kable](#func.RMSE_kable) function described above, which is called internally to print the table, created from the final _RMSEs Result Tibble_ data.
+
+It is assumed that the  _Final RMSEs Result Tibble_ is previously constructed from the original _RMSEs Result Tibble_ using the [RMSEs.AddDiffColumn](#func.RMSEs.AddDiffColumn) function described above.
 

### 2025-11-02 reports/capstone-movielens.site/05.appendix.Rmd
RMSE.Total_kable function: hotfix.
Helper functions: refactoring.

@@
 
-#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) Function {#func.clamp}
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section are available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) script on _GitHub_.
+:::
+
+#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) Function {#func.clamp}
 \
@@
 
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) function is shown below:
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L504) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) script on _GitHub_.
-:::
-:::
-
-#### [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) Function {#func.msg.set_arg}
+The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) script on _GitHub_.
+:::
+:::
+
+#### [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) Function {#func.msg.set_arg}
 \
@@
 This function is a wrapper for the [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` function, which is called internally to replace all occurrences of the pattern (placeholder) specified by the [arg_name](#func.msg.set_arg.args.arg.name) argument (`%1` by default), in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.
-
 :::
@@
 The character vector returned by the internally called [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
-
 :::
@@
 
-The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) function is shown below:
+The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) function is defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) script on _GitHub_.
+The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) script on _GitHub_.
 :::
@@
 
-#### [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) Function {#func.msg.glue}
+#### [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) Function {#func.msg.glue}
 \
@@
 
-The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) function is shown below:
+The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#453) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) function is defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) script on _GitHub_.
+The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+The complete source code of the functions described in this section are available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) script on _GitHub_.
 :::
@@
 
-### Result RMSEs Table Functions
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+### Result RMSEs Tibble Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section are available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) script on _GitHub_.
 :::
@@
 ::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
-  - ***RMSEs:*** The final _RMSEs Result Tibble_ to print;
+  - ***RMSEs:*** The _Final RMSEs Result Tibble_ to print;
 
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
+The complete source code of the functions described in this section are available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
+The complete version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
 :::

### 2025-11-02 r/src/support-functions/OMR-model.functions.R

@@ -1,0 +1,9 @@
+# Overall Mean Rating Model ---------------------------------------------------
+naive_model_MSEs <- function(val) {
+  sapply(edx_CV, function(cv_item){
+    mse(cv_item$validation_set$rating - val)
+  })
+}
+naive_model_RMSE <- function(val){
+  sqrt(mean(naive_model_MSEs(val)))
+}

### 2025-11-02 r/src/support-functions/common-helper.functions.R

@@ -66,15 +66,6 @@ RMSE.Total_kable <- function(RMSEs,
 RSME.tibble.col_width <- function(x){
   "%1em" |> msg.glue(x)
 }
-## Overall Mean Rating Model ---------------------------------------------------
-naive_model_MSEs <- function(val) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - val)
-  })
-}
-naive_model_RMSE <- function(val){
-  sqrt(mean(naive_model_MSEs(val)))
-}
 ## Regularization --------------------------------------------------------------
 mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
   if (is.na(lambda)) {
@@ -87,7 +78,6 @@ mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
   N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
   sums/(N + lambda)
 }
-## Model Tuning ---------------------------------------------------------
 get_fine_tune.param.endpoints <- function(preset.result) {
 
   preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
@@ -103,8 +93,7 @@ get_fine_tune.param.endpoints <- function(preset.result) {
 get_fine_tune.param.endpoints.idx <- function(preset.result) {
   best_RMSE <- min(preset.result$RMSE)
   best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-  
+
   preset.result.N <- length(preset.result$RMSE)
   i <- best_RMSE.idx
   j <- i
@@ -234,9 +223,7 @@ model.tune.param_range <- function(loop_starter,
   if (interval_divisor < 4) {
     interval_divisor <- 4
   }
-  # max_interval_divisor <- loop_starter[4]
-  
-  
+
   best_RMSE <- NA
   param.best_value <- 0
   
@@ -257,8 +244,6 @@ Final best RMSE for `parameter value = %1`: %2",
                param_values.best_result["best_RMSE"])
       
       put(param_values.best_result)
-      # param.best_value   best_RMSE 
-      # -75.0000000   0.8578522  
       # browser()
       break
     }
@@ -306,9 +291,6 @@ Tuning data has been loaded from file: %1", file_path_tmp)
       
       tuned.result <- tuned_result$tuned.result
       
-      
-      #     put_log1("Function `model.tune.param_range`:
[…]

### 2025-11-04 reports/capstone-movielens.site/02-0.methods.Rmd
Data Helper functions: working...

@@
 ```
-
-#### `edx.mx` Matrix Object
-\
-
-We will use the array representation described in [Section 18.5 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook (New Edition)_, for the training data[@IDS2_18-5].
-For this purpose, we will convert the `edx` dataset into a matrix using the `tidyr::pivot_wider` function:
-
-```{r eval=FALSE}
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-
-```
-
-```{r}
-  str(edx.mx)
-```
-
-#### `edx.sgr` Object
-\
-
-To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-```
-```{r}
-str(edx.sgr)
-summary(edx.sgr)
-```
-
-Note that we use the `splitGenreRows` function to split rows of the original dataset:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The [source code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) of the function mentioned above is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
-
-#### `movie_map` Object
-\
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r eval=FALSE}
-movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-```
-
-```{r}
-str(movie_map)
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we cannot use them as IDs[@IDS2_25-1].
-
-#### `date_days_map` Object
-\
-
-We have a `timestamp` field in the `edx` dataset.
-To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-```
-``` {r}
-  str(date_days_map)
-  summary(date_days_map)
-```
-
-#### `edx_CV` Object
-\
-
-Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 31.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6]:
-```{r eval=FALSE}
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
-```
-```{r}
-str(edx_CV)
-```
-
-::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](#func.make_source_datasets) _function_ code described above.
-:::
-
-Note that we used the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function call to split the original dataset (`edx` in this case):
-```{r eval=FALSE}
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-```
-
-which returns a pair of train/validation sets:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets ----------------------------------------------------    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function is defined in the same script as the [make_source_datasets](#func.make_source_datasets), from which it is called.
-:::
-
-\newpage

### 2025-11-04 reports/capstone-movielens.site/05.appendix.Rmd
Data Helper functions: working...

@@
-# Appendix {#appndx_a}
+# Appendix A: Support Functions {#appndx_a}
 ## Common Helper Functions
@@
 ::: { #func.clamp.args.min .sidebar }
-  - **min:** Minimum allowed value;
+  - **min:** Minimum allowed value (0.5 by default);
 
@@
 ::: { #func.clamp.args.max .sidebar }
-  - **max:** Maximum allowed value;
+  - **max:** Maximum allowed value (5 by default);
 
@@
 \
-
-As explained in [Section  23.4 *User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
-For this reason, we need a function described in that section[@IDS2_23-4]:
-
-Therefore, in our project this function is used to clamp the computed movie rating values between 0.5 and 5.
-
+As explained in [Section 25.1 *Case study: recommendation systems / User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
+For this reason, we need a function described in that section[@IDS2_25-1]:
+
+This function is a wrapper for the [base::pmin](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/Extremes) and [base::pmax](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/Extremes) `R` functions, which are called internally to constrain the input value passed in the [r](#func.clamp.args.r) argument to be within the values passed in the [min](#func.clamp.args.min) and [max](#func.clamp.args.max) arguments, respectively.
+
+In our project this function is used to clamp the computed movie rating values between 0.5 and 5.
 :::
@@
 
-The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#453) function is shown below:
+The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) function is shown below:
 ```{r eval=FALSE}
@@
 
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
+### Initializing Input Datasets
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) script on _GitHub_.
+:::
+
+#### [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) Function {#func.make_source_datasets}
+\
+
+Creates the major input datasets used throughout the project.
+
+::: { #func.make_source_datasets.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+movielens_datasets <- make_source_datasets()
+
+```
+:::
+
+##### Details
+\
+
+This function produces datasets listed in the [Value](#func.make_source_datasets.value) section below and described in detail in [Appendix B: Model Training Datasets] using the `edx` as the original dataset.
+
+:::
+
+::: { #func.make_source_datasets.value .sidebar }
+##### Value
+\
+
+The list of the following datasets are returned to the client code:
+
+  - [`edx.mx` Matrix Object];
+
+  - [`edx.sgr` Object];
+
+  - [`movie_map` Object];
+
+  - [`date_days_map` Object];
+
+  - [`edx_CV` Object];
+
+:::
+
+::: { #func.make_source_datasets.code .sidebar }
+##### Source Code
+\
+
+The pseudocode of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is shown below:
+```{r eval=FALSE}
+make_source_datasets <- function(){
+
+    put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
+  edx.mx <- edx |> 
+    mutate(userId = factor(userId),
+           movieId = factor(movieId)) |>
+    select(movieId, userId, rating) |>
+    pivot_wider(names_from = movieId, values_from = rating) |>
+    column_to_rownames("userId") |>
+    as.matrix()
+
+  put_log("Function: `make_source_datasets`:
+Matrix created: `edx.mx` of the following dimentions:")
+  put(dim(edx.mx))
+
+  #> To be able to map movie IDs to titles we create the following lookup table:
+  movie_map <- edx |> select(movieId, title, genres) |> 
+    distinct(movieId, .keep_all = TRUE)
+
+  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
+
+  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
+  date_days_map <- edx |>
+    mutate(date_time = as_datetime(timestamp)) |>
+    mutate(date = as_date(date_time)) |>
+    mutate(year = year(date_time)) |>
+    mutate(days = as.integer(date - min(date))) |>
+    select(timestamp, date_time, date, year, days) |>
+    distinct(timestamp, .keep_all = TRUE)
+
+  str(date_days_map)
+  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
+
+  put_log("Function: `make_source_datasets`: 
+To account for the Movie Genre Effect, we need a dataset with split rows 
+for movies belonging to multiple genres.")
+  edx.sgr <- splitGenreRows(edx)
+
+  #> We will use K-fold cross validation as explained in 
+  #> Section 29.6.1: "K-fold validation" of the Cource Textbook:
+  #> https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation
+  edx_CV <- lapply(kfold_index, function(fold_i){...}
+
+  list(edx_CV = edx_CV,
+       edx.mx = edx.mx,
+       edx.sgr = edx.sgr,
+       tuning_sets = tuning_sets,
+       movie_map = movie_map,
+       date_days_map = date_days_map)
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is available in the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) script on _GitHub_.
+:::
 :::
@@
 
-##### Usage
+::: { #func.sample_train_validation_sets.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+split_sets <- data |>
+      sample_train_validation_sets(seed)
+```
+:::
+
+::: { #func.sample_train_validation_sets.args .sidebar }
+##### Arguments
+\
+
+::: { #func.sample_train_validation_sets.args.data .sidebar }
+  - **data:** ;
+
+:::
+::: { #func.sample_train_validation_sets.args.seed .sidebar }
+  - **seed:** ;
+
+:::
+:::
+
+::: { #func.sample_train_validation_sets.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.sample_train_validation_sets.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.sample_train_validation_sets.code .sidebar }
+##### Source Code
+\
+
+The source code of the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function is shown below:
+```{r eval=FALSE}
+sample_train_validation_sets <- function(data, seed){
+  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
+  set.seed(seed)
+  validation_ind <- 
+    sapply(splitByUser(data),
+           function(i) sample(i, ceiling(length(i)*.2))) |> 
+    unlist() |> 
+    sort()
+
+  put_log("Function: `sample_train_validation_sets`: 
+Extracting 80% of the original `data` not used for the Validation Set, 
+excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
+
+  train_set <- data[-validation_ind,]
+
+  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
+  put(summary(train_set))
+
+  put_log("Function: `sample_train_validation_sets`: 
+To make sure we don’t include movies in the Training Set that should not be there, 
+we exclude entries using the semi_join function from the Validation Set.")
+  tmp.data <- data[validation_ind,]
+
+  validation_set <- tmp.data |> 
+    semi_join(train_set, by = "movieId") |> 
+    semi_join(train_set, by = "userId") |>
+    as.data.frame()
+
+  # Add rows excluded from `validation_set` into `train_set`
+  tmp.excluded <- anti_join(tmp.data, validation_set)
+  train_set <- rbind(train_set, tmp.excluded)
+
+  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
+  put(summary(validation_set))
+
+  # CV train & test sets Consistency Test
+  validation.left_join.Nas <- train_set |>
+    mutate(tst.col = rating) |>
+    select(userId, movieId, tst.col) |>
+    data.consistency.test(validation_set)
+
+  put_log("Function: `sample_train_validation_sets`:
+Below are the data consistency verification results")
+  put(validation.left_join.Nas)
+
+  # Return result datassets    
+  list(train_set = train_set, 
+       validation_set = validation_set)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) script on _GitHub_.
+:::
+:::
 
@@
 \newpage
+
+## Model Training: Support Functions
+\
+
+### Overal Mean Rating (OMR) Model Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R) script on _GitHub_.
+:::
+
+#### [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) Function {#func.@@func}
+\
+
+::: { #func.@@func.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+@@func()
+
+```
+:::
+
+::: { #func.@@func.args .sidebar }
+##### Arguments
+\
+
+::: { #func.@@func.args. .sidebar }
+  - **x:** ;
+
+:::
+:::
+
+::: { #func.@@func.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.@@func.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.@@func.code .sidebar }
+##### Source Code
+\
+
+The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) script on _GitHub_.
+:::
+:::
+
+# Appendix B: Model Training Datasets {#appndx_b}
+\
+
+## `edx.mx` Matrix Object
+\
+
+We use the array representation described in [Section 18.5 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook (New Edition)_, for the training data[@IDS2_18-5].
+For this purpose, we will convert the `edx` dataset into a matrix using the `tidyr::pivot_wider` function:
+
+```{r eval=FALSE}
+
+  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
+  edx.mx <- edx |> 
+    mutate(userId = factor(userId),
+           movieId = factor(movieId)) |>
+    select(movieId, userId, rating) |>
+    pivot_wider(names_from = movieId, values_from = rating) |>
+    column_to_rownames("userId") |>
+    as.matrix()
+
+  put_log("Function: `make_source_datasets`:
+Matrix created: `edx.mx` of the following dimentions:")
+  put(dim(edx.mx))
+```
+
+```{r}
+  str(edx.mx)
+```
+
+## `edx.sgr` Object
+\
+
+To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
+```{r eval=FALSE}
+  put_log("Function: `make_source_datasets`: 
+To account for the Movie Genre Effect, we need a dataset with split rows 
+for movies belonging to multiple genres.")
+  edx.sgr <- splitGenreRows(edx)
+```
+```{r}
+str(edx.sgr)
+summary(edx.sgr)
+```
+
+Note that we use the `splitGenreRows` function to split rows of the original dataset:
+```{r eval=FALSE}
+splitGenreRows <- function(data){
+  put("Splitting dataset rows related to multiple genres...")
+  start <- put_start_date()
+  gs_splitted <- data |>
+    separate_rows(genres, sep = "\\|")
+  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
+  put_end_date(start)
+  gs_splitted
+}
+```
+
+::: {.noteblock data-latex=""}
+The [source code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) of the function mentioned above is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
+:::
+
+## `movie_map` Object
+\
+
+To be able to map movie IDs to titles we create the following lookup table:
+```{r eval=FALSE}
+movie_map <- edx |> select(movieId, title, genres) |> 
+    distinct(movieId, .keep_all = TRUE)
+
+  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
+```
+
+```{r}
+str(movie_map)
+summary(movie_map)
+```
+
+Note that titles cannot be considered unique, so we cannot use them as IDs[@IDS2_25-1].
+
+## `date_days_map` Object
+\
+
+We have a `timestamp` field in the `edx` dataset.
+To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
+```{r eval=FALSE}
+  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
+  date_days_map <- edx |>
+    mutate(date_time = as_datetime(timestamp)) |>
+    mutate(date = as_date(date_time)) |>
+    mutate(year = year(date_time)) |>
+    mutate(days = as.integer(date - min(date))) |>
+    select(timestamp, date_time, date, year, days) |>
+    distinct(timestamp, .keep_all = TRUE)
+
+  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
+```
+``` {r}
+  str(date_days_map)
+  summary(date_days_map)
+```
+
+## `edx_CV` Object
+\
+
+Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
+as explained in [Section 31.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6]:
+```{r eval=FALSE}
+  start <- put_start_date()
+  edx_CV <- lapply(kfold_index,  function(fold_i){
+
+    put_log1("Method `make_source_datasets`: 
+Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
+
+    #> We split the initial datasets into training sets, which we will use to build 
+    #> and train our models, and validation sets in which we will compute the accuracy 
+    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
+    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
+    #> of the Course Textbook.
+
+    split_sets <- edx |>
+      sample_train_validation_sets(fold_i*1000)
+
+    train_set <- split_sets$train_set
+    validation_set <- split_sets$validation_set
+
+    put_log("Function: `make_source_datasets`: 
+Sampling 20% from the split-row version of the `edx` dataset...")
+    split_sets.gs <- edx.sgr |>
+      sample_train_validation_sets(fold_i*2000)
+
+    train.sgr <- split_sets.gs$train_set
+    validation.sgr <- split_sets.gs$validation_set
+
+    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
+    # put(summary(validation.sgr))
+
+    #> We will use the array representation described in `Section 17.5 of the Textbook`
+    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
+    #> for the training data. 
+    #> To create this matrix, we use `tidyr::pivot_wider` function:
+
+    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
+    train_mx <- train_set |> 
+      mutate(userId = factor(userId),
+             movieId = factor(movieId)) |>
+      select(movieId, userId, rating) |>
+      pivot_wider(names_from = movieId, values_from = rating) |>
+      column_to_rownames("userId") |>
+      as.matrix()
+
+    put_log("Function: `make_source_datasets`:
+Matrix created: `train_mx` of the following dimentions:")
+    put(dim(train_mx))
+
+    list(train_set = train_set,
+         train_mx = train_mx,
+         train.sgr = train.sgr,
+         validation_set = validation_set)
+  })
+  put_end_date(start)
+  put_log("Function: `make_source_datasets`: 
+Set of K-Fold Cross Validation datasets created: edx_CV")
+```
+```{r}
+str(edx_CV)
+```
+
+::: {.noteblock data-latex=""}
+This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](#func.make_source_datasets) _function_ code described above.
+:::
+
+Note that we used the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function call to split the original dataset (`edx` in this case):
+```{r eval=FALSE}
+    split_sets <- edx |>
+      sample_train_validation_sets(fold_i*1000)
+```
+
+which returns a pair of train/validation sets:
+```{r eval=FALSE}
+sample_train_validation_sets <- function(data, seed){
+  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
+  set.seed(seed)
+  validation_ind <- 
+    sapply(splitByUser(data),
+           function(i) sample(i, ceiling(length(i)*.2))) |> 
+    unlist() |> 
+    sort()
+
+  put_log("Function: `sample_train_validation_sets`: 
+Extracting 80% of the original `data` not used for the Validation Set, 
+excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
+
+  train_set <- data[-validation_ind,]
+
+  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
+  put(summary(train_set))
+
+  put_log("Function: `sample_train_validation_sets`: 
+To make sure we don’t include movies in the Training Set that should not be there, 
+we exclude entries using the semi_join function from the Validation Set.")
+  tmp.data <- data[validation_ind,]
+
+  validation_set <- tmp.data |> 
+    semi_join(train_set, by = "movieId") |> 
+    semi_join(train_set, by = "userId") |>
+    as.data.frame()
+
+  # Add rows excluded from `validation_set` into `train_set`
+  tmp.excluded <- anti_join(tmp.data, validation_set)
+  train_set <- rbind(train_set, tmp.excluded)
+
+  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
+  put(summary(validation_set))
+
+  # CV train & test sets Consistency Test
+  validation.left_join.Nas <- train_set |>
+    mutate(tst.col = rating) |>
+    select(userId, movieId, tst.col) |>
+    data.consistency.test(validation_set)
+
+  put_log("Function: `sample_train_validation_sets`:
+Below are the data consistency verification results")
+  put(validation.left_join.Nas)
+
+  # Return result datassets ----------------------------------------------------    
+  list(train_set = train_set, 
+       validation_set = validation_set)
+}
+
+```
+
+::: {.noteblock data-latex=""}
+The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function is defined in the same script as the [make_source_datasets](#func.make_source_datasets), from which it is called.
+:::
+
+\newpage
+
+# End of Report -------------------------------------------------------------

### 2025-11-04 reports/capstone-movielens.site/work/func-descr.template.Rmd
Data Helper functions: working...

@@
 
-#### [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.dat-func.tmpl}
+## Data Helper Functions
+\
+#### [dat_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.dat_func.tmpl}
 \
 
-::: { #func.dat-func.tmpl.Usage .sidebar }
+::: { #func.dat_func.tmpl.Usage .sidebar }
 ##### Usage
@@
 ```{r eval=FALSE}
-dat-func.tmpl()
+dat_func.tmpl()
 
@@
 
-::: { #func.dat-func.tmpl.args .sidebar }
+::: { #func.dat_func.tmpl.args .sidebar }
 ##### Arguments
@@
 
-::: { #func.dat-func.tmpl.args. .sidebar }
+::: { #func.dat_func.tmpl.args. .sidebar }
   - **:** ;
@@
 :::
-::: { #func.dat-func.tmpl.args. .sidebar }
+::: { #func.dat_func.tmpl.args. .sidebar }
   - **:** ;
@@
 
-::: { #func.dat-func.tmpl.details .sidebar }
+::: { #func.dat_func.tmpl.details .sidebar }
 ##### Details
@@
 
-::: { #func.dat-func.tmpl.value .sidebar }
+::: { #func.dat_func.tmpl.value .sidebar }
 ##### Value
@@
 
-::: { #func.dat-func.tmpl.code .sidebar }
+::: { #func.dat_func.tmpl.code .sidebar }
 ##### Source Code
@@
 
-The source code of the [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is shown below:
+The source code of the [dat_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) script on _GitHub_.
+The source code of the [dat_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) script on _GitHub_.
+:::
+:::
+
+### Data processing function
+\
+
+#### [datproc_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.datproc_func.tmpl}
+\
+
+::: { #func.datproc_func.tmpl.Usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.datproc_func.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.datproc_func.tmpl.args.data .sidebar }
+  - **data:** ;
+
+:::
+::: { #func.datproc_func.tmpl.args.seed .sidebar }
+  - **seed:** ;
+
+:::
+:::
+
+::: { #func.datproc_func.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.datproc_func.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.datproc_func.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [datproc_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [datproc_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) script on _GitHub_.
 :::

### 2025-11-04 r/src/support-functions/data.helper.functions.R

@@ -85,7 +85,7 @@ filter_noMore_nratings <- function(data, nratings){
     filter(n() > nratings) |>
     ungroup()  
 }
-## Initialize input datasets ---------------------------------------------------
+## Initializing input datasets ---------------------------------------------------
 make_source_datasets <- function(){
   put_log("Function: `make_source_datasets`: Creating source datasets...")
   

### 2025-11-04 r/src/support-functions/data.helper.functions.R
Appendix A: [Initializing Input Datasets] section described.

@@ -220,6 +220,7 @@ Unzipping MovieLens data file from zip-archive: {movielens_datasets_zip}...")
     
     start <- put_start_date()
     unzip(movielens_datasets_zip, movielens_datasets_file_path)
+    put_end_date(start)
     
     if(!file.exists(movielens_datasets_file_path)) {
       put_log("Method `init_source_datasets`: 
@@ -268,16 +269,6 @@ Failed to zip file: {movielens_datasets_file_path}.")
       } else {
         put_log("Method `init_source_datasets`: 
 Zip-archive created: {movielens_datasets_zip}.")
-        #file.remove(movielens_datasets_file)
-        
-        if(file.exists(movielens_datasets_file_path)){
-          put_log("Method `init_source_datasets`: 
-Failed to remove file: {movielens_datasets_file_path}.")
-          warning("Failed to remove MovieLens data file.")
-        } else {
-          put_log("Method `init_source_datasets`: 
-File has been removed: {movielens_datasets_file_path}")
-        }
       }
     }
   }

### 2025-11-04 reports/capstone-movielens.site/05.appendix.Rmd

@@
 
-::: { #func.open_logfile.Usage .sidebar }
+::: { #func.open_logfile.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.print_start_date.Usage .sidebar }
+::: { #func.print_start_date.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.put_start_date.Usage .sidebar }
+::: { #func.put_start_date.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.print_end_date.Usage .sidebar }
+::: { #func.print_end_date.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.put_end_date.Usage .sidebar }
+::: { #func.put_end_date.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.print_log.Usage .sidebar }
+::: { #func.print_log.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.put_log.Usage .sidebar }
+::: { #func.put_log.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.get_log1.Usage .sidebar }
+::: { #func.get_log1.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.print_log1.Usage .sidebar }
+::: { #func.print_log1.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.put_log1.Usage .sidebar }
+::: { #func.put_log1.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.get_log2.Usage .sidebar }
+::: { #func.get_log2.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.print_log2.Usage .sidebar }
+::: { #func.print_log2.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.put_log2.Usage .sidebar }
+::: { #func.put_log2.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.get_log3.Usage .sidebar }
+::: { #func.get_log3.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.print_log3.Usage .sidebar }
+::: { #func.print_log3.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.put_log3.Usage .sidebar }
+::: { #func.put_log3.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.get_log4.Usage .sidebar }
+::: { #func.get_log4.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.print_log4.Usage .sidebar }
+::: { #func.print_log4.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.put_log4.Usage .sidebar }
+::: { #func.put_log4.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.clamp.Usage .sidebar }
+::: { #func.clamp.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.msg.set_arg.Usage .sidebar }
+::: { #func.msg.set_arg.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.msg.glue.Usage .sidebar }
+::: { #func.msg.glue.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.mse.Usage .sidebar }
+::: { #func.mse.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.mse_cv.Usage .sidebar }
+::: { #func.mse_cv.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.rmse.Usage .sidebar }
+::: { #func.rmse.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.rmse2.Usage .sidebar }
+::: { #func.rmse2.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.make_source_datasets.Usage .sidebar }
+::: { #func.make_source_datasets.usage .sidebar }
 ##### Usage
@@
 
-##### Details
-\
-
-This function produces datasets listed in the [Value](#func.make_source_datasets.value) section below and described in detail in [Appendix B: Model Training Datasets] using the `edx` as the original dataset.
-
+::: { #func.make_source_datasets.details .sidebar }
+##### Details
+\
+
+This function produces datasets listed in the [Value](#func.make_source_datasets.value) section below and described in detail in [Appendix B: Models Training Datasets] using the `edx` as the original dataset.
+
+::: {.noteblock data-latex=""}
+The function calls internally the following functions described below:
+
+  - [splitGenreRows](#) to create the [`edx.sgr` Object];
+  - [sample_train_validation_sets](#) to create *train* and *validation* sets of the inner datasets of the [`edx_CV` Object].
+
+:::
 :::
@@
 
-The pseudocode of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is shown below:
+The source code of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is shown below:
 ```{r eval=FALSE}
 make_source_datasets <- function(){
+  put_log("Function: `make_source_datasets`: Creating source datasets...")
 
@@
   put_log("Function: `make_source_datasets`: Dataset created: movie_map")
+  put(summary(movie_map))
 
@@
   put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
+  put(summary(date_days_map))
 
@@
   #> https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation
-  edx_CV <- lapply(kfold_index, function(fold_i){...}
+  #> We are going to compute the following version of the MSE introducing in that section:
+
+  # $$
+  #   \mbox{MSE}(\lambda) \approx\frac{1}{B} \sum_{b = 1}^B \frac{1}{N}\sum_{i = 1}^N \left(\hat{y}_i^b(\lambda) - y_i^b\right)^2 
+  # $$
+
+  start <- put_start_date()
+  edx_CV <- lapply(kfold_index,  function(fold_i){
+
+    put_log1("Method `make_source_datasets`: 
+Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
+
+    #> We split the initial datasets into training sets, which we will use to build 
+    #> and train our models, and validation sets in which we will compute the accuracy 
+    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
+    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
+    #> of the Course Textbook.
+
+    split_sets <- edx |>
+      sample_train_validation_sets(fold_i*1000)
+
+    train_set <- split_sets$train_set
+    validation_set <- split_sets$validation_set
+
+    put_log("Function: `make_source_datasets`: 
+Sampling 20% from the split-row version of the `edx` dataset...")
+    split_sets.gs <- edx.sgr |>
+      sample_train_validation_sets(fold_i*2000)
+
+    train.sgr <- split_sets.gs$train_set
+    validation.sgr <- split_sets.gs$validation_set
+
+    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
+    # put(summary(validation.sgr))
+
+    #> We will use the array representation described in `Section 17.5 of the Textbook`
+    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
+    #> for the training data. 
+    #> To create this matrix, we use `tidyr::pivot_wider` function:
+
+    # train_set <- mutate(train_set, userId = factor(userId), movieId = factor(movieId))
+    # train.sgr <- mutate(train.sgr, userId = factor(userId), movieId = factor(movieId))
+
+    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
+    train_mx <- train_set |> 
+      mutate(userId = factor(userId),
+             movieId = factor(movieId)) |>
+      select(movieId, userId, rating) |>
+      pivot_wider(names_from = movieId, values_from = rating) |>
+      column_to_rownames("userId") |>
+      as.matrix()
+
+    put_log("Function: `make_source_datasets`:
+Matrix created: `train_mx` of the following dimentions:")
+    put(dim(train_mx))
+
+    list(train_set = train_set,
+         train_mx = train_mx,
+         train.sgr = train.sgr,
+         validation_set = validation_set)
+  })
+  put_end_date(start)
+  put_log("Function: `make_source_datasets`: 
+Set of K-Fold Cross Validation datasets created: edx_CV")
+
+  tuning_sets <- edx |>
+    sample_train_validation_sets(5423)
 
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is available in the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) script on _GitHub_.
+The source code of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is also available in the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) script on _GitHub_.
+:::
+:::
+
+#### [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) Function {#func.init_source_datasets}
+\
+
+Creates the major input datasets used throughout the project.
+
+::: { #func.init_source_datasets.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+movielens_datasets <- init_source_datasets()
+
+```
+:::
+
+##### Details
+\
+
+This function produces datasets listed in the [Value](#func.init_source_datasets.value) section below and described in detail in [Appendix B: Models Training Datasets] using the `edx` as the original dataset.
+
+:::
+
+::: { #func.init_source_datasets.value .sidebar }
+##### Value
+\
+
+The list of the following datasets are returned to the client code:
+
+  - [`edx.mx` Matrix Object];
+
+  - [`edx.sgr` Object];
+
+  - [`movie_map` Object];
+
+  - [`date_days_map` Object];
+
+  - [`edx_CV` Object];
+
+:::
+
+::: { #func.init_source_datasets.code .sidebar }
+##### Source Code
+\
+
+The simplified source code of the [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is shown below:
+```{r eval=FALSE}
+init_source_datasets <- function(){
+  put_log("Method `init_source_datasets`: 
+Initializing sourse datasets...")
+
+  if(file.exists(movielens_datasets_file_path)){
+    movielens_datasets <- load_movielens_data_from_file(movielens_datasets_file_path)
+  } else if(file.exists(movielens_datasets_zip)) {
+    put_log("Method `init_source_datasets`: 
+Unzipping MovieLens data file from zip-archive: {movielens_datasets_zip}...")
+
+    unzip(movielens_datasets_zip, movielens_datasets_file_path)
+
+    if(!file.exists(movielens_datasets_file_path)) {
+      put_log("Method `init_source_datasets`: 
+File does not exists: {movielens_datasets_file}.")
+      stop("Failed to unzip MovieLens data zip-archive.")
+    }
+
+    movielens_datasets <- load_movielens_data_from_file(movielens_datasets_file_path)
+  } else {
+    put_log("Method `init_source_datasets`: 
+Creating datasets...")
+    library(edx.capstone.movielens.data)
+    put_log("Method `init_source_datasets`: 
+Library attached: 'edx.capstone.movielens.data'")
+
+    movielens_datasets <- make_source_datasets()
+    put("Method `init_source_datasets`: 
+All required datasets have been created.")
+
+    put_log("Method `init_source_datasets`: 
+Saving newly created input datasets to file...")
+    save(movielens_datasets, file =  movielens_datasets_file_path)
+
+    if(!file.exists(movielens_datasets_file_path)) {
+      put_log("Method `init_source_datasets`: 
+File was not created: {movielens_datasets_file}.")
+      warning("MovieLens data was not saved to file.")
+    } else {
+      put_log("Method `init_source_datasets`: 
+Datasets have been saved to file: {movielens_datasets_file_path}.")
+
+      put_log("Method `init_source_datasets`: 
+Creating zip-archive: {movielens_datasets_zip}...")
+
+      zip(movielens_datasets_zip, movielens_datasets_file_path)
+
+      if(!file.exists(movielens_datasets_zip)){
+        put_log("Method `init_source_datasets`: 
+Failed to zip file: {movielens_datasets_file_path}.")
+        warning("Failed to zip MovieLens data file.")
+      } else {
+        put_log("Method `init_source_datasets`: 
+Zip-archive created: {movielens_datasets_zip}.")
+      }
+    }
+  }
+  movielens_datasets
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is available in the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) script on _GitHub_.
 :::
@@
 
+#### [load_movielens_data_from_file](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L4) Function {#func.load_movielens_data_from_file}
+\
+
+::: { #func.load_movielens_data_from_file.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.load_movielens_data_from_file.args .sidebar }
+##### Arguments
+\
+
+:::
+::: { #func.load_movielens_data_from_file.args.seed .sidebar }
+  - **file_path:** Data file full path.
+
+:::
+:::
+
+::: { #func.load_movielens_data_from_file.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.load_movielens_data_from_file.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.load_movielens_data_from_file.code .sidebar }
+##### Source Code
+\
+
+The source code of the [load_movielens_data_from_file](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L4) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [load_movielens_data_from_file](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L4) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L4) script on _GitHub_.
+:::
+:::
+
+#### [splitByUser](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L14) Function {#func.splitByUser}
+\
+
+::: { #func.splitByUser.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.splitByUser.args .sidebar }
+##### Arguments
+\
+
+::: { #func.splitByUser.args.data .sidebar }
+  - **data:** ;
+
+:::
+:::
+
+::: { #func.splitByUser.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.splitByUser.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.splitByUser.code .sidebar }
+##### Source Code
+\
+
+The source code of the [splitByUser](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L14) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [splitByUser](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L14) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L14) script on _GitHub_.
+:::
+:::
+
 #### [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) Function {#func.sample_train_validation_sets}
@@
 
-::: { #func.sample_train_validation_sets.Usage .sidebar }
+Splits the input dataset passed in the [data](#func.sample_train_validation_sets.args.data) argument into *train* and *validation* datasets in the way described in [Section 31.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
+
+::: { #func.sample_train_validation_sets.usage .sidebar }
 ##### Usage
@@
 ::: { #func.sample_train_validation_sets.args.data .sidebar }
-  - **data:** ;
+  - **data:** Input dataset to split;
 
@@
 ::: { #func.sample_train_validation_sets.args.seed .sidebar }
-  - **seed:** ;
+  - **seed:** Seed value;
 
@@
 
-### Model Training Functions
+#### [mutateDateTimeAndDays](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L66) Function {#func.mutateDateTimeAndDays}
+\
+
+::: { #func.mutateDateTimeAndDays.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.mutateDateTimeAndDays.args .sidebar }
+##### Arguments
+\
+
+::: { #func.mutateDateTimeAndDays.args.data .sidebar }
+  - **data:** ;
+
+:::
+:::
+
+::: { #func.mutateDateTimeAndDays.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.mutateDateTimeAndDays.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.mutateDateTimeAndDays.code .sidebar }
+##### Source Code
+\
+
+The source code of the [mutateDateTimeAndDays](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L66) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mutateDateTimeAndDays](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L66) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L66) script on _GitHub_.
+:::
+:::
+
+#### [splitGenreRows](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) Function {#func.splitGenreRows}
+\
+Splits rows of the original dataset passed in the [data](#) argument for movies that belong to multiple genres.
+
+::: { #func.splitGenreRows.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+dat.sgr <- splitGenreRows(data)
+```
+:::
+
+::: { #func.splitGenreRows.args .sidebar }
+##### Arguments
+\
+
+::: { #func.splitGenreRows.args.data .sidebar }
+  - **data:** A dataset containing rows corresponding to movies that belong to multiple genres..
+
+:::
+:::
+
+::: { #func.splitGenreRows.details .sidebar }
+##### Details
+\
+
+This function is used internally in the [make_source_datasets](#func.make_source_datasets) function described above in the [Initializing Input Datasets] section to create the `edx.sgr` dataset described below in the [`edx.sgr` Object] section of the [Appendix B: Models Training Datasets].
+
+:::
+
+::: { #func.splitGenreRows.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.splitGenreRows.code .sidebar }
+##### Source Code
+\
+
+The source code of the [splitGenreRows](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [splitGenreRows](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) script on _GitHub_.
+:::
+:::
+
+#### [filter_noMore_nratings](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L82) Function {#func.filter_noMore_nratings}
+\
+
+::: { #func.filter_noMore_nratings.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.filter_noMore_nratings.args .sidebar }
+##### Arguments
+\
+
+::: { #func.filter_noMore_nratings.args.data .sidebar }
+  - **data:** ;
+
+:::
+::: { #func.filter_noMore_nratings.args.seed .sidebar }
+  - **seed:** ;
+
+:::
+:::
+
+::: { #func.filter_noMore_nratings.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.filter_noMore_nratings.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.filter_noMore_nratings.code .sidebar }
+##### Source Code
+\
+
+The source code of the [filter_noMore_nratings](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L82) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [filter_noMore_nratings](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L82) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L82) script on _GitHub_.
+:::
+:::
+
+### Models Training Functions
 
@@
 
-::: { #func.union_cv_results.Usage .sidebar }
+::: { #func.union_cv_results.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.get_best_param.result.Usage .sidebar }
+::: { #func.get_best_param.result.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.data.plot.Usage .sidebar }
+::: { #func.data.plot.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.data.plot.left.n.Usage .sidebar }
+::: { #func.data.plot.left.n.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.data.plot.left_detailed.Usage .sidebar }
+::: { #func.data.plot.left_detailed.usage .sidebar }
 ##### Usage
@@
 
-## Model Training: Support Functions
+## Models Training: Support Functions
 \
@@
 
-::: { #func.@@func.Usage .sidebar }
+::: { #func.@@func.usage .sidebar }
 ##### Usage
@@
 
-# Appendix B: Model Training Datasets {#appndx_b}
+# Appendix B: Models Training Datasets {#appndx_b}
 \
@@
 
-Note that we use the `splitGenreRows` function to split rows of the original dataset:
+Note that we use the [splitGenreRows](#func.splitGenreRows) function described above to split rows of the original dataset:
 ```{r eval=FALSE}

### 2025-11-04 reports/capstone-movielens.site/work/func-descr.template.Rmd

@@
 
-::: { #func.log_func_tmpl.Usage .sidebar }
+::: { #func.log_func_tmpl.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.helper-func.tmpl.Usage .sidebar }
+::: { #func.helper-func.tmpl.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.dat_func.tmpl.Usage .sidebar }
+::: { #func.dat_func.tmpl.usage .sidebar }
 ##### Usage
@@
 
-::: { #func.dat_func.tmpl.args. .sidebar }
-  - **:** ;
+::: { #func.dat_func.tmpl.args.data .sidebar }
+  - **data:** ;
 
@@
 
-::: { #func.datproc_func.tmpl.Usage .sidebar }
+::: { #func.datproc_func.tmpl.usage .sidebar }
 ##### Usage

### 2025-11-05 reports/capstone-movielens.site/02-0.methods.Rmd
Capstone Report: `Preparing train and set datasets` section completed.

@@
 We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 25.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_25-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 31.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
-To prepare datasets for processing, we will use the following functions, specifically designed for these operations:
+To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of the [Appendix A: Support Functions]), specifically designed for these operations:
+
+  - [make_source_datasets](#func.make_source_datasets)
 
@@
 
-  - [make_source_datasets](#func.make_source_datasets)
+As a result of executing these functions, we will obtain the following datasets (detailed in [Appendix B: Models Training Datasets]), which we will use throughout the project:
 
-::: {.noteblock data-latex=""}
-The full source code of the function listed above is available in the [Initialize input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
+  - [`edx.mx` Matrix Object];
 
-### [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L211) Function {#func.init_source_datasets}
+  - [`edx.sgr` Object];
 
-The _init_source_datasets_ function checks whether the required source datasets are cached on the hard disk, and, if so, loads the datasets from the cache file.
+  - [`movie_map` Object];
 
-Otherwise, it calls the [make_source_datasets](#func.make_source_datasets) function, which creates all the necessary datasets.
+  - [`date_days_map` Object];
 
-Finally, it stores the data into a cache file on the disk.
-
-The simplified version of the function's source code is shown below:
-
-```{r eval=FALSE}
-init_source_datasets <- function(){
-  put_log("Method `init_source_datasets`: 
-Initializing sourse datasets...")
-
-  if(file.exists(movielens_datasets_file_path)){
-    movielens_datasets <- load_movielens_data_from_file(movielens_datasets_file_path)
-  } else if(file.exists(movielens_datasets_zip)) {
-    put_log("Method `init_source_datasets`: 
-Unzipping MovieLens data file from zip-archive: {movielens_datasets_zip}...")
-
-    unzip(movielens_datasets_zip, movielens_datasets_file_path)
-
-    if(!file.exists(movielens_datasets_file_path)) {
-      put_log("Method `init_source_datasets`: 
-File does not exists: {movielens_datasets_file}.")
-      stop("Failed to unzip MovieLens data zip-archive.")
-    }
-
-    movielens_datasets <- load_movielens_data_from_file(movielens_datasets_file_path)
-  } else {
-    put_log("Method `init_source_datasets`: 
-Creating datasets...")
-    library(edx.capstone.movielens.data)
-    put_log("Method `init_source_datasets`: 
-Library attached: 'edx.capstone.movielens.data'")
-
-    movielens_datasets <- make_source_datasets()
-    put("Method `init_source_datasets`: 
-All required datasets have been created.")
-
-    put_log("Method `init_source_datasets`: 
-Saving newly created input datasets to file...")
-    save(movielens_datasets, file =  movielens_datasets_file_path)
-
-    if(!file.exists(movielens_datasets_file_path)) {
-      put_log("Method `init_source_datasets`: 
-File was not created: {movielens_datasets_file}.")
-      warning("MovieLens data was not saved to file.")
-    } else {
-      put_log("Method `init_source_datasets`: 
-Datasets have been saved to file: {movielens_datasets_file_path}.")
-
-      put_log("Method `init_source_datasets`: 
-Creating zip-archive: {movielens_datasets_zip}...") 
-      zip(movielens_datasets_zip, movielens_datasets_file_path)
-    # ...
-    }
-  }
-  movielens_datasets
-}
-```
-
-### [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) Function {#func.make_source_datasets}
-
-Let's take a closer look at the objects we will receive as a result of executing this function.
-
-```{r eval=FALSE}
-make_source_datasets <- function(){
-  # ...
-  list(edx_CV = edx_CV,
-       edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
-       tuning_sets = tuning_sets,
-       movie_map = movie_map,
-       date_days_map = date_days_map)
-}
-```
+  - [`edx_CV` Object].

### 2025-11-05 reports/capstone-movielens.site/05.appendix.Rmd
Capstone Report: `Preparing train and set datasets` section completed.

@@
 
-  - [`edx_CV` Object];
+  - [`edx_CV` Object].
 
@@
 
-#### [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) Function {#func.init_source_datasets}
+#### [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L211) Function {#func.init_source_datasets}
 \
@@
 
-This function produces datasets listed in the [Value](#func.init_source_datasets.value) section below and described in detail in [Appendix B: Models Training Datasets] using the `edx` as the original dataset.
+The function checks whether the required source datasets are cached on the hard disk and, if so, loads them from the cache file.
+
+Otherwise, it calls the [make_source_datasets](#func.make_source_datasets) function, which creates all the necessary datasets using the `edx` as the original dataset.
 
@@
 
-The list of the following datasets are returned to the client code:
+The list of the following datasets (described in detail in [Appendix B: Models Training Datasets]) is returned to the client code:
 
@@
 
-The simplified source code of the [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is shown below:
+The simplified source code of the [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L211) function is shown below:
 ```{r eval=FALSE}
@@
 
-      if(!file.exists(movielens_datasets_zip)){
-        put_log("Method `init_source_datasets`: 
-Failed to zip file: {movielens_datasets_file_path}.")
-        warning("Failed to zip MovieLens data file.")
-      } else {
       put_log("Method `init_source_datasets`: 
@@
   }
-  }
   movielens_datasets
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is available in the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) script on _GitHub_.
+The complete source code of the [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L211) function is available in the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L211) script on _GitHub_.
 :::

### 2025-11-05 reports/capstone-movielens.site/05.appendix.Rmd
Appendix B: Models Training Datasets: move to a new page.
Appendix B, "`edx.sgr` Object" section updated.

@@
 
+\newpage
+
 # Appendix B: Models Training Datasets {#appndx_b}
@@
 We use the array representation described in [Section 18.5 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook (New Edition)_, for the training data[@IDS2_18-5].
-For this purpose, we will convert the `edx` dataset into a matrix using the `tidyr::pivot_wider` function:
+For this purpose, we will convert the `edx` dataset into a matrix using the [tidyr::pivot_wider](https://www.rdocumentation.org/packages/tidyr/versions/1.3.0/topics/pivot_wider) function:
 
@@
 ```
+
+::: {.noteblock data-latex=""}
+We use the [splitGenreRows](#func.splitGenreRows) function (described in the [Data Processing Functions] section of the [Appendix A: Support Function]) to split rows of the original dataset.
+:::
+
 ```{r}
@@
 ```
-
-Note that we use the [splitGenreRows](#func.splitGenreRows) function described above to split rows of the original dataset:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The [source code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) of the function mentioned above is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
-:::
 

### 2025-11-05 reports/capstone-movielens.site/05.appendix.Rmd
Capstone Report: Appendix B: Models Training Datasets updated.

@@
 
+::: {.noteblock data-latex=""}
+To create the `edx.mx` object, the above code snippet is used in the [make_source_datasets](#func.make_source_datasets) function described in the [Initializing Input Datasets] section of [Appendix A: Support Functions].
+:::
+
 ```{r}
@@
 ::: {.noteblock data-latex=""}
-We use the [splitGenreRows](#func.splitGenreRows) function (described in the [Data Processing Functions] section of the [Appendix A: Support Function]) to split rows of the original dataset.
+To create the `edx.sgr` object, the above code snippet is used in the [make_source_datasets](#func.make_source_datasets) function described in the [Initializing Input Datasets] section of [Appendix A: Support Functions].
+
+The custom function [splitGenreRows](#func.splitGenreRows) used in the code snippet to split the rows of the original dataset (`edx` in this case) is described in the [Data Processing Functions] section of [Appendix A: Support Functions].
 :::
@@
 ```
+
+::: {.noteblock data-latex=""}
+To create the `movie_map` object, the above code snippet is used in the [make_source_datasets](#func.make_source_datasets) function described in the [Initializing Input Datasets] section of [Appendix A: Support Functions].
+:::
 
@@
 ```
+
+::: {.noteblock data-latex=""}
+To create the `date_days_map` object, the above code snippet is used in the [make_source_datasets](#func.make_source_datasets) function described in the [Initializing Input Datasets] section of [Appendix A: Support Functions].
+:::
+
 ``` {r}
@@
 ```
+
+::: {.noteblock data-latex=""}
+To create the `edx_CV` object, the above code snippet is used in the [make_source_datasets](#func.make_source_datasets) function described in the [Initializing Input Datasets] section of [Appendix A: Support Functions].
+
+The custom function [sample_train_validation_sets](#func.sample_train_validation_sets) used in the code snippet to split the original dataset (`edx` in this case) into *train* and *validation* datasets, is described in the [Data Processing Functions] section of [Appendix A: Support Functions].
+:::
+
 ```{r}
@@
 
-::: {.noteblock data-latex=""}
-This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](#func.make_source_datasets) _function_ code described above.
-:::
-
-Note that we used the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function call to split the original dataset (`edx` in this case):
-```{r eval=FALSE}
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-```
-
-which returns a pair of train/validation sets:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets ----------------------------------------------------    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function is defined in the same script as the [make_source_datasets](#func.make_source_datasets), from which it is called.
-:::
-
 \newpage
@@
 # End of Report -------------------------------------------------------------
+v

### 2025-11-06 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Capstone Report: `Overall Mean Rating (OMR) Model` sectioni updated.

@@
 
-If we predict all unknown ratings with $\hat{\mu}$, we obtain the following RMSE: 
+If we predict all unknown ratings with $\hat{\mu}$, we can obtain RMSE as follows:: 
 ```{r}
@@
 ::: {.noteblock data-latex=""}
-For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+
+The following custom functions described in [Appendix A: Support Functions] of *this Report*, are used in the code snippets above:
+
+  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [Overall Mean Rating (OMR) Model Helper Functions]) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method;
+
+  - [data.plot](#func.data.plot) (described in section [Data Visualization Functions]) for the _Mean Squared Errors_ data visualization.
+
 :::
 
-Here we also used [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L89) function defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L89) script (already mentioned above) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method:
-
-```{r eval=FALSE }
-naive_model_MSEs <- function(val) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - val)
-  })
-}
-```
-
-One more function, defined in the [same script](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L94), that we will need for further analysis of the current model, is the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L94) one:
-```{r eval=FALSE }
-naive_model_RMSE <- function(val){
-  sqrt(mean(naive_model_MSEs(val)))
-}
-```
 \newpage
@@
 
-If we plug in any other number, we will get a higher RMSE. Let's prove that by the following small investigation:
+If we plug in any other number, we will get a higher *RMSE*. Let's prove that by the following small investigation:
 ```{r }
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom function [naive_model_RMSE](#func.naive_model_RMSE) described in the [Overall Mean Rating (OMR) Model Helper Functions] section of [Appendix A: Support Functions] to calculate *RMSEs* for the sequence of the deviation values.
+:::
 
@@
 ```
+
+::: {.noteblock data-latex=""}
+To print the log, we use the custom function [print_log1](#func.print_log1) described in the [Logging Functions] section of [Appendix A: Support Functions].
+:::
+
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) custom functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
 :::

### 2025-11-06 reports/capstone-movielens.site/05.appendix.Rmd
Capstone Report: `Overall Mean Rating (OMR) Model` sectioni updated.

@@
 
-### Overal Mean Rating (OMR) Model Functions
+### Overall Mean Rating (OMR) Model Helper Functions
 \
@@
 
-#### [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) Function {#func.@@func}
-\
-
-::: { #func.@@func.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-@@func()
-
-```
-:::
-
-::: { #func.@@func.args .sidebar }
-##### Arguments
-\
-
-::: { #func.@@func.args. .sidebar }
-  - **x:** ;
-
-:::
-:::
-
-::: { #func.@@func.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.@@func.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.@@func.code .sidebar }
-##### Source Code
-\
-
-The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) script on _GitHub_.
+#### [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) Function {#func.naive_model_MSEs}
+\
+
+Calculates the Mean Squared Errors (MSEs) for the *Overall Mean Rating (OMR) Model* using the *K-Fold Cross Validation* method as described in section [OMR Model Building] of *this Report*.
+
+::: { #func.naive_model_MSEs.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+mu <- mean(edx$rating)
+mu.MSEs <- naive_model_MSEs(mu)
+
+```
+:::
+
+::: { #func.naive_model_MSEs.args .sidebar }
+##### Arguments
+\
+
+::: { #func.naive_model_MSEs.args. .sidebar }
+  - **mu:** The overall mean rating value.
+
+:::
+:::
+
+::: { #func.naive_model_MSEs.value .sidebar }
+##### Value
+\
+
+The Mean Squared Errors (MSEs) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*.
+:::
+
+::: { #func.naive_model_MSEs.code .sidebar }
+##### Source Code
+\
+
+The source code of the [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) function is shown below:
+```{r eval=FALSE}
+naive_model_MSEs <- function(mu) {
+  sapply(edx_CV, function(cv_item){
+    mse(cv_item$validation_set$rating - mu)
+  })
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L2) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) Function {#func.naive_model_RMSE}
+\
+Calculates the Root Mean Squared Error (RMSE) for the *Overall Mean Rating (OMR) Model* using the *K-Fold Cross Validation* method as described in section [OMR Model Building] of *this Report*.
+
+::: { #func.naive_model_RMSE.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+mu <- mean(edx$rating)
+mu.RMSE <- naive_model_RMSE(mu)
+```
+:::
+
+::: { #func.naive_model_RMSE.args .sidebar }
+##### Arguments
+\
+
+::: { #func.naive_model_RMSE.args. .sidebar }
+  - **mu:** The overall mean rating value.
+
+:::
+:::
+
+::: { #func.naive_model_RMSE.details .sidebar }
+##### Details
+\
+
+This function internally calls the [naive_model_MSEs](#func.naive_model_MSEs) function described above.
+:::
+
+::: { #func.naive_model_RMSE.value .sidebar }
+##### Value
+\
+
+The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*.
+:::
+
+::: { #func.naive_model_RMSE.code .sidebar }
+##### Source Code
+\
+
+The source code of the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) function is shown below:
+```{r eval=FALSE}
+naive_model_RMSE <- function(mu){
+  sqrt(mean(naive_model_MSEs(mu)))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L7) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) script on _GitHub_.
 :::
@@
 
+\newpage
+
 ## `edx.sgr` Object
@@
 
+\newpage
+
 ## `movie_map` Object
@@
 Note that titles cannot be considered unique, so we cannot use them as IDs[@IDS2_25-1].
+
+\newpage
 
@@
 
+\newpage
+
 ## `edx_CV` Object
@@
 \newpage
-
-# End of Report -------------------------------------------------------------
-v

### 2025-11-06 reports/capstone-movielens.site/work/func-descr.template.Rmd
Capstone Report: `Overall Mean Rating (OMR) Model` sectioni updated.

@@
 
+### Overal Mean Rating (OMR) Model Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R) script on _GitHub_.
+:::
+
+#### [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) Function {#func.OMR_model_func.tmpl}
+\
+
+::: { #func.OMR_model_func.tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+OMR_model_func.tmpl()
+
+```
+:::
+
+::: { #func.OMR_model_func.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.OMR_model_func.tmpl.args. .sidebar }
+  - **x:** ;
+
+:::
+:::
+
+::: { #func.OMR_model_func.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.OMR_model_func.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.OMR_model_func.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) script on _GitHub_.
+:::
+:::
+
+\newpage
+
 #### [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) Function {#func.@@func}

### 2025-11-06 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Capstone Report: `Overall Mean Rating (OMR) Model` section completed..

@@
 
-Let's begin our analysis by evaluating the simplest model described in [Section 25.1 *Case study: recommendation systems / A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook*[@IDS2_25-1], and then gradually refine it through further research.
+Let's begin our analysis by evaluating the simplest model described in [Section 25.1 *Case study: recommendation systems / A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook (New Edition)*[@IDS2_25-1], and then gradually refine it through further research.
 

### 2025-11-06 reports/capstone-movielens.site/work/draft-snippert.Rmd

@@
 
-#### [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) Function {#func.open_logfile}
-\
-
-A function to initialize the log file.
-
-::: { #func.open_logfile.Usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-open_logfile(file_name)
-```
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom function [@fn](#func.@fn) described in the [sec_name] section of [Appendix A: Support Functions].
 :::
-
-::: { #func.open_logfile.args .sidebar }
-##### Arguments
-\
-
-::: { #func.open_logfile.args.r .sidebar }
-  - **file_name:** A name used as a base to generate a unique log file name;
-
-:::
-:::
-
-::: { #func.open_logfile.details .sidebar }
-##### Details
-\
-
-This function is a wrapper to [logr::log_open](https://www.rdocumentation.org/packages/logr/versions/1.3.9/topics/log_open) function.
-It also calls internally the following functions to generate a unique file name based on the [file_name] argument and _system time_:
-  - [Sys.time]();
-  - [stringr::str_replace](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace);
-  - [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace)
-
-For more information on the _inner functions_ listed above, see the [R Documentation](https://www.rdocumentation.org/).
-
-:::
-
-::: { #func.open_logfile.value .sidebar }
-##### Value
-\
-
-The path of the log.
-
-:::
-
-::: { #func.open_logfile.code .sidebar }
-##### Source Code
-\
-
-The source code of the [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) function is shown below:
-```{r eval=FALSE}
-library(logr)
-library(stringr)
-
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) script on _GitHub_.
-:::
-:::

### 2025-11-07 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Capstone Report: `User Effect (UE) Model described.

@@
 \
+
+::: {.noteblock data-latex=""}
+The complete source code of the *Overall Mean Rating* computation described in this section is available in the [Overall Mean Rating (Naive) Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L66) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L66) script on _GitHub_.
+:::
 

### 2025-11-07 reports/capstone-movielens.site/02.4.UE-model.Rmd
Capstone Report: `User Effect (UE) Model described.

@@
 
-To improve our model let's now take into consideration user effects as explained in [Section 23.4 *User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook*.
+To improve our model let's now take into consideration user effects as explained in [Section 25.1 *Case study: recommendation systems / User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook (New Edition)*.
 
-If we visualize the average rating for each user the way the [the author](https://x.com/rafalab) shows, we can see that there is substantial variability in the average ratings across users[@IDS2_23-4]:
+If we visualize the average rating for each user the way the the author shows, we can see that there is substantial variability in the average ratings across users[@IDS2_25-1]: 
 ```{r}
-hist(edx.user_mean_ratings$mean_rating, nclass = 30)
-```
-
-\newpage
-
-#### Ratings per user
-\
-eponymous
-homonymous
-
-::: {.noteblock data-latex=""}
-The code in this section is cited from [the eponymous section](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Ratings-per-user) of the article _Movie Recommendation System using R - BEST_[@MRS-R-BEST].
-:::
-##### User rating count (activity measure)
-\
-```{r}
-print(edx |> 
-  group_by(userId) |> 
-  summarize(count = n()) |>
-  slice_head(n = 10)
-)
-```
-
-##### User rating summary
-\
-```{r}
-summary(edx |> group_by(userId) |> summarize(count = n()) |> select(count))
-```
-\newpage
-
-##### Ratings per user plot
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = userId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per user") +
-  xlab("Users") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-\newpage
-
-##### Users' rating histogram
-\
-```{r}
-edx |>
-  group_by(userId) |>
-  summarize(count = n()) |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Users' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of users") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
+hist(edx.user_mean_ratings$mean_rating,
+     xlab = "User Average Rating",
+     nclass = 30)
 ```
@@
 
-Following the author's further explanation, to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
+Following the *Course Textbook* author's [further explanation](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects), to account for this variability, we will use a linear model with a _treatment effect_  $\alpha_i$ for each user.
 The sum $\mu+\alpha_i$ can be interpreted as the typical rating user $i$ gives to movies.
@@
 
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_23-4; @MFT_RS].
+Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_25-1; @MFT_RS].
 
@@
 
-As it is stated here[@IDS2_23-4], it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$. So we can compute them this way:
+::: {.noteblock data-latex=""}
+The complete source code of the _User Effect_ computation described in this section is available in the [User Effect (UE) Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L210) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L210) script on _GitHub_.
+:::
+
+As it is stated in the [Course Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects), it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$.
+So we can compute them this way[@IDS2_25-1]:
 ```{r eval=FALSE}
@@
 
-::: {.noteblock data-latex=""}
-The full source code of the _User Effect_ computation is available in the [Model building: User Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L531) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
-
-Now, we are ready to compute the _Mean Squared Errors_ from the _5-Fold Cross Validation_ (additionally using the [clamp](#func.clamp) helper function we described above):
+Now, we are ready to compute the _Mean Squared Errors_ from the _5-Fold Cross Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A: Support Functions]):
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report.
-
-The full source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L655) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Visualization Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+In the code snippet above we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions] to this report.
+
+The complete source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L341) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L341) script on _GitHub_.
+
 :::

### 2025-11-07 reports/capstone-movielens.site/02.5.UME-model.Rmd
Capstone Report: `User Effect (UE) Model described.

@@
 The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report).
+We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions]).
 We will explain that later in the [User+Movie Effect Model Regularization] section. 
@@
 ::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions]).
 :::
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
 :::
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
 
@@
 ::: {.noteblock data-latex=""}
-We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions], which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
 :::
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
 

### 2025-11-07 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Capstone Report: `User Effect (UE) Model described.

@@
 Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report).
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions]).
 We have already explained that in the [UME Model Regularization] section. 
@@
 ::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions]).
 :::
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
 
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
 

### 2025-11-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Capstone Report: `User Effect (UE) Model described.

--- 2025-06-06 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
@@
 Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report).
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions]).
 We have already explained that in the [UME Model Regularization] section. 
@@
 ::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions]).
 :::
@@
 ::: {.noteblock data-latex=""}
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+:::
+
 Now, we have a bit better result than one for the previous model.
-:::
 
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
 
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
 
@@
 ::: {.noteblock data-latex=""}
-Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
+Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions] to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
 :::
@@
 
+::: {.noteblock data-latex=""}
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+:::
+
 \newpage

### 2025-11-07 reports/capstone-movielens.site/03.results.Rmd
Capstone Report: `User Effect (UE) Model described.

@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddDiffColumn](#func.RMSEs.AddDiffColumn) and [RMSE.Total_kable](#func.RMSE.Total_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
+Here use the [RMSEs.AddDiffColumn](#func.RMSEs.AddDiffColumn) and [RMSE.Total_kable](#func.RMSE.Total_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
 :::

### 2025-11-07 reports/capstone-movielens.site/02.4.UE-model.Rmd
Minor fix for histogram.

@@
      xlab = "User Average Rating",
+     main = "Histogram of User Average Rating",
      nclass = 30)

### 2025-11-07 reports/capstone-movielens.site/02-0.methods.Rmd
Report review: OMR, User Effects models.

@@
 We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 25.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_25-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 31.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
-To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of the [Appendix A: Support Functions]), specifically designed for these operations:
+To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of the [Appendix A: Support Functions] of *this Report*), specifically designed for these operations:
 
@@
 
-  - [`edx.mx` Matrix Object];
+  - [`edx.mx` Matrix Object]: The `edx` dataset converted to a matrix;
 
-  - [`edx.sgr` Object];
+  - [`edx.sgr` Object]: A dataset derived from the `edx` by splitting each row corresponding to a movie belonging to multiple genres;
 
-  - [`movie_map` Object];
+  - [`movie_map` Object]: A map establishing a one-to-one correspondence between a movie ID and its title.;
 
-  - [`date_days_map` Object];
+  - [`date_days_map` Object]: A map between the rating date and the number of days since the earliest entry in the edx dataset;
 
-  - [`edx_CV` Object].
+  - [`edx_CV` Object]: A list of objects created from samples made from the `edx` dataset to use them for the _5-Fold Cross Validation_ in the way explained in [Section 31.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].

### 2025-11-07 reports/capstone-movielens.site/02.4.UE-model.Rmd
Report review: OMR, User Effects models.

@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions] to this report.
-
 The complete source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L341) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L341) script on _GitHub_.

### 2025-11-07 reports/capstone-movielens.site/02-0.methods.Rmd
Fix for Section: Preparing train and set datasets.

--- 2025-11-05 reports/capstone-movielens.site/02-0.methods.Rmd
@@
 We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 25.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_25-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 31.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
-To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of the [Appendix A: Support Functions]), specifically designed for these operations:
+To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of the [Appendix A: Support Functions] of *this Report*), specifically designed for these operations:
 
-  - [make_source_datasets](#func.make_source_datasets)
+  - [make_source_datasets](#func.make_source_datasets);
 
-  - [init_source_datasets](#func.init_source_datasets)
+  - [init_source_datasets](#func.init_source_datasets).
 
@@
 
-  - [`edx.mx` Matrix Object];
+  - [`edx.mx` Matrix Object](#appndx_b.edx.mx): The `edx` dataset converted to a matrix;
 
-  - [`edx.sgr` Object];
+  - [`edx.sgr` Object](#appndx_b.edx.sgr): A dataset derived from the `edx` by splitting each row corresponding to a movie belonging to multiple genres;
 
-  - [`movie_map` Object];
+  - [`movie_map` Object](#appndx_b.movie_map): A map establishing a one-to-one correspondence between a movie ID and its title.;
 
-  - [`date_days_map` Object];
+  - [`date_days_map` Object](#appndx_b.date_days_map): A map between the rating date and the number of days since the earliest entry in the edx dataset;
 
-  - [`edx_CV` Object].
+  - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the _5-Fold Cross Validation_ in the way explained in [Section 31.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].

### 2025-11-09 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Report review: OMR, User Effects models.
Report: UME Model describtion updated.

@@
 
-The following custom functions described in [Appendix A: Support Functions] of *this Report*, are used in the code snippets above:
+The following custom functions described in [Appendix A: Support Functions], are used in the code snippets above:
 
-  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [Overall Mean Rating (OMR) Model Helper Functions]) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method;
+  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model Helper Functions]) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method;
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the custom function [naive_model_RMSE](#func.naive_model_RMSE) described in the [Overall Mean Rating (OMR) Model Helper Functions] section of [Appendix A: Support Functions] to calculate *RMSEs* for the sequence of the deviation values.
+In the code snippet above, we use the custom function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model Helper Functions] section of [Appendix A: Support Functions] to calculate *RMSEs* for the sequence of the deviation values.
 :::

### 2025-11-09 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report: UME Model describtion updated.

@@
 
-::: {#textbook.23.5.movie_effects .sidebar }
-In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others.
+::: {#textbook.25.1.movie_effects .sidebar }
+In [Section 25.1 *Case study: recommendation systems / Movie effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) of the *Course Textbook (New Edition)*, the author draws our attention to the fact that some movies are generally rated higher than others[@IDS2_25-1].
 :::
@@
 ```
-
-\newpage
 
@@
 
-The more sophisticated way of visualizing the rating distribution shown below is cited from the [Rating distribution plot](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Rating-distribution-plot) section of the article _Movie Recommendation System using R - BEST_[@MRS-R-BEST] already referenced above in the [Ratings per user] section of this report.
-
-```{r}
-edx.rating_groups |>
-  ggplot(aes(x = rating, y = count)) +
-  geom_bar(stat = "identity", fill = "#8888ff") +
-  ggtitle("Rating Distribution") +
-  xlab("Rating") +
-  ylab("Occurrences Count") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-> This graph is another confirmation of what we found out above: rounded ratings occur more often than half-stared ones.
-The upward trend previously discussed is now perfectly clear, although it seems to top right between the 3 and 4-star ratings lowering the occurrences count afterward.
-That might be due to users being more hesitant to rate with the highest mark for whichever reasons they might hold[@MRS-R-BEST].
-
-The two more plots below, from the same article, give us an additional visual representation of the movies' popularity.
-
-\newpage
-
-##### [Ratings per movie plot](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Ratings-per-movie-plot)
-\
-
-```{r}
-edx.movie_groups <- edx |>
-  group_by(movieId) |>
-  summarize(count = n())
-
-edx.movie_groups |>
-  ggplot(aes(x = movieId, y = count)) +
-  geom_point(alpha = 0.2, color = "#4020dd") +
-  geom_smooth(color = "red") +
-  ggtitle("Ratings per movie") +
-  xlab("Movies") +
-  ylab("Number of ratings") +
-  scale_y_continuous(labels = comma) +
-  scale_x_continuous(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-\newpage
-
-##### [Movies' rating histogram](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Movies'-rating-histogram)
-\
-
-```{r}
-edx.movie_groups |>
-  ggplot(aes(x = count)) +
-  geom_histogram(fill = "#8888ff", color = "#4020dd") +
-  ggtitle("Movies' rating histogram") +
-  xlab("Rating count") +
-  ylab("Number of movies") +
-  scale_y_continuous(labels = comma) +
-  scale_x_log10(n.breaks = 10) +
-  theme_economist() +
-  theme(axis.title.x = element_text(vjust = -5, face = "bold"), 
-        axis.title.y = element_text(vjust = 10, face = "bold"), 
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
-> This histogram better conveys the information provided by the summary() function, where the quantiles’ values state that half the movies are rated between 30 and 565 times[@MRS-R-BEST].
-
-\newpage
-
 ### Mathematical Description of the UME Model
@@
 
-The author of the *Course Textbook* mentioned [above](#textbook.23.5.movie_effects) also explains that in this case one can use a linear model with a _treatment effect_ $\beta_j$ for each movie, which can be interpreted as the movie effect, or the difference between the average rating for movie $j$ and the overall average $\mu$:
+In the source mentioned [above](#textbook.25.1.movie_effects) the author also explains that in this case one can use a linear model with a _treatment effect_ $\beta_j$ for each movie, which can be interpreted as the movie effect, or the difference between the average rating for movie $j$ and the overall average $\mu$[@IDS2_25-1]:
 
@@
 ::: {.noteblock data-latex=""}
-The complete source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+The complete source code of the _User+Movie Effect_ computation described in this section is available in the [User+Movie Effect (UME) Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L382) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L382) script on _GitHub_.
 :::
@@
 
-[Section 23.6 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook* explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects[@IDS2_23-6]:
+ [Section 25.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_ explains why and how we should use _Penalized least squares_ to improve our predictions.
+The author also explains that the general idea of penalized regression is to control the total variability of the movie effects[@IDS2_25-1]:
 $$
@@
 Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_23-6].
+The larger the $\lambda$, the more we shrink[@IDS2_25-1].
 

### 2025-11-09 reports/capstone-movielens.site/05.appendix.Rmd
Fix for Section: Preparing train and set datasets.
Report: UME Model describtion updated.

@@
 
-A general function for computing the arithmetic mean given a _regularization parameter_ $\lambda$. We will call it the _penaized mean_.
+Calculates the arithmetic mean taking into account the _regularization parameter_ $\lambda$ passed in the [lambda] argument. We will call it the _penaized mean_.
 
@@
 \
-We call this function internally from the functions that compute the _penalized estimates_  as described in section [23.6 Penalized Least Squares](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook_[@IDS2_23-6].
+
+The function calculates the _penalized mean_ of the values passed in the [vals](#func.mean_reg.args.vals) argument as follows:
+$$
+\mu(\lambda) = \frac{1}{\lambda + N} \sum_{i=1}^{N} x_i
+$$
+
+When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean as follows:
+$$
+\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
+$$
+
+We call this function internally from the functions that compute the _penalized estimates_  as described in section [Section 25.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_25-1].
 
@@
 :::
+:::
+
+::: { #func.mean_reg.value .sidebar }
+##### Value
+\
+
+The [penalized mean](#func.mean_reg.details) of the values passed in the [vals](#func.mean_reg.args.vals) argument.
 :::
@@
 :::
-:::
-
-::: { #func.mean_reg.value .sidebar }
-##### Value
-\
-
-The function calculates the _penalized mean_ of the [vals](#func.mean_reg.args.vals) parameter as follows:
-$$
-\mu(\lambda) = \frac{1}{\lambda + N} \sum_{i=1}^{N} x_i
-$$
-
-When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean as follows:
-$$
-\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
-$$
-
 :::
@@
 
-#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
+#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) Function {#func.get_best_param.result}
 \
@@
 \
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is shown below:
 ```{r eval=FALSE}
@@
 ```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) script on _GitHub_.
+:::
 
@@
 
-### Overall Mean Rating (OMR) Model Helper Functions
+### OMR Model Helper Functions
 \
@@
 ::: {.noteblock data-latex=""}
-The source code of the [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L2) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) script on _GitHub_.
+The source code of the [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L7) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) script on _GitHub_.
+The source code of the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) script on _GitHub_.
 :::
@@
 
+### UME Model Utility Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the  [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) script on _GitHub_.
+:::
+
+#### [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) Function {#func.train_user_movie_effect}
+\
+
+Computes the *Regularized User+Movie (UM) Effect* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) parameter.
+
+::: { #func.train_user_movie_effect.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  UM_effect <- train_user_movie_effect(train_set, lambda = 0)
+```
+:::
+
+::: { #func.train_user_movie_effect.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_user_movie_effect.args.train_set .sidebar }
+  - **train_set:** Training dataset;
+
+:::
+::: { #func.train_user_movie_effect.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.train_user_movie_effect.details .sidebar }
+##### Details
+\
+
+The *Regularization technique* (described in section [Section 25.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_25-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the section [Regularization Functions].
+:::
+
+::: { #func.train_user_movie_effect.value .sidebar }
+##### Value
+\
+
+Data frame representing the (regularized if [lambda](#func.train_user_movie_effect.args.lambda) arg value other than default) *UM Effect* model.
+:::
+
+::: { #func.train_user_movie_effect.code .sidebar }
+##### Source Code
+\
+
+The source code of the [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is shown below:
+```{r eval=FALSE}
+train_user_movie_effect <- function(train_set, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_user_movie_effect
+`lambda` is `NA`")
+  }
+
+  UM.effect <- train_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    mutate(resid = rating - (mu + a)) |> 
+    group_by(movieId) |>
+    summarise(b = mean_reg(resid, lambda), n = n())
+
+  stopifnot(!is.na(mean(UM.effect$b)))
+  UM.effect
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) Function {#func.train_user_movie_effect.cv}
+\
+
+::: { #func.train_user_movie_effect.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+train_user_movie_effect.cv()
+
+```
+:::
+
+::: { #func.train_user_movie_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_user_movie_effect.cv.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.train_user_movie_effect.cv.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.train_user_movie_effect.cv.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.train_user_movie_effect.cv.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.train_user_movie_effect.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) Function {#func.calc_user_movie_effect_RMSE}
+\
+
+::: { #func.calc_user_movie_effect_RMSE.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+calc_user_movie_effect_RMSE()
+
+```
+:::
+
+::: { #func.calc_user_movie_effect_RMSE.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_user_movie_effect_RMSE.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.calc_user_movie_effect_RMSE.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.calc_user_movie_effect_RMSE.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.calc_user_movie_effect_RMSE.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.calc_user_movie_effect_RMSE.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L57) Function {#func.calc_user_movie_effect_MSE}
+\
+
+::: { #func.calc_user_movie_effect_MSE.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+calc_user_movie_effect_MSE()
+
+```
+:::
+
+::: { #func.calc_user_movie_effect_MSE.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_user_movie_effect_MSE.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.calc_user_movie_effect_MSE.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.calc_user_movie_effect_MSE.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.calc_user_movie_effect_MSE.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.calc_user_movie_effect_MSE.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L57) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L57) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L57) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) Function {#func.calc_user_movie_effect_RMSE.cv}
+\
+
+::: { #func.calc_user_movie_effect_RMSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+calc_user_movie_effect_RMSE.cv()
+
+```
+:::
+
+::: { #func.calc_user_movie_effect_RMSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_user_movie_effect_RMSE.cv.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.calc_user_movie_effect_RMSE.cv.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.calc_user_movie_effect_RMSE.cv.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.calc_user_movie_effect_RMSE.cv.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.calc_user_movie_effect_RMSE.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L74) Function {#func.calc_user_movie_effect_MSE.cv}
+\
+
+::: { #func.calc_user_movie_effect_MSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+calc_user_movie_effect_MSE.cv()
+
+```
+:::
+
+::: { #func.calc_user_movie_effect_MSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_user_movie_effect_MSE.cv.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.calc_user_movie_effect_MSE.cv.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.calc_user_movie_effect_MSE.cv.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.calc_user_movie_effect_MSE.cv.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.calc_user_movie_effect_MSE.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L74) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L74) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L74) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+### UME Model Regularization
+\
+
+#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) Function {#func.regularize.test_lambda.UM_effect.cv}
+\
+
+::: { #func.regularize.test_lambda.UM_effect.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+regularize.test_lambda.UM_effect.cv()
+
+```
+:::
+
+::: { #func.regularize.test_lambda.UM_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.regularize.test_lambda.UM_effect.cv.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.regularize.test_lambda.UM_effect.cv.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.regularize.test_lambda.UM_effect.cv.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.regularize.test_lambda.UM_effect.cv.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.regularize.test_lambda.UM_effect.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) script on _GitHub_.
+:::
+:::
+
+\newpage
+
 # Appendix B: Models Training Datasets {#appndx_b}
@@
 
-## `edx.mx` Matrix Object
+## `edx.mx` Matrix Object {#appndx_b.edx.mx}
 \
@@
 
-## `edx.sgr` Object
+## `edx.sgr` Object {#appndx_b.edx.sgr}
 \
@@
 
-## `movie_map` Object
+## `movie_map` Object {#appndx_b.movie_map}
 \
@@
 
-## `date_days_map` Object
+## `date_days_map` Object {#appndx_b.date_days_map}
 \
@@
 
-## `edx_CV` Object
+## `edx_CV` Object {#appndx_b.edx_CV}
 \

### 2025-11-09 r/src/support-functions/UM-effect.functions.R

@@ -1,4 +1,4 @@
-# User+Movie Effect (UME) Model Support Functions 
+# User+Movie Effect (UME) Model Support Functions
 
 ## UME Model Utility Functions --------------------------------------------------
 train_user_movie_effect <- function(train_set, lambda = 0){

### 2025-11-09 r/src/support-functions/data.helper.functions.R

@@ -432,11 +432,6 @@ union_cv_results <- function(data_list) {
   
   out_dat
 }
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-}
 ## Data Visualization ----------------------------------------------------------
 data.plot.left_detailed <- function(data, 
                                     left.n = 0,

### 2025-11-10 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for functions: mean_reg, train_user_movie_effect.

@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) script on _GitHub_.
-:::
-
-#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) Function {#func.mean_reg}
-\
-
-Calculates the arithmetic mean taking into account the _regularization parameter_ $\lambda$ passed in the [lambda] argument. We will call it the _penaized mean_.
+The complete source code of the functions described in this section are available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) script on _GitHub_.
+:::
+
+#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) Function {#func.mean_reg}
+\
+
+Calculates the arithmetic mean taking into account the _regularization parameter_ $\lambda$ passed in the [lambda](#func.mean_reg.args.lambda) argument. We will call it the _penalized mean_.
 
@@
 ::: { #func.mean_reg.args.vals .sidebar }
-  - **vals:** values (usually a numeric vector) to calculate the _penalized mean_;
+  - **vals:** Values (usually a numeric vector) to calculate the _penalized mean_;
 
@@
 ::: { #func.mean_reg.args.lambda .sidebar }
-  - **lambda:** a _regularization parameter_ $\lambda$ used in the _Regularization techniques_.
+  - **lambda:** (0 by default) _Regularization parameter_ $\lambda$ used in the _Regularization techniques_.
 
@@
 
-When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean as follows:
+When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean:
 $$
@@
 
-The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function is shown below:
+The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L62) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) script on _GitHub_.
+The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the  [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) script on _GitHub_.
+The complete source code of the functions described in this section is available in the  [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
+The source code of the [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
 :::

### 2025-11-11 reports/capstone-movielens.site/02-0.methods.Rmd
Course textbook chapter number changed: 25 -> 24.

@@
 
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 25.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_25-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 31.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
+We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 24.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_25-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 31.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
 To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of the [Appendix A: Support Functions] of *this Report*), specifically designed for these operations:

### 2025-11-11 reports/capstone-movielens.site/02.4.UE-model.Rmd
Course textbook chapter number changed: 25 -> 24.

@@
 
-To improve our model let's now take into consideration user effects as explained in [Section 25.1 *Case study: recommendation systems / User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook (New Edition)*.
+To improve our model let's now take into consideration user effects as explained in [Section 24.1 *Case study: recommendation systems / User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the *Course Textbook (New Edition)*.
 

### 2025-11-11 reports/capstone-movielens.site/02.5.UME-model.Rmd
Course textbook chapter number changed: 25 -> 24.

@@
 ::: {#textbook.25.1.movie_effects .sidebar }
-In [Section 25.1 *Case study: recommendation systems / Movie effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) of the *Course Textbook (New Edition)*, the author draws our attention to the fact that some movies are generally rated higher than others[@IDS2_25-1].
+In [Section 24.1 *Case study: recommendation systems / Movie effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) of the *Course Textbook (New Edition)*, the author draws our attention to the fact that some movies are generally rated higher than others[@IDS2_25-1].
 :::
@@
 
- [Section 25.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_ explains why and how we should use _Penalized least squares_ to improve our predictions.
+ [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_ explains why and how we should use _Penalized least squares_ to improve our predictions.
 The author also explains that the general idea of penalized regression is to control the total variability of the movie effects[@IDS2_25-1]:

### 2025-11-11 reports/capstone-movielens.site/05.appendix.Rmd
Course textbook chapter number changed: 25 -> 24.

@@
 \
-As explained in [Section 25.1 *Case study: recommendation systems / User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
-For this reason, we need a function described in that section[@IDS2_25-1]:
+As explained in [Section 24.1 *Case study: recommendation systems / User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
+For this reason, we need a function described in that section[@IDS2_24-1]:
 
@@
 
-Calculates *Mean Squared Error* as described in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_25-1].
+Calculates *Mean Squared Error* as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1].
 
@@
 ::: { #func.mse.args.r .sidebar }
-  - **r:** Numeric vector representing a set of residuals as described in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_25-1].
+  - **r:** Numeric vector representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1].
 
@@
 ::: { #func.mse_cv.args.r_list .sidebar }
-  - **r_list:** List of numeric vectors, each representing a set of residuals as described in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_25-1], calculated in `K`th iteration using the _K-Fold Cross Validation_ method.
+  - **r_list:** List of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1], calculated in `K`th iteration using the _K-Fold Cross Validation_ method.
 
@@
 
-Calculates *Root Mean Squared Error* as described in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_25-1].
+Calculates *Root Mean Squared Error* as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1].
 
@@
 ::: { #func.rmse.args.r .sidebar }
-  - **r:** Numeric vector representing a set of residuals as described in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_25-1].
+  - **r:** Numeric vector representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1].
 
@@
 
-We call this function internally from the functions that compute the _penalized estimates_  as described in section [Section 25.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_25-1].
+We call this function internally from the functions that compute the _penalized estimates_  as described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1].
 
@@
 
-The *Regularization technique* (described in section [Section 25.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_25-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the section [Regularization Functions].
@@
 
-Note that titles cannot be considered unique, so we cannot use them as IDs[@IDS2_25-1].
+Note that titles cannot be considered unique, so we cannot use them as IDs[@IDS2_24-1].
 

### 2025-11-12 reports/capstone-movielens.site/05.appendix.Rmd
Bibliography fixed, functions described: train_user_movie_effect, train_user_movie_effect.cv .

@@
 
-Calculates the average value of the *Mean Squared Errors* calculated using the _K-Fold Cross Validation_ method as described in [Section 31.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
+Calculates the average value of the *Mean Squared Errors* calculated using the _K-Fold Cross Validation_ method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 
-Splits the input dataset passed in the [data](#func.sample_train_validation_sets.args.data) argument into *train* and *validation* datasets in the way described in [Section 31.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
+Splits the input dataset passed in the [data](#func.sample_train_validation_sets.args.data) argument into *train* and *validation* datasets in the way described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 
-Computes the *Regularized User+Movie (UM) Effect* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) parameter.
+Computes the *(Regularized) User+Movie (UM) Effect* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) parameter.
 
@@
 The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
-The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the section [Regularization Functions].
+The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
 :::
@@
 
-Data frame representing the (regularized if [lambda](#func.train_user_movie_effect.args.lambda) arg value other than default) *UM Effect* model.
+Data frame representing the trained (and also *regularized* if [lambda](#func.train_user_movie_effect.args.lambda) arg value other than default) *UM Effect Model*.
 :::
@@
 
+Trains the *(Regularized) User+Movie (UM) Effect Model* using the the _5-Fold Cross Validation_ 
+as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+
 ::: { #func.train_user_movie_effect.cv.usage .sidebar }
@@
 ```{r eval=FALSE}
-train_user_movie_effect.cv()
-
+  cv.UM_effect <- train_user_movie_effect.cv()
 ```
@@
 
-::: { #func.train_user_movie_effect.cv.args. .sidebar }
-  - **:** ;
-
-:::
-::: { #func.train_user_movie_effect.cv.args. .sidebar }
-  - **:** ;
+::: { #func.train_user_movie_effect.cv.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
 
@@
 
+Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for every iteration of the _5-Fold Cross Validation_.
+It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+:::
 :::
@@
 
+Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.args.lambda) argument value is other than the default) using _5-Fold Cross-Validation_.
 :::
@@
 
-The source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) script on _GitHub_.
+The most important part of the source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is shown below:
+```{r eval=FALSE}
+train_user_movie_effect.cv <- function(lambda = 0){
+# ...
+  start <- put_start_date()
+  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
+    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
+  })
+  put_end_date(start)
+  put_log("Function: train_user_movie_effect.cv:
+User+Movie Effect list have been computed")
+
+  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
+
+  user_movie_effect <- user_movie_effects_united |>
+    group_by(movieId) |>
+    summarise(b = mean(b), n = mean(n))
+  # ...
+  user_movie_effect
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) script on _GitHub_.
 :::
@@
 Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
-as explained in [Section 31.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6]:
+as explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6]:
 ```{r eval=FALSE}

### 2025-11-12 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions: union_cv_results, train_user_movie_effect.cv.

@@
 
-The function is used to aggregate the _N-Fold Cross Validation_ method result data into a single data frame for further processing.
-
+This function internally uses the [base::union]((https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) function to aggregate the _N-Fold Cross-Validation_ result data into a single data frame for further processing.
 :::
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) script on _GitHub_.
+The complete source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) script on _GitHub_.
 :::

### 2025-11-12 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix.

@@
 
-This function internally uses the [base::union]((https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) function to aggregate the _N-Fold Cross-Validation_ result data into a single data frame for further processing.
+This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) function to aggregate the _N-Fold Cross-Validation_ result data list into a single data frame for further processing.
 :::

### 2025-11-12 r/src/support-functions/UM-effect.functions.R
Describing functions: calc_user_movie_effect_MSE.cv, calc_user_movie_effect_RMSE.cv (in progress)

@@ -50,10 +50,6 @@ Training completed: User+Movie Effects model for lambda: %1...",
   
   user_movie_effect
 }
-calc_user_movie_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-  sqrt(mse)
-}
 calc_user_movie_effect_MSE <- function(test_set, um_effect){
   mse.result <- test_set |>
     left_join(edx.user_effect, by = "userId") |>
@@ -64,12 +60,9 @@ calc_user_movie_effect_MSE <- function(test_set, um_effect){
   stopifnot(!is.na(mse.result))
   mse.result
 }
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
-  um_effect_RMSE
+calc_user_movie_effect_RMSE <- function(test_set, um_effect){
+  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
+  sqrt(mse)
 }
 calc_user_movie_effect_MSE.cv <- function(um_effect){
   put_log("Function: user_movie_effects_MSE.cv:
@@ -85,6 +78,13 @@ MSE values have been plotted for the %1-Fold Cross Validation samples.",
            CVFolds_N)
   
   mean(user_movie_effects_MSEs)
+}
+calc_user_movie_effect_RMSE.cv <- function(um_effect){
+  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
+  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
+  put_log2("Function: user_movie_effects_RMSE.cv:
+%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
+  um_effect_RMSE
 }
 
 ## UME Model Regularization ----------------------------------------------------

### 2025-11-13 reports/capstone-movielens.site/01.intro.Rmd
Report review: OMR, User Effects models.

@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 25.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_, is defined as:
+Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_, is defined as:
 $$
@@
 
-To start with we have to generate two datasets derived from the _MovieLens_ dataset mentioned [above](#intro):
+To start with we have to generate two datasets derived from the _MovieLens_ dataset mentioned above:
 

### 2025-11-13 reports/capstone-movielens.site/02-0.methods.Rmd

@@
 
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 24.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_25-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 31.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
+We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 24.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_25-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of the [Appendix A: Support Functions] of *this Report*), specifically designed for these operations:
@@
 
-  - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the _5-Fold Cross Validation_ in the way explained in [Section 31.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6].
+  - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the _5-Fold Cross Validation_ in the way explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].

### 2025-11-13 reports/capstone-movielens.site/02-3.OMR-model.Rmd

@@
 
-Let's begin our analysis by evaluating the simplest model described in [Section 25.1 *Case study: recommendation systems / A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook (New Edition)*[@IDS2_25-1], and then gradually refine it through further research.
+Let's begin our analysis by evaluating the simplest model described in [Section 24.1 *Case study: recommendation systems / A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook (New Edition)*[@IDS2_25-1], and then gradually refine it through further research.
 

### 2025-11-13 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd

@@
 Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A: Support Functions]).
 We have already explained that in the [UME Model Regularization] section. 
@@
 ::: {.noteblock data-latex=""}
-The custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) we used above is described in the [Data Helper Functions] section of the [Appendix] to this report.
+The custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) we used above is described in the [Data Helper Functions] section of [Appendix A: Support Functions].
 :::
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
 
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
 
@@
 ::: {.noteblock data-latex=""}
-Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
+Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A: Support Functions] to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
 :::

### 2025-11-13 reports/capstone-movielens.site/05.appendix.Rmd

--- 2025-11-12 reports/capstone-movielens.site/05.appendix.Rmd
@@
 ```{r eval=FALSE}
-union_cv_results(data_list = data)
+data_list <- as.list(data)
+df <- union_cv_results(data_list)
 
@@
 \
-
-This function internally uses the [base::union]((https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) function to aggregate the _N-Fold Cross-Validation_ result data into a single data frame for further processing.
+This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the _N-Fold Cross Validation_) passed in the [data_list] argument into a single data frame for further processing.
 :::
@@
 
-A data frame that is a union of the input data frames.
+A data frame that is a union of the input list of data frames.
 :::
@@
 
-Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for every iteration of the _5-Fold Cross Validation_.
+Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for every iteration of the _5-Fold Cross Validation_ applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
 It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
 :::
@@
 
-Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.args.lambda) argument value is other than the default) using _5-Fold Cross-Validation_.
+Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) using _5-Fold Cross-Validation_.
 :::
@@
 
-#### [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) Function {#func.calc_user_movie_effect_RMSE}
-\
-
-::: { #func.calc_user_movie_effect_RMSE.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE()
-
-```
-:::
-
-::: { #func.calc_user_movie_effect_RMSE.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_user_movie_effect_RMSE.args. .sidebar }
-  - **:** ;
-
-:::
-::: { #func.calc_user_movie_effect_RMSE.args. .sidebar }
-  - **:** ;
-
-:::
-:::
-
-::: { #func.calc_user_movie_effect_RMSE.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.calc_user_movie_effect_RMSE.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.calc_user_movie_effect_RMSE.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) script on _GitHub_.
+#### [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) Function {#func.calc_user_movie_effect_MSE}
+\
+
+Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
+
+::: { #func.calc_user_movie_effect_MSE.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
+
+```
+:::
+
+::: { #func.calc_user_movie_effect_MSE.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_user_movie_effect_MSE.args.test_set .sidebar }
+  - **test_set:** Validation dataset;
+
+:::
+::: { #func.calc_user_movie_effect_MSE.args.um_effect .sidebar }
+  - **um_effect:** Data frame representing the *UM Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_user_movie_effect_MSE.details .sidebar }
+##### Details
+\
+
+To calculate the *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_MSE.args.um_effect) argument, the function uses the validation dataset passed in the [test_set](#func.calc_user_movie_effect_MSE.args.test_set) arg.
+
+:::
+
+::: { #func.calc_user_movie_effect_MSE.value .sidebar }
+##### Value
+\
+
+*MSE* value calculated for the *UME Model*.
+:::
+
+::: { #func.calc_user_movie_effect_MSE.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) function is shown below:
+```{r eval=FALSE}
+calc_user_movie_effect_MSE <- function(test_set, um_effect){
+  mse.result <- test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(um_effect, by = "movieId") |>
+    mutate(resid = rating - clamp(mu + a + b)) |> 
+    pull(resid) |> mse()
+
+  stopifnot(!is.na(mse.result))
+  mse.result
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) script on _GitHub_.
 :::
@@
 
-#### [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L57) Function {#func.calc_user_movie_effect_MSE}
-\
-
-::: { #func.calc_user_movie_effect_MSE.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-calc_user_movie_effect_MSE()
-
-```
-:::
-
-::: { #func.calc_user_movie_effect_MSE.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_user_movie_effect_MSE.args. .sidebar }
-  - **:** ;
-
-:::
-::: { #func.calc_user_movie_effect_MSE.args. .sidebar }
-  - **:** ;
-
-:::
-:::
-
-::: { #func.calc_user_movie_effect_MSE.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.calc_user_movie_effect_MSE.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.calc_user_movie_effect_MSE.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L57) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L57) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L57) script on _GitHub_.
+#### [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) Function {#func.calc_user_movie_effect_MSE.cv}
+\
+
+Calculates *Root Mean Squared Error (RMSE)* for the *UM Effect (UME) Model* produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
+
+::: { #func.calc_user_movie_effect_MSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
+
+```
+:::
+
+::: { #func.calc_user_movie_effect_MSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_user_movie_effect_MSE.cv.args.um_effect .sidebar }
+  - **um_effect:** Data frame representing the *UM Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_user_movie_effect_MSE.cv.details .sidebar }
+##### Details
+\
+
+To calculate the *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.args.um_effect) argument, the function uses the validation dataset passed in the [test_set](#func.calc_user_movie_effect_RMSE.args.test_set) arg.
+
+:::
+
+::: { #func.calc_user_movie_effect_MSE.cv.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.calc_user_movie_effect_MSE.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) function is shown below:
+```{r eval=FALSE}
+calc_user_movie_effect_MSE.cv <- function(um_effect){
+  put_log("Function: user_movie_effects_MSE.cv:
+Computing the RMSE taking into account User+Movie Effects...")
+  start <- put_start_date()
+  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
+    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
+  })
+  put_end_date(start)
+
+  put_log1("Function: user_movie_effects_MSE.cv:
+MSE values have been plotted for the %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  mean(user_movie_effects_MSEs)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) script on _GitHub_.
 :::
@@
 
-#### [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) Function {#func.calc_user_movie_effect_RMSE.cv}
-\
+#### [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) Function {#func.calc_user_movie_effect_RMSE.cv}
+\
+
+Calculates *Root Mean Squared Error (RMSE)* for the *UM Effect (UME) Model* produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
 
@@
 ```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv()
+cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
 
@@
 
-::: { #func.calc_user_movie_effect_RMSE.cv.args. .sidebar }
-  - **:** ;
-
-:::
-::: { #func.calc_user_movie_effect_RMSE.cv.args. .sidebar }
-  - **:** ;
+::: { #func.calc_user_movie_effect_RMSE.cv.args.um_effect .sidebar }
+  - **um_effect:** Data frame representing the *UM Effect Model*.
 
@@
 
+To calculate the *RMSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.args.um_effect) argument, the function uses the validation dataset passed in the [test_set](#func.calc_user_movie_effect_RMSE.args.test_set) arg.
+
 :::
@@
 
-The source code of the [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L74) Function {#func.calc_user_movie_effect_MSE.cv}
-\
-
-::: { #func.calc_user_movie_effect_MSE.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv()
-
-```
-:::
-
-::: { #func.calc_user_movie_effect_MSE.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_user_movie_effect_MSE.cv.args. .sidebar }
-  - **:** ;
-
-:::
-::: { #func.calc_user_movie_effect_MSE.cv.args. .sidebar }
-  - **:** ;
-
-:::
-:::
-
-::: { #func.calc_user_movie_effect_MSE.cv.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.calc_user_movie_effect_MSE.cv.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.calc_user_movie_effect_MSE.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L74) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L74) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L74) script on _GitHub_.
+The source code of the [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) function is shown below:
+```{r eval=FALSE}
+calc_user_movie_effect_RMSE.cv <- function(um_effect){
+  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
+  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
+  put_log2("Function: user_movie_effects_RMSE.cv:
+%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
+  um_effect_RMSE
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) script on _GitHub_.
 :::

### 2025-11-13 reports/capstone-movielens.site/work/func-descr.template.Rmd

@@
 
-#### [helper-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.helper-func.tmpl}
+#### [cmmn_helper_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.cmmn_helper_func.tmpl}
 \
 
-::: { #func.helper-func.tmpl.usage .sidebar }
+::: { #func.cmmn_helper_func.tmpl.usage .sidebar }
 ##### Usage
@@
 ```{r eval=FALSE}
-helper-func.tmpl()
+cmmn_helper_func.tmpl()
 
@@
 
-::: { #func.helper-func.tmpl.args .sidebar }
+::: { #func.cmmn_helper_func.tmpl.args .sidebar }
 ##### Arguments
@@
 
-::: { #func.helper-func.tmpl.args. .sidebar }
+::: { #func.cmmn_helper_func.tmpl.args. .sidebar }
   - **:** ;
@@
 :::
-::: { #func.helper-func.tmpl.args. .sidebar }
+::: { #func.cmmn_helper_func.tmpl.args. .sidebar }
   - **:** ;
@@
 
-::: { #func.helper-func.tmpl.details .sidebar }
+::: { #func.cmmn_helper_func.tmpl.details .sidebar }
 ##### Details
@@
 
-::: { #func.helper-func.tmpl.value .sidebar }
+::: { #func.cmmn_helper_func.tmpl.value .sidebar }
 ##### Value
@@
 
-::: { #func.helper-func.tmpl.code .sidebar }
+::: { #func.cmmn_helper_func.tmpl.code .sidebar }
 ##### Source Code
@@
 
-The source code of the [helper-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
+The source code of the [cmmn_helper_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [helper-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L0) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+The source code of the [cmmn_helper_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L0) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
 :::
@@
 
+## Model Helper Functions
 ### Overal Mean Rating (OMR) Model Functions
@@
 ::: {.noteblock data-latex=""}
-The source code of the [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) script on _GitHub_.
+The source code of the [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) script on _GitHub_.
 :::
@@
 \newpage
+
+### UME Model Utility Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the  [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) script on _GitHub_.
+:::
+
+#### [ume_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) Function {#func.ume_helper.tmpl}
+\
+
+::: { #func.ume_helper.tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+ume_helper.tmpl()
+
+```
+:::
+
+::: { #func.ume_helper.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.ume_helper.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.ume_helper.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.ume_helper.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.ume_helper.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.ume_helper.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [ume_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [ume_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+### UME Model Regularization
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the  [UME Model Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) script on _GitHub_.
+:::
+
+#### [ume_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) Function {#func.ume_rglr_helper.tmpl}
+\
+
+::: { #func.ume_rglr_helper.tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+ume_rglr_helper.tmpl()
+
+```
+:::
+
+::: { #func.ume_rglr_helper.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.ume_rglr_helper.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.ume_rglr_helper.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.ume_rglr_helper.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.ume_rglr_helper.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.ume_rglr_helper.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [ume_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [ume_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+## General Func Tempates -------------------------------------------------------
 
@@
 ::: {.noteblock data-latex=""}
-The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) script on _GitHub_.
+The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L) section of the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) script on _GitHub_.
 :::
 :::
+
+\newpage

### 2025-11-13 reports/capstone-movielens.site/02-0.methods.Rmd
Functions described: calc_user_movie_effect_MSE.cv, calc_user_movie_effect_RMSE.cv.

@@
 
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 24.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_25-1].We will also use the _5-Fold Cross Validation_ method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 24.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_25-1].We will also use the _5-Fold Cross-Validation_ method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of the [Appendix A: Support Functions] of *this Report*), specifically designed for these operations:
@@
 
-  - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the _5-Fold Cross Validation_ in the way explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+  - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the _5-Fold Cross-Validation_ in the way explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].

### 2025-11-13 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Functions described: calc_user_movie_effect_MSE.cv, calc_user_movie_effect_RMSE.cv.

@@
 
-  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model Helper Functions]) to compute _Mean Squared Errors_ using _5-Fold Cross Validation_ method;
+  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model Helper Functions]) to compute _Mean Squared Errors_ using _5-Fold Cross-Validation_ method;
 

### 2025-11-13 reports/capstone-movielens.site/02.4.UE-model.Rmd
Functions described: calc_user_movie_effect_MSE.cv, calc_user_movie_effect_RMSE.cv.

@@
 
-Now, we are ready to compute the _Mean Squared Errors_ from the _5-Fold Cross Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A: Support Functions]):
+Now, we are ready to compute the _Mean Squared Errors_ from the _5-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A: Support Functions]):
 ```{r eval=FALSE}
@@
 
-Finally, we calculate the `RMSE` as the _square root_ of the average of the _Mean Squared Errors_ we obtained through the _5-Fold Cross Validation_ above:   
+Finally, we calculate the `RMSE` as the _square root_ of the average of the _Mean Squared Errors_ we obtained through the _5-Fold Cross-Validation_ above:   
 ```{r, eval=FALSE}

### 2025-11-13 reports/capstone-movielens.site/02.5.UME-model.Rmd
Functions described: calc_user_movie_effect_MSE.cv, calc_user_movie_effect_RMSE.cv.

@@
 
-We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method.
+We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the *5-Fold Cross-Validation* method.
 Below, we provide the most important part of the code of that function:
@@
 ::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions]).
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross-Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions]).
 :::
@@
 
-The source code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the _5-Fold Cross Validation_ **MSE**_ result of the _UME Model_ is provided below:
+The source code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the _5-Fold Cross-Validation_ **MSE**_ result of the _UME Model_ is provided below:
 ```{r eval=FALSE}
@@
   put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross Validation samples.", 
+MSE values have been plotted for the %1-Fold Cross-Validation samples.", 
            CVFolds_N)
@@
 
-The source code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:
+The source code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the *5-Fold Cross-Validation* RMSE result of the `UME Model` is provided below:
 
@@
   put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
+%1-Fold Cross-Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
   um_effect_RMSE
@@
 
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
+Below, we provide the most significant part of the code for training our model using the *5-Fold Cross-Validation* method:
 ```{r eval=FALSE}
@@
 
-  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
+  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the *5-Fold Cross-Validation* samples;
 
@@
 
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
+This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross-Validation_ method for the given $\lambda$ parameter value:
 ```{r, eval=FALSE}
@@
 put_log1("Preliminary regularization set-up of `lambda`s range for the UME Model has been completed
-for the %1-Fold Cross Validation samples.",
+for the %1-Fold Cross-Validation samples.",
 CVFolds_N)

### 2025-11-13 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: calc_user_movie_effect_MSE.cv, calc_user_movie_effect_RMSE.cv.

@@
 
-Calculates the average value of the *Mean Squared Errors* calculated using the _K-Fold Cross Validation_ method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Calculates the average value of the *Mean Squared Errors* calculated using the _K-Fold Cross-Validation_ method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 ::: { #func.mse_cv.args.r_list .sidebar }
-  - **r_list:** List of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1], calculated in `K`th iteration using the _K-Fold Cross Validation_ method.
+  - **r_list:** List of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1], calculated in `K`th iteration using the _K-Fold Cross-Validation_ method.
 
@@
     put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)
+Creating K-Fold Cross-Validation Datasets, Fold %1", fold_i)
 
@@
   put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
+Set of K-Fold Cross-Validation datasets created: edx_CV")
 
@@
 ::: { #func.union_cv_results.args.data_list .sidebar }
-  - **data_list:** List of data frames representing the results of the _N-Fold Cross Validation_ method execution.;
+  - **data_list:** List of data frames representing the results of the _N-Fold Cross-Validation_ method execution.;
 
@@
 \
-This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the _N-Fold Cross Validation_) passed in the [data_list] argument into a single data frame for further processing.
+This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the _N-Fold Cross-Validation_) passed in the [data_list] argument into a single data frame for further processing.
 :::
@@
 
-Calculates the Mean Squared Errors (MSEs) for the *Overall Mean Rating (OMR) Model* using the *K-Fold Cross Validation* method as described in section [OMR Model Building] of *this Report*.
+Calculates the Mean Squared Errors (MSEs) for the *Overall Mean Rating (OMR) Model* using the *K-Fold Cross-Validation* method as described in section [OMR Model Building] of *this Report*.
 
@@
 \
-Calculates the Root Mean Squared Error (RMSE) for the *Overall Mean Rating (OMR) Model* using the *K-Fold Cross Validation* method as described in section [OMR Model Building] of *this Report*.
+Calculates the Root Mean Squared Error (RMSE) for the *Overall Mean Rating (OMR) Model* using the *K-Fold Cross-Validation* method as described in section [OMR Model Building] of *this Report*.
 
@@
 
-Trains the *(Regularized) User+Movie (UM) Effect Model* using the the _5-Fold Cross Validation_ 
+Trains the *(Regularized) User+Movie (UM) Effect Model* using the the _N-Fold Cross-Validation_ 
 as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
@@
 
-Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for every iteration of the _5-Fold Cross Validation_ applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for every iteration of the _N-Fold Cross-Validation_ applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
 It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
 
+The `N` value for the *N-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+
 ::: {.noteblock data-latex=""}
@@
 
-Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) using _5-Fold Cross-Validation_.
+Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) using _N-Fold Cross-Validation_.
 :::
@@
 
-Calculates *Root Mean Squared Error (RMSE)* for the *UM Effect (UME) Model* produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
+Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.
 
@@
 
-To calculate the *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.args.um_effect) argument, the function uses the validation dataset passed in the [test_set](#func.calc_user_movie_effect_RMSE.args.test_set) arg.
-
+The function utilizes *N-Fold Cross-Validation* to calculate *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_MSE.cv.args.um_effect) argument using the validation datasets contained by the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_effect_MSE](#func.calc_user_movie_effect_MSE) function for each iteration of the *N-Fold Cross-Validation* method, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
+
+The `N` value for the *N-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+:::
 :::
@@
 
+The *MSE* value calculated for the *UM Effect Model* using the *N-Fold Cross-Validation*, where the `N` is the length of the [`edx_CV` Object].
 :::
@@
 
-Calculates *Root Mean Squared Error (RMSE)* for the *UM Effect (UME) Model* produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
+Calculates *Root Mean Squared Error (RMSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.
 
@@
 
-To calculate the *RMSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.args.um_effect) argument, the function uses the validation dataset passed in the [test_set](#func.calc_user_movie_effect_RMSE.args.test_set) arg.
-
+The function utilizes *N-Fold Cross-Validation* to calculate *RMSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained by the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_effect_MSE.cv](#func.calc_user_movie_effect_MSE.cv) function described above, to calculate the *MSE* for the *UME Model* using *N-Fold Cross-Validation*, and then calculates the square root of the result.
+
+The `N` value for the *N-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+:::
 :::
@@
   put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
+%1-Fold Cross-Validation ultimate RMSE: %2", length(edx_CV), um_effect_RMSE)
   um_effect_RMSE
@@
 
-Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
+Here we have a list of sample objects we need to perform the _5-Fold Cross-Validation_ 
 as explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6]:
@@
   put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross Validation datasets created: edx_CV")
+Set of K-Fold Cross-Validation datasets created: edx_CV")
 ```

### 2025-11-13 r/src/support-functions/UM-effect.functions.R

@@ -75,7 +75,7 @@ Computing the RMSE taking into account User+Movie Effects...")
   
   put_log1("Function: user_movie_effects_MSE.cv:
 MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
+           length(edx_CV))
   
   mean(user_movie_effects_MSEs)
 }
@@ -83,7 +83,7 @@ calc_user_movie_effect_RMSE.cv <- function(um_effect){
   user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
   um_effect_RMSE <- sqrt(user_movie_effects_MSE)
   put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
+%1-Fold Cross Validation ultimate RMSE: %2", length(edx_CV), um_effect_RMSE)
   um_effect_RMSE
 }
 

### 2025-11-13 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: calc_user_movie_effect_MSE.cv, calc_user_movie_effect_RMSE.cv.
Fix for functions' description.

@@
 
-Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for every iteration of the _N-Fold Cross-Validation_ applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for each iteration of the _N-Fold Cross-Validation_ applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
 It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
@@
 
-Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
+Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* produced by the  [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
 
@@
 
-Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.
+Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.
 
@@
 
-Calculates *Root Mean Squared Error (RMSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.
+Calculates *Root Mean Squared Error (RMSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.
 
@@
 
+The *RMSE* value calculated for the *UM Effect Model* using the *N-Fold Cross-Validation*, where the `N` is the length of the [`edx_CV` Object].
 :::

### 2025-11-14 reports/capstone-movielens.site/05.appendix.Rmd
Update  for functions' description relate to k-fold cross-validation.

@@
 
-Calculates the average value of the *Mean Squared Errors* calculated using the _K-Fold Cross-Validation_ method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Calculates the average value of the *Mean Squared Errors* calculated using the *K-Fold Cross-Validation* method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 ::: { #func.mse_cv.args.r_list .sidebar }
-  - **r_list:** List of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1], calculated in `K`th iteration using the _K-Fold Cross-Validation_ method.
+  - **r_list:** List of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1], calculated in `K`th iteration using the *K-Fold Cross-Validation* method.
 
@@
 ::: { #func.union_cv_results.args.data_list .sidebar }
-  - **data_list:** List of data frames representing the results of the _N-Fold Cross-Validation_ method execution.;
+  - **data_list:** List of data frames representing the results of the *K-Fold Cross-Validation* method execution.;
 
@@
 \
-This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the _N-Fold Cross-Validation_) passed in the [data_list] argument into a single data frame for further processing.
+This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the *K-Fold Cross-Validation*) passed in the [data_list] argument into a single data frame for further processing.
 :::
@@
 
-Calculates the Mean Squared Errors (MSEs) for the *Overall Mean Rating (OMR) Model* using the *K-Fold Cross-Validation* method as described in section [OMR Model Building] of *this Report*.
+Validates the *Overall Mean Rating (OMR) Model* with use of *K-Fold Cross-Validation* method as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
 
@@
 
-The Mean Squared Errors (MSEs) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*.
+The Mean Squared Errors (MSEs) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object].
+
 :::
@@
 \
-Calculates the Root Mean Squared Error (RMSE) for the *Overall Mean Rating (OMR) Model* using the *K-Fold Cross-Validation* method as described in section [OMR Model Building] of *this Report*.
+Validates the *Overall Mean Rating (OMR) Model* with use of *K-Fold Cross-Validation* method as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 
-This function internally calls the [naive_model_MSEs](#func.naive_model_MSEs) function described above.
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [naive_model_MSEs](#func.naive_model_MSEs) function described above and then calculates the square root of the mean of the obtained results.
+:::
 :::
@@
 
-The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*.
+The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object].
 :::
@@
 
-Computes the *(Regularized) User+Movie (UM) Effect* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) parameter.
+Trains the *(Regularized) User+Movie (UM) Effect Model* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) parameter.
 
@@
 
-Trains the *(Regularized) User+Movie (UM) Effect Model* using the the _N-Fold Cross-Validation_ 
-as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Trains the *(Regularized) User+Movie (UM) Effect Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 
-Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for each iteration of the _N-Fold Cross-Validation_ applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
 It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
 
-The `N` value for the *N-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
 
@@
 
-Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) using _N-Fold Cross-Validation_.
+Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
 :::
@@
 
-Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.
+Validates the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 
-The function utilizes *N-Fold Cross-Validation* to calculate *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_MSE.cv.args.um_effect) argument using the validation datasets contained by the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_user_movie_effect_MSE](#func.calc_user_movie_effect_MSE) function for each iteration of the *N-Fold Cross-Validation* method, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
-
-The `N` value for the *N-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+The function calculates *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_MSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_effect_MSE](#func.calc_user_movie_effect_MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
 :::
@@
 
-The *MSE* value calculated for the *UM Effect Model* using the *N-Fold Cross-Validation*, where the `N` is the length of the [`edx_CV` Object].
+The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
 :::
@@
 
-Calculates *Root Mean Squared Error (RMSE)* for the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) using *N-Fold Cross-Validation*.
+Validates the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 
-The function utilizes *N-Fold Cross-Validation* to calculate *RMSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained by the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_user_movie_effect_MSE.cv](#func.calc_user_movie_effect_MSE.cv) function described above, to calculate the *MSE* for the *UME Model* using *N-Fold Cross-Validation*, and then calculates the square root of the result.
-
-The `N` value for the *N-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+The function calculates *RMSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_effect_MSE.cv](#func.calc_user_movie_effect_MSE.cv) function described above, to calculate the *MSE* for the *UME Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
 :::
@@
 
-The *RMSE* value calculated for the *UM Effect Model* using the *N-Fold Cross-Validation*, where the `N` is the length of the [`edx_CV` Object].
+The *RMSE* value calculated for the *UM Effect Model* using the *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
 :::
@@
 
-Here we have a list of sample objects we need to perform the _5-Fold Cross-Validation_ 
+`edx_CV` object is a list of sample objects we need to perform the *K-Fold Cross-Validation* 
 as explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6]:
@@
 
-::: {.noteblock data-latex=""}
 To create the `edx_CV` object, the above code snippet is used in the [make_source_datasets](#func.make_source_datasets) function described in the [Initializing Input Datasets] section of [Appendix A: Support Functions].
 
+The `K` value for the *K-Fold Cross-Validation* is determined by the length of the list composing the `edx_CV` object. In *this Project*, we choose `K = 5`.
+
+::: {.noteblock data-latex=""}
 The custom function [sample_train_validation_sets](#func.sample_train_validation_sets) used in the code snippet to split the original dataset (`edx` in this case) into *train* and *validation* datasets, is described in the [Data Processing Functions] section of [Appendix A: Support Functions].

### 2025-11-14 reports/capstone-movielens.site/05.appendix.Rmd
Minor fixes for functions' descriptions related to k-fold cross-validation.

@@
 
-This function produces datasets listed in the [Value](#func.make_source_datasets.value) section below and described in detail in [Appendix B: Models Training Datasets] using the `edx` as the original dataset.
+This function produces datasets listed in the [Value](#func.make_source_datasets.value) section below and described in detail in [Appendix B: Models Training Datasets], using the `edx` as the original dataset.
 
@@
 ::: { #func.union_cv_results.args.data_list .sidebar }
-  - **data_list:** List of data frames representing the results of the *K-Fold Cross-Validation* method execution.;
+  - **data_list:** List of data frames representing the results of the *K-Fold Cross-Validation* method execution.
 
@@
 \
-This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the *K-Fold Cross-Validation*) passed in the [data_list] argument into a single data frame for further processing.
+This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the *K-Fold Cross-Validation*) passed in the [data_list](#func.union_cv_results.args.data_list) argument into a single data frame for further processing.
 :::
@@
 
-The Mean Squared Errors (MSEs) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object].
+The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object].
 
@@
 
-Calculates *Mean Squared Error (MSE)* for the *UM Effect (UME) Model* produced by the  [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
+Validates the *UM Effect (UME) Model* produced by the  [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
 
@@
 
-To calculate the *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_MSE.args.um_effect) argument, the function uses the validation dataset passed in the [test_set](#func.calc_user_movie_effect_MSE.args.test_set) arg.
+The function calculates *Mean Squared Error (MSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_MSE.args.um_effect) argument using the validation dataset passed in the [test_set](#func.calc_user_movie_effect_MSE.args.test_set) arg.
 
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object].
 :::
@@
 
-The function calculates *RMSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+The function calculates *Root Squared Error (RMSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
 
@@
 
-The *RMSE* value calculated for the *UM Effect Model* using the *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
 :::

### 2025-11-14 reports/capstone-movielens.site/02-0.methods.Rmd
Capstone Report: `UME Model Building` completed.

@@
 
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 24.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_25-1].We will also use the _5-Fold Cross-Validation_ method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
-To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of the [Appendix A: Support Functions] of *this Report*), specifically designed for these operations:
+We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 24.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_24-1].We will also use the *K-Fold Cross-Validation* method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+
+To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of the [Appendix A: Support Functions] of *This Report*), specifically designed for these operations:
 
@@
   - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the _5-Fold Cross-Validation_ in the way explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+
+::: {.noteblock data-latex=""}
+The `K` value for the *K-Fold Cross-Validation* we use in *This Project* is determined by the length of the list composing the [`edx_CV` Object].
+In our case, the length of the `edx_CV` is 5, meaning we use *5-Fold Cross-Validation*.
+:::

### 2025-11-14 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Capstone Report: `UME Model Building` completed.

@@
 
-Let's begin our analysis by evaluating the simplest model described in [Section 24.1 *Case study: recommendation systems / A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook (New Edition)*[@IDS2_25-1], and then gradually refine it through further research.
+Let's begin our analysis by evaluating the simplest model described in [Section 24.1 *Case study: recommendation systems / A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook (New Edition)*[@IDS2_24-1], and then gradually refine it through further research.
 

### 2025-11-14 reports/capstone-movielens.site/02.4.UE-model.Rmd
Capstone Report: `UME Model Building` completed.

@@
 
-If we visualize the average rating for each user the way the the author shows, we can see that there is substantial variability in the average ratings across users[@IDS2_25-1]: 
+If we visualize the average rating for each user the way the the author shows, we can see that there is substantial variability in the average ratings across users[@IDS2_24-1]: 
 ```{r}
@@
 
-Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_25-1; @MFT_RS].
+Statistics textbooks refer to the $\alpha$s as treatment effects. In the Netflix challenge papers, they refer to them as _bias_[@IDS2_24-1; @MFT_RS].
 
@@
 As it is stated in the [Course Textbook](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects), it can be shown that the least squares estimate $\hat{\alpha}_i$ is just the average of $y_{i,j} - \hat{\mu}$ for each user $i$.
-So we can compute them this way[@IDS2_25-1]:
+So we can compute them this way[@IDS2_24-1]:
 ```{r eval=FALSE}

### 2025-11-14 reports/capstone-movielens.site/02.5.UME-model.Rmd
Capstone Report: `UME Model Building` completed.

@@
 
-::: {#textbook.25.1.movie_effects .sidebar }
-In [Section 24.1 *Case study: recommendation systems / Movie effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) of the *Course Textbook (New Edition)*, the author draws our attention to the fact that some movies are generally rated higher than others[@IDS2_25-1].
+::: {#textbook.24.1.movie_effects .sidebar }
+In [Section 24.1 *Case study: recommendation systems / Movie effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) of the *Course Textbook (New Edition)*, the author draws our attention to the fact that some movies are generally rated higher than others[@IDS2_24-1].
 :::
@@
 
-In the source mentioned [above](#textbook.25.1.movie_effects) the author also explains that in this case one can use a linear model with a _treatment effect_ $\beta_j$ for each movie, which can be interpreted as the movie effect, or the difference between the average rating for movie $j$ and the overall average $\mu$[@IDS2_25-1]:
+In the source mentioned [above](#textbook.24.1.movie_effects) the author also explains that in this case one can use a linear model with a _treatment effect_ $\beta_j$ for each movie, which can be interpreted as the movie effect, or the difference between the average rating for movie $j$ and the overall average $\mu$[@IDS2_24-1]:
 
@@
 
-### UME Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the [UME Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
-:::
-
-#### [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) Function {#func.train_user_movie_effect}
-\
-
-We use this function to build and train our model using the `train_set` dataset:
-```{r eval=FALSE}
-train_user_movie_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_effect
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions]).
-We will explain that later in the [User+Movie Effect Model Regularization] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
-In this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
-:::
-
-#### `train_user_movie_effect.cv` Function {#func.train_user_movie_effect.cv}
-\
-
-We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the *5-Fold Cross-Validation* method.
-Below, we provide the most important part of the code of that function:
-```{r eval=FALSE}
-train_user_movie_effect.cv <- function(lambda = 0){
-# ...
-  start <- put_start_date()
-  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
-  })
-  put_end_date(start)
-  put_log("Function: train_user_movie_effect.cv:
-User+Movie Effect list have been computed")
-
-  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-
-  user_movie_effect <- user_movie_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  # ...
-  user_movie_effect
-}
-
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross-Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions]).
-:::
-
-#### `calc_user_movie_effect_MSE` Function
-\
-
-The source code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the _Mean Squared Error (MSE)_ of the _UME Model_ for the given `Test Set` is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE <- function(test_set, um_effect){
-  mse.result <- test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(um_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    pull(resid) |> mse()
-
-  stopifnot(!is.na(mse.result))
-  mse.result
-}
-```
-
-#### `calc_user_movie_effect_MSE.cv` Function
-\
-
-The source code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the _5-Fold Cross-Validation_ **MSE**_ result of the _UME Model_ is provided below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv <- function(um_effect){
-  put_log("Function: user_movie_effects_MSE.cv:
-Computing the RMSE taking into account User+Movie Effects...")
-  start <- put_start_date()
-  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
-  })
-  put_end_date(start)
-
-  put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross-Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_effects_MSEs)
-}
-
-```
-
-#### `calc_user_movie_effect_RMSE` Function
-\
-
-The source code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE <- function(test_set, um_effect){
-  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-  sqrt(mse)
-}
-```
-
-#### `calc_user_movie_effect_RMSE.cv` Function { #func.calc_user_movie_effect_RMSE.cv }
-\
-
-The source code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the *5-Fold Cross-Validation* RMSE result of the `UME Model` is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross-Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
-  um_effect_RMSE
-}
-
-```
-
-\newpage
-
 ### UME Model Building
@@
 
-Below, we provide the most significant part of the code for training our model using the *5-Fold Cross-Validation* method:
+Below, we provide the most significant part of the code for training our model with the use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied:
 ```{r eval=FALSE}
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the [UME Model Utility Functions] section of [Appendix A: Support Functions].
+:::
+
 ```{r}
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the [UME Model Utility Functions] section) to calculate the *RMSE* for the *Current Model*;
+
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Result RMSEs Tibble Functions] section) to update and print the table above.
 :::
@@
  [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_ explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects[@IDS2_25-1]:
+The author also explains that the general idea of penalized regression is to control the total variability of the movie effects[@IDS2_24-1]:
 $$
@@
 Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0.
-The larger the $\lambda$, the more we shrink[@IDS2_25-1].
+The larger the $\lambda$, the more we shrink[@IDS2_24-1].
 

### 2025-11-14 reports/capstone-movielens.site/02-0.methods.Rmd
OMR, UE, UME models: review.

@@
 
-As a result of executing these functions, we will obtain the following datasets (detailed in [Appendix B: Models Training Datasets]), which we will use throughout the project:
+As a result of executing these functions, we will obtain the following datasets (detailed in [Appendix B: Models Training Datasets]), which we will use throughout *This Project*:
 
@@
 
-  - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the _5-Fold Cross-Validation_ in the way explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+  - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the *K-Fold Cross-Validation* in the way explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 

### 2025-11-14 reports/capstone-movielens.site/02-3.OMR-model.Rmd
OMR, UE, UME models: review.

@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the custom function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model Helper Functions] section of [Appendix A: Support Functions] to calculate *RMSEs* for the sequence of the deviation values.
+In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model Helper Functions] section of [Appendix A: Support Functions] to calculate *RMSEs* for the sequence of the deviation values.
 :::
@@
 ::: {.noteblock data-latex=""}
-To print the log, we use the custom function [print_log1](#func.print_log1) described in the [Logging Functions] section of [Appendix A: Support Functions].
+To print the log, we use the function [print_log1](#func.print_log1) described in the [Logging Functions] section of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) custom functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
 :::

### 2025-11-14 reports/capstone-movielens.site/02.4.UE-model.Rmd
OMR, UE, UME models: review.

@@
 ::: {.noteblock data-latex=""}
-The complete source code of the _User Effect Model RMSE_ computation is available in the [Compute RMSE for User Effect Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L341) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L341) script on _GitHub_.
-
+To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
 :::

### 2025-11-15 r/src/support-functions/common-helper.functions.R
Script refactored: common-helper.functions.R.

@@ -78,18 +78,6 @@ mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
   N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
   sums/(N + lambda)
 }
-get_fine_tune.param.endpoints <- function(preset.result) {
-
-  preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
-  
-  i <- preset.result.idx["start"]
-  j <- preset.result.idx["end"]
-  best.idx <- preset.result.idx["best"]
-  
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-}
 get_fine_tune.param.endpoints.idx <- function(preset.result) {
   best_RMSE <- min(preset.result$RMSE)
   best_RMSE.idx <- which.min(preset.result$RMSE)
@@ -117,6 +105,18 @@ get_fine_tune.param.endpoints.idx <- function(preset.result) {
   c(start = i, 
     end = j,
     best = best_RMSE.idx)
+}
+get_fine_tune.param.endpoints <- function(preset.result) {
+
+  preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
+  
+  i <- preset.result.idx["start"]
+  j <- preset.result.idx["end"]
+  best.idx <- preset.result.idx["best"]
+  
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
 }
 get_best_param.result <- function(param_values, rmses){
   best_pvalue_idx <- which.min(rmses)

### 2025-11-15 reports/capstone-movielens.site/05.appendix.Rmd
OMR, UE, UME models: review.

@@
 
+#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.get_fine_tune.param.endpoints.idx}
+\
+
+::: { #func.get_fine_tune.param.endpoints.idx.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
+
+```
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.args .sidebar }
+##### Arguments
+\
+
+::: { #func.get_fine_tune.param.endpoints.idx.args. .sidebar }
+  - **preset.result:** ;
+
+:::
+::: { #func.get_fine_tune.param.endpoints.idx.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.code .sidebar }
+##### Source Code
+\
+
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+:::
+:::
+
+#### [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.cmmn_hlp.rglr.fn.tmpl}
+\
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+cmmn_hlp.rglr.fn.tmpl()
+
+```
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+:::
+:::
+
 #### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
@@
 ::: {.noteblock data-latex=""}
-Note that the algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
+The algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
 That is, it is assumed that the function has a single minimum on the given interval.
@@
 ```{r eval=FALSE}
-regularize.test_lambda.UM_effect.cv()
+UME.lambda_RMSE <- regularize.test_lambda.UM_effect.cv(lambda)
 

### 2025-11-15 reports/capstone-movielens.site/work/func-descr.template.Rmd

@@
 ::: {.noteblock data-latex=""}
-The source code of the [cmmn_helper_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L0) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+The source code of the [cmmn_helper_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L0) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+:::
+:::
+
+### Regularization
+
+#### [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.cmmn_hlp.rglr.fn.tmpl}
+\
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+cmmn_hlp.rglr.fn.tmpl()
+
+```
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
 :::

### 2025-11-16 reports/capstone-movielens.site/05.appendix.Rmd
CReport:, function described: tune.model_param.

@@
 
-#### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) Function {#func.tune.model_param}
-\
-
-The function searches for the parameter value corresponding to the minimum value of the `RMSE` from the list of values specified by the `param_values` parameter.
+#### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) Function {#func.tune.model_param}
+\
+
+Implements an algorithm to find a value of the *regularization parameter* $\lambda$ that corresponds to the minimum value of the *Root Mean Squared Error (RMSE)* for the model under test (we call this the *best value of the regularization parameter* or *best value of $\lambda$*) from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
 
@@
 
-##### Arguments
-\
-
-  - **param_values:** A list of values to search for the value corresponding to the minimum value of the `RMSE` ;
+::: { #func.tune.model_param.args .sidebar }
+##### Arguments
+\
+
+::: { #func.tune.model_param.args.param_values .sidebar }
+  - **param_values:** Vector containing a sorted list of $\lambda$ values to search for the best one during the model regularization process;
+
+:::
 
 ::: { #func.tune.model_param.args.fn_tune.test.param_value .sidebar }
-  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.;
-
-:::  
-  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
-
-  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.
-
-##### Details
-\
-During execution, the function uses a helper function specified by the `fn_tune.test.param_value` parameter, which calculates the `RMSE` value for the given parameter from the list determined by the `param_values` parameter.
-
-::: {.noteblock data-latex=""}
-The algorithm assumes that the dependence of the `RMSE` on the input parameter is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function has a single minimum on the given interval.
+  - **fn_tune.test.param_value:** Model-specific helper function that validates the model by computing the model's *RMSE* value for a given value of the $\lambda$ parameter;
+
+:::
+
+::: { #func.tune.model_param.args.break.if_min .sidebar }
+  - **break.if_min:** (`TRUE` by default) Boolean value that determines whether the algorithm should terminate after completing the number of steps specified by the [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min) argument from the moment the minimum `RMSE` value is found;
+
+:::
+
+::: { #func.tune.model_param.args.steps.beyond_min .sidebar }
+  - **steps.beyond_min:** (default 2; only takes effect if [break.if_min](func.tune.model_param.args.break.if_min) is `TRUE`) Specifies the number of steps after finding the minimum *RMSE* value after which the algorithm should terminate.
+
+:::
+:::
+
+##### Details
+\
+The algorithm iterates through the $\lambda$ parameter values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the model's *RMSE* for each of them, using the helper function specified by the [fn_tune.test.param_value](#fn_tune.test.param_value) argument.
+
+When the minimum *RMSE* value is reached, the algorithm terminates if [break.if_min](#func.tune.model_param.args.break.if_min) is `FALSE`.
+Otherwise, the algorithm continues iterating and terminates after the number of cycles specified by the [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min) argument.
+
+::: {.noteblock data-latex=""}
+The algorithm assumes that the dependence of *RMSE* on the parameter $\lambda$ is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
+That is, it is assumed that the function can have only one minimum on a given interval.
 :::
@@
 \
-The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-:::
-
-##### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function:
+
+This function returns a list of two objects:
+
+  - A vector containing a *pair of values*: the found *best value of the regularization parameter* $\lambda$ for which the *RMSE* value is minimal, along with the minimal *RMSE* value itself;
+```{r eval=FALSE}
+  param_values.best_result <- c(param.best_value, 
+                                best_RMSE)
+```
+
+  - A data frame containing two variables:
+
+    - *parameter.value*: A vector containing all processed values of the parameter $\lambda$;
+
+    - *RMSE*: A vector containing the *RMSE* values corresponding to the processed values of $\lambda$.
+```{r eval=FALSE}
+tuned.result = data.frame(RMSE, parameter.value)
+```
+:::
+
+##### Source Code
+\
+Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) function:
 ```{r eval=FALSE}
@@
 ```
+
+::: {.noteblock data-latex=""}
+The source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) script on _GitHub_.
+:::
 

### 2025-11-16 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function description: tune.model_param.

@@
 
+\newpage
+
 #### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) Function {#func.tune.model_param}
@@
 ::: { #func.tune.model_param.args.steps.beyond_min .sidebar }
-  - **steps.beyond_min:** (default 2; only takes effect if [break.if_min](func.tune.model_param.args.break.if_min) is `TRUE`) Specifies the number of steps after finding the minimum *RMSE* value after which the algorithm should terminate.
-
-:::
-:::
-
-##### Details
-\
-The algorithm iterates through the $\lambda$ parameter values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the model's *RMSE* for each of them, using the helper function specified by the [fn_tune.test.param_value](#fn_tune.test.param_value) argument.
-
-When the minimum *RMSE* value is reached, the algorithm terminates if [break.if_min](#func.tune.model_param.args.break.if_min) is `FALSE`.
-Otherwise, the algorithm continues iterating and terminates after the number of cycles specified by the [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min) argument.
+  - **steps.beyond_min:** (2 by default; only takes effect if [break.if_min](#func.tune.model_param.args.break.if_min) is `TRUE`) Specifies the number of steps after finding the minimum *RMSE* value after which the algorithm should terminate.
+
+:::
+:::
+
+##### Details
+\
+
+The algorithm iterates through the $\lambda$ parameter values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the model's *RMSE* for each of them, using the helper function specified by the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument.
+
+The algorithm continues iterating until the end of the  $\lambda$ parameter values list if [break.if_min](#func.tune.model_param.args.break.if_min) is `FALSE`.
+
+Otherwise, the algorithm terminates after the number of cycles specified by the argument [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min) has completed since the minimum *RMSE* value was reached.
 

### 2025-11-17 reports/capstone-movielens.site/05.appendix.Rmd
Describing helper function (in progress): model.tune.param_range.

@@
 ::: { #func.tune.model_param.args.param_values .sidebar }
-  - **param_values:** Vector containing a sorted list of $\lambda$ values to search for the best one during the model regularization process;
+  - **param_values:** Numeric vector containing a sorted list of $\lambda$ values to search for the best one during the model regularization process;
 
@@
 ::: { #func.tune.model_param.args.break.if_min .sidebar }
-  - **break.if_min:** (`TRUE` by default) Boolean value that determines whether the algorithm should terminate after completing the number of steps specified by the [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min) argument from the moment the minimum `RMSE` value is found;
+  - **break.if_min:** (Optional, `TRUE` by default) Boolean value that determines whether the algorithm should terminate after completing the number of steps specified by the [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min) argument from the moment the minimum `RMSE` value is found;
 
@@
 ::: { #func.tune.model_param.args.steps.beyond_min .sidebar }
-  - **steps.beyond_min:** (2 by default; only takes effect if [break.if_min](#func.tune.model_param.args.break.if_min) is `TRUE`) Specifies the number of steps after finding the minimum *RMSE* value after which the algorithm should terminate.
+  - **steps.beyond_min:** (Optional, 2 by default; only takes effect if [break.if_min](#func.tune.model_param.args.break.if_min) is `TRUE`) Specifies the number of steps after finding the minimum *RMSE* value after which the algorithm should terminate.
 
@@
 ::: {.noteblock data-latex=""}
-The source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) script on _GitHub_.
+The complete source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) script on _GitHub_.
 :::
@@
 
-The function fine-tunes the model by searching for the best possible value of the input parameter over a given interval for which the corresponding `RMSE` value is minimal.
+Implements an algorithm for fine-tuning the model under test by finding the most precise value possible of the *regularization parameter* $\lambda$ that corresponds to the minimum value of the *Root Mean Squared Error (RMSE)* (we call this the *best value of the regularization parameter* or *best value of $\lambda$*) over a given interval determined by the start and end values of the interval passed in the [loop_starter] argument.
 
@@
 
-##### **Parameters**
+::: { #func.model.tune.param_range.args .sidebar }
+##### Arguments
 \
@@
 \
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
-`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
-For this purpose, the sequence step is calculated as follows:
+A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval over which the value of the parameter $\lambda$ that minimizes *RMSE* has to be found.
+
+The `dvs` is a divisor used to calculate the step size for partitioning the interval into a sequence of $\lambda$ values, among which the value that minimizes *RMSE* has to be found.
+
+So the step size of the sequence is calculated as follows:
 $$
@@
 
-The sequence obtained as a result of the transformation is equivalent to the one generated by the function `seq` as follows:
+The sequence obtained as a result of the transformation is equivalent to the one generated by the function [base::seq](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/seq) as follows:
 ```{r eval=FALSE}
@@
 ```  
-In fact, the `seq` function is called internally to generate the sequence during the execution of the `model.tune.param_range` function.
+In fact, the `seq` function is called internally to generate the sequence during the execution of the algorithm.
 :::
@@
 \
-To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.
+To improve performance, the algorithm caches intermediate results in the file system. The value passed in *this argument* specifies the path to the directory where the files are cached.
 :::
@@
 \
-The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.
+The algorithm generates unique names for cache files based on this and the [loop_starter](#func.model.tune.param_range.args.loop_starter) arguments' values, as well as a few other intermediate values calculated at runtime.
 :::
@@
 \
-This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+Model-specific helper function name to pass to the [same-named argument](#func.tune.model_param.args.fn_tune.test.param_value) of the [tune.model_param](#func.tune.model_param) function (see description above) that is called internally during the execution of the algorithm.
 :::
@@
 ::: { #func.model.tune.param_range.args.max.identical.min_RMSE.count .sidebar }
-###### ***max.identical.min_RMSE.count = 4***
-\
-If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter.
+###### ***max.identical.min_RMSE.count***
+\
+(Optional, 4 by default) If more than one identical minimum *RMSE* value is calculated during execution, the number of identical minimums is limited by the value of *this argument*.
 When it is reached, the algorithm considers the task execution to be complete.
@@
 ::: { #func.model.tune.param_range.args.endpoint.min_diff .sidebar }
-###### ***endpoint.min_diff = 0***
-\
-Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (for details, see the `Details` section [below](#func.model.tune.param_range.details)).
+###### ***endpoint.min_diff***
+\
+(Optional, 0 by default) Defines the sensitivity threshold for determining the neighborhood boundaries of the minimum `RMSE` value (see the [Details](#func.model.tune.param_range.details) section below for more details).
 :::
@@
 ::: { #func.model.tune.param_range.args.break.if_min .sidebar }
-###### ***break.if_min = TRUE***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+###### ***break.if_min***
+\
+(Optional, `TRUE` by default) Boolean value to pass to the [same-named argument](#func.tune.model_param.args.break.if_min) of the [tune.model_param](#func.tune.model_param) function (see description above) that is called internally during the execution of the algorithm.
 :::
@@
 ::: { #func.model.tune.param_range.args.steps.beyond_min .sidebar }
-###### ***steps.beyond_min = 2***
-\
-This is a parameter that is required for the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).
+###### ***steps.beyond_min***
+\
+(Optional, 2 by default) Numeric value to pass to the [same-named argument](#func.tune.model_param.args.steps.beyond_min) of the [tune.model_param](#func.tune.model_param) function (see description above) that is called internally during the execution of the algorithm.
+:::
+:::
 
@@
 \
-First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.args.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.
-
-The `tune.model_param` function returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
+During execution, the algorithm performs the following steps:
+
+  1. Creates a vector containing a sequence of $\lambda$ values generated as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above.
+
+  2.
+Calls the [tune.model_param](#func.tune.model_param) function, passing the vector created in the previous step to the [param_values](#func.tune.model_param.args.param_values) argument (along with the values of the other arguments) of the `tune.model_param` function.
+
+returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
 

### 2025-11-17 reports/capstone-movielens.site/05.appendix.Rmd
Describing helper function (in progress): model.tune.param_range.

@@
 
-The `dvs` is a divisor used to calculate the step size for partitioning the interval into a sequence of $\lambda$ values, among which the value that minimizes *RMSE* has to be found.
-
-So the step size of the sequence is calculated as follows:
+The `dvs` is a divisor used to calculate the *step size* for partitioning the interval into a sequence of $\lambda$ values, among which the value that minimizes *RMSE* has to be found.
+
+So the *step size* of the sequence is calculated as follows:
 $$
@@
 ```
-In fact, the `seq` function is called internally to generate the sequence during the execution of the algorithm.
+
+::: {.noteblock data-latex=""}
+In the function body, the *step size* is stored in the local variable `seq_increment`, and the values of $\start$, $\end$, and $\dvs$ are stored in the local variables `seq_start`, `seq_end`, and `interval_divisor`, respectively.
+:::
+
+In fact, the `seq` function is called internally to generate the sequence during the algorithm's execution.
+
+Thus, the sequence is generated by the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L256):
+```{r eval=FALSE}
+    test_param_vals <- seq(seq_start, seq_end, seq_increment)
+```
 :::
@@
 \
-During execution, the algorithm performs the following steps:
-
-  1. Creates a vector containing a sequence of $\lambda$ values generated as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above.
+During execution, the algorithm organizes a cycle consisting of the following steps:
+
+  1.
+Calculates the divisor to calculate the step size for partitioning the interval into a sequence of $\lambda$ values as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L240):
+```{r eval=FALSE}
+    seq_increment <- (seq_end - seq_start)/interval_divisor 
+```
+
+  2. Checks if the *step size* of the generated sequence is less than the minimum allowed value (in the current implementation, we use `1e-13`), and if `TRUE`, breaks out of the loop:
+```{r eval=FALSE}
+    if (seq_increment < 0.0000000000001) {
+      warning("Function `model.tune.param_range`:
+parameter value increment is too small.")
+
+      put_log2("Function `model.tune.param_range`:
+Final best RMSE for `parameter value = %1`: %2",
+               param_values.best_result["param.best_value"],
+               param_values.best_result["best_RMSE"])
+
+      put(param_values.best_result)
+      # browser()
+      break
+    }
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom function [put_log2](#func.put_log2) described above in the [Logging Functions] section of *This Appendix*.
+:::
+
+  3. Creates a vector containing a sequence of $\lambda$ values generated as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above.
 

### 2025-11-18 reports/capstone-movielens.site/05.appendix.Rmd
Update: Describing helper function (in progress): model.tune.param_range.

@@
 ::: {.noteblock data-latex=""}
-In the function body, the *step size* is stored in the local variable `seq_increment`, and the values of $\start$, $\end$, and $\dvs$ are stored in the local variables `seq_start`, `seq_end`, and `interval_divisor`, respectively.
+In the function body, the *step size* is stored in the local variable `seq_increment`, and the values of $start$, $end$, and $dvs$ are stored in the local variables `seq_start`, `seq_end`, and `interval_divisor`, respectively.
 :::
@@
 
-  2. Checks if the *step size* of the generated sequence is less than the minimum allowed value (in the current implementation, we use `1e-13`), and if `TRUE`, breaks out of the loop:
+  2.
+Checks if the *step size* of the generated sequence is less than the minimum allowed value (in the current implementation, we use `1e-13`), and if `TRUE`, breaks out of the loop.
+Otherwise, the execution continues to the next step:
 ```{r eval=FALSE}
@@
 
-  3. Creates a vector containing a sequence of $\lambda$ values generated as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above.
-
-  2.
-Calls the [tune.model_param](#func.tune.model_param) function, passing the vector created in the previous step to the [param_values](#func.tune.model_param.args.param_values) argument (along with the values of the other arguments) of the `tune.model_param` function.
+  3.
+If the *step size* is no less than the minimum allowed value (`seq_increment >= 1e-13` in our case) creates a vector containing a sequence of $\lambda$ values generated as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above:
+```{r eval=FALSE}
+    test_param_vals <- seq(seq_start, seq_end, seq_increment)
+```
+
+  4.
+Calls the [tune.model_param](#func.tune.model_param) helper function, passing the vector created in the previous step to the [param_values](#func.tune.model_param.args.param_values) argument (along with the values of the other arguments of the function `tune.model_param`).
 

### 2025-11-18 reports/capstone-movielens.site/05.appendix.Rmd
Fixes for functions` descriptions: `tune.model_param` ,`model.tune.param_range`.

@@
 
-We call this function internally from the functions that compute the _penalized estimates_  as described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1].
+We call this function internally from the functions that compute the _penalized estimates_  as described in [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook (New Edition)*[@IDS2_24-1].
 
@@
 
-Implements an algorithm to find a value of the *regularization parameter* $\lambda$ that corresponds to the minimum value of the *Root Mean Squared Error (RMSE)* for the model under test (we call this the *best value of the regularization parameter* or *best value of $\lambda$*) from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
+Implements an algorithm for selecting the best value of the *regularization parameter* $\lambda$ from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
 
@@
 
-The algorithm iterates through the $\lambda$ parameter values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the model's *RMSE* for each of them, using the helper function specified by the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument.
+With the approach used in this algorithm, the best value of the *regularization parameter* $\lambda$ (we call this the *best value of the regularization parameter* or the *best value of $\lambda$*) is considered to be the value corresponding to the minimum value of the *Root Mean Square Error (RMSE)* for the model being tested.
+
+To find the best value of the $\lambda$ parameter, the algorithm iterates over the values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the *RMSE* of the model for each of them, using the helper function specified in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument.
 
@@
 
-Implements an algorithm for fine-tuning the model under test by finding the most precise value possible of the *regularization parameter* $\lambda$ that corresponds to the minimum value of the *Root Mean Squared Error (RMSE)* (we call this the *best value of the regularization parameter* or *best value of $\lambda$*) over a given interval determined by the start and end values of the interval passed in the [loop_starter] argument.
+Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *regularization parameter* $\lambda$ over a given interval determined by the start and end values of the interval passed in the [loop_starter] argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
 
@@
 \
-During execution, the algorithm organizes a cycle consisting of the following steps:
+
+With the approach used in this algorithm, the best value of the *regularization parameter* $\lambda$ (we call this the *best value of the regularization parameter* or the *best value of $\lambda$*) is considered to be the value corresponding to the minimum value of the *Root Mean Square Error (RMSE)* for the model being tested.
+
+During the execution, the algorithm organizes a cycle consisting of the following steps:
 

### 2025-11-18 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for function: `model.tune.param_range`.

@@
 
-Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *regularization parameter* $\lambda$ over a given interval determined by the start and end values of the interval passed in the [loop_starter] argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *regularization parameter* $\lambda$ over a given interval determined by the $start$ and $end$ values of the interval passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
 

### 2025-11-19 reports/capstone-movielens.site/05.appendix.Rmd
Update  for function: `model.tune.param_range`.

--- 2025-11-18 reports/capstone-movielens.site/05.appendix.Rmd
@@
 
+Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) (see the description below) and, using one more helper function [get_best_param.result](#func.get_best_param.result)  (see the description below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
+
 ::: { #func.get_fine_tune.param.endpoints.idx.usage .sidebar }
@@
 
-Implements an algorithm for selecting the best value of the *regularization parameter* $\lambda$ from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+Implements an algorithm for selecting the best value of the *regularization parameter* $\lambda$ from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
 
@@
 
-Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *regularization parameter* $\lambda$ over a given interval determined by the start and end values of the interval passed in the [loop_starter] argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *regularization parameter* $\lambda$ over a given interval determined by the $start$ and $end$ values of the interval passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
 
@@
   2.
-Checks if the *step size* of the generated sequence is less than the minimum allowed value (in the current implementation, we use `1e-13`), and if `TRUE`, breaks out of the loop.
-Otherwise, the execution continues to the next step:
+Checks if the *step size* of the generated sequence is less than the minimum allowed value (in the current implementation, we use `1e-13`), and if so, exits the loop.
+Otherwise, proceeds to the [next step](#func.model.tune.param_range.details.step3):
 ```{r eval=FALSE}
@@
 
+::: { #func.model.tune.param_range.details.step3 .sidebar }
   3.
-If the *step size* is no less than the minimum allowed value (`seq_increment >= 1e-13` in our case) creates a vector containing a sequence of $\lambda$ values generated as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above:
+If the *step size* is no less than the minimum allowed value (`seq_increment >= 1e-13` in our case), creates a vector containing a sequence of $\lambda$ values (as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above) using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L256):
 ```{r eval=FALSE}
@@
 
+:::
+
+::: { #func.model.tune.param_range.details.step4 .sidebar }
   4.
-Calls the [tune.model_param](#func.tune.model_param) helper function, passing the vector created in the previous step to the [param_values](#func.tune.model_param.args.param_values) argument (along with the values of the other arguments of the function `tune.model_param`).
+Generates a unique name for the current iteration's cache file based on the values passed in the [cache_file_base_name](#func.model.tune.param_range.args.cache_file_base_name) and [loop_starter](#func.model.tune.param_range.args.loop_starter) arguments, along with the values stored in the local variables `seq_start`, `seq_end`, and `interval_divisor`, concatenates the name with the path passed in the [tune_dir_path](#func.model.tune.param_range.args.tune_dir_path) argument, and stores the value in the local variable `file_path_tmp`:
+```{r eval=FALSE}
+    file_name_tmp <- cache_file_base_name |>
+      str_c("_") |>
+      str_c(as.character(loop_starter[1])) |>
+      str_c("_") |>
+      str_c(as.character(loop_starter[3])) |>
+      str_c("_") |>
+      str_c(as.character(interval_divisor)) |>
+      str_c(".") |>
+      str_c(as.character(seq_start)) |>
+      str_c("-") |>
+      str_c(as.character(seq_end)) |>
+      str_c(".RData")
+
+    file_path_tmp <- file.path(tune_dir_path, file_name_tmp)
+
+    put_log1("Function `model.tune.param_range`:
+File path generated: %1", file_path_tmp)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom function [put_log1](#func.put_log2) described above in the [Logging Functions] section of *This Appendix*.
+:::
+:::
+
+5.
+Checks whether a file with the full name stored in the `file_path_tmp` variable exists, and if so, loads all the necessary information for the current iteration from it and goes to [step 8](#func.model.tune.param_range.details.step8).
+Otherwise, proceeds to the [next step](#func.model.tune.param_range.details.step6):
+```{r eval=FALSE}
+    if (file.exists(file_path_tmp)) {
+      put_log1("Function `model.tune.param_range`:
+Loading tuning data from file: %1...", file_path_tmp)
+
+      load(file_path_tmp)
+      put_log1("Function `model.tune.param_range`:
+Tuning data has been loaded from file: %1", file_path_tmp)
+
+      tuned.result <- tuned_result$tuned.result
+    } else {
+      # ...
+    }
+```
+
+::: { #func.model.tune.param_range.details.step6 .sidebar }
+  6.
+Calls the helper function [tune.model_param](#func.tune.model_param), passing the vector created earlier in [step 3](#func.model.tune.param_range.details.step3) to the [param_values](#func.tune.model_param.args.param_values) argument (along with the values of the rest arguments: [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value), [break.if_min](#func.tune.model_param.args.break.if_min), [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min)) of the called function and stores the returned result in the local variable `tuned_result`:
+```{r eval=FALSE}
+      tuned_result <- tune.model_param(test_param_vals, 
+                                        fn_tune.test.param_value,
+                                        break.if_min,
+                                        steps.beyond_min)
+```
+
+:::
+
+::: { #func.model.tune.param_range.details.step7 .sidebar }
+  7.
+Extracts the internal data frame stored in the variable `tuned_result$tuned.result` from the data returned by the [tune.model_param](#func.tune.model_param) helper function (and saved in the local variable `tuned_result`) in the [previous step](#func.model.tune.param_range.details.step6) and stores it in the local variable `tuned.result`.
+Then stores `tuned_result` along with the necessary auxiliary information in the cache file with the full name created earlier in [step 4](#func.model.tune.param_range.details.step4):
+```{r eval=FALSE}
+      tuned.result <- tuned_result$tuned.result
+
+      save(tuned_result,
+           param.best_value,
+           seq_increment,
+           interval_divisor,
+           file = file_path_tmp)
+
+      put_log1("Function `model.tune.param_range`:
+File saved: %1", file_path_tmp)
+```
+:::
+
+::: { #func.model.tune.param_range.details.step8 .sidebar }
+Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) (see the description below) and, using one more helper function [get_best_param.result](#func.get_best_param.result)  (see the description below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.model.tune.param_range.details.step .sidebar }
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.model.tune.param_range.details.step?? .sidebar }
+
+```{r eval=FALSE}
+```
+:::
 
 returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
+```{r eval=FALSE}
+```
 
@@
                              fn_tune.test.param_value,
+                             # interval_divisor.multiplier = 4,
                              max.identical.min_RMSE.count = 4,
-                             is.cv = TRUE,
                              endpoint.min_diff = 0, #1e-07,
@@
   seq_end <- loop_starter[2]
+
+  prm_val.leftmost <- seq_start
+  prm_val.rightmost <- seq_end
+
+  RMSE.leftmost <- NA
+  RMSE.rightmost <- NA
+
   interval_divisor <- loop_starter[3]
-
   if (interval_divisor < 4) {
@@
   }
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
 
@@
 parameter value increment is too small.")
+
+      put_log2("Function `model.tune.param_range`:
+Final best RMSE for `parameter value = %1`: %2",
+               param_values.best_result["param.best_value"],
+               param_values.best_result["best_RMSE"])
+
+      put(param_values.best_result)
       break
@@
 
+    file_name_tmp <- cache_file_base_name |>
+      str_c("_") |>
+      str_c(as.character(loop_starter[1])) |>
+      str_c("_") |>
+      str_c(as.character(loop_starter[3])) |>
+      str_c("_") |>
+      str_c(as.character(interval_divisor)) |>
+      str_c(".") |>
+      str_c(as.character(seq_start)) |>
+      str_c("-") |>
+      str_c(as.character(seq_end)) |>
+      str_c(".RData")
+
+    file_path_tmp <- file.path(tune_dir_path, file_name_tmp)
+
+    put_log1("Function `model.tune.param_range`:
+File path generated: %1", file_path_tmp)
+
+    if (file.exists(file_path_tmp)) {
+      put_log1("Function `model.tune.param_range`:
+Loading tuning data from file: %1...", file_path_tmp)
+
+      load(file_path_tmp)
+      put_log1("Function `model.tune.param_range`:
+Tuning data has been loaded from file: %1", file_path_tmp)
+
+      tuned.result <- tuned_result$tuned.result
+    } else {
       tuned_result <- tune.model_param(test_param_vals, 
@@
       tuned.result <- tuned_result$tuned.result
+
+      save(tuned_result,
+           param.best_value,
+           seq_increment,
+           interval_divisor,
+           file = file_path_tmp)
+
+      put_log1("Function `model.tune.param_range`:
+File saved: %1", file_path_tmp)
+    }
+
     plot(tuned.result$parameter.value, tuned.result$RMSE)
-
     bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
@@
       warning("`tuned.result$parameter.value` sequential start index are the same or greater than end one.")
+      put_log1("Function `model.tune.param_range`:
+Current minimal RMSE: %1", rmse_min)
+
+      put_log2("Function `model.tune.param_range`:
+Reached minimal RMSE for the test parameter value = %1: %2",
+               param_values.best_result["param.best_value"],
+               param_values.best_result["best_RMSE"])
+
+      put(param_values.best_result)
       break
@@
 
+      put_log2("Function `model.tune.param_range`:
+Current minimal RMSE for `parameter value = %1`: %2",
+               tuned.result$parameter.value[which.min(tuned.result$RMSE)],
+               min_RMSE)
+
+      put_log2("Function `model.tune.param_range`:
+So far reached best RMSE for `parameter value = %1`: %2",
+               param_values.best_result["param.best_value"],
+               param_values.best_result["best_RMSE"])
+
+      put(param_values.best_result)
+
       if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
@@
                 max.identical.min_RMSE.count)
+        put(tuned.result$RMSE)
 
@@
                                 tuned.result$RMSE)
+        put_log2("Function `model.tune.param_range`:
+      Reached the best RMSE for `parameter value = %1`: %2",
+                 param_values.best_result["param.best_value"],
+                 param_values.best_result["best_RMSE"])
         break
       }
-
     } else if (best_RMSE < min_RMSE) {
+      warning("Current minimal RMSE is greater than previously computed best value: ",
+              best_RMSE, "
+Currently computed minial value is: ", min_RMSE)
       stop("Current minimal RMSE is greater than previously computed best value: ",
@@
                           tuned.result$RMSE)
+
+    put_log2("Function `model.tune.param_range`:
+Currently reached best RMSE for `parameter value = %1`: %2",
+             param_values.best_result["param.best_value"],
+             param_values.best_result["best_RMSE"])
+
+    put(param_values.best_result)
   }
@@
   n <- length(tuned.result$parameter.value)
+
   parameter.value <- tuned.result$parameter.value
@@
   }
-
   list(best_result = param_values.best_result,

### 2025-11-20 reports/capstone-movielens.site/bak/05.appendix000.Rmd
Function described: get_fine_tune.param.endpoints.idx

--- 2025-11-19 reports/capstone-movielens.site/05.appendix.Rmd
@@
 
-#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) (see the description below) and, using one more helper function [get_best_param.result](#func.get_best_param.result)  (see the description below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
+#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
+\
+
+Implements an algorithm that finds the pair of indices of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
+
+::: {.noteblock data-latex=""}
+The algorithm assumes that the set of values in the *RMSE* column is a monotonically non-increasing function of the index until the minimum is reached and monotonically non-decreasing thereafter.
+That is, it is assumed that the function can have only one minimum on the given set.
+:::
 
@@
 
-```{r eval=FALSE}
+::: {.noteblock data-latex=""}
+The element named `tuned.result` of the *list* returned by the [tune.model_param](#func.tune.model_param) function described below is a *data frame* suitable for use as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
+:::
+
+The following code snippet shows how to use the data returned by the [tune.model_param](#func.tune.model_param) function as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument:
+```{r eval=FALSE}
+cv.UME.preset.result <- 
+  tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)
+
+```
+```{r}
+cv.UME.preset.result$tuned.result |>
+  data.plot(title = TeX(r'[UME Model Regularization: $\lambda$ Range Pre-configuration]'),
+              xname = "parameter.value", 
+              yname = "RMSE", 
+              xlabel = TeX(r'[$\lambda$]'), 
+              ylabel = "RMSE")
+
+preset.result <- cv.UME.preset.result$tuned.result
 preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
-
-```
+print(preset.result.idx)
+```
+
 :::
@@
 
-::: { #func.get_fine_tune.param.endpoints.idx.args. .sidebar }
-  - **preset.result:** ;
-
-:::
-::: { #func.get_fine_tune.param.endpoints.idx.args. .sidebar }
-  - **:** ;
-
-:::
-:::
-
-::: { #func.get_fine_tune.param.endpoints.idx.details .sidebar }
-##### Details
-\
-
+::: {#func.get_fine_tune.param.endpoints.idx.args.preset.result .sidebar }
+  - **preset.result:** Any data frame that has an *RMSE* column containing the `RMSE` values corresponding to the *regularization parameter* $\lambda$ values for the model being regularized, as described in the [Details](#func.tune.model_param.details) section of the [tune.model_param](#func.tune.model_param) function description below.
+
+:::
 :::
@@
 \
+A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start, # interval start index
+    end,   # interval end index
+    best)  # index of the best `RMSE`
+```
+
+In the example shown above in the [Usage](#func.get_fine_tune.param.endpoints.idx.usage) section we can see the value return by *this function*:
+```{r}
+print(preset.result.idx)
+```
 
@@
 
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
-:::
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints.idx <- function(preset.result) {
+  best_RMSE <- min(preset.result$RMSE)
+  best_RMSE.idx <- which.min(preset.result$RMSE)
+  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
+
+  preset.result.N <- length(preset.result$RMSE)
+  i <- best_RMSE.idx
+  j <- i
+
+  while (i > 1) {
+    i <- i - 1
+
+    if (preset.result$RMSE[i] > best_RMSE) {
+      break
+    }
+  }
+
+  while (j < preset.result.N) {
+    j <- j + 1
+
+    if (preset.result$RMSE[j] > best_RMSE) {
+      break
+    }
+  }
+
+  c(start = i, 
+    end = j,
+    best = best_RMSE.idx)
+}
+
+```
+:::
+
+\newpage
+
+#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) Function {#func.get_fine_tune.param.endpoints}
+\
+
+The algorithm finds the values of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
+
+##### Signature
+\
+```{r eval=FALSE}
+get_fine_tune.param.endpoints <- function(preset.result) {
+  # ...
+
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+}
+```
+
+##### Arguments
+\
+
+::: {#func.get_fine_tune.param.endpoints.args.preset.result .sidebar }
+###### ***preset.result***
+\
+A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
+Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
+```{r eval=FALSE}
+    tuned_result <- tune.model_param(test_param_vals, 
+                                  fn_tune.test.param_value,
+                                  break.if_min,
+                                  steps.beyond_min)
+
+    tuned.result <- tuned_result$tuned.result
+    # tuned.result = data.frame(RMSE, parameter.value)
+    # ...
+    bound.idx <- get_fine_tune.param.endpoints(tuned.result)
+    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
+```
+:::
+
+##### Details
+\
+
+Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) parameter.
+
+##### Value
+\
+A vector containing the element value corresponding to the minimum `RMSE` in a given sequence, along with the values of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+```
+
+##### Source Code
+\
+The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) function is provided below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints <- function(preset.result) {
+
+  preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
+
+  i <- preset.result.idx["start"]
+  j <- preset.result.idx["end"]
+  best.idx <- preset.result.idx["best"]
+
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+}
+```
+
+\newpage
+
+#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) Function {#func.get_best_param.result}
+\
+
+##### Signature
+\
+```{r eval=FALSE}
+get_best_param.result <- function(param_values, rmses){
+  # ...
+
+  c(param.best_value = param_values[best_pvalue_idx], 
+    best_RMSE = rmses[best_pvalue_idx])
+
+```
+
+##### Arguments
+\
+A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
+
+  - **param_values:** A vector containing the values of the input parameters for tuning;; 
+  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
+
+##### Details
+\
+Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
+
+##### Value
+\
+A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
+```{r eval=FALSE}
+c(param.best_value, best_RMSE)
+```
+
+##### Source Code
+\
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is shown below:
+```{r eval=FALSE}
+get_best_param.result <- function(param_values, rmses){
+  best_pvalue_idx <- which.min(rmses)
+  c(param.best_value = param_values[best_pvalue_idx], 
+    best_RMSE = rmses[best_pvalue_idx])
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) script on _GitHub_.
 :::
@@
 
+::: { #func.tune.model_param.details .sidebar }
 ##### Details
@@
 ::: {.noteblock data-latex=""}
-The algorithm assumes that the dependence of *RMSE* on the parameter $\lambda$ is a monotonically decreasing function until a minimum is reached and monotonically increasing thereafter.
-That is, it is assumed that the function can have only one minimum on a given interval.
+The algorithm assumes that the set of the *RMSE* values is a monotonically non-increasing function of the *regularization parameter* $\lambda$ until the minimum is reached and monotonically non-decreasing thereafter.
+That is, it is assumed that the function can have only one minimum on the given set.
+:::
 :::
@@
 \newpage
-
-#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) Function {#func.get_fine_tune.param.endpoints}
-\
-
-The algorithm finds the values of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-##### Signature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints <- function(preset.result) {
-  # ...
-
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-}
-```
-
-##### Arguments
-\
-
-::: {#func.get_fine_tune.param.endpoints.args.preset.result .sidebar }
-###### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-##### Details
-\
-
-Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) parameter.
-
-##### Value
-\
-A vector containing the element value corresponding to the minimum `RMSE` in a given sequence, along with the values of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-```
-
-##### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) function is provided below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints <- function(preset.result) {
-
-  preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
-
-  i <- preset.result.idx["start"]
-  j <- preset.result.idx["end"]
-  best.idx <- preset.result.idx["best"]
-
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-}
-```
-
-\newpage
-
-#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-##### Signature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  # ...
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-```
-
-##### Arguments
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.args.preset.result .sidebar }
-###### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-##### Details
-\
-The algorithm finds the indices of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-##### Value
-\
-A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-##### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-\newpage
-
-#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) Function {#func.get_best_param.result}
-\
-
-##### Signature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-##### Arguments
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-##### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-##### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-##### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) script on _GitHub_.
-:::
 

### 2025-11-20 reports/capstone-movielens.site/bak/05.appendix.bak.Rmd

--- 2025-11-20 reports/capstone-movielens.site/bak/05.appendix000.Rmd
@@
 
+\newpage
+
 #### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
@@
 cv.UME.preset.result$tuned.result |>
-  data.plot(title = TeX(r'[UME Model Regularization: $\lambda$ Range Pre-configuration]'),
+  data.plot(title = "UME Model Regularization: `lambda` Range Pre-configuration",
               xname = "parameter.value",
               yname = "RMSE",
-              xlabel = TeX(r'[$\lambda$]'), 
+              xlabel = "Regularization parameter (`lambda`)",
               ylabel = "RMSE")

### 2025-11-20 reports/capstone-movielens.site/work/draft-snippert.Rmd

@@
 :::
+
+### Regularization Functions {#appndx_a.CHF.regularization}
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section are available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) script on _GitHub_.
+:::
+
+#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) Function {#func.mean_reg}
+\
+
+Calculates the arithmetic mean taking into account the _regularization parameter_ $\lambda$ passed in the [lambda](#func.mean_reg.args.lambda) argument. We will call it the _penalized mean_.
+
+::: { #func.mean_reg.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+mean_reg(vals, lambda = 0, na.rm = TRUE)
+
+```
+:::
+
+::: { #func.mean_reg.args .sidebar }
+##### Arguments
+\
+
+::: { #func.mean_reg.args.vals .sidebar }
+  - **vals:** Values (usually a numeric vector) to calculate the _penalized mean_;
+
+:::
+::: { #func.mean_reg.args.lambda .sidebar }
+  - **lambda:** (0 by default) _Regularization parameter_ $\lambda$ used in the _Regularization techniques_.
+
+:::
+  - **na.rm:** a logical evaluating to TRUE or FALSE indicating whether NA values should be stripped before the computation proceeds.
+
+:::
+
+::: { #func.mean_reg.details .sidebar }
+##### Details
+\
+
+The function calculates the _penalized mean_ of the values passed in the [vals](#func.mean_reg.args.vals) argument as follows:
+$$
+\mu(\lambda) = \frac{1}{\lambda + N} \sum_{i=1}^{N} x_i
+$$
+
+When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean:
+$$
+\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
+$$
+
+We call this function internally from the functions that compute the _penalized estimates_  as described in [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+
+::: {.noteblock data-latex=""}
+If the [lambda](#func.mean_reg.args.lambda) parameter is `0` (the default), the function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean), calling with the parameter `trim = 0` (the default for the `base::mean` function).
+:::
+:::
+
+::: { #func.mean_reg.value .sidebar }
+##### Value
+\
+
+The [penalized mean](#func.mean_reg.details) of the values passed in the [vals](#func.mean_reg.args.vals) argument.
+:::
+
+::: { #func.mean_reg.code .sidebar }
+##### Source Code
+\
+
+The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) function is shown below:
+```{r eval=FALSE}
+mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
+  if (is.na(lambda)) {
+    stop("Function: mean_reg
+`lambda` is `NA`")
+  }
+
+  names(lambda) <- NULL
+  sums <- sum(vals, na.rm = na.rm)
+  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
+  sums/(N + lambda)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) script on _GitHub_.
+:::
+:::
+
+#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
+\
+
+Implements an algorithm that finds the pair of indices of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
+
+::: {.noteblock data-latex=""}
+The algorithm assumes that the set of values in the *RMSE* column is a monotonically non-increasing function of the index until the minimum is reached and monotonically non-decreasing thereafter.
+That is, it is assumed that the function can have only one minimum on the given set.
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.usage .sidebar }
+##### Usage
+\
+
+::: {.noteblock data-latex=""}
+The element named `tuned.result` of the *list* returned by the [tune.model_param](#func.tune.model_param) function described below is a *data frame* suitable for use as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
+:::
+
+The following code snippet shows how to use the data returned by the [tune.model_param](#func.tune.model_param) function as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument:
+```{r eval=FALSE}
+cv.UME.preset.result <- 
+  tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)
+
+```
+```{r}
+cv.UME.preset.result$tuned.result |>
+  data.plot(title = "UME Model Regularization",#TeX(r'[UME Model Regularization: $\lambda$ Range Pre-configuration]'),
+              xname = "parameter.value",
+              yname = "RMSE",
+              xlabel = "lambda", #TeX(r'[$\lambda$]'),
+              ylabel = "RMSE")
+
+preset.result <- cv.UME.preset.result$tuned.result
+preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
+print(preset.result.idx)
+```
+
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.args .sidebar }
+##### Arguments
+\
+
+::: {#func.get_fine_tune.param.endpoints.idx.args.preset.result .sidebar }
+  - **preset.result:** Any data frame that has an *RMSE* column containing the `RMSE` values corresponding to the *regularization parameter* $\lambda$ values for the model being regularized, as described in the [Details](#func.tune.model_param.details) section of the [tune.model_param](#func.tune.model_param) function description below.
+
+:::
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.value .sidebar }
+##### Value
+\
+A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start, # interval start index
+    end,   # interval end index
+    best)  # index of the best `RMSE`
+```
+
+In the example shown above in the [Usage](#func.get_fine_tune.param.endpoints.idx.usage) section we can see the value return by *this function*:
+```{r}
+print(preset.result.idx)
+```
+
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.code .sidebar }
+##### Source Code
+\
+
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints.idx <- function(preset.result) {
+  best_RMSE <- min(preset.result$RMSE)
+  best_RMSE.idx <- which.min(preset.result$RMSE)
+  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
+
+  preset.result.N <- length(preset.result$RMSE)
+  i <- best_RMSE.idx
+  j <- i
+
+  while (i > 1) {
+    i <- i - 1
+
+    if (preset.result$RMSE[i] > best_RMSE) {
+      break
+    }
+  }
+
+  while (j < preset.result.N) {
+    j <- j + 1
+
+    if (preset.result$RMSE[j] > best_RMSE) {
+      break
+    }
+  }
+
+  c(start = i, 
+    end = j,
+    best = best_RMSE.idx)
+}
+
+```
+:::
+
+#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) Function {#func.mean_reg}
+\
+
+Calculates the arithmetic mean taking into account the _regularization parameter_ $\lambda$ passed in the [lambda](#func.mean_reg.args.lambda) argument. We will call it the _penalized mean_.
+
+::: { #func.mean_reg.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+mean_reg(vals, lambda = 0, na.rm = TRUE)
+
+```
+:::
+
+::: { #func.mean_reg.args .sidebar }
+##### Arguments
+\
+
+::: { #func.mean_reg.args.vals .sidebar }
+  - **vals:** Values (usually a numeric vector) to calculate the _penalized mean_;
+
+:::
+::: { #func.mean_reg.args.lambda .sidebar }
+  - **lambda:** (0 by default) _Regularization parameter_ $\lambda$ used in the _Regularization techniques_.
+
+:::
+  - **na.rm:** a logical evaluating to TRUE or FALSE indicating whether NA values should be stripped before the computation proceeds.
+
+:::
+
+::: { #func.mean_reg.details .sidebar }
+##### Details
+\
+
+The function calculates the _penalized mean_ of the values passed in the [vals](#func.mean_reg.args.vals) argument as follows:
+$$
+\mu(\lambda) = \frac{1}{\lambda + N} \sum_{i=1}^{N} x_i
+$$
+
+When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean:
+$$
+\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
+$$
+
+We call this function internally from the functions that compute the _penalized estimates_  as described in [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+
+::: {.noteblock data-latex=""}
+If the [lambda](#func.mean_reg.args.lambda) parameter is `0` (the default), the function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean), calling with the parameter `trim = 0` (the default for the `base::mean` function).
+:::
+:::
+
+::: { #func.mean_reg.value .sidebar }
+##### Value
+\
+
+The [penalized mean](#func.mean_reg.details) of the values passed in the [vals](#func.mean_reg.args.vals) argument.
+:::
+
+::: { #func.mean_reg.code .sidebar }
+##### Source Code
+\
+
+The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) function is shown below:
+```{r eval=FALSE}
+mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
+  if (is.na(lambda)) {
+    stop("Function: mean_reg
+`lambda` is `NA`")
+  }
+
+  names(lambda) <- NULL
+  sums <- sum(vals, na.rm = na.rm)
+  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
+  sums/(N + lambda)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) script on _GitHub_.
+:::
+:::
+
+#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) Function {#func.get_fine_tune.param.endpoints.idx}
+\
+
+Implements an algorithm that finds the pair of indices of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
+
+::: {.noteblock data-latex=""}
+The algorithm assumes that the set of values in the *RMSE* column is a monotonically non-increasing function of the index until the minimum is reached and monotonically non-decreasing thereafter.
+That is, it is assumed that the function can have only one minimum on the given set.
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.usage .sidebar }
+##### Usage
+\
+
+::: {.noteblock data-latex=""}
+The element named `tuned.result` of the *list* returned by the [tune.model_param](#func.tune.model_param) function described below is a *data frame* suitable for use as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
+:::
+
+The following code snippet shows how to use the data returned by the [tune.model_param](#func.tune.model_param) function as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument:
+```{r eval=FALSE}
+cv.UME.preset.result <- 
+  tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)
+
+```
+```{r}
+cv.UME.preset.result$tuned.result |>
+  data.plot(title = TeX(r'[UME Model Regularization: $\lambda$ Range Pre-configuration]'),
+              xname = "parameter.value", 
+              yname = "RMSE", 
+              xlabel = TeX(r'[$\lambda$]'), 
+              ylabel = "RMSE")
+
+preset.result <- cv.UME.preset.result$tuned.result
+preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
+print(preset.result.idx)
+```
+
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.args .sidebar }
+##### Arguments
+\
+
+::: {#func.get_fine_tune.param.endpoints.idx.args.preset.result .sidebar }
+  - **preset.result:** Any data frame that has an *RMSE* column containing the `RMSE` values corresponding to the *regularization parameter* $\lambda$ values for the model being regularized, as described in the [Details](#func.tune.model_param.details) section of the [tune.model_param](#func.tune.model_param) function description below.
+
+:::
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.value .sidebar }
+##### Value
+\
+A vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start, # interval start index
+    end,   # interval end index
+    best)  # index of the best `RMSE`
+```
+
+In the example shown above in the [Usage](#func.get_fine_tune.param.endpoints.idx.usage) section we can see the value return by *this function*:
+```{r}
+print(preset.result.idx)
+```
+
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.code .sidebar }
+##### Source Code
+\
+
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L87) function is shown below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints.idx <- function(preset.result) {
+  best_RMSE <- min(preset.result$RMSE)
+  best_RMSE.idx <- which.min(preset.result$RMSE)
+  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
+
+  preset.result.N <- length(preset.result$RMSE)
+  i <- best_RMSE.idx
+  j <- i
+
+  while (i > 1) {
+    i <- i - 1
+
+    if (preset.result$RMSE[i] > best_RMSE) {
+      break
+    }
+  }
+
+  while (j < preset.result.N) {
+    j <- j + 1
+
+    if (preset.result$RMSE[j] > best_RMSE) {
+      break
+    }
+  }
+
+  c(start = i, 
+    end = j,
+    best = best_RMSE.idx)
+}
+
+```
+:::
+
+\newpage
+
+#### [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.cmmn_hlp.rglr.fn.tmpl}
+\
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+cmmn_hlp.rglr.fn.tmpl()
+
+```
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+:::
+:::
+
+#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) Function {#func.mean_reg}
+\
+
+Calculates the arithmetic mean taking into account the _regularization parameter_ $\lambda$ passed in the [lambda](#func.mean_reg.args.lambda) argument. We will call it the _penalized mean_.
+
+::: { #func.mean_reg.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+mean_reg(vals, lambda = 0, na.rm = TRUE)
+
+```
+:::
+
+::: { #func.mean_reg.args .sidebar }
+##### Arguments
+\
+
+::: { #func.mean_reg.args.vals .sidebar }
+  - **vals:** Values (usually a numeric vector) to calculate the _penalized mean_;
+
+:::
+::: { #func.mean_reg.args.lambda .sidebar }
+  - **lambda:** (0 by default) _Regularization parameter_ $\lambda$ used in the _Regularization techniques_.
+
+:::
+  - **na.rm:** a logical evaluating to TRUE or FALSE indicating whether NA values should be stripped before the computation proceeds.
+
+:::
+
+::: { #func.mean_reg.details .sidebar }
+##### Details
+\
+
+The function calculates the _penalized mean_ of the values passed in the [vals](#func.mean_reg.args.vals) argument as follows:
+$$
+\mu(\lambda) = \frac{1}{\lambda + N} \sum_{i=1}^{N} x_i
+$$
+
+When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean:
+$$
+\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
+$$
+
+We call this function internally from the functions that compute the _penalized estimates_  as described in [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+
+::: {.noteblock data-latex=""}
+If the [lambda](#func.mean_reg.args.lambda) parameter is `0` (the default), the function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean), calling with the parameter `trim = 0` (the default for the `base::mean` function).
+:::
+:::
+
+::: { #func.mean_reg.value .sidebar }
+##### Value
+\
+
+The [penalized mean](#func.mean_reg.details) of the values passed in the [vals](#func.mean_reg.args.vals) argument.
+:::
+
+::: { #func.mean_reg.code .sidebar }
+##### Source Code
+\
+
+The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) function is shown below:
+```{r eval=FALSE}
+mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
+  if (is.na(lambda)) {
+    stop("Function: mean_reg
+`lambda` is `NA`")
+  }
+
+  names(lambda) <- NULL
+  sums <- sum(vals, na.rm = na.rm)
+  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
+  sums/(N + lambda)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) script on _GitHub_.
+:::
+:::
+
+### Regularization Functions2 {#appndx_a.CHF.regularization2}
+\

### 2025-11-21 reports/capstone-movielens.site/05.appendix.Rmd
Update  for function: `model.tune.param_range` (Detais section, steps 7,8).

@@
 
-#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) (see the description below) and, using one more helper function [get_best_param.result](#func.get_best_param.result)  (see the description below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
+\newpage
+
+#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) Function {#func.get_fine_tune.param.endpoints.idx}
+\
+
+Implements an algorithm that finds the pair of indices of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
+
+::: {.noteblock data-latex=""}
+The algorithm assumes that the set of values in the *RMSE* column is a monotonically non-increasing function of the index until the minimum is reached and monotonically non-decreasing thereafter.
+That is, it is assumed that the function can have only one minimum on the given set.
+:::
 
@@
 
-```{r eval=FALSE}
+::: {.noteblock data-latex=""}
+The element named `tuned.result` of the *list* returned by the [tune.model_param](#func.tune.model_param) function described below is a *data frame* suitable for use as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
+:::
+
+The following code snippet shows how to use the data returned by the [tune.model_param](#func.tune.model_param) function as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument:
+```{r eval=FALSE}
+cv.UME.preset.result <- 
+  tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)
+
+```
+```{r}
+cv.UME.preset.result$tuned.result |>
+  data.plot(title = "UME Model Regularization: `lambda` Range Pre-configuration",
+              xname = "parameter.value",
+              yname = "RMSE",
+              xlabel = "Regularization parameter (`lambda`)",
+              ylabel = "RMSE")
+
+preset.result <- cv.UME.preset.result$tuned.result
 preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
-
-```
+print(preset.result.idx)
+```
+
 :::
@@
 
-::: { #func.get_fine_tune.param.endpoints.idx.args. .sidebar }
-  - **preset.result:** ;
-
-:::
-::: { #func.get_fine_tune.param.endpoints.idx.args. .sidebar }
-  - **:** ;
-
-:::
-:::
-
-::: { #func.get_fine_tune.param.endpoints.idx.details .sidebar }
-##### Details
-\
-
+::: {#func.get_fine_tune.param.endpoints.idx.args.preset.result .sidebar }
+  - **preset.result:** Data frame that has an *RMSE* column containing the `RMSE` values corresponding to the *regularization parameter* $\lambda$ values for the model being regularized, as described in the [Details](#func.tune.model_param.details) section of the [tune.model_param](#func.tune.model_param) function description below.
+
+:::
 :::
@@
 \
+Vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start, # interval start index
+    end,   # interval end index
+    best)  # index of the best `RMSE`
+```
+
+In the example shown above in the [Usage](#func.get_fine_tune.param.endpoints.idx.usage) section we can see the value return by *this function*:
+```{r}
+print(preset.result.idx)
+```
 
@@
 
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
-:::
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) function is shown below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints.idx <- function(preset.result) {
+  best_RMSE <- min(preset.result$RMSE)
+  best_RMSE.idx <- which.min(preset.result$RMSE)
+  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
+
+  preset.result.N <- length(preset.result$RMSE)
+  i <- best_RMSE.idx
+  j <- i
+
+  while (i > 1) {
+    i <- i - 1
+
+    if (preset.result$RMSE[i] > best_RMSE) {
+      break
+    }
+  }
+
+  while (j < preset.result.N) {
+    j <- j + 1
+
+    if (preset.result$RMSE[j] > best_RMSE) {
+      break
+    }
+  }
+
+  c(start = i, 
+    end = j,
+    best = best_RMSE.idx)
+}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) script on _GitHub_.
+:::
+:::
+
+#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) Function {#func.get_fine_tune.param.endpoints}
+\
+
+The algorithm finds the values of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
+
+##### Signature
+\
+```{r eval=FALSE}
+get_fine_tune.param.endpoints <- function(preset.result) {
+  # ...
+
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+}
+```
+
+##### Arguments
+\
+
+::: {#func.get_fine_tune.param.endpoints.args.preset.result .sidebar }
+###### ***preset.result***
+\
+A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
+Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
+```{r eval=FALSE}
+    tuned_result <- tune.model_param(test_param_vals, 
+                                  fn_tune.test.param_value,
+                                  break.if_min,
+                                  steps.beyond_min)
+
+    tuned.result <- tuned_result$tuned.result
+    # tuned.result = data.frame(RMSE, parameter.value)
+    # ...
+    bound.idx <- get_fine_tune.param.endpoints(tuned.result)
+    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
+```
+:::
+
+##### Details
+\
+
+Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) parameter.
+
+##### Value
+\
+A vector containing the element value corresponding to the minimum `RMSE` in a given sequence, along with the values of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+```
+
+##### Source Code
+\
+The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) function is provided below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints <- function(preset.result) {
+
+  preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
+
+  i <- preset.result.idx["start"]
+  j <- preset.result.idx["end"]
+  best.idx <- preset.result.idx["best"]
+
+  c(start = preset.result$parameter.value[i], 
+    end = preset.result$parameter.value[j],
+    best = preset.result$parameter.value[best.idx])
+}
+```
+
+\newpage
+
+#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) Function {#func.get_best_param.result}
+\
+
+##### Signature
+\
+```{r eval=FALSE}
+get_best_param.result <- function(param_values, rmses){
+  # ...
+
+  c(param.best_value = param_values[best_pvalue_idx], 
+    best_RMSE = rmses[best_pvalue_idx])
+
+```
+
+##### Arguments
+\
+A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
+
+  - **param_values:** A vector containing the values of the input parameters for tuning;; 
+  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
+
+##### Details
+\
+Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
+
+##### Value
+\
+A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
+```{r eval=FALSE}
+c(param.best_value, best_RMSE)
+```
+
+##### Source Code
+\
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is shown below:
+```{r eval=FALSE}
+get_best_param.result <- function(param_values, rmses){
+  best_pvalue_idx <- which.min(rmses)
+  c(param.best_value = param_values[best_pvalue_idx], 
+    best_RMSE = rmses[best_pvalue_idx])
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the custom function [put_log1](#func.put_log2) described above in the [Logging Functions] section of *This Appendix*.
+In the code snippet above, we use the custom function [put_log1](#func.put_log1) described above in the [Logging Functions] section of *This Appendix*.
 :::
@@
   6.
-Calls the helper function [tune.model_param](#func.tune.model_param), passing the vector created earlier in [step 3](#func.model.tune.param_range.details.step3) to the [param_values](#func.tune.model_param.args.param_values) argument (along with the values of the rest arguments: [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value), [break.if_min](#func.tune.model_param.args.break.if_min), [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min)) of the called function and stores the returned result in the local variable `tuned_result`:
+Calls the helper function [tune.model_param](#func.tune.model_param) and stores the returned result in the local variable `tuned_result`, passing the vector created earlier in [step 3](#func.model.tune.param_range.details.step3) to the argument [param_values](#func.tune.model_param.args.param_values) along with the values of the remaining arguments passed in the following arguments of the same name to *this function*:
+    - [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value);
+    - [break.if_min](#func.model.tune.param_range.args.break.if_min);
+    - [steps.beyond_min](#func.model.tune.param_range.args.steps.beyond_min):
 ```{r eval=FALSE}
@@
   7.
-Extracts the internal data frame stored in the variable `tuned_result$tuned.result` from the data returned by the [tune.model_param](#func.tune.model_param) helper function (and saved in the local variable `tuned_result`) in the [previous step](#func.model.tune.param_range.details.step6) and stores it in the local variable `tuned.result`.
-Then stores `tuned_result` along with the necessary auxiliary information in the cache file with the full name created earlier in [step 4](#func.model.tune.param_range.details.step4):
+Extracts the data frame element stored in the variable `tuned_result$tuned.result` from the *list object* saved in the local variable `tuned_result` in the [previous step](#func.model.tune.param_range.details.step6) and stores it in the local variable `tuned.result`.
+Then stores the variable `tuned_result` along with the necessary auxiliary information in the cache file with the full name created earlier in [step 4](#func.model.tune.param_range.details.step4):
 ```{r eval=FALSE}
@@
 ::: { #func.model.tune.param_range.details.step8 .sidebar }
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) (see the description below) and, using one more helper function [get_best_param.result](#func.get_best_param.result)  (see the description below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-```{r eval=FALSE}
-```
-:::
-
+8.
+Determines the endpoints for a new interval of $\lambda$ values in the neighborhood of the minimum *RMSE* value figured out so far, with use of the helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described above, to improve the accuracy of the *RMSE* calculation in the next iteration, and stores them in the `seq_start` and `seq_end` local variables:
+```{r eval=FALSE}
+    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
+    start.idx <- bound.idx["start"]
+    end.idx <- bound.idx["end"]
+
+    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
+    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
+
+    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
+    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
+
+    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
+    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
+
+    seq_start <- prm_val.leftmost.tmp
+    seq_end <- prm_val.rightmost.tmp
+```
+:::
+
+::: { #func.model.tune.param_range.details.step .sidebar }
+
+```{r eval=FALSE}
+    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
+      prm_val.leftmost <- prm_val.leftmost.tmp
+      RMSE.leftmost <- RMSE.leftmost.tmp
+      # browser()
+    }
+
+    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
+      prm_val.rightmost <- prm_val.rightmost.tmp
+      RMSE.rightmost <- RMSE.rightmost.tmp
+      # browser()
+    } 
+```
+:::
+
+::: { #func.model.tune.param_range.details.step .sidebar }
+
+```{r eval=FALSE}
+```
+:::
 ::: { #func.model.tune.param_range.details.step .sidebar }
@@
 \
+
 Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:

### 2025-11-22 reports/capstone-movielens.site/05.appendix.Rmd
Function description completed: model.tune.param_range.

@@
   2.
-Checks if the *step size* of the generated sequence is less than the minimum allowed value (in the current implementation, we use `1e-13`), and if so, exits the loop.
+Checks if the *step size* of the generated sequence is less than the minimum allowed value (in the current implementation, we use `1e-13`), and if so, exits the loop and goes to the [Finalizing Execution](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L426) section of the code described in the [Finalizing Execution](#func.model.tune.param_range.details.finalizing) subsection below.
+
   Otherwise, proceeds to the [next step](#func.model.tune.param_range.details.step3):  
@@
 ::: { #func.model.tune.param_range.details.step8 .sidebar }
-8.
-Determines the endpoints for a new interval of $\lambda$ values in the neighborhood of the minimum *RMSE* value figured out so far, with use of the helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described above, to improve the accuracy of the *RMSE* calculation in the next iteration, and stores them in the `seq_start` and `seq_end` local variables:
+  8.Determines endpoints for a new interval of $\lambda$ values in the neighborhood of the minimum *RMSE* value (figured out so far)  with use of the helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described above, to improve the accuracy of the *RMSE* calculation in the next iteration:
 ```{r eval=FALSE}
@@
 
-::: { #func.model.tune.param_range.details.step .sidebar }
-
+::: { #func.model.tune.param_range.details.step9 .sidebar }
+  9.
+Checks whether the local variable `best_RMSE` is already initialized, and if not, initializes it to the minimum *RMSE* value for the current iteration, figured out in the [previous step](#func.model.tune.param_range.details.step8), along with local variables intended to store the endpoint values:
+```{r eval=FALSE}
+    if (is.na(best_RMSE)) {
+      prm_val.leftmost <- prm_val.leftmost.tmp
+      RMSE.leftmost <- RMSE.leftmost.tmp
+
+      prm_val.rightmost <- prm_val.rightmost.tmp
+      RMSE.rightmost <- RMSE.rightmost.tmp
+
+      param.best_value <- min_RMSE.prm_val
+      best_RMSE <- min_RMSE
+    }
+```
+:::
+
+::: { #func.model.tune.param_range.details.step10 .sidebar }
+  10.
+Checks deviations from the minimum *RMSE* value for the values corresponding to the endpoints of the new interval of the $\lambda$ parameter values figured out in the [step 8](#func.model.tune.param_range.details.step8) and updates in corresponding local variables those endpoint values of $\lambda$ and *RMSE* for which the corresponding deviation reaches the minimum threshold specified by the value passed in the [endpoint.min_diff](#func.model.tune.param_range.args.endpoint.min_diff) argument:
 ```{r eval=FALSE}
@@
       RMSE.leftmost <- RMSE.leftmost.tmp
-      # browser()
     }
@@
       RMSE.rightmost <- RMSE.rightmost.tmp
-      # browser()
-    } 
-```
-:::
-
-::: { #func.model.tune.param_range.details.step .sidebar }
-
-```{r eval=FALSE}
-```
-:::
-::: { #func.model.tune.param_range.details.step .sidebar }
-
-```{r eval=FALSE}
-```
-:::
-
-::: { #func.model.tune.param_range.details.step?? .sidebar }
-
-```{r eval=FALSE}
-```
-:::
-
-returns a range of input parameter values associated with the set of corresponding _Root Mean Squared Errors_ that is also guaranteed to include their minimum value, as described in the [Value](#func.tune.model_param.value) subsection of the [tune.model_param](#func.tune.model_param) function description.
-```{r eval=FALSE}
-```
-
-Next, the function figures out the boundary indices of a range of values from the neighborhood of the minimum `RMSE` by calling internally another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) (see the description below) and, using one more helper function [get_best_param.result](#func.get_best_param.result)  (see the description below), a pair of values,  corresponding to the best result: minimal  `RMSE` and corresponding input parameter value (which is considered the best).
-
-The found values of the boundary indices are then used as the endpoints of a new interval to regenerate the sequence based on it in the next iteration, just as it was done based on the values of the `loop_starter` parameter at the very beginning of the execution.
-The value of `step divisor`, used to calculate the step of the generated sequence, remains unchanged during the entire execution (see the description of the [loop_strarter](#func.model.tune.param_range.args.loop_starter) parameter above for details).
-
-Thus, with each subsequent iteration, the minimum `RMSE` value is calculated more accurately, over an ever-decreasing interval, with the boundary values tending to the minimum `RMSE` value, and the sequence generated with an ever-decreasing step.
-
-The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
-:::
-
-##### **Value**
-\
-
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
-```{r eval=FALSE}
-  list(best_result = param_values.best_result,
-       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
-       tuned.result = data.frame(parameter.value = parameter.value,
-                                 RMSE = result.RMSE))
-```
-
-::: {#func.model.tune.param_range.code .sidebar }
-##### Source Code
-\
-
-Below is the simplified version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) function:
-```{r eval=FALSE}
-model.tune.param_range <- function(loop_starter,
-                             tune_dir_path,
-                             cache_file_base_name,
-                             fn_tune.test.param_value,
-                             # interval_divisor.multiplier = 4,
-                             max.identical.min_RMSE.count = 4,
-                             endpoint.min_diff = 0, #1e-07,
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-  seq_start <- loop_starter[1]
-  seq_end <- loop_starter[2]
-
-  prm_val.leftmost <- seq_start
-  prm_val.rightmost <- seq_end
-
-  RMSE.leftmost <- NA
-  RMSE.rightmost <- NA
-
-  interval_divisor <- loop_starter[3]
-  if (interval_divisor < 4) {
-    interval_divisor <- 4
-  }
-
-  best_RMSE <- NA
-  param.best_value <- 0
-
-  param_values.best_result <- c(param.best_value = param.best_value, 
-                                best_RMSE = best_RMSE)
-  # Start repeat loop
-  repeat{
-    seq_increment <- (seq_end - seq_start)/interval_divisor
-
-    if (seq_increment < 0.0000000000001) {
-      warning("Function `model.tune.param_range`:
-parameter value increment is too small.")
-
-      put_log2("Function `model.tune.param_range`:
-Final best RMSE for `parameter value = %1`: %2",
-               param_values.best_result["param.best_value"],
-               param_values.best_result["best_RMSE"])
-
-      put(param_values.best_result)
-      break
-    }
-
-    test_param_vals <- seq(seq_start, seq_end, seq_increment)
-
-    file_name_tmp <- cache_file_base_name |>
-      str_c("_") |>
-      str_c(as.character(loop_starter[1])) |>
-      str_c("_") |>
-      str_c(as.character(loop_starter[3])) |>
-      str_c("_") |>
-      str_c(as.character(interval_divisor)) |>
-      str_c(".") |>
-      str_c(as.character(seq_start)) |>
-      str_c("-") |>
-      str_c(as.character(seq_end)) |>
-      str_c(".RData")
-
-    file_path_tmp <- file.path(tune_dir_path, file_name_tmp)
-
-    put_log1("Function `model.tune.param_range`:
-File path generated: %1", file_path_tmp)
-
-    if (file.exists(file_path_tmp)) {
-      put_log1("Function `model.tune.param_range`:
-Loading tuning data from file: %1...", file_path_tmp)
-
-      load(file_path_tmp)
-      put_log1("Function `model.tune.param_range`:
-Tuning data has been loaded from file: %1", file_path_tmp)
-
-      tuned.result <- tuned_result$tuned.result
-    } else {
-      tuned_result <- tune.model_param(test_param_vals, 
-                                        fn_tune.test.param_value,
-                                        break.if_min,
-                                        steps.beyond_min)
-
-      tuned.result <- tuned_result$tuned.result
-
-      save(tuned_result,
-           param.best_value,
-           seq_increment,
-           interval_divisor,
-           file = file_path_tmp)
-
-      put_log1("Function `model.tune.param_range`:
-File saved: %1", file_path_tmp)
-    }
-
-    plot(tuned.result$parameter.value, tuned.result$RMSE)
-    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
-    start.idx <- bound.idx["start"]
-    end.idx <- bound.idx["end"]
-    best_RMSE.idx <- bound.idx["best"]
-
-    prm_val.leftmost.tmp <- tuned.result$parameter.value[start.idx]
-    RMSE.leftmost.tmp <- tuned.result$RMSE[start.idx]
-
-    prm_val.rightmost.tmp <- tuned.result$parameter.value[end.idx]
-    RMSE.rightmost.tmp <- tuned.result$RMSE[end.idx]
-
-    min_RMSE <- tuned.result$RMSE[best_RMSE.idx]
-    min_RMSE.prm_val <- tuned.result$parameter.value[best_RMSE.idx]
-
-    seq_start <- prm_val.leftmost.tmp
-    seq_end <- prm_val.rightmost.tmp
-
-    if (is.na(best_RMSE)) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-
-      param.best_value <- min_RMSE.prm_val
-      best_RMSE <- min_RMSE
-    }
-
-    if (RMSE.leftmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.leftmost <- prm_val.leftmost.tmp
-      RMSE.leftmost <- RMSE.leftmost.tmp
-    }
-
-    if (RMSE.rightmost.tmp - min_RMSE >= endpoint.min_diff) {
-      prm_val.rightmost <- prm_val.rightmost.tmp
-      RMSE.rightmost <- RMSE.rightmost.tmp
-    }
-
+    } 
+```
+:::
+
+::: { #func.model.tune.param_range.details.step11 .sidebar }
+  11.
+Makes sure that the index of the start endpoint of the interval of the $\lambda$ parameter values figured out in the [step8](#func.model.tune.param_range.details.step8) is less than the index of the end endpoint and, if not, exits the loop with the *warning message* and goes to the [Finalizing Execution](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L426) section of the code described in the [Finalizing Execution](#func.model.tune.param_range.details.finalizing) subsection below:
+```{r eval=FALSE}
     if (end.idx - start.idx <= 0) {
@@
     }
-
+```
+:::
+
+::: { #func.model.tune.param_range.details.step11 .sidebar }
+  12.
+Checks if the minimum *RMSE* value determined so far (and stored in the local variable `best_RMSE`) is equal to the minimum *RMSE* value calculated for the current iteration (stored in the `min_RMSE`), and if so, outputs an appropriate warning message and proceeds to the [next step](#func.model.tune.param_range.details.step13).
+
+  Otherwise, makes sure that the minimum *RMSE* value determined so far is no less than the minimum *RMSE* value calculated for the current iteration (`best_RMSE >= min_RMSE`) and goes to [step ?](#).
+
+  Otherwise, **stops execution** with the error message (considers a fatal error!):
+```{r eval=FALSE}
     if (best_RMSE == min_RMSE) {
@@
 
-      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
-        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
-                max.identical.min_RMSE.count)
-        put(tuned.result$RMSE)
-
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-        put_log2("Function `model.tune.param_range`:
-      Reached the best RMSE for `parameter value = %1`: %2",
-                 param_values.best_result["param.best_value"],
-                 param_values.best_result["best_RMSE"])
-        break
-      }
+      # goes to the next step of the current iteration
+      # ...
+
     } else if (best_RMSE < min_RMSE) {
@@
     }
+```
+:::
+
+::: { #func.model.tune.param_range.details.step13 .sidebar }
+  13.
+(`best_RMSE == min_RMSE`) Checks the number of matches between the minimum *RMSE* value determined so far and the minimum *RMSE* value calculated for the current iteration (`best_RMSE == min_RMSE`), and if it exceeds the value passed in the argument [max.identical.min_RMSE.count](#func.model.tune.param_range.args.max.identical.min_RMSE.count), saves the best results for the $\lambda$ and *RMSE* values figured out in the current iteration in the local variable `param_values.best_result` and exits the loop with an appropriate warning message and goes to the [Finalizing Execution](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L426) section of the code described in the [Finalizing Execution](#func.model.tune.param_range.details.finalizing) subsection below.
+
+  Otherwise, proceeds to the [next step](#func.model.tune.param_range.details.step14):
+```{r eval=FALSE}
+    if (best_RMSE == min_RMSE) {
+
+      # Outputs an appropriate warning message
+      # ...
+
+      if (sum(tuned.result$RMSE[tuned.result$RMSE == min_RMSE]) >= max.identical.min_RMSE.count) {
+        warning("Minimal `RMSE`identical values count reached it maximum allowed value: ",
+                max.identical.min_RMSE.count)
+
+        put(tuned.result$RMSE)
+
+        param_values.best_result <-
+          get_best_param.result(tuned.result$parameter.value,
+                                tuned.result$RMSE)
+
+        put_log2("Function `model.tune.param_range`:
+      Reached the best RMSE for `parameter value = %1`: %2",
+                 param_values.best_result["param.best_value"],
+                 param_values.best_result["best_RMSE"])
+        break
+      }
+    } else if (best_RMSE < min_RMSE) {
+      # Fatal Error! (stops the execution)
+    }
+```
+
+::: {.noteblock data-latex=""}
+To retrieve the best results for the current iteration from the data stored in the local variable `tuned.result`, the helper function [get_best_param.result] described above is used.
+:::
+:::
+
+::: { #func.model.tune.param_range.details.step14 .sidebar }
+  14.
+Updates the following local variables: `best_RMSE` (wihich stores the current best *RMSE* value) with the minimum *RMSE* value computed for the current iteration (stored in the `min_RMSE`) and `param_values.best_result` with the best results retrieved from the  `tuned.result`, and proceeds to the next iteration from the [step 1]:
+
+```{r eval=FALSE}
+    # ...
 
@@
   # End repeat loop
-
+```
+:::
+
+::: { #func.model.tune.param_range.details.finalizing .sidebar }
+###### Finalizing Execution
+\
+
+Finally, the algorithm initializes the objects to be included in the return list with the results obtained during execution and returns the list to the client code:
+```{r eval=FALSE}
+  # Finalizing execution:
   n <- length(tuned.result$parameter.value)
 
+  # browser()
   parameter.value <- tuned.result$parameter.value
@@
     result.RMSE[1] <- RMSE.leftmost
+    # browser()
   }
@@
     result.RMSE[n+1] <- RMSE.rightmost
-  }
+    # browser()
+  }
+  # browser()
   list(best_result = param_values.best_result,
@@
                                  RMSE = result.RMSE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
-:::
+```
+:::
+
+##### **Value**
+\
+
+A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
+```{r eval=FALSE}
+  list(best_result = param_values.best_result,
+       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
+       tuned.result = data.frame(parameter.value = parameter.value,
+                                 RMSE = result.RMSE))
+```
+
+::: {#func.model.tune.param_range.code .sidebar }
+##### Source Code
+\
+
+The complete source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
 :::

### 2025-11-22 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function description: model.tune.param_range.

@@
 This function returns a list of two objects:
-
-  - A vector containing a *pair of values*: the found *best value of the regularization parameter* $\lambda$ for which the *RMSE* value is minimal, along with the minimal *RMSE* value itself;
-```{r eval=FALSE}
-  param_values.best_result <- c(param.best_value, 
-                                best_RMSE)
-```
-
-  - A data frame containing two variables:
+```{r eval=FALSE}
+  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
+                                parameter.value = param_vals_tmp),
+       best_result = param_values.best_result)
+```
+
+The objects comprising the return list are as follows:
+
+  - `best_result`: Vector containing a *pair of values*: the found *best value of the regularization parameter* $\lambda$ for which the *RMSE* value is minimal, along with the minimal *RMSE* value itself;
+
+  - `tuned.result`: Data frame containing two variables:
 
@@
     - *RMSE*: A vector containing the *RMSE* values corresponding to the processed values of $\lambda$.
-```{r eval=FALSE}
-tuned.result = data.frame(RMSE, parameter.value)
-```
+
 :::
@@
 
+\newpage
+
 ::: { #func.model.tune.param_range.details .sidebar }
@@
   1.
-Calculates the divisor to calculate the step size for partitioning the interval into a sequence of $\lambda$ values as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L240):
+Calculates the step size for partitioning the interval into a sequence of $\lambda$ values as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L240):
 ```{r eval=FALSE}
@@
 
-  # browser()
   parameter.value <- tuned.result$parameter.value
@@
     result.RMSE[1] <- RMSE.leftmost
-    # browser()
-  }
+  }
+
   if (result.RMSE[n] == best_RMSE) {
@@
     result.RMSE[n+1] <- RMSE.rightmost
-    # browser()
-  }
-  # browser()
+  }
+
   list(best_result = param_values.best_result,
@@
 
+::: {#func.model.tune.param_range.value .sidebar }
 ##### **Value**
@@
 
-A data structure containing the minimum `RMSE` value reached during the fine-tuning process, the corresponding input parameter value, and information about the final sequence, on which the best output values were found:
+This function returns a list of three objects:
 ```{r eval=FALSE}
@@
 ```
+
+The objects comprising the return list are as follows:
+
+  - `best_result`: A vector containing a *pair of values*: the found *best value of the regularization parameter* $\lambda$ for which the *RMSE* value is minimal, along with the minimal *RMSE* value itself;
+
+  - `param_values.endpoints`: Information related to the final interval of the *regularization parameter* $\lambda$ values.;
+
+  - `tuned.result`: A data frame containing two variables:
+
+    - *parameter.value*: A vector containing all processed values of the parameter $\lambda$;
+
+    - *RMSE*: A vector containing the *RMSE* values corresponding to the processed values of $\lambda$.
+
+:::
 

### 2025-11-22 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function description: model.tune.param_range.

@@
 
-#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
+#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) Function {#func.model.tune.param_range}
 \
@@
 
-The complete source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
+The complete source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) script on _GitHub_.
 :::

### 2025-11-23 reports/capstone-movielens.site/05.appendix.Rmd
Function described: get_best_param.result.

@@
 
-##### Signature
-\
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  # ...
-
+Selects the best values from a pair of matched vectors: a vector of sorted *regularization parameter* $\lambda$ values and a vector of *Root Mean Squared Errors (RMSE)* values passed in the [param_values](#func.tune.model_param.args.param_values) and [RMSEs](#func.get_best_param.result.args.RMSEs) arguments, respectively.
+
+::: { #func.get_best_param.result.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+        param_values.best_result <-
+          get_best_param.result(tuned.result$parameter.value,
+                                tuned.result$RMSE)
+```
+:::
+
+::: { #func.get_best_param.result.args .sidebar }
+##### Arguments
+\
+
+A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
+
+::: { #func.get_best_param.result.args.param_values .sidebar }
+  - **param_values:** Numeric vector containing a sorted list of the *regularization parameter* $\lambda$ values to search for the best one during the *Model Regularization* process;
+
+:::
+::: { #func.get_best_param.result.args.RMSEs .sidebar }
+  - **RMSEs:** *RMSE* values computed during the *Model Regularization* process.
+
+:::
+:::
+
+::: { #func.get_best_param.result.details .sidebar }
+##### Details
+\
+
+This is a *utility function* used to select the *best values* during the *Model Regularization* process utilizing the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+
+With this approach the best value of the *regularization parameter* $\lambda$ (we call this the *best value of the regularization parameter* or the *best value of $\lambda$*) is considered to be the value corresponding to the minimum value of the *RMSE* for the model being tested.
+
+In *This Project* this function is used internally in the [model.tune.param_range](#func.model.tune.param_range) function described in *This Section* below.
+:::
+
+::: { #func.get_best_param.result.value .sidebar }
+##### Value
+\
+
+Numeric vector containing a pair of values: the best *regularization parameter* $\lambda$ value and corresponding *minimal RMSE* 
+:::
+
+::: { #func.get_best_param.result.code .sidebar }
+##### Source Code
+\
+
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is shown below:
+```{r eval=FALSE}
+get_best_param.result <- function(param_values, RMSEs){
+  best_pvalue_idx <- which.min(RMSEs)
   c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-
-```
-
-##### Arguments
-\
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
-  - **param_values:** A vector containing the values of the input parameters for tuning;; 
-  - **rmses:** A vector containing values of the corresponding `Root Mean Squared Errors`..
-
-##### Details
-\
-Extracts the best values from the input data and returns them as a vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_.
-
-##### Value
-\
-A vector containing a pair of the best _input parameter_ value and the corresponding _minimum `RMSE`_:
-```{r eval=FALSE}
-c(param.best_value, best_RMSE)
-```
-
-##### Source Code
-\
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) script on _GitHub_.
-:::
+    best_RMSE = RMSEs[best_pvalue_idx])
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) script on _GitHub_.
+:::
+:::
+
+\newpage
 
@@
   1.
-Calculates the step size for partitioning the interval into a sequence of $\lambda$ values as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L240):
+Calculates the step size for partitioning the interval into a sequence of $\lambda$ values and save it to the local variable `seq_increment` as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L240):
 ```{r eval=FALSE}
@@
 
-  Otherwise, makes sure that the minimum *RMSE* value determined so far is no less than the minimum *RMSE* value calculated for the current iteration (`best_RMSE >= min_RMSE`) and goes to [step ?](#).
-
-  Otherwise, **stops execution** with the error message (considers a fatal error!):
+  - Otherwise, makes sure that the minimum *RMSE* value determined so far is no less than the minimum *RMSE* value calculated for the current iteration (`best_RMSE >= min_RMSE`) and goes to [step ?](#).
+
+  - Otherwise, **stops execution** with the error message (considers a fatal error!):
 ```{r eval=FALSE}
@@
 
-  Otherwise, proceeds to the [next step](#func.model.tune.param_range.details.step14):
+  - Otherwise, proceeds to the [next step](#func.model.tune.param_range.details.step14):
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-To retrieve the best results for the current iteration from the data stored in the local variable `tuned.result`, the helper function [get_best_param.result] described above is used.
+To retrieve the best results for the current iteration from the data stored in the local variable `tuned.result`, the helper function [get_best_param.result](#func.get_best_param.result) described above is used.
 :::
@@
 ::: { #func.model.tune.param_range.details.finalizing .sidebar }
-###### Finalizing Execution
-\
-
-Finally, the algorithm initializes the objects to be included in the return list with the results obtained during execution and returns the list to the client code:
+###### ***Finalizing Execution***
+\
+
+Finally, the algorithm initializes the objects to be included in the return list with the results obtained during execution and returns the *list object* to the client code:
 ```{r eval=FALSE}
@@
 
-The complete source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) script on _GitHub_.
+The complete source code of the function [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) script on _GitHub_.
 :::

### 2025-11-23 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for function: model.tune.param_range.

@@
 
-Selects the best values from a pair of matched vectors: a vector of sorted *regularization parameter* $\lambda$ values and a vector of *Root Mean Squared Errors (RMSE)* values passed in the [param_values](#func.tune.model_param.args.param_values) and [RMSEs](#func.get_best_param.result.args.RMSEs) arguments, respectively.
+Selects the best values from a pair of matched vectors: a vector of sorted *regularization parameter* $\lambda$ values and a vector of corresponding *Root Mean Squared Errors (RMSE)* values passed in the [param_values](#func.tune.model_param.args.param_values) and [RMSEs](#func.get_best_param.result.args.RMSEs) arguments, respectively.
 
@@
 
-A pair of matched vectors, the first of which contains the values of the input parameters for tuning, and the second, the corresponding values of the `RMSE`.
-
 ::: { #func.get_best_param.result.args.param_values .sidebar }
@@
 
-This is a *utility function* used to select the *best values* during the *Model Regularization* process utilizing the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
-
-With this approach the best value of the *regularization parameter* $\lambda$ (we call this the *best value of the regularization parameter* or the *best value of $\lambda$*) is considered to be the value corresponding to the minimum value of the *RMSE* for the model being tested.
-
-In *This Project* this function is used internally in the [model.tune.param_range](#func.model.tune.param_range) function described in *This Section* below.
+This is a *utility function* used to select the *best values* during the *Model Regularization* process, utilizing the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+
+With this approach, the best value of the *regularization parameter* $\lambda$ (we call this the *best value of the regularization parameter* or the *best value of $\lambda$*) is considered to be the value corresponding to the minimum value of the *RMSE* for the model being tested.
+
+In *This Project*, this function is used internally in the [model.tune.param_range](#func.model.tune.param_range) function described in *This Section* below.
 :::
@@
 
-Numeric vector containing a pair of values: the best *regularization parameter* $\lambda$ value and corresponding *minimal RMSE* 
+Numeric vector containing a pair of values: the best *regularization parameter* $\lambda$ value and corresponding *minimal RMSE*. 
 :::
@@
 
-  Otherwise, proceeds to the [next step](#func.model.tune.param_range.details.step3):  
+  - Otherwise, proceeds to the [next step](#func.model.tune.param_range.details.step3):  
 ```{r eval=FALSE}
@@
 ```
+
 :::

### 2025-11-23 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for function: model.tune.param_range.

@@
 ::: { #func.model.tune.param_range.details.step8 .sidebar }
-  8.Determines endpoints for a new interval of $\lambda$ values in the neighborhood of the minimum *RMSE* value (figured out so far)  with use of the helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described above, to improve the accuracy of the *RMSE* calculation in the next iteration:
+  8.
+Determines endpoints for a new interval of $\lambda$ values in the neighborhood of the minimum *RMSE* value (figured out so far)  with use of the helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described above, to improve the accuracy of the *RMSE* calculation in the next iteration:
 ```{r eval=FALSE}

### 2025-11-23 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for function: model.tune.param_range.

@@
 
+::: { #func.model.tune.param_range.details.step1 .sidebar }
   1.
@@
 
+:::
+
+::: { #func.model.tune.param_range.details.step2 .sidebar }
   2.
@@
 ```
+
+:::
 
@@
   14.
-Updates the following local variables: `best_RMSE` (wihich stores the current best *RMSE* value) with the minimum *RMSE* value computed for the current iteration (stored in the `min_RMSE`) and `param_values.best_result` with the best results retrieved from the  `tuned.result`, and proceeds to the next iteration from the [step 1]:
+Updates the following local variables: `best_RMSE` (wihich stores the current best *RMSE* value) with the minimum *RMSE* value computed for the current iteration (stored in the `min_RMSE`) and `param_values.best_result` with the best results retrieved from the  `tuned.result`, and proceeds to the next iteration from the [step 1](#func.model.tune.param_range.details.step1):
 

### 2025-11-23 reports/capstone-movielens.site/02.5.UME-model.Rmd
OMR, UE, UME models: review.
Description refining: UME Model.

@@
 ```
-
-Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.
 
@@
 
-  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the *5-Fold Cross-Validation* samples;
+  1. **Pre-configuration:** Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples;
 
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
+  2. **Fine-tuning:** Figuring out the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* of the model.
 
-  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.
+  3. **Retraining:** Retraining the model with the best value of $\lambda$ determined in the previous step.
 

### 2025-11-23 r/src/support-functions/UM-effect.functions.R
Function described: regularize.test_lambda.UM_effect.cv.

@@ -1,6 +1,6 @@
 # User+Movie Effect (UME) Model Support Functions
 
-## UME Model Utility Functions --------------------------------------------------
+## Utility Functions --------------------------------------------------
 train_user_movie_effect <- function(train_set, lambda = 0){
   if (is.na(lambda)) {
     stop("Function: train_user_movie_effect
@@ -87,7 +87,7 @@ calc_user_movie_effect_RMSE.cv <- function(um_effect){
   um_effect_RMSE
 }
 
-## UME Model Regularization ----------------------------------------------------
+## Regularization ----------------------------------------------------
 regularize.test_lambda.UM_effect.cv <- function(lambda){
   if (is.na(lambda)) {
     stop("Function: regularize.test_lambda.UM_effect.cv

### 2025-11-23 reports/capstone-movielens.site/05.appendix.Rmd

@@
 
-Trains the *(Regularized) User+Movie (UM) Effect Model* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) parameter.
+Trains (and optionally *regularizes* if the [lambda](#) argument is non-default) the *User+Movie (UM) Effect Model* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) argument.
 
@@
 
-Trains the *(Regularized) User+Movie (UM) Effect Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Trains the *User+Movie (UM) Effect Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 
+Validates the *Regularization Parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument for the *User+Movie (UM) Effect Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6] in the *regularization process* using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+
+::: {.noteblock data-latex=""}
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+:::
+
 ::: { #func.regularize.test_lambda.UM_effect.cv.usage .sidebar }
@@
 
-::: { #func.regularize.test_lambda.UM_effect.cv.args. .sidebar }
-  - **:** ;
-
-:::
-::: { #func.regularize.test_lambda.UM_effect.cv.args. .sidebar }
-  - **:** ;
+::: { #func.regularize.test_lambda.UM_effect.cv.args.lambda .sidebar }
+  - **lambda:** Regularization parameter.
 
@@
 
+This is a helper function that is used to pass as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*, in the *regularization process* using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1], with use of the *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6],where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
 :::
@@
 
+The *Root Mean Squared Errors (RMSE)* value computed for the UME Model applying the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument.
+
 :::
@@
 ```{r eval=FALSE}
+regularize.test_lambda.UM_effect.cv <- function(lambda){
+  if (is.na(lambda)) {
+    stop("Function: regularize.test_lambda.UM_effect.cv
+`lambda` is `NA`")
+  }
+  um_effect <- train_user_movie_effect.cv(lambda)
+  calc_user_movie_effect_RMSE.cv(um_effect)
+}
 ```

### 2025-11-23 reports/capstone-movielens.site/bak/05.appendix.bak.Rmd

@@
 
-### UME Model Utility Functions
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the  [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) script on _GitHub_.
+### Utility Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
+The source code of the [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) script on _GitHub_.
+The complete source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) script on _GitHub_.
+The source code of the [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) script on _GitHub_.
+The source code of the [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) script on _GitHub_.
+The source code of the [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) script on _GitHub_.
+The source code of the [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) script on _GitHub_.
 :::

### 2025-11-23 reports/capstone-movielens.site/work/func-descr.template.Rmd

@@
 
-### UME Model Utility Functions
+### Utility Functions
 \
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the  [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) script on _GitHub_.
+The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [ume_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) script on _GitHub_.
+The source code of the [ume_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [ume_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) script on _GitHub_.
+The source code of the [ume_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) script on _GitHub_.
 :::

### 2025-11-23 reports/capstone-movielens.site/05.appendix.Rmd
Hotfix for functioin: Function described: regularize.test_lambda.UM_effect.cv..

@@
 
-Validates the *Regularization Parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument for the *User+Movie (UM) Effect Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6] in the *regularization process* using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
-
-::: {.noteblock data-latex=""}
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
-:::
+Validates the *Regularization Parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument for the *User+Movie (UM) Effect Model* with use of *K-Fold Cross-Validation* in the *regularization process*.
 
@@
 
-This is a helper function that is used to pass as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*, in the *regularization process* using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1], with use of the *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6],where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
+This is a helper function that is used to pass as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*, in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1], with use of the *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6],where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
 :::
@@
 ::: {.noteblock data-latex=""}
-The source code of the [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) script on _GitHub_.
+The source code of the [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) script on _GitHub_.
 :::

### 2025-11-24 reports/capstone-movielens.site/05.appendix.Rmd
Hotfix for functioin: Function described: regularize.test_lambda.UM_effect.cv.

@@
 
-Validates the *Regularization Parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument for the *User+Movie (UM) Effect Model* with use of *K-Fold Cross-Validation* in the *regularization process*.
+Validates the *Regularization Parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument for the *User+Movie (UM) Effect Model* in the *regularization process* using the *penalized approach* with use of *K-Fold Cross-Validation*.
 
@@
 This is a helper function that is used to pass as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*, in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1], with use of the *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6],where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+We choose `K = 5`in *This Project*.
+:::
 :::

### 2025-11-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function description: regularize.test_lambda.UM_effect.cv.

--- 2025-11-23 reports/capstone-movielens.site/05.appendix.Rmd
@@
 
-Validates the *Regularization Parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument for the *User+Movie (UM) Effect Model* with use of *K-Fold Cross-Validation* in the *regularization process*.
+Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument for the *User+Movie Effect (UME) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
 
@@
 ::: { #func.regularize.test_lambda.UM_effect.cv.args.lambda .sidebar }
-  - **lambda:** Regularization parameter.
+  - **lambda:** *Regularization parameter* $\lambda$ used to validate the model in the *regularization process*.
 
@@
 
-This is a helper function that is used to pass as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*, in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1], with use of the *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6],where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+The function is used in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument) as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+
+Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
+
+::: {.noteblock data-latex=""}
+This function is also used to pass as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*, .
+:::
 :::

### 2025-11-24 reports/capstone-movielens.site/05.appendix.Rmd
Appendixes refactoring: replaced string "[UME Model Utility Functions]" --> "[Utility Functions]"

@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the  [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) script on _GitHub_.
+The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) script on _GitHub_.
 :::
@@
 
-Trains (and optionally *regularizes* if the [lambda](#) argument is non-default) the *User+Movie (UM) Effect Model* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) argument.
+Trains (and optionally *regularizes* if the [lambda](#) argument is non-default) the *User+Movie Effect (UME) Model* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) argument.
 
@@
 
-Trains the *User+Movie (UM) Effect Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Trains the *User+Movie Effect (UME) Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 

### 2025-11-24 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report, "UME Model Regulariztion" section  refactoing: extra subsection removed.

@@
 
-#### UME Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
-:::
-
-##### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function {#func.regularize.test_lambda.UM_effect.cv}
-\
-
-This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross-Validation_ method for the given $\lambda$ parameter value:
-```{r, eval=FALSE}
-regularize.test_lambda.UM_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UM_effect.cv
-`lambda` is `NA`")
-  }
-  um_effect <- train_user_movie_effect.cv(lambda)
-  calc_user_movie_effect_RMSE.cv(um_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) calling it from the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
-:::
-
-\newpage
-
-#### UME Model Regularization: Pre-configuration
+#### UME Model Regularization: *Pre-configuration*
 \

### 2025-11-24 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report, "UME Model Regulariztion" section  review.

@@
 
-Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
+We need to do some pre-configuration to determine a suitable range of $\lambda$ for subsequent fine-tuning of our current model.
+For this purpose, we will use the helper function [tune.model_param](#func.tune.model_param), passing [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) (another helper function) as the value of its argument [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value).
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
+::: {.noteblock data-latex=""}
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model Regularization] of [Appendix A: Support Functions], respectively.
+:::
 
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [UME Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
+The complete version of the source code provided in this section can be found in the [UME Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L554) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L554) script.
 :::
 
-Now, let's visualize the results of the $\lambda$ range preconfiguration:
+Now, let's visualize the results of the $\lambda$ range pre-configuration:
 ``` {r}
@@
 ::: {.noteblock data-latex=""}
-We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions], which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions].
 :::

### 2025-11-25 reports/capstone-movielens.site/02.5.UME-model.Rmd
Documentation: Function review: get_fine_tune.param.endpoints.idx.

@@
 We need to do some pre-configuration to determine a suitable range of $\lambda$ for subsequent fine-tuning of our current model.
-For this purpose, we will use the helper function [tune.model_param](#func.tune.model_param), passing [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) (another helper function) as the value of its argument [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value).
+For this purpose, we will use the helper function [tune.model_param](#func.tune.model_param), passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) (another helper function) as the value of its argument [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value).
 
@@
 We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
+For this purpose, we will use the helper function [model.tune.param_range](#func.model.tune.param_range), passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function (already mentioned above in the [UME Model Regularization: *Pre-configuration*] section) as the value of its argument [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value).
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
+::: {.noteblock data-latex=""}
+The function [model.tune.param_range](#func.model.tune.param_range) is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
+:::
 
@@
                          regularize.test_lambda.UM_effect.cv)
-                         #endpoint.min_diff = 1e-07/4)
 

### 2025-11-25 reports/capstone-movielens.site/05.appendix.Rmd
Documentation: Function review: get_fine_tune.param.endpoints.idx.

@@
 
-Implements an algorithm that finds the pair of indices of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
+Implements an algorithm that finds, in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument, the indices of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value.
 
@@
 
-The algorithm finds the values of the nearest neighboring elements of the element corresponding to the minimum RMSE value in the given sequence.
-
-##### Signature
-\
-```{r eval=FALSE}
-get_fine_tune.param.endpoints <- function(preset.result) {
-  # ...
-
+Implements an algorithm that finds, in the *RMSE* column of the data frame passed in the [preset.result](#) argument, the pair of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value.
+
+::: {.noteblock data-latex=""}
+The algorithm assumes that the set of values in the *RMSE* column is a monotonically non-increasing function of the index until the minimum is reached and monotonically non-decreasing thereafter.
+That is, it is assumed that the function can have only one minimum on the given set.
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.usage .sidebar }
+##### Usage
+\
+
+::: {.noteblock data-latex=""}
+The element named `tuned.result` of the *list* returned by the [tune.model_param](#func.tune.model_param) function described below is a *data frame* suitable for use as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
+:::
+
+The following code snippet shows how to use the data returned by the [tune.model_param](#func.tune.model_param) function as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument:
+```{r eval=FALSE}
+cv.UME.preset.result <- 
+  tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)
+
+```
+```{r}
+cv.UME.preset.result$tuned.result |>
+  data.plot(title = "UME Model Regularization: `lambda` Range Pre-configuration",
+              xname = "parameter.value",
+              yname = "RMSE",
+              xlabel = "Regularization parameter (`lambda`)",
+              ylabel = "RMSE")
+
+preset.result <- cv.UME.preset.result$tuned.result
+preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
+print(preset.result.idx)
+```
+
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.args .sidebar }
+##### Arguments
+\
+
+::: {#func.get_fine_tune.param.endpoints.idx.args.preset.result .sidebar }
+  - **preset.result:** Data frame that has an *RMSE* column containing the `RMSE` values corresponding to the *regularization parameter* $\lambda$ values for the model being regularized, as described in the [Details](#func.tune.model_param.details) section of the [tune.model_param](#func.tune.model_param) function description below.
+
+:::
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.value .sidebar }
+##### Value
+\
+Vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
+```{r eval=FALSE}
+  c(start, # interval start index
+    end,   # interval end index
+    best)  # index of the best `RMSE`
+```
+
+In the example shown above in the [Usage](#func.get_fine_tune.param.endpoints.idx.usage) section we can see the value return by *this function*:
+```{r}
+print(preset.result.idx)
+```
+
+:::
+
+::: { #func.get_fine_tune.param.endpoints.idx.code .sidebar }
+##### Source Code
+\
+
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) script on _GitHub_.
+:::
+:::
+
+##### Details
+\
+
+Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) parameter.
+
+##### Value
+\
+A vector containing the element value corresponding to the minimum `RMSE` in a given sequence, along with the values of its nearest neighboring elements:
+```{r eval=FALSE}
   c(start = preset.result$parameter.value[i], 
@@
     best = preset.result$parameter.value[best.idx])
-}
-```
-
-##### Arguments
-\
-
-::: {#func.get_fine_tune.param.endpoints.args.preset.result .sidebar }
-###### ***preset.result***
-\
-A data structure compatible with the `tuned.result` item of the data structure returned by the [tune.model_param](#func.tune.model_param) function (see the [Value](#func.tune.model_param.value) subsection of the `tune.model_param` function description section for more details).
-Here is a sample of using this parameter in the `model.tune.param_range` function [code](#func.model.tune.param_range.code):
-```{r eval=FALSE}
-    tuned_result <- tune.model_param(test_param_vals, 
-                                  fn_tune.test.param_value,
-                                  break.if_min,
-                                  steps.beyond_min)
-
-    tuned.result <- tuned_result$tuned.result
-    # tuned.result = data.frame(RMSE, parameter.value)
-    # ...
-    bound.idx <- get_fine_tune.param.endpoints(tuned.result)
-    # bounnd.idx =  c(start.index, end.index, min_RMSE.index)
-```
-:::
-
-##### Details
-\
-
-Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) parameter.
-
-##### Value
-\
-A vector containing the element value corresponding to the minimum `RMSE` in a given sequence, along with the values of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-```
-
-##### Source Code
-\
-The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) function is provided below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints <- function(preset.result) {
-
-  preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
-
-  i <- preset.result.idx["start"]
-  j <- preset.result.idx["end"]
-  best.idx <- preset.result.idx["best"]
-
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-}
 ```

### 2025-11-25 reports/capstone-movielens.site/05.appendix.Rmd
Function described: get_fine_tune.param.endpoints.

@@
 
-Implements an algorithm that finds, in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument, the indices of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value.
+Implements an algorithm that finds in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument the indices of the pair of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value.
 
@@
 The algorithm assumes that the set of values in the *RMSE* column is a monotonically non-increasing function of the index until the minimum is reached and monotonically non-decreasing thereafter.
-That is, it is assumed that the function can have only one minimum on the given set.
+That is, it is assumed that the function has only one minimum on the given set.
 :::
@@
 \
-Vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
+
+Vector containing the index of the first element corresponding to the minimum `RMSE` value in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument, along with the indices of the pair of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value:
 ```{r eval=FALSE}
@@
 ```{r}
+str(preset.result.idx)
 print(preset.result.idx)
@@
 
-Implements an algorithm that finds, in the *RMSE* column of the data frame passed in the [preset.result](#) argument, the pair of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value.
+Implements an algorithm that finds in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) argument the pair of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value.
 
@@
 The algorithm assumes that the set of values in the *RMSE* column is a monotonically non-increasing function of the index until the minimum is reached and monotonically non-decreasing thereafter.
-That is, it is assumed that the function can have only one minimum on the given set.
-:::
-
-::: { #func.get_fine_tune.param.endpoints.idx.usage .sidebar }
-##### Usage
-\
-
-::: {.noteblock data-latex=""}
-The element named `tuned.result` of the *list* returned by the [tune.model_param](#func.tune.model_param) function described below is a *data frame* suitable for use as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
-:::
-
-The following code snippet shows how to use the data returned by the [tune.model_param](#func.tune.model_param) function as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument:
+That is, it is assumed that the function has only one minimum on the given set.
+:::
+
+::: { #func.get_fine_tune.param.endpoints.usage .sidebar }
+##### Usage
+\
+
+::: {.noteblock data-latex=""}
+The element named `tuned.result` of the *list* returned by the [tune.model_param](#func.tune.model_param) function described below is a *data frame* suitable for use as the value of the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) argument.
+:::
+
+The following code snippet shows how to use the data returned by the [tune.model_param](#func.tune.model_param) function as the value of the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) argument:
 ```{r eval=FALSE}
@@
 preset.result <- cv.UME.preset.result$tuned.result
-preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
-print(preset.result.idx)
-```
-
-:::
-
-::: { #func.get_fine_tune.param.endpoints.idx.args .sidebar }
-##### Arguments
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.args.preset.result .sidebar }
+fine_tune.param.endpoints <- get_fine_tune.param.endpoints(preset.result)
+print(fine_tune.param.endpoints)
+```
+
+:::
+
+::: { #func.get_fine_tune.param.endpoints.args .sidebar }
+##### Arguments
+\
+
+::: {#func.get_fine_tune.param.endpoints.args.preset.result .sidebar }
   - **preset.result:** Data frame that has an *RMSE* column containing the `RMSE` values corresponding to the *regularization parameter* $\lambda$ values for the model being regularized, as described in the [Details](#func.tune.model_param.details) section of the [tune.model_param](#func.tune.model_param) function description below.
@@
 
-::: { #func.get_fine_tune.param.endpoints.idx.value .sidebar }
-##### Value
-\
-Vector containing the index of the element corresponding to the minimum `RMSE` value in a given sequence, along with the indices of its nearest neighboring elements:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-In the example shown above in the [Usage](#func.get_fine_tune.param.endpoints.idx.usage) section we can see the value return by *this function*:
+::: { #func.get_fine_tune.param.endpoints.details .sidebar }
+##### Details
+\
+
+This function internally calls [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) function described above to figure out the indices of the elements, the values of which have to be determined.
+:::
+
+::: { #func.get_fine_tune.param.endpoints.value .sidebar }
+##### Value
+\
+
+Vector containing a value equals to minimum `RMSE` value in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument, along with the pair of values those equal to the values of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value:
+
+In the example shown above in the [Usage](#func.get_fine_tune.param.endpoints.usage) section we can see the value return by *this function*:
 ```{r}
-print(preset.result.idx)
-```
-
-:::
-
-::: { #func.get_fine_tune.param.endpoints.idx.code .sidebar }
-##### Source Code
-\
-
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) script on _GitHub_.
-:::
-:::
-
-##### Details
-\
-
-Under the hood, the function internally calls another helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described below to figure out the boundary indices of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) parameter.
-
-##### Value
-\
-A vector containing the element value corresponding to the minimum `RMSE` in a given sequence, along with the values of its nearest neighboring elements:
-```{r eval=FALSE}
+str(fine_tune.param.endpoints)
+print(fine_tune.param.endpoints)
+```
+
+:::
+
+::: { #func.get_fine_tune.param.endpoints.code .sidebar }
+##### Source Code
+\
+
+The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L109) function is shown below:
+```{r eval=FALSE}
+get_fine_tune.param.endpoints <- function(preset.result) {
+
+  preset.result.idx <- get_fine_tune.param.endpoints(preset.result)
+
+  i <- preset.result.idx["start"]
+  j <- preset.result.idx["end"]
+  best.idx <- preset.result.idx["best"]
+
   c(start = preset.result$parameter.value[i], 
@@
     best = preset.result$parameter.value[best.idx])
-```
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L109) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L109) script on _GitHub_.
+:::
+:::
 

### 2025-11-25 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the function description: get_fine_tune.param.endpoints.

@@
 
-Vector containing a value equals to minimum `RMSE` value in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument, along with the pair of values those equal to the values of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value:
+Vector containing the *regularization parameter* $\lambda$ value corresponding to the first element with the minimum `RMSE` value in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument, along with the pair of the $\lambda$ values corresponding to the nearest neighboring elements with values greater than the minimum `RMSE` to the left and right of the element (or group of elements) with the minimum `RMSE` value:
 

### 2025-11-25 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for function description: get_fine_tune.param.endpoints.

@@
 
-#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L80) Function {#func.get_fine_tune.param.endpoints}
+#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L109) Function {#func.get_fine_tune.param.endpoints}
 \

### 2025-11-25 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report section [UME Model Regularization: Fine-tuning\: review.

@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the [UME Model Utility Functions] section of [Appendix A: Support Functions].
+In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the [UME Model: Utility Functions] section of [Appendix A: Support Functions].
 :::
@@
 
-  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the [UME Model Utility Functions] section) to calculate the *RMSE* for the *Current Model*;
+  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the [UME Model: Utility Functions] section) to calculate the *RMSE* for the *Current Model*;
 
@@
 ::: {.noteblock data-latex=""}
-The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model Regularization] of [Appendix A: Support Functions], respectively.
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization] of [Appendix A: Support Functions], respectively.
 :::
@@
                             8)
-UM_effect.loop_starter
-#> [1] 0.3 0.5 8.0
-
 UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"
+```
+```{r}
+print(UM_effect.loop_starter)
+print(UME.rglr.fine_tune.cache.path)
+print(UME.rglr.fine_tune.cache.base_name)
+class(regularize.test_lambda.UM_effect.cv)
+```
+```{r, eval=FALSE}
 
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be also found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
 :::

### 2025-11-26 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report: UME Model documented.

@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the [UME Model: Utility Functions] section of [Appendix A: Support Functions].
+In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A: Support Functions].
 :::
@@
 ```
+
+::: {.noteblock data-latex=""}
+The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
+:::
+
 ```{r}
@@
 print(UME.rglr.fine_tune.cache.base_name)
-class(regularize.test_lambda.UM_effect.cv)
 ```
@@
 writeLines("*** Fine-tuning results object data structure ***")
+```
+```{r}
 str(UME.rglr.fine_tune.results)
-
+```
+```{r, echo=FALSE}
 writeLines("*** Fine-tuning: best results ***")
+```
+```{r}
 UME.rglr.fine_tune.results$best_result
 ```
-
-::: {.noteblock data-latex=""}
-The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
-:::
 
@@
 ```
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section are available in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L607) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L607) script on _GitHub_.
+:::
+
 \newpage
@@
 
-Now, we can calculate the _Regularized User+Movie Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
+Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model*), for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
 ```{r, eval=FALSE}
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above we use the [train_user_movie_effect](#func.train_user_movie_effect) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A: Support Functions].
+
+Later in this section, we will also use the custom logging function [print_log1](#func.print_log1) described in the [Logging Functions] section of *the same Appendix*.
+:::
+
 ```{r, echo=FALSE}
 writeLines("*** The Best Fine-tuning Results ***")
+```
+```{r}
 UME.rglr.fine_tune.results$best_result
+```
 
+```{r, echo=FALSE}
 writeLines("*** Regularized User+Movie Effect Structure ***")
+```
+```{r}
 str(rglr.UM_effect)
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section are available in the [Re-training Regularized User+Movie Effect Model for the best $\lambda$](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) script on _GitHub_.
+The complete version of the source code provided in this section are available in the [Re-training Regularized Model for the best `lambda`](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L650) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L650) script on _GitHub_.
 :::
 
-We calculate the _Root Mean Squared Error_ for the ultimately computed _User+Movie Effect_ using [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function described above as follows:
+We calculate the *RMSE* for the ultimately *Regularized User+Movie Effect Model* using [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function already used above in the [UME Model Building] section:
 ```{r, eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
 :::

### 2025-11-26 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report: UME Model review.

@@
 
-  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the [UME Model: Utility Functions] section) to calculate the *RMSE* for the *Current Model*;
+  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section) to calculate the *RMSE* for the *Current Model*;
 
-  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Result RMSEs Tibble Functions] section) to update and print the table above.
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
 :::
@@
                             8)
-UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"
 ```
@@
 ```{r}
-print(UM_effect.loop_starter)
-print(UME.rglr.fine_tune.cache.path)
-print(UME.rglr.fine_tune.cache.base_name)
+UM_effect.loop_starter
+UME.rglr.fine_tune.cache.path
 ```
 ```{r, eval=FALSE}
+UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"
 
@@
 UME.rglr.fine_tune.results$best_result
+UME.rglr.fine_tune.RMSE.best
 ```
@@
 
-Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model*), for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
+Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model*), for the definitive _RMSE_ calculation and use in subsequent models.
 ```{r, eval=FALSE}
+best_result <- UME.rglr.fine_tune.results$best_result
 UME.rglr.best_lambda <- best_result["param.best_value"]
-  UME.rglr.best_lambda
 
@@
 :::
+
+```{r}
+```
 
@@
 
-We calculate the *RMSE* for the ultimately *Regularized User+Movie Effect Model* using [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function already used above in the [UME Model Building] section:
+We calculate the *RMSE* for the ultimately *Regularized User+Movie Effect Model* using [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function (already used above in the [UME Model Building] section):
 ```{r, eval=FALSE}

### 2025-11-27 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report, Appendix A: UMGE Model & MF Support Functions description prototype added.

@@
 
-As mentioned in [Chapter 23: *Regularization*, Section 23.7: *Exercises*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the *Course Textbook* the `Movielens` dataset also has a genres column.
-This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_23-7].
+As mentioned in [Chapter 24: *Regularization*, Section 24.4: *Exercises*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) (*Exercises 9-15*) of the *Course Textbook* the `Movielens` dataset also has a genres column.
+This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_24-4].
 
@@
 
-Another way of visualizing a genre effect is shown in the section [Average rating for each genre](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook#Average-rating-for-each-genre) of the article [Movie Recommendation System using R - BEST](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook) mentioned above[@MRS-R-BEST]:
-```{r }
-# For better visibility, we reduce the data for plotting 
-# while keeping the worst and best rating rows:
-plot_ind <- odd(1:nrow(genre_ratins_grp))
-plot_dat <- genre_ratins_grp_sorted[plot_ind,]
-
-plot_dat |>
-  ggplot(aes(x = rating_avg, y = genres)) +
-  ggtitle("Genre Average Rating") +
-  geom_bar(stat = "identity", width = 0.6, fill = "#8888ff") +
-  xlab("Average ratings") +
-  ylab("Genres") +
-  scale_x_continuous(labels = comma, limits = c(0.0, 5.0)) +
-  theme_economist() +
-  theme(plot.title = element_text(vjust = 3.5),
-        axis.title.x = element_text(vjust = -5, face = "bold"),
-        axis.title.y = element_text(vjust = 10, face = "bold"),
-        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 0),
-        axis.text.y = element_text(vjust = 0.25, hjust = 1, size = 8),
-        plot.margin = margin(0.7, 0.5, 1, 1.2, "cm"))
-```
-
 ### Mathematical Description of the UMGE Model
@@
 
-To account for a _genre effect_ we will use the model suggested in the [Chapter 23: *Regularization*, Section 23.7: *Exercises*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) of the *Course Textbook*:
-
-If we define a _genre treatment effect_ $g_{i,j}$ for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect[@IDS2_23-7]:
+If we define a _genre treatment effect_ $g_{i,j}$ for user's $i$ rating of movie $j$, we can use the following models to account for the `genre` effect:
 

### 2025-11-27 reports/capstone-movielens.site/05.appendix.Rmd
Report section [UME Model Regularization: Fine-tuning\: review.
Report, Appendix A: UMGE Model & MF Support Functions description prototype added.

@@
 The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.cmmn_hlp.rglr.fn.tmpl}
-\
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-cmmn_hlp.rglr.fn.tmpl()
-
-```
-:::
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.args .sidebar }
-##### Arguments
-\
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
-  - **:** ;
-
-:::
-::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
-  - **:** ;
-
-:::
-:::
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.code .sidebar }
-##### Source Code
-\
-
-The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
 :::
@@
 The complete source code of the function [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) script on _GitHub_.
+:::
+
+\newpage
+
+#### [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.cmmn_hlp.rglr.fn.tmpl}
+\
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+cmmn_hlp.rglr.fn.tmpl()
+
+```
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+:::
 :::
@@
 
-### OMR Model Helper Functions
+### OMR Model: Helper Functions
 \
@@
 
-### UME Model Utility Functions
+### UME Model: Utility Functions
 \
@@
 
-### UME Model Regularization
+### UME Model: Regularization
 \
@@
 \newpage
+
+### UMGE Model: Utility Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) script on _GitHub_.
+:::
+
+#### [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) Function {#func.train_user_movie_genre_effect}
+\
+
+Trains (and optionally *regularizes* if the [lambda](#) argument is non-default) the *User+Movie Effect (UME) Model* using the training dataset passed in the [train_set](#func.train_user_movie_genre_effect.args.train_set) argument.
+
+::: { #func.train_user_movie_genre_effect.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.train_user_movie_genre_effect.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_user_movie_genre_effect.args.train_set .sidebar }
+  - **train_set:** Training dataset;
+
+:::
+::: { #func.train_user_movie_genre_effect.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.train_user_movie_genre_effect.details .sidebar }
+##### Details
+\
+
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
+
+::: { #func.train_user_movie_genre_effect.value .sidebar }
+##### Value
+\
+
+Data frame representing the trained (and also *regularized* if [lambda](#func.train_user_movie_genre_effect.args.lambda) arg value other than default) *UM Effect Model*.
+:::
+
+::: { #func.train_user_movie_genre_effect.code .sidebar }
+##### Source Code
+\
+
+The source code of the [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) function is shown below:
+```{r eval=FALSE}
+train_user_movie_genre_effect <- function(train.sgr, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_user_movie_genre_effect
+`lambda` is `NA`")
+  }
+
+  genre_bias <- train.sgr |>
+      left_join(edx.user_effect, by = "userId") |>
+      left_join(rglr.UM_effect, by = "movieId") |>
+      mutate(resid = rating - (mu + a + b)) |>
+      group_by(genres) |>
+      summarise(g = mean_reg(resid, lambda), n = n())
+
+    train.sgr |>
+      left_join(genre_bias, by = "genres") |>
+      left_join(rglr.UM_effect, by = "movieId") |>
+      group_by(movieId) |>
+      summarise(g = mean(g))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) Function {#func.train_user_movie_genre_effect.cv}
+\
+
+Trains the *User+Movie Effect (UME) Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+
+::: { #func.train_user_movie_genre_effect.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.train_user_movie_genre_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_user_movie_genre_effect.cv.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.train_user_movie_genre_effect.cv.details .sidebar }
+##### Details
+\
+
+Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+:::
+:::
+
+::: { #func.train_user_movie_genre_effect.cv.value .sidebar }
+##### Value
+\
+
+Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
+:::
+
+::: { #func.train_user_movie_genre_effect.cv.code .sidebar }
+##### Source Code
+\
+
+The most important part of the source code of the [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) function is shown below:
+```{r eval=FALSE}
+train_user_movie_genre_effect.cv <- function(lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_user_movie_genre_effect.cv
+`lambda` is `NA`")
+  }
+
+  if(lambda == 0) put_log("Function `train_user_movie_genre_effect.cv`:
+Computing User+Movie+Genre Effect...")
+  else put_log1("Function `train_user_movie_genre_effect.cv`:
+Computing User+Movie+Genre Effect for lambda: %1...",
+                lambda)
+
+  put_log1("Function `train_user_movie_genre_effect.cv`:
+Computing User+Movie+Genre Effects list for %1-Fold Cross Validation samples...", 
+           CVFolds_N)
+
+  start <- put_start_date()
+  user_movie_genre_effects_ls <- lapply(kfold_index, function(fold_i){
+    cv_fold_dat <- edx_CV[[fold_i]]
+
+    put_log2("Processing User+Movie+Genre Effects for %1-Fold Cross Validation samples (Fold %2)...",
+             CVFolds_N,
+             fold_i)
+    umg_effect <- cv_fold_dat$train.sgr |> train_user_movie_genre_effect(lambda)
+
+    put_log2("User+Movie+Genre Effects have been computed for the Fold %1 
+of the %2-Fold Cross Validation samples.",
+             fold_i,
+             CVFolds_N)
+    umg_effect
+  })
+  put_end_date(start)
+  put_log1("Function `train_user_movie_genre_effect.cv`:
+User+Movie+Genre Effects list has been computed for %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  user_movie_genre_effects_united <- union_cv_results(user_movie_genre_effects_ls)
+
+  user_movie_genre_effect <- user_movie_genre_effects_united |>
+    group_by(movieId) |>
+    summarise(g = mean(g))
+
+  if(lambda == 0) put_log("Function `train_user_movie_genre_effect.cv`:
+Training completed: User+Movie+Genre Effects model.")
+  else put_log1("Function `train_user_movie_genre_effect.cv`:
+Training completed: User+Movie+Genre Effects model for lambda: %1...",
+                lambda)
+
+  user_movie_genre_effect
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) Function {#func.calc_user_movie_genre_effect_MSE}
+\
+
+Validates the *UM Effect (UME) Model* produced by the  [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
+
+::: { #func.calc_user_movie_genre_effect_MSE.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.calc_user_movie_genre_effect_MSE.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_user_movie_genre_effect_MSE.args.test_set .sidebar }
+  - **test_set:** Validation dataset;
+
+:::
+::: { #func.calc_user_movie_genre_effect_MSE.args.um_effect .sidebar }
+  - **um_effect:** Data frame representing the *UM Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_user_movie_genre_effect_MSE.details .sidebar }
+##### Details
+\
+
+The function calculates *Mean Squared Error (MSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_MSE.args.um_effect) argument using the validation dataset passed in the [test_set](#func.calc_user_movie_genre_effect_MSE.args.test_set) arg.
+
+:::
+
+::: { #func.calc_user_movie_genre_effect_MSE.value .sidebar }
+##### Value
+\
+
+*MSE* value calculated for the *UME Model*.
+:::
+
+::: { #func.calc_user_movie_genre_effect_MSE.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) function is shown below:
+```{r eval=FALSE}
+calc_user_movie_genre_effect_MSE <- function(test_set, umg_effect){
+  test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(umg_effect, by = "movieId") |>
+    mutate(resid = rating - clamp(mu + a + b + g)) |> 
+    pull(resid) |> mse()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) Function {#func.calc_user_movie_genre_effect_MSE.cv}
+\
+
+Validates the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+
+::: { #func.calc_user_movie_genre_effect_MSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.calc_user_movie_genre_effect_MSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_user_movie_genre_effect_MSE.cv.args.um_effect .sidebar }
+  - **um_effect:** Data frame representing the *UM Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_user_movie_genre_effect_MSE.cv.details .sidebar }
+##### Details
+\
+
+The function calculates *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_MSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_effect_MSE](#func.calc_user_movie_effect_MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
+
+The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object].
+:::
+:::
+
+::: { #func.calc_user_movie_genre_effect_MSE.cv.value .sidebar }
+##### Value
+\
+
+The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+:::
+
+::: { #func.calc_user_movie_genre_effect_MSE.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is shown below:
+```{r eval=FALSE}
+calc_user_movie_genre_effect_MSE.cv <- function(umg_effect){
+  put_log("Computing RMSEs.ResultTibble on Validation Sets...")
+  start <- put_start_date()
+  user_movie_genre_effects_MSEs <- sapply(edx_CV, function(cv_dat){
+    cv_dat$validation_set |> calc_user_movie_genre_effect_MSE(umg_effect)
+  })
+  put_end_date(start)
+
+  plot(user_movie_genre_effects_MSEs)
+  put_log1("MSE values have been plotted for the %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  mean(user_movie_genre_effects_MSEs)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) Function {#func.calc_user_movie_genre_effect_RMSE.cv}
+\
+
+Validates the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+
+::: { #func.calc_user_movie_genre_effect_RMSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+cv.UM_effect.RMSE <- calc_user_movie_genre_effect_RMSE.cv(cv.UM_effect)
+
+```
+:::
+
+::: { #func.calc_user_movie_genre_effect_RMSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_user_movie_genre_effect_RMSE.cv.args.um_effect .sidebar }
+  - **um_effect:** Data frame representing the *UM Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_user_movie_genre_effect_RMSE.cv.details .sidebar }
+##### Details
+\
+
+The function calculates *Root Squared Error (RMSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_effect_MSE.cv](#func.calc_user_movie_effect_MSE.cv) function described above, to calculate the *MSE* for the *UME Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+:::
+:::
+
+::: { #func.calc_user_movie_genre_effect_RMSE.cv.value .sidebar }
+##### Value
+\
+
+The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+:::
+
+::: { #func.calc_user_movie_genre_effect_RMSE.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is shown below:
+```{r eval=FALSE}
+calc_user_movie_genre_effect_RMSE.cv <- function(um_effect){
+  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
+  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
+  put_log2("Function: user_movie_effects_RMSE.cv:
+%1-Fold Cross-Validation ultimate RMSE: %2", length(edx_CV), um_effect_RMSE)
+  um_effect_RMSE
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+### UMGE Model: Regularization
+\
+
+#### [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) Function {#func.regularize.test_lambda.UMG_effect.cv}
+\
+
+Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument for the *User+Movie Effect (UME) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
+
+::: { #func.regularize.test_lambda.UMG_effect.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.regularize.test_lambda.UMG_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.regularize.test_lambda.UMG_effect.cv.args.lambda .sidebar }
+  - **lambda:** *Regularization parameter* $\lambda$ used to validate the model in the *regularization process*.
+
+:::
+:::
+
+::: { #func.regularize.test_lambda.UMG_effect.cv.details .sidebar }
+##### Details
+\
+
+The function is used in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument) as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+
+Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
+
+::: {.noteblock data-latex=""}
+This function is also used to pass as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*, .
+:::
+:::
+
+::: { #func.regularize.test_lambda.UMG_effect.cv.value .sidebar }
+##### Value
+\
+
+The *Root Mean Squared Errors (RMSE)* value computed for the UME Model applying the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument.
+
+:::
+
+::: { #func.regularize.test_lambda.UMG_effect.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is shown below:
+```{r eval=FALSE}
+regularize.test_lambda.UMG_effect.cv <- function(lambda){
+  if (is.na(lambda)) {
+    stop("Function: regularize.test_lambda.user_movie_genre_effect.cv
+`lambda` is `NA`")
+  }
+
+  umg_effect <- train_user_movie_genre_effect.cv(lambda)
+  calc_user_movie_genre_effect_RMSE.cv(umg_effect)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L147) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+### Matrix Factorization Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R) script on _GitHub_.
+:::
+
+#### [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) Function {#func.mf.residual.dataframe}
+\
+
+::: { #func.mf.residual.dataframe.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.mf.residual.dataframe.args .sidebar }
+##### Arguments
+\
+
+::: { #func.mf.residual.dataframe.args.file_name .sidebar }
+  - **train_set:** ;
+
+:::
+:::
+
+::: { #func.mf.residual.dataframe.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.mf.residual.dataframe.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.mf.residual.dataframe.code .sidebar }
+##### Source Code
+\
+
+The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) function is shown below:
+```{r eval=FALSE}
+mf.residual.dataframe <- function(train_set){
+  train_set |> 
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(rglr.UMGY_effect, by='year') |>
+    left_join(rglr.UMGYD_effect, by='days') |>
+    mutate(rsdl = rating - (mu + a + b + g + ye + de_smoothed)) |>
+    select(userId, movieId, rsdl)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) script on _GitHub_.
+:::
+:::
+
+#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) Function {#func.UMGYDE_model.predict}
+\
+
+::: { #func.UMGYDE_model.predict.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.UMGYDE_model.predict.args .sidebar }
+##### Arguments
+\
+
+::: { #func.UMGYDE_model.predict.args.file_name .sidebar }
+  - **test_set:** ;
+
+:::
+:::
+
+::: { #func.UMGYDE_model.predict.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.UMGYDE_model.predict.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.UMGYDE_model.predict.code .sidebar }
+##### Source Code
+\
+
+The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is shown below:
+```{r eval=FALSE}
+UMGYDE_model.predict <- function(test_set) {
+  test_set |>
+    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) script on _GitHub_.
+:::
+:::
 

### 2025-11-27 reports/capstone-movielens.site/work/func-descr.template.Rmd
Report, Appendix A: UMGE Model & MF Support Functions description prototype added.

@@
 :::
+
+#### [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.cmmn_hlp.rglr.fn.tmpl}
+\
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+cmmn_hlp.rglr.fn.tmpl()
+
+```
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.cmmn_hlp.rglr.fn.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
+:::
+:::
+
+\newpage
 
@@
 
+### Matrix Factorization Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R) script on _GitHub_.
+:::
+
+#### [mf_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#Lx) Function {#func.mf_func_tmpl}
+\
+
+::: { #func.mf_func_tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.mf_func_tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.mf_func_tmpl.args.file_name .sidebar }
+  - **file_name:** A name used as a base to generate a unique log file name;
+
+:::
+:::
+
+::: { #func.mf_func_tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.mf_func_tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.mf_func_tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [mf_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#Lx) function is shown below:
+```{r eval=FALSE}
+
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mf_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#Lx) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#Lx) script on _GitHub_.
+:::
+:::
+
 ## General Func Tempates -------------------------------------------------------

### 2025-11-27 reports/capstone-movielens.site/work/draft-snippert.Rmd
Function described: train_user_movie_genre_effect.

@@
 :::
+
+### UMGE Model: Support Functions
+\
+
+::: {.noteblock data-latex=""}
+Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions]).
+We have already explained that in the [UME Model Regularization] section. 
+For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
+Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
+:::
+
+#### [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L40) Function {#func.train_user_movie_genre_effect}
+\
+
+We use this function to build and train our model using a _Train Set_ (passing it to the `train.sgr` parameter), which can be any sample of the `edx.sgr` dataset (or the entire dataset itself) described above in the [`edx.sgr` Object] section.
+Here, I only remind that it is the dataset created from the `edx` one by splitting its rows to ensure each belongs to a single _genre_.
+Here is the source code of the function:
+```{r eval=FALSE}
+train_user_movie_genre_effect <- function(train.sgr, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_user_movie_genre_effect
+`lambda` is `NA`")
+  }
+
+  genre_bias <- train.sgr |>
+      left_join(edx.user_effect, by = "userId") |>
+      left_join(rglr.UM_effect, by = "movieId") |>
+      mutate(resid = rating - (mu + a + b)) |>
+      group_by(genres) |>
+      summarise(g = mean_reg(resid, lambda), n = n())
+
+    train.sgr |>
+      left_join(genre_bias, by = "genres") |>
+      left_join(rglr.UM_effect, by = "movieId") |>
+      group_by(movieId) |>
+      summarise(g = mean(g))
+}
+```
+
+#### [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) Function {#func.train_user_movie_genre_effect.cv}
+\
+
+We use this function, defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) script, to train the current model using the _5-Fold Cross Validation_ method.
+Below, we provide a slightly simplified version of the source code of that function:
+```{r eval=FALSE}
+train_user_movie_genre_effect.cv <- function(lambda = 0){
+  # ...
+
+put_log1("Function `train_user_movie_genre_effect.cv`:
+Computing User+Movie+Genre Effects list for %1-Fold Cross Validation samples...", 
+           CVFolds_N)
+
+  start <- put_start_date()
+  user_movie_genre_effects_ls <- lapply(kfold_index, function(fold_i){
+    cv_fold_dat <- edx_CV[[fold_i]]
+
+    put_log2("Processing User+Movie+Genre Effects for %1-Fold Cross Validation samples (Fold %2)...",
+             CVFolds_N,
+             fold_i)
+    umg_effect <- cv_fold_dat$train.sgr |> train_user_movie_genre_effect(lambda)
+
+    put_log2("User+Movie+Genre Effects have been computed for the Fold %1 
+of the %2-Fold Cross Validation samples.",
+             fold_i,
+             CVFolds_N)
+    umg_effect
+  })
+  put_end_date(start)
+  put_log1("Function `train_user_movie_genre_effect.cv`:
+User+Movie+Genre Effects list has been computed for %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  user_movie_genre_effects_united <- union_cv_results(user_movie_genre_effects_ls)
+
+  user_movie_genre_effect <- user_movie_genre_effects_united |>
+    group_by(movieId) |>
+    summarise(g = mean(g))
+
+  if(lambda == 0) put_log("Function `train_user_movie_genre_effect.cv`:
+Training completed: User+Movie+Genre Effects model.")
+  else put_log1("Function `train_user_movie_genre_effect.cv`:
+Training completed: User+Movie+Genre Effects model for lambda: %1...",
+                lambda)
+
+  user_movie_genre_effect
+}
+```
+
+::: {.noteblock data-latex=""}
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions]).
+:::
+
+#### `calc_user_movie_genre_effect_MSE` Function
+\
+
+The source code of the function [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L110) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _Mean Squared Error (MSE)_ of the _UMGE Model_ for the given _Test Set_ is provided below:
+```{r eval=FALSE}
+calc_user_movie_genre_effect_MSE <- function(test_set, umg_effect){
+  test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(umg_effect, by = "movieId") |>
+    mutate(resid = rating - clamp(mu + a + b + g)) |> 
+    pull(resid) |> mse()
+}
+```
+
+\newpage
+
+#### `calc_user_movie_genre_effect_MSE.cv` Function
+\
+
+The source code of the function [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L122) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _5-Fold Cross Validation MSE_ result of the _UMGE Model_ is provided below:
+```{r eval=FALSE}
+calc_user_movie_genre_effect_MSE.cv <- function(umg_effect){
+  put_log("Computing RMSEs.ResultTibble on Validation Sets...")
+  start <- put_start_date()
+  user_movie_genre_effects_MSEs <- sapply(edx_CV, function(cv_dat){
+    cv_dat$validation_set |> calc_user_movie_genre_effect_MSE(umg_effect)
+  })
+  put_end_date(start)
+
+  plot(user_movie_genre_effects_MSEs)
+  put_log1("MSE values have been plotted for the %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  mean(user_movie_genre_effects_MSEs)
+}
+```
+
+#### `calc_user_movie_genre_effect_RMSE` Function
+\
+
+The source code of the function [calc_user_movie_genre_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L118) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _Root Mean Squared Error (RMSE)_ of the _UMGE Model_ for the given _Test Set_ is provided below:
+
+```{r eval=FALSE}
+calc_user_movie_genre_effect_RMSE <- function(test_set, umg_effect){
+  umg_mse <- test_set |> calc_user_movie_genre_effect_MSE(umg_effect)
+  sqrt(umg_mse)
+}
+```
+
+#### `calc_user_movie_genre_effect_RMSE.cv` Function { #func.calc_user_movie_genre_effect_RMSE.cv }
+\
+
+The source code of the function [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L136) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _5-Fold Cross Validation **RMSE**_ result of the _UMGE Model_ is provided below:
+
+```{r eval=FALSE}
+calc_user_movie_genre_effect_RMSE.cv <- function(umg_effect){
+  umg_effect_RMSE <- sqrt(calc_user_movie_genre_effect_MSE.cv(umg_effect))
+  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
+           CVFolds_N, 
+           umg_effect_RMSE)
+
+  umg_effect_RMSE
+}
+```
+
+\newpage
 

### 2025-11-27 reports/capstone-movielens.site/02-3.OMR-model.Rmd

@@
 
-  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model Helper Functions]) to compute _Mean Squared Errors_ using _5-Fold Cross-Validation_ method;
+  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model: Helper Functions]) to compute _Mean Squared Errors_ using _5-Fold Cross-Validation_ method;
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model Helper Functions] section of [Appendix A: Support Functions] to calculate *RMSEs* for the sequence of the deviation values.
+In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model: Helper Functions] section of [Appendix A: Support Functions] to calculate *RMSEs* for the sequence of the deviation values.
 :::

### 2025-11-27 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 ```{r }
-print(head(edx.ordered_movie_ratings))
+head(edx.ordered_movie_ratings)
 ```
@@
 ```{r, include=TRUE}
-print(edx.rating_groups)
+edx.rating_groups
 ```
-
-\newpage
 
@@
 ```{r, include=TRUE}
-print(edx.rating_groups |> arrange(rating))
+edx.rating_groups |> arrange(rating)
 ```

### 2025-11-27 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

@@
 
-As mentioned in [Chapter 24: *Regularization*, Section 24.4: *Exercises*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#exercises) (*Exercises 9-15*) of the *Course Textbook* the `Movielens` dataset also has a genres column.
-This column includes every genre that applies to the movie (some movies fall under several genres)[@IDS2_24-4].
+As we can see from the `edx` dataset structure, the `Movielens` dataset also has a genres column. This column includes every genre that applies to the movie (some movies fall under several genres):
+```{r}
+str(edx)
+```
 
@@
 
-dim(genre_ratins_grp)
-genre_ratins_grp_sorted <- genre_ratins_grp |> sort_by.data.frame(~ rating_avg)
-print(genre_ratins_grp_sorted)
-
 # Creating plot:
@@
 ```
+
 Below are worst and best ratings categories:
@@
 \end{equation}
-
-### UMGE Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions]).
-We have already explained that in the [UME Model Regularization] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
-Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
-:::
-
-#### [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L40) Function {#func.train_user_movie_genre_effect}
-\
-
-We use this function to build and train our model using a _Train Set_ (passing it to the `train.sgr` parameter), which can be any sample of the `edx.sgr` dataset (or the entire dataset itself) described above in the [`edx.sgr` Object] section.
-Here, I only remind that it is the dataset created from the `edx` one by splitting its rows to ensure each belongs to a single _genre_.
-Here is the source code of the function:
-```{r eval=FALSE}
-train_user_movie_genre_effect <- function(train.sgr, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_genre_effect
-`lambda` is `NA`")
-  }
-
-  genre_bias <- train.sgr |>
-      left_join(edx.user_effect, by = "userId") |>
-      left_join(rglr.UM_effect, by = "movieId") |>
-      mutate(resid = rating - (mu + a + b)) |>
-      group_by(genres) |>
-      summarise(g = mean_reg(resid, lambda), n = n())
-
-    train.sgr |>
-      left_join(genre_bias, by = "genres") |>
-      left_join(rglr.UM_effect, by = "movieId") |>
-      group_by(movieId) |>
-      summarise(g = mean(g))
-}
-```
-
-#### [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) Function {#func.train_user_movie_genre_effect.cv}
-\
-
-We use this function, defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L59) script, to train the current model using the _5-Fold Cross Validation_ method.
-Below, we provide a slightly simplified version of the source code of that function:
-```{r eval=FALSE}
-train_user_movie_genre_effect.cv <- function(lambda = 0){
-  # ...
-
-put_log1("Function `train_user_movie_genre_effect.cv`:
-Computing User+Movie+Genre Effects list for %1-Fold Cross Validation samples...", 
-           CVFolds_N)
-
-  start <- put_start_date()
-  user_movie_genre_effects_ls <- lapply(kfold_index, function(fold_i){
-    cv_fold_dat <- edx_CV[[fold_i]]
-
-    put_log2("Processing User+Movie+Genre Effects for %1-Fold Cross Validation samples (Fold %2)...",
-             CVFolds_N,
-             fold_i)
-    umg_effect <- cv_fold_dat$train.sgr |> train_user_movie_genre_effect(lambda)
-
-    put_log2("User+Movie+Genre Effects have been computed for the Fold %1 
-of the %2-Fold Cross Validation samples.",
-             fold_i,
-             CVFolds_N)
-    umg_effect
-  })
-  put_end_date(start)
-  put_log1("Function `train_user_movie_genre_effect.cv`:
-User+Movie+Genre Effects list has been computed for %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  user_movie_genre_effects_united <- union_cv_results(user_movie_genre_effects_ls)
-
-  user_movie_genre_effect <- user_movie_genre_effects_united |>
-    group_by(movieId) |>
-    summarise(g = mean(g))
-
-  if(lambda == 0) put_log("Function `train_user_movie_genre_effect.cv`:
-Training completed: User+Movie+Genre Effects model.")
-  else put_log1("Function `train_user_movie_genre_effect.cv`:
-Training completed: User+Movie+Genre Effects model for lambda: %1...",
-                lambda)
-
-  user_movie_genre_effect
-}
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions]).
-:::
-
-#### `calc_user_movie_genre_effect_MSE` Function
-\
-
-The source code of the function [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L110) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _Mean Squared Error (MSE)_ of the _UMGE Model_ for the given _Test Set_ is provided below:
-```{r eval=FALSE}
-calc_user_movie_genre_effect_MSE <- function(test_set, umg_effect){
-  test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(umg_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b + g)) |> 
-    pull(resid) |> mse()
-}
-```
-
-\newpage
-
-#### `calc_user_movie_genre_effect_MSE.cv` Function
-\
-
-The source code of the function [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L122) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _5-Fold Cross Validation MSE_ result of the _UMGE Model_ is provided below:
-```{r eval=FALSE}
-calc_user_movie_genre_effect_MSE.cv <- function(umg_effect){
-  put_log("Computing RMSEs.ResultTibble on Validation Sets...")
-  start <- put_start_date()
-  user_movie_genre_effects_MSEs <- sapply(edx_CV, function(cv_dat){
-    cv_dat$validation_set |> calc_user_movie_genre_effect_MSE(umg_effect)
-  })
-  put_end_date(start)
-
-  plot(user_movie_genre_effects_MSEs)
-  put_log1("MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_genre_effects_MSEs)
-}
-```
-
-#### `calc_user_movie_genre_effect_RMSE` Function
-\
-
-The source code of the function [calc_user_movie_genre_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L118) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _Root Mean Squared Error (RMSE)_ of the _UMGE Model_ for the given _Test Set_ is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_genre_effect_RMSE <- function(test_set, umg_effect){
-  umg_mse <- test_set |> calc_user_movie_genre_effect_MSE(umg_effect)
-  sqrt(umg_mse)
-}
-```
-
-#### `calc_user_movie_genre_effect_RMSE.cv` Function { #func.calc_user_movie_genre_effect_RMSE.cv }
-\
-
-The source code of the function [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L136) defined in the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R) script to calculate the _5-Fold Cross Validation **RMSE**_ result of the _UMGE Model_ is provided below:
-
-```{r eval=FALSE}
-calc_user_movie_genre_effect_RMSE.cv <- function(umg_effect){
-  umg_effect_RMSE <- sqrt(calc_user_movie_genre_effect_MSE.cv(umg_effect))
-  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
-           CVFolds_N, 
-           umg_effect_RMSE)
-
-  umg_effect_RMSE
-}
-```
-
-\newpage
 

### 2025-11-27 reports/capstone-movielens.site/05.appendix.Rmd

@@
 \
-Splits rows of the original dataset passed in the [data](#) argument for movies that belong to multiple genres.
+Splits rows of the original dataset passed in the [data](#func.splitGenreRows.args.data) argument for movies that belong to multiple genres.
 
@@
 ```{r eval=FALSE}
-dat.sgr <- splitGenreRows(data)
+edx.sgr <- splitGenreRows(edx)
 ```
@@
 \
-
-This function is used internally in the [make_source_datasets](#func.make_source_datasets) function described above in the [Initializing Input Datasets] section to create the `edx.sgr` dataset described below in the [`edx.sgr` Object] section of the [Appendix B: Models Training Datasets].
-
+This function is a wrapper for the [tidyr::separate_rows](https://www.rdocumentation.org/packages/tidyr/versions/1.3.0/topics/separate_rows) `R` function used in *This Project* to split rows belonging to multiple genres of a dataset containing a `genres` column, which is passed in the [data](#func.splitGenreRows.args.data) argument.
+
+::: {.noteblock data-latex=""}
+The `splitGenreRows` function is used internally in the [make_source_datasets](#func.make_source_datasets) function described above in the [Initializing Input Datasets] section to create the `edx.sgr` dataset described below in the [`edx.sgr` Object] section of the [Appendix B: Models Training Datasets].
+:::
 :::
@@
 
+Dataset with the same structure as the one passed in the [data](#func.splitGenreRows.args.data) argument, but with rows that belong to multiple genres split.
 :::
@@
 ```{r eval=FALSE}
+splitGenreRows <- function(data){
+  put("Splitting dataset rows related to multiple genres...")
+  start <- put_start_date()
+  gs_splitted <- data |>
+    separate_rows(genres, sep = "\\|")
+  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
+  put_end_date(start)
+  gs_splitted
+}
 ```
@@
 
-Trains (and optionally *regularizes* if the [lambda](#) argument is non-default) the *User+Movie Effect (UME) Model* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) argument.
+Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_effect.args.lambda) argument value is non-default) the *User+Movie Effect (UME) Model* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) argument.
 
@@
 
-Trains (and optionally *regularizes* if the [lambda](#) argument is non-default) the *User+Movie Effect (UME) Model* using the training dataset passed in the [train_set](#func.train_user_movie_genre_effect.args.train_set) argument.
+Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGE) Model* using the training sample of the `Movielens` dataset (passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument), specially prepared to train the *UMGE Model*.
 
@@
 ```{r eval=FALSE}
+  rglr.UMG_effect <- edx.sgr |> train_user_movie_genre_effect(UMGE.rglr.best_lambda)
 ```
@@
 
-::: { #func.train_user_movie_genre_effect.args.train_set .sidebar }
-  - **train_set:** Training dataset;
+::: { #func.train_user_movie_genre_effect.args.train.sgr .sidebar }
+  - **train.sgr:** Training sample of the `Movielens` dataset with split rows belonging to multiple genres;
 
@@
 \
-
+The dataset passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *This Appendix*.
+
+For example, the [`edx.sgr` Object] is an appropriate dataset as the value of [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr).
+
+::: {.noteblock data-latex=""}
 The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
@@
 
-Data frame representing the trained (and also *regularized* if [lambda](#func.train_user_movie_genre_effect.args.lambda) arg value other than default) *UM Effect Model*.
+Data frame representing the trained (and also *regularized* if [lambda](#func.train_user_movie_genre_effect.args.lambda) arg value other than default) *UMG Effect Model*.
 :::
@@
 
-Trains the *User+Movie Effect (UME) Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Trains the *User+Movie+Genre Effect (UMGE) Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 
-Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
+Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
 :::
@@
 
-Validates the *UM Effect (UME) Model* produced by the  [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
+Validates the *UMG Effect (UMGE) Model* produced by the  [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
 
@@
 ::: { #func.calc_user_movie_genre_effect_MSE.args.um_effect .sidebar }
-  - **um_effect:** Data frame representing the *UM Effect Model*.
+  - **um_effect:** Data frame representing the *UMG Effect Model*.
 
@@
 
-The function calculates *Mean Squared Error (MSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_MSE.args.um_effect) argument using the validation dataset passed in the [test_set](#func.calc_user_movie_genre_effect_MSE.args.test_set) arg.
+The function calculates *Mean Squared Error (MSE)* for the *UMGE Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_MSE.args.um_effect) argument using the validation dataset passed in the [test_set](#func.calc_user_movie_genre_effect_MSE.args.test_set) arg.
 
@@
 
-*MSE* value calculated for the *UME Model*.
+*MSE* value calculated for the *UMGE Model*.
 :::
@@
 
-Validates the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Validates the *UMG Effect (UMGE) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 ::: { #func.calc_user_movie_genre_effect_MSE.cv.args.um_effect .sidebar }
-  - **um_effect:** Data frame representing the *UM Effect Model*.
+  - **um_effect:** Data frame representing the *UMG Effect Model*.
 
@@
 
-The function calculates *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_MSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+The function calculates *MSE* for the *UMGE Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_MSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
 
@@
 
-The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
 :::
@@
 ::: { #func.calc_user_movie_genre_effect_RMSE.cv.args.um_effect .sidebar }
-  - **um_effect:** Data frame representing the *UM Effect Model*.
+  - **um_effect:** Data frame representing the *UMG Effect Model*.
 
@@
 
-The function calculates *Root Squared Error (RMSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_user_movie_effect_MSE.cv](#func.calc_user_movie_effect_MSE.cv) function described above, to calculate the *MSE* for the *UME Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
+The function calculates *Root Squared Error (RMSE)* for the *UMGE Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_effect_MSE.cv](#func.calc_user_movie_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
 
@@
 
-The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
 :::
@@
 
-Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument for the *User+Movie Effect (UME) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
+Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument for the *User+Movie+Genre Effect (UMGE) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
 
@@
 
-The function is used in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument) as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
-
-Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
+The function is used in the *regularization process* of the *UMGE Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument) as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+
+Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
 
@@
 
-The *Root Mean Squared Errors (RMSE)* value computed for the UME Model applying the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument.
+The *Root Mean Squared Errors (RMSE)* value computed for the UMGE Model applying the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument.
 

### 2025-11-28 reports/capstone-movielens.site/05.appendix.Rmd
UMGE Model Support Functions described.

@@
 
-Trains the *User+Movie Effect (UME) Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_effect.args.cv.lambda) argument value is non-default) the *User+Movie Effect (UME) Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 ```{r eval=FALSE}
-UME.lambda_RMSE <- regularize.test_lambda.UM_effect.cv(lambda)
-
-```
+  lambdas <- seq(0, 1, 0.1)
+  cv.UME.preset.result <- 
+    tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above this function is used as a parameter to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*.
+
+Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UM_effect.cv.details) section of *This Description* below.
+:::
 :::
@@
 ::: {.noteblock data-latex=""}
-This function is also used to pass as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*, .
+This function is also intended to be passed as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
 :::
@@
 
-For example, the [`edx.sgr` Object] is an appropriate dataset as the value of [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr).
+For example, the [`edx.sgr` Object] is an appropriate dataset as the value of the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr).
 
@@
 
-Trains the *User+Movie+Genre Effect (UMGE) Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGE) Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 ```{r eval=FALSE}
+# `lambda = 0` by default (the regularization technique is not applied)
+cv.UMG_effect <- train_user_movie_genre_effect.cv()
+
+umg_effect <- train_user_movie_genre_effect.cv(lambda)
 ```
@@
 
-Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+Under the hood, this function internally calls the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
 It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
@@
 ```{r eval=FALSE}
-train_user_movie_genre_effect.cv <- function(lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_genre_effect.cv
-`lambda` is `NA`")
-  }
-
-  if(lambda == 0) put_log("Function `train_user_movie_genre_effect.cv`:
-Computing User+Movie+Genre Effect...")
-  else put_log1("Function `train_user_movie_genre_effect.cv`:
-Computing User+Movie+Genre Effect for lambda: %1...",
-                lambda)
-
-  put_log1("Function `train_user_movie_genre_effect.cv`:
-Computing User+Movie+Genre Effects list for %1-Fold Cross Validation samples...", 
-           CVFolds_N)
-
-  start <- put_start_date()
   user_movie_genre_effects_ls <- lapply(kfold_index, function(fold_i){
     cv_fold_dat <- edx_CV[[fold_i]]
-
-    put_log2("Processing User+Movie+Genre Effects for %1-Fold Cross Validation samples (Fold %2)...",
-             CVFolds_N,
-             fold_i)
     umg_effect <- cv_fold_dat$train.sgr |> train_user_movie_genre_effect(lambda)
-
-    put_log2("User+Movie+Genre Effects have been computed for the Fold %1 
-of the %2-Fold Cross Validation samples.",
-             fold_i,
-             CVFolds_N)
     umg_effect
   })
-  put_end_date(start)
-  put_log1("Function `train_user_movie_genre_effect.cv`:
-User+Movie+Genre Effects list has been computed for %1-Fold Cross Validation samples.", 
-           CVFolds_N)
 
@@
 
-  if(lambda == 0) put_log("Function `train_user_movie_genre_effect.cv`:
-Training completed: User+Movie+Genre Effects model.")
-  else put_log1("Function `train_user_movie_genre_effect.cv`:
-Training completed: User+Movie+Genre Effects model for lambda: %1...",
-                lambda)
-
   user_movie_genre_effect
@@
 
-Validates the *UMG Effect (UMGE) Model* produced by the  [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
+Validates the *UMG Effect (UMGE) Model* produced by the  [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call.
 
@@
 ```{r eval=FALSE}
+umg_mse <- test_set |> calc_user_movie_genre_effect_MSE(umg_effect)
 ```
@@
 :::
-::: { #func.calc_user_movie_genre_effect_MSE.args.um_effect .sidebar }
-  - **um_effect:** Data frame representing the *UMG Effect Model*.
+::: { #func.calc_user_movie_genre_effect_MSE.args.umg_effect .sidebar }
+  - **umg_effect:** Data frame representing the *UMG Effect Model*.
 
@@
 
-The function calculates *Mean Squared Error (MSE)* for the *UMGE Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_MSE.args.um_effect) argument using the validation dataset passed in the [test_set](#func.calc_user_movie_genre_effect_MSE.args.test_set) arg.
+The function calculates *Mean Squared Error (MSE)* for the *UMGE Model* passed in the [umg_effect](#func.calc_user_movie_genre_effect_MSE.args.umg_effect) argument using the validation dataset passed in the [test_set](#func.calc_user_movie_genre_effect_MSE.args.test_set) arg.
 
@@
 
-Validates the *UMG Effect (UMGE) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Validates the *UMG Effect (UMGE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
 
@@
 ```{r eval=FALSE}
+  umg_effect_RMSE <- sqrt(calc_user_movie_genre_effect_MSE.cv(umg_effect))
 ```
@@
 
-::: { #func.calc_user_movie_genre_effect_MSE.cv.args.um_effect .sidebar }
-  - **um_effect:** Data frame representing the *UMG Effect Model*.
+::: { #func.calc_user_movie_genre_effect_MSE.cv.args.umg_effect .sidebar }
+  - **umg_effect:** Data frame representing the *UMG Effect Model*.
 
@@
 
-The function calculates *MSE* for the *UMGE Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_MSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_user_movie_effect_MSE](#func.calc_user_movie_effect_MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
+The function calculates *MSE* for the *UMGE Model* passed in the [umg_effect](#func.calc_user_movie_genre_effect_MSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_genre_effect_MSE](#func.calc_user_movie_genre_effect_MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
 
@@
 
-The source code of the [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is shown below:
+The simplified version of the source code of the [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is shown below:
 ```{r eval=FALSE}
 calc_user_movie_genre_effect_MSE.cv <- function(umg_effect){
-  put_log("Computing RMSEs.ResultTibble on Validation Sets...")
-  start <- put_start_date()
   user_movie_genre_effects_MSEs <- sapply(edx_CV, function(cv_dat){
@@
   })
-  put_end_date(start)
-
-  plot(user_movie_genre_effects_MSEs)
-  put_log1("MSE values have been plotted for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
 
@@
 ::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) script on _GitHub_.
+The completed source code of the [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) script on _GitHub_.
 :::
@@
 ```{r eval=FALSE}
-cv.UM_effect.RMSE <- calc_user_movie_genre_effect_RMSE.cv(cv.UM_effect)
-
+cv.UMG_effect.RMSE <- calc_user_movie_genre_effect_RMSE.cv(cv.UMG_effect)
 ```
@@
 
-::: { #func.calc_user_movie_genre_effect_RMSE.cv.args.um_effect .sidebar }
-  - **um_effect:** Data frame representing the *UMG Effect Model*.
+::: { #func.calc_user_movie_genre_effect_RMSE.cv.args.umg_effect .sidebar }
+  - **umg_effect:** Data frame representing the *UMG Effect Model*.
 
@@
 
-The function calculates *Root Squared Error (RMSE)* for the *UMGE Model* passed in the [um_effect](#func.calc_user_movie_genre_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_user_movie_effect_MSE.cv](#func.calc_user_movie_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
+The function calculates *Root Squared Error (RMSE)* for the *UMGE Model* passed in the [umg_effect](#func.calc_user_movie_genre_effect_RMSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_genre_effect_MSE.cv](#func.calc_user_movie_genre_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
 
@@
 
-The source code of the [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is shown below:
-```{r eval=FALSE}
-calc_user_movie_genre_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross-Validation ultimate RMSE: %2", length(edx_CV), um_effect_RMSE)
-  um_effect_RMSE
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) script on _GitHub_.
+The simplified version of the source code of the [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is shown below:
+```{r eval=FALSE}
+calc_user_movie_genre_effect_RMSE.cv <- function(umg_effect){
+  sqrt(calc_user_movie_genre_effect_MSE.cv(umg_effect))
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) script on _GitHub_.
 :::
@@
 ```{r eval=FALSE}
-```
+lambdas <- seq(0, 0.2, 0.01)
+cv.UMGE.preset.result <- 
+  tune.model_param(lambdas, regularize.test_lambda.UMG_effect.cv)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above this function is used as a parameter to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*.
+
+Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMG_effect.cv.details) section of *This Description* below.
+:::
 :::
@@
 
-Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
-
-::: {.noteblock data-latex=""}
-This function is also used to pass as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*, .
+Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
+
+::: {.noteblock data-latex=""}
+This function is also intended to be passed as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
 :::
@@
 
-The source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is shown below:
+The simplified version of the source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is shown below:
 ```{r eval=FALSE}
 regularize.test_lambda.UMG_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.user_movie_genre_effect.cv
-`lambda` is `NA`")
-  }
-
   umg_effect <- train_user_movie_genre_effect.cv(lambda)
@@
 ::: {.noteblock data-latex=""}
-The source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L147) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) script on _GitHub_.
+The complete source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L147) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) script on _GitHub_.
 :::

### 2025-11-28 reports/capstone-movielens.site/02.5.UME-model.Rmd
`UMGE Model Regularization: Fine-tuning` section described.

@@
 ::: {.noteblock data-latex=""}
-The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization] of [Appendix A: Support Functions], respectively.
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization] of [Appendix A: Support Functions], respectively.
 :::
@@
 CVFolds_N)
-
 ```
@@
 str(cv.UME.preset.result)
+cv.UME.preset.result$best_result
 ```

### 2025-11-28 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
`UMGE Model Regularization: Fine-tuning` section described.

@@
 
-The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 20, 000 ratings).
+The plot below shows strong evidence of a genre effect (for illustrative purposes, the plot shows only categories with more than 40, 000 ratings).
 
@@
 ::: {.noteblock data-latex=""}
-The complete source code of builing and training the current model is available in the [Model building: User+Movie+Genre Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1149) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+The complete source code of builing and training the current model is available in the [UMGE Model Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L878) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L878) script on _GitHub_.
 :::
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above we use the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section of [Appendix A: Support Functions].
+:::
+
 ```{r, hist.cv.UMG_effect }
@@
 
-We can now construct predictors and calculate the _RMSE_ of the current model using the
-[calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) function described above:
-
+We can now construct predictors and calculate the _RMSE_ of the *UMGE Model* using the
+following code:
 ```{r, eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGE Model*;
+
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
 :::
@@
 
-As stated in the [UME Model Regularization] section, we implement the _Regularization_ method for our models in the following three steps:
+As we decided earlier (and outlined in the [UME Model Regularization] section), we implement the *Regularization method* for our models in the following three steps:
 
-  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
+  1. **Pre-configuration:** Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples;
 
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
+  2. **Fine-tuning:** Figuring out the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* of the model.
 
-  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.
-
-\newpage
-
-#### UMGE Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L146) function described below are defined in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L145) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L146) script.
-:::
-
-##### [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L146) Function {#func.regularize.test_lambda.UMG_effect.cv}
-\
-
-This function calculates _RMSE_ of the _UMGE Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
-```{r, eval=FALSE}
-regularize.test_lambda.UMG_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.user_movie_genre_effect.cv
-`lambda` is `NA`")
-  }
-
-  umg_effect <- train_user_movie_genre_effect.cv(lambda)
-  calc_user_movie_genre_effect_RMSE.cv(umg_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) calling it from the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
-:::
+  3. **Retraining:** Retraining the model with the best value of $\lambda$ determined in the previous step.
 
@@
 \
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [UMGE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L961) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L961) script.
+:::
+
+As we explain earlier in the [UME Model Regularization: *Pre-configuration*], we need to do some pre-configuration to determine a suitable range of $\lambda$ for subsequent fine-tuning of our current model.
+
+Below we provide the most significant part of the code that performs this operation:
+
+::: {.noteblock data-latex=""}
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGE Model: Regularization] of [Appendix A: Support Functions], respectively.
+:::
 
@@
 ```{r, eval=FALSE}
-  put_log1("Preliminary setting-up of `lambda`s range for %1-Fold Cross Validation samples...",
-           CVFolds_N)
+lambdas <- seq(0, 0.2, 0.01)
 
-  start <- put_start_date()
-  lambdas <- seq(0, 0.2, 0.01)
 cv.UMGE.preset.result <- 
   tune.model_param(lambdas, regularize.test_lambda.UMG_effect.cv)
-  put_end_date(start)
+
 put_log1("Preliminary regularization set-up of `lambda`s range for the UMGE Model has been completed
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [UMGE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
+The custom functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGE Model: Regularization] of [Appendix A: Support Functions], respectively.
 :::
@@
 
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [UMGE Model Regularization: Fine-tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1019) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1019) script on _GitHub_.
+:::
+
 We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
@@
 Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
+
+We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
+For this purpose, we will use the helper function [model.tune.param_range](#func.model.tune.param_range), passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function (already mentioned above in the [UME Model Regularization: *Pre-configuration*] section) as the value of its argument [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value).
 
@@
                             8)
+```
+
+::: {.noteblock data-latex=""}
+The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
+:::
+
+```{r}
 UMG_effect.loop_starter
-#> [1] 0.0   0.1   8.0
-
+UMGE.rglr.fine_tune.cache.path
+```
+```{r, eval=FALSE}
 UMGE.rglr.fine_tune.cache.base_name <- "UMGE.rglr.fine-tuning"
@@
 UMGE.rglr.fine_tune.RMSE.best <- UMGE.rglr.fine_tune.results$best_result["best_RMSE"]
-# best_RMSE 
-#  0.872973
+```
 
+::: {.noteblock data-latex=""}
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization] of [Appendix A: Support Functions], respectively.
+:::
+
+```{r, echo=FALSE}
+writeLines("*** Fine-tuning results object data structure ***")
 ```
@@
 str(UMGE.rglr.fine_tune.results)
+```
+```{r, echo=FALSE}
+writeLines("*** Fine-tuning: best results ***")
+```
+```{r}
 UMGE.rglr.fine_tune.results$best_result
+UMGE.rglr.fine_tune.RMSE.best
 ```
-
-::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be also found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
-:::
 

### 2025-11-28 r/src/capstone-movielens.main.R
Fixes for UME, UMGE models Fine-tuning, and the main script.

@@ -604,7 +604,7 @@ cv.UME.preset.result$tuned.result |>
 log_close()
 #### Open log file for `Fine-tuning` step --------------------------------------
 open_logfile(".UME.rg.fine-tuning")
-#### Fine-tuning Step of the Regularization Method for the User+Movie Model ---- 
+#### UME Model Regularization: Fine-tuning ------------------------------------- 
 endpoints <- 
   get_fine_tune.param.endpoints(cv.UME.preset.result$tuned.result)
 

### 2025-11-28 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [UME Model Regularization: Fine-tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L607) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L607) script on _GitHub_.
+:::
+
 We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section are available in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L607) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L607) script on _GitHub_.
+Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions]) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that the deviations from the mean of $y$ are used to plot, rather than the $y$ values themselves.
 :::

### 2025-11-28 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
-
-We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
-For this purpose, we will use the helper function [model.tune.param_range](#func.model.tune.param_range), passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function (already mentioned above in the [UME Model Regularization: *Pre-configuration*] section) as the value of its argument [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value).
-
 Below we provide the most significant part of the code that performs this operation:
@@
 ```
+
+::: {.noteblock data-latex=""}
+Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions]) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that the deviations from the mean of $y$ are used to plot, rather than the $y$ values themselves.
+:::
+
 \newpage

### 2025-11-29 r/src/capstone-movielens.main.R
UME Model description & Main R script refined.

@@ -647,7 +647,7 @@ UME.rglr.fine_tune.results$tuned.result |>
 log_close()
 #### Open log file for re-training Regularized Model ---------------------------
 open_logfile(".UME.rg.re-train.best-lambda")
-#### Re-training Regularized Model for the best `lambda` -------
+#### UME Model Regularization: Re-training with the best `lambda` -------
 file_name_tmp <- "2.UME.rglr.re-train.best-lambda.RData"
 file_path_tmp <- file.path(UME.regularization.path, file_name_tmp)
 
@@ -1059,7 +1059,7 @@ UMGE.rglr.fine_tune.results$tuned.result |>
 log_close()
 #### Open log for re-training Regularized UMGE Model for the best `lambda` value ----
 open_logfile(".UMGE.rglr.re-train.best-lambda")
-#### Re-train `Regularized UMGE Model` for the best `lambda` value ------------
+#### UMGE Model Regularization: Re-training with the best `lambda` ------------
 file_name_tmp <- "2.UMGE.rglr.re-train.best-lambda.RData"
 file_path_tmp <- file.path(UMGE.regularization.path, file_name_tmp)
 
@@ -1317,7 +1317,7 @@ UMGYE.rglr.fine_tune.results$tuned.result |>
 log_close()
 ### Open log for Re-training Regularized Model for the best `lambda` value------
 open_logfile(".UMGYE.rg.re-train.best-lambda")
-### Re-train Regularized UMGYE Model for the best `lambda` ---------------------
+### UMGYE Model Regularization: Re-training with the best `lambda` ---------------------
 file_name_tmp <- "2.UMGYE.rglr.re-train.best-lambda.RData"
 file_path_tmp <- file.path(UMGYE.regularization.path, file_name_tmp)
 
@@ -1895,7 +1895,7 @@ RMSE_kable(RMSEs.ResultTibble.UMGYDE2)
 #### Close Log -----------------------------------------------------------------
 log_close()
 
-####  Open log for UMGYDE Tuned Model: Re-training with the Best Rarams --------
+####  Open log for UMGYDE Tuned Model: Re-training with the Best Params --------
 open_logfile(".lss.UMGYDE.re-train.best_degree&span")
 #### UMGYDE Tuned Model: Retraining with the best params -----------------------
 file_name_tmp <- "1.lss.UMGYE.re-train.best-params.RData"
[…]

### 2025-11-29 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [UME Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L554) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L554) script.
+:::
+
 We need to do some pre-configuration to determine a suitable range of $\lambda$ for subsequent fine-tuning of our current model.
@@
 ```
-
-::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [UME Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L554) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L554) script.
-:::
 
@@
 
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section are available in the [UME Model Regularization: Re-training with the best `lambda`](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L650) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L650) script on _GitHub_.
+:::
+
 Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model*), for the definitive _RMSE_ calculation and use in subsequent models.
@@
 In the code snippet above we use the [train_user_movie_effect](#func.train_user_movie_effect) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A: Support Functions].
-
-Later in this section, we will also use the custom logging function [print_log1](#func.print_log1) described in the [Logging Functions] section of *the same Appendix*.
 :::
@@
 
-::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section are available in the [Re-training Regularized Model for the best `lambda`](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L650) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L650) script on _GitHub_.
-:::
-
-We calculate the *RMSE* for the ultimately *Regularized User+Movie Effect Model* using [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function (already used above in the [UME Model Building] section):
+Finally, we calculate the *RMSE* for the ultimately *Regularized User+Movie Effect Model* and add the definitive result to our _Result Table_:
 ```{r, eval=FALSE}
@@
 ```
-
-Finally, we add the definitive result for the current model to our _Result Table_:
 ```{r, eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section) to calculate the *RMSE* for the *Current Model*;
+
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
 :::

### 2025-11-29 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 \
+
+::: {.noteblock data-latex=""}
+The complete source code of the _User+Movie Effect_ computation described in this section is available in the [User+Movie Effect (UME) Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L382) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L382) script on _GitHub_.
+:::
 
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the _User+Movie Effect_ computation described in this section is available in the [User+Movie Effect (UME) Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L382) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L382) script on _GitHub_.
+The complete source code of the _User+Movie Effect_ computation described in this section is available in the [UME Model Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L456) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L456) script on _GitHub_.
 :::
@@
 \
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [UME Model Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L526) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L526) script.
+:::
 
@@
 
-Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model*), for the definitive _RMSE_ calculation and use in subsequent models.
+Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model* or *Regularized UME Model* for short), for the definitive _RMSE_ calculation and use in subsequent models:
 ```{r, eval=FALSE}
@@
 
-```{r}
-```
-
 ```{r, echo=FALSE}
-writeLines("*** The Best Fine-tuning Results ***")
+writeLines("*** The Best UM Effect Fine-tuning Results ***")
 ```
@@
 ```{r, echo=FALSE}
-writeLines("*** Regularized User+Movie Effect Structure ***")
+writeLines("*** Regularized UM Effect Structure ***")
 ```
@@
 
-print_log1("Regularized User+Movie Effect Model has been re-trained for the best `lambda`: %1.",
+print_log1("Regularized UME Model has been re-trained for the best `lambda`: %1.",
          UME.rglr.best_lambda)
@@
 
-Finally, we calculate the *RMSE* for the ultimately *Regularized User+Movie Effect Model* and add the definitive result to our _Result Table_:
+Finally, we calculate the *RMSE* for the ultimately *Regularized UME Model* and add the definitive result to our _Result Table_:
 ```{r, eval=FALSE}
@@
 ```{r}
-print_log1("The best RMSE after being regularized: %1",
+print_log1("The best RMSE for the UME Model after being regularized: %1",
          UME.rglr.retrain.RMSE)
@@
 
-  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section) to calculate the *RMSE* for the *Current Model*;
+  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section) to calculate the *RMSE* for the *UME Model*;
 

### 2025-11-29 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

@@
 \
+
+::: {.noteblock data-latex=""}
+The complete source code of the _User+Movie+Genre Effect_ computation described in this section is available in the [User+Movie+Genre Effect (UMGE) Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L730) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L730) script on _GitHub_.
+:::
 
@@
 \
+
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [UMGE Model Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L948) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L948) script.
+:::
 
@@
 
-Now, we can calculate the _Regularized UMG Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section are available in the [UMGE Model Regularization: Re-training with the best `lambda`](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1062) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1062) script on _GitHub_.
+:::
+
+Now, we can refine our _User+Movie+Genre Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie+Genre Effect Model* or *Regularized UMGE Model* for short), for the definitive _RMSE_ calculation and use in subsequent models:
 ```{r, eval=FALSE}
   best_result <- UMGE.rglr.fine_tune.results$best_result
-  # param.best_value        best_RMSE 
-  #     0.03554688       0.87297303
-
   UMGE.rglr.best_lambda <- best_result["param.best_value"]
-  UMGE.rglr.best_RMSE <- best_result["best_RMSE"]
-
-  put_log1("Re-training Regularized User+Movie+Genre Effect Model for the best `lambda`: %1...",
-           UMGE.rglr.best_lambda)
+#  UMGE.rglr.best_RMSE <- best_result["best_RMSE"]
 
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above we use the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A: Support Functions].
+:::
+
+```{r, echo=FALSE}
+writeLines("*** The Best UMG Effect Fine-tuning Results ***")
+```
+```{r}
+UMGE.rglr.fine_tune.results$best_result
+```
+
+```{r, echo=FALSE}
+writeLines("*** Regularized UMG Effect Structure ***")
+```
 ```{r}
 str(rglr.UMG_effect)
+
+print_log1("Regularized UMGE Model has been re-trained for the best `lambda`: %1.",
+         UMGE.rglr.best_lambda)
 ```
 
-::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section are available in the [Re-training Regularized UMG Effect Model for the best $\lambda$](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) script on _GitHub_.
-:::
-
-We calculate the _Root Mean Squared Error_ for the ultimately computed _UMG Effect_ using [calc_UMG_effect_RMSE.cv](#func.calc_UMG_effect_RMSE.cv) function described above as follows:
+Finally, we calculate the *RMSE* for the ultimately *Regularized UMGE Model* and add the definitive result to our _Result Table_:
 ```{r, eval=FALSE}
@@
 ```
-```{r, echo=FALSE}
-  print_log2("Regularized User+Movie+Genre Effect RMSE has been computed for the best `lambda = %1`: %2.",
-           UMGE.rglr.best_lambda,
+```{r}
+print_log1("The best RMSE for the UME Model after being regularized: %1",
          rglr.UMG_effect.RMSE)
 ```
-
-Finally, we add the definitive result for the current model to our _Result Table_:
 ```{r, eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [calc_UMG_effect_RMSE.cv](#func.calc_UMG_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGE Model*;
+
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
 :::

### 2025-12-01 reports/capstone-movielens.site/02-0.methods.Rmd
Fix for bibliography.

@@
 
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 24.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_24-1].We will also use the *K-Fold Cross-Validation* method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 24.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_24-1].We will also use the *Cross-Validation* method as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].
 
@@
 
-  - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the *K-Fold Cross-Validation* in the way explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+   - [`edx_CV` Object](#appndx_b.edx_CV): A list of objects created from samples made from the `edx` dataset to use them for the *K-Fold Cross-Validation* in the way explained in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 

### 2025-12-01 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Fix for bibliography.

@@
 
-Let's begin our analysis by evaluating the simplest model described in [Section 24.1 *Case study: recommendation systems / A first model*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-first-model) of the *Course Textbook (New Edition)*[@IDS2_24-1], and then gradually refine it through further research.
+Let's begin our analysis by evaluating the simplest model described in [Section 33.7.4: *A first model*](https://rafalab.dfci.harvard.edu/dsbook/large-datasets.html#a-first-model) of the *Course Textbook (First Edition)*[@IDS_E1_33-7-4], and then gradually refine it through further research.
 

### 2025-12-01 reports/capstone-movielens.site/05.appendix.Rmd
Fix for bibliography.

@@
 
-Calculates *Mean Squared Error* as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1].
+Calculates *Mean Squared Error* as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].
 
@@
 ::: { #func.mse.args.r .sidebar }
-  - **r:** Numeric vector representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1].
+  - **r:** Numeric vector representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].
 
@@
 
-Calculates the average value of the *Mean Squared Errors* calculated using the *K-Fold Cross-Validation* method as described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Calculates the average value of the *Mean Squared Errors* calculated using the *K-Fold Cross-Validation* method as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].
 
@@
 ::: { #func.mse_cv.args.r_list .sidebar }
-  - **r_list:** List of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1], calculated in `K`th iteration using the *K-Fold Cross-Validation* method.
+  - **r_list:** List of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF], calculated in `K`th iteration using the *K-Fold Cross-Validation* method.
 
@@
 
-Calculates *Root Mean Squared Error* as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1].
+Calculates *Root Mean Squared Error* as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].
 
@@
 ::: { #func.rmse.args.r .sidebar }
-  - **r:** Numeric vector representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1].
+  - **r:** Numeric vector representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].
 
@@
 
-Splits the input dataset passed in the [data](#func.sample_train_validation_sets.args.data) argument into *train* and *validation* datasets in the way described in [Section 30.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Splits the input dataset passed in the [data](#func.sample_train_validation_sets.args.data) argument into *train* and *validation* datasets in the way described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].
 
@@
 
-Validates the *Overall Mean Rating (OMR) Model* with use of *K-Fold Cross-Validation* method as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Validates the *Overall Mean Rating (OMR) Model* with use of *K-Fold Cross-Validation* method as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 \
-Validates the *Overall Mean Rating (OMR) Model* with use of *K-Fold Cross-Validation* method as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Validates the *Overall Mean Rating (OMR) Model* with use of *K-Fold Cross-Validation* method as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 
-Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_effect.args.cv.lambda) argument value is non-default) the *User+Movie Effect (UME) Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_effect.args.cv.lambda) argument value is non-default) the *User+Movie Effect (UME) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 
-Validates the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Validates the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 
-Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
+Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
 
@@
 
-Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGE) Model* with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 
-Validates the *UMG Effect (UMGE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6].
+Validates the *UMG Effect (UMGE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 
-Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
+Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
 
@@
 
-We use the array representation described in [Section 18.5 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook (New Edition)_, for the training data[@IDS2_18-5].
+We use the array representation described in [Section 17.6 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook (New Edition)_, for the training data[@IDS2_17-6].
 For this purpose, we will convert the `edx` dataset into a matrix using the [tidyr::pivot_wider](https://www.rdocumentation.org/packages/tidyr/versions/1.3.0/topics/pivot_wider) function:
@@
 `edx_CV` object is a list of sample objects we need to perform the *K-Fold Cross-Validation* 
-as explained in [Section 30.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_30-6]:
+as explained in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV]:
 ```{r eval=FALSE}

### 2025-12-02 reports/capstone-movielens.site/02-0.methods.Rmd
UMGYE Model support functions documentation prototype added.

@@
 
-We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 24.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_ mentioned above[@IDS2_24-1].We will also use the *Cross-Validation* method as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].
+We will split the `edx` dataset into a training set, which we will use to build and train our models, and a test set in which we will compute the accuracy of our predictions, the way described in [Section 24.1 *Case study: recommendation systems*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-recommendation-systems) of the _Course Textbook (New Edition)_[@IDS2_24-1].We will also use the *Cross-Validation* method as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].
 

### 2025-12-02 reports/capstone-movielens.site/05.appendix.Rmd
UMGYE Model support functions documentation prototype added.

@@
 ```{r eval=FALSE}
+train_user_movie_genre_effect.cv <- function(lambda = 0){
   user_movie_genre_effects_ls <- lapply(kfold_index, function(fold_i){
@@
     umg_effect <- cv_fold_dat$train.sgr |> train_user_movie_genre_effect(lambda)
+
+    put_log2("User+Movie+Genre Effects have been computed for the Fold %1 
+of the %2-Fold Cross Validation samples.",
+             fold_i,
+             CVFolds_N)
+
     umg_effect
@@
     summarise(g = mean(g))
+
+  if(lambda == 0) put_log("Function `train_user_movie_genre_effect.cv`:
+Training completed: User+Movie+Genre Effects model.")
+  else put_log1("Function `train_user_movie_genre_effect.cv`:
+Training completed: User+Movie+Genre Effects model for lambda: %1...",
+                lambda)
 
@@
 The complete source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L147) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+### UMGYE Model: Utility Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) script on _GitHub_.
+:::
+
+#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) Function {#func.train_UMGY_effect}
+\
+
+Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGE) Model* using the training sample of the `Movielens` dataset (passed in the [train.sgr](#func.train_UMGY_effect.args.train.sgr) argument), specially prepared to train the *UMGE Model*.
+
+::: { #func.train_UMGY_effect.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  rglr.UMGY_effect <- edx |> train_UMGY_effect(UMGYE.rglr.best_lambda)
+```
+:::
+
+::: { #func.train_UMGY_effect.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_UMGY_effect.args.train.sgr .sidebar }
+  - **train.sgr:** Training sample of the `Movielens` dataset with split rows belonging to multiple genres;
+
+:::
+::: { #func.train_UMGY_effect.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.train_UMGY_effect.details .sidebar }
+##### Details
+\
+The dataset passed in the [train.sgr](#func.train_UMGY_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *This Appendix*.
+
+For example, the [`edx.sgr` Object] is an appropriate dataset as the value of the [train.sgr](#func.train_UMGY_effect.args.train.sgr).
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
+:::
+
+::: { #func.train_UMGY_effect.value .sidebar }
+##### Value
+\
+
+Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) arg value other than default) *UMG Effect Model*.
+:::
+
+::: { #func.train_UMGY_effect.code .sidebar }
+##### Source Code
+\
+
+The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) Function {#func.train_UMGY_effect.cv}
+\
+
+Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: { #func.train_UMGY_effect.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  cv.UMGY_effect <- train_UMGY_effect.cv()
+```
+:::
+
+::: { #func.train_UMGY_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_UMGY_effect.cv.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.train_UMGY_effect.cv.details .sidebar }
+##### Details
+\
+
+Under the hood, this function internally calls the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+:::
+:::
+
+::: { #func.train_UMGY_effect.cv.value .sidebar }
+##### Value
+\
+
+Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
+:::
+
+::: { #func.train_UMGY_effect.cv.code .sidebar }
+##### Source Code
+\
+
+The most important part of the source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) Function {#func.calc_UMGY_effect_MSE}
+\
+
+Validates the *UMG Effect (UMGE) Model* produced by the  [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call.
+
+::: { #func.calc_UMGY_effect_MSE.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.calc_UMGY_effect_MSE.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_effect_MSE.args.test_set .sidebar }
+  - **test_set:** Validation dataset;
+
+:::
+::: { #func.calc_UMGY_effect_MSE.args.umg_effect .sidebar }
+  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_UMGY_effect_MSE.details .sidebar }
+##### Details
+\
+
+The function calculates *Mean Squared Error (MSE)* for the *UMGE Model* passed in the [umg_effect](#func.calc_UMGY_effect_MSE.args.umg_effect) argument using the validation dataset passed in the [test_set](#func.calc_UMGY_effect_MSE.args.test_set) arg.
+
+:::
+
+::: { #func.calc_UMGY_effect_MSE.value .sidebar }
+##### Value
+\
+
+*MSE* value calculated for the *UMGE Model*.
+:::
+
+::: { #func.calc_UMGY_effect_MSE.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) Function {#func.calc_UMGY_effect_MSE.cv}
+\
+
+Validates the *UMG Effect (UMGE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: { #func.calc_UMGY_effect_MSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.calc_UMGY_effect_MSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_effect_MSE.cv.args.umg_effect .sidebar }
+  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_UMGY_effect_MSE.cv.details .sidebar }
+##### Details
+\
+
+The function calculates *MSE* for the *UMGE Model* passed in the [umg_effect](#func.calc_UMGY_effect_MSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_genre_effect_MSE](#func.calc_user_movie_genre_effect_MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
+
+The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object].
+:::
+:::
+
+::: { #func.calc_UMGY_effect_MSE.cv.value .sidebar }
+##### Value
+\
+
+The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+:::
+
+::: { #func.calc_UMGY_effect_MSE.cv.code .sidebar }
+##### Source Code
+\
+
+The simplified version of the source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The completed source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) Function {#func.calc_UMGY_effect_RMSE.cv}
+\
+
+Validates the *UMG Effect (UMGE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: { #func.calc_UMGY_effect_RMSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.calc_UMGY_effect_RMSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_effect_RMSE.cv.args.umg_effect .sidebar }
+  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_UMGY_effect_RMSE.cv.details .sidebar }
+##### Details
+\
+
+The function calculates *Root Squared Error (RMSE)* for the *UMGE Model* passed in the [umg_effect](#func.calc_UMGY_effect_RMSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_genre_effect_MSE.cv](#func.calc_user_movie_genre_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+:::
+:::
+
+::: { #func.calc_UMGY_effect_RMSE.cv.value .sidebar }
+##### Value
+\
+
+The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+:::
+
+::: { #func.calc_UMGY_effect_RMSE.cv.code .sidebar }
+##### Source Code
+\
+
+The simplified version of the source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) script on _GitHub_.
 :::

### 2025-12-04 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `calc_date_general_effect`.

--- 2025-12-01 reports/capstone-movielens.site/05.appendix.Rmd
@@
 The complete source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L147) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+### UMGYE Model: Utility Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) script on _GitHub_.
+:::
+
+#### [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) Function {#func.calc_date_general_effect}
+\
+
+This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default)of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+
+::: { #func.calc_date_general_effect.usage .sidebar }
+##### Usage
+\
+```{r eval=FALSE}
+  train_set |>
+    calc_date_general_effect(lambda) |>
+    calc_UMGY_effect()
+```
+
+::: {.noteblock data-latex=""}
+In the sample code snippet above the function `calc_date_general_effect` is used internally in the [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+:::
+:::
+
+::: { #func.calc_date_general_effect.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_date_general_effect.args.train_set .sidebar }
+  - **train_set:** Training dataset;
+
+:::
+::: { #func.calc_date_general_effect.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.calc_date_general_effect.details .sidebar }
+##### Details
+\
+
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, is non-default (to be more exact, greater than zero).
+The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
+
+::: { #func.calc_date_general_effect.value .sidebar }
+##### Value
+\
+
+Data frame representing (*regularized* if [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) *Date General Effect*.
+:::
+
+::: { #func.calc_date_general_effect.code .sidebar }
+##### Source Code
+\
+
+Below is a simplified version of the source code for the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function:
+```{r eval=FALSE}
+  dg_effect <- train_set |> 
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    mutate(resid = rating - (mu + a + b + g)) |>
+  group_by(days) |>
+    summarise(de = mean_reg(resid, lambda), 
+              year = mean(year))
+
+  if(lambda == 0) put_log("Function `calc_date_general_effect`:
+Date Global Effect has been computed.")
+  else put_log1("Function `calc_date_general_effect`:
+Date Global Effect has been computed for lambda: %1...",
+                lambda)
+  dg_effect
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) Function {#func.calc_date_general_effect.cv}
+\
+
+Trains (and optionally *regularizes* if the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) the *User+Movie Effect (UME) Model* using the training dataset passed in the [train_set](#func.calc_date_general_effect.cv.args.train_set) argument.
+
+::: { #func.calc_date_general_effect.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  UM_effect <- calc_date_general_effect.cv(train_set, lambda = 0)
+```
+:::
+
+::: { #func.calc_date_general_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_date_general_effect.cv.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.calc_date_general_effect.cv.details .sidebar }
+##### Details
+\
+
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
+
+::: { #func.calc_date_general_effect.cv.value .sidebar }
+##### Value
+\
+
+Data frame representing the trained (and also *regularized* if [lambda](#func.calc_date_general_effect.cv.args.lambda) arg value other than default) *UM Effect Model*.
+:::
+
+::: { #func.calc_date_general_effect.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is shown below:
+```{r eval=FALSE}
+calc_date_general_effect.cv <- function(train_set, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: calc_date_general_effect.cv
+`lambda` is `NA`")
+  }
+
+  UM.effect <- train_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    mutate(resid = rating - (mu + a)) |> 
+    group_by(movieId) |>
+    summarise(b = mean_reg(resid, lambda), n = n())
+
+  stopifnot(!is.na(mean(UM.effect$b)))
+  UM.effect
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) Function {#func.calc_UMGY_effect}
+\
+
+::: { #func.calc_UMGY_effect.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+calc_UMGY_effect()
+
+```
+:::
+
+::: { #func.calc_UMGY_effect.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_effect.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.calc_UMGY_effect.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.calc_UMGY_effect.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.calc_UMGY_effect.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L90) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) Function {#func.train_UMGY_effect}
+\
+
+Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGYE) Model* using the training sample of the `Movielens` dataset (passed in the [train.sgr](#func.train_UMGY_effect.args.train.sgr) argument), specially prepared to train the *UMGYE Model*.
+
+::: { #func.train_UMGY_effect.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  rglr.UMGY_effect <- edx |> train_UMGY_effect(UMGYE.rglr.best_lambda)
+```
+:::
+
+::: { #func.train_UMGY_effect.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_UMGY_effect.args.train.sgr .sidebar }
+  - **train.sgr:** Training sample of the `Movielens` dataset with split rows belonging to multiple genres;
+
+:::
+::: { #func.train_UMGY_effect.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.train_UMGY_effect.details .sidebar }
+##### Details
+\
+The dataset passed in the [train.sgr](#func.train_UMGY_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *This Appendix*.
+
+For example, the [`edx.sgr` Object] is an appropriate dataset as the value of the [train.sgr](#func.train_UMGY_effect.args.train.sgr).
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
+:::
+
+::: { #func.train_UMGY_effect.value .sidebar }
+##### Value
+\
+
+Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) arg value other than default) *UMG Effect Model*.
+:::
+
+::: { #func.train_UMGY_effect.code .sidebar }
+##### Source Code
+\
+
+The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) Function {#func.train_UMGY_effect.cv}
+\
+
+Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGYE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: { #func.train_UMGY_effect.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  cv.UMGY_effect <- train_UMGY_effect.cv()
+```
+:::
+
+::: { #func.train_UMGY_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_UMGY_effect.cv.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.train_UMGY_effect.cv.details .sidebar }
+##### Details
+\
+
+Under the hood, this function internally calls the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+:::
+:::
+
+::: { #func.train_UMGY_effect.cv.value .sidebar }
+##### Value
+\
+
+Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
+:::
+
+::: { #func.train_UMGY_effect.cv.code .sidebar }
+##### Source Code
+\
+
+The most important part of the source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) Function {#func.calc_UMGY_effect_MSE}
+\
+
+Validates the *UMG Effect (UMGYE) Model* produced by the  [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call.
+
+::: { #func.calc_UMGY_effect_MSE.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.calc_UMGY_effect_MSE.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_effect_MSE.args.test_set .sidebar }
+  - **test_set:** Validation dataset;
+
+:::
+::: { #func.calc_UMGY_effect_MSE.args.umg_effect .sidebar }
+  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_UMGY_effect_MSE.details .sidebar }
+##### Details
+\
+
+The function calculates *Mean Squared Error (MSE)* for the *UMGYE Model* passed in the [umg_effect](#func.calc_UMGY_effect_MSE.args.umg_effect) argument using the validation dataset passed in the [test_set](#func.calc_UMGY_effect_MSE.args.test_set) arg.
+
+:::
+
+::: { #func.calc_UMGY_effect_MSE.value .sidebar }
+##### Value
+\
+
+*MSE* value calculated for the *UMGYE Model*.
+:::
+
+::: { #func.calc_UMGY_effect_MSE.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) Function {#func.calc_UMGY_effect_MSE.cv}
+\
+
+Validates the *UMG Effect (UMGYE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: { #func.calc_UMGY_effect_MSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.calc_UMGY_effect_MSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_effect_MSE.cv.args.umg_effect .sidebar }
+  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_UMGY_effect_MSE.cv.details .sidebar }
+##### Details
+\
+
+The function calculates *MSE* for the *UMGYE Model* passed in the [umg_effect](#func.calc_UMGY_effect_MSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_genre_effect_MSE](#func.calc_user_movie_genre_effect_MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
+
+The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object].
+:::
+:::
+
+::: { #func.calc_UMGY_effect_MSE.cv.value .sidebar }
+##### Value
+\
+
+The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+:::
+
+::: { #func.calc_UMGY_effect_MSE.cv.code .sidebar }
+##### Source Code
+\
+
+The simplified version of the source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The completed source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) Function {#func.calc_UMGY_effect_RMSE.cv}
+\
+
+Validates the *UMG Effect (UMGYE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: { #func.calc_UMGY_effect_RMSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.calc_UMGY_effect_RMSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_effect_RMSE.cv.args.umg_effect .sidebar }
+  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_UMGY_effect_RMSE.cv.details .sidebar }
+##### Details
+\
+
+The function calculates *Root Squared Error (RMSE)* for the *UMGYE Model* passed in the [umg_effect](#func.calc_UMGY_effect_RMSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_user_movie_genre_effect_MSE.cv](#func.calc_user_movie_genre_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGYE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+:::
+:::
+
+::: { #func.calc_UMGY_effect_RMSE.cv.value .sidebar }
+##### Value
+\
+
+The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+:::
+
+::: { #func.calc_UMGY_effect_RMSE.cv.code .sidebar }
+##### Source Code
+\
+
+The simplified version of the source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) script on _GitHub_.
 :::

### 2025-12-04 reports/capstone-movielens.site/work/func-descr.template.Rmd
Function described: `calc_date_general_effect`.

@@
 
+### UMGYE Model Regularization
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) script on _GitHub_.
+:::
+
+#### [umgye_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) Function {#func.umgye_rglr_helper.tmpl}
+\
+
+::: { #func.umgye_rglr_helper.tmpl.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+umgye_rglr_helper.tmpl()
+
+```
+:::
+
+::: { #func.umgye_rglr_helper.tmpl.args .sidebar }
+##### Arguments
+\
+
+::: { #func.umgye_rglr_helper.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+::: { #func.umgye_rglr_helper.tmpl.args. .sidebar }
+  - **:** ;
+
+:::
+:::
+
+::: { #func.umgye_rglr_helper.tmpl.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.umgye_rglr_helper.tmpl.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.umgye_rglr_helper.tmpl.code .sidebar }
+##### Source Code
+\
+
+The source code of the [umgye_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [umgye_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L90) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) script on _GitHub_.
+:::
+:::
+
+\newpage
+
 ### Matrix Factorization Functions

### 2025-12-04 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Regularized UMGE Model description: minor fix.
Function described: `calc_date_general_effect.cv`.

@@
 :::
-
-#### [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) Function {#func.calc_date_general_effect}
-\
-
-This is a helper function that calculates the _date general effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
-
-The following is a slightly simplified version of the function's source code:
-```{r eval=FALSE}
-calc_date_general_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: calc_date_general_effect
-`lambda` is `NA`")
-  }
-
-  if(lambda == 0) put_log("Function `calc_date_general_effect`:
-Computing Date Global Effect for given Train Set data...")
-  else put_log1("Function `calc_date_general_effect`:
-Computing Date Global Effect for lambda: %1...",
-                lambda)
-  dg_effect <- train_set |> 
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    mutate(resid = rating - (mu + a + b + g)) |>
-  group_by(days) |>
-    summarise(de = mean_reg(resid, lambda), 
-              year = mean(year))
-  dg_effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete version of the source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) function is available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L2) script on _GitHub_.
-:::
-
-##### Return
-
-A data structure containing information about _Date General Effect_.
-
-#### [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) Function {#func.calc_date_general_effect.cv}
-\
-
-This is a helper function that calculates the _date general effect_ of the user ratings using the _5-Fold Cross Validation_ method and is intended to be used in other functions and scripts (such as [train_UMGY_effect.cv](#func.train_UMGY_effect.cv)) described below.
-
-##### Souurce Code
-\
-
-::: {.noteblock data-latex=""}
-The complete version of the source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) function is available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L30) script on _GitHub_.
-:::
-
-The following is a simplified version of the function's source code:
-```{r eval=FALSE}
-calc_date_general_effect.cv <- function(lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: calc_date_general_effect.cv
-`lambda` is `NA`")
-  }
-
-  date_general_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
-    cv_fold_dat$train_set |> calc_date_general_effect(lambda)
-  })
-  str(date_general_effect_ls)
-
-  date_general_effect_united <- union_cv_results(date_general_effect_ls)
-
-  date_general_effect_united |>
-    group_by(days) |>
-    summarise(de = mean(de, na.rm = TRUE), year = mean(year, na.rm = TRUE))
-}
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions]).
-:::
-
-##### Return
-
-A data structure containing information about _Date General Effect_ as result of _5-Fold Cross Validation_.
-
-\newpage
 
@@
 
-Now, we have a bit better result than one for the previous model.
+Now, we have a bit better result than one for the previous (*Regularized UMGE*) model.
 

### 2025-12-04 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `calc_date_general_effect.cv`.

@@
 
-#### [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) Function {#func.calc_date_general_effect}
-\
-
-This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default)of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+#### [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L4) Function {#func.calc_date_general_effect}
+\
+
+This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
 
@@
 ::: {.noteblock data-latex=""}
-In the sample code snippet above the function `calc_date_general_effect` is used internally in the [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+In the code snippet above, the function `calc_date_general_effect` is called internally from the [train_UMGY_effect](#func.train_UMGY_effect) function described below.
 :::
@@
 
-Below is a simplified version of the source code for the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function:
-```{r eval=FALSE}
+Below is a slightly simplified version of the source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L4) function:
+```{r eval=FALSE}
+calc_date_general_effect <- function(train_set, lambda = 0){
   dg_effect <- train_set |> 
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
+The complete source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L4) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L4) script on _GitHub_.
 :::
@@
 
-#### [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) Function {#func.calc_date_general_effect.cv}
-\
-
-Trains (and optionally *regularizes* if the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) the *User+Movie Effect (UME) Model* using the training dataset passed in the [train_set](#func.calc_date_general_effect.cv.args.train_set) argument.
+#### [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L32) Function {#func.calc_date_general_effect.cv}
+\
+
+This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the _5-Fold Cross Validation_ and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
 
@@
 \
-
-```{r eval=FALSE}
-  UM_effect <- calc_date_general_effect.cv(train_set, lambda = 0)
-```
+```{r eval=FALSE}
+calc_date_general_effect.cv(lambda) |> calc_UMGY_effect()  
+```
+
+::: {.noteblock data-latex=""}
+In the above code snippet, the `calc_date_general_effect.cv` function is called internally from the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv function) function, along with the [calc_UMGY_effect](#func.calc_UMGY_effect) function (both described below).
+:::
 :::
@@
 
-The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
-The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, is non-default (to be more exact, greater than zero).
+The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
 :::
@@
 
-Data frame representing the trained (and also *regularized* if [lambda](#func.calc_date_general_effect.cv.args.lambda) arg value other than default) *UM Effect Model*.
+Data frame representing (*regularized* if [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) *Date General Effect*.
 :::
@@
 
-The source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is shown below:
-```{r eval=FALSE}
-calc_date_general_effect.cv <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: calc_date_general_effect.cv
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
+Below is a simplified version of the source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L32) function:
+```{r eval=FALSE}
+calc_date_general_effect.cv <- function(lambda = 0){
+
+  date_general_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
+    cv_fold_dat$train_set |> calc_date_general_effect(lambda)
+  })
+  put_log1("Function `calc_date_general_effect.cv`:
+Date Global Effect list has been computed for %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  date_general_effect_united <- union_cv_results(date_general_effect_ls)
+
+  date_general_effect <- date_general_effect_united |>
+    group_by(days) |>
+    summarise(de = mean(de, na.rm = TRUE), year = mean(year, na.rm = TRUE))
+
+  if(lambda == 0) put_log("Function `calc_date_general_effect.cv`:
+Training completed: Date Global Effects model.")
+  else put_log1("Function `calc_date_general_effect.cv`:
+Training completed: Date Global Effects model for lambda: %1...",
+                lambda)
+
+  date_general_effect
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L32) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L32) script on _GitHub_.
 :::

### 2025-12-05 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Function described: `calc_UMGY_effect`.

@@
 :::
-
-#### [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L69) Function {#func.calc_UMGY_effect}
-\
-
-This is a helper function that calculates the _UMGY effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
-
-##### Arguments
-\
-
-The function accepts the only parameter `date_general_effect`, which is a data structure returned by any of the following functions described above:
-
-  - [calc_date_general_effect](#func.calc_date_general_effect);
-  - [calc_date_general_effect.cv](#func.calc_date_general_effect.cv).
-
-##### Source Code
-\
-
-The following is the source code of the function:
-```{r eval=FALSE}
-calc_UMGY_effect <- function(date_general_effect){
-  date_general_effect |>
-    group_by(year) |>
-    summarise(ye = mean(de, na.rm = TRUE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L69) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L69) script on _GitHub_.
-:::
-
-##### Return
-
-A data structure containing information about _User+Movie+Genre+Year (UMGY) Effect_.
 

### 2025-12-05 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `calc_UMGY_effect`.

@@
 
+Builds the *User+Movie+Genre+Year Effect (UMGYE) Model* based on the *Date General Effect* data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) or [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_effect.args.date_general_effect) argument.
+
 ::: { #func.calc_UMGY_effect.usage .sidebar }
@@
 ```{r eval=FALSE}
+  train_set |>
+    calc_date_general_effect(lambda) |>
     calc_UMGY_effect()
-
-```
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the function `calc_UMGY_effect` is called internally from the [train_UMGY_effect](#func.train_UMGY_effect) function described below.
+:::
 :::
@@
 
-::: { #func.calc_UMGY_effect.args. .sidebar }
-  - **:** ;
+::: { #func.calc_UMGY_effect.args.date_general_effect .sidebar }
+  - **date_general_effect:** Data frame representing the *Date General Effect*;
 
@@
 
+This is a helper function that is intended to be used internally in the following functions (both described below in this section):
+
+  - [train_UMGY_effect](#func.train_UMGY_effect);
+
+  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
+
+An example of using it in the [train_UMGY_effect](#func.train_UMGY_effect) function is shown above in the [Usage](#func.calc_UMGY_effect.usage) section of *This Description*:
+
 :::
@@
 
+Data frame representing the *UMGYE Model*.
 :::
@@
 ```{r eval=FALSE}
+calc_UMGY_effect <- function(date_general_effect){
+  date_general_effect |>
+    group_by(year) |>
+    summarise(ye = mean(de, na.rm = TRUE))
+}
 ```
@@
 
-Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) arg value other than default) *UMG Effect Model*.
+Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) arg value other than default) *UMGY Effect Model*.
 :::
@@
 
-Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
+Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
 :::
@@
 
-Validates the *UMG Effect (UMGYE) Model* produced by the  [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call.
+Validates the *UMGY Effect (UMGYE) Model* produced by the  [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call.
 
@@
 ::: { #func.calc_UMGY_effect_MSE.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+  - **umg_effect:** Data frame representing the *UMGY Effect Model*.
 
@@
 
-Validates the *UMG Effect (UMGYE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+Validates the *UMGY Effect (UMGYE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 ::: { #func.calc_UMGY_effect_MSE.cv.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+  - **umg_effect:** Data frame representing the *UMGY Effect Model*.
 
@@
 
-The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
 :::
@@
 ::: { #func.calc_UMGY_effect_RMSE.cv.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+  - **umg_effect:** Data frame representing the *UMGY Effect Model*.
 
@@
 
-The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
 :::
@@
 The complete source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+### UMGYE Model: Regularization
+\
+
+#### [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) Function {#func.regularize.test_lambda.UMGY_effect.cv}
+\
+
+Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGY_effect.cv.args.lambda) argument for the *User+Movie+Genre Effect (UMGYE) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
+
+::: { #func.regularize.test_lambda.UMGY_effect.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+lambdas <- seq(0, 0.2, 0.01)
+cv.UMGYE.preset.result <- 
+  tune.model_param(lambdas, regularize.test_lambda.UMGY_effect.cv)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above this function is used as a parameter to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*.
+
+Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMGY_effect.cv.details) section of *This Description* below.
+:::
+:::
+
+::: { #func.regularize.test_lambda.UMGY_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.regularize.test_lambda.UMGY_effect.cv.args.lambda .sidebar }
+  - **lambda:** *Regularization parameter* $\lambda$ used to validate the model in the *regularization process*.
+
+:::
+:::
+
+::: { #func.regularize.test_lambda.UMGY_effect.cv.details .sidebar }
+##### Details
+\
+
+The function is used in the *regularization process* of the *UMGYE Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMGY_effect.cv.args.lambda) argument) as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+
+Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
+
+::: {.noteblock data-latex=""}
+This function is also intended to be passed as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
+:::
+:::
+
+::: { #func.regularize.test_lambda.UMGY_effect.cv.value .sidebar }
+##### Value
+\
+
+The *Root Mean Squared Errors (RMSE)* value computed for the UMGYE Model applying the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGY_effect.cv.args.lambda) argument.
+
+:::
+
+::: { #func.regularize.test_lambda.UMGY_effect.cv.code .sidebar }
+##### Source Code
+\
+
+The simplified version of the source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) function is shown below:
+```{r eval=FALSE}
+regularize.test_lambda.UMGY_effect.cv <- function(lambda){
+  umg_effect <- train_user_movie_genre_effect.cv(lambda)
+  calc_user_movie_genre_effect_RMSE.cv(umg_effect)
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L147) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) script on _GitHub_.
 :::

### 2025-12-05 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 ::: {#textbook.24.1.movie_effects .sidebar }
-In [Section 24.1 *Case study: recommendation systems / Movie effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) of the *Course Textbook (New Edition)*, the author draws our attention to the fact that some movies are generally rated higher than others[@IDS2_24-1].
+In [Section 24.1 *Case study: recommendation systems / Movie effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-movie-effects) of the *Course Textbook (New Edition)*, the author draws our attention to the fact that some movies are generally rated higher than others[@IDS2_24-1_ME].
 :::
@@
 
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
+We can now construct predictors and see how much the `RMSE` improves[@IDS2_24-1_ME]:
 ```{r eval=FALSE}

### 2025-12-05 reports/capstone-movielens.site/05.appendix.Rmd

@@
 
-#### [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) Function {#func.calc_UMGY_effect}
+#### [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) Function {#func.calc_UMGY_effect}
 \
@@
 
-The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) function is shown below:
+The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L90) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#LX) script on _GitHub_.
+The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L90) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) script on _GitHub_.
 :::

### 2025-12-06 reports/capstone-movielens.site/02.5.UME-model.Rmd
Function described: `train_UMGY_effect`.

@@
 
-[Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_ explains why and how we should use _Penalized least squares_ to improve our predictions.
+[Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_ explains why and how we should use _Penalized least squares_ to improve our predictions.
 The author also explains that the general idea of penalized regression is to control the total variability of the movie effects[@IDS2_24-1]:

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `train_UMGY_effect`.

@@
 
-We call this function internally from the functions that compute the _penalized estimates_  as described in [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+We call this function internally from the functions that compute the _penalized estimates_  as described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook (New Edition)*[@IDS2_24-1].
 
@@
 
-The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
 :::
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
 :::
@@
 
-The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, is non-default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, is non-default (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, is non-default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, is non-default (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L90) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) script on _GitHub_.
+The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) script on _GitHub_.
 :::
@@
 
-#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) Function {#func.train_UMGY_effect}
-\
-
-Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGYE) Model* using the training sample of the `Movielens` dataset (passed in the [train.sgr](#func.train_UMGY_effect.args.train.sgr) argument), specially prepared to train the *UMGYE Model*.
+#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L76) Function {#func.train_UMGY_effect}
+\
+
+Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.train_UMGY_effect.args.train_set) argument.
 
@@
 
-::: { #func.train_UMGY_effect.args.train.sgr .sidebar }
-  - **train.sgr:** Training sample of the `Movielens` dataset with split rows belonging to multiple genres;
+::: { #func.train_UMGY_effect.args.train_set .sidebar }
+  - **train_set:** Training sample of the `Movielens` dataset;
 
@@
 \
-The dataset passed in the [train.sgr](#func.train_UMGY_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *This Appendix*.
-
-For example, the [`edx.sgr` Object] is an appropriate dataset as the value of the [train.sgr](#func.train_UMGY_effect.args.train.sgr).
-
-::: {.noteblock data-latex=""}
-The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
-:::
+
 :::
@@
 
-Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) arg value other than default) *UMGY Effect Model*.
+Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
 :::
@@
 
-The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L42) script on _GitHub_.
+The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L76) function is shown below:
+```{r eval=FALSE}
+train_UMGY_effect <- function(train_set, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_UMGY_effect
+`lambda` is `NA`")
+  }
+
+  train_set |>
+    calc_date_general_effect(lambda) |>
+    calc_UMGY_effect()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L76) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L76) script on _GitHub_.
 :::
@@
 
-Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGYE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
 :::
@@
 
-Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGY_effect.cv.args.lambda) argument for the *User+Movie+Genre Effect (UMGYE) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
+Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGY_effect.cv.args.lambda) argument for the *User+Movie+Genre+Year Effect (UMGYE) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
 

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Fix for citing to `Section 24.2 *Penalized least squares*`.

@@
 
-We call this function internally from the functions that compute the _penalized estimates_  as described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+We call this function internally from the functions that compute the _penalized estimates_  as described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook (New Edition)*[@IDS2_24-2].
 
@@
 
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
 :::
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
 :::
@@
 
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, is non-default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, is non-default (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, is non-default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, is non-default (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
 :::

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Function described: train_UMGY_effect.cv.

@@
 ::: {.noteblock data-latex=""}
-In the above code snippet, the `calc_date_general_effect.cv` function is called internally from the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv function) function, along with the [calc_UMGY_effect](#func.calc_UMGY_effect) function (both described below).
+In the above code snippet, the `calc_date_general_effect.cv` function is called internally from the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function, along with the [calc_UMGY_effect](#func.calc_UMGY_effect) function (both described below).
 :::
@@
 
-#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) Function {#func.train_UMGY_effect.cv}
+#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) Function {#func.train_UMGY_effect.cv}
 \
@@
 
+::: {.noteblock data-latex=""}
+This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function (described below in section [UMGYE Model: Regularization] of *This Appendix*) as shown in the [Usage](#func.train_UMGY_effect.cv.usage) subsection of *This Function's Description Section* below.
+:::
+
 ::: { #func.train_UMGY_effect.cv.usage .sidebar }
@@
 ```{r eval=FALSE}
-  cv.UMGY_effect <- train_UMGY_effect.cv()
-```
+  train_UMGY_effect.cv(lambda) |>
+    calc_UMGY_effect_RMSE.cv()
+```
+
+::: {.noteblock data-latex=""}
+In the above code snippet, the `train_UMGY_effect.cv` function is called internally from the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYE Model: Regularization] section and *This Section*, respectively).
+:::
 :::
@@
 
-Under the hood, this function internally calls the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
-It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
-
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in *This Section*).
 
@@
 
-The most important part of the source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) script on _GitHub_.
+The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) function is shown below:
+```{r eval=FALSE}
+train_UMGY_effect.cv <- function(lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_UMGY_effect.cv
+`lambda` is `NA`")
+  }
+
+  calc_date_general_effect.cv(lambda) |> calc_UMGY_effect()  
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) script on _GitHub_.
 :::

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Function described: calc_UMGY_effect_MSE.

@@
 
+Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in *This Section*).
+
+::: {.noteblock data-latex=""}
 The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
-The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
-
+:::
 :::
@@
 
-#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) Function {#func.calc_UMGY_effect_MSE}
-\
-
-Validates the *UMGY Effect (UMGYE) Model* produced by the  [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call.
+#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L94) Function {#func.calc_UMGY_effect_MSE}
+\
+
+Validates the *UMGY Effect (UMGYE) Model* produced by the  [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call.
+
+::: {.noteblock data-latex=""}
+This helper function is used internally in the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function (described below in *This Section*) as shown in the [Usage](#func.calc_UMGY_effect_MSE.usage) subsection of *This Function's Description Section* below.
+:::
 
@@
 ```{r eval=FALSE}
-```
+    cv_fold_dat$validation_set |> calc_UMGY_effect_MSE(UMGY_effect)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the function `calc_UMGY_effect_MSE` is called internally from the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described below in *This Section*.
+:::
 :::
@@
 :::
-::: { #func.calc_UMGY_effect_MSE.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame representing the *UMGY Effect Model*.
+::: { #func.calc_UMGY_effect_MSE.args.UMGY_effect .sidebar }
+  - **UMGY_effect:** Data frame representing the *UMGY Effect Model*.
 
@@
 
-The function calculates *Mean Squared Error (MSE)* for the *UMGYE Model* passed in the [umg_effect](#func.calc_UMGY_effect_MSE.args.umg_effect) argument using the validation dataset passed in the [test_set](#func.calc_UMGY_effect_MSE.args.test_set) arg.
-
+The function calculates *Mean Squared Error (MSE)* for the *UMGYE Model* passed in the [UMGY_effect](#func.calc_UMGY_effect_MSE.args.UMGY_effect) argument using the validation dataset passed in the [test_set](#func.calc_UMGY_effect_MSE.args.test_set) arg.
 :::
@@
 
-The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L112) script on _GitHub_.
+The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L94) function is shown below:
+```{r eval=FALSE}
+calc_UMGY_effect_MSE <- function(test_set, UMGY_effect){
+  test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(UMGY_effect, by='year') |>
+    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
+    pull(resid) |> mse()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L94) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L94) script on _GitHub_.
 :::
@@
 
-::: { #func.calc_UMGY_effect_MSE.cv.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame representing the *UMGY Effect Model*.
+::: { #func.calc_UMGY_effect_MSE.cv.args.UMGY_effect .sidebar }
+  - **UMGY_effect:** Data frame representing the *UMGY Effect Model*.
 
@@
 
-The function calculates *MSE* for the *UMGYE Model* passed in the [umg_effect](#func.calc_UMGY_effect_MSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+The function calculates *MSE* for the *UMGYE Model* passed in the [UMGY_effect](#func.calc_UMGY_effect_MSE.cv.args.UMGY_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
 
@@
 
-::: { #func.calc_UMGY_effect_RMSE.cv.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame representing the *UMGY Effect Model*.
+::: { #func.calc_UMGY_effect_RMSE.cv.args.UMGY_effect .sidebar }
+  - **UMGY_effect:** Data frame representing the *UMGY Effect Model*.
 
@@
 
-The function calculates *Root Squared Error (RMSE)* for the *UMGYE Model* passed in the [umg_effect](#func.calc_UMGY_effect_RMSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+The function calculates *Root Squared Error (RMSE)* for the *UMGYE Model* passed in the [UMGY_effect](#func.calc_UMGY_effect_RMSE.cv.args.UMGY_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
 
@@
 regularize.test_lambda.UMGY_effect.cv <- function(lambda){
-  umg_effect <- train_user_movie_genre_effect.cv(lambda)
-  calc_user_movie_genre_effect_RMSE.cv(umg_effect)
+  umgy_effect <- train_user_movie_genre_effect.cv(lambda)
+  calc_user_movie_genre_effect_RMSE.cv(umgy_effect)
 }

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Function described: calc_UMGY_effect_MSE.cv.

@@
 
-Validates the *UMGY Effect (UMGYE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+Validates the *UMGY Effect (UMGYE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: {.noteblock data-latex=""}
+This helper function is used internally in the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (described below in *This Section*) as shown in the [Usage](#func.calc_UMGY_effect_MSE.cv.usage) subsection of *This Function's Description Section* below.
+:::
 
@@
 ```{r eval=FALSE}
-```
+  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGY_effect))
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the function `calc_UMGY_effect_MSE.cv` is called internally from the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described below in *This Section*.
+:::
 :::
@@
 ::: {.noteblock data-latex=""}
-This function internally calls the [calc_user_movie_genre_effect_MSE](#func.calc_user_movie_genre_effect_MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
+This function internally calls the [calc_UMGY_effect_MSE](#func.calc_UMGY_effect_MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
 
@@
 ```{r eval=FALSE}
+calc_UMGY_effect_MSE.cv <- function(UMGY_effect){
+  start <- put_start_date()
+  UMGY_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
+    cv_fold_dat$validation_set |> calc_UMGY_effect_MSE(UMGY_effect)
+  })
+  put_end_date(start)
+  put_log1("Function: calc_UMGY_effect_MSE.cv
+Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  mean(UMGY_effect_MSEs)
+}
 ```

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Function described: calc_UMGY_effect_RMSE.cv.

@@
 
-#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) Function {#func.calc_UMGY_effect_MSE.cv}
+#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) Function {#func.calc_UMGY_effect_MSE.cv}
 \
@@
 
-The simplified version of the source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) function is shown below:
+The simplified version of the source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The completed source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L124) script on _GitHub_.
+The completed source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) script on _GitHub_.
 :::
@@
 
-Validates the *UMGY Effect (UMGYE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+Validates the *UMGY Effect (UMGYE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 ```{r eval=FALSE}
+cv.UMGY_effect.RMSE <- calc_UMGY_effect_RMSE.cv(cv.UMGY_effect)
 ```
@@
 ```{r eval=FALSE}
+calc_UMGY_effect_RMSE.cv <- function(UMGY_effect){
+  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGY_effect))
+  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
+           CVFolds_N, 
+           UMGY_effect_RMSE)
+
+  UMGY_effect_RMSE
+}
 ```

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Function described: regularize.test_lambda.UMGY_effect.cv.

@@
 
-#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) Function {#func.calc_UMGY_effect_RMSE.cv}
+#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) Function {#func.calc_UMGY_effect_RMSE.cv}
 \
@@
 Validates the *UMGY Effect (UMGYE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: {.noteblock data-latex=""}
+This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function described below in section [UMGYE Model: Regularization] of *This Appendix*.
+:::
 
@@
 ::: {.noteblock data-latex=""}
-This function internally calls the [calc_user_movie_genre_effect_MSE.cv](#func.calc_user_movie_genre_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGYE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
+This function internally calls the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGYE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
 
@@
 
-The simplified version of the source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) function is shown below:
+The source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L138) script on _GitHub_.
+The source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) script on _GitHub_.
 :::
@@
 
-#### [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) Function {#func.regularize.test_lambda.UMGY_effect.cv}
+#### [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) Function {#func.regularize.test_lambda.UMGY_effect.cv}
 \
@@
 ```{r eval=FALSE}
-lambdas <- seq(0, 0.2, 0.01)
+  lambdas <- seq(0, 512, 32)
   cv.UMGYE.preset.result <- 
-  tune.model_param(lambdas, regularize.test_lambda.UMGY_effect.cv)
+    tune.model_param(lambdas, 
+                     regularize.test_lambda.UMGY_effect.cv,
+                     steps.beyond_min = 16)
 ```
@@
 
-The simplified version of the source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) function is shown below:
+The simplified version of the source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) function is shown below:
 ```{r eval=FALSE}
 regularize.test_lambda.UMGY_effect.cv <- function(lambda){
-  umgy_effect <- train_user_movie_genre_effect.cv(lambda)
-  calc_user_movie_genre_effect_RMSE.cv(umgy_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L147) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L148) script on _GitHub_.
+  if (is.na(lambda)) {
+    stop("Function: regularize.test_lambda.UMGY_effect.cv
+`lambda` is `NA`")
+  }
+
+  train_UMGY_effect.cv(lambda) |>
+    calc_UMGY_effect_RMSE.cv()
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L129) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) script on _GitHub_.
 :::

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Function amended: regularize.test_lambda.UMGY_effect.cv.

@@
 
-Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
+Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
 

### 2025-12-06 reports/capstone-movielens.site/02.5.UME-model.Rmd
Fix for citing to `Section 24.2 *Penalized least squares*`.
Citing general review: K-cross validation, Selecting the penalty term / Penalized least squares.

@@
 
-Below, we provide the most significant part of the code for training our model with the use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied:
+Below, we provide the most significant part of the code for training our model with the use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in our project we use `K = 5`):
 ```{r eval=FALSE}
@@
 [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_ explains why and how we should use _Penalized least squares_ to improve our predictions.
-The author also explains that the general idea of penalized regression is to control the total variability of the movie effects[@IDS2_24-1]:
+The author also explains that the general idea of penalized regression is to control the total variability of the movie effects[@IDS2_24-2]:
 $$

### 2025-12-06 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Citing general review: K-cross validation, Selecting the penalty term / Penalized least squares.

@@
 ::: {.noteblock data-latex=""}
-The complete source code of building and training the current model is available in the [UMGYE Model Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1432) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1432) script on _GitHub_.
+The complete source code of building and training the current model is available in the [UMGYE Model Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1163) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1163) script on _GitHub_.
 :::
@@
 ::: {.noteblock data-latex=""}
-We use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function described above to compute the _UMGY Effect_.
+In the code snippet above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function described in section [UMGYE Model: Utility Functions] of [Appendix A: Support Functions] to *This Report*.
 :::

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Citing general review: K-cross validation, Selecting the penalty term / Penalized least squares.

@@
 
-This is a *utility function* used to select the *best values* during the *Model Regularization* process, utilizing the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+This is a *utility function* used to select the *best values* during the *Model Regularization* process, utilizing the *penalized approach* to regularize predictions as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2].
 
@@
 
-Implements an algorithm for selecting the best value of the *regularization parameter* $\lambda$ from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+Implements an algorithm for selecting the best value of the *regularization parameter* $\lambda$ from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument, using a simple approach of selecting the *penalty term* as described in [Section 24.3 *Selecting the penalty term*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-selecting-penalty-term)*[@IDS2_24-3].
 
@@
 
-Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *regularization parameter* $\lambda$ over a given interval determined by the $start$ and $end$ values of the interval passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *regularization parameter* $\lambda$ over a given interval determined by the $start$ and $end$ values of the interval passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
+The algorithm is based on a simple approach of selecting the *penalty term* as described in [Section 24.3 *Selecting the penalty term*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-selecting-penalty-term)*[@IDS2_24-3].
 
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
 
@@
 
-The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object].
+The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 
@@
 
-The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object].
+The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 
@@
 
-Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
+Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object].
+The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object].
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The function is used in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument) as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+The function is used in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument) as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2].
 
@@
 
-Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
+Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The function is used in the *regularization process* of the *UMGE Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument) as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+The function is used in the *regularization process* of the *UMGE Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument) as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2].
 
@@
 
-Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object]..
+Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object].
+The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
 :::
@@
 
-The function is used in the *regularization process* of the *UMGYE Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMGY_effect.cv.args.lambda) argument) as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].
+The function is used in the *regularization process* of the *UMGYE Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMGY_effect.cv.args.lambda) argument) as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2].
 
@@
 
-The simplified version of the source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) function is shown below:
+The source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L129) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) script on _GitHub_.
+The source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L129) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) script on _GitHub_.
 :::

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Helper functions review: Model regularization process.

@@
 ::: {.noteblock data-latex=""}
-This function is also intended to be passed as a parameter to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
+This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
 :::

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Fix for helper functions review: Model regularization process.

@@
 ::: {.noteblock data-latex=""}
-In the code snippet above this function is used as a parameter to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*.
+In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*.
 

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Helper functions review: Model regularization process.

@@
 
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
 :::
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
 :::
@@
 
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, is non-default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the *Date General Effect* calculated by this function only when the *Regularization parameter* value, passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, is non-default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
 The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
 :::
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *Regularization parameter* value, passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, is other than default (to be more exact, greater than zero).
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
 :::

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report section updated: UMGYE Model Building.

@@
 :::
-
-#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) Function {#func.train_UMGY_effect}
-\
-
-This function is used to train the current model using the _Train Set_ dataset passed in the `train_set` parameter.
-The following is the source code of the function:
-```{r eval=FALSE}
-train_UMGY_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_UMGY_effect
-`lambda` is `NA`")
-  }
-
-  train_set |>
-    calc_date_general_effect(lambda) |>
-    calc_UMGY_effect()
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) script on _GitHub_.
-:::
-
-##### Return
-
-A data structure containing information about _User+Movie+Genre+Year (UMGY) Effect_.
-
-#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) Function {#func.train_UMGY_effect.cv}
-\
-
-This function is used to train the current model using the _5-Fold Cross Validation_.
-The following is the source code of the function:
-```{r eval=FALSE}
-train_UMGY_effect.cv <- function(lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_UMGY_effect.cv
-`lambda` is `NA`")
-  }
-
-  calc_date_general_effect.cv(lambda) |> calc_UMGY_effect()  
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) script on _GitHub_.
-:::
-
-##### Return
-
-A data structure containing information about _User+Movie+Genre+Year (UMGY) Effect_.
 
@@
 
-::: {.noteblock data-latex=""}
-In the code snippet above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function described in section [UMGYE Model: Utility Functions] of [Appendix A: Support Functions] to *This Report*.
-:::
-
-We can now construct predictors and calculate the _RMSE_ of the current model using the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described above:
+We can now construct predictors and calculate the *RMSE* of the current model as shown in the code snippet below:
 
@@
 
+```
+
+::: {.noteblock data-latex=""}
+In the code snippets above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described in the [UMGYE Model: Utility Functions] section of [Appendix A: Support Functions] to *This Report*.
+:::
+
+```{r, eval=FALSE}
 RMSEs.ResultTibble.UMGYE <- RMSEs.ResultTibble.rglr.UMGE |> 

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
UMGYE Model: Support Functions: section removed.

@@
 
-### UMGYE Model: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions]).
-We have already explained that in the [UME Model Regularization] section. 
-For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`.
-Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
-:::
-
-#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) Function {#func.calc_UMGY_effect_MSE}
-\
-
-The function calculates the _Mean Squared Error (MSE)_ of the _UMGYE Model_ for the given _Test Set_ passed in the `test_set` parameter.
-
-##### Arguments
-\
-
-  - **test_set:** A _Test Set_ dataset used for _UMGYE Model_ validation;
-  - **UMGY_effect:** A data structure returned by any of the following functions described above:
-    - [calc_UMGY_effect](#func.train_UMGY_effect);
-    - [train_UMGY_effect](#func.train_UMGY_effect);
-    - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
-
-\newpage
-
-##### Source Code
-\
-
-The source code of the function is provided below:
-```{r eval=FALSE}
-calc_UMGY_effect_MSE <- function(test_set, UMGY_effect){
-  test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    left_join(UMGY_effect, by='year') |>
-    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
-    pull(resid) |> mse()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) script.
-:::
-
-#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) Function {#func.calc_UMGY_effect_MSE.cv}
-\
-
-The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGY Effect_ data passed in the `UMGY_effect` parameter.
-
-##### Arguments
-\
-
-The function accepts the only parameter: `UMGY_effect`, which is a data structure returned by the one of the following functions described above:
-
-  - [calc_UMGY_effect](#func.train_UMGY_effect);
-  - [train_UMGY_effect](#func.train_UMGY_effect);
-  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
-
-##### Source Code
-\
-
-The source code of the function is provided below:
-```{r eval=FALSE}
-calc_UMGY_effect_MSE.cv <- function(UMGY_effect){
-  start <- put_start_date()
-  UMGY_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_UMGY_effect_MSE(UMGY_effect)
-  })
-  put_end_date(start)
-  put_log1("Function: calc_UMGY_effect_MSE.cv
-Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(UMGY_effect_MSEs)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) script.
-:::
-
-#### [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) Function {#func.calc_UMGY_effect_RMSE}
-\
-
-The function calculates the _Mean Squared Error (MSE)_ of the _UMGYE Model_ for the given _Test Set_ passed in the `test_set` parameter.
-
-##### Arguments
-\
-
-  - **test_set:** A _Test Set_ dataset used for _UMGYE Model_ validation;
-  - **UMGY_effect:** A data structure returned by any of the following functions described above:
-    - [calc_UMGY_effect](#func.train_UMGY_effect);
-    - [train_UMGY_effect](#func.train_UMGY_effect);
-    - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
-
-##### Source Code
-\
-
-The source code of the function is provided below:
-```{r eval=FALSE}
-calc_UMGY_effect_RMSE <- function(test_set, UMGY_effect){
-  mse <- test_set |> calc_UMGY_effect_MSE(UMGY_effect)
-  sqrt(mse)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) script.
-:::
-
-#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) Function {#func.calc_UMGY_effect_RMSE.cv}
-\
-
-The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGY Effect_ data passed in the `UMGY_effect` parameter.
-
-##### Arguments
-\
-
-The function accepts the only parameter: `UMGY_effect`, which is a data structure returned by the one of the following functions described above:
-
-  - [calc_UMGY_effect](#func.train_UMGY_effect);
-  - [train_UMGY_effect](#func.train_UMGY_effect);
-  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
-
-##### Source Code
-\
-
-The source code of the function is provided below:
-```{r eval=FALSE}
-calc_UMGY_effect_RMSE.cv <- function(UMGY_effect){
-  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGY_effect))
-  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
-           CVFolds_N, 
-           UMGY_effect_RMSE)
-
-  UMGY_effect_RMSE
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) script.
-:::
-
-\newpage
-
 ### UMGYE Model Building
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+In the code snippets above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
 :::

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
UMGYE Model Regularization: Support Functions: section removed.

@@
 
-#### UMGYE Model Regularization: Support Functions
-\
-
-::: {.noteblock data-latex=""}
-The [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L128) function described below are defined in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L127) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L128) script.
-:::
-
-##### [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#128) Function {#func.regularize.test_lambda.UMGY_effect.cv}
-\
-
-This function calculates _RMSE_ of the _UMGYE Model_ using _5-Fold Cross Validation_ for the given $\lambda$ parameter value:
-```{r, eval=FALSE}
-regularize.test_lambda.UMGY_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UMGY_effect.cv
-`lambda` is `NA`")
-  }
-
-  train_UMGY_effect.cv(lambda) |>
-    calc_UMGY_effect_RMSE.cv()
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) calling it from the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
-:::
-
-\newpage
-
 #### UMGYE Model Regularization: Pre-configuration
@@
 
-Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
+Let's perform the pre-configuration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
 

### 2025-12-07 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Fix for bibliography
Fix for the report section: UMGE Model Regularization: Pre-configuration.

@@
 
-Below we provide the most significant part of the code that performs this operation:
+As before, we are going to use the helper function [tune.model_param](#func.tune.model_param), but this time, passing another function as its argument [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value): the function [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) specifically design for the *UMGE Model*.
 
@@
 :::
-
-Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
-
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
 
@@
 
-  - [calc_UMG_effect_RMSE.cv](#func.calc_UMG_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGE Model*;
+  - [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGE Model*;
 

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Fix for the report section: UMGE Model Regularization: Pre-configuration.

@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
 

### 2025-12-07 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report section updated: UMGYE Model Regularization: Pre-configuration.

@@
 ::: {.noteblock data-latex=""}
-The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization] of [Appendix A: Support Functions], respectively.
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::

### 2025-12-07 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report section updated: UMGYE Model Regularization: Pre-configuration.

@@
 
-As we explain earlier in the [UME Model Regularization: *Pre-configuration*], we need to do some pre-configuration to determine a suitable range of $\lambda$ for subsequent fine-tuning of our current model.
+As we explained earlier in the [UME Model Regularization: *Pre-configuration*], we need to do some pre-configuration to determine a suitable range of $\lambda$ for subsequent fine-tuning of our current model.
 
@@
 ::: {.noteblock data-latex=""}
-The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGE Model: Regularization] of [Appendix A: Support Functions], respectively.
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report section updated: UMGYE Model Regularization: Pre-configuration.

--- 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
@@
 
-Let's perform the pre-configuration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1224) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1224) script on _GitHub_.
+:::
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
+As for previous models, we will use the function [tune.model_param](#func.tune.model_param) passing in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument the model-specific helper function (this time designed for the *UMGYE Model*): [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv).
+
+::: {.noteblock data-latex=""}
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
+:::
 
@@
 
-::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) script on _GitHub_.
-:::
-
 Now, let's visualize the results of the $\lambda$ range preconfiguration:

### 2025-12-07 reports/capstone-movielens.site/02.5.UME-model.Rmd
Fix for the following report sections: UME Model Regularization: Fine-tuning, UMGE Model Regularization: Fine-tuning

@@
 We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
-For this purpose, we will use the helper function [model.tune.param_range](#func.model.tune.param_range), passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function (already mentioned above in the [UME Model Regularization: *Pre-configuration*] section) as the value of its argument [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value).
 
-::: {.noteblock data-latex=""}
-The function [model.tune.param_range](#func.model.tune.param_range) is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
-:::
+\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+For this purpose, we will use the helper function [model.tune.param_range](#func.model.tune.param_range), passing the  function (already mentioned above in the [UME Model Regularization: *Pre-configuration*] section) as the value of its argument [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value).
+
+\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
 
@@
 ::: {.noteblock data-latex=""}
-The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
+The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in the code snippet above is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
 :::
@@
 ```
+
+::: {.noteblock data-latex=""}
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization], respectively, of [Appendix A: Support Functions].
+:::
+
 ```{r, echo=FALSE}

### 2025-12-07 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Fix for the following report sections: UME Model Regularization: Fine-tuning, UMGE Model Regularization: Fine-tuning

@@
 ::: {.noteblock data-latex=""}
-The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization] of [Appendix A: Support Functions], respectively.
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::

### 2025-12-07 reports/capstone-movielens.site/02.5.UME-model.Rmd
Fix for fine-tuning-related sections of the report (UME, UMGE, UMGYE models).

@@
 
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
-For this purpose, we will use the helper function [model.tune.param_range](#func.model.tune.param_range), passing the  function (already mentioned above in the [UME Model Regularization: *Pre-configuration*] section) as the value of its argument [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value).
-
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
-
 Below we provide the most significant part of the code that performs this operation:
@@
 ::: {.noteblock data-latex=""}
-Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions]) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that the deviations from the mean of $y$ are used to plot, rather than the $y$ values themselves.
+Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions]) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves.
 :::

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Fix for fine-tuning-related sections of the report (UME, UMGE, UMGYE models).

@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
+The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Fine-tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1281) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1281) script on _GitHub_.
 :::
@@
 We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
-
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
 
@@
                         8)
+```
+
+::: {.noteblock data-latex=""}
+The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
+:::
+
+```{r}
 UMGYE.loop_starter
-#> [1]
-
+UMGYE.rglr.fine_tune.cache.path
+```
+```{r, eval=FALSE}
 cache.base_name <- "UMGYE.rglr.fine-tuning"
@@
                          regularize.test_lambda.UMGY_effect.cv)
+
+UMGYE.rglr.fine_tune.RMSE.best <- UMGYE.rglr.fine_tune.results$best_result["best_RMSE"]
+```
+
+::: {.noteblock data-latex=""}
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
+:::
+
+```{r, echo=FALSE}
+writeLines("*** Fine-tuning results object data structure ***")
 ```
@@
 str(UMGYE.rglr.fine_tune.results)
+```
+```{r, echo=FALSE}
+writeLines("*** Fine-tuning: best results ***")
+```
+```{r}
 UMGYE.rglr.fine_tune.results$best_result
+UMGYE.rglr.fine_tune.RMSE.best
 ```
-
-::: {.noteblock data-latex=""}
-Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions] to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
-:::
 
@@
 ::: {.noteblock data-latex=""}
-We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions], which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions]) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves.
 :::

### 2025-12-07 reports/capstone-movielens.site/05.appendix.Rmd
Fix for fine-tuning-related sections of the report (UME, UMGE, UMGYE models).

@@
 ::: { #func.data.plot.args.normalize .sidebar }
-  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
+- **normalize = FALSE:** If `TRUE`, deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves. Otherwise, the $y$ values are used.
 

### 2025-12-07 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report section completed:  UMGYE Model Regularization: Retraining Model with the best $\lambda$.

@@
 
+\newpage
+
 ```{r, echo=FALSE}
@@
   UMGE.rglr.best_lambda <- best_result["param.best_value"]
-#  UMGE.rglr.best_RMSE <- best_result["best_RMSE"]
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A: Support Functions].
+In the code snippet above we use the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section of [Appendix A: Support Functions].
 :::
@@
 ```{r}
-print_log1("The best RMSE for the UME Model after being regularized: %1",
+print_log1("The best RMSE for the UMGE Model after being regularized: %1",
          rglr.UMG_effect.RMSE)

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report section completed:  UMGYE Model Regularization: Retraining Model with the best $\lambda$.

@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section are available in the [Re-train Regularized UMGYE Model for the best `lambda`](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1589) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1589) script on _GitHub_.
+The complete version of the source code provided in this section are available in the [UMGYE Model Regularization: Re-training with the best `lambda`](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1320) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1320) script on _GitHub_.
 :::
 
-Now, we can calculate the _Regularized UMGYE Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
+Now, we can refine our _User+Movie+Genre+Year Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie+Genre+Year Effect Model* or *Regularized UMGYE Model* for short), for the definitive _RMSE_ calculation and use in subsequent models:
 
 ```{r, eval=FALSE}
+  best_result <- UMGYE.rglr.fine_tune.results$best_result
+  UMGYE.rglr.best_lambda <- best_result["param.best_value"]
+
   rglr.UMGY_effect <- edx |> train_UMGY_effect(UMGYE.rglr.best_lambda)
-
 ```
@@
 ::: {.noteblock data-latex=""}
-Here we use the helper function [train_UMGY_effect](#func.train_UMGY_effect) described above in the [UMGYE Model Regularization: Support Functions] section.
+In the code snippet above we use the [train_UMGY_effect](#func.train_UMGY_effect) function described in the *Models Training: Support Functions /* [UMGYE Model: Utility Functions] section of [Appendix A: Support Functions].
 :::
 
-We calculate the _Root Mean Squared Error_ for the ultimately computed _UMGYE Effect_ using the helper function [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) described above in the [UMGYE Model Regularization: Support Functions] section as follows:
+```{r, echo=FALSE}
+writeLines("*** The Best UMG Effect Fine-tuning Results ***")
+```
+```{r}
+UMGYE.rglr.fine_tune.results$best_result
+```
+
+```{r, echo=FALSE}
+writeLines("*** Regularized UMG Effect Structure ***")
+```
+```{r}
+str(rglr.UMGY_effect)
+
+print_log1("Regularized UMGE Model has been re-trained for the best `lambda`: %1.",
+         UMGYE.rglr.best_lambda)
+```
+
+Finally, we calculate the *RMSE* for the ultimately *Regularized UMGYE Model* and add the definitive result to our _Result Table_:
 ```{r, eval=FALSE}
@@
 ```
-
-Finally, we add the definitive result for the current model to our _Result Table_:
+```{r}
+print_log1("The best RMSE for the UMGYE Model after being regularized: %1",
+         rglr.UMGY_effect.RMSE)
+```
 ```{r, eval=FALSE}
@@
                  msg.glue(UMGYE.rglr.best_lambda))
-
 ```
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UMGYE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYE Model*;
+
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
 :::

### 2025-12-07 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Micro fix for section: User+Movie+Genre+Year+Day Effect (UMGYDE) Model.

@@
 \
+
 ### Mathematical Description of the UMGYDE Model
@@
 
-If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@ref(eq:UMGYDE-model) describing the _UMGYDE Model_, for the current model, takes the form:
+If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@ref(eq:UMGYE-model) describing the _UMGYDE Model_, for the current model, takes the form:
 

### 2025-12-08 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
UMGYDE Model description started (prototype added to Appendix A).

@@
 
-This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
+This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
 
@@
 
-This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset using the _5-Fold Cross Validation_ and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.
+This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset using the _5-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.
 
@@
 
-This is a helper function that calculates the _Smoothed Day Effect_ of user ratings and is intended to be used in other functions and scripts (such as [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)) described below.
+This is a helper function that calculates the _Smoothed Day Effect_ of user ratings and is intended to be used in other custom functions (such as [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)) described below.
 
@@
 
-This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
+This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
 
@@
 
-This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.
+This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.
 

### 2025-12-08 reports/capstone-movielens.site/05.appendix.Rmd
UMGYDE Model description started (prototype added to Appendix A).

@@
 
-In *This Project*, this function is used internally in the [model.tune.param_range](#func.model.tune.param_range) function described in *This Section* below.
+In *This Project*, this function is used internally in the [model.tune.param_range](#func.model.tune.param_range) function described below in this section.
 :::
@@
 
-This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) of the user ratings and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) of the user ratings using a *training dataset* passed in the [train_set](#func.calc_date_general_effect.args.train_set) argument, and is intended for use in other helper functions (such as [train_UMGY_effect](#func.train_UMGY_effect)), described below in this section.
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_date_general_effect` is called internally from the [train_UMGY_effect](#func.train_UMGY_effect) function described below.
+In the code snippet above, the function `calc_date_general_effect` is called internally from the [train_UMGY_effect](#func.train_UMGY_effect) function described below in this section.
 :::
@@
 
-This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the _5-Fold Cross Validation_ and is intended to be used in other functions and scripts (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the _K-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
 
@@
 
-Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in *This Section*).
+Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
 
@@
 ::: {.noteblock data-latex=""}
-In the above code snippet, the `train_UMGY_effect.cv` function is called internally from the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYE Model: Regularization] section and *This Section*, respectively).
+In the above code snippet, the `train_UMGY_effect.cv` function is called internally from the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYE Model: Regularization] section and this section, respectively).
 :::
@@
 
-Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in *This Section*).
+Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
 
@@
 ::: {.noteblock data-latex=""}
-This helper function is used internally in the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function (described below in *This Section*) as shown in the [Usage](#func.calc_UMGY_effect_MSE.usage) subsection of *This Function's Description Section* below.
+This helper function is used internally in the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_effect_MSE.usage) subsection of *This Function's Description Section* below.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_UMGY_effect_MSE` is called internally from the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described below in *This Section*.
+In the code snippet above, the function `calc_UMGY_effect_MSE` is called internally from the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described below in this section.
 :::
@@
 ::: {.noteblock data-latex=""}
-This helper function is used internally in the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (described below in *This Section*) as shown in the [Usage](#func.calc_UMGY_effect_MSE.cv.usage) subsection of *This Function's Description Section* below.
+This helper function is used internally in the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_effect_MSE.cv.usage) subsection of *This Function's Description Section* below.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_UMGY_effect_MSE.cv` is called internally from the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described below in *This Section*.
+In the code snippet above, the function `calc_UMGY_effect_MSE.cv` is called internally from the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described below in this section.
 :::
@@
 The source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L129) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+### UMGYDE Model: Utility Functions
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) script on _GitHub_.
+:::
+
+#### [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) Function {#func.calc_day_general_effect}
+\
+
+This is a helper function that computes the *Day General Effect(hereafter DG Effect or DGI for short)* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) of user ratings on a *given day since the earliest record* in the `edx` dataset, using a *training dataset* passed in the [train_set](#) argument, and is intended for use in other helper functions such as [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (both described below in this section).
+
+::: { #func.calc_day_general_effect.usage .sidebar }
+##### Usage
+\
+```{r eval=FALSE}
+  train_set |> 
+    calc_day_general_effect(lambda) |>
+    calc_UMGY_SmoothedDay_effect(degree, span)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the function `calc_day_general_effect` is called internally along with the [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function from the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function (both described below).
+:::
+:::
+
+::: { #func.calc_day_general_effect.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_day_general_effect.args.train_set .sidebar }
+  - **train_set:** Training dataset;
+
+:::
+::: { #func.calc_day_general_effect.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.calc_day_general_effect.details .sidebar }
+##### Details
+\
+
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
+The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
+
+::: { #func.calc_day_general_effect.value .sidebar }
+##### Value
+\
+
+Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) *Date General Effect*.
+:::
+
+::: { #func.calc_day_general_effect.code .sidebar }
+##### Source Code
+\
+
+Below is a slightly simplified version of the source code of the [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) function:
+```{r eval=FALSE}
+calc_day_general_effect <- function(train_set, lambda = 0){
+  gday_effect <- train_set |> 
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(rglr.UMGY_effect, by='year') |>
+    mutate(resid = rating - (mu + a + b + g + ye)) |>
+    group_by(days) |>
+    summarise(de = mean_reg(resid, lambda), 
+              year = mean(year))
+
+  if(lambda == 0) put_log("Function `calc_day_general_effect`:
+Day General Effect has been computed.")
+  else put_log1("Function `calc_day_general_effect`:
+Day General Effect has been computed for lambda: %1...",
+                lambda)
+  gday_effect
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) Function {#func.calc_day_general_effect.cv}
+\
+
+This is a helper function that calculates the *Day General Effect* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the _5-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+
+::: { #func.calc_day_general_effect.cv.usage .sidebar }
+##### Usage
+\
+```{r eval=FALSE}
+calc_day_general_effect.cv(lambda) |> calc_UMGY_effect()  
+```
+
+::: {.noteblock data-latex=""}
+In the above code snippet, the `calc_day_general_effect.cv` function is called internally from the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function, along with the [calc_UMGY_effect](#func.calc_UMGY_effect) function (both described below).
+:::
+:::
+
+::: { #func.calc_day_general_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_day_general_effect.cv.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.calc_day_general_effect.cv.details .sidebar }
+##### Details
+\
+
+Under the hood, this function internally calls the [calc_day_general_effect](#func.calc_day_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
+The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
+:::
+
+::: { #func.calc_day_general_effect.cv.value .sidebar }
+##### Value
+\
+
+Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) *Date General Effect*.
+:::
+
+::: { #func.calc_day_general_effect.cv.code .sidebar }
+##### Source Code
+\
+
+Below is a simplified version of the source code of the [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) function:
+```{r eval=FALSE}
+calc_day_general_effect.cv <- function(lambda = 0){
+
+  date_general_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
+    cv_fold_dat$train_set |> calc_day_general_effect(lambda)
+  })
+  put_log1("Function `calc_day_general_effect.cv`:
+Date Global Effect list has been computed for %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  date_general_effect_united <- union_cv_results(date_general_effect_ls)
+
+  date_general_effect <- date_general_effect_united |>
+    group_by(days) |>
+    summarise(de = mean(de, na.rm = TRUE), year = mean(year, na.rm = TRUE))
+
+  if(lambda == 0) put_log("Function `calc_day_general_effect.cv`:
+Training completed: Date Global Effects model.")
+  else put_log1("Function `calc_day_general_effect.cv`:
+Training completed: Date Global Effects model for lambda: %1...",
+                lambda)
+
+  date_general_effect
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) Function {#func.calc_UMGY_SmoothedDay_effect}
+\
+
+Builds the *User+Movie+Genre+Year Effect (UMGYDE) Model* based on the *Date General Effect* data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) or [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.
+
+::: { #func.calc_UMGY_SmoothedDay_effect.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  train_set |>
+    calc_date_general_effect(lambda) |>
+    calc_UMGY_SmoothedDay_effect()
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the function `calc_UMGY_SmoothedDay_effect` is called internally from the [train_UMGY_effect](#func.train_UMGY_effect) function described below.
+:::
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_SmoothedDay_effect.args.date_general_effect .sidebar }
+  - **date_general_effect:** Data frame representing the *Date General Effect*;
+
+:::
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.details .sidebar }
+##### Details
+\
+
+This is a helper function that is intended to be used internally in the following functions (both described below in this section):
+
+  - [train_UMGY_effect](#func.train_UMGY_effect);
+
+  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
+
+An example of using it in the [train_UMGY_effect](#func.train_UMGY_effect) function is shown above in the [Usage](#func.calc_UMGY_SmoothedDay_effect.usage) section of *This Description*:
+
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.value .sidebar }
+##### Value
+\
+
+Data frame representing the *UMGYDE Model*.
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) function is shown below:
+```{r eval=FALSE}
+calc_UMGY_SmoothedDay_effect <- function(date_general_effect){
+  date_general_effect |>
+    group_by(year) |>
+    summarise(ye = mean(de, na.rm = TRUE))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) Function {#func.train_UMGY_SmoothedDay_effect}
+\
+
+Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.train_UMGY_SmoothedDay_effect.args.train_set) argument.
+
+::: { #func.train_UMGY_SmoothedDay_effect.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  rglr.UMGYD_effect <- edx |> train_UMGY_SmoothedDay_effect(UMGYDE.rglr.best_lambda)
+```
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.args.train_set .sidebar }
+  - **train_set:** Training sample of the `Movielens` dataset;
+
+:::
+::: { #func.train_UMGY_SmoothedDay_effect.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.details .sidebar }
+##### Details
+\
+
+Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.value .sidebar }
+##### Value
+\
+
+Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.code .sidebar }
+##### Source Code
+\
+
+The source code of the [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is shown below:
+```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect <- function(train_set, lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_UMGY_SmoothedDay_effect
+`lambda` is `NA`")
+  }
+
+  train_set |>
+    calc_date_general_effect(lambda) |>
+    calc_UMGY_effect()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) Function {#func.train_UMGY_SmoothedDay_effect.cv}
+\
+
+Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: {.noteblock data-latex=""}
+This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in section [UMGYDE Model: Regularization] of *This Appendix*) as shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) subsection of *This Function's Description Section* below.
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  train_UMGY_SmoothedDay_effect.cv(lambda) |>
+    calc_UMGY_effect_RMSE.cv()
+```
+
+::: {.noteblock data-latex=""}
+In the above code snippet, the `train_UMGY_SmoothedDay_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYDE Model: Regularization] section and this section, respectively).
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.cv.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.cv.details .sidebar }
+##### Details
+\
+
+Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.cv.value .sidebar }
+##### Value
+\
+
+Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) function is shown below:
+```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect.cv <- function(lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_UMGY_SmoothedDay_effect.cv
+`lambda` is `NA`")
+  }
+
+  calc_date_general_effect.cv(lambda) |> calc_UMGY_effect()  
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) Function {#func.UMGY_SmoothedDay_effect.predict}
+\
+
+Validates the *UMGY Effect (UMGYDE) Model* produced by the  [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call.
+
+::: {.noteblock data-latex=""}
+This helper function is used internally in the [UMGY_SmoothedDay_effect.predict.cv](#func.UMGY_SmoothedDay_effect.predict.cv) function (described below in this section) as shown in the [Usage](#func.UMGY_SmoothedDay_effect.predict.usage) subsection of *This Function's Description Section* below.
+:::
+
+::: { #func.UMGY_SmoothedDay_effect.predict.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+    cv_fold_dat$validation_set |> UMGY_SmoothedDay_effect.predict(UMGYD_effect)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the function `UMGY_SmoothedDay_effect.predict` is called internally from the [UMGY_SmoothedDay_effect.predict.cv](#func.UMGY_SmoothedDay_effect.predict.cv) function described below in this section.
+:::
+:::
+
+::: { #func.UMGY_SmoothedDay_effect.predict.args .sidebar }
+##### Arguments
+\
+
+::: { #func.UMGY_SmoothedDay_effect.predict.args.test_set .sidebar }
+  - **test_set:** Validation dataset;
+
+:::
+::: { #func.UMGY_SmoothedDay_effect.predict.args.UMGYD_effect .sidebar }
+  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.
+
+:::
+:::
+
+::: { #func.UMGY_SmoothedDay_effect.predict.details .sidebar }
+##### Details
+\
+
+The function calculates *Mean Squared Error (MSE)* for the *UMGYDE Model* passed in the [UMGYD_effect](#func.UMGY_SmoothedDay_effect.predict.args.UMGYD_effect) argument using the validation dataset passed in the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) arg.
+:::
+
+::: { #func.UMGY_SmoothedDay_effect.predict.value .sidebar }
+##### Value
+\
+
+*MSE* value calculated for the *UMGYDE Model*.
+:::
+
+::: { #func.UMGY_SmoothedDay_effect.predict.code .sidebar }
+##### Source Code
+\
+
+The source code of the [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) function is shown below:
+```{r eval=FALSE}
+UMGY_SmoothedDay_effect.predict <- function(test_set, UMGYD_effect){
+  test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(UMGYD_effect, by='year') |>
+    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
+    pull(resid) |> mse()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) Function {#func.calc_UMGY_SmoothedDay_effect.MSE}
+\
+
+Validates the *UMGY Effect (UMGYDE) Model* produced by the  [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call.
+
+::: {.noteblock data-latex=""}
+This helper function is used internally in the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.usage) subsection of *This Function's Description Section* below.
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+    cv_fold_dat$validation_set |> calc_UMGY_SmoothedDay_effect.MSE(UMGYD_effect)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the function `calc_UMGY_SmoothedDay_effect.MSE` is called internally from the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) function described below in this section.
+:::
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set .sidebar }
+  - **test_set:** Validation dataset;
+
+:::
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.UMGYD_effect .sidebar }
+  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.details .sidebar }
+##### Details
+\
+
+The function calculates *Mean Squared Error (MSE)* for the *UMGYDE Model* passed in the [UMGYD_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.args.UMGYD_effect) argument using the validation dataset passed in the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) arg.
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.value .sidebar }
+##### Value
+\
+
+*MSE* value calculated for the *UMGYDE Model*.
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) function is shown below:
+```{r eval=FALSE}
+calc_UMGY_SmoothedDay_effect.MSE <- function(test_set, UMGYD_effect){
+  test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(UMGYD_effect, by='year') |>
+    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
+    pull(resid) |> mse()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L147) Function {#func.calc_UMGY_SmoothedDay_effect.MSE.cv}
+\
+
+Validates the *UMGY Effect (UMGYDE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: {.noteblock data-latex=""}
+This helper function is used internally in the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.usage) subsection of *This Function's Description Section* below.
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  UMGY_effect_RMSE <- sqrt(calc_UMGY_SmoothedDay_effect.MSE.cv(UMGYD_effect))
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the function `calc_UMGY_SmoothedDay_effect.MSE.cv` is called internally from the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described below in this section.
+:::
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.UMGYD_effect .sidebar }
+  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.details .sidebar }
+##### Details
+\
+
+The function calculates *MSE* for the *UMGYDE Model* passed in the [UMGYD_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.UMGYD_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_UMGY_SmoothedDay_effect.MSE](#func.calc_UMGY_SmoothedDay_effect.MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
+
+The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+:::
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.value .sidebar }
+##### Value
+\
+
+The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.code .sidebar }
+##### Source Code
+\
+
+The simplified version of the source code of the [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L147) function is shown below:
+```{r eval=FALSE}
+calc_UMGY_SmoothedDay_effect.MSE.cv <- function(UMGYD_effect){
+  start <- put_start_date()
+  UMGY_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
+    cv_fold_dat$validation_set |> calc_UMGY_SmoothedDay_effect.MSE(UMGYD_effect)
+  })
+  put_end_date(start)
+  put_log1("Function: calc_UMGY_SmoothedDay_effect.MSE.cv
+Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+
+  mean(UMGY_effect_MSEs)
+}
+```
+
+::: {.noteblock data-latex=""}
+The completed source code of the [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L147) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L147) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) Function {#func.calc_UMGY_SmoothedDay_effect.RMSE.cv}
+\
+
+Validates the *UMGY Effect (UMGYDE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: {.noteblock data-latex=""}
+This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below in section [UMGYDE Model: Regularization] of *This Appendix*.
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+cv.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(cv.UMGYD_effect)
+```
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.UMGYD_effect .sidebar }
+  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.
+
+:::
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.details .sidebar }
+##### Details
+\
+
+The function calculates *Root Squared Error (RMSE)* for the *UMGYDE Model* passed in the [UMGYD_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.UMGYD_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGYDE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
+
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+:::
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.value .sidebar }
+##### Value
+\
+
+The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) function is shown below:
+```{r eval=FALSE}
+calc_UMGY_SmoothedDay_effect.RMSE.cv <- function(UMGYD_effect){
+  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGYD_effect))
+  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
+           CVFolds_N, 
+           UMGY_effect_RMSE)
+
+  UMGY_effect_RMSE
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+### UMGYDE Model: Regularization
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the  [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) script on _GitHub_.
+:::
+
+#### [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L86) Function {#func.regularize.train_UMGYD_effect.cv}
+\
+
+Trains (and optionally *regularizes* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: {.noteblock data-latex=""}
+This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in section [UMGYDE Model: Regularization] of *This Appendix*) as shown in the [Usage](#func.regularize.train_UMGYD_effect.cv.usage) subsection of *This Function's Description Section* below.
+:::
+
+::: { #func.regularize.train_UMGYD_effect.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+In the above code snippet, the `regularize.train_UMGYD_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYDE Model: Regularization] section and this section, respectively).
+:::
+:::
+
+::: { #func.regularize.train_UMGYD_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.regularize.train_UMGYD_effect.cv.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter.
+
+:::
+:::
+
+::: { #func.regularize.train_UMGYD_effect.cv.details .sidebar }
+##### Details
+\
+
+Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
+:::
+:::
+
+::: { #func.regularize.train_UMGYD_effect.cv.value .sidebar }
+##### Value
+\
+
+Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+:::
+
+::: { #func.regularize.train_UMGYD_effect.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L86) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L86) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L86) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) Function {#func.regularize.test_lambda.UMGYD_effect.cv}
+\
+
+Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.args.lambda) argument for the *User+Movie+Genre+Year Effect (UMGYDE) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
+
+::: { #func.regularize.test_lambda.UMGYD_effect.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  lambdas <- seq(0, 512, 32)
+  cv.UMGYDE.preset.result <- 
+    tune.model_param(lambdas, 
+                     regularize.test_lambda.UMGYD_effect.cv,
+                     steps.beyond_min = 16)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*.
+
+Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMGYD_effect.cv.details) section of *This Description* below.
+:::
+:::
+
+::: { #func.regularize.test_lambda.UMGYD_effect.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.regularize.test_lambda.UMGYD_effect.cv.args.lambda .sidebar }
+  - **lambda:** *Regularization parameter* $\lambda$ used to validate the model in the *regularization process*.
+
+:::
+:::
+
+::: { #func.regularize.test_lambda.UMGYD_effect.cv.details .sidebar }
+##### Details
+\
+
+The function is used in the *regularization process* of the *UMGYDE Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.args.lambda) argument) as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2].
+
+Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
+
+::: {.noteblock data-latex=""}
+This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
+:::
+:::
+
+::: { #func.regularize.test_lambda.UMGYD_effect.cv.value .sidebar }
+##### Value
+\
+
+The *Root Mean Squared Errors (RMSE)* value computed for the UMGYDE Model applying the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.args.lambda) argument.
+
+:::
+
+::: { #func.regularize.test_lambda.UMGYD_effect.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) function is shown below:
+```{r eval=FALSE}
+regularize.test_lambda.UMGYD_effect.cv <- function(lambda){
+  if (is.na(lambda)) {
+    stop("Function: regularize.test_lambda.UMGYD_effect.cv
+`lambda` is `NA`")
+  }
+
+  train_UMGY_effect.cv(lambda) |>
+    calc_UMGY_effect_RMSE.cv()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) script on _GitHub_.
 :::

### 2025-12-08 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function description: calc_day_general_effect.

@@
 
-This is a helper function that computes the *Day General Effect(hereafter DG Effect or DGI for short)* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) of user ratings on a *given day since the earliest record* in the `edx` dataset, using a *training dataset* passed in the [train_set](#) argument, and is intended for use in other helper functions such as [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (both described below in this section).
+This is a helper function that computes the *Day General Effect(hereafter DG Effect or DGI for short)* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) of user ratings on a *given day since the earliest record* in the `edx` dataset, using a *training dataset* passed in the [train_set](#func.calc_day_general_effect.args.train_set) argument, and is intended for use in other helper functions such as [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (both described below in this section).
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_day_general_effect` is called internally along with the [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function from the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function (both described below).
+In the code snippet above, the function `calc_day_general_effect` is called internally along with the [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function from the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function (both described below in this section).
 :::
@@
 ::: { #func.calc_day_general_effect.args.train_set .sidebar }
-  - **train_set:** Training dataset;
+  - **train_set:** Training dataset containing data to compute the *DG Effect*;
 
@@
 ::: { #func.calc_day_general_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 
-Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) *Date General Effect*.
+Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) *DG Effect*.
 :::
@@
 
-Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) *Date General Effect*.
+Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) *Day General Effect*.
 :::
@@
 
-Builds the *User+Movie+Genre+Year Effect (UMGYDE) Model* based on the *Date General Effect* data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) or [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.
+Builds the *User+Movie+Genre+Year Effect (UMGYDE) Model* based on the *Day General Effect* data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) or [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.
 
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.args.date_general_effect .sidebar }
-  - **date_general_effect:** Data frame representing the *Date General Effect*;
+  - **date_general_effect:** Data frame representing the *Day General Effect*;
 

### 2025-12-09 reports/capstone-movielens.site/02-0.methods.Rmd
Refactoring (in progress): K-Fold Cross-Validation citing.

@@
 
-To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of the [Appendix A: Support Functions] of *This Report*), specifically designed for these operations:
+To prepare datasets for processing, we will use the following functions (described in detail in the [Initializing Input Datasets] section of [Appendix A](#appndx_a)), specifically designed for these operations:
 

### 2025-12-09 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Refactoring (in progress): K-Fold Cross-Validation citing.

@@
 
-  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model: Helper Functions]) to compute _Mean Squared Errors_ using _5-Fold Cross-Validation_ method;
+  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model: Helper Functions]) to compute *Mean Squared Errors* with the use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`);
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model: Helper Functions] section of [Appendix A: Support Functions] to calculate *RMSEs* for the sequence of the deviation values.
+In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model: Helper Functions] section of [Appendix A](#appndx_a) to calculate *RMSEs* for the sequence of the deviation values.
 :::
@@
 ::: {.noteblock data-latex=""}
-To print the log, we use the function [print_log1](#func.print_log1) described in the [Logging Functions] section of [Appendix A: Support Functions].
+To print the log, we use the function [print_log1](#func.print_log1) described in the [Logging Functions] section of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
 :::

### 2025-12-09 reports/capstone-movielens.site/02.4.UE-model.Rmd
Refactoring (in progress): K-Fold Cross-Validation citing.

@@
 
-Now, we are ready to compute the _Mean Squared Errors_ from the _5-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A: Support Functions]):
+Now, we are ready to compute the _Mean Squared Errors_ for samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A](#appndx_a)).
+
+::: {.noteblock data-latex=""}
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+:::
+
+The code that performs this operation is shown below:
 ```{r eval=FALSE}
 put_log("Computing the RMSE taking into account user effects...")
-start <- put_start_date()
 edx.user_effect.MSEs <- sapply(edx_CV, function(cv_fold_dat){
@@
 })
-put_end_date(start)
 ```
@@
 ::: {.noteblock data-latex=""}
-For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Visualization Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions].
+For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Visualization Functions](#appndx_a.data_helper.functions) section of [Appendix A](#appndx_a).
 :::

### 2025-12-09 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report section completed:  UMGYE Model Regularization: Retraining Model with the best $\lambda$.
Refactoring (in progress): K-Fold Cross-Validation citing.

@@
 
-Below, we provide the most significant part of the code for training our model with the use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in our project we use `K = 5`):
+Below, we provide the most significant part of the code for training our model with the use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`):
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A: Support Functions].
+In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions].
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions]) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves.
+Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a)) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_effect](#func.train_user_movie_effect) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A: Support Functions].
+In the code snippet above we use the [train_user_movie_effect](#func.train_user_movie_effect) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::

### 2025-12-09 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Refactoring (in progress): K-Fold Cross-Validation citing.

@@
 
-Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
+Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L902) for training our model using the `K-Fold Cross Validation` method, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`):
 ```{r, fn.train_user_movie_genre_effect.cv,   eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section of [Appendix A: Support Functions].
+In the code snippet above we use the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section of [Appendix A: Support Functions].
+In the code snippet above we use the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::

### 2025-12-09 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Refactoring (in progress): K-Fold Cross-Validation citing.

@@
 Below, we provide the most significant line of the code for training our model using the `5-Fold Cross Validation` method:
+
+Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1177) for training our model using the `K-Fold Cross Validation` method, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`):
 ```{r, eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-In the code snippets above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described in the [UMGYE Model: Utility Functions] section of [Appendix A: Support Functions] to *This Report*.
+In the code snippets above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described in the [UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a) to *This Report*.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippets above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+In the code snippets above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
 :::
@@
 
-  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
+  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the `K-Fold Cross Validation` samples (in *this Project* we use `K = 5`);
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_UMGY_effect](#func.train_UMGY_effect) function described in the *Models Training: Support Functions /* [UMGYE Model: Utility Functions] section of [Appendix A: Support Functions].
+In the code snippet above we use the [train_UMGY_effect](#func.train_UMGY_effect) function described in the *Models Training: Support Functions /* [UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::

### 2025-12-09 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Refactoring (in progress): K-Fold Cross-Validation citing.

@@
 Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A: Support Functions]).
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A](#appndx_a)).
 We have already explained that in the [UME Model Regularization] section. 
@@
 ::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions]).
+Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A](#appndx_a)).
 :::
@@
 
-Below, we provide the most significant line of the code for training our model using the `5-Fold Cross Validation` method:
+Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1495) for training our model using the `K-Fold Cross Validation` method, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`):
 ```{r, eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
+Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-The custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) we used above is described in the [Data Helper Functions] section of [Appendix A: Support Functions].
+The custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) we used above is described in the [Data Helper Functions] section of [Appendix A](#appndx_a).
 :::
@@
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
+We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A](#appndx_a), passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
 
@@
 ::: {.noteblock data-latex=""}
-We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A: Support Functions], which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A](#appndx_a), which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
 :::
@@
 
-Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
+Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A](#appndx_a), passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
 
@@
 ::: {.noteblock data-latex=""}
-Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A: Support Functions] to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
+Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A](#appndx_a) to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
 :::

### 2025-12-09 reports/capstone-movielens.site/05.appendix.Rmd
Refactoring (in progress): K-Fold Cross-Validation citing.

@@
 
-In our project this function is used to clamp the computed movie rating values between 0.5 and 5.
+in *this Project* this function is used to clamp the computed movie rating values between 0.5 and 5.
 :::
@@
 
-Calculates the average value of the *Mean Squared Errors* calculated using the *K-Fold Cross-Validation* method as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].
+Calculates the average value of the *Mean Squared Errors* calculated with the use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].
+
+::: {.noteblock data-latex=""}
+The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
+:::
 
@@
 ::: { #func.mse_cv.args.r_list .sidebar }
-  - **r_list:** List of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF], calculated in `K`th iteration using the *K-Fold Cross-Validation* method.
+  - **r_list:** A list of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case Study: Recommender Systems / Loss Function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the *Course Textbook (New Edition)*[@IDS2_24-1_LF], computed in the corresponding iteration of *K-fold cross-validation* (the $K$ is $5$ for *this Project*).
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the custom function [put_log2](#func.put_log2) described above in the [Logging Functions] section of *This Appendix*.
+In the code snippet above, we use the custom function [put_log2](#func.put_log2) described above in the [Logging Functions] section of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the custom function [put_log1](#func.put_log1) described above in the [Logging Functions] section of *This Appendix*.
+In the code snippet above, we use the custom function [put_log1](#func.put_log1) described above in the [Logging Functions] section of *this Appendix*.
 :::
@@
 
-Aggregates the input data frames into a single data frame.
+Aggregates the input data frames passed in the [data_list](#func.union_cv_results.args.data_list) argument into a single data frame.
 
@@
 ::: { #func.union_cv_results.args.data_list .sidebar }
-  - **data_list:** List of data frames representing the results of the *K-Fold Cross-Validation* method execution.
+  - **data_list:** List of data frames representing the results of the *K-Fold Cross-Validation* execution (as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV]).
 
@@
 \
+
 This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the *K-Fold Cross-Validation*) passed in the [data_list](#func.union_cv_results.args.data_list) argument into a single data frame for further processing.
+
+::: {.noteblock data-latex=""}
+The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
+:::
+
 :::
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
+::: {.noteblock data-latex=""}
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+:::
 
@@
 
-The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
 
@@
 
-The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
-The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
+
+::: {.noteblock data-latex=""}
+*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
 :::
@@
 
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
+
 Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
-
-::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
+::: {.noteblock data-latex=""}
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*.
+In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
 
@@
 
-Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
-
-::: {.noteblock data-latex=""}
-This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
+Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+
+::: {.noteblock data-latex=""}
+This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
 :::
@@
 \
-The dataset passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *This Appendix*.
+The dataset passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *this Appendix*.
 
@@
 
-::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
-The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
+
+::: {.noteblock data-latex=""}
+*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
 :::
@@
 
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
+
 Under the hood, this function internally calls the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
-
-::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
+::: {.noteblock data-latex=""}
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
-
-::: {.noteblock data-latex=""}
-This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
+Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+
+::: {.noteblock data-latex=""}
+This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
 :::
@@
 The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
-The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+
+::: {.noteblock data-latex=""}
+*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+::: {.noteblock data-latex=""}
 :::
@@
 
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
+
 Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
-
-::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
-The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+::: {.noteblock data-latex=""}
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
 :::
@@
 ::: {.noteblock data-latex=""}
-This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function (described below in section [UMGYE Model: Regularization] of *This Appendix*) as shown in the [Usage](#func.train_UMGY_effect.cv.usage) subsection of *This Function's Description Section* below.
+This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function (described below in section [UMGYE Model: Regularization] of *this Appendix*) as shown in the [Usage](#func.train_UMGY_effect.cv.usage) subsection of *This Function's Description Section* below.
 :::
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
 :::
@@
 
-Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 ::: {.noteblock data-latex=""}
-This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function described below in section [UMGYE Model: Regularization] of *This Appendix*.
+This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function described below in section [UMGYE Model: Regularization] of *this Appendix*.
 :::
@@
 
-The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
-
-::: {.noteblock data-latex=""}
-This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
+Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+
+::: {.noteblock data-latex=""}
+This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
 :::
@@
 
-This is a helper function that computes the *Day General Effect(hereafter DG Effect or DGI for short)* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) of user ratings on a *given day since the earliest record* in the `edx` dataset, using a *training dataset* passed in the [train_set](#func.calc_day_general_effect.args.train_set) argument, and is intended for use in other helper functions such as [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (both described below in this section).
+Computes the *Day General Effect* (hereafter *DG Effect* or *DGI* for short) (optionally *regularized* if the [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) of user ratings on a *given day since the earliest record* in the `edx` dataset, using a *training dataset* passed in the [train_set](#func.calc_day_general_effect.args.train_set) argument.
 
@@
 
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
-The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+This is a helper function that is intended for use in other helper functions such as [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (both described below in this section).
+
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
+
+::: {.noteblock data-latex=""}
+*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
 :::
@@
 
-This is a helper function that calculates the *Day General Effect* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the _5-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
+This is a helper function that calculates the *Day General Effect* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the K-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
 
@@
 ```{r eval=FALSE}
-calc_day_general_effect.cv(lambda) |> calc_UMGY_effect()  
 ```
@@
 
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
+
 Under the hood, this function internally calls the [calc_day_general_effect](#func.calc_day_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in our project we use `K = 5`).
-
-::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
-The regularization is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+::: {.noteblock data-latex=""}
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 ```{r eval=FALSE}
-calc_day_general_effect.cv <- function(lambda = 0){
-
-  date_general_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
-    cv_fold_dat$train_set |> calc_day_general_effect(lambda)
-  })
-  put_log1("Function `calc_day_general_effect.cv`:
-Date Global Effect list has been computed for %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  date_general_effect_united <- union_cv_results(date_general_effect_ls)
-
-  date_general_effect <- date_general_effect_united |>
-    group_by(days) |>
-    summarise(de = mean(de, na.rm = TRUE), year = mean(year, na.rm = TRUE))
-
-  if(lambda == 0) put_log("Function `calc_day_general_effect.cv`:
-Training completed: Date Global Effects model.")
-  else put_log1("Function `calc_day_general_effect.cv`:
-Training completed: Date Global Effects model for lambda: %1...",
-                lambda)
-
-  date_general_effect
-}
 ```
@@
 ```{r eval=FALSE}
-  rglr.UMGYD_effect <- edx |> train_UMGY_SmoothedDay_effect(UMGYDE.rglr.best_lambda)
 ```
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
 :::
@@
 ```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_UMGY_SmoothedDay_effect
-`lambda` is `NA`")
-  }
-
-  train_set |>
-    calc_date_general_effect(lambda) |>
-    calc_UMGY_effect()
-}
 ```
@@
 ::: {.noteblock data-latex=""}
-This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in section [UMGYDE Model: Regularization] of *This Appendix*) as shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) subsection of *This Function's Description Section* below.
+This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in section [UMGYDE Model: Regularization] of *this Appendix*) as shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) subsection of *This Function's Description Section* below.
 :::
@@
 ```{r eval=FALSE}
-  train_UMGY_SmoothedDay_effect.cv(lambda) |>
-    calc_UMGY_effect_RMSE.cv()
 ```
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
 :::
@@
 
-Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 ::: {.noteblock data-latex=""}
-This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below in section [UMGYDE Model: Regularization] of *This Appendix*.
+This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below in section [UMGYDE Model: Regularization] of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in section [UMGYDE Model: Regularization] of *This Appendix*) as shown in the [Usage](#func.regularize.train_UMGYD_effect.cv.usage) subsection of *This Function's Description Section* below.
+This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in section [UMGYDE Model: Regularization] of *this Appendix*) as shown in the [Usage](#func.regularize.train_UMGYD_effect.cv.usage) subsection of *This Function's Description Section* below.
 :::
@@
 
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
+
 Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
@@
 ::: {.noteblock data-latex=""}
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument, has non-default value (to be more exact, greater than zero).
 :::
@@
 
-Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in our project we use `K = 5`).
+Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
 :::
@@
 
-Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in our project we use `K = 5`).
-
-::: {.noteblock data-latex=""}
-This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *This Appendix*.
+Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+
+::: {.noteblock data-latex=""}
+This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
 :::

### 2025-12-09 reports/capstone-movielens.site/05.appendix.Rmd
Temporary fix1.

@@
 
-Trains (and optionally *regularizes* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in section [UMGYDE Model: Regularization] of *this Appendix*) as shown in the [Usage](#func.regularize.train_UMGYD_effect.cv.usage) subsection of *This Function's Description Section* below.
+Trains and *regularizes* the *User+Movie+Genre+Year Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: {.noteblock data-latex=""}
+The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
 :::
@@
 ::: {.noteblock data-latex=""}
-In the above code snippet, the `regularize.train_UMGYD_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYDE Model: Regularization] section and this section, respectively).
+In the above code snippet, the `regularize.train_UMGYD_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below, along with the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function described above in this section.
 :::
@@
 ::: { #func.regularize.train_UMGYD_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** Regularization parameter $\lambda$.
 
@@
 
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-
-Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
-
-::: {.noteblock data-latex=""}
+This is a helper function that is used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below in this section as shown in the [Usage](#func.regularize.train_UMGYD_effect.cv.usage) section of *this Description* above.
+
+Under the hood, it calls internally the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+
+::: {.noteblock data-latex=""}
+For the *regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) to be correctly applied to the model being trained, the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument must be greater than zero (when the $\lambda$ is $0$ the *regularization* is disabled).
 :::
@@
 
-Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::

### 2025-12-09 reports/capstone-movielens.site/02-0.methods.Rmd
Refactoring (in progress): K-Fold Cross-Validation references.

@@
 ::: {.noteblock data-latex=""}
-The `K` value for the *K-Fold Cross-Validation* we use in *This Project* is determined by the length of the list composing the [`edx_CV` Object].
+The $K$ value for the *K-Fold Cross-Validation* we use in *This Project* is determined by the length of the list composing the [`edx_CV` Object].
 In our case, the length of the `edx_CV` is 5, meaning we use *5-Fold Cross-Validation*.

### 2025-12-09 reports/capstone-movielens.site/02.4.UE-model.Rmd
Refactoring (in progress): K-Fold Cross-Validation references.

@@
 ::: {.noteblock data-latex=""}
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
 :::

### 2025-12-09 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Refactoring (in progress): K-Fold Cross-Validation references.

@@
 
-Below, we provide the most significant line of the code for training our model using the `5-Fold Cross Validation` method:
-
-Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1177) for training our model using the `K-Fold Cross Validation` method, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`):
+Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1177) for training our model using the *K-Fold Cross Validation* method, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
 ```{r, eval=FALSE}
@@
 
-  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the `K-Fold Cross Validation` samples (in *this Project* we use `K = 5`);
+  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the *K-Fold Cross Validation* samples (in *this Project* we use $K = 5$);
 

### 2025-12-09 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Refactoring (in progress): K-Fold Cross-Validation references.

@@
 
-Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1495) for training our model using the `K-Fold Cross Validation` method, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`):
+Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1495) for training our model using the *K-Fold Cross Validation* method, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
 ```{r, eval=FALSE}

### 2025-12-09 reports/capstone-movielens.site/05.appendix.Rmd
Refactoring (in progress): K-Fold Cross-Validation references.

@@
 ::: { #func.mse_cv.args.r_list .sidebar }
-  - **r_list:** A list of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case Study: Recommender Systems / Loss Function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the *Course Textbook (New Edition)*[@IDS2_24-1_LF], computed in the corresponding iteration of *K-fold cross-validation* (the $K$ is $5$ for *this Project*).
+  - **r_list:** A list of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case Study: Recommender Systems / Loss Function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the *Course Textbook (New Edition)*[@IDS2_24-1_LF], computed in the corresponding iteration of *K-Fold Cross-Validation* (the $K$ is $5$ for *this Project*).
 
@@
 
-The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the $K$ value is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
 
@@
 
-The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the $K$ value is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 ::: { #func.train_user_movie_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 ::: { #func.train_user_movie_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 ::: {.noteblock data-latex=""}
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
 
@@
 ::: { #func.train_user_movie_genre_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 ::: { #func.train_user_movie_genre_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 
-Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
 
@@
 ::: { #func.calc_date_general_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 ::: { #func.calc_date_general_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 ::: { #func.train_UMGY_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 ::: { #func.train_UMGY_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 
-Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
 
@@
 ::: { #func.calc_day_general_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter.
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
 
@@
 
-Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
+Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
+#### [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) Function {#func.regularize.train_UMGYD_effect}
+\
+
+Trains (and optionally *regularizes* if the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.regularize.train_UMGYD_effect.args.train_set) argument.
+
+::: { #func.regularize.train_UMGYD_effect.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+:::
+
+::: { #func.regularize.train_UMGYD_effect.args .sidebar }
+##### Arguments
+\
+
+::: { #func.regularize.train_UMGYD_effect.args.train_set .sidebar }
+  - **train_set:** Training sample of the `Movielens` dataset;
+
+:::
+::: { #func.regularize.train_UMGYD_effect.args.lambda .sidebar }
+  - **lambda:** (0 by default) Regularization parameter $\lambda$.
+
+:::
+:::
+
+::: { #func.regularize.train_UMGYD_effect.details .sidebar }
+##### Details
+\
+
+Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+
+::: {.noteblock data-latex=""}
+The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
+:::
+:::
+
+::: { #func.regularize.train_UMGYD_effect.value .sidebar }
+##### Value
+\
+
+Data frame representing the trained (and also *regularized* if [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
+:::
+
+::: { #func.regularize.train_UMGYD_effect.code .sidebar }
+##### Source Code
+\
+
+The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) script on _GitHub_.
+:::
+:::
+
+\newpage
+
 #### [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L86) Function {#func.regularize.train_UMGYD_effect.cv}
@@
 
-Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
+Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
 
@@
 
-The `K` value for the *K-Fold Cross-Validation* is determined by the length of the list composing the `edx_CV` object. In *this Project*, we choose `K = 5`.
+The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the list composing the `edx_CV` object. In *this Project*, we choose $K = 5$.
 

### 2025-12-09 reports/capstone-movielens.site/05.appendix.Rmd
Appendix A review, function refined: mean_reg.

@@
 ```{r eval=FALSE}
-mean_reg(vals, lambda = 0, na.rm = TRUE)
-
-```
+  UM.effect <- train_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    mutate(resid = rating - (mu + a)) |> 
+    group_by(movieId) |>
+    summarise(b = mean_reg(resid, lambda), n = n())
+```
+
+::: {.noteblock data-latex=""}
+In the sample code snippet above, the `mean_reg` function is called internally from the [train_user_movie_effect](#func.train_user_movie_effect) function described below in section *Models Training: Support Functions \* [UME Model: Utility Functions] of *this Appendix*.
+:::
 :::
@@
 :::
-  - **na.rm:** a logical evaluating to TRUE or FALSE indicating whether NA values should be stripped before the computation proceeds.
+  - **na.rm:** (`TRUE` by default) Logical value indicating whether `NA` values should be stripped before the computation proceeds.
 
@@
 
-The function calculates the _penalized mean_ of the values passed in the [vals](#func.mean_reg.args.vals) argument as follows:
+This function is used in the *regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) to calculate the _penalized mean_ of the values passed in the [vals](#func.mean_reg.args.vals) argument as follows:
 $$
@@
 $$
+
+::: {.noteblock data-latex=""}
+This is a helper function intended for use in other helper functions that compute *penalized estimates* during the *regularization* process of the models being trained[@IDS2_24-2].
+All these functions are described below in section [Models Training: Support Functions] of *this Appendix*.
+:::
 
@@
 
-We call this function internally from the functions that compute the _penalized estimates_  as described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook (New Edition)*[@IDS2_24-2].
-
 ::: {.noteblock data-latex=""}
@@
 
-The [penalized mean](#func.mean_reg.details) of the values passed in the [vals](#func.mean_reg.args.vals) argument.
+(Numeric) *Penalized mean* of the values passed in the [vals](#func.mean_reg.args.vals) argument.
 :::
@@
 
-The soure code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) function is shown below:
+The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) function is shown below:
 ```{r eval=FALSE}
@@
 ```{r eval=FALSE}
-  train_set |>
-    calc_date_general_effect(lambda) |>
-    calc_UMGY_SmoothedDay_effect()
 ```
@@
 ```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect <- function(date_general_effect){
-  date_general_effect |>
-    group_by(year) |>
-    summarise(ye = mean(de, na.rm = TRUE))
-}
 ```
@@
 ```{r eval=FALSE}
-    cv_fold_dat$validation_set |> UMGY_SmoothedDay_effect.predict(UMGYD_effect)
 ```
@@
 ```{r eval=FALSE}
-UMGY_SmoothedDay_effect.predict <- function(test_set, UMGYD_effect){
-  test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    left_join(UMGYD_effect, by='year') |>
-    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
-    pull(resid) |> mse()
-}
 ```
@@
 ```{r eval=FALSE}
-    cv_fold_dat$validation_set |> calc_UMGY_SmoothedDay_effect.MSE(UMGYD_effect)
 ```
@@
 ```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect.MSE <- function(test_set, UMGYD_effect){
-  test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    left_join(UMGYD_effect, by='year') |>
-    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
-    pull(resid) |> mse()
-}
 ```
@@
 ```{r eval=FALSE}
-  UMGY_effect_RMSE <- sqrt(calc_UMGY_SmoothedDay_effect.MSE.cv(UMGYD_effect))
 ```
@@
 ```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect.MSE.cv <- function(UMGYD_effect){
-  start <- put_start_date()
-  UMGY_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_UMGY_SmoothedDay_effect.MSE(UMGYD_effect)
-  })
-  put_end_date(start)
-  put_log1("Function: calc_UMGY_SmoothedDay_effect.MSE.cv
-Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(UMGY_effect_MSEs)
-}
 ```
@@
 ```{r eval=FALSE}
-cv.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(cv.UMGYD_effect)
 ```
@@
 ```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect.RMSE.cv <- function(UMGYD_effect){
-  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGYD_effect))
-  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
-           CVFolds_N, 
-           UMGY_effect_RMSE)
-
-  UMGY_effect_RMSE
-}
 ```
@@
 ```{r eval=FALSE}
-  lambdas <- seq(0, 512, 32)
-  cv.UMGYDE.preset.result <- 
-    tune.model_param(lambdas, 
-                     regularize.test_lambda.UMGYD_effect.cv,
-                     steps.beyond_min = 16)
 ```
@@
 ```{r eval=FALSE}
-regularize.test_lambda.UMGYD_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UMGYD_effect.cv
-`lambda` is `NA`")
-  }
-
-  train_UMGY_effect.cv(lambda) |>
-    calc_UMGY_effect_RMSE.cv()
-}
 ```

### 2025-12-09 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix.

@@
 ::: {.noteblock data-latex=""}
-In the sample code snippet above, the `mean_reg` function is called internally from the [train_user_movie_effect](#func.train_user_movie_effect) function described below in section *Models Training: Support Functions \* [UME Model: Utility Functions] of *this Appendix*.
+In the sample code snippet above, the `mean_reg` function is called internally from the [train_user_movie_effect](#func.train_user_movie_effect) function described below in section *Models Training: Support Functions /* [UME Model: Utility Functions] of *this Appendix*.
 :::
@@
 ::: { #func.mean_reg.args.lambda .sidebar }
-  - **lambda:** (0 by default) _Regularization parameter_ $\lambda$ used in the _Regularization techniques_.
+  - **lambda:** (0 by default) _Regularization parameter_ $\lambda$.
 

### 2025-12-09 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions: mse, mse.cv.

@@
 
-Calculates *Mean Squared Error* as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].
+Calculates *Mean Squared Error* of the set of *residuals* (passed in the [r](func.mse.args.r) argument) as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].
 
@@
 ::: { #func.mse.args.r .sidebar }
-  - **r:** Numeric vector representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].
+  - **r:** Numeric vector representing a set of *residuals*.
 
@@
 
-Calculates the average value of the *Mean Squared Errors* calculated with the use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].
+Calculates the average value of the *Mean Squared Errors* calculated with the use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 

### 2025-12-10 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Function described: `loess_de`.

@@
 :::
-
-#### [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) Function {#func.calc_day_general_effect}
-\
-
-This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
-
-##### Arguments
-\
-
-###### ***train_set***
-\
-The _Train Set_ dataset.
-
-###### ***lambda***
-\
-As explained [above](#sec.umgydem.support_functions.note.lambda) in this section, this parameter is used for the _Regularization_ techniques.
-Otherwise, it is omitted, meaning its default (zero) value is used.
-
-##### Source Code
-\
-
-The following is a simplified version of the function's source code:
-```{r eval=FALSE}
-calc_day_general_effect <- function(train_set, lambda = 0){
-  train_set |> 
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    left_join(rglr.UMGY_effect, by='year') |>
-    mutate(resid = rating - (mu + a + b + g + ye)) |>
-    group_by(days) |>
-    summarise(de = mean_reg(resid, lambda), 
-              year = mean(year))
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete version of the source code of the [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) function is available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L2) script on _GitHub_.
-:::
-
-##### Return
-\
-A data frame object representing the _Day General Effect_.
-
-\newpage
-
-#### [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L31) Function {#func.calc_day_general_effect.cv}
-\
-
-This is a helper function that calculates the _Day General Effect_ of user ratings on a _given day since the earliest record_ in the `edx` dataset using the _5-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.
-
-##### Arguments
-\
-
-###### ***lambda***
-\
-As explained [above](#sec.umgydem.support_functions.note.lambda) in this section, this parameter is used for the _Regularization_ techniques.
-Otherwise, it is omitted, meaning its default (zero) value is used.
-
-##### Souurce Code
-\
-
-::: {.noteblock data-latex=""}
-The complete version of the source code of the [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L31) function is available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L30) script on _GitHub_.
-:::
-
-The following is a simplified version of the function's source code:
-```{r eval=FALSE}
-calc_day_general_effect.cv <- function(lambda = 0){
-  gday_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
-    cv_fold_dat$train_set |> calc_day_general_effect(lambda)
-  })
-
-  gday_effect_united <- union_cv_results(gday_effect_ls)
-
-  gday_effect_united |>
-    group_by(days) |>
-    summarise(de = mean(de), year = mean(year))
-}
-```
-
-::: {.noteblock data-latex=""}
-Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) to aggregate the _5-Fold Cross Validation_ results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A](#appndx_a)).
-:::
-
-##### Return
-\
-A data frame object representing the _Day General Effect_.
-
-\newpage
-
-#### [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) Function {#func.loess_de}
-\
-
-This is a helper function that calculates the _Smoothed Day Effect_ of user ratings and is intended to be used in other custom functions (such as [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)) described below.
-
-##### Arguments
-\
-
-###### ***de_bias.dat***
-\
-A data frame object representing the _Day General Effect_. It can be returned by the following functions described above:
-
-  - [calc_day_general_effect](#func.calc_day_general_effect);
-  - [calc_day_general_effect.cv](#func.calc_day_general_effect.cv).
-
-###### ***degree***
-\
-A parameter to pass to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function (see the [Details](#func.loess_de.details) section below), meaning the degree of the polynomials to be used.
-
-###### ***span***
-\
-A parameter to pass to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function (see the [Details](#func.loess_de.details) section below) to control the degree of smoothing.
-
-::: { #func.loess_de.details .sidebar }
-##### Details
-\
-The function is a wrapper for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) and calls it under the hood.
-:::
-
-##### Source Code
-\
-
-The following is the source code of the function:
-```{r eval=FALSE}
-loess_de <- function(de_bias.dat, degree = NA, span = NA){
-  if(is.na(degree)) degree = 2
-  if(is.na(span)) span = 0.75
-  loess(de ~ days, span = span, degree = degree, data = de_bias.dat)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) script on _GitHub_.
-:::
-
-##### Return
-\
-An object of class `loess` returned by the internally called function [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) (see the [Details](#func.loess_de.details) section above).
-
-\newpage
 

### 2025-12-10 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `loess_de`.

@@
 
+#### [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) Function {#func.loess_de}
+\
+
+Using local fitting, fits a polynomial surface determined by the *Day General Effect* (hereafter *DG Effect* or *DGE* for short) information passed in the [de_bias.dat](#func.loess_de.args.de_bias.dat) argument.
+
+::: {.noteblock data-latex=""}
+In *this Project*, the *DGE* data object to be passed in the [de_bias.dat](#func.loess_de.args.de_bias.dat) argument is returned by the [calc_day_general_effect](#func.calc_day_general_effect) and [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) functions (both described above).
+:::
+
+::: { #func.loess_de.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  fit <- day_gen_effect |> loess_de(degree, span)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the `loess_de` is called internally from the [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function described below.
+:::
+:::
+
+::: { #func.loess_de.args .sidebar }
+##### Arguments
+\
+
+::: { #func.loess_de.args.de_bias.dat .sidebar }
+###### ***de_bias.dat***
+\
+
+Dataframe object representing the *Day General Effect* data.
+
+:::
+::: { #func.loess_de.args.degree .sidebar }
+###### ***degree***
+\
+
+(Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function).
+
+::: {.noteblock data-latex=""}
+When the value is $NA$ (default), $1$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function. 
+:::
+:::
+::: { #func.loess_de.args.span .sidebar }
+###### ***span***
+\
+
+(Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function).
+
+::: {.noteblock data-latex=""}
+When the value is $NA$ (default), $0.75$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
+:::
+:::
+:::
+
+::: { #func.loess_de.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `R` function, which is called internally to make a required fit.
+
+::: {.noteblock data-latex=""}
+This is a helper function intended for use in other helper functions, such as the [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described below in this section.
+:::
+:::
+
+::: { #func.loess_de.value .sidebar }
+##### Value
+\
+
+Object of class `loess` returned by the internally called function [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess).
+:::
+
+::: { #func.loess_de.code .sidebar }
+##### Source Code
+\
+
+The source code of the [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L71) function is shown below:
+```{r eval=FALSE}
+loess_de <- function(de_bias.dat, degree = NA, span = NA){
+  if(is.na(degree)) degree = 1
+  if(is.na(span)) span = 0.75
+  loess(de ~ days, span = span, degree = degree, data = de_bias.dat)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L71) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L71) script on _GitHub_.
+:::
+:::
+
+\newpage
+
 #### [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) Function {#func.calc_UMGY_SmoothedDay_effect}
@@
 
-Builds the *User+Movie+Genre+Year Effect (UMGYDE) Model* based on the *Day General Effect* data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) or [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.
+Builds the *User+Movie+Genre+Year Effect (UMGYDE) Model* based on the *Day General Effect* data structure returned by the [calc_day_general_effect](#func.calc_day_general_effect) or [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.
 
@@
 
-Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+Under the hood, this function internally calls the [calc_day_general_effect](#func.calc_day_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
 
@@
 
-Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+Under the hood, this function internally calls the [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
 
@@
 
-  calc_date_general_effect.cv(lambda) |> calc_UMGY_effect()  
+  calc_day_general_effect.cv(lambda) |> calc_UMGY_effect()  
 }
@@
 
+### UMGYDE Model: Tuning `loess` Params
+\
+
+::: {.noteblock data-latex=""}
+The complete source code of the functions described in this section is available in the  [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L172) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L172) script on _GitHub_.
+:::
+
 ### UMGYDE Model: Regularization
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the  [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) script on _GitHub_.
+The complete source code of the functions described in this section is available in the  [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) script on _GitHub_.
 :::
@@
 
-Under the hood, it calls internally the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+Under the hood, it calls internally the [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
 

### 2025-12-10 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for function description: loess_de.

@@
 
-The source code of the [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L71) function is shown below:
+The source code of the [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L71) function is shown below:
 ```{r eval=FALSE}

### 2025-12-10 reports/capstone-movielens.site/05.appendix.Rmd
Micro fix for function description: loess_de.

@@
 
-#### [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) Function {#func.loess_de}
+#### [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L71) Function {#func.loess_de}
 \

### 2025-12-10 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `calc_UMGY_SmoothedDay_effect`.

@@
 
-Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UM_effect.cv.details) section of *This Description* below.
+Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UM_effect.cv.details) section of *this Description* below.
 :::
@@
 
-Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMG_effect.cv.details) section of *This Description* below.
+Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMG_effect.cv.details) section of *this Description* below.
 :::
@@
 
-An example of using it in the [train_UMGY_effect](#func.train_UMGY_effect) function is shown above in the [Usage](#func.calc_UMGY_effect.usage) section of *This Description*:
+An example of using it in the [train_UMGY_effect](#func.train_UMGY_effect) function is shown above in the [Usage](#func.calc_UMGY_effect.usage) section of *this Description*:
 
@@
 
-Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMGY_effect.cv.details) section of *This Description* below.
+Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMGY_effect.cv.details) section of *this Description* below.
 :::
@@
 
-Builds the *User+Movie+Genre+Year Effect (UMGYDE) Model* based on the *Day General Effect* data structure returned by the [calc_day_general_effect](#func.calc_day_general_effect) or [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.
+Builds the *User+Movie+Genre+Year+SmoothedDay Effect (hereafter UMGYDE for short) Model* based on the *Day General Effect* (*DG Effect* for short) data structure returned by the [calc_day_general_effect](#func.calc_day_general_effect) or [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.
 
@@
 ```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_UMGY_SmoothedDay_effect` is called internally from the [train_UMGY_effect](#func.train_UMGY_effect) function described below.
+  train_set |> 
+    calc_day_general_effect(lambda) |>
+    calc_UMGY_SmoothedDay_effect(degree, span)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the function `calc_UMGY_SmoothedDay_effect` is called internally from the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described below.
 :::
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.args.date_general_effect .sidebar }
-  - **date_general_effect:** Data frame representing the *Day General Effect*;
+  - **date_general_effect:** Dataframe object representing the *DG Effect* (to pass in the [de_bias.dat](#func.loess_de.args.de_bias.dat) argument to the internally called [loess_de](#func.loess_de) described above);
+
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.args. .sidebar }
+  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);
+
+:::
+::: { #func.calc_UMGY_SmoothedDay_effect.args. .sidebar }
+  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);
 
@@
 
-This is a helper function that is intended to be used internally in the following functions (both described below in this section):
-
-  - [train_UMGY_effect](#func.train_UMGY_effect);
-
-  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
-
-An example of using it in the [train_UMGY_effect](#func.train_UMGY_effect) function is shown above in the [Usage](#func.calc_UMGY_SmoothedDay_effect.usage) section of *This Description*:
-
+This auxiliary function is a wrapper for the [loess_de](#func.loess_de) described above, intended to be used internally in the following helper functions (both described below in this section):
+
+  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
+
+  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
+
+An example of using it in the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function is shown above in the [Usage](#func.calc_UMGY_SmoothedDay_effect.usage) section of *this Description*:
 :::
@@
 
-The source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) script on _GitHub_.
+Below is a slightly simplified version of the source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) function:
+```{r eval=FALSE}
+calc_UMGY_SmoothedDay_effect <- function(day_gen_effect, 
+                                         degree = NA, 
+                                         span = NA){
+  fit <- day_gen_effect |> loess_de(degree, span)
+  smth_day_effect <- day_gen_effect |> mutate(de_smoothed = fit$fitted)
+
+  put_log2("Function `calc_UMGY_SmoothedDay_effect`: 
+Model has been trained using `loess` function with the following parameters:
+degree: %1;
+span: %2.",
+           degree,
+           span)
+
+  smth_day_effect
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) script on _GitHub_.
 :::
@@
 
-Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.train_UMGY_SmoothedDay_effect.args.train_set) argument.
+Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.train_UMGY_SmoothedDay_effect.args.train_set) argument.
 
@@
 
-Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 
-Trains (and optionally *regularizes* if the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.regularize.train_UMGYD_effect.args.train_set) argument.
+Trains (and optionally *regularizes* if the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.regularize.train_UMGYD_effect.args.train_set) argument.
 
@@
 
-Trains and *regularizes* the *User+Movie+Genre+Year Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+Trains and *regularizes* the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 
-Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.args.lambda) argument for the *User+Movie+Genre+Year Effect (UMGYDE) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
+Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.args.lambda) argument for the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
 
@@
 
-Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMGYD_effect.cv.details) section of *This Description* below.
+Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMGYD_effect.cv.details) section of *this Description* below.
 :::

### 2025-12-11 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Function described: `train_UMGY_SmoothedDay_effect`.

@@
 :::
-
-#### [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) Function {#func.calc_UMGY_SmoothedDay_effect}
-\
-
-This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
-
-##### Arguments
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.args.day_gen_effect .sidebar }
-###### ***day_gen_effect***
-\
-A data frame object representing the _Day General Effect_. It can be returned by the following functions described above:
-
-  - [calc_day_general_effect](#func.calc_day_general_effect);
-  - [calc_day_general_effect.cv](#func.calc_day_general_effect.cv).
-
-:::
-
-###### ***degree***
-\
-A parameter to pass to the internally called [loess_de](#func.loess_de) function (see the [Details](#func.calc_UMGY_SmoothedDay_effect.details) section below), meaning the degree of the polynomials to be used.
-
-###### ***span***
-\
-A parameter to pass to the internally called [loess_de](#func.loess_de) function (see the [Details](#func.calc_UMGY_SmoothedDay_effect.details) section below) to control the degree of smoothing.
-
-::: { #func.calc_UMGY_SmoothedDay_effect.details .sidebar }
-##### Details
-\
-Under the hood, the function internally calls the [loess_de](#func.loess_de) described above and constructs the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ data object based on the object of class `loess` it returns along with the data passed by the [day_gen_effect](#func.calc_UMGY_SmoothedDay_effect.args.day_gen_effect) parameter.
-:::
-
-##### Source Code
-\
-
-The following is the source code of the function:
-```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect <- function(day_gen_effect, 
-                                         degree = NA, 
-                                         span = NA){
-  put_log2("Function `calc_UMGY_SmoothedDay_effect`: 
-Training model using `loess` function with the following parameters:
-degree: %1;
-span: %2
-...",
-           degree,
-           span)
-  # browser()
-  fit <- day_gen_effect |> loess_de(degree, span)
-  smth_day_effect <- day_gen_effect |> mutate(de_smoothed = fit$fitted)
-
-  put_log2("Function `calc_UMGY_SmoothedDay_effect`: 
-Model has been trained using `loess` function with the following parameters:
-degree: %1;
-span: %2.",
-           degree,
-           span)
-
-  smth_day_effect
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L74) script on _GitHub_.
-:::
-
-##### Return
-\
-A data frame object representing the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_.
-
-\newpage
 

### 2025-12-11 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `train_UMGY_SmoothedDay_effect`.

@@
 
-Builds the *User+Movie+Genre+Year+SmoothedDay Effect (hereafter UMGYDE for short) Model* based on the *Day General Effect* (*DG Effect* for short) data structure returned by the [calc_day_general_effect](#func.calc_day_general_effect) or [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.
+Builds the *User+Movie+Genre+Year+SmoothedDay Effect* (hereafter *UMGYDE* for short) *Model* based on the *Day General Effect* (*DG Effect* for short) data structure returned by the [calc_day_general_effect](#func.calc_day_general_effect) or [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.
 
@@
 :::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.args. .sidebar }
+::: { #func.calc_UMGY_SmoothedDay_effect.args.degree .sidebar }
   - **degree:** (Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);
@@
 :::
-::: { #func.calc_UMGY_SmoothedDay_effect.args. .sidebar }
+::: { #func.calc_UMGY_SmoothedDay_effect.args.span .sidebar }
   - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);
@@
 ```{r eval=FALSE}
+  lss.UMGYD_effect <- edx |> 
+    train_UMGY_SmoothedDay_effect(lss.best_degree, lss.best_span)
 ```
@@
 :::
+
+::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
+  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above);
+
+:::
+::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
+  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above);
+
+:::
 ::: { #func.train_UMGY_SmoothedDay_effect.args.lambda .sidebar }
@@
 
-Under the hood, this function internally calls the [calc_day_general_effect](#func.calc_day_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+Internally, this function calls the helper functions [calc_day_general_effect](#func.calc_day_general_effect) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.calc_UMGY_SmoothedDay_effect.args.degree) and [span](#func.calc_UMGY_SmoothedDay_effect.args.span) to the latter function in the same-named arguments.
 
@@
 
-Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
+Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) *UMGYDE Model*.
 :::
@@
 ```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect <- function(train_set, 
+                                          degree = NA, 
+                                          span = NA,
+                                          lambda = 0){
+  if (is.na(lambda)) {
+    stop("Function: train_UMGY_SmoothedDay_effect
+`lambda` is `NA`")
+  }
+
+  train_set |> 
+    calc_day_general_effect(lambda) |>
+    calc_UMGY_SmoothedDay_effect(degree, span)
+}
 ```
@@
 
-Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 ::: { #func.UMGY_SmoothedDay_effect.predict.args.UMGYD_effect .sidebar }
-  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.
+  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.
 
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.UMGYD_effect .sidebar }
-  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.
+  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.
 
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.UMGYD_effect .sidebar }
-  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.
+  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.
 
@@
 
-The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+The *MSE* value calculated for the *UMGYDE Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.UMGYD_effect .sidebar }
-  - **UMGYD_effect:** Data frame representing the *UMGY Effect Model*.
+  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.
 
@@
 
-The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+The *RMSE* value calculated for the *UMGYDE Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-Data frame representing the trained (and also *regularized* if [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
+Data frame representing the trained (and also *regularized* if [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) *UMGYDE Model*.
 :::
@@
 
-Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::

### 2025-12-11 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `train_UMGY_SmoothedDay_effect.cv`.

@@
 
-(Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function).
+(Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
 
@@
 
-(Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function).
+(Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
 
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.args.degree .sidebar }
-  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);
+  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above;
 
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.args.span .sidebar }
-  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);
+  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above.
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
-  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above);
+  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
-  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above);
+  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.
 
@@
 ::: {.noteblock data-latex=""}
-This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in section [UMGYDE Model: Regularization] of *this Appendix*) as shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) subsection of *This Function's Description Section* below.
+This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) function (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively).
+The usage in the latter function is shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) section of *this Description* below.
 :::
@@
 ```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-In the above code snippet, the `train_UMGY_SmoothedDay_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYDE Model: Regularization] section and this section, respectively).
+  train_UMGY_SmoothedDay_effect.cv(best_degree, 
+                                   best_span, 
+                                   lambda)
+```
+
+::: {.noteblock data-latex=""}
+In the above code snippet, the `train_UMGY_SmoothedDay_effect.cv` function is called internally from the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) function described below in section [UMGYDE Model: Regularization] of *this Appendix*.
 :::
@@
 
+::: { #func.train_UMGY_SmoothedDay_effect.cv.args.degree .sidebar }
+  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;
+
+:::
+::: { #func.train_UMGY_SmoothedDay_effect.cv.args.span .sidebar }
+  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.
+
+:::
 ::: { #func.train_UMGY_SmoothedDay_effect.cv.args.lambda .sidebar }
@@
 
-Under the hood, this function internally calls the [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+Under the hood, this function internally calls the [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) functions (both described above in this section).
 
@@
 
-Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 ```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect.cv <- function(lambda = 0){
+train_UMGY_SmoothedDay_effect.cv <- function(degree = NA, 
+                                             span = NA,
+                                             lambda = 0){
   if (is.na(lambda)) {
@@
 
-  calc_day_general_effect.cv(lambda) |> calc_UMGY_effect()  
+  calc_day_general_effect.cv(lambda) |>
+    calc_UMGY_SmoothedDay_effect(degree, span)
 }

### 2025-12-11 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions' description: `train_UMGY_SmoothedDay_effect`, `train_UMGY_SmoothedDay_effect.cv`.

@@
 
-Internally, this function calls the helper functions [calc_day_general_effect](#func.calc_day_general_effect) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.calc_UMGY_SmoothedDay_effect.args.degree) and [span](#func.calc_UMGY_SmoothedDay_effect.args.span) to the latter function in the same-named arguments.
+Internally, this function calls the helper functions [calc_day_general_effect](#func.calc_day_general_effect) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.args.span) to the latter function in the same-named arguments.
 
@@
 
-Under the hood, this function internally calls the [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) functions (both described above in this section).
+Internally, this function calls the auxiliary functions [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) to the latter function in the same-named arguments..
 

### 2025-12-11 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function's description: `train_UMGY_SmoothedDay_effect.cv`.

@@
 ::: {.noteblock data-latex=""}
-This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) function (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively).
-The usage in the latter function is shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) section of *this Description* below.
+The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
 :::
@@
 
-Internally, this function calls the auxiliary functions [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) to the latter function in the same-named arguments..
+Internally, this function calls the auxiliary functions [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) to the latter function in the same-named arguments.
+
+This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) function (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively).
+The usage in the latter function is shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) section of *this Description* below.
 

### 2025-12-11 reports/capstone-movielens.site/05.appendix.Rmd
Micro fix for function's description: `train_UMGY_SmoothedDay_effect.cv`.

@@
 
-This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) function (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively).
+This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively).
 The usage in the latter function is shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) section of *this Description* below.

### 2025-12-11 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Function described: `UMGY_SmoothedDay_effect.predict`.

@@
 :::
-
-#### [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) Function {#func.train_UMGY_SmoothedDay_effect}
-\
-
-This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)) described below.
-
-##### Arguments
-\
-
-###### ***train_set***
-\
-The _Train Set_ dataset.
-
-::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
-###### ***degree***
-\
-A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.details) section below), meaning the degree of the polynomials to be used.
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
-###### ***span***
-\
-A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.details) section below) to control the degree of smoothing.
-:::
-
-###### ***lambda***
-\
-As explained [above](#sec.umgydem.support_functions.note.lambda) in this section, this parameter is used for the _Regularization_ techniques.
-Otherwise, it is omitted, meaning its default (zero) value is used.
-
-::: { #func.train_UMGY_SmoothedDay_effect.details .sidebar }
-##### Details
-\
-Under the hood, the function internally calls the [calc_day_general_effect](#func.calc_day_general_effect) and then [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above, and returns the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ data object that the latter inner function returns.
-:::
-
-##### Source Code
-\
-
-The following is the source code of the function:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect <- function(train_set, 
-                                          degree = NA, 
-                                          span = NA,
-                                          lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_UMGY_SmoothedDay_effect
-`lambda` is `NA`")
-  }
-
-  train_set |> 
-    calc_day_general_effect(lambda) |>
-    train_UMGY_SmoothedDay_effect(degree, span)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L97) script on _GitHub_.
-:::
-
-##### Return
-\
-A data frame object representing the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_.
-
-\newpage
-
-#### [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L111) Function {#func.train_UMGY_SmoothedDay_effect.cv}
-\
-
-This is a helper function that calculates the _Smoothed Day Effect_ of the user ratings and is intended to be used in other custom functions (such as [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv)) described below.
-
-##### Arguments
-\
-
-###### ***degree***
-\
-A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.cv.details) section below), meaning the degree of the polynomials to be used.
-
-###### ***span***
-\
-A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.cv.details) section below) to control the degree of smoothing.
-
-###### ***lambda***
-\
-As explained [above](#sec.umgydem.support_functions.note.lambda) in this section, this parameter is used for the _Regularization_ techniques.
-Otherwise, it is omitted, meaning its default (zero) value is used.
-
-::: { #func.train_UMGY_SmoothedDay_effect.cv.details .sidebar }
-##### Details
-\
-Under the hood, the function internally calls the [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and then [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above, and returns the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ data object that the latter inner function returns.
-:::
-
-##### Source Code
-\
-
-The following is the source code of the function:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect.cv <- function(degree = NA, 
-                                             span = NA,
-                                             lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_UMGY_SmoothedDay_effect.cv
-`lambda` is `NA`")
-  }
-
-  calc_day_general_effect.cv.cv(lambda) |>
-    calc_UMGY_SmoothedDay_effect(degree, span)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L111) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L111) script on _GitHub_.
-:::
-
-##### Return
-\
-A data frame object representing the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_.
-
-#### [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L123) Function {#func.UMGY_SmoothedDay_effect.predict}
-\
-
-This is a helper function that predicts user rating values on the _Test Set_ passed by the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) parameter, taking into account the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ passed by the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) parameter.
-
-##### Arguments
-\
-
-::: { #func.UMGY_SmoothedDay_effect.predict.args.test_set .sidebar }
-###### ***test_set***
-\
-A _Test Set_ dataset for the _UMGYDE Model_ validation.
-:::
-
-::: { #func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect .sidebar }
-###### ***day_smoothed_effect***
-\
-A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:
-
-  - [calc_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
-  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
-  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
-
-:::
-
-##### Source Code
-\
-
-Below is the source code of the function:
-```{r eval=FALSE}
-UMGY_SmoothedDay_effect.predict <- function(test_set, day_smoothed_effect) {
-  test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    left_join(rglr.UMGY_effect, by='year') |>
-    left_join(day_smoothed_effect, by='days') |>
-    mutate(predicted = clamp(mu + a + b + g + 
-                               ifelse(is.na(ye), 0, ye) +
-                               ifelse(is.na(de_smoothed), 
-                                      0, 
-                                      de_smoothed))) |> 
-    select(userId, movieId, timestamp, rating, predicted)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L123) function is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L123) script on _GitHub_.
-:::
-
-##### Return
-\
-
-A data frame object containing predicted values.
-
-\newpage
 

### 2025-12-11 reports/capstone-movielens.site/02-3.OMR-model.Rmd

@@
 
-  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model: Helper Functions]) to compute *Mean Squared Errors* with the use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`);
+  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model: Helper Functions]) to compute *Mean Squared Errors* with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
 

### 2025-12-11 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 
-Below, we provide the most significant part of the code for training our model with the use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`):
+Below, we provide the most significant part of the code for training our model with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
 ```{r eval=FALSE}

### 2025-12-11 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

@@
 
-Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L902) for training our model using the `K-Fold Cross Validation` method, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`):
+Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L902) for training our model using the *K-Fold Cross Validation* method, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
 ```{r, fn.train_user_movie_genre_effect.cv,   eval=FALSE}

### 2025-12-11 reports/capstone-movielens.site/04.conclusion.Rmd

@@
 
-In this project, a _Machine Learning Algorithm_ was successfully developed for a _Recommender System_ (hereinafter referred to as _RS MLA_) to predict movie ratings using the [10M version of the MovieLens](http://grouplens.org/datasets/movielens/10m/) dataset.
+In this project, a _Machine Learning Algorithm_ was successfully developed for a _Recommender System_ (hereafter referred to as _RS MLA_) to predict movie ratings using the [10M version of the MovieLens](http://grouplens.org/datasets/movielens/10m/) dataset.
 

### 2025-12-11 reports/capstone-movielens.site/05.appendix.Rmd

@@
 
-Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+Dataframe representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-Validates the *UMGY Effect (UMGYDE) Model* produced by the  [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call.
-
-::: {.noteblock data-latex=""}
-This helper function is used internally in the [UMGY_SmoothedDay_effect.predict.cv](#func.UMGY_SmoothedDay_effect.predict.cv) function (described below in this section) as shown in the [Usage](#func.UMGY_SmoothedDay_effect.predict.usage) subsection of *This Function's Description Section* below.
+Predicts *user rating* values on the *Test dataset* passed in the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) argument based on the data of the trained *UMGY Effect (UMGYDE) Model* passed in the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) argument.
+
+::: {.noteblock data-latex=""}
+This function is also called within other helper functions, such as the [calc_UMGY_SmoothedDay_effect.MSE](#func.calc_UMGY_SmoothedDay_effect.MSE) and [UMGYDE_model.predict](#func.UMGYDE_model.predict) described below in this section and [Matrix Factorization Functions] section of *this Appendix*, respectively.
 :::
@@
 ```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the function `UMGY_SmoothedDay_effect.predict` is called internally from the [UMGY_SmoothedDay_effect.predict.cv](#func.UMGY_SmoothedDay_effect.predict.cv) function described below in this section.
-:::
+final.UMGYDE.predicted <- final_holdout_test |>
+  UMGY_SmoothedDay_effect.predict(rglr.day_smoothed_effect)
+```
 :::
@@
 :::
-::: { #func.UMGY_SmoothedDay_effect.predict.args.UMGYD_effect .sidebar }
-  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.
+::: { #func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect .sidebar }
+  - **day_smoothed_effect:** Data frame representing the *UMGYDE Model*.
 
@@
 
-The function calculates *Mean Squared Error (MSE)* for the *UMGYDE Model* passed in the [UMGYD_effect](#func.UMGY_SmoothedDay_effect.predict.args.UMGYD_effect) argument using the validation dataset passed in the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) arg.
+This function implements an algorithm for computing the *user rating values* in accordance with the *mathematical description* of the *UMGYDE Model*, as described in section [Mathematical Description of the UMGYDE Model] of *this Report*.
 :::
@@
 
-*MSE* value calculated for the *UMGYDE Model*.
+Dataframe containing *predicted user rating values* based on the *UMGYDE Model*
 :::
@@
 ```{r eval=FALSE}
+UMGY_SmoothedDay_effect.predict <- function(test_set, day_smoothed_effect) {
+  test_set |>
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(rglr.UMGY_effect, by='year') |>
+    left_join(day_smoothed_effect, by='days') |>
+    mutate(predicted = clamp(mu + a + b + g + 
+                               ifelse(is.na(ye), 0, ye) +
+                               ifelse(is.na(de_smoothed), 
+                                      0, 
+                                      de_smoothed))) |> 
+    select(userId, movieId, timestamp, rating, predicted)
+}
 ```

### 2025-12-12 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions: UMGY_SmoothedDay_effect.predict.

@@
 
-Predicts *user rating* values on the *Test dataset* passed in the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) argument based on the data of the trained *UMGY Effect (UMGYDE) Model* passed in the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) argument.
+Predicts *user rating* values on the *test dataset* passed in the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) argument based on the data of the trained *UMGY Effect (UMGYDE) Model* passed in the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) argument.
 
@@
 ::: { #func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect .sidebar }
-  - **day_smoothed_effect:** Data frame representing the *UMGYDE Model*.
+  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.
 
@@
 
-Dataframe containing *predicted user rating values* based on the *UMGYDE Model*
+Dataframe object containing *predicted user rating* values based on the *UMGYDE Model*
 :::

### 2025-12-12 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `calc_UMGY_SmoothedDay_effect.MSE`.

@@
 
-::: {.noteblock data-latex=""}
-This helper function is used internally in the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_effect_MSE.usage) subsection of *This Function's Description Section* below.
-:::
-
 ::: { #func.calc_UMGY_effect_MSE.usage .sidebar }
@@
 The function calculates *Mean Squared Error (MSE)* for the *UMGYE Model* passed in the [UMGY_effect](#func.calc_UMGY_effect_MSE.args.UMGY_effect) argument using the validation dataset passed in the [test_set](#func.calc_UMGY_effect_MSE.args.test_set) arg.
+
+::: {.noteblock data-latex=""}
+This auxiliary function is used internally in the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_effect_MSE.usage) subsection of *this Description* above.
+:::
 :::
@@
 
+::: {.noteblock data-latex=""}
 This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively).
 The usage in the latter function is shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) section of *this Description* below.
+:::
 
@@
 
-Predicts *user rating* values on the *test dataset* passed in the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) argument based on the data of the trained *UMGY Effect (UMGYDE) Model* passed in the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) argument.
-
-::: {.noteblock data-latex=""}
-This function is also called within other helper functions, such as the [calc_UMGY_SmoothedDay_effect.MSE](#func.calc_UMGY_SmoothedDay_effect.MSE) and [UMGYDE_model.predict](#func.UMGYDE_model.predict) described below in this section and [Matrix Factorization Functions] section of *this Appendix*, respectively.
-:::
+Predicts *user rating* values on the *test dataset* passed in the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) argument based on the data of the trained *UMGYD Effect (UMGYDE) Model* passed in the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) argument.
 
@@
 This function implements an algorithm for computing the *user rating values* in accordance with the *mathematical description* of the *UMGYDE Model*, as described in section [Mathematical Description of the UMGYDE Model] of *this Report*.
+
+::: {.noteblock data-latex=""}
+This function is also called within other helper functions, such as the [calc_UMGY_SmoothedDay_effect.MSE](#func.calc_UMGY_SmoothedDay_effect.MSE) and [UMGYDE_model.predict](#func.UMGYDE_model.predict) described below in this section and [Matrix Factorization Functions] section of *this Appendix*, respectively.
+:::
 :::
@@
 
-Validates the *UMGY Effect (UMGYDE) Model* produced by the  [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call.
-
-::: {.noteblock data-latex=""}
-This helper function is used internally in the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.usage) subsection of *This Function's Description Section* below.
-:::
+Validates the *UMGYD Effect (UMGYDE) Model* using data passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect) argument on the *test dataset* passed in the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) argument.
 
@@
 ```{r eval=FALSE}
+    cv_fold_dat$validation_set |> 
+      calc_UMGY_SmoothedDay_effect.MSE(day_smoothed_effect)
 ```
@@
 :::
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.UMGYD_effect .sidebar }
-  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect .sidebar }
+  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.
 
@@
 
-The function calculates *Mean Squared Error (MSE)* for the *UMGYDE Model* passed in the [UMGYD_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.args.UMGYD_effect) argument using the validation dataset passed in the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) arg.
+This function commits the *UMGYDE Model* validation by calculating the *Mean Squared Error (MSE)*.
+
+In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.loess_de.args.de_bias.dat) argument) is created and returned by the following functions described above in *this Section*:
+  - [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) 
+  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) 
+  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
+
+Internally, this function calls the auxiliary functions [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) (described above in this section), passing to it the value of the argument [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect) in the same-named argument.
+
+::: {.noteblock data-latex=""}
+This auxiliary function is used internally in the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.usage) section of *This Description* above.
+:::
 :::
@@
 ```{r eval=FALSE}
+calc_UMGY_SmoothedDay_effect.MSE <- function(test_set, day_smoothed_effect) {
+  test_set |>
+    UMGY_SmoothedDay_effect.predict(day_smoothed_effect) |>
+    mutate(resid = rating - predicted) |> 
+    pull(resid) |> mse()
+}
 ```
@@
 
-Validates the *UMGY Effect (UMGYDE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+Validates the *UMGYD Effect (UMGYDE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 

### 2025-12-13 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Function described: `calc_UMGY_SmoothedDay_effect.MSE.cv`.

@@
 :::
-
-#### [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L139) Function {#func.calc_UMGY_SmoothedDay_effect.MSE}
-\
-
-The function calculates the _Mean Squared Error (MSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) parameter.
-
-##### Arguments
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set .sidebar }
-###### ***test_set***
-\
-A _Test Set_ dataset for the _UMGYDE Model_ validation.
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect .sidebar }
-###### ***day_smoothed_effect***
-\
-A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:
-
-  - [calc_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
-  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
-  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
-
-:::
-
-##### Source Code
-\
-
-The source code of the function is provided below:
-```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect.MSE <- function(test_set, day_smoothed_effect) {
-  test_set |>
-    UMGY_SmoothedDay_effect.predict(day_smoothed_effect) |>
-    mutate(resid = rating - predicted) |> 
-    pull(resid) |> mse()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L139) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L139) script on _GitHub_.
-:::
-
-##### Return
-\
-The _Mean Squared Error (MSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) parameter.
 

### 2025-12-13 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `calc_UMGY_SmoothedDay_effect.MSE.cv`.

@@
 ::: { #func.calc_UMGY_effect_MSE.cv.args.UMGY_effect .sidebar }
-  - **UMGY_effect:** Data frame representing the *UMGY Effect Model*.
+  - **UMGY_effect:** Dataframe object representing the *UMGY Effect Model*.
 
@@
 
-Validates the *UMGYD Effect (UMGYDE) Model* using data passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect) argument on the *test dataset* passed in the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) argument.
+Validates the *UMGYD Effect (UMGYDE) Model* represented by the data passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect) argument on the *test dataset* passed in the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) argument.
 
@@
 In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.loess_de.args.de_bias.dat) argument) is created and returned by the following functions described above in *this Section*:
+
   - [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)
+
   - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)
+
   - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
 
-Internally, this function calls the auxiliary functions [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) (described above in this section), passing to it the value of the argument [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect) in the same-named argument.
+Internally, this function calls the auxiliary functions [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) (described above in this section), passing to it the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect) value in the same-named argument.
 
@@
 
-Validates the *UMGYD Effect (UMGYDE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-This helper function is used internally in the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.usage) subsection of *This Function's Description Section* below.
-:::
+Validates the *UMGYD Effect (UMGYDE) Model* represented by the data object passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) argument with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV] (we use $K = 5$ in *this Project*).
 
@@
 ```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_UMGY_SmoothedDay_effect.MSE.cv` is called internally from the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described below in this section.
+  sqrt(calc_UMGY_SmoothedDay_effect.MSE.cv(day_smoothed_effect))
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the function `calc_UMGY_SmoothedDay_effect.MSE.cv` is called internally from the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function described below in this section.
 :::
@@
 
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.UMGYD_effect .sidebar }
-  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.
+::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect .sidebar }
+  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.
 
@@
 
-The function calculates *MSE* for the *UMGYDE Model* passed in the [UMGYD_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.UMGYD_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_UMGY_SmoothedDay_effect.MSE](#func.calc_UMGY_SmoothedDay_effect.MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
+This function commits the *UMGYDE Model* validation by calculating the *Mean Squared Error (MSE)* on the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_UMGY_SmoothedDay_effect.MSE](#func.calc_UMGY_SmoothedDay_effect.MSE) function for each iteration of the *K-Fold Cross-Validation*, passing [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) value in the same-named argument to the called function and calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object].
+After that, it calculates the mean of the obtained results.
 
@@
 :::
+
+In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in *this Section*:
+
+  - [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)
+
+  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)
+
+  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
+
+::: {.noteblock data-latex=""}
+This is an auxiliary function that is called internally from the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.usage) section of *This Description* above.
+:::
 :::
@@
 
-The simplified version of the source code of the [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L147) function is shown below:
-```{r eval=FALSE}
+The slightly simplified version of the source code of the [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L147) function is shown below:
+```{r eval=FALSE}
+calc_UMGY_SmoothedDay_effect.MSE.cv <- function(day_smoothed_effect){
+  smth_day_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
+    cv_fold_dat$validation_set |> 
+      calc_UMGY_SmoothedDay_effect.MSE(day_smoothed_effect)
+  })
+  put_end_date(start)
+  put_log1("Function `calc_UMGY_SmoothedDay_effect.MSE.cv`:
+MSE value have been computed for the %1-Fold Cross Validation samples.", 
+           CVFolds_N)
+  mean(smth_day_effect_MSEs)
+}
 ```

### 2025-12-13 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Function described: `calc_UMGY_SmoothedDay_effect.RMSE.cv`.

@@
 \end{equation}
-
-\newpage
-
-### UMGYDE Model: Helper Functions
-\
-
-::: {#sec.umgydem.support_functions.note.lambda .noteblock data-latex=""}
-Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A](#appndx_a)).
-We have already explained that in the [UME Model Regularization] section. 
-For now, we omit the `lambda` parameter, implicitly using its default value `lambda = 0`.
-Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
-:::
-
-#### [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L145) Function {#func.calc_UMGY_SmoothedDay_effect.MSE.cv}
-\
-
-The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) parameter.
-
-##### Arguments
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect .sidebar }
-###### ***day_smoothed_effect***
-\
-A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:
-
-  - [calc_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
-  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
-  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
-
-:::
-
-##### Source Code
-\
-
-Below is a simplified version of the function's source code:
-```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect.MSE.cv <- function(day_smoothed_effect){
-  smth_day_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> 
-      calc_UMGY_SmoothedDay_effect.MSE(day_smoothed_effect)
-  })
-
-  mean(smth_day_effect_MSEs)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The complete version of the source code of the [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L145) function is available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L145) script on _GitHub_.
-:::
-
-##### Return
-\
-The _Mean Squared Error (MSE)_ value of the _UMGYDE Model_ computed as the mean of the _5-Fold Cross Validation_ results.
-
-#### [calc_UMGY_SmoothedDay_effect.RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L161) Function {#func.calc_UMGY_SmoothedDay_effect.RMSE}
-\
-
-The function calculates the _Root Mean Squared Error (RMSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.args.test_set) parameter.
-
-##### Arguments
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.args.test_set .sidebar }
-###### ***test_set***
-\
-A _Test Set_ dataset for the _UMGYDE Model_ validation.
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.args.day_smoothed_effect .sidebar }
-###### ***day_smoothed_effect***
-\
-A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:
-
-  - [calc_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
-  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
-  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
-
-:::
-
-##### Source Code
-\
-
-The source code of the function is provided below:
-```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect.RMSE <- function(test_set, day_smoothed_effect){
-  day_smth_effect_MSe <- test_set |> 
-    calc_UMGY_SmoothedDay_effect.MSE(day_smoothed_effect)
-
-  sqrt(day_smth_effect_MSe)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function [calc_UMGY_SmoothedDay_effect.RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L161) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L161) script.
-:::
-
-##### Return
-\
-The _Root Mean Squared Error (RMSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.args.test_set) parameter.
-
-#### [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L167) Function {#func.calc_UMGY_SmoothedDay_effect.RMSE.cv}
-\
-
-The function calculates the _5-Fold Cross Validation RMSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) parameter.
-
-##### Arguments
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect .sidebar }
-###### ***day_smoothed_effect***
-\
-A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:
-
-  - [calc_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
-  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
-  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
-
-:::
-
-##### Source Code
-\
-
-The source code of the function is provided below:
-```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect.RMSE.cv <- function(day_smoothed_effect){
-  sqrt(calc_UMGY_SmoothedDay_effect.MSE.cv(day_smoothed_effect))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the function [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L167) is also available in the [UMGYDE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L1) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L167)  script.
-:::
-
-##### Return
-\
-The _Root Mean Squared Error (RMSE)_ of the _UMGYD Model_ computed as the square root of the _5-Fold Cross Validation MSE_ result.
 

### 2025-12-13 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `calc_UMGY_SmoothedDay_effect.RMSE.cv`.

@@
 
+Validates the *UMGYD Effect (UMGYDE) Model* represented by the data object passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) argument with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: {.noteblock data-latex=""}
+The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+lss.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(lss.UMGYD_effect)
+```
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect .sidebar }
+  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.
+
+:::
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.details .sidebar }
+##### Details
+\
+
+This function commits the *UMGYDE Model* validation by calculating the *Root Mean Squared Error (RMSE)* on the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
+
+::: {.noteblock data-latex=""}
+This function internally calls the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) auxiliary function described above in *this Section* to compute the *MSE* for the *UMGYDE Model* and then calculates the *square root* of the obtained result.
+:::
+
+In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in *this Section*:
+
+  - [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)
+
+  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)
+
+  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
+
+::: {.noteblock data-latex=""}
+This function is also called internally as an auxiliary function from the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) functions described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization], respectively, of *this Appendix*.
+:::
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.value .sidebar }
+##### Value
+\
+
+The *RMSE* value calculated for the *UMGYDE Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+:::
+
+::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.code .sidebar }
+##### Source Code
+\
+
+The source code of the [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) function is shown below:
+```{r eval=FALSE}
+calc_UMGY_SmoothedDay_effect.RMSE.cv <- function(day_smoothed_effect){
+  sqrt(calc_UMGY_SmoothedDay_effect.MSE.cv(day_smoothed_effect))
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) Function {#func.calc_UMGY_SmoothedDay_effect.RMSE.cv}
+\
+
 Validates the *UMGYD Effect (UMGYDE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].

### 2025-12-13 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the previous commit.

@@
 
-In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.loess_de.args.de_bias.dat) argument) is created and returned by the following functions described above in *this Section*:
+In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.loess_de.args.de_bias.dat) argument) is created and returned by the following functions described above in this section:
 
@@
 
-In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in *this Section*:
+In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in this section:
 
@@
 ::: {.noteblock data-latex=""}
-This function internally calls the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) auxiliary function described above in *this Section* to compute the *MSE* for the *UMGYDE Model* and then calculates the *square root* of the obtained result.
-:::
-
-In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in *this Section*:
+This function internally calls the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) auxiliary function described above in this section to compute the *MSE* for the *UMGYDE Model* and then calculates the *square root* of the obtained result.
+:::
+
+In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in this section:
 
@@
 }
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) Function {#func.calc_UMGY_SmoothedDay_effect.RMSE.cv}
-\
-
-Validates the *UMGYD Effect (UMGYDE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below in section [UMGYDE Model: Regularization] of *this Appendix*.
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-```
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.UMGYD_effect .sidebar }
-  - **UMGYD_effect:** Data frame representing the *UMGYDE Model*.
-
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.details .sidebar }
-##### Details
-\
-
-The function calculates *Root Squared Error (RMSE)* for the *UMGYDE Model* passed in the [UMGYD_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.UMGYD_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGYDE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
-
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.value .sidebar }
-##### Value
-\
-
-The *RMSE* value calculated for the *UMGYDE Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) function is shown below:
-```{r eval=FALSE}
 ```

### 2025-12-13 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `train_UMGY_SmoothedDay_effect.RMSE.cv`.

@@
 
+#### [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L173) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv}
+\
+
+Trains and validate (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the given parameter values passed in the [degree](#) and [span](#) arguments, with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+
+::: {.noteblock data-latex=""}
+The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 1, span)
+```
+
+::: {.noteblock data-latex=""}
+In the above code snippet, the `train_UMGY_SmoothedDay_effect.RMSE.cv` function is called internally from the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) function described below in this section.
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree .sidebar }
+  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above;
+
+:::
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span .sidebar }
+  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above.
+
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.details .sidebar }
+##### Details
+\
+
+This is a wrapper for the function [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described above in section [UMGYDE Model: Utility Functions] of *this Appendix*), which it calls internally, passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) in the same-named arguments.
+
+Unlike the internal function  [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv), this one also validates the *UMGYDE Model* created and trained by that function, for which it calls internally another helper function, [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) (also described above in the [UMGYDE Model: Utility Functions] section), computing *RMSE* for that model.
+
+::: {.noteblock data-latex=""}
+This is an auxiliary  function intended to be called internally from the following helper functions (described below in this section), specifically designed for tuning the `degree` and `span` [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters:
+
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0): a helper function designed for tuning the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter while keeping the `degree` parameter fixed at $0$;
+
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1): a helper function designed for tuning the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter while keeping the `degree` parameter fixed at $1$;
+
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2): a helper function designed for tuning the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter while keeping the `degree` parameter fixed at $2$;
+
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.value .sidebar }
+##### Value
+\
+
+The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters passed in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) arguments, and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.code .sidebar }
+##### Source Code
+\
+
+The slightly simplified version of the source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L173) function is shown below:
+```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect.RMSE.cv <- function(degree = NA, span = NA) {
+  smth_de.RMSE <- train_UMGY_SmoothedDay_effect.cv(degree, span) |>
+    calc_UMGY_SmoothedDay_effect.RMSE.cv()
+
+  put_log2("Function `train_UMGY_SmoothedDay_effect.RMSE.cv`:
+RMSE has been computed for the `loess` function parameters: 
+degree = %1, span = %2.", 
+           degree,
+           span)
+
+  smth_de.RMSE
+}
+```
+
+::: {.noteblock data-latex=""}
+The complete source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L173) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L173) script on _GitHub_.
+:::
+:::
+
+\newpage
+
 ### UMGYDE Model: Regularization

### 2025-12-14 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Function description prototype added: train_UMGY_SmoothedDay_effect.RMSE.cv.degree<N>

@@
 \
-
-##### [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L171) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv}
-\
-The function is designed to tune the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function's parameters ([degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span)), which is ultimately called internally under the hood.
-
-###### Arguments
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree .sidebar }
-  - ***degree:***
-A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to specify the degree of the polynomials to be used.
-
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span .sidebar }
-  - ***span:***
-A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.
-
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.details .sidebar }
-###### Details
-\
-Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) and then [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above to compute the `RMSE` of the model to be tuned.
-:::
-
-###### Source Code
-\
-Below is a simplified version of the function's source code:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect.RMSE.cv <- function(degree = NA, span = NA) {
-  train_UMGY_SmoothedDay_effect.cv(degree, span) |>
-    calc_UMGY_SmoothedDay_effect.RMSE.cv()
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete version of the source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L171) function is available in the [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L170) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L171) script on _GitHub_.
-:::
-
-###### Return
-\
-The _Root Mean Squared Error (RMSE)_ of the _UMGYD Model_.
 

### 2025-12-14 reports/capstone-movielens.site/05.appendix.Rmd
Function description prototype added: train_UMGY_SmoothedDay_effect.RMSE.cv.degree<N>

@@
 
-Trains and validate (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the given parameter values passed in the [degree](#) and [span](#) arguments, with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+Trains and validate (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the given parameter values passed in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) arguments, with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 
-This is a wrapper for the function [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described above in section [UMGYDE Model: Utility Functions] of *this Appendix*), which it calls internally, passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) in the same-named arguments.
+This is a wrapper for the function [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described above in section [UMGYDE Model: Utility Functions] of *this Appendix*) it calls internally, passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) in the same-named arguments.
 
@@
 The complete source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L173) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L173) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0}
+\
+
+Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) and the `degree` parameter equals $0$.
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree0` function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span .sidebar }
+  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above.
+
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in the [UMGYDE Model: Auxiliary Functions] section of this application), which it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument along with the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) value to the same-named argument of the called function.
+
+::: {.noteblock data-latex=""}
+This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.value .sidebar }
+##### Value
+\
+
+The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (the `degree` equals $0$ and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.code .sidebar }
+##### Source Code
+\
+
+The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) function is shown below:
+```{r eval=FALSE}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) script on _GitHub_.
 :::

### 2025-12-14 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the function description prototype: `train_UMGY_SmoothedDay_effect.RMSE.cv.degree<N>`.

@@
 
-Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) and the `degree` parameter equals $0$.
+Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument and the `degree` parameter equals $0$.
 
@@
 
-This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in the [UMGYDE Model: Auxiliary Functions] section of this application), which it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument along with the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) value to the same-named argument of the called function.
+This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.
 
@@
 
-The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (the `degree` equals $0$ and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 0` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::

### 2025-12-14 reports/capstone-movielens.site/05.appendix.Rmd
Functions described:   - `train_UMGY_SmoothedDay_effect.RMSE.cv.degree0`;   - `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1`;   - `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2`.

@@
 
-(Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
-
-::: {.noteblock data-latex=""}
-When the value is $NA$ (default), $1$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function. 
+(Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
+
+::: {.noteblock data-latex=""}
+When the value is `NA` (default), $1$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function. 
 :::
@@
 
-(Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
-
-::: {.noteblock data-latex=""}
-When the value is $NA$ (default), $0.75$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
+(Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
+
+::: {.noteblock data-latex=""}
+When the value is `NA` (default), $0.75$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
 :::
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.args.degree .sidebar }
-  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above;
+  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above;
 
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.args.span .sidebar }
-  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above.
+  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above.
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
-  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;
+  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
-  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.
+  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.cv.args.degree .sidebar }
-  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;
+  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.cv.args.span .sidebar }
-  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.
+  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree .sidebar }
-  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above;
+  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above;
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span .sidebar }
-  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above.
+  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above.
 
@@
 ```{r eval=FALSE}
+  lss.UMGYDE.preset.degree0.result <- 
+    tune.model_param(spans, train_UMGY_SmoothedDay_effect.RMSE.cv.degree0)
 ```
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span .sidebar }
-  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above.
+  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
 
@@
 ```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect.RMSE.cv.degree0 <- function(span) {
+  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 0, span)
+}
 ```
@@
 The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1}
+\
+
+Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument and the `degree` parameter equals $0$.
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+lss.UMGYDE.fine_tune.degree1.result <- 
+  model.tune.param_range(lss.fine_tune.loop_starter,
+                         UMGYDE.fine_tune.degree1.data.path,
+                         cache_file.base_name,
+                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree1)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span .sidebar }
+  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
+
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.
+
+::: {.noteblock data-latex=""}
+This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.value .sidebar }
+##### Value
+\
+
+The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 0` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.code .sidebar }
+##### Source Code
+\
+
+The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) function is shown below:
+```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect.RMSE.cv.degree1 <- function(span) {
+  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 1, span)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) script on _GitHub_.
+:::
+:::
+
+\newpage
+
+#### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2}
+\
+
+Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument and the `degree` parameter equals $0$.
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+lss.UMGYDE.fine_tune.degree2.result <- 
+  model.tune.param_range(lss.fine_tune.loop_starter,
+                         UMGYDE.fine_tune.degree2.data.path,
+                         cache_file.base_name,
+                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree2)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args .sidebar }
+##### Arguments
+\
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span .sidebar }
+  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
+
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.details .sidebar }
+##### Details
+\
+
+This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.
+
+::: {.noteblock data-latex=""}
+This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+:::
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.value .sidebar }
+##### Value
+\
+
+The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 0` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+:::
+
+::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.code .sidebar }
+##### Source Code
+\
+
+The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) function is shown below:
+```{r eval=FALSE}
+train_UMGY_SmoothedDay_effect.RMSE.cv.degree2 <- function(span) {
+  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 2, span)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) script on _GitHub_.
 :::

### 2025-12-14 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Fix for the previous commit.

@@
 \
-
-#### UMGYDE Model Tuning: Support Functions
-\
-
-##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0}
-\
-The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 0.
-
-###### Arguments
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span .sidebar }
-  - ***span:***
-A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.
-
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.details .sidebar }
-###### Details
-\
-Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 0 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) of this function to compute the `RMSE` of the model to be tuned.
-:::
-
-###### Source Code
-\
-Below is the function's source code:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect.RMSE.cv.degree0 <- function(span) {
-  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 0, span)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) function is also available in the [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L170) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) script on _GitHub_.
-:::
-
-###### Return
-\
-_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) parameter and the `degree` parameter value equal to 0.
-
-\newpage
-
-##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L193) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1}
-\
-The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 1.
-
-###### Arguments
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span .sidebar }
-  - ***span:***
-A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.
-
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.details .sidebar }
-###### Details
-\
-Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 1 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) of this function to compute the `RMSE` of the model to be tuned.
-:::
-
-###### Source Code
-\
-Below is the function's source code:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect.RMSE.cv.degree1 <- function(span) {
-  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 1, span)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L193) function is also available in the [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L170) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L193) script on _GitHub_.
-:::
-
-###### Return
-\
-_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) parameter and the `degree` parameter value equal to 1.
-
-##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L196) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2}
-\
-The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 2.
-
-###### Arguments
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span .sidebar }
-  - ***span:***
-A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.
-
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.details .sidebar }
-###### Details
-\
-Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 2 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) of this function to compute the `RMSE` of the model to be tuned.
-:::
-
-###### Source Code
-\
-Below is the function's source code:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect.RMSE.cv.degree2 <- function(span) {
-  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 2, span)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L196) function is also available in the [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L170) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L196) script on _GitHub_.
-:::
-
-###### Return
-\
-_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) parameter and the `degree` parameter value of 2.
-
-\newpage
 

### 2025-12-14 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions description: `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1`, `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2`.

@@
 
+\newpage
+
 ::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.code .sidebar }
@@
 
-Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument and the `degree` parameter equals $0$.
+Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument and the `degree` parameter equals $1$.
 
@@
 
-This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.
+This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $1$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.
 
@@
 
-The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 0` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 1` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 
-Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument and the `degree` parameter equals $0$.
+Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument and the `degree` parameter equals $2$.
 
@@
 
-This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.
+This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $2$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.
 
@@
 
-The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 0` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 2` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::

### 2025-12-15 reports/capstone-movielens.site/02-0.methods.Rmd
Functions described: `regularize.train_UMGYD_effect`, `regularize.train_UMGYD_effect.cv`.

@@
 
-As a result of executing these functions, we will obtain the following datasets (detailed in [Appendix B: Models Training Datasets]), which we will use throughout *This Project*:
+As a result of executing these functions, we will obtain the following datasets (detailed in [Appendix B: Models Training Datasets]), which we will use throughout *this Project*:
 
@@
 ::: {.noteblock data-latex=""}
-The $K$ value for the *K-Fold Cross-Validation* we use in *This Project* is determined by the length of the list composing the [`edx_CV` Object].
+The $K$ value for the *K-Fold Cross-Validation* we use in *this Project* is determined by the length of the list composing the [`edx_CV` Object].
 In our case, the length of the `edx_CV` is 5, meaning we use *5-Fold Cross-Validation*.

### 2025-12-15 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Functions described: `regularize.train_UMGYD_effect`, `regularize.train_UMGYD_effect.cv`.

@@
 ::: {.noteblock data-latex=""}
-In the code snippets above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described in the [UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a) to *This Report*.
+In the code snippets above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described in the [UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a) to *this Report*.
 :::

### 2025-12-15 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: `regularize.train_UMGYD_effect`, `regularize.train_UMGYD_effect.cv`.

@@
 
-This function is a wrapper for the [tibble::tibble](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble) function, which is called internally to construct a data frame representing the _RMSEs Result Tibble_ to store the _RMSE_ values for every model used in the project to predict movie ratings.
+This function is a wrapper for the [tibble::tibble](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble) function, which is called internally to construct a data frame object representing the _RMSEs Result Tibble_ to store the _RMSE_ values for every model used in the project to predict movie ratings.
 
@@
 
-This function is a wrapper for the [tibble::add_row](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row) function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
+This function is a wrapper for the [tibble::add_row](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row) function, which is called internally to modify a data frame object representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
 
@@
 
-This function is a wrapper for the [tibble::add_column](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_column) function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_.
+This function is a wrapper for the [tibble::add_column](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_column) function, which is called internally to modify a data frame object representing the original _RMSEs Result Tibble_.
 It also internally uses the [RMSEs.AddRow](#func.RMSEs.AddRow) function described above to perform the necessary intermediate calculations.
@@
 
-Data frame representing the trained (and also *regularized* if [lambda](#func.train_user_movie_effect.args.lambda) arg value other than default) *UM Effect Model*.
+Data frame object representing the trained (and also *regularized* if [lambda](#func.train_user_movie_effect.args.lambda) arg value other than default) *UM Effect Model*.
 :::
@@
 
-Under the hood, this function internally calls the [train_user_movie_effect](#func.train_user_movie_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+Internally, this function calls the helper function [train_user_movie_effect](#func.train_user_movie_effect) described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
 It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
@@
 
-Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+Data frame object representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 ::: { #func.calc_user_movie_effect_MSE.args.um_effect .sidebar }
-  - **um_effect:** Data frame representing the *UM Effect Model*.
+  - **um_effect:** Data frame object representing the *UM Effect Model*.
 
@@
 ::: { #func.calc_user_movie_effect_MSE.cv.args.um_effect .sidebar }
-  - **um_effect:** Data frame representing the *UM Effect Model*.
+  - **um_effect:** Data frame object representing the *UM Effect Model*.
 
@@
 ::: { #func.calc_user_movie_effect_RMSE.cv.args.um_effect .sidebar }
-  - **um_effect:** Data frame representing the *UM Effect Model*.
+  - **um_effect:** Data frame object representing the *UM Effect Model*.
 
@@
 
-Data frame representing the trained (and also *regularized* if [lambda](#func.train_user_movie_genre_effect.args.lambda) arg value other than default) *UMG Effect Model*.
+Data frame object representing the trained (and also *regularized* if [lambda](#func.train_user_movie_genre_effect.args.lambda) arg value other than default) *UMG Effect Model*.
 :::
@@
 
-Under the hood, this function internally calls the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+Internally, this function calls the helper function [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
 It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
@@
 
-Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+Data frame object representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 ::: { #func.calc_user_movie_genre_effect_MSE.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+  - **umg_effect:** Data frame object representing the *UMG Effect Model*.
 
@@
 ::: { #func.calc_user_movie_genre_effect_MSE.cv.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+  - **umg_effect:** Data frame object representing the *UMG Effect Model*.
 
@@
 ::: { #func.calc_user_movie_genre_effect_RMSE.cv.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame representing the *UMG Effect Model*.
+  - **umg_effect:** Data frame object representing the *UMG Effect Model*.
 
@@
 
-Data frame representing (*regularized* if [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) *Date General Effect*.
+Data frame object representing (*regularized* if [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) *Date General Effect*.
 :::
@@
 
-Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+Internally, this function calls the helper function [calc_date_general_effect](#func.calc_date_general_effect) described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
 It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
@@
 
-Data frame representing (*regularized* if [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) *Date General Effect*.
+Data frame object representing (*regularized* if [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) *Date General Effect*.
 :::
@@
 ::: { #func.calc_UMGY_effect.args.date_general_effect .sidebar }
-  - **date_general_effect:** Data frame representing the *Date General Effect*;
+  - **date_general_effect:** Data frame object representing the *Date General Effect*;
 
@@
 
-Data frame representing the *UMGYE Model*.
+Data frame object representing the *UMGYE Model*.
 :::
@@
 
-Under the hood, this function internally calls the [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+Internally, this function calls the helper functions [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) (both described above in this section).
 
@@
 
-Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
+Data frame object representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
 :::
@@
 
-Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
+Internally, this function calls the helper functions [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) (both described above in this section).
 
@@
 
-Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+Data frame object representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 ::: { #func.calc_UMGY_effect_MSE.args.UMGY_effect .sidebar }
-  - **UMGY_effect:** Data frame representing the *UMGY Effect Model*.
+  - **UMGY_effect:** Data frame object representing the *UMGY Effect Model*.
 
@@
 ::: { #func.calc_UMGY_effect_MSE.cv.args.UMGY_effect .sidebar }
-  - **UMGY_effect:** Dataframe object representing the *UMGY Effect Model*.
+  - **UMGY_effect:** Data frame object representing the *UMGY Effect Model*.
 
@@
 ::: { #func.calc_UMGY_effect_RMSE.cv.args.UMGY_effect .sidebar }
-  - **UMGY_effect:** Data frame representing the *UMGY Effect Model*.
+  - **UMGY_effect:** Data frame object representing the *UMGY Effect Model*.
 
@@
 
-Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) *DG Effect*.
+Data frame object representing (*regularized* if [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) *DG Effect*.
 :::
@@
 
-Under the hood, this function internally calls the [calc_day_general_effect](#func.calc_day_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
+Internally, this function calls the helper functions [calc_day_general_effect](#func.calc_day_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
 It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
@@
 
-Data frame representing (*regularized* if [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) *Day General Effect*.
+Data frame object representing (*regularized* if [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) *Day General Effect*.
 :::
@@
 
-Dataframe object representing the *Day General Effect* data.
+Data frame object representing the *Day General Effect* data.
 
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.args.date_general_effect .sidebar }
-  - **date_general_effect:** Dataframe object representing the *DG Effect* (to pass in the [de_bias.dat](#func.loess_de.args.de_bias.dat) argument to the internally called [loess_de](#func.loess_de) described above);
+  - **date_general_effect:** Data frame object representing the *DG Effect* (to pass in the [de_bias.dat](#func.loess_de.args.de_bias.dat) argument to the internally called [loess_de](#func.loess_de) described above);
 
@@
 
-Data frame representing the *UMGYDE Model*.
+Data frame object representing the *UMGYDE Model*.
 :::
@@
 
-Data frame representing the trained (and also *regularized* if [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) *UMGYDE Model*.
+Data frame object representing the trained (and also *regularized* if [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) *UMGYDE Model*.
 :::
@@
 
-Dataframe representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
 :::
@@
 ::: { #func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect .sidebar }
-  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.
+  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.
 
@@
 
-Dataframe object containing *predicted user rating* values based on the *UMGYDE Model*
+Data frame object containing *predicted user rating* values based on the *UMGYDE Model*
 :::
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect .sidebar }
-  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.
+  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.
 
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect .sidebar }
-  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.
+  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.
 
@@
 ::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect .sidebar }
-  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.
+  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.
 
@@
 
-Trains and validate (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the given parameter values passed in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) arguments, with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+Trains and validate (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the given [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters passed in the corresponding arguments ([degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span)), with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree .sidebar }
-  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above;
+  - **degree:** (Integer, `NA` by default) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the degree of the polynomials to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above;
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span .sidebar }
-  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above.
+  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above.
 
@@
 
-Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument and the `degree` parameter equals $0$.
+Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument and the `degree` parameter equals $0$.
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span .sidebar }
-  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
+  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
 
@@
 
-This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $0$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.
+This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing it the following [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters :
+
+  - $0$ in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument;
+
+  - The [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument value (of this function) in the same-named argument [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span).
 
@@
 
-Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument and the `degree` parameter equals $1$.
+Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument and the `degree` parameter equals $1$.
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span .sidebar }
-  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
+  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
 
@@
 
-This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $1$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.
+This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing it the following [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters :
+
+  - $1$ in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument;
+
+  - The [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument value (of this function) in the same-named argument [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span).
 
@@
 
-Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument and the `degree` parameter equals $2$.
+Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument and the `degree` parameter equals $2$.
 
@@
 ::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span .sidebar }
-  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
+  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
 
@@
 
-This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing $2$ to the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) value to the [same-named argument](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) of the called function.
+This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing it the following [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters :
+
+  - $2$ in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument;
+
+  - The [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument value (of this function) in the same-named argument [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span).
 
@@
 
-Trains (and optionally *regularizes* if the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.regularize.train_UMGYD_effect.args.train_set) argument.
+Trains and *regularizes* the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for a given value of the parameter $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument and preliminary figured out *best values* of the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters, using the training set of the `Movielens` dataset passed in the [train_set](#func.regularize.train_UMGYD_effect.args.train_set) argument.
 
@@
 ```{r eval=FALSE}
+  rglr.UMGYD_effect <- edx |> 
+    regularize.train_UMGYD_effect(UMGYDE.rglr.best_lambda)
 ```
@@
 ::: { #func.regularize.train_UMGYD_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
+  - **lambda:** Regularization parameter $\lambda$.
 
@@
 
-Under the hood, this function internally calls the [calc_day_general_effect](#func.calc_day_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
-
-::: {.noteblock data-latex=""}
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
+This function is a wrapper for the function [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (described above in section [UMGYDE Model: Utility Functions] of *this Appendix*) that it calls internally, passing it the best values of the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters `degree` and `span` in the corresponding arguments ([degree](#func.train_UMGY_SmoothedDay_effect.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.args.span), respectively)
+
+::: {.noteblock data-latex=""}
+The *UMGYDE Model* is regularized using the *regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
 :::
@@
 
-Data frame representing the trained (and also *regularized* if [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) *UMGYDE Model*.
+Data frame object representing the *UMGYDE Model*, regularized by the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument) and tuned for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) *best parameters* `degree` and `span`.
 :::
@@
 ```{r eval=FALSE}
+regularize.train_UMGYD_effect <- function(train_set, lambda) {
+  best_degree <- lss.UMGYDE.best_params["degree"]
+  best_span <- lss.UMGYDE.best_params["span"]
+
+  train_set |>
+    train_UMGY_SmoothedDay_effect(best_degree, 
+                                  best_span, 
+                                  lambda)
+}
 ```
@@
 
-Trains and *regularizes* the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
+Trains and *regularizes* the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for a given value of the parameter $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument and preliminary figured out *best values* of the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters, with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
 
@@
 ```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-In the above code snippet, the `regularize.train_UMGYD_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below, along with the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function described above in this section.
+  regularize.train_UMGYD_effect.cv(lambda) |>
+    calc_UMGY_SmoothedDay_effect.RMSE.cv()
+```
+
+::: {.noteblock data-latex=""}
+In the above code snippet, the `regularize.train_UMGYD_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below in this section, along with the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function described above in section [UMGYDE Model: Utility Functions].
 :::
@@
 
-This is a helper function that is used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below in this section as shown in the [Usage](#func.regularize.train_UMGYD_effect.cv.usage) section of *this Description* above.
-
-Under the hood, it calls internally the [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).
-
-::: {.noteblock data-latex=""}
-For the *regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) to be correctly applied to the model being trained, the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument must be greater than zero (when the $\lambda$ is $0$ the *regularization* is disabled).
+This is an auxiliary function intended to be called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.usage) section of *this Description* above.
+
+The function is a wrapper for the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described above in section [UMGYDE Model: Utility Functions] of *this Appendix*) that it calls internally, passing it the best values of the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters `degree` and `span` in the corresponding arguments ([degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span), respectively)
+
+::: {.noteblock data-latex=""}
+The *UMGYDE Model* is regularized using the *regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
 :::
@@
 
-Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.regularize.train_UMGYD_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
+Data frame object representing the *UMGYDE Model*, tuned for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) *best parameters* `degree` and `span`, trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$), and regularized by the given *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument.
 :::

### 2025-12-15 reports/capstone-movielens.site/work/func-descr.template.Rmd
Function described: `loess_de`.
Functions described: `regularize.train_UMGYD_effect`, `regularize.train_UMGYD_effect.cv`.

@@
 ```{r eval=FALSE}
-cmmn_helper_func.tmpl()
-
 ```
@@
 
-This function is a wrapper for the [tibble::]() function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
+This function is a wrapper for the [tibble::]() function, which is called internally to modify a data frame object representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
 
@@
 ```{r eval=FALSE}
-umgye_rglr_helper.tmpl()
-
 ```

### 2025-12-15 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function description: `regularize.train_UMGYD_effect`, `regularize.train_UMGYD_effect.cv`.

@@
 
-#### [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) Function {#func.regularize.train_UMGYD_effect}
+#### [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L225) Function {#func.regularize.train_UMGYD_effect}
 \
@@
 
-The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is shown below:
+The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L225) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) script on _GitHub_.
+The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L225) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L225) script on _GitHub_.
 :::
@@
 
-#### [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L86) Function {#func.regularize.train_UMGYD_effect.cv}
+#### [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L234) Function {#func.regularize.train_UMGYD_effect.cv}
 \
@@
 
-The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L86) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L86) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L86) script on _GitHub_.
+The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L234) function is shown below:
+```{r eval=FALSE}
+regularize.train_UMGYD_effect.cv <- function(lambda) {
+  best_degree <- lss.UMGYDE.best_params["degree"]
+  best_span <- lss.UMGYDE.best_params["span"]
+
+  train_UMGY_SmoothedDay_effect.cv(best_degree, 
+                                   best_span, 
+                                   lambda)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L234) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L234) script on _GitHub_.
 :::

### 2025-12-15 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Function described: `regularize.test_lambda.UMGYD_effect.cv`.

@@
 
-##### [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L223) Function {#func.regularize.train_UMGYD_effect}
-\
-
-The function is an overloaded version of the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.args.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.
-
-###### Arguments
-\
-
-::: { #func.regularize.train_UMGYD_effect.args.train_set .sidebar }
-  - ***train_set:***
-The _Train Set_ dataset .
-
-:::
-
-::: { #func.regularize.train_UMGYD_effect.args.lambda .sidebar }
-  - ***lambda:***
-  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.
-
-:::
-
-###### Source Code
-\
-
-The following is the source code of the function:
-```{r eval=FALSE}
-regularize.train_UMGYD_effect <- function(train_set, lambda) {
-  best_degree <- lss.UMGYDE.best_params["degree"]
-  best_span <- lss.UMGYDE.best_params["span"]
-
-  train_set |>
-    train_UMGY_SmoothedDay_effect(best_degree, 
-                                  best_span, 
-                                  lambda)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L223) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L222) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L223) script on _GitHub_.
-:::
-
-###### Return
-\
-A data frame object representing the _UMGYD Effect_.
-
-\newpage
-
-##### [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L232) Function {#func.regularize.train_UMGYD_effect.cv}
-\
-
-::: {.noteblock data-latex=""}
-The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L232) function is defined in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L222) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L232) script on _GitHub_.
-:::
-
-The function is an overloaded version of the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.
-
-###### Arguments
-\
-
-::: { #func.regularize.train_UMGYD_effect.cv.args.lambda .sidebar }
-  - ***lambda:***
-  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.
-
-:::
-
-###### Source Code
-\
-The source code of the function is provided below:
-```{r eval=FALSE}
-regularize.train_UMGYD_effect.cv <- function(lambda) {
-  best_degree <- lss.UMGYDE.best_params["degree"]
-  best_span <- lss.UMGYDE.best_params["span"]
-
-  train_UMGY_SmoothedDay_effect.cv(best_degree, 
-                                   best_span, 
-                                   lambda)
-}
-```
-
-::: {.noteblock data-latex=""}
-Note that we reuse the function [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) calling it internally from the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
-:::
-
-###### Return
-\
-A data frame object representing the _UMGYD Effect_.
-
-\newpage
-
 ##### [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L240) Function {#func.regularize.test_lambda.UMGYD_effect.cv}

### 2025-12-15 r/src/support-functions/UMGYD-effect.functions.R

@@ -241,7 +241,7 @@ regularize.train_UMGYD_effect.cv <- function(lambda) {
 }
 regularize.test_lambda.UMGYD_effect.cv <- function(lambda){
   if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UMGY_effect.cv
+    stop("Function: regularize.test_lambda.UMGYD_effect.cv
 `lambda` is `NA`")
   }
   

### 2025-12-15 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
The obsolete helper functions description removed.

@@
 
-#### UMGYDE Model Regularization: Helper Functions
-\
-
-##### [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L240) Function {#func.regularize.test_lambda.UMGYD_effect.cv}
-\
-
-The function calculates _RMSE_ of the _UMGYDE Model_ using _5-Fold Cross Validation_ for the given $\lambda$ parameter value.
-
-::: { #func.regularize.test_lambda.UMGYD_effect.cv.args.lambda .sidebar }
-  - ***lambda:***
-  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.
-
-:::
-
-::: { #func.regularize.test_lambda.UMGYD_effect.cv.details .sidebar }
-###### Details
-\
-Under the hood, the function internally calls the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) and then [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above, and returns the _RMSE_ value that the latter inner function calculates for the given [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.args.lambda) parameter value passed to the former one.
-:::
-
-###### Source Code
-\
-The source code of the function is provided below:
-```{r, eval=FALSE}
-regularize.test_lambda.UMGYD_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UMGY_effect.cv
-`lambda` is `NA`")
-  }
-
-  regularize.train_UMGYD_effect.cv(lambda) |>
-    calc_UMGY_SmoothedDay_effect.RMSE.cv()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L240) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L222) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L240) script on _GitHub_.
-:::
-
-###### Return
-\
-_Root Mean Squared Error (RMSE)_ of the _UMGYD Model_ trained for the given [lambda](#func.regularize.train_UMGYD_effect.cv.args.span) parameter value.
-
-\newpage
-
 #### UMGYDE Model Regularization: Pre-configuration

### 2025-12-15 reports/capstone-movielens.site/05.appendix.Rmd

@@
 ::: {.noteblock data-latex=""}
-This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
 :::
@@
 
-#### [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) Function {#func.regularize.test_lambda.UMGYD_effect.cv}
+#### [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) Function {#func.regularize.test_lambda.UMGYD_effect.cv}
 \
@@
 ```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
+UMGYDE.rglr.fine_tune.results <- 
+  model.tune.param_range(UMGYDE.loop_starter,
+                         UMGYDE.rglr.fine_tune.cache.path,
+                         cache.base_name,
+                         regularize.test_lambda.UMGYD_effect.cv)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
 
@@
 
-Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
-
-::: {.noteblock data-latex=""}
-This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+Internally it uses the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) (described above in this section) and [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) functions (described in section [UMGYDE Model: Utility Functions] above) to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
+
+::: {.noteblock data-latex=""}
+This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
 :::
@@
 
-The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) script on _GitHub_.
+The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) function is shown below:
+```{r eval=FALSE}
+regularize.test_lambda.UMGYD_effect.cv <- function(lambda){
+  if (is.na(lambda)) {
+    stop("Function: regularize.test_lambda.UMGYD_effect.cv
+`lambda` is `NA`")
+  }
+
+  regularize.train_UMGYD_effect.cv(lambda) |>
+    calc_UMGY_SmoothedDay_effect.RMSE.cv()
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) script on _GitHub_.
 :::

### 2025-12-16 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Function description refined: `model.tune.param_range`.

@@
 ::: {.noteblock data-latex=""}
-The complete source code of building and training the current model is available in the [UMGYDEM Training with default parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1745) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1745) script on _GitHub_.
+The complete source code of building and training the current model is available in the [UMGYDEM Training with default parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1477) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1477) script on _GitHub_.
 :::
 
-We are going to use our helper function [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described in the [UMGYDE Model: Helper Functions] section, which, as we explained, internally calls the R function [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess).
+We are going to use the helper function ([train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A: Support Functions]) specifically designed to train the *UMGYDE Model*, which under the hood calls the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `R` function, passing its `degree` and `span` parameters values taken from the caller's [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) arguments, respectively.
 
-We will start by calling the `train_UMGY_SmoothedDay_effect.cv` with default parameters, which means that the `loess` function will be implicitly called with `degree = 1` and `span = 0.75` parameters (the default values for our custom [loess_de](#func.loess_de) function, which, in turn, calls the `loess` under the hood).
+We will start by calling the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) with default parameters, which means that the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function will be implicitly called with `degree = 1` and `span = 0.75` arguments - the default values for the auxiliary function [loess_de](#func.loess_de) (described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a)) included in the call chain that actually, calls the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
 
-Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1495) for training our model using the *K-Fold Cross Validation* method, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
+Below is the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1495) that trains our model with the default `degree` and `span` parameter values using *K-Fold Cross Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
 ```{r, eval=FALSE}
@@
 
-Let's calculate the _RMSE_ of the current model using the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function described above:
+Let's calculate the _RMSE_ of the current model using the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) helper function described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a):
 
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
+In the code snippet above we also use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section *Common Helper Functions /* [Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three steps - one per each possible value of the `degree` parameter.
+Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three steps - one for each possible value of the `degree`.
 :::
@@
 
-##### Pre-configuration: `span` Range Determination
+##### Pre-configuration: `span` Determining the optimal range of the *span* parameter
 \
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration (`degree = 0`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1827) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1827) script on _GitHub_.
+The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration (`degree = 0`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1558) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1558) script on _GitHub_.
 :::
 
-Below the most significant part of the code performing the current model tuning, the _Pre-configuration Step_ is provided:
+Below is the [lines of code]() that determines the optimal range of `span` for the further model tuning when `degree = 0`:
 ```{r, eval=FALSE}
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [tune.model_param](#func.tune.model_param) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) section) to update and print the table above.
+
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) to calculate the *RMSE* for the *UMGE Model*;
+:::
 

### 2025-12-16 reports/capstone-movielens.site/05.appendix.Rmd
Function description refined: `model.tune.param_range`.

@@
 
-Implements an algorithm for selecting the best value of the *regularization parameter* $\lambda$ from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument, using a simple approach of selecting the *penalty term* as described in [Section 24.3 *Selecting the penalty term*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-selecting-penalty-term)*[@IDS2_24-3].
+Implements an algorithm for selecting the best value of the *tuning parameter* from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
 
@@
 ::: { #func.tune.model_param.args.param_values .sidebar }
-  - **param_values:** Numeric vector containing a sorted list of $\lambda$ values to search for the best one during the model regularization process;
+  - **param_values:** Numeric vector containing a sorted list of parameter values to search for the best one during the model regularization process;
 
@@
 ::: { #func.tune.model_param.args.fn_tune.test.param_value .sidebar }
-  - **fn_tune.test.param_value:** Model-specific helper function that validates the model by computing the model's *RMSE* value for a given value of the $\lambda$ parameter;
+  - **fn_tune.test.param_value:** Model-specific helper function that validates the model by computing the model's *RMSE* value for a given parameter value;
 
@@
 
-With the approach used in this algorithm, the best value of the *regularization parameter* $\lambda$ (we call this the *best value of the regularization parameter* or the *best value of $\lambda$*) is considered to be the value corresponding to the minimum value of the *Root Mean Square Error (RMSE)* for the model being tested.
-
-To find the best value of the $\lambda$ parameter, the algorithm iterates over the values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the *RMSE* of the model for each of them, using the helper function specified in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument.
-
-The algorithm continues iterating until the end of the  $\lambda$ parameter values list if [break.if_min](#func.tune.model_param.args.break.if_min) is `FALSE`.
+With the approach used in this algorithm, the best value of the *tuning parameter* (we call this the *best value of the tuning parameter*) is considered to be the value corresponding to the minimum value of the *Root Mean Square Error (RMSE)* for the model being tested.
+
+To find the best value, the algorithm iterates over the values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the *RMSE* of the model for each of them, using the helper function specified in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument.
+
+The algorithm continues iterating until the end of the parameter values list if [break.if_min](#func.tune.model_param.args.break.if_min) is `FALSE`.
 
@@
 ::: {.noteblock data-latex=""}
-The algorithm assumes that the set of the *RMSE* values is a monotonically non-increasing function of the *regularization parameter* $\lambda$ until the minimum is reached and monotonically non-decreasing thereafter.
+The algorithm assumes that the set of the *RMSE* values is a monotonically non-increasing function of the *tuning parameter* until the minimum is reached and monotonically non-decreasing thereafter.
 That is, it is assumed that the function can have only one minimum on the given set.
@@
 
-  - `best_result`: Vector containing a *pair of values*: the found *best value of the regularization parameter* $\lambda$ for which the *RMSE* value is minimal, along with the minimal *RMSE* value itself;
+  - `best_result`: Vector containing a *pair of values*: the found *best value of the tuning parameter* for which the *RMSE* value is minimal, along with the minimal *RMSE* value itself;
 
@@
 
-    - *parameter.value*: A vector containing all processed values of the parameter $\lambda$;
-
-    - *RMSE*: A vector containing the *RMSE* values corresponding to the processed values of $\lambda$.
+    - *parameter.value*: A vector containing all processed values of the *tuning parameter*;
+
+    - *RMSE*: A vector containing the *RMSE* values corresponding to the processed values of the *tuning parameter*.
 
@@
 
-Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *regularization parameter* $\lambda$ over a given interval determined by the $start$ and $end$ values of the interval passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
-The algorithm is based on a simple approach of selecting the *penalty term* as described in [Section 24.3 *Selecting the penalty term*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-selecting-penalty-term)*[@IDS2_24-3].
+Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *tuning parameter* over a given interval determined by the $start$ and $end$ values of the interval passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
 
@@
 \
-A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval over which the value of the parameter $\lambda$ that minimizes *RMSE* has to be found.
-
-The `dvs` is a divisor used to calculate the *step size* for partitioning the interval into a sequence of $\lambda$ values, among which the value that minimizes *RMSE* has to be found.
+A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval over which the value of the *tuning parameter* that minimizes *RMSE* has to be found.
+
+The `dvs` is a divisor used to calculate the *step size* for partitioning the interval into a sequence of parameter values, among which the value that minimizes *RMSE* has to be found.
 
@@
 
-In fact, the `seq` function is called internally to generate the sequence during the algorithm's execution.
-
-Thus, the sequence is generated by the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L256):
+In fact, the [seq](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/seq) function is called internally to generate the sequence during the algorithm's execution by the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L256):
 ```{r eval=FALSE}
@@
 \
+
 To improve performance, the algorithm caches intermediate results in the file system. The value passed in *this argument* specifies the path to the directory where the files are cached.
@@
 \
+
 The algorithm generates unique names for cache files based on this and the [loop_starter](#func.model.tune.param_range.args.loop_starter) arguments' values, as well as a few other intermediate values calculated at runtime.
@@
 \
-Model-specific helper function name to pass to the [same-named argument](#func.tune.model_param.args.fn_tune.test.param_value) of the [tune.model_param](#func.tune.model_param) function (see description above) that is called internally during the execution of the algorithm.
+
+Name of a model-specific helper function to pass to the [same-named argument](#func.tune.model_param.args.fn_tune.test.param_value) of the [tune.model_param](#func.tune.model_param) function (see description above) that is called internally during the execution of the algorithm.
 :::
@@
 
-With the approach used in this algorithm, the best value of the *regularization parameter* $\lambda$ (we call this the *best value of the regularization parameter* or the *best value of $\lambda$*) is considered to be the value corresponding to the minimum value of the *Root Mean Square Error (RMSE)* for the model being tested.
+With the approach used in this algorithm, the best value of the *tuning parameter* (we call this the *best value of the tuning parameter*) is considered to be the value corresponding to the minimum value of the *Root Mean Square Error (RMSE)* for the model being tested.
 
@@
   1.
-Calculates the step size for partitioning the interval into a sequence of $\lambda$ values and save it to the local variable `seq_increment` as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L240):
+Calculates the step size for partitioning the interval into a sequence of values and save it to the local variable `seq_increment` as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L240):
 ```{r eval=FALSE}
@@
   3.
-If the *step size* is no less than the minimum allowed value (`seq_increment >= 1e-13` in our case), creates a vector containing a sequence of $\lambda$ values (as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above) using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L256):
+If the *step size* is no less than the minimum allowed value (`seq_increment >= 1e-13` in our case), creates a vector containing a sequence of parameter values (as described in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument description above) using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L256):
 ```{r eval=FALSE}
@@
   8.
-Determines endpoints for a new interval of $\lambda$ values in the neighborhood of the minimum *RMSE* value (figured out so far)  with use of the helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described above, to improve the accuracy of the *RMSE* calculation in the next iteration:
+Determines endpoints for a new interval of the *tuning parameter* values in the neighborhood of the minimum *RMSE* value (figured out so far)  with use of the helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described above, to improve the accuracy of the *RMSE* calculation in the next iteration:
 ```{r eval=FALSE}
@@
   10.
-Checks deviations from the minimum *RMSE* value for the values corresponding to the endpoints of the new interval of the $\lambda$ parameter values figured out in the [step 8](#func.model.tune.param_range.details.step8) and updates in corresponding local variables those endpoint values of $\lambda$ and *RMSE* for which the corresponding deviation reaches the minimum threshold specified by the value passed in the [endpoint.min_diff](#func.model.tune.param_range.args.endpoint.min_diff) argument:
+Checks the deviations from the minimum *RMSE* value for the values corresponding to the endpoints of the new interval of the *tuning parameter* values figured out in the [step 8](#func.model.tune.param_range.details.step8), and updates in corresponding local variables those parameter endpoint and correspondinng *RMSE* values, for which the corresponding deviation reaches the minimum threshold specified by the value passed in the [endpoint.min_diff](#func.model.tune.param_range.args.endpoint.min_diff) argument:
 ```{r eval=FALSE}
@@
   11.
-Makes sure that the index of the start endpoint of the interval of the $\lambda$ parameter values figured out in the [step8](#func.model.tune.param_range.details.step8) is less than the index of the end endpoint and, if not, exits the loop with the *warning message* and goes to the [Finalizing Execution](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L426) section of the code described in the [Finalizing Execution](#func.model.tune.param_range.details.finalizing) subsection below:
+Makes sure that the index of the start endpoint of the parameter interval figured out in the [step8](#func.model.tune.param_range.details.step8) is less than the index of the end endpoint and, if not, exits the loop with the *warning message* and goes to the [Finalizing Execution](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L426) section of the code described in the [Finalizing Execution](#func.model.tune.param_range.details.finalizing) subsection below:
 ```{r eval=FALSE}
@@
   13.
-(`best_RMSE == min_RMSE`) Checks the number of matches between the minimum *RMSE* value determined so far and the minimum *RMSE* value calculated for the current iteration (`best_RMSE == min_RMSE`), and if it exceeds the value passed in the argument [max.identical.min_RMSE.count](#func.model.tune.param_range.args.max.identical.min_RMSE.count), saves the best results for the $\lambda$ and *RMSE* values figured out in the current iteration in the local variable `param_values.best_result` and exits the loop with an appropriate warning message and goes to the [Finalizing Execution](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L426) section of the code described in the [Finalizing Execution](#func.model.tune.param_range.details.finalizing) subsection below.
+(`best_RMSE == min_RMSE`) Checks the number of matches between the minimum *RMSE* value determined so far and the minimum *RMSE* value calculated for the current iteration (`best_RMSE == min_RMSE`), and if it exceeds the value passed in the argument [max.identical.min_RMSE.count](#func.model.tune.param_range.args.max.identical.min_RMSE.count), saves the best results for the *tuning parameter* and corresponding *RMSE* values figured out in the current iteration in the local variable `param_values.best_result` and exits the loop with an appropriate warning message and goes to the [Finalizing Execution](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L426) section of the code described in the [Finalizing Execution](#func.model.tune.param_range.details.finalizing) subsection below.
 
@@
 
-  - `best_result`: A vector containing a *pair of values*: the found *best value of the regularization parameter* $\lambda$ for which the *RMSE* value is minimal, along with the minimal *RMSE* value itself;
-
-  - `param_values.endpoints`: Information related to the final interval of the *regularization parameter* $\lambda$ values.;
+  - `best_result`: A vector containing a *pair of values*: the found *best value of the tuning parameter* for which the *RMSE* value is minimal, along with the minimal *RMSE* value itself;
+
+  - `param_values.endpoints`: Information related to the final interval of the *tuning parameter* values;
 
@@
 
-    - *parameter.value*: A vector containing all processed values of the parameter $\lambda$;
-
-    - *RMSE*: A vector containing the *RMSE* values corresponding to the processed values of $\lambda$.
+    - *parameter.value*: A vector containing all processed values of the *tuning parameter*;
+
+    - *RMSE*: A vector containing the *RMSE* values corresponding to the processed *tuning parameter* values.
 
@@
 The complete source code of the function [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) script on _GitHub_.
-:::
-
-\newpage
-
-#### [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.cmmn_hlp.rglr.fn.tmpl}
-\
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-cmmn_hlp.rglr.fn.tmpl()
-
-```
-:::
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.args .sidebar }
-##### Arguments
-\
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
-  - **:** ;
-
-:::
-::: { #func.cmmn_hlp.rglr.fn.tmpl.args. .sidebar }
-  - **:** ;
-
-:::
-:::
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.cmmn_hlp.rglr.fn.tmpl.code .sidebar }
-##### Source Code
-\
-
-The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [cmmn_hlp.rglr.fn.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
-:::
 :::

### 2025-12-16 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report section documented: UMGYDE Model Tuning: Step 1 (`degree = 0`) / Pre-Configuration.

@@
 ::: {.noteblock data-latex=""}
-The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization], respectively, of [Appendix A: Support Functions].
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UME Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in the code snippet above is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
+The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in the code snippet above is described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization], respectively, of [Appendix A: Support Functions].
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UME Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::

### 2025-12-16 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report section documented: UMGYDE Model Tuning: Step 1 (`degree = 0`) / Pre-Configuration.

@@
 ::: {.noteblock data-latex=""}
-The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-The custom functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGE Model: Regularization] of [Appendix A: Support Functions], respectively.
+The custom functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGE Model: Regularization] of [Appendix A: Support Functions], respectively.
 :::
@@
 ::: {.noteblock data-latex=""}
-The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
+The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::

### 2025-12-16 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report section documented: UMGYDE Model Tuning: Step 1 (`degree = 0`) / Pre-Configuration.

@@
 ::: {.noteblock data-latex=""}
-The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::

### 2025-12-16 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report section documented: UMGYDE Model Tuning: Step 1 (`degree = 0`) / Pre-Configuration.

@@
 
-  - [tune.model_param](#func.tune.model_param) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) section) to update and print the table above.
+  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to to select the best value of the *tuning parameter* from the given sequence of the *parameter values* (passed in the [param_values](#func.tune.model_param.args.param_values) argument).
 
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) to calculate the *RMSE* for the *UMGE Model*;
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument of the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.
+
 :::
 
-Below is the visual representation of the `span` parameter values range we have figured out in this step of tuning:
+Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the selected interval, with the parameter `degree = 0`, as we have figured out in this step of tuning:
 ```{r}
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
+:::
 

### 2025-12-16 reports/capstone-movielens.site/05.appendix.Rmd
Report section documented: UMGYDE Model Tuning: Step 1 (`degree = 0`) / Pre-Configuration.

@@
 
-### Regularization Functions {#appndx_a.CHF.regularization}
+### Model Tuning Utils {#appndx_a.CHF.model_tuning_utils}
 \
@@
 
-Selects the best values from a pair of matched vectors: a vector of sorted *regularization parameter* $\lambda$ values and a vector of corresponding *Root Mean Squared Errors (RMSE)* values passed in the [param_values](#func.tune.model_param.args.param_values) and [RMSEs](#func.get_best_param.result.args.RMSEs) arguments, respectively.
+Selects the best values from a pair of matched vectors: a vector of sorted *tuning parameter* values and a vector of corresponding *Root Mean Squared Errors (RMSE)* values passed in the [param_values](#func.tune.model_param.args.param_values) and [RMSEs](#func.get_best_param.result.args.RMSEs) arguments, respectively.
 
@@
 ::: { #func.get_best_param.result.args.param_values .sidebar }
-  - **param_values:** Numeric vector containing a sorted list of the *regularization parameter* $\lambda$ values to search for the best one during the *Model Regularization* process;
+  - **param_values:** Numeric vector containing a sorted list of the *tuning parameter* values to search for the best one during the *Model Regularization* process;
 
@@
 
-This is a *utility function* used to select the *best values* during the *Model Regularization* process, utilizing the *penalized approach* to regularize predictions as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2].
-
-With this approach, the best value of the *regularization parameter* $\lambda$ (we call this the *best value of the regularization parameter* or the *best value of $\lambda$*) is considered to be the value corresponding to the minimum value of the *RMSE* for the model being tested.
+This is a *utility function* used to select the *best values* during the *Model Parameter Tuning* process (including the *Model Regularization* procedure that utilizes the *penalized approach* to regularize predictions as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]).
+
+With this approach, the best value of the *tuning parameter* is considered to be the value corresponding to the minimum value of the *RMSE* for the model being tested.
 
@@
 
-Numeric vector containing a pair of values: the best *regularization parameter* $\lambda$ value and corresponding *minimal RMSE*. 
+Numeric vector containing a pair of values: the best *tuning parameter* value and corresponding *minimal RMSE*. 
 :::
@@
 
-With the approach used in this algorithm, the best value of the *tuning parameter* (we call this the *best value of the tuning parameter*) is considered to be the value corresponding to the minimum value of the *Root Mean Square Error (RMSE)* for the model being tested.
+With the approach used in this algorithm, the best value of the *tuning parameter* is considered to be the value corresponding to the minimum value of the *Root Mean Square Error (RMSE)* for the model being tested.
 
@@
 ::: {.noteblock data-latex=""}
-*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
+In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
 
@@
 ::: {.noteblock data-latex=""}
-This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
 ::: {.noteblock data-latex=""}
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree0` function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
+In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree0` function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
+This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
+In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
+In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.
+In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
 

### 2025-12-16 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Mino fix for the previous commit.

@@
 
-  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to to select the best value of the *tuning parameter* from the given sequence of the *parameter values* (passed in the [param_values](#func.tune.model_param.args.param_values) argument).
+  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* from the given sequence of the *parameter values* (passed in the [param_values](#func.tune.model_param.args.param_values) argument).
 

### 2025-12-16 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report section documented: UMGYDE Model Tuning: Step 1 (`degree = 0`) .

@@
 ::: {.noteblock data-latex=""}
-The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 0`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1893) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1893) script on _GitHub_.
+The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 0`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1624) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1624) script on _GitHub_.
 :::
 
-Below the most significant part of the code performing the current model _Fine-tuning_ is provided:
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1625) performs the *fine-tuning* of the *UMGYDE Model* by precise selection of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter with the `degree` parameter set to $0$:
 ```{r, eval=FALSE}
@@
 
-Below is the visual representation of the current model _Fine-tuning_ results for the parameter value: `degree = 0`:
+\newpage
+
+Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the neighborhood of its *best value* (when the parameter `degree = 0`), which we have determined in this (*fine-tuning*) step:
 ```{r}
@@
 ```
-Now, we can add the _UMGYDE Model Tuning_ result for `degree = 0` to our _Result Table_:
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
+:::
+
+\newpage
+
+Now, we can add the best *RMSE* figured out for the *UMGYDE Fine-tuned Model* with the [loess] `degree = 0` (let's call it *Tuned UMGYDE.d0 Model*) to our *Result Table*:
 ```{r, eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
+In the code snippet above we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section *Common Helper Functions /* [Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
 :::

### 2025-12-17 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Fix for the Report section: UMGYDE Model Tuning: Step 1 (`degree = 0`) .

@@
 
-Below is the [lines of code]() that determines the optimal range of `span` for the further model tuning when `degree = 0`:
+Below is the [lines of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1578) that determines the optimal range of `span` for the further model tuning when `degree = 0`:
 ```{r, eval=FALSE}
@@
 
-Now, we can add the best *RMSE* figured out for the *UMGYDE Fine-tuned Model* with the [loess] `degree = 0` (let's call it *Tuned UMGYDE.d0 Model*) to our *Result Table*:
+Now, we can add the best *RMSE* figured out for the *UMGYDE Fine-tuned Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree = 0` (let's call it *Tuned UMGYDE.d0 Model*) to our *Result Table*:
 ```{r, eval=FALSE}

### 2025-12-18 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report section documented: UMGYDE Model Tuning: Step 1 (`degree = 1`) + fix for section UMGYDE Model Tuning: Step 1 (`degree = 0`) .

@@
 
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [model.tune.param_range](#func.model.tune.param_range) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter* best value using the *best value neighborhood* information* passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
+
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (already mentioned in the previous section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument of the [model.tune.param_range](#func.model.tune.param_range) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.
+
+:::
+
 \newpage
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration  (`degree = 1`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1944) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1944) script on _GitHub_.
+The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration  (`degree = 1`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1675) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1675) script on _GitHub_.
 :::
 
-Below the most significant part of the code performing the current model tuning, the _Pre-configuration Step_ is provided:
+Below is the [lines of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1695) that determines the optimal range of `span` for the further model tuning when `degree = 1`:
 ```{r, eval=FALSE}
+  spans <- seq(0.0005, 1, 0.001)
   lss.UMGYDE.preset.degree1.result <- 
@@
 
-Below is the visual representation of the `span` parameter values range we have figured out in this step of tuning:
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* from the given sequence of the *parameter values* (passed in the [param_values](#func.tune.model_param.args.param_values) argument).
+
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument of the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.
+
+:::
+
+\newpage
+
+Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the selected interval, with the parameter `degree = 1`, as we have figured out in this step of tuning:
 ```{r}
@@
 
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
+:::
+
+\newpage
+
 ##### UMGYDE Model Fine-tuning (`degree = 1`)
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 1`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2007) script on _GitHub_.
+The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 1`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1738) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1738) script on _GitHub_.
 :::
 
-Below the most significant part of the code performing the current model _Fine-tuning_ is provided:
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1739) performs the *fine-tuning* of the *UMGYDE Model* by precise selection of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter with the `degree` parameter set to $1$:
 ```{r, eval=FALSE}
@@
 
-Below is the visual representation of the current model _Fine-tuning_ results for the parameter value: `degree = 1`:
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [model.tune.param_range](#func.model.tune.param_range) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter* best value using the *best value neighborhood* information* passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
+
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) (already mentioned in the previous section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument of the [model.tune.param_range](#func.model.tune.param_range) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $1$.
+
+:::
+
+\newpage
+
+Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the neighborhood of its *best value* (when the parameter `degree = 1`), which we have determined in this (*fine-tuning*) step:
 ```{r}
@@
 
-Now, we can add the _UMGYDE Model Tuning_ result for `degree = 1` to our _Result Table_:
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
+:::
+
+\newpage
+
+Now, we can add the best *RMSE* figured out for the *UMGYDE Fine-tuned Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree = 1` (let's call it *Tuned UMGYDE.d1 Model*) to our *Result Table*:
 ```{r, eval=FALSE}

### 2025-12-18 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report section documented: UMGYDE Model Tuning: Step 2 & 3 (`degree = 1, 2`).

@@
 \
+
+::: {.noteblock data-latex=""}
+The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Step 1 (`degree = 0`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1554) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1554) script on _GitHub_.
+:::
 
@@
 
+::: {.noteblock data-latex=""}
+The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Step 2 (`degree = 1`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1671) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1671) script on _GitHub_.
+:::
+
 ##### Pre-configuration: `span` Range Determination
@@
 
+::: {.noteblock data-latex=""}
+The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Step 3 (`degree = 2`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1783) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1783) script on _GitHub_.
+:::
+
 ##### Pre-configuration: `span` Range Determination
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration (`degree = 2`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2056) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2057) script on _GitHub_.
+The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration (`degree = 2`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1787) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1787) script on _GitHub_.
 :::
 
-Below the most significant part of the code performing the current model tuning, the _Pre-configuration Step_ is provided:
+Below is the [lines of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1807) that determines the optimal range of `span` for the further model tuning when `degree = 2`:
 ```{r, eval=FALSE}
@@
 
-Below is the visual representation of the `span` parameter values range we have figured out in this step of tuning:
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* from the given sequence of the *parameter values* (passed in the [param_values](#func.tune.model_param.args.param_values) argument).
+
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument of the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $2$.
+
+:::
+
+\newpage
+
+Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the selected interval, with the parameter `degree = 2`, as we have figured out in this step of tuning:
 ```{r}
@@
 
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
+:::
+
+\newpage
+
 ##### UMGYDE Model Fine-tuning (`degree = 2`)
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 2`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2119) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2119) script on _GitHub_.
+The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 2`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1850) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1850) script on _GitHub_.
 :::
 
-Below the most significant part of the code performing the current model _Fine-tuning_ is provided:
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1851) performs the *fine-tuning* of the *UMGYDE Model* by precise selection of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter with the `degree` parameter set to $2$:
 ```{r, eval=FALSE}
@@
 
-Below is the visual representation of the current model _Fine-tuning_ results for the parameter value: `degree = 2`:
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [model.tune.param_range](#func.model.tune.param_range) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter* best value using the *best value neighborhood* information* passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
+
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2) (already mentioned in the previous section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument of the [model.tune.param_range](#func.model.tune.param_range) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $2$.
+
+:::
+
+\newpage
+
+Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the neighborhood of its *best value* (when the parameter `degree = 2`), which we have determined in this (*fine-tuning*) step:
 ```{r}
@@
 ::: {.noteblock data-latex=""}
-The custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) we used above is described in the [Data Helper Functions] section of [Appendix A](#appndx_a).
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
 :::
 
-Now, we can add the _UMGYDE Model Tuning_ result for `degree = 2` to our _Result Table_:
+\newpage
+
+Now, we can add the best *RMSE* figured out for the *UMGYDE Fine-tuned Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree = 2` (let's call it *Tuned UMGYDE.d2 Model*) to our *Result Table*:
 ```{r, eval=FALSE}

### 2025-12-18 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Fix for Report sections:  UMGYDE Model Tuning: Step 2 & 3 (`degree = 1, 2`).

@@
 
-##### Pre-configuration: `span` Determining the optimal range of the *span* parameter
+##### Pre-configuration: `span` Optimal `span` Range Determination (`degree = 0`)
 \
@@
 
-  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* from the given sequence of the *parameter values* (passed in the [param_values](#func.tune.model_param.args.param_values) argument).
+  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
 
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument of the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.
 
@@
 
-  - [model.tune.param_range](#func.model.tune.param_range) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter* best value using the *best value neighborhood* information* passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
+  - [model.tune.param_range](#func.model.tune.param_range) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter best value* using the *best value neighborhood* information passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
 
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (already mentioned in the previous section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument of the [model.tune.param_range](#func.model.tune.param_range) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (already mentioned in the previous section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument) to the [model.tune.param_range](#func.model.tune.param_range) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.
 
@@
 
-##### Pre-configuration: `span` Range Determination
+##### Pre-configuration: Optimal `span` Range Determination (`degree = 1`)
 \
@@
 
-  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* from the given sequence of the *parameter values* (passed in the [param_values](#func.tune.model_param.args.param_values) argument).
+  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
 
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument of the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $1$.
 
@@
 
-  - [model.tune.param_range](#func.model.tune.param_range) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter* best value using the *best value neighborhood* information* passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
+  - [model.tune.param_range](#func.model.tune.param_range) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter best value* using the *best value neighborhood* information passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
 
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) (already mentioned in the previous section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument of the [model.tune.param_range](#func.model.tune.param_range) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $1$.
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) (already mentioned in the previous section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument) to the [model.tune.param_range](#func.model.tune.param_range) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $1$.
 
@@
 
-##### Pre-configuration: `span` Range Determination
+##### Pre-configuration: Optimal `span` Range Determination (`degree = 2`)
 \
@@
 
-  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* from the given sequence of the *parameter values* (passed in the [param_values](#func.tune.model_param.args.param_values) argument).
+  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
 
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument of the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $2$.
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $2$.
 
@@
 
-  - [model.tune.param_range](#func.model.tune.param_range) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter* best value using the *best value neighborhood* information* passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
+  - [model.tune.param_range](#func.model.tune.param_range) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter best value* using the *best value neighborhood* information passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
 
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2) (already mentioned in the previous section) used as an auxiliary function passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument of the [model.tune.param_range](#func.model.tune.param_range) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $2$.
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2) (already mentioned in the previous section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument) to the [model.tune.param_range](#func.model.tune.param_range) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $2$.
 

### 2025-12-19 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Fix for the Report section: `UMGYDE Model Tuning: Step 3`.

@@
 
-::: {.noteblock data-latex=""}
-The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Step 1 (`degree = 0`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1554) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1554) script on _GitHub_.
-:::
-
-##### Pre-configuration: `span` Optimal `span` Range Determination (`degree = 0`)
+##### Pre-configuration: Optimal `span` Range Determination (`degree = 0`)
 \
@@
 
-  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
+  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
 
@@
 
-::: {.noteblock data-latex=""}
-The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Step 2 (`degree = 1`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1671) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1671) script on _GitHub_.
-:::
-
 ##### Pre-configuration: Optimal `span` Range Determination (`degree = 1`)
@@
 
+\newpage
+
 #### UMGYDE Model Tuning: Step 3 (`degree = 2`)
 \
-
-::: {.noteblock data-latex=""}
-The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Step 3 (`degree = 2`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1783) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1783) script on _GitHub_.
-:::
 
@@
 
-Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the neighborhood of its *best value* (when the parameter `degree = 2`), which we have determined in this (*fine-tuning*) step:
+Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the neighborhood of its *best value* (when the parameter `degree = 2`), which we have determined in this (*fine-tuning*) step.
+Since the left endpoint value of the *RMSE* range has much smaller deviation from the minimum than the value of the right endpoint, for visual clarity, we plot the left part of the graph once more on an *enlarged scale* (below the main graph):
 ```{r}
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
+In the code snippet above, we use the custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
 :::

### 2025-12-19 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the Report section: `UMGYDE Model Tuning: Step 3`.

@@
 
-#### [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) Function {#func.data.plot}
+#### [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L580) Function {#func.data.plot}
 \
@@
 ```{r eval=FALSE}
-data.plot(data, 
-          title, 
-          xname, 
-          yname, 
-          xlabel = NULL, 
-          ylabel = NULL,
-          line_col = "blue",
-          normalize = FALSE)
+lss.UMGYDE.preset.degree2.result$tuned.result |>
+  data.plot(title = "UMGYDE Model, `loess` function args: range of `span` values for `degree = 2`",
+              xname = "parameter.value", 
+              yname = "RMSE", 
+              xlabel = "spans", 
+              ylabel = "RMSE")
 ```
@@
 ::: { #func.data.plot.args.xlabel .sidebar }
-  - **xlabel = NULL:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
+  - **xlabelL:** (Character string, `NULL` by default) The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
 
@@
 ::: { #func.data.plot.args.ylabel .sidebar }
-  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;
+  - **ylabel:** (Character string, `NULL` by default) The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;
 
@@
 ::: { #func.data.plot.args.line_col .sidebar }
-  - **line_col = blue:** The line color;
+  - **line_col:** (Character string, \textcolor{blue}{blue} by default) Line color.
 
@@
 ::: { #func.data.plot.args.normalize .sidebar }
-- **normalize = FALSE:** If `TRUE`, deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves. Otherwise, the $y$ values are used.
+- **normalize:** (Boolean, `FALSE` by default) If `TRUE`, deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves. Otherwise, the $y$ values are used.
 
@@
 
-The function is a wrapper for the [ggplot2::ggplot](https://ggplot2.tidyverse.org/reference/ggplot.html) function and is a simple and convenient tool for visualizing the data of this project.
+The function is a wrapper for the [ggplot2::ggplot](https://ggplot2.tidyverse.org/reference/ggplot.html) function and is a simple and convenient tool for visualizing the data of *this Project*.
 
@@
 
-The soure code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function is shown below:
+The soure code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L580) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
-:::
-:::
-
-#### [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) Function {#func.data.plot.left.n}
+The source code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L580) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L435) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L580) script on _GitHub_.
+:::
+:::
+
+#### [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L481) Function {#func.data.plot.left.n}
 \
@@
 ::: { #func.data.plot.left.n.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-data.plot.left.n <- function(data, 
-                             left.n = 0,
-                             title, 
-                             xname, 
-                             yname, 
-                             xlabel, 
-                             ylabel,
-                             line_col = "red",
-                             normalize = FALSE)
-```
-:::
-
-::: { #func.data.plot.left.n.args .sidebar }
-##### Arguments
-\
-
-::: { #func.data.plot.left.n.args.data .sidebar }
-  - **data:** Dataset to use for the plot.
-
-:::
-::: { #func.data.plot.left.n.args.left.n .sidebar }
-  - **left.n:** If a positive numeric value, specifies the number of the first rows of the dataset to plot. Otherwise, the entire dataset data is set to plot.
-
-:::
-::: { #func.data.plot.left.n.args.title .sidebar }
-  - **title:** Title of the plot.
-
-:::
-::: { #func.data.plot.left.n.args.xname .sidebar }
-  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot.
-
-:::
-::: { #func.data.plot.left.n.args.yname .sidebar }
-  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot.
-
-:::
-::: { #func.data.plot.left.n.args.xlabel .sidebar }
-  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left.n.args.ylabel .sidebar }
-  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left.n.args.line_col .sidebar }
-  - **line_col = blue:** The line color.
-
-:::
-::: { #func.data.plot.left.n.args.normalize .sidebar }
-  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
-
-:::
-:::
-
-::: { #func.data.plot.left.n.details .sidebar }
-##### Details
-\
-
-The function is a wrapper for the [data.plot](#func.data.plot) function described above and is a simple and convenient tool for more detailed visualization of the left part of the graph, initially built based on the entire data set passed in the [data](#func.data.plot.left.n.args.data) parameter.
-:::
-
-::: { #func.data.plot.left.n.code .sidebar }
-##### Source Code
-\
-
-The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) function is shown below:
-```{r eval=FALSE}
-data.plot.left.n <- function(data, 
-                             left.n = 0,
-                             title, 
-                             xname, 
-                             yname, 
-                             xlabel, 
-                             ylabel,
-                             line_col = "red",
-                             normalize = FALSE) {
-  x_col <- data[, xname] 
-  y_col <- data[, yname]
-
-  data.left <- data
-
-  if (left.n > 0) {
-    data.left <- data |> 
-      head(left.n)
-  }
-
-  data.left |>
-    data.plot(title = title,
-              xname = xname,
-              yname = yname,
-              xlabel = xlabel,
-              ylabel = ylabel,
-              line_col = line_col,
-              normalize = normalize)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) script on _GitHub_.
-:::
-:::
-
-#### [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) Function {#func.data.plot.left_detailed}
-\
-
-Combines two graphs plotted by the internally called helper functions in a grid: the first is a standard graph plotted by the [data.plot](#func.data.plot) function described above, the second is a graph based on the first $n$ rows (the $n$ is specified by the [left.n](#func.data.plot.left.n.args.left.n) parameter) of the dataset plotted by the [data.plot.left.n](#func.data.plot.left.n) function also described above (The data for both graphs is passed in the [data]).(#func.data.plot.left.n.args.data) parameter).
-
-::: {.noteblock data-latex=""}
-The dataset passed in the [data](#func.data.plot.left.n.args.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.args.xname) parameter).
-:::
-
-::: { #func.data.plot.left_detailed.usage .sidebar }
 ##### Usage
@@
                                     line_col2 = "red",
-                                    normalize = FALSE)
+                                    normalize = FALSE) {
+# ...
+
+  p2 <- data |>
+    data.plot.left.n(left.n = left.n,
+                     title = title.left,
+                     xname = xname, 
+                     yname = yname, 
+                     xlabel = xlabel2, 
+                     ylabel = ylabel2,
+                     line_col = line_col2,
+                     normalize = normalize)
+  grid.arrange(p1, p2)
+}
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, the function `data.plot.left.n` is called internally from the [data.plot.left_detailed](#func.data.plot.left_detailed) function described below in this section.
+:::
+:::
+
+::: { #func.data.plot.left.n.args .sidebar }
+##### Arguments
+\
+
+::: { #func.data.plot.left.n.args.data .sidebar }
+  - **data:** Dataset to use for the plot.
+
+:::
+::: { #func.data.plot.left.n.args.left.n .sidebar }
+  - **left.n:** (Integer, $0$ by default)If a positive numeric value, specifies the number of the first rows of the dataset to plot. Otherwise, the entire dataset data is set to plot.
+
+:::
+::: { #func.data.plot.left.n.args.title .sidebar }
+  - **title:** Title of the plot.
+
+:::
+::: { #func.data.plot.left.n.args.xname .sidebar }
+  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot.
+
+:::
+::: { #func.data.plot.left.n.args.yname .sidebar }
+  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot.
+
+:::
+::: { #func.data.plot.left.n.args.xlabel .sidebar }
+  - *xlabel*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label.
+
+:::
+::: { #func.data.plot.left.n.args.ylabel .sidebar }
+  - **ylabel:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.
+
+:::
+::: { #func.data.plot.left.n.args.line_col .sidebar }
+  - **line_col:** (Character string, \textcolor{red}{red} by default) Line color.
+
+:::
+::: { #func.data.plot.left.n.args.normalize .sidebar }
+  - **normalize:** (Boolean, `FALSE` by default) If `TRUE`, deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves. Otherwise, the $y$ values are used.
+
+:::
+:::
+
+::: { #func.data.plot.left.n.details .sidebar }
+##### Details
+\
+
+The function is a wrapper for the [data.plot](#func.data.plot) function described above and is a simple and convenient tool for more detailed visualization of the left part of the graph, initially built based on the entire data set passed in the [data](#func.data.plot.left.n.args.data) parameter.
+
+::: {.noteblock data-latex=""}
+This is an auxiliary function that is used internally in the [data.plot.left_detailed](#func.data.plot.left_detailed) function (described below in this section) as shown above in the [Usage](#func.data.plot.left.n.usage) section of *this Description*.
+:::
+:::
+
+::: { #func.data.plot.left.n.code .sidebar }
+##### Source Code
+\
+
+The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L481) function is shown below:
+```{r eval=FALSE}
+data.plot.left.n <- function(data, 
+                             left.n = 0,
+                             title, 
+                             xname, 
+                             yname, 
+                             xlabel, 
+                             ylabel,
+                             line_col = "red",
+                             normalize = FALSE) {
+  x_col <- data[, xname] 
+  y_col <- data[, yname]
+
+  data.left <- data
+
+  if (left.n > 0) {
+    data.left <- data |> 
+      head(left.n)
+  }
+
+  data.left |>
+    data.plot(title = title,
+              xname = xname,
+              yname = yname,
+              xlabel = xlabel,
+              ylabel = ylabel,
+              line_col = line_col,
+              normalize = normalize)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L481) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L435) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L481) script on _GitHub_.
+:::
+:::
+
+#### [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L536) Function {#func.data.plot.left_detailed}
+\
+
+Plots two graphs, placing them vertically one above the other: the first one at the top is the *main graph* plotted by the internally called auxiliary function [data.plot](#func.data.plot) (described above in this section) based on the data passed in the [data](#func.data.plot.left_detailed.args.data) argument, and the second one is the left part of the *main graph*, based on the first $n$ rows of the data used for the *main graph*, and plotted on an *enlarged scale* (the $n$ value is passed in the [left.n](#func.data.plot.left.n.args.left.n) argument).
+
+::: {.noteblock data-latex=""}
+The dataset passed in the [data](#func.data.plot.left.n.args.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.args.xname) parameter).
+:::
+
+::: { #func.data.plot.left_detailed.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+  data.plot.left_detailed(title = "Fine-tuned UMGYDE Model with `loess` parameter: `degree = 2`", 
+                             title.left = "Left Part of the Chart Above (Zoomed in)",
+                             left.n = 8,
+                             xname = "parameter.value", 
+                             yname = "RMSE", 
+                             xlabel1 = "spans", 
+                             ylabel1 = "RMSE")
 ```
@@
 ::: { #func.data.plot.left_detailed.args.xlabel1 .sidebar }
-  - *xlabel1 = NULL*:** The $x$ axis label for the first plot. If `NULL`, the value of the `xname` parameter is used for the label.
+  - **xlabel1:** (Character string, `NULL` by default) The $x$ axis label for the first plot. If `NULL`, the value of the `xname` parameter is used for the label.
 
@@
 ::: { #func.data.plot.left_detailed.args.xlabel2 .sidebar }
-  - *xlabel2 = NULL*:** The $x$ axis label for the second plot. If `NULL`, the value of the `xname` parameter is used for the label.
+  - **xlabel2:** (Character string, `NULL` by default) The $x$ axis label for the second plot. If `NULL`, the value of the `xname` parameter is used for the label.
 
@@
 ::: { #func.data.plot.left_detailed.args.ylabel1 .sidebar }
-  - **ylabel1 = NULL:** The $y$ axis label for the first plot. If `NULL`, the value of the `yname` parameter is used for the label.
+  - **ylabel1:** (Character string, `NULL` by default) The $y$ axis label for the first plot. If `NULL`, the value of the `yname` parameter is used for the label.
 
@@
 ::: { #func.data.plot.left_detailed.args.ylabel2 .sidebar }
-  - **ylabel2 = NULL:** The $y$ axis label for the second plot. If `NULL`, the value of the `yname` parameter is used for the label.
+  - **ylabel2:** (Character string, `NULL` by default) The $y$ axis label for the second plot. If `NULL`, the value of the `yname` parameter is used for the label.
 
@@
 ::: { #func.data.plot.left_detailed.args.line_col .sidebar }
-  - **line_col = blue:** The line color.
+  - **line_col1** (Character string, \textcolor{blue}{blue} by default) The line color (main graqh).
+
+:::
+::: { #func.data.plot.left_detailed.args.line_col .sidebar }
+  - **line_col2** (Character string, \textcolor{red}{red} by default) The line color (second graph: the left part of the main graph, which is shown on an enlarged scale).
 
@@
 ::: { #func.data.plot.left_detailed.args.normalize .sidebar }
-  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
+  - **normalize:** (Boolean, `FALSE` by default) If `TRUE`, deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves. Otherwise, the $y$ values are used.
 
@@
 
-Under the hood, the function calls internally the [data.plot](#func.data.plot) and [data.plot.left.n](#func.data.plot.left.n) functions (described above) to build two graphs and combines them into a grid.
+Internally, this function calls the [data.plot](#func.data.plot) and [data.plot.left.n](#func.data.plot.left.n) functions (the both described above in this section) to build two graphs, which it then combines into a grid using [gridExtra::grid.arrange](https://www.rdocumentation.org/packages/gridExtra/versions/2.3/topics/arrangeGrob) `R` function.
 :::
@@
 
-The soure code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) function is shown below:
+The soure code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L536) function is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The source code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) script on _GitHub_.
+The source code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L536) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L435) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L536) script on _GitHub_.
 :::

### 2025-12-19 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the data visualization functions' descriptions.

@@
 ::: { #func.data.plot.args.line_col .sidebar }
-  - **line_col:** (Character string, \textcolor{blue}{blue} by default) Line color.
+  - **line_col:** (Character string, ***\textcolor{blue}{blue}*** by default) Line color.
 
@@
 ::: { #func.data.plot.left.n.args.line_col .sidebar }
-  - **line_col:** (Character string, \textcolor{red}{red} by default) Line color.
+  - **line_col:** (Character string, ***\textcolor{red}{red}*** by default) Line color.
 
@@
 ::: { #func.data.plot.left_detailed.args.line_col .sidebar }
-  - **line_col1** (Character string, \textcolor{blue}{blue} by default) The line color (main graqh).
+  - **line_col1** (Character string, ***\textcolor{blue}{blue}*** by default) The line color (main graqh).
 
@@
 ::: { #func.data.plot.left_detailed.args.line_col .sidebar }
-  - **line_col2** (Character string, \textcolor{red}{red} by default) The line color (second graph: the left part of the main graph, which is shown on an enlarged scale).
+  - **line_col2** (Character string, ***\textcolor{red}{red}*** by default) The line color (second graph: the left part of the main graph, which is shown on an enlarged scale).
 

### 2025-12-20 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report sectioin described: UMGYDE Model Tuning: Re-training with the Best `degree` & `span` Parameters.

@@
 
-Below is the visual representation of the UMGYD Effect data we have just computed:
+Below is the visual representation of the *Smoothed Day Effect* data we have just computed:
 
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section are available in the [UMGYDE Tuned Model: Retraining with the best params](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#2169) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2169) script on _GitHub_.
+The complete version of the source code provided in this section are available in the [UMGYDE Tuned Model: Retraining with the best params](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1900) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1900) script on _GitHub_.
 :::
 
-Now, we can calculate the _Regularized UMGYDE Effect_ by retraining our model on the entire `edx` dataset with the best values of the `degree` and `span` parameters we figured out above, for the definitive _Root Mean Squared Error_ calculation and use in subsequent processing.
+Now, we can refine our *User+Movie+Genre+Year+SmoothedDay Effect Model* by retraining on the entire `edx` dataset with the best values of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters `degree` and `span` we just figured out (let's call it *Tuned UMGYDE Best Model*), for the definitive _RMSE_ calculation and use in subsequent models:
 
-The most significant part of the code that performs this operation is shown below:
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1913) performs this operation:
 ```{r, eval=FALSE}
+# The Best Parameters and RMSE Value 
 lss.best_results <- data.frame(degree = degree, 
@@
 ::: {.noteblock data-latex=""}
-Here we use the helper function [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) described above in the [UMGYDE Model: Helper Functions] section.
+In the code snippet above we use the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described in the *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::
 
-Let's now visualize final Smoothed Day effect we have obtained:
+Let's now visualize the final *Smoothed Day Effect* we have just obtained:
 ```{r}
@@
 ::: {.noteblock data-latex=""}
-It should be noted, however, that the graph above is not as smooth as before, although the data now provides better results.
+It should be noted, however, that the graph above is not as smooth as when training the model with default [loess] parameters (`degree` and `span`), although we have now obtained a better (*RMSE*) result.
 :::
 
-We calculate the _Root Mean Squared Error_ for the ultimately computed _UMGYDE Effect_ using the helper function [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above in the [UMGYDE Model: Helper Functions] section above as follows:
+Now, we are ready to calculate the *RMSE* for the ultimately *Tuned UMGYDE Best Model* and add the definitive result to our *Result Table*:
 ```{r, eval=FALSE}
 lss.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(lss.UMGYD_effect)
-```
 
-Finally, we add the definitive result for the current model to our _Result Table_:
-```{r, eval=FALSE}
 RMSEs.ResultTibble.UMGYDE.tuned <- RMSEs.ResultTibble.UMGYDE2 |> 
@@
 ::: {.noteblock data-latex=""}
-Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
+In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+
+  - [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) (described in the *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYDE Model*;
+
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
 :::
 
-Finally, let's regularize our tuned model as we did with the previous ones.
+Finally, let's *regularize* the tuned *UMGYDE Model* as we did above with the previous models.
 

### 2025-12-21 reports/capstone-movielens.site/02.5.UME-model.Rmd
Fix for the `XXXX Model Regularization: Fine-tuning` sections of the report.

@@
 
+#### UME Model Regularization: Mathematical Description
+\
+
 [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_ explains why and how we should use _Penalized least squares_ to improve our predictions.
@@
 
-  1. **Pre-configuration:** Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples;
+  1.
+**Pre-configuration:** Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
 
@@
 
-Below we provide the most significant part of the code that performs this operation:
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L571) performs this operation:
 ```{r, eval=FALSE}
 lambdas <- seq(0, 1, 0.1)
-
 cv.UME.preset.result <- 
@@
 
-We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
+We are now ready to perform the *fine-tuning step* of our model _regularization_ process to determine the best value for the $\lambda$ parameter.
 
-Below we provide the most significant part of the code that performs this operation:
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L608) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
 ```{r, eval=FALSE}
@@
 ```
+```{r}
+UM_effect.loop_starter
+```
 
@@
 
-```{r}
-UM_effect.loop_starter
-UME.rglr.fine_tune.cache.path
-```
+And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L617) below accomplishes the task of *fine-tuning* the model:
 ```{r, eval=FALSE}
@@
 
+Below are the results of fine-tuning the *UMGYE Model*:
+
+```{r, echo=FALSE}
+writeLines("*** Path to the cache directory for intermediate fine-tuning results ***")
+```
+```{r}
+UME.rglr.fine_tune.cache.path
+```
 ```{r, echo=FALSE}

### 2025-12-21 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Fix for the `XXXX Model Regularization: Fine-tuning` sections of the report.

@@
 
+#### UMGE Model Regularization: Mathematical Description
+\
+
 We have already explained the idea of the _Linear Model Regularization_ in the [UME Model Regularization] section above. Let's extend the concept outlined there to our current model.
@@
 
-Below we provide the most significant part of the code that performs this operation:
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L978) performs this operation:
 ```{r, eval=FALSE}
 lambdas <- seq(0, 0.2, 0.01)
-
 cv.UMGE.preset.result <- 
@@
 
-Below we provide the most significant part of the code that performs this operation:
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1020) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
 ```{r, eval=FALSE}
@@
 ```
+```{r}
+UMG_effect.loop_starter
+```
 
@@
 
-```{r}
-UMG_effect.loop_starter
-UMGE.rglr.fine_tune.cache.path
-```
+And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1029) below accomplishes the task of *fine-tuning* the model:
 ```{r, eval=FALSE}
@@
 
+Below are the results of fine-tuning the *UMGYE Model*:
+
+```{r, echo=FALSE}
+writeLines("*** Path to the cache directory for intermediate fine-tuning results ***")
+```
+```{r}
+UMGE.rglr.fine_tune.cache.path
+```
 ```{r, echo=FALSE}

### 2025-12-21 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Fix for the `XXXX Model Regularization: Fine-tuning` sections of the report.

@@
 
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1210) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1210) script.
+:::
+
+#### UMGYE Model Regularization: Mathematical Description
+\
+
 We have already explained the idea of _Linear Model Regularization_ in the [UME Model Regularization] section above.
@@
 
-And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
+And the formula \@ref(eq:GE-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
 
@@
 
-  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the *K-Fold Cross Validation* samples (in *this Project* we use $K = 5$);
+  1.
+**Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the *K-Fold Cross Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
 
@@
 
-Below we provide the most significant part of the code that performs this operation:
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1241) performs this operation:
 ```{r, eval=FALSE}
@@
 
-Now, let's visualize the results of the $\lambda$ range preconfiguration:
+Now, let's visualize the results of the $\lambda$ range pre-configuration:
 ``` {r}
@@
 
-Below we provide the most significant part of the code that performs this operation:
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1282) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
 ```{r, eval=FALSE}
@@
 ```
+```{r}
+UMGYE.loop_starter
+```
 
@@
 
-```{r}
-UMGYE.loop_starter
-UMGYE.rglr.fine_tune.cache.path
-```
+And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1291) below accomplishes the task of *fine-tuning* the model:
 ```{r, eval=FALSE}
@@
 
+Below are the results of fine-tuning the *UMGYE Model*:
+
+```{r, echo=FALSE}
+writeLines("*** Path to the cache directory for intermediate fine-tuning results ***")
+```
+```{r}
+UMGYE.rglr.fine_tune.cache.path
+```
 ```{r, echo=FALSE}

### 2025-12-21 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd

@@
 
-Below is the [lines of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1578) that determines the optimal range of `span` for the further model tuning when `degree = 0`:
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1578) determines the optimal range of `span` for the further model tuning when `degree = 0`:
 ```{r, eval=FALSE}
@@
 
+::: {.noteblock data-latex=""}
+The complete version of the source code provided in this section can be found in the [UMGYDE Model Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1239) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1239) script.
+:::
+
 #### UMGYDE Model Regularization: Mathematical Description
@@
 We have already explained the idea of _Linear Model Regularization_ in the [UME Model Regularization] section above.
-We have also seen how the formula \@ref(eq:ME-penalty) for adding a penalty to the _UME Model_ is transformed into the formula \@ref(eq:GE-penalty) for the _UMGE Model_ and then into the formula \@ref(eq:GYE-penalty) for the _UMGYDE Model_.
+We have also seen how the formula \@ref(eq:ME-penalty) for adding a penalty to the _UME Model_ is transformed into the formula \@ref(eq:GE-penalty) for the _UMGE Model_ and then into the formula \@ref(eq:YE-penalty) for the _UMGYE Model_.
 For the current model, this formula takes the form:
@@
 
-And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
+And the formula \@ref(eq:YE-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
 
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code shown in this section is available in the [UMGYDE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2322) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2322) script on _GitHub_.
+The complete version of the source code shown in this section is available in the [UMGYDE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2053) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2053) script on _GitHub_.
 :::
 
-Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:
+As for previous models, we will use the function [tune.model_param](#func.tune.model_param) passing in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument the model-specific helper function (this time designed for the *UMGYDE Model*): [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv).
 
-We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A](#appndx_a), passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.
+::: {.noteblock data-latex=""}
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
+:::
 
-Below we provide the most significant part of the code that performs this operation:
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2070) performs this operation:
 ```{r, eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A](#appndx_a), which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code shown in this section can be found in the [UMGYDE Model Regularization: Fine-tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2378) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2378) script on _GitHub_.
+The complete version of the source code shown in this section can be found in the [UMGYDE Model Regularization: Fine-tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2109) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2109) script on _GitHub_.
 :::
@@
 
-Below we provide the most significant part of the code that performs this operation:
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2110) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
 ```{r, eval=FALSE}
@@
                         8)
+```
+```{r}
+UMGYDE.loop_starter
+```
 
+::: {.noteblock data-latex=""}
+The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
+:::
+
+And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2120) below accomplishes the task of *fine-tuning* the model:
+```{r, eval=FALSE}
 cache.base_name <- "UMGYDE.rglr.fine-tuning"
@@
                          regularize.test_lambda.UMGYD_effect.cv)
+
+UMGYDE.rglr.fine_tune.RMSE.best <- UMGYDE.rglr.fine_tune.results$best_result["best_RMSE"]
+```
+
+::: {.noteblock data-latex=""}
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
+:::
+
+\newpage
+
+Below are the results of fine-tuning the *UMGYDE Model*:
+
+```{r, echo=FALSE}
+writeLines("*** Path to the cache directory for intermediate fine-tuning results ***")
+```
+```{r}
+UMGYDE.rglr.fine_tune.cache.path
+```
+```{r, echo=FALSE}
+writeLines("*** Fine-tuning results object data structure ***")
 ```
@@
 str(UMGYDE.rglr.fine_tune.results)
+```
+```{r, echo=FALSE}
+writeLines("*** Fine-tuning: best results ***")
+```
+```{r}
 UMGYDE.rglr.fine_tune.results$best_result
+UMGYDE.rglr.fine_tune.RMSE.best
 ```
-
-::: {.noteblock data-latex=""}
-Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A](#appndx_a) to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
-:::
-
 \newpage
@@
 ::: {.noteblock data-latex=""}
-We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A](#appndx_a), which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
+Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a)) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves.
 :::

### 2025-12-21 reports/capstone-movielens.site/work/draft-snippert.Rmd

@@
 Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method.
-We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions]).
+We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Common Helper Functions: Regularization](#appndx_a.CHF.model_tuning_utils) section of [Appendix A: Support Functions]).
 We have already explained that in the [UME Model Regularization] section. 
@@
 
-### Regularization Functions {#appndx_a.CHF.regularization}
+### Regularization Functions {#appndx_a.CHF.model_tuning_utils}
 \
@@
 
-### Regularization Functions2 {#appndx_a.CHF.regularization2}
+### Regularization Functions2 {#appndx_a.CHF.model_tuning_utils2}
 \

### 2025-12-21 reports/capstone-movielens.site/work/tmp/func_tmp.Rmd

--- 2025-12-16 reports/capstone-movielens.site/05.appendix.Rmd
@@
-# Appendix A: Support Functions {#appndx_a}
-## Common Helper Functions
-### Logging Functions {#appndx_a.CHF.logging-funcs}
-
-::: {.noteblock data-latex=""}
-The full source code of the functions described in this section is available in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R) script on _GitHub_.
-:::
-
-#### [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) Function {#func.open_logfile}
-\
-
-A function to initialize the log file.
-
-::: { #func.open_logfile.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-open_logfile(file_name)
-```
-:::
-
-::: { #func.open_logfile.args .sidebar }
-##### Arguments
-\
-
-::: { #func.open_logfile.args.file_name .sidebar }
-  - **file_name:** A name used as a base to generate a unique log file name;
-
-:::
-:::
-
-::: { #func.open_logfile.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the [logr::log_open](https://www.rdocumentation.org/packages/logr/versions/1.3.9/topics/log_open) function.
-It also calls internally the following functions to generate a unique file name based on the [file_name](#func.open_logfile.args.file_name) argument and _system time_:
-
-  - [Sys.time](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/Sys.time);
-
-  - [stringr::str_replace](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace);
-
-  - [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace)
-
-For more information on the _inner functions_ listed above, see the [R Documentation](https://www.rdocumentation.org/).
-
-:::
-
-::: { #func.open_logfile.value .sidebar }
-##### Value
-\
-
-The path of the log.
-
-:::
-
-::: { #func.open_logfile.code .sidebar }
-##### Source Code
-\
-
-The source code of the [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) function is shown below:
-```{r eval=FALSE}
-library(logr)
-library(stringr)
-
-open_logfile <- function(file_name){
-  log_file_name <- as.character(Sys.time()) |> 
-    str_replace_all(':', '_') |> 
-    str_replace(' ', 'T') |>
-    str_c(file_name)
-
-  log_open(file_name = log_file_name)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [open_logfile](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L3) script on _GitHub_.
-:::
-:::
-
-#### [print_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) Function {#func.print_start_date}
-\
-
-Prints the system date and time at the time the function is called and returns the system's idea of the current date and time.
-
-::: { #func.print_start_date.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-print_start_date()
-```
-:::
-
-::: { #func.print_start_date.details .sidebar }
-##### Details
-\
-
-This function internally calls [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print), [base::date](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/date), and [base::Sys.time](https://www.rdocumentation.org/link/Sys.time?package=base&version=3.6.2) `R` functions.
-
-It first prints the value returned by the `date` function, then returns the object returned by the `Sys.time` function.
-:::
-
-::: { #func.print_start_date.value .sidebar }
-##### Value
-\
-
-An object of class `POSIXct` (see [DateTimeClasses](https://www.rdocumentation.org/link/DateTimeClasses?package=base&version=3.6.2)).
-
-:::
-
-::: { #func.print_start_date.code .sidebar }
-##### Source Code
-\
-
-The source code of the [print_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) function is shown below:
-```{r eval=FALSE}
-print_start_date <- function(){
-  print(date())
-  Sys.time()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [print_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) script on _GitHub_.
-:::
-:::
-
-#### [put_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) Function {#func.put_start_date}
-\
-
-Outputs the system date and time to the currently opened log (using the [open_logfile](#func.open_logfile) function described above) at the time the function is called and returns the system's idea of the current date and time.
-
-::: { #func.put_start_date.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-put_start_date()
-```
-:::
-
-::: { #func.put_start_date.details .sidebar }
-##### Details
-\
-
-This function internally calls [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print), [base::date](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/date), and [base::Sys.time](https://www.rdocumentation.org/link/Sys.time?package=base&version=3.6.2) `R` functions.
-
-It first outputs the value returned by the `date` function to the currently opened log, then returns the object returned by the `Sys.time` function.
-:::
-
-::: { #func.put_start_date.value .sidebar }
-##### Value
-\
-
-An object of class `POSIXct` (see [DateTimeClasses](https://www.rdocumentation.org/link/DateTimeClasses?package=base&version=3.6.2)).
-
-:::
-
-::: { #func.put_start_date.code .sidebar }
-##### Source Code
-\
-
-The source code of the [put_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) function is shown below:
-```{r eval=FALSE}
-put_start_date <- function(){
-  put(date())
-  Sys.time()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [put_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) script on _GitHub_.
-:::
-:::
-
-#### [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) Function {#func.print_end_date}
-\
-
-Prints the system date and time at the time the function is called, and then the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
-
-::: { #func.print_end_date.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-print_end_date(start)
-```
-:::
-
-::: { #func.print_end_date.args .sidebar }
-##### Arguments
-\
-
-::: { #func.print_end_date.args.start .sidebar }
-  - **start:** An object of class `POSIXct` representing the value of the moment from which time is measured.
-
-:::
-:::
-
-::: { #func.print_end_date.details .sidebar }
-##### Details
-\
-
-This function internally calls [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print), [base::date](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/date), and [base::Sys.time](https://www.rdocumentation.org/link/Sys.time?package=base&version=3.6.2) `R` functions.
-
-It first prints the value returned by the `date` function, then builds an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument, prints the object, and, finally, returns the object to the client code.
-
-:::
-
-::: { #func.print_end_date.value .sidebar }
-##### Value
-\
-
-An object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
-
-:::
-
-::: { #func.print_end_date.code .sidebar }
-##### Source Code
-\
-
-The source code of the [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is shown below:
-```{r eval=FALSE}
-print_end_date <- function(start){
-  print(date())
-  print(Sys.time() - start)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) script on _GitHub_.
-:::
-:::
-
-#### [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L23) Function {#func.put_end_date}
-\
-
-Outputs the system date and time to the currently open log (using the [open_logfile](#func.open_logfile) function described above).
-
-The first value in the output is the system date and time at the time the function is called, and the second value is the time elapsed since the date and time specified by the [start](#func.put_end_date.args.start) argument.
-
-::: { #func.put_end_date.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-put_end_date(start)
-```
-:::
-
-::: { #func.put_end_date.args .sidebar }
-##### Arguments
-\
-
-::: { #func.put_end_date.args.start .sidebar }
-  - **start:** An object of class `POSIXct` representing the value of the moment from which time is measured.
-
-:::
-:::
-
-::: { #func.put_end_date.details .sidebar }
-##### Details
-\
-
-This function works similarly to the [print_end_date](#func.print_end_date) function described above, but unlike the latter, it outputs the information to the currently open log file.
-
-:::
-
-::: { #func.put_end_date.value .sidebar }
-##### Value
-\
-
-An object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.put_end_date.args.start) argument.
-
-:::
-
-::: { #func.put_end_date.code .sidebar }
-##### Source Code
-\
-
-The source code of the [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L23) function is shown below:
-```{r eval=FALSE}
-put_end_date <- function(start){
-  put(date())
-  put(Sys.time() - start)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [put_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L23) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L23) script on _GitHub_.
-:::
-:::
-
-#### [print_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L28) Function {#func.print_log}
-\
-
-Prints a multiline string specified by the [msg](#func.print_log.args.msg) argument.
-
-::: { #func.print_log.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-print_log(msg)
-```
-:::
-
-::: { #func.print_log.args .sidebar }
-##### Arguments
-\
-
-::: { #func.print_log.args.msg .sidebar }
-  - **msg:** A string to print (can be multiline).
-
-:::
-:::
-
-::: { #func.print_log.details .sidebar }
-##### Details
-\
-
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` functions to print the (possibly multiline) string specified by the [msg](#func.print_log.args.msg) argument.
-
-:::
-
-::: { #func.print_log.value .sidebar }
-##### Value
-\
-
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html)
-
-:::
-
-::: { #func.print_log.code .sidebar }
-##### Source Code
-\
-
-The source code of the [print_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L28) function is shown below:
-```{r eval=FALSE}
-print_log <- function(msg){
-  print(str_glue(msg))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [print_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L28) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L28) script on _GitHub_.
-:::
-:::
-
-#### [put_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L31) Function {#func.put_log}
-\
-
-Outputs a multiline string specified by the [msg](#func.put_log.args.msg) argument to the currently opened log (using the [open_logfile](#func.open_logfile) function described above).
-
-::: { #func.put_log.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-put_log(msg)
-```
-:::
-
-::: { #func.put_log.args .sidebar }
-##### Arguments
-\
-
-::: { #func.put_log.args.msg .sidebar }
-  - **msg:** A string to print (can be multiline).
-
-:::
-:::
-
-::: { #func.put_log.details .sidebar }
-##### Details
-\
-
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` functions to output the (possibly multiline) string specified by the [msg](#func.put_log.args.msg) argument.
-
-The function works similarly to the [print_log](#func.print_log) function described above, but unlike the latter, it outputs the information to the currently open log file.
-
-:::
-
-::: { #func.put_log.value .sidebar }
-##### Value
-\
-
-A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html)
-
-:::
-
-::: { #func.put_log.code .sidebar }
-##### Source Code
-\
-
-The source code of the [put_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L31) function is shown below:
-```{r eval=FALSE}
-put_log <- function(msg){
-  put(str_glue(msg))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [put_log](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L31) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L31) script on _GitHub_.
-:::
-:::
-
-#### [get_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L35) Function {#func.get_log1}
-\
-
-Creates a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument, using the value specified by the [arg1](#func.get_log1.args.arg1) argument to replace all the occurrences of the pattern `%1` found in the template.
-
-::: { #func.get_log1.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-get_log1(msg_template, arg1)
-```
-:::
-
-::: { #func.get_log1.args .sidebar }
-##### Arguments
-\
-
-::: { #func.get_log1.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of the pattern `%1` to be replaced by the value specified by the [arg1](#func.get_log1.args.arg1) argument.
-
-:::
-
-::: { #func.get_log1.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the pattern `%1` in the message template passed in the [msg_template](#func.get_log1.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.get_log1.details .sidebar }
-##### Details
-\
-
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument, using the value specified by the [arg1](#func.get_log1.args.arg1)  argument to replace all the occurrences of the pattern `%1` found in the template.
-
-:::
-
-::: { #func.get_log1.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) function, created from the character vector returned by the (also internally called) function [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
-
-:::
-
-::: { #func.get_log1.code .sidebar }
-##### Source Code
-\
-
-The source code of the [get_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L35) function is shown below:
-```{r eval=FALSE}
-get_log1 <- function(msg_template, arg1) {
-  str_glue(str_replace_all(msg_template, "%1", as.character(arg1)))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L35) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L35) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [print_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L38) Function {#func.print_log1}
-\
-
-Prints a log created from the template passed in the [msg_template](#func.print_log1.args.msg_template) argument, using the value specified by the [arg1](#func.print_log1.args.arg1) argument to replace all the occurrences of the pattern `%1` found in the template.
-
-::: { #func.print_log1.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-print_log1(msg_template, arg1)
-```
-:::
-
-::: { #func.print_log1.args .sidebar }
-##### Arguments
-\
-
-::: { #func.print_log1.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of the pattern `%1` to be replaced by the value specified by the [arg1](#func.print_log1.args.arg1) argument.
-
-:::
-
-::: { #func.print_log1.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the pattern `%1` in the message template passed in the [msg_template](#func.print_log1.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.print_log1.details .sidebar }
-##### Details
-\
-
-This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the object returned by the [get_log1](#func.get_log1) function (also called internally) described above.
-
-:::
-
-::: { #func.print_log1.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called function [get_log1](#func.get_log1) described above.
-:::
-
-::: { #func.print_log1.code .sidebar }
-##### Source Code
-\
-
-The source code of the [print_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L38) function is shown below:
-```{r eval=FALSE}
-print_log1 <- function(msg_template, arg1){
-  print(get_log1(msg_template, arg1))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [print_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L38) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L38) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [put_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) Function {#func.put_log1}
-\
-
-Outputs a log to the currently open log file (using the [open_logfile](#func.open_logfile) function described above), created from the template passed in the [msg_template](#func.put_log1.args.msg_template) argument, using the value specified by the [arg1](#func.put_log1.args.arg1) argument to replace all the occurrences of the pattern `%1` found in the template.
-
-::: { #func.put_log1.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-put_log1(msg_template, arg1)
-```
-:::
-
-::: { #func.put_log1.args .sidebar }
-##### Arguments
-\
-
-::: { #func.put_log1.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of the pattern `%1` to be replaced by the value specified by the [arg1](#func.put_log1.args.arg1) argument.
-
-:::
-
-::: { #func.put_log1.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the pattern `%1` in the message template passed in the [msg_template](#func.put_log1.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.put_log1.details .sidebar }
-##### Details
-\
-
-This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log1](#func.get_log1) function described above.
-
-The function works similarly to the [print_log1](#func.print_log1) function described above, but unlike the latter, it outputs the information to the currently open log file.
-
-:::
-
-::: { #func.put_log1.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called function [get_log1](#func.get_log1) described above.
-
-:::
-
-::: { #func.put_log1.code .sidebar }
-##### Source Code
-\
-
-The source code of the [put_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) function is shown below:
-```{r eval=FALSE}
-put_log1 <- function(msg_template, arg1){
-  put(get_log1(msg_template, arg1))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [put_log1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L41) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [get_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) Function {#func.get_log2}
-\
-
-Creates a character vector from the template passed in the [msg_template](#func.get_log2.args.msg_template) argument, using the values specified by the [arg1](#func.get_log2.args.arg1) and [arg2](#func.get_log2.args.arg2) arguments to replace all the occurrences of the placeholders `%1` and `%2`, respectively, found in the template.
-
-::: { #func.get_log2.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-get_log2(msg_template, arg1, arg2)
-```
-:::
-
-::: { #func.get_log2.args .sidebar }
-##### Arguments
-\
-
-::: { #func.get_log2.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.get_log2.args.arg1) and  [arg2](#func.get_log2.args.arg2) arguments, respectively.
-
-:::
-
-::: { #func.get_log2.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.get_log2.args.msg_template) argument.
-
-:::
-
-::: { #func.get_log2.args.arg2 .sidebar }
-  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.get_log2.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.get_log2.details .sidebar }
-##### Details
-\
-
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log2.args.msg_template) argument, using the values specified by the [arg1](#func.get_log2.args.arg1) and [arg2](#func.get_log2.args.arg2)  arguments to replace all the occurrences of the placeholders `%1` and `%2`, respectively, found in the template.
-
-:::
-
-::: { #func.get_log2.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) function, created from the character vector returned by the (also internally called) function [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
-
-:::
-
-::: { #func.get_log2.code .sidebar }
-##### Source Code
-\
-
-The source code of the [get_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) function is shown below:
-```{r eval=FALSE}
-get_log2 <- function(msg_template, arg1, arg2) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_glue()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L45) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [print_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) Function {#func.print_log2}
-\
-
-Prints a log created from the template passed in the [msg_template](#func.print_log2.args.msg_template) argument, using the values specified by the [arg1](#func.print_log2.args.arg1) and [arg2](#func.print_log2.args.arg2) arguments to replace all the occurrences of the placeholders `%1` and `%2`, respectively, found in the template.
-
-::: { #func.print_log2.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-print_log2(msg_template, arg1, arg2)
-```
-:::
-
-::: { #func.print_log2.args .sidebar }
-##### Arguments
-\
-
-::: { #func.print_log2.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.print_log2.args.arg1) and  [arg2](#func.print_log2.args.arg2) arguments, respectively.
-
-:::
-
-::: { #func.print_log2.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.print_log2.args.msg_template) argument.
-
-:::
-
-::: { #func.print_log2.args.arg2 .sidebar }
-  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.print_log2.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.print_log2.details .sidebar }
-##### Details
-\
-
-This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the object returned by the [get_log2](#func.get_log2) function (also called internally) described above.
-
-:::
-
-::: { #func.print_log2.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called function [get_log2](#func.get_log2) described above.
-
-:::
-
-::: { #func.print_log2.code .sidebar }
-##### Source Code
-\
-
-The source code of the [print_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) function is shown below:
-```{r eval=FALSE}
-print_log2 <- function(msg_template, arg1, arg2){
-  print(get_log2(msg_template, arg1, arg2))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [print_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L51) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [put_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) Function {#func.put_log2}
-\
-
-Outputs a log to the currently open log file (using the [open_logfile](#func.open_logfile) function described above), created from the template passed in the [msg_template](#func.put_log2.args.msg_template) argument, using the values specified by the [arg1](#func.put_log2.args.arg1) and [arg2](#func.put_log2.args.arg2) arguments to replace all the occurrences of the placeholders `%1` and `%2`, respectively, found in the template.
-
-::: { #func.put_log2.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-put_log2(msg_template, arg1, arg2)
-```
-:::
-
-::: { #func.put_log2.args .sidebar }
-##### Arguments
-\
-
-::: { #func.put_log2.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1` and `%2`, to be replaced by the values specified by the [arg1](#func.put_log2.args.arg1) and  [arg2](#func.put_log2.args.arg2) arguments, respectively.
-
-:::
-
-::: { #func.put_log2.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.put_log2.args.msg_template) argument.
-
-:::
-
-::: { #func.put_log2.args.arg2 .sidebar }
-  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.put_log2.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.put_log2.details .sidebar }
-##### Details
-\
-
-This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log2](#func.get_log2) function described above.
-
-The function works similarly to the [print_log2](#func.print_log2) function described above, but unlike the latter, it outputs the information to the currently open log file.
-
-:::
-
-::: { #func.put_log2.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called function [get_log2](#func.get_log2) described above.
-:::
-
-::: { #func.put_log2.code .sidebar }
-##### Source Code
-\
-
-The source code of the [put_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) function is shown below:
-```{r eval=FALSE}
-put_log2 <- function(msg_template, arg1, arg2){
-  put(get_log2(msg_template, arg1, arg2))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [put_log2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L54) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [get_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) Function {#func.get_log3}
-\
-
-Creates a character vector from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument, using the values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3) arguments to replace all the occurrences of the placeholders `%1`, `%2`, and `%3`, respectively, found in the template.
-
-::: { #func.get_log3.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-get_log3(msg_template, arg1, arg2, arg3)
-```
-:::
-
-::: { #func.get_log3.args .sidebar }
-##### Arguments
-\
-
-::: { #func.get_log3.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.get_log3.args.arg1),  [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3) arguments, respectively.
-
-:::
-
-::: { #func.get_log3.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.get_log3.args.msg_template) argument.
-
-:::
-
-::: { #func.get_log3.args.arg2 .sidebar }
-  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.get_log3.args.msg_template) argument.
-
-:::
-
-::: { #func.get_log3.args.arg3 .sidebar }
-  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.get_log3.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.get_log3.details .sidebar }
-##### Details
-\
-
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument, using the values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3)  arguments to replace all the occurrences of the placeholders `%1`, `%2`, and `%3`, respectively, found in the template.
-
-:::
-
-::: { #func.get_log3.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) function, created from the character vector returned by the (also internally called) function [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
-
-:::
-
-::: { #func.get_log3.code .sidebar }
-##### Source Code
-\
-
-The source code of the [get_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) function is shown below:
-```{r eval=FALSE}
-get_log3 <- function(msg_template, arg1, arg2, arg3) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_replace_all("%3", as.character(arg3)) |>
-    str_glue()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L58) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [print_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) Function {#func.print_log3}
-\
-
-Prints a log created from the template passed in the [msg_template](#func.print_log3.args.msg_template) argument, using the values specified by the [arg1](#func.print_log3.args.arg1), [arg2](#func.print_log3.args.arg2), and [arg3](#func.print_log3.args.arg3) arguments to replace all the occurrences of the placeholders `%1`, `%2`, and `%3`, respectively, found in the template.
-
-::: { #func.print_log3.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-print_log3(msg_template, arg1, arg2, arg3)
-```
-:::
-
-::: { #func.print_log3.args .sidebar }
-##### Arguments
-\
-
-::: { #func.print_log3.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.print_log3.args.arg1),  [arg2](#func.print_log3.args.arg2), and [arg3](#func.print_log3.args.arg3) arguments, respectively.
-
-:::
-
-::: { #func.print_log3.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.print_log3.args.msg_template) argument.
-
-:::
-
-::: { #func.print_log3.args.arg2 .sidebar }
-  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.print_log3.args.msg_template) argument.
-
-:::
-
-::: { #func.print_log3.args.arg3 .sidebar }
-  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.print_log3.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.print_log3.details .sidebar }
-##### Details
-\
-
-This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the object returned by the [get_log3](#func.get_log3) function (also called internally) described above.
-
-:::
-
-::: { #func.print_log3.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called function [get_log3](#func.get_log3) described above.
-
-:::
-
-::: { #func.print_log3.code .sidebar }
-##### Source Code
-\
-
-The source code of the [print_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) function is shown below:
-```{r eval=FALSE}
-print_log3 <- function(msg_template, arg1, arg2, arg3){
-  print(get_log3(msg_template, arg1, arg2, arg3))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [print_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L65) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [put_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) Function {#func.put_log3}
-\
-
-Outputs a log to the currently open log file (using the [open_logfile](#func.open_logfile) function described above), created from the template passed in the [msg_template](#func.put_log3.args.msg_template) argument, using the values specified by the [arg1](#func.put_log3.args.arg1), [arg2](#func.put_log3.args.arg2), and [arg3](#func.put_log3.args.arg3) arguments to replace all the occurrences of the placeholders `%1`, `%2`, and `%3`, respectively, found in the template.
-
-::: { #func.put_log3.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-put_log3(msg_template, arg1, arg2, arg3)
-```
-:::
-
-::: { #func.put_log3.args .sidebar }
-##### Arguments
-\
-
-::: { #func.put_log3.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, and `%3` to be replaced by the values specified by the [arg1](#func.put_log3.args.arg1),  [arg2](#func.put_log3.args.arg2), and [arg3](#func.put_log3.args.arg3) arguments, respectively.
-
-:::
-
-::: { #func.put_log3.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.put_log3.args.msg_template) argument.
-
-:::
-
-::: { #func.put_log3.args.arg2 .sidebar }
-  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.put_log3.args.msg_template) argument.
-
-:::
-
-::: { #func.put_log3.args.arg3 .sidebar }
-  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.put_log3.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.put_log3.details .sidebar }
-##### Details
-\
-
-This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log3](#func.get_log3) function described above.
-
-The function works similarly to the [print_log3](#func.print_log3) function described above, but unlike the latter, it outputs the information to the currently open log file.
-
-:::
-
-::: { #func.put_log3.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called function [get_log3](#func.get_log3) described above.
-
-:::
-
-::: { #func.put_log3.code .sidebar }
-##### Source Code
-\
-
-The source code of the [put_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) function is shown below:
-```{r eval=FALSE}
-put_log3 <- function(msg_template, arg1, arg2, arg3){
-  put(get_log3(msg_template, arg1, arg2, arg3))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [put_log3](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L68) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [get_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L72) Function {#func.get_log4}
-\
-
-Creates a character vector from the template passed in the [msg_template](#func.get_log4.args.msg_template) argument, using the values specified by the [arg1](#func.get_log4.args.arg1), [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3), and [arg4](#func.get_log4.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
-
-::: { #func.get_log4.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-get_log4(msg_template, arg1, arg2, arg3, arg4)
-```
-:::
-
-::: { #func.get_log4.args .sidebar }
-##### Arguments
-\
-
-::: { #func.get_log4.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, `%3`, and `%4` to be replaced by the values specified by the [arg1](#func.get_log4.args.arg1),  [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3), and [arg4](#func.get_log4.args.arg4) arguments, respectively.
-
-:::
-
-::: { #func.get_log4.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.get_log4.args.msg_template) argument.
-
-:::
-
-::: { #func.get_log4.args.arg2 .sidebar }
-  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.get_log4.args.msg_template) argument.
-
-:::
-
-::: { #func.get_log4.args.arg3 .sidebar }
-  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.get_log4.args.msg_template) argument.
-
-:::
-
-::: { #func.get_log4.args.arg4 .sidebar }
-  - **arg4:** Value to replace all occurrences of the placeholder `%4` in the message template passed in the [msg_template](#func.get_log4.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.get_log4.details .sidebar }
-##### Details
-\
-
-This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log4.args.msg_template) argument, using the values specified by the [arg1](#func.get_log4.args.arg1), [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3), and [arg4](#func.get_log4.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
-
-:::
-
-::: { #func.get_log4.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) function, created from the character vector returned by the (also internally called) function [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
-
-:::
-
-::: { #func.get_log4.code .sidebar }
-##### Source Code
-\
-
-The source code of the [get_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L72) function is shown below:
-```{r eval=FALSE}
-get_log4 <- function(msg_template, arg1, arg2, arg3, arg4) {
-  msg_template |> 
-    str_replace_all("%1", as.character(arg1)) |>
-    str_replace_all("%2", as.character(arg2)) |>
-    str_replace_all("%3", as.character(arg3)) |>
-    str_replace_all("%4", as.character(arg4)) |>
-    str_glue()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L72) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L72) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [print_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L80) Function {#func.print_log4}
-\
-
-Prints a log created from the template passed in the [msg_template](#func.print_log4.args.msg_template) argument, using the values specified by the [arg1](#func.print_log4.args.arg1), [arg2](#func.print_log4.args.arg2), [arg3](#func.print_log4.args.arg3), and [arg4](#func.print_log4.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
-
-::: { #func.print_log4.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-print_log4(msg_template, arg1, arg2, arg3, arg4)
-```
-:::
-
-::: { #func.print_log4.args .sidebar }
-##### Arguments
-\
-
-::: { #func.print_log4.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, `%3`, and `%4` to be replaced by the values specified by the [arg1](#func.print_log4.args.arg1),  [arg2](#func.print_log4.args.arg2), [arg3](#func.print_log4.args.arg3), and [arg4](#func.print_log4.args.arg4) arguments, respectively.
-
-:::
-
-::: { #func.print_log4.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.print_log4.args.msg_template) argument.
-
-:::
-
-::: { #func.print_log4.args.arg2 .sidebar }
-  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.print_log4.args.msg_template) argument.
-
-:::
-
-::: { #func.print_log4.args.arg3 .sidebar }
-  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.print_log4.args.msg_template) argument.
-
-:::
-
-::: { #func.print_log4.args.arg4 .sidebar }
-  - **arg4:** Value to replace all occurrences of the placeholder `%4` in the message template passed in the [msg_template](#func.print_log4.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.print_log4.details .sidebar }
-##### Details
-\
-
-This function internally calls the [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print) `R` function to print the object returned by the [get_log4](#func.get_log4) function (also called internally) described above.
-
-:::
-
-::: { #func.print_log4.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called function [get_log4](#func.get_log4) described above.
-
-:::
-
-::: { #func.print_log4.code .sidebar }
-##### Source Code
-\
-
-The source code of the [print_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L80) function is shown below:
-```{r eval=FALSE}
-print_log4 <- function(msg_template, arg1, arg2, arg3, arg4){
-  print(get_log4(msg_template, arg1, arg2, arg3, arg4))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [print_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L80) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L80) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [put_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L83) Function {#func.put_log4}
-\
-
-Outputs a log to the currently open log file (using the [open_logfile](#func.open_logfile) function described above), created from the template passed in the [msg_template](#func.put_log4.args.msg_template) argument, using the values specified by the [arg1](#func.put_log4.args.arg1), [arg2](#func.put_log4.args.arg2), [arg3](#func.put_log4.args.arg3), and [arg4](#func.put_log4.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
-
-::: { #func.put_log4.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-put_log4(msg_template, arg1, arg2, arg3, arg4)
-```
-:::
-
-::: { #func.put_log4.args .sidebar }
-##### Arguments
-\
-
-::: { #func.put_log4.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of each of the placeholders `%1`, `%2`, `%3`, and `%4` to be replaced by the values specified by the [arg1](#func.put_log4.args.arg1),  [arg2](#func.put_log4.args.arg2), [arg3](#func.put_log4.args.arg3), and [arg4](#func.put_log4.args.arg4) arguments, respectively.
-
-:::
-
-::: { #func.put_log4.args.arg1 .sidebar }
-  - **arg1:** Value to replace all occurrences of the placeholder `%1` in the message template passed in the [msg_template](#func.put_log4.args.msg_template) argument.
-
-:::
-
-::: { #func.put_log4.args.arg2 .sidebar }
-  - **arg2:** Value to replace all occurrences of the placeholder `%2` in the message template passed in the [msg_template](#func.put_log4.args.msg_template) argument.
-
-:::
-
-::: { #func.put_log4.args.arg3 .sidebar }
-  - **arg3:** Value to replace all occurrences of the placeholder `%3` in the message template passed in the [msg_template](#func.put_log4.args.msg_template) argument.
-
-:::
-
-::: { #func.put_log4.args.arg4 .sidebar }
-  - **arg4:** Value to replace all occurrences of the placeholder `%4` in the message template passed in the [msg_template](#func.put_log4.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.put_log4.details .sidebar }
-##### Details
-\
-
-This function internally calls the [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print) `R` function to output the log object returned by the (also called internally) [get_log4](#func.get_log4) function described above.
-
-The function works similarly to the [print_log4](#func.print_log4) function described above, but unlike the latter, it outputs the information to the currently open log file.
-
-:::
-
-::: { #func.put_log4.value .sidebar }
-##### Value
-\
-
-A glue object, returned by the internally called function [get_log4](#func.get_log4) described above.
-:::
-
-::: { #func.put_log4.code .sidebar }
-##### Source Code
-\
-
-The source code of the [put_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L83) function is shown below:
-```{r eval=FALSE}
-put_log4 <- function(msg_template, arg1, arg2, arg3, arg4){
-  put(get_log4(msg_template, arg1, arg2, arg3, arg4))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [put_log4](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L83) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L83) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### Utility Functions {#appndx_a.CHF.utility_funcs}
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) script on _GitHub_.
-:::
-
-#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) Function {#func.clamp}
-\
-
-Clamps the input value passed in [r](#func.clamp.args.r) argument between the values passed in [min](#func.clamp.args.min) and [max](#func.clamp.args.max) arguments.
-
-::: { #func.clamp.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-r_clamped <- clamp(r, min = 0.5, max = 5)
-```
-:::
-
-::: { #func.clamp.args .sidebar }
-##### Arguments
-\
-
-::: { #func.clamp.args.r .sidebar }
-  - **r:** Value to clamp;
-
-:::
-::: { #func.clamp.args.min .sidebar }
-  - **min:** Minimum allowed value (0.5 by default);
-
-:::
-:::
-::: { #func.clamp.args.max .sidebar }
-  - **max:** Maximum allowed value (5 by default);
-
-:::
-:::
-
-::: { #func.clamp.details .sidebar }
-##### Details
-\
-As explained in [Section 24.1 *Case study: recommendation systems / User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5.
-For this reason, we need a function described in that section[@IDS2_24-1]:
-
-This function is a wrapper for the [base::pmin](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/Extremes) and [base::pmax](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/Extremes) `R` functions, which are called internally to constrain the input value passed in the [r](#func.clamp.args.r) argument to be within the values passed in the [min](#func.clamp.args.min) and [max](#func.clamp.args.max) arguments, respectively.
-
-in *this Project* this function is used to clamp the computed movie rating values between 0.5 and 5.
-:::
-
-::: { #func.clamp.value .sidebar }
-##### Value
-\
-
-The value clamped between [min](#func.clamp.args.min) and [max](#func.clamp.args.max) argument values.
-
-:::
-
-::: { #func.clamp.code .sidebar }
-##### Source Code
-\
-
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) function is shown below:
-```{r eval=FALSE}
-clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) script on _GitHub_.
-:::
-:::
-
-#### [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) Function {#func.msg.set_arg}
-\
-
-Creates a character vector from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument, using the value specified by the [arg](#func.msg.set_arg.args.arg) argument to replace all the occurrences of the placeholder passed in the [arg.name](#func.msg.set_arg.args.arg.name) argument found in the template.
-
-::: { #func.msg.set_arg.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-msg.set_arg(msg_template, arg, arg.name = "%1")
-```
-:::
-
-::: { #func.msg.set_arg.args .sidebar }
-##### Arguments
-\
-
-::: { #func.msg.set_arg.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of a pattern specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument.
-
-:::
-
-::: { #func.msg.set_arg.args.arg.name .sidebar }
-  - **arg.name:** (*Optional: `%1` by default*) Substring (pattern or *placeholder*) to replace all occurrences found in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.
-
-:::
-
-::: { #func.msg.set_arg.args.arg .sidebar }
-  - **arg:** Value to replace all occurrences of the pattern specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.msg.set_arg.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` function, which is called internally to replace all occurrences of the pattern (placeholder) specified by the [arg_name](#func.msg.set_arg.args.arg.name) argument (`%1` by default), in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.
-:::
-
-::: { #func.msg.set_arg.value .sidebar }
-##### Value
-\
-
-The character vector returned by the internally called [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
-:::
-
-::: { #func.msg.set_arg.code .sidebar }
-##### Source Code
-\
-
-The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) function is shown below:
-```{r eval=FALSE}
-msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
-  msg_template |> 
-    str_replace_all(arg.name, as.character(arg))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) Function {#func.msg.glue}
-\
-
-Creates a [glue::glue](https://glue.tidyverse.org/reference/glue.html) object from the template passed in the [msg_template](#func.msg.glue.args.msg_template) argument, using the value specified by the [arg](#func.msg.glue.args.arg) argument to replace all the occurrences of the placeholder passed in the [arg.name](#func.msg.glue.args.arg.name) argument found in the template.
-
-::: { #func.msg.glue.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-msg.glue(msg_template, arg, arg, arg.name = "%1")
-```
-:::
-
-::: { #func.msg.glue.args .sidebar }
-##### Arguments
-\
-
-::: { #func.msg.glue.args.msg_template .sidebar }
-  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of a pattern specified by the [arg.name](#func.msg.glue.args.arg.name) argument.
-
-:::
-
-::: { #func.msg.glue.args.arg.name .sidebar }
-  - **arg.name:** (*Optional: `%1` by default*) Substring (pattern or *placeholder*) to replace all occurrences found in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument with the value specified in the [arg](#func.msg.glue.args.arg) argument.
-
-:::
-
-::: { #func.msg.glue.args.arg .sidebar }
-  - **arg:** Value to replace all occurrences of the pattern specified by the [arg.name](#func.msg.glue.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument.
-
-:::
-:::
-
-::: { #func.msg.glue.details .sidebar }
-##### Details
-\
-
-This function internally calls the [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) `R` function to format the character vector returned by the (also called internally) [msg.set_arg](#func.msg.set_arg) function described above.
-
-:::
-
-::: { #func.msg.glue.value .sidebar }
-##### Value
-\
-
-A [glue::glue](https://glue.tidyverse.org/reference/glue.html) object created from the character vector returned by the internally called [msg.set_arg()](#func.msg.set_arg).
-
-:::
-
-::: { #func.msg.glue.code .sidebar }
-##### Source Code
-\
-
-The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) function is shown below:
-```{r eval=FALSE}
-msg.glue <- function(msg_template, arg, arg.name = "%1"){
-  msg_template |>
-    msg.set_arg(arg, arg.name) |>
-    str_glue()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### (Root) Mean Squared Error Calculation
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) script on _GitHub_.
-:::
-
-#### [mse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) Function {#func.mse}
-\
-
-Calculates *Mean Squared Error* of the set of *residuals* (passed in the [r](func.mse.args.r) argument) as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].
-
-::: { #func.mse.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-mse(r)
-
-```
-:::
-
-::: { #func.mse.args .sidebar }
-##### Arguments
-\
-
-::: { #func.mse.args.r .sidebar }
-  - **r:** Numeric vector representing a set of *residuals*.
-
-:::
-:::
-
-::: { #func.mse.code .sidebar }
-##### Source Code
-\
-
-The source code of the [mse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) function is shown below:
-```{r eval=FALSE}
-mse <- function(r) mean(r^2)
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [mse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L5) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) Function {#func.mse_cv}
-\
-
-Calculates the average value of the *Mean Squared Errors* calculated with the use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.mse_cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-mse_cv(r_list)
-
-```
-:::
-
-::: { #func.mse_cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.mse_cv.args.r_list .sidebar }
-  - **r_list:** A list of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case Study: Recommender Systems / Loss Function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the *Course Textbook (New Edition)*[@IDS2_24-1_LF], computed in the corresponding iteration of *K-Fold Cross-Validation* (the $K$ is $5$ for *this Project*).
-
-:::
-:::
-
-::: { #funcc.mse_cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is shown below:
-```{r eval=FALSE}
-mse_cv <- function(r_list) {
-  mses <- sapply(r_list, mse(r))
-  mean(mses)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [mse_cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L6) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [rmse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) Function {#func.rmse}
-\
-
-Calculates *Root Mean Squared Error* as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].
-
-::: { #func.rmse.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-rmse(r)
-
-```
-:::
-
-::: { #func.rmse.args .sidebar }
-##### Arguments
-\
-
-::: { #func.rmse.args.r .sidebar }
-  - **r:** Numeric vector representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].
-
-:::
-:::
-
-::: { #func.rmse.code .sidebar }
-##### Source Code
-\
-
-The source code of the [rmse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) function is shown below:
-```{r eval=FALSE}
-rmse <- function(r) sqrt(mse(r))
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [rmse](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L10) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L11) Function {#func.rmse2}
-\
-
-Calculates *Root Mean Squared Error* as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].
-
-::: { #func.rmse2.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-rmse2(true_ratings, predicted_ratings)
-
-```
-:::
-
-::: { #func.rmse2.args .sidebar }
-##### Arguments
-\
-
-::: { #func.rmse2.args.true_ratings .sidebar }
-  - **true_ratings:** Numeric vector representing a set of *actual rating* values stored in the validation dataset.
-
-:::
-
-::: { #func.rmse2.args.predicted_ratings .sidebar }
-  - **predicted_ratings:** A numeric vector representing a set of *predicted rating* values computed from the data stored in the test dataset.
-
-:::
-:::
-
-::: { #func.rmse2.code .sidebar }
-##### Source Code
-\
-
-The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L11) function is shown below:
-```{r eval=FALSE}
-rmse2 <- function(true_ratings, predicted_ratings) {
-  rmse(true_ratings - predicted_ratings)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L11) function is also available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L11) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### Result RMSEs Tibble Functions
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) script on _GitHub_.
-:::
-
-#### [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) Function {#func.CreateRMSEs_ResultTibble}
-\
-
-Creates a _RMSEs Result Tibble_ of type *data frame*.
-
-::: { #func.CreateRMSEs_ResultTibble.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSEs.ResultTibble <- CreateRMSEs_ResultTibble()
-```
-:::
-
-::: { #func.CreateRMSEs_ResultTibble.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the [tibble::tibble](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble) function, which is called internally to construct a data frame object representing the _RMSEs Result Tibble_ to store the _RMSE_ values for every model used in the project to predict movie ratings.
-
-The result data frame, which is returned to the client code, has the following columns:
-
-  - *Method* (chr);
-  - *RMSE* (num);
-  - *Comment* (chr)
-
-::: { #func.CreateRMSEs_ResultTibble.value .sidebar }
-##### Value
-\
-
-A tibble returned by the internally called [tibble::tibble()](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/tibble)
-
-:::
-
-::: { #func.CreateRMSEs_ResultTibble.code .sidebar }
-##### Source Code
-\
-
-The source code of the [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) function is shown below:
-```{r eval=FALSE}
-CreateRMSEs_ResultTibble <- function(){
-  tibble(Method = c("Project Objective"),
-         RMSE = project_objective,
-         Comment = " ")
-}
-```
-:::
-
-::: {.noteblock data-latex=""}
-The source code of the [CreateRMSEs_ResultTibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L16) script on _GitHub_.
-:::
-
-\newpage
-
-#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L21) Function {#func.RMSEs.AddRow}
-\
-
-Adds a row to the original _RMSEs Result Tibble_ passed in the [RMSEs](#func.RMSEs.AddRow.args.RMSEs) argument.
-
-::: { #func.RMSEs.AddRow.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSEs.AddRow(RMSEs, 
-             method, 
-             value, 
-             comment = "", 
-             before = NULL)
-```
-:::
-
-::: { #func.RMSEs.AddRow.args .sidebar }
-##### Arguments
-\
-
-::: { #func.RMSEs.AddRow.args.RMSEs .sidebar }
-  - ***RMSEs:*** Original _RMSEs Result Tibble_ (of type *data frame*) to modify;
-
-:::
-
-::: { #func.RMSEs.AddRow.args.method .sidebar }
-  - ***method:*** The _Method or Model_ being evaluated;
-
-:::
-
-::: { #func.RMSEs.AddRow.args.value .sidebar }
-  - ***value:*** The _Root Mean Squared Error (RMSE)_ value;
-
-:::
-
-::: { #func.RMSEs.AddRow.args.comment .sidebar }
-  - ***comment:*** Detailed information about the record or any other comment (if needed);
-
-:::
-
-::: { #func.RMSEs.AddRow.args.before .sidebar }
-  - ***before:*** One-based row index where to add the new rows, if NULL (default): after last row;
-
-:::
-:::
-
-::: { #func.RMSEs.AddRow.code.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the [tibble::add_row](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row) function, which is called internally to modify a data frame object representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.
-
-For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
-
-:::
-
-::: { #func.RMSEs.AddRow.value .sidebar }
-##### Value
-\
-
-The modified tibble returned by the internally called [tibble::add_row()](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_row).
-
-:::
-
-::: { #func.RMSEs.AddRow.code .sidebar }
-##### Source Code
-\
-
-The source code of the [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L21) function is shown below:
-```{r eval=FALSE}
-RMSEs.AddRow <- function(RMSEs, 
-                         method, 
-                         value, 
-                         comment = "", 
-                         before = NULL){
-  RMSEs |>
-    add_row(Method = method,
-            RMSE = value,
-            Comment = comment,
-            .before = before)
-}
-```
-:::
-
-::: {.noteblock data-latex=""}
-The source code of the [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L21) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L21) script on _GitHub_.
-:::
-
-\newpage
-
-#### [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) Function {#func.RMSEs.AddDiffColumn}
-\
-
-Adds a calculated column named _Diff_ to the _RMSEs Result Tibble_ (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.args.RMSEs) argument) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row.
-This is true for each row except the first, for which the value is always zero.
-
-::: { #func.RMSEs.AddDiffColumn.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSEs.ModifiedTable <- RMSEs.AddDiffColumn(RMSEs)
-```
-:::
-
-::: { #func.RMSEs.AddDiffColumn.args .sidebar }
-##### Arguments
-\
-
-::: { #func.RMSEs.AddDiffColumn.args.RMSEs .sidebar }
-  - ***RMSEs:*** _RMSEs Result Tibble_ to modify;
-
-:::
-:::
-
-::: { #func.RMSEs.AddDiffColumn.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the [tibble::add_column](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_column) function, which is called internally to modify a data frame object representing the original _RMSEs Result Tibble_.
-It also internally uses the [RMSEs.AddRow](#func.RMSEs.AddRow) function described above to perform the necessary intermediate calculations.
-
-For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
-:::
-
-::: { #func.RMSEs.AddRow.value .sidebar }
-##### Value
-\
-
-The modified tibble returned by the internally called [tibble::add_column()](https://www.rdocumentation.org/packages/tibble/versions/3.2.1/topics/add_column).
-:::
-
-::: { #func.RMSEs.AddDiffColumn.code .sidebar }
-##### Source Code
-\
-
-The source code of the [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) function is shown below:
-```{r eval=FALSE}
-RMSEs.AddDiffColumn <- function(RMSEs){
-  RMSEs.Diff <- RMSEs |>
-    RMSEs.AddRow(NULL, project_objective, before = 1) #|>
-
-  RMSEs.Diff <- RMSEs.Diff[-nrow(RMSEs.Diff),]
-
-  RMSEs |>
-  add_column(Diff = RMSEs.Diff$RMSE - RMSEs$RMSE, 
-             .before = "Comment")
-
-}
-```
-:::
-
-::: {.noteblock data-latex=""}
-The source code of the [RMSEs.AddDiffColumn](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) script on _GitHub_.
-:::
-
-#### [RSME.tibble.col_width](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) Function {#func.RSME.tibble.col_width}
-\
-
-Converts the _RMSEs Result Tibble_ column width value passed in argument [x](#func.RSME.tibble.col_width.args.x) to a character string compatible for use as the `width` argument value to pass to the [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) function.
-
-::: { #func.RSME.tibble.col_width.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-width_em <- RSME.tibble.col_width(x)
-```
-:::
-
-::: { #func.RSME.tibble.col_width.args .sidebar }
-##### Arguments
-\
-
-::: { #func.RSME.tibble.col_width.args.x .sidebar }
-  - ***x:*** (Numeric) Column width value to be formatted;
-
-:::
-:::
-
-::: { #func.RSME.tibble.col_width.details .sidebar }
-##### Details
-\
-
-This is a utility function, a wrapper for the [msg.glue](#func.msg.glue) function described above, which is called internally to format the value passed in argument [x](#func.RSME.tibble.col_width.args.x) for subsequent passing to the function [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) as a value of the `width` argument.
-:::
-
-::: { #func.RSME.tibble.col_width.value .sidebar }
-##### Value
-\
-
-A character string representing the formatted column width value.
-:::
-
-::: { #func.RSME.tibble.col_width.code .sidebar }
-##### Source Code
-\
-
-The source code of the [RSME.tibble.col_width](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) function is shown below:
-```{r eval=FALSE}
-RSME.tibble.col_width <- function(x){
-  "%1em" |> msg.glue(x)
-}
-```
-:::
-
-::: {.noteblock data-latex=""}
-The source code of the [RSME.tibble.col_width](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) script on _GitHub_.
-:::
-
-\newpage
-
-#### [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) Function {#func.RMSE_kable}
-\
-
-Prints the _RMSEs Result Tibble_.
-
-::: {.noteblock data-latex=""}
-It is assumed that the tibble has the following three columns:
-
-  1. *Method*;
-  2. *RMSE*;
-  3. *Comment*;
-
-:::
-
-::: { #func.RMSE_kable.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSE_kable(RMSEs,
-           col1width = 15,
-           col2width = 5,
-           col3width = 30)
-```
-:::
-
-::: { #func.RMSE_kable.args .sidebar }
-##### Arguments
-\
-
-::: { #func.RMSE_kable.args.RMSEs .sidebar }
-  - ***RMSEs:*** _RMSEs Result Tibble_ to print;
-
-:::
-
-::: { #func.RMSE_kable.args.col1width .sidebar }
-  - ***col1width:*** Width of the first column (15 by default);
-
-:::
-
-::: { #func.RMSE_kable.args.col2width .sidebar }
-  - ***col2width:*** Width of the second column (5 by default);
-
-:::
-
-::: { #func.RMSE_kable.args.col3width .sidebar }
-  - ***col3width:*** Width of the third column (30 by default).
-
-:::
-:::
-
-::: { #func.RMSE_kable.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the [knitr::kable](https://www.rdocumentation.org/packages/knitr/versions/1.43/topics/kable) function, which is called internally to create a table (based on the _RMSEs Result Tibble_ data), formatted for output in the project report.
-
-The [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) function, along with the [RSME.tibble.col_width](#func.RSME.tibble.col_width) function described above, are also used internally to specify the width of the table columns.
-
-For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
-:::
-
-::: { #func.RMSE_kable.value .sidebar }
-##### Value
-\
-
-The table created by the internally called [knitr::kable()](https://www.rdocumentation.org/packages/knitr/versions/1.43/topics/kable).
-
-:::
-
-::: { #func.RMSE_kable.code .sidebar }
-##### Source Code
-\
-
-The source code of the [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) function is shown below:
-```{r eval=FALSE}
-RMSE_kable <- function(RMSEs,
-                       col1width = 15,
-                       col2width = 5,
-                       col3width = 30){
-  RMSEs |>
-    kable(align='lcl', booktabs = T, padding = 5) |> 
-    row_spec(0, bold = T) |>
-    column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
-    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
-    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
-}
-```
-:::
-
-::: {.noteblock data-latex=""}
-The source code of the [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) script on _GitHub_.
-:::
-
-\newpage
-
-#### [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) Function {#func.RMSE.Total_kable}
-\
-
-Prints the _Final RMSEs Result Tibble_.
-
-::: {.noteblock data-latex=""}
-It is assumed that the tibble has the following four columns:
-
-  1. *Method*;
-  2. *RMSE*;
-  3. *Diff*;
-  4. *Comment*;
-
-:::
-
-::: { #func.RMSE.Total_kableusage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-RMSE.Total_kable(RMSEs,
-                 col1width = 15,
-                 col2width = 7,
-                 col3width = 5,
-                 col4width = 25)
-```
-:::
-
-::: { #func.RMSE.Total_kable.args .sidebar }
-##### Arguments
-\
-
-::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
-  - ***RMSEs:*** The _Final RMSEs Result Tibble_ to print;
-
-:::
-
-::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col1width:*** Width of the first column (15 by default);
-
-:::
-
-::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col2width:*** Width of the second column (7 by default);
-
-:::
-
-::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col3width:*** Width of the third column(5 by default);
-
-:::
-
-::: { #func.RMSE.Total_kable.args. .sidebar }
-  - ***col4width:*** Width of the fourth column (25 by default);
-
-:::
-:::
-
-::: { #func.RMSE.Total_kable.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the [RMSE_kable](#func.RMSE_kable) function described above, which is called internally to print the table, created from the final _RMSEs Result Tibble_ data.
-
-It is assumed that the  _Final RMSEs Result Tibble_ is previously constructed from the original _RMSEs Result Tibble_ using the [RMSEs.AddDiffColumn](#func.RMSEs.AddDiffColumn) function described above.
-
-The [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) function, along with the [RSME.tibble.col_width](#func.RSME.tibble.col_width) function described above, are also used internally to set the width of the last column of the table.
-
-For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
-:::
-
-::: { #func.RMSE.Total_kable.value .sidebar }
-##### Value
-\
-
-The table returned by the internally called [RMSE_kable()](#func.RMSE_kable).
-:::
-
-::: { #func.RMSE.Total_kable.code .sidebar }
-##### Source Code
-\
-
-The source code of the [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function is shown below:
-```{r eval=FALSE}
-RMSE.Total_kable <- function(RMSEs,
-                       col1width = 15,
-                       col2width = 7,
-                       col3width = 5, 
-                       col4width = 25){
-  RMSEs |> 
-    RMSE.Total_kable(col1width,
-               col2width,
-               col3width) |>
-    column_spec(column = 4, 
-                width = RSME.tibble.col_width(col4width)) 
-}
-```
-:::
-
-::: {.noteblock data-latex=""}
-The source code of the [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) script on _GitHub_.
-:::
-
-\newpage
-
-### Model Tuning Utils {#appndx_a.CHF.model_tuning_utils}
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section are available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) script on _GitHub_.
-:::
-
-#### [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) Function {#func.mean_reg}
-\
-
-Calculates the arithmetic mean taking into account the _regularization parameter_ $\lambda$ passed in the [lambda](#func.mean_reg.args.lambda) argument. We will call it the _penalized mean_.
-
-::: { #func.mean_reg.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-```
-
-::: {.noteblock data-latex=""}
-In the sample code snippet above, the `mean_reg` function is called internally from the [train_user_movie_effect](#func.train_user_movie_effect) function described below in section *Models Training: Support Functions /* [UME Model: Utility Functions] of *this Appendix*.
-:::
-:::
-
-::: { #func.mean_reg.args .sidebar }
-##### Arguments
-\
-
-::: { #func.mean_reg.args.vals .sidebar }
-  - **vals:** Values (usually a numeric vector) to calculate the _penalized mean_;
-
-:::
-::: { #func.mean_reg.args.lambda .sidebar }
-  - **lambda:** (0 by default) _Regularization parameter_ $\lambda$.
-
-:::
-  - **na.rm:** (`TRUE` by default) Logical value indicating whether `NA` values should be stripped before the computation proceeds.
-
-:::
-
-::: { #func.mean_reg.details .sidebar }
-##### Details
-\
-
-This function is used in the *regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) to calculate the _penalized mean_ of the values passed in the [vals](#func.mean_reg.args.vals) argument as follows:
-$$
-\mu(\lambda) = \frac{1}{\lambda + N} \sum_{i=1}^{N} x_i
-$$
-
-::: {.noteblock data-latex=""}
-This is a helper function intended for use in other helper functions that compute *penalized estimates* during the *regularization* process of the models being trained[@IDS2_24-2].
-All these functions are described below in section [Models Training: Support Functions] of *this Appendix*.
-:::
-
-When the [lambda](#func.mean_reg.args.lambda) parameter is `0` (meaning the $\lambda = 0$), the function calculates the simple arithmetic mean:
-$$
-\mu = \frac{1}{N} \sum_{i=1}^{N} x_i
-$$
-
-::: {.noteblock data-latex=""}
-If the [lambda](#func.mean_reg.args.lambda) parameter is `0` (the default), the function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean), calling with the parameter `trim = 0` (the default for the `base::mean` function).
-:::
-:::
-
-::: { #func.mean_reg.value .sidebar }
-##### Value
-\
-
-(Numeric) *Penalized mean* of the values passed in the [vals](#func.mean_reg.args.vals) argument.
-:::
-
-::: { #func.mean_reg.code .sidebar }
-##### Source Code
-\
-
-The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) function is shown below:
-```{r eval=FALSE}
-mean_reg <- function(vals, lambda = 0, na.rm = TRUE){
-  if (is.na(lambda)) {
-    stop("Function: mean_reg
-`lambda` is `NA`")
-  }
-
-  names(lambda) <- NULL
-  sums <- sum(vals, na.rm = na.rm)
-  N <- ifelse(na.rm, sum(!is.na(vals)), length(vals))
-  sums/(N + lambda)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L70) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) Function {#func.get_fine_tune.param.endpoints.idx}
-\
-
-Implements an algorithm that finds in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument the indices of the pair of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value.
-
-::: {.noteblock data-latex=""}
-The algorithm assumes that the set of values in the *RMSE* column is a monotonically non-increasing function of the index until the minimum is reached and monotonically non-decreasing thereafter.
-That is, it is assumed that the function has only one minimum on the given set.
-:::
-
-::: { #func.get_fine_tune.param.endpoints.idx.usage .sidebar }
-##### Usage
-\
-
-::: {.noteblock data-latex=""}
-The element named `tuned.result` of the *list* returned by the [tune.model_param](#func.tune.model_param) function described below is a *data frame* suitable for use as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument.
-:::
-
-The following code snippet shows how to use the data returned by the [tune.model_param](#func.tune.model_param) function as the value of the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument:
-```{r eval=FALSE}
-cv.UME.preset.result <- 
-  tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)
-
-```
-```{r}
-cv.UME.preset.result$tuned.result |>
-  data.plot(title = "UME Model Regularization: `lambda` Range Pre-configuration",
-              xname = "parameter.value",
-              yname = "RMSE",
-              xlabel = "Regularization parameter (`lambda`)",
-              ylabel = "RMSE")
-
-preset.result <- cv.UME.preset.result$tuned.result
-preset.result.idx <- get_fine_tune.param.endpoints.idx(preset.result)
-print(preset.result.idx)
-```
-
-:::
-
-::: { #func.get_fine_tune.param.endpoints.idx.args .sidebar }
-##### Arguments
-\
-
-::: {#func.get_fine_tune.param.endpoints.idx.args.preset.result .sidebar }
-  - **preset.result:** Data frame that has an *RMSE* column containing the `RMSE` values corresponding to the *regularization parameter* $\lambda$ values for the model being regularized, as described in the [Details](#func.tune.model_param.details) section of the [tune.model_param](#func.tune.model_param) function description below.
-
-:::
-:::
-
-::: { #func.get_fine_tune.param.endpoints.idx.value .sidebar }
-##### Value
-\
-
-Vector containing the index of the first element corresponding to the minimum `RMSE` value in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument, along with the indices of the pair of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value:
-```{r eval=FALSE}
-  c(start, # interval start index
-    end,   # interval end index
-    best)  # index of the best `RMSE`
-```
-
-In the example shown above in the [Usage](#func.get_fine_tune.param.endpoints.idx.usage) section we can see the value return by *this function*:
-```{r}
-str(preset.result.idx)
-print(preset.result.idx)
-```
-
-:::
-
-::: { #func.get_fine_tune.param.endpoints.idx.code .sidebar }
-##### Source Code
-\
-
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints.idx <- function(preset.result) {
-  best_RMSE <- min(preset.result$RMSE)
-  best_RMSE.idx <- which.min(preset.result$RMSE)
-  # best_lambda <- preset.result$parameter.value[best_RMSE.idx]
-
-  preset.result.N <- length(preset.result$RMSE)
-  i <- best_RMSE.idx
-  j <- i
-
-  while (i > 1) {
-    i <- i - 1
-
-    if (preset.result$RMSE[i] > best_RMSE) {
-      break
-    }
-  }
-
-  while (j < preset.result.N) {
-    j <- j + 1
-
-    if (preset.result$RMSE[j] > best_RMSE) {
-      break
-    }
-  }
-
-  c(start = i, 
-    end = j,
-    best = best_RMSE.idx)
-}
-
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_fine_tune.param.endpoints.idx](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L81) script on _GitHub_.
-:::
-:::
-
-#### [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L109) Function {#func.get_fine_tune.param.endpoints}
-\
-
-Implements an algorithm that finds in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) argument the pair of the nearest neighboring elements with values greater than the minimum to the left and right of the element (or group of elements) with the minimum value.
-
-::: {.noteblock data-latex=""}
-The algorithm assumes that the set of values in the *RMSE* column is a monotonically non-increasing function of the index until the minimum is reached and monotonically non-decreasing thereafter.
-That is, it is assumed that the function has only one minimum on the given set.
-:::
-
-::: { #func.get_fine_tune.param.endpoints.usage .sidebar }
-##### Usage
-\
-
-::: {.noteblock data-latex=""}
-The element named `tuned.result` of the *list* returned by the [tune.model_param](#func.tune.model_param) function described below is a *data frame* suitable for use as the value of the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) argument.
-:::
-
-The following code snippet shows how to use the data returned by the [tune.model_param](#func.tune.model_param) function as the value of the [preset.result](#func.get_fine_tune.param.endpoints.args.preset.result) argument:
-```{r eval=FALSE}
-cv.UME.preset.result <- 
-  tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)
-
-```
-```{r}
-cv.UME.preset.result$tuned.result |>
-  data.plot(title = "UME Model Regularization: `lambda` Range Pre-configuration",
-              xname = "parameter.value",
-              yname = "RMSE",
-              xlabel = "Regularization parameter (`lambda`)",
-              ylabel = "RMSE")
-
-preset.result <- cv.UME.preset.result$tuned.result
-fine_tune.param.endpoints <- get_fine_tune.param.endpoints(preset.result)
-print(fine_tune.param.endpoints)
-```
-
-:::
-
-::: { #func.get_fine_tune.param.endpoints.args .sidebar }
-##### Arguments
-\
-
-::: {#func.get_fine_tune.param.endpoints.args.preset.result .sidebar }
-  - **preset.result:** Data frame that has an *RMSE* column containing the `RMSE` values corresponding to the *regularization parameter* $\lambda$ values for the model being regularized, as described in the [Details](#func.tune.model_param.details) section of the [tune.model_param](#func.tune.model_param) function description below.
-
-:::
-:::
-
-::: { #func.get_fine_tune.param.endpoints.details .sidebar }
-##### Details
-\
-
-This function internally calls [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) function described above to figure out the indices of the elements, the values of which have to be determined.
-:::
-
-::: { #func.get_fine_tune.param.endpoints.value .sidebar }
-##### Value
-\
-
-Vector containing the *regularization parameter* $\lambda$ value corresponding to the first element with the minimum `RMSE` value in the *RMSE* column of the data frame passed in the [preset.result](#func.get_fine_tune.param.endpoints.idx.args.preset.result) argument, along with the pair of the $\lambda$ values corresponding to the nearest neighboring elements with values greater than the minimum `RMSE` to the left and right of the element (or group of elements) with the minimum `RMSE` value:
-
-In the example shown above in the [Usage](#func.get_fine_tune.param.endpoints.usage) section we can see the value return by *this function*:
-```{r}
-str(fine_tune.param.endpoints)
-print(fine_tune.param.endpoints)
-```
-
-:::
-
-::: { #func.get_fine_tune.param.endpoints.code .sidebar }
-##### Source Code
-\
-
-The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L109) function is shown below:
-```{r eval=FALSE}
-get_fine_tune.param.endpoints <- function(preset.result) {
-
-  preset.result.idx <- get_fine_tune.param.endpoints(preset.result)
-
-  i <- preset.result.idx["start"]
-  j <- preset.result.idx["end"]
-  best.idx <- preset.result.idx["best"]
-
-  c(start = preset.result$parameter.value[i], 
-    end = preset.result$parameter.value[j],
-    best = preset.result$parameter.value[best.idx])
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_fine_tune.param.endpoints](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L109) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L109) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) Function {#func.get_best_param.result}
-\
-
-Selects the best values from a pair of matched vectors: a vector of sorted *tuning parameter* values and a vector of corresponding *Root Mean Squared Errors (RMSE)* values passed in the [param_values](#func.tune.model_param.args.param_values) and [RMSEs](#func.get_best_param.result.args.RMSEs) arguments, respectively.
-
-::: { #func.get_best_param.result.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-        param_values.best_result <-
-          get_best_param.result(tuned.result$parameter.value,
-                                tuned.result$RMSE)
-```
-:::
-
-::: { #func.get_best_param.result.args .sidebar }
-##### Arguments
-\
-
-::: { #func.get_best_param.result.args.param_values .sidebar }
-  - **param_values:** Numeric vector containing a sorted list of the *tuning parameter* values to search for the best one during the *Model Regularization* process;
-
-:::
-::: { #func.get_best_param.result.args.RMSEs .sidebar }
-  - **RMSEs:** *RMSE* values computed during the *Model Regularization* process.
-
-:::
-:::
-
-::: { #func.get_best_param.result.details .sidebar }
-##### Details
-\
-
-This is a *utility function* used to select the *best values* during the *Model Parameter Tuning* process (including the *Model Regularization* procedure that utilizes the *penalized approach* to regularize predictions as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]).
-
-With this approach, the best value of the *tuning parameter* is considered to be the value corresponding to the minimum value of the *RMSE* for the model being tested.
-
-In *This Project*, this function is used internally in the [model.tune.param_range](#func.model.tune.param_range) function described below in this section.
-:::
-
-::: { #func.get_best_param.result.value .sidebar }
-##### Value
-\
-
-Numeric vector containing a pair of values: the best *tuning parameter* value and corresponding *minimal RMSE*. 
-:::
-
-::: { #func.get_best_param.result.code .sidebar }
-##### Source Code
-\
-
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, RMSEs){
-  best_pvalue_idx <- which.min(RMSEs)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = RMSEs[best_pvalue_idx])
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L121) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) Function {#func.tune.model_param}
-\
-
-Implements an algorithm for selecting the best value of the *tuning parameter* from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
-
-##### Signature
-\
-
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-
-# ...
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}  
-```
-
-::: { #func.tune.model_param.args .sidebar }
-##### Arguments
-\
-
-::: { #func.tune.model_param.args.param_values .sidebar }
-  - **param_values:** Numeric vector containing a sorted list of parameter values to search for the best one during the model regularization process;
-
-:::
-
-::: { #func.tune.model_param.args.fn_tune.test.param_value .sidebar }
-  - **fn_tune.test.param_value:** Model-specific helper function that validates the model by computing the model's *RMSE* value for a given parameter value;
-
-:::
-
-::: { #func.tune.model_param.args.break.if_min .sidebar }
-  - **break.if_min:** (Optional, `TRUE` by default) Boolean value that determines whether the algorithm should terminate after completing the number of steps specified by the [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min) argument from the moment the minimum `RMSE` value is found;
-
-:::
-
-::: { #func.tune.model_param.args.steps.beyond_min .sidebar }
-  - **steps.beyond_min:** (Optional, 2 by default; only takes effect if [break.if_min](#func.tune.model_param.args.break.if_min) is `TRUE`) Specifies the number of steps after finding the minimum *RMSE* value after which the algorithm should terminate.
-
-:::
-:::
-
-::: { #func.tune.model_param.details .sidebar }
-##### Details
-\
-
-With the approach used in this algorithm, the best value of the *tuning parameter* is considered to be the value corresponding to the minimum value of the *Root Mean Square Error (RMSE)* for the model being tested.
-
-To find the best value, the algorithm iterates over the values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the *RMSE* of the model for each of them, using the helper function specified in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument.
-
-The algorithm continues iterating until the end of the parameter values list if [break.if_min](#func.tune.model_param.args.break.if_min) is `FALSE`.
-
-Otherwise, the algorithm terminates after the number of cycles specified by the argument [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min) has completed since the minimum *RMSE* value was reached.
-
-::: {.noteblock data-latex=""}
-The algorithm assumes that the set of the *RMSE* values is a monotonically non-increasing function of the *tuning parameter* until the minimum is reached and monotonically non-decreasing thereafter.
-That is, it is assumed that the function can have only one minimum on the given set.
-:::
-:::
-
-::: { #func.tune.model_param.value .sidebar }
-##### Value
-\
-
-This function returns a list of two objects:
-```{r eval=FALSE}
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-```
-
-The objects comprising the return list are as follows:
-
-  - `best_result`: Vector containing a *pair of values*: the found *best value of the tuning parameter* for which the *RMSE* value is minimal, along with the minimal *RMSE* value itself;
-
-  - `tuned.result`: Data frame containing two variables:
-
-    - *parameter.value*: A vector containing all processed values of the *tuning parameter*;
-
-    - *RMSE*: A vector containing the *RMSE* values corresponding to the processed values of the *tuning parameter*.
-
-:::
-
-##### Source Code
-\
-Below is the most significant part of the source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) function:
-```{r eval=FALSE}
-tune.model_param <- function(param_values, 
-                             fn_tune.test.param_value, 
-                             break.if_min = TRUE,
-                             steps.beyond_min = 2){
-  n <- length(param_values)
-  param_vals_tmp <- numeric()
-  RMSEs_tmp <- numeric()
-  RMSE_min <- Inf
-  i_max.beyond_RMSE_min <- Inf
-  prm_val.best <- NA
-
-  # ...
-
-  for (i in 1:n) {
-    put_log1("Function: `tune.model_param`:
-Iteration %1", i)
-    prm_val <- param_values[i]
-    param_vals_tmp[i] <- prm_val
-
-    RMSE_tmp <- fn_tune.test.param_value(prm_val)
-    RMSEs_tmp[i] <- RMSE_tmp
-
-    plot(param_vals_tmp[RMSEs_tmp], RMSEs_tmp[RMSEs_tmp])
-
-    if(RMSE_tmp > RMSE_min){
-      warning("Function: `tune.model_param`:
-`RSME` reached its minimum: ", RMSE_min, "
-for parameter value: ", prm_val)
-      put_log2("Function: `tune.model_param`:
-Current `RMSE` value is %1 related to parameter value: %2",
-               RMSE_tmp,
-               prm_val)
-
-      if (i > i_max.beyond_RMSE_min) {
-        warning("Function: `tune.model_param`:
-Operation is breaked (after `RSME` reached its minimum) on the following step: ", i)
-        break
-      }
-      next
-    }
-
-    RMSE_min <- RMSE_tmp
-    prm_val.best <- prm_val
-
-    if (break.if_min) {
-      i_max.beyond_RMSE_min <- i + steps.beyond_min
-    }
-  }
-
-  param_values.best_result <- c(param.best_value = prm_val.best, 
-                                best_RMSE = RMSE_min)
-
-  list(tuned.result = data.frame(RMSE = RMSEs_tmp,
-                                parameter.value = param_vals_tmp),
-       best_result = param_values.best_result)
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L126) script on _GitHub_.
-:::
-
-\newpage
+---
+title: "func_tmp"
+output: html_document
+---
 
@@
 \newpage
-
-## Data Helper Functions {#appndx_a.data_helper.functions}
-\
-
-### Initializing Input Datasets
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) script on _GitHub_.
-:::
-
-#### [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) Function {#func.make_source_datasets}
-\
-
-Creates the major input datasets used throughout the project.
-
-::: { #func.make_source_datasets.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-movielens_datasets <- make_source_datasets()
-
-```
-:::
-
-::: { #func.make_source_datasets.details .sidebar }
-##### Details
-\
-
-This function produces datasets listed in the [Value](#func.make_source_datasets.value) section below and described in detail in [Appendix B: Models Training Datasets], using the `edx` as the original dataset.
-
-::: {.noteblock data-latex=""}
-The function calls internally the following functions described below:
-
-  - [splitGenreRows](#) to create the [`edx.sgr` Object];
-  - [sample_train_validation_sets](#) to create *train* and *validation* sets of the inner datasets of the [`edx_CV` Object].
-
-:::
-:::
-
-::: { #func.make_source_datasets.value .sidebar }
-##### Value
-\
-
-The list of the following datasets are returned to the client code:
-
-  - [`edx.mx` Matrix Object];
-
-  - [`edx.sgr` Object];
-
-  - [`movie_map` Object];
-
-  - [`date_days_map` Object];
-
-  - [`edx_CV` Object].
-
-:::
-
-::: { #func.make_source_datasets.code .sidebar }
-##### Source Code
-\
-
-The source code of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is shown below:
-```{r eval=FALSE}
-make_source_datasets <- function(){
-  put_log("Function: `make_source_datasets`: Creating source datasets...")
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-  put(dim(edx.mx))
-
-  #> To be able to map movie IDs to titles we create the following lookup table:
-  movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-  put(summary(movie_map))
-
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  str(date_days_map)
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-  put(summary(date_days_map))
-
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-
-  #> We will use K-fold cross validation as explained in 
-  #> Section 29.6.1: "K-fold validation" of the Cource Textbook:
-  #> https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation
-  #> We are going to compute the following version of the MSE introducing in that section:
-
-  # $$
-  #   \mbox{MSE}(\lambda) \approx\frac{1}{B} \sum_{b = 1}^B \frac{1}{N}\sum_{i = 1}^N \left(\hat{y}_i^b(\lambda) - y_i^b\right)^2 
-  # $$
-
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross-Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    # train_set <- mutate(train_set, userId = factor(userId), movieId = factor(movieId))
-    # train.sgr <- mutate(train.sgr, userId = factor(userId), movieId = factor(movieId))
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross-Validation datasets created: edx_CV")
-
-  tuning_sets <- edx |>
-    sample_train_validation_sets(5423)
-
-  list(edx_CV = edx_CV,
-       edx.mx = edx.mx,
-       edx.sgr = edx.sgr,
-       tuning_sets = tuning_sets,
-       movie_map = movie_map,
-       date_days_map = date_days_map)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is also available in the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) script on _GitHub_.
-:::
-:::
-
-#### [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L211) Function {#func.init_source_datasets}
-\
-
-Creates the major input datasets used throughout the project.
-
-::: { #func.init_source_datasets.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-movielens_datasets <- init_source_datasets()
-
-```
-:::
-
-##### Details
-\
-
-The function checks whether the required source datasets are cached on the hard disk and, if so, loads them from the cache file.
-
-Otherwise, it calls the [make_source_datasets](#func.make_source_datasets) function, which creates all the necessary datasets using the `edx` as the original dataset.
-
-:::
-
-::: { #func.init_source_datasets.value .sidebar }
-##### Value
-\
-
-The list of the following datasets (described in detail in [Appendix B: Models Training Datasets]) is returned to the client code:
-
-  - [`edx.mx` Matrix Object];
-
-  - [`edx.sgr` Object];
-
-  - [`movie_map` Object];
-
-  - [`date_days_map` Object];
-
-  - [`edx_CV` Object].
-
-:::
-
-::: { #func.init_source_datasets.code .sidebar }
-##### Source Code
-\
-
-The simplified source code of the [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L211) function is shown below:
-```{r eval=FALSE}
-init_source_datasets <- function(){
-  put_log("Method `init_source_datasets`: 
-Initializing sourse datasets...")
-
-  if(file.exists(movielens_datasets_file_path)){
-    movielens_datasets <- load_movielens_data_from_file(movielens_datasets_file_path)
-  } else if(file.exists(movielens_datasets_zip)) {
-    put_log("Method `init_source_datasets`: 
-Unzipping MovieLens data file from zip-archive: {movielens_datasets_zip}...")
-
-    unzip(movielens_datasets_zip, movielens_datasets_file_path)
-
-    if(!file.exists(movielens_datasets_file_path)) {
-      put_log("Method `init_source_datasets`: 
-File does not exists: {movielens_datasets_file}.")
-      stop("Failed to unzip MovieLens data zip-archive.")
-    }
-
-    movielens_datasets <- load_movielens_data_from_file(movielens_datasets_file_path)
-  } else {
-    put_log("Method `init_source_datasets`: 
-Creating datasets...")
-    library(edx.capstone.movielens.data)
-    put_log("Method `init_source_datasets`: 
-Library attached: 'edx.capstone.movielens.data'")
-
-    movielens_datasets <- make_source_datasets()
-    put("Method `init_source_datasets`: 
-All required datasets have been created.")
-
-    put_log("Method `init_source_datasets`: 
-Saving newly created input datasets to file...")
-    save(movielens_datasets, file =  movielens_datasets_file_path)
-
-    if(!file.exists(movielens_datasets_file_path)) {
-      put_log("Method `init_source_datasets`: 
-File was not created: {movielens_datasets_file}.")
-      warning("MovieLens data was not saved to file.")
-    } else {
-      put_log("Method `init_source_datasets`: 
-Datasets have been saved to file: {movielens_datasets_file_path}.")
-
-      put_log("Method `init_source_datasets`: 
-Creating zip-archive: {movielens_datasets_zip}...")
-
-      zip(movielens_datasets_zip, movielens_datasets_file_path)
-
-      put_log("Method `init_source_datasets`: 
-Zip-archive created: {movielens_datasets_zip}.")
-    }
-  }
-  movielens_datasets
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [init_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L211) function is available in the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L211) script on _GitHub_.
-:::
-:::
-
-### Data Processing Functions
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) script on _GitHub_.
-:::
-
-#### [load_movielens_data_from_file](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L4) Function {#func.load_movielens_data_from_file}
-\
-
-::: { #func.load_movielens_data_from_file.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-```
-:::
-
-::: { #func.load_movielens_data_from_file.args .sidebar }
-##### Arguments
-\
-
-:::
-::: { #func.load_movielens_data_from_file.args.seed .sidebar }
-  - **file_path:** Data file full path.
-
-:::
-:::
-
-::: { #func.load_movielens_data_from_file.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.load_movielens_data_from_file.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.load_movielens_data_from_file.code .sidebar }
-##### Source Code
-\
-
-The source code of the [load_movielens_data_from_file](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L4) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [load_movielens_data_from_file](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L4) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L4) script on _GitHub_.
-:::
-:::
-
-#### [splitByUser](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L14) Function {#func.splitByUser}
-\
-
-::: { #func.splitByUser.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-```
-:::
-
-::: { #func.splitByUser.args .sidebar }
-##### Arguments
-\
-
-::: { #func.splitByUser.args.data .sidebar }
-  - **data:** ;
-
-:::
-:::
-
-::: { #func.splitByUser.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.splitByUser.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.splitByUser.code .sidebar }
-##### Source Code
-\
-
-The source code of the [splitByUser](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L14) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [splitByUser](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L14) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L14) script on _GitHub_.
-:::
-:::
-
-#### [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) Function {#func.sample_train_validation_sets}
-\
-
-Splits the input dataset passed in the [data](#func.sample_train_validation_sets.args.data) argument into *train* and *validation* datasets in the way described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].
-
-::: { #func.sample_train_validation_sets.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-split_sets <- data |>
-      sample_train_validation_sets(seed)
-```
-:::
-
-::: { #func.sample_train_validation_sets.args .sidebar }
-##### Arguments
-\
-
-::: { #func.sample_train_validation_sets.args.data .sidebar }
-  - **data:** Input dataset to split;
-
-:::
-::: { #func.sample_train_validation_sets.args.seed .sidebar }
-  - **seed:** Seed value;
-
-:::
-:::
-
-::: { #func.sample_train_validation_sets.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.sample_train_validation_sets.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.sample_train_validation_sets.code .sidebar }
-##### Source Code
-\
-
-The source code of the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function is shown below:
-```{r eval=FALSE}
-sample_train_validation_sets <- function(data, seed){
-  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
-  set.seed(seed)
-  validation_ind <- 
-    sapply(splitByUser(data),
-           function(i) sample(i, ceiling(length(i)*.2))) |> 
-    unlist() |> 
-    sort()
-
-  put_log("Function: `sample_train_validation_sets`: 
-Extracting 80% of the original `data` not used for the Validation Set, 
-excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")
-
-  train_set <- data[-validation_ind,]
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
-  put(summary(train_set))
-
-  put_log("Function: `sample_train_validation_sets`: 
-To make sure we don’t include movies in the Training Set that should not be there, 
-we exclude entries using the semi_join function from the Validation Set.")
-  tmp.data <- data[validation_ind,]
-
-  validation_set <- tmp.data |> 
-    semi_join(train_set, by = "movieId") |> 
-    semi_join(train_set, by = "userId") |>
-    as.data.frame()
-
-  # Add rows excluded from `validation_set` into `train_set`
-  tmp.excluded <- anti_join(tmp.data, validation_set)
-  train_set <- rbind(train_set, tmp.excluded)
-
-  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
-  put(summary(validation_set))
-
-  # CV train & test sets Consistency Test
-  validation.left_join.Nas <- train_set |>
-    mutate(tst.col = rating) |>
-    select(userId, movieId, tst.col) |>
-    data.consistency.test(validation_set)
-
-  put_log("Function: `sample_train_validation_sets`:
-Below are the data consistency verification results")
-  put(validation.left_join.Nas)
-
-  # Return result datassets    
-  list(train_set = train_set, 
-       validation_set = validation_set)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) script on _GitHub_.
-:::
-:::
-
-#### [mutateDateTimeAndDays](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L66) Function {#func.mutateDateTimeAndDays}
-\
-
-::: { #func.mutateDateTimeAndDays.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-```
-:::
-
-::: { #func.mutateDateTimeAndDays.args .sidebar }
-##### Arguments
-\
-
-::: { #func.mutateDateTimeAndDays.args.data .sidebar }
-  - **data:** ;
-
-:::
-:::
-
-::: { #func.mutateDateTimeAndDays.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.mutateDateTimeAndDays.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.mutateDateTimeAndDays.code .sidebar }
-##### Source Code
-\
-
-The source code of the [mutateDateTimeAndDays](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L66) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [mutateDateTimeAndDays](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L66) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L66) script on _GitHub_.
-:::
-:::
-
-#### [splitGenreRows](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) Function {#func.splitGenreRows}
-\
-Splits rows of the original dataset passed in the [data](#func.splitGenreRows.args.data) argument for movies that belong to multiple genres.
-
-::: { #func.splitGenreRows.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-edx.sgr <- splitGenreRows(edx)
-```
-:::
-
-::: { #func.splitGenreRows.args .sidebar }
-##### Arguments
-\
-
-::: { #func.splitGenreRows.args.data .sidebar }
-  - **data:** A dataset containing rows corresponding to movies that belong to multiple genres..
-
-:::
-:::
-
-::: { #func.splitGenreRows.details .sidebar }
-##### Details
-\
-This function is a wrapper for the [tidyr::separate_rows](https://www.rdocumentation.org/packages/tidyr/versions/1.3.0/topics/separate_rows) `R` function used in *This Project* to split rows belonging to multiple genres of a dataset containing a `genres` column, which is passed in the [data](#func.splitGenreRows.args.data) argument.
-
-::: {.noteblock data-latex=""}
-The `splitGenreRows` function is used internally in the [make_source_datasets](#func.make_source_datasets) function described above in the [Initializing Input Datasets] section to create the `edx.sgr` dataset described below in the [`edx.sgr` Object] section of the [Appendix B: Models Training Datasets].
-:::
-:::
-
-::: { #func.splitGenreRows.value .sidebar }
-##### Value
-\
-
-Dataset with the same structure as the one passed in the [data](#func.splitGenreRows.args.data) argument, but with rows that belong to multiple genres split.
-:::
-
-::: { #func.splitGenreRows.code .sidebar }
-##### Source Code
-\
-
-The source code of the [splitGenreRows](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) function is shown below:
-```{r eval=FALSE}
-splitGenreRows <- function(data){
-  put("Splitting dataset rows related to multiple genres...")
-  start <- put_start_date()
-  gs_splitted <- data |>
-    separate_rows(genres, sep = "\\|")
-  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
-  put_end_date(start)
-  gs_splitted
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [splitGenreRows](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) script on _GitHub_.
-:::
-:::
-
-#### [filter_noMore_nratings](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L82) Function {#func.filter_noMore_nratings}
-\
-
-::: { #func.filter_noMore_nratings.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-```
-:::
-
-::: { #func.filter_noMore_nratings.args .sidebar }
-##### Arguments
-\
-
-::: { #func.filter_noMore_nratings.args.data .sidebar }
-  - **data:** ;
-
-:::
-::: { #func.filter_noMore_nratings.args.seed .sidebar }
-  - **seed:** ;
-
-:::
-:::
-
-::: { #func.filter_noMore_nratings.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.filter_noMore_nratings.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.filter_noMore_nratings.code .sidebar }
-##### Source Code
-\
-
-The source code of the [filter_noMore_nratings](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L82) function is shown below:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [filter_noMore_nratings](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L82) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L82) script on _GitHub_.
-:::
-:::
-
-### Models Training Functions
-
-#### [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) Function {#func.union_cv_results}
-\
-
-Aggregates the input data frames passed in the [data_list](#func.union_cv_results.args.data_list) argument into a single data frame.
-
-::: { #func.union_cv_results.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-data_list <- as.list(data)
-df <- union_cv_results(data_list)
-
-```
-:::
-
-::: { #func.union_cv_results.args .sidebar }
-##### Arguments
-\
-
-::: { #func.union_cv_results.args.data_list .sidebar }
-  - **data_list:** List of data frames representing the results of the *K-Fold Cross-Validation* execution (as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV]).
-
-:::
-:::
-
-::: { #func.union_cv_results.details .sidebar }
-##### Details
-\
-
-This function internally uses the [base::union](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/sets) `R` function to combine the data from the list of data frames (result of the *K-Fold Cross-Validation*) passed in the [data_list](#func.union_cv_results.args.data_list) argument into a single data frame for further processing.
-
-::: {.noteblock data-latex=""}
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
-:::
-
-:::
-
-::: { #func.union_cv_results.value .sidebar }
-##### Value
-\
-
-A data frame that is a union of the input list of data frames.
-:::
-
-::: { #func.union_cv_results.code .sidebar }
-##### Source Code
-\
-
-The source code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) function is shown below:
-```{r eval=FALSE}
-union_cv_results <- function(data_list) {
-  out_dat <- data_list[[1]]
-
-  for (i in 2:CVFolds_N){
-    out_dat <- union(out_dat, 
-                     data_list[[i]])
-  }
-
-  out_dat
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) is also available in the [Model training](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L431) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) script on _GitHub_.
-:::
-:::
-
-#### [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) Function {#func.get_best_param.result}
-\
-
-Selects the best parameter value and the corresponding minimum Root Mean Squared Error value from the function's input arguments.
-
-::: { #func.get_best_param.result.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-get_best_param.result(param_values, rmses)
-
-```
-:::
-
-::: { #func.get_best_param.result.args .sidebar }
-##### Arguments
-\
-
-::: { #func.get_best_param.result.args.param_values .sidebar }
-  - **param_values:** List of parameters to choose the best value.;
-
-:::
-::: { #func.get_best_param.result.args.rmses .sidebar }
-  - **rmses:** A list of Root Mean Squared Errors corresponding to the parameter values specified in the list passed by the argument [param_values](#func.get_best_param.result.args.param_values).
-
-:::
-:::
-
-::: { #func.get_best_param.result.details .sidebar }
-##### Details
-\
-
-A parameter value that corresponds to the minimum RMSE is considered the best.
-
-:::
-
-::: { #func.get_best_param.result.value .sidebar }
-##### Value
-\
-
-A data frame that is a union of the input data frames.
-:::
-
-::: { #func.get_best_param.result.code .sidebar }
-##### Source Code
-\
-
-The soure code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) function is shown below:
-```{r eval=FALSE}
-get_best_param.result <- function(param_values, rmses){
-  best_pvalue_idx <- which.min(rmses)
-  c(param.best_value = param_values[best_pvalue_idx], 
-    best_RMSE = rmses[best_pvalue_idx])
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [get_best_param.result](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) is also available in the [Model training](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L431) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L442) script on _GitHub_.
-:::
-:::
-
-### Data Visualization Functions
-
-#### [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) Function {#func.data.plot}
-\
-
-Plots a graph based on the dataset passed in the [data](#func.data.plot.args.data) parameter, using both points and a line.
-
-::: { #func.data.plot.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-data.plot(data, 
-          title, 
-          xname, 
-          yname, 
-          xlabel = NULL, 
-          ylabel = NULL,
-          line_col = "blue",
-          normalize = FALSE)
-```
-:::
-
-::: { #func.data.plot.args .sidebar }
-##### Arguments
-\
-
-::: { #func.data.plot.args.data .sidebar }
-  - **data:** Dataset to use for the plot;
-
-:::
-::: { #func.data.plot.args.title .sidebar }
-  - **title:** Title of the plot;
-
-:::
-::: { #func.data.plot.args.xname .sidebar }
-  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;
-
-:::
-::: { #func.data.plot.args.yname .sidebar }
-  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;
-
-:::
-::: { #func.data.plot.args.xlabel .sidebar }
-  - **xlabel = NULL:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;
-
-:::
-::: { #func.data.plot.args.ylabel .sidebar }
-  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;
-
-:::
-::: { #func.data.plot.args.line_col .sidebar }
-  - **line_col = blue:** The line color;
-
-:::
-::: { #func.data.plot.args.normalize .sidebar }
-- **normalize = FALSE:** If `TRUE`, deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves. Otherwise, the $y$ values are used.
-
-:::
-:::
-
-::: { #func.data.plot.details .sidebar }
-##### Details
-\
-
-The function is a wrapper for the [ggplot2::ggplot](https://ggplot2.tidyverse.org/reference/ggplot.html) function and is a simple and convenient tool for visualizing the data of this project.
-
-:::
-
-::: { #func.data.plot.code .sidebar }
-##### Source Code
-\
-
-The soure code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function is shown below:
-```{r eval=FALSE}
-data.plot <- function(data, 
-                      title, 
-                      xname, 
-                      yname, 
-                      xlabel = NULL, 
-                      ylabel = NULL,
-                      line_col = "blue",
-                      normalize = FALSE) {
-  y <- data[, yname]
-
-  if (normalize) {
-    y <- y - min(y)
-  }
-
-  if (is.null(xlabel)) {
-    xlabel = xname
-  }
-  if (is.null(ylabel)) {
-    ylabel = yname
-  }
-
-  aes_mapping <- aes(x = data[, xname], y = y)
-
-  data |> 
-    ggplot(mapping = aes_mapping) +
-    ggtitle(title) +
-    xlab(xlabel) +
-    ylab(ylabel) +
-    geom_point() + 
-    geom_line(color=line_col)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [data.plot](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
-:::
-:::
-
-#### [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) Function {#func.data.plot.left.n}
-\
-
-Plots a graph based on the first $n$ rows (the $n$ is specified by the [left.n](#func.data.plot.left.n.args.left.n) parameter) of the dataset passed in the [data](#func.data.plot.left.n.args.data) parameter, using both points and a line.
-
-::: {.noteblock data-latex=""}
-The dataset passed in the [data](#func.data.plot.left.n.args.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.args.xname) parameter).
-:::
-
-::: { #func.data.plot.left.n.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-data.plot.left.n <- function(data, 
-                             left.n = 0,
-                             title, 
-                             xname, 
-                             yname, 
-                             xlabel, 
-                             ylabel,
-                             line_col = "red",
-                             normalize = FALSE)
-```
-:::
-
-::: { #func.data.plot.left.n.args .sidebar }
-##### Arguments
-\
-
-::: { #func.data.plot.left.n.args.data .sidebar }
-  - **data:** Dataset to use for the plot.
-
-:::
-::: { #func.data.plot.left.n.args.left.n .sidebar }
-  - **left.n:** If a positive numeric value, specifies the number of the first rows of the dataset to plot. Otherwise, the entire dataset data is set to plot.
-
-:::
-::: { #func.data.plot.left.n.args.title .sidebar }
-  - **title:** Title of the plot.
-
-:::
-::: { #func.data.plot.left.n.args.xname .sidebar }
-  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot.
-
-:::
-::: { #func.data.plot.left.n.args.yname .sidebar }
-  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot.
-
-:::
-::: { #func.data.plot.left.n.args.xlabel .sidebar }
-  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left.n.args.ylabel .sidebar }
-  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left.n.args.line_col .sidebar }
-  - **line_col = blue:** The line color.
-
-:::
-::: { #func.data.plot.left.n.args.normalize .sidebar }
-  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
-
-:::
-:::
-
-::: { #func.data.plot.left.n.details .sidebar }
-##### Details
-\
-
-The function is a wrapper for the [data.plot](#func.data.plot) function described above and is a simple and convenient tool for more detailed visualization of the left part of the graph, initially built based on the entire data set passed in the [data](#func.data.plot.left.n.args.data) parameter.
-:::
-
-::: { #func.data.plot.left.n.code .sidebar }
-##### Source Code
-\
-
-The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) function is shown below:
-```{r eval=FALSE}
-data.plot.left.n <- function(data, 
-                             left.n = 0,
-                             title, 
-                             xname, 
-                             yname, 
-                             xlabel, 
-                             ylabel,
-                             line_col = "red",
-                             normalize = FALSE) {
-  x_col <- data[, xname] 
-  y_col <- data[, yname]
-
-  data.left <- data
-
-  if (left.n > 0) {
-    data.left <- data |> 
-      head(left.n)
-  }
-
-  data.left |>
-    data.plot(title = title,
-              xname = xname,
-              yname = yname,
-              xlabel = xlabel,
-              ylabel = ylabel,
-              line_col = line_col,
-              normalize = normalize)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) script on _GitHub_.
-:::
-:::
-
-#### [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) Function {#func.data.plot.left_detailed}
-\
-
-Combines two graphs plotted by the internally called helper functions in a grid: the first is a standard graph plotted by the [data.plot](#func.data.plot) function described above, the second is a graph based on the first $n$ rows (the $n$ is specified by the [left.n](#func.data.plot.left.n.args.left.n) parameter) of the dataset plotted by the [data.plot.left.n](#func.data.plot.left.n) function also described above (The data for both graphs is passed in the [data]).(#func.data.plot.left.n.args.data) parameter).
-
-::: {.noteblock data-latex=""}
-The dataset passed in the [data](#func.data.plot.left.n.args.data) parameter is assumed to be sorted by the column used for the $x$ axis (specified by the column name passed in the [xname](#func.data.plot.left.n.args.xname) parameter).
-:::
-
-::: { #func.data.plot.left_detailed.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-data.plot.left_detailed <- function(data, 
-                                    left.n = 0,
-                                    title = NULL,
-                                    title.left = NULL,
-                                    xname, 
-                                    yname, 
-                                    xlabel1 = NULL, 
-                                    xlabel2 = NULL, 
-                                    ylabel1 = NULL,
-                                    ylabel2 = NULL,
-                                    line_col1 = "blue",
-                                    line_col2 = "red",
-                                    normalize = FALSE)
-```
-:::
-
-::: { #func.data.plot.left_detailed.args .sidebar }
-##### Arguments
-\
-
-::: { #func.data.plot.left_detailed.args.data .sidebar }
-  - **data:** Dataset to use for the plot.
-
-:::
-::: { #func.data.plot.left.n.args.left.n .sidebar }
-  - **left.n:** If a positive numeric value, specifies the number of the first rows of the dataset to plot. Otherwise, the entire dataset data is set to plot.
-
-:::
-::: { #func.data.plot.left_detailed.args.title .sidebar }
-  - **title:** Title of the plot.
-
-:::
-::: { #func.data.plot.left_detailed.args.xname .sidebar }
-  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot.
-
-:::
-::: { #func.data.plot.left_detailed.args.yname .sidebar }
-  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot.
-
-:::
-::: { #func.data.plot.left_detailed.args.xlabel1 .sidebar }
-  - *xlabel1 = NULL*:** The $x$ axis label for the first plot. If `NULL`, the value of the `xname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left_detailed.args.xlabel2 .sidebar }
-  - *xlabel2 = NULL*:** The $x$ axis label for the second plot. If `NULL`, the value of the `xname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left_detailed.args.ylabel1 .sidebar }
-  - **ylabel1 = NULL:** The $y$ axis label for the first plot. If `NULL`, the value of the `yname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left_detailed.args.ylabel2 .sidebar }
-  - **ylabel2 = NULL:** The $y$ axis label for the second plot. If `NULL`, the value of the `yname` parameter is used for the label.
-
-:::
-::: { #func.data.plot.left_detailed.args.line_col .sidebar }
-  - **line_col = blue:** The line color.
-
-:::
-::: { #func.data.plot.left_detailed.args.normalize .sidebar }
-  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.
-
-:::
-:::
-
-::: { #func.data.plot.left_detailed.details .sidebar }
-##### Details
-\
-
-Under the hood, the function calls internally the [data.plot](#func.data.plot) and [data.plot.left.n](#func.data.plot.left.n) functions (described above) to build two graphs and combines them into a grid.
-:::
-
-::: { #func.data.plot.left_detailed.code .sidebar }
-##### Source Code
-\
-
-The soure code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) function is shown below:
-```{r eval=FALSE}
-data.plot.left_detailed <- function(data, 
-                                    left.n = 0,
-                                    title = NULL,
-                                    title.left = NULL,
-                                    xname, 
-                                    yname, 
-                                    xlabel1 = NULL, 
-                                    xlabel2 = NULL, 
-                                    ylabel1 = NULL,
-                                    ylabel2 = NULL,
-                                    line_col1 = "blue",
-                                    line_col2 = "red",
-                                    normalize = FALSE) {
-  if(is.null(xlabel1)) {
-    xlabel1 <- xname
-  }
-  if(is.null(xlabel2)) {
-    xlabel2 <- str_glue(xlabel1, " (left part)")
-  }
-  if(is.null(ylabel1)) {
-    ylabel1 <- yname
-  }
-  if(is.null(ylabel2)) {
-    ylabel2 <- ylabel1
-  }
-
-  p1 <- data |>
-    data.plot(title = title,
-              xname = xname, 
-              yname = yname, 
-              xlabel = xlabel1, 
-              ylabel = ylabel1,
-              line_col = line_col1)
-
-  p2 <- data |>
-    data.plot.left.n(left.n = left.n,
-                     title = title.left,
-                     xname = xname, 
-                     yname = yname, 
-                     xlabel = xlabel2, 
-                     ylabel = ylabel2,
-                     line_col = line_col2,
-                     normalize = normalize)
-  grid.arrange(p1, p2)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-## Models Training: Support Functions
-\
-
-### OMR Model: Helper Functions
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R) script on _GitHub_.
-:::
-
-#### [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) Function {#func.naive_model_MSEs}
-\
-
-Validates the *Overall Mean Rating (OMR) Model* with use of *K-Fold Cross-Validation* method as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.naive_model_MSEs.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-mu <- mean(edx$rating)
-mu.MSEs <- naive_model_MSEs(mu)
-
-```
-:::
-
-::: { #func.naive_model_MSEs.args .sidebar }
-##### Arguments
-\
-
-::: { #func.naive_model_MSEs.args. .sidebar }
-  - **mu:** The overall mean rating value.
-
-:::
-:::
-
-::: { #func.naive_model_MSEs.value .sidebar }
-##### Value
-\
-
-The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the $K$ value is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-
-:::
-
-::: { #func.naive_model_MSEs.code .sidebar }
-##### Source Code
-\
-
-The source code of the [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) function is shown below:
-```{r eval=FALSE}
-naive_model_MSEs <- function(mu) {
-  sapply(edx_CV, function(cv_item){
-    mse(cv_item$validation_set$rating - mu)
-  })
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [naive_model_MSEs](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L2) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) Function {#func.naive_model_RMSE}
-\
-Validates the *Overall Mean Rating (OMR) Model* with use of *K-Fold Cross-Validation* method as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: { #func.naive_model_RMSE.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-mu <- mean(edx$rating)
-mu.RMSE <- naive_model_RMSE(mu)
-```
-:::
-
-::: { #func.naive_model_RMSE.args .sidebar }
-##### Arguments
-\
-
-::: { #func.naive_model_RMSE.args. .sidebar }
-  - **mu:** The overall mean rating value.
-
-:::
-:::
-
-::: { #func.naive_model_RMSE.details .sidebar }
-##### Details
-\
-
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
-
-::: {.noteblock data-latex=""}
-This function internally calls the [naive_model_MSEs](#func.naive_model_MSEs) function described above and then calculates the square root of the mean of the obtained results.
-:::
-:::
-
-::: { #func.naive_model_RMSE.value .sidebar }
-##### Value
-\
-
-The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the $K$ value is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.naive_model_RMSE.code .sidebar }
-##### Source Code
-\
-
-The source code of the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) function is shown below:
-```{r eval=FALSE}
-naive_model_RMSE <- function(mu){
-  sqrt(mean(naive_model_MSEs(mu)))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [naive_model_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#L7) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### UME Model: Utility Functions
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) script on _GitHub_.
-:::
-
-#### [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) Function {#func.train_user_movie_effect}
-\
-
-Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_effect.args.lambda) argument value is non-default) the *User+Movie Effect (UME) Model* using the training dataset passed in the [train_set](#func.train_user_movie_effect.args.train_set) argument.
-
-::: { #func.train_user_movie_effect.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  UM_effect <- train_user_movie_effect(train_set, lambda = 0)
-```
-:::
-
-::: { #func.train_user_movie_effect.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_user_movie_effect.args.train_set .sidebar }
-  - **train_set:** Training dataset;
-
-:::
-::: { #func.train_user_movie_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.train_user_movie_effect.details .sidebar }
-##### Details
-\
-
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-
-::: {.noteblock data-latex=""}
-*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
-:::
-:::
-
-::: { #func.train_user_movie_effect.value .sidebar }
-##### Value
-\
-
-Data frame object representing the trained (and also *regularized* if [lambda](#func.train_user_movie_effect.args.lambda) arg value other than default) *UM Effect Model*.
-:::
-
-::: { #func.train_user_movie_effect.code .sidebar }
-##### Source Code
-\
-
-The source code of the [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is shown below:
-```{r eval=FALSE}
-train_user_movie_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_effect
-`lambda` is `NA`")
-  }
-
-  UM.effect <- train_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    mutate(resid = rating - (mu + a)) |> 
-    group_by(movieId) |>
-    summarise(b = mean_reg(resid, lambda), n = n())
-
-  stopifnot(!is.na(mean(UM.effect$b)))
-  UM.effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L4) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) Function {#func.train_user_movie_effect.cv}
-\
-
-Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_effect.args.cv.lambda) argument value is non-default) the *User+Movie Effect (UME) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: { #func.train_user_movie_effect.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  cv.UM_effect <- train_user_movie_effect.cv()
-```
-:::
-
-::: { #func.train_user_movie_effect.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_user_movie_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.train_user_movie_effect.cv.details .sidebar }
-##### Details
-\
-
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-
-Internally, this function calls the helper function [train_user_movie_effect](#func.train_user_movie_effect) described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
-It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
-
-::: {.noteblock data-latex=""}
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-:::
-
-::: { #func.train_user_movie_effect.cv.value .sidebar }
-##### Value
-\
-
-Data frame object representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.train_user_movie_effect.cv.code .sidebar }
-##### Source Code
-\
-
-The most important part of the source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is shown below:
-```{r eval=FALSE}
-train_user_movie_effect.cv <- function(lambda = 0){
-# ...
-  start <- put_start_date()
-  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
-  })
-  put_end_date(start)
-  put_log("Function: train_user_movie_effect.cv:
-User+Movie Effect list have been computed")
-
-  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)
-
-  user_movie_effect <- user_movie_effects_united |>
-    group_by(movieId) |>
-    summarise(b = mean(b), n = mean(n))
-  # ...
-  user_movie_effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L19) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) Function {#func.calc_user_movie_effect_MSE}
-\
-
-Validates the *UM Effect (UME) Model* produced by the  [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call.
-
-::: { #func.calc_user_movie_effect_MSE.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
-
-```
-:::
-
-::: { #func.calc_user_movie_effect_MSE.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_user_movie_effect_MSE.args.test_set .sidebar }
-  - **test_set:** Validation dataset;
-
-:::
-::: { #func.calc_user_movie_effect_MSE.args.um_effect .sidebar }
-  - **um_effect:** Data frame object representing the *UM Effect Model*.
-
-:::
-:::
-
-::: { #func.calc_user_movie_effect_MSE.details .sidebar }
-##### Details
-\
-
-The function calculates *Mean Squared Error (MSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_MSE.args.um_effect) argument using the validation dataset passed in the [test_set](#func.calc_user_movie_effect_MSE.args.test_set) arg.
-
-:::
-
-::: { #func.calc_user_movie_effect_MSE.value .sidebar }
-##### Value
-\
-
-*MSE* value calculated for the *UME Model*.
-:::
-
-::: { #func.calc_user_movie_effect_MSE.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) function is shown below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE <- function(test_set, um_effect){
-  mse.result <- test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(um_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b)) |> 
-    pull(resid) |> mse()
-
-  stopifnot(!is.na(mse.result))
-  mse.result
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L53) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) Function {#func.calc_user_movie_effect_MSE.cv}
-\
-
-Validates the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: { #func.calc_user_movie_effect_MSE.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-
-```
-:::
-
-::: { #func.calc_user_movie_effect_MSE.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_user_movie_effect_MSE.cv.args.um_effect .sidebar }
-  - **um_effect:** Data frame object representing the *UM Effect Model*.
-
-:::
-:::
-
-::: { #func.calc_user_movie_effect_MSE.cv.details .sidebar }
-##### Details
-\
-
-The function calculates *MSE* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_MSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_user_movie_effect_MSE](#func.calc_user_movie_effect_MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
-
-The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-:::
-
-::: { #func.calc_user_movie_effect_MSE.cv.value .sidebar }
-##### Value
-\
-
-The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.calc_user_movie_effect_MSE.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) function is shown below:
-```{r eval=FALSE}
-calc_user_movie_effect_MSE.cv <- function(um_effect){
-  put_log("Function: user_movie_effects_MSE.cv:
-Computing the RMSE taking into account User+Movie Effects...")
-  start <- put_start_date()
-  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
-  })
-  put_end_date(start)
-
-  put_log1("Function: user_movie_effects_MSE.cv:
-MSE values have been plotted for the %1-Fold Cross-Validation samples.", 
-           CVFolds_N)
-
-  mean(user_movie_effects_MSEs)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L67) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) Function {#func.calc_user_movie_effect_RMSE.cv}
-\
-
-Validates the *UM Effect (UME) Model* (produced by the [train_user_movie_effect](#func.train_user_movie_effect) or [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: { #func.calc_user_movie_effect_RMSE.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
-
-```
-:::
-
-::: { #func.calc_user_movie_effect_RMSE.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_user_movie_effect_RMSE.cv.args.um_effect .sidebar }
-  - **um_effect:** Data frame object representing the *UM Effect Model*.
-
-:::
-:::
-
-::: { #func.calc_user_movie_effect_RMSE.cv.details .sidebar }
-##### Details
-\
-
-The function calculates *Root Squared Error (RMSE)* for the *UME Model* passed in the [um_effect](#func.calc_user_movie_effect_RMSE.cv.args.um_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_user_movie_effect_MSE.cv](#func.calc_user_movie_effect_MSE.cv) function described above, to calculate the *MSE* for the *UME Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
-
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-:::
-
-::: { #func.calc_user_movie_effect_RMSE.cv.value .sidebar }
-##### Value
-\
-
-The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.calc_user_movie_effect_RMSE.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) function is shown below:
-```{r eval=FALSE}
-calc_user_movie_effect_RMSE.cv <- function(um_effect){
-  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
-  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
-  put_log2("Function: user_movie_effects_RMSE.cv:
-%1-Fold Cross-Validation ultimate RMSE: %2", length(edx_CV), um_effect_RMSE)
-  um_effect_RMSE
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L3) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L82) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### UME Model: Regularization
-\
-
-#### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) Function {#func.regularize.test_lambda.UM_effect.cv}
-\
-
-Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument for the *User+Movie Effect (UME) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
-
-::: { #func.regularize.test_lambda.UM_effect.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  lambdas <- seq(0, 1, 0.1)
-  cv.UME.preset.result <- 
-    tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
-
-Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UM_effect.cv.details) section of *this Description* below.
-:::
-:::
-
-::: { #func.regularize.test_lambda.UM_effect.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.regularize.test_lambda.UM_effect.cv.args.lambda .sidebar }
-  - **lambda:** *Regularization parameter* $\lambda$ used to validate the model in the *regularization process*.
-
-:::
-:::
-
-::: { #func.regularize.test_lambda.UM_effect.cv.details .sidebar }
-##### Details
-\
-
-The function is used in the *regularization process* of the *UME Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument) as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2].
-
-Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
-
-::: {.noteblock data-latex=""}
-This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
-:::
-:::
-
-::: { #func.regularize.test_lambda.UM_effect.cv.value .sidebar }
-##### Value
-\
-
-The *Root Mean Squared Errors (RMSE)* value computed for the UME Model applying the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UM_effect.cv.args.lambda) argument.
-
-:::
-
-::: { #func.regularize.test_lambda.UM_effect.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) function is shown below:
-```{r eval=FALSE}
-regularize.test_lambda.UM_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UM_effect.cv
-`lambda` is `NA`")
-  }
-  um_effect <- train_user_movie_effect.cv(lambda)
-  calc_user_movie_effect_RMSE.cv(um_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L91) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### UMGE Model: Utility Functions
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) script on _GitHub_.
-:::
-
-#### [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) Function {#func.train_user_movie_genre_effect}
-\
-
-Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGE) Model* using the training sample of the `Movielens` dataset (passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument), specially prepared to train the *UMGE Model*.
-
-::: { #func.train_user_movie_genre_effect.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  rglr.UMG_effect <- edx.sgr |> train_user_movie_genre_effect(UMGE.rglr.best_lambda)
-```
-:::
-
-::: { #func.train_user_movie_genre_effect.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_user_movie_genre_effect.args.train.sgr .sidebar }
-  - **train.sgr:** Training sample of the `Movielens` dataset with split rows belonging to multiple genres;
-
-:::
-::: { #func.train_user_movie_genre_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.train_user_movie_genre_effect.details .sidebar }
-##### Details
-\
-The dataset passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *this Appendix*.
-
-For example, the [`edx.sgr` Object] is an appropriate dataset as the value of the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr).
-
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-
-::: {.noteblock data-latex=""}
-*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
-:::
-:::
-
-::: { #func.train_user_movie_genre_effect.value .sidebar }
-##### Value
-\
-
-Data frame object representing the trained (and also *regularized* if [lambda](#func.train_user_movie_genre_effect.args.lambda) arg value other than default) *UMG Effect Model*.
-:::
-
-::: { #func.train_user_movie_genre_effect.code .sidebar }
-##### Source Code
-\
-
-The source code of the [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) function is shown below:
-```{r eval=FALSE}
-train_user_movie_genre_effect <- function(train.sgr, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_user_movie_genre_effect
-`lambda` is `NA`")
-  }
-
-  genre_bias <- train.sgr |>
-      left_join(edx.user_effect, by = "userId") |>
-      left_join(rglr.UM_effect, by = "movieId") |>
-      mutate(resid = rating - (mu + a + b)) |>
-      group_by(genres) |>
-      summarise(g = mean_reg(resid, lambda), n = n())
-
-    train.sgr |>
-      left_join(genre_bias, by = "genres") |>
-      left_join(rglr.UM_effect, by = "movieId") |>
-      group_by(movieId) |>
-      summarise(g = mean(g))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_user_movie_genre_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L42) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) Function {#func.train_user_movie_genre_effect.cv}
-\
-
-Trains (and optionally *regularizes* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre Effect (UMGE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: { #func.train_user_movie_genre_effect.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-# `lambda = 0` by default (the regularization technique is not applied)
-cv.UMG_effect <- train_user_movie_genre_effect.cv()
-
-umg_effect <- train_user_movie_genre_effect.cv(lambda)
-```
-:::
-
-::: { #func.train_user_movie_genre_effect.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_user_movie_genre_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.train_user_movie_genre_effect.cv.details .sidebar }
-##### Details
-\
-
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-
-Internally, this function calls the helper function [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
-It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
-
-::: {.noteblock data-latex=""}
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-:::
-
-::: { #func.train_user_movie_genre_effect.cv.value .sidebar }
-##### Value
-\
-
-Data frame object representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.train_user_movie_genre_effect.cv.code .sidebar }
-##### Source Code
-\
-
-The most important part of the source code of the [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) function is shown below:
-```{r eval=FALSE}
-train_user_movie_genre_effect.cv <- function(lambda = 0){
-  user_movie_genre_effects_ls <- lapply(kfold_index, function(fold_i){
-    cv_fold_dat <- edx_CV[[fold_i]]
-    umg_effect <- cv_fold_dat$train.sgr |> train_user_movie_genre_effect(lambda)
-
-    put_log2("User+Movie+Genre Effects have been computed for the Fold %1 
-of the %2-Fold Cross Validation samples.",
-             fold_i,
-             CVFolds_N)
-
-    umg_effect
-  })
-
-  user_movie_genre_effects_united <- union_cv_results(user_movie_genre_effects_ls)
-
-  user_movie_genre_effect <- user_movie_genre_effects_united |>
-    group_by(movieId) |>
-    summarise(g = mean(g))
-
-  if(lambda == 0) put_log("Function `train_user_movie_genre_effect.cv`:
-Training completed: User+Movie+Genre Effects model.")
-  else put_log1("Function `train_user_movie_genre_effect.cv`:
-Training completed: User+Movie+Genre Effects model for lambda: %1...",
-                lambda)
-
-  user_movie_genre_effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [train_user_movie_genre_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L61) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) Function {#func.calc_user_movie_genre_effect_MSE}
-\
-
-Validates the *UMG Effect (UMGE) Model* produced by the  [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call.
-
-::: { #func.calc_user_movie_genre_effect_MSE.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-umg_mse <- test_set |> calc_user_movie_genre_effect_MSE(umg_effect)
-```
-:::
-
-::: { #func.calc_user_movie_genre_effect_MSE.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_user_movie_genre_effect_MSE.args.test_set .sidebar }
-  - **test_set:** Validation dataset;
-
-:::
-::: { #func.calc_user_movie_genre_effect_MSE.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame object representing the *UMG Effect Model*.
-
-:::
-:::
-
-::: { #func.calc_user_movie_genre_effect_MSE.details .sidebar }
-##### Details
-\
-
-The function calculates *Mean Squared Error (MSE)* for the *UMGE Model* passed in the [umg_effect](#func.calc_user_movie_genre_effect_MSE.args.umg_effect) argument using the validation dataset passed in the [test_set](#func.calc_user_movie_genre_effect_MSE.args.test_set) arg.
-
-:::
-
-::: { #func.calc_user_movie_genre_effect_MSE.value .sidebar }
-##### Value
-\
-
-*MSE* value calculated for the *UMGE Model*.
-:::
-
-::: { #func.calc_user_movie_genre_effect_MSE.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) function is shown below:
-```{r eval=FALSE}
-calc_user_movie_genre_effect_MSE <- function(test_set, umg_effect){
-  test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(umg_effect, by = "movieId") |>
-    mutate(resid = rating - clamp(mu + a + b + g)) |> 
-    pull(resid) |> mse()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_user_movie_genre_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L112) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) Function {#func.calc_user_movie_genre_effect_MSE.cv}
-\
-
-Validates the *UMG Effect (UMGE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: { #func.calc_user_movie_genre_effect_MSE.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  umg_effect_RMSE <- sqrt(calc_user_movie_genre_effect_MSE.cv(umg_effect))
-```
-:::
-
-::: { #func.calc_user_movie_genre_effect_MSE.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_user_movie_genre_effect_MSE.cv.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame object representing the *UMG Effect Model*.
-
-:::
-:::
-
-::: { #func.calc_user_movie_genre_effect_MSE.cv.details .sidebar }
-##### Details
-\
-
-The function calculates *MSE* for the *UMGE Model* passed in the [umg_effect](#func.calc_user_movie_genre_effect_MSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_user_movie_genre_effect_MSE](#func.calc_user_movie_genre_effect_MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
-
-The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-:::
-
-::: { #func.calc_user_movie_genre_effect_MSE.cv.value .sidebar }
-##### Value
-\
-
-The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.calc_user_movie_genre_effect_MSE.cv.code .sidebar }
-##### Source Code
-\
-
-The simplified version of the source code of the [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is shown below:
-```{r eval=FALSE}
-calc_user_movie_genre_effect_MSE.cv <- function(umg_effect){
-  user_movie_genre_effects_MSEs <- sapply(edx_CV, function(cv_dat){
-    cv_dat$validation_set |> calc_user_movie_genre_effect_MSE(umg_effect)
-  })
-
-  mean(user_movie_genre_effects_MSEs)
-}
-```
-
-::: {.noteblock data-latex=""}
-The completed source code of the [calc_user_movie_genre_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L124) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) Function {#func.calc_user_movie_genre_effect_RMSE.cv}
-\
-
-Validates the *UMG Effect (UMGE) Model* (produced by the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) or [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: { #func.calc_user_movie_genre_effect_RMSE.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-cv.UMG_effect.RMSE <- calc_user_movie_genre_effect_RMSE.cv(cv.UMG_effect)
-```
-:::
-
-::: { #func.calc_user_movie_genre_effect_RMSE.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_user_movie_genre_effect_RMSE.cv.args.umg_effect .sidebar }
-  - **umg_effect:** Data frame object representing the *UMG Effect Model*.
-
-:::
-:::
-
-::: { #func.calc_user_movie_genre_effect_RMSE.cv.details .sidebar }
-##### Details
-\
-
-The function calculates *Root Squared Error (RMSE)* for the *UMGE Model* passed in the [umg_effect](#func.calc_user_movie_genre_effect_RMSE.cv.args.umg_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_user_movie_genre_effect_MSE.cv](#func.calc_user_movie_genre_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
-
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-:::
-
-::: { #func.calc_user_movie_genre_effect_RMSE.cv.value .sidebar }
-##### Value
-\
-
-The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.calc_user_movie_genre_effect_RMSE.cv.code .sidebar }
-##### Source Code
-\
-
-The simplified version of the source code of the [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is shown below:
-```{r eval=FALSE}
-calc_user_movie_genre_effect_RMSE.cv <- function(umg_effect){
-  sqrt(calc_user_movie_genre_effect_MSE.cv(umg_effect))
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [calc_user_movie_genre_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L3) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L138) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### UMGE Model: Regularization
-\
-
-#### [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) Function {#func.regularize.test_lambda.UMG_effect.cv}
-\
-
-Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument for the *User+Movie+Genre Effect (UMGE) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
-
-::: { #func.regularize.test_lambda.UMG_effect.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-lambdas <- seq(0, 0.2, 0.01)
-cv.UMGE.preset.result <- 
-  tune.model_param(lambdas, regularize.test_lambda.UMG_effect.cv)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
-
-Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMG_effect.cv.details) section of *this Description* below.
-:::
-:::
-
-::: { #func.regularize.test_lambda.UMG_effect.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.regularize.test_lambda.UMG_effect.cv.args.lambda .sidebar }
-  - **lambda:** *Regularization parameter* $\lambda$ used to validate the model in the *regularization process*.
-
-:::
-:::
-
-::: { #func.regularize.test_lambda.UMG_effect.cv.details .sidebar }
-##### Details
-\
-
-The function is used in the *regularization process* of the *UMGE Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument) as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2].
-
-Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
-
-::: {.noteblock data-latex=""}
-This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
-:::
-:::
-
-::: { #func.regularize.test_lambda.UMG_effect.cv.value .sidebar }
-##### Value
-\
-
-The *Root Mean Squared Errors (RMSE)* value computed for the UMGE Model applying the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMG_effect.cv.args.lambda) argument.
-
-:::
-
-::: { #func.regularize.test_lambda.UMG_effect.cv.code .sidebar }
-##### Source Code
-\
-
-The simplified version of the source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is shown below:
-```{r eval=FALSE}
-regularize.test_lambda.UMG_effect.cv <- function(lambda){
-  umg_effect <- train_user_movie_genre_effect.cv(lambda)
-  calc_user_movie_genre_effect_RMSE.cv(umg_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [regularize.test_lambda.UMG_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) function is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L147) section of the [UMG-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMG-effect.functions.R#L148) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### UMGYE Model: Utility Functions
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) script on _GitHub_.
-:::
-
-#### [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L4) Function {#func.calc_date_general_effect}
-\
-
-This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) of the user ratings using a *training dataset* passed in the [train_set](#func.calc_date_general_effect.args.train_set) argument, and is intended for use in other helper functions (such as [train_UMGY_effect](#func.train_UMGY_effect)), described below in this section.
-
-::: { #func.calc_date_general_effect.usage .sidebar }
-##### Usage
-\
-```{r eval=FALSE}
-  train_set |>
-    calc_date_general_effect(lambda) |>
-    calc_UMGY_effect()
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_date_general_effect` is called internally from the [train_UMGY_effect](#func.train_UMGY_effect) function described below in this section.
-:::
-:::
-
-::: { #func.calc_date_general_effect.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_date_general_effect.args.train_set .sidebar }
-  - **train_set:** Training dataset;
-
-:::
-::: { #func.calc_date_general_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.calc_date_general_effect.details .sidebar }
-##### Details
-\
-
-The *Regularization technique* (described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2]) is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_date_general_effect.args.lambda) argument, has non-default value (to be more exact, greater than zero).
-
-::: {.noteblock data-latex=""}
-*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
-::: {.noteblock data-latex=""}
-:::
-
-::: { #func.calc_date_general_effect.value .sidebar }
-##### Value
-\
-
-Data frame object representing (*regularized* if [lambda](#func.calc_date_general_effect.args.lambda) argument value is non-default) *Date General Effect*.
-:::
-
-::: { #func.calc_date_general_effect.code .sidebar }
-##### Source Code
-\
-
-Below is a slightly simplified version of the source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L4) function:
-```{r eval=FALSE}
-calc_date_general_effect <- function(train_set, lambda = 0){
-  dg_effect <- train_set |> 
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    mutate(resid = rating - (mu + a + b + g)) |>
-  group_by(days) |>
-    summarise(de = mean_reg(resid, lambda), 
-              year = mean(year))
-
-  if(lambda == 0) put_log("Function `calc_date_general_effect`:
-Date Global Effect has been computed.")
-  else put_log1("Function `calc_date_general_effect`:
-Date Global Effect has been computed for lambda: %1...",
-                lambda)
-  dg_effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [calc_date_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L4) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L4) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L32) Function {#func.calc_date_general_effect.cv}
-\
-
-This is a helper function that calculates the _Date General Effect_ (optionally *regularizes* if the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the _K-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
-
-::: { #func.calc_date_general_effect.cv.usage .sidebar }
-##### Usage
-\
-```{r eval=FALSE}
-calc_date_general_effect.cv(lambda) |> calc_UMGY_effect()  
-```
-
-::: {.noteblock data-latex=""}
-In the above code snippet, the `calc_date_general_effect.cv` function is called internally from the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function, along with the [calc_UMGY_effect](#func.calc_UMGY_effect) function (both described below).
-:::
-:::
-
-::: { #func.calc_date_general_effect.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_date_general_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.calc_date_general_effect.cv.details .sidebar }
-##### Details
-\
-
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_date_general_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-
-Internally, this function calls the helper function [calc_date_general_effect](#func.calc_date_general_effect) described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
-It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
-
-::: {.noteblock data-latex=""}
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-:::
-
-::: { #func.calc_date_general_effect.cv.value .sidebar }
-##### Value
-\
-
-Data frame object representing (*regularized* if [lambda](#func.calc_date_general_effect.cv.args.lambda) argument value is non-default) *Date General Effect*.
-:::
-
-::: { #func.calc_date_general_effect.cv.code .sidebar }
-##### Source Code
-\
-
-Below is a simplified version of the source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L32) function:
-```{r eval=FALSE}
-calc_date_general_effect.cv <- function(lambda = 0){
-
-  date_general_effect_ls <- lapply(edx_CV,  function(cv_fold_dat){
-    cv_fold_dat$train_set |> calc_date_general_effect(lambda)
-  })
-  put_log1("Function `calc_date_general_effect.cv`:
-Date Global Effect list has been computed for %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  date_general_effect_united <- union_cv_results(date_general_effect_ls)
-
-  date_general_effect <- date_general_effect_united |>
-    group_by(days) |>
-    summarise(de = mean(de, na.rm = TRUE), year = mean(year, na.rm = TRUE))
-
-  if(lambda == 0) put_log("Function `calc_date_general_effect.cv`:
-Training completed: Date Global Effects model.")
-  else put_log1("Function `calc_date_general_effect.cv`:
-Training completed: Date Global Effects model for lambda: %1...",
-                lambda)
-
-  date_general_effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [calc_date_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L32) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L32) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) Function {#func.calc_UMGY_effect}
-\
-
-Builds the *User+Movie+Genre+Year Effect (UMGYE) Model* based on the *Date General Effect* data structure returned by the [calc_date_general_effect](#func.calc_date_general_effect) or [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_effect.args.date_general_effect) argument.
-
-::: { #func.calc_UMGY_effect.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  train_set |>
-    calc_date_general_effect(lambda) |>
-    calc_UMGY_effect()
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_UMGY_effect` is called internally from the [train_UMGY_effect](#func.train_UMGY_effect) function described below.
-:::
-:::
-
-::: { #func.calc_UMGY_effect.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_UMGY_effect.args.date_general_effect .sidebar }
-  - **date_general_effect:** Data frame object representing the *Date General Effect*;
-
-:::
-:::
-
-::: { #func.calc_UMGY_effect.details .sidebar }
-##### Details
-\
-
-This is a helper function that is intended to be used internally in the following functions (both described below in this section):
-
-  - [train_UMGY_effect](#func.train_UMGY_effect);
-
-  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).
-
-An example of using it in the [train_UMGY_effect](#func.train_UMGY_effect) function is shown above in the [Usage](#func.calc_UMGY_effect.usage) section of *this Description*:
-
-:::
-
-::: { #func.calc_UMGY_effect.value .sidebar }
-##### Value
-\
-
-Data frame object representing the *UMGYE Model*.
-:::
-
-::: { #func.calc_UMGY_effect.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) function is shown below:
-```{r eval=FALSE}
-calc_UMGY_effect <- function(date_general_effect){
-  date_general_effect |>
-    group_by(year) |>
-    summarise(ye = mean(de, na.rm = TRUE))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L71) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L76) Function {#func.train_UMGY_effect}
-\
-
-Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.train_UMGY_effect.args.train_set) argument.
-
-::: { #func.train_UMGY_effect.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  rglr.UMGY_effect <- edx |> train_UMGY_effect(UMGYE.rglr.best_lambda)
-```
-:::
-
-::: { #func.train_UMGY_effect.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_UMGY_effect.args.train_set .sidebar }
-  - **train_set:** Training sample of the `Movielens` dataset;
-
-:::
-::: { #func.train_UMGY_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.train_UMGY_effect.details .sidebar }
-##### Details
-\
-
-Internally, this function calls the helper functions [calc_date_general_effect](#func.calc_date_general_effect) and [calc_UMGY_effect](#func.calc_UMGY_effect) (both described above in this section).
-
-::: {.noteblock data-latex=""}
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-:::
-:::
-
-::: { #func.train_UMGY_effect.value .sidebar }
-##### Value
-\
-
-Data frame object representing the trained (and also *regularized* if [lambda](#func.train_UMGY_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
-:::
-
-::: { #func.train_UMGY_effect.code .sidebar }
-##### Source Code
-\
-
-The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L76) function is shown below:
-```{r eval=FALSE}
-train_UMGY_effect <- function(train_set, lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_UMGY_effect
-`lambda` is `NA`")
-  }
-
-  train_set |>
-    calc_date_general_effect(lambda) |>
-    calc_UMGY_effect()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L76) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L76) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) Function {#func.train_UMGY_effect.cv}
-\
-
-Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function (described below in section [UMGYE Model: Regularization] of *this Appendix*) as shown in the [Usage](#func.train_UMGY_effect.cv.usage) subsection of *This Function's Description Section* below.
-:::
-
-::: { #func.train_UMGY_effect.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  train_UMGY_effect.cv(lambda) |>
-    calc_UMGY_effect_RMSE.cv()
-```
-
-::: {.noteblock data-latex=""}
-In the above code snippet, the `train_UMGY_effect.cv` function is called internally from the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYE Model: Regularization] section and this section, respectively).
-:::
-:::
-
-::: { #func.train_UMGY_effect.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_UMGY_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.train_UMGY_effect.cv.details .sidebar }
-##### Details
-\
-
-Internally, this function calls the helper functions [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) (both described above in this section).
-
-::: {.noteblock data-latex=""}
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-:::
-:::
-
-::: { #func.train_UMGY_effect.cv.value .sidebar }
-##### Value
-\
-
-Data frame object representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.train_UMGY_effect.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) function is shown below:
-```{r eval=FALSE}
-train_UMGY_effect.cv <- function(lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_UMGY_effect.cv
-`lambda` is `NA`")
-  }
-
-  calc_date_general_effect.cv(lambda) |> calc_UMGY_effect()  
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L94) Function {#func.calc_UMGY_effect_MSE}
-\
-
-Validates the *UMGY Effect (UMGYE) Model* produced by the  [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call.
-
-::: { #func.calc_UMGY_effect_MSE.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-    cv_fold_dat$validation_set |> calc_UMGY_effect_MSE(UMGY_effect)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_UMGY_effect_MSE` is called internally from the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described below in this section.
-:::
-:::
-
-::: { #func.calc_UMGY_effect_MSE.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_UMGY_effect_MSE.args.test_set .sidebar }
-  - **test_set:** Validation dataset;
-
-:::
-::: { #func.calc_UMGY_effect_MSE.args.UMGY_effect .sidebar }
-  - **UMGY_effect:** Data frame object representing the *UMGY Effect Model*.
-
-:::
-:::
-
-::: { #func.calc_UMGY_effect_MSE.details .sidebar }
-##### Details
-\
-
-The function calculates *Mean Squared Error (MSE)* for the *UMGYE Model* passed in the [UMGY_effect](#func.calc_UMGY_effect_MSE.args.UMGY_effect) argument using the validation dataset passed in the [test_set](#func.calc_UMGY_effect_MSE.args.test_set) arg.
-
-::: {.noteblock data-latex=""}
-This auxiliary function is used internally in the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_effect_MSE.usage) subsection of *this Description* above.
-:::
-:::
-
-::: { #func.calc_UMGY_effect_MSE.value .sidebar }
-##### Value
-\
-
-*MSE* value calculated for the *UMGYE Model*.
-:::
-
-::: { #func.calc_UMGY_effect_MSE.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L94) function is shown below:
-```{r eval=FALSE}
-calc_UMGY_effect_MSE <- function(test_set, UMGY_effect){
-  test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    left_join(UMGY_effect, by='year') |>
-    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
-    pull(resid) |> mse()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L94) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L94) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) Function {#func.calc_UMGY_effect_MSE.cv}
-\
-
-Validates the *UMGY Effect (UMGYE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-This helper function is used internally in the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_effect_MSE.cv.usage) subsection of *This Function's Description Section* below.
-:::
-
-::: { #func.calc_UMGY_effect_MSE.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGY_effect))
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_UMGY_effect_MSE.cv` is called internally from the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described below in this section.
-:::
-:::
-
-::: { #func.calc_UMGY_effect_MSE.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_UMGY_effect_MSE.cv.args.UMGY_effect .sidebar }
-  - **UMGY_effect:** Data frame object representing the *UMGY Effect Model*.
-
-:::
-:::
-
-::: { #func.calc_UMGY_effect_MSE.cv.details .sidebar }
-##### Details
-\
-
-The function calculates *MSE* for the *UMGYE Model* passed in the [UMGY_effect](#func.calc_UMGY_effect_MSE.cv.args.UMGY_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_UMGY_effect_MSE](#func.calc_UMGY_effect_MSE) function for each iteration of the *K-Fold Cross-Validation*, calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object], and then calculates the mean of the obtained results.
-
-The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-:::
-
-::: { #func.calc_UMGY_effect_MSE.cv.value .sidebar }
-##### Value
-\
-
-The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.calc_UMGY_effect_MSE.cv.code .sidebar }
-##### Source Code
-\
-
-The simplified version of the source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) function is shown below:
-```{r eval=FALSE}
-calc_UMGY_effect_MSE.cv <- function(UMGY_effect){
-  start <- put_start_date()
-  UMGY_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> calc_UMGY_effect_MSE(UMGY_effect)
-  })
-  put_end_date(start)
-  put_log1("Function: calc_UMGY_effect_MSE.cv
-Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-
-  mean(UMGY_effect_MSEs)
-}
-```
-
-::: {.noteblock data-latex=""}
-The completed source code of the [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L104) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) Function {#func.calc_UMGY_effect_RMSE.cv}
-\
-
-Validates the *UMGY Effect (UMGYE) Model* (produced by the [train_UMGY_effect](#func.train_UMGY_effect) or [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function call) with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function described below in section [UMGYE Model: Regularization] of *this Appendix*.
-:::
-
-::: { #func.calc_UMGY_effect_RMSE.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-cv.UMGY_effect.RMSE <- calc_UMGY_effect_RMSE.cv(cv.UMGY_effect)
-```
-:::
-
-::: { #func.calc_UMGY_effect_RMSE.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_UMGY_effect_RMSE.cv.args.UMGY_effect .sidebar }
-  - **UMGY_effect:** Data frame object representing the *UMGY Effect Model*.
-
-:::
-:::
-
-::: { #func.calc_UMGY_effect_RMSE.cv.details .sidebar }
-##### Details
-\
-
-The function calculates *Root Squared Error (RMSE)* for the *UMGYE Model* passed in the [UMGY_effect](#func.calc_UMGY_effect_RMSE.cv.args.UMGY_effect) argument using the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_UMGY_effect_MSE.cv](#func.calc_UMGY_effect_MSE.cv) function described above, to calculate the *MSE* for the *UMGYE Model* with use of *K-Fold Cross-Validation*, and then calculates the square root of the result.
-
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-:::
-
-::: { #func.calc_UMGY_effect_RMSE.cv.value .sidebar }
-##### Value
-\
-
-The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.calc_UMGY_effect_RMSE.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) function is shown below:
-```{r eval=FALSE}
-calc_UMGY_effect_RMSE.cv <- function(UMGY_effect){
-  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGY_effect))
-  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
-           CVFolds_N, 
-           UMGY_effect_RMSE)
-
-  UMGY_effect_RMSE
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L120) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### UMGYE Model: Regularization
-\
-
-#### [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) Function {#func.regularize.test_lambda.UMGY_effect.cv}
-\
-
-Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGY_effect.cv.args.lambda) argument for the *User+Movie+Genre+Year Effect (UMGYE) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
-
-::: { #func.regularize.test_lambda.UMGY_effect.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  lambdas <- seq(0, 512, 32)
-  cv.UMGYE.preset.result <- 
-    tune.model_param(lambdas, 
-                     regularize.test_lambda.UMGY_effect.cv,
-                     steps.beyond_min = 16)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
-
-Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMGY_effect.cv.details) section of *this Description* below.
-:::
-:::
-
-::: { #func.regularize.test_lambda.UMGY_effect.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.regularize.test_lambda.UMGY_effect.cv.args.lambda .sidebar }
-  - **lambda:** *Regularization parameter* $\lambda$ used to validate the model in the *regularization process*.
-
-:::
-:::
-
-::: { #func.regularize.test_lambda.UMGY_effect.cv.details .sidebar }
-##### Details
-\
-
-The function is used in the *regularization process* of the *UMGYE Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMGY_effect.cv.args.lambda) argument) as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2].
-
-Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
-
-::: {.noteblock data-latex=""}
-This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
-:::
-:::
-
-::: { #func.regularize.test_lambda.UMGY_effect.cv.value .sidebar }
-##### Value
-\
-
-The *Root Mean Squared Errors (RMSE)* value computed for the UMGYE Model applying the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGY_effect.cv.args.lambda) argument.
-
-:::
-
-::: { #func.regularize.test_lambda.UMGY_effect.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) function is shown below:
-```{r eval=FALSE}
-regularize.test_lambda.UMGY_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UMGY_effect.cv
-`lambda` is `NA`")
-  }
-
-  train_UMGY_effect.cv(lambda) |>
-    calc_UMGY_effect_RMSE.cv()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [regularize.test_lambda.UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L129) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L130) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### UMGYDE Model: Utility Functions
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the  [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) script on _GitHub_.
-:::
-
-#### [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) Function {#func.calc_day_general_effect}
-\
-
-Computes the *Day General Effect* (hereafter *DG Effect* or *DGI* for short) (optionally *regularized* if the [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) of user ratings on a *given day since the earliest record* in the `edx` dataset, using a *training dataset* passed in the [train_set](#func.calc_day_general_effect.args.train_set) argument.
-
-::: { #func.calc_day_general_effect.usage .sidebar }
-##### Usage
-\
-```{r eval=FALSE}
-  train_set |> 
-    calc_day_general_effect(lambda) |>
-    calc_UMGY_SmoothedDay_effect(degree, span)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_day_general_effect` is called internally along with the [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function from the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function (both described below in this section).
-:::
-:::
-
-::: { #func.calc_day_general_effect.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_day_general_effect.args.train_set .sidebar }
-  - **train_set:** Training dataset containing data to compute the *DG Effect*;
-
-:::
-::: { #func.calc_day_general_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.calc_day_general_effect.details .sidebar }
-##### Details
-\
-
-This is a helper function that is intended for use in other helper functions such as [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (both described below in this section).
-
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-
-::: {.noteblock data-latex=""}
-*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
-:::
-:::
-
-::: { #func.calc_day_general_effect.value .sidebar }
-##### Value
-\
-
-Data frame object representing (*regularized* if [lambda](#func.calc_day_general_effect.args.lambda) argument value is non-default) *DG Effect*.
-:::
-
-::: { #func.calc_day_general_effect.code .sidebar }
-##### Source Code
-\
-
-Below is a slightly simplified version of the source code of the [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) function:
-```{r eval=FALSE}
-calc_day_general_effect <- function(train_set, lambda = 0){
-  gday_effect <- train_set |> 
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    left_join(rglr.UMGY_effect, by='year') |>
-    mutate(resid = rating - (mu + a + b + g + ye)) |>
-    group_by(days) |>
-    summarise(de = mean_reg(resid, lambda), 
-              year = mean(year))
-
-  if(lambda == 0) put_log("Function `calc_day_general_effect`:
-Day General Effect has been computed.")
-  else put_log1("Function `calc_day_general_effect`:
-Day General Effect has been computed for lambda: %1...",
-                lambda)
-  gday_effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [calc_day_general_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L4) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) Function {#func.calc_day_general_effect.cv}
-\
-
-This is a helper function that calculates the *Day General Effect* (optionally *regularizes* if the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) of the user ratings using the K-Fold Cross Validation_ and is intended to be used in other custom functions (such as [train_UMGY_effect](#func.train_UMGY_effect)) described below.
-
-::: { #func.calc_day_general_effect.cv.usage .sidebar }
-##### Usage
-\
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-In the above code snippet, the `calc_day_general_effect.cv` function is called internally from the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function, along with the [calc_UMGY_effect](#func.calc_UMGY_effect) function (both described below).
-:::
-:::
-
-::: { #func.calc_day_general_effect.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_day_general_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.calc_day_general_effect.cv.details .sidebar }
-##### Details
-\
-
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.calc_day_general_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-
-Internally, this function calls the helper functions [calc_day_general_effect](#func.calc_day_general_effect) function described above for each iteration of the *K-Fold Cross-Validation* applied to the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets].
-It also calls internally the [union_cv_results](#func.union_cv_results) function described above in the *Data Helper Functions / [Models Training Functions]* section of this *Appendix* to aggregate the cross-validation results.
-
-::: {.noteblock data-latex=""}
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-:::
-
-::: { #func.calc_day_general_effect.cv.value .sidebar }
-##### Value
-\
-
-Data frame object representing (*regularized* if [lambda](#func.calc_day_general_effect.cv.args.lambda) argument value is non-default) *Day General Effect*.
-:::
-
-::: { #func.calc_day_general_effect.cv.code .sidebar }
-##### Source Code
-\
-
-Below is a simplified version of the source code of the [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) function:
-```{r eval=FALSE}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [calc_day_general_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L33) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L71) Function {#func.loess_de}
-\
-
-Using local fitting, fits a polynomial surface determined by the *Day General Effect* (hereafter *DG Effect* or *DGE* for short) information passed in the [de_bias.dat](#func.loess_de.args.de_bias.dat) argument.
-
-::: {.noteblock data-latex=""}
-In *this Project*, the *DGE* data object to be passed in the [de_bias.dat](#func.loess_de.args.de_bias.dat) argument is returned by the [calc_day_general_effect](#func.calc_day_general_effect) and [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) functions (both described above).
-:::
-
-::: { #func.loess_de.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  fit <- day_gen_effect |> loess_de(degree, span)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the `loess_de` is called internally from the [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function described below.
-:::
-:::
-
-::: { #func.loess_de.args .sidebar }
-##### Arguments
-\
-
-::: { #func.loess_de.args.de_bias.dat .sidebar }
-###### ***de_bias.dat***
-\
-
-Data frame object representing the *Day General Effect* data.
-
-:::
-::: { #func.loess_de.args.degree .sidebar }
-###### ***degree***
-\
-
-(Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
-
-::: {.noteblock data-latex=""}
-When the value is `NA` (default), $1$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function. 
-:::
-:::
-::: { #func.loess_de.args.span .sidebar }
-###### ***span***
-\
-
-(Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
-
-::: {.noteblock data-latex=""}
-When the value is `NA` (default), $0.75$ is passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
-:::
-:::
-:::
-
-::: { #func.loess_de.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `R` function, which is called internally to make a required fit.
-
-::: {.noteblock data-latex=""}
-This is a helper function intended for use in other helper functions, such as the [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described below in this section.
-:::
-:::
-
-::: { #func.loess_de.value .sidebar }
-##### Value
-\
-
-Object of class `loess` returned by the internally called function [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess).
-:::
-
-::: { #func.loess_de.code .sidebar }
-##### Source Code
-\
-
-The source code of the [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L71) function is shown below:
-```{r eval=FALSE}
-loess_de <- function(de_bias.dat, degree = NA, span = NA){
-  if(is.na(degree)) degree = 1
-  if(is.na(span)) span = 0.75
-  loess(de ~ days, span = span, degree = degree, data = de_bias.dat)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L71) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L71) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) Function {#func.calc_UMGY_SmoothedDay_effect}
-\
-
-Builds the *User+Movie+Genre+Year+SmoothedDay Effect* (hereafter *UMGYDE* for short) *Model* based on the *Day General Effect* (*DG Effect* for short) data structure returned by the [calc_day_general_effect](#func.calc_day_general_effect) or [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) function (both described above) and passed in the [date_general_effect](#func.calc_UMGY_SmoothedDay_effect.args.date_general_effect) argument.
-
-::: { #func.calc_UMGY_SmoothedDay_effect.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  train_set |> 
-    calc_day_general_effect(lambda) |>
-    calc_UMGY_SmoothedDay_effect(degree, span)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_UMGY_SmoothedDay_effect` is called internally from the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described below.
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.args.date_general_effect .sidebar }
-  - **date_general_effect:** Data frame object representing the *DG Effect* (to pass in the [de_bias.dat](#func.loess_de.args.de_bias.dat) argument to the internally called [loess_de](#func.loess_de) described above);
-
-:::
-::: { #func.calc_UMGY_SmoothedDay_effect.args.degree .sidebar }
-  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above;
-
-:::
-::: { #func.calc_UMGY_SmoothedDay_effect.args.span .sidebar }
-  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above.
-
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.details .sidebar }
-##### Details
-\
-
-This auxiliary function is a wrapper for the [loess_de](#func.loess_de) described above, intended to be used internally in the following helper functions (both described below in this section):
-
-  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect);
-
-  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
-
-An example of using it in the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function is shown above in the [Usage](#func.calc_UMGY_SmoothedDay_effect.usage) section of *this Description*:
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.value .sidebar }
-##### Value
-\
-
-Data frame object representing the *UMGYDE Model*.
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.code .sidebar }
-##### Source Code
-\
-
-Below is a slightly simplified version of the source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) function:
-```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect <- function(day_gen_effect, 
-                                         degree = NA, 
-                                         span = NA){
-  fit <- day_gen_effect |> loess_de(degree, span)
-  smth_day_effect <- day_gen_effect |> mutate(de_smoothed = fit$fitted)
-
-  put_log2("Function `calc_UMGY_SmoothedDay_effect`: 
-Model has been trained using `loess` function with the following parameters:
-degree: %1;
-span: %2.",
-           degree,
-           span)
-
-  smth_day_effect
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [calc_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L76) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) Function {#func.train_UMGY_SmoothedDay_effect}
-\
-
-Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.train_UMGY_SmoothedDay_effect.args.train_set) argument.
-
-::: { #func.train_UMGY_SmoothedDay_effect.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  lss.UMGYD_effect <- edx |> 
-    train_UMGY_SmoothedDay_effect(lss.best_degree, lss.best_span)
-```
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.args.train_set .sidebar }
-  - **train_set:** Training sample of the `Movielens` dataset;
-
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
-  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;
-
-:::
-::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
-  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.
-
-:::
-::: { #func.train_UMGY_SmoothedDay_effect.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.details .sidebar }
-##### Details
-\
-
-Internally, this function calls the helper functions [calc_day_general_effect](#func.calc_day_general_effect) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.args.span) to the latter function in the same-named arguments.
-
-::: {.noteblock data-latex=""}
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.value .sidebar }
-##### Value
-\
-
-Data frame object representing the trained (and also *regularized* if [lambda](#func.train_UMGY_SmoothedDay_effect.args.lambda) argument value is non-default) *UMGYDE Model*.
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.code .sidebar }
-##### Source Code
-\
-
-The source code of the [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is shown below:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect <- function(train_set, 
-                                          degree = NA, 
-                                          span = NA,
-                                          lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_UMGY_SmoothedDay_effect
-`lambda` is `NA`")
-  }
-
-  train_set |> 
-    calc_day_general_effect(lambda) |>
-    calc_UMGY_SmoothedDay_effect(degree, span)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_SmoothedDay_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) Function {#func.train_UMGY_SmoothedDay_effect.cv}
-\
-
-Trains (and optionally *regularizes* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  train_UMGY_SmoothedDay_effect.cv(best_degree, 
-                                   best_span, 
-                                   lambda)
-```
-
-::: {.noteblock data-latex=""}
-In the above code snippet, the `train_UMGY_SmoothedDay_effect.cv` function is called internally from the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) function described below in section [UMGYDE Model: Regularization] of *this Appendix*.
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.cv.args.degree .sidebar }
-  - **degree:** (Integer, `NA` by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;
-
-:::
-::: { #func.train_UMGY_SmoothedDay_effect.cv.args.span .sidebar }
-  - **span:** (Numeric, `NA` by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.
-
-:::
-::: { #func.train_UMGY_SmoothedDay_effect.cv.args.lambda .sidebar }
-  - **lambda:** (0 by default) Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.cv.details .sidebar }
-##### Details
-\
-
-Internally, this function calls the auxiliary functions [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) (both described above in this section), passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) to the latter function in the same-named arguments.
-
-::: {.noteblock data-latex=""}
-This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively).
-The usage in the latter function is shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) section of *this Description* below.
-:::
-
-::: {.noteblock data-latex=""}
-The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.cv.value .sidebar }
-##### Value
-\
-
-Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) function is shown below:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect.cv <- function(degree = NA, 
-                                             span = NA,
-                                             lambda = 0){
-  if (is.na(lambda)) {
-    stop("Function: train_UMGY_SmoothedDay_effect.cv
-`lambda` is `NA`")
-  }
-
-  calc_day_general_effect.cv(lambda) |>
-    calc_UMGY_SmoothedDay_effect(degree, span)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) Function {#func.UMGY_SmoothedDay_effect.predict}
-\
-
-Predicts *user rating* values on the *test dataset* passed in the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) argument based on the data of the trained *UMGYD Effect (UMGYDE) Model* passed in the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) argument.
-
-::: { #func.UMGY_SmoothedDay_effect.predict.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-final.UMGYDE.predicted <- final_holdout_test |>
-  UMGY_SmoothedDay_effect.predict(rglr.day_smoothed_effect)
-```
-:::
-
-::: { #func.UMGY_SmoothedDay_effect.predict.args .sidebar }
-##### Arguments
-\
-
-::: { #func.UMGY_SmoothedDay_effect.predict.args.test_set .sidebar }
-  - **test_set:** Validation dataset;
-
-:::
-::: { #func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect .sidebar }
-  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.
-
-:::
-:::
-
-::: { #func.UMGY_SmoothedDay_effect.predict.details .sidebar }
-##### Details
-\
-
-This function implements an algorithm for computing the *user rating values* in accordance with the *mathematical description* of the *UMGYDE Model*, as described in section [Mathematical Description of the UMGYDE Model] of *this Report*.
-
-::: {.noteblock data-latex=""}
-This function is also called within other helper functions, such as the [calc_UMGY_SmoothedDay_effect.MSE](#func.calc_UMGY_SmoothedDay_effect.MSE) and [UMGYDE_model.predict](#func.UMGYDE_model.predict) described below in this section and [Matrix Factorization Functions] section of *this Appendix*, respectively.
-:::
-:::
-
-::: { #func.UMGY_SmoothedDay_effect.predict.value .sidebar }
-##### Value
-\
-
-Data frame object containing *predicted user rating* values based on the *UMGYDE Model*
-:::
-
-\newpage
-
-::: { #func.UMGY_SmoothedDay_effect.predict.code .sidebar }
-##### Source Code
-\
-
-The source code of the [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) function is shown below:
-```{r eval=FALSE}
-UMGY_SmoothedDay_effect.predict <- function(test_set, day_smoothed_effect) {
-  test_set |>
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    left_join(rglr.UMGY_effect, by='year') |>
-    left_join(day_smoothed_effect, by='days') |>
-    mutate(predicted = clamp(mu + a + b + g + 
-                               ifelse(is.na(ye), 0, ye) +
-                               ifelse(is.na(de_smoothed), 
-                                      0, 
-                                      de_smoothed))) |> 
-    select(userId, movieId, timestamp, rating, predicted)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [UMGY_SmoothedDay_effect.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L125) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) Function {#func.calc_UMGY_SmoothedDay_effect.MSE}
-\
-
-Validates the *UMGYD Effect (UMGYDE) Model* represented by the data passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect) argument on the *test dataset* passed in the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) argument.
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-    cv_fold_dat$validation_set |> 
-      calc_UMGY_SmoothedDay_effect.MSE(day_smoothed_effect)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_UMGY_SmoothedDay_effect.MSE` is called internally from the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) function described below in this section.
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set .sidebar }
-  - **test_set:** Validation dataset;
-
-:::
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect .sidebar }
-  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.
-
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.details .sidebar }
-##### Details
-\
-
-This function commits the *UMGYDE Model* validation by calculating the *Mean Squared Error (MSE)*.
-
-In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.loess_de.args.de_bias.dat) argument) is created and returned by the following functions described above in this section:
-
-  - [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)
-
-  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)
-
-  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
-
-Internally, this function calls the auxiliary functions [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) (described above in this section), passing to it the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect) value in the same-named argument.
-
-::: {.noteblock data-latex=""}
-This auxiliary function is used internally in the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.usage) section of *This Description* above.
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.value .sidebar }
-##### Value
-\
-
-*MSE* value calculated for the *UMGYDE Model*.
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) function is shown below:
-```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect.MSE <- function(test_set, day_smoothed_effect) {
-  test_set |>
-    UMGY_SmoothedDay_effect.predict(day_smoothed_effect) |>
-    mutate(resid = rating - predicted) |> 
-    pull(resid) |> mse()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_SmoothedDay_effect.MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L141) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L147) Function {#func.calc_UMGY_SmoothedDay_effect.MSE.cv}
-\
-
-Validates the *UMGYD Effect (UMGYDE) Model* represented by the data object passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) argument with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV] (we use $K = 5$ in *this Project*).
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  sqrt(calc_UMGY_SmoothedDay_effect.MSE.cv(day_smoothed_effect))
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above, the function `calc_UMGY_SmoothedDay_effect.MSE.cv` is called internally from the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function described below in this section.
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect .sidebar }
-  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.
-
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.details .sidebar }
-##### Details
-\
-
-This function commits the *UMGYDE Model* validation by calculating the *Mean Squared Error (MSE)* on the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_UMGY_SmoothedDay_effect.MSE](#func.calc_UMGY_SmoothedDay_effect.MSE) function for each iteration of the *K-Fold Cross-Validation*, passing [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) value in the same-named argument to the called function and calculating the *MSE* for the corresponding validation dataset of the [`edx_CV` Object].
-After that, it calculates the mean of the obtained results.
-
-The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in this section:
-
-  - [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)
-
-  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)
-
-  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
-
-::: {.noteblock data-latex=""}
-This is an auxiliary function that is called internally from the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.usage) section of *This Description* above.
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.value .sidebar }
-##### Value
-\
-
-The *MSE* value calculated for the *UMGYDE Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.code .sidebar }
-##### Source Code
-\
-
-The slightly simplified version of the source code of the [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L147) function is shown below:
-```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect.MSE.cv <- function(day_smoothed_effect){
-  smth_day_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
-    cv_fold_dat$validation_set |> 
-      calc_UMGY_SmoothedDay_effect.MSE(day_smoothed_effect)
-  })
-  put_end_date(start)
-  put_log1("Function `calc_UMGY_SmoothedDay_effect.MSE.cv`:
-MSE value have been computed for the %1-Fold Cross Validation samples.", 
-           CVFolds_N)
-  mean(smth_day_effect_MSEs)
-}
-```
-
-::: {.noteblock data-latex=""}
-The completed source code of the [calc_UMGY_SmoothedDay_effect.MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L147) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L147) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) Function {#func.calc_UMGY_SmoothedDay_effect.RMSE.cv}
-\
-
-Validates the *UMGYD Effect (UMGYDE) Model* represented by the data object passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) argument with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-lss.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(lss.UMGYD_effect)
-```
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect .sidebar }
-  - **day_smoothed_effect:** Data frame object representing the *UMGYDE Model*.
-
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.details .sidebar }
-##### Details
-\
-
-This function commits the *UMGYDE Model* validation by calculating the *Root Mean Squared Error (RMSE)* on the validation datasets contained in the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets].
-
-::: {.noteblock data-latex=""}
-This function internally calls the [calc_UMGY_SmoothedDay_effect.MSE.cv](#func.calc_UMGY_SmoothedDay_effect.MSE.cv) auxiliary function described above in this section to compute the *MSE* for the *UMGYDE Model* and then calculates the *square root* of the obtained result.
-:::
-
-In *this Project*, the *UMGYDE* data object representing the *UMGYDE Model* (and being passed in the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) argument) is created and returned by the following functions described above in this section:
-
-  - [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect)
-
-  - [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect)
-
-  - [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv).
-
-::: {.noteblock data-latex=""}
-This function is also called internally as an auxiliary function from the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) functions described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization], respectively, of *this Appendix*.
-:::
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.value .sidebar }
-##### Value
-\
-
-The *RMSE* value calculated for the *UMGYDE Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) function is shown below:
-```{r eval=FALSE}
-calc_UMGY_SmoothedDay_effect.RMSE.cv <- function(day_smoothed_effect){
-  sqrt(calc_UMGY_SmoothedDay_effect.MSE.cv(day_smoothed_effect))
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [calc_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L169) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### UMGYDE Model: Tuning `loess` Params
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the  [Tuning `loess` Parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L172) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L172) script on _GitHub_.
-:::
-
-#### [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L173) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv}
-\
-
-Trains and validate (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the given [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters passed in the corresponding arguments ([degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span)), with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 1, span)
-```
-
-::: {.noteblock data-latex=""}
-In the above code snippet, the `train_UMGY_SmoothedDay_effect.RMSE.cv` function is called internally from the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) function described below in this section.
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree .sidebar }
-  - **degree:** (Integer, `NA` by default) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the degree of the polynomials to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above;
-
-:::
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span .sidebar }
-  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) described above.
-
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.details .sidebar }
-##### Details
-\
-
-This is a wrapper for the function [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described above in section [UMGYDE Model: Utility Functions] of *this Appendix*) it calls internally, passing the values of the arguments [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) in the same-named arguments.
-
-Unlike the internal function  [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv), this one also validates the *UMGYDE Model* created and trained by that function, for which it calls internally another helper function, [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) (also described above in the [UMGYDE Model: Utility Functions] section), computing *RMSE* for that model.
-
-::: {.noteblock data-latex=""}
-This is an auxiliary  function intended to be called internally from the following helper functions (described below in this section), specifically designed for tuning the `degree` and `span` [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters:
-
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0): a helper function designed for tuning the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter while keeping the `degree` parameter fixed at $0$;
-
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1): a helper function designed for tuning the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter while keeping the `degree` parameter fixed at $1$;
-
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2): a helper function designed for tuning the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter while keeping the `degree` parameter fixed at $2$;
-
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.value .sidebar }
-##### Value
-\
-
-The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters passed in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) arguments, and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.code .sidebar }
-##### Source Code
-\
-
-The slightly simplified version of the source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L173) function is shown below:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect.RMSE.cv <- function(degree = NA, span = NA) {
-  smth_de.RMSE <- train_UMGY_SmoothedDay_effect.cv(degree, span) |>
-    calc_UMGY_SmoothedDay_effect.RMSE.cv()
-
-  put_log2("Function `train_UMGY_SmoothedDay_effect.RMSE.cv`:
-RMSE has been computed for the `loess` function parameters: 
-degree = %1, span = %2.", 
-           degree,
-           span)
-
-  smth_de.RMSE
-}
-```
-
-::: {.noteblock data-latex=""}
-The complete source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L173) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L173) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0}
-\
-
-Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument and the `degree` parameter equals $0$.
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  lss.UMGYDE.preset.degree0.result <- 
-    tune.model_param(spans, train_UMGY_SmoothedDay_effect.RMSE.cv.degree0)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree0` function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span .sidebar }
-  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
-
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing it the following [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters :
-
-  - $0$ in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument;
-
-  - The [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument value (of this function) in the same-named argument [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span).
-
-::: {.noteblock data-latex=""}
-This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.value .sidebar }
-##### Value
-\
-
-The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 0` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-\newpage
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.code .sidebar }
-##### Source Code
-\
-
-The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) function is shown below:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect.RMSE.cv.degree0 <- function(span) {
-  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 0, span)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L192) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1}
-\
-
-Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument and the `degree` parameter equals $1$.
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-lss.UMGYDE.fine_tune.degree1.result <- 
-  model.tune.param_range(lss.fine_tune.loop_starter,
-                         UMGYDE.fine_tune.degree1.data.path,
-                         cache_file.base_name,
-                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree1)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span .sidebar }
-  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
-
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing it the following [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters :
-
-  - $1$ in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument;
-
-  - The [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument value (of this function) in the same-named argument [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span).
-
-::: {.noteblock data-latex=""}
-This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.value .sidebar }
-##### Value
-\
-
-The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 1` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.code .sidebar }
-##### Source Code
-\
-
-The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) function is shown below:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect.RMSE.cv.degree1 <- function(span) {
-  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 1, span)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L195) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2}
-\
-
-Trains and validates (without *regularization*) the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument and the `degree` parameter equals $2$.
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-lss.UMGYDE.fine_tune.degree2.result <- 
-  model.tune.param_range(lss.fine_tune.loop_starter,
-                         UMGYDE.fine_tune.degree2.data.path,
-                         cache_file.base_name,
-                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree2)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args .sidebar }
-##### Arguments
-\
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span .sidebar }
-  - **span:** (Numeric, `NA` by default ) *The [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameter*: the parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above.
-
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the function [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) (described above in this section) that it calls internally, passing it the following [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters :
-
-  - $2$ in the [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) argument;
-
-  - The [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument value (of this function) in the same-named argument [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span).
-
-::: {.noteblock data-latex=""}
-This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
-:::
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.value .sidebar }
-##### Value
-\
-
-The *RMSE* value calculated for the *UMGYDE Model* fitted for the given [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters (`degree = 2` and the `span` value passed in the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) argument), and trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
-:::
-
-::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.code .sidebar }
-##### Source Code
-\
-
-The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) function is shown below:
-```{r eval=FALSE}
-train_UMGY_SmoothedDay_effect.RMSE.cv.degree2 <- function(span) {
-  train_UMGY_SmoothedDay_effect.RMSE.cv(degree = 2, span)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L198) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### UMGYDE Model: Regularization
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the  [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) script on _GitHub_.
-:::
-
-#### [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L225) Function {#func.regularize.train_UMGYD_effect}
-\
-
-Trains and *regularizes* the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for a given value of the parameter $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument and preliminary figured out *best values* of the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters, using the training set of the `Movielens` dataset passed in the [train_set](#func.regularize.train_UMGYD_effect.args.train_set) argument.
-
-::: { #func.regularize.train_UMGYD_effect.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  rglr.UMGYD_effect <- edx |> 
-    regularize.train_UMGYD_effect(UMGYDE.rglr.best_lambda)
-```
-:::
-
-::: { #func.regularize.train_UMGYD_effect.args .sidebar }
-##### Arguments
-\
-
-::: { #func.regularize.train_UMGYD_effect.args.train_set .sidebar }
-  - **train_set:** Training sample of the `Movielens` dataset;
-
-:::
-::: { #func.regularize.train_UMGYD_effect.args.lambda .sidebar }
-  - **lambda:** Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.regularize.train_UMGYD_effect.details .sidebar }
-##### Details
-\
-
-This function is a wrapper for the function [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) (described above in section [UMGYDE Model: Utility Functions] of *this Appendix*) that it calls internally, passing it the best values of the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters `degree` and `span` in the corresponding arguments ([degree](#func.train_UMGY_SmoothedDay_effect.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.args.span), respectively)
-
-::: {.noteblock data-latex=""}
-The *UMGYDE Model* is regularized using the *regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-:::
-:::
-
-::: { #func.regularize.train_UMGYD_effect.value .sidebar }
-##### Value
-\
-
-Data frame object representing the *UMGYDE Model*, regularized by the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument) and tuned for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) *best parameters* `degree` and `span`.
-:::
-
-::: { #func.regularize.train_UMGYD_effect.code .sidebar }
-##### Source Code
-\
-
-The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L225) function is shown below:
-```{r eval=FALSE}
-regularize.train_UMGYD_effect <- function(train_set, lambda) {
-  best_degree <- lss.UMGYDE.best_params["degree"]
-  best_span <- lss.UMGYDE.best_params["span"]
-
-  train_set |>
-    train_UMGY_SmoothedDay_effect(best_degree, 
-                                  best_span, 
-                                  lambda)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L225) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L225) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L234) Function {#func.regularize.train_UMGYD_effect.cv}
-\
-
-Trains and *regularizes* the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* for a given value of the parameter $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument and preliminary figured out *best values* of the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters, with use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
-
-::: {.noteblock data-latex=""}
-The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
-:::
-
-::: { #func.regularize.train_UMGYD_effect.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-  regularize.train_UMGYD_effect.cv(lambda) |>
-    calc_UMGY_SmoothedDay_effect.RMSE.cv()
-```
-
-::: {.noteblock data-latex=""}
-In the above code snippet, the `regularize.train_UMGYD_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function described below in this section, along with the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) function described above in section [UMGYDE Model: Utility Functions].
-:::
-:::
-
-::: { #func.regularize.train_UMGYD_effect.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.regularize.train_UMGYD_effect.cv.args.lambda .sidebar }
-  - **lambda:** Regularization parameter $\lambda$.
-
-:::
-:::
-
-::: { #func.regularize.train_UMGYD_effect.cv.details .sidebar }
-##### Details
-\
-
-This is an auxiliary function intended to be called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in this section) as shown in the [Usage](#func.calc_UMGY_SmoothedDay_effect.MSE.usage) section of *this Description* above.
-
-The function is a wrapper for the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described above in section [UMGYDE Model: Utility Functions] of *this Appendix*) that it calls internally, passing it the best values of the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters `degree` and `span` in the corresponding arguments ([degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span), respectively)
-
-::: {.noteblock data-latex=""}
-The *UMGYDE Model* is regularized using the *regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
-:::
-:::
-
-::: { #func.regularize.train_UMGYD_effect.cv.value .sidebar }
-##### Value
-\
-
-Data frame object representing the *UMGYDE Model*, tuned for the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) *best parameters* `degree` and `span`, trained with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$), and regularized by the given *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument.
-:::
-
-::: { #func.regularize.train_UMGYD_effect.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L234) function is shown below:
-```{r eval=FALSE}
-regularize.train_UMGYD_effect.cv <- function(lambda) {
-  best_degree <- lss.UMGYDE.best_params["degree"]
-  best_span <- lss.UMGYDE.best_params["span"]
-
-  train_UMGY_SmoothedDay_effect.cv(best_degree, 
-                                   best_span, 
-                                   lambda)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [regularize.train_UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L234) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L234) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-#### [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) Function {#func.regularize.test_lambda.UMGYD_effect.cv}
-\
-
-Validates the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.args.lambda) argument for the *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* in the *regularization process* using *penalized approach* with use of *K-Fold Cross-Validation*.
-
-::: { #func.regularize.test_lambda.UMGYD_effect.cv.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-UMGYDE.rglr.fine_tune.results <- 
-  model.tune.param_range(UMGYDE.loop_starter,
-                         UMGYDE.rglr.fine_tune.cache.path,
-                         cache.base_name,
-                         regularize.test_lambda.UMGYD_effect.cv)
-```
-
-::: {.noteblock data-latex=""}
-In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
-
-Such a use of this function is also noted in the [Details](#func.regularize.test_lambda.UMGYD_effect.cv.details) section of *this Description* below.
-:::
-:::
-
-::: { #func.regularize.test_lambda.UMGYD_effect.cv.args .sidebar }
-##### Arguments
-\
-
-::: { #func.regularize.test_lambda.UMGYD_effect.cv.args.lambda .sidebar }
-  - **lambda:** *Regularization parameter* $\lambda$ used to validate the model in the *regularization process*.
-
-:::
-:::
-
-::: { #func.regularize.test_lambda.UMGYD_effect.cv.details .sidebar }
-##### Details
-\
-
-The function is used in the *regularization process* of the *UMGYDE Model* using the *penalized approach* to regularize predictions for the given *regularization parameter* $\lambda$ (passed in the [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.args.lambda) argument) as explained in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2].
-
-Internally it uses the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) (described above in this section) and [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) functions (described in section [UMGYDE Model: Utility Functions] above) to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
-
-::: {.noteblock data-latex=""}
-This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
-:::
-:::
-
-::: { #func.regularize.test_lambda.UMGYD_effect.cv.value .sidebar }
-##### Value
-\
-
-The *Root Mean Squared Errors (RMSE)* value computed for the UMGYDE Model applying the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.args.lambda) argument.
-
-:::
-
-::: { #func.regularize.test_lambda.UMGYD_effect.cv.code .sidebar }
-##### Source Code
-\
-
-The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) function is shown below:
-```{r eval=FALSE}
-regularize.test_lambda.UMGYD_effect.cv <- function(lambda){
-  if (is.na(lambda)) {
-    stop("Function: regularize.test_lambda.UMGYD_effect.cv
-`lambda` is `NA`")
-  }
-
-  regularize.train_UMGYD_effect.cv(lambda) |>
-    calc_UMGY_SmoothedDay_effect.RMSE.cv()
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) script on _GitHub_.
-:::
-:::
-
-\newpage
-
-### Matrix Factorization Functions
-\
-
-::: {.noteblock data-latex=""}
-The complete source code of the functions described in this section is available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R) script on _GitHub_.
-:::
-
-#### [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) Function {#func.mf.residual.dataframe}
-\
-
-::: { #func.mf.residual.dataframe.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.mf.residual.dataframe.args .sidebar }
-##### Arguments
-\
-
-::: { #func.mf.residual.dataframe.args.file_name .sidebar }
-  - **train_set:** ;
-
-:::
-:::
-
-::: { #func.mf.residual.dataframe.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.mf.residual.dataframe.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.mf.residual.dataframe.code .sidebar }
-##### Source Code
-\
-
-The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) function is shown below:
-```{r eval=FALSE}
-mf.residual.dataframe <- function(train_set){
-  train_set |> 
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    left_join(rglr.UMGY_effect, by='year') |>
-    left_join(rglr.UMGYD_effect, by='days') |>
-    mutate(rsdl = rating - (mu + a + b + g + ye + de_smoothed)) |>
-    select(userId, movieId, rsdl)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) script on _GitHub_.
-:::
-:::
-
-#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) Function {#func.UMGYDE_model.predict}
-\
-
-::: { #func.UMGYDE_model.predict.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.UMGYDE_model.predict.args .sidebar }
-##### Arguments
-\
-
-::: { #func.UMGYDE_model.predict.args.file_name .sidebar }
-  - **test_set:** ;
-
-:::
-:::
-
-::: { #func.UMGYDE_model.predict.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.UMGYDE_model.predict.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.UMGYDE_model.predict.code .sidebar }
-##### Source Code
-\
-
-The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is shown below:
-```{r eval=FALSE}
-UMGYDE_model.predict <- function(test_set) {
-  test_set |>
-    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) script on _GitHub_.
-:::
-:::
-
-# Appendix B: Models Training Datasets {#appndx_b}
-\
-
-## `edx.mx` Matrix Object {#appndx_b.edx.mx}
-\
-
-We use the array representation described in [Section 17.6 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook (New Edition)_, for the training data[@IDS2_17-6].
-For this purpose, we will convert the `edx` dataset into a matrix using the [tidyr::pivot_wider](https://www.rdocumentation.org/packages/tidyr/versions/1.3.0/topics/pivot_wider) function:
-
-```{r eval=FALSE}
-
-  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
-  edx.mx <- edx |> 
-    mutate(userId = factor(userId),
-           movieId = factor(movieId)) |>
-    select(movieId, userId, rating) |>
-    pivot_wider(names_from = movieId, values_from = rating) |>
-    column_to_rownames("userId") |>
-    as.matrix()
-
-  put_log("Function: `make_source_datasets`:
-Matrix created: `edx.mx` of the following dimentions:")
-  put(dim(edx.mx))
-```
-
-::: {.noteblock data-latex=""}
-To create the `edx.mx` object, the above code snippet is used in the [make_source_datasets](#func.make_source_datasets) function described in the [Initializing Input Datasets] section of [Appendix A: Support Functions].
-:::
-
-```{r}
-  str(edx.mx)
-```
-
-\newpage
-
-## `edx.sgr` Object {#appndx_b.edx.sgr}
-\
-
-To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: 
-To account for the Movie Genre Effect, we need a dataset with split rows 
-for movies belonging to multiple genres.")
-  edx.sgr <- splitGenreRows(edx)
-```
-
-::: {.noteblock data-latex=""}
-To create the `edx.sgr` object, the above code snippet is used in the [make_source_datasets](#func.make_source_datasets) function described in the [Initializing Input Datasets] section of [Appendix A: Support Functions].
-
-The custom function [splitGenreRows](#func.splitGenreRows) used in the code snippet to split the rows of the original dataset (`edx` in this case) is described in the [Data Processing Functions] section of [Appendix A: Support Functions].
-:::
-
-```{r}
-str(edx.sgr)
-summary(edx.sgr)
-```
-
-\newpage
-
-## `movie_map` Object {#appndx_b.movie_map}
-\
-
-To be able to map movie IDs to titles we create the following lookup table:
-```{r eval=FALSE}
-movie_map <- edx |> select(movieId, title, genres) |> 
-    distinct(movieId, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
-```
-
-::: {.noteblock data-latex=""}
-To create the `movie_map` object, the above code snippet is used in the [make_source_datasets](#func.make_source_datasets) function described in the [Initializing Input Datasets] section of [Appendix A: Support Functions].
-:::
-
-```{r}
-str(movie_map)
-summary(movie_map)
-```
-
-Note that titles cannot be considered unique, so we cannot use them as IDs[@IDS2_24-1].
-
-\newpage
-
-## `date_days_map` Object {#appndx_b.date_days_map}
-\
-
-We have a `timestamp` field in the `edx` dataset.
-To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
-```{r eval=FALSE}
-  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
-  date_days_map <- edx |>
-    mutate(date_time = as_datetime(timestamp)) |>
-    mutate(date = as_date(date_time)) |>
-    mutate(year = year(date_time)) |>
-    mutate(days = as.integer(date - min(date))) |>
-    select(timestamp, date_time, date, year, days) |>
-    distinct(timestamp, .keep_all = TRUE)
-
-  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
-```
-
-::: {.noteblock data-latex=""}
-To create the `date_days_map` object, the above code snippet is used in the [make_source_datasets](#func.make_source_datasets) function described in the [Initializing Input Datasets] section of [Appendix A: Support Functions].
-:::
-
-``` {r}
-  str(date_days_map)
-  summary(date_days_map)
-```
-
-\newpage
-
-## `edx_CV` Object {#appndx_b.edx_CV}
-\
-
-`edx_CV` object is a list of sample objects we need to perform the *K-Fold Cross-Validation* 
-as explained in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV]:
-```{r eval=FALSE}
-  start <- put_start_date()
-  edx_CV <- lapply(kfold_index,  function(fold_i){
-
-    put_log1("Method `make_source_datasets`: 
-Creating K-Fold Cross-Validation Datasets, Fold %1", fold_i)
-
-    #> We split the initial datasets into training sets, which we will use to build 
-    #> and train our models, and validation sets in which we will compute the accuracy 
-    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
-    #> of the Course Textbook.
-
-    split_sets <- edx |>
-      sample_train_validation_sets(fold_i*1000)
-
-    train_set <- split_sets$train_set
-    validation_set <- split_sets$validation_set
-
-    put_log("Function: `make_source_datasets`: 
-Sampling 20% from the split-row version of the `edx` dataset...")
-    split_sets.gs <- edx.sgr |>
-      sample_train_validation_sets(fold_i*2000)
-
-    train.sgr <- split_sets.gs$train_set
-    validation.sgr <- split_sets.gs$validation_set
-
-    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
-    # put(summary(validation.sgr))
-
-    #> We will use the array representation described in `Section 17.5 of the Textbook`
-    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
-    #> for the training data. 
-    #> To create this matrix, we use `tidyr::pivot_wider` function:
-
-    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
-    train_mx <- train_set |> 
-      mutate(userId = factor(userId),
-             movieId = factor(movieId)) |>
-      select(movieId, userId, rating) |>
-      pivot_wider(names_from = movieId, values_from = rating) |>
-      column_to_rownames("userId") |>
-      as.matrix()
-
-    put_log("Function: `make_source_datasets`:
-Matrix created: `train_mx` of the following dimentions:")
-    put(dim(train_mx))
-
-    list(train_set = train_set,
-         train_mx = train_mx,
-         train.sgr = train.sgr,
-         validation_set = validation_set)
-  })
-  put_end_date(start)
-  put_log("Function: `make_source_datasets`: 
-Set of K-Fold Cross-Validation datasets created: edx_CV")
-```
-
-To create the `edx_CV` object, the above code snippet is used in the [make_source_datasets](#func.make_source_datasets) function described in the [Initializing Input Datasets] section of [Appendix A: Support Functions].
-
-The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the list composing the `edx_CV` object. In *this Project*, we choose $K = 5$.
-
-::: {.noteblock data-latex=""}
-The custom function [sample_train_validation_sets](#func.sample_train_validation_sets) used in the code snippet to split the original dataset (`edx` in this case) into *train* and *validation* datasets, is described in the [Data Processing Functions] section of [Appendix A: Support Functions].
-:::
-
-```{r}
-str(edx_CV)
-```
-
-\newpage

### 2025-12-21 reports/capstone-movielens.site/02.5.UME-model.Rmd
Fix for the `XXXX Model Regularization: Fine-tuning` sections of the report.

@@
 ```
+```{r, echo=FALSE}
+writeLines("*** Values of the endpoints and the divisor for the interval of `lambda` values ***")
+```
 ```{r}
@@
 
-Below are the results of fine-tuning the *UMGYE Model*:
+Below are the results of fine-tuning the *UME Model*:
 

### 2025-12-21 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Fix for the `XXXX Model Regularization: Fine-tuning` sections of the report.

@@
 
-Below are the results of fine-tuning the *UMGYE Model*:
+Below are the results of fine-tuning the *UMGE Model*:
 

### 2025-12-22 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Code chunks: global refactoring.

@@
 
-We can now construct predictors and calculate the *RMSE* of the current model as shown in the code snippet below:
-
+We can now validate the current model by computing the *RMSE* for the *UMGY* Effect using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L):
 ```{r, eval=FALSE}
@@
 
-#### UMGYE Model Regularization: Retraining Model with the best $\lambda$
+#### UMGYE Model Regularization: Retraining the Model with the best $\lambda$
 \
@@
 
-Now, we can refine our _User+Movie+Genre+Year Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie+Genre+Year Effect Model* or *Regularized UMGYE Model* for short), for the definitive _RMSE_ calculation and use in subsequent models:
+Now, we can refine our *User+Movie+Genre+Year Effect (UMGYE) Model* by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie+Genre+Year Effect Model* or *Regularized UMGYE Model* for short), for the definitive *RMSE* calculation and use in subsequent models.
 
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1333) performs this operation:
 ```{r, eval=FALSE}
@@
 UMGYE.rglr.best_lambda <- best_result["param.best_value"]
+
+put_log1("Re-training Regularized User+Movie+Genre+Year Effect Model for the best `lambda`: %1...",
+         UMGYE.rglr.best_lambda)
 
@@
 ```{r, echo=FALSE}
-writeLines("*** The Best UMG Effect Fine-tuning Results ***")
+writeLines("*** The Best UMGY Effect Fine-tuning Results ***")
 ```
@@
 ```{r, echo=FALSE}
-writeLines("*** Regularized UMG Effect Structure ***")
+writeLines("*** Regularized UMGY Effect Structure ***")
 ```
@@
 
-print_log1("Regularized UMGE Model has been re-trained for the best `lambda`: %1.",
+print_log1("Regularized UMGYE Model has been re-trained for the best `lambda`: %1.",
          UMGYE.rglr.best_lambda)
@@
 
-Finally, we calculate the *RMSE* for the ultimately *Regularized UMGYE Model* and add the definitive result to our _Result Table_:
+Finally, we calculate the *RMSE* for the ultimately *Regularized UMGYE Model* and add the definitive result to our *Result Table*:
 ```{r, eval=FALSE}

### 2025-12-22 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Code chunks: global refactoring.

@@
 
-#### UMGYDE Model Regularization: Retraining Model with the best $\lambda$
+#### UMGYDE Model Regularization: Retraining the Model with the best $\lambda$
 \
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code shown in this section is available in the [UMGYDE Regularized Model: Retraining with the best params](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2417) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2417) script on _GitHub_.
+The complete version of the source code shown in this section is available in the [UMGYDE Model Regularization: Retraining with the best params](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2148) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2148) script on _GitHub_.
 :::
 
-Now, we can compute the _Regularized UMGYDE Effect_ by re-training our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we have just figured out and use it in subsequent analysis.
+Now, we can refine our *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie+Genre+Year+SmoothedDay Effect Model* or *Regularized UMGYDE Model* for short), for the definitive *RMSE* calculation and use in subsequent models:
 
-The most significant part of the code for this operation is shown below: 
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2161) performs this operation:
 ```{r, eval=FALSE}
@@
 UMGYDE.rglr.best_lambda <- best_result["param.best_value"]
-  UMGYDE.rglr.best_RMSE <- best_result["best_RMSE"]
 
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above we use the [regularize.train_UMGYD_effect](#func.regularize.train_UMGYD_effect) function described in the *Models Training: Support Functions /* [UMGYDE Model: Regularization] section of [Appendix A](#appndx_a).
+:::
+
+```{r, echo=FALSE}
+writeLines("*** The Best UMGYD Effect Fine-tuning Results ***")
+```
+```{r}
+UMGYDE.rglr.fine_tune.results$best_result
+```
+
+```{r, echo=FALSE}
+writeLines("*** Regularized UMGYD Effect Structure ***")
+```
 ```{r}
   str(rglr.UMGYD_effect)
+
+print_log1("Regularized UMGYDE Model has been re-trained for the best `lambda`: %1.",
+         UMGYDE.rglr.best_lambda)
 ```
-
-::: {.noteblock data-latex=""}
-Here we use the helper function [regularize.train_UMGYD_effect](#func.regularize.train_UMGYD_effect) described above in the [UMGYDE Model: Helper Functions] section.
-:::
 

### 2025-12-22 r/src/capstone-movielens.main.R

@@ -2189,6 +2189,7 @@ if (file.exists(file_path_tmp)) {
        rglr.UMGY_effect,
        rglr.UMGYD_effect,
        rglr.UMGYD_effect.RMSE,
+       UMGYDE.rglr.best_lambda,
        file = file_path_tmp)
   put_end_date(start)
   put_log1("User+Movie+Genre+Year+(Smoothed)Day Effect Model data has been saved to file: %1", 

### 2025-12-22 reports/capstone-movielens.site/02-3.OMR-model.Rmd

@@
 
-We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings:
-
-```{r pressure, echo=TRUE}
+We know that the estimate that minimizes the RMSE is the least squares estimate of $\mu$ and, in this case, is the average of all ratings.
+We calculate this using the folowing [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L106):
+```{{r main-script-l106, echo=TRUE, }
 mu <- mean(edx$rating)
-print(mu)
+mu
 ```
 
-If we predict all unknown ratings with $\hat{\mu}$, we can obtain RMSE as follows:: 
-```{r}
+If we predict all unknown ratings with $\hat{\mu}$, we can obtain *RMSE* using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L108):
+```{r main-script-l08 }
 mu.MSEs <- naive_model_MSEs(mu)
@@
 
-  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model: Helper Functions]) to compute *Mean Squared Errors* with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
+  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model: Helper Functions]) to compute *Mean Squared Errors* (hereafter *MSE* for short) with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
 
-  - [data.plot](#func.data.plot) (described in section [Data Visualization Functions]) for the _Mean Squared Errors_ data visualization.
+  - [data.plot](#func.data.plot) (described in section [Data Visualization Functions]) for the *MSE* data visualization.
 
@@
 
-If we plug in any other number, we will get a higher *RMSE*. Let's prove that by the following small investigation:
-```{r }
+If we plug in any other number, we will get a higher *RMSE*.
+Let's prove this with a small experiment using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L155):
+```{r main-script-l155 }
   deviation <- seq(0, 6, 0.1) - 3
@@
 
-Let's make a quick investigation of the `deviation.RMSE` result we have just got: 
-```{r}
+Let's quickly analyze the resulting `deviation.RMSE` vector we have just got.
+The following [data visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L189) code will help us with this:
+```{r main-script-l189}
 data.frame(delta = deviation, 
@@
 
-```{r eval=FALSE}
+Finally, we add the *RMSE* value calculated for the *OMR Model* to our *Result Table* and print the table using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L200):
+```{r main-script-l200, eval=FALSE}
 RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 

### 2025-12-22 reports/capstone-movielens.site/02.4.UE-model.Rmd

@@
 
-These considerations alows us to compute a _User Mean Ratings_ the following way:
+These considerations allow us to compute a _User Mean Ratings_ using the following [piece code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L231):
 ```{r eval=FALSE}
@@
 
-And then we compute a _User Effect_ this way:
+And then we compute a _User Effect_ using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L290):
 ```{r eval=FALSE}
@@
 
-Now, we are ready to compute the _Mean Squared Errors_ for samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A](#appndx_a)).
+Now, we are ready to compute the *Mean Squared Errors (MSE)* for samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A](#appndx_a)).
 
@@
 
-The code that performs this operation is shown below:
+The [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L345) that performs this operation is shown below:
 ```{r eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Visualization Functions](#appndx_a.data_helper.functions) section of [Appendix A](#appndx_a).
+For the *MSE* data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Visualization Functions](#appndx_a.data_helper.functions) section of [Appendix A](#appndx_a).
 :::
 
-Finally, we calculate the `RMSE` as the _square root_ of the average of the _Mean Squared Errors_ we obtained through the _5-Fold Cross-Validation_ above:   
+We can now calculate the *Root Mean Squared Error (RMSE)* for the current model as a *square root* of the average of the *MSE* values we obtained above, using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L364):
 ```{r, eval=FALSE}
 edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
+```
 
+Finally, we add the *RMSE* value calculated for the *UE Model* to our *Result Table* and print the table using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L372):
+```{r, eval=FALSE}
 RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 

### 2025-12-22 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_24-1_ME]:
+We can now construct predictors and see how much the `RMSE` improves[@IDS2_24-1_ME].
+
+The following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L513) allows us to perform this task:
 ```{r eval=FALSE}
 cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
+```
 
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
+Finally, we add the obtained result to our *Result Table* and print the table using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L):
+```{r eval=FALSE}
 RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
@@
 
-  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section) to calculate the *RMSE* for the *Current Model*;
+  -  to calculate the *RMSE* for the *Current Model*;
 
@@
 
-#### UME Model Regularization: Retraining Model with the best $\lambda$
+#### UME Model Regularization: Retraining the Model with the best $\lambda$
 \
@@
 
-Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model* or *Regularized UME Model* for short), for the definitive _RMSE_ calculation and use in subsequent models:
+Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model* or *Regularized UME Model* for short), for the definitive _RMSE_ calculation and use in subsequent models.
+
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L664) performs this operation:
 ```{r, eval=FALSE}
@@
 UME.rglr.best_lambda <- best_result["param.best_value"]
+
+put_log1("Re-training Regularized User+Movie Effect Model for the best `lambda`: %1...",
+         UME.rglr.best_lambda)
 

### 2025-12-22 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

@@
 
-#### UMGE Model Regularization: Retraining Model with the best $\lambda$
+#### UMGE Model Regularization: Retraining the Model with the best $\lambda$
 \
@@
 
-Now, we can refine our _User+Movie+Genre Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie+Genre Effect Model* or *Regularized UMGE Model* for short), for the definitive _RMSE_ calculation and use in subsequent models:
+Now, we can refine our *User+Movie+Genre Effect (UMGE) Model* by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie+Genre Effect Model* or *Regularized UMGE Model* for short), for the definitive *RMSE* calculation and use in subsequent models.
+
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1076) performs this operation:
 ```{r, eval=FALSE}
@@
 UMGE.rglr.best_lambda <- best_result["param.best_value"]
+
+put_log1("Re-training Regularized User+Movie+Genre Effect Model for the best `lambda`: %1...",
+         UMGE.rglr.best_lambda)
 

### 2025-12-22 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Code chunks: fix for OMR Model.

@@
 We calculate this using the folowing [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L106):
-```{{r main-script-l106, echo=TRUE, }
+```{r main-script-l106, echo=TRUE }
 mu <- mean(edx$rating)
@@
 Let's quickly analyze the resulting `deviation.RMSE` vector we have just got.
-The following [data visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L189) code will help us with this:
+The following [data visualization code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L189) will help us with this:
 ```{r main-script-l189}

### 2025-12-22 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Fix for report section: 2.2 OMR Model

@@
 
-If we predict all unknown ratings with $\hat{\mu}$, we can obtain *RMSE* using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L108):
-```{r main-script-l08 }
+If we predict all unknown ratings with $\hat{\mu}$, we can obtain *RMSE* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L108):
+```{r main-script@L108 }
 mu.MSEs <- naive_model_MSEs(mu)
+```
+
+\newpage
+
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L110) provides a visual representation of the results we have just obtained:
+```{r main-script@L110 }
 data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
@@
 Let's prove this with a small experiment using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L155):
-```{r main-script-l155 }
+```{r main-script@l155 }
   deviation <- seq(0, 6, 0.1) - 3
@@
 
+\newpage
+
 Let's quickly analyze the resulting `deviation.RMSE` vector we have just got.
 The following [data visualization code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L189) will help us with this:
-```{r main-script-l189}
+```{r main-script@l189}
 data.frame(delta = deviation, 
@@
               ylabel = "RMSE")
+```
 
+\newpage
+
+The piece of code below prints a quick recap of the results:
+```{r main-script@l189.recap}
 which_min_deviation <- deviation[which.min(deviation.RMSE)]
@@
 Finally, we add the *RMSE* value calculated for the *OMR Model* to our *Result Table* and print the table using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L200):
-```{r main-script-l200, eval=FALSE}
+```{r main-script@l200, eval=FALSE}
 RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 

### 2025-12-23 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Report section review: OMR Model.

@@
 
-If we predict all unknown ratings with $\hat{\mu}$, we can obtain *RMSE* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L108):
+If we predict all unknown ratings with $\hat{\mu}$, we can use the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L108)  to compute *Mean Squared Errors* (hereafter *MSE* for short) with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
 ```{r main-script@L108 }
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the user-defined function [naive_model_MSEs](#func.naive_model_MSEs) described in the [OMR Model: Helper Functions] section of [Appendix A](#appndx_a) to calculate *RMSEs* for the sequence of the deviation values.
+:::
 
@@
 ::: {.noteblock data-latex=""}
-
-The following custom functions described in [Appendix A: Support Functions], are used in the code snippets above:
-
-  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model: Helper Functions]) to compute *Mean Squared Errors* (hereafter *MSE* for short) with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
-
-  - [data.plot](#func.data.plot) (described in section [Data Visualization Functions]) for the *MSE* data visualization.
-
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions] / [Data Visualization Functions] section of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model: Helper Functions] section of [Appendix A](#appndx_a) to calculate *RMSEs* for the sequence of the deviation values.
+In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [Models Training: Support Functions] / [OMR Model: Helper Functions] section of [Appendix A](#appndx_a) to calculate *RMSEs* for the sequence of the deviation values.
 :::
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions] / [Data Visualization Functions] section of [Appendix A](#appndx_a).
+:::
 

### 2025-12-23 reports/capstone-movielens.site/01.intro.Rmd
Fix for bibliography.
Report section review: UE Model.

@@
 The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
-Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the _Root Mean Square Error_ (_RMSE_) score, which, as shown in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_, is defined as:
+Following the [Netflix Grand Prize Contest](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/index.html) requirements, we will evaluate the *Root Mean Square Error* (hereafter *RMSE* for short) score, which, as shown in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_, is defined as:
 $$
@@
 
-with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_25-1].
+with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations[@IDS2_24-1_LF].
 

### 2025-12-23 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Report section review: UE Model.

--- 2025-12-22 reports/capstone-movielens.site/02-3.OMR-model.Rmd
@@
 We calculate this using the folowing [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L106):
-```{r main-script-l106, echo=TRUE }
+```{r main-script@l106, echo=TRUE }
 mu <- mean(edx$rating)
@@
 
-If we predict all unknown ratings with $\hat{\mu}$, we can obtain *RMSE* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L108):
-```{r main-script@L108 }
+If we predict all unknown ratings with $\hat{\mu}$, we can use the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L108)  to compute *Mean Squared Errors* (hereafter *MSE* for short) with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
+```{r main-script@l108 }
 mu.MSEs <- naive_model_MSEs(mu)
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the user-defined function [naive_model_MSEs](#func.naive_model_MSEs) described in the [Models Training: Support Functions]/[OMR Model: Helper Functions] section of [Appendix A](#appndx_a).
+:::
 
@@
 The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L110) provides a visual representation of the results we have just obtained:
-```{r main-script@L110 }
+```{r main-script@l110 }
 data.frame(fold_No = 1:5, MSE = mu.MSEs) |>
@@
               yname = "MSE")
+```
 
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions]/[Data Visualization Functions] section of [Appendix A](#appndx_a).
+:::
+
+We can now calculate the *Root Mean Squared Error (RMSE)* for the current model as a *square root* of the average of the *MSE* values we obtained above, using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L117):
+```{r main-script@l110 }
 mu.RMSE <- sqrt(mean(mu.MSEs))
@@
 ::: {.noteblock data-latex=""}
-
-The following custom functions described in [Appendix A: Support Functions], are used in the code snippets above:
-
-  - [naive_model_MSEs](#func.naive_model_MSEs) (described in section [OMR Model: Helper Functions]) to compute *Mean Squared Errors* (hereafter *MSE* for short) with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
-
-  - [data.plot](#func.data.plot) (described in section [Data Visualization Functions]) for the *MSE* data visualization.
-
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions]/[Data Visualization Functions] section of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [OMR Model: Helper Functions] section of [Appendix A](#appndx_a) to calculate *RMSEs* for the sequence of the deviation values.
+In the code snippet above, we use the function [naive_model_RMSE](#func.naive_model_RMSE) described in the [Models Training: Support Functions]/[OMR Model: Helper Functions] section of [Appendix A](#appndx_a) to calculate *RMSEs* for the sequence of the deviation values.
 :::
@@
 
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions]/[Data Visualization Functions] section of [Appendix A](#appndx_a).
+:::
+
 \newpage
 
-The piece of code below prints a quick recap of the results:
-```{r main-script@l189.recap}
+The [piece of code] below prints a quick recap of the results:
+```{r main-script@l177}
 which_min_deviation <- deviation[which.min(deviation.RMSE)]
@@
 RMSEs.ResultTibble.OMR <- RMSEs.ResultTibble |> 
-  RMSEs.AddRow("Overall Mean Rating Model", mu.RMSE)
+  RMSEs.AddRow("OMR Model", 
+               mu.RMSE,
+               comment = "Overall Mean Rating (OMR) Model")
 ```
@@
 ::: {.noteblock data-latex=""}
-To print the table above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
+In the code snippet above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
 :::

### 2025-12-23 reports/capstone-movielens.site/02.4.UE-model.Rmd
Report section review: UE Model.

--- 2025-12-09 reports/capstone-movielens.site/02.4.UE-model.Rmd
@@
 
-These considerations alows us to compute a _User Mean Ratings_ the following way:
-```{r eval=FALSE}
+These considerations allow us to compute a _User Mean Ratings_ using the following [piece code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L231):
+```{r  main-script@l1231, eval=FALSE}
 put_log("Computing Average Ratings per User (User Mean Ratings)...")
@@
 
-And then we compute a _User Effect_ this way:
-```{r eval=FALSE}
-put_log("Computing User Effect per users ...")
+\newpage
+
+And then we compute a _User Effect_ using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L291):
+```{r main-script@l291, eval=FALSE}
 edx.user_effect <- edx.user_mean_ratings |>
@@
          a = mean_rating - mu)
-
-put_log("A User Effect Model has been builded")
 ```
 ```{r}
+str(edx.user_effect)
+```
+
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L336) plots a histogram that provides a visual representation of the *User Effect* data object we have just obtained:
+```{r main-script@l336}
 par(cex = 0.7)
@@
 
-str(edx.user_effect)
 ```
 
-Now, we are ready to compute the _Mean Squared Errors_ for samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A](#appndx_a)).
+Now, we are ready to compute the *Mean Squared Errors (MSE)* for samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A](#appndx_a)).
 
@@
 
-The code that performs this operation is shown below:
-```{r eval=FALSE}
+The [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L345) that performs this operation is shown below:
+```{r main-script@l345, eval=FALSE}
 put_log("Computing the RMSE taking into account user effects...")
@@
 ```
-```{r}
+
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L355) visualizes the results obtained above:
+```{r main-script@l355}
 data.frame(fold_No = 1:5, MSE = edx.user_effect.MSEs) |>
@@
 ::: {.noteblock data-latex=""}
-For the _Mean Squared Errors_ data visualization we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Visualization Functions](#appndx_a.data_helper.functions) section of [Appendix A](#appndx_a).
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions]/[Data Visualization Functions] section of [Appendix A](#appndx_a).
 :::
 
-Finally, we calculate the `RMSE` as the _square root_ of the average of the _Mean Squared Errors_ we obtained through the _5-Fold Cross-Validation_ above:   
-```{r, eval=FALSE}
+We can now calculate the *RMSE* for the current model as a *square root* of the average of the *MSE* values we obtained above, using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L364):
+```{r main-script@l364, eval=FALSE}
 edx.user_effect.RMSE <- sqrt(mean(edx.user_effect.MSEs))
+```
 
+\newpage
+
+Finally, we add the *RMSE* value calculated for the *UE Model* to our *Result Table* and print the table using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L372):
+```{r main-script@l372, eval=FALSE}
 RMSEs.ResultTibble.UE <- RMSEs.ResultTibble.OMR |> 
-  RMSEs.AddRow("User Effect Model", edx.user_effect.RMSE)
+  RMSEs.AddRow("UE Model", 
+               edx.user_effect.RMSE,
+               comment = "User Effect (UE) Model")
 ```

### 2025-12-23 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Fix for code chunk (duplicate name) in report section: OMR Model

@@
 We can now calculate the *Root Mean Squared Error (RMSE)* for the current model as a *square root* of the average of the *MSE* values we obtained above, using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L117):
-```{r main-script@l110 }
+```{r main-script@l117 }
 mu.RMSE <- sqrt(mean(mu.MSEs))

### 2025-12-23 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Report refactoring: references to `Appendix A`.

@@
 
-::: {.noteblock data-latex=""}
-In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions]/[Data Visualization Functions] section of [Appendix A](#appndx_a).
-:::
-
 \newpage
@@
 
-The [piece of code] below prints a quick recap of the results:
+The [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L177) below prints a quick recap of the results:
 ```{r main-script@l177}
@@
 ::: {.noteblock data-latex=""}
-To print the log, we use the function [print_log1](#func.print_log1) described in the [Logging Functions] section of [Appendix A](#appndx_a).
+To print the log, we use the function [print_log1](#func.print_log1) described in the [Common Helper Functions]/[Logging Functions] section of [Appendix A](#appndx_a).
 :::

### 2025-12-23 reports/capstone-movielens.site/02.4.UE-model.Rmd
Report refactoring: references to `Appendix A`.

@@
 
-These considerations allow us to compute a _User Mean Ratings_ using the following [piece code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L231):
+These considerations allow us to compute a _User Mean Ratings_ using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L231):
 ```{r  main-script@l1231, eval=FALSE}
@@
 
-The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L336) plots a histogram that provides a visual representation of the *User Effect* data object we have just obtained:
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L336) plots a histogram that provides a visual representation of the variability of the *User Effect* across users in the *data frame object* we have just obtained:
 ```{r main-script@l336}
@@
 
-Now, we are ready to compute the *Mean Squared Errors (MSE)* for samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A](#appndx_a)).
+Now, we are ready to compute the *Mean Squared Errors (MSEs)* for the samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A](#appndx_a)).
 
@@
 
+\newpage
+
 We can now calculate the *RMSE* for the current model as a *square root* of the average of the *MSE* values we obtained above, using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L364):

### 2025-12-23 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report refactoring: references to `Appendix A`.

@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A](#appndx_a).
+In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A](#appndx_a).
+In the code snippet above, we use the [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::
@@
 
-  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
 :::
@@
 ::: {.noteblock data-latex=""}
-The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UME Model: Regularization], respectively, of [Appendix A: Support Functions].
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UME Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
+In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions]/[Data Visualization Functions] section of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in the code snippet above is described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
+The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in the code snippet above is described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UME Model: Regularization], respectively, of [Appendix A: Support Functions].
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) used in the code snippet above are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UME Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a)) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves.
+Note that in the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) (described in the [Data Helper Functions]/[Data Visualization Functions] section of [Appendix A](#appndx_a)) with the argument [normalize](#func.data.plot.args.normalize) set to `TRUE`, which means that deviations from the minimum $y$ value are used to plot, rather than the $y$ values themselves.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_effect](#func.train_user_movie_effect) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A](#appndx_a).
+In the code snippet above we use the [train_user_movie_effect](#func.train_user_movie_effect) function described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::
@@
 
-  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section) to calculate the *RMSE* for the *UME Model*;
+  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section) to calculate the *RMSE* for the *UME Model*;
 
-  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
 :::

### 2025-12-23 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report refactoring: references to `Appendix A`.

@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
+In the code snippet above we use the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) function described in the [Models Training: Support Functions]/[UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::
@@
 
-  - [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGE Model*;
+  - [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) (described in the [Models Training: Support Functions]/[UMGE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGE Model*;
 
-  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
 :::
@@
 ::: {.noteblock data-latex=""}
-The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-The custom functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGE Model: Regularization] of [Appendix A: Support Functions], respectively.
+The custom functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGE Model: Regularization] of [Appendix A: Support Functions], respectively.
 :::
@@
 ::: {.noteblock data-latex=""}
-The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
+The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
+In the code snippet above we use the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described in the [Models Training: Support Functions]/[UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::

### 2025-12-23 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report refactoring: references to `Appendix A`.

@@
 ::: {.noteblock data-latex=""}
-The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) used in the code snippet above are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_UMGY_effect](#func.train_UMGY_effect) function described in the *Models Training: Support Functions /* [UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a).
+In the code snippet above we use the [train_UMGY_effect](#func.train_UMGY_effect) function described in the [Models Training: Support Functions]/[UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::
@@
 
-  - [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UMGYE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYE Model*;
+  - [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) (described in the [Models Training: Support Functions]/[UMGYE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYE Model*;
 
-  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
 :::

### 2025-12-23 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report refactoring: references to `Appendix A`.

@@
 
-We are going to use the helper function ([train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A: Support Functions]) specifically designed to train the *UMGYDE Model*, which under the hood calls the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `R` function, passing its `degree` and `span` parameters values taken from the caller's [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) arguments, respectively.
+We are going to use the helper function ([train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described in section [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A: Support Functions]) specifically designed to train the *UMGYDE Model*, which under the hood calls the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `R` function, passing its `degree` and `span` parameters values taken from the caller's [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) arguments, respectively.
 
-We will start by calling the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) with default parameters, which means that the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function will be implicitly called with `degree = 1` and `span = 0.75` arguments - the default values for the auxiliary function [loess_de](#func.loess_de) (described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a)) included in the call chain that actually, calls the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
+We will start by calling the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) with default parameters, which means that the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function will be implicitly called with `degree = 1` and `span = 0.75` arguments - the default values for the auxiliary function [loess_de](#func.loess_de) (described in section [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a)) included in the call chain that actually, calls the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.
 
@@
 
-Let's calculate the _RMSE_ of the current model using the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) helper function described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a):
+Let's calculate the _RMSE_ of the current model using the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) helper function described in section [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a):
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we also use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section *Common Helper Functions /* [Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
+In the code snippet above we also use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section [Common Helper Functions]/[Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
 :::
@@
 
-  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
+  - [tune.model_param](#func.tune.model_param) (described in the [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
 
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (described in the [Models Training: Support Functions]/[UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $0$.
 
@@
 
-  - [model.tune.param_range](#func.model.tune.param_range) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter best value* using the *best value neighborhood* information passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
+  - [model.tune.param_range](#func.model.tune.param_range) (described in the [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to enhance the accuracy of the *tuning parameter best value* using the *best value neighborhood* information passed in the [loop_starter](#func.model.tune.param_range.args.loop_starter) argument.
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section *Common Helper Functions /* [Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
+In the code snippet above we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section [Common Helper Functions]/[Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
 :::
@@
 
-  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
+  - [tune.model_param](#func.tune.model_param) (described in the [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
 
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $1$.
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1) (described in the [Models Training: Support Functions]/[UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $1$.
 
@@
 
-  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
+  - [tune.model_param](#func.tune.model_param) (described in the [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* (`span` in our case) from the given sequence of the *parameter values* passed in the [param_values](#func.tune.model_param.args.param_values) argument.
 
-  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $2$.
+  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2) (described in the [Models Training: Support Functions]/[UMGYDE Model: Tuning `loess` Params] section) used as an auxiliary function passed (in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument) to the [tune.model_param](#func.tune.model_param) to test the *UMGYDE Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree` parameter set to $2$.
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A](#appndx_a).
+In the code snippet above, we use the custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) described in the [Data Helper Functions]/[Data Visualization Functions] section of [Appendix A](#appndx_a).
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described in the *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
+In the code snippet above we use the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::
@@
 
-  - [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) (described in the *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYDE Model*;
+  - [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) (described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYDE Model*;
 
-  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
+  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
 :::
@@
 ::: {.noteblock data-latex=""}
-The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
+The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) used in the code snippet above are described in the sections *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
+The custom functions [model.tune.param_range](#func.model.tune.param_range) and [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) used in the code snippet above are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [regularize.train_UMGYD_effect](#func.regularize.train_UMGYD_effect) function described in the *Models Training: Support Functions /* [UMGYDE Model: Regularization] section of [Appendix A](#appndx_a).
+In the code snippet above we use the [regularize.train_UMGYD_effect](#func.regularize.train_UMGYD_effect) function described in the [Models Training: Support Functions]/[UMGYDE Model: Regularization] section of [Appendix A](#appndx_a).
 :::

### 2025-12-23 reports/capstone-movielens.site/05.appendix.Rmd
Report refactoring: references to `Appendix A`.

@@
 ::: {.noteblock data-latex=""}
-In the sample code snippet above, the `mean_reg` function is called internally from the [train_user_movie_effect](#func.train_user_movie_effect) function described below in section *Models Training: Support Functions /* [UME Model: Utility Functions] of *this Appendix*.
+In the sample code snippet above, the `mean_reg` function is called internally from the [train_user_movie_effect](#func.train_user_movie_effect) function described below in section [Models Training: Support Functions]/[UME Model: Utility Functions] of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
+*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the [Common Helper Functions]/[Model Tuning Utils] section of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
+In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section [Common Helper Functions]/[Model Tuning Utils] of *this Appendix*.
 
@@
 ::: {.noteblock data-latex=""}
-This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
+This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the [Common Helper Functions]/[Model Tuning Utils] section of *this Appendix*.
 :::
@@
 \
-The dataset passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *this Appendix*.
+The dataset passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the [Data Helper Functions]/[Data Processing Functions] section of *this Appendix*.
 
@@
 ::: {.noteblock data-latex=""}
-*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
+*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the [Common Helper Functions]/[Model Tuning Utils] section of *this Appendix*.
 ::: {.noteblock data-latex=""}
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree0` function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
+In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree0` function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section [Common Helper Functions]/[Model Tuning Utils] of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
+This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the [Common Helper Functions]/[Model Tuning Utils] section of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
+In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section [Common Helper Functions]/[Model Tuning Utils] of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
+In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section [Common Helper Functions]/[Model Tuning Utils] of *this Appendix*.
 :::
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
+In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section [Common Helper Functions]/[Model Tuning Utils] of *this Appendix*.
 

### 2025-12-23 reports/capstone-movielens.site/02.4.UE-model.Rmd
Fix for report section: "UE Model"

@@
 
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the user-defined function [mse](#func.mse) described in the [Common Helper Functions]/[(Root) Mean Squared Error Calculation] section of [Appendix A](#appndx_a).
+:::
+
 The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L355) visualizes the results obtained above:
@@
 
-Finally, we add the *RMSE* value calculated for the *UE Model* to our *Result Table* and print the table using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L372):
+Finally, we add the *RMSE* value calculated for the *UE Model* to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L372):
 ```{r main-script@l372, eval=FALSE}

### 2025-12-24 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report section review: UME Effect: Model Building.

@@
 ::: {.noteblock data-latex=""}
-The complete source code of the _User+Movie Effect_ computation described in this section is available in the [User+Movie Effect (UME) Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L382) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L382) script on _GitHub_.
+The complete source code of the _User+Movie Effect_  (hereafter *UM Effect* or *UME* for short) computation described in this section is available in the [User+Movie Effect (UME) Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L382) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L382) script on _GitHub_.
 :::
@@
 
-To prove this fact, we can find out the movies with the highest number of ratings using the following code:
-```{r, eval=FALSE}
+To prove this fact, we can find out the movies with the highest number of ratings using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L413):
+```{r  main-script@l413, eval=FALSE}
 edx.ordered_movie_ratings <- edx |> group_by(movieId, title) |>
@@
 ```
-```{r }
+```{r}
 head(edx.ordered_movie_ratings)
@@
 
-Now, we can figure out the most given ratings in order from most to least:
-```{r, eval=FALSE}
+Now, we can figure out the most given ratings in order from most to least.
+The [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L422) below performs this operation:
+```{r  main-script@l422, eval=FALSE}
 edx.rating_groups <- edx |>  group_by(rating) |>
@@
 
-We can visually see that from the following plot:
-```{r}
+We can visualize this using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L433) to plot the data:
+```{r  main-script@l433}
 edx.rating_groups |>
@@
 ::: {.noteblock data-latex=""}
-The complete source code of the _User+Movie Effect_ computation described in this section is available in the [UME Model Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L456) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L456) script on _GitHub_.
+The complete source code of the _User+Movie (UM) Effect_ computation described in this section is available in the [UME Model Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L456) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L456) script on _GitHub_.
 :::
 
-Below, we provide the most significant part of the code for training our model with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
-```{r eval=FALSE}
+Below is the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L472) that trains our model with the use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
+```{r  main-script@l472, eval=FALSE}
   cv.UM_effect <- train_user_movie_effect.cv()
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section of [Appendix A](#appndx_a).
+In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) helper function described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::
@@
 str(cv.UM_effect)
+```
 
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L508) plots a histogram that provides a visual representation of the variability of the *UM Effect* across movies in the *data frame object* we have just obtained:
+```{r  main-script@l508}
 par(cex = 0.7)
@@
 
-The following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L513) allows us to perform this task:
-```{r eval=FALSE}
+As we already outlined above, to accomplish such tasks, we use *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]).
+
+::: {.noteblock data-latex=""}
+In *this Project*, we use $K = 5$.
+:::
+
+The following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L513) validates our model by computing the *RMSE* score for the predictors constructed based on the *UM Effect*:
+```{r  main-script@l513, eval=FALSE}
 cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)
+```
+```{r}
+cv.UM_effect.RMSE
 ```
@@
 
-Finally, we add the obtained result to our *Result Table* and print the table using the following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L):
-```{r eval=FALSE}
+Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L516):
+```{r  main-script@l516, eval=FALSE}
 RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
-  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)
-
+  RMSEs.AddRow("UME Model", 
+               cv.UM_effect.RMSE,
+               comment = "User+Movie Effect (UME) Model")
 ```
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
-
-  -  to calculate the *RMSE* for the *Current Model*;
-
-  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
+In the code snippet above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
 :::
@@
 The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L571) performs this operation:
-```{r, eval=FALSE}
+```{r  main-script@l571, eval=FALSE}
 lambdas <- seq(0, 1, 0.1)
@@
 Now, let's visualize the results of the $\lambda$ range pre-configuration:
-``` {r}
+``` {r  main-script@l}
 cv.UME.preset.result$tuned.result |>

### 2025-12-24 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report section review: UME Effect: Model Building.

@@
 Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1177) for training our model using the *K-Fold Cross Validation* method, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
-```{r, eval=FALSE}
+```{r  main-script@l1177, eval=FALSE}
   cv.UMGY_effect <- train_UMGY_effect.cv()
@@
 
-We can now validate the current model by computing the *RMSE* for the *UMGY* Effect using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L):
-```{r, eval=FALSE}
+We can now validate the current model by computing the *RMSE* for the *UMGY* Effect using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1195):
+```{r  main-script@l1195, eval=FALSE}
 cv.UMGY_effect.RMSE <- calc_UMGY_effect_RMSE.cv(cv.UMGY_effect)
@@
 The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1241) performs this operation:
-```{r, eval=FALSE}
+```{r  main-script@l1241, eval=FALSE}
   lambdas <- seq(0, 512, 32)

### 2025-12-24 reports/capstone-movielens.site/02.5.UME-model.Rmd
Fix for report section review: Movie Effect Analysis.

@@
 ```
-```{r, include=TRUE}
-edx.rating_groups
+```{r}
+print(edx.rating_groups)
 ```
+
+\newpage
 
@@
 
-The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
-```{r, include=TRUE}
-edx.rating_groups |> arrange(rating)
+The following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L430) allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
+```{r  main-script@l430, include=TRUE}
+print(edx |> group_by(rating) |> summarize(count = n()))
 ```
 
-We can visualize this using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L433) to plot the data:
+We can give even more visibility for the *rating distribution* by plotting the data for the *rating groups* (the `edx.rating_groups` object) we obtained above using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L433):
+
 ```{r  main-script@l433}
@@
   geom_line() 
-
 ```

### 2025-12-24 reports/capstone-movielens.site/02.5.UME-model.Rmd
Fix for Report section: UME Model Regularization.

@@
 
-The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L508) plots a histogram that provides a visual representation of the variability of the *UM Effect* across movies in the *data frame object* we have just obtained:
-```{r  main-script@l508}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L507) plots a histogram that provides a visual representation of the variability of the *UM Effect* across movies in the *data frame object* we have just obtained:
+```{r  main-script@l507}
 par(cex = 0.7)
@@
 
+\newpage
+
 Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L516):
@@
 :::
+
+We begin this section with the concept's mathematical description presented below in the subsection [UME Model Regularization: Mathematical Description].
+
+Next, we will implement the *UME Model Regularization* in the following three steps:
+
+  1.
+**Pre-configuration:** (Described in subsection [UME Model Regularization: *Pre-configuration*]) Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
+
+2.
+**Fine-tuning:** (Described in the subsection [UME Model Regularization: Fine-tuning]) Determining the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* score for the model.
+
+  3.
+**Retraining:** (Described in subsection [UME Model Regularization: Retraining the Model with the best $\lambda$]) Retraining the model with the best value of $\lambda$ determined in the previous step.
 
@@
 The larger the $\lambda$, the more we shrink[@IDS2_24-1].
-
-We will implement the _Regularization_ method on our  models (starting from the current model) in following three steps:
-
-  1.
-**Pre-configuration:** Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
-
-  2. **Fine-tuning:** Figuring out the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* of the model.
-
-  3. **Retraining:** Retraining the model with the best value of $\lambda$ determined in the previous step.
 

### 2025-12-25 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report refactoring: Model Regularization sections.

@@
 
-We begin this section with the concept's mathematical description presented below in the subsection [UME Model Regularization: Mathematical Description].
+We begin this section with the concept's mathematical description presented below in the subsection [UME Model Regularization: *Mathematical Description*].
 
@@
 2.
-**Fine-tuning:** (Described in the subsection [UME Model Regularization: Fine-tuning]) Determining the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* score for the model.
+**Fine-tuning:** (Described in the subsection [UME Model Regularization: *Fine-tuning*]) Determining the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* score for the model.
 
   3.
-**Retraining:** (Described in subsection [UME Model Regularization: Retraining the Model with the best $\lambda$]) Retraining the model with the best value of $\lambda$ determined in the previous step.
+**Retraining:** (Described in subsection [UME Model Regularization: *Retraining the Model with the best* $\lambda$]) Retraining the model with the best value of $\lambda$ determined in the previous step.
 
-#### UME Model Regularization: Mathematical Description
+#### UME Model Regularization: *Mathematical Description*
 \
@@
 
-#### UME Model Regularization: Fine-tuning
+#### UME Model Regularization: *Fine-tuning*
 \
@@
 
-#### UME Model Regularization: Retraining the Model with the best $\lambda$
+#### UME Model Regularization: *Retraining the Model with the best* $\lambda$
 \

### 2025-12-25 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report refactoring: Model Regularization sections.

@@
 
-#### UMGE Model Regularization: Mathematical Description
+We begin this section with the concept's mathematical description presented below in the subsection [UMGE Model Regularization: *Mathematical Description*].
+
+Next, we will implement the *UMGE Model Regularization* in the following three steps:
+
+  1.
+**Pre-configuration:** (Described in subsection [UMGE Model Regularization: *Pre-configuration*]) Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
+
+2.
+**Fine-tuning:** (Described in the subsection [UMGE Model Regularization: *Fine-tuning*]) Determining the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* score for the model.
+
+  3.
+**Retraining:** (Described in subsection [UMGE Model Regularization: *Retraining the Model with the best* $\lambda$]) Retraining the model with the best value of $\lambda$ determined in the previous step.
+
+#### UMGE Model Regularization: *Mathematical Description*
 \
@@
 
-As we decided earlier (and outlined in the [UME Model Regularization] section), we implement the *Regularization method* for our models in the following three steps:
-
-  1.
-**Pre-configuration:** Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
-
-  2. **Fine-tuning:** Figuring out the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* of the model.
-
-  3. **Retraining:** Retraining the model with the best value of $\lambda$ determined in the previous step.
-
 \newpage
 
-#### UMGE Model Regularization: Pre-configuration
+#### UMGE Model Regularization: *Pre-configuration*
 \
@@
 
-#### UMGE Model Regularization: Fine-tuning
+#### UMGE Model Regularization: *Fine-tuning*
 \
@@
 
-#### UMGE Model Regularization: Retraining the Model with the best $\lambda$
+#### UMGE Model Regularization: *Retraining the Model with the best* $\lambda$
 \

### 2025-12-25 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report refactoring: Model Regularization sections.

@@
 
-#### UMGYE Model Regularization: Mathematical Description
+We begin this section with the concept's mathematical description presented below in the subsection [UMGYE Model Regularization: *Mathematical Description*].
+
+Next, we will implement the *UME Model Regularization* in the following three steps:
+
+  1.
+**Pre-configuration:** (Described in subsection [UMGYE Model Regularization: *Pre-configuration*]) Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
+
+2.
+**Fine-tuning:** (Described in the subsection [UMGYE Model Regularization: *Fine-tuning*]) Determining the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* score for the model.
+
+  3.
+**Retraining:** (Described in subsection [UMGYE Model Regularization: *Retraining the Model with the best* $\lambda$]) Retraining the model with the best value of $\lambda$ determined in the previous step.
+
+#### UMGYE Model Regularization: *Mathematical Description*
 \
@@
 
-As with the previous models, we implement the _Regularization_ method for the current model in the following three steps:
-
-  1.
-**Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the *K-Fold Cross Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
-
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
-
-  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.
-
 \newpage
 
-#### UMGYE Model Regularization: Pre-configuration
+#### UMGYE Model Regularization: *Pre-configuration*
 \
@@
 
-#### UMGYE Model Regularization: Fine-tuning
+#### UMGYE Model Regularization: *Fine-tuning*
 \
@@
 
-#### UMGYE Model Regularization: Retraining the Model with the best $\lambda$
+#### UMGYE Model Regularization: *Retraining the Model with the best* $\lambda$
 \

### 2025-12-25 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report refactoring: Model Regularization sections.

@@
 
-#### UMGYDE Model Regularization: Mathematical Description
+We begin this section with the concept's mathematical description presented below in the subsection [UMGYDE Model Regularization: *Mathematical Description*].
+
+Next, we will implement the *UME Model Regularization* in the following three steps:
+
+  1.
+**Pre-configuration:** (Described in subsection [UMGYDE Model Regularization: *Pre-configuration*]) Preliminary determination of the optimal range of *regularization parameter* $\lambda$ values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
+
+2.
+**Fine-tuning:** (Described in the subsection [UMGYDE Model Regularization: *Fine-tuning*]) Determining the best value of $\lambda$ with the highest possible accuracy that minimizes the *RMSE* score for the model.
+
+  3.
+**Retraining:** (Described in subsection [UMGYDE Model Regularization: *Retraining the Model with the best* $\lambda$]) Retraining the model with the best value of $\lambda$ determined in the previous step.
+
+#### UMGYDE Model Regularization: *Mathematical Description*
 \
@@
 
-As with the previous models, we implement the _Regularization_ method for the current model in the following three steps:
-
-  1.
-**Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the *K-Fold Cross Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
-
-  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
-
-  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.
-
 \newpage
 
-#### UMGYDE Model Regularization: Pre-configuration
+#### UMGYDE Model Regularization: *Pre-configuration*
 \
@@
 
-#### UMGYDE Model Regularization: Fine-tuning
+#### UMGYDE Model Regularization: *Fine-tuning*
 \
@@
 
-#### UMGYDE Model Regularization: Retraining the Model with the best $\lambda$
+#### UMGYDE Model Regularization: *Retraining the Model with the best* $\lambda$
 \

### 2025-12-25 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report sections review: the model tuning & regularization.

@@
 
-::: {.noteblock data-latex=""}
-Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three steps - one for each possible value of the `degree`.
-:::
-
 \newpage
@@
 
-#### UMGYDE Model Tuning: Step 1 (`degree = 0`)
+::: {.noteblock data-latex=""}
+The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning by `span` & `degree` parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1553) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1553) script on _GitHub_.
+:::
+
+Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three stages - one for each possible value of the `degree`.
+
+For each value of the `degree` parameter, we will divide each stage into the following two steps for tuning the model by the `span` parameter:
+
+  1.
+**Pre-configuration:**  Preliminary determination of the optimal range of the `span` parameter values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);
+
+  2. **Fine-tuning:** Determining the best value of the `span` parameter with the highest possible accuracy that minimizes the *RMSE* score for the model.
+
+Finally, we will retrain the model with the best `degree` and `span` values determined by the tuning result.
+
+#### UMGYDE Model Tuning: Stage 1 (`degree = 0`)
 \
@@
 
-#### UMGYDE Model Tuning: Step 2 (`degree = 1`)
+#### UMGYDE Model Tuning: Stage 2 (`degree = 1`)
 \
@@
 
-#### UMGYDE Model Tuning: Step 3 (`degree = 2`)
+#### UMGYDE Model Tuning: Stage 3 (`degree = 2`)
 \

### 2025-12-25 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Fix for Report section: UMGYDE Model Tuning by `degree` and `span` Parameters.

@@
 
-Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three stages - one for each possible value of the `degree`.
+Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three stages - one for each value.
 
-For each value of the `degree` parameter, we will divide each stage into the following two steps for tuning the model by the `span` parameter:
+In addition, we will divide each stage into the following two steps for tuning the model by the `span` parameter:
 

### 2025-12-26 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report sections review: the model tuning & regularization.
Report review: Model Building sections.

@@
 
-Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L902) for training our model using the *K-Fold Cross Validation* method, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
-```{r, fn.train_user_movie_genre_effect.cv,   eval=FALSE}
+Below is the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L902) that trains our model with the use of *K-Fold Cross Validation* method, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
+```{r  main-script@l902, fn.train_user_movie_genre_effect.cv,   eval=FALSE}
 cv.UMG_effect <- train_user_movie_genre_effect.cv()
@@
 
-```{r, hist.cv.UMG_effect }
+```{r}
 str(cv.UMG_effect)
+```
 
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L925) plots a histogram that provides a visual representation of the variability of the *UM Effect* across movies in the *data frame object* we have just obtained:
+```{r  main-script@l925}
 par(cex = 0.7)
@@
 
-We can now construct predictors and calculate the _RMSE_ of the *UMGE Model* using the
-following code:
-```{r, eval=FALSE}
+We can now construct predictors and calculate the *RMSE* score for the *UMGE Model* using the
+following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L932):
+```{r main-script@l932, eval=FALSE}
 cv.UMG_effect.RMSE <- calc_user_movie_genre_effect_RMSE.cv(cv.UMG_effect)
+```
+```{r}
+cv.UMG_effect.RMSE
+```
 
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) function described in the [Models Training: Support Functions]/[UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
+Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L937):
+```{r main-script@l937, eval=FALSE}
 RMSEs.ResultTibble.UMGE <- RMSEs.ResultTibble.rglr.UME |> 
-  RMSEs.AddRow("User+Movie+Genre Effect (UMGE) Model", cv.UMG_effect.RMSE)
+  RMSEs.AddRow("UMGE Model", 
+               cv.UMG_effect.RMSE,
+               comment = "User+Movie+Genre Effect (UMGE) Model")
 ```
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
-
-  - [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) (described in the [Models Training: Support Functions]/[UMGE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGE Model*;
-
-  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
+In the code snippet above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
 :::
@@
 
-Now, let's visualize the results of the $\lambda$ range preconfiguration:
+Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1004):
 ``` {r}

### 2025-12-26 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report sections review: the model tuning & regularization.
Report review: Model Building sections.

@@
 
-Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1177) for training our model using the *K-Fold Cross Validation* method, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
+Below is the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1177) that trains our model with the use of *K-Fold Cross Validation* method, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
 ```{r  main-script@l1177, eval=FALSE}
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) user-defined function described in the [Models Training: Support Functions]/[UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
 ```{r}
 str(cv.UMGY_effect)
-summary(cv.UMGY_effect)
 ```
 
-We can now validate the current model by computing the *RMSE* for the *UMGY* Effect using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1195):
+We can now construct predictors and calculate the *RMSE* score for the *UMGYE Model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1195):
 ```{r main-script@l1195, eval=FALSE}
 cv.UMGY_effect.RMSE <- calc_UMGY_effect_RMSE.cv(cv.UMGY_effect)
-
+```
+```{r}
+cv.UMGY_effect.RMSE
 ```
@@
 ::: {.noteblock data-latex=""}
-In the code snippets above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described in the [UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a) to *this Report*.
+In the code snippets above, we use the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) user-defined function described in the [Models Training: Support Functions]/[UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a).
 :::
 
-```{r, eval=FALSE}
+Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1199):
+```{r main-script@l1199, eval=FALSE}
 RMSEs.ResultTibble.UMGYE <- RMSEs.ResultTibble.rglr.UMGE |> 
@@
 
-Now, let's visualize the results of the $\lambda$ range pre-configuration:
+Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1270):
 ``` {r}

### 2025-12-26 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report review: Model Building sections.

@@
 
-Below is the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1495) that trains our model with the default `degree` and `span` parameter values using *K-Fold Cross Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
-```{r, eval=FALSE}
+Below is the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1495) that trains our model with the default `degree` and `span` parameter values with the use of *K-Fold Cross Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
+```{r main-script@l1495, eval=FALSE}
   cv.UMGYDE.default_params <- train_UMGY_SmoothedDay_effect.cv()
@@
 
-Below is the visual representation of the *Smoothed Day Effect* data we have just computed:
-
-```{r}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1521) provides a visual representation of the *Smoothed Day Effect* data we have just computed:
+```{r main-script@l1521}
 cv.UMGYDE.default_params |>
@@
 
-Let's calculate the _RMSE_ of the current model using the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) helper function described in section [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a):
-
-```{r, eval=FALSE}
+Now, let's construct predictors and calculate the *RMSE* score for the *current model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1195):
+```{r main-script@l1195, eval=FALSE}
 cv.UMGYDE.default_params.RMSE <- cv.UMGYDE.default_params |>
   calc_UMGY_SmoothedDay_effect.RMSE.cv()
+```
+```{r}
+cv.UMGYDE.default_params.RMSE
+```
 
+::: {.noteblock data-latex=""}
+In the code snippets above, we use the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) user-defined described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
+Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1199):
+```{r main-script@l1199, eval=FALSE}
 RMSEs.ResultTibble.UMGYDE <- RMSEs.ResultTibble.rglr.UMGYE |> 
@@
 
-Now, let's visualize the results of the $\lambda$ range pre-configuration:
+Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2098):
 ``` {r}

### 2025-12-26 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report section review: "UMGYDE Model Tuning by `degree` and `span` Parameters".

@@
 The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1578) determines the optimal range of `span` for the further model tuning when `degree = 0`:
-```{r, eval=FALSE}
+```{r main-script@l1578, eval=FALSE}
   spans <- seq(0.0005, 1, 0.001)
@@
 
-Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the selected interval, with the parameter `degree = 0`, as we have figured out in this step of tuning:
-```{r}
+The [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1609) below provides a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the selected interval, with the parameter `degree = 0`, as we have figured out in this step of tuning:
+```{r main-script@l1609}
 plt.title = "UMGYDE Model, `loess` function args: range of `span` values for `degree = 0`"
@@
 The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1625) performs the *fine-tuning* of the *UMGYDE Model* by precise selection of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter with the `degree` parameter set to $0$:
-```{r, eval=FALSE}
+```{r main-script@l1625, eval=FALSE}
 lss.fine_tune.loop_starter <- 
@@
 
-Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the neighborhood of its *best value* (when the parameter `degree = 0`), which we have determined in this (*fine-tuning*) step:
-```{r}
+The [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1651) below provides a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the neighborhood of its *best value* (when the parameter `degree = 0`), which we have determined in this (*fine-tuning*) step:
+```{r main-script@l1651}
 plt.title = "Fine-tuned UMGYDE Model with `loess` parameter: `degree` = 0"
@@
 
-Now, we can add the best *RMSE* figured out for the *UMGYDE Fine-tuned Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree = 0` (let's call it *Tuned UMGYDE.d0 Model*) to our *Result Table*:
-```{r, eval=FALSE}
+Now, we can add the best *RMSE* figured out for the *UMGYDE Fine-tuned Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree = 0` (let's call it *Tuned UMGYDE.d0 Model*) to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1662):
+```{r main-script@l1662, eval=FALSE}
 RMSEs.ResultTibble.UMGYDE0 <- RMSEs.ResultTibble.UMGYDE |> 
@@
 
-Below is the [lines of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1695) that determines the optimal range of `span` for the further model tuning when `degree = 1`:
-```{r, eval=FALSE}
+Below is the [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1695) that determines the optimal range of `span` for the further model tuning when `degree = 1`:
+```{r main-script@l1695, eval=FALSE}
   spans <- seq(0.0005, 1, 0.001)
@@
 
-Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the selected interval, with the parameter `degree = 1`, as we have figured out in this step of tuning:
-```{r}
+The [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1726) below provides a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the selected interval, with the parameter `degree = 1`, as we have figured out in this step of tuning:
+```{r main-script@l1726}
 lss.UMGYDE.preset.degree1.result$tuned.result |>
@@
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1739) performs the *fine-tuning* of the *UMGYDE Model* by precise selection of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter with the `degree` parameter set to $1$:
-```{r, eval=FALSE}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1739) performs the *fine-tuning* of the *UMGYDE Model* by precise selection of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter with the `degree` parameter set to $1$:
+```{r main-script@l1739, eval=FALSE}
 lss.fine_tune.loop_starter <- 
@@
 
-Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the neighborhood of its *best value* (when the parameter `degree = 1`), which we have determined in this (*fine-tuning*) step:
-```{r}
+The [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1765) below provides a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the neighborhood of its *best value* (when the parameter `degree = 1`), which we have determined in this (*fine-tuning*) step:
+```{r main-script@l1765}
 lss.UMGYDE.fine_tune.degree1.result$tuned.result |>
@@
 
-Now, we can add the best *RMSE* figured out for the *UMGYDE Fine-tuned Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree = 1` (let's call it *Tuned UMGYDE.d1 Model*) to our *Result Table*:
-```{r, eval=FALSE}
+Now, we can add the best *RMSE* figured out for the *UMGYDE Fine-tuned Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree = 1` (let's call it *Tuned UMGYDE.d1 Model*) to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1773):
+```{r main-script@l1773, eval=FALSE}
 RMSEs.ResultTibble.UMGYDE1 <- RMSEs.ResultTibble.UMGYDE0 |> 
@@
 
-Below is the [lines of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1807) that determines the optimal range of `span` for the further model tuning when `degree = 2`:
-```{r, eval=FALSE}
+Below is the [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1807) that determines the optimal range of `span` for the further model tuning when `degree = 2`:
+```{r main-script@l1807, eval=FALSE}
   spans <- seq(0.0005, 1, 0.001)
@@
 
-Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the selected interval, with the parameter `degree = 2`, as we have figured out in this step of tuning:
-```{r}
+The [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1838) below provides a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the selected interval, with the parameter `degree = 2`, as we have figured out in this step of tuning:
+```{r main-script@l1838}
 lss.UMGYDE.preset.degree2.result$tuned.result |>
@@
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1851) performs the *fine-tuning* of the *UMGYDE Model* by precise selection of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter with the `degree` parameter set to $2$:
-```{r, eval=FALSE}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1851) performs the *fine-tuning* of the *UMGYDE Model* by precise selection of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter with the `degree` parameter set to $2$:
+```{r main-script@l1851, eval=FALSE}
 lss.fine_tune.loop_starter <- 
@@
 
-Below is a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the neighborhood of its *best value* (when the parameter `degree = 2`), which we have determined in this (*fine-tuning*) step.
+The [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1877) below provides a visual representation of the dependence of the *RMSE* value on the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter value over the neighborhood of its *best value* (when the parameter `degree = 2`), which we have determined in this (*fine-tuning*) step.
 Since the left endpoint value of the *RMSE* range has much smaller deviation from the minimum than the value of the right endpoint, for visual clarity, we plot the left part of the graph once more on an *enlarged scale* (below the main graph):
-```{r}
+```{r main-script@l1877}
 lss.UMGYDE.fine_tune.degree2.result$tuned.result |>
@@
 
-Now, we can add the best *RMSE* figured out for the *UMGYDE Fine-tuned Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree = 2` (let's call it *Tuned UMGYDE.d2 Model*) to our *Result Table*:
-```{r, eval=FALSE}
+Now, we can add the best *RMSE* value figured out for the *UMGYDE Fine-tuned Model* with the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `degree = 2` (let's call it *Tuned UMGYDE.d2 Model*) to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1887):
+```{r main-script@l1887, eval=FALSE}
 RMSEs.ResultTibble.UMGYDE2 <- RMSEs.ResultTibble.UMGYDE1 |> 
@@
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1913) performs this operation:
-```{r, eval=FALSE}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1913) performs this operation:
+```{r main-script@l1913, eval=FALSE}
 # The Best Parameters and RMSE Value 
@@
 
-Let's now visualize the final *Smoothed Day Effect* we have just obtained:
-```{r}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1993) provides a visual representation of the final *Smoothed Day Effect* data we have just obtained:
+```{r main-script@l1993}
 lss.UMGYD_effect |>
@@
 
-Now, we are ready to calculate the *RMSE* for the ultimately *Tuned UMGYDE Best Model* and add the definitive result to our *Result Table*:
-```{r, eval=FALSE}
+Now, we are ready to construct predictors and calculate the *RMSE* score for the ultimately *Tuned UMGYDE Best Model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2007):
+```{r main-script@l2007, eval=FALSE}
 lss.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(lss.UMGYD_effect)
+```
+```{r}
+lss.UMGYD_effect.RMSE
+```
 
+::: {.noteblock data-latex=""}
+In the code snippets above, we use the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) user-defined described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
+Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2024):
+```{r main-script@l2024, eval=FALSE}
 RMSEs.ResultTibble.UMGYDE.tuned <- RMSEs.ResultTibble.UMGYDE2 |> 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
-
-  - [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) (described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYDE Model*;
-
-  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
+In the code snippet above we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section [Common Helper Functions]/[Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
 :::
 
-Finally, let's *regularize* the tuned *UMGYDE Model* as we did above with the previous models.
+Now, as the final stage of the tuning process, let's *regularize* our model (as we did with the previous models).
 

### 2025-12-26 reports/capstone-movielens.site/02.4.UE-model.Rmd

@@
 
-Now, we are ready to compute the *Mean Squared Errors (MSEs)* for the samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A](#appndx_a)).
+Now, we are ready to compute the *Mean Squared Errors (MSEs)* for the samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function described in the [Common Helper Functions]/[Utility Functions] section of [Appendix A](#appndx_a)).
 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the user-defined function [mse](#func.mse) described in the [Common Helper Functions]/[(Root) Mean Squared Error Calculation] section of [Appendix A](#appndx_a).
+In the code snippet above, we also use the user-defined function [mse](#func.mse) described in the [Common Helper Functions]/[(Root) Mean Squared Error Calculation] section of [Appendix A](#appndx_a).
 :::

### 2025-12-26 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report sections review: the model tuning & regularization.

@@
 
-We can now construct predictors and see how much the `RMSE` improves[@IDS2_24-1_ME].
+We can now construct predictors and see how much the *RMSE* score improves[@IDS2_24-1_ME].
 
@@
 
-Now, let's visualize the results of the $\lambda$ range pre-configuration:
+Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L596):
 ``` {r  main-script@l}

### 2025-12-26 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Minor fix for `UMGYDE Model`.

@@
 
-Now, let's construct predictors and calculate the *RMSE* score for the *current model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1195):
-```{r main-script@l1195, eval=FALSE}
+Now, let's construct predictors and calculate the *RMSE* score for the *current model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1531):
+```{r main-script@l1531, eval=FALSE}
 cv.UMGYDE.default_params.RMSE <- cv.UMGYDE.default_params |>

### 2025-12-26 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Minor fix for `UMGYDE Model`: Duplicate chunk label 'main-script@l1199'.

@@
 
-Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1199):
-```{r main-script@l1199, eval=FALSE}
+Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1542):
+```{r main-script@l1542, eval=FALSE}
 RMSEs.ResultTibble.UMGYDE <- RMSEs.ResultTibble.rglr.UMGYE |> 

### 2025-12-26 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report section review: UME Model Regularization.

@@
 Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L596):
-``` {r  main-script@l}
+``` {r  main-script@l596}
 cv.UME.preset.result$tuned.result |>
@@
 The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L608) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
-```{r, eval=FALSE}
+```{r  main-script@l608, eval=FALSE}
 endpoints <- 
@@
 And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L617) below accomplishes the task of *fine-tuning* the model:
-```{r, eval=FALSE}
+```{r  main-script@l617, eval=FALSE}
 UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"
@@
 
-Let's visualize the fine-tuning results:
-```{r}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L636) provides a visual representation of the *fine-tuning results* we have just computed:
+```{r  main-script@l636}
 UME.rglr.fine_tune.results$tuned.result |>
@@
 
-#### UME Model Regularization: *Retraining the Model with the best* $\lambda$
+#### UME Model Regularization: *Re-training on the `edx` with the best* $\lambda$
 \
@@
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L664) performs this operation:
-```{r, eval=FALSE}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L664) performs this operation:
+```{r  main-script@l664, eval=FALSE}
 best_result <- UME.rglr.fine_tune.results$best_result
@@
 
-Finally, we calculate the *RMSE* for the ultimately *Regularized UME Model* and add the definitive result to our _Result Table_:
-```{r, eval=FALSE}
+Now, we are ready to construct predictors and calculate the *RMSE* score for the ultimately *Regularized UME Model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L712):
+```{r  main-script@l712, eval=FALSE}
 UME.rglr.retrain.RMSE <- calc_user_movie_effect_RMSE.cv(rglr.UM_effect)
@@
 ```
-```{r, eval=FALSE}
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
+Finally, we add the definitive *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L720):
+```{r  main-script@l720, eval=FALSE}
 RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
-
-  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the [Models Training: Support Functions]/[UME Model: Utility Functions] section) to calculate the *RMSE* for the *UME Model*;
-
-  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
+In the code snippet above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
 :::

### 2025-12-27 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report section review: UMGE Model Regularization.

@@
 
-Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L596):
+Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L596):
 ``` {r  main-script@l596}
@@
 
+\newpage
+
 Now, we are ready to construct predictors and calculate the *RMSE* score for the ultimately *Regularized UME Model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L712):

### 2025-12-27 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report section review: UMGE Model Regularization.

@@
 
-The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L925) plots a histogram that provides a visual representation of the variability of the *UM Effect* across movies in the *data frame object* we have just obtained:
+\newpage
+
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L925) plots a histogram that provides a visual representation of the variability of the *UMG Effect* across movies in the *data frame object* we have just obtained:
 ```{r  main-script@l925}
@@
 The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L978) performs this operation:
-```{r, eval=FALSE}
+```{r main-script@l978, eval=FALSE}
 lambdas <- seq(0, 0.2, 0.01)
@@
 
-::: {.noteblock data-latex=""}
-The custom functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) used in the code snippet above are described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) and  [Models Training: Support Functions]/[UMGE Model: Regularization] of [Appendix A: Support Functions], respectively.
-:::
+\newpage
 
-Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1004):
-``` {r}
+Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1004):
+``` {r main-script@l1004}
 cv.UMGE.preset.result$tuned.result |>
@@
 The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1020) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
-```{r, eval=FALSE}
+```{r main-script@l1020, eval=FALSE}
 endpoints <- 
@@
 And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1029) below accomplishes the task of *fine-tuning* the model:
-```{r, eval=FALSE}
+```{r main-script@l1029, eval=FALSE}
 UMGE.rglr.fine_tune.cache.base_name <- "UMGE.rglr.fine-tuning"
@@
 
-Let's visualize the fine-tuning results:
-```{r}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1048) provides a visual representation of the *fine-tuning results* we have just computed:
+```{r main-script@l1048}
 UMGE.rglr.fine_tune.results$tuned.result |>
@@
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1076) performs this operation:
-```{r, eval=FALSE}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1076) performs this operation:
+```{r  main-script@l1076, eval=FALSE}
 best_result <- UMGE.rglr.fine_tune.results$best_result
@@
 
-Finally, we calculate the *RMSE* for the ultimately *Regularized UMGE Model* and add the definitive result to our _Result Table_:
-```{r, eval=FALSE}
+\newpage
+
+Now, we are ready to construct predictors and calculate the *RMSE* score for the ultimately *Regularized UMGE Model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1087):
+```{r  main-script@l1087, eval=FALSE}
   rglr.UMG_effect.RMSE <- calc_user_movie_genre_effect_RMSE.cv(rglr.UMG_effect)
@@
 ```
-```{r, eval=FALSE}
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) function described in the [Models Training: Support Functions]/[UMGE Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
+Finally, we add the definitive *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1114):
+```{r  main-script@l1114, eval=FALSE}
 RMSEs.ResultTibble.rglr.UMGE <- RMSEs.ResultTibble.UMGE |> 
@@
 As we can see, the current model still does not show much improvement after _regularization_, even though the data analysis we made in the [Movie Genres Effect] section showed strong evidence of a genre effect.
-It looks like we need a better model to account for a genre effect more efficiently.
 
-Or, maybe, we have implemented the current model not quite correctly (?)
+Apparently, we need a better model to account for a genre effect more efficiently.
 

### 2025-12-28 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report section review & fix: User+Movie+Genre+Year Effect (UMGYE) Model.

@@
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L978) performs this operation:
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L978) performs this operation:
 ```{r main-script@l978, eval=FALSE}
@@
 
-The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1020) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1020) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
 ```{r main-script@l1020, eval=FALSE}
@@
 
-And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1029) below accomplishes the task of *fine-tuning* the model:
+And the next [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1029) below accomplishes the task of *fine-tuning* the model:
 ```{r main-script@l1029, eval=FALSE}

### 2025-12-28 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report section review & fix: User+Movie+Genre+Year Effect (UMGYE) Model.

@@
 
+\newpage
+
 Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1199):
@@
 
-And the formula \@ref(eq:GE-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:
+And the formula \@ref(eq:GE-regularized) for calculating the values of the _treatment effect_ that minimizes the equation, for the current model, takes the form:
 
@@
 
-As for previous models, we will use the function [tune.model_param](#func.tune.model_param) passing in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument the model-specific helper function (this time designed for the *UMGYE Model*): [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv).
+As for the previous models, we will use the function [tune.model_param](#func.tune.model_param) passing in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument the model-specific helper function (this time designed for the *UMGYE Model*): [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv).
 
@@
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1241) performs this operation:
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1241) performs this operation:
 ```{r main-script@l1241, eval=FALSE}
@@
 
+\newpage
+
 Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1270):
-``` {r}
+``` {r main-script@l1270}
 cv.UMGYE.preset.result$tuned.result |>
@@
 
-The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1282) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
-```{r, eval=FALSE}
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1282) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
+```{r main-script@l1282, eval=FALSE}
 endpoints <- 
@@
 
-And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1291) below accomplishes the task of *fine-tuning* the model:
-```{r, eval=FALSE}
+And the next [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1291) below accomplishes the task of *fine-tuning* the model:
+```{r main-script@l1291, eval=FALSE}
 cache.base_name <- "UMGYE.rglr.fine-tuning"
@@
 
-Let's visualize the fine-tuning results:
-```{r}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1306) provides a visual representation of the *fine-tuning results* we have just computed:
+```{r main-script@l1306}
 UMGYE.rglr.fine_tune.results$tuned.result |>
@@
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1333) performs this operation:
-```{r, eval=FALSE}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1333) performs this operation:
+```{r main-script@l1333, eval=FALSE}
 best_result <- UMGYE.rglr.fine_tune.results$best_result
@@
 
-Finally, we calculate the *RMSE* for the ultimately *Regularized UMGYE Model* and add the definitive result to our *Result Table*:
-```{r, eval=FALSE}
+\newpage
+
+Now, we are ready to construct predictors and calculate the *RMSE* score for the ultimately *Regularized UMGYE Model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1341):
+```{r main-script@l1341, eval=FALSE}
   rglr.UMGY_effect.RMSE <- calc_UMGY_effect_RMSE.cv(rglr.UMGY_effect)
@@
 ```
-```{r, eval=FALSE}
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described in the [Models Training: Support Functions]/[UMGYE Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
+Finally, we add the definitive *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1366):
+```{r main-script@l1366, eval=FALSE}
 RMSEs.ResultTibble.rglr.UMGYE <- RMSEs.ResultTibble.UMGYE |> 
@@
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
-
-  - [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) (described in the [Models Training: Support Functions]/[UMGYE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGYE Model*;
-
-  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section) to update and print the table above.
+In the code snippet above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
 :::

### 2025-12-28 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report section review: UME Model Regularization.
Report section review: User+Movie+Genre+Year+Day Effect (UMGYDE) Model.

@@
 
-If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@ref(eq:UMGYE-model) describing the _UMGYDE Model_, for the current model, takes the form:
+If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@ref(eq:UMGYE-model) describing the _UMGYE Model_, for the current model, takes the form:
 
@@
 
-We are going to use the helper function ([train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described in section [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A: Support Functions]) specifically designed to train the *UMGYDE Model*, which under the hood calls the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `R` function, passing its `degree` and `span` parameters values taken from the caller's [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) arguments, respectively.
+We are going to use the helper function ([train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described in section [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A: Support Functions]) specifically designed to train the *UMGYDE Model*, which under the hood implicitly calls the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `R` function, passing its `degree` and `span` parameters values taken from the caller's [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) arguments, respectively.
 
@@
 
+\newpage
+
 #### UMGYDE Model Tuning: Stage 1 (`degree = 0`)
@@
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1578) determines the optimal range of `span` for the further model tuning when `degree = 0`:
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1578) determines the optimal range of `span` for the further model tuning when `degree = 0`:
 ```{r main-script@l1578, eval=FALSE}
@@
 ```
-```{r}
-str(lss.UMGYDE.preset.degree0.result)
-```
 
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+In the code snippet above, we use the following functions described in [Appendix A](#appndx_a):
 
@@
 :::
+
+```{r}
+str(lss.UMGYDE.preset.degree0.result)
+```
 
@@
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1625) performs the *fine-tuning* of the *UMGYDE Model* by precise selection of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter with the `degree` parameter set to $0$:
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1625) performs the *fine-tuning* of the *UMGYDE Model* by precise selection of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `span` parameter with the `degree` parameter set to $0$:
 ```{r main-script@l1625, eval=FALSE}
@@
 ```
-```{r}
-lss.fine_tune.loop_starter
-str(lss.UMGYDE.fine_tune.degree0.result)
-```
 
@@
 :::
+
+```{r}
+lss.fine_tune.loop_starter
+str(lss.UMGYDE.fine_tune.degree0.result)
+```
 
@@
 ```
-```{r}
-str(lss.UMGYDE.preset.degree1.result)
-```
 
@@
 :::
+
+```{r}
+str(lss.UMGYDE.preset.degree1.result)
+```
 
@@
 ```
-```{r}
-lss.fine_tune.loop_starter
-str(lss.UMGYDE.fine_tune.degree1.result)
-```
 
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+In the code snippet above, we use the following functions described in [Appendix A](#appndx_a):
 
@@
 :::
+
+```{r}
+lss.fine_tune.loop_starter
+str(lss.UMGYDE.fine_tune.degree1.result)
+```
 
@@
 ```
-```{r}
-str(lss.UMGYDE.preset.degree2.result)
-```
 
 ::: {.noteblock data-latex=""}
-In the code snippet above, we use the following functions described in [Appendix A: Support Functions]:
+In the code snippet above, we use the following functions described in [Appendix A](#appndx_a):
 
@@
 :::
+
+```{r}
+str(lss.UMGYDE.preset.degree2.result)
+```
 
@@
 ```
-```{r}
-lss.fine_tune.loop_starter
-str(lss.UMGYDE.fine_tune.degree2.result)
-```
 
@@
 :::
+
+```{r}
+lss.fine_tune.loop_starter
+str(lss.UMGYDE.fine_tune.degree2.result)
+```
 
@@
 
-#### UMGYDE Model Tuning: Re-training with the Best `degree` & `span` Parameters
+#### UMGYDE Model Tuning: Re-training on the `edx` with the Best Params
 \
@@
 
-Now, we can refine our *User+Movie+Genre+Year+SmoothedDay Effect Model* by retraining on the entire `edx` dataset with the best values of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters `degree` and `span` we just figured out (let's call it *Tuned UMGYDE Best Model*), for the definitive _RMSE_ calculation and use in subsequent models:
+Now, we can refine the current model by retraining on the entire `edx` dataset with the best values of the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) parameters `degree` and `span` we just figured out (let's call it *Tuned UMGYDE Best Model*), for the definitive _RMSE_ calculation and use in subsequent models:
 
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above we use the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
+\newpage
+
 ```{r}
@@
 ```
-
-::: {.noteblock data-latex=""}
-In the code snippet above we use the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
-:::
 
@@
 
+\newpage
+
 Now, we are ready to construct predictors and calculate the *RMSE* score for the ultimately *Tuned UMGYDE Best Model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2007):
@@
 
-Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2024):
+Finally, we add the *RMSE* value obtained above for the fully tuned model (let's call it *Tuned UMGYDE Best Model*) to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2024):
 ```{r main-script@l2024, eval=FALSE}
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code provided in this section can be found in the [UMGYDE Model Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1239) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1239) script.
+The complete version of the source code provided in this section can be found in the [UMGYDE Model Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2039) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2039) script.
 :::
@@
 
-Next, we will implement the *UME Model Regularization* in the following three steps:
+Next, we will implement the *UMGYDE Model Regularization* in the following three steps:
 
@@
 The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2070) performs this operation:
-```{r, eval=FALSE}
+```{r main-script@l, eval=FALSE}
   lambdas <- seq(0, 256, 16)
@@
 
-Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2098):
-``` {r}
+\newpage
+
+Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2098):
+``` {r main-script@l2098}
 cv.UMGYDE.preset.result$tuned.result |>
@@
 
-The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2110) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
-```{r, eval=FALSE}
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2110) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
+```{r main-script@l2110, eval=FALSE}
 endpoints <- 
@@
 ```
+
+::: {.noteblock data-latex=""}
+The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
+:::
+
 ```{r, echo=FALSE}
@@
 
-::: {.noteblock data-latex=""}
-The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections [Common Helper Functions]/[Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) of [Appendix A: Support Functions].
-:::
-
-And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2120) below accomplishes the task of *fine-tuning* the model:
-```{r, eval=FALSE}
+And the next [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2120) below accomplishes the task of *fine-tuning* the model:
+```{r main-script@l2120, eval=FALSE}
 cache.base_name <- "UMGYDE.rglr.fine-tuning"
@@
 ```
+
 \newpage
 
-Let's visualize the fine-tuning results:
-```{r}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2135) provides a visual representation of the *fine-tuning results* we have just computed:
+```{r main-script@l2135}
 UMGYDE.rglr.fine_tune.results$tuned.result |>
@@
 
-Now, we can refine our *User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model* by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie+Genre+Year+SmoothedDay Effect Model* or *Regularized UMGYDE Model* for short), for the definitive *RMSE* calculation and use in subsequent models:
+Now, we can refine the *UMGYDE Model* by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized UMGYDE Model*), for the definitive *RMSE* calculation and use in subsequent models:
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2161) performs this operation:
-```{r, eval=FALSE}
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2161) performs this operation:
+```{r main-script@l2161, eval=FALSE}
 best_result <- UMGYDE.rglr.fine_tune.results$best_result
@@
 
-We calculate the _Root Mean Squared Error_ for the ultimately computed _Regularized UMGYDE Effect_ using the helper function [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above in the [UMGYDE Model: Helper Functions] section as follows:
-```{r, eval=FALSE}
+\newpage
+
+Now, we are ready to construct predictors and calculate the *RMSE* score for the ultimately *Regularized UMGYE Model* using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2172):
+```{r main-script@l2172, eval=FALSE}
   rglr.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(rglr.UMGYD_effect)
@@
 
-As always, we add the definitive result for the current model to our _Result Table_:
-```{r, eval=FALSE}
+::: {.noteblock data-latex=""}
+In the code snippets above, we use the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) user-defined described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
+Finally, we add the definitive *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2218):
+```{r main-script@l2218, eval=FALSE}
 RMSEs.ResultTibble.UMGYDE.rglr.tuned <- RMSEs.ResultTibble.UMGYDE.tuned |> 
@@
 ::: {.noteblock data-latex=""}
-Now, we have a better result than the ones for the previous models, but still insufficient to meet the Project Objective. Let's see what else we can do to achieve our ultimate goal. 
+In the code snippet above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
 :::
+
+Now, we have a better result than the ones for the previous models, but still insufficient to meet the Project Objective. 
+Despite this, let's conduct our very first *final holdout test* to see what we have actually achieved so far.
 
@@
 ::: {.noteblock data-latex=""}
-The complete version of the source code shown in this section is available in the [UMGYDE Model: Final Holdout Test](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2498) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2498) script on _GitHub_.
+The complete version of the source code shown in this section is available in the [UMGYDE Model: Final Holdout Test (Preliminary Assessment)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2230) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2230) script on _GitHub_.
 :::
@@
 Let's see what we have achieved so far, using the `final_holdout_test` dataset for the first time.
-Firstly, we compute predictions for our current model:
-```{r, eval=FALSE}
+
+First, we compute predictions for our current model using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2232):
+```{r main-script@l2232, eval=FALSE}
 final.UMGYDE.predicted <- final_holdout_test |>
@@
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippet above we use the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
 ```{r}
@@
 ```
+
+Then we compute the *RMSE* score using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2258):
+```{r main-script@l2258, eval=FALSE}
+final.UMGYDE.predicted.RMSE <- rmse2(final_holdout_test$rating,
+                                     final.UMGYDE.predicted$predicted)
+```
+
 ::: {.noteblock data-latex=""}
-Here we use the helper function [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) described above in the [UMGYDE Model: Helper Functions] section.
+In the code snippet above, we use the [rmse2](#func.rmse2) user-defined function described in the [Common Helper Functions]/[(Root) Mean Squared Error Calculation] section of [Appendix A](#appndx_a).
 :::
 
-Then we compute the _RMSE_ and add the result to our _Result Table_:
-```{r, eval=FALSE}
-final.UMGYDE.predicted.RMSE <- rmse2(final_holdout_test$rating,
-                                     final.UMGYDE.predicted$predicted)
-
+Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2264):
+```{r main-script@l2264, eval=FALSE}
 final.RMSEs.ResultTibble.UMGYDE.rglr.tuned <- RMSEs.ResultTibble.UMGYDE.rglr.tuned |> 
@@
 ```
-
-::: {.noteblock data-latex=""}
-Here we use the helper function [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) to calculate the _RMSE_ that is defined in the  [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L18) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) script on _GitHub_.
-:::
-
-And finally, we print out the results:
 ```{r}
@@
 ::: {.noteblock data-latex=""}
-As expected, we have not yet achieved a result that meets our Project Objective.
+In the code snippet above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
 :::
+
+As expected, we have not yet achieved a result that meets our Project Objective. Let's see what else we can do to achieve our ultimate goal.
 

### 2025-12-28 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@
 
-The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L571) performs this operation:
+The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L571) performs this operation:
 ```{r main-script@l571, eval=FALSE}
@@
 
-The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L608) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
+The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L608) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
 ```{r main-script@l608, eval=FALSE}
@@
 
-And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L617) below accomplishes the task of *fine-tuning* the model:
+And the next [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L617) below accomplishes the task of *fine-tuning* the model:
 ```{r main-script@l617, eval=FALSE}

### 2025-12-30 reports/capstone-movielens.site/work/draft-snippert.Rmd
Report section review (completed): UMGYDE Model: Matrix Factorization (MF).

@@
 :::
+### MF: Helper Functions
+
+#### [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) Function {#func.mf.residual.dataframe}
+\
+
+::: { #func.mf.residual.dataframe.args.description .sidebar }
+##### Description
+\
+
+Computes residuals, defined as the difference between the observed and predicted values of the fully trained _UMGYDE Model_ as described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section.
+
+##### Arguments
+\
+
+###### ***train_set***
+\
+
+::: { #func.mf.residual.dataframe.args.train_set .sidebar }
+The dataset to be trained.
+:::
+
+##### Source Code
+\
+
+The folowing is the source code of the function:
+```{r eval=FALSE}
+mf.residual.dataframe <- function(train_set){
+  train_set |> 
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(rglr.UMGY_effect, by='year') |>
+    left_join(rglr.UMGYD_effect, by='days') |>
+    mutate(rsdl = rating - (mu + a + b + g + ye + de_smoothed)) |>
+    select(userId, movieId, rsdl)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) script on _GitHub_.
+:::
+
+##### Return
+\
+
+A data frame object containing the residuals (see the [Description](#func.mf.residual.dataframe.args.description) above for the details).
+
+\newpage
+
+#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) Function {#func.UMGYDE_model.predict}
+\
+
+This is a wrapper for the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [UMGYDE Model: Helper Functions] section above with the fixed [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) parameter value obtained after the _UMGYDE Model_ (described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section)  has been fully trained.
+
+##### Arguments
+\
+
+::: { #func.UMGYDE_model.predict.args.test_set .sidebar }
+###### ***test_set***
+\
+
+The dataset for testing the _UMGYDE Model_ after it has been fully trained.
+:::
+
+##### Source Code
+\
+
+The following is the source code of the function:
+```{r eval=FALSE}
+UMGYDE_model.predict <- function(test_set) {
+  test_set |>
+    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) script on _GitHub_.
+:::
+
+##### Return
+\
+
+A data frame object containing predicted values.
+
+\newpage
 
@@
 \
+
+### MF: Helper Functions
+
+#### [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) Function {#func.mf.residual.dataframe}
+\
+
+::: { #func.mf.residual.dataframe.args.description .sidebar }
+##### Description
+\
+
+Computes residuals, defined as the difference between the observed and predicted values of the fully trained _UMGYDE Model_ as described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section.
+
+##### Arguments
+\
+
+###### ***train_set***
+\
+
+::: { #func.mf.residual.dataframe.args.train_set .sidebar }
+The dataset to be trained.
+:::
+
+##### Source Code
+\
+
+The folowing is the source code of the function:
+```{r eval=FALSE}
+mf.residual.dataframe <- function(train_set){
+  train_set |> 
+    left_join(edx.user_effect, by = "userId") |>
+    left_join(rglr.UM_effect, by = "movieId") |>
+    left_join(rglr.UMG_effect, by = "movieId") |>
+    left_join(date_days_map, by = "timestamp") |>
+    left_join(rglr.UMGY_effect, by='year') |>
+    left_join(rglr.UMGYD_effect, by='days') |>
+    mutate(rsdl = rating - (mu + a + b + g + ye + de_smoothed)) |>
+    select(userId, movieId, rsdl)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) script on _GitHub_.
+:::
+
+##### Return
+\
+
+A data frame object containing the residuals (see the [Description](#func.mf.residual.dataframe.args.description) above for the details).
+
+\newpage
+
+#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) Function {#func.UMGYDE_model.predict}
+\
+
+This is a wrapper for the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [UMGYDE Model: Helper Functions] section above with the fixed [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) parameter value obtained after the _UMGYDE Model_ (described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section)  has been fully trained.
+
+##### Arguments
+\
+
+::: { #func.UMGYDE_model.predict.args.test_set .sidebar }
+###### ***test_set***
+\
+
+The dataset for testing the _UMGYDE Model_ after it has been fully trained.
+:::
+
+##### Source Code
+\
+
+The following is the source code of the function:
+```{r eval=FALSE}
+UMGYDE_model.predict <- function(test_set) {
+  test_set |>
+    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) script on _GitHub_.
+:::
+
+##### Return
+\
+
+A data frame object containing predicted values.
+
+\newpage

### 2025-12-30 reports/capstone-movielens.site/work/func-descr.template.Rmd
Report section review (completed): UMGYDE Model: Matrix Factorization (MF).

@@
 
+#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) Function {#func.UMGYDE_model.predict}
+\
+
+::: { #func.UMGYDE_model.predict.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.UMGYDE_model.predict.args .sidebar }
+##### Arguments
+\
+
+::: { #func.UMGYDE_model.predict.args.file_name .sidebar }
+  - **test_set:** ;
+
+:::
+:::
+
+::: { #func.UMGYDE_model.predict.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.UMGYDE_model.predict.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.UMGYDE_model.predict.code .sidebar }
+##### Source Code
+\
+
+The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is shown below:
+```{r eval=FALSE}
+UMGYDE_model.predict <- function(test_set) {
+  test_set |>
+    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) script on _GitHub_.
+:::
+:::
+
 ## General Func Tempates -------------------------------------------------------

### 2025-12-30 reports/capstone-movielens.site/work/tmp/func_tmp.Rmd
Report section review (completed): UMGYDE Model: Matrix Factorization (MF).

@@
 \newpage
+
+#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) Function {#func.UMGYDE_model.predict}
+\
+
+::: { #func.UMGYDE_model.predict.usage .sidebar }
+##### Usage
+\
+
+```{r eval=FALSE}
+
+```
+:::
+
+::: { #func.UMGYDE_model.predict.args .sidebar }
+##### Arguments
+\
+
+::: { #func.UMGYDE_model.predict.args.file_name .sidebar }
+  - **test_set:** ;
+
+:::
+:::
+
+::: { #func.UMGYDE_model.predict.details .sidebar }
+##### Details
+\
+
+:::
+
+::: { #func.UMGYDE_model.predict.value .sidebar }
+##### Value
+\
+
+:::
+
+::: { #func.UMGYDE_model.predict.code .sidebar }
+##### Source Code
+\
+
+The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is shown below:
+```{r eval=FALSE}
+UMGYDE_model.predict <- function(test_set) {
+  test_set |>
+    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
+}
+```
+
+::: {.noteblock data-latex=""}
+The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) script on _GitHub_.
+:::
+:::

### 2025-12-30 reports/capstone-movielens.site/05.appendix.Rmd

@@
 
-### Matrix Factorization Functions
+### UMGYDE Model: Matrix Factorization
 \
@@
 
+Computes residuals, defined as the difference between the observed and predicted values of the fully trained _UMGYDE Model_ as described in the [User+Movie+Genre+Year+SmoothedDay Effect (UMGYDE) Model] section.
+
 ::: { #func.mf.residual.dataframe.usage .sidebar }
@@
 ```{r eval=FALSE}
-
+  mf.edx.residual <- mf.residual.dataframe(edx)
 ```
@@
 
-::: { #func.mf.residual.dataframe.args.file_name .sidebar }
-  - **train_set:** ;
+::: { #func.mf.residual.dataframe.args.train_set .sidebar }
+  - **train_set:** Training dataset;
 
@@
 
+This function calculates the residuals on the *training dataset* passed as the [train_set](#func.mf.residual.dataframe.args.train_set) argument, taking into account all the effects of the previously trained models, and creates a new data frame that includes the results as a calculated column `rsdsl`, along with the `movieId` and `userId` columns selected from the training dataset.
 :::
@@
 \
+
+Data frame containing the following three variables:
+
+  - *rsdl*: (Numeric)Calculated column containing results of the function computation;
+
+  - *userId*: (Integer) User Identifier;
+
+  - *movieId* (Integer) Movie Identifier.
 
@@
 ::: {.noteblock data-latex=""}
-The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) script on _GitHub_.
-:::
-:::
-
-#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) Function {#func.UMGYDE_model.predict}
-\
-
-::: { #func.UMGYDE_model.predict.usage .sidebar }
-##### Usage
-\
-
-```{r eval=FALSE}
-
-```
-:::
-
-::: { #func.UMGYDE_model.predict.args .sidebar }
-##### Arguments
-\
-
-::: { #func.UMGYDE_model.predict.args.file_name .sidebar }
-  - **test_set:** ;
-
-:::
-:::
-
-::: { #func.UMGYDE_model.predict.details .sidebar }
-##### Details
-\
-
-:::
-
-::: { #func.UMGYDE_model.predict.value .sidebar }
-##### Value
-\
-
-:::
-
-::: { #func.UMGYDE_model.predict.code .sidebar }
-##### Source Code
-\
-
-The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is shown below:
-```{r eval=FALSE}
-UMGYDE_model.predict <- function(test_set) {
-  test_set |>
-    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
-}
-```
-
-::: {.noteblock data-latex=""}
-The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) function is defined in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L14) script on _GitHub_.
+The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L3) script on _GitHub_.
 :::

### 2025-12-30 reports/capstone-movielens.site/bak/02.8-1.MF.UMGYDE-model.bak2.Rmd

--- 2025-09-28 reports/capstone-movielens.site/02.8-1.MF.UMGYDE-model.Rmd
@@
 \
+
+::: {.noteblock data-latex=""}
+The complete source code shown in this section is available in the [Matrix Factorization (MF)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2276) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2276) script on _GitHub_.
+:::
 
@@
 
-### MF: Performing Operation
+### MF: Model Building
 
 ::: {.noteblock data-latex=""}
-The complete source code shown in this section is available in the [Perform the Matrix Factorization & Final Test](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2567) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2567) script on _GitHub_.
+The complete source code shown in this section is available in the [Perform the Matrix Factorization & Final Test](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2299) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2299) script on _GitHub_.
 :::
 
-We assume that the _Matrix Factorization_ method is going to be the last one to provide sufficient results, so we will use the entire `edx` dataset as a _Training Set_ and `final_holdout_test` as a _Test Set_ for our final model, skipping the intermediate _train/test_ operations on the split _train/validation_ datasets.
+We assume that the _Matrix Factorization_ method will be the last one to provide sufficient results, so we will use the entire `edx` dataset as the _Training Set_ and `final_holdout_test` as the _Test Set_ for our final model, skipping the intermediate *training/validation split operations* that were performed for the previous models.
 
@@
 
-First, we get residuals from the _UMGYDE Model_ prediction values using the [mf.residual.dataframe](#func.mf.residual.dataframe) function described above:
-```{r, eval=FALSE}
+First, we will obtain residuals from the _UMGYDE Model_ prediction values using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2314):
+```{r main-script@l2314, eval=FALSE}
   mf.edx.residual <- mf.residual.dataframe(edx)
 ```
+
+::: {.noteblock data-latex=""}
+In the code snippets above, we use the [mf.residual.dataframe](#func.mf.residual.dataframe) user-defined described in the [Models Training: Support Functions]/[UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a).
+:::
+
 ```{r}
@@
 ```
+
 #### MF: Transforming Input Data to Be Compatible With the `recosystem` Package
@@
 
-Now, let's convert the residuals data and `final_holdout_test` dataset to the input data compatible with the [recosystem](https://cran.r-project.org/web/packages/recosystem/index.html) package to process:
-```{r, eval=FALSE}
+Next, we convert the residuals data and `final_holdout_test` dataset to the input data compatible with the [recosystem](https://cran.r-project.org/web/packages/recosystem/index.html) package using the following [conde snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2319):
+```{r main-script@l2319, eval=FALSE}
   set.seed(5430)

### 2025-12-30 reports/capstone-movielens.site/02.8-1.MF.UMGYDE-model.Rmd
Minor fixes.

--- 2025-06-04 reports/capstone-movielens.site/02.8-1.MF.UMGYDE-model.Rmd
@@
 
-### MF: Helper Functions
+### MF: Model Building
 
-#### [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) Function {#func.mf.residual.dataframe}
+::: {.noteblock data-latex=""}
+The complete source code shown in this section is available in the [Perform the Matrix Factorization & Final Test](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2299) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2299) script on _GitHub_.
+:::
+
+We assume that the _Matrix Factorization_ method will be the last one to provide sufficient results, so we will use the entire `edx` dataset as the _Training Set_ and `final_holdout_test` as the _Test Set_ for our final model, skipping the intermediate *training/validation split operations* that were performed for the previous models.
+
+#### MF: Getting Residuals From the UMGYDE Model Prediction Values
 \
 
-::: { #func.mf.residual.dataframe.params.description .sidebar }
-##### Description
-\
-
-Computes residuals, defined as the difference between the observed and predicted values of the fully trained _UMGYDE Model_ as described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section.
-
-##### Parameters
-\
-
-###### ***train_set***
-\
-
-::: { #func.mf.residual.dataframe.params.train_set .sidebar }
-The dataset to be trained.
-:::
-
-##### Source Code
-\
-
-The folowing is the source code of the function:
-```{r eval=FALSE}
-mf.residual.dataframe <- function(train_set){
-  train_set |> 
-    left_join(edx.user_effect, by = "userId") |>
-    left_join(rglr.UM_effect, by = "movieId") |>
-    left_join(rglr.UMG_effect, by = "movieId") |>
-    left_join(date_days_map, by = "timestamp") |>
-    left_join(rglr.UMGY_effect, by='year') |>
-    left_join(rglr.UMGYD_effect, by='days') |>
-    mutate(rsdl = rating - (mu + a + b + g + ye + de_smoothed)) |>
-    select(userId, movieId, rsdl)
-}
+First, we will obtain residuals from the _UMGYDE Model_ prediction values using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2314):
+```{r main-script@l2314, eval=FALSE}
+  mf.edx.residual <- mf.residual.dataframe(edx)
 ```
@@
 ::: {.noteblock data-latex=""}
-The source code of the [mf.residual.dataframe](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functions.R#L1) script on _GitHub_.
+In the code snippets above, we use the [mf.residual.dataframe](#func.mf.residual.dataframe) user-defined described in the [Models Training: Support Functions]/[UMGYDE Model: Matrix Factorization] section of [Appendix A](#appndx_a).
 :::
 
-##### Return
+```{r}
+  str(mf.edx.residual)
+```
+
+#### MF: Transforming Input Data to Be Compatible With the `recosystem` Package
 \
 
-A data frame object containing the residuals (see the [Description](#func.mf.residual.dataframe.params.description) above for the details).
+Next, we convert the residuals data and `final_holdout_test` dataset to the input data objects compatible with the [recosystem](https://cran.r-project.org/web/packages/recosystem/index.html) package using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2319):
+```{r main-script@l2319, eval=FALSE}
+  set.seed(5430)
+  mf.edx.residual.reco <- with(mf.edx.residual, 
+                               data_memory(user_index = userId, 
+                                           item_index = movieId,
+                                           rating = rsdl))
 
-#### [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) Function {#func.UMGYDE_model.predict}
+  final_holdout_test.reco <- with(final_holdout_test, 
+                          data_memory(user_index = userId, 
+                                      item_index = movieId, 
+                                      rating = rating))
+```
+```{r}
+str(mf.edx.residual.reco)
+str(final_holdout_test.reco)
+```
+
+#### MF: Creating and Tuning the `Reco` Object
 \
 
-This is a wrapper for the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [UMGYDE Model: Helper Functions] section above with the fixed [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect) parameter value obtained after the _UMGYDE Model_ (described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section)  has been fully trained.
+Now we can create a `reco` object of the `Reco` class and tune it using the `reco$tune` method, passing the residual data prepared in the previous step in the `train_data` argument using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2332):
+```{r main-script@l2332, eval=FALSE}
+  reco <- Reco()
 
-##### Parameters
+  reco.tuned <- reco$tune(mf.edx.residual.reco, opts = list(dim = c(10, 20, 30),
+                                                lrate    = c(0.1, 0.2),
+                                                nthread  = 4,
+                                                niter    = 10,
+                                                verbose  = TRUE))
+```
+```{r}
+str(reco)
+str(reco.tuned)
+```
+
+#### MF: Final Training
 \
 
-::: { #func.UMGYDE_model.predict.params.test_set .sidebar }
-###### ***test_set***
+Finally, we train the model for the last time using the `reco$train` method, passing the same residual data we used for the tuning, in the train_data` argument, using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2342):
+```{r main-script@l2342, eval=FALSE}
+  reco$train(mf.edx.residual.reco, opts = c(reco.tuned$min,
+                                       niter = 20, 
+                                       nthread = 4)) 
+```
+
+#### MF: Final Holdout Test
 \
 
-The dataset for testing the _UMGYDE Model_ after it has been fully trained.
-:::
+From now on, we will work with the `final_holdout_test` dataset for the final testing of our model, including obtaining final predictions and computing the final *RMSE* score.
 
-##### Source Code
-\
+Now, let's compute the final predictions, combining the predicted residuals from the `reco` objects and predicted values we lastly get from the _UMGYDE Model_ as described in the [UMGYDE Model: Final Holdout Test (Preliminary Assessment)] section, using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2346):
+```{r main-script@l2346, eval=FALSE}
+  mf.reco.residual <- reco$predict(final_holdout_test.reco, out_memory())
 
-The following is the source code of the function:
-```{r eval=FALSE}
-UMGYDE_model.predict <- function(test_set) {
-  test_set |>
-    UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
-}
+  mf.predicted_ratings <- 
+    clamp(final.UMGYDE.predicted$predicted + mf.reco.residual)
 ```
@@
 ::: {.noteblock data-latex=""}
-The source code of the [UMGYDE_model.predict](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) function is also available in the [MF.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/MF.functionsR#L12) script on _GitHub_.
+In the code snippet above, we use the [clamp](#func.clamp) user-defined function described in the [Common Helper Functions]/[Utility Functions] section of [Appendix A](#appndx_a).
 :::
 
-##### Return
-\
+```{r}
+str(mf.reco.residual)
+str(mf.predicted_ratings)
+```
 
-A data frame object containing predicted values.
+And ultimately, we are ready to compute the  final *RMSE* score using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2374):
+```{r main-script@l2374, eval=FALSE}
+final_holdout_test.RMSE <- rmse2(final_holdout_test$rating,
+                                     mf.predicted_ratings)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the [rmse2](#func.rmse2) user-defined function described in the [Common Helper Functions]/[(Root) Mean Squared Error Calculation] section of [Appendix A](#appndx_a).
+:::
+
+Finally, we add the *RMSE* value obtained above to our *Result Table* and print the table using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2380):
+```{r main-script@l2380, eval=FALSE}
+final.MF.RMSEs.ResultTibble <- final.RMSEs.ResultTibble.UMGYDE.rglr.tuned |> 
+  RMSEs.AddRow("MF (Final Test)", 
+               final_holdout_test.RMSE,
+               comment = "Matrix Factorization of the Best Model Residuals, Final Holdout Test")
+```
+```{r}
+RMSE_kable(final.MF.RMSEs.ResultTibble)
+```
+
+::: {.noteblock data-latex=""}
+In the code snippet above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions]/[Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
+:::
+
+Eventually, we have reached our ultimate goal, as the *RMSE* we obtained has achieved the required Project Objective.
 
